### 2019-10-25 notebooks/20191025_mobility_to_sentence.rmd

---
title: "Mobility Transition Processing"
author: "Dakota Murray"
output: html_notebook
---

```{r}
library(tidyverse)

# Read the transitions file, this will take a few seconds
mobility <- readr::read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Raw/20191024_mobility_transitions.txt", delim = "\t")
```

The total number of publications represented
```{r}
dim(mobility)[1]
```

The head of the file, showing the features
```{r}
head(mobility)
```

Total number and proportion of publications by year
```{r}
t <- table(mobility$pub_year)
t
prop.table(t)
```

Select only the 6 most recent years
```{r}
mobility.2014to2019 <- mobility %>% filter(pub_year >= 2014)
```

Now, lets do the work of creating the mobility sentences
```{r}
mobility2014to2019.processed <- mobility.2014to2019 %>%
  group_by(cluster_id) %>%
  summarize(
    inst_sentence = paste(cwts_org_no, collapse = " ")
  )
```

Top rows showing these mobility sentences
```{r}
head(mobility2014to2019.processed)
```

The total number of mobility sentences
```{r}
dim(mobility2014to2019.processed)[1]
```

Save the result
```{r}
readr::write_csv(mobility2014to2019.processed, path = "/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/mobility_sentences/institution_sentences_2019to2019.csv")
```

### 2019-10-25 notebooks/20191025_visualizing_embeddings.rmd

---
title: "Visualizing Institution Mobility Vectors"
author: "Dakota Murray"
output: html_notebook
---

```{r}
library(tidyverse)
library(readr)

inst_coords <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/dim_reduced/inst_umap.csv")
colnames(inst_coords) <- c("rownum", "axis1", "axis2", "token")
inst_lookup <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/20191024_institution_lookup.txt", delim = "\t")

country_lookup <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/iso_to_country.txt", delim = "\t")
country_lookup
```

```{r}
inst_coords_details <- inst_coords %>%
  left_join(inst_lookup, by = c("token" = "cwts_org_no")) %>%
  left_join(country_lookup, by = c("country_iso_alpha" = "Alpha_code_3"))

inst_coords
inst_coords_details
```

```{r}
org_types <- unique(inst_coords_details$org_type)
org_types_simplified <- c("Univ", "Univ", "Institute", "Institute", "Other", 
                          "Other", "Other", "Other","Hospital", "Other", 
                          "Hospital", "Hospital", "Univ", "Industry")
library(plotly)
g <- inst_coords_details %>%
  filter(!is.na(Continent_name)) %>%
  mutate(
    org = plyr::mapvalues(org_type, org_types, org_types_simplified),
    org = factor(org, levels = c("Univ", "Hospital", "Industry", "Gov", "Other")),
    to_highlight = ifelse(Country_name == "Italy, Italian Republic", T, F)
  ) %>%
  ggplot(aes(x = axis1, y = axis2, color = org, shape = org, group = city, label = full_name, label2 = Country_name, label3 = org_type)) +
  geom_point(size = 0.6, alpha = 0.5, shape = 16) +
  theme_minimal() +
  guides(color = guide_legend(override.aes = list(size=5)),
         shape = guide_legend(override.aes = list(size=5))) +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")

ggsave("~/Desktop/mobility_institution_byorg.pdf", g)

ggplotly(g, tooltip = c("Continent_name", "Country_name", "city", "full_name", "org_type"))
```

```{r}
inst_coords <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/dim_reduced/inst_pca.csv")
colnames(inst_coords) <- c("ignore", "axis1", "axis2", "token")
inst_coords_details <- inst_coords %>%
  left_join(inst_lookup, by = c("token" = "cwts_org_no")) %>%
  left_join(country_lookup, by = c("country_iso_alpha" = "Alpha_code_3"))

g <- inst_coords_details %>%
  filter(!is.na(Continent_name)) %>%
  ggplot(aes(x = axis1, y = axis2, color = Continent_name, group = city, label = full_name, label2 = Country_name, label3 = org_type)) +
  geom_point(size = 0.5, alpha = 0.5) +
  theme_minimal() +
  guides(colour = guide_legend(override.aes = list(size=5))) +
  scale_color_brewer(palette = "Set2")

g
ggplotly(g, tooltip = c("Continent_name", "Country_name", "city", "full_name", "org_type"))
```

### 2019-10-28 notebooks/20191025_visualizing_embeddings.rmd
Updated the visualization notebook with new country and city-level visualizations

@@
 
-inst_coords <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/dim_reduced/inst_umap.csv")
-colnames(inst_coords) <- c("rownum", "axis1", "axis2", "token")
+inst_coords <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Figures/UMAP/data/org_2014-2019_umap_data.csv")
+
 inst_lookup <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/20191024_institution_lookup.txt", delim = "\t") 
-
 country_lookup <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/iso_to_country.txt", delim = "\t")
@@
     org = plyr::mapvalues(org_type, org_types, org_types_simplified),
-    org = factor(org, levels = c("Univ", "Hospital", "Industry", "Gov", "Other")),
-    to_highlight = ifelse(Country_name == "Italy, Italian Republic", T, F)
+    org = factor(org, levels = c("Univ", "Hospital", "Industry", "Institute", "Other")),
   ) %>%
-  ggplot(aes(x = axis1, y = axis2, color = org, shape = org, group = city, label = full_name, label2 = Country_name, label3 = org_type)) +
-  geom_point(size = 0.6, alpha = 0.5, shape = 16) +
+  ggplot(aes(x = axis1, y = axis2, color = Continent_name, shape = Continent_name, group = city, label = full_name, label2 = Country_name, label3 = org_type)) +
+  geom_point(size = 0.6, alpha = 0.8) +
   theme_minimal() +
@@
          shape = guide_legend(override.aes = list(size=5))) +
-  scale_color_brewer(palette = "Set1") +
+  scale_color_brewer(palette = "Set2") +
   theme(legend.position = "bottom")
 
-ggsave("~/Desktop/mobility_institution_byorg.pdf", g)
+#ggsave("~/Desktop/mobility_institution_bycontinent.pdf", g, width = 10, height = 8)
 
@@
 ```{r}
-inst_coords <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/dim_reduced/inst_pca.csv")
-colnames(inst_coords) <- c("ignore", "axis1", "axis2", "token")
-inst_coords_details <- inst_coords %>%
-  left_join(inst_lookup, by = c("token" = "cwts_org_no")) %>%
+city_lookup <- inst_lookup %>%
+  select(c(city_country, city, country_iso_alpha)) %>%
+  group_by(city_country) %>%
+  slice(1) %>% 
+  rowwise() %>%
+  mutate(city_country = gsub("[ ]", "_", city_country))
+
+city_lookup
+city_coords <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Figures/UMAP/data/city_2014-2019_umap_data.csv") %>%
+  left_join(city_lookup, by = c("token" = "city_country")) %>%
   left_join(country_lookup, by = c("country_iso_alpha" = "Alpha_code_3"))
 
-g <- inst_coords_details %>%
+g <- city_coords %>%
+  ggplot(aes(x = axis1, y = axis2,  label = token, color = Continent_name, label2 = Country_name)) +
+  geom_point(size = 0.8, alpha = 0.8) +
+  theme_minimal() +
+  guides(color = guide_legend(override.aes = list(size=5)),
+         shape = guide_legend(override.aes = list(size=5))) +
+  scale_color_brewer(palette = "Set2") +
+  theme(legend.position = "bottom")
+
+ggplotly(g, tooltip = c("token", "name", "Continent_name", "Country_name"))
+
+unique(city_coords$labels)
+```
+
+```{r}
+country_coords <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Figures/UMAP/data/country_2008-2013_umap_data.csv") %>%
+  left_join(country_lookup, by = c("token" = "Alpha_code_3"))
+
+g <- country_coords %>%
   filter(!is.na(Continent_name)) %>%
-  ggplot(aes(x = axis1, y = axis2, color = Continent_name, group = city, label = full_name, label2 = Country_name, label3 = org_type)) +
-  geom_point(size = 0.5, alpha = 0.5) +
+  ggplot(aes(x = axis1, y = axis2,  label = token, label2 = Country_name, color = Continent_name, shape = Continent_name)) +
+  #geom_point(size = 1.2, alpha = 0.8) +
   theme_minimal() +
-  guides(colour = guide_legend(override.aes = list(size=5))) +
-  scale_color_brewer(palette = "Set2")
+  geom_text() +
+  guides(color = guide_legend(override.aes = list(size=5)),
+         shape = guide_legend(override.aes = list(size=5))) +
+  scale_color_brewer(palette = "Set2") +
+  theme(legend.position = "bottom")
 
-g
-ggplotly(g, tooltip = c("Continent_name", "Country_name", "city", "full_name", "org_type"))
+ggplotly(g, tooltip = c("labels", "Continent_name", "Country_name"))
 ```
+
+```{r}
+country_coords <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Figures/UMAP/data/country_2014-2019_umap_data.csv") %>%
+  left_join(country_lookup, by = c("token" = "Alpha_code_3"))
+
+g <- country_coords %>%
+  filter(!is.na(Continent_name)) %>%
+  ggplot(aes(x = axis1, y = axis2,  label = token, label2 = Country_name, color = Continent_name, shape = Continent_name)) +
+  #geom_point(size = 1.2, alpha = 0.8) +
+  theme_minimal() +
+  geom_text() +
+  guides(color = guide_legend(override.aes = list(size=5)),
+         shape = guide_legend(override.aes = list(size=5))) +
+  scale_color_brewer(palette = "Set2") +
+  theme(legend.position = "bottom")
+
+ggplotly(g, tooltip = c("labels", "Continent_name", "Country_name"))
+```

### 2019-11-05 workflow/scripts/calculate_org_geo_distance.py
Bugfix: now column names are properly assigned

@@ -47,7 +47,8 @@ distance_df = pd.DataFrame(squareform(dist))
 
 # Set the row and column names
 distance_df.columns = organizations.cwts_org_no
-distance_df.rows = organizations.cwts_org_no
+distance_df['org1'] = organizations.cwts_org_no
+distance_df = distance_df.set_index('org1')
 
 # Get upper triangle
 upper_tri = distance_df.where(np.triu(np.ones(distance_df.shape)).astype(np.bool))
@@ -57,4 +58,4 @@ upper_tri = upper_tri.stack().reset_index()
 upper_tri.columns = ['org1', 'org2', 'distance']
 
 # Write to csv
-upper_tri.to_csv(args.output, index = False)
+upper_tri.to_csv(args.output)

### 2019-11-05 workflow/scripts/calculate_org_flows.py
Don't save the column label

@@ -67,4 +67,4 @@ upper_tri = upper_tri.stack().reset_index()
 upper_tri.columns = ['org1', 'org2', 'count']
 
 # Write to csv
-upper_tri.to_csv(args.output, index_label = False)
+upper_tri.to_csv(args.output, index = False)

### 2019-11-05 notebooks/20191104_institution_size_flows.rmd
Notebook experimentin with analysis and visualization

---
title: "Instituion sizes and flows"
author: "Dakota Murray"
output: html_notebook
---

```{r}
library(readr)
library(tidyverse)
sizes <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Raw/2008-2019_inst_sizes.txt", delim = "\t")
flows <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Descriptive/org/organization_flows.csv")
lookup <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/20191024_institution_lookup.txt", delim = "\t")

geographic_distance <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Descriptive/org/organization_geographic_distance.csv")
word2vec_similarities <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Descriptive/org/2014-2019_word2vec_d200_sim.csv")
```

```{r}
flows <- flows %>%
  select(-index) %>%
  filter(org1 != org2) %>%
  mutate(
    count = ifelse(count == 0, 1, count)
  )

head(flows)
```

```{r}
sizes <- sizes %>%
  group_by(cwts_org_no) %>%
  summarize(
    all_person_count = mean(person_count)
  ) %>%
  arrange(desc(all_person_count))

head(sizes)
```

```{r}
flows_all <- flows %>%
  left_join(sizes, by = c("org1" = "cwts_org_no")) %>%
  left_join(sizes, by = c("org2" = "cwts_org_no")) %>%
  rename(org1_size = all_person_count.x, org2_size = all_person_count.y) %>%
  mutate(gravity = (org1_size * org2_size) / count) %>%
  inner_join(geographic_distance) %>%
  inner_join(word2vec_similarities)

head(flows_all, 100)
```

```{r}
p1_all <- flows_all %>%
  ggplot(aes(x = log(distance), y = log(gravity))) +
  geom_hex(bins = 200) +
  theme_minimal() +
  labs(x = "Log(Kilometers distance)",
       y = "P1 * P2 / F12")

p1_all
```

```{r}
p2_all <- flows_all %>%
  ggplot(aes(x = (similarity), y = log(gravity))) +
  geom_hex(bins = 100) +
  theme_minimal() +
  labs(x = "Cosine Similarity",
       y = "Log(Kilometer Distance)")

p2_all
```

```{r}
p1_

```

```{r}
library(grid)
library(gridExtra)

```

### 2019-11-27 paper/current/main.tex

\documentclass[12pt]{article} %{{{

% Figures
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\def\figdir{figs}

% Math
\usepackage{amsmath}
\usepackage{amssymb}
\DeclareMathOperator*{\argmin}{\arg\!\min}
\DeclareMathOperator*{\argmax}{\arg\!\max}

% abbreviations
\def\etal{\emph{et~al}.\ }
\def\eg{e.g.,~}
\def\ie{i.e.,~}
\def\cf{cf.\ }
\def\viz{viz.\ }
\def\vs{vs.\ }

% Refs
\usepackage{biblatex}
\addbibresource{main.bib}

\usepackage{url}

\newcommand{\secref}[1]{Section~\ref{sec:#1}}
\newcommand{\figref}[1]{Fig.~\ref{fig:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
%\newcommand{\eqnref}[1]{\eqref{eq:#1}}
%\newcommand{\thmref}[1]{Theorem~\ref{#1}}
%\newcommand{\prgref}[1]{Program~\ref{#1}}
%\newcommand{\algref}[1]{Algorithm~\ref{#1}}
%\newcommand{\clmref}[1]{Claim~\ref{#1}}
%\newcommand{\lemref}[1]{Lemma~\ref{#1}}
%\newcommand{\ptyref}[1]{Property~\ref{#1}}

% for quick author comments 
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\definecolor{light-gray}{gray}{0.8}
\def\del#1{ {\color{light-gray}{#1}} }
\def\yy#1{ {\color{red}\textbf{yy: #1}} }

%}}}

\begin{document} %{{{

\title{An awesome paper} %{{{
\date{\today}
\maketitle %}}}

\section{Introduction}\label{sec:introduction} %{{{

%}}}

\section{Results}\label{sec:results} %{{{

Let $f_{ij}$ represents the total flux (the number of people who moved) between $i$ and $j$. 
Because we are ignoring the directions, $f_{ij} = f_{ji}$. 
The total flux from or to $i$ can be written as $\mu_{i} = \sum_k f_{ik}$. 
Then the conditional probability $p(j|i)$ is simply
\begin{equation}\label{fig:flux_conditional_prob}
p(j|i) = \frac{f_{ij}}{\mu_i}. 
\end{equation}

Let us assume that we have identified the best embedding vector $v_i$ for every institution. 
The skip-gram model maximizes the average log probability
\begin{equation}
\frac{1}{T}\sum_{t=1}^{T} \sum_{-c \le j \le c, j \neq 0} \log p(w_{t+j}|w_t),  
\end{equation}
where 
\begin{equation}
p(w_O|w_I) = \frac{\exp(v'_{w_O} \cdot v_{w_I})}{\sum_{w=1}^{W} \exp(v'_w \cdot v_w_I)}, 
\end{equation}
where $v_w$ and $v'_w$ are `input' and `output' vector representations of $w$.

The best embedding should be able to closely approximate the true conditional probability Eq.~\ref{fig:flux_conditional_prob}.  \yy{why? can we prove this?}

\begin{equation}
p(j|i) = \frac{f_{ij}}{\mu_i} \simeq \frac{\exp(v'_j \cdot v_i)}{\sum_{w=1}^{W} \exp(v'_w \cdot v_i)}
\end{equation}

%\begin{minipage}{\figwidth} 
%\includegraphics[width=\linewidth]{\figdir/img} 
%\end{minipage}

%}}}

\section{Methods}\label{sec:methods} %{{{

%}}}

\printbibliography{}

\end{document} %}}}

### 2020-01-08 notebooks/20191025_visualizing_embeddings.rmd
Miscelaneous notebooks

@@
 library(readr)
+library(plotly)
 
-inst_coords <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Figures/UMAP/data/org_2014-2019_umap_data.csv")
+inst_coords <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Figures/UMAP/USA/d200/data/2014-2019_USA_umap_d200_euclidean_neighbors20_mindist0.0_data.csv")
 
-inst_lookup <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/20191024_institution_lookup.txt", delim = "\t") 
+inst_lookup <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t") 
 country_lookup <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/iso_to_country.txt", delim = "\t")
@@
 ```{r}
-org_types <- unique(inst_coords_details$org_type)
-org_types_simplified <- c("Univ", "Univ", "Institute", "Institute", "Other", 
-                          "Other", "Other", "Other","Hospital", "Other", 
-                          "Hospital", "Hospital", "Univ", "Industry")
-library(plotly)
+org_types = unique(inst_coords_details$org_type)
+org_types_simplified <- c(
+  "University" = "Univ",
+  "Research organisation" = "Institute",
+  "Hospital" = "Hospital",
+  "Teaching Organisation" = "Other",
+  "Governmental Institution" = "Gov",
+  "Funding Organisation" = "Gov",
+  "Funding Channel" = "Gov",
+  "University Component" = "Univ",
+  "Hospital Group" = "Hospital",
+  "Teaching Organisation" = "Other",
+  "Ambiguous" = "Other",
+  "Collegiate University" = "Univ"
+)
+
 g <- inst_coords_details %>%
   filter(!is.na(Continent_name)) %>%
-  mutate(
-    org = plyr::mapvalues(org_type, org_types, org_types_simplified),
-    org = factor(org, levels = c("Univ", "Hospital", "Industry", "Institute", "Other")),
-  ) %>%
-  ggplot(aes(x = axis1, y = axis2, color = Continent_name, shape = Continent_name, group = city, label = full_name, label2 = Country_name, label3 = org_type)) +
-  geom_point(size = 0.6, alpha = 0.8) +
+  mutate(org_type = plyr::mapvalues(org_type, from = names(org_types_simplified), to = org_types_simplified)) %>%
+  ggplot(aes(x = axis1, y = axis2, fill = org_type, group = city, label = full_name, label2 = Country_name, label3 = org_type, label4 = region)) +
+  geom_point(size = 3, alpha = 0.9, shape = 21, color = "black") +
   theme_minimal() +
@@
          shape = guide_legend(override.aes = list(size=5))) +
-  scale_color_brewer(palette = "Set2") +
+  scale_fill_brewer(palette = "Accent") +
   theme(legend.position = "bottom")
@@
 #ggsave("~/Desktop/mobility_institution_bycontinent.pdf", g, width = 10, height = 8)
-
-ggplotly(g, tooltip = c("Continent_name", "Country_name", "city", "full_name", "org_type"))
+g
+ggplotly(g, tooltip = c("Continent_name", "Country_name", "region", "city", "full_name", "org_type", "org"))
 ```

### 2020-01-08 notebooks/20191104_institution_size_flows.rmd
Miscelaneous notebooks

@@
 flows <- flows %>%
-  select(-index) %>%
   filter(org1 != org2) %>%
@@
 head(flows)
+```
+
+```{r}
+
+lookup <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/20191024_institution_lookup.txt",
+                     delim = "\t")
+
+coords <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/fixed_org_coordinates.txt", delim = "\t")
+
+lookup %>%
+  select(-new_lat, -new_long) %>%
+  left_join(coords, by = "cwts_org_no") %>%
+  mutate(
+    latitude = ifelse(latitude == "NULL", new_lat, latitude),
+    longitude = ifelse(longitude == "NULL", new_long, longitude),
+    ) %>%
+  select(-new_lat, -new_long)
+
 ```
@@
 ```{r}
+
+lookup <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t")
+
+lookup_trim <- lookup %>% select(cwts_org_no, city, region, country_iso_name)
 flows_all <- flows %>%
@@
   inner_join(geographic_distance) %>%
-  inner_join(word2vec_similarities)
+  inner_join(word2vec_similarities) %>%
+  left_join(lookup_trim, by = c("org1" = "cwts_org_no")) %>%
+  rename(org1_city = city, org1_region = region, org1_country = country_iso_name) %>%
+  left_join(lookup_trim, by = c("org2" = "cwts_org_no")) %>%
+  rename(org2_city = city, org2_region = region, org2_country = country_iso_name)
 
@@
 ```{r}
-p1_all <- flows_all %>%
-  ggplot(aes(x = log(distance), y = log(gravity))) +
-  geom_hex(bins = 200) +
-  theme_minimal() +
-  labs(x = "Log(Kilometers distance)",
-       y = "P1 * P2 / F12")
+library(tidyverse)
+library(readr)
+library(latex2exp)
+library(ggpmisc)
 
-p1_all
+lookup <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t")
+lookup_trim <- lookup %>% select(cwts_org_no, city, region, country_iso_name)
+
+dist_raw = read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Descriptive/org/aggregate_org_distances.csv") %>%
+  select(-X1) %>%
+  left_join(lookup_trim, by = c("org1" = "cwts_org_no")) %>%
+  rename(org1_city = city, org1_region = region, org1_country = country_iso_name) %>%
+  left_join(lookup_trim, by = c("org2" = "cwts_org_no")) %>%
+  rename(org2_city = city, org2_region = region, org2_country = country_iso_name) %>%
+  unique()
+
+head(dist_raw) 
 ```
@@
 ```{r}
-p2_all <- flows_all %>%
-  ggplot(aes(x = (similarity), y = log(gravity))) +
-  geom_hex(bins = 100) +
+dist <- dist_raw %>% 
+  #filter(org1_city != org2_city) %>%
+  filter(emb_similarity >= 0) %>%
+  filter(count > 0) %>%
+  mutate(
+         geo_distance = ifelse(geo_distance < 1, 1, geo_distance),
+         geo_distance_logged = log(geo_distance),
+         gravity = imputed_count / (org1_size * org2_size),
+         gravity_logged = log(gravity)
+     )
+
+dist_binned <- dist %>%
+  gather(metric, distance, geo_distance_logged, emb_similarity) %>%
+  mutate(metric = factor(metric, 
+                         levels = c("geo_distance_logged", "emb_similarity"), 
+                         labels = c("log(km distance)", "cosine similarity"))
+  ) %>%
+  group_by(metric) %>%
+  mutate(
+    bin = cut(round(distance, 2), 40)
+  ) %>%
+  arrange(bin) %>%
+  group_by(metric, bin) %>%
+  summarize(
+    pos = min(distance) + ((max(distance) - min(distance)) / 2),
+    #pos = (as.numeric(first(bin)) * 0.05) - 0.025,
+    mu = mean(gravity_logged, na.rm = T),
+    se = sd(gravity_logged, na.rm = T) / sqrt(n()),
+    ci = 2.576 * se
+  )
+
+dist_binned
+
+dist %>%
+  gather(metric, distance, geo_distance_logged, emb_similarity) %>%
+  mutate(metric = factor(metric, 
+                         levels = c("geo_distance_logged", "emb_similarity"), 
+                         labels = c("log(km distance)", "cosine similarity"))
+  ) %>%
+  ggplot(aes(x = distance, y = gravity_logged)) +
+  geom_hex(bins = 20, 
+           color = "lightgrey") +
+  stat_poly_eq(formula = y ~ x,
+               aes(label = paste(..rr.label.., sep = "~~~")), 
+               parse=TRUE,
+               coef.digits = 2,
+               label.x.npc = "right") +
+  stat_smooth(method = "lm", formula = y ~ x, color = "#c0392b", size = 1.5) + 
+  geom_point(data = dist_binned, aes(x = pos, y = mu, group = bin), size = 2) +
+  geom_errorbar(data = dist_binned, aes(x = pos, ymin = mu - ci, ymax = mu + ci, y = NULL)) +
+  facet_wrap(~metric, scale = "free_x", strip.position = "bottom") +
   theme_minimal() +
-  labs(x = "Cosine Similarity",
-       y = "Log(Kilometer Distance)")
-
-p2_all
+  scale_fill_gradientn(colours=c("white", "blue"), 
+                       name = "Frequency",
+                       na.value=NA) +
+  theme(
+    legend.position = "right",
+    strip.text = element_text(size = 12),
+    axis.title.y = element_text(size = 12, face = "bold", angle = 0, vjust = 0.5),
+    axis.title.x = element_blank()
+  ) +
+  ylab(TeX("$\\log\\left(\\frac{F_{ij}}{P_{i}P_{j}}\\right)$"))
 ```
@@
 ```{r}
-p1_
+g1 <- dist %>% 
+  filter(count > 0) %>%
+  mutate(
+         geo_distance = ifelse(geo_distance < 1, 1, geo_distance),
+         geo_distance_logged = log(geo_distance),
+         gravity = imputed_count / (org1_size * org2_size),
+         gravity_logged = log(gravity)
+         ) %>%
+  gather(metric, distance, geo_distance_logged, emb_similarity) %>%
+  mutate(metric = factor(metric, 
+                         levels = c("geo_distance_logged", "emb_similarity"), 
+                         labels = c("log(km distance)", "cosine similarity"))
+  ) %>%
+  ggplot(aes(x = gravity_logged, y = distance)) +
+  geom_hex(bins = 20, 
+           color = "lightgrey") +
+  stat_poly_eq(formula = y ~ x,
+               aes(label = paste(..rr.label.., sep = "~~~")), 
+               parse=TRUE,
+               coef.digits = 2,
+               label.x.npc = "right") +
+  stat_smooth(method = "lm", formula = y ~ x, color = "#c0392b", size = 1.5) + 
+  facet_wrap(~metric, scale = "free_y", strip.position = "left") +
+  theme_minimal() +
+  scale_fill_gradientn(colours=c("white", "blue"), 
+                       name = "Frequency",
+                       na.value=NA) +
+  theme(
+    legend.position = "right",
+    strip.text = element_text(size = 12),
+    axis.title.x = element_text(size = 12, face = "bold"),
+    axis.title.y = element_blank()
+  ) +
+  xlab(TeX("$\\log\\left(\\frac{F_{ij}}{P_{i}P_{j}}\\right)$")) +
+  ylab("Metric")
+
+g1
+ggsave("~/Desktop/plot1.png", g1, width = 9, height = 5)
+```
+
+We can also look at log ratios.
+Note that I filter to only values of cosine similarity that are at least 0.
+The log function is only defined for non-negative numbers, however cosine simialrity is defined between -1 and 1 (though there are relatively few negative comparisons).
+
+Higher values on the y-axis correpond to cases where cosine similarity is much greater than the gravity, i.e., the cosine similarity indicates stronger relationship than the flow.
+
+The "gravity" is the flow, as a factor of the "mass" or size of the institions. Higher values suggest that the flow is greater than expected given the institution sizes. 
+```{r}
+dist %>%
+  filter(emb_similarity >= 0) %>%
+  mutate(
+    gravity = imputed_count / (org1_size * org2_size),
+    cosine_bin = cut(round(emb_similarity, 2), 20),
+    log_ratio = log(emb_similarity / gravity)
+  ) %>%
+  arrange(cosine_bin) %>%
+  group_by(cosine_bin) %>%
+  summarize(
+    mu_lr = mean(log_ratio, na.rm = T),
+    se_lr = sd(log_ratio, na.rm = T) / sqrt(n())
+  ) %>%
+  ggplot(aes(x = cosine_bin, y = mu_lr)) +
+  geom_point(size = 4, alpha = 0.8, shape = 21) +
+  geom_errorbar(aes(ymin = mu_lr - se_lr, ymax = mu_lr + se_lr), width = 0.4) +
+  theme_minimal() +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
+    axis.title.y = element_text(angle = 0, vjust = 0.5)
+  ) +
+  xlab("Cosine similarity (binned)") +
+  ylab(TeX("$\\log\\left[\\frac{\\cos(\\theta)}{\\frac{F_{ij}}{P_{i}P_{j}}}\\right]"))
+```
+
+```{r}
+dist2 <- dist %>%
+  filter(emb_similarity >= 0) %>%
+  mutate(
+    sim = 1 - emb_similarity,
+    y = sim, 
+    x = imputed_count / (org1_size * org2_size),
+  )
+
+fitted <- nls(y ~ a * exp(b * x),
+    data = dist2,
+    start=list(a=0.5, b=-0.1))
 
@@
 ```{r}
-library(grid)
-library(gridExtra)
+dist %>%
+  filter(count > 0) %>%
+  filter(emb_similarity >= 0) %>%
+  mutate(
+    gravity = imputed_count / (org1_size * org2_size),
+    sim = 1 - emb_similarity
+  ) %>%
+  ggplot(aes(x = gravity, y = sim)) +
+  geom_hex(bins = 30) +
+  geom_smooth(method = "nls", formula = y ~ a * exp(b * x), method.args = list(start=c(a = 0.5, b= -0.01)), se = FALSE) +
+  theme_minimal() +
+  labs(x = "f12 / (p1 * p2), not transformed", y = "(1 - cosine similarity)")
+```
+
+```{r}
+dist %>%
+  filter(emb_similarity >= 0) %>%
+  ggplot(aes(x = geo_distance_logged, y = gravity_logged)) +
+  geom_hex(bins = 20, 
+           color = "lightgrey") +
+  #geom_point(alpha = 0.1) +
+  stat_poly_eq(formula = y ~ x,
+               aes(label = paste(..rr.label.., sep = "~~~")), 
+               parse=TRUE,
+               coef.digits = 2,
+               label.x.npc = "right") +
+  stat_smooth(method = "lm", formula = y ~ x, color = "#c0392b", size = 1.5) + 
+  theme_minimal() +
+  scale_fill_gradientn(colours=c("white", "blue"), 
+                       name = "Frequency",
+                       na.value=NA) +
+  theme(
+    legend.position = "right",
+    strip.text = element_text(size = 12),
+    axis.title.x = element_text(size = 12, face = "bold"),
+    axis.title.y = element_text(size = 12, face = "bold", angle = 0, vjust = 0.5)
+  ) +
+  xlab("Log(Geo. Distance, km)") +
+  ylab(TeX("$\\log\\left(\\frac{F_{ij}}{P_{i}P_{j}}\\right)$"))
 
 ```
+
+```{r}
+lookup_country <- lookup %>%
+  select(cwts_org_no, country_iso_name, city_country)
+dist_geo <- dist %>%
+  left_join(lookup_country, by = c("org1" = "cwts_org_no")) %>%
+  rename(country1 = country_iso_name, city1 = city_country) %>%
+  left_join(lookup_country, by = c("org2" = "cwts_org_no")) %>%
+  rename(country2 = country_iso_name, city2 = city_country) %>%
+  mutate(
+    same_country = country1 == country2,
+    same_city = city1 == city2
+  ) %>%
+  filter()
+
+dist_geo
+```
+
+```{r}
+completed <- c(10410, 1292, 18381, 3505, 18538, 18480, 15219, 846, 1742, 1868, 3047, 15229, 15202, 18503, 15929, 18178, 15980, 15939, 3962, 15852, 15865, 3961, 15966, 3961, 1247, 10384, 3022, 30218, 30219, 818, 2007, 3109, 1062, 10345, 1076, 3614, 7377, 427, 31919, 31913, 38, 2625, 10358, 2628, 1846, 1847, 2732, 2663, 3112, 2662, 2738, 31306)
+dist_geo %>%
+  filter(same_country == T) %>%
+  filter(!org1 %in% completed) %>%
+  filter(!org2 %in% completed) %>%
+  group_by(country1) %>%
+  mutate(
+    mu = mean(geo_distance),
+    #top_percentile = quantile(geo_distance, seq(0,1, by=0.01))[100],
+    #diff = abs(mu - geo_distance),
+    #is_anomoly = geo_distance > (top_percentile)
+    is_anomoly = geo_distance > ( 15 * mu)
+  ) %>%
+  filter(is_anomoly)
+
+```
+
+```{r}
+lookup %>%
+  group_by(country_iso_name) %>%
+  mutate(
+    mean_lat = mean(as.numeric(latitude), na.rm = T),
+    mean_long = mean(as.numeric(longitude), na.rm = T),
+    is_anomoly = abs(latitude - mean_lat) > 10 | abs(longitude - mean_long) > 10
+  ) %>%
+  filter(is_anomoly == T)
+
+```

### 2020-01-08 notebooks/20191118_descriptive_info.rmd
Miscelaneous notebooks

---
title: "Mobility Descriptive Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(readr)
library(viridis)

lookup <- read_delim('/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/institution_lookup_with_states.txt', delim = "\t")

flows <- read_delim('/Users/dakotamurray/Dropbox/SME-dropbox/Data/Raw/20191024_mobility_transitions.txt', delim = "\t")
```

```{r}
data <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Raw/2008-2019_transitions.txt", delim = "\t")
lookup <- read_delim('/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/institution_lookup_with_states.txt', delim = "\t")
```

Get a table of each person.
```{r}
researchers <- data %>% 
  left_join(lookup, by = "cwts_org_no") %>%
  group_by(cluster_id) %>%
  summarize(
    num_org = length(unique(cwts_org_no)),
    num_city = length(unique(city)),
    num_region = length(unique(region)),
    num_country = length(unique(region)),
    org_mobile = num_org > 1,
    city_mobile = num_city > 1,
    region_mobile = num_city > 1,
    country_mobile = num_country > 1,
    num_fields = length(unique(LR_main_field_no)),
    main_field = sort(table(LR_main_field_no))[1]
  )

head(researchers)
```

We need to calculate the number of mbile + nonmobile redearchers per organization

```{r}
orgs <- data %>%
  left_join(researchers, by = "cluster_id") %>%
  select(cwts_org_no, cluster_id, org_mobile) %>%
  group_by(cwts_org_no, org_mobile) %>%
  summarize(num_researchers = length(unique(cluster_id)))

dim(orgs)
head(orgs)
```

```{r}
orgs %>%
  spread(org_mobile, num_researchers) %>%
  rename(nonmobile = `FALSE`, mobile = `TRUE`) %>%
  mutate(total = nonmobile + mobile,
         prop.mobile = mobile / total) %>%
  arrange(desc(prop.mobile)) %>%
  left_join(lookup, by = "cwts_org_no") %>%
  select(cwts_org_no, mobile, nonmobile, total, prop.mobile, full_name, city, region, country_iso_alpha)

```

19001 10415 2733 2727 18695
```{r}
data %>%
  group_by(cluster_id) %>%
  filter(19001 %in% cwts_org_no) %>%
  arrange(cluster_id, pub_year)
```

```{r}
mobile <- flows %>%
  group_by(cluster_id, cwts_org_no) %>%
  slice(1) %>%
  select(cluster_id, cwts_org_no) %>%
  mutate(type = "mobile")

nonmobile$type <- "nonmobile"
```

Number of mobile (between organizations)
```{r}
num_mobile <- length(unique(mobile$cluster_id))
num_mobile
```

Number of non-mobile (between organizations)
```{r}
num_nonmobile <- dim(nonmobile)[1]

num_nonmobile
```

```{r}
count_by_org <- data.table::rbindlist(list(mobile, nonmobile)) %>%
  group_by(cwts_org_no, type) %>%
  summarize(
    count = length(unique(cluster_id))
  ) %>%
  spread(type, value = count) %>%
  mutate(
    all = mobile + nonmobile,
    prop_mobile = mobile / all
  ) %>%
  left_join(lookup, by = "cwts_org_no") %>%
  arrange(desc(prop_mobile)) %>%
  distinct()

count_by_org
```

```{r}
nonmobile %>% group_by(cwts_org_no) %>%
  summarize(count = n()) %>%
  arrange(desc(count)) 
```

```{r}
count_by_org %>%
  arrange(desc(mobile))
```

Proportion of mobile researchers out of total population
```{r}
num_mobile / (num_mobile + num_nonmobile)
```

Now, aggregate at different levels
```{r}
all_people <- all_people %>%
  left_join(lookup, by = c("cwts_org_no"))

```

Percentage of mobile researchers (between institutions)
```{r}
num_mobile <- flows %>%
  group_by(cwts_org_no) %>%
  summarize(mobile = length(unique(cluster_id))) # unique people affiliated with each organization

all_counts <- num_mobile %>%
  inner_join(sizes, by = "cwts_org_no") %>%
  left_join(lookup, by = "cwts_org_no")

all_counts
sum(all_counts$mobile) / sum(all_counts$person_count)
```

Percentage of inter-city mobility
```{r}
num_mobile <- flows %>%
  left_join(lookup, by = "cwts_org_no") %>%
  group_by(city) %>%
  summarize(mobile = length(unique(cluster_id))) # unique people affiliated with each organization

num_total <- sizes %>%
  left_join(lookup, by = "cwts_org_no") %>%
  group_by(city) %>%
  summarize(all = sum(person_count))

sum(num_mobile$mobile, na.rm = T) / sum(num_total$all, na.rm = T)
```

Percentage of inter-region mobility
```{r}
num_mobile <- flows %>%
  left_join(lookup, by = "cwts_org_no") %>%
  group_by(region) %>%
  summarize(mobile = length(unique(cluster_id))) # unique people affiliated with each organization

num_total <- sizes %>%
  left_join(lookup, by = "cwts_org_no") %>%
  group_by(region) %>%
  summarize(all = sum(person_count))

all_counts <- num_mobile %>%
  inner_join(num_total, by = "region")

sum(num_mobile$mobile, na.rm = T) / sum(num_total$all, na.rm = T)
```

Percentage of inter-national mobility
```{r}
num_mobile <- flows %>%
  left_join(lookup, by = "cwts_org_no") %>%
  group_by(country_iso_alpha) %>%
  summarize(mobile = length(unique(cluster_id))) # unique people affiliated with each organization

num_total <- sizes %>%
  left_join(lookup, by = "cwts_org_no") %>%
  group_by(country_iso_alpha) %>%
  summarize(all = sum(person_count, na.rm = T))

sum(num_mobile$mobile, na.rm = T) / sum(num_total$all, na.rm = T)
```

```{r}
all_counts %>%
  group_by(city)

```

```{r}
flows <- read_delim('/Users/dakotamurray/Dropbox/SME-dropbox/Data/Raw/2008-2019_transitions.txt', delim = "\t")

res <- researchers %>%
  select(cluster_id, org_mobile, city_mobile, region_mobile, country_mobile)

flows <- flows %>%
  left_join(res, by = c("cluster_id"))

```

### Distribution of papers over time
```{r}
data <- flows %>%
  filter(pub_year < 2019) %>%
  mutate(pub_year = factor(pub_year)) %>%
  group_by(pub_year) %>%
  summarize(
    count = n(),
    count_org_mobile = sum(org_mobile, na.rm = T),
    count_city_mobile = sum(city_mobile, na.rm = T),
    count_region_mobile = sum(region_mobile, na.rm = T),
    count_country_mobile = sum(country_mobile, na.rm = T)
  ) %>%
  gather(key, value, count, count_org_mobile, count_city_mobile, count_region_mobile, count_country_mobile) %>%
  mutate(
    key = factor(key, 
                 levels = c("count", "count_org_mobile", "count_city_mobile", "count_region_mobile", "count_country_mobile"),
                 labels = c("All", "Org", "City", "Region", "Country"))
  )

data
p1 <- data %>%
  ggplot(aes(x = pub_year, y = value, group = key, fill = key)) +
  geom_line() +
  geom_point(size = 3, shape = 21) +
  theme_minimal() +
  expand_limits(y=0) + 
  scale_y_continuous(breaks = c(0, 1000000, 2000000, 3000000, 4000000),
                     labels = c("0", "1,000,000", "2,000,000", "3,000,000", "4,000,000")) +
  scale_fill_viridis(discrete = T) +
  guides(color = guide_legend(ncol = 2)) +
  theme(
    axis.title.x = element_blank(),
    legend.text = element_text(size = 11),
    legend.title = element_blank(),
    legend.position = c(0.80, 0.15),
    legend.background = element_rect()
  ) +
  ylab("count")

p1
```

### Distribution of papers by discipline

Among mobile researchers only
```{r}
p2 <- flows %>%
  filter(pub_year < 2019) %>%
  mutate(pub_year = factor(pub_year),
         Discipline = factor(LR_main_field_no),
         Discipline = recode(Discipline, 
                             `1` = "SS & HUM",
                             `2` = "BIO & HEALTH",
                             `3` = "PHYS & ENGR",
                             `4` = "LIFE & EARTH",
                             `5` = "MATH & CS"),
         Discipline = factor(Discipline, levels = c("BIO & HEALTH", "PHYS & ENGR", "LIFE & EARTH", "SS & HUM", "MATH & CS"))
         ) %>%
  group_by(pub_year) %>%
  mutate(count = n()) %>%
  group_by(pub_year, Discipline) %>%
  summarize(
    prop = n() / first(count)
  ) %>%
  ggplot(aes(x = pub_year, y = prop, group = Discipline, fill = Discipline)) +
  geom_line() +
  geom_point(size = 3, shape = 21) +
  ylim(0, 1) +
  scale_fill_viridis(discrete = T, option = "A") +
  theme_minimal() +
  theme(
    axis.title.x = element_blank(),
    legend.text = element_text(size = 11),
    legend.title = element_text(size = 12, face = "bold"),
    legend.position = c(0.20, 0.75),
    legend.background = element_rect()
  ) +
  ylab("Proportion")

p2
```

```{r}
library(tidyverse)
library(readr)
researchers <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Descriptive/researcher/researcher_metadata.txt", delim = "\t")

head(researchers)
```

```{r}
data <- researchers %>%
  filter(num_org > 1) %>%
  select(cluster_id, num_org, num_city, num_region, num_country) %>% # reduce the footprint of the data
  gather(key, value, num_org, num_city, num_region, num_country) %>%
  mutate(
    key = factor(key,
                   levels = c("num_org", "num_city", "num_region", "num_country"),
                   labels = c("Organization", "City", "Region", "Country"))
  )

labels <- data %>%
  group_by(key) %>%
  summarize(
    ypos = (sum(value > 1) / n()),
    cumulative = (sum(value > 1) / n())
  )

data %>% ggplot(aes(x = value, group = key)) +
  geom_step(aes(y = 1 - ..y..), stat='ecdf') +
  facet_wrap(~key, nrow = 2, ncol = 2) +
  scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10), limits = c(0, 10)) +
  scale_y_continuous(breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1.0), limits = c(-0.1, 1.1)) +
  theme_minimal() +
  geom_label(data = labels, aes(x = 2, y = ypos, label = format(round(cumulative, 2), nsmall = 2))) + 
  theme(
    axis.title = element_text(size = 12, face = "bold"),
    strip.text = element_text(size = 12, face = "bold"),
  ) +
  xlab("#Affiliations per researcher") +
  ylab("Fraction of data")
```

```{r}
library(tidyverse)
library(readr)
orgs <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Descriptive/org/org_metadata.txt", delim = "\t") %>%
  distinct(cwts_org_no, .keep_all = T)

orgs
orgs %>%
  ggplot(aes(x = prop.mobile)) +
  geom_histogram(fill = "darkgrey", color = "white") +
  theme_minimal()

```

```{r}

orgs %>% 
  filter(prop.mobile > 0.95) %>%
  group_by(country_iso_alpha) %>%
  summarize(count = n()) %>%
  arrange(desc(count))
```

```{r}
orgs %>%
  filter(country_iso_alpha != "NULL" & !is.na(country_iso_alpha)) %>%
  group_by(country_iso_alpha) %>%
  summarize(
    total_mobile = sum(mobile, na.rm = T),
    total_nonmobile = sum(nonmobile, na.rm = T),
    prop.mobile = total_mobile / (total_mobile + total_nonmobile)
  ) %>%
  arrange(desc(prop.mobile))
```

```{r}

agg <- flows %>%
  group_by(city, org_mobile) %>%
  summarize(
    count = length(unique(cluster_id))
  )

agg %>%
  spread(org_mobile, count) %>%
  mutate(
    `TRUE` = ifelse(is.na(`TRUE`), 0, `TRUE`),
    total = `TRUE` + `FALSE`,
    prop = `TRUE` / total
  ) %>%
  filter(city != "NULL" & total > 100) %>%
  arrange(desc(prop))
```

```{r}

flows %>% 
  filter(org_mobile) %>%
  group_by(cluster_id) %>%
  filter(any(city == "ANN ARBOR")) %>%
  arrange(cluster_id)
```

```{r}
net <- flows %>%
  filter(org_mobile) %>%
  distinct(cluster_id, cwts_org_no) %>%
  arrange(cluster_id)

net %>% arrange(cluster_id)

```

```{r}
real_flows <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Descriptive/org/organization_flows.csv")
renamed <- real_flows %>%
  rename(Source = org1, Target = org2, Weight = count)

write_csv(renamed, path = "~/Desktop/org_network.csv")
```

```{r}
library(tidyverse)
library(readr)
library(ggrepel)
lookup <- read_delim('/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/institution_lookup_with_states.txt', delim = "\t") %>%
  select(cwts_org_no, country_iso_alpha, city)
flows <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Raw/2008-2019_transitions.txt", delim = "\t")
researchers <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Descriptive/researcher/researcher_metadata.txt", delim = "\t")

mobility_status <- researchers %>% 
  select(cluster_id, org_mobile, country_mobile)

remove(researchers)

flows <- flows %>%
  select(-LR_main_field_no, -pub_year) %>%
  left_join(mobility_status, by = "cluster_id") %>%
  left_join(lookup, by = "cwts_org_no")
```

```{r}
agg <- flows %>%
  group_by(country_iso_alpha, org_mobile) %>%
  summarize(
    count = length(unique(cluster_id))
  )

exp <- sum(mobility_status$org_mobile) / dim(mobility_status)[1]

plotdata <- agg %>%
  spread(org_mobile, count) %>%
  rename(mobile = `TRUE`, nonmobile = `FALSE`) %>% 
  mutate(
    mobile = ifelse(is.na(mobile), 0, mobile),
    total = mobile + nonmobile,
    prop = mobile / total
  ) %>%
  filter(country_iso_alpha != "NULL" & total > 100) %>%
  arrange(desc(prop)) %>%
  ungroup() %>%
  mutate(index = row_number())

labels_top <- plotdata %>%
  top_n(8, prop)

labels_bot <- plotdata %>%
  filter(!is.na(prop)) %>%
  top_n(8, rev(prop))

plotdata %>%
  ggplot(aes(x = index, y = prop)) +
  geom_bar(stat = "identity", alpha = 0.8) +
  geom_hline(yintercept = exp, linetype = "dashed") +
  geom_label_repel(data = labels_top, aes(label = country_iso_alpha), size = 3, direction = "y", nudge_x = 5) +
  geom_label_repel(data = labels_bot, aes(label = country_iso_alpha), size = 3, direction = "y", nudge_x = -5) +
  scale_x_continuous(expand = c(0, 0)) +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ylab("Proportion mobility")
```

```{r}

exp.org <- sum(mobility_status$org_mobile) / dim(mobility_status)[1]
exp.country <- sum(mobility_status$country_mobile) / dim(mobility_status)[1]

agg <- flows %>%
  filter(!is.na(country_iso_alpha) & country_iso_alpha != "NULL") %>%
  gather(key, value, org_mobile, country_mobile) %>%
  group_by(country_iso_alpha, key, value) %>%
  summarize(
    count = length(unique(cluster_id))
  )

plotdata <- agg %>%
  spread(value, count) %>%
  mutate(
    `TRUE` = ifelse(is.na(`TRUE`), 0, `TRUE`),
    total = `TRUE` + `FALSE`,
    prop = `TRUE` / total
  ) %>%
  filter(total > 100) %>%
  select(country_iso_alpha, key, prop) %>%
  spread(key, prop)

labels.country.top <- plotdata %>%
  ungroup() %>%
  top_n(4, country_mobile)

labels.country.bot <- plotdata %>%
  ungroup() %>%
  top_n(4, desc(country_mobile))

labels.org.top <- plotdata %>%
  ungroup() %>%
  top_n(8, org_mobile)

labels.org.bot <- plotdata %>%
  ungroup() %>%
  top_n(5, desc(org_mobile))

labels <- data.table::rbindlist(list(labels.country.top, labels.country.bot, labels.org.top, labels.org.bot)) %>%
  distinct(country_iso_alpha, .keep_all = T)

p <- plotdata %>%
  ungroup() %>%
  ggplot(aes(x = country_mobile, y = org_mobile, group = country_iso_alpha)) +
  geom_point() +
  geom_abline() +
  geom_label_repel(data = labels, aes(label = country_iso_alpha), size = 3) +
  theme_minimal() +
  theme(
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 12, face = "bold")
  ) +
  xlab("Proportion mobile across countries") +
  ylab("Proportion mobile across organizations")

p
```

```{r}
agg <- flows %>%
  group_by(country_iso_alpha, org_mobile) %>%
  summarize(
    count = length(unique(cluster_id))
  )

plotdata <- agg %>%
  filter(org_mobile) %>%
  ungroup() %>%
  mutate(
    prop = count / sum(count, na.rm = T),
    country_iso_alpha = reorder(country_iso_alpha, desc(prop))
  ) %>%
  arrange(desc(prop)) %>%
  mutate(
    index = row_number(),
    cumulative = cumsum(prop)
  )

labels = plotdata %>%
  top_n(5, prop) %>%
  mutate(
    text = ifelse(country_iso_alpha == "USA", "USA", paste0("+", country_iso_alpha))
  )

plotdata

plotdata %>%
  ggplot(aes(x = index, y = cumulative)) +
  geom_step() +
  scale_x_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30, 50, 100, 120), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.7, 0.8, 0.9, 1.0), expand = c(0, 0)) +
  geom_segment(x = 0, xend = 10, y = 0.80, yend = 0.80, linetype = "dashed", color = "darkgrey") +
  geom_segment(x = 10, xend = 10, y = 0, yend = 0.80, linetype = "dashed", color = "darkgrey") +
  geom_segment(x = 0, xend = 17, y = 0.90, yend = 0.90, linetype = "dashed", color = "darkgrey") +
  geom_segment(x = 17, xend = 17, y = 0.0, yend = 0.90, linetype = "dashed", color = "darkgrey") +
  geom_segment(x = 0, xend = 30, y = 0.964, yend = 0.965, linetype = "dashed", color = "darkgrey") +
  geom_segment(x = 30, xend = 30, y = 0.0, yend = 0.964, linetype = "dashed", color = "darkgrey") +
  geom_label(data = labels, aes(x = index, y = cumulative, label = text), size = 3, nudge_x = 6) +
  theme_minimal() +
  theme(
    axis.title.x = element_blank(),
    axis.text = element_text(size = 10),
    axis.text.y = element_text(face = c(rep("plain", 9), "bold", "bold", "plain"))
  ) +
  ylab("Cumulative proportion")
```

```{r}
labels = plotdata %>%
  top_n(10, prop) %>%
  mutate(
    text = country_iso_alpha
  )

plotdata %>%
  ggplot(aes(x = index, y = prop)) +
  geom_bar(stat = "identity") +
  geom_label_repel(data = labels, aes(label = country_iso_alpha), nudge_x = 5, size = 3, force = 2, direction = "y") +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ylab("Proportion of global mobile researchers")

```

### 2020-01-16 paper/ic2s2-2020/ic2s2_mobility_emb.tex
Adding initial paper and bib

\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{mathptmx}
\usepackage[singlespacing]{setspace}
\usepackage[headheight=1in,margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage[labelfont=bf, font=small]{caption}

\usepackage[style=nature,
					backend=bibtex,
					sortcites=true,
					autocite=superscript
]{biblatex}
\addbibresource{mobility.bib}

\renewcommand{\headrulewidth}{0pt}
\pagestyle{fancy}
\chead{%
  6$^{th}$ International Conference on Computational Social Science IC$^{2}$S$^{2}$\\
  July 17-20, 2020, Massachusetts Institute of Technology, United States%
}

\graphicspath{{images/}}

\title{Embedding co-affiliation trajectories reveals structure of global scientific mobility}

\author[]{} % Please leave Author-field blank for blind review and remove information that may identify the author(s)

\date{}

\begin{document}

\maketitle
\thispagestyle{fancy}

\vspace{-6em}
\begin{center}
\textbf{\textit{Keywords: Science Studies; Mobility; Deep Learning; word2vec; Gravity Law }}
\newline
\end{center}

\section*{Extended Abstract}
To compete for global talent, policy-makers and administrators at all levels of governance require an understanding of \textit{scientific mobility} — the flows or researchers between organizations. 
Many interacting factors shape these flows, including geography, organizational prestigee, and policy~\autocite{deville_career_2014, clauset_systematic_2015}.
However, the complexity of scientific mobility have resulted in a fragmented understanding, limited to specific regions and mobility types.
We leverage recent advances in neural networks and representation learning in order to construct a dense, meaningful, and coherent vector-space representation of global scientific mobility, defined as researcher's co-affiliations during a time window. 
This representation facilitates the holistic study of scientific mobility, one that captures the complex relationships between organizations the world over.

We source bibliographic data on more than 22 million papers published between 2008 and mid 2019, comprising 3.7 million disambiguated authors and 8,445 organizations from the Web of Science database hosted by Leiden University. 
A "sentence" is constructed for each author by concatenating organization ids for each affiliation listed on their papers, ordered by year of publication, as shown in Fig \ref{fig:image}.a for two example authors. 
These sentences are used as input into the standard (\textit{word2vec}) skip-gram model~\autocite{mikolov_distributed_2013}.

Similarity between vectors in the embedding space reasonably approximate actual mobility flows, and are an effective distance. 
The cosine similarity between vectors is more strongly correlated with \textit{flux} between organizations than geographic distance (Fig~\ref{fig:image}.b). 
Flux, the flows of researchers between two organizations given their sizes, is derived from the gravity law of mobility ~\autocite{simini_universal_2012}.
Moreover, defining the gravity law as a function of cosine similarity produces better predictions of flux than using geographic distance (Fig~\ref{fig:image}.c).

We project the embedding into a 2-dimensional space using \textit{umap} ~\autocite{mcinnes_umap_2018} and identify that organizations are largely clustered geographically (Fig ~\ref{fig:image}.d). 
By re-projecting subsets of vectors, we reveal more granular structure.
For example, a re-projection of U.S. universities again demonstrates state-level geographic structure (Fig~\ref{fig:image}.e), however re-projecting Massachusetts (Fig~\ref{fig:image}.d) reveals additional structure based on urban centers (Boston vs. Worcester), but also organization (hospitals tend to be near one another) and political organization (UMass system cluster separate from Harvard, MIT, etc.).
This embedding also reflects a mix of geographic, historical, religious, and linguistic relationships between countries, demonstrated by the complex clustering of Central and South-East Asian countries (Fig~\ref{fig:image}.g) and between Spain, Portugal, and Central and South American countries (Fig~\ref{fig:image}.h).

By embedding scientific mobility, we offer a new way to study scientific mobility, and mobility more generally. 
This approach transforms complex and high-dimensional data into a dense, coherent, and meaningful vector space that is convenient for visualization, and computation, and can be incorporated into a variety of analyses.

\begin{figure}[ht!]
	\centering
	\includegraphics[width=0.83\textwidth]{../Figs/ic2s2-2020/ic2s2_2020_mainfig.pdf}
	\caption{ 
	\textbf{Embedding offer robust model of co-affiliation, reveals multi-scale structure.}
	\textbf{a:} Examples of how "sentences" for the skip-gram model are created from author's affiliations listed on papers.
	\textbf{b:} Relationship between \textit{flux} and embedding similarity stronger than for geographic distance. 
	Red line is line of best fit.
	Black points are the mean flux for each binned by distance or similarity. 
	\textbf{c:} Predicting flux using gravity law.
	Box-plots show distribution of actual flux binned by expected, and color represents the the degree to which the distribution overlaps the line $x = y$. 
	\textbf{d:} Umap projection of embedding space demonstrating geographic clustering or organizations.
	Umap re-projections of subsets of organization vectors vectors for organizations in the United States (\textbf{e}), Massachusetts (\textbf{f.}), Central- and South-East Asia (\textbf{g}) and Central and South-American and Iberian countries (\textbf{h}). 
	 }
	\label{fig:image}
\end{figure}

%
% Bibliography
%
%\bibliographystyle{acm}
\begingroup
\setstretch{0.8}
\small
\setlength\bibitemsep{1pt}
\printbibliography
\endgroup

\end{document}

### 2020-01-17 paper/ic2s2-2020/ic2s2_mobility_emb.tex
Fixed double-quote marks

@@
 We source bibliographic data on more than 22 million papers published between 2008 and mid 2019, comprising 3.7 million disambiguated authors and 8,445 organizations from the Web of Science database hosted by Leiden University.
-A "sentence" is constructed for each author by concatenating organization ids for each affiliation listed on their papers, ordered by year of publication, as shown in Fig \ref{fig:image}.a for two example authors.
+A ``sentence'' is constructed for each author by concatenating organization ids for each affiliation listed on their papers, ordered by year of publication, as shown in Fig \ref{fig:image}.a for two example authors.
 These sentences are used as input into the standard (\textit{word2vec}) skip-gram model~\autocite{mikolov_distributed_2013}.
@@
 	\textbf{Embedding offer robust model of co-affiliation, reveals multi-scale structure.}
-	\textbf{a:} Examples of how "sentences" for the skip-gram model are created from author's affiliations listed on papers.
+	\textbf{a:} Examples of how ``sentences'' for the skip-gram model are created from author's affiliations listed on papers.
 	\textbf{b:} Relationship between \textit{flux} and embedding similarity stronger than for geographic distance. 

### 2020-01-17 paper/ic2s2-2020/ic2s2_mobility_emb.tex
Updated figure and references.

--- 2020-01-16 paper/ic2s2-2020/ic2s2_mobility_emb.tex
@@
 \begin{center}
-\textbf{\textit{Keywords: Science Studies; Mobility; Deep Learning; word2vec; Gravity Law }}
+\textbf{\textit{Keywords: Science Studies; Mobility; Deep Learning; word2vec; Gravity Model}}
 \newline
@@
 To compete for global talent, policy-makers and administrators at all levels of governance require an understanding of \textit{scientific mobility} — the flows or researchers between organizations. 
-Many interacting factors shape these flows, including geography, organizational prestigee, and policy~\autocite{deville_career_2014, clauset_systematic_2015}.
-However, the complexity of scientific mobility have resulted in a fragmented understanding, limited to specific regions and mobility types.
+Many interacting factors shape these flows, including geography, organizational prestigee, and policy~\autocite{deville_career_2014, clauset_systematic_2015}.However, the complexity of scientific mobility have resulted in a fragmented understanding, limited to specific regions and mobility types.
 We leverage recent advances in neural networks and representation learning in order to construct a dense, meaningful, and coherent vector-space representation of global scientific mobility, defined as researcher's co-affiliations during a time window.
@@
 We source bibliographic data on more than 22 million papers published between 2008 and mid 2019, comprising 3.7 million disambiguated authors and 8,445 organizations from the Web of Science database hosted by Leiden University.
-A "sentence" is constructed for each author by concatenating organization ids for each affiliation listed on their papers, ordered by year of publication, as shown in Fig \ref{fig:image}.a for two example authors.
-These sentences are used as input into the standard (\textit{word2vec}) skip-gram model~\autocite{mikolov_distributed_2013}.
+A ``sentence'' is constructed for each author by concatenating organization ids for each affiliation listed on their papers, ordered by year of publication (Fig~\ref{fig:image}.a).
+These sentences are used as input into the standard (\textit{word2vec}) skip-gram model~\autocite{mikolov_distributed_2013}, and result in a dense vector-space representation of organizations (Fig~\ref{fig:image}.b)
 
 Similarity between vectors in the embedding space reasonably approximate actual mobility flows, and are an effective distance. 
-The cosine similarity between vectors is more strongly correlated with \textit{flux} between organizations than geographic distance (Fig~\ref{fig:image}.b). 
+The cosine similarity between vectors is more strongly correlated with \textit{flux} between organizations than geographic distance (Fig~\ref{fig:image}.c). 
 Flux, the flows of researchers between two organizations given their sizes, is derived from the gravity law of mobility ~\autocite{simini_universal_2012}.
-Moreover, defining the gravity law as a function of cosine similarity produces better predictions of flux than using geographic distance (Fig~\ref{fig:image}.c).
+Moreover, defining the gravity law as a function of cosine similarity produces better predictions of flux than using geographic distance (Fig~\ref{fig:image}.d).
 
-We project the embedding into a 2-dimensional space using \textit{umap} ~\autocite{mcinnes_umap_2018} and identify that organizations are largely clustered geographically (Fig ~\ref{fig:image}.d). 
+We project the embedding into a 2-dimensional space using \textit{umap} ~\autocite{mcinnes_umap_2018} and identify that organizations are largely clustered geographically (Fig ~\ref{fig:image}.e).
+This embedding reflects a mix of geographic, historical, religious, and linguistic relationships between countries. 
+For example, South American countires are near Spain and Portugal, French-speaking universities from Quebec are near France, and the Switzerland cluster is positioned between Germany, Austria, and Italy.
 By re-projecting subsets of vectors, we reveal more granular structure.
 For example, a re-projection of U.S.
-universities again demonstrates state-level geographic structure (Fig~\ref{fig:image}.e), however re-projecting Massachusetts (Fig~\ref{fig:image}.d) reveals additional structure based on urban centers (Boston vs.
+universities again demonstrates state-level geographic structure (Fig~\ref{fig:image}.f), however re-projecting Massachusetts (Fig~\ref{fig:image}.g) reveals additional structure based on urban centers (Boston vs.
 Worcester), but also organization (hospitals tend to be near one another) and political organization (UMass system cluster separate from Harvard, MIT, etc.).
-This embedding also reflects a mix of geographic, historical, religious, and linguistic relationships between countries, demonstrated by the complex clustering of Central and South-East Asian countries (Fig~\ref{fig:image}.g) and between Spain, Portugal, and Central and South American countries (Fig~\ref{fig:image}.h).
 
@@
 	\centering
-	\includegraphics[width=0.83\textwidth]{../Figs/ic2s2-2020/ic2s2_2020_mainfig.pdf}
+	\includegraphics[width=\textwidth]{../Figs/ic2s2-2020/ic2s2_2020_mainfig.pdf}
 	\caption{ 
 	\textbf{Embedding offer robust model of co-affiliation, reveals multi-scale structure.}
-	\textbf{a:} Examples of how "sentences" for the skip-gram model are created from author's affiliations listed on papers.
-	\textbf{b:} Relationship between \textit{flux} and embedding similarity stronger than for geographic distance. 
+	\textbf{a.} Examples of how ``sentences'' for the skip-gram model are created from author's affiliations listed on papers.
+	\textbf{b.} Embedded organizations are represented as vectors.
+	\textbf{c.} Relationship between \textit{flux} and embedding similarity stronger than for geographic distance. 
 	Red line is line of best fit.
 	Black points are the mean flux for each binned by distance or similarity. 
-	\textbf{c:} Predicting flux using gravity law.
-	Box-plots show distribution of actual flux binned by expected, and color represents the the degree to which the distribution overlaps the line $x = y$. 
-	\textbf{d:} Umap projection of embedding space demonstrating geographic clustering or organizations.
-	Umap re-projections of subsets of organization vectors vectors for organizations in the United States (\textbf{e}), Massachusetts (\textbf{f.}), Central- and South-East Asia (\textbf{g}) and Central and South-American and Iberian countries (\textbf{h}).
+	\textbf{d.} Predicting flux using gravity law.
+	Box-plots show distribution of actual flux binned across predicted.
+	Color represents degree to which the distribution overlaps the line $x = y$. 
+	\textbf{e.} Umap projection of embedding space demonstrating geographic clustering or organizations.
+	Re-projections of vector subsets for the \textbf{f.} United States and \textbf{g.} Massachusetts. 
 	 }
@@
 \setlength\bibitemsep{1pt}
-\printbibliography
+{\renewcommand{\markboth}[2]{}% Remove header adjustment
+\printbibliography}
 \endgroup

### 2020-01-20 paper/ic2s2-2020/ic2s2_mobility_emb.tex
Updated text given new comments at link: https://www.dropbox.com/s/sxaykg0yr6a8qds/ic2s2_mobility_emb.pdf?dl=0

@@
 \begin{center}
-\textbf{\textit{Keywords: Science Studies; Mobility; Deep Learning; word2vec; Gravity Model}}
+\textbf{\textit{Keywords: Science of Science; Mobility; Graph embedding; word2vec; Gravity Model}}
 \newline
@@
 \section*{Extended Abstract}
-To compete for global talent, policy-makers and administrators at all levels of governance require an understanding of \textit{scientific mobility} — the flows or researchers between organizations. 
-Many interacting factors shape these flows, including geography, organizational prestigee, and policy~\autocite{deville_career_2014, clauset_systematic_2015}.However, the complexity of scientific mobility have resulted in a fragmented understanding, limited to specific regions and mobility types.
-We leverage recent advances in neural networks and representation learning in order to construct a dense, meaningful, and coherent vector-space representation of global scientific mobility, defined as researcher's co-affiliations during a time window.
-This representation facilitates the holistic study of scientific mobility, one that captures the complex relationships between organizations the world over.
 
-We source bibliographic data on more than 22 million papers published between 2008 and mid 2019, comprising 3.7 million disambiguated authors and 8,445 organizations from the Web of Science database hosted by Leiden University.
-A ``sentence'' is constructed for each author by concatenating organization ids for each affiliation listed on their papers, ordered by year of publication (Fig~\ref{fig:image}.a).
-These sentences are used as input into the standard (\textit{word2vec}) skip-gram model~\autocite{mikolov_distributed_2013}, and result in a dense vector-space representation of organizations (Fig~\ref{fig:image}.b)
+Scientific mobility is closely linked to impact~\autocite{sugimoto_scientists_2017} and is essential to understanding the scientific ecosystem.
+This mobility is shaped by many factors, including geography, prestige, and policy\autocite{deville_career_2014}.
+Such complexity has resulted in a fragmented understanding of scientific mobility, limited to specific regions and mobility types.
+We leverage recent advances in neural networks and representation learning to construct a dense, meaningful, and coherent vector-space embedding of global scientific mobility, using individual mobility documented bibliographic data.
+This representation facilitates the holistic study of scientific mobility, capturing the complex relationships between organizations around the world.
 
-Similarity between vectors in the embedding space reasonably approximate actual mobility flows, and are an effective distance. 
-The cosine similarity between vectors is more strongly correlated with \textit{flux} between organizations than geographic distance (Fig~\ref{fig:image}.c). 
-Flux, the flows of researchers between two organizations given their sizes, is derived from the gravity law of mobility ~\autocite{simini_universal_2012}.
-Moreover, defining the gravity law as a function of cosine similarity produces better predictions of flux than using geographic distance (Fig~\ref{fig:image}.d).
+We source the Web of Science for bibliographic data on more than 22 million papers published between 2008 and mid 2019, comprising 3.7 million disambiguated authors and 8,445 organizations. 
+A ``sentence'' is constructed for each author by concatenating organization IDs for each affiliation listed on their papers, ordered by year of publication (Fig~\ref{fig:image}.a).
+These sentences are used as input into the standard word embedding~\autocite{mikolov_distributed_2013}, which learns a dense vector-space embedding of organizations (Fig~\ref{fig:image}.b)
 
-We project the embedding into a 2-dimensional space using \textit{umap} ~\autocite{mcinnes_umap_2018} and identify that organizations are largely clustered geographically (Fig ~\ref{fig:image}.e).
-This embedding reflects a mix of geographic, historical, religious, and linguistic relationships between countries. 
-For example, South American countires are near Spain and Portugal, French-speaking universities from Quebec are near France, and the Switzerland cluster is positioned between Germany, Austria, and Italy.
-By re-projecting subsets of vectors, we reveal more granular structure.
-For example, a re-projection of U.S.
-universities again demonstrates state-level geographic structure (Fig~\ref{fig:image}.f), however re-projecting Massachusetts (Fig~\ref{fig:image}.g) reveals additional structure based on urban centers (Boston vs.
-Worcester), but also organization (hospitals tend to be near one another) and political organization (UMass system cluster separate from Harvard, MIT, etc.).
+We show that similarity between vectors in the embedding space can be considered as a reasonable measure of effective distance. 
+The cosine similarity between vectors can explain more than twice the variance in mobility between pairs of organizations than geographic distance (Fig~\ref{fig:image}.c). 
+Moreover, applying the gravity law of mobility~\cite{simini_universal_2012} with cosine similarity produces better predictions of mobility than does using geographic distance (Fig~\ref{fig:image}.
 
-By embedding scientific mobility, we offer a new way to study scientific mobility, and mobility more generally. 
-This approach transforms complex and high-dimensional data into a dense, coherent, and meaningful vector space that is convenient for visualization, and computation, and can be incorporated into a variety of analyses.
+We visualize the embedding using UMAP~\autocite{mcinnes_umap_2018} and observe strong geographic clustering (Fig~\ref{fig:image}.e), while also reflecting a mix of historical, religious, and linguistic relationships between countries.
+For example, South American countries are near Spain and Portugal and French-speaking universities from Quebec are near France. 
+By visualizing subsets of vectors, we reveal more granular structure.
+For example, the structure of U.S.
+universities demonstrates state-level geographic clustering (Fig~\ref{fig:image}.f), whereas Massachusetts (Fig~\ref{fig:image}.g) instead shows structure based on urban centers (Boston vs.
+Worcester), organization type (hospitals tend to be adjacent) and different university systems (UMass system cluster separate from Harvard, MIT, etc.).
+
+By embedding scientific mobility, we offer a new quantitative framework to study scientific mobility, and potentially mobility in general. 
+This approach transforms complex and high-dimensional data into a dense, coherent, and meaningful vector space that is convenient for visualization, computation, and can be incorporated into a variety of analyses.
+\newpage
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{../Figs/ic2s2-2020/ic2s2_2020_mainfig.pdf}
+	\includegraphics[width=0.96\textwidth]{../Figs/ic2s2-2020/ic2s2_2020_mainfig.pdf}
 	\caption{ 
@@
 	\textbf{a.} Examples of how ``sentences'' for the skip-gram model are created from author's affiliations listed on papers.
-	\textbf{b.} Embedded organizations are represented as vectors.
-	\textbf{c.} Relationship between \textit{flux} and embedding similarity stronger than for geographic distance. 
-	Red line is line of best fit.
+	\textbf{b.} Each organization is represented as a vector.
+	\textbf{c.} Organization embedding better captures closeness (flux) than does geographic distance. 
+ $P_{i}$ and $P_{j}$ are the number of researchers in organization $i$ and $j$, and $F_{ij}$ is the symmetric flow between them.
 	Black points are the mean flux for each binned by distance or similarity. 
-	\textbf{d.} Predicting flux using gravity law.
-	Box-plots show distribution of actual flux binned across predicted.
-	Color represents degree to which the distribution overlaps the line $x = y$. 
-	\textbf{e.} Umap projection of embedding space demonstrating geographic clustering or organizations.
-	Re-projections of vector subsets for the \textbf{f.} United States and \textbf{g.} Massachusetts. 
+	\textbf{d.} Cosine similarity better predictor of flux than geographic distance, using gravity law. 
+	Box-plots show distribution of actual flux binned across predicted, colored by the degree to which it overlaps $x = y$. 
+	\textbf{e.} UMAP visualizarion of embedding demonstrates geographic structure.
+	Visualization of vector subsets reveal additional structure for the \textbf{f.} U.S. and \textbf{g.} Massachusetts. 
 	 }

### 2020-01-21 paper/ic2s2-2020/ic2s2_mobility_emb.tex
Change keyword

@@
 \begin{center}
-\textbf{\textit{Keywords: Science of Science; Mobility; Graph embedding; word2vec; Gravity Model}}
+\textbf{\textit{Keywords: Science of Science; Mobility; Graph embedding; Geography; Gravity Model}}
 \newline
@@
 
-Scientific mobility is closely linked to impact~\autocite{sugimoto_scientists_2017} and is essential to understanding the scientific ecosystem.
-This mobility is shaped by many factors, including geography, prestige, and policy\autocite{deville_career_2014}.
+Scientific mobility is closely linked to impact~\autocite{sugimoto_scientists_2017} and is an essential component of the scientific ecosystem.
+This mobility is shaped by many factors, including geography, prestige, and policy\autocite{deville_career_2014,clauset_systematic_2015}.
 Such complexity has resulted in a fragmented understanding of scientific mobility, limited to specific regions and mobility types.
-We leverage recent advances in neural networks and representation learning to construct a dense, meaningful, and coherent vector-space embedding of global scientific mobility, using individual mobility documented bibliographic data.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\textwidth]{../Figs/ic2s2-2020/ic2s2_2020_mainfig.pdf}
+	\caption{ 
+	\textbf{Embedding offer robust model of co-affiliation, reveals multi-scale structure.}
+	\textbf{a.} Examples of how ``sentences'' for the skip-gram model are created from author's affiliations listed on papers.
+	\textbf{b.} Organization sentences are used as input for word embedding model. Each organization is represented as a vector.
+	\textbf{c.} Organization embedding better captures closeness (flux) than does geographic distance. 
+ $P_{i}$ and $P_{j}$ are the number of researchers in organization $i$ and $j$, and $F_{ij}$ is the symmetric flow between them.
+	Black points are the mean flux for each binned by distance or similarity. 
+	\textbf{d.} Cosine similarity better predictor of flux than geographic distance, using gravity law.
+	Box-plots show distribution of actual flux binned across predicted, colored by the degree to which it overlaps $x = y$. 
+	Cosine similarity is better predictor when considering only pairs of organizations within the same country (\textbf{e}) and only pairs in different countries (\textbf{f}). 
+	\textbf{g.} UMAP visualization of embedding demonstrates geographic structure.
+	Visualization of vector subsets reveal additional structure for the \textbf{h.} U.S. and \textbf{i.} Massachusetts. 
+	 }
+	\label{fig:image}
+\end{figure}
+
+We leverage recent advances in neural networks and representation learning to construct a dense, meaningful, and coherent vector-space embedding of global scientific mobility, using individual mobility trajectories documented in bibliographic data.
 This representation facilitates the holistic study of scientific mobility, capturing the complex relationships between organizations around the world.
 
-We source the Web of Science for bibliographic data on more than 22 million papers published between 2008 and mid 2019, comprising 3.7 million disambiguated authors and 8,445 organizations. 
+We source the Web of Science for bibliographic data on more than 22 million papers from mobile authors published between 2008 and mid 2019, comprising 3.7 million disambiguated authors and 8,445 organizations.
 A ``sentence'' is constructed for each author by concatenating organization IDs for each affiliation listed on their papers, ordered by year of publication (Fig~\ref{fig:image}.a).
@@
 The cosine similarity between vectors can explain more than twice the variance in mobility between pairs of organizations than geographic distance (Fig~\ref{fig:image}.c). 
-Moreover, applying the gravity law of mobility~\cite{simini_universal_2012} with cosine similarity produces better predictions of mobility than does using geographic distance (Fig~\ref{fig:image}.
+Moreover, applying the gravity law of mobility~\autocite{simini_universal_2012} with cosine similarity produces better predictions of mobility than does using geographic distance (Fig~\ref{fig:image}.d.
+These predictions are also more robust than geographic distance when considering only same-country (Fig~\ref{fig:image}.e) and different-country (Fig~\ref{fig:image}.f) mobility.
 
-We visualize the embedding using UMAP~\autocite{mcinnes_umap_2018} and observe strong geographic clustering (Fig~\ref{fig:image}.e), while also reflecting a mix of historical, religious, and linguistic relationships between countries.
-For example, South American countries are near Spain and Portugal and French-speaking universities from Quebec are near France. 
+We visualize the embedding using UMAP~\autocite{mcinnes_umap_2018} and observe strong geographic clustering (Fig~\ref{fig:image}.g), while also reflecting a mix of historical, religious, and linguistic relationships between countries.
+For example, South American countries are near Spain and Portugal and organizations in French-speaking Quebec and North Africa are nearer France. 
 By visualizing subsets of vectors, we reveal more granular structure.
 For example, the structure of U.S.
-universities demonstrates state-level geographic clustering (Fig~\ref{fig:image}.f), whereas Massachusetts (Fig~\ref{fig:image}.g) instead shows structure based on urban centers (Boston vs.
+universities demonstrates state-level geographic clustering (Fig~\ref{fig:image}.h) roughly organized by state and region, whereas Massachusetts (Fig~\ref{fig:image}.i) instead shows structure based on urban centers (Boston vs.
 Worcester), organization type (hospitals tend to be adjacent) and different university systems (UMass system cluster separate from Harvard, MIT, etc.).
 
-By embedding scientific mobility, we offer a new quantitative framework to study scientific mobility, and potentially mobility in general. 
+By embedding scientific mobility, we offer a novel quantitative framework to study scientific mobility, and potentially mobility in general. 
 This approach transforms complex and high-dimensional data into a dense, coherent, and meaningful vector space that is convenient for visualization, computation, and can be incorporated into a variety of analyses.
-\newpage
-
-\begin{figure}[ht!]
-	\centering
-	\includegraphics[width=0.96\textwidth]{../Figs/ic2s2-2020/ic2s2_2020_mainfig.pdf}
-	\caption{ 
-	\textbf{Embedding offer robust model of co-affiliation, reveals multi-scale structure.}
-	\textbf{a.} Examples of how ``sentences'' for the skip-gram model are created from author's affiliations listed on papers.
-	\textbf{b.} Each organization is represented as a vector.
-	\textbf{c.} Organization embedding better captures closeness (flux) than does geographic distance. 
- $P_{i}$ and $P_{j}$ are the number of researchers in organization $i$ and $j$, and $F_{ij}$ is the symmetric flow between them.
-	Black points are the mean flux for each binned by distance or similarity. 
-	\textbf{d.} Cosine similarity better predictor of flux than geographic distance, using gravity law. 
-	Box-plots show distribution of actual flux binned across predicted, colored by the degree to which it overlaps $x = y$. 
-	\textbf{e.} UMAP visualizarion of embedding demonstrates geographic structure.
-	Visualization of vector subsets reveal additional structure for the \textbf{f.} U.S. and \textbf{g.} Massachusetts. 
-	 }
-	\label{fig:image}
-\end{figure}
 

### 2020-01-26 paper/current/main.tex
Introduce main data

@@
 \usepackage{biblatex}
-\addbibresource{main.bib}
+\addbibresource{mobility.bib}
 
@@
 
+%
+% DATA AND METHODS
+%
+\section{Data and Methods}
+\label{sec:datamethods} %{{{
+
+%% Introduce main dataset
+% Where do we 
+% Do we need to add the Leiden field classificaiton infomration? It doesn't seem like its relevant for the current analysis.
+% Do we need to talk about how we define mobility in relation to past papers?
+We source co-affiliation trajectories of authors from the Web of Science database hosted by the Center for Science and Technology Studies at Leiden University. 
+Trajectories are constructed from author affiliations listed on the byline of publications for a given author.
+Given the limitations of author-name disambiguation, we limit to papers published after 2008, when the Web of Science began providing full names and institutional affiliations (cite) and when performance is strongest (ref to SI?).
+This yields 37,542,144 author-affiliation representing 12,963,792 authors. 
+Each author-affiliation combination is associated with the publication year and a unique id that maps the affiliation to a disambiguate organization. 
+Combinations are ordered by the year of publication, and are randomized for combinations within the same year. 
+Authors are classified as mobile when they have at least two distinct organization ids in their trajectory, meaning that they have published using two or more distinct affiliations between 2008 and 2019.
+Mobile authors constitute 3,709,869 or 28.6 percent of all authors, and 22,436,637 author-affiliation combinations.
+
+Affiliations mapped to one of 8,661 organizations, disambiguated following a mostly manual process originally designed for the Leiden Rankings of World Universities (cite). 
+Organizational records were associated with a full name, a type indicating the sector (e.g., University, Government, Industry), and an identifier for the country and city of the organization. 
+Sixteen different sector types were included in the analysis, which we aggregated to a four high-level codes: \textit{University}, \textit{Hospital}, \textit{Government}, and \textit{Other}. 
+Each record was also associated with a latitude and longitude, however for many organizations these were missing or incorrect.
+We manually updated the coordinates of 2,267 organizations by searching the institution name and city on Google Maps;
+in cases where a precise location of the organization could not be identified, we used the coordinates returned when searching the name of the city.
+State/province level  information were added using the reverse geocoding service LocationIQ using each organization's latitude and longitude as input. 
+Organizations were also assigned continental information (e.g., North America, Asia, Europe) manually, by country. 
+For each organization, we also calculated a size as the average number of unique authors (mobile and non-mobile) who published with that organization across each year of our dataset;
+in the case that authors publish with multiple affiliations in a single year, they are counted towards each.
+
+% Leiden bibliographic data
+	% Basic details
+	% How was mobility determined?
+	% How were university sizes extracted?
+	% Organization information? (count, etc.)
+% Manually-identified geographic coordiantes
+% Leiden rankings (if using prestige)
+%
+
+%% Introduce embedding methodology and approach
+% Introduce embedding and why we use it
+% How were sentences created (use figure)
+
+%% Gravity Law
+% Why use gravity law?
+% How were geographic distances calculated?
+% How are distnaces calculated within the embedding space
+
+%% Introduce gravity measurements
+
 \section{Results}\label{sec:results} %{{{
@@
 \begin{equation}
-p(w_O|w_I) = \frac{\exp(v'_{w_O} \cdot v_{w_I})}{\sum_{w=1}^{W} \exp(v'_w \cdot v_w_I)}, 
+p(w_O|w_I) = \frac{\exp(v'_{w_{O} }\cdot v_{w_{I}})}{\sum_{w=1}^{W} \exp(v'_w \cdot v_{w_{)}}}, 
 \end{equation}
@@
 
-\section{Methods}\label{sec:methods} %{{{
-
 %}}}

### 2020-01-26 paper/current/main.tex
added embedding subsection, other small changes

@@
 \usepackage{graphicx}
-\def\figdir{figs}
+\def\figdir{../Figs}
 
@@
 
-%% Introduce main dataset
-% Where do we 
+Data, analysis, and associated code have been made publicly available and can be found at \textit{https://github.com/murrayds/...}
+
+\subsection*{Data}
+%% Main dataset
 % Do we need to add the Leiden field classificaiton infomration? It doesn't seem like its relevant for the current analysis.
@@
 Each author-affiliation combination is associated with the publication year and a unique id that maps the affiliation to a disambiguate organization. 
-Combinations are ordered by the year of publication, and are randomized for combinations within the same year. 
+Trajectories are represented as the list of author-affiliation combinations, ordered by year of publication, and randomly ordered for combinations within the same year. 
 Authors are classified as mobile when they have at least two distinct organization ids in their trajectory, meaning that they have published using two or more distinct affiliations between 2008 and 2019.
@@
 
+% %Organization information
 Affiliations mapped to one of 8,661 organizations, disambiguated following a mostly manual process originally designed for the Leiden Rankings of World Universities (cite). 
@@
 in the case that authors publish with multiple affiliations in a single year, they are counted towards each.
+
+%% Distance calculations
+We calculate $f_{ij}$, the pairwise number of co-affiliations between organizations within our data, calculated as the number of co-occurrences of organizations within author co-affiliation trajectories.
+Similarly, we also calculate $d_{ij}$, the pairwise geographic distance between organizations.
+Geographic distance is calculated as the great circle distance, in kilometers, between pairs of organizations. 
+When less than one kilometer, a distance of one is imputed.
+
+\subsection*{Embedding}
+%% Mobility sentences
+We embed co-affiliation trajectories by treating them analogously to sentences, and organizations analogously to words. 
+The trajectories of mobile authors were converted to ''mobility sentences`` by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:methods:mobility_sentence}.a.
+In more complex cases, such as listing multiple affiliations on the same paper or publishing with different affiliations on multiple affiliations in the same year, the order is randomized within that year, as shown in  Fig.~\ref{fig:methods:mobility_sentence}.b.
+The mean length of mobility sentences is 6.0, whereas the largest is 251.
+duplicate organization ids appearing in the same sentence are not removed.
+
+%% word2vec
+These mobility sentences are used as input to the standard skip-gram negative sampling (SGNS) model for word embedding, commonly known as \textit{word2vec} (cite). 
+In natural-language processing, word embeddings are used to construct dense vector-space representations of words and phrases, in which distance relationships between words correspond to a notion of semantic distance.
+By embedding co-affiliation trajectories, we aim to learn a dense vector for every organization where distance between vectors relates to the tendency for two organizations to co-occur in a token window around the target term in the same career trajectory.
+Vectors are learned by training a neural network to optimize the prediction of so-called context term given a target, in our case using one organization to predict the others appearing in the same co-affiliation trajectory.
+
+%% Word2vec parameters and training procedure
+The SGNS model has several tunable hyper-parameters, including the size of the learned vectors, the size of the token window  considered when training, the minimum frequency threshold for including an organization, and the number of iterations.
+We iterate through several values of vector size and window size, repeating analysis for each combination. 
+To mitigate the effect of less common organizations, only organizations appearing at least 50 times in mobility sentences are included in the embedding;
+this yields 6,580, or 76 percent of all organizations.
+We iterate the SGNS training for five epochs over all mobility sentences. 
+All word embeddings are trained using the \textit{gensim} implementation of the SGNS \textit{word2vec} model.
+
+%
+% Figure - Example of mobility sentences
+%
+\begin{figure}[ht!]
+	\centering
+	\label{fig:methods:mobility_sentence}
+	\includegraphics[width=0.7\textwidth]{\figdir/mobility_example_combined.pdf}
+	\caption{
+		\textbf{Co-affiliation trajectories represented as sentences}
+		\textbf{a.} 
+		An authors published five papers across five time periods, with only one affiliation listed in the byline of each paper. 
+		A unique identifier is assigned to each organization, and these are concatenated into a mobility sentence. 
+		\textbf{b.}
+		In a more complex case, an author lists several affiliations on the byline of papers in $t_{2}$, $t_{3}$, and $t_{4}$.
+Here, organization ids are still ordered by year, however order within a single year is random.
+	}
+\end{figure}
 

### 2020-01-26 paper/current/main.tex
added references

@@
 % Refs
-\usepackage{biblatex}
+\usepackage[style=nature,
+					backend=bibtex,
+					sortcites=true,
+					autocite=superscript
+]{biblatex}
 \addbibresource{mobility.bib}
@@
 Trajectories are constructed from author affiliations listed on the byline of publications for a given author.
-Given the limitations of author-name disambiguation, we limit to papers published after 2008, when the Web of Science began providing full names and institutional affiliations (cite) and when performance is strongest (ref to SI?).
+Given the limitations of author-name disambiguation, we limit to papers published after 2008, when the Web of Science began providing full names and institutional affiliations~\cite{caron2014disambiguation} and when performance is strongest (ref to SI?).
 This yields 37,542,144 author-affiliation representing 12,963,792 authors. 
@@
 % %Organization information
-Affiliations mapped to one of 8,661 organizations, disambiguated following a mostly manual process originally designed for the Leiden Rankings of World Universities (cite). 
+Affiliations mapped to one of 8,661 organizations, disambiguated following a mostly manual process originally designed for the Leiden Rankings of World Universities~\cite{waltman2012leidenrankings}. 
 Organizational records were associated with a full name, a type indicating the sector (e.g., University, Government, Industry), and an identifier for the country and city of the organization. 
@@
 %% word2vec
-These mobility sentences are used as input to the standard skip-gram negative sampling (SGNS) model for word embedding, commonly known as \textit{word2vec} (cite). 
+These mobility sentences are used as input to the standard skip-gram negative sampling (SGNS) model for word embedding, commonly known as \textit{word2vec}~\cite{mikolov2013word2vec} . 
 In natural-language processing, word embeddings are used to construct dense vector-space representations of words and phrases, in which distance relationships between words correspond to a notion of semantic distance.

### 2020-01-26 paper/current/main.tex
one possible title
Added distance subsection, move para accordingly

@@
 
-\title{An awesome paper} %{{{
+\title{Word2vec learns effective distance of scientific co-affiliation} %{{{
 \date{\today}
@@
 
-%% Distance calculations
-We calculate $f_{ij}$, the pairwise number of co-affiliations between organizations within our data, calculated as the number of co-occurrences of organizations within author co-affiliation trajectories.
-Similarly, we also calculate $d_{ij}$, the pairwise geographic distance between organizations.
-Geographic distance is calculated as the great circle distance, in kilometers, between pairs of organizations. 
-When less than one kilometer, a distance of one is imputed.
-
 \subsection*{Embedding}
@@
 We iterate the SGNS training for five epochs over all mobility sentences. 
-All word embeddings are trained using the \textit{gensim} implementation of the SGNS \textit{word2vec} model.
+All word embeddings are trained using the \textit{gensim} python implementation of the SGNS \textit{word2vec} model.
+
+%
+% Distances subsection
+%
+\subsection{Distance}
+%% Distance calculations
+We calculate $f_{ij}$, the pairwise number of co-affiliations between organizations, calculated as the number of co-occurrences of organizations within author co-affiliation trajectories. 
+For example, $f_{ij} = 10$ indicates that ten authors were co-affiliated with both organization $i$ and $j$ between 2008 and 2019, as evidenced from their publications. 
+In contrast to traditional mobility studies, all co-affiliations are symmetric, meaning that $f_{ij} = f_{ji}$.
+
+We also calculate two forms of proximity between organizations. 
+The geographic distance, $g_{ij}$, is the pairwise geographic distance between organizations.
+Geographic distance is calculated as the great circle distance, in kilometers, between pairs of organizations. 
+When less than one kilometer, a distance of one is imputed. 
+The embedding proximity, $d_{ij}$, is calculated as the pairwise cosine similarity between vectors from the learned organization embedding, where $v_{i}$ and $v_{j}$ represent the vectors and $d_{ij} = \frac{v_{i} \dot v_{j}}{\lVert v_{i} \rVert \lVert v_{j} \rVert}$.
 

### 2020-01-27 paper/current/main.tex
putmobility sentence figure in right place
Adding gravity law section

@@
 \def\yy#1{ {\color{red}\textbf{yy: #1}} }
+\def\dk#1{ {\color{red}\textbf{dk: #1}} }
 
@@
 
+%
+% Figure - Example of mobility sentences
+%
+\begin{figure}[ht!]
+	\centering
+	\label{fig:methods:mobility_sentence}
+	\includegraphics[width=0.7\textwidth]{\figdir/mobility_example_combined.pdf}
+	\caption{
+		\textbf{Co-affiliation trajectories represented as sentences}
+		\textbf{a.} 
+		An authors published five papers across five time periods, with only one affiliation listed in the byline of each paper. 
+		A unique identifier is assigned to each organization, and these are concatenated into a mobility sentence. 
+		\textbf{b.}
+		In a more complex case, an author lists several affiliations on the byline of papers in $t_{2}$, $t_{3}$, and $t_{4}$.
+Here, organization ids are still ordered by year, however order within a single year is random.
+	}
+\end{figure}
+
 %% word2vec
@@
 
-%
-% Figure - Example of mobility sentences
-%
-\begin{figure}[ht!]
-	\centering
-	\label{fig:methods:mobility_sentence}
-	\includegraphics[width=0.7\textwidth]{\figdir/mobility_example_combined.pdf}
-	\caption{
-		\textbf{Co-affiliation trajectories represented as sentences}
-		\textbf{a.} 
-		An authors published five papers across five time periods, with only one affiliation listed in the byline of each paper. 
-		A unique identifier is assigned to each organization, and these are concatenated into a mobility sentence. 
-		\textbf{b.}
-		In a more complex case, an author lists several affiliations on the byline of papers in $t_{2}$, $t_{3}$, and $t_{4}$.
-Here, organization ids are still ordered by year, however order within a single year is random.
-	}
-\end{figure}
+\subsection{Gravity Law}
 
-% Leiden bibliographic data
-	% Basic details
-	% How was mobility determined?
-	% How were university sizes extracted?
-	% Organization information? (count, etc.)
-% Manually-identified geographic coordiantes
-% Leiden rankings (if using prestige)
-%
+We model flow of authors across organizations, $f_{ij}$, using the gravity law. 
+the gravity law of mobility loosely derives from the physical law of gravity, whereby the attraction between two objects is a function of their mass and the distance between them.
+Given its simplicity and flexibility, this formulation and variants have proven incredibly useful for modeling and predicting many kinds of mobility~\cite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
+Following the gravity law, the expected flow between two organizations is defined as follows,
 
-%% Introduce embedding methodology and approach
-% Introduce embedding and why we use it
-% How were sentences created (use figure)
+\begin{equation}
+	\label{eq:gravity_basic}
+	f_{ij} = C\frac{m_{i}m_{j}}{f(r_{ij})}
+\end{equation}
 
-%% Gravity Law
-% Why use gravity law?
-% How were geographic distances calculated?
-% How are distnaces calculated within the embedding space
+where $m_{i}$ and $m_{j}$ are the yearly-average size of each organization during the time window, and $f(r_{ij}$ is a function of the distance between the two organizations, chosen as to fit the data, and $C$ is a constant.
+Form this standard formulation we also define what we term the \textit{flux}, or the expected flow between organizations given their size, as a function of distance,
+
+\begin{equation}
+	\label{eq:gravity_flux}
+	F_{ij} = \frac{f_{ij}}{m_{i}m_{j}} = Cf(r_{ij})
+\end{equation}
+
+\dk{We need to mention why we choose these distance functions}
+
+We consider separate variants of $f(r_{ij})$ for geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$. 
+For geographic distance, we use the power-law function of the gravity law, with $f(g_{ij})= g^{\alpha}_{ij}$, where $\alpha$ is estimated from the data. 
+For embedding distance , we use the exponential function, with $f(d_{ij}) = e^{\beta d_{ij}}$, where $\beta$ is estimated from the data. 
+To estimate parameters $\alpha$ and $\beta$ are estimated by log-transforming each variant of \label{eq:gravity_flux}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.
+
+\begin{equation}
+	\label{eq:linear_flux_geo}
+	\ln(F_{ij}) = \ln(C) - \alpha \ln(g_{ij})
+\end{equation}
+
+\begin{equation}
+	\label{eq:linear_flux_emb}
+	\ln(F_{ij}) = \ln(C) + \beta d_{ij}
+\end{equation}
+
+The gravity law of mobility is known to be sensitive to the case where $f_{ij} = 0$, or zero movement between organizations. 
+Here, non-zero flows account for only 4.2 percent of all possible pairs of  the 6,580 organizations represented in the embedding.
+This value is comparable to other common applications of the gravity law, such as to hone calls, commuting, and migration \cite{simini2012universal}.
+We follow standard practice and exclude from our analysis zero flows.
 
@@
 \section{Results}\label{sec:results} %{{{ 
-
 Let $f_{ij}$ represents the total flux (the number of people who moved) between $i$ and $j$. 

### 2020-01-27 paper/current/main.tex
Added figures with captions

@@
 All word embeddings are trained using the \textit{gensim} python implementation of the SGNS \textit{word2vec} model. 
+We visualize embeddings by projecting into two dimensions using UMAP~\cite{mcinnes2018umap}.
 
@@
 
-%% Introduce gravity measurements
+\section{Results}\label{sec:results} %{{{
 
-\section{Results}\label{sec:results} %{{{ 
+%
+% Figure - Gravity law performance
+%
+\begin{figure}[h!]
+	\centering
+	\label{fig:gravity_performance}
+	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance.pdf}
+	\caption{
+		\textbf{Embedding proximity outperform and are more robust than geographic distance.}
+		Embedding proximity (\textbf{a}) explains more of the total distance than does geographic distance (\textbf{b}). 
+		Red line is line of best fit. 
+		Black dots are mean flux across binned proximity meas.
+		Predictions  of flux between organization pairs made using embedding proximity (\textbf{c}) out-perform those made using geographic distance (\textbf{d}). 
+		Boxplots show distirbution of actual flux for binned values of predicted flux.
+		Box color corresponds to the degree to which the distribution overlaps $x = y$.
+		Predictions made for only pairs of organizations within the same country using embedding proximity (\textbf{e}) outperform those made for geographic distance (\textbf{f}).
+		Embedding proximity (\textbf{g}) also outperforms geographic distance (\textbf{h}) when predicting flux between only pairs of organizations in different countries. 
+	}
+\end{figure}
+
+%
+% Figure - 
+%
+\begin{figure}[hp!]
+	\centering
+	\label{fig:projection}
+	\includegraphics[width=\textwidth]{\figdir/Projection/big_embedding_picture.png}
+	\caption{
+		\textbf{Projection of embedding demonstrates complex multi-scale structure.}
+		\textbf{a.}
+		UMAP projection of the entire embedding space reveals geographic clustering.
+		Each point corresponds to an organization.
+		Color indicates the continent. 
+		We re-project subsets of organizational vectors to uncover more complex local structure.
+		\textbf{b.} Re-projection of organizational vectors roughly correponding to West-Asian, Southeast Asian, and South Asian countries. 
+		\textbf{c.} Re-projection of organizations in Spain, Portugal, and the Portougese- and Spanish-speaking counriees in South and Central America. 
+		\textbf{d.} Re-projection of organizations in the United States reveal geographic clustering based on state.
+		Color indicates Census Bureau-designated regions,
+		\textbf{e.} Re-projection of organizations in Massachusetts reveal clustering based on organizational sector, prestige. 
+		Color indicates sector designation of organization. 
+	}
+\end{figure}
+
 Let $f_{ij}$ represents the total flux (the number of people who moved) between $i$ and $j$. 
@@
 
+\newpage
 \printbibliography{}

### 2020-01-27 paper/current/main.tex
updated figure text, added supporting figure for gravity correlation

@@
 		\textbf{Embedding proximity outperform and are more robust than geographic distance.}
-		Embedding proximity (\textbf{a}) explains more of the total distance than does geographic distance (\textbf{b}). 
+		\textbf{a.} embedding proximity (the cosine similarity between vectors) explains more of the flux between organization pairs than does geographic distance (\textbf{b}). 
 		Red line is line of best fit. 
 		Black dots are mean flux across binned proximity meas.
-		Predictions  of flux between organization pairs made using embedding proximity (\textbf{c}) out-perform those made using geographic distance (\textbf{d}). 
+		Color indicates frequency of organization pairs within each hex bin.
+		\textbf{c-d.} Predictions  of flux between organization pairs made using embedding proximity out-perform those made using geographic distance. 
 		Boxplots show distirbution of actual flux for binned values of predicted flux.
 		Box color corresponds to the degree to which the distribution overlaps $x = y$.
-		Predictions made for only pairs of organizations within the same country using embedding proximity (\textbf{e}) outperform those made for geographic distance (\textbf{f}).
-		Embedding proximity (\textbf{g}) also outperforms geographic distance (\textbf{h}) when predicting flux between only pairs of organizations in different countries. 
+		\textbf{e-f.} Predictions made for only pairs of organizations within the same country using embedding proximity outperform those made for geographic distance.
+		\textbf{g-h.} Embedding proximity also outperforms geographic distance when predicting flux between only pairs of organizations in different countries. 
 	}
@@
 \newpage
+\section{Supporting Information}
+
+%
+% Figure - gravity correlation
+%
+\begin{figure}[hp!]
+	\centering
+	\label{fig:projection}
+	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_correlations.pdf}
+	\caption{
+		\textbf{Embedding proximity explains more variance for global, within, and between country flux than geographic distance.}
+		\textbf{a.}
+		Embedding proximity (cosine similarity between vectors) explains more of the total distance than does geographic distance (\textbf{b}). 
+		Red line is line of best fit. 
+		Black dots are mean flux across binned proximity meas.
+		Color indicates frequency of organization pairs within each hex bin.
+		Results here are identical to those shown in Fig.~\ref{fig:gravity_performance}a and Fig.~\ref{fig:gravity_performance}.
+		\textbf{c-d.}	embedding proximity explains more variance when considering only pairs of organizations within the same country. 
+		\textbf{e-f.} embedding proximity more robust than geographic distance for pairs of organizations in different countries. 
+	}
+\end{figure}
+
 \printbibliography{}

### 2020-01-27 paper/current/main.tex
Added formatting for supporting information
Added descriptive supporting figure showing reverse cdf of #affiliations by geo scale

@@
 \def\figdir{../Figs}
+
+% define a command to setup the format of supporting infomration figures and tables. 
+% source: http://bytesizebio.net/2013/03/11/adding-supplementary-tables-and-figures-in-latex/
+\newcommand{\beginsupplement}{%
+        \setcounter{table}{0}
+        \renewcommand{\thetable}{S\arabic{table}}%
+        \setcounter{figure}{0}
+        \renewcommand{\thefigure}{S\arabic{figure}}%
+     }
 
@@
 \section{Supporting Information}
+\beginsupplement
 
+%
+% Figure - reverse CDF by scale
+%
+\begin{figure}[hp!]
+	\centering
+	\label{fig:supp:rcdf_by_scale}
+	\includegraphics[width=0.8\textwidth]{\figdir/Descriptive/rcdf_by_scale.pdf}
+	\caption{
+		\textbf{Reverse cumulative-distribution function of mobile authors by geographic scale.}
+		\textbf{a.}
+		Proportion of mobile authors by how many organizations are represented 	in their career trajectories. 
+		For example, for mobile authors, 100 percent of authors held an affiliation with at least two organizations, whereas about 35 percent were affiliated with 3 ore more organizations between 2008 and 2019.
+		Mobile authors are defined as those with at least two distinct organizational affiliations represented in our data. 
+		\textbf{b.} 68 percent of mobile authors have at least two cities represented in their career trajectories.
+		\textbf{c.} 45 percent of mobile authors have 2 or more regions represented in their career trajectories.
+		\textbf{d.} Only 14 percent of mobile authors had 2 or more countries represented in their career trajectories. 
+	}
+\end{figure}
+
+\newpage
 %
@@
 	\centering
-	\label{fig:projection}
+	\label{fig:supp:gravity_correlation}
 	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_correlations.pdf}

### 2020-01-27 paper/current/main.tex
Supp figure for absolute and proportion publications over time

@@
 Each author-affiliation combination is associated with the publication year and a unique id that maps the affiliation to a disambiguate organization. 
+Combinations are also associated with a publication-level disciplinary classification, one of ``Social sciences and humanities'',
+``Biomedical and health sciences'', ``Physical sciences and engineering'', ``Life and earth sciences'', and ``Mathematics and computer science''.
 Trajectories are represented as the list of author-affiliation combinations, ordered by year of publication, and randomly ordered for combinations within the same year. 
@@
 \newpage
+\beginsupplement
 \section{Supporting Information}
-\beginsupplement
 
+%
+% Figure - publications over time
+%
+\begin{figure}[p!]
+	\centering
+	\label{fig:supp:pubs_over_time}
+	\includegraphics[width=\textwidth]{\figdir/Descriptive/pubs_over_time.pdf}
+	\caption{
+		\textbf{Publications over time.}
+		\textbf{a.}
+		The number of papers published by mobile authors has been steadily increasing from 2008 to 2017, with a small decrease in 2018,  likely an artifact of the Web of Science indexing process.
+		Lines corresponds to publications by mobile authors (org, purple), by authors with affiliations in at least two cities (blue), at least two regions (green), and at least two countries (yellow).
+		There is no evidence of major changes in publication patterns of mobile authors during this time period. 
+		\textbf{b.}
+		Lines correspond to the proportion of publications classified as Biology and Health (black), Physics and Engineering (purple), Life and Earth Science (magenta), Social Science and Humanities (orange), and Math and Computer Science (yellow).
+		The rate of publication in Biology and Health has leveled since about 2013, whereas the rate of publication in other fields has steadily increased. 
+		\textbf{c.} 
+		Despite increasing absolute counts, the percentage of mobile scholars, and those with at least two city, regional, or country affiliations, as a proportion of all publications, has decreased over time.
+		\textbf{d.} 
+		The proportion of authors publications across fields has largely remained steady.
+		Biology and Health Science has comprised the majority of publications across nearly all years, but has steadily declined in proportion. 
+		However, the proportion of Social Science and Humanities publications has been steadily increasing. 
+	}
+\end{figure}
+
+\newpage
 %
@@
 %
-\begin{figure}[hp!]
+\begin{figure}[p!]
 	\centering
@@
 
-\newpage
+\clearpage
 \printbibliography{}

### 2020-01-27 workflow/scripts/PlotPropOverTime.R

@@ -59,17 +59,18 @@ plotdata <- flows.withmeta %>%
     Scale = factor(Scale,
                  levels = c("count_org_mobile", "count_city_mobile", "count_region_mobile", "count_country_mobile"),
                  labels = c("Org", "City", "Region", "Country"))
+  ) %>%
+  group_by(Scale, pub_year) %>%
+  summarize(
+    prop = value / count
   )
 
 # Draw the plot
 plot <- plotdata %>%
-  ggplot(aes(x = pub_year, y = value, group = Scale, fill = Scale)) +
+  ggplot(aes(x = pub_year, y = prop, group = Scale, fill = Scale)) +
   geom_line() +
   geom_point(size = 3, shape = 21) +
-  expand_limits(y = 0) + # Make sure that y=axis stretches to 0
-  scale_y_continuous(limits = c(0, 3000000),
-                     breaks = c(0, 1000000, 2000000, 3000000),
-                     labels = c("0", "1,000,000", "2,000,000", "3,000,000")) +
+  ylim(0, 1) +
   viridis::scale_fill_viridis(discrete = T) +
   guides(fill = guide_legend(ncol = 2)) +
   theme_minimal() +
@@ -81,7 +82,7 @@ plot <- plotdata %>%
     legend.position = c(0.2, 0.85),
     legend.background = element_rect()
   ) +
-  ylab("Count")
+  ylab("Proportion")
 
 p <- egg::set_panel_size(plot,
                          width  = unit(FIG_WIDTH, "in"),

### 2020-01-28 paper/current/main.tex
new figure to show how embedding performance differs by choice of params

@@
 
+%
+% Figure - Hyperparameter performance
+%
+\begin{figure}[p!]
+	\centering
+	\label{fig:supp:hyperparams}
+	\includegraphics[width=\textwidth]{\figdir/Descriptive/hyperparameter_performance.pdf}
+	\caption{
+		\textbf{Larger dimensions, smaller window size improves embedding performance.}
+		The correlation, or amount of flux explained by the embedding proximity with varying skip-gram negative sampling hyperparameters. 
+		Window size refers to the window, on either side of the target token, to use as context for training. 
+		Smaller window sizes results in an embedding that explain more of the flux. 
+		Embedding dimensions refer to the size of the organization vector.
+		Larger vectors perform better, though little difference between 200 and 300. 
+		All variants perform better on same-country pairs of organizations than on all organizations.
+		All variants perform worse on different-country pairs on organizations.
+		Larger embeddings outperform mid-size embeddings for the different-country case.
+	}
+\end{figure}
+
 \newpage

### 2020-01-28 paper/current/main.tex
Added plot showing predicted vs. actual using global orgs, not subsets

@@
 		\textbf{c-d.} Predictions  of flux between organization pairs made using embedding proximity out-perform those made using geographic distance. 
-		Boxplots show distirbution of actual flux for binned values of predicted flux.
+		Boxplots show distribution of actual flux for binned values of predicted flux.
 		Box color corresponds to the degree to which the distribution overlaps $x = y$.
-		\textbf{e-f.} Predictions made for only pairs of organizations within the same country using embedding proximity outperform those made for geographic distance.
-		\textbf{g-h.} Embedding proximity also outperforms geographic distance when predicting flux between only pairs of organizations in different countries. 
+		\textbf{e-f.} Predictions made using model parameters learned from subset of same-country organization pairs. 
+		Embedding proximity outperform those made for geographic distance.
+		\textbf{g-h.} Embedding proximity also outperforms geographic distance when predicting flux using model parameters estimated from only pairs of organizations in different countries. 
+		Predictions are not meaningfully different if estimates are learned on all pairs of organizations (Fig. S\ref{fig:supp:gravity_prediction_subsets}).
 	}
@@
 
+%
+% Figure - gravity predictions based on subset or global
+%
+\begin{figure}[p!]
+	\centering
+	\label{fig:supp:gravity_prediction_subsets}
+	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_different_fits.pdf}
+	\caption{
+		\textbf{Little difference between gravity predictions fit on all or subsets of data.}
+		Predictions  of flux between organization pairs made using embedding proximity out-perform those made using geographic distance. 
+		Boxplots show distribution of actual flux for binned values of predicted flux.
+		Box color corresponds to the degree to which the distribution overlaps $x = y$.
+		\textbf{a-b.} Predictions are made with parameter, estimating parameters from all pairs of organizatioons, making global predictions (as in Fig.~\ref{fig:gravity_performance}c), and showing only subsets of predictions for organization pairs in the same country (\textbf{a}) and in different countries (\textbf{b}).
+		\textbf{c-d.} Predictions made by estimating gravity law parameters on subset of organizations in the same country (\textbf{c}) and different country \textbf{d}); 
+		this is the same data as shown in Fig.~\ref{fig:gravity_performance}f and Fig.~\ref{fig:gravity_performance}h. 
+	}
+\end{figure}
+
 \clearpage

### 2020-01-28 workflow/scripts/GetAggregateGravityR2.R
reduce the number of replcations for bootstrapping, CIs are small anyway

@@ -7,7 +7,7 @@
 # stores them all into a single file
 #
 
-NUM_REPLICATIONS = 100
+NUM_REPLICATIONS = 50
 NUM_WORKERS = 4
 
 

### 2020-01-30 paper/ic2s2-2020/ic2s2_mobility_emb.tex
Updated text of ic2s2 paper

@@
 
-Scientific mobility is closely linked to impact~\autocite{sugimoto_scientists_2017} and is an essential component of the scientific ecosystem.
-This mobility is shaped by many factors, including geography, prestige, and policy\autocite{deville_career_2014,clauset_systematic_2015}.
-Such complexity has resulted in a fragmented understanding of scientific mobility, limited to specific regions and mobility types.
+Scientific mobility is closely linked to impact, innovation, and knoweldge diffusion~\autocite{sugimoto_scientists_2017, wagner_new_2008}.
+Central to mobility is the notion of proximity~\autocite{torre_proximity_2005} between places — in the case of scientific mobility, research organizations. 
+However, geography itself in insufficient to understand mobility, and other forms of proximity are too intangible to meaningfully measure~\autocite{boschma_proximity_2005}, 
+resulting in a fragmented and incomplete understanding of scientific mobility.
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{../Figs/ic2s2-2020/ic2s2_2020_mainfig.pdf}
+	\includegraphics[width=0.97\textwidth]{../Figs/ic2s2-2020/ic2s2_2020_mainfig.pdf}
 	\caption{ 
@@
 We leverage recent advances in neural networks and representation learning to construct a dense, meaningful, and coherent vector-space embedding of global scientific mobility, using individual mobility trajectories documented in bibliographic data.
-This representation facilitates the holistic study of scientific mobility, capturing the complex relationships between organizations around the world.
+This representation implicitely captures organizational and cognitive proximity between organizations~\autocite{boschma_proximity_2005}, allowing for the holistic study of scientific mobility.
 
@@
 
-We visualize the embedding using UMAP~\autocite{mcinnes_umap_2018} and observe strong geographic clustering (Fig~\ref{fig:image}.g), while also reflecting a mix of historical, religious, and linguistic relationships between countries.
+We visualize the embedding using UMAP~\autocite{mcinnes_umap_2018} and observe strong geographic clustering (Fig~\ref{fig:image}.g), while also reflecting a mix of historic, cultural, and linguistic relationships between countries.
 For example, South American countries are near Spain and Portugal and organizations in French-speaking Quebec and North Africa are nearer France. 
@@
 For example, the structure of U.S.
-universities demonstrates state-level geographic clustering (Fig~\ref{fig:image}.h) roughly organized by state and region, whereas Massachusetts (Fig~\ref{fig:image}.i) instead shows structure based on urban centers (Boston vs.
+universities demonstrates state-level geographic clustering (Fig~\ref{fig:image}.h) roughly organized by state and region, whereas states such as Massachusetts (Fig~\ref{fig:image}.i), California, and New York (not shown) instead show structure based on urban centers (Boston vs.
 Worcester), organization type (hospitals tend to be adjacent) and different university systems (UMass system cluster separate from Harvard, MIT, etc.).
@@
 \setstretch{0.8}
+\setlength\bibitemsep{1pt}
+{
 \small
-\setlength\bibitemsep{1pt}
-{\renewcommand{\markboth}[2]{}% Remove header adjustment
-\printbibliography}
+\renewcommand{\markboth}[2]{}% Remove header adjustment
+\printbibliography
+}
 \endgroup

### 2020-01-31 paper/current/main.tex
basic .tex cleanup and structuring of results section
removed "we" para openings, simplified intro.

@@
 %
+% Subsection: Embedding performance
+%
+\subsection*{Embedding performance}
+
+%
 % Figure - Gravity law performance
@@
 %
+% Subsection: Applications
+%
+\subsection*{Applications}
+% Here we will examine several applications of this effective distnace, including for clustering, visualization + descriptive analysis, and maybe something else?
+
+%
 % Figure - 
@@
 \end{figure}
+
+%
+% Subsection: Mathematical Exploration
+%
+\subsection*{Mathematical Exploration}
 
@@
 \end{equation}
-
-%\begin{minipage}{\figwidth} 
-%\includegraphics[width=\linewidth]{\figdir/img} 
-%\end{minipage}
 
@@
 		However, the proportion of Social Science and Humanities publications has been steadily increasing. 
+	}
+\end{figure}
+
+%
+% Figure - publications over time
+%
+\begin{figure}[p!]
+	\centering
+	\label{fig:supp:pubs_over_time}
+	\includegraphics[width=\textwidth]{\figdir/Descriptive/mobility_by_country.pdf}
+	\caption{
+		\textbf{Extend and nature of mobility by country.}
+		\textbf{a.}
+		Proportion of researchers in each country classified as mobile, meaning that they have at least two organization affiliations within the period of study. 
+		The countires with the most mobile researchers are the United States, China, France, Great Britain, and Germany. 
+		\textbf{b.}
+		The same information, arranged into a cumulative distribution.
+		The five countires with the highest mobility account for a total of 
 	}

### 2020-02-03 paper/ic2s2-2020/ic2s2_mobility_emb.tex

@@
 Scientific mobility is closely linked to impact, innovation, and knoweldge diffusion~\autocite{sugimoto_scientists_2017, wagner_new_2008}.
-Central to mobility is the notion of proximity~\autocite{torre_proximity_2005} between places — in the case of scientific mobility, research organizations. 
-However, geography itself in insufficient to understand mobility, and other forms of proximity are too intangible to meaningfully measure~\autocite{boschma_proximity_2005}, 
-resulting in a fragmented and incomplete understanding of scientific mobility.
+Central to mobility is the notion of proximity~\autocite{torre_proximity_2005} between places.
+However, geography alone is insufficient to understand scientific mobility, whereas other kinds of proximity are difficult to meaningfully measure~\autocite{boschma_proximity_2005}.
+The result is a fragmented and partial understanding of scientific mobility.
 
@@
 	\centering
-	\includegraphics[width=0.97\textwidth]{../Figs/ic2s2-2020/ic2s2_2020_mainfig.pdf}
+	\includegraphics[width=\textwidth]{../Figs/ic2s2-2020/ic2s2_2020_mainfig.pdf}
 	\caption{ 
@@
 
-We leverage recent advances in neural networks and representation learning to construct a dense, meaningful, and coherent vector-space embedding of global scientific mobility, using individual mobility trajectories documented in bibliographic data.
+Leveraging recent advances in neural networks and representation learning, we construct a dense, meaningful, and coherent vector-space embedding of global scientific mobility, using individual mobility trajectories documented in bibliographic data.
 This representation implicitely captures organizational and cognitive proximity between organizations~\autocite{boschma_proximity_2005}, allowing for the holistic study of scientific mobility.
@@
 
-We show that similarity between vectors in the embedding space can be considered as a reasonable measure of effective distance. 
+Similarity between vectors in the embedding space can be considered as a reasonable measure of effective distance. 
 The cosine similarity between vectors can explain more than twice the variance in mobility between pairs of organizations than geographic distance (Fig~\ref{fig:image}.c). 
 Moreover, applying the gravity law of mobility~\autocite{simini_universal_2012} with cosine similarity produces better predictions of mobility than does using geographic distance (Fig~\ref{fig:image}.d.
-These predictions are also more robust than geographic distance when considering only same-country (Fig~\ref{fig:image}.e) and different-country (Fig~\ref{fig:image}.f) mobility.
+These predictions are also more robust than geographic distance when considering only mobility between organizations in the same-country (Fig~\ref{fig:image}.e) and in different countries (Fig~\ref{fig:image}.f).
 
-We visualize the embedding using UMAP~\autocite{mcinnes_umap_2018} and observe strong geographic clustering (Fig~\ref{fig:image}.g), while also reflecting a mix of historic, cultural, and linguistic relationships between countries.
+Visualizing the embedding using UMAP~\autocite{mcinnes_umap_2018} reveals organizational clusters that reflect a mix of geographic, historic, cultural, and linguistic relationships between countries (Fig~\ref{fig:image}.g).
 For example, South American countries are near Spain and Portugal and organizations in French-speaking Quebec and North Africa are nearer France. 

### 2020-02-03 workflow/scripts/PlotPredictedVsActual.R
Add RMSE to the predictes. vs. actual plot, change #bins

@@ -7,7 +7,7 @@
 #
 
 # Plotting options
-NUM_BINS = 30
+NUM_BINS = 36
 
 COLOR_BAD_FIT = "white"
 COLOR_GOOD_FIT = "#1E88E5"
@@ -77,7 +77,8 @@ binned <- data %>%
     crosses_ab_weak = (percentile_max > pos & pos > mu) | (percentile_min < pos & pos < mu),
   )
 
-print(binned)
+error <- sqrt(mean((log10(data$expected) ^ 2) - (log10(data$actual) ^ 2)))
+
 # Build the plot
 plot <- data %>%
   ggplot(aes(x = log10(expected), y = log10(actual))) +
@@ -119,6 +120,12 @@ plot <- data %>%
                      labels = function(x) { parse(text=paste0("10^", x)) },
                      expand = c(0, 0)) +
   coord_fixed() +
+  annotate(geom = "text",
+           x = 1.2,
+           y = 6.2,
+           label = paste0("Err = ", round(error, 2)),
+           size = 7
+         ) +
   # Define the gradient
   scale_fill_gradientn(colours=c(FILL_GRADIENT_MIN, FILL_GRADIENT_MAX),
                        name = "Frequency",

### 2020-02-03 workflow/scripts/PlotHyperparameterPerformance.R
Add proper axes to hyperparameter performance plot

@@ -9,7 +9,7 @@
 
 # Plot dimensions
 FIG_WIDTH = 7
-FIG_HEIGHT = 4
+FIG_HEIGHT = 5
 
 
 library(readr)
@@ -46,7 +46,15 @@ plot <- plotdata %>%
     geom_line() +
     geom_linerange(aes(ymin = ci.lower, ymax = ci.upper)) +
     facet_grid(traj~case) +
-    scale_color_manual(name = "Embedding Dimension", values = c("#b2bec3", "#636e72", "#2d3436")) +
+    scale_x_continuous(breaks = unique(plotdata$ws)) +
+    scale_y_continuous(
+      limits = c(0.2, 0.6),
+      breaks = c(0.2, 0.4, 0.6)
+    ) +
+    scale_color_manual(
+      name = "Embedding Dimension",
+      values = c("#b2bec3", "#636e72", "#2d3436")
+    ) +
     scale_shape_discrete(name = "Embedding Dimension") +
     theme_minimal() +
     theme(
@@ -55,7 +63,7 @@ plot <- plotdata %>%
       axis.title = element_text(size = 12),
       legend.title = element_text(size = 12, face = "bold"),
       legend.position = "bottom",
-      panel.grid.major = element_blank(),
+      panel.grid.minor = element_blank(),
       panel.spacing = unit(1.5, "lines")
     ) +
     xlab("Window Size") +

### 2020-02-03 paper/current/main.tex
Update draft with new text for precedence data, new numbers

@@
 Given the limitations of author-name disambiguation, we limit to papers published after 2008, when the Web of Science began providing full names and institutional affiliations~\cite{caron2014disambiguation} and when performance is strongest (ref to SI?).
-This yields 37,542,144 author-affiliation representing 12,963,792 authors. 
+This yields 33,934,672 author-affiliation combinations representing 112,963,792 authors. 
 Each author-affiliation combination is associated with the publication year and a unique id that maps the affiliation to a disambiguate organization. 
@@
 Authors are classified as mobile when they have at least two distinct organization ids in their trajectory, meaning that they have published using two or more distinct affiliations between 2008 and 2019.
-Mobile authors constitute 3,709,869 or 28.6 percent of all authors, and 22,436,637 author-affiliation combinations.
 
@@
 
+Some affiliations are mapped to two organizations, one specific, and one more general, as a result of the disambiguation procedure. 
+For example, any author affiliated with the "Indiana University Bloomington" will also be listed as being affiliated with the "Indiana University System", a more general designation for all public universities in Indiana.
+However, a more general organization may not always occur alongside the more specific one.
+For example, a researcher affiliated with the smaller regional school "Indiana University South Bend" will be listed as affiliated with only the "Indiana University System". 
+We identify all specific organizations that always co-occur along a more general one.
+For every career trajectory that includes one of these specific organizations, we remove all occurrences of the more general organization;
+trajectories containing only a general designation are not altered.
+
+Scientific mobility is complex and can be defined in many possible ways~\cite{robinson2019mobility}.
+Here, we consider an author as mobile when at least two distinct organizational affiliations appear in their trajectory during the 2008-2019 time window. 
+Under this definition, mobile authors constitute 3,007,192 or 23.2 percent of all authors, and 17,700,095 author-affiliation combinations. 
+Mobile authors were associated with, on average, 2.5 distinct organizational affiliations. 
+Rates of mobility tended to differ across country. 
+For example, France, Qatar, the USA, Iraq, and Luxembourg had the most mobile authors (ref figure).
+However, due to their size, the USA, accounted for nearly 40 percent of all mobile authors worldwide, with  10 countries accounting for 80 percent of all mobility (ref figure).
+In most cases, countries with a high degree inter-organization mobility also had a high degree of international mobility;
+however, the USA and France had a high degree of inter-organization mobility with the corresponding international mobility (ref figure).
+
 \subsection*{Embedding}
@@
 In more complex cases, such as listing multiple affiliations on the same paper or publishing with different affiliations on multiple affiliations in the same year, the order is randomized within that year, as shown in  Fig.~\ref{fig:methods:mobility_sentence}.b.
-The mean length of mobility sentences is 6.0, whereas the largest is 251.
-duplicate organization ids appearing in the same sentence are not removed.
 

### 2020-02-18 lib/py_scimobility/py_scimobility/core.py
Basic packaging setup

@@ -1,0 +1,19 @@
+""" core utils for the project """
+import os
+import numpy as np
+
+from geopy.distance import great_circle
+
+
+def compute_geo_distance(u, v):
+    """Compute geographic distance (great circle), between two
+       sets of coordinates. Outputs NaN when any distnace is NaN
+
+    arguments:
+    u -- First coordinate, list in form [<lat>, <lon>]
+    v -- Second coordinate, list in form [<lat>, <lon>]
+    """
+    if np.isnan([u[0], u[1], v[0], v[1]]).any():
+        return(np.nan)
+    else:
+        return(great_circle(u, v).kilometers)

### 2020-02-18 lib/py_scimobility/setup.py

@@ -1,0 +1,13 @@
+""" setup script for science mobility embedding project project. """
+#!/usr/bin/env python
+# encoding: utf-8
+
+from setuptools import find_packages
+from setuptools import setup
+
+setup(name='py_scimobility',
+      version='0.1',
+      description='package for the science mobility embedding project',
+      author='Dakota Murray, Jisung Yoon, YY Ahn',
+      packages=find_packages(exclude=('tests',)),
+     )

### 2020-02-18 workflow/scripts/calculate_org_geo_distance.py
Use package verison of geographic distance calculation

@@ -12,6 +12,8 @@ import numpy as np
 from scipy.spatial.distance import pdist, squareform
 from geopy.distance import great_circle
 
+import py_scimobility.core as mob
+
 import logging
 logging.basicConfig(format='%(levelname)s:%(message)s', level=logging.INFO)
 
@@ -30,20 +32,12 @@ args = parser.parse_args()
 logging.info('Loading organization transitions')
 organizations = pd.read_csv(args.input, sep = "\t", encoding = "ISO-8859-1")
 
-# Small helper function to help us compute distnace. basically, just output
-# a NaN when the distances are NaN. Otherwise, compute the distance.
-def compute_distance_helper(u, v):
-    if np.isnan([u[0], u[1], v[0], v[1]]).any():
-        return(np.nan)
-    else:
-        return(great_circle(u, v).kilometers)
-
 
 coordinates = [[row.latitude, row.longitude] for index, row in organizations.iterrows()]
 
 # Using the vincenty distance function.
 logging.info('Computing geographic distances')
-dist = pdist(coordinates, lambda u, v: compute_distance_helper(u, v))
+dist = pdist(coordinates, lambda u, v: mob.compute_geo_distance(u, v))
 
 # Convert distance matrix to a dataframe
 distance_df = pd.DataFrame(squareform(dist))

### 2020-02-18 lib/py_scimobility/py_scimobility/tests/test_core.py
basic testing framework

@@ -1,0 +1,46 @@
+from unittest import TestCase
+import warnings
+
+import py_scimobility.core as mob
+
+import numpy as np
+
+class Test_ComputeGeoDistance(TestCase):
+
+    def test_with_all_nan(self):
+        """
+        Test to ensure that input of all NaN returns NaN
+        """
+        distance = mob.compute_geo_distance([np.nan, np.nan], [np.nan, np.nan])
+        self.assertTrue(np.isnan(distance))
+
+    def test_with_one_nan(self):
+        """
+        Test to ensure that input of one NaN returns NaN
+        """
+        distance = mob.compute_geo_distance([1, 1], [-1, np.nan])
+        self.assertTrue(np.isnan(distance))
+
+    def test_with_same_coords(self):
+        """
+        Test that same coordinates returns distance of zero
+        """
+        distance = mob.compute_geo_distance([1, 1], [1, 1])
+        self.assertTrue(distance == 0)
+
+    def test_with_diff_coords_nonzero(self):
+        """
+        Test that different coordinates returns non-zero distance
+        """
+        distance = mob.compute_geo_distance([1, 1], [-1, -1])
+        self.assertTrue(distance > 0)
+
+    def test_with_invalid_coords(self):
+        """
+        Test that invalid coordinates returns NaN
+        """
+        with self.assertRaises(Exception) as context:
+            distance = mob.compute_geo_distance([500, 500], [500, 500])
+            print(distance)
+
+        self.assertTrue(isinstance(context.exception, ValueError))

### 2020-02-18 test_py.sh

@@ -1,0 +1,5 @@
+
+#!/bin/bash
+
+# Run tests
+python -m unittest lib/py_scimobility/py_scimobility/tests/test_core.py

### 2020-02-18 lib/py_scimobility/py_scimobility/tests/test_core.py
additional unit test

@@ -44,3 +44,13 @@ class Test_ComputeGeoDistance(TestCase):
             print(distance)
 
         self.assertTrue(isinstance(context.exception, ValueError))
+
+    def test_flipped_coords(self):
+        """
+        Test that invalid coordinates returns NaN
+        """
+        distance1 = mob.compute_geo_distance([1, -1], [2, -2])
+        distance2 = mob.compute_geo_distance([2, -2], [1, -1])
+
+        # Some difference is expected, check that they are nearly the same
+        self.assertAlmostEqual(distance1, distance2)

### 2020-02-18 lib/py_scimobility/py_scimobility/SemAxis.py
Offload SemAxis functions to package

@@ -1,0 +1,35 @@
+"""
+SemAxis utils
+
+Adapted from the SemAxis approach authored by Jisun An, Haewoon Kwak,
+and Yong-Yeol Ahn at the following repository:
+
+https://github.com/ghdi6758/SemAxis
+
+"""
+import numpy as np
+from gensim.models import Word2Vec
+from scipy import spatial
+
+# Functions should be offloaded to a package at a later date,
+def get_avg_vec_from_list(emb, wordlist):
+    """Calculate the average vector in a word2vec embedding model
+       from the provided list of terms
+
+    arguments:
+    emb -- Word2vec embedding model
+    wordlist -- The list of terms in the model
+    """
+    tmp = [emb.wv[word] for word in wordlist if word in emb.wv.vocab]
+    return np.mean(tmp, axis=0)
+
+def project_onto_axis(emb, word, antonym):
+    """Project word in model onto the defined antonym axis
+
+    arguments:
+    emb -- Word2vec embedding model
+    word -- The term to project onto the antonym axis
+    antonym -- List of two vectors to be used as the poles of the antonym axis
+    """
+    axis = antonym[1] - antonym[0]
+    return(1.0 - spatial.distance.cosine(emb.wv[word], axis))

### 2020-02-18 workflow/scripts/calculate_SemAxis_projections.py

@@ -11,9 +11,8 @@ by individual.
 from gensim.models import Word2Vec
 import pandas as pd
 
-# For SemAxis
-import numpy as np
-from scipy import spatial
+import py_scimobility.SemAxis as sx
+
 import argparse
 
 parser = argparse.ArgumentParser()
@@ -36,15 +35,6 @@ parser.add_argument(
 parser.add_argument("-o", "--output", help="Output data path", type=str, required=True)
 args = parser.parse_args()
 
-# Functions should be offloaded to a package at a later date,
-def get_avg_vec_from_list(emb, wordlist):
-    tmp = [emb.wv[word] for word in wordlist if word in model.wv.vocab]
-    return np.mean(tmp, axis=0)
-
-def project_onto_axis(emb, word, antonym):
-    axis = antonym[1] - antonym[0]
-    return(1.0 - spatial.distance.cosine(emb.wv[word], axis))
-
 # Load the word2vec model
 model = Word2Vec.load(args.input)
 vocab = model.wv.vocab
@@ -60,14 +50,14 @@ pole1, pole2 = list(set(axis['type']))
 pole1_orgs = [str(org) for org in axis[axis.type == pole1]['cwts_org_no']]
 pole2_orgs = [str(org) for org in axis[axis.type == pole2]['cwts_org_no']]
 
-pole1_avg = get_avg_vec_from_list(model, pole1_orgs)
-pole2_avg = get_avg_vec_from_list(model, pole2_orgs)
+pole1_avg = sx.get_avg_vec_from_list(model, pole1_orgs)
+pole2_avg = sx.get_avg_vec_from_list(model, pole2_orgs)
 
 orgs = []
 sims = []
 for org in vocab:
     orgs.append(org)
-    sims.append(project_onto_axis(model, org, [pole1_avg, pole2_avg]))
+    sims.append(sx.project_onto_axis(model, org, [pole1_avg, pole2_avg]))
 
 # Convert to dataframe and save
 df = pd.DataFrame({"cwts_org_no": orgs, "sim": sims})

### 2020-02-18 notebooks/20191205_model_fitting_exp.rmd
Add miscelaneous notebooks that have not yet been version controlled

---
title: "Mobility Aggregate R2 plot"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

In this notebook I will attempt to work through the calculations for estimating the parameters of the standard gravity model using OLS regression and compare the set of predicted fluxes between organizations against the actual ones. First, I will load the data and quickly format it:
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(readr)

agg <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Descriptive/org/2008-2019_aggregate_org_distances_d100_ws2.csv") %>%
  filter(count > 0) %>%
  rename(actual = count) %>%
  select(org1_size, org2_size, actual, geo_distance, emb_similarity, gravity)

head(agg)
```

For the basic gravity model estimation based on geographic distance, I am following the procedure outlined in the 2011 paper by Simini et al., titled *"A universal model for mobility and migration patterns"*, which is listed in their supplamental materials, [linked here](https://arxiv.org/ftp/arxiv/papers/1111/1111.0586.pdf), on page 27-29. This procedure assumes a gravity law defined as follows:

$$F_{ij} = C \frac{m_{i}^{\alpha}n_{j}^{\beta}}{r_{ij}^{\gamma}}$$

where $F_{ij}$ is the flux, or in our case the degree of co-affiliation, between organizations $i$ and $j$, $m_{i}$ is the "mass" or the population of organization $i$, $n_{j}$ is similariy the "mass" or size of organization $j$. $r_{ij}$ is the geographic distance (here in kilometers) between the two organizations, which serves as our decay function. Note that we are considering only the power law decay function, whereas we might in the future extend to the exponential decay function, $e^{dr_{ij}}$. $C$, $\alpha$, $\beta$, and $\gamma$ are all contants that can be estimated from the data.

Following the procedure in Simini et al., (2011), we estimate the constant parameters from the data using a simple OLS regression. The form of the regression equation, after taking the (natural) logarithm of both sides is:

$$
\ln(F_{ij}) = \ln(C) + \alpha\ln(m_{i}) + \beta\ln(n_{j}) - \gamma\ln(r_{ij})
$$

The original Simini et al., paper used a more complex, 9-parameter equation, as they fit short and long distances separately. I do not currently use this approach, as "short" distnaces make less sense in the case of our data. However, extending to this more complex case appears mostly straightforward.

```{r}
# Perform the regression
fit <- lm(log(actual) ~ log(org1_size) + log(org2_size) + log(geo_distance), data = agg)
summ <- summary(fit)

# Save the coefficients for use later
intercept <- summ$coefficients["(Intercept)", "Estimate"]
org1_coef <- summ$coefficients["log(org1_size)", "Estimate"]
org2_coef <- summ$coefficients["log(org2_size)", "Estimate"]
geo_coef <- summ$coefficients["log(geo_distance)", "Estimate"]

# Display a summary of the regression
summary(fit)
```

Using these coefficients, we will calculated the expected flux, $F_{ij}^{\text{e}}$, for every pair of organizations in our dataset. To do so, we simply plug the constants back into the original gravity equation
```{r}
agg <- agg %>%
  # add a variable
  mutate(
    expected = intercept * (org1_size ^ org1_coef) * (org2_size ^ org2_coef) / (geo_distance ^ abs(geo_coef))
  )

head(agg %>% select(expected, actual))
```

We can build a figrue from the expected and actual counts as follows. Here, the expercted fluxes between pairs of organizations are all displayed on the x-axis, whereas the actual fluxes are displayed on the y-axis. Each point represents a pair of organizations. The red points represent the mean and 99th percentile confidence intervals of the actual flux within a window/bin of the expected flux. The blue line is the line of $y = x$; points are near to the line when the expected flux matches the actual flux. 
```{r message=FALSE, warning=FALSE}
# Create binned values that will be plotted over top
binned <- agg %>%
  mutate(
    expected = log10(expected),
    bin = cut(round(expected, 2), 30)
  ) %>%
  arrange(bin) %>%
  group_by(bin) %>%
  summarize(
    # Plot the point at the midpoint in each bin
    pos = min(expected) + ((max(expected) - min(expected)) / 2),
    #pos = (as.numeric(first(bin)) * 0.05) - 0.025,
    mu = mean(log10(actual), na.rm = T),
    ci = 2.576 * (sd(log10(actual), na.rm = T) / sqrt(n())) # using the 99th percentile CI
  )

agg %>%
  sample_n(50000) %>% # take only a sample of the data, in order to keep the time drawing points low
  ggplot(aes(x = log10(expected), y = log10(actual))) +
  geom_point(alpha = 0.01) +
  #geom_hex(bins = 30, color = "white", aes(alpha = ..count..)) +
  scale_fill_gradient(low = "white", high = "black") +
  geom_pointrange(data = binned, aes(x = pos, y = mu, ymin = mu - ci, ymax = mu + ci), color = "red", size = 1, shape = 21, stroke = 2) +
  xlim(0, 4) +
  ylim(0, 4) +
  geom_abline(color = "blue") +
  guides(alpha = F) +
  theme_minimal() +
  theme(
    panel.grid.minor = element_blank(),
    axis.title = element_text(size = 14)
  ) +
  xlab("Log10(expected flux)") +
  ylab("Log10(actual flux)")
```

Now, we can repeat this entire process, but instead of calculating a decay function based on geographic distnace, as was the case for the traditional gravity model, we will instead consider the cosine similarity from our embeddings as the decay function—as cosine similarity goes down, the relationship between two organization fades.

Unlike geogrpahic distnace, for which the logarithm makes sense, cosine similarity sits on a scale between 0 and 1, and so we should approach it in a different way. Here, our gravity law equation looks like the following:

$$F_{ij} = C \frac{m_{i}^{\alpha}n_{j}^{\beta}}{\cos (i, j)^{\gamma}}$$

As before, we will attempt to estimate each of the parameters using OLS regression, but we will treat the embedding similarity as having already been logarythmically transformed:
$$
\ln(F_{ij}) = \ln(C) + \alpha\ln(m_{i}) + \beta\ln(n_{j}) + \gamma\cos (ij)
$$

Here, we run the regression and extract the relevant coefficients

```{r}
# Perform the regression
fit <- lm(log(actual) ~ log(org1_size) + log(org2_size) + emb_similarity, data = agg)
summ <- summary(fit)

# Save the coefficients for use later
intercept <- summ$coefficients["(Intercept)", "Estimate"]
org1_coef <- summ$coefficients["log(org1_size)", "Estimate"]
org2_coef <- summ$coefficients["log(org2_size)", "Estimate"]
emb_coef <- summ$coefficients["emb_similarity", "Estimate"]

# Display a summary of the regression
summary(fit)
```

And now that we have the coefficients, our calculation of the flux will be slightly different as we must transform the embedding similarity by its exponential:

$$
F_{ij}^{e} = m_{i}^{\alpha}n_{j}^{\beta} * \exp^{\cos(ij) * \gamma * C}
$$

```{r}
agg <- agg %>%
  mutate(
    expected = ((org1_size ^ org1_coef * org2_size ^ org2_coef) * exp((emb_coef * emb_similarity) + intercept))
  )

head(agg %>% select(actual, expected))
```

As before, we can build a graph from the expected vs. actual counts. Assuming everything was done correctly, the fit between expected and actual appears to be much better. 
```{r message=FALSE, warning=FALSE}
# Create binned values that will be plotted over top
binned <- agg %>%
  mutate(
    expected = log10(expected),
    bin = cut(round(expected, 2), 30)
  ) %>%
  arrange(bin) %>%
  group_by(bin) %>%
  summarize(
    # Plot the point at the midpoint in each bin
    pos = min(expected) + ((max(expected) - min(expected)) / 2),
    #pos = (as.numeric(first(bin)) * 0.05) - 0.025,
    mu = mean(log10(actual), na.rm = T),
    ci = 2.576 * (sd(log10(actual), na.rm = T) / sqrt(n())) # using the 99th percentile CI
  )

agg %>%
  sample_n(50000) %>% # take only a sample of the data, in order to keep the time drawing points low
  ggplot(aes(x = log10(expected), y = log10(actual))) +
  geom_point(alpha = 0.01) +
  #geom_hex(bins = 30, color = "white", aes(alpha = ..count..)) +
  scale_fill_gradient(low = "white", high = "black") +
  geom_pointrange(data = binned, aes(x = pos, y = mu, ymin = mu - ci, ymax = mu + ci), color = "red", size = 1, shape = 21, stroke = 2) +
  xlim(0, 4) +
  ylim(0, 4) +
  geom_abline(color = "blue") +
  guides(alpha = F) +
  theme_minimal() +
  theme(
    panel.grid.minor = element_blank(),
    axis.title = element_text(size = 14)
  ) +
  xlab("Log10(expected flux)") +
  ylab("Log10(actual flux)")
```

### 2020-02-18 notebooks/20200207_plotting_notebook.rmd
Add miscelaneous notebooks that have not yet been version controlled

---
title: "Model Hyperparameters"
output: html_notebook
---

```{r}
library(tidyverse)
library(readr)

sims <- read_csv("/Users/dakotamurray/Desktop/sims_coasts.csv")

lookup <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/data/Additional/institution_lookup_with_states.txt", delim = "\t", col_types = readr::cols())

sims <- sims %>%
  left_join(lookup, by = "cwts_org_no") %>%
  distinct(cwts_org_no, .keep_all = T)

coasts <- sims
```

```{r fig.width=3, fig.height=1}
averages <- sims %>%
  group_by(region) %>%
  summarize(
    mu = mean(sim)
  ) %>%
  ungroup() %>%
  filter(region %in% c("Arizona", "Connecticut"))

sims %>%
  mutate(
    highlight = ifelse(region == "Connecticut", "CT", 
                       ifelse(region == "Arizona", "AZ", "other"))
  ) %>%
  ggplot(aes(x = sim, y = 0, color = highlight, alpha = ifelse(highlight == "other", 0.9, 1))) +
  geom_segment(y = -1, yend = 1, aes(xend = sim)) +
  geom_hline(yintercept = 0, size = 1) +
  geom_segment(y = -0.2, yend = 0.2, x = 0, xend = 0, size = 1, color = "black") +
  geom_point(data = averages, 
             aes(x = mu, y = 0),
             color = ifelse(averages$region == "Arizona", "#c0392b", "#2980b9"),
             alpha = 1,
             size = 5,
             shape = 21,
             stroke = 2
  ) +
  xlim(-0.3, 0.3) +
  scale_y_continuous(
    limits = c(-1.1, 1.1), 
    name = "   California",
    sec.axis = dup_axis(name = "Massachusetts")
  ) +
  scale_color_manual(values = c("#c0392b", "#2980b9", "grey")) +
  guides(alpha = F,
         color = guide_legend(override.aes = list(size = 2))
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    axis.text.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 11),
    axis.title.y.left = element_text(angle = 0, vjust = 0.5),
    axis.title.y.right = element_text(angle = 0, vjust = 0.5),
    panel.grid = element_blank()
  )
```

```{r}
sims <- read_csv("/Users/dakotamurray/Desktop/sims_statevuc.csv")

sims <- sims %>%
  left_join(lookup, by = "cwts_org_no") %>%
  distinct(cwts_org_no, .keep_all = T)
```

```{r fig.width=3, fig.height=1}
elite <- c(1277, 1187, 1255, 1188, 1251, 1296, 1193, 1272, 1192, 1208)
nonelite <- c(3501, 18086, 18530, 18486, 1471, 1468, 1558, 1287, 3538, 18373, 9856, 3482, 1268, 10379, 18514)
averages <- sims %>%
  mutate(
    elite = ifelse(cwts_org_no %in% elite, "Elite", 
                   ifelse(cwts_org_no %in% nonelite, "Not elite", "other")
            )
    ) %>%
  filter(elite != "other") %>%
  group_by(elite) %>%
  summarize(
    mu = mean(sim)
  ) %>%
  ungroup()

sims %>%
  mutate(
    elite = ifelse(cwts_org_no %in% elite, "Elite", ifelse(cwts_org_no %in% nonelite, "Not elite", "other"))
  ) %>%
  ggplot(aes(x = sim, y = 0, color = elite, alpha = ifelse(elite %in% c("Elite", "Not elite"), 1, 0.9))) +
  geom_segment(y = -1, yend = 1, aes(xend = sim)) +
  geom_hline(yintercept = 0, size = 1) +
  geom_segment(y = -0.2, yend = 0.2, x = 0, xend = 0, size = 1, color = "black") +
  geom_point(data = averages, 
             aes(x = mu, y = 0),
             color = ifelse(averages$elite == "Elite", "#f39c12", "#27ae60"),
             alpha = 1,
             size = 5,
             shape = 21,
             stroke = 2
  ) +
  xlim(-0.3, 0.3) +
  scale_y_continuous(
    limits = c(-1.1, 1.1), 
    name = "Cal. State",
    sec.axis = dup_axis(name = "Univ. Cal.")
  ) +
  scale_color_manual(values = c("#f39c12", "#27ae60", "grey")) +
  guides(alpha = F,
         color = guide_legend(override.aes = list(size = 2))
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    axis.text.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 11),
    axis.title.y.left = element_text(angle = 0, vjust = 0.5),
    axis.title.y.right = element_text(angle = 0, vjust = 0.5),
    panel.grid = element_blank()
  )
```

```{r}
sims <- read_csv("/Users/dakotamurray/Desktop/sims_prestige.csv")

sims <- sims %>%
  left_join(lookup, by = "cwts_org_no") %>%
  distinct(cwts_org_no, .keep_all = T)

prestige <- sims
```

```{r fig.width=3, fig.height=1}
averages <- sims %>%
  group_by(region) %>%
  summarize(
    mu = mean(sim)
  ) %>%
  ungroup() %>%
  filter(region %in% c("Indiana", "Maryland"))

sims %>%
  mutate(
    highlight = ifelse(region %in% c("Indiana", "Maryland"), region, "other")
  ) %>%
  ggplot(aes(x = sim, y = 0, color = highlight, alpha = ifelse(highlight == "other", 0.9, 1))) +
  geom_segment(y = -1, yend = 1, aes(xend = sim)) +
  geom_hline(yintercept = 0, size = 1) +
  geom_segment(y = -0.2, yend = 0.2, x = 0, xend = 0, size = 1, color = "black") +
  geom_point(data = averages, 
             aes(x = mu, y = 0),
             color = ifelse(averages$region == "Indiana", "#8e44ad", "#22a6b3"),
             alpha = 1,
             size = 5,
             shape = 21,
             stroke = 2
  ) +
  xlim(-0.3, 0.3) +
  scale_y_continuous(
    limits = c(-1.1, 1.1), 
    name = "Non Elite",
    sec.axis = dup_axis(name = "Elite   ")
  ) +
  scale_color_manual(values = c("#8e44ad", "#22a6b3", "grey")) +
  guides(alpha = F,
         color = guide_legend(override.aes = list(size = 2))
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    axis.text.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 11),
    axis.title.y.left = element_text(angle = 0, vjust = 0.5),
    axis.title.y.right = element_text(angle = 0, vjust = 0.5),
    panel.grid = element_blank()
  )
```

```{r fig.width=5, fig.height=3}
library(plotly)

all <- prestige %>%
  select(cwts_org_no, sim) %>%
  left_join(coasts, by = "cwts_org_no") %>%
  rename(sim.prestige = sim.x, sim.coasts = sim.y)

to_color <- c("Indiana", "Ohio", "Connecticut", "New York", "Arizona", "California", "Massachusetts", "Florida")

labels <- readr::read_csv("/Users/dakotamurray/Desktop/axis_unis_labels.csv") %>%
  inner_join(all, by = c("cwts_org_no"))

p <- all %>%
  filter(org_type_code == "U") %>%
  mutate(
    state = ifelse(region %in% to_color, region, "Others"),
    state = factor(state, levels = c(sort(to_color), "Others"))
  ) %>%
  filter(state != "Others") %>%
  ggplot(aes(x = sim.coasts, y = sim.prestige, fill = state, label1 = full_name, label2 = region, label3 = city)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(size = 3.5, shape = 21) +
  ggrepel::geom_label_repel(data = labels, 
             inherit.aes = F,
             aes(x = sim.coasts, y = sim.prestige, label = short_name)
             ) +
  scale_fill_manual(name = "Region", values = c("#7fc97f", "#beaed4", "#fdc086", "#ffff99", "#386cb0", "#f0027f", "#bf5b17", "#666666")) +
  scale_x_continuous(
    limits = c(-0.4, 0.4),
    name = "Lower Research Impact",
    sec.axis = dup_axis(name = "High Research Impact")
  ) +
  scale_y_continuous(
    limits = c(-0.42, 0.42),
    name = "California",
    sec.axis = dup_axis(name = "Massachusetts")
  ) +
  theme_minimal() +
  theme(
    text = element_text(family = "Helvetica", size = 11),
    axis.title.x = element_text(angle = 0, size = 12, face = "bold", vjust = 0.5),
    axis.title.x.top = element_text(angle = 0, size = 12, face = "bold", vjust = 0.5),
    axis.title.y = element_text(angle = 0, size = 12, face = "bold", vjust = 0.5),
    axis.title.y.right = element_text(angle = 0, size = 12, face = "bold", vjust = 0.5),
    legend.text = element_text(size = 12),
    legend.title = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "bottom"
  )

p
widget <- ggplotly(p, tooltip = c("full_name", "region", "city"))
widget
htmlwidgets::saveWidget(as.widget(widget), "~/Desktop/UniCoastPrestigeAxis.html")
```

### 2020-02-20 notebooks/20190116_notebook_descriptive_info.Rmd

---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(readr)

mobile <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/data/Derived/Trajectories/precedence_mobility_trajectories.txt", delim = "\t") 
nonmobile <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/data/raw/nonmobile_researcher_trajectories.txt", delim = "\t")

dist <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/data/Derived/Descriptive/org/aggregate/precedence/aggregate_org_distances_precedence_d300_ws1.csv")

flows <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/data/Derived/Descriptive/org/precedence_organization_flows.csv")
```

The total number of co-affiliations (mobile and nonmobile)
```{r}
dim(mobile)[1] + dim(nonmobile)[1]
```

The total number of authors
```{r}
length(unique(mobile$cluster_id)) + length(unique(nonmobile$cluster_id))
```

```{r}
mobile_real <- mobile %>%
  group_by(cluster_id) %>%
  filter(length(unique(cwts_org_no)) > 1) %>%
  ungroup()
```

Total number of mobile authors
```{r}
length(unique(mobile_real$cluster_id))
```

Percentage of mobile authors of all authors
```{r}
length(unique(mobile_real$cluster_id)) / (length(unique(mobile$cluster_id)) + length(unique(nonmobile$cluster_id)))
```

Total number of co-affiliation links
```{r}
dim(mobile_real)[1]
```

Number of unique organizations
```{r}
length(unique(c(nonmobile$cwts_org_no, mobile$cwts_org_no)))
```

Number of unique organizations among nonmobile researchers
```{r}
length(unique(nonmobile$cwts_org_no))
```

The longest trajectory among mobile scholars
```{r}
counted <- mobile_real %>%
  group_by(cluster_id) %>%
  summarize(
    count = length(unique(cwts_org_no))
  )

# Mean
mean(counted$count)

# Median 
median(counted$count)

# Max
max(counted$count)

```

Total number of organizations in the final, embedded dataset
```{r}
length(unique(c(dist$org1, unique(dist$org2))))
```

Percentage of total unique organizations covered by the embeddingc
```{r}
length(unique(c(dist$org1, unique(dist$org2)))) / length(unique(c(nonmobile$cwts_org_no, mobile$cwts_org_no)))

```

```{r}

```

### 2020-02-23 paper/current/main.tex
changed proximity to distance, added PPR figure

@@
 When less than one kilometer, a distance of one is imputed. 
-The embedding proximity, $d_{ij}$, is calculated as the pairwise cosine similarity between vectors from the learned organization embedding, where $v_{i}$ and $v_{j}$ represent the vectors and $d_{ij} = \frac{v_{i} \dot v_{j}}{\lVert v_{i} \rVert \lVert v_{j} \rVert}$.
+The embedding distance, $d_{ij}$, is calculated as the pairwise cosine distance between vectors from the learned organization embedding, where $v_{i}$ and $v_{j}$ represent the vectors and $d_{ij} = \frac{v_{i} \dot v_{j}}{\lVert v_{i} \rVert \lVert v_{j} \rVert}$.
 
@@
 	\caption{
-		\textbf{Embedding proximity outperform and are more robust than geographic distance.}
-		\textbf{a.} embedding proximity (the cosine similarity between vectors) explains more of the flux between organization pairs than does geographic distance (\textbf{b}). 
+		\textbf{Embedding distance outperforms and is more robust than geographic distance.}
+		\textbf{a.} embedding distance (cosine distnace between vectors) explains more of the flux between organization pairs than does geographic distance (\textbf{b}). 
 		Red line is line of best fit. 
@@
 		Color indicates frequency of organization pairs within each hex bin.
-		\textbf{c-d.} Predictions  of flux between organization pairs made using embedding proximity out-perform those made using geographic distance. 
+		\textbf{c-d.} Predictions  of flux between organization pairs made using embedding distance out-perform those made using geographic distance. 
 		Boxplots show distribution of actual flux for binned values of predicted flux.
@@
 		\textbf{e-f.} Predictions made using model parameters learned from subset of same-country organization pairs. 
-		Embedding proximity outperform those made for geographic distance.
-		\textbf{g-h.} Embedding proximity also outperforms geographic distance when predicting flux using model parameters estimated from only pairs of organizations in different countries. 
+		Embedding distance outperforms those made for geographic distance.
+		\textbf{g-h.} Embedding distance also outperforms geographic distance when predicting flux using model parameters estimated from only pairs of organizations in different countries. 
 		Predictions are not meaningfully different if estimates are learned on all pairs of organizations (Fig. S\ref{fig:supp:gravity_prediction_subsets}).
@@
 	\caption{
-		\textbf{Extend and nature of mobility by country.}
+		\textbf{Extent and nature of mobility by country.}
 		\textbf{a.}
 		Proportion of researchers in each country classified as mobile, meaning that they have at least two organization affiliations within the period of study. 
-		The countires with the most mobile researchers are the United States, China, France, Great Britain, and Germany. 
+		The countries with the most mobile researchers are the United States, China, France, Great Britain, and Germany. 
 		\textbf{b.}
 		The same information, arranged into a cumulative distribution.
-		The five countires with the highest mobility account for a total of 
+		The five countires with the highest mobility account for approximately 70 percent of all mobility. 
+		\textbf{c.} The proportion of researchers labeled as mobile by country.
+		\textbf{d.} First two principal components of four variables: proportion in each country mobile across organizations, proportion mobile across cities, proportion mobile across regions, and proportion mobile across countries.
+		First component captures overall degree of mobile, whereas the second compares within-country against across-country mobility. 		
 	}
@@
 		\textbf{Larger dimensions, smaller window size improves embedding performance.}
-		The correlation, or amount of flux explained by the embedding proximity with varying skip-gram negative sampling hyperparameters. 
+		The correlation, or amount of flux explained by the embedding distance with varying skip-gram negative sampling hyperparameters. 
 		Window size refers to the window, on either side of the target token, to use as context for training. 
@@
 	\caption{
-		\textbf{Embedding proximity explains more variance for global, within, and between country flux than geographic distance.}
+		\textbf{Embedding distance explains more variance for global, within, and between country flux than geographic distance.}
 		\textbf{a.}
-		Embedding proximity (cosine similarity between vectors) explains more of the total distance than does geographic distance (\textbf{b}). 
+		Embedding distance (cosine distance between vectors) explains more of the total distance than does geographic distance (\textbf{b}). 
 		Red line is line of best fit. 
@@
 		Results here are identical to those shown in Fig.~\ref{fig:gravity_performance}a and Fig.~\ref{fig:gravity_performance}.
-		\textbf{c-d.}	embedding proximity explains more variance when considering only pairs of organizations within the same country. 
-		\textbf{e-f.} embedding proximity more robust than geographic distance for pairs of organizations in different countries. 
+		\textbf{c-d.}	embedding distance explains more variance when considering only pairs of organizations within the same country. 
+		\textbf{e-f.} embedding distance is more robust than geographic distance for pairs of organizations in different countries. 
 	}
@@
 		\textbf{Little difference between gravity predictions fit on all or subsets of data.}
-		Predictions  of flux between organization pairs made using embedding proximity out-perform those made using geographic distance. 
+		Predictions of flux between organization pairs made using embedding distance out-performs those made using geographic distance. 
 		Boxplots show distribution of actual flux for binned values of predicted flux.
 		Box color corresponds to the degree to which the distribution overlaps $x = y$.
-		\textbf{a-b.} Predictions are made with parameter, estimating parameters from all pairs of organizatioons, making global predictions (as in Fig.~\ref{fig:gravity_performance}c), and showing only subsets of predictions for organization pairs in the same country (\textbf{a}) and in different countries (\textbf{b}).
+		\textbf{a-b.} Predictions are made with parameter, estimating parameters from all pairs of organizations, making global predictions (as in Fig.~\ref{fig:gravity_performance}c), and showing only subsets of predictions for organization pairs in the same country (\textbf{a}) and in different countries (\textbf{b}).
 		\textbf{c-d.} Predictions made by estimating gravity law parameters on subset of organizations in the same country (\textbf{c}) and different country \textbf{d}); 
 		this is the same data as shown in Fig.~\ref{fig:gravity_performance}f and Fig.~\ref{fig:gravity_performance}h. 
+	}
+\end{figure}
+
+%
+% Figure - PPR gravity model and predictions
+%
+\begin{figure}[p!]
+	\centering
+	\label{fig:supp:gravity_prediction_subsets}
+	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_ppr.pdf}
+	\caption{
+		\textbf{Personalized page rank does not capture mobility.}
+		Performance of personalized page rank scores in explaining and predicting mobility.
+		Personalized page rank is calculated for the underlying mobility network, and similarity between resulting vectors used as the PPR distance.
+		PPR distance does not explain global mobility (\textbf{a}), or same (\textbf{b}) or different (\textbf{c}) country mobility, performing worse than geographic distance (Fig.~\ref{fig:supp:gravity_correlation}).
+		Red line is line of best fit. 
+		Black dots are mean flux across binned proximity meas.
+		Color indicates frequency of organization pairs within each hex bin.
+		Similarly, PPR distance performs poorly as a distance metric for gravity model predictions globally (\textbf{d}), and across pairs of organizations in the same (\textit{e}) and in different (\textbf{f}) countries.
+		Boxplots show distribution of actual flux for binned values of predicted flux.
+		Box color corresponds to the degree to which the distribution overlaps $x = y$.
 	}

### 2020-02-23 workflow/scripts/PlotPredictedVsActual.R
Updated figures to be prettier for new draft

@@ -123,7 +123,7 @@ plot <- data %>%
   annotate(geom = "text",
            x = 1.2,
            y = 6.2,
-           label = paste0("Err = ", round(error, 2)),
+           label = paste0("Err = ", sprintf("%.2f", round(error,3))),
            size = 7
          ) +
   # Define the gradient

### 2020-02-23 workflow/scripts/PlotPrestigeRankCorrelation.R

@@ -45,19 +45,14 @@ plot <- corr %>%
   geom_line() +
   theme_minimal() +
   theme(
-    text = element_text(size = 11, family = "Helvetica"),
+    text = element_text(size = 12, family = "Helvetica"),
     strip.text = element_text(size = 12, face = "bold"),
-    axis.title = element_text(size = 12, face = "bold"),
+    axis.title = element_text(size = 14, face = "bold"),
     panel.grid.minor = element_blank(),
     panel.spacing = unit(2, 'lines')
   ) +
   xlab("Num orgs in axis") +
   ylab("Spearman's Rho")
 
-
-
-p <- egg::set_panel_size(plot,
-                         width  = unit(FIG_WIDTH, "in"),
-                         height = unit(FIG_HEIGHT, "in"))
 # Save the plot
-ggsave(opt$output, p, width = FIG_WIDTH + 1, height = FIG_HEIGHT + 1)
+ggsave(opt$output, plot, width = FIG_WIDTH, height = FIG_HEIGHT)

### 2020-02-23 paper/current/main.tex
added simaxis results

@@
 %
+% Figure - SemAxis results
+%
+\begin{figure}[hp!]
+	\centering
+	\label{fig:projection}
+	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_fig.pdf}
+	\caption{
+		\textbf{Embedding captures latent prestige hierarchy.}
+		\textbf{a.} illustrates SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S.
+Universities (bottom to top).
+		Points correspond to organizations, and a sample of individual states are highlighted. 
+		\textbf{b.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity to the "Elite" end of the axis prestige axis \textit{a}.
+		White points are those top and bottom 20 universities aggregated to define the ends of the axis. 
+		The grey box corresponds to the top 20 and bottom 20 ranks. 
+	  	The estimate of the spearman rank correlation between the SimAxis and Times ranking is 0.81 (n = 145).
+	}
+\end{figure}
+
+%
 % Subsection: Mathematical Exploration
@@
 \newpage
+\clearpage
 \beginsupplement

### 2020-02-24 paper/current/main.tex
minor updates to methods

@@
 
-\title{Word2vec learns effective distance of scientific co-affiliation} %{{{
+\title{Unsupervised embeddings capture latent structure of scientific mobility} %{{{
 \date{\today}
@@
 in cases where a precise location of the organization could not be identified, we used the coordinates returned when searching the name of the city.
+The data was further enriched with country-level information, including continent, majority language spoken, and language family of the majority language (e.g., the language family of \textit{Spanish} is \textit{Italic}).
 State/province level  information were added using the reverse geocoding service LocationIQ using each organization's latitude and longitude as input. 
-Organizations were also assigned continental information (e.g., North America, Asia, Europe) manually, by country. 
+Regional census classifications were also added for states in the United States.
 For each organization, we also calculated a size as the average number of unique authors (mobile and non-mobile) who published with that organization across each year of our dataset;
@@
 
-Some affiliations are mapped to two organizations, one specific, and one more general, as a result of the disambiguation procedure. 
+As a result of our disambiguation procedure, some affiliations are mapped to two organizations, one specific, and one more general.
 For example, any author affiliated with the "Indiana University Bloomington" will also be listed as being affiliated with the "Indiana University System", a more general designation for all public universities in Indiana.
@@
 %
-% Distances subsection
+% SUBSECTION: DISTANCE
 %
@@
 
+%
+% SUBSECTION: GRAVITY LAW
+%
 \subsection{Gravity Law}
@@
 We follow standard practice and exclude from our analysis zero flows.
+
+%
+% SUBSECTION: SEMAXIS
+%
+\subsection{SemAxis}
 
@@
 	\centering
-	\label{fig:projection}
+	\label{fig:semaxis}
 	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_fig.pdf}
@@
 		The grey box corresponds to the top 20 and bottom 20 ranks. 
-	  	The estimate of the spearman rank correlation between the SimAxis and Times ranking is 0.81 (n = 145).
+	  	The estimate of the spearman rank correlation between the SemAxis and Times ranking is 0.81 (n = 145).
 	}
@@
 	\centering
-	\label{fig:supp:gravity_prediction_subsets}
+	\label{fig:supp:gravity_ppr}
 	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_ppr.pdf}
@@
 
+%
+% Figure - SemAxis results
+%
+\begin{figure}[hp!]
+	\centering
+	\label{fig:supp:semaxis_compare}
+	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_compare_fig.pdf}
+	\caption{
+		\textbf{SemRank hierarchy is robust.}
+		\textbf{a.} Spearman correlation (n = 143) between Times prestige rank and SemAxis rank, by the number of high and bottom-ranked (geographically matched) universities aggregated to form the poles. 
+		More universities improves performance, but quickly saturates after around five universities. 
+		\textbf{b - f.} Comparison between the Times and SemAxis ranks of universities, by number of universities used to define the poles (n). 
+		White points are those top and bottom 20 universities aggregated to define the ends of the axis. 
+		The grey box corresponds to the top 20 and bottom 20 ranks. 
+	  	PCC details the estimate from Spearman correlation between the two rankings. 
+	}
+\end{figure}
+
 \clearpage

### 2020-02-24 paper/current/main.tex
Added additional semaxis results to SI

@@
 	\caption{
-		\textbf{Embedding captures latent prestige hierarchy.}
+		\textbf{Embedding captures latent geography and prestige hierarchy.}
 		\textbf{a.} illustrates SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S.
@@
 
+%
+% Figure - SemAxis By State
+%
+\begin{figure}[hp!]
+	\centering
+	\label{fig:supp:semaxis_states}
+	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_states_fig.pdf}
+	\caption{
+		\textbf{Geography and prestige SemAxis by U.S. state.}
+		SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S.
+Universities (bottom to top).
+		Points correspond to universities shown for California (\textbf{a}), Arizona (\textbf{b}), Washington (\textbf{c}), Massachusetts (\textbf{d}), Connecticut (\textbf{e}), New York (\textbf{f}), Texas (\textbf{g}), Pennsylvania (\textbf{h}), and Florida (\textbf{i}).
+		Grey points correspond to all other U.S. universities. 
+	}
+\end{figure}
+
+%
+% Figure - SemAxis By Sector
+%
+\begin{figure}[hp!]
+	\centering
+	\label{fig:supp:semaxis_sectors}
+	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_sectors_fig.pdf}
+	\caption{
+		\textbf{Geography and prestige SemAxis in U.S. by Sector.}
+		SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S.
+Universities (bottom to top).
+		Points correspond to organizations labeled as Government (\textbf{a}), Institute (\textbf{b}), and Teaching (\textbf{c}), corresponding to government organizations, research institutes, and teaching organizations, respectively.
+		Grey points correspond to all U.S. universities.  
+	}
+\end{figure}
+
 \clearpage

### 2020-02-24 paper/current/main.tex
Added clustering figure

@@
 %
-\subsection*{Applications}
-% Here we will examine several applications of this effective distnace, including for clustering, visualization + descriptive analysis, and maybe something else?
+\subsection*{Embeddings capture complex structure}
 
 %
-% Figure - 
+% Figure - UMAP Projections
 %
@@
 		We re-project subsets of organizational vectors to uncover more complex local structure.
-		\textbf{b.} Re-projection of organizational vectors roughly correponding to West-Asian, Southeast Asian, and South Asian countries. 
-		\textbf{c.} Re-projection of organizations in Spain, Portugal, and the Portougese- and Spanish-speaking counriees in South and Central America. 
+		\textbf{b.} Re-projection of organizational vectors roughly corresponding to West-Asian, Southeast Asian, and South Asian countries. 
+		\textbf{c.} Re-projection of organizations in Spain, Portugal, and the Portuguese- and Spanish-speaking counriees in South and Central America. 
 		\textbf{d.} Re-projection of organizations in the United States reveal geographic clustering based on state.
@@
 
+\subsection*{Embeddings capture international relationships}
+
+%
+% Figure - CLUSTERING
+%
+\begin{figure}[p!]
+	\centering
+	\label{fig:clustering}
+	\includegraphics[width=\textwidth]{\figdir/Clustering/cluster_country.pdf}
+	\caption{
+		\textbf{Geography, then language, dictate international mobility.}
+		\textbf{a.} Hierarchically clsutered similarity matrix of country vectors, aggregated as the mean of all organization vectors within the country, excluding the United States. 
+		Color of matrix cells corresponds to similarity between country vectors.
+		Color of country names corresponds to their cluster.
+		Color of three cell rows separated from the matrix correspond to, from left to right, the continent of the country, the language family, and the individual language. 
+		\textbf{b.}	\textit{CluSim} results demonstrating the factors dictating hierarchical clustering, varying by scaling parameter, $r$. 
+		Continent better explains the grouping of country vectors at higher levels of the clustering processes.
+		Language family, and then majority spoken language, better explain the grouping of countries at more granular 
+	}
+\end{figure}
+
+\subsection*{Embeddings capture latent geography and hierarchy}
 %

### 2020-02-24 paper/current/main.tex
revise gravity part and add mathmetical proof

@@
 \usepackage{amssymb}
+\usepackage{newtxmath}
+\DeclareMathAlphabet{\mathpzc}{T1}{pzc}{m}{it}
 \DeclareMathOperator*{\argmin}{\arg\!\min}
@@
 \def\dk#1{ {\color{red}\textbf{dk: #1}} }
+\def\js#1{ {\color{red}\textbf{js: #1}} }
 
@@
 For every career trajectory that includes one of these specific organizations, we remove all occurrences of the more general organization;
-trajectories containing only a general designation are not altered.
+trajectories containing only a general designation are not alted.
 
@@
 When less than one kilometer, a distance of one is imputed. 
-The embedding distance, $d_{ij}$, is calculated as the pairwise cosine distance between vectors from the learned organization embedding, where $v_{i}$ and $v_{j}$ represent the vectors and $d_{ij} = \frac{v_{i} \dot v_{j}}{\lVert v_{i} \rVert \lVert v_{j} \rVert}$.
+The embedding distance, $d_{ij}$, is calculated as the pairwise cosine distance between vectors from the learned organization embedding, where $v_{i}$ and $v_{j}$ represent the vectors and $d_{ij} = 1 - \frac{v_{i} \dot v_{j}}{\lVert v_{i} \rVert \lVert v_{j} \rVert}$.
+\js{cosine similarity itself is not the distance}
 
@@
 	\label{eq:gravity_basic}
-	f_{ij} = C\frac{m_{i}m_{j}}{f(r_{ij})}
+	f_{ij} = C*m_{i}m_{j}*f(r_{ij})
 \end{equation}
 
-where $m_{i}$ and $m_{j}$ are the yearly-average size of each organization during the time window, and $f(r_{ij}$ is a function of the distance between the two organizations, chosen as to fit the data, and $C$ is a constant.
+where $m_{i}$ and $m_{j}$ are the yearly-average size of each organization during the time window, and $f(r_{ij})$ is a distance-decaying function  between the two organizations.
+There are two popular forms of the $f(r_{ij})$.
+The first one is power-law function with $f(r_{ij})= r^{-\alpha}_{ij}  (\alpha > 0)$, and the another one is exponential function with $f(r_{ij}) = e^{-\beta r_{ij}} (\beta > 0)$ \cite{chen2015distance}.
+$f(r_{ij})$, $C$ can be chosen as to fit the data with the simple regression.
 Form this standard formulation we also define what we term the \textit{flux}, or the expected flow between organizations given their size, as a function of distance,
@@
 	\label{eq:gravity_flux}
-	F_{ij} = \frac{f_{ij}}{m_{i}m_{j}} = Cf(r_{ij})
+	\widetilde{f_{ij}} = C*m_{i}m_{j}*f(r_{ij})
 \end{equation}
 
-\dk{We need to mention why we choose these distance functions}
-
-We consider separate variants of $f(r_{ij})$ for geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$. 
-For geographic distance, we use the power-law function of the gravity law, with $f(g_{ij})= g^{\alpha}_{ij}$, where $\alpha$ is estimated from the data. 
-For embedding distance , we use the exponential function, with $f(d_{ij}) = e^{\beta d_{ij}}$, where $\beta$ is estimated from the data. 
+\js{I think we need a results, geographical distance with exponential function, emb distance with power-law function. And It will goes to supplement for sure}
+We consider separate variants of $f(r_{ij})$ for geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$, report the best-fit model of each distance.
+For geographic distance, we use the power-law function of the gravity law, with $f(g_{ij})= g^{-\alpha}_{ij}$, where $\alpha$ is estimated from the data. 
+For embedding distance , we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data. 
 To estimate parameters $\alpha$ and $\beta$ are estimated by log-transforming each variant of \label{eq:gravity_flux}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.
@@
 	\label{eq:linear_flux_geo}
-	\ln(F_{ij}) = \ln(C) - \alpha \ln(g_{ij})
+	\ln(\frac{f_{ij}}{m_im_j}) = \ln(C)  - \alpha \ln(g_{ij})
 \end{equation}
@@
 	\label{eq:linear_flux_emb}
-	\ln(F_{ij}) = \ln(C) + \beta d_{ij}
+	\ln(\frac{f_{ij}}{m_im_j}) = \ln(C) - \beta d_{ij}
 \end{equation}
@@
 
-Let $f_{ij}$ represents the total flux (the number of people who moved) between $i$ and $j$. 
-Because we are ignoring the directions, $f_{ij} = f_{ji}$. 
-The total flux from or to $i$ can be written as $\mu_{i} = \sum_k f_{ik}$. 
-Then the conditional probability $p(j|i)$ is simply
-\begin{equation}\label{fig:flux_conditional_prob}
-p(j|i) = \frac{f_{ij}}{\mu_i}. 
+Let $f_{ij}$ represents the total \textbf{flux}, the number of people who moved between organizations $i$ and $j$.
+$M_{i}$ and $M_{j}$ represent the size of an organization.
+According to our gravity model on the embedding space,
+
+\begin{equation}
+    \label{eq:gravity_model}
+    \frac{f_{ij}}{M_{i} * M_{j}} \propto \exp(\cos(v_i,v_j))
 \end{equation}
 
-Let us assume that we have identified the best embedding vector $v_i$ for every institution. 
-The skip-gram model maximizes the average log probability
+where the cosine similarity between two vectors, $\cos(v_{i}, v_{j})$, is defined as,
+
 \begin{equation}
+    \cos(v_j, v_i) = \frac{v_j \cdot v_i}{|v_j||v_i|} 
+\end{equation}
+
+In the case of scientific co-affiliation, all movements are without direction (symmetric), meaning that  $f_{ij} = f_{ji}$.
+Let's denote $\mathpzc{N}_i$ as the neighborhood set of organization i, which are organizations with non-zero co-affiliation to organization i.
+Then, the total flux to or from $i$ can be written as
+
+\begin{equation}
+    \mu_{i} = \sum_{k\in\mathpzc{N}_i} f_{ik} \propto M_i
+\end{equation}
+
+with the hypothesis that a similar fraction of the scholars are mobile in each organization. Then, our gravity model can be written with only terms from mobility data,
+
+\begin{equation}
+    \label{eq:gravity_model_approx}
+    \frac{f_{ij}}{\mu_i * \mu_j} \propto \exp(\cos(v_i,v_j))
+\end{equation}
+
+The embedding that best represents the data should closely approximate the true conditional probability defined in
+Eq.~\ref{eq:flux_conditional_prob},
+
+\begin{equation}
+    \label{eq:flux_conditional_prob}
+    p(j|i) = \frac{f_{ij}}{\mu_i} 
+\end{equation}
+
+We can then rewrite Eq.~\ref{eq:gravity_model_approx} as,
+
+\begin{equation}
+    \label{eq:gravity_relationship}
+    \frac{f_{ij}}{\mu_i * \mu_j} = \frac{\mu_i * p(j|i)}{\mu_i * \mu_j} =  \frac{p(j|i)}{\mu_j} \propto \exp(\cos(v_i,v_j))
+\end{equation}
+
+Then, the word embedding model will learns vectors under the condition,
+
+\begin{equation}
+    \label{eq:gravity_relationship}
+      p(j|i) \propto {\mu_j}* \exp(\cos(v_i,v_j))
+\end{equation}
+
+which is restricted to, sum of the conditional probability must be one,
+
+\begin{equation}
+    \label{eq:gravity_relationship}
+    \sum_{j\in\mathpzc{N}_i} p(j|i) = 1
+\end{equation}
+
+Then, we can write $p(j|i)$ with $\mu_{j}$
+
+\begin{equation}
+    \label{eq:gravity_relationship}
+    p(j|i) \propto \frac{{\mu_j}* \exp(\cos(v_i,v_j)}{\sum_{k\in\mathpzc{N}_i} {\mu_k}* \exp(\cos(v_i,v_k))}
+\end{equation}
+
+And, if we remove ${\mu_*}$ for simplicity (or for our special case with $\mu_{i} = \mu_{j} = \mu_*$), then $p(j|i)$ can be written as,
+
+\begin{equation}
+    \label{eq:real_embedding_relationship}
+    p(j|i) \propto \frac{\exp(\cos(v_j, v_i))}{\sum_{k\in\mathpzc{N}_i} \exp(\cos(v_k,v_i))}
+\end{equation}
+
+% $p(j|i)$ and ${\mu_j}$ is given from data, and the our model trains $\exp(\cos(v_i,v_j))$ with the data.
+Then, can we infer the functional form of the $p(j|i)$ which is written with the results of the model?
+
+% Cosine similarity capture the relative importance of neighborhood, because, with same $p(j|i)$, if $\mu_j$ is large, $\exp(\cos(v_i,v_j)$ should small and if $\mu_j$ is small, $\exp(\cos(v_i,v_j)$ should be large.
+Based on this relationship, cosine similarity capture the relative importance.
+Simply, we can use $p(j|i)$ as just normalized importance with
+
+% Also, we can validate this proxy with checking inverse relationship, \ref{eq:inverse_relationship}.
+
+% \begin{equation}
+%     \frac{f_{ij}}{\mu_i * \mu_j} \propto \frac{\exp(\cos(v_i, v_j))}{\mu_i * \sum_{w\in\mathpzc{N}_j} \exp(\cos(v_w,v_j))} \propto \exp(\cos(v_i,v_j))
+% \end{equation}
+% \begin{equation}
+% \label{eq:inverse_relationship}
+%      \mu_i * \sum_{w\in\mathpzc{N}_j} \exp(\cos(v_w,v_j)) \propto C
+% \end{equation}
+
+% According to Fig.
+\ref{fig:inverse_relationship}, $\mu_{i}$ and $\sum_{w \in \mathcal{N}_{j}} \exp(\cos(v_w \cdot v_j))$ have either a negative power-law relationship, or a weak inverse relationship.
+% This relationship may result form hub nodes, or major organizations central to the global network of co-affiliations. 
+% A node with large $\mu_{i}$ would be considered a hub node in the network, and following the friendship paradox, neighboring nodes will likely have fewer neighbors than the hub.
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.8\columnwidth]{test.png}
+%     \caption{Relationship between the conditional probability and the cosine similarity}
+%     \label{fig:inverse_relationship}
+% \end{figure}
+
+We can check the evidence that Eq.\ref{eq:real_embedding_relationship} is a good approximation functional form of is $p(i|j)$ in Fig.
+\ref{fig:real_embedding_relationship}, as high values of flow correspond to high Eq.\ref{eq:real_embedding_relationship} values.
+
+%
+% Figure - Conditional Probability
+%
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\columnwidth]{\figdir/Math/approxi_proof.png}
+    \caption{Relationship between the conditional probability and the cosine similarity}
+    \label{fig:real_embedding_relationship}
+\end{figure}
+
+This finding relates to the objective function of \textit{word2vec} (skip-gram) model.
+The skip-gram model attempts to maximize the average log probability of observing a target word in a sentence, $w_{t}$, given the words in the surrounding context window, $w_{t + k}$.
+This can be written as follows, where $c$ is the size of the context window and $T$ iterates through possible target words:
+
+\begin{equation}
+    \label{eq:skipgram_log_prob_condensed}
     \frac{1}{T}\sum_{t=1}^{T} \sum_{-c \le j \le c, j \neq 0} \log p(w_{t+j}|w_t),  
 \end{equation}
-where 
-\begin{equation}
-p(w_O|w_I) = \frac{\exp(v'_{w_{O} }\cdot v_{w_{I}})}{\sum_{w=1}^{W} \exp(v'_w \cdot v_{w_{)}}}, 
-\end{equation}
-where $v_w$ and $v'_w$ are `input' and `output' vector representations of $w$.
 
-The best embedding should be able to closely approximate the true conditional probability Eq.~\ref{fig:flux_conditional_prob}.  \yy{why? can we prove this?}
+where the conditional probability of observing one word, $w_{0}$, given another, $w_{1}$, is defined as,
 
 \begin{equation}
-p(j|i) = \frac{f_{ij}}{\mu_i} \simeq \frac{\exp(v'_j \cdot v_i)}{\sum_{w=1}^{W} \exp(v'_w \cdot v_i)}
+    \label{eq:skipgram_conditional_expanded}
+    p(w_O|w_I) = \frac{\exp(v'_{w_O} \cdot v_{w_I})}{\sum_{w=1}^{W} \exp(v'_w \cdot v_{w_I})}, 
 \end{equation}
 
-%}}}
+where $v_w$ and $v'_w$ are `input' and `output' vector representations of each word in the vocabulary.
+In the negative sampling strategies, the denominator is not calculated directly.
+In general, the cosine similarity of in-vectors is used as a measure of affinity.
+Eq.
+\ref{eq:skipgram_conditional_expanded} and Eq.
+\ref{eq:real_embedding_relationship} share a similar functional form (or Eq.~\ref{eq:real_embedding_relationship} is a special case of Eq.
+~\ref{eq:skipgram_conditional_expanded}).
 
-%}}}
+The \textit{word2vec} skip-gram model can be an effective model for investigating any kind of mobility trajectory data, stemming from the mathematical relationship between it and the gravity model of mobility.
 

### 2020-02-24 paper/current/main.tex
minor_equation_label_edit

@@
 For embedding distance , we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data. 
-To estimate parameters $\alpha$ and $\beta$ are estimated by log-transforming each variant of \label{eq:gravity_flux}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.
+To estimate parameters $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_flux}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.
 
@@
 \begin{equation}
-    \label{eq:gravity_relationship}
+    \label{eq:conditional probability}
       p(j|i) \propto {\mu_j}* \exp(\cos(v_i,v_j))
@@
 \begin{equation}
-    \label{eq:gravity_relationship}
+    \label{eq:sum of the conditional probabiitliy}
     \sum_{j\in\mathpzc{N}_i} p(j|i) = 1
@@
 \begin{equation}
-    \label{eq:gravity_relationship}
     p(j|i) \propto \frac{{\mu_j}* \exp(\cos(v_i,v_j)}{\sum_{k\in\mathpzc{N}_i} {\mu_k}* \exp(\cos(v_i,v_k))}

### 2020-02-24 paper/current/main.tex
minor_typo,add comment

@@
 		\textbf{a.}
-		UMAP projection of the entire embedding space reveals geographic clustering.
+		UMAP projection \cite{mcinnes2018umap} of the entire embedding space reveals geographic clustering.
 		Each point corresponds to an organization. 
+		Size indicates the size of the organization.
 		Color indicates the continent. 
@@
 		\textbf{b.} Re-projection of organizational vectors roughly corresponding to West-Asian, Southeast Asian, and South Asian countries. 
-		\textbf{c.} Re-projection of organizations in Spain, Portugal, and the Portuguese- and Spanish-speaking counriees in South and Central America. 
+		\textbf{c.} Re-projection of organizations in Spain, Portugal, and the Portuguese- and Spanish-speaking countries South and Central America. 
 		\textbf{d.} Re-projection of organizations in the United States reveal geographic clustering based on state.

### 2020-02-24 paper/current/main.tex
add_clusim_ref_and_add_explnation

@@
 		\textbf{Geography, then language, dictate international mobility.}
-		\textbf{a.} Hierarchically clsutered similarity matrix of country vectors, aggregated as the mean of all organization vectors within the country, excluding the United States. 
+		\textbf{a.} Hierarchically clustered similarity matrix of country vectors, aggregated as the mean of all organization vectors within the country that has a more than 25 organizations, excluding the United States.
 		Color of matrix cells corresponds to similarity between country vectors.
@@
 		Color of three cell rows separated from the matrix correspond to, from left to right, the continent of the country, the language family, and the individual language. 
-		\textbf{b.}	\textit{CluSim} results demonstrating the factors dictating hierarchical clustering, varying by scaling parameter, $r$. 
+		\textbf{b.}	\textit{CluSim} \cite{gates2019element} results demonstrating the factors dictating hierarchical clustering, varying by scaling parameter, $r$. 
 		Continent better explains the grouping of country vectors at higher levels of the clustering processes.
-		Language family, and then majority spoken language, better explain the grouping of countries at more granular 
+		Language family, and then majority spoken language, better explain the grouping of countries at more granular. 
 	}

### 2020-02-24 paper/current/main.tex
First results para about correlation findings

@@
 Authors are classified as mobile when they have at least two distinct organization ids in their trajectory, meaning that they have published using two or more distinct affiliations between 2008 and 2019.
+While the number of publications has increased year-to-year, the mobility and disciplinary makeup of the dataset has not significantly changed across the period of study (see Fig.~\ref{fig:supp:pubs_over_time}).
 
@@
 
-%
-% SUBSECTION: SEMAXIS
-%
-\subsection{SemAxis}
-
 \section{Results}\label{sec:results} %{{{
@@
 \subsection*{Embedding performance}
+
+We find that embedding distance, the distance between vectors in the embedding space, produces an effective measure of distance.
+Embedding distance explains more of the total flux between pairs of organizations, with correlation ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) over double that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
+Similarly, embedding distance outperforms personalized-page rank distance ($R^{2} = 0.001$, Fig.
+SI~\ref{fig:supp:gravity_ppr}a), a measure produced from the factorized nodes in the underlying mobility network.
+When controlling for only mobility between pairs of organizations within the same country, embedding distance ($R^{2} = 0.48$, Fig.
+SI~\ref{fig:supp:gravity_correlation}c) than does geographic distance ($R^{2} = 0.19$, Fig.
+SI~\ref{fig:supp:gravity_correlation}d).
+Embedding distnace is also far more robust in explaining international flux, with a correlation nearly seven times higher ($R^{2} = 0.28$, Fig.
+SI~\ref{fig:supp:gravity_correlation}e) than that of geographic distance ($R^{2} = 0.041$, Fig.
+SI~\ref{fig:supp:gravity_correlation}f).
 

### 2020-02-24 paper/current/main.tex
add_contents_to_viualziation_para

--- 2020-02-24 paper/current/main.tex
@@
 
+We visualize whole organization vectors in  Fig. \ref{fig:projection}a.
+The coordinates of each organization come from a 2-D projection of the  embedding vectors with UMAP \cite{mcinnes2018umap} and the colors indicates the continent that organization belongs.
+Overall structure is almost similar to geographical map seen from the north pole while coherent structures of the communities are detected.
+For instance, french-spoken region of the Canada (Quebec, Montreal) is more close to French cluster rather than mainland of Canada.
 %
@@
 \end{equation}
-
-% $p(j|i)$ and ${\mu_j}$ is given from data, and the our model trains $\exp(\cos(v_i,v_j))$ with the data.
-Then, can we infer the functional form of the $p(j|i)$ which is written with the results of the model?
-
-% Cosine similarity capture the relative importance of neighborhood, because, with same $p(j|i)$, if $\mu_j$ is large, $\exp(\cos(v_i,v_j)$ should small and if $\mu_j$ is small, $\exp(\cos(v_i,v_j)$ should be large.
-Based on this relationship, cosine similarity capture the relative importance.
-Simply, we can use $p(j|i)$ as just normalized importance with
-
-% Also, we can validate this proxy with checking inverse relationship, \ref{eq:inverse_relationship}.
-
-% \begin{equation}
-%     \frac{f_{ij}}{\mu_i * \mu_j} \propto \frac{\exp(\cos(v_i, v_j))}{\mu_i * \sum_{w\in\mathpzc{N}_j} \exp(\cos(v_w,v_j))} \propto \exp(\cos(v_i,v_j))
-% \end{equation}
-% \begin{equation}
-% \label{eq:inverse_relationship}
-%      \mu_i * \sum_{w\in\mathpzc{N}_j} \exp(\cos(v_w,v_j)) \propto C
-% \end{equation}
-
-% According to Fig.
-\ref{fig:inverse_relationship}, $\mu_{i}$ and $\sum_{w \in \mathcal{N}_{j}} \exp(\cos(v_w \cdot v_j))$ have either a negative power-law relationship, or a weak inverse relationship.
-% This relationship may result form hub nodes, or major organizations central to the global network of co-affiliations. 
-% A node with large $\mu_{i}$ would be considered a hub node in the network, and following the friendship paradox, neighboring nodes will likely have fewer neighbors than the hub.
-
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.8\columnwidth]{test.png}
-%     \caption{Relationship between the conditional probability and the cosine similarity}
-%     \label{fig:inverse_relationship}
-% \end{figure}
 

### 2020-02-24 paper/current/main.tex
Added paragraph discussing predictions

--- 2020-02-24 paper/current/main.tex
@@
 \end{figure}
+
+We also find that defining the gravity model as a function of embedding distance produces better predictions than does geographic distance.
+Comparing predicted against actual flux, we find that using the embedding distance in the gravity function has lower error, and are closer than are predictions made using geographic distance (Fig.~\ref{fig:gravity_performance}c-d).
+Embedding distance also produces better predictions for pairs of organizations within the same country (Fig.~\ref{fig:supp:gravity_correlation}e-f) and for pairs of organizations in different countries (Fig.~\ref{fig:supp:gravity_correlation}g-h).
+We find that these predictions are robust whether we make predictions using a model fit on the subsets themselves (Fig.~\ref{fig:gravity_performance}e-h) or fit on the global data and then applied to the subsets (Fig.
+SI~\ref{fig:supp:gravity_prediction_subsets}).
+This performance is also much better than that using personalized page rank distance (Fig. SI~\ref{fig:supp:gravity_ppr}).
 

### 2020-02-24 paper/current/main.tex
fixed typos

@@
 		\textbf{Embedding distance outperforms and is more robust than geographic distance.}
-		\textbf{a.} embedding distance (cosine distnace between vectors) explains more of the flux between organization pairs than does geographic distance (\textbf{b}). 
+		\textbf{a.} embedding distance (cosine distance between vectors) explains more of the flux between organization pairs than does geographic distance (\textbf{b}). 
 		Red line is line of best fit. 

### 2020-02-24 paper/current/main.tex
replaced proximity with distance

@@
 
-We also calculate two forms of proximity between organizations. 
+We also calculate two forms of distance between organizations. 
 The geographic distance, $g_{ij}$, is the pairwise geographic distance between organizations.
@@
 The embedding distance, $d_{ij}$, is calculated as the pairwise cosine distance between vectors from the learned organization embedding, where $v_{i}$ and $v_{j}$ represent the vectors and $d_{ij} = 1 - \frac{v_{i} \dot v_{j}}{\lVert v_{i} \rVert \lVert v_{j} \rVert}$.
-\js{cosine similarity itself is not the distance}
 
@@
 		Red line is line of best fit. 
-		Black dots are mean flux across binned proximity meas.
+		Black dots are mean flux across binned distances.
 		Color indicates frequency of organization pairs within each hex bin.
@@
 %
-% Subsection: Applications
-%
-\subsection*{Embeddings capture complex structure}
-
-We visualize whole organization vectors in  Fig. \ref{fig:projection}a.
-The coordinates of each organization come from a 2-D projection of the  embedding vectors with UMAP \cite{mcinnes2018umap} and the colors indicates the continent that organization belongs.
-Overall structure is almost similar to geographical map seen from the north pole while coherent structures of the communities are detected.
-For instance, french-spoken region of the Canada (Quebec, Montreal) is more close to French cluster rather than mainland of Canada.
-%
-% Figure - UMAP Projections
-%
-\begin{figure}[hp!]
-	\centering
-	\label{fig:projection}
-	\includegraphics[width=\textwidth]{\figdir/Projection/big_embedding_picture.png}
-	\caption{
-		\textbf{Projection of embedding demonstrates complex multi-scale structure.}
-		\textbf{a.}
-		UMAP projection \cite{mcinnes2018umap} of the entire embedding space reveals geographic clustering.
-		Each point corresponds to an organization. 
-		Size indicates the size of the organization.
-		Color indicates the continent. 
-		We re-project subsets of organizational vectors to uncover more complex local structure.
-		\textbf{b.} Re-projection of organizational vectors roughly corresponding to West-Asian, Southeast Asian, and South Asian countries. 
-		\textbf{c.} Re-projection of organizations in Spain, Portugal, and the Portuguese- and Spanish-speaking countries South and Central America. 
-		\textbf{d.} Re-projection of organizations in the United States reveal geographic clustering based on state.
-		Color indicates Census Bureau-designated regions,
-		\textbf{e.} Re-projection of organizations in Massachusetts reveal clustering based on organizational sector, prestige. 
-		Color indicates sector designation of organization. 
-	}
-\end{figure}
-
-\subsection*{Embeddings capture international relationships}
-
-%
-% Figure - CLUSTERING
-%
-\begin{figure}[p!]
-	\centering
-	\label{fig:clustering}
-	\includegraphics[width=\textwidth]{\figdir/Clustering/cluster_country.pdf}
-	\caption{
-		\textbf{Geography, then language, dictate international mobility.}
-		\textbf{a.} Hierarchically clustered similarity matrix of country vectors, aggregated as the mean of all organization vectors within the country that has a more than 25 organizations, excluding the United States.
-		Color of matrix cells corresponds to similarity between country vectors.
-		Color of country names corresponds to their cluster.
-		Color of three cell rows separated from the matrix correspond to, from left to right, the continent of the country, the language family, and the individual language. 
-		\textbf{b.}	\textit{CluSim} \cite{gates2019element} results demonstrating the factors dictating hierarchical clustering, varying by scaling parameter, $r$. 
-		Continent better explains the grouping of country vectors at higher levels of the clustering processes.
-		Language family, and then majority spoken language, better explain the grouping of countries at more granular. 
-	}
-\end{figure}
-
-\subsection*{Embeddings capture latent geography and hierarchy}
-%
-% Figure - SemAxis results
-%
-\begin{figure}[hp!]
-	\centering
-	\label{fig:semaxis}
-	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_fig.pdf}
-	\caption{
-		\textbf{Embedding captures latent geography and prestige hierarchy.}
-		\textbf{a.} illustrates SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S.
-Universities (bottom to top).
-		Points correspond to organizations, and a sample of individual states are highlighted. 
-		\textbf{b.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity to the "Elite" end of the axis prestige axis \textit{a}.
-		White points are those top and bottom 20 universities aggregated to define the ends of the axis. 
-		The grey box corresponds to the top 20 and bottom 20 ranks. 
-	  	The estimate of the spearman rank correlation between the SemAxis and Times ranking is 0.81 (n = 145).
-	}
-\end{figure}
-
-%
 % Subsection: Mathematical Exploration
 %
-\subsection*{Mathematical Exploration}
+\subsection*{Mathematical explanation}
+
+We observed that word embedding models trained on scientific mobility trajectories offers a reasonable measure of effective distance, one that explains flux between organizations far better than geographic distance.
+Why is this true?
+Why does the skip-gram model learn vectors which approximate gravity law relationships?
+We find evidence of a latent mathematical connection between the two models, one that makes the skip-gram model applicable to many other forms of mobility trajectory.
 
@@
 
+%
+% Subsection: Applications
+%
+\subsection*{Embeddings capture complex structure}
+
+We visualize whole organization vectors in  Fig. \ref{fig:projection}a.
+The coordinates of each organization come from a 2-D projection of the  embedding vectors with UMAP \cite{mcinnes2018umap} and the colors indicates the continent that organization belongs.
+Overall structure is almost similar to geographical map seen from the north pole while coherent structures of the communities are detected.
+For instance, french-spoken region of the Canada (Quebec, Montreal) is more close to French cluster rather than mainland of Canada.
+%
+% Figure - UMAP Projections
+%
+\begin{figure}[hp!]
+	\centering
+	\label{fig:projection}
+	\includegraphics[width=\textwidth]{\figdir/Projection/big_embedding_picture.png}
+	\caption{
+		\textbf{Projection of embedding demonstrates complex multi-scale structure.}
+		\textbf{a.}
+		UMAP projection \cite{mcinnes2018umap} of the entire embedding space reveals geographic clustering.
+		Each point corresponds to an organization. 
+		Size indicates the size of the organization.
+		Color indicates the continent. 
+		We re-project subsets of organizational vectors to uncover more complex local structure.
+		\textbf{b.} Re-projection of organizational vectors roughly corresponding to West-Asian, Southeast Asian, and South Asian countries. 
+		\textbf{c.} Re-projection of organizations in Spain, Portugal, and the Portuguese- and Spanish-speaking countries South and Central America. 
+		\textbf{d.} Re-projection of organizations in the United States reveal geographic clustering based on state.
+		Color indicates Census Bureau-designated regions,
+		\textbf{e.} Re-projection of organizations in Massachusetts reveal clustering based on organizational sector, prestige. 
+		Color indicates sector designation of organization. 
+	}
+\end{figure}
+
+\subsection*{Embeddings capture international relationships}
+
+%
+% Figure - CLUSTERING
+%
+\begin{figure}[p!]
+	\centering
+	\label{fig:clustering}
+	\includegraphics[width=\textwidth]{\figdir/Clustering/cluster_country.pdf}
+	\caption{
+		\textbf{Geography, then language, dictate international mobility.}
+		\textbf{a.} Hierarchically clustered similarity matrix of country vectors, aggregated as the mean of all organization vectors within the country that has a more than 25 organizations, excluding the United States.
+		Color of matrix cells corresponds to similarity between country vectors.
+		Color of country names corresponds to their cluster.
+		Color of three cell rows separated from the matrix correspond to, from left to right, the continent of the country, the language family, and the individual language. 
+		\textbf{b.}	\textit{CluSim} \cite{gates2019element} results demonstrating the factors dictating hierarchical clustering, varying by scaling parameter, $r$. 
+		Continent better explains the grouping of country vectors at higher levels of the clustering processes.
+		Language family, and then majority spoken language, better explain the grouping of countries at more granular. 
+	}
+\end{figure}
+
+%
+% Subsection - hierarchy
+% 
+\subsection*{Embeddings capture latent geography and hierarchy}
+%
+% Figure - SemAxis results
+%
+\begin{figure}[hp!]
+	\centering
+	\label{fig:semaxis}
+	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_fig.pdf}
+	\caption{
+		\textbf{Embedding captures latent geography and prestige hierarchy.}
+		\textbf{a.} illustrates SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S.
+Universities (bottom to top).
+		Points correspond to organizations, and a sample of individual states are highlighted. 
+		\textbf{b.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity to the "Elite" end of the axis prestige axis \textit{a}.
+		White points are those top and bottom 20 universities aggregated to define the ends of the axis. 
+		The grey box corresponds to the top 20 and bottom 20 ranks. 
+	  	The estimate of the spearman rank correlation between the SemAxis and Times ranking is 0.81 (n = 145).
+	}
+\end{figure}
+
+%
+% SECTION: DISCUSSION
+% 
+\section*{Discussion}
+
+%
+% SECTION: CONCLUSION
+% 
+\section*{Conclusion}
+
 \newpage

### 2020-02-24 paper/current/main.tex
paragraph for semaxis

@@
 Vectors are learned by training a neural network to optimize the prediction of so-called context term given a target, in our case using one organization to predict the others appearing in the same co-affiliation trajectory.
+The hidden layer of the trained neural network is used as the
 
@@
 We follow standard practice and exclude from our analysis zero flows.
+
+%
+% SUBSECTION: SEMAXIS
+%
+\subsection*{SemAxis}
+By constructing semantic embeddings from mobility trajectories, we allow for unique methodology for understading the embedding space, such as SemAxis.
+SemAxis is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these term to the concept.
+The precise axis is an antonym pair defined \textit{ad-hoc} for the specific use case.
+In the case of language, the ends of the axis could be "good" and "bad", "surprising" and "unsurprising", or "masculine" and "feminine". 
+In the case of scientific mobility, SemAxis offers a means of operationalizing abstract relationships between organizations.
 
@@
 
+The skip-gram model learns an effective distance from trajectories, one that 
 We visualize whole organization vectors in  Fig. \ref{fig:projection}a.

### 2020-02-24 paper/current/main.tex
semaxis reference and second methods paragraph

@@
 By constructing semantic embeddings from mobility trajectories, we allow for unique methodology for understading the embedding space, such as SemAxis.
-SemAxis is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these term to the concept.
+SemAxis~\autocite{an2018semaxis} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these term to the concept.
 The precise axis is an antonym pair defined \textit{ad-hoc} for the specific use case.
@@
 In the case of scientific mobility, SemAxis offers a means of operationalizing abstract relationships between organizations.
+
+Here, we apply SemAxis to U.S. universities by defining two axes, one of geography and one of academic prestige. 
+The poles of the geographic axis are defined as the mean vector of all vectors corresponding to organizations in California, and then the mean of all vectors of organizations in Massachusetts. 
+For the prestige axis, we define a subset of top-ranked universities according to either the Times World University Rankings or based on the mean normalized research impact sourced from the Leiden Rankings.
+The other end of the prestige axis is the geographically-matched (according to census region) set of universities ranked at the bottom of these rankings.
+For example, if 20 universities top-ranked universities are selected and six of them are in the Northeastern United States, then the bottom six universities according to the same ranking will be included in the low-ranked subset.
+From the prestige axis we also derive what we call \textit{SemRank}, a university ranking based on the nearness of universities to the \textit{Elite} end of the axis. 
+We compare the SemAxis ranking to the traditional university rankings using Spearman rank correlations.
 

### 2020-02-24 paper/current/main.tex
added small hyperparameter paragraph
Added SemAxis results section

@@
 
+Results are reported for embeddings with a dimensionality of 300 and a window size of one, which were the parameters that produced  that best explained the flux between organizations (see Fig.
+SI~\ref{fig:supp:hyperparams}).
+We note that this performance and the outcomes of analysis was robust to hyperparemeters settings.
+
 %
@@
 \subsection*{Embeddings capture latent geography and hierarchy}
+
+Using SemAxis, a technique unique to semantic embedding, we reconstruct geographic relationships and prestige hierarchies based defined axis between California and Massachusetts, and between lowly and highly ranked universities according to the Times Ranking of World Universities and the Leiden Ranking field-normalized citation impact (Fig.~\ref{fig:semaxis}).
+We find that, with a few exceptions, all universities in California are nearer the appropriate end of the axis than are Massachusetts universities, and \textit{vice versa}.
+Universities in bordering states, such as Arizona and Connecticut, are closer to the ends of the axis (Fig. SI~\ref{fig:supp:semaxis_states}b and Fig. SI~\ref{fig:supp:semaxis_states}e). 
+Universities in new York are nearer to the Massachusetts end of the axis (Fig.
+SI~\ref{fig:supp:semaxis_states}f), whereas universities in Florida are less aligned to either (Fig.
+SI~\ref{fig:supp:semaxis_states}i).
+
+In terms of prestige, we find prestigious universities towards the top of the axis, such as Stanford, Colombia, MIT, Harvard, and NYU. 
+Universities at the bottom of this axis tend to be regional universities with lower national profiles, such as California State University Long Beach, University of West Florida, and Barry University.
+There are strong differences by state in terms of prestige—overall, universities in Massachusetts are nearer the \textit{Elite} end of the axis than are universities in Arizona, Connecticut, Pennsylvania, and Florida (see Fig.
+SI~\ref{fig:supp:semaxis_states}).
+
+Once these axes are constructed using university rankings, we can even relate other types of organizations that wouldn't typically be fit onto university rankings.
+For example, among Government institutions, we see that the U.S.
+Department of Energy is more aligned with Californian universities, whereas the Mayo Clinic is more aligned with Massachusetts and organizations like the National Institute of Arthritis, Musculoskeletal, and Skin Disease and more aligned with elite universities than is the U.S.
+Department of Agriculture (Fig SI~\ref{fig:supp:semaxis_sectors}a).
+Among research institutes, the most aligned with elite universities are typically those prestigious university-adjacent institutes such as the Whitehead Institute, the Broad Institute, and the Dana Faber institute (Fig SI~\ref{fig:supp:semaxis_sectors}b); those institutes aligned with lowly-ranked universities tend to be ecological or agricultural institutes such as the Joseph W.
+Jones Ecological Research Center and the Louisiana Agriculture Center.
+Among teaching organizations, the top-ranked tend to be notable private liberal arts colleges such as Wellesley College and Carleton College, whereas community colleges and military colleges tend to be more aligned with lowly-ranked universities (Fig.
+SI~\ref{fig:supp:semaxis_sectors}c).
+
 %
@@
 
-%
-% SECTION: DISCUSSION
-% 
-\section*{Discussion}
+To what extent are semantic embeddings of mobility actually learning the latent hierarchy of academic mobility?
+To test this, we derive a ranking using the prestige axis that we call \textit{SemRank}, and compare them to traditional university rankings. 
+SemRank is defined from the position of organizations along the prestige axis, with the top ranked being the furthest towards the \textit{Elite} end of the axis.
+We find that SemRank derived is highly correlated with the Times ranking ($\rho = 0.81$, Fig.~\ref{fig:semaxis}b). 
+This correlation is robust with the number of organizations used to define the axes (Fig.
+SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities is strongly correlated with the Times Ranking ($\rho = 0.46$).
+For reference, SemRank achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking mean-normalized citation score ($\rho = 0.87$). 
+This suggests that word embeddings, in addition to learning the latent geography of mobility, also capture more nuanced characteristics such as latent hierarchy.
 

### 2020-02-25 paper/current/main.tex
add_umap_part

@@
 
-We model flow of authors across organizations, $f_{ij}$, using the gravity law. 
+We model the flow of authors across organizations, $f_{ij}$, using the gravity law. 
 the gravity law of mobility loosely derives from the physical law of gravity, whereby the attraction between two objects is a function of their mass and the distance between them.
@@
 $f(r_{ij})$, $C$ can be chosen as to fit the data with the simple regression.
-Form this standard formulation we also define what we term the \textit{flux}, or the expected flow between organizations given their size, as a function of distance,
 
-\begin{equation}
-	\label{eq:gravity_flux}
-	\widetilde{f_{ij}} = C*m_{i}m_{j}*f(r_{ij})
-\end{equation}
-
-\js{I think we need a results, geographical distance with exponential function, emb distance with power-law function. And It will goes to supplement for sure}
 We consider separate variants of $f(r_{ij})$ for geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$, report the best-fit model of each distance.
@@
 By constructing semantic embeddings from mobility trajectories, we allow for unique methodology for understading the embedding space, such as SemAxis.
-SemAxis~\autocite{an2018semaxis} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these term to the concept.
+SemAxis~\cite{an2018semaxis} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these term to the concept.
 The precise axis is an antonym pair defined \textit{ad-hoc} for the specific use case.
@@
 
-which is restricted to, sum of the conditional probability must be one,
+which is restricted to, sum of the conditional probability should be one,
 
@@
     \includegraphics[width=0.8\columnwidth]{\figdir/Math/approxi_proof.png}
-    \caption{Relationship between the conditional probability and the cosine similarity}
+    \caption{Relationship between the conditional probability $p(j|i)$ and approximate functional form Eq. \ref{eq:real_embedding_relationship}}.
     \label{fig:real_embedding_relationship}
@@
 where $v_w$ and $v'_w$ are `input' and `output' vector representations of each word in the vocabulary.
-In the negative sampling strategies, the denominator is not calculated directly.
-In general, the cosine similarity of in-vectors is used as a measure of affinity.
-Eq.
+With facts that the denominator is not calculated entirely in the negative sampling strategies and the cosine similarity of in-vectors is used as a measure of affinity in general, Eq.
 \ref{eq:skipgram_conditional_expanded} and Eq.
@@
 
-The \textit{word2vec} skip-gram model can be an effective model for investigating any kind of mobility trajectory data, stemming from the mathematical relationship between it and the gravity model of mobility.
+Hence, the \textit{word2vec} skip-gram model can be an effective model for investigating any kind of mobility trajectory data, stemming from the mathematical relationship between it and the gravity model of mobility.
 
@@
 
-The skip-gram model learns an effective distance from trajectories, one that 
-We visualize whole organization vectors in  Fig. \ref{fig:projection}a.
-The coordinates of each organization come from a 2-D projection of the  embedding vectors with UMAP \cite{mcinnes2018umap} and the colors indicates the continent that organization belongs.
-Overall structure is almost similar to geographical map seen from the north pole while coherent structures of the communities are detected.
-For instance, french-spoken region of the Canada (Quebec, Montreal) is more close to French cluster rather than mainland of Canada.
-%
-% Figure - UMAP Projections
-%
+The SGNS model learns an effective distance from trajectories, one that we visualize whole organization vectors in  Fig.
+\ref{fig:projection}a, revealing organizational clusters that reflect a mix of geographic, historic, cultural, and linguistic relationships between countries.
+The coordinates of each organization come from a 2-D projection of the embedding vectors with UMAP \cite{mcinnes2018umap} and the colors indicate the continent that the organization belongs to.
+The overall structure is almost similar to the geographical map seen from the north pole while coherent structures of the communities are detected.
+For instance, french-spoken regions of Canada (Quebec, Montreal) are more close to the French cluster rather than the mainland of Canada, which is the result of the linguistic relationship.
+Also, the cluster of Algeria and Morocco is closed to the French cluster, which is far from the mainland of Africa cluster, which reflects colonial historical facts.
+
+To look at the multi-scale structure of the embedding closely, we re-project organization vectors using a subset of embedding vectors, which is another advantage of our proposed method.
+In Fig.
+\ref{fig:projection}b, we find the cultural, religious, and regional spectrum of the country clusters across the Western, South, Southeast Asia.
+Also, we observe the clear linguistic separation of the country cluster, which are Portuguese speaking countries (Brazil, Portugal) and Spanish speaking countries (Spain, Mexico, Chile, etc.)  in Fig.
+\ref{fig:projection}c.
+
+By visualizing subsets of vectors within a specific country, we reveal a more granular structure.
+We re-project the embedding vectors within the United States in Fig.
+\ref{fig:projection}d, find state-level geographical clustering the structure of organizations roughly organized by state and region with spectrum from the East-coast to the West-coast.
+The more interesting part is re-projection results on state levels.
+In Fig.
+\ref{fig:projection}e, we re-project the embedding vectors with only organization in Massachusetts, finding structure based on urban centers (Boston vs.
+Worcester), organization type (hospitals tend to be adjacent)
+and different university systems (UMass system cluster separate from Harvard, MIT, etc.).
+Even though UMass Boston is located in Boston, it clusters with other universities in the UMass System and it observed throughout many states (New York, California, etc.) with state university system (See SI~?).
+
 \begin{figure}[hp!]

### 2020-02-25 paper/current/main.tex
add clusering para

@@
 
+Based on findings on visualizing results, we try to capture the international relationship of the cluster in a more quantitative manner.
+We calculate the representative vector of each country with averaging organization vectors within the given country, calculate pairwise cosine similarity and do the hierarchical clustering (see Fig.
+\ref{fig:clustering}a).
+Countries that have more than 25 organizations are collected for the clustering analysis, excluding the United States because all countries are closed to the United States.
+We report the similarity matrix, deprogram and meta-data of each country.
+Color of the country name is colored by the cluster and the color of the three cell rows represents the continent, language, and language family respectively.
+We assign a single language to country with the largest used language based on language demographic data \cite{ethnologue}.
+
+We found 6 clusters, which is a mixture of the regional, linguistic, historical clusters.
+For instance, the purple cluster is well-known commonwealth countries and the lower part of the sky-blue clusters is post-soviet countries, reflecting historical relationships among countries.
+Also, the upper part of the sky-blue clusters is the linguistic cluster.
+By looking closely at the deprogram and meta-data, there is a tendency that countries are merged as a group if they share the language in the early stage of the deprogram and geographical aspect plays a more major role in the later stage of the dendrogram.
+
+We measure this phenomena quantitatively with \textit{CluSim} method \cite{gates2019element}.
+\textit{CluSim} is a method that calculates the similarity between the cluster results and, for the hierarchical cluster, it can adjust the relative importance of membership at different levels of the hierarchy with scaling parameter r, acting likes ``zooming lens''.
+If r is high, the similarity is based on the lower part of the deprogram and the similarity is based on higher part of the deprogram with low r.
+We identify the dominant factor that determines the hierarchy by comparing hierarchical results and each meta-data membership in each level, leveraging characteristic of \textit{CluSim}.
+
+In fig. \ref{fig:clustering}a, we report three cluster similarity curves (continent, language, language family) with varying scaling parameter r.
+As expected, the continent plays a major role at higher levels of clustering process (low r), language and language family explain the clustering process more at the lower levels (high r).
+It suggests that language is quite an important factor for scientific mobility, researchers tend to moves to the country that uses the same language or belongs to the same language family at least.
+
 %

### 2020-02-25 paper/current/main.tex
edited clustering section

--- 2020-02-25 paper/current/main.tex
@@
 %
-\subsection*{Embeddings capture complex structure}
+\subsection*{Embeddings capture global structure of mobility}
 
-The SGNS model learns an effective distance from trajectories, one that we visualize whole organization vectors in  Fig.
-\ref{fig:projection}a, revealing organizational clusters that reflect a mix of geographic, historic, cultural, and linguistic relationships between countries.
-The coordinates of each organization come from a 2-D projection of the embedding vectors with UMAP \cite{mcinnes2018umap} and the colors indicate the continent that the organization belongs to.
-The overall structure is almost similar to the geographical map seen from the north pole while coherent structures of the communities are detected.
-For instance, french-spoken regions of Canada (Quebec, Montreal) are more close to the French cluster rather than the mainland of Canada, which is the result of the linguistic relationship.
-Also, the cluster of Algeria and Morocco is closed to the French cluster, which is far from the mainland of Africa cluster, which reflects colonial historical facts.
+The SGNS model learns an effective distance from trajectories, one which we can visualize by projecting organizational vectors into two dimensions using UMAP \cite{mcinnes2018umap} (Fig.~\ref{fig:projection}a).
+Overall, organizations are clustered by geography, according to the nations in which they are location;
+however, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions at multiple scales.
 
-To look at the multi-scale structure of the embedding closely, we re-project organization vectors using a subset of embedding vectors, which is another advantage of our proposed method.
-In Fig.
-\ref{fig:projection}b, we find the cultural, religious, and regional spectrum of the country clusters across the Western, South, Southeast Asia.
-Also, we observe the clear linguistic separation of the country cluster, which are Portuguese speaking countries (Brazil, Portugal) and Spanish speaking countries (Spain, Mexico, Chile, etc.)  in Fig.
-\ref{fig:projection}c.
+Re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries related to geography and religion moving from majority-Muslim nations in the Middle East towards similarity-religious nations of Pakistan, Bangladesh, and Indonesia, and finally towards East-Asian nations with different religious majorities such as Vietnam, the Philippines, and Thailand.
+Linguistic and historical ties are also important. 
+For example, we observe that Spanish-speaking and colonized Latin American nations (Mexico, Chile, Peru, etc.) are positioned near Spain, whereas Brazil is instead positioned nearer to Portugal (Fig.~\ref{fig:projection}c).
+Similarly, Algeria and Morocco, nations in close proximity to and with historic ties to France, and positioned near the French cluster of organizations (Fig.~\ref{fig:projection}a). 
+These dynamics can manifest even within the same country. 
+For example, organizations located within the french-speaking region of Quebec in Canada are positioned near the French cluster rather than Canada.
 
-By visualizing subsets of vectors within a specific country, we reveal a more granular structure.
-We re-project the embedding vectors within the United States in Fig.
-\ref{fig:projection}d, find state-level geographical clustering the structure of organizations roughly organized by state and region with spectrum from the East-coast to the West-coast.
-The more interesting part is re-projection results on state levels.
-In Fig.
-\ref{fig:projection}e, we re-project the embedding vectors with only organization in Massachusetts, finding structure based on urban centers (Boston vs.
-Worcester), organization type (hospitals tend to be adjacent)
-and different university systems (UMass system cluster separate from Harvard, MIT, etc.).
-Even though UMass Boston is located in Boston, it clusters with other universities in the UMass System and it observed throughout many states (New York, California, etc.) with state university system (See SI~?).
+A unique characteristic of semantic mobility embeddings is the ability to capture structure at multiple scales of granularity.
+For example, just as the global embedding captures geographic structure between nations, so too does a projection or organizations in the United States reflect organizational structure based on states and oriented along an East-West axis (Fig.~\ref{fig:projection}d).
+My re-projecting at the state-level for Massachusetts (Fig.~\ref{fig:projection}e), we observe structure between urban Centers (Boston vs.
+Worcester), but also based on organization type (hospitals tend to be adjacent) and different university systems.
+Even though UMass Boston is located in Boston, it clusters near other universities in the UMass System, reflecting a relative lack of mobility between the two systems, even within the same state.
+Similar dynamics can be observed in many states (New York, California, etc.), such that prestigious university systems are separate from more regional ones (See SI~?).
 
@@
 		\textbf{a.}
-		UMAP projection \cite{mcinnes2018umap} of the entire embedding space reveals geographic clustering.
+		UMAP projection \autocite{mcinnes2018umap} of the entire embedding space reveals geographic clustering.
 		Each point corresponds to an organization. 
@@
 
+Based on descriptive findings, we more rigorously assess the extent to which embeddings capture the structure of international mobility. 
+We calculate the representative vector of each country with averaging organization vectors within the given country, calculate pairwise cosine similarity, and perform hierarchical clustering (see Fig.
+\ref{fig:clustering}a).
+Countries that have more than 25 organizations are collected for the clustering analysis, though we exclude the United States due to its high similarity with all other countries.
+
+Six country clusters were identified, reflecting a mixture of the regional, linguistic, historical clusters. 
+From top-to-bottom, we identify a primarily East-Asian cluster (orange), a Scandinavian cluster (dark purple), a cluster of British Commonwealth countries (light purple), a central and eastern European cluster (sky blue), a diverse cluster of European and South American clusters (dark green), and finally another diverse cluster consisting of countries bordering the Mediterranean or the Black Sea.
+When not defined by geography, clusters appear to be defined by linguistic and historical ties, as is the case for the commonwealth countries. 
+By looking closely at the deprogram and meta-data, there is a tendency that countries are merged as a group if they share the language in the early stage of the deprogram and geographical aspect plays a more major role in the later stage of the dendrogram.
+
+We investigate the extent to which geography and language dictate the formation of clusters using \textit{CluSim}~\autocite{gates2019element}.
+\textit{CluSim} is a method that calculates the similarity between the cluster results and, for hierarchical clustering, can adjust the relative importance of membership at different levels of the hierarchy with scaling parameter $r$, acting likes ``zooming lens''.
+If $r$ is high, the similarity is based on the lower levels of the deprogram , and when $r$ is low, similarity is based on higher levels dendrogram. 
+In fig. \ref{fig:clustering}a, we report three cluster similarity curves (continent, language, language family) with varying scaling parameter r.
+As expected, continent plays a major role at higher levels of clustering process (low $r$), language and language family explain the clustering process more at the lower levels (high $r$). 
+This suggests that geography, then language, are important factors contributing to the structure of international scientific mobility.
+
 %
@@
 		Color of country names corresponds to their cluster.
-		Color of three cell rows separated from the matrix correspond to, from left to right, the continent of the country, the language family, and the individual language. 
-		\textbf{b.}	\textit{CluSim} \cite{gates2019element} results demonstrating the factors dictating hierarchical clustering, varying by scaling parameter, $r$. 
+		Color of three cell rows separated from the matrix correspond to, from left to right, the continent of the country, the language family~\autocite{ethnologue}, and the individual language. 
+		\textbf{b.}	\textit{CluSim} \autocite{gates2019element} results demonstrating the factors dictating hierarchical clustering, varying by scaling parameter, $r$. 
 		Continent better explains the grouping of country vectors at higher levels of the clustering processes.

### 2020-02-25 paper/current/main.tex
fixed quotation characters

@@
 As a result of our disambiguation procedure, some affiliations are mapped to two organizations, one specific, and one more general.
-For example, any author affiliated with the "Indiana University Bloomington" will also be listed as being affiliated with the "Indiana University System", a more general designation for all public universities in Indiana.
+For example, any author affiliated with ``Indiana University Bloomington'' will also be listed as being affiliated with the ``Indiana University System'', a more general designation for all public universities in Indiana.
 However, a more general organization may not always occur alongside the more specific one.
-For example, a researcher affiliated with the smaller regional school "Indiana University South Bend" will be listed as affiliated with only the "Indiana University System". 
+For example, a researcher affiliated with the smaller regional school ``Indiana University South Bend'' will be listed as affiliated with only the ``Indiana University System''. 
 We identify all specific organizations that always co-occur along a more general one.
 For every career trajectory that includes one of these specific organizations, we remove all occurrences of the more general organization;
-trajectories containing only a general designation are not alted.
+trajectories containing only a general designation are not altered.
 
@@
 The precise axis is an antonym pair defined \textit{ad-hoc} for the specific use case.
-In the case of language, the ends of the axis could be "good" and "bad", "surprising" and "unsurprising", or "masculine" and "feminine". 
+In the case of language, the ends of the axis could be ``good'' and ``bad'', ``surprising'' and ``unsurprising'', or ``masculine'' and ``feminine''. 
 In the case of scientific mobility, SemAxis offers a means of operationalizing abstract relationships between organizations.
@@
 		Points correspond to organizations, and a sample of individual states are highlighted. 
-		\textbf{b.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity to the "Elite" end of the axis prestige axis \textit{a}.
+		\textbf{b.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity to the \textit{Elite} end of the axis prestige axis \textit{a}.
 		White points are those top and bottom 20 universities aggregated to define the ends of the axis. 

### 2020-02-25 workflow/clustering_figure/script/draw_clustering_figure_country_level.py
add color legend and adjust order

@@ -181,12 +181,12 @@ def draw_figure(
         col_linkage=linked,
         row_colors=[
             continent_color_list,
-            languae_color_list,
             languae_family_color_list,
+            languae_color_list,
         ],
         linewidths=0.01,
         figsize=(20, 16),
-        cbar_pos=(0.98, 0.4, 0.03, 0.2),
+        cbar_pos=(0.98, 0.55, 0.03, 0.2),
     )
     g.ax_col_dendrogram.set_visible(False)
     g.ax_row_dendrogram.set_visible(False)
@@ -198,7 +198,7 @@ def draw_figure(
             label._y + 0.22,
             label.get_text(),
             c=leaves_color_dict[label.get_text()],
-            fontproperties=small_prop,
+            fontproperties=small_prop
         )
     ax.set_yticks([])
 
@@ -235,6 +235,27 @@ def draw_figure(
             (-4.6, 31), 4.6, 5, fill=False, clip_on=False, edgecolor="black", lw=3
         )
     )
+    lp = lambda i: plt.plot([],color=c_list[continent_color_mapper[i]], ms=10, mec="none",
+                        label=i[0].upper() + i[1:], ls="", marker="o")[0]
+    handles = [lp(k) for k in ["Asia", "Europe", "North America", "Africa", "Oceania", "South America"]]
+    continent_legend = plt.legend(handles=handles, bbox_to_anchor=(8,1.1), prop=prop,frameon=False)
+    plt.text(1.8,0.838,'Continent', fontproperties=prop)
+    
+    lp = lambda i: plt.plot([],color=languae_family_color_mapper[i], ms=10, mec="none",
+                        label=i[0].upper() + i[1:], ls="", marker="o")[0]
+    handles = [lp(k) for k in ["Sintic", "Germanic", "Slavic", "Italic", "Semitic"]]
+    language_family_legend = plt.legend(handles=handles, bbox_to_anchor=(12,1.1), prop=prop,frameon=False)
+    plt.text(4.35, 0.838,'Language Family', fontproperties=prop)
+    
+    language_name_convert_dict = {"en": "English", "zh": "Chinese", "de": "German", "pt": "Portuguese", "nl": "Dutch"}
+    lp = lambda i: plt.plot([],color=languae_color_mapper[i], ms=10, mec="none",
+                        label=language_name_convert_dict[i], ls="", marker="o")[0]
[…]

### 2020-02-25 workflow/clustering_figure/script/draw_clustering_figure_country_level.py
edit_with_black

@@ -198,7 +198,7 @@ def draw_figure(
             label._y + 0.22,
             label.get_text(),
             c=leaves_color_dict[label.get_text()],
-            fontproperties=small_prop
+            fontproperties=small_prop,
         )
     ax.set_yticks([])
 
@@ -235,25 +235,68 @@ def draw_figure(
             (-4.6, 31), 4.6, 5, fill=False, clip_on=False, edgecolor="black", lw=3
         )
     )
-    lp = lambda i: plt.plot([],color=c_list[continent_color_mapper[i]], ms=10, mec="none",
-                        label=i[0].upper() + i[1:], ls="", marker="o")[0]
-    handles = [lp(k) for k in ["Asia", "Europe", "North America", "Africa", "Oceania", "South America"]]
-    continent_legend = plt.legend(handles=handles, bbox_to_anchor=(8,1.1), prop=prop,frameon=False)
-    plt.text(1.8,0.838,'Continent', fontproperties=prop)
-    
-    lp = lambda i: plt.plot([],color=languae_family_color_mapper[i], ms=10, mec="none",
-                        label=i[0].upper() + i[1:], ls="", marker="o")[0]
+    lp = lambda i: plt.plot(
+        [],
+        color=c_list[continent_color_mapper[i]],
+        ms=10,
+        mec="none",
+        label=i[0].upper() + i[1:],
+        ls="",
+        marker="o",
+    )[0]
+    handles = [
+        lp(k)
+        for k in [
+            "Asia",
+            "Europe",
+            "North America",
+            "Africa",
+            "Oceania",
+            "South America",
+        ]
+    ]
+    continent_legend = plt.legend(
+        handles=handles, bbox_to_anchor=(8, 1.1), prop=prop, frameon=False
+    )
+    plt.text(1.8, 0.838, "Continent", fontproperties=prop)
+
+    lp = lambda i: plt.plot(
+        [],
+        color=languae_family_color_mapper[i],
+        ms=10,
+        mec="none",
+        label=i[0].upper() + i[1:],
+        ls="",
+        marker="o",
+    )[0]
     handles = [lp(k) for k in ["Sintic", "Germanic", "Slavic", "Italic", "Semitic"]]
-    language_family_legend = plt.legend(handles=handles, bbox_to_anchor=(12,1.1), prop=prop,frameon=False)
-    plt.text(4.35, 0.838,'Language Family', fontproperties=prop)
-    
[…]

### 2020-02-25 paper/current/main.tex
Added correct panel label to clustering figure

@@
 \textit{CluSim} is a method that calculates the similarity between the cluster results and, for hierarchical clustering, can adjust the relative importance of membership at different levels of the hierarchy with scaling parameter $r$, acting likes ``zooming lens''.
-If $r$ is high, the similarity is based on the lower levels of the deprogram , and when $r$ is low, similarity is based on higher levels dendrogram. 
-In fig. \ref{fig:clustering}a, we report three cluster similarity curves (continent, language, language family) with varying scaling parameter r.
+If $r$ is high, the similarity is based on the lower levels of the dendrogram, and when $r$ is low, similarity is based on higher levels dendrogram. 
+In fig. \ref{fig:clustering}b, we report three cluster similarity curves (continent, language, language family) with varying scaling parameter $r$.
 As expected, continent plays a major role at higher levels of clustering process (low $r$), language and language family explain the clustering process more at the lower levels (high $r$). 

### 2020-02-25 paper/current/main.tex
edit typo

--- 2020-02-25 paper/current/main.tex
@@
 When not defined by geography, clusters appear to be defined by linguistic and historical ties, as is the case for the commonwealth countries. 
-By looking closely at the deprogram and meta-data, there is a tendency that countries are merged as a group if they share the language in the early stage of the deprogram and geographical aspect plays a more major role in the later stage of the dendrogram.
+By looking closely at the dendrogram and meta-data, there is a tendency that countries are merged as a group if they share the language in the early stage of the deprogram and geographical aspect plays a more major role in the later stage of the dendrogram.
 
@@
 \textit{CluSim} is a method that calculates the similarity between the cluster results and, for hierarchical clustering, can adjust the relative importance of membership at different levels of the hierarchy with scaling parameter $r$, acting likes ``zooming lens''.
-If $r$ is high, the similarity is based on the lower levels of the deprogram , and when $r$ is low, similarity is based on higher levels dendrogram. 
-In fig. \ref{fig:clustering}a, we report three cluster similarity curves (continent, language, language family) with varying scaling parameter r.
+If $r$ is high, the similarity is based on the lower levels of the dendrogram , and when $r$ is low, the similarity is based on higher levels of the dendrogram. 
+In fig. \ref{fig:clustering}a, we report three cluster similarity curves (continent, language, language family) with varying scaling parameter $r$.
 As expected, continent plays a major role at higher levels of clustering process (low $r$), language and language family explain the clustering process more at the lower levels (high $r$). 

### 2020-02-25 paper/current/main.tex
typo and the change umap part

@@
 All word embeddings are trained using the \textit{gensim} python implementation of the SGNS \textit{word2vec} model.
-We visualize embeddings by projecting into two dimensions using UMAP~\cite{mcinnes2018umap}.
 
@@
 For embedding distance , we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data. 
-To estimate parameters $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_flux}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.
+To estimate parameters $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_basic}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.
 
@@
     \centering
-    \includegraphics[width=0.8\columnwidth]{\figdir/Math/approxi_proof.png}
-    \caption{Relationship between the conditional probability $p(j|i)$ and approximate functional form Eq. \ref{eq:real_embedding_relationship}}.
+    \includegraphics[width=0.8\columnwidth]{\figdir/Math/approxi_proof.pdf}
+    \caption{Relationship between the conditional probability $p(j|i)$ from data and approximate functional form Eq. \ref{eq:real_embedding_relationship}}.
     \label{fig:real_embedding_relationship}
@@
 
-The SGNS model learns an effective distance from trajectories, one which we can visualize by projecting organizational vectors into two dimensions using UMAP \cite{mcinnes2018umap} (Fig.~\ref{fig:projection}a).
+The SGNS model learns an effective distance from trajectories, one which we can visualize the results into two dimensional space by projecting high dimensional organizational vectors into two dimensions vectors using UMAP \cite{mcinnes2018umap} (Fig.~\ref{fig:projection}a).
 Overall, organizations are clustered by geography, according to the nations in which they are location;

### 2020-02-25 paper/current/main.tex
edit minor things

@@
 Sixteen different sector types were included in the analysis, which we aggregated to a four high-level codes: \textit{University}, \textit{Hospital}, \textit{Government}, and \textit{Other}. 
-Each record was also associated with a latitude and longitude, however for many organizations these were missing or incorrect.
+Each record was also associated with a latitude and longitude, however, for many organizations, these were missing or incorrect.
 We manually updated the coordinates of 2,267 organizations by searching the institution name and city on Google Maps;
@@
 The data was further enriched with country-level information, including continent, majority language spoken, and language family of the majority language (e.g., the language family of \textit{Spanish} is \textit{Italic}).
-State/province level  information were added using the reverse geocoding service LocationIQ using each organization's latitude and longitude as input. 
+State/province-level information was added using the reverse geocoding service LocationIQ using each organization's latitude and longitude as input. 
 Regional census classifications were also added for states in the United States.
-For each organization, we also calculated a size as the average number of unique authors (mobile and non-mobile) who published with that organization across each year of our dataset;
+For each organization, we also calculated size as the average number of unique authors (mobile and non-mobile) who published with that organization across each year of our dataset;
 in the case that authors publish with multiple affiliations in a single year, they are counted towards each.
@@
 For example, a researcher affiliated with the smaller regional school ``Indiana University South Bend'' will be listed as affiliated with only the ``Indiana University System''. 
-We identify all specific organizations that always co-occur along a more general one.
+We identify all specific organizations that always co-occur along with a more general one.
 For every career trajectory that includes one of these specific organizations, we remove all occurrences of the more general organization;
@@
 Here, we consider an author as mobile when at least two distinct organizational affiliations appear in their trajectory during the 2008-2019 time window. 
-Under this definition, mobile authors constitute 3,007,192 or 23.2 percent of all authors, and 17,700,095 author-affiliation combinations. 
+Under this definition, mobile authors constitute 3,007,192 or 23.2 percent of all authors and 17,700,095 author-affiliation combinations. 
 Mobile authors were associated with, on average, 2.5 distinct organizational affiliations. 
-Rates of mobility tended to differ across country. 
+Rates of mobility tended to differ across the country. 
 For example, France, Qatar, the USA, Iraq, and Luxembourg had the most mobile authors (ref figure).
@@
 In natural-language processing, word embeddings are used to construct dense vector-space representations of words and phrases, in which distance relationships between words correspond to a notion of semantic distance.
-By embedding co-affiliation trajectories, we aim to learn a dense vector for every organization where distance between vectors relates to the tendency for two organizations to co-occur in a token window around the target term in the same career trajectory.
-Vectors are learned by training a neural network to optimize the prediction of so-called context term given a target, in our case using one organization to predict the others appearing in the same co-affiliation trajectory.
+By embedding co-affiliation trajectories, we aim to learn a dense vector for every organization where the distance between vectors relates to the tendency for two organizations to co-occur in a token window around the target term in the same career trajectory.
+Vectors are learned by training a neural network to optimize the prediction of the so-called context term given a target, in our case using one organization to predict the others appearing in the same co-affiliation trajectory.
 The hidden layer of the trained neural network is used as the
@@
 The SGNS model has several tunable hyper-parameters, including the size of the learned vectors, the size of the token window considered when training, the minimum frequency threshold for including an organization, and the number of iterations.
-We iterate through several values of vector size and window size, repeating analysis for each combination. 
+We iterate through several values of vector size and window size, repeating the analysis for each combination. 
 To mitigate the effect of less common organizations, only organizations appearing at least 50 times in mobility sentences are included in the embedding;
 this yields 6,580, or 76 percent of all organizations.
-We iterate the SGNS training for five epochs over all mobility sentences. 
+We iterate the SGNS training for five epochs overall mobility sentences. 
 All word embeddings are trained using the \textit{gensim} python implementation of the SGNS \textit{word2vec} model.
@@
 
-We also calculate two forms of distance between organizations. 
+We also calculate two forms of the distance between organizations. 
 The geographic distance, $g_{ij}$, is the pairwise geographic distance between organizations.
@@
 This value is comparable to other common applications of the gravity law, such as to hone calls, commuting, and migration \cite{simini2012universal}.
-We follow standard practice and exclude from our analysis zero flows.
+We follow standard practice and exclude from our analysis of zero flows.
 
@@
 \subsection*{SemAxis}
-By constructing semantic embeddings from mobility trajectories, we allow for unique methodology for understading the embedding space, such as SemAxis.
-SemAxis~\cite{an2018semaxis} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these term to the concept.
+By constructing semantic embeddings from mobility trajectories, we allow for a unique methodology for understanding the embedding space, such as SemAxis.
+SemAxis~\cite{an2018semaxis} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these terms to the concept.
 The precise axis is an antonym pair defined \textit{ad-hoc} for the specific use case.
@@
 For example, if 20 universities top-ranked universities are selected and six of them are in the Northeastern United States, then the bottom six universities according to the same ranking will be included in the low-ranked subset.
-From the prestige axis we also derive what we call \textit{SemRank}, a university ranking based on the nearness of universities to the \textit{Elite} end of the axis. 
+From the prestige axis, we also derive what we call \textit{SemRank}, a university ranking based on the nearness of universities to the \textit{Elite} end of the axis. 
 We compare the SemAxis ranking to the traditional university rankings using Spearman rank correlations.
@@
 
-Results are reported for embeddings with a dimensionality of 300 and a window size of one, which were the parameters that produced  that best explained the flux between organizations (see Fig.
+Results are reported for embeddings with a dimensionality of 300 and a window size of one, which was the parameters that produced that best explained the flux between organizations (see Fig.
 SI~\ref{fig:supp:hyperparams}).
-We note that this performance and the outcomes of analysis was robust to hyperparemeters settings.
+We note that this performance and the outcomes of analysis were robust to hyperparameters settings.
 
@@
 		\textbf{a.} embedding distance (cosine distance between vectors) explains more of the flux between organization pairs than does geographic distance (\textbf{b}). 
-		Red line is line of best fit. 
+		Red line is the line of best fit. 
 		Black dots are mean flux across binned distances.
-		Color indicates frequency of organization pairs within each hex bin.
+		The color indicates the frequency of organization pairs within each hex bin.
 		\textbf{c-d.} Predictions of flux between organization pairs made using embedding distance out-perform those made using geographic distance. 
-		Boxplots show distribution of actual flux for binned values of predicted flux.
+		Boxplots show the distribution of actual flux for binned values of predicted flux.
 		Box color corresponds to the degree to which the distribution overlaps $x = y$.
-		\textbf{e-f.} Predictions made using model parameters learned from subset of same-country organization pairs. 
+		\textbf{e-f.} Predictions made using model parameters learned from the subset of same-country organization pairs. 
 		Embedding distance outperforms those made for geographic distance.
@@
 We also find that defining the gravity model as a function of embedding distance produces better predictions than does geographic distance.
-Comparing predicted against actual flux, we find that using the embedding distance in the gravity function has lower error, and are closer than are predictions made using geographic distance (Fig.~\ref{fig:gravity_performance}c-d).
+Comparing predicted against actual flux, we find that using the embedding distance in the gravity function has a lower error, and are closer than are predictions made using geographic distance (Fig.~\ref{fig:gravity_performance}c-d).
 Embedding distance also produces better predictions for pairs of organizations within the same country (Fig.~\ref{fig:supp:gravity_correlation}e-f) and for pairs of organizations in different countries (Fig.~\ref{fig:supp:gravity_correlation}g-h).
@@
 
-We observed that word embedding models trained on scientific mobility trajectories offers a reasonable measure of effective distance, one that explains flux between organizations far better than geographic distance.
+We observed that word embedding models trained on scientific mobility trajectories offer a reasonable measure of effective distance, one that explains flux between organizations far better than geographic distance.
 Why is this true?
@@
 In the case of scientific co-affiliation, all movements are without direction (symmetric), meaning that  $f_{ij} = f_{ji}$.
-Let's denote $\mathpzc{N}_i$ as the neighborhood set of organization i, which are organizations with non-zero co-affiliation to organization i.
+Let's denote $\mathpzc{N}_i$ as the neighborhood set of organization i, which are organizations with non-zero co-affiliation to the organization i.
 Then, the total flux to or from $i$ can be written as
@@
 
-with the hypothesis that a similar fraction of the scholars are mobile in each organization. Then, our gravity model can be written with only terms from mobility data,
+with the hypothesis that a similar fraction of the scholars is mobile in each organization. Then, our gravity model can be written with only terms from mobility data,
 
@@
 
-Then, the word embedding model will learns vectors under the condition,
+Then, the word embedding model will learn vectors under the condition,
 
@@
 
-which is restricted to, sum of the conditional probability should be one,
+which is restricted to, a sum of the conditional probability should be one,
 
@@
 
-The SGNS model learns an effective distance from trajectories, one which we can visualize the results into two dimensional space by projecting high dimensional organizational vectors into two dimensions vectors using UMAP \cite{mcinnes2018umap} (Fig.~\ref{fig:projection}a).
-Overall, organizations are clustered by geography, according to the nations in which they are location;
+The SGNS model learns an effective distance from trajectories, one which we can visualize the results into two-dimensional space by projecting high dimensional organizational vectors into two dimensions vectors using UMAP \cite{mcinnes2018umap} (Fig.~\ref{fig:projection}a).
+Overall, organizations are clustered by geography, according to the nations in which they are located;
 however, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions at multiple scales.
@@
 A unique characteristic of semantic mobility embeddings is the ability to capture structure at multiple scales of granularity.
-For example, just as the global embedding captures geographic structure between nations, so too does a projection or organizations in the United States reflect organizational structure based on states and oriented along an East-West axis (Fig.~\ref{fig:projection}d).
+For example, just as the global embedding captures geographic structure between nations, so too does a projection or organization in the United States reflect organizational structure based on states and oriented along an East-West axis (Fig.~\ref{fig:projection}d).
 My re-projecting at the state-level for Massachusetts (Fig.~\ref{fig:projection}e), we observe structure between urban Centers (Boston vs.
-Worcester), but also based on organization type (hospitals tend to be adjacent) and different university systems.
+Worcester) but also based on organization type (hospitals tend to be adjacent) and different university systems.
 Even though UMass Boston is located in Boston, it clusters near other universities in the UMass System, reflecting a relative lack of mobility between the two systems, even within the same state.
@@
 		Size indicates the size of the organization.
-		Color indicates the continent. 
-		We re-project subsets of organizational vectors to uncover more complex local structure.
+		The color indicates the continent. 
+		We re-project subsets of organizational vectors to uncover more complex local structures.
 		\textbf{b.} Re-projection of organizational vectors roughly corresponding to West-Asian, Southeast Asian, and South Asian countries. 
@@
 		\textbf{d.} Re-projection of organizations in the United States reveal geographic clustering based on state.
-		Color indicates Census Bureau-designated regions,
-		\textbf{e.} Re-projection of organizations in Massachusetts reveal clustering based on organizational sector, prestige. 
+		The color indicates Census Bureau-designated regions,
+		\textbf{e.} Re-projection of organizations in Massachusetts reveal clustering based on the organizational sector, prestige. 
 		Color indicates sector designation of organization. 
@@
 \textit{CluSim} is a method that calculates the similarity between the cluster results and, for hierarchical clustering, can adjust the relative importance of membership at different levels of the hierarchy with scaling parameter $r$, acting likes ``zooming lens''.
-If $r$ is high, the similarity is based on the lower levels of the dendrogram , and when $r$ is low, the similarity is based on higher levels of the dendrogram. 
+If $r$ is high, the similarity is based on the lower levels of the dendrogram, and when $r$ is low, the similarity is based on higher levels of the dendrogram. 
 In fig. \ref{fig:clustering}a, we report three cluster similarity curves (continent, language, language family) with varying scaling parameter $r$.
@@
 		\textbf{Geography, then language, dictate international mobility.}
-		\textbf{a.} Hierarchically clustered similarity matrix of country vectors, aggregated as the mean of all organization vectors within the country that has a more than 25 organizations, excluding the United States.
-		Color of matrix cells corresponds to similarity between country vectors.
+		\textbf{a.} Hierarchically clustered similarity matrix of country vectors, aggregated as the mean of all organization vectors within the country that has more than 25 organizations, excluding the United States.
+		The color of matrix cells corresponds to the similarity between country vectors.
 		Color of country names corresponds to their cluster.
@@
 Universities in bordering states, such as Arizona and Connecticut, are closer to the ends of the axis (Fig. SI~\ref{fig:supp:semaxis_states}b and Fig. SI~\ref{fig:supp:semaxis_states}e). 
-Universities in new York are nearer to the Massachusetts end of the axis (Fig.
+Universities in New York are nearer to the Massachusetts end of the axis (Fig.
 SI~\ref{fig:supp:semaxis_states}f), whereas universities in Florida are less aligned to either (Fig.
@@
 Universities at the bottom of this axis tend to be regional universities with lower national profiles, such as California State University Long Beach, University of West Florida, and Barry University.
-There are strong differences by state in terms of prestige—overall, universities in Massachusetts are nearer the \textit{Elite} end of the axis than are universities in Arizona, Connecticut, Pennsylvania, and Florida (see Fig.
+There are strong differences by the state in terms of prestige—overall, universities in Massachusetts are nearer the \textit{Elite} end of the axis than are universities in Arizona, Connecticut, Pennsylvania, and Florida (see Fig.
 SI~\ref{fig:supp:semaxis_states}).
@@
 		\textbf{Embedding captures latent geography and prestige hierarchy.}
-		\textbf{a.} illustrates SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S.
+		\textbf{a.} illustrates SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and the geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S.
 Universities (bottom to top).
@@
 		White points are those top and bottom 20 universities aggregated to define the ends of the axis. 
-		The grey box corresponds to the top 20 and bottom 20 ranks. 
+		The gray box corresponds to the top 20 and bottom 20 ranks. 
 	  	The estimate of the spearman rank correlation between the SemAxis and Times ranking is 0.81 (n = 145).
@@
 To test this, we derive a ranking using the prestige axis that we call \textit{SemRank}, and compare them to traditional university rankings. 
-SemRank is defined from the position of organizations along the prestige axis, with the top ranked being the furthest towards the \textit{Elite} end of the axis.
+SemRank is defined from the position of organizations along the prestige axis, with the top-ranked being the furthest towards the \textit{Elite} end of the axis.
 We find that SemRank derived is highly correlated with the Times ranking ($\rho = 0.81$, Fig.~\ref{fig:semaxis}b). 

### 2020-02-25 paper/current/main.tex
edit minor things

@@
         \textbf{a.} 
-		An authors published five papers across five time periods, with only one affiliation listed in the byline of each paper. 
+        An author published five papers across five time periods, with only one affiliation listed in the byline of each paper. 
         A unique identifier is assigned to each organization, and these are concatenated into a mobility sentence. 
@@
 SI~\ref{fig:supp:hyperparams}).
-We note that this performance and the outcomes of analysis were robust to hyperparameters settings.
+We note that this performance and the outcomes of the analysis were robust to hyperparameters settings.
 
@@
         The number of papers published by mobile authors has been steadily increasing from 2008 to 2017, with a small decrease in 2018,  likely an artifact of the Web of Science indexing process.
-		Lines corresponds to publications by mobile authors (org, purple), by authors with affiliations in at least two cities (blue), at least two regions (green), and at least two countries (yellow).
-		There is no evidence of major changes in publication patterns of mobile authors during this time period. 
+        Lines correspond to publications by mobile authors (org, purple), by authors with affiliations in at least two cities (blue), at least two regions (green), and at least two countries (yellow).
+        There is no evidence of major changes in the publication patterns of mobile authors during this period. 
         \textbf{b.}
@@
         \textbf{d.} 
-		The proportion of authors publications across fields has largely remained steady.
-		Biology and Health Science has comprised the majority of publications across nearly all years, but has steadily declined in proportion. 
+        The proportion of authors' publications across fields has largely remained steady.
+        Biology and Health Science has comprised the majority of publications across nearly all years but has steadily declined in proportion. 
         However, the proportion of Social Science and Humanities publications has been steadily increasing. 
@@
         \textbf{a.}
-		Proportion of researchers in each country classified as mobile, meaning that they have at least two organization affiliations within the period of study. 
+        The proportion of researchers in each country classified as mobile, meaning that they have at least two organization affiliations within the period of study. 
         The countries with the most mobile researchers are the United States, China, France, Great Britain, and Germany. 
@@
         The same information, arranged into a cumulative distribution.
-		The five countires with the highest mobility account for approximately 70 percent of all mobility. 
+        The five countries with the highest mobility account for approximately 70 percent of all mobility. 
         \textbf{c.} The proportion of researchers labeled as mobile by country.
-		\textbf{d.} First two principal components of four variables: proportion in each country mobile across organizations, proportion mobile across cities, proportion mobile across regions, and proportion mobile across countries.
-		First component captures overall degree of mobile, whereas the second compares within-country against across-country mobility. 		
+        \textbf{d.} The first two principal components of four variables: proportion in each country mobile across organizations, proportion mobile across cities, proportion mobile across regions, and proportion mobile across countries.
+        The first component captures the overall degree of mobile, whereas the second compares within-country against across-country mobility.         
     }
@@
         \textbf{a.}
-		Proportion of mobile authors by how many organizations are represented 	in their career trajectories. 
+        The proportion of mobile authors by how many organizations are represented in their career trajectories. 
         For example, for mobile authors, 100 percent of authors held an affiliation with at least two organizations, whereas about 35 percent were affiliated with 3 ore more organizations between 2008 and 2019.
@@
         \textbf{Larger dimensions, smaller window size improves embedding performance.}
-		The correlation, or amount of flux explained by the embedding distance with varying skip-gram negative sampling hyperparameters. 
+        The correlation or amount of flux explained by the embedding distance with varying skip-gram negative sampling hyperparameters. 
         Window size refers to the window, on either side of the target token, to use as context for training. 
-		Smaller window sizes results in an embedding that explain more of the flux. 
+        Smaller window sizes result in an embedding that explains more of the flux. 
         Embedding dimensions refer to the size of the organization vector.
@@
     \caption{
-		\textbf{Embedding distance explains more variance for global, within, and between country flux than geographic distance.}
+        \textbf{Embedding distance explains more variance for global, within, and between-country flux than geographic distance.}
         \textbf{a.}
         Embedding distance (cosine distance between vectors) explains more of the total distance than does geographic distance (\textbf{b}). 
-		Red line is line of best fit. 
+        Red line is a line of best fit. 
         Black dots are mean flux across binned distances.
-		Color indicates frequency of organization pairs within each hex bin.
+        The color indicates the frequency of organization pairs within each hex bin.
         Results here are identical to those shown in Fig.~\ref{fig:gravity_performance}a and Fig.~\ref{fig:gravity_performance}.
@@
         Predictions of flux between organization pairs made using embedding distance out-performs those made using geographic distance. 
-		Boxplots show distribution of actual flux for binned values of predicted flux.
+        Boxplots show the distribution of actual flux for binned values of predicted flux.
         Box color corresponds to the degree to which the distribution overlaps $x = y$.
@@
         Performance of personalized page rank scores in explaining and predicting mobility.
-		Personalized page rank is calculated for the underlying mobility network, and similarity between resulting vectors used as the PPR distance.
+        Personalized page rank is calculated for the underlying mobility network and similarity between resulting vectors used as the PPR distance.
         PPR distance does not explain global mobility (\textbf{a}), or same (\textbf{b}) or different (\textbf{c}) country mobility, performing worse than geographic distance (Fig.~\ref{fig:supp:gravity_correlation}).
-		Red line is line of best fit. 
+        Red line is the line of best fit. 
         Black dots are mean flux across binned distances.
-		Color indicates frequency of organization pairs within each hex bin.
+        The color indicates the frequency of organization pairs within each hex bin.
         Similarly, PPR distance performs poorly as a distance metric for gravity model predictions globally (\textbf{d}), and across pairs of organizations in the same (\textit{e}) and in different (\textbf{f}) countries.
-		Boxplots show distribution of actual flux for binned values of predicted flux.
+        Boxplots show the distribution of actual flux for binned values of predicted flux.
         Box color corresponds to the degree to which the distribution overlaps $x = y$.
@@
         \textbf{a.} Spearman correlation (n = 143) between Times prestige rank and SemAxis rank, by the number of high and bottom-ranked (geographically matched) universities aggregated to form the poles.
-		More universities improves performance, but quickly saturates after around five universities. 
-		\textbf{b - f.} Comparison between the Times and SemAxis ranks of universities, by number of universities used to define the poles (n). 
+        More universities improve performance but quickly saturates after around five universities. 
+        \textbf{b - f.} Comparison between the Times and SemAxis ranks of universities, by the number of universities used to define the poles (n). 
         White points are those top and bottom 20 universities aggregated to define the ends of the axis. 
-		The grey box corresponds to the top 20 and bottom 20 ranks. 
+        The gray box corresponds to the top 20 and bottom 20 ranks. 
           PCC details the estimate from Spearman correlation between the two rankings. 
@@
         \textbf{Geography and prestige SemAxis by U.S. state.}
-		SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S.
+        SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and the geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S.
 Universities (bottom to top).
@@
     \caption{
-		\textbf{Geography and prestige SemAxis in U.S. by Sector.}
-		SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S.
+        \textbf{Geography and prestige SemAxis in the U.S. by Sector.}
+        SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and the geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S.
 Universities (bottom to top).

### 2020-02-25 paper/current/main.tex
added basic abstract with some references

--- 2020-02-25 paper/current/main.tex
@@
 
+%
+% ABSTRACT
+%
+
+\begin{abstract}
+
+Scientific mobility, the movement of scientists between organizations, drives innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige} however the complexity of factors driving global scientific mobility~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career} necessitates simplified models for reasoning about and crafting policy around mobility.
+Common models of mobility, such as the Gravity Model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity, simini2012universal}, are a function on the \textit{distance} between places.
+However, amid a globalizing scientific enterprise~\autocite{czaika2018globalisation}, geographic distance is only becoming less useful for understanding mobility, and other abstract notions of distance~\autocite{boschma2005proximity} cannot be measured.
+Here, we learn an effective distance directly from mobility data using the skip-gram word embedding model~\autocite{mikolov2013word2vec}, treating organizations analogously to words and career trajectories to sentences.
+We source publications of disaambiguated authors from the Web of Science database to construct mobility embeddings for authors career trajectories between 2008 and 2019. 
+We demonstrate distance between vectors in the learned embedding better explains and predicts mobility between organizations than does geographic distance, a result of an underlying connection between word embeddings and the gravity model of mobility.
+In additional to capturing geographic relationships, these embeddings capture latent religious, cultural, social, and linguistic relationships between organizations at multiple scales of granularity. 
+Without explicit inclusion of prestige, embeddings also capture complex organizational hierarchies and can be used to re-construct university rankings. 
+Our findings demonstrate the potential of learning efficient, dense, and meaningful vector-space representations of scientific mobility directly from the data, one that models a complex notion of inter-organization distance and which points towards a generalized methodology of reasoning about all kinds of mobility.
+
+\end{abstract}
+
+%
+% INTRODUCTION
+%
 \section{Introduction}\label{sec:introduction} %{{{
@@
 For embedding distance , we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data. 
-To estimate parameters $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_basic}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.
+To estimate parameters $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_flux}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.
 
@@
     \centering
-    \includegraphics[width=0.8\columnwidth]{\figdir/Math/approxi_proof.pdf}
-    \caption{Relationship between the conditional probability $p(j|i)$ from data and approximate functional form Eq. \ref{eq:real_embedding_relationship}}.
+    \includegraphics[width=0.8\columnwidth]{\figdir/Math/approxi_proof.png}
+    \caption{Relationship between the conditional probability $p(j|i)$ and approximate functional form Eq. \ref{eq:real_embedding_relationship}}.
     \label{fig:real_embedding_relationship}
@@
 
-The SGNS model learns an effective distance from trajectories, one which we can visualize the results into two dimensional space by projecting high dimensional organizational vectors into two dimensions vectors using UMAP \cite{mcinnes2018umap} (Fig.~\ref{fig:projection}a).
+The SGNS model learns an effective distance from trajectories, one which we can visualize by projecting organizational vectors into two dimensions using UMAP \cite{mcinnes2018umap} (Fig.~\ref{fig:projection}a).
 Overall, organizations are clustered by geography, according to the nations in which they are location;
@@
 When not defined by geography, clusters appear to be defined by linguistic and historical ties, as is the case for the commonwealth countries. 
-By looking closely at the dendrogram and meta-data, there is a tendency that countries are merged as a group if they share the language in the early stage of the deprogram and geographical aspect plays a more major role in the later stage of the dendrogram.
+By looking closely at the deprogram and meta-data, there is a tendency that countries are merged as a group if they share the language in the early stage of the deprogram and geographical aspect plays a more major role in the later stage of the dendrogram.
 
@@
 \textit{CluSim} is a method that calculates the similarity between the cluster results and, for hierarchical clustering, can adjust the relative importance of membership at different levels of the hierarchy with scaling parameter $r$, acting likes ``zooming lens''.
-If $r$ is high, the similarity is based on the lower levels of the dendrogram , and when $r$ is low, the similarity is based on higher levels of the dendrogram. 
-In fig. \ref{fig:clustering}a, we report three cluster similarity curves (continent, language, language family) with varying scaling parameter $r$.
+If $r$ is high, the similarity is based on the lower levels of the dendrogram, and when $r$ is low, similarity is based on higher levels dendrogram. 
+In fig. \ref{fig:clustering}b, we report three cluster similarity curves (continent, language, language family) with varying scaling parameter $r$.
 As expected, continent plays a major role at higher levels of clustering process (low $r$), language and language family explain the clustering process more at the lower levels (high $r$). 

### 2020-02-26 paper/current/main.tex
Abstract edits

@@
 
-Scientific mobility, the movement of scientists between organizations, drives innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige} however the complexity of factors driving global scientific mobility~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career} necessitates simplified models for reasoning about and crafting policy around mobility.
+Scientific mobility, the movement of scientists between organizations, drives innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige} however the complexity of factors driving global scientific mobility~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics} necessitates simplified models for reasoning about and crafting policy around mobility.
 Common models of mobility, such as the Gravity Model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity, simini2012universal}, are a function on the \textit{distance} between places.
-However, amid a globalizing scientific enterprise~\autocite{czaika2018globalisation}, geographic distance is only becoming less useful for understanding mobility, and other abstract notions of distance~\autocite{boschma2005proximity} cannot be measured.
-Here, we learn an effective distance directly from mobility data using the skip-gram word embedding model~\autocite{mikolov2013word2vec}, treating organizations analogously to words and career trajectories to sentences.
-We source publications of disaambiguated authors from the Web of Science database to construct mobility embeddings for authors career trajectories between 2008 and 2019. 
-We demonstrate distance between vectors in the learned embedding better explains and predicts mobility between organizations than does geographic distance, a result of an underlying connection between word embeddings and the gravity model of mobility.
-In additional to capturing geographic relationships, these embeddings capture latent religious, cultural, social, and linguistic relationships between organizations at multiple scales of granularity. 
-Without explicit inclusion of prestige, embeddings also capture complex organizational hierarchies and can be used to re-construct university rankings. 
+However, amid a globalizing scientific enterprise~\autocite{czaika2018globalisation}, geographic distance is only becoming less useful for understanding mobility, and other abstract notions of distance~\autocite{boschma2005proximity} cannot be meaningfully measured.
+Here, we demonstrate a data-driven approach of learning an effective distance that encodes the latent structure of mobility using the skip-gram word embedding model~\autocite{mikolov2013word2vec}, treating organizations analogously to words and career trajectories to sentences.
+We source publications of disambiguated authors from the Web of Science database to construct mobility embeddings for authors career trajectories between 2008 and 2019. 
+Distance between vectors in the learned embedding space better explain and predict mobility between organizations than does geographic distance, which we speculate emerges from an underlying connection between embeddings and the gravity model.
+In additional to geography, these embeddings capture latent religious, cultural, social, and linguistic, and implicit hierarchical relationships between organizations at multiple levels of granularity.
 Our findings demonstrate the potential of learning efficient, dense, and meaningful vector-space representations of scientific mobility directly from the data, one that models a complex notion of inter-organization distance and which points towards a generalized methodology of reasoning about all kinds of mobility.

### 2020-02-26 paper/current/main.tex
more minor abstract edits

@@
 
-Scientific mobility, the movement of scientists between organizations, drives innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige} however the complexity of factors driving global scientific mobility~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics} necessitates simplified models for reasoning about and crafting policy around mobility.
+Mobility is essential to science --- it drives innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige} however the complexity of factors driving global scientific mobility~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics} necessitates simplified models for reasoning about and crafting policy around mobility.
 Common models of mobility, such as the Gravity Model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity, simini2012universal}, are a function on the \textit{distance} between places.
@@
 \section{Introduction}\label{sec:introduction} %{{{
+
+% Introduce the question, why is it important?
+
+%
 

### 2020-02-27 paper/current/main.tex
edits to abstract

@@
 
-Mobility is essential to science --- it drives innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige} however the complexity of factors driving global scientific mobility~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics} necessitates simplified models for reasoning about and crafting policy around mobility.
+Mobility is essential to science---it drives innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige} however the complexity of factors driving global scientific mobility~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics} necessitates simplified models for reasoning about and crafting effective policy.
 Common models of mobility, such as the Gravity Model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity, simini2012universal}, are a function on the \textit{distance} between places.
-However, amid a globalizing scientific enterprise~\autocite{czaika2018globalisation}, geographic distance is only becoming less useful for understanding mobility, and other abstract notions of distance~\autocite{boschma2005proximity} cannot be meaningfully measured.
+However, amid a globalizing scientific enterprise~\autocite{czaika2018globalisation}, geographic distance is only becoming less useful for understanding mobility, whereas other abstract notions of distance~\autocite{boschma2005proximity} cannot be meaningfully measured.
 Here, we demonstrate a data-driven approach of learning an effective distance that encodes the latent structure of mobility using the skip-gram word embedding model~\autocite{mikolov2013word2vec}, treating organizations analogously to words and career trajectories to sentences.

### 2020-02-27 paper/current/main.tex
introduction draft

@@
 
-%
+When scientists move, so does their knowledge, and for scientific mobility, like all human movement, distance matters. 
+However, how exactly do we measure the distance between two places?
+Australia may be physically close to Indonesia, but in terms of language, history, and shared culture, they are essentially neighbors to geographically distant countries like the United Kingdom or United States.
+There are many ways to think about the distance~\autocite{boschma2005proximity}, but only geographic distance can be meaningfully quantified. 
+In turn, models of human mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation models ~\autocite{simini2012universal}, rely almost exclusively on geographic distance, rather than other less measurable though important forms.
+Encoding distance in a way that considers not just geography, but also historical, linguistic, cultural, and cognitive proximity would improve our models and thus ability to reason about science and immigration policies.
+
+The skip-gram embedding model preserves semantic relationships between words in a dense and meaningful low-dimensional vector-space representation~\cite{mikolov2013word2vec}, and just as its has been applied to and revealed insights implicit in text~\cite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}, so too might this model encode the latent structures of global scientific mobility.
+As scientist's careers progress, they move institutions or pick up additional affiliations, forming co-affiliation or \textit{mobility trajectories} that can be derived from their publication histories~\autocite{robinson2019mobility, sugimoto2017mostimpact}.
+We embed mobility trajectories by treating organizations analogously to words and trajectories analogously to sentences, and feed the resulting "sentence" into the standard skip-gram model (Fig.~\ref{fig:methods:mobility_sentence}).
+The result is a vector-space representation of organizations in which the \textit{cosine distance} between vectors represents the tendency for pairs of organizations to occur near one another in the same career path.
+In addition to encoding latent structure, these embeddings are computationally and space efficient, robust to noise, and allow for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.
+
+We embed the trajectories of the three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019 as evidenced by their publications indexed in the Web of Science.
 

### 2020-02-27 paper/current/main.tex
minor changes throughout—updated \cite to \autocite

@@
 \documentclass[12pt]{article} %{{{
+
+% Text
+\setlength{\marginparwidth}{2.3cm}
 
@@
 \usepackage{url}
+
+% Figure caption
+\usepackage{setspace}
+\usepackage[font=small,labelfont=bf]{caption}
+\captionsetup[subfigure]{font={bf,small}, skip=1pt, singlelinecheck=false}
 
@@
 Trajectories are constructed from author affiliations listed on the byline of publications for a given author.
-Given the limitations of author-name disambiguation, we limit to papers published after 2008, when the Web of Science began providing full names and institutional affiliations~\cite{caron2014disambiguation} and when performance is strongest (ref to SI?).
-This yields 33,934,672 author-affiliation combinations representing 112,963,792 authors. 
+Given the limitations of author-name disambiguation, we limit to papers published after 2008, when the Web of Science began providing full names and institutional affiliations~\autocite{caron2014disambiguation} and when performance is strongest (ref to SI?).
+This yields 33,934,672 author-affiliation combinations representing 12,963,792 authors. 
 Each author-affiliation combination is associated with the publication year and a unique id that maps the affiliation to a disambiguate organization. 
@@
 % %Organization information
-Affiliations mapped to one of 8,661 organizations, disambiguated following a mostly manual process originally designed for the Leiden Rankings of World Universities~\cite{waltman2012leidenrankings}. 
+Affiliations mapped to one of 8,661 organizations, disambiguated following a mostly manual process originally designed for the Leiden Rankings of World Universities~\autocite{waltman2012leidenrankings}.
 Organizational records were associated with a full name, a type indicating the sector (e.g., University, Government, Industry), and an identifier for the country and city of the organization. 
@@
 
-Scientific mobility is complex and can be defined in many possible ways~\cite{robinson2019mobility}.
+Scientific mobility is complex and can be defined in many possible ways~\autocite{robinson2019mobility}.
 Here, we consider an author as mobile when at least two distinct organizational affiliations appear in their trajectory during the 2008-2019 time window. 
@@
 	\centering
-	\label{fig:methods:mobility_sentence}
 	\includegraphics[width=0.7\textwidth]{\figdir/mobility_example_combined.pdf}
 	\caption{
-		\textbf{Co-affiliation trajectories represented as sentences}
+		\textbf{Co-affiliation trajectories represented as sentences.}
 		\textbf{a.} 
@@
 	}
+	\label{fig:methods:mobility_sentence}
 \end{figure}
@@
 %% word2vec
-These mobility sentences are used as input to the standard skip-gram negative sampling (SGNS) model for word embedding, commonly known as \textit{word2vec}~\cite{mikolov2013word2vec} . 
+These mobility sentences are used as input to the standard skip-gram negative sampling (SGNS) model for word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec} . 
 In natural-language processing, word embeddings are used to construct dense vector-space representations of words and phrases, in which distance relationships between words correspond to a notion of semantic distance.
@@
 All word embeddings are trained using the \textit{gensim} python implementation of the SGNS \textit{word2vec} model. 
-We visualize embeddings by projecting into two dimensions using UMAP~\cite{mcinnes2018umap}.
+We visualize embeddings by projecting into two dimensions using UMAP~\autocite{mcinnes2018umap}.
 
@@
 the gravity law of mobility loosely derives from the physical law of gravity, whereby the attraction between two objects is a function of their mass and the distance between them.
-Given its simplicity and flexibility, this formulation and variants have proven incredibly useful for modeling and predicting many kinds of mobility~\cite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
+Given its simplicity and flexibility, this formulation and variants have proven incredibly useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
 Following the gravity law, the expected flow between two organizations is defined as follows,
@@
 There are two popular forms of the $f(r_{ij})$.
-The first one is power-law function with $f(r_{ij})= r^{-\alpha}_{ij}  (\alpha > 0)$, and the another one is exponential function with $f(r_{ij}) = e^{-\beta r_{ij}} (\beta > 0)$ \cite{chen2015distance}.
+The first one is power-law function with $f(r_{ij})= r^{-\alpha}_{ij}  (\alpha > 0)$, and the another one is exponential function with $f(r_{ij}) = e^{-\beta r_{ij}} (\beta > 0)$ \autocite{chen2015distance}.
 $f(r_{ij})$, $C$ can be chosen as to fit the data with the simple regression.
@@
 Here, non-zero flows account for only 4.2 percent of all possible pairs of  the 6,580 organizations represented in the embedding.
-This value is comparable to other common applications of the gravity law, such as to hone calls, commuting, and migration \cite{simini2012universal}.
+This value is comparable to other common applications of the gravity law, such as to hone calls, commuting, and migration \autocite{simini2012universal}.
 We follow standard practice and exclude from our analysis zero flows.
@@
 By constructing semantic embeddings from mobility trajectories, we allow for unique methodology for understading the embedding space, such as SemAxis.
-SemAxis~\cite{an2018semaxis} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these term to the concept.
+SemAxis~\autocite{an2018semaxis} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these term to the concept.
 The precise axis is an antonym pair defined \textit{ad-hoc} for the specific use case.
@@
 
-The SGNS model learns an effective distance from trajectories, one which we can visualize by projecting organizational vectors into two dimensions using UMAP \cite{mcinnes2018umap} (Fig.~\ref{fig:projection}a).
+The SGNS model learns an effective distance from trajectories, one which we can visualize by projecting organizational vectors into two dimensions using UMAP \autocite{mcinnes2018umap} (Fig.~\ref{fig:projection}a).
 Overall, organizations are clustered by geography, according to the nations in which they are location;

### 2020-02-27 paper/current/main.tex

@@
 Sixteen different sector types were included in the analysis, which we aggregated to a four high-level codes: \textit{University}, \textit{Hospital}, \textit{Government}, and \textit{Other}.
-Each record was also associated with a latitude and longitude, however for many organizations these were missing or incorrect.
+Each record was also associated with a latitude and longitude, however, for many organizations, these were missing or incorrect.
 We manually updated the coordinates of 2,267 organizations by searching the institution name and city on Google Maps;
@@
 The data was further enriched with country-level information, including continent, majority language spoken, and language family of the majority language (e.g., the language family of \textit{Spanish} is \textit{Italic}).
-State/province level  information were added using the reverse geocoding service LocationIQ using each organization's latitude and longitude as input. 
+State/province-level information was added using the reverse geocoding service LocationIQ using each organization's latitude and longitude as input.
 Regional census classifications were also added for states in the United States.
-For each organization, we also calculated a size as the average number of unique authors (mobile and non-mobile) who published with that organization across each year of our dataset;
+For each organization, we also calculated size as the average number of unique authors (mobile and non-mobile) who published with that organization across each year of our dataset;
 in the case that authors publish with multiple affiliations in a single year, they are counted towards each.
@@
 For example, a researcher affiliated with the smaller regional school ``Indiana University South Bend'' will be listed as affiliated with only the ``Indiana University System''.
-We identify all specific organizations that always co-occur along a more general one.
+We identify all specific organizations that always co-occur along with a more general one.
 For every career trajectory that includes one of these specific organizations, we remove all occurrences of the more general organization;
@@
 Here, we consider an author as mobile when at least two distinct organizational affiliations appear in their trajectory during the 2008-2019 time window.
-Under this definition, mobile authors constitute 3,007,192 or 23.2 percent of all authors, and 17,700,095 author-affiliation combinations. 
+Under this definition, mobile authors constitute 3,007,192 or 23.2 percent of all authors and 17,700,095 author-affiliation combinations.
 Mobile authors were associated with, on average, 2.5 distinct organizational affiliations.
-Rates of mobility tended to differ across country. 
+Rates of mobility tended to differ across the country.
 For example, France, Qatar, the USA, Iraq, and Luxembourg had the most mobile authors (ref figure).
@@
 The SGNS model has several tunable hyper-parameters, including the size of the learned vectors, the size of the token window considered when training, the minimum frequency threshold for including an organization, and the number of iterations.
-We iterate through several values of vector size and window size, repeating analysis for each combination. 
+We iterate through several values of vector size and window size, repeating the analysis for each combination.
 To mitigate the effect of less common organizations, only organizations appearing at least 50 times in mobility sentences are included in the embedding;
 this yields 6,580, or 76 percent of all organizations.
-We iterate the SGNS training for five epochs over all mobility sentences. 
+We iterate the SGNS training for five epochs overall mobility sentences.
 All word embeddings are trained using the \textit{gensim} python implementation of the SGNS \textit{word2vec} model.
@@
 
-We also calculate two forms of distance between organizations. 
+We also calculate two forms of the distance between organizations.
 The geographic distance, $g_{ij}$, is the pairwise geographic distance between organizations.
@@
 For embedding distance , we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data.
-To estimate parameters $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_flux}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.
+To estimate parameters $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_basic}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.
 
@@
 For example, if 20 universities top-ranked universities are selected and six of them are in the Northeastern United States, then the bottom six universities according to the same ranking will be included in the low-ranked subset.
-From the prestige axis we also derive what we call \textit{SemRank}, a university ranking based on the nearness of universities to the \textit{Elite} end of the axis. 
+From the prestige axis, we also derive what we call \textit{SemRank}, a university ranking based on the nearness of universities to the \textit{Elite} end of the axis.
 We compare the SemAxis ranking to the traditional university rankings using Spearman rank correlations.
@@
 
-Results are reported for embeddings with a dimensionality of 300 and a window size of one, which were the parameters that produced  that best explained the flux between organizations (see Fig.
+Results are reported for embeddings with a dimensionality of 300 and a window size of one, which was the parameters that produced that best explained the flux between organizations (see Fig.
 SI~\ref{fig:supp:hyperparams}).
-We note that this performance and the outcomes of analysis was robust to hyperparemeters settings.
+We note that this performance and the outcomes of the analysis were robust to hyperparameters settings.
 
@@
         \textbf{a.} embedding distance (cosine distance between vectors) explains more of the flux between organization pairs than does geographic distance (\textbf{b}).
-		Red line is line of best fit. 
+        Red line is the line of best fit.
         Black dots are mean flux across binned distances.
-		Color indicates frequency of organization pairs within each hex bin.
+        The color indicates the frequency of organization pairs within each hex bin.
         \textbf{c-d.} Predictions of flux between organization pairs made using embedding distance out-perform those made using geographic distance.
-		Boxplots show distribution of actual flux for binned values of predicted flux.
+        Boxplots show the distribution of actual flux for binned values of predicted flux.
         Box color corresponds to the degree to which the distribution overlaps $x = y$.
-		\textbf{e-f.} Predictions made using model parameters learned from subset of same-country organization pairs. 
+        \textbf{e-f.} Predictions made using model parameters learned from the subset of same-country organization pairs.
         Embedding distance outperforms those made for geographic distance.
@@
         Size indicates the size of the organization.
-		Color indicates the continent. 
-		We re-project subsets of organizational vectors to uncover more complex local structure.
+        The color indicates the continent.
+        We re-project subsets of organizational vectors to uncover more complex local structures.
         \textbf{b.} Re-projection of organizational vectors roughly corresponding to West-Asian, Southeast Asian, and South Asian countries.
@@
         \textbf{d.} Re-projection of organizations in the United States reveal geographic clustering based on state.
-		Color indicates Census Bureau-designated regions,
-		\textbf{e.} Re-projection of organizations in Massachusetts reveal clustering based on organizational sector, prestige. 
+        The color indicates Census Bureau-designated regions,
+        \textbf{e.} Re-projection of organizations in Massachusetts reveal clustering based on the organizational sector, prestige.
         Color indicates sector designation of organization.
@@
 When not defined by geography, clusters appear to be defined by linguistic and historical ties, as is the case for the commonwealth countries.
-By looking closely at the deprogram and meta-data, there is a tendency that countries are merged as a group if they share the language in the early stage of the deprogram and geographical aspect plays a more major role in the later stage of the dendrogram.
+By looking closely at the dendrogram and meta-data, there is a tendency that countries are merged as a group if they share the language in the early stage of the deprogram and geographical aspect plays a more major role in the later stage of the dendrogram.
 
@@
 \textit{CluSim} is a method that calculates the similarity between the cluster results and, for hierarchical clustering, can adjust the relative importance of membership at different levels of the hierarchy with scaling parameter $r$, acting likes ``zooming lens''.
-If $r$ is high, the similarity is based on the lower levels of the dendrogram, and when $r$ is low, similarity is based on higher levels dendrogram. 
-In fig. \ref{fig:clustering}b, we report three cluster similarity curves (continent, language, language family) with varying scaling parameter $r$.
+If $r$ is high, the similarity is based on the lower levels of the dendrogram, and when $r$ is low, the similarity is based on higher levels of the dendrogram.
+In fig. \ref{fig:clustering}a, we report three cluster similarity curves (continent, language, language family) with varying scaling parameter $r$.
 As expected, continent plays a major role at higher levels of clustering process (low $r$), language and language family explain the clustering process more at the lower levels (high $r$).
@@
         \textbf{Geography, then language, dictate international mobility.}
-		\textbf{a.} Hierarchically clustered similarity matrix of country vectors, aggregated as the mean of all organization vectors within the country that has a more than 25 organizations, excluding the United States.
-		Color of matrix cells corresponds to similarity between country vectors.
+        \textbf{a.} Hierarchically clustered similarity matrix of country vectors, aggregated as the mean of all organization vectors within the country that has more than 25 organizations, excluding the United States.
+        The color of matrix cells corresponds to the similarity between country vectors.
         Color of country names corresponds to their cluster.
@@
 Universities in bordering states, such as Arizona and Connecticut, are closer to the ends of the axis (Fig. SI~\ref{fig:supp:semaxis_states}b and Fig. SI~\ref{fig:supp:semaxis_states}e).
-Universities in new York are nearer to the Massachusetts end of the axis (Fig.
+Universities in New York are nearer to the Massachusetts end of the axis (Fig.
 SI~\ref{fig:supp:semaxis_states}f), whereas universities in Florida are less aligned to either (Fig.
@@
         \textbf{Embedding captures latent geography and prestige hierarchy.}
-		\textbf{a.} illustrates SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S.
+        \textbf{a.} illustrates SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and the geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S.
 Universities (bottom to top).
@@
         White points are those top and bottom 20 universities aggregated to define the ends of the axis.
-		The grey box corresponds to the top 20 and bottom 20 ranks. 
+        The gray box corresponds to the top 20 and bottom 20 ranks.
           The estimate of the spearman rank correlation between the SemAxis and Times ranking is 0.81 (n = 145).
@@
 To test this, we derive a ranking using the prestige axis that we call \textit{SemRank}, and compare them to traditional university rankings.
-SemRank is defined from the position of organizations along the prestige axis, with the top ranked being the furthest towards the \textit{Elite} end of the axis.
+SemRank is defined from the position of organizations along the prestige axis, with the top-ranked being the furthest towards the \textit{Elite} end of the axis.
 We find that SemRank derived is highly correlated with the Times ranking ($\rho = 0.81$, Fig.~\ref{fig:semaxis}b).
@@
         The number of papers published by mobile authors has been steadily increasing from 2008 to 2017, with a small decrease in 2018,  likely an artifact of the Web of Science indexing process.
-		Lines corresponds to publications by mobile authors (org, purple), by authors with affiliations in at least two cities (blue), at least two regions (green), and at least two countries (yellow).
-		There is no evidence of major changes in publication patterns of mobile authors during this time period. 
+        Lines correspond to publications by mobile authors (org, purple), by authors with affiliations in at least two cities (blue), at least two regions (green), and at least two countries (yellow).
+        There is no evidence of major changes in the publication patterns of mobile authors during this period.
         \textbf{b.}
@@
         \textbf{d.}
-		The proportion of authors publications across fields has largely remained steady.
-		Biology and Health Science has comprised the majority of publications across nearly all years, but has steadily declined in proportion. 
+        The proportion of authors' publications across fields has largely remained steady.
+        Biology and Health Science has comprised the majority of publications across nearly all years but has steadily declined in proportion.
         However, the proportion of Social Science and Humanities publications has been steadily increasing.
@@
         \textbf{a.}
-		Proportion of researchers in each country classified as mobile, meaning that they have at least two organization affiliations within the period of study. 
+        The proportion of researchers in each country classified as mobile, meaning that they have at least two organization affiliations within the period of study.
         The countries with the most mobile researchers are the United States, China, France, Great Britain, and Germany.
@@
         The same information, arranged into a cumulative distribution.
-		The five countires with the highest mobility account for approximately 70 percent of all mobility. 
+        The five countries with the highest mobility account for approximately 70 percent of all mobility.
         \textbf{c.} The proportion of researchers labeled as mobile by country.
-		\textbf{d.} First two principal components of four variables: proportion in each country mobile across organizations, proportion mobile across cities, proportion mobile across regions, and proportion mobile across countries.
-		First component captures overall degree of mobile, whereas the second compares within-country against across-country mobility. 		
+        \textbf{d.} The first two principal components of four variables: proportion in each country mobile across organizations, proportion mobile across cities, proportion mobile across regions, and proportion mobile across countries.
+        The first component captures the overall degree of mobile, whereas the second compares within-country against across-country mobility.
     }
@@
         \textbf{a.}
-		Proportion of mobile authors by how many organizations are represented 	in their career trajectories. 
+        The proportion of mobile authors by how many organizations are represented in their career trajectories.
         For example, for mobile authors, 100 percent of authors held an affiliation with at least two organizations, whereas about 35 percent were affiliated with 3 ore more organizations between 2008 and 2019.
@@
         \textbf{Larger dimensions, smaller window size improves embedding performance.}
-		The correlation, or amount of flux explained by the embedding distance with varying skip-gram negative sampling hyperparameters. 
+        The correlation or amount of flux explained by the embedding distance with varying skip-gram negative sampling hyperparameters.
         Window size refers to the window, on either side of the target token, to use as context for training.
-		Smaller window sizes results in an embedding that explain more of the flux. 
+        Smaller window sizes result in an embedding that explains more of the flux.
         Embedding dimensions refer to the size of the organization vector.
@@
     \caption{
-		\textbf{Embedding distance explains more variance for global, within, and between country flux than geographic distance.}
+        \textbf{Embedding distance explains more variance for global, within, and between-country flux than geographic distance.}
         \textbf{a.}
         Embedding distance (cosine distance between vectors) explains more of the total distance than does geographic distance (\textbf{b}).
-		Red line is line of best fit. 
+        Red line is a line of best fit.
         Black dots are mean flux across binned distances.
-		Color indicates frequency of organization pairs within each hex bin.
+        The color indicates the frequency of organization pairs within each hex bin.
         Results here are identical to those shown in Fig.~\ref{fig:gravity_performance}a and Fig.~\ref{fig:gravity_performance}.
@@
         Predictions of flux between organization pairs made using embedding distance out-performs those made using geographic distance.
-		Boxplots show distribution of actual flux for binned values of predicted flux.
+        Boxplots show the distribution of actual flux for binned values of predicted flux.
         Box color corresponds to the degree to which the distribution overlaps $x = y$.
@@
         Performance of personalized page rank scores in explaining and predicting mobility.
-		Personalized page rank is calculated for the underlying mobility network, and similarity between resulting vectors used as the PPR distance.
+        Personalized page rank is calculated for the underlying mobility network and similarity between resulting vectors used as the PPR distance.
         PPR distance does not explain global mobility (\textbf{a}), or same (\textbf{b}) or different (\textbf{c}) country mobility, performing worse than geographic distance (Fig.~\ref{fig:supp:gravity_correlation}).
-		Red line is line of best fit. 
+        Red line is the line of best fit.
         Black dots are mean flux across binned distances.
-		Color indicates frequency of organization pairs within each hex bin.
+        The color indicates the frequency of organization pairs within each hex bin.
         Similarly, PPR distance performs poorly as a distance metric for gravity model predictions globally (\textbf{d}), and across pairs of organizations in the same (\textit{e}) and in different (\textbf{f}) countries.
-		Boxplots show distribution of actual flux for binned values of predicted flux.
+        Boxplots show the distribution of actual flux for binned values of predicted flux.
         Box color corresponds to the degree to which the distribution overlaps $x = y$.
@@
         \textbf{a.} Spearman correlation (n = 143) between Times prestige rank and SemAxis rank, by the number of high and bottom-ranked (geographically matched) universities aggregated to form the poles.
-		More universities improves performance, but quickly saturates after around five universities. 
-		\textbf{b - f.} Comparison between the Times and SemAxis ranks of universities, by number of universities used to define the poles (n). 
+        More universities improve performance but quickly saturates after around five universities.
+        \textbf{b - f.} Comparison between the Times and SemAxis ranks of universities, by the number of universities used to define the poles (n).
         White points are those top and bottom 20 universities aggregated to define the ends of the axis.
-		The grey box corresponds to the top 20 and bottom 20 ranks. 
+        The gray box corresponds to the top 20 and bottom 20 ranks.
           PCC details the estimate from Spearman correlation between the two rankings.

### 2020-02-27 paper/current/main.tex
strange merge—lerge diff that I think is a technical issue

--- 2020-02-27 paper/current/main.tex
@@
 In additional to geography, these embeddings capture latent religious, cultural, social, and linguistic, and implicit hierarchical relationships between organizations at multiple levels of granularity.
-Our findings demonstrate the potential of learning efficient, dense, and meaningful vector-space representations of scientific mobility directly from the data, one that models a complex notion of inter-organization distance and which points towards a generalized methodology of reasoning about all kinds of mobility.
+With this approach, we can learn efficient, dense, and meaningful vector-space representations of scientific mobility directly from the data, one that models a complex notion of inter-organization distance and which points towards a generalized methodology of reasoning about all kinds of mobility.
 
@@
 We embed the trajectories of the three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019 as evidenced by their publications indexed in the Web of Science.
+We adopt the Gravity Model of mobility~\autocite{zipf1946gravity}, one of the most common and broadly applied mobility models () to assess how well the embedding captures mobility.
 

### 2020-02-27 paper/current/main.tex
added text transitioning form intro into gravity law

@@
 The result is a vector-space representation of organizations in which the \textit{cosine distance} between vectors represents the tendency for pairs of organizations to occur near one another in the same career path.
-In addition to encoding latent structure, these embeddings are computationally and space efficient, robust to noise, and allow for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.
+In addition to encoding latent structure, these  are computationally and space efficient, robust to noise, and allow for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.
 
 We embed the trajectories of the three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019 as evidenced by their publications indexed in the Web of Science.
-We adopt the Gravity Model of mobility~\autocite{zipf1946gravity}, one of the most common and broadly applied mobility models () to assess how well the embedding captures mobility.
+We adopt the Gravity Model of mobility~\autocite{zipf1946gravity}, one of the most common and broadly applied mobility models~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} to assess how well the embedding captures mobility.
+We derive the \textit{expected flow} from the base gravity model, defined as,
+
+\begin{equation}
+	\label{eq:gravity_basic}
+	f_{ij} = C*m_{i}m_{j}*f(r_{ij})
+\end{equation}
+
+Where the flow, or number of authors co-affiliated with two organizations during the time period $f_{ij}$, increases with the organization's sizes, $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+We consider two distances, $f_{ij}$, the geographic distance between the organizations, and the \textit{embedding distance} defined as the cosine distance between the organization's vector in the trained embedding space.
+We argue that the performance of a distance measure can be observed from their ability to explain expected mobility between organizations, as well as to predict flows using the gravity model. 
+For geographic distance, we define $f(r_{ij})$ as the standard power-decay function, and for the embedding distance, we use the exponential form, selected as the best performing for each case.
 

### 2020-02-27 paper/current/main.tex
moved data + methods to the end
moved extra text to methods
cleaned up gravity performance text

@@
 
-%}}}
-
-%
-% DATA AND METHODS
-%
-\section{Data and Methods}
-\label{sec:datamethods} %{{{
-
-Data, analysis, and associated code have been made publicly available and can be found at \textit{https://github.com/murrayds/...}
-
-\subsection*{Data}
-%% Main dataset
-% Do we need to add the Leiden field classificaiton infomration? It doesn't seem like its relevant for the current analysis.
-% Do we need to talk about how we define mobility in relation to past papers?
-We source co-affiliation trajectories of authors from the Web of Science database hosted by the Center for Science and Technology Studies at Leiden University. 
-Trajectories are constructed from author affiliations listed on the byline of publications for a given author.
-Given the limitations of author-name disambiguation, we limit to papers published after 2008, when the Web of Science began providing full names and institutional affiliations~\autocite{caron2014disambiguation} and when performance is strongest (ref to SI?).
-This yields 33,934,672 author-affiliation combinations representing 12,963,792 authors. 
-Each author-affiliation combination is associated with the publication year and a unique id that maps the affiliation to a disambiguate organization. 
-Combinations are also associated with a publication-level disciplinary classification, one of ``Social sciences and humanities'',
-``Biomedical and health sciences'', ``Physical sciences and engineering'', ``Life and earth sciences'', and ``Mathematics and computer science''.
-Trajectories are represented as the list of author-affiliation combinations, ordered by year of publication, and randomly ordered for combinations within the same year. 
-Authors are classified as mobile when they have at least two distinct organization ids in their trajectory, meaning that they have published using two or more distinct affiliations between 2008 and 2019.
-While the number of publications has increased year-to-year, the mobility and disciplinary makeup of the dataset has not significantly changed across the period of study (see Fig.~\ref{fig:supp:pubs_over_time}).
-
-% %Organization information
-Affiliations mapped to one of 8,661 organizations, disambiguated following a mostly manual process originally designed for the Leiden Rankings of World Universities~\autocite{waltman2012leidenrankings}.
-Organizational records were associated with a full name, a type indicating the sector (e.g., University, Government, Industry), and an identifier for the country and city of the organization. 
-Sixteen different sector types were included in the analysis, which we aggregated to a four high-level codes: \textit{University}, \textit{Hospital}, \textit{Government}, and \textit{Other}. 
-Each record was also associated with a latitude and longitude, however for many organizations these were missing or incorrect.
-We manually updated the coordinates of 2,267 organizations by searching the institution name and city on Google Maps;
-in cases where a precise location of the organization could not be identified, we used the coordinates returned when searching the name of the city.
-The data was further enriched with country-level information, including continent, majority language spoken, and language family of the majority language (e.g., the language family of \textit{Spanish} is \textit{Italic}).
-State/province level  information were added using the reverse geocoding service LocationIQ using each organization's latitude and longitude as input. 
-Regional census classifications were also added for states in the United States.
-For each organization, we also calculated a size as the average number of unique authors (mobile and non-mobile) who published with that organization across each year of our dataset;
-in the case that authors publish with multiple affiliations in a single year, they are counted towards each.
-
-As a result of our disambiguation procedure, some affiliations are mapped to two organizations, one specific, and one more general.
-For example, any author affiliated with ``Indiana University Bloomington'' will also be listed as being affiliated with the ``Indiana University System'', a more general designation for all public universities in Indiana.
-However, a more general organization may not always occur alongside the more specific one.
-For example, a researcher affiliated with the smaller regional school ``Indiana University South Bend'' will be listed as affiliated with only the ``Indiana University System''. 
-We identify all specific organizations that always co-occur along a more general one.
-For every career trajectory that includes one of these specific organizations, we remove all occurrences of the more general organization;
-trajectories containing only a general designation are not altered.
-
-Scientific mobility is complex and can be defined in many possible ways~\autocite{robinson2019mobility}.
-Here, we consider an author as mobile when at least two distinct organizational affiliations appear in their trajectory during the 2008-2019 time window. 
-Under this definition, mobile authors constitute 3,007,192 or 23.2 percent of all authors, and 17,700,095 author-affiliation combinations. 
-Mobile authors were associated with, on average, 2.5 distinct organizational affiliations. 
-Rates of mobility tended to differ across country. 
-For example, France, Qatar, the USA, Iraq, and Luxembourg had the most mobile authors (ref figure).
-However, due to their size, the USA, accounted for nearly 40 percent of all mobile authors worldwide, with  10 countries accounting for 80 percent of all mobility (ref figure).
-In most cases, countries with a high degree inter-organization mobility also had a high degree of international mobility;
-however, the USA and France had a high degree of inter-organization mobility with the corresponding international mobility (ref figure).
-
-\subsection*{Embedding}
-%% Mobility sentences
-We embed co-affiliation trajectories by treating them analogously to sentences, and organizations analogously to words. 
-The trajectories of mobile authors were converted to ''mobility sentences`` by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:methods:mobility_sentence}.a.
-In more complex cases, such as listing multiple affiliations on the same paper or publishing with different affiliations on multiple affiliations in the same year, the order is randomized within that year, as shown in  Fig.~\ref{fig:methods:mobility_sentence}.b.
-
-%
-% Figure - Example of mobility sentences
-%
-\begin{figure}[ht!]
-	\centering
-	\includegraphics[width=0.7\textwidth]{\figdir/mobility_example_combined.pdf}
-	\caption{
-		\textbf{Co-affiliation trajectories represented as sentences.}
-		\textbf{a.} 
-		An authors published five papers across five time periods, with only one affiliation listed in the byline of each paper. 
-		A unique identifier is assigned to each organization, and these are concatenated into a mobility sentence. 
-		\textbf{b.}
-		In a more complex case, an author lists several affiliations on the byline of papers in $t_{2}$, $t_{3}$, and $t_{4}$.
-Here, organization ids are still ordered by year, however order within a single year is random.
-	}
-	\label{fig:methods:mobility_sentence}
-\end{figure}
-
-%% word2vec
-These mobility sentences are used as input to the standard skip-gram negative sampling (SGNS) model for word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec} . 
-In natural-language processing, word embeddings are used to construct dense vector-space representations of words and phrases, in which distance relationships between words correspond to a notion of semantic distance.
-By embedding co-affiliation trajectories, we aim to learn a dense vector for every organization where distance between vectors relates to the tendency for two organizations to co-occur in a token window around the target term in the same career trajectory.
-Vectors are learned by training a neural network to optimize the prediction of so-called context term given a target, in our case using one organization to predict the others appearing in the same co-affiliation trajectory.
-The hidden layer of the trained neural network is used as the
-
-%% Word2vec parameters and training procedure
-The SGNS model has several tunable hyper-parameters, including the size of the learned vectors, the size of the token window  considered when training, the minimum frequency threshold for including an organization, and the number of iterations.
-We iterate through several values of vector size and window size, repeating analysis for each combination. 
-To mitigate the effect of less common organizations, only organizations appearing at least 50 times in mobility sentences are included in the embedding;
-this yields 6,580, or 76 percent of all organizations.
-We iterate the SGNS training for five epochs over all mobility sentences. 
-All word embeddings are trained using the \textit{gensim} python implementation of the SGNS \textit{word2vec} model. 
-We visualize embeddings by projecting into two dimensions using UMAP~\autocite{mcinnes2018umap}.
-
-%
-% SUBSECTION: DISTANCE
-%
-\subsection{Distance}
-%% Distance calculations
-We calculate $f_{ij}$, the pairwise number of co-affiliations between organizations, calculated as the number of co-occurrences of organizations within author co-affiliation trajectories. 
-For example, $f_{ij} = 10$ indicates that ten authors were co-affiliated with both organization $i$ and $j$ between 2008 and 2019, as evidenced from their publications. 
-In contrast to traditional mobility studies, all co-affiliations are symmetric, meaning that $f_{ij} = f_{ji}$.
-
-We also calculate two forms of distance between organizations. 
-The geographic distance, $g_{ij}$, is the pairwise geographic distance between organizations.
-Geographic distance is calculated as the great circle distance, in kilometers, between pairs of organizations. 
-When less than one kilometer, a distance of one is imputed. 
-The embedding distance, $d_{ij}$, is calculated as the pairwise cosine distance between vectors from the learned organization embedding, where $v_{i}$ and $v_{j}$ represent the vectors and $d_{ij} = 1 - \frac{v_{i} \dot v_{j}}{\lVert v_{i} \rVert \lVert v_{j} \rVert}$.
-
-%
-% SUBSECTION: GRAVITY LAW
-%
-\subsection{Gravity Law}
-
-We model the flow of authors across organizations, $f_{ij}$, using the gravity law. 
-the gravity law of mobility loosely derives from the physical law of gravity, whereby the attraction between two objects is a function of their mass and the distance between them.
-Given its simplicity and flexibility, this formulation and variants have proven incredibly useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
-Following the gravity law, the expected flow between two organizations is defined as follows,
-
-\begin{equation}
-	\label{eq:gravity_basic}
-	f_{ij} = C*m_{i}m_{j}*f(r_{ij})
-\end{equation}
-
-where $m_{i}$ and $m_{j}$ are the yearly-average size of each organization during the time window, and $f(r_{ij})$ is a distance-decaying function  between the two organizations.
-There are two popular forms of the $f(r_{ij})$.
-The first one is power-law function with $f(r_{ij})= r^{-\alpha}_{ij}  (\alpha > 0)$, and the another one is exponential function with $f(r_{ij}) = e^{-\beta r_{ij}} (\beta > 0)$ \autocite{chen2015distance}.
-$f(r_{ij})$, $C$ can be chosen as to fit the data with the simple regression.
-
-We consider separate variants of $f(r_{ij})$ for geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$, report the best-fit model of each distance.
-For geographic distance, we use the power-law function of the gravity law, with $f(g_{ij})= g^{-\alpha}_{ij}$, where $\alpha$ is estimated from the data. 
-For embedding distance , we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data. 
-To estimate parameters $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_flux}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.
-
-\begin{equation}
-	\label{eq:linear_flux_geo}
-	\ln(\frac{f_{ij}}{m_im_j}) = \ln(C)  - \alpha \ln(g_{ij})
-\end{equation}
-
-\begin{equation}
-	\label{eq:linear_flux_emb}
-	\ln(\frac{f_{ij}}{m_im_j}) = \ln(C) - \beta d_{ij}
-\end{equation}
-
-The gravity law of mobility is known to be sensitive to the case where $f_{ij} = 0$, or zero movement between organizations. 
-Here, non-zero flows account for only 4.2 percent of all possible pairs of  the 6,580 organizations represented in the embedding.
-This value is comparable to other common applications of the gravity law, such as to hone calls, commuting, and migration \autocite{simini2012universal}.
-We follow standard practice and exclude from our analysis zero flows.
-
-%
-% SUBSECTION: SEMAXIS
-%
-\subsection*{SemAxis}
-By constructing semantic embeddings from mobility trajectories, we allow for unique methodology for understading the embedding space, such as SemAxis.
-SemAxis~\autocite{an2018semaxis} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these term to the concept.
-The precise axis is an antonym pair defined \textit{ad-hoc} for the specific use case.
-In the case of language, the ends of the axis could be ``good'' and ``bad'', ``surprising'' and ``unsurprising'', or ``masculine'' and ``feminine''. 
-In the case of scientific mobility, SemAxis offers a means of operationalizing abstract relationships between organizations.
-
-Here, we apply SemAxis to U.S. universities by defining two axes, one of geography and one of academic prestige. 
-The poles of the geographic axis are defined as the mean vector of all vectors corresponding to organizations in California, and then the mean of all vectors of organizations in Massachusetts. 
-For the prestige axis, we define a subset of top-ranked universities according to either the Times World University Rankings or based on the mean normalized research impact sourced from the Leiden Rankings.
-The other end of the prestige axis is the geographically-matched (according to census region) set of universities ranked at the bottom of these rankings.
-For example, if 20 universities top-ranked universities are selected and six of them are in the Northeastern United States, then the bottom six universities according to the same ranking will be included in the low-ranked subset.
-From the prestige axis we also derive what we call \textit{SemRank}, a university ranking based on the nearness of universities to the \textit{Elite} end of the axis. 
-We compare the SemAxis ranking to the traditional university rankings using Spearman rank correlations.
-
-\section{Results}\label{sec:results} %{{{
-
-Results are reported for embeddings with a dimensionality of 300 and a window size of one, which were the parameters that produced  that best explained the flux between organizations (see Fig.
-SI~\ref{fig:supp:hyperparams}).
-We note that this performance and the outcomes of analysis was robust to hyperparemeters settings.
-
 %
@@
 
-We find that embedding distance, the distance between vectors in the embedding space, produces an effective measure of distance.
-Embedding distance explains more of the total flux between pairs of organizations, with correlation ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) over double that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
-Similarly, embedding distance outperforms personalized-page rank distance ($R^{2} = 0.001$, Fig.
-SI~\ref{fig:supp:gravity_ppr}a), a measure produced from the factorized nodes in the underlying mobility network.
-When controlling for only mobility between pairs of organizations within the same country, embedding distance ($R^{2} = 0.48$, Fig.
-SI~\ref{fig:supp:gravity_correlation}c) than does geographic distance ($R^{2} = 0.19$, Fig.
-SI~\ref{fig:supp:gravity_correlation}d).
-Embedding distnace is also far more robust in explaining international flux, with a correlation nearly seven times higher ($R^{2} = 0.28$, Fig.
-SI~\ref{fig:supp:gravity_correlation}e) than that of geographic distance ($R^{2} = 0.041$, Fig.
-SI~\ref{fig:supp:gravity_correlation}f).
+The skip-gram model learns an effective distance that explains and predicts scientific mobility better than alternatives. 
+Embedding distance explains more of the expected flow between pairs of organizations, with correlation ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) over double that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
+Similarly, embedding distance outperforms personalized-page rank distance ($R^{2} = XYZ$, Fig. SI~\ref{fig:supp:gravity_ppr}a), a network-based measure. 
+Embedding distance also explains more of the variance of domestic (Fig.~\ref{fig:supp:gravity_correlation}c) and international mobility flows (Fig.
+~\ref{fig:supp:gravity_correlation}d) than does geographic distance.
+After fitting model parameters from the data, the embedding distance produces better predictions of expected flow than does geographic distance globally (Fig.~\ref{fig:gravity_performance}c-d) and for domestic (Fig.~\ref{fig:supp:gravity_correlation}e-f) and international mobility(Fig.~\ref{fig:supp:gravity_correlation}g-h).
+Geographic distance alone is a poor tool for understanding international scientific mobility---rather, by learning a distance directly from the data, it is possible to better explain, and better predict flows between organizations.
 
@@
 	\centering
-	\label{fig:gravity_performance}
 	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance.pdf}
@@
 		\textbf{Embedding distance outperforms and is more robust than geographic distance.}
-		\textbf{a.} embedding distance (cosine distance between vectors) explains more of the flux between organization pairs than does geographic distance (\textbf{b}). 
+		\textbf{a.} embedding distance (cosine distance between organization vectors) explains more of the flow between organization pairs than does geographic distance (\textbf{b}). 
 		Red line is line of best fit. 
@@
 		Predictions are not meaningfully different if estimates are learned on all pairs of organizations (Fig. S\ref{fig:supp:gravity_prediction_subsets}).
+		These predictions are robust whether the model is fit on the global data, or on the domestic (Fig.~\ref{fig:gravity_performance}e-h) or international Fig.~\ref{fig:supp:gravity_prediction_subsets}) subsets .
 	}
+	\label{fig:gravity_performance}
 \end{figure}
-
-We also find that defining the gravity model as a function of embedding distance produces better predictions than does geographic distance.
-Comparing predicted against actual flux, we find that using the embedding distance in the gravity function has lower error, and are closer than are predictions made using geographic distance (Fig.~\ref{fig:gravity_performance}c-d).
-Embedding distance also produces better predictions for pairs of organizations within the same country (Fig.~\ref{fig:supp:gravity_correlation}e-f) and for pairs of organizations in different countries (Fig.~\ref{fig:supp:gravity_correlation}g-h).
-We find that these predictions are robust whether we make predictions using a model fit on the subsets themselves (Fig.~\ref{fig:gravity_performance}e-h) or fit on the global data and then applied to the subsets (Fig.
-SI~\ref{fig:supp:gravity_prediction_subsets}).
-This performance is also much better than that using personalized page rank distance (Fig. SI~\ref{fig:supp:gravity_ppr}).
 
@@
 
-We observed that word embedding models trained on scientific mobility trajectories offers a reasonable measure of effective distance, one that explains flux between organizations far better than geographic distance.
-Why is this true?
-Why does the skip-gram model learn vectors which approximate gravity law relationships?
-We find evidence of a latent mathematical connection between the two models, one that makes the skip-gram model applicable to many other forms of mobility trajectory.
+Why does the skip-gram model, a tool designed for natural language processing, produce such a reasonable distance that models gravity relationships between organizations?
+We find evidence of a theoretical connection between the two models, one that makes the skip-gram model applicable to many other forms of mobility trajectory.
 
@@
 
+%
+% DATA AND METHODS
+%
+\section*{Data and Methods}
+\label{sec:datamethods} %{{{
+
+Data, analysis, and associated code have been made publicly available and can be found at \textit{https://github.com/murrayds/...}
+
+\subsection*{Data}
+%% Main dataset
+% Do we need to add the Leiden field classificaiton infomration? It doesn't seem like its relevant for the current analysis.
+% Do we need to talk about how we define mobility in relation to past papers?
+We source co-affiliation trajectories of authors from the Web of Science database hosted by the Center for Science and Technology Studies at Leiden University. 
+Trajectories are constructed from author affiliations listed on the byline of publications for a given author.
+Given the limitations of author-name disambiguation, we limit to papers published after 2008, when the Web of Science began providing full names and institutional affiliations~\autocite{caron2014disambiguation} and when performance is strongest (ref to SI?).
+This yields 33,934,672 author-affiliation combinations representing 12,963,792 authors. 
+Each author-affiliation combination is associated with the publication year and a unique id that maps the affiliation to a disambiguate organization. 
+Combinations are also associated with a publication-level disciplinary classification, one of ``Social sciences and humanities'',
+``Biomedical and health sciences'', ``Physical sciences and engineering'', ``Life and earth sciences'', and ``Mathematics and computer science''.
+Trajectories are represented as the list of author-affiliation combinations, ordered by year of publication, and randomly ordered for combinations within the same year. 
+Authors are classified as mobile when they have at least two distinct organization ids in their trajectory, meaning that they have published using two or more distinct affiliations between 2008 and 2019.
+While the number of publications has increased year-to-year, the mobility and disciplinary makeup of the dataset has not significantly changed across the period of study (see Fig.~\ref{fig:supp:pubs_over_time}).
+
+% %Organization information
+Affiliations mapped to one of 8,661 organizations, disambiguated following a mostly manual process originally designed for the Leiden Rankings of World Universities~\autocite{waltman2012leidenrankings}.
+Organizational records were associated with a full name, a type indicating the sector (e.g., University, Government, Industry), and an identifier for the country and city of the organization. 
+Sixteen different sector types were included in the analysis, which we aggregated to a four high-level codes: \textit{University}, \textit{Hospital}, \textit{Government}, and \textit{Other}. 
+Each record was also associated with a latitude and longitude, however for many organizations these were missing or incorrect.
+We manually updated the coordinates of 2,267 organizations by searching the institution name and city on Google Maps;
+in cases where a precise location of the organization could not be identified, we used the coordinates returned when searching the name of the city.
+The data was further enriched with country-level information, including continent, majority language spoken, and language family of the majority language (e.g., the language family of \textit{Spanish} is \textit{Italic}).
+State/province level  information were added using the reverse geocoding service LocationIQ using each organization's latitude and longitude as input. 
+Regional census classifications were also added for states in the United States.
+For each organization, we also calculated a size as the average number of unique authors (mobile and non-mobile) who published with that organization across each year of our dataset;
+in the case that authors publish with multiple affiliations in a single year, they are counted towards each.
+
+As a result of our disambiguation procedure, some affiliations are mapped to two organizations, one specific, and one more general.
+For example, any author affiliated with ``Indiana University Bloomington'' will also be listed as being affiliated with the ``Indiana University System'', a more general designation for all public universities in Indiana.
+However, a more general organization may not always occur alongside the more specific one.
+For example, a researcher affiliated with the smaller regional school ``Indiana University South Bend'' will be listed as affiliated with only the ``Indiana University System''. 
+We identify all specific organizations that always co-occur along a more general one.
+For every career trajectory that includes one of these specific organizations, we remove all occurrences of the more general organization;
+trajectories containing only a general designation are not altered.
+
+Scientific mobility is complex and can be defined in many possible ways~\autocite{robinson2019mobility}.
+Here, we consider an author as mobile when at least two distinct organizational affiliations appear in their trajectory during the 2008-2019 time window. 
+Under this definition, mobile authors constitute 3,007,192 or 23.2 percent of all authors, and 17,700,095 author-affiliation combinations. 
+Mobile authors were associated with, on average, 2.5 distinct organizational affiliations. 
+Rates of mobility tended to differ across country. 
+For example, France, Qatar, the USA, Iraq, and Luxembourg had the most mobile authors (ref figure).
+However, due to their size, the USA, accounted for nearly 40 percent of all mobile authors worldwide, with  10 countries accounting for 80 percent of all mobility (ref figure).
+In most cases, countries with a high degree inter-organization mobility also had a high degree of international mobility;
+however, the USA and France had a high degree of inter-organization mobility with the corresponding international mobility (ref figure).
+
+\subsection*{Embedding}
+%% Mobility sentences
+We embed co-affiliation trajectories by treating them analogously to sentences, and organizations analogously to words. 
+The trajectories of mobile authors were converted to ''mobility sentences`` by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:methods:mobility_sentence}.a.
+In more complex cases, such as listing multiple affiliations on the same paper or publishing with different affiliations on multiple affiliations in the same year, the order is randomized within that year, as shown in  Fig.~\ref{fig:methods:mobility_sentence}.b.
+
+%
+% Figure - Example of mobility sentences
+%
+\begin{figure}[ht!]
+	\centering
+	\includegraphics[width=0.7\textwidth]{\figdir/mobility_example_combined.pdf}
+	\caption{
+		\textbf{Co-affiliation trajectories represented as sentences.}
+		\textbf{a.} 
+		An authors published five papers across five time periods, with only one affiliation listed in the byline of each paper. 
+		A unique identifier is assigned to each organization, and these are concatenated into a mobility sentence. 
+		\textbf{b.}
+		In a more complex case, an author lists several affiliations on the byline of papers in $t_{2}$, $t_{3}$, and $t_{4}$.
+Here, organization ids are still ordered by year, however order within a single year is random.
+	}
+	\label{fig:methods:mobility_sentence}
+\end{figure}
+
+%% word2vec
+These mobility sentences are used as input to the standard skip-gram negative sampling (SGNS) model for word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec} . 
+In natural-language processing, word embeddings are used to construct dense vector-space representations of words and phrases, in which distance relationships between words correspond to a notion of semantic distance.
+By embedding co-affiliation trajectories, we aim to learn a dense vector for every organization where distance between vectors relates to the tendency for two organizations to co-occur in a token window around the target term in the same career trajectory.
+Vectors are learned by training a neural network to optimize the prediction of so-called context term given a target, in our case using one organization to predict the others appearing in the same co-affiliation trajectory.
+The hidden layer of the trained neural network is used as the
+
+%% Word2vec parameters and training procedure
+The SGNS model has several tunable hyper-parameters, including the size of the learned vectors, the size of the token window  considered when training, the minimum frequency threshold for including an organization, and the number of iterations.
+We iterate through several values of vector size and window size, repeating analysis for each combination. 
+To mitigate the effect of less common organizations, only organizations appearing at least 50 times in mobility sentences are included in the embedding;
+this yields 6,580, or 76 percent of all organizations.
+We iterate the SGNS training for five epochs over all mobility sentences. 
+All word embeddings are trained using the \textit{gensim} python implementation of the SGNS \textit{word2vec} model. 
+We visualize embeddings by projecting into two dimensions using UMAP~\autocite{mcinnes2018umap}.
+
+Results are reported for embeddings with a dimensionality of 300 and a window size of one, which were the parameters that produced  that best explained the flux between organizations (see Fig.
+SI~\ref{fig:supp:hyperparams}).
+We note that this performance and the outcomes of analysis was robust to hyperparemeters settings.
+
+%
+% SUBSECTION: DISTANCE
+%
+\subsection{Distance}
+%% Distance calculations
+We calculate $f_{ij}$, the pairwise number of co-affiliations between organizations, calculated as the number of co-occurrences of organizations within author co-affiliation trajectories. 
+For example, $f_{ij} = 10$ indicates that ten authors were co-affiliated with both organization $i$ and $j$ between 2008 and 2019, as evidenced from their publications. 
+In contrast to traditional mobility studies, all co-affiliations are symmetric, meaning that $f_{ij} = f_{ji}$.
+
+We also calculate two forms of distance between organizations. 
+The geographic distance, $g_{ij}$, is the pairwise geographic distance between organizations.
+Geographic distance is calculated as the great circle distance, in kilometers, between pairs of organizations. 
+When less than one kilometer, a distance of one is imputed. 
+The embedding distance, $d_{ij}$, is calculated as the pairwise cosine distance between vectors from the learned organization embedding, where $v_{i}$ and $v_{j}$ represent the vectors and $d_{ij} = 1 - \frac{v_{i} \dot v_{j}}{\lVert v_{i} \rVert \lVert v_{j} \rVert}$.
+
+%
+% SUBSECTION: GRAVITY LAW
+%
+\subsection{Gravity Law}
+
+We model the flow of authors across organizations, $f_{ij}$, using the gravity law. 
+the gravity law of mobility loosely derives from the physical law of gravity, whereby the attraction between two objects is a function of their mass and the distance between them.
+Given its simplicity and flexibility, this formulation and variants have proven incredibly useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
+Following the gravity law, the expected flow between two organizations is defined as follows,
+
+\begin{equation}
+	\label{eq:gravity_basic}
+	f_{ij} = C*m_{i}m_{j}*f(r_{ij})
+\end{equation}
+
+where $m_{i}$ and $m_{j}$ are the yearly-average size of each organization during the time window, and $f(r_{ij})$ is a distance-decaying function  between the two organizations.
+There are two popular forms of the $f(r_{ij})$.
+The first one is power-law function with $f(r_{ij})= r^{-\alpha}_{ij}  (\alpha > 0)$, and the another one is exponential function with $f(r_{ij}) = e^{-\beta r_{ij}} (\beta > 0)$ \autocite{chen2015distance}.
+$f(r_{ij})$, $C$ can be chosen as to fit the data with the simple regression.
+
+We consider separate variants of $f(r_{ij})$ for geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$, report the best-fit model of each distance.
+For geographic distance, we use the power-law function of the gravity law, with $f(g_{ij})= g^{-\alpha}_{ij}$, where $\alpha$ is estimated from the data. 
+For embedding distance , we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data. 
+To estimate parameters $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_flux}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.
+
+\begin{equation}
+	\label{eq:linear_flux_geo}
+	\ln(\frac{f_{ij}}{m_im_j}) = \ln(C)  - \alpha \ln(g_{ij})
+\end{equation}
+
+\begin{equation}
+	\label{eq:linear_flux_emb}
+	\ln(\frac{f_{ij}}{m_im_j}) = \ln(C) - \beta d_{ij}
+\end{equation}
+
+The gravity law of mobility is known to be sensitive to the case where $f_{ij} = 0$, or zero movement between organizations. 
+Here, non-zero flows account for only 4.2 percent of all possible pairs of  the 6,580 organizations represented in the embedding.
+This value is comparable to other common applications of the gravity law, such as to hone calls, commuting, and migration \autocite{simini2012universal}.
+We follow standard practice and exclude from our analysis zero flows.
+
+%
+% SUBSECTION: SEMAXIS
+%
+\subsection*{SemAxis}
+By constructing semantic embeddings from mobility trajectories, we allow for unique methodology for understading the embedding space, such as SemAxis.
+SemAxis~\autocite{an2018semaxis} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these term to the concept.
+The precise axis is an antonym pair defined \textit{ad-hoc} for the specific use case.
+In the case of language, the ends of the axis could be ``good'' and ``bad'', ``surprising'' and ``unsurprising'', or ``masculine'' and ``feminine''. 
+In the case of scientific mobility, SemAxis offers a means of operationalizing abstract relationships between organizations.
+
+Here, we apply SemAxis to U.S. universities by defining two axes, one of geography and one of academic prestige. 
+The poles of the geographic axis are defined as the mean vector of all vectors corresponding to organizations in California, and then the mean of all vectors of organizations in Massachusetts. 
+For the prestige axis, we define a subset of top-ranked universities according to either the Times World University Rankings or based on the mean normalized research impact sourced from the Leiden Rankings.
+The other end of the prestige axis is the geographically-matched (according to census region) set of universities ranked at the bottom of these rankings.
+For example, if 20 universities top-ranked universities are selected and six of them are in the Northeastern United States, then the bottom six universities according to the same ranking will be included in the low-ranked subset.
+From the prestige axis we also derive what we call \textit{SemRank}, a university ranking based on the nearness of universities to the \textit{Elite} end of the axis. 
+We compare the SemAxis ranking to the traditional university rankings using Spearman rank correlations.
+
 \newpage
@@
 	\centering
-	\label{fig:supp:gravity_correlation}
 	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_correlations.pdf}
@@
 	}
+	\label{fig:supp:gravity_correlation}
 \end{figure}
@@
 	\centering
-	\label{fig:supp:gravity_prediction_subsets}
 	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_different_fits.pdf}
@@
 	}
+	\label{fig:supp:gravity_prediction_subsets}
 \end{figure}
@@
 	\centering
-	\label{fig:supp:gravity_ppr}
 	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_ppr.pdf}
@@
 	}
+	\label{fig:supp:gravity_ppr}
 \end{figure}

### 2020-02-27 paper/current/main.tex
replace figure 1 which I had accidentally deleted earlier

@@
 In addition to encoding latent structure, these  are computationally and space efficient, robust to noise, and allow for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.
+
+%
+% Figure - Example of mobility sentences
+%
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{\figdir/mobility_example_combined.pdf}
+    \caption{
+        \textbf{Co-affiliation trajectories represented as sentences}
+        \textbf{a.} 
+        An author published five papers across five time periods, with only one affiliation listed in the byline of each paper. 
+        A unique identifier is assigned to each organization, and these are concatenated into a mobility sentence. 
+        \textbf{b.}
+        In a more complex case, an author lists several affiliations on the byline of papers in $t_{2}$, $t_{3}$, and $t_{4}$.
+Here, organization ids are still ordered by year, however order within a single year is random.
+    }
+    \label{fig:methods:mobility_sentence}
+\end{figure}
 
@@
 
-The SGNS model learns an effective distance from trajectories, one which we can visualize by projecting organizational vectors into two dimensions using UMAP \autocite{mcinnes2018umap} (Fig.~\ref{fig:projection}a).
+The skip-gram model produces an effective distnace from mobility which can be visualized by projecting the embedding space into two dimensions using UMAP~\autocite{mcinnes2018umap} (Fig.~\ref{fig:projection}a).
 Overall, organizations are clustered by geography, according to the nations in which they are location;
@@
 	\centering
-	\label{fig:projection}
 	\includegraphics[width=\textwidth]{\figdir/Projection/big_embedding_picture.png}
@@
 	}
+	\label{fig:projection}
 \end{figure}
@@
 	\centering
-	\label{fig:clustering}
 	\includegraphics[width=\textwidth]{\figdir/Clustering/cluster_country.pdf}
@@
 	}
+	\label{fig:clustering}
 \end{figure}

### 2020-02-27 paper/current/main.tex
Changes throughout—finish moving things around

@@
 A unique characteristic of semantic mobility embeddings is the ability to capture structure at multiple scales of granularity.
-For example, just as the global embedding captures geographic structure between nations, so too does a projection or organizations in the United States reflect organizational structure based on states and oriented along an East-West axis (Fig.~\ref{fig:projection}d).
-My re-projecting at the state-level for Massachusetts (Fig.~\ref{fig:projection}e), we observe structure between urban Centers (Boston vs.
+For example, just as the global embedding captures geographic structure between nations, so too does a projection or organizations in the United States reflect organizational structure based on states (Fig.~\ref{fig:projection}d).
+By re-projecting at the state-level for Massachusetts (Fig.~\ref{fig:projection}e), we observe structure between urban Centers (Boston vs.
 Worcester), but also based on organization type (hospitals tend to be adjacent) and different university systems.
@@
 
-Based on descriptive findings, we more rigorously assess the extent to which embeddings capture the structure of international mobility. 
+What latent information do embeddings of scientific mobility capture, beyond geography?
+We build on descriptive results to quantitatively assess the national factors captured in the learned vector-space.
 We calculate the representative vector of each country with averaging organization vectors within the given country, calculate pairwise cosine similarity, and perform hierarchical clustering (see Fig.
-\ref{fig:clustering}a).
-Countries that have more than 25 organizations are collected for the clustering analysis, though we exclude the United States due to its high similarity with all other countries.
+\ref{fig:clustering}a) of nations that have at least 25 organizations, excluding the United States which has high similarity with most other countries.
 
-Six country clusters were identified, reflecting a mixture of the regional, linguistic, historical clusters. 
-From top-to-bottom, we identify a primarily East-Asian cluster (orange), a Scandinavian cluster (dark purple), a cluster of British Commonwealth countries (light purple), a central and eastern European cluster (sky blue), a diverse cluster of European and South American clusters (dark green), and finally another diverse cluster consisting of countries bordering the Mediterranean or the Black Sea.
+Six country clusters were identified, reflecting a mixture of the regional, linguistic, historical clusters, with clusters consisting of East-Asian (orange), Scandinavian (dark purple), British Commonwealth (light purple), Central and Eastern European countries (light blue), and then two cluster diverse clusters with a mix of European, Latin American, and Mediterranean countries.
 When not defined by geography, clusters appear to be defined by linguistic and historical ties, as is the case for the commonwealth countries. 
-By looking closely at the deprogram and meta-data, there is a tendency that countries are merged as a group if they share the language in the early stage of the deprogram and geographical aspect plays a more major role in the later stage of the dendrogram.
+There is a tendency that countries are grouped if they are in the same geographic region, if they are historically or culturally aligned, and if they share a similar language.
 
-We investigate the extent to which geography and language dictate the formation of clusters using \textit{CluSim}~\autocite{gates2019element}.
-\textit{CluSim} is a method that calculates the similarity between the cluster results and, for hierarchical clustering, can adjust the relative importance of membership at different levels of the hierarchy with scaling parameter $r$, acting likes ``zooming lens''.
-If $r$ is high, the similarity is based on the lower levels of the dendrogram, and when $r$ is low, similarity is based on higher levels dendrogram. 
-In fig. \ref{fig:clustering}b, we report three cluster similarity curves (continent, language, language family) with varying scaling parameter $r$.
-As expected, continent plays a major role at higher levels of clustering process (low $r$), language and language family explain the clustering process more at the lower levels (high $r$). 
+We investigate the extent to which geography and language dictate the formation of clusters using \textit{CluSim}~\autocite{gates2019element}, a method that compares different groupings and, for hierarchical clustering, can adjust the relative importance of membership at different levels of the hierarchy with scaling parameter $r$, acting like a ``zooming lens''.
+If $r$ is high, the similarity is based on the lower levels of the dendrogram, whereas when $r$ is low, similarity is based on higher levels. 
+Fig.
+\ref{fig:clustering}b demonstrates that continent plays a major role at higher levels of clustering process (low $r$), and language family and then language explain the clustering process more at the lower levels (high $r$).
 This suggests that geography, then language, are important factors contributing to the structure of international scientific mobility.
@@
 
-Using SemAxis, a technique unique to semantic embedding, we reconstruct geographic relationships and prestige hierarchies based defined axis between California and Massachusetts, and between lowly and highly ranked universities according to the Times Ranking of World Universities and the Leiden Ranking field-normalized citation impact (Fig.~\ref{fig:semaxis}).
-We find that, with a few exceptions, all universities in California are nearer the appropriate end of the axis than are Massachusetts universities, and \textit{vice versa}.
-Universities in bordering states, such as Arizona and Connecticut, are closer to the ends of the axis (Fig. SI~\ref{fig:supp:semaxis_states}b and Fig. SI~\ref{fig:supp:semaxis_states}e). 
-Universities in new York are nearer to the Massachusetts end of the axis (Fig.
-SI~\ref{fig:supp:semaxis_states}f), whereas universities in Florida are less aligned to either (Fig.
-SI~\ref{fig:supp:semaxis_states}i).
+In addition to encoding national characteristics, the embedding also encodes domestic geography and latent hierarchy. 
+We employ SemAxis~\autocite{an2018semaxis}, a tool utilizing the unique vector arithmetic of semantic embeddings, to project U.S. universities onto two defined axes. 
+The first axis is geographic, defined using the mean vector of universities in California on one end, and Massachusetts on the other.
+The second axis relates instead to prestige.
+Universities hiring and mobility networks are known to exhbit latent pretige hierarchies ~\autocite{deville2014career, clauset2015hierarchy} that should be encoded in the embedding space. 
+The elite end of the axis is defined as the top 20 U.S.
+universities according to the Times Ranking of World Universities, whereas the non-elite axis is defined as bottom-ranked geographically matched (by U.S.
+census region) set of universities.
+A university projected onto the axis corresponds to their nearness to the mean vector defining each pole.
+With a few exceptions, all universities in California are nearer the appropriate end of the axis than are Massachusetts universities, and \textit{vice versa} (Fig.~\ref{fig:semaxis}).
+Universities in bordering states, such as Arizona and Connecticut, are closer to the ends of the axis (Fig.~\ref{fig:supp:semaxis_states}b and Fig.~\ref{fig:supp:semaxis_states}e). 
+Universities in new York are nearer to the Massachusetts end of the axis (Fig.~\ref{fig:supp:semaxis_states}f), whereas universities in Florida are less aligned to either (Fig.~\ref{fig:supp:semaxis_states}i).
 
-In terms of prestige, we find prestigious universities towards the top of the axis, such as Stanford, Colombia, MIT, Harvard, and NYU. 
+Prestigious universities, such as Stanford, Colombia, MIT, Harvard, and NYU, group towards the top of the axis.
 Universities at the bottom of this axis tend to be regional universities with lower national profiles, such as California State University Long Beach, University of West Florida, and Barry University.
-There are strong differences by state in terms of prestige—overall, universities in Massachusetts are nearer the \textit{Elite} end of the axis than are universities in Arizona, Connecticut, Pennsylvania, and Florida (see Fig.
-SI~\ref{fig:supp:semaxis_states}).
+There are strong differences by state in terms of prestige---overall, universities in Massachusetts are nearer the \textit{Elite} end of the axis than are universities in Arizona, Connecticut, Pennsylvania, and Florida (see Fig.~\ref{fig:supp:semaxis_states}).
 
@@
 Department of Energy is more aligned with Californian universities, whereas the Mayo Clinic is more aligned with Massachusetts and organizations like the National Institute of Arthritis, Musculoskeletal, and Skin Disease and more aligned with elite universities than is the U.S.
-Department of Agriculture (Fig SI~\ref{fig:supp:semaxis_sectors}a).
-Among research institutes, the most aligned with elite universities are typically those prestigious university-adjacent institutes such as the Whitehead Institute, the Broad Institute, and the Dana Faber institute (Fig SI~\ref{fig:supp:semaxis_sectors}b); those institutes aligned with lowly-ranked universities tend to be ecological or agricultural institutes such as the Joseph W.
+Department of Agriculture (Fig.~\ref{fig:supp:semaxis_sectors}a).
+Among research institutes, the most aligned with elite universities are typically those prestigious university-adjacent institutes such as the Whitehead Institute, the Broad Institute, and the Dana Faber institute (Fig.~\ref{fig:supp:semaxis_sectors}b); those institutes aligned with lowly-ranked universities tend to be ecological or agricultural institutes such as the Joseph W.
 Jones Ecological Research Center and the Louisiana Agriculture Center.
-Among teaching organizations, the top-ranked tend to be notable private liberal arts colleges such as Wellesley College and Carleton College, whereas community colleges and military colleges tend to be more aligned with lowly-ranked universities (Fig.
-SI~\ref{fig:supp:semaxis_sectors}c).
+Among teaching organizations, the top-ranked tend to be notable private liberal arts colleges such as Wellesley College and Carleton College, whereas community colleges and military colleges tend to be more aligned with lowly-ranked universities (Fig.~\ref{fig:supp:semaxis_sectors}c).
 
@@
 	\centering
-	\label{fig:semaxis}
 	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_fig.pdf}
@@
 	}
+	\label{fig:semaxis}
 \end{figure}
 
-To what extent are semantic embeddings of mobility actually learning the latent hierarchy of academic mobility?
+In addition to learning geography, its clear that the skip-gram model is also encoding the latent prestige hierarchies of academic mobility. 
 To test this, we derive a ranking using the prestige axis that we call \textit{SemRank}, and compare them to traditional university rankings. 
@@
 In more complex cases, such as listing multiple affiliations on the same paper or publishing with different affiliations on multiple affiliations in the same year, the order is randomized within that year, as shown in  Fig.~\ref{fig:methods:mobility_sentence}.b.
-
-%
-% Figure - Example of mobility sentences
-%
-\begin{figure}[ht!]
-	\centering
-	\includegraphics[width=0.7\textwidth]{\figdir/mobility_example_combined.pdf}
-	\caption{
-		\textbf{Co-affiliation trajectories represented as sentences.}
-		\textbf{a.} 
-		An authors published five papers across five time periods, with only one affiliation listed in the byline of each paper. 
-		A unique identifier is assigned to each organization, and these are concatenated into a mobility sentence. 
-		\textbf{b.}
-		In a more complex case, an author lists several affiliations on the byline of papers in $t_{2}$, $t_{3}$, and $t_{4}$.
-Here, organization ids are still ordered by year, however order within a single year is random.
-	}
-	\label{fig:methods:mobility_sentence}
-\end{figure}
 
@@
 	\centering
-	\label{fig:supp:pubs_over_time}
 	\includegraphics[width=\textwidth]{\figdir/Descriptive/pubs_over_time.pdf}
@@
 	}
+	\label{fig:supp:pubs_over_time}
 \end{figure}
@@
 	\centering
-	\label{fig:supp:pubs_over_time}
 	\includegraphics[width=\textwidth]{\figdir/Descriptive/mobility_by_country.pdf}
@@
 	\centering
-	\label{fig:supp:rcdf_by_scale}
 	\includegraphics[width=0.8\textwidth]{\figdir/Descriptive/rcdf_by_scale.pdf}
@@
 	}
+	\label{fig:supp:rcdf_by_scale}
 \end{figure}
@@
 	\centering
-	\label{fig:supp:hyperparams}
 	\includegraphics[width=\textwidth]{\figdir/Descriptive/hyperparameter_performance.pdf}
@@
 	}
+	\label{fig:supp:hyperparams}
 \end{figure}
@@
 	\centering
-	\label{fig:supp:semaxis_compare}
 	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_compare_fig.pdf}
@@
 	}
+	\label{fig:supp:semaxis_compare}
 \end{figure}
@@
 	\centering
-	\label{fig:supp:semaxis_states}
 	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_states_fig.pdf}
@@
 	}
+	\label{fig:supp:semaxis_states}
 \end{figure}
@@
 	\centering
-	\label{fig:supp:semaxis_sectors}
 	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_sectors_fig.pdf}
@@
 	}
+	\label{fig:supp:semaxis_sectors}
 \end{figure}

### 2020-02-27 paper/current/main.tex
Added conclusion section

@@
 
+By learning a distance directly from the data, the skip-gram model effectively and efficiently captures a robust measure of semantic distance between entities, all with existing tools and minor data processing.
+This methodology is broadly applicable to studies of mobility.
+Its success also points to the broad applicability of ideas from language and graph embedding techniques such as GLoVE~\autocite{pennington2014glove}, BERT~\autocite{devlin2018bert}, hyperbolic embeddings~\autocite{nickel2017poincare, linzhuo2020hyperbolic}, and persona2vec () to other problem domains, such as the social sciences.
+In addition to their technical advantages and the unique suite of methodologies they allow, they are also  readily transferable and can be trivially fit into a diverse array of analyses.
+
+Globally, science has experienced many changes, from gradual globalization to the more sudden 2017 U.S. travel bans. 
+The consequences of these changes are far-reaching, and how nations respond to them will shape the future of the scientific enterprise~\autocite{chinchilla2018travelban, wagner2017open, sugimoto2017mostimpact}.
+Given mobility's importance, its vital that we gain a better understanding of where, how, and why researchers move, and what the impact of these movements will be. 
+With this new data-driven approach to learning distances relating to mobility, we capture the latent and nuanced structure of mobility at multiple scales;
+with this, predictive models can be improved and new insights gained, which in turn will inform more effective science and immigration policy, allowing global science to dictate the terms and leverage the benefits of our own migrations.
+
 %

### 2020-02-27 paper/current/main.tex
replce `skip-gram` with a macro for SGNS. Other minor changes

@@
 
+% CUSTOM MACROS
+\def\SGNS{\textit{SGNS}}
+
 %}}}
@@
 However, amid a globalizing scientific enterprise~\autocite{czaika2018globalisation}, geographic distance is only becoming less useful for understanding mobility, whereas other abstract notions of distance~\autocite{boschma2005proximity} cannot be meaningfully measured.
-Here, we demonstrate a data-driven approach of learning an effective distance that encodes the latent structure of mobility using the skip-gram word embedding model~\autocite{mikolov2013word2vec}, treating organizations analogously to words and career trajectories to sentences.
+Here, we demonstrate a data-driven approach of learning an effective distance that encodes the latent structure of mobility using the skip-gram  negative sampling word embedding model~\autocite{mikolov2013word2vec}, treating organizations analogously to words and career trajectories to sentences.
 We source publications of disambiguated authors from the Web of Science database to construct mobility embeddings for authors career trajectories between 2008 and 2019. 
@@
 
-The skip-gram embedding model preserves semantic relationships between words in a dense and meaningful low-dimensional vector-space representation~\cite{mikolov2013word2vec}, and just as its has been applied to and revealed insights implicit in text~\cite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}, so too might this model encode the latent structures of global scientific mobility.
+The skip-gram negative-sampling embedding (\SGNS) model preserves semantic relationships between words in a dense and meaningful low-dimensional vector-space representation~\cite{mikolov2013word2vec}, and just as its has been applied to and revealed insights implicit in text~\cite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}, so too might this model encode the latent structures of global scientific mobility.
 As scientist's careers progress, they move institutions or pick up additional affiliations, forming co-affiliation or \textit{mobility trajectories} that can be derived from their publication histories~\autocite{robinson2019mobility, sugimoto2017mostimpact}.
-We embed mobility trajectories by treating organizations analogously to words and trajectories analogously to sentences, and feed the resulting "sentence" into the standard skip-gram model (Fig.~\ref{fig:methods:mobility_sentence}).
+We embed mobility trajectories by treating organizations analogously to words and trajectories analogously to sentences, and feed the resulting "sentence" into the standard \SGNS{} model (Fig.~\ref{fig:methods:mobility_sentence}).
 The result is a vector-space representation of organizations in which the \textit{cosine distance} between vectors represents the tendency for pairs of organizations to occur near one another in the same career path.
@@
 We adopt the Gravity Model of mobility~\autocite{zipf1946gravity}, one of the most common and broadly applied mobility models~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} to assess how well the embedding captures mobility.
-We derive the \textit{expected flow} from the base gravity model, defined as,
+We derive the \textit{expected flux} from the base gravity model, defined as,
 
@@
 
-Where the flow, or number of authors co-affiliated with two organizations during the time period $f_{ij}$, increases with the organization's sizes, $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+Where the flux, or number of authors co-affiliated with two organizations during the time period $f_{ij}$, increases with the organization's sizes, $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
 We consider two distances, $f_{ij}$, the geographic distance between the organizations, and the \textit{embedding distance} defined as the cosine distance between the organization's vector in the trained embedding space.
-We argue that the performance of a distance measure can be observed from their ability to explain expected mobility between organizations, as well as to predict flows using the gravity model. 
+We argue that the performance of a distance measure can be observed from their ability to explain expected mobility between organizations, as well as to predict flux using the gravity model. 
 For geographic distance, we define $f(r_{ij})$ as the standard power-decay function, and for the embedding distance, we use the exponential form, selected as the best performing for each case.
@@
 
-The skip-gram model learns an effective distance that explains and predicts scientific mobility better than alternatives. 
+The \SGNS{} model learns an effective distance that explains and predicts scientific mobility better than alternatives. 
 Embedding distance explains more of the expected flow between pairs of organizations, with correlation ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) over double that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
@@
 ~\ref{fig:supp:gravity_correlation}d) than does geographic distance.
-After fitting model parameters from the data, the embedding distance produces better predictions of expected flow than does geographic distance globally (Fig.~\ref{fig:gravity_performance}c-d) and for domestic (Fig.~\ref{fig:supp:gravity_correlation}e-f) and international mobility(Fig.~\ref{fig:supp:gravity_correlation}g-h).
-Geographic distance alone is a poor tool for understanding international scientific mobility---rather, by learning a distance directly from the data, it is possible to better explain, and better predict flows between organizations.
+After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance globally (Fig.~\ref{fig:gravity_performance}c-d) and for domestic (Fig.~\ref{fig:supp:gravity_correlation}e-f) and international mobility(Fig.~\ref{fig:supp:gravity_correlation}g-h).
+Geographic distance alone is a poor tool for understanding international scientific mobility---rather, by learning a distance directly from the data, it is possible to better explain, and better predict flux between organizations.
 
@@
 		\textbf{Embedding distance outperforms and is more robust than geographic distance.}
-		\textbf{a.} embedding distance (cosine distance between organization vectors) explains more of the flow between organization pairs than does geographic distance (\textbf{b}). 
+		\textbf{a.} embedding distance (cosine distance between organization vectors) explains more of the expected flux between organization pairs than does geographic distance (\textbf{b}). 
 		Red line is line of best fit. 
@@
 
-Why does the skip-gram model, a tool designed for natural language processing, produce such a reasonable distance that models gravity relationships between organizations?
+Why does the SNGS model, a tool designed for natural language processing, produce such a reasonable distance that models gravity relationships between organizations?
 We find evidence of a theoretical connection between the two models, one that makes the skip-gram model applicable to many other forms of mobility trajectory.
@@
 
-This finding relates to the objective function of \textit{word2vec} (skip-gram) model.
-The skip-gram model attempts to maximize the average log probability of observing a target word in a sentence, $w_{t}$, given the words in the surrounding context window, $w_{t + k}$.
+This finding relates to the objective function of the \SGNS{} model.
+The model attempts to maximize the average log probability of observing a target word in a sentence, $w_{t}$, given the words in the surrounding context window, $w_{t + k}$.
 This can be written as follows, where $c$ is the size of the context window and $T$ iterates through possible target words:
@@
 
-Hence, the \textit{word2vec} skip-gram model can be an effective model for investigating any kind of mobility trajectory data, stemming from the mathematical relationship between it and the gravity model of mobility.
+Hence, the \SGNS{} model can be an effective model for investigating any kind of mobility trajectory data, stemming from the mathematical relationship between it and the gravity model of mobility.
 
@@
 
-The skip-gram model produces an effective distnace from mobility which can be visualized by projecting the embedding space into two dimensions using UMAP~\autocite{mcinnes2018umap} (Fig.~\ref{fig:projection}a).
+The \SGNS{} model produces an effective distnace from mobility which can be visualized by projecting the embedding space into two dimensions using UMAP~\autocite{mcinnes2018umap} (Fig.~\ref{fig:projection}a).
 Overall, organizations are clustered by geography, according to the nations in which they are location;
@@
 
-In addition to learning geography, its clear that the skip-gram model is also encoding the latent prestige hierarchies of academic mobility. 
+In addition to learning geography, its clear that the \SGNS{} model is also encoding the latent prestige hierarchies of academic mobility. 
 To test this, we derive a ranking using the prestige axis that we call \textit{SemRank}, and compare them to traditional university rankings. 
@@
 
-By learning a distance directly from the data, the skip-gram model effectively and efficiently captures a robust measure of semantic distance between entities, all with existing tools and minor data processing.
+By learning a distance directly from the data, the \SGNS{} model effectively and efficiently captures a robust measure of semantic distance between entities, all with existing tools and minor data processing.
 This methodology is broadly applicable to studies of mobility.
@@
 %% word2vec
-These mobility sentences are used as input to the standard skip-gram negative sampling (SGNS) model for word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec} . 
+These mobility sentences are used as input to the standard skip-gram negative sampling (\SGNS) model, for word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec} . 
 In natural-language processing, word embeddings are used to construct dense vector-space representations of words and phrases, in which distance relationships between words correspond to a notion of semantic distance.
@@
 %% Word2vec parameters and training procedure
-The SGNS model has several tunable hyper-parameters, including the size of the learned vectors, the size of the token window  considered when training, the minimum frequency threshold for including an organization, and the number of iterations.
+The \SGNS{} model has several tunable hyper-parameters, including the size of the learned vectors, the size of the token window  considered when training, the minimum frequency threshold for including an organization, and the number of iterations.
 We iterate through several values of vector size and window size, repeating analysis for each combination. 
@@
 this yields 6,580, or 76 percent of all organizations.
-We iterate the SGNS training for five epochs over all mobility sentences. 
-All word embeddings are trained using the \textit{gensim} python implementation of the SGNS \textit{word2vec} model. 
+We iterate the \SGNS{} training for five epochs over all mobility sentences. 
+All word embeddings are trained using the \textit{gensim} python implementation of the \SGNS{} \textit{word2vec} model. 
 We visualize embeddings by projecting into two dimensions using UMAP~\autocite{mcinnes2018umap}.
@@
 
-We model the flow of authors across organizations, $f_{ij}$, using the gravity law. 
+We model the flux of authors between organizations, $f_{ij}$, using the gravity law. 
 the gravity law of mobility loosely derives from the physical law of gravity, whereby the attraction between two objects is a function of their mass and the distance between them.
 Given its simplicity and flexibility, this formulation and variants have proven incredibly useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
-Following the gravity law, the expected flow between two organizations is defined as follows,
+Following the gravity law, the expected flux between two organizations is defined as follows,
 

### 2020-02-27 paper/current/main.tex
an extra interesting reference

@@
 Globally, science has experienced many changes, from gradual globalization to the more sudden 2017 U.S. travel bans. 
-The consequences of these changes are far-reaching, and how nations respond to them will shape the future of the scientific enterprise~\autocite{chinchilla2018travelban, wagner2017open, sugimoto2017mostimpact}.
+The consequences of these changes are far-reaching, and how nations respond to them will shape the future of the scientific enterprise~\autocite{chinchilla2018travelban, wagner2017open, sugimoto2017mostimpact, whetsell2019democracy}.
 Given mobility's importance, its vital that we gain a better understanding of where, how, and why researchers move, and what the impact of these movements will be. 

### 2020-02-28 paper/current/main.tex
Using both Cosine Dist and JSD of PPR, edited existing and added new graph

@@
 Embedding distance explains more of the expected flow between pairs of organizations, with correlation ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) over double that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
-Similarly, embedding distance outperforms personalized-page rank distance ($R^{2} = XYZ$, Fig. SI~\ref{fig:supp:gravity_ppr}a), a network-based measure. 
 Embedding distance also explains more of the variance of domestic (Fig.~\ref{fig:supp:gravity_correlation}c) and international mobility flows (Fig.
@@
 After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance globally (Fig.~\ref{fig:gravity_performance}c-d) and for domestic (Fig.~\ref{fig:supp:gravity_correlation}e-f) and international mobility(Fig.~\ref{fig:supp:gravity_correlation}g-h).
+Similarly, embedding distance outperforms distances derived from calculating personalized-page rank scores on the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
 Geographic distance alone is a poor tool for understanding international scientific mobility---rather, by learning a distance directly from the data, it is possible to better explain, and better predict flux between organizations.
@@
 		Predictions are not meaningfully different if estimates are learned on all pairs of organizations (Fig. S\ref{fig:supp:gravity_prediction_subsets}).
-		These predictions are robust whether the model is fit on the global data, or on the domestic (Fig.~\ref{fig:gravity_performance}e-h) or international Fig.~\ref{fig:supp:gravity_prediction_subsets}) subsets .
+		These predictions are robust whether the model is fit on the global data, or on the domestic (Fig.~\ref{fig:gravity_performance}e-h) or international Fig.~\ref{fig:supp:gravity_prediction_subsets}) subsets.
 	}
@@
 %
-% Figure - PPR gravity model and predictions
+% Figure - PPR with COSINE DISTANCE gravity model and predictions
 %
@@
 	\centering
-	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_ppr.pdf}
+	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_pprcos.pdf}
 	\caption{
-		\textbf{Personalized page rank does not capture mobility.}
+		\textbf{Personalized page rank with cosine distance.}
 		Performance of personalized page rank scores in explaining and predicting mobility.
-		Personalized page rank is calculated for the underlying mobility network, and similarity between resulting vectors used as the PPR distance.
-		PPR distance does not explain global mobility (\textbf{a}), or same (\textbf{b}) or different (\textbf{c}) country mobility, performing worse than geographic distance (Fig.~\ref{fig:supp:gravity_correlation}).
+		Personalized page rank is calculated for the underlying mobility network, and distance measured as the cosine distnace between PPR probability distribution vectors.
+		PPR cosine distance performs roughly similar to geographic distance in explaining global mobility (\textbf{a}), or domestic (\textbf{b}) or international (\textbf{c}) country mobility.
 		Red line is line of best fit. 
@@
 		Color indicates frequency of organization pairs within each hex bin.
-		Similarly, PPR distance performs poorly as a distance metric for gravity model predictions globally (\textbf{d}), and across pairs of organizations in the same (\textit{e}) and in different (\textbf{f}) countries.
+		Similarly, PPR distance performs comparably to geographic distance in predicting global (\textbf{d}), domestic (\textit{e}) and international (\textbf{f}) scientific mobility. 
 		Boxplots show distribution of actual flux for binned values of predicted flux.
@@
 	}
-	\label{fig:supp:gravity_ppr}
+	\label{fig:supp:gravity_pprcos}
+\end{figure}
+
+%
+% Figure - PPR with JSD gravity model and predictions
+%
+\begin{figure}[p!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_pprjsd.pdf}
+	\caption{
+		\textbf{Personalized page rank with cosine distance.}
+		Performance of personalized page rank scores in explaining and predicting mobility.
+		Personalized page rank is calculated for the underlying mobility network, and distance measured as the Jensen-Shannon Divergence (JSD) between PPR probability distribution vectors.
+		PPR JSD performs roughly similar to geographic distance in explaining global mobility (\textbf{a}), or domestic (\textbf{b}) or international (\textbf{c}) country mobility.
+		Overall, PPR JSD explains more vairance in mobility than using cosine distance (Fig.~\ref{fig:supp:gravity_pprcos}), except for international mobility, for which cosine similarity out-performs JSD. 
+		Red line is line of best fit. 
+		Black dots are mean flux across binned distances.
+		Color indicates frequency of organization pairs within each hex bin.
+		Similarly, PPR JSD performs comparably to geographic distance in predicting global (\textbf{d}), domestic (\textit{e}) and international (\textbf{f}) scientific mobility. 
+		Boxplots show distribution of actual flux for binned values of predicted flux.
+		Box color corresponds to the degree to which the distribution overlaps $x = y$.
+	}
+	\label{fig:supp:gravity_pprjsd}
 \end{figure}

### 2020-02-28 paper/current/main.tex
add_sentense_to_semaxis

--- 2020-02-27 paper/current/main.tex
@@
 In additional to geography, these embeddings capture latent religious, cultural, social, and linguistic, and implicit hierarchical relationships between organizations at multiple levels of granularity.
-With this approach, we can learn efficient, dense, and meaningful vector-space representations of scientific mobility directly from the data, one that models a complex notion of inter-organization distance and which points towards a generalized methodology of reasoning about all kinds of mobility.
+With this approach, we can learn scalable, dense, and meaningful vector representations of scientific mobility directly from the data, one that models a complex notion of inter-organization distance and which points towards a generalized methodology of reasoning about all kinds of mobility.
 
@@
 The result is a vector-space representation of organizations in which the \textit{cosine distance} between vectors represents the tendency for pairs of organizations to occur near one another in the same career path.
-In addition to encoding latent structure, these  are computationally and space efficient, robust to noise, and allow for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.
+In addition to encoding latent structure, these  are computationally efficient and scalable, robust to noise, and allow for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.
 
@@
 \subsection*{SemAxis}
-By constructing semantic embeddings from mobility trajectories, we allow for unique methodology for understading the embedding space, such as SemAxis.
+By constructing semantic embeddings from mobility trajectories, we allow for unique methodology for understanding the embedding space, such as SemAxis.
 SemAxis~\autocite{an2018semaxis} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these term to the concept.
@@
 In the case of language, the ends of the axis could be ``good'' and ``bad'', ``surprising'' and ``unsurprising'', or ``masculine'' and ``feminine''.
+It is shown that projection of words to given specific axis fit well with widely shared cultural connotation from surveyed
+responses and labeled historical data \autocite{kozlowski2018geometry}.
 In the case of scientific mobility, SemAxis offers a means of operationalizing abstract relationships between organizations.

### 2020-02-28 paper/current/main.tex
add_papera_and_relplace_cite_with_autocite"

--- 2020-02-28 paper/current/main.tex
@@
 
-The skip-gram negative-sampling embedding (\SGNS) model preserves semantic relationships between words in a dense and meaningful low-dimensional vector-space representation~\cite{mikolov2013word2vec}, and just as its has been applied to and revealed insights implicit in text~\cite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}, so too might this model encode the latent structures of global scientific mobility.
+The skip-gram negative-sampling embedding (\SGNS) model preserves semantic relationships between words in a dense and meaningful low-dimensional vector representation~\autocite{mikolov2013word2vec}, and just as its has been applied to and revealed insights implicit in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}, so too might this model encode the latent structures of global scientific mobility.
 As scientist's careers progress, they move institutions or pick up additional affiliations, forming co-affiliation or \textit{mobility trajectories} that can be derived from their publication histories~\autocite{robinson2019mobility, sugimoto2017mostimpact}.

### 2020-02-28 paper/current/main.tex
add_sentense_to_semaxis_result

--- 2020-02-28 paper/current/main.tex
@@
 For reference, SemRank achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking mean-normalized citation score ($\rho = 0.87$). 
-This suggests that word embeddings, in addition to learning the latent geography of mobility, also capture more nuanced characteristics such as latent hierarchy.
+This suggests that \SGNS{} model, in addition to learning the latent geography of mobility, while capture more nuanced characteristics such as latent hierarchy in the axis of the embedding, which is fascinating characteristic of our approach.
 
@@
 
-By learning a distance directly from the data, the \SGNS{} model effectively and efficiently captures a robust measure of semantic distance between entities, all with existing tools and minor data processing.
+By learning a distance directly from the data, the \SGNS{} model successfully  and efficiently captures a robust measure of semantic distance between entities, all with existing tools and minor data processing.
 This methodology is broadly applicable to studies of mobility.

### 2020-02-28 paper/current/main.tex
re-integrated ppr cos and jsd figures

--- 2020-02-28 paper/current/main.tex
@@
 		Predictions are not meaningfully different if estimates are learned on all pairs of organizations (Fig. S\ref{fig:supp:gravity_prediction_subsets}).
-		These predictions are robust whether the model is fit on the global data, or on the domestic (Fig.~\ref{fig:gravity_performance}e-h) or international Fig.~\ref{fig:supp:gravity_prediction_subsets}) subsets.
+		These predictions are robust whether the model is fit on the global data, or on the domestic (Fig.~\ref{fig:gravity_performance}e-h) or international Fig.~\ref{fig:supp:gravity_prediction_subsets}) subsets .
 	}

### 2020-02-28 paper/current/main.tex
edit introcution part:

--- 2020-02-28 paper/current/main.tex
@@
 
-The skip-gram negative-sampling embedding (\SGNS) model preserves semantic relationships between words in a dense and meaningful low-dimensional vector representation~\autocite{mikolov2013word2vec}, and just as its has been applied to and revealed insights implicit in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}, so too might this model encode the latent structures of global scientific mobility.
+The skip-gram negative-sampling embedding (\SGNS) model preserves semantic relationships between words in a dense, continuous and meaningful low-dimensional vector representation~\autocite{mikolov2013word2vec}, and just as its has been applied to and revealed insights implicit in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}, so too might this model encode the latent structures of global scientific mobility.
 As scientist's careers progress, they move institutions or pick up additional affiliations, forming co-affiliation or \textit{mobility trajectories} that can be derived from their publication histories~\autocite{robinson2019mobility, sugimoto2017mostimpact}.
-We embed mobility trajectories by treating organizations analogously to words and trajectories analogously to sentences, and feed the resulting "sentence" into the standard \SGNS{} model (Fig.~\ref{fig:methods:mobility_sentence}).
-The result is a vector-space representation of organizations in which the \textit{cosine distance} between vectors represents the tendency for pairs of organizations to occur near one another in the same career path.
-In addition to encoding latent structure, these  are computationally efficient and scalable, robust to noise, and allow for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.
+We embed mobility trajectories by treating organizations analogously to words and trajectories analogously to sentences, and feed the resulting "sentence" into the standard \SGNS{} model (See Fig.~\ref{fig:methods:mobility_sentence}).
+The result is a vector representation of organizations in which the \textit{cosine distance} between vectors represents the tendency for pairs of organizations to occur near one another in the same career path.
+In addition to encoding latent structure, this approach is computationally efficient, scalable for large dataset, robust to noise, and allow for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.
 
@@
 
-We embed the trajectories of the three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019 as evidenced by their publications indexed in the Web of Science.
+We embed the trajectories of the three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019 as evidenced by their publications indexed in the Web of Science databse.
 We adopt the Gravity Model of mobility~\autocite{zipf1946gravity}, one of the most common and broadly applied mobility models~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} to assess how well the embedding captures mobility.
-We derive the \textit{expected flux} from the base gravity model, defined as,
+After fitting the parameters of the gravity model, we derive the \textit{expected flux} $\widetilde{f_{ij}}$ from the obtained gravity model, defined as,
 
@@
 	\label{eq:gravity_basic}
-	f_{ij} = C*m_{i}m_{j}*f(r_{ij})
+	\widetilde{f_{ij}} = C*m_{i}m_{j}*f(r_{ij})
 \end{equation}
@@
 Where the flux, or number of authors co-affiliated with two organizations during the time period $f_{ij}$, increases with the organization's sizes, $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
-We consider two distances, $f_{ij}$, the geographic distance between the organizations, and the \textit{embedding distance} defined as the cosine distance between the organization's vector in the trained embedding space.
+We consider two distances, the geographic distance between the organizations as a baseline, and the \textit{embedding distance} defined as the cosine distance between the organization's vector in the trained embedding space.
 We argue that the performance of a distance measure can be observed from their ability to explain expected mobility between organizations, as well as to predict flux using the gravity model. 
-For geographic distance, we define $f(r_{ij})$ as the standard power-decay function, and for the embedding distance, we use the exponential form, selected as the best performing for each case.
+For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function. selected as the best performing for each case.
 

### 2020-02-28 paper/current/main.tex
edit math part

@@
 		\textbf{g-h.} Embedding distance also outperforms geographic distance when predicting flux using model parameters estimated from only pairs of organizations in different countries. 
-		Predictions are not meaningfully different if estimates are learned on all pairs of organizations (Fig. S\ref{fig:supp:gravity_prediction_subsets}).
+		Predictions are not meaningfully different if estimates are learned on all pairs of organizations (Fig. \ref{fig:supp:gravity_prediction_subsets}).
 		These predictions are robust whether the model is fit on the global data, or on the domestic (Fig.~\ref{fig:gravity_performance}e-h) or international Fig.~\ref{fig:supp:gravity_prediction_subsets}) subsets .
@@
 
-And, if we remove ${\mu_*}$ for simplicity (or for our special case with $\mu_{i} = \mu_{j} = \mu_*$), then $p(j|i)$ can be written as,
+And, if we remove ${\mu_*}$ for simplicity (or for the special case with $\mu_{i} = \mu_{j} = \mu_*$), then $p(j|i)$ can be written as,
 
@@
     \includegraphics[width=0.8\columnwidth]{\figdir/Math/approxi_proof.png}
-    \caption{Relationship between the conditional probability $p(j|i)$ and approximate functional form Eq. \ref{eq:real_embedding_relationship}}.
+    \caption{Relationship between the conditional probability $p(j|i)$ from Eq.\ref{eq:flux_conditional_prob} which is measured in the data and approximate functional form Eq.
+\ref{eq:real_embedding_relationship}}.
     \label{fig:real_embedding_relationship}
@@
 
-where $v_w$ and $v'_w$ are `input' and `output' vector representations of each word in the vocabulary.
+where $v_w$ and $v'_w$ are ``input'' and ``output'' vector representations of each word in the vocabulary.
 With facts that the denominator is not calculated entirely in the negative sampling strategies and the cosine similarity of in-vectors is used as a measure of affinity in general, Eq.

### 2020-02-28 paper/current/main.tex
unify (see Fig 1) to just (Fig1)

@@
 As scientist's careers progress, they move institutions or pick up additional affiliations, forming co-affiliation or \textit{mobility trajectories} that can be derived from their publication histories~\autocite{robinson2019mobility, sugimoto2017mostimpact}.
-We embed mobility trajectories by treating organizations analogously to words and trajectories analogously to sentences, and feed the resulting "sentence" into the standard \SGNS{} model (See Fig.~\ref{fig:methods:mobility_sentence}).
+We embed mobility trajectories by treating organizations analogously to words and trajectories analogously to sentences, and feed the resulting "sentence" into the standard \SGNS{} model (Fig.~\ref{fig:methods:mobility_sentence}).
 The result is a vector representation of organizations in which the \textit{cosine distance} between vectors represents the tendency for pairs of organizations to occur near one another in the same career path.
@@
     \includegraphics[width=0.8\columnwidth]{\figdir/Math/approxi_proof.png}
-    \caption{Relationship between the conditional probability $p(j|i)$ from Eq.\ref{eq:flux_conditional_prob} which is measured in the data and approximate functional form Eq.
+    \caption{Relationship between the conditional probability $p(j|i)$ \ref{eq:flux_conditional_prob} which is measured in the data and approximate functional form Eq.
 \ref{eq:real_embedding_relationship}}.
@@
 Even though UMass Boston is located in Boston, it clusters near other universities in the UMass System, reflecting a relative lack of mobility between the two systems, even within the same state.
-Similar dynamics can be observed in many states (New York, California, etc.), such that prestigious university systems are separate from more regional ones (See SI~?).
+Similar dynamics can be observed in many states (New York, California, etc.), such that prestigious university systems are separate from more regional ones (SI~?).
 
@@
 We build on descriptive results to quantitatively assess the national factors captured in the learned vector-space.
-We calculate the representative vector of each country with averaging organization vectors within the given country, calculate pairwise cosine similarity, and perform hierarchical clustering (see Fig.
+We calculate the representative vector of each country with averaging organization vectors within the given country, calculate pairwise cosine similarity, and perform hierarchical clustering (Fig.
 \ref{fig:clustering}a) of nations that have at least 25 organizations, excluding the United States which has high similarity with most other countries.
@@
 Universities at the bottom of this axis tend to be regional universities with lower national profiles, such as California State University Long Beach, University of West Florida, and Barry University.
-There are strong differences by state in terms of prestige---overall, universities in Massachusetts are nearer the \textit{Elite} end of the axis than are universities in Arizona, Connecticut, Pennsylvania, and Florida (see Fig.~\ref{fig:supp:semaxis_states}).
+There are strong differences by state in terms of prestige---overall, universities in Massachusetts are nearer the \textit{Elite} end of the axis than are universities in Arizona, Connecticut, Pennsylvania, and Florida (Fig.~\ref{fig:supp:semaxis_states}).
 
@@
 Authors are classified as mobile when they have at least two distinct organization ids in their trajectory, meaning that they have published using two or more distinct affiliations between 2008 and 2019.
-While the number of publications has increased year-to-year, the mobility and disciplinary makeup of the dataset has not significantly changed across the period of study (see Fig.~\ref{fig:supp:pubs_over_time}).
+While the number of publications has increased year-to-year, the mobility and disciplinary makeup of the dataset has not significantly changed across the period of study (Fig.~\ref{fig:supp:pubs_over_time}).
 
@@
 
-Results are reported for embeddings with a dimensionality of 300 and a window size of one, which were the parameters that produced  that best explained the flux between organizations (see Fig.
+Results are reported for embeddings with a dimensionality of 300 and a window size of one, which were the parameters that produced  that best explained the flux between organizations (Fig.
 SI~\ref{fig:supp:hyperparams}).

### 2020-02-28 paper/current/main.tex
edit_gravity_part

@@
 Given its simplicity and flexibility, this formulation and variants have proven incredibly useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
-Following the gravity law, the expected flux between two organizations is defined as follows,
+Following the gravity law, the expected flux $\widetilde{f_{ij}}$ between two organizations is defined as follows,
 
@@
 For embedding distance , we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data. 
-To estimate parameters $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_flux}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.
+To estimate parameters $C$, $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_basic}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.
 
@@
 
-The gravity law of mobility is known to be sensitive to the case where $f_{ij} = 0$, or zero movement between organizations. 
+where $f_{ij}$ is the real flux from dataset. The gravity law of mobility is known to be sensitive to the case where $f_{ij} = 0$, or zero movement between organizations. 
 Here, non-zero flows account for only 4.2 percent of all possible pairs of  the 6,580 organizations represented in the embedding.

### 2020-02-28 paper/current/main.tex

@@
 
+We also examine the gravity model on the Personalized Page Rank (PPR)\autocite{jeh2003scaling} as a benchmark on the network.
+We construct the co-occurrence network whose nodes are organization and edges are co-occurrence between two organizations.
+We use 0.9 in here.
+
+\begin{equation}
+	\label{eq:ppr}
+	p_i = (1.0 - \alpha) * v_i + \alpha p_i W,
+\end{equation}
+
+where $v_i$ is a vector with 1 in the ith entry, whose length is the N, the number of nodes in the network, W is the weighted adjacency matrix, and $\alpha$ is the hyper-parameter is called the teleportation parameter that controls the probability that random walker revisits the original node i.
+We can think of this PPR vector as a representation of a node, which is N-length embedding.
+For examining the gravity law, we use two distance measures for PPR.
+The first one is cosine distance which is used for our embedding method, and the second one is the Jensen–Shannon divergence (JSD).
+
+\begin{equation}
+	\label{eq:JSD}
+	JSD(P||Q) = \frac{1}{2}D_{KL}(P||M) + \frac{1}{2}D_{KL}(Q||M),
+\end{equation}
+
+\begin{equation}
+	\label{eq:KL}
+	D_{KL} = \sum p(x)\log(\frac{p(x)}{q(x)})
+\end{equation}
+
+where $M=\frac{1}{2}(P+Q)$.
+We report the both results, PPR with cosine distance (Fig.
+\ref{fig:supp:gravity_pprcos}) and (Fig.
+\ref{fig:supp:gravity_pprjsd}).
+In both cases, the performance is under the performance of the model with geographical distance.
+Even though the length of the PPR vectors is extremely larger than the length of our embedding vectors, our result on the embedding outperforms than network approach.
+Moreover, it is also computationally efficient and salable for large dataset.
 %
@@
 %
+
 \begin{figure}[p!]
@@
 	\caption{
-		\textbf{Personalized page rank with cosine distance.}
+		\textbf{Personalized page rank with Jensen-Shannon Divergence.}
 		Performance of personalized page rank scores in explaining and predicting mobility.

### 2020-02-28 workflow/scripts/BuildAggregateDistanceFile.R
Plot variations of the gravity law plots based on PPR cosine distnace and JSD

@@ -22,7 +22,9 @@ option_list = list(
               help="Path to file containing organization geographic distances"),
   make_option(c("-e", "--emb"), action="store", default=NA, type='character',
               help="Path to file containing organization embedding distances"),
-  make_option(c("--ppr"), action="store", default=NA, type='character',
+  make_option(c("--pprcos"), action="store", default=NA, type='character',
+              help="Path to file containing organization PPR distances"),
+  make_option(c("--pprjsd"), action="store", default=NA, type='character',
               help="Path to file containing organization PPR distances"),
   make_option(c("-o", "--out"), action="store", default=NA, type='character',
               help="Path to save aggregated distance file")
@@ -130,10 +132,11 @@ distance_all <- data.table::rbindlist(list(emb1, emb2)) %>%
 remove("emb1", "emb2", "embedding_similarities")
 
 
-# PPR distnaces
-ppr <- read_csv(opt$ppr, col_types = cols()) %>%
+# PPR Cosine distnaces
+ppr <- read_csv(opt$pprcos, col_types = cols()) %>%
   select(org1, org2, distance) %>%
-  rename(ppr_distance = distance)
+  rename(pprcos_distance = distance) %>%
+  mutate(pprcos_distance = 1 - pprcos_distance)
 
 ppr1 <- distance_all %>%
   inner_join(ppr, by = c("org1" = "org1", "org2" = "org2"))
@@ -145,6 +148,24 @@ distance_all <- data.table::rbindlist(list(ppr1, ppr2)) %>%
   distinct(org1, org2, .keep_all = TRUE)
 
 remove("ppr", "ppr1", "ppr2")
+
+
+# PPR JSD
+ppr <- read_csv(opt$pprjsd, col_types = cols()) %>%
+  select(org1, org2, distance) %>%
+  rename(pprjsd_distance = distance)
+
+ppr1 <- distance_all %>%
+  inner_join(ppr, by = c("org1" = "org1", "org2" = "org2"))
+
+ppr2 <- distance_all %>%
+  inner_join(ppr, by = c("org2" = "org1", "org1" = "org2"))
+
+distance_all <- data.table::rbindlist(list(ppr1, ppr2)) %>%
+  distinct(org1, org2, .keep_all = TRUE)
+
+remove("ppr", "ppr1", "ppr2")
+
 
 #
 # ORG LOOKUP TABLES
@@ -168,7 +189,8 @@ distance_all <- distance_all %>%
   # Select only relevant variables
   select(org1, org2, count,
[…]

### 2020-02-28 workflow/scripts/CalculatePredictedVsActual.R

@@ -30,7 +30,7 @@ agg <- readr::read_csv(opt$input, col_types = readr::cols()) %>%
   select(org1_size, org2_size,
          org1_country, org2_country,
          count, gravity,
-         geo_distance, ppr_distance, emb_distance) %>%
+         geo_distance, pprcos_distance, pprjsd_distance, emb_distance) %>%
   rename(actual = count)
 
 # If the geographic constraint (--geo) is set, then filter the
@@ -69,17 +69,29 @@ if (opt$distance == "geo") {
       # Calculate the expected value using the embedding similarity formula
       expected = org1_size * org2_size * exp((emb_coef * emb_distance) + intercept)
     )
-} else if (opt$distance == "ppr") {
-  fit <- summary(lm(log(gravity) ~ ppr_distance, data = agg))
+} else if (opt$distance == "pprcos") {
+  fit <- summary(lm(log(gravity) ~ pprcos_distance, data = agg))
 
   # Save the coefficients for use later
   intercept <- fit$coefficients["(Intercept)", "Estimate"]
-  ppr_coef <- fit$coefficients["ppr_distance", "Estimate"]
+  ppr_coef <- fit$coefficients["pprcos_distance", "Estimate"]
 
   agg <- agg %>%
     mutate(
       # Calculate the expected value using the embedding similarity formula
-      expected = org1_size * org2_size * exp((ppr_coef * ppr_distance) + intercept)
+      expected = org1_size * org2_size * exp((ppr_coef * pprcos_distance) + intercept)
+    )
+} else if (opt$distance == "pprjsd") {
+  fit <- summary(lm(log(gravity) ~ pprjsd_distance, data = agg))
+
+  # Save the coefficients for use later
+  intercept <- fit$coefficients["(Intercept)", "Estimate"]
+  ppr_coef <- fit$coefficients["pprjsd_distance", "Estimate"]
+
+  agg <- agg %>%
+    mutate(
+      # Calculate the expected value using the embedding similarity formula
+      expected = org1_size * org2_size * exp((ppr_coef * pprjsd_distance) + intercept)
     )
 }
 

### 2020-02-28 workflow/scripts/PlotPredictedVsActual.R

@@ -77,7 +77,8 @@ binned <- data %>%
     crosses_ab_weak = (percentile_max > pos & pos > mu) | (percentile_min < pos & pos < mu),
   )
 
-error <- sqrt(mean((log10(data$expected) ^ 2) - (log10(data$actual) ^ 2)))
+error <- sqrt(mean((log10(data$expected) - log10(data$actual)) ^ 2, na.rm = T))
+print(error)
 
 # Build the plot
 plot <- data %>%

### 2020-02-28 workflow/scripts/GetAggregateSlopes.R
The script to actually aggregate the slopes

@@ -1,0 +1,79 @@
+#
+# GetAggregateSlopes.R
+#
+# author: Dakota Murray
+#
+# Iterates through a list of aggregate files, getting the slope of the line of
+# best fit for variables in the file.
+#
+
+library(dplyr)
+library(readr)
+library(boot)
+# Command line arguments
+# Optparse doesn't have a way of taking arbitrary files as input, so use default
+# argument parsing
+args = commandArgs(trailingOnly=TRUE)
+
+DISTANCE_FILES = args[1:length(args) - 1]
+OUTPUT_FILE_PATH = last(args)
+
+# Iterate through each given input file
+agg <- data.table::rbindlist(lapply(DISTANCE_FILES, function(path) {
+
+  print(paste0("Loading file: ", path))
+
+  # Load the file, perform the necessary transformations and remove
+  # unecessary data
+  dist <- read_csv(path, col_types = cols()) %>%
+    filter(count > 0) %>%
+    mutate(gravity = log10(gravity),
+           geo_distance = log10(geo_distance),
+           same_country = org1_country == org2_country,
+           diff_country = org1_country != org2_country
+    ) %>%
+    select(gravity, geo_distance, emb_distance, pprcos_distance, pprjsd_distance, same_country, diff_country)
+
+
+    # Global fits
+    global_geo = coef(lm(gravity ~ geo_distance, data = dist))[2]
+    global_pprcos = coef(lm(gravity ~ pprcos_distance, data = dist))[2]
+    global_pprjsd = coef(lm(gravity ~ pprjsd_distance, data = dist))[2]
+    global_emb = coef(lm(gravity ~ emb_distance, data = dist))[2]
+
+    # Same-country fits
+    same_dist <- dist %>% filter(same_country)
+    same_geo = coef(lm(gravity ~ geo_distance, data = same_dist))[2]
+    same_pprcos = coef(lm(gravity ~ pprcos_distance, data = same_dist))[2]
+    same_pprjsd = coef(lm(gravity ~ pprjsd_distance, data = same_dist))[2]
+    same_emb = coef(lm(gravity ~ emb_distance, data = same_dist))[2]
+
+    # Different-country fits
+    diff_dist <- dist %>% filter(diff_country)
+    diff_geo = coef(lm(gravity ~ geo_distance, data = diff_dist))[2]
[…]

### 2020-03-02 paper/current/main.tex
Moved PPR supp to its own page
revise_abstract

@@
 
-\title{Unsupervised embeddings capture latent structure of scientific mobility} %{{{
+\title{Unsupervised embeddings of institutions capture latent structure of scientific mobility} %{{{
 \date{\today}
@@
 
-Mobility is essential to science---it drives innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige} however the complexity of factors driving global scientific mobility~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics} necessitates simplified models for reasoning about and crafting effective policy.
-Common models of mobility, such as the Gravity Model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity, simini2012universal}, are a function on the \textit{distance} between places.
-However, amid a globalizing scientific enterprise~\autocite{czaika2018globalisation}, geographic distance is only becoming less useful for understanding mobility, whereas other abstract notions of distance~\autocite{boschma2005proximity} cannot be meaningfully measured.
-Here, we demonstrate a data-driven approach of learning an effective distance that encodes the latent structure of mobility using the skip-gram  negative sampling word embedding model~\autocite{mikolov2013word2vec}, treating organizations analogously to words and career trajectories to sentences.
-We source publications of disambiguated authors from the Web of Science database to construct mobility embeddings for authors career trajectories between 2008 and 2019. 
-Distance between vectors in the learned embedding space better explain and predict mobility between organizations than does geographic distance, which we speculate emerges from an underlying connection between embeddings and the gravity model.
-In additional to geography, these embeddings capture latent religious, cultural, social, and linguistic, and implicit hierarchical relationships between organizations at multiple levels of granularity.
-With this approach, we can learn scalable, dense, and meaningful vector representations of scientific mobility directly from the data, one that models a complex notion of inter-organization distance and which points towards a generalized methodology of reasoning about all kinds of mobility.
-
+Scientific mobility drives innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}.
+Common models of mobility, such as the Gravity Model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity, simini2012universal}, describes the of mobility using \textit{distance} between places.
+However, amid a globalizing scientific enterprise~\autocite{czaika2018globalisation}, geographic distance is losing its relevance for understanding mobility, whereas other abstract notions of distance~\autocite{boschma2005proximity} pose challenges; too many choices.
+Accordingly, the complexity of factors driving global scientific mobility~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics} necessitates simplified models for reasoning about and crafting effective policy.
+Here, we demonstrate a data-driven approach of learning an effective distance that encodes the latent structure of mobility using a neural embedding model~\autocite{mikolov2013word2vec} by sourcing publications of disambiguated authors from the Web of Science database between 2008 and 2019.
+Distance between vectors in the learned embedding space explain and predict mobility between organizations better than  geographic distance or network distance.
+We argue that such power emerges from an underlying connection between embeddings and the gravity model.
+In addition to geography, these embeddings also capture latent religious, cultural, social, and linguistic, and even prestige of organizations at multiple levels of granularity.
+With this approach, we can learn scalable, dense, and meaningful vector representations of scientific mobility directly from the data and it can be generalized methodology of reasoning about all kinds of mobility.
 \end{abstract}
@@
 
-\newpage
 \clearpage
@@
 \section{Supporting Information}
+
+%
+% S1 TEXT
+\newpage
+\paragraph*{S1 Text}
+\label{si:text:ppr_dist}
+{\bf Network-based personalized page rank distances.}
+
+We also examine the gravity model on the Personalized Page Rank (PPR)\autocite{jeh2003scaling} as a benchmark on the network.
+We construct the co-occurrence network whose nodes are organization and edges are co-occurrence between two organizations.
+We use 0.9 in here.
+
+\begin{equation}
+	\label{eq:ppr}
+	p_i = (1.0 - \alpha) * v_i + \alpha p_i W,
+\end{equation}
+
+where $v_i$ is a vector with 1 in the ith entry, whose length is the N, the number of nodes in the network, W is the weighted adjacency matrix, and $\alpha$ is the hyper-parameter is called the teleportation parameter that controls the probability that random walker revisits the original node i.
+We can think of this PPR vector as a representation of a node, which is N-length embedding.
+For examining the gravity law, we use two distance measures for PPR.
+The first one is cosine distance which is used for our embedding method, and the second one is the Jensen–Shannon divergence (JSD).
+
+\begin{equation}
+	\label{eq:JSD}
+	JSD(P||Q) = \frac{1}{2}D_{KL}(P||M) + \frac{1}{2}D_{KL}(Q||M),
+\end{equation}
+
+\begin{equation}
+	\label{eq:KL}
+	D_{KL} = \sum p(x)\log(\frac{p(x)}{q(x)})
+\end{equation}
+
+where $M=\frac{1}{2}(P+Q)$.
+We report the both results, PPR with cosine distance (Fig.
+\ref{fig:supp:gravity_pprcos}) and (Fig.
+\ref{fig:supp:gravity_pprjsd}).
+In both cases, the performance is under the performance of the model with geographical distance.
+Even though the length of the PPR vectors is extremely larger than the length of our embedding vectors, our result on the embedding outperforms than network approach.
+Moreover, it is also computationally efficient and salable for large dataset.
 
@@
 
-We also examine the gravity model on the Personalized Page Rank (PPR)\autocite{jeh2003scaling} as a benchmark on the network.
-We construct the co-occurrence network whose nodes are organization and edges are co-occurrence between two organizations.
-We use 0.9 in here.
-
-\begin{equation}
-	\label{eq:ppr}
-	p_i = (1.0 - \alpha) * v_i + \alpha p_i W,
-\end{equation}
-
-where $v_i$ is a vector with 1 in the ith entry, whose length is the N, the number of nodes in the network, W is the weighted adjacency matrix, and $\alpha$ is the hyper-parameter is called the teleportation parameter that controls the probability that random walker revisits the original node i.
-We can think of this PPR vector as a representation of a node, which is N-length embedding.
-For examining the gravity law, we use two distance measures for PPR.
-The first one is cosine distance which is used for our embedding method, and the second one is the Jensen–Shannon divergence (JSD).
-
-\begin{equation}
-	\label{eq:JSD}
-	JSD(P||Q) = \frac{1}{2}D_{KL}(P||M) + \frac{1}{2}D_{KL}(Q||M),
-\end{equation}
-
-\begin{equation}
-	\label{eq:KL}
-	D_{KL} = \sum p(x)\log(\frac{p(x)}{q(x)})
-\end{equation}
-
-where $M=\frac{1}{2}(P+Q)$.
-We report the both results, PPR with cosine distance (Fig.
-\ref{fig:supp:gravity_pprcos}) and (Fig.
-\ref{fig:supp:gravity_pprjsd}).
-In both cases, the performance is under the performance of the model with geographical distance.
-Even though the length of the PPR vectors is extremely larger than the length of our embedding vectors, our result on the embedding outperforms than network approach.
-Moreover, it is also computationally efficient and salable for large dataset.
 %

### 2020-03-03 paper/current/main.tex
revise introduction para

@@
 
-\title{Unsupervised embeddings of institutions capture latent structure of scientific mobility} %{{{
+\title{Unsupervised embeddings of organizations capture latent structure of scientific mobility} %{{{
 \date{\today}
@@
 Scientific mobility drives innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}.
-Common models of mobility, such as the Gravity Model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity, simini2012universal}, describes the of mobility using \textit{distance} between places.
+Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity, xia2005measlesgravity, jung2008highwaygravity, barbosa2018human, curiel2018citygravity, lewer2008immigrationgravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity, simini2012universal}, describes the of mobility using \textit{distance} between places.
 However, amid a globalizing scientific enterprise~\autocite{czaika2018globalisation}, geographic distance is losing its relevance for understanding mobility, whereas other abstract notions of distance~\autocite{boschma2005proximity} pose challenges; too many choices.
@@
 However, how exactly do we measure the distance between two places?
-Australia may be physically close to Indonesia, but in terms of language, history, and shared culture, they are essentially neighbors to geographically distant countries like the United Kingdom or United States.
-There are many ways to think about the distance~\autocite{boschma2005proximity}, but only geographic distance can be meaningfully quantified. 
-In turn, models of human mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation models ~\autocite{simini2012universal}, rely almost exclusively on geographic distance, rather than other less measurable though important forms.
-Encoding distance in a way that considers not just geography, but also historical, linguistic, cultural, and cognitive proximity would improve our models and thus ability to reason about science and immigration policies.
+Although many alternative ways to quantify the distance~\autocite{boschma2005proximity} exist, geographic distance is an unambiguous and foundational quantity for the distance.
+In turn, models of human mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation models ~\autocite{simini2012universal}, rely almost exclusively on geographic distance, yet, geographic distance fails to capture historical, linguistic, cultural, and cognitive proximity.
+For instance, Australia may be physically close to Indonesia, but in terms of language, history, and shared culture, they are essentially neighbors to geographically distant countries like the United Kingdom.
+Then, how can we quantify meaningful, useful distance between institutions, cities and countries?
 
-The skip-gram negative-sampling embedding (\SGNS) model preserves semantic relationships between words in a dense, continuous and meaningful low-dimensional vector representation~\autocite{mikolov2013word2vec}, and just as its has been applied to and revealed insights implicit in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}, so too might this model encode the latent structures of global scientific mobility.
-As scientist's careers progress, they move institutions or pick up additional affiliations, forming co-affiliation or \textit{mobility trajectories} that can be derived from their publication histories~\autocite{robinson2019mobility, sugimoto2017mostimpact}.
-We embed mobility trajectories by treating organizations analogously to words and trajectories analogously to sentences, and feed the resulting "sentence" into the standard \SGNS{} model (Fig.~\ref{fig:methods:mobility_sentence}).
-The result is a vector representation of organizations in which the \textit{cosine distance} between vectors represents the tendency for pairs of organizations to occur near one another in the same career path.
+% Let's rephease and reuse to somewhere else:)
+%Encoding distance in a way that considers not just geography, but also historical, linguistic, cultural, and cognitive proximity would improve our models and thus ability to reason about science and immigration policies.
+
+It has been demonstrated that neural embedding model preserves semantic relationships between words in a dense, continuous and meaningful low-dimensional vector representation~\autocite{mikolov2013word2vec}, and just as its has been applied to and revealed insights implicit in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
 In addition to encoding latent structure, this approach is computationally efficient, scalable for large dataset, robust to noise, and allow for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.
+Here, we propose a neural embedding models an effective way to estimate distance between  from massive trajectory data.
+
+As scientist's careers progress, they move organizations or pick up additional affiliations, forming co-affiliation or \textit{mobility trajectories} that can be derived from their publication histories~\autocite{robinson2019mobility, sugimoto2017mostimpact}.
+From these mobility trajectories, by treating geo-located organizations analogously to words and trajectories analogously to sentences, we obtain vector-space embeddings of organizations  from neural embedding method, which learn vector representation of organizations by using neural networks (Fig.~\ref{fig:methods:mobility_sentence}).
+The result vector of organizations is representation that the \textit{cosine distance} between vectors represents the distance in the landscape of the scientific mobility data.
 
@@
 
-We embed the trajectories of the three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019 as evidenced by their publications indexed in the Web of Science databse.
-We adopt the Gravity Model of mobility~\autocite{zipf1946gravity}, one of the most common and broadly applied mobility models~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} to assess how well the embedding captures mobility.
-After fitting the parameters of the gravity model, we derive the \textit{expected flux} $\widetilde{f_{ij}}$ from the obtained gravity model, defined as,
+We use the trajectories of the three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science databse.
+We adopt the Gravity Model of mobility~\autocite{zipf1946gravity, barbosa2018human}, one of the most common and broadly applied mobility models~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} to assess how well the embedding captures mobility.
+After fitting the parameters of the gravity model, we derive the \textit{expected flux} $\hat{t_{ij}}$ from the obtained gravity model, defined as,
 
@@
 	\label{eq:gravity_basic}
-	\widetilde{f_{ij}} = C*m_{i}m_{j}*f(r_{ij})
+	\hat{t_{ij}} = Cm_{i}m_{j}f(r_{ij})
 \end{equation}
 
-Where the flux, or number of authors co-affiliated with two organizations during the time period $f_{ij}$, increases with the organization's sizes, $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+Where the flux, or number of authors co-affiliated with two organizations during the time period $t_{ij}$, increases with the organization's sizes, $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
 We consider two distances, the geographic distance between the organizations as a baseline, and the \textit{embedding distance} defined as the cosine distance between the organization's vector in the trained embedding space.

### 2020-03-03 paper/current/main.tex
revise another para

@@
         An author published five papers across five time periods, with only one affiliation listed in the byline of each paper. 
-        A unique identifier is assigned to each organization, and these are concatenated into a mobility sentence. 
+        To each organization, a unique identifier is assigned, and they are assembled into a mobility sentence. 
         \textbf{b.}
@@
 
-The \SGNS{} model learns an effective distance that explains and predicts scientific mobility better than alternatives. 
-Embedding distance explains more of the expected flow between pairs of organizations, with correlation ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) over double that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
-Embedding distance also explains more of the variance of domestic (Fig.~\ref{fig:supp:gravity_correlation}c) and international mobility flows (Fig.
-~\ref{fig:supp:gravity_correlation}d) than does geographic distance.
-After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance globally (Fig.~\ref{fig:gravity_performance}c-d) and for domestic (Fig.~\ref{fig:supp:gravity_correlation}e-f) and international mobility(Fig.~\ref{fig:supp:gravity_correlation}g-h).
-Similarly, embedding distance outperforms distances derived from calculating personalized-page rank scores on the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+The effective distance  estimated by our embedding model explains and predicts scientific mobility best. 
+Embedding distance ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) is more than twice that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
+This pattern holds for the variance of domestic (Fig.~\ref{fig:supp:gravity_correlation}c) and international mobility flows (Fig.~\ref{fig:supp:gravity_correlation}d). 
+After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance globally (Fig.~\ref{fig:gravity_performance}c--d) and for domestic (Fig.~\ref{fig:supp:gravity_correlation}e--f) and international mobility(Fig.~\ref{fig:supp:gravity_correlation}g--h).
+Similarly, embedding ``diffusion'' distance outperforms distances derived from calculating personalized-page rank scores on the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
 Geographic distance alone is a poor tool for understanding international scientific mobility---rather, by learning a distance directly from the data, it is possible to better explain, and better predict flux between organizations.
@@
 		Color indicates frequency of organization pairs within each hex bin.
-		\textbf{c-d.} Predictions  of flux between organization pairs made using embedding distance out-perform those made using geographic distance. 
+		\textbf{c-d.} Predictions  of flux between organization pairs made using embedding distance outperform those made using geographic distance. 
 		Boxplots show distribution of actual flux for binned values of predicted flux.
@@
 
-Why does the SNGS model, a tool designed for natural language processing, produce such a reasonable distance that models gravity relationships between organizations?
+Why does the word embedding model, a tool designed for natural language processing, produce such a reasonable distance that models gravity relationships between organizations?
 We find evidence of a theoretical connection between the two models, one that makes the skip-gram model applicable to many other forms of mobility trajectory.
 
-Let $f_{ij}$ represents the total \textbf{flux}, the number of people who moved between organizations $i$ and $j$.
+Let $t_{ij}$ represents the total \textbf{flux}, the number of people who moved between organizations $i$ and $j$.
 $M_{i}$ and $M_{j}$ represent the size of an organization.
@@
     \label{eq:gravity_model}
-    \frac{f_{ij}}{M_{i} * M_{j}} \propto \exp(\cos(v_i,v_j))
+    \frac{f_{ij}}{M_{i} M_{j}} \propto \exp(\cos(v_i,v_j))
 \end{equation}
@@
     \label{eq:gravity_model_approx}
-    \frac{f_{ij}}{\mu_i * \mu_j} \propto \exp(\cos(v_i,v_j))
+    \frac{f_{ij}}{\mu_i  \mu_j} \propto \exp(\cos(v_i,v_j))
 \end{equation}
@@
     \label{eq:gravity_relationship}
-    \frac{f_{ij}}{\mu_i * \mu_j} = \frac{\mu_i * p(j|i)}{\mu_i * \mu_j} =  \frac{p(j|i)}{\mu_j} \propto \exp(\cos(v_i,v_j))
+    \frac{f_{ij}}{\mu_i  \mu_j} = \frac{\mu_i  p(j|i)}{\mu_i\mu_j} =  \frac{p(j|i)}{\mu_j} \propto \exp(\cos(v_i,v_j))
 \end{equation}
@@
     \label{eq:conditional probability}
-      p(j|i) \propto {\mu_j}* \exp(\cos(v_i,v_j))
+      p(j|i) \propto {\mu_j} \exp(\cos(v_i,v_j))
 \end{equation}
@@
 \begin{equation}
-    p(j|i) \propto \frac{{\mu_j}* \exp(\cos(v_i,v_j)}{\sum_{k\in\mathpzc{N}_i} {\mu_k}* \exp(\cos(v_i,v_k))}
+    p(j|i) \propto \frac{{\mu_j}\exp(\cos(v_i,v_j)}{\sum_{k\in\mathpzc{N}_i} {\mu_k}\exp(\cos(v_i,v_k))}
 \end{equation}

### 2020-03-04 paper/current/main.tex
replace f as t
replace_t_with_T,_rephrase_title_of_the_first_para

@@
 Scientific mobility drives innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}.
-Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity, xia2005measlesgravity, jung2008highwaygravity, barbosa2018human, curiel2018citygravity, lewer2008immigrationgravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity, simini2012universal}, describes the of mobility using \textit{distance} between places.
+Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity, xia2005measlesgravity, jung2008highwaygravity, barbosa2018human, curiel2018citygravity, lewer2008immigrationgravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity, simini2012universal}, describes mobility flow using \textit{distance} between places.
 However, amid a globalizing scientific enterprise~\autocite{czaika2018globalisation}, geographic distance is losing its relevance for understanding mobility, whereas other abstract notions of distance~\autocite{boschma2005proximity} pose challenges; too many choices.
@@
 We adopt the Gravity Model of mobility~\autocite{zipf1946gravity, barbosa2018human}, one of the most common and broadly applied mobility models~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} to assess how well the embedding captures mobility.
-After fitting the parameters of the gravity model, we derive the \textit{expected flux} $\hat{t_{ij}}$ from the obtained gravity model, defined as,
+After fitting the parameters of the gravity model, we derive the \textit{expected flux} $\hat{T_{ij}}$ from the obtained gravity model, defined as,
 
@@
 	\label{eq:gravity_basic}
-	\hat{t_{ij}} = Cm_{i}m_{j}f(r_{ij})
+	\hat{T_{ij}} = Cm_{i}m_{j}f(r_{ij})
 \end{equation}
 
-Where the flux, or number of authors co-affiliated with two organizations during the time period $t_{ij}$, increases with the organization's sizes, $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+Where the flux, or number of authors co-affiliated with two organizations during the time period $T_{ij}$, increases with the organization's sizes, $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
 We consider two distances, the geographic distance between the organizations as a baseline, and the \textit{embedding distance} defined as the cosine distance between the organization's vector in the trained embedding space.
@@
 %
-\subsection*{Embedding performance}
+\subsection*{Embeddings estimate the effective distance between organizations}
 
@@
 
-Let $t_{ij}$ represents the total \textbf{flux}, the number of people who moved between organizations $i$ and $j$.
+Let $T_{ij}$ represents the total \textbf{flux}, the number of people who moved between organizations $i$ and $j$.
 $M_{i}$ and $M_{j}$ represent the size of an organization.
@@
     \label{eq:gravity_model}
-    \frac{f_{ij}}{M_{i} M_{j}} \propto \exp(\cos(v_i,v_j))
+    \frac{T_{ij}}{M_{i} M_{j}} \propto \exp(\cos(v_i,v_j))
 \end{equation}
@@
 
-In the case of scientific co-affiliation, all movements are without direction (symmetric), meaning that  $f_{ij} = f_{ji}$.
+In the case of scientific co-affiliation, all movements are without direction (symmetric), meaning that  $T_{ij} = T_{ji}$.
 Let's denote $\mathpzc{N}_i$ as the neighborhood set of organization i, which are organizations with non-zero co-affiliation to organization i.
@@
 \begin{equation}
-    \mu_{i} = \sum_{k\in\mathpzc{N}_i} f_{ik} \propto M_i
+    \mu_{i} = \sum_{k\in\mathpzc{N}_i} t_{ik} \propto M_i
 \end{equation}
@@
     \label{eq:gravity_model_approx}
-    \frac{f_{ij}}{\mu_i  \mu_j} \propto \exp(\cos(v_i,v_j))
+    \frac{T_{ij}}{\mu_i  \mu_j} \propto \exp(\cos(v_i,v_j))
 \end{equation}
@@
     \label{eq:flux_conditional_prob}
-    p(j|i) = \frac{f_{ij}}{\mu_i} 
+    p(j|i) = \frac{T_{ij}}{\mu_i} 
 \end{equation}
@@
     \label{eq:gravity_relationship}
-    \frac{f_{ij}}{\mu_i  \mu_j} = \frac{\mu_i  p(j|i)}{\mu_i\mu_j} =  \frac{p(j|i)}{\mu_j} \propto \exp(\cos(v_i,v_j))
+    \frac{T_{ij}}{\mu_i  \mu_j} = \frac{\mu_i  p(j|i)}{\mu_i\mu_j} =  \frac{p(j|i)}{\mu_j} \propto \exp(\cos(v_i,v_j))
 \end{equation}

### 2020-03-05 paper/current/main.tex
change para text
just change t to T
general paper updates

@@
 Scientific mobility drives innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}.
-Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity, xia2005measlesgravity, jung2008highwaygravity, barbosa2018human, curiel2018citygravity, lewer2008immigrationgravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity, simini2012universal}, describes mobility flow using \textit{distance} between places.
-However, amid a globalizing scientific enterprise~\autocite{czaika2018globalisation}, geographic distance is losing its relevance for understanding mobility, whereas other abstract notions of distance~\autocite{boschma2005proximity} pose challenges; too many choices.
-Accordingly, the complexity of factors driving global scientific mobility~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics} necessitates simplified models for reasoning about and crafting effective policy.
-Here, we demonstrate a data-driven approach of learning an effective distance that encodes the latent structure of mobility using a neural embedding model~\autocite{mikolov2013word2vec} by sourcing publications of disambiguated authors from the Web of Science database between 2008 and 2019.
+Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity, xia2005measlesgravity, jung2008highwaygravity, barbosa2018human, curiel2018citygravity, lewer2008immigrationgravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity, simini2012universal}, describes mobility using the \textit{distance} between places.
+However, amid a globalizing scientific enterprise~\autocite{czaika2018globalisation}, geographic distance is losing its relevance for understanding mobility, whereas other abstract notions of distance~\autocite{boschma2005proximity} pose practical and theoretical challenges.
+Accordingly, the complexity of factors shaping global scientific mobility~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics} necessitates simplified models for reasoning about and crafting effective policy.
+Here, we demonstrate a data-driven approach of learning an effective distance that encodes the latent structure of mobility using a neural embedding model~\autocite{mikolov2013word2vec} trained on mobility traces sourced from the publications of disambiguated authors from the Web of Science database between 2008 and 2019.
 Distance between vectors in the learned embedding space explain and predict mobility between organizations better than  geographic distance or network distance.
@@
 In addition to geography, these embeddings also capture latent religious, cultural, social, and linguistic, and even prestige of organizations at multiple levels of granularity.
-With this approach, we can learn scalable, dense, and meaningful vector representations of scientific mobility directly from the data and it can be generalized methodology of reasoning about all kinds of mobility.
+With this approach, we can learn scalable, dense, and meaningful vector representations of scientific mobility directly from the data using a methodology that can be easily applied to all kinds of mobility.
 \end{abstract}
@@
 
-When scientists move, so does their knowledge, and for scientific mobility, like all human movement, distance matters. 
+When scientists move, they bring their knowledge with them. 
+For scientific mobility, like all human movement, distance matters. 
 However, how exactly do we measure the distance between two places?
-Although many alternative ways to quantify the distance~\autocite{boschma2005proximity} exist, geographic distance is an unambiguous and foundational quantity for the distance.
+Although many alternative ways to quantify the distance~\autocite{boschma2005proximity} exist, geographic distance remains an unambiguous and foundational quantity for the distance.
 In turn, models of human mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation models ~\autocite{simini2012universal}, rely almost exclusively on geographic distance, yet, geographic distance fails to capture historical, linguistic, cultural, and cognitive proximity.
@@
 
-It has been demonstrated that neural embedding model preserves semantic relationships between words in a dense, continuous and meaningful low-dimensional vector representation~\autocite{mikolov2013word2vec}, and just as its has been applied to and revealed insights implicit in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
-In addition to encoding latent structure, this approach is computationally efficient, scalable for large dataset, robust to noise, and allow for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.
-Here, we propose a neural embedding models an effective way to estimate distance between  from massive trajectory data.
+It has been demonstrated that neural embedding models preserves semantic relationships between words in a dense, continuous and meaningful low-dimensional vector representation~\autocite{mikolov2013word2vec}, and have been applied to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
+In addition to encoding latent structure, this approach is computationally efficient, scalable for large datasets, robust to noise, and allows for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.
+Here, we propose a neural embedding model as an effective means of encoding an effective measure of distance using massive trajectory data.
 
-As scientist's careers progress, they move organizations or pick up additional affiliations, forming co-affiliation or \textit{mobility trajectories} that can be derived from their publication histories~\autocite{robinson2019mobility, sugimoto2017mostimpact}.
-From these mobility trajectories, by treating geo-located organizations analogously to words and trajectories analogously to sentences, we obtain vector-space embeddings of organizations  from neural embedding method, which learn vector representation of organizations by using neural networks (Fig.~\ref{fig:methods:mobility_sentence}).
-The result vector of organizations is representation that the \textit{cosine distance} between vectors represents the distance in the landscape of the scientific mobility data.
+As scientist's careers progress, they move between organizations or pick up additional affiliations, forming co-affiliation or \textit{mobility trajectories} that can be derived from their publication histories~\autocite{robinson2019mobility, sugimoto2017mostimpact}.
+By treating geo-located organizations analogously to words and trajectories analogously to sentences, we learn vector-space embedding of organizations using neural embedding (Fig.~\ref{fig:methods:mobility_sentence}).
+The resulting vector of organizations is representation that the \textit{cosine distance} between vectors represents the distance in the landscape of scientific mobility.
 
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{\figdir/mobility_example_combined.pdf}
+    \includegraphics[width=\textwidth]{\figdir/mobility_example_combined.pdf}
     \caption{
@@
 
-We use the trajectories of the three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science databse.
+We use the trajectories of the three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
 We adopt the Gravity Model of mobility~\autocite{zipf1946gravity, barbosa2018human}, one of the most common and broadly applied mobility models~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} to assess how well the embedding captures mobility.
-After fitting the parameters of the gravity model, we derive the \textit{expected flux} $\hat{T_{ij}}$ from the obtained gravity model, defined as,
+After fitting the parameters of the gravity model, we use it to derive the \textit{expected flux} $\hat{T_{ij}}$ between organizations, defined as,
 
@@
 
-Where the flux, or number of authors co-affiliated with two organizations during the time period $T_{ij}$, increases with the organization's sizes, $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+Where the flux, $T_{ij}$, or number of authors co-affiliated with a pair organizations during the time period increases with the organization's sizes, $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
 We consider two distances, the geographic distance between the organizations as a baseline, and the \textit{embedding distance} defined as the cosine distance between the organization's vector in the trained embedding space.
-We argue that the performance of a distance measure can be observed from their ability to explain expected mobility between organizations, as well as to predict flux using the gravity model. 
-For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function. selected as the best performing for each case.
+We argue that the performance of a distance measure can be observed from their ability to explain expected mobility between organizations and to make predictions using the gravity model. 
+For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (ref SI.XYZ).
 
@@
 The effective distance estimated by our embedding model explains and predicts scientific mobility best. 
-Embedding distance ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) is more than twice that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
-This pattern holds for the variance of domestic (Fig.~\ref{fig:supp:gravity_correlation}c) and international mobility flows (Fig.~\ref{fig:supp:gravity_correlation}d). 
+The amount of variance explained by embedding distance ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) is more than twice that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
+This pattern holds for the variance of only domestic (Fig.~\ref{fig:supp:gravity_correlation}c) and international mobility flows (Fig.~\ref{fig:supp:gravity_correlation}d). 
 After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance globally (Fig.~\ref{fig:gravity_performance}c--d) and for domestic (Fig.~\ref{fig:supp:gravity_correlation}e--f) and international mobility(Fig.~\ref{fig:supp:gravity_correlation}g--h).
-Similarly, embedding ``diffusion'' distance outperforms distances derived from calculating personalized-page rank scores on the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+Similarly, embedding distance outperforms ``diffusion''  distances such as those derived from calculating personalized-page rank scores on the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
 Geographic distance alone is a poor tool for understanding international scientific mobility---rather, by learning a distance directly from the data, it is possible to better explain, and better predict flux between organizations.
@@
 		Black dots are mean flux across binned distances.
+		Error bars are 99\% confidence intervals. 
 		Color indicates frequency of organization pairs within each hex bin.
@@
 		Box color corresponds to the degree to which the distribution overlaps $x = y$.
-		\textbf{e-f.} Predictions made using model parameters learned from subset of same-country organization pairs. 
+		``Err'' is calculated as the root-mean squared error between the actual and predicted values. 
+		\textbf{e-f.} Predictions made using model parameters learned from subset of domestic (within-country) organization pairs. 
 		Embedding distance outperforms those made for geographic distance.
-		\textbf{g-h.} Embedding distance also outperforms geographic distance when predicting flux using model parameters estimated from only pairs of organizations in different countries. 
+		\textbf{g-h.} Embedding distance also outperforms geographic distance when predicting flux using model parameters estimated from only international mobility (across-country organization pairs). 
 		Predictions are not meaningfully different if estimates are learned on all pairs of organizations (Fig. \ref{fig:supp:gravity_prediction_subsets}).
@@
 %
-\subsection*{Mathematical explanation}
+\subsection*{Mathematical connection between gravity model and neural embedding }
 
@@
 \begin{equation}
-    \mu_{i} = \sum_{k\in\mathpzc{N}_i} t_{ik} \propto M_i
+    \mu_{i} = \sum_{k\in\mathpzc{N}_i} T_{ik} \propto M_i
 \end{equation}
@@
     \centering
-    \includegraphics[width=0.8\columnwidth]{\figdir/Math/approxi_proof.png}
+%   \includegraphics[width=0.8\columnwidth]{\figdir/Math/approxi_proof.png}
     \caption{Relationship between the conditional probability $p(j|i)$ \ref{eq:flux_conditional_prob} which is measured in the data and approximate functional form Eq.
@@
 
-The \SGNS{} model produces an effective distnace from mobility which can be visualized by projecting the embedding space into two dimensions using UMAP~\autocite{mcinnes2018umap} (Fig.~\ref{fig:projection}a).
+Word embeddigns produces an effective distnace from mobility which can be visualized by projecting the embedding space into two dimensions using UMAP~\autocite{mcinnes2018umap} (Fig.~\ref{fig:projection}a).
 Overall, organizations are clustered by geography, according to the nations in which they are location;

### 2020-03-05 paper/current/main.tex
revise_math_part

--- 2020-03-04 paper/current/main.tex
@@
 In the case of scientific co-affiliation, all movements are without direction (symmetric), meaning that  $T_{ij} = T_{ji}$.
-Let's denote $\mathpzc{N}_i$ as the neighborhood set of organization i, which are organizations with non-zero co-affiliation to organization i.
+Let's denote $N$ as set of organizations in the data.
 Then, the total flux to or from $i$ can be written as
@@
 \begin{equation}
-    \mu_{i} = \sum_{k\in\mathpzc{N}_i} t_{ik} \propto M_i
+    \mu_{i} = \sum_{k \in N} T_{ik} \propto M_i
 \end{equation}
@@
 \begin{equation}
-    p(j|i) \propto \frac{{\mu_j}\exp(\cos(v_i,v_j)}{\sum_{k\in\mathpzc{N}_i} {\mu_k}\exp(\cos(v_i,v_k))}
+    p(j|i) \propto \frac{{\mu_j}\exp(\cos(v_i,v_j)}{\sum_{k \in N} {\mu_k}\exp(\cos(v_i,v_k))}
 \end{equation}
@@
     \label{eq:real_embedding_relationship}
-    p(j|i) \propto \frac{\exp(\cos(v_j, v_i))}{\sum_{k\in\mathpzc{N}_i} \exp(\cos(v_k,v_i))}
+    p(j|i) \propto \frac{\exp(\cos(v_j, v_i))}{\sum_{k \in N} \exp(\cos(v_k,v_i))}
 \end{equation}
@@
     \centering
-    \includegraphics[width=0.8\columnwidth]{\figdir/Math/approxi_proof.png}
+    \includegraphics[width=0.8\columnwidth]{\figdir/Math/use_all_log.pdf}
     \caption{Relationship between the conditional probability $p(j|i)$ \ref{eq:flux_conditional_prob} which is measured in the data and approximate functional form Eq.
@@
 where $v_w$ and $v'_w$ are ``input'' and ``output'' vector representations of each word in the vocabulary.
-With facts that the denominator is not calculated entirely in the negative sampling strategies and the cosine similarity of in-vectors is used as a measure of affinity in general, Eq.
+With facts that the cosine similarity of in-vectors is used as a measure of affinity in general, Eq.
 \ref{eq:skipgram_conditional_expanded} and Eq.
-\ref{eq:real_embedding_relationship} share a similar functional form (or Eq.~\ref{eq:real_embedding_relationship} is a special case of Eq.
-~\ref{eq:skipgram_conditional_expanded}).
+\ref{eq:real_embedding_relationship} share a similar functional form, or exact same if vectors are normalized.
 

### 2020-03-05 paper/current/main.tex
add_description_on_new_figure_and _update_big_figure

@@
 
-with the hypothesis that a similar fraction of the scholars are mobile in each organization. Then, our gravity model can be written with only terms from mobility data,
+with the hypothesis that a similar fraction of the scholars are mobile in each organization.
+It can be checked in Fig.~\ref{fig:math_part}a.
+Then, our gravity model can be written with only terms from mobility data,
 
@@
     \label{eq:sum of the conditional probabiitliy}
-    \sum_{j\in\mathpzc{N}_i} p(j|i) = 1
+    \sum_{j \in N} p(j|i) = 1
 \end{equation}
@@
 
-We can check the evidence that Eq.\ref{eq:real_embedding_relationship} is a good approximation functional form of is $p(i|j)$ in Fig.
-\ref{fig:real_embedding_relationship}, as high values of flow correspond to high Eq.\ref{eq:real_embedding_relationship} values.
+We can check the evidence that Eq.\ref{eq:real_embedding_relationship} is a good approximation functional form of is $p(i|j)$ in Fig.~\ref{fig:math_part}b, as high values of flow correspond to high Eq.\ref{eq:real_embedding_relationship} values.
 
@@
     \includegraphics[width=0.8\columnwidth]{\figdir/Math/use_all_log.pdf}
-    \caption{Relationship between the conditional probability $p(j|i)$ \ref{eq:flux_conditional_prob} which is measured in the data and approximate functional form Eq.
+    \caption{
+    \textbf{a}.   Relationship between $M_i$ and $\mu_i$.
+    \textbf{b}.
+Relationship between the conditional probability $p(j|i)$, Eq.
+\ref{eq:flux_conditional_prob} which is measured in the data and approximate functional form Eq.
 \ref{eq:real_embedding_relationship}}.
-    \label{fig:real_embedding_relationship}
+    \label{fig:math_part}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=\textwidth]{\figdir/Projection/big_embedding_picture.png}
+	\includegraphics[width=\textwidth]{\figdir/Projection/big_embedding_picture.pdf}
 	\caption{

### 2020-03-05 paper/current/main.tex

@@
 %% Distance calculations
-We calculate $f_{ij}$, the pairwise number of co-affiliations between organizations, calculated as the number of co-occurrences of organizations within author co-affiliation trajectories. 
-For example, $f_{ij} = 10$ indicates that ten authors were co-affiliated with both organization $i$ and $j$ between 2008 and 2019, as evidenced from their publications. 
-In contrast to traditional mobility studies, all co-affiliations are symmetric, meaning that $f_{ij} = f_{ji}$.
+We calculate $T_{ij}$, the pairwise number of co-affiliations between organizations, calculated as the number of co-occurrences of organizations within author co-affiliation trajectories. 
+For example, $T_{ij} = 10$ indicates that ten authors were co-affiliated with both organization $i$ and $j$ between 2008 and 2019, as evidenced from their publications. 
+In contrast to traditional mobility studies, all co-affiliations are symmetric, meaning that $T_{ij} = T_{ji}$.
 
@@
 
-We model the flux of authors between organizations, $f_{ij}$, using the gravity law. 
+We model the flux of authors between organizations, $T_{ij}$, using the gravity law. 
 the gravity law of mobility loosely derives from the physical law of gravity, whereby the attraction between two objects is a function of their mass and the distance between them.
 Given its simplicity and flexibility, this formulation and variants have proven incredibly useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
-Following the gravity law, the expected flux $\widetilde{f_{ij}}$ between two organizations is defined as follows,
+Following the gravity law, the expected flux $\hat{T_{ij}}$ between two organizations is defined as follows,
 
@@
 	\label{eq:gravity_basic}
-	\widetilde{f_{ij}} = C*m_{i}m_{j}*f(r_{ij})
+	\hat{T_{ij}} = Cm_{i}m_{j}f(r_{ij})
 \end{equation}
@@
 	\label{eq:linear_flux_geo}
-	\ln(\frac{f_{ij}}{m_im_j}) = \ln(C)  - \alpha \ln(g_{ij})
+	\ln(\frac{T_{ij}}{m_im_j}) = \ln(C)  - \alpha \ln(g_{ij})
 \end{equation}
@@
 	\label{eq:linear_flux_emb}
-	\ln(\frac{f_{ij}}{m_im_j}) = \ln(C) - \beta d_{ij}
+	\ln(\frac{T_{ij}}{m_im_j}) = \ln(C) - \beta d_{ij}
 \end{equation}
 
-where $f_{ij}$ is the real flux from dataset. The gravity law of mobility is known to be sensitive to the case where $f_{ij} = 0$, or zero movement between organizations. 
+where $T_{ij}$ is the real flux from dataset. The gravity law of mobility is known to be sensitive to the case where $T_{ij} = 0$, or zero movement between organizations. 
 Here, non-zero flows account for only 4.2 percent of all possible pairs of  the 6,580 organizations represented in the embedding.

### 2020-03-06 paper/current/main.tex
Plot prestige rank with and without included axis points

@@
 
-When scientists move, so does their knowledge, and for scientific mobility, like all human movement, distance matters. 
+When scientists move, they bring their knowledge with them.
+For scientific mobility, like all human movement, distance matters.
 However, how exactly do we measure the distance between two places?
-Although many alternative ways to quantify the distance~\autocite{boschma2005proximity} exist, geographic distance is an unambiguous and foundational quantity for the distance.
+Although many alternative ways to quantify the distance~\autocite{boschma2005proximity} exist, geographic distance remains an unambiguous and foundational quantity for the distance.
 In turn, models of human mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation models ~\autocite{simini2012universal}, rely almost exclusively on geographic distance, yet, geographic distance fails to capture historical, linguistic, cultural, and cognitive proximity.
@@
 
-Where the flux, or number of authors co-affiliated with two organizations during the time period $T_{ij}$, increases with the organization's sizes, $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+Where the flux, $T_{ij}$, or number of authors co-affiliated with a pair organizations during the time period increases with the organization's sizes, $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
 We consider two distances, the geographic distance between the organizations as a baseline, and the \textit{embedding distance} defined as the cosine distance between the organization's vector in the trained embedding space.
-We argue that the performance of a distance measure can be observed from their ability to explain expected mobility between organizations, as well as to predict flux using the gravity model. 
-For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function. selected as the best performing for each case.
+We argue that the performance of a distance measure can be observed from their ability to explain expected mobility between organizations and to make predictions using the gravity model.
+For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (ref SI.XYZ).
 
@@
 The effective distance estimated by our embedding model explains and predicts scientific mobility best.
-Embedding distance ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) is more than twice that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
-This pattern holds for the variance of domestic (Fig.~\ref{fig:supp:gravity_correlation}c) and international mobility flows (Fig.~\ref{fig:supp:gravity_correlation}d). 
+The amount of variance explained by embedding distance ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) is more than twice that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
+This pattern holds for the variance of only domestic (Fig.~\ref{fig:supp:gravity_correlation}c) and international mobility flows (Fig.~\ref{fig:supp:gravity_correlation}d).
 After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance globally (Fig.~\ref{fig:gravity_performance}c--d) and for domestic (Fig.~\ref{fig:supp:gravity_correlation}e--f) and international mobility(Fig.~\ref{fig:supp:gravity_correlation}g--h).
-Similarly, embedding ``diffusion'' distance outperforms distances derived from calculating personalized-page rank scores on the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+Similarly, embedding distance outperforms ``diffusion''  distances such as those derived from calculating personalized-page rank scores on the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
 Geographic distance alone is a poor tool for understanding international scientific mobility---rather, by learning a distance directly from the data, it is possible to better explain, and better predict flux between organizations.
@@
 		Black dots are mean flux across binned distances.
+		Error bars are 99\% confidence intervals.
 		Color indicates frequency of organization pairs within each hex bin.
@@
 		Box color corresponds to the degree to which the distribution overlaps $x = y$.
-		\textbf{e-f.} Predictions made using model parameters learned from subset of same-country organization pairs. 
+		``Err'' is calculated as the root-mean squared error between the actual and predicted values.
+		\textbf{e-f.} Predictions made using model parameters learned from subset of domestic (within-country) organization pairs.
 		Embedding distance outperforms those made for geographic distance.
-		\textbf{g-h.} Embedding distance also outperforms geographic distance when predicting flux using model parameters estimated from only pairs of organizations in different countries. 
+		\textbf{g-h.} Embedding distance also outperforms geographic distance when predicting flux using model parameters estimated from only international mobility (across-country organization pairs).
 		Predictions are not meaningfully different if estimates are learned on all pairs of organizations (Fig. \ref{fig:supp:gravity_prediction_subsets}).
@@
 		\textbf{a.} Spearman correlation (n = 143) between Times prestige rank and SemAxis rank, by the number of high and bottom-ranked (geographically matched) universities aggregated to form the poles.
+		Black points show spearman correlation using all organizations; white points show correlation using only universalizes not aggregated in the poles. 
 		More universities improves performance, but quickly saturates after around five universities.

### 2020-03-06 workflow/scripts/GetAggregatePrestigeAxisTests.R

@@ -79,7 +79,7 @@ agg <- data.table::rbindlist(lapply(SEMAXIS_FILES, function(path) {
                              data=subset(data, included == F),
                              method = "spearman",
                              continuity = FALSE,
-                             conf.level = 0.95)
+                             conf.level = 0.99)
 
   # Build dataframe, extracting relevant fields from the filename
   df <- data.frame(

### 2020-03-08 paper/current/main.tex
Add plots for alternative gravity models

@@
 We argue that the performance of a distance measure can be observed from their ability to explain expected mobility between organizations and to make predictions using the gravity model.
-For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (ref SI.XYZ).
+For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_emb_bymodel} and Fig.~\ref{fig:supp:predict_geo_bymodel}).
 
@@
 After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance globally (Fig.~\ref{fig:gravity_performance}c--d) and for domestic (Fig.~\ref{fig:supp:gravity_correlation}e--f) and international mobility(Fig.~\ref{fig:supp:gravity_correlation}g--h).
-Similarly, embedding distance outperforms ``diffusion''  distances such as those derived from calculating personalized-page rank scores on the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+Similarly, embedding distance outperforms ``diffusion''  distances such as those derived from calculating personalized-page rank scores (see supporting materials) on the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
 Geographic distance alone is a poor tool for understanding international scientific mobility---rather, by learning a distance directly from the data, it is possible to better explain, and better predict flux between organizations.
@@
 % S1 TEXT
-\newpage
 \paragraph*{S1 Text}
@@
 
-\newpage
+%
+% Figure - Geographic predictions, by model
+%
+\begin{figure}[p!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance_geo_bymodel.pdf}
+	\caption{
+		\textbf{For geographic distance, the power-decay gravity model is better.}
+		Predictions of flux between organization pairs made using geographic distance the exponential gravity model (top), and the power-law decay model (bottom). 
+		Boxplots show distribution of actual flux for binned values of predicted flux.
+		Box color corresponds to the degree to which the distribution overlaps $x = y$.
+		Shown using all pairs of organization (\textbf{a-b}), domestic (\textbf{c-d}), and international only (\textbf{e-f}) mobility. 
+		The power-decay model outperforms the exponential gravity model.
+	}
+	\label{fig:supp:predict_geo_bymodel}
+\end{figure}
+
+%
+% Figure - Embedding predictions, by model
+%
+\begin{figure}[p!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance_emb_bymodel.pdf}
+	\caption{
+		\textbf{For embedding distance, the exponential gravity model is better.}
+		Predictions of flux between organization pairs made using embedding distance the exponential gravity model (top), and the power-law decay model (bottom). 
+		Boxplots show distribution of actual flux for binned values of predicted flux.
+		Box color corresponds to the degree to which the distribution overlaps $x = y$.
+		Shown using all pairs of organization (\textbf{a-b}), domestic (\textbf{c-d}), and international only (\textbf{e-f}) mobility. 
+		The exponential gravity model out-performs the power-decay model. 
+	}
+	\label{fig:supp:predict_emb_bymodel}
+\end{figure}
+
 %

### 2020-03-08 paper/current/main.tex
Plot times ranking vs. leiden ranking correlation

@@
 SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities is strongly correlated with the Times Ranking ($\rho = 0.46$).
-For reference, SemRank achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking mean-normalized citation score ($\rho = 0.87$).
+For reference, SemRank achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking mean-normalized citation score ($\rho = 0.87$, Fig.~\ref{fig:supp:times_vs_leiden}).
 This suggests that \SGNS{} model, in addition to learning the latent geography of mobility, while capture more nuanced characteristics such as latent hierarchy in the axis of the embedding, which is fascinating characteristic of our approach.
@@
 %
+% Figure - Times Ranking vs. Leiden Ranking
+%
+\begin{figure}[hp!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/SemAxis/times_leiden_compare.pdf}
+	\caption{
+		\textbf{Correlation between Times and Leiden Ranking.}
+		Comparison between the Times and Leiden rankings of universities.
+		Here, the Leiden Ranking is operationalized as the mean normalized fractional citation impact for each university~\autocite{waltman2012leidenrankings}. 
+	  	PCC details the estimate from Spearman correlation between the two rankings.
+	}
+	\label{fig:supp:times_vs_leiden}
+\end{figure}
+
+%
 % Figure - SemAxis By State

### 2020-03-08 paper/current/main.tex
removed the \SGNS macro

@@
 % CUSTOM MACROS
-\def\SGNS{\textit{SGNS}}
 
@@
 
-This finding relates to the objective function of the \SGNS{} model.
+This finding relates to the objective function of the skip-gram model.
 The model attempts to maximize the average log probability of observing a target word in a sentence, $w_{t}$, given the words in the surrounding context window, $w_{t + k}$.
@@
 
-Hence, the \SGNS{} model can be an effective model for investigating any kind of mobility trajectory data, stemming from the mathematical relationship between it and the gravity model of mobility.
+Hence, the skip-gram word embedding model can be an effective model for investigating any kind of mobility trajectory data, stemming from the mathematical relationship between it and the gravity model of mobility.
 
@@
 
-In addition to learning geography, its clear that the \SGNS{} model is also encoding the latent prestige hierarchies of academic mobility.
+In addition to learning geography, its clear that the word embedding also encodes the latent prestige hierarchies of academic mobility.
 To test this, we derive a ranking using the prestige axis that we call \textit{SemRank}, and compare them to traditional university rankings.
@@
 For reference, SemRank achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking mean-normalized citation score ($\rho = 0.87$, Fig.~\ref{fig:supp:times_vs_leiden}).
-This suggests that \SGNS{} model, in addition to learning the latent geography of mobility, while capture more nuanced characteristics such as latent hierarchy in the axis of the embedding, which is fascinating characteristic of our approach.
+This suggests that word embeddings, in addition to learning the latent geography of mobility, while capture more nuanced characteristics such as latent hierarchy in the axis of the embedding, which is fascinating characteristic of our approach.
 
@@
 
-By learning a distance directly from the data, the \SGNS{} model successfully  and efficiently captures a robust measure of semantic distance between entities, all with existing tools and minor data processing.
+By learning a distance directly from the data, word embeddings successfully  and efficiently captures a robust measure of semantic distance between entities, all with existing tools and minor data processing.
 This methodology is broadly applicable to studies of mobility.
@@
 %% word2vec
-These mobility sentences are used as input to the standard skip-gram negative sampling (\SGNS) model, for word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec} .
+These mobility sentences are used as input to the standard skip-gram negative sampling model, for word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec} .
 In natural-language processing, word embeddings are used to construct dense vector-space representations of words and phrases, in which distance relationships between words correspond to a notion of semantic distance.
@@
 %% Word2vec parameters and training procedure
-The \SGNS{} model has several tunable hyper-parameters, including the size of the learned vectors, the size of the token window  considered when training, the minimum frequency threshold for including an organization, and the number of iterations.
+The skip-gram model has several tunable hyper-parameters, including the size of the learned vectors, the size of the token window  considered when training, the minimum frequency threshold for including an organization, and the number of iterations.
 We iterate through several values of vector size and window size, repeating analysis for each combination.
@@
 this yields 6,580, or 76 percent of all organizations.
-We iterate the \SGNS{} training for five epochs over all mobility sentences.
-All word embeddings are trained using the \textit{gensim} python implementation of the \SGNS{} \textit{word2vec} model.
+We iterate the skip-gram training for five epochs over all mobility sentences.
+All word embeddings are trained using the \textit{gensim} python implementation of the skip-gram \textit{word2vec} model.
 We visualize embeddings by projecting into two dimensions using UMAP~\autocite{mcinnes2018umap}.

### 2020-03-08 paper/current/main.tex

--- 2020-03-08 paper/current/main.tex
@@
 We argue that the performance of a distance measure can be observed from their ability to explain expected mobility between organizations and to make predictions using the gravity model.
-For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_emb_bymodel} and Fig.~\ref{fig:supp:predict_geo_bymodel}).
+For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (ref SI.XYZ).
 
@@
 After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance globally (Fig.~\ref{fig:gravity_performance}c--d) and for domestic (Fig.~\ref{fig:supp:gravity_correlation}e--f) and international mobility(Fig.~\ref{fig:supp:gravity_correlation}g--h).
-Similarly, embedding distance outperforms ``diffusion''  distances such as those derived from calculating personalized-page rank scores (see supporting materials) on the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+Similarly, embedding distance outperforms ``diffusion''  distances such as those derived from calculating personalized-page rank scores on the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
 Geographic distance alone is a poor tool for understanding international scientific mobility---rather, by learning a distance directly from the data, it is possible to better explain, and better predict flux between organizations.
@@
 % S1 TEXT
+\newpage
 \paragraph*{S1 Text}
@@
 
-%
-% Figure - Geographic predictions, by model
-%
-\begin{figure}[p!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance_geo_bymodel.pdf}
-	\caption{
-		\textbf{For geographic distance, the power-decay gravity model is better.}
-		Predictions of flux between organization pairs made using geographic distance the exponential gravity model (top), and the power-law decay model (bottom). 
-		Boxplots show distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps $x = y$.
-		Shown using all pairs of organization (\textbf{a-b}), domestic (\textbf{c-d}), and international only (\textbf{e-f}) mobility. 
-		The power-decay model outperforms the exponential gravity model.
-	}
-	\label{fig:supp:predict_geo_bymodel}
-\end{figure}
-
-%
-% Figure - Embedding predictions, by model
-%
-\begin{figure}[p!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance_emb_bymodel.pdf}
-	\caption{
-		\textbf{For embedding distance, the exponential gravity model is better.}
-		Predictions of flux between organization pairs made using embedding distance the exponential gravity model (top), and the power-law decay model (bottom). 
-		Boxplots show distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps $x = y$.
-		Shown using all pairs of organization (\textbf{a-b}), domestic (\textbf{c-d}), and international only (\textbf{e-f}) mobility. 
-		The exponential gravity model out-performs the power-decay model. 
-	}
-	\label{fig:supp:predict_emb_bymodel}
-\end{figure}
-
+\newpage
 %
@@
 		\textbf{a.} Spearman correlation (n = 143) between Times prestige rank and SemAxis rank, by the number of high and bottom-ranked (geographically matched) universities aggregated to form the poles.
-		Black points show spearman correlation using all organizations; white points show correlation using only universalizes not aggregated in the poles. 
 		More universities improves performance, but quickly saturates after around five universities.

### 2020-03-09 paper/current/main.tex
abstract_and_introduction

--- 2020-03-08 paper/current/main.tex
@@
 Here, we demonstrate a data-driven approach of learning an effective distance that encodes the latent structure of mobility using a neural embedding model~\autocite{mikolov2013word2vec} trained on mobility traces sourced from the publications of disambiguated authors from the Web of Science database between 2008 and 2019.
-Distance between vectors in the learned embedding space explain and predict mobility between organizations better than  geographic distance or network distance.
-We argue that such power emerges from an underlying connection between embeddings and the gravity model.
+Distance between vectors in the learned embedding space explains and predicts mobility between organizations better than  geographic distance or network distance.
+We argue that such power emerges from an underlying connection between the neural embedding model and the gravity model.
 In addition to geography, these embeddings also capture latent religious, cultural, social, and linguistic, and even prestige of organizations at multiple levels of granularity.
-With this approach, we can learn scalable, dense, and meaningful vector representations of scientific mobility directly from the data using a methodology that can be easily applied to all kinds of mobility.
+With this approach, we can learn scalable, dense, and meaningful vector representations of scientific mobility directly from the data using a methodology that can be easily applied to all kinds of mobility data.
 \end{abstract}
@@
 
-It has been demonstrated that neural embedding models preserves semantic relationships between words in a dense, continuous and meaningful low-dimensional vector representation~\autocite{mikolov2013word2vec}, and have been applied to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
+It has been demonstrated that neural embedding model preserves semantic relationships between words in a dense, continuous and meaningful low-dimensional vector representation~\autocite{mikolov2013word2vec}, and has been applied to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
 In addition to encoding latent structure, this approach is computationally efficient, scalable for large datasets, robust to noise, and allows for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.
-Here, we propose a neural embedding model as an effective means of encoding an effective measure of distance using massive trajectory data.
+Here, we propose a neural embedding model as an efficient means of encoding an effective measure of distance using massive trajectory data.
 
 As scientist's careers progress, they move between organizations or pick up additional affiliations, forming co-affiliation or \textit{mobility trajectories} that can be derived from their publication histories~\autocite{robinson2019mobility, sugimoto2017mostimpact}.
-By treating geo-located organizations analogously to words and trajectories analogously to sentences, we learn vector-space embedding of organizations using neural embedding (Fig.~\ref{fig:methods:mobility_sentence}).
+By treating geo-located organizations analogously to words and trajectories analogously to sentences, we learn vector-space embedding of organizations using a neural embedding method(Fig.~\ref{fig:methods:mobility_sentence}).
 The resulting vector of organizations is representation that the \textit{cosine distance} between vectors represents the distance in the landscape of scientific mobility.
@@
 
-Where the flux, $T_{ij}$, or number of authors co-affiliated with a pair organizations during the time period increases with the organization's sizes, $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+Where the \textit{expected flux}, $\hat{T_{ij}}$, or expected number of authors co-affiliated with a pair organizations during the time period increases with the organization's sizes, $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
 We consider two distances, the geographic distance between the organizations as a baseline, and the \textit{embedding distance} defined as the cosine distance between the organization's vector in the trained embedding space.

### 2020-03-09 paper/current/main.tex
simple things

@@
 When scientists move, they bring their knowledge with them.
-For scientific mobility, like all human movement, distance matters.
+For scientific mobility, like all human movements, distance matters.
 However, how exactly do we measure the distance between two places?
@@
 For instance, Australia may be physically close to Indonesia, but in terms of language, history, and shared culture, they are essentially neighbors to geographically distant countries like the United Kingdom.
-Then, how can we quantify meaningful, useful distance between institutions, cities and countries?
+Then, how can we quantify meaningful, useful distance between institutions, cities, and countries?
 
@@
 
-It has been demonstrated that neural embedding model preserves semantic relationships between words in a dense, continuous and meaningful low-dimensional vector representation~\autocite{mikolov2013word2vec}, and has been applied to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
+It has been demonstrated that the neural embedding model preserves semantic relationships between words in a dense, continuous and meaningful low-dimensional vector representation~\autocite{mikolov2013word2vec}, and has been applied to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
 In addition to encoding latent structure, this approach is computationally efficient, scalable for large datasets, robust to noise, and allows for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.
@@
 		Error bars are 99\% confidence intervals.
-		Color indicates frequency of organization pairs within each hex bin.
+		Color indicates the frequency of organization pairs within each hex bin.
 		\textbf{c-d.} Predictions of flux between organization pairs made using embedding distance outperform those made using geographic distance.
@@
 		Box color corresponds to the degree to which the distribution overlaps $x = y$.
-		``Err'' is calculated as the root-mean squared error between the actual and predicted values.
-		\textbf{e-f.} Predictions made using model parameters learned from subset of domestic (within-country) organization pairs.
+		``Err'' is calculated as the root-mean-squared error between the actual and predicted values.
+		\textbf{e-f.} Predictions made using model parameters learned from a subset of domestic (within-country) organization pairs.
 		Embedding distance outperforms those made for geographic distance.
@@
 \begin{equation}
-    \cos(v_j, v_i) = \frac{v_j \cdot v_i}{|v_j||v_i|}
+    \cos(v_i, v_j) = \frac{v_i \cdot v_j}{\Vert v_j \Vert \Vert v_i  \Vert}
 \end{equation}
@@
 
-This finding relates to the objective function of the skip-gram model.
+This finding relates to the objective function of the neural embedding model.
 The model attempts to maximize the average log probability of observing a target word in a sentence, $w_{t}$, given the words in the surrounding context window, $w_{t + k}$.
@@
 
-Hence, the skip-gram word embedding model can be an effective model for investigating any kind of mobility trajectory data, stemming from the mathematical relationship between it and the gravity model of mobility.
+Hence, the neural embedding model can be an effective model for investigating any kind of mobility trajectory data, stemming from the mathematical relationship between it and the gravity model of mobility.
 
@@
 		Color indicates the continent.
-		We re-project subsets of organizational vectors to uncover more complex local structure.
+		We re-project subsets of organizational vectors to uncover more complex local structures.
 		\textbf{b.} Re-projection of organizational vectors roughly corresponding to West-Asian, Southeast Asian, and South Asian countries.
@@
 By embedding co-affiliation trajectories, we aim to learn a dense vector for every organization where distance between vectors relates to the tendency for two organizations to co-occur in a token window around the target term in the same career trajectory.
-Vectors are learned by training a neural network to optimize the prediction of so-called context term given a target, in our case using one organization to predict the others appearing in the same co-affiliation trajectory.
+Vectors are learned by training a neural network to optimize the prediction of the so-called context term given a target, in our case using one organization to predict the others appearing in the same co-affiliation trajectory.
 The hidden layer of the trained neural network is used as the
@@
 Given its simplicity and flexibility, this formulation and variants have proven incredibly useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
-Following the gravity law, the expected flux $\hat{T_{ij}}$ between two organizations is defined as follows,
+Following the gravity law, the \textit{expected flux} $\hat{T_{ij}}$ between two organizations is defined as follows,
 

### 2020-03-09 workflow/scripts/Plot2DSemAxis.R
remove non-government orgs from the sector plots

@@ -45,6 +45,8 @@ option_list = list(
               help="Name of the state to highlight"),
   make_option(c("--types"), action="store", default=NA, type='character',
               help="Path to file containing org types"),
+  make_option(c("--exclude"), action="store", default=NA, type='character',
+              help="Path to file containing orgs to exclude due to being mis-classified"),
   make_option(c("--sector"), action="store", default=NA, type='character',
               help="Name of sector: Teaching, Government, or Institute"),
   make_option(c("-o", "--output"), action="store", default=NA, type='character',
@@ -98,8 +100,11 @@ if (opt$overall == TRUE) {
   ###
   if (!is.na(opt$sector)) {
     org_types <- read_csv(opt$types, col_types = cols())
+    orgs_excluded <- read_csv(opt$exclude, col_types = cols())
+
     plotdata <- plotdata %>%
       left_join(org_types, by = "org_type") %>%
+      anti_join(orgs_excluded, by = "cwts_org_no") %>%
       filter(org_type_simplified == opt$sector | org_type_code == "U") %>%
       mutate(
         highlight = ifelse(org_type_simplified %in% ORG_TYPES, org_type_simplified, "Others"),

### 2020-03-09 paper/current/main.tex

@@
 When scientists move, they bring their knowledge with them.
-For scientific mobility, like all human movements, distance matters.
+When it comes to mobility, whether scientific or more otherwise, distance matters.
 However, how exactly do we measure the distance between two places?
@@
 In addition to encoding latent structure, this approach is computationally efficient, scalable for large datasets, robust to noise, and allows for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.
-Here, we propose a neural embedding model as an efficient means of encoding an effective measure of distance using massive trajectory data.
+Here, we propose a neural embedding model as an efficient means of encoding an effective measure of distance using large-scale data on mobility trajectories.
 
 As scientist's careers progress, they move between organizations or pick up additional affiliations, forming co-affiliation or \textit{mobility trajectories} that can be derived from their publication histories~\autocite{robinson2019mobility, sugimoto2017mostimpact}.
-By treating geo-located organizations analogously to words and trajectories analogously to sentences, we learn vector-space embedding of organizations using a neural embedding method(Fig.~\ref{fig:methods:mobility_sentence}).
-The resulting vector of organizations is representation that the \textit{cosine distance} between vectors represents the distance in the landscape of scientific mobility.
+By treating geo-located organizations analogously to words and trajectories analogously to sentences, we learn vector-space embedding of organizations using a neural embedding method (Fig.~\ref{fig:methods:mobility_sentence}).
+In the resulting embedding, each organization corresponds to a vector, and the \textit{cosine distance} between vectors represents the distance in the landscape of scientific mobility.
 
@@
 
-Why does the word embedding model, a tool designed for natural language processing, produce such a reasonable distance that models gravity relationships between organizations?
-We find evidence of a theoretical connection between the two models, one that makes the skip-gram model applicable to many other forms of mobility trajectory.
+Why does the word embedding model, originally designed for natural language processing, produce a reasonable distance that models gravity relationships between organizations?
+We find evidence of a theoretical connection between the two models, one that makes the skip-gram model applicable to embedding many forms of mobility trajectories.
 
@@
 
-In addition to learning geography, its clear that the word embedding also encodes the latent prestige hierarchies of academic mobility.
-To test this, we derive a ranking using the prestige axis that we call \textit{SemRank}, and compare them to traditional university rankings.
+In addition to capturing geography, the word embedding also encodes the well-known latent prestige hierarchies of academic mobility~\autocite{deville2014career, clauset2015hierarchy}.
+We derive a ranking using the prestige axis that we call \textit{SemRank}, and compare them to traditional university rankings.
 SemRank is defined from the position of organizations along the prestige axis, with the top ranked being the furthest towards the \textit{Elite} end of the axis.
@@
 This correlation is robust with the number of organizations used to define the axes (Fig.
-SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities is strongly correlated with the Times Ranking ($\rho = 0.46$).
-For reference, SemRank achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking mean-normalized citation score ($\rho = 0.87$, Fig.~\ref{fig:supp:times_vs_leiden}).
-This suggests that word embeddings, in addition to learning the latent geography of mobility, while capture more nuanced characteristics such as latent hierarchy in the axis of the embedding, which is fascinating characteristic of our approach.
+SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities is strongly correlated with the Times Ranking ($\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
+For reference, SemRank achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking~\autocite{waltman2012leidenrankings}, a common and bibliometrically informed university ranking ($\rho = 0.87$, Fig.~\ref{fig:supp:times_vs_leiden}).
+This suggests that word embeddings, in addition to learning the latent geography of mobility, also capture more nuanced characteristics such as latent hierarchy in the axis of the embedding, which is a unique and fascinating characteristic of this approach.
 
@@
 
-By learning a distance directly from the data, word embeddings successfully  and efficiently captures a robust measure of semantic distance between entities, all with existing tools and minor data processing.
+By learning a distance directly from data, word embeddings successfully  and efficiently captures a robust measure of semantic distance between entities, all with existing tools and minor data processing.
 This methodology is broadly applicable to studies of mobility.
 Its success also points to the broad applicability of ideas from language and graph embedding techniques such as GLoVE~\autocite{pennington2014glove}, BERT~\autocite{devlin2018bert}, hyperbolic embeddings~\autocite{nickel2017poincare, linzhuo2020hyperbolic}, and persona2vec () to other problem domains, such as the social sciences.
-In addition to their technical advantages and the unique suite of methodologies they allow, they are also  readily transferable and can be trivially fit into a diverse array of analyses.
+In addition to their technical advantages and their unique suite of analytical tools, they are also readily transferable and can be trivially fit into a diverse array of analyses.
 
-Globally, science has experienced many changes, from gradual globalization to the more sudden 2017 U.S. travel bans.
+Globally, science has experienced many changes, from gradual globalization~\autocite{czaika2018globalisation} to the more sudden 2016 Brexit and 2017 U.S. travel bans.
 The consequences of these changes are far-reaching, and how nations respond to them will shape the future of the scientific enterprise~\autocite{chinchilla2018travelban, wagner2017open, sugimoto2017mostimpact, whetsell2019democracy}.

### 2020-03-31 paper/current/main.tex
Updating abstract

@@
 However, amid a globalizing scientific enterprise~\autocite{czaika2018globalisation}, geographic distance is losing its relevance for understanding mobility, whereas other abstract notions of distance~\autocite{boschma2005proximity} pose practical and theoretical challenges.
-Accordingly, the complexity of factors shaping global scientific mobility~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics} necessitates simplified models for reasoning about and crafting effective policy.
-Here, we demonstrate a data-driven approach of learning an effective distance that encodes the latent structure of mobility using a neural embedding model~\autocite{mikolov2013word2vec} trained on mobility traces sourced from the publications of disambiguated authors from the Web of Science database between 2008 and 2019.
+%Accordingly, the complexity of factors shaping global scientific mobility~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics} necessitates simplified models for reasoning about and crafting effective policy.
+Leveraging neural embedding~\autocite{mikolov2013word2vec}, we demonstrate a data-driven approach for learning a dense, meaningful, and useful vector-space representation of organizations that encodes the latent, complex, and multi-faceted structure of mobility.
+We train scientific mobility embedding using the organizational trajectories derived from the publications of disambiguated authors from the Web of Science database between 2008 and 2019.
 Distance between vectors in the learned embedding space explains and predicts mobility between organizations better than  geographic distance or network distance.

### 2020-03-31 paper/current/main.tex
revising introduction

@@
 %Accordingly, the complexity of factors shaping global scientific mobility~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics} necessitates simplified models for reasoning about and crafting effective policy.
-Leveraging neural embedding~\autocite{mikolov2013word2vec}, we demonstrate a data-driven approach for learning a dense, meaningful, and useful vector-space representation of organizations that encodes the latent, complex, and multi-faceted structure of mobility.
+Leveraging the neural embedding model~\autocite{mikolov2013word2vec}, we demonstrate a data-driven approach for learning a vector-space representation that encodes an effective distance between places and captures the latent and multi-faceted structure of mobility.
 We train scientific mobility embedding using the organizational trajectories derived from the publications of disambiguated authors from the Web of Science database between 2008 and 2019.
@@
 
-When scientists move, they bring their knowledge with them.
-When it comes to mobility, whether scientific or more otherwise, distance matters.
-However, how exactly do we measure the distance between two places?
+When scientists move, they bring their knowledge with them, and so understanding the flows of scientists allows us to understand the flow of knowledge around the world. 
+However, given its complexity~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, new approaches are needed to make sense of landscape of global scientific mobility.
+A basic component of mobility is distance--people are more likely to move nearby than to cross continents.
 Although many alternative ways to quantify the distance~\autocite{boschma2005proximity} exist, geographic distance remains an unambiguous and foundational quantity for the distance.
-In turn, models of human mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation models ~\autocite{simini2012universal}, rely almost exclusively on geographic distance, yet, geographic distance fails to capture historical, linguistic, cultural, and cognitive proximity.
-For instance, Australia may be physically close to Indonesia, but in terms of language, history, and shared culture, they are essentially neighbors to geographically distant countries like the United Kingdom.
+In turn, models of human mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation models ~\autocite{simini2012universal}, rely almost exclusively on geographic distance.
+However, distance is not always so straightforward as simple geography. 
+Geographic distance fails to capture the host of historical, linguistic, cultural, and cognitive distance that also drive mobility. 
+For instance, Australia may be physically close to Indonesia, but in terms of language, history, and shared culture, they are essentially neighbors to the United Kingdom.
 Then, how can we quantify meaningful, useful distance between institutions, cities, and countries?
 
-% Let's rephease and reuse to somewhere else:)
-%Encoding distance in a way that considers not just geography, but also historical, linguistic, cultural, and cognitive proximity would improve our models and thus ability to reason about science and immigration policies.
-
+Here, we propose a neural embedding model as an efficient means of encoding an effective measure of distance using large-scale data on mobility trajectories.
 It has been demonstrated that the neural embedding model preserves semantic relationships between words in a dense, continuous and meaningful low-dimensional vector representation~\autocite{mikolov2013word2vec}, and has been applied to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
 In addition to encoding latent structure, this approach is computationally efficient, scalable for large datasets, robust to noise, and allows for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.
-Here, we propose a neural embedding model as an efficient means of encoding an effective measure of distance using large-scale data on mobility trajectories.
 
@@
 We use the trajectories of the three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
-We adopt the Gravity Model of mobility~\autocite{zipf1946gravity, barbosa2018human}, one of the most common and broadly applied mobility models~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} to assess how well the embedding captures mobility.
+We adopt the Gravity Model of mobility~\autocite{zipf1946gravity, barbosa2018human}, one of the most broadly applied mobility models~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} to assess how well the embedding captures mobility.
 After fitting the parameters of the gravity model, we use it to derive the \textit{expected flux} $\hat{T_{ij}}$ between organizations, defined as,
@@
 
-Where the \textit{expected flux}, $\hat{T_{ij}}$, or expected number of authors co-affiliated with a pair organizations during the time period increases with the organization's sizes, $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+Where the \textit{expected flux}, $\hat{T_{ij}}$, or expected number of authors co-affiliated with a pair organizations during the time period is proportional to the organization's sizes, $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
 We consider two distances, the geographic distance between the organizations as a baseline, and the \textit{embedding distance} defined as the cosine distance between the organization's vector in the trained embedding space.
@@
 Similarly, embedding distance outperforms ``diffusion''  distances such as those derived from calculating personalized-page rank scores (see supporting materials) on the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-Geographic distance alone is a poor tool for understanding international scientific mobility---rather, by learning a distance directly from the data, it is possible to better explain, and better predict flux between organizations.
+Geographic distance alone is a poor perspective for understanding international scientific mobility---rather, by learning a distance directly from the data, it is possible to better explain, and better predict flux between organizations.
 

### 2020-03-31 paper/current/main.tex
Updated section relating to figure 4

@@
 
-Word embeddigns produces an effective distnace from mobility which can be visualized by projecting the embedding space into two dimensions using UMAP~\autocite{mcinnes2018umap} (Fig.~\ref{fig:projection}a).
-Overall, organizations are clustered by geography, according to the nations in which they are location;
-however, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions at multiple scales.
+Given that embeddings capture effective distance between organizations, we can now examine the global structure of scientific mobility.
+Because the embeddings are defined in a high-dimensional space, we apply a widely-used dimensionality reduction technique (UMAP~\autocite{mcinnes2018umap}) to visualize the overall structure (Fig.~\ref{fig:projection}a).
+Globally, the effect of geography is conspicuous; organizations tend to form clusters based on their national affiliations and national clusters tend to be near their geographic neighbors. 
+At the same time, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions.
 
-Re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries related to geography and religion moving from majority-Muslim nations in the Middle East towards similarity-religious nations of Pakistan, Bangladesh, and Indonesia, and finally towards East-Asian nations with different religious majorities such as Vietnam, the Philippines, and Thailand.
+Re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries from majority-Muslim countries in the Middle East to South Asian countries of Pakistan, Bangladesh, and Indonesia, and finally towards Southeast-Asian nations with different religious majorities such as Vietnam, the Philippines, and Thailand.
 Linguistic and historical ties are also important.
-For example, we observe that Spanish-speaking and colonized Latin American nations (Mexico, Chile, Peru, etc.) are positioned near Spain, whereas Brazil is instead positioned nearer to Portugal (Fig.~\ref{fig:projection}c).
-Similarly, Algeria and Morocco, nations in close proximity to and with historic ties to France, and positioned near the French cluster of organizations (Fig.~\ref{fig:projection}a).
-These dynamics can manifest even within the same country.
-For example, organizations located within the french-speaking region of Quebec in Canada are positioned near the French cluster rather than Canada.
+For example, we observe that Spanish-speaking post-colonial Latin American nations (Mexico, Chile, Peru, etc.) are positioned near Spain, whereas Brazil is nearer to Portugal (Fig.~\ref{fig:projection}c).
+Similarly, Algeria and Morocco are near the French cluster (Fig.~\ref{fig:projection}a).
+Comparable structural patterns exist even within a single country.
+For example, organizations within Quebec in Canada are located near the French cluster rather than the rest of Canada.
 
-A unique characteristic of semantic mobility embeddings is the ability to capture structure at multiple scales of granularity.
-For example, just as the global embedding captures geographic structure between nations, so too does a projection or organizations in the United States reflect organizational structure based on states (Fig.~\ref{fig:projection}d).
+Just as the global embedding captures national-level geographic structure, so does a projection of organizations in the United States reflect organizational structure based on states (Fig.~\ref{fig:projection}d).
 By re-projecting at the state-level for Massachusetts (Fig.~\ref{fig:projection}e), we observe structure between urban Centers (Boston vs.
-Worcester), but also based on organization type (hospitals tend to be adjacent) and different university systems.
-Even though UMass Boston is located in Boston, it clusters near other universities in the UMass System, reflecting a relative lack of mobility between the two systems, even within the same state.
-Similar dynamics can be observed in many states (New York, California, etc.), such that prestigious university systems are separate from more regional ones (SI~?).
+Worcester), but also based on organization type (e.g., hospitals vs.
+universities) and university systems.
+Even though UMass Boston is located in Boston, it clusters near other universities in the UMass System rather than the typically more elite and research-focused universities in Boston, reflecting a relative lack of mobility between the two systems, even within the same state.
+Similar structures can be observed in many states (New York, California, etc.), such that prestigious university systems are separate from more regional ones (SI~TBD).
 
@@
 		\textbf{a.}
-		UMAP projection \autocite{mcinnes2018umap} of the entire embedding space reveals geographic clustering.
-		Each point corresponds to an organization.
-		Size indicates the size of the organization.
+		UMAP projection \autocite{mcinnes2018umap} of the embedding space reveals strong country-level clustering.
+		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019. 
 		Color indicates the continent.
-		We re-project subsets of organizational vectors to uncover more complex local structures.
-		\textbf{b.} Re-projection of organizational vectors roughly corresponding to West-Asian, Southeast Asian, and South Asian countries.
-		\textbf{c.} Re-projection of organizations in Spain, Portugal, and the Portuguese- and Spanish-speaking countries South and Central America.
-		\textbf{d.} Re-projection of organizations in the United States reveal geographic clustering based on state.
-		Color indicates Census Bureau-designated regions,
-		\textbf{e.} Re-projection of organizations in Massachusetts reveal clustering based on organizational sector, prestige.
-		Color indicates sector designation of organization.
+		\textbf{b.} Zooming into (re-projecting) the area containing countries in the Middle East and South and Southeast Asia shows a geographic and cultural gradient of country clusters. 
+		\textbf{c.} Similarly, zooming into the area organizations in Spain, Portugal, South and Central America show clustering by majority language group--Spanish and Portuguese.
+		\textbf{d.} Doing the same for organizations in the United States reveals geographic clustering based on state, roughly grouped by Census Bureau-designated regions,
+		\textbf{e.} Zooming in further on Massachusetts reveals clustering based on urban center (Boston, Worcester), organizational sector (hospitals vs.
+universities), and university systems and prestige (UMass system vs.
+Harvard, MIT, etc.).
 	}

### 2020-03-31 paper/current/main.tex
small paragraph change, fig 4

@@
 
-Re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries from majority-Muslim countries in the Middle East to South Asian countries of Pakistan, Bangladesh, and Indonesia, and finally towards Southeast-Asian nations with different religious majorities such as Vietnam, the Philippines, and Thailand.
+By learning and leveraging the embedding space, these complex national and regional relationships can be quantified and visualized.  
+For example, by re-projecting or \textit{zooming into} organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries from majority-Muslim countries in the Middle East to South Asian countries of Pakistan, Bangladesh, and Indonesia, and finally towards Southeast-Asian nations with different religious majorities such as Vietnam, the Philippines, and Thailand.
 Linguistic and historical ties are also important.

### 2020-03-31 paper/current/main.tex
revisions related to figure 5

@@
 
-\subsection*{Embeddings capture international relationships}
+We can also examine high-level structure by estimating aggregate embeddings of countries. 
+Namely, we calculate the representative vector of each country by averaging organization vectors within the given country.
+We then perform hierarchical clustering of nations that have at least 25 organizations represented in the embedding space, excluding the United States which has high similarity with most other countries (see Fig.
+\ref{fig:clustering}a).
+The identified six clusters roughly correspond to: East-Asian (orange), Scandinavian (dark purple), British Commonwealth (light purple), Central and Eastern European countries (light blue), and then two cluster diverse clusters with a mix of European, Latin American, and Mediterranean countries.
+Countries are either grouped geographically or by linguistic or historical ties.
 
-What latent information do embeddings of scientific mobility capture, beyond geography?
-We build on descriptive results to quantitatively assess the national factors captured in the learned vector-space.
-We calculate the representative vector of each country with averaging organization vectors within the given country, calculate pairwise cosine similarity, and perform hierarchical clustering (Fig.
-\ref{fig:clustering}a) of nations that have at least 25 organizations, excluding the United States which has high similarity with most other countries.
-
-Six country clusters were identified, reflecting a mixture of the regional, linguistic, historical clusters, with clusters consisting of East-Asian (orange), Scandinavian (dark purple), British Commonwealth (light purple), Central and Eastern European countries (light blue), and then two cluster diverse clusters with a mix of European, Latin American, and Mediterranean countries.
-When not defined by geography, clusters appear to be defined by linguistic and historical ties, as is the case for the commonwealth countries.
-There is a tendency that countries are grouped if they are in the same geographic region, if they are historically or culturally aligned, and if they share a similar language.
-
-We investigate the extent to which geography and language dictate the formation of clusters using \textit{CluSim}~\autocite{gates2019element}, a method that compares different groupings and, for hierarchical clustering, can adjust the relative importance of membership at different levels of the hierarchy with scaling parameter $r$, acting like a ``zooming lens''.
+We investigate the extent to which geography and language dictate the formation of clusters using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering by explicitly adjusting the relative importance of different levels of the hierarchy with scaling parameter $r$, acting like a ``zooming lens''.
 If $r$ is high, the similarity is based on the lower levels of the dendrogram, whereas when $r$ is low, similarity is based on higher levels.
 Fig.
-\ref{fig:clustering}b demonstrates that continent plays a major role at higher levels of clustering process (low $r$), and language family and then language explain the clustering process more at the lower levels (high $r$).
+\ref{fig:clustering}b demonstrates that continent plays a major role at higher levels of clustering process (low $r$), and language (family) explain the clustering more at the lower levels (high $r$).
 This suggests that geography, then language, are important factors contributing to the structure of international scientific mobility.

### 2020-03-31 paper/current/main.tex
Update figure 6 and related text

@@
 
+The results demonstrating embeddings' ability to capture various features governing mobility raise the question of whether they can also capture semantic axes analogously to word embeddings. 
+For instance, does the mobility embedding encode information about the prestige or universities?
 In addition to encoding national characteristics, the embedding also encodes domestic geography and latent hierarchy.
-We employ SemAxis~\autocite{an2018semaxis}, a tool utilizing the unique vector arithmetic of semantic embeddings, to project U.S. universities onto two defined axes.
-The first axis is geographic, defined using the mean vector of universities in California on one end, and Massachusetts on the other.
-The second axis relates instead to prestige.
+Employing the SemAxis approach~\autocite{an2018semaxis} we define two axes.
+The first is the California--Massachusetts axis defined by the mean vector of universities in California on one end, and in Massachusetts on the other. 
+The second axis is the low- to high- prestige axis;
+the elite end of the axis is defined as the top 20 U.S.
+universities according to the Times Ranking of World Universities, whereas the non-elite axis is defined as bottom-ranked and geographically matched (by U.S.
+census region) set of universities.
+A university projected onto the axis corresponds to their nearness to the mean vector defining each pole (Fig.~\ref{fig:semaxis}a).
+Generally, universities in Western states, such as Arizona (Fig.~\ref{fig:supp:semaxis_states}b) are nearer to the California end of the axis, whereas states in the Northeast such as New York (Fig.~\ref{fig:supp:semaxis_states}f) and Connecticut (Fig.~\ref{fig:supp:semaxis_states}e) are nearer the Massachusetts end.
+Universities geographically distance from both California and Massahcussets are less aligned with either, such as Texas (Fig.~\ref{fig:supp:semaxis_states}g)s and Florida (Fig.~\ref{fig:supp:semaxis_states}i).
+
 Universities hiring and mobility networks are known to exhbit latent pretige hierarchies ~\autocite{deville2014career, clauset2015hierarchy} that should be encoded in the embedding space.
-The elite end of the axis is defined as the top 20 U.S.
-universities according to the Times Ranking of World Universities, whereas the non-elite axis is defined as bottom-ranked geographically matched (by U.S.
-census region) set of universities.
-A university projected onto the axis corresponds to their nearness to the mean vector defining each pole.
-With a few exceptions, all universities in California are nearer the appropriate end of the axis than are Massachusetts universities, and \textit{vice versa} (Fig.~\ref{fig:semaxis}).
-Universities in bordering states, such as Arizona and Connecticut, are closer to the ends of the axis (Fig.~\ref{fig:supp:semaxis_states}b and Fig.~\ref{fig:supp:semaxis_states}e).
-Universities in new York are nearer to the Massachusetts end of the axis (Fig.~\ref{fig:supp:semaxis_states}f), whereas universities in Florida are less aligned to either (Fig.~\ref{fig:supp:semaxis_states}i).
+Accordingly, prestigious universities such as Stanford, Colombia, MIT, Harvard, and NYU, group towards the top of the axis.
+Universities at the bottom of this axis tend to be regional universities with lower national profiles.
 
-Prestigious universities, such as Stanford, Colombia, MIT, Harvard, and NYU, group towards the top of the axis.
-Universities at the bottom of this axis tend to be regional universities with lower national profiles, such as California State University Long Beach, University of West Florida, and Barry University.
-There are strong differences by state in terms of prestige---overall, universities in Massachusetts are nearer the \textit{Elite} end of the axis than are universities in Arizona, Connecticut, Pennsylvania, and Florida (Fig.~\ref{fig:supp:semaxis_states}).
-
-Once these axes are constructed using university rankings, we can even relate other types of organizations that wouldn't typically be fit onto university rankings.
+Once these axes are constructed using university rankings, we can even relate other types of organizations that would not typically be fit onto university rankings.
 For example, among Government institutions, we see that the U.S.
@@
 Department of Agriculture (Fig.~\ref{fig:supp:semaxis_sectors}a).
-Among research institutes, the most aligned with elite universities are typically those prestigious university-adjacent institutes such as the Whitehead Institute, the Broad Institute, and the Dana Faber institute (Fig.~\ref{fig:supp:semaxis_sectors}b); those institutes aligned with lowly-ranked universities tend to be ecological or agricultural institutes such as the Joseph W.
+Among research institutes, the most aligned with elite universities are typically those prestigious university-adjacent institutes such as the Whitehead Institute, the Broad Institute, and the Dana Faber institute (Fig.~\ref{fig:supp:semaxis_sectors}b); those institutes aligned with low-ranked universities tend to be ecological or agricultural institutes such as the Joseph W.
 Jones Ecological Research Center and the Louisiana Agriculture Center.
-Among teaching organizations, the top-ranked tend to be notable private liberal arts colleges such as Wellesley College and Carleton College, whereas community colleges and military colleges tend to be more aligned with lowly-ranked universities (Fig.~\ref{fig:supp:semaxis_sectors}c).
+Among teaching organizations, the top-ranked tend to be notable private liberal arts colleges such as Wellesley College and Carleton College, whereas community colleges and military colleges tend to be more aligned with low-ranked universities (Fig.~\ref{fig:supp:semaxis_sectors}c).
 

### 2020-03-31 paper/current/main.tex
revise + re-organize data and methods

@@
 
-Data, analysis, and associated code have been made publicly available and can be found at \textit{https://github.com/murrayds/...}
+Data, analysis, and associated code have been made publicly available and can be found at \url{https://github.com/murrayds/sci-mobility-emb}
 
@@
 %% Main dataset
-% Do we need to add the Leiden field classificaiton infomration? It doesn't seem like its relevant for the current analysis.
 % Do we need to talk about how we define mobility in relation to past papers?
@@
 Trajectories are constructed from author affiliations listed on the byline of publications for a given author.
-Given the limitations of author-name disambiguation, we limit to papers published after 2008, when the Web of Science began providing full names and institutional affiliations~\autocite{caron2014disambiguation} and when performance is strongest (ref to SI?).
+Given the limitations of author-name disambiguation, we limit to papers published after 2008, when the Web of Science began providing full names and institutional affiliations~\autocite{caron2014disambiguation} that improved disambigatuon (see supporting materials).
 This yields 33,934,672 author-affiliation combinations representing 12,963,792 authors.
-Each author-affiliation combination is associated with the publication year and a unique id that maps the affiliation to a disambiguate organization.
-Combinations are also associated with a publication-level disciplinary classification, one of ``Social sciences and humanities'',
-``Biomedical and health sciences'', ``Physical sciences and engineering'', ``Life and earth sciences'', and ``Mathematics and computer science''.
+Each author-affiliation combination is associated with the publication year and an ID linking it to one of 8,661 a dismabiguated organizational affiliation (see supporting materials for more detail)
 Trajectories are represented as the list of author-affiliation combinations, ordered by year of publication, and randomly ordered for combinations within the same year.
-Authors are classified as mobile when they have at least two distinct organization ids in their trajectory, meaning that they have published using two or more distinct affiliations between 2008 and 2019.
-While the number of publications has increased year-to-year, the mobility and disciplinary makeup of the dataset has not significantly changed across the period of study (Fig.~\ref{fig:supp:pubs_over_time}).
-
-% %Organization information
-Affiliations mapped to one of 8,661 organizations, disambiguated following a mostly manual process originally designed for the Leiden Rankings of World Universities~\autocite{waltman2012leidenrankings}.
-Organizational records were associated with a full name, a type indicating the sector (e.g., University, Government, Industry), and an identifier for the country and city of the organization.
-Sixteen different sector types were included in the analysis, which we aggregated to a four high-level codes: \textit{University}, \textit{Hospital}, \textit{Government}, and \textit{Other}.
-Each record was also associated with a latitude and longitude, however for many organizations these were missing or incorrect.
-We manually updated the coordinates of 2,267 organizations by searching the institution name and city on Google Maps;
-in cases where a precise location of the organization could not be identified, we used the coordinates returned when searching the name of the city.
-The data was further enriched with country-level information, including continent, majority language spoken, and language family of the majority language (e.g., the language family of \textit{Spanish} is \textit{Italic}).
-State/province level  information were added using the reverse geocoding service LocationIQ using each organization's latitude and longitude as input.
-Regional census classifications were also added for states in the United States.
-For each organization, we also calculated a size as the average number of unique authors (mobile and non-mobile) who published with that organization across each year of our dataset;
-in the case that authors publish with multiple affiliations in a single year, they are counted towards each.
-
-As a result of our disambiguation procedure, some affiliations are mapped to two organizations, one specific, and one more general.
-For example, any author affiliated with ``Indiana University Bloomington'' will also be listed as being affiliated with the ``Indiana University System'', a more general designation for all public universities in Indiana.
-However, a more general organization may not always occur alongside the more specific one.
-For example, a researcher affiliated with the smaller regional school ``Indiana University South Bend'' will be listed as affiliated with only the ``Indiana University System''.
-We identify all specific organizations that always co-occur along a more general one.
-For every career trajectory that includes one of these specific organizations, we remove all occurrences of the more general organization;
-trajectories containing only a general designation are not altered.
 
 Scientific mobility is complex and can be defined in many possible ways~\autocite{robinson2019mobility}.
-Here, we consider an author as mobile when at least two distinct organizational affiliations appear in their trajectory during the 2008-2019 time window.
+Here, authors are classified as mobile when they have at least two distinct organization ids in their trajectory, meaning that they have published using two or more distinct affiliations between 2008 and 2019.
 Under this definition, mobile authors constitute 3,007,192 or 23.2 percent of all authors, and 17,700,095 author-affiliation combinations.
@@
 Rates of mobility tended to differ across country.
-For example, France, Qatar, the USA, Iraq, and Luxembourg had the most mobile authors (ref figure).
-However, due to their size, the USA, accounted for nearly 40 percent of all mobile authors worldwide, with  10 countries accounting for 80 percent of all mobility (ref figure).
+For example, France, Qatar, the USA, Iraq, and Luxembourg had the most mobile authors (Fig.~\ref{fig:supp:descriptives}c).
+However, due to their size, the USA, accounted for nearly 40 percent of all mobile authors worldwide (Fig.~\ref{fig:supp:descriptives}a), with 10 countries accounting for 80 percent of all mobility (Fig.~\ref{fig:supp:descriptives}b).
 In most cases, countries with a high degree inter-organization mobility also had a high degree of international mobility;
-however, the USA and France had a high degree of inter-organization mobility with the corresponding international mobility (ref figure).
+however, the USA and France had a high degree of inter-organization mobility with the corresponding international mobility (Fig.~\ref{fig:supp:descriptives}c).
+While the number of publications has increased year-to-year, the mobility and disciplinary makeup of the dataset has not significantly changed across the period of study (Fig.~\ref{fig:supp:pubs_over_time}).
 
@@
 %
-\subsection{Distance}
+\subsection*{Distance}
 %% Distance calculations
@@
 %
-\subsection{Gravity Law}
+\subsection*{Gravity Law}
 
@@
 	\label{eq:ppr}
-	p_i = (1.0 - \alpha) * v_i + \alpha p_i W,
+	p_i = (1.0 - \alpha) v_i + \alpha p_i W,
 \end{equation}
@@
 Moreover, it is also computationally efficient and salable for large dataset.
+
+%
+% S2 TEXT
+\paragraph*{S2 Text}
+\label{si:text:organizations}
+{\bf Organization disambiguation and metadata.}
+
+Affiliations mapped to one of 8,661 organizations, disambiguated following that origionally designed for the Leiden Rankings of World Universities~\autocite{waltman2012leidenrankings}.
+Organizational records were associated with a full name, a type indicating the sector (e.g., University, Government, Industry), and an identifier for the country and city of the organization.
+Sixteen different sector types were included in the analysis, which we aggregated to a four high-level codes: \textit{University}, \textit{Hospital}, \textit{Government}, and \textit{Other}.
+Each record was also associated with a latitude and longitude, however for many organizations these were missing or incorrect.
+We manually updated the coordinates of 2,267 organizations by searching the institution name and city on Google Maps;
+in cases where a precise location of the organization could not be identified, we used the coordinates returned when searching the name of the city.
+The data was further enriched with country-level information, including continent, majority language spoken, and language family of the majority language (e.g., the language family of \textit{Spanish} is \textit{Italic}).
+State/province level  information were added using the reverse geocoding service LocationIQ using each organization's latitude and longitude as input.
+Regional census classifications were also added for states in the United States.
+For each organization, we also calculated a size as the average number of unique authors (mobile and non-mobile) who published with that organization across each year of our dataset;
+in the case that authors publish with multiple affiliations in a single year, they are counted towards each.
+
+As a result of our disambiguation procedure, some affiliations are mapped to two organizations, one specific, and one more general.
+For example, any author affiliated with ``Indiana University Bloomington'' will also be listed as being affiliated with the ``Indiana University System'', a more general designation for all public universities in Indiana.
+However, a more general organization may not always occur alongside the more specific one.
+For example, a researcher affiliated with the smaller regional school ``Indiana University South Bend'' will be listed as affiliated with only the ``Indiana University System''.
+We identify all specific organizations that always co-occur along a more general one.
+For every career trajectory that includes one of these specific organizations, we remove all occurrences of the more general organization;
+trajectories containing only a general designation are not altered.
+
+%
+% S3 TEXT
+\paragraph*{S3 Text}
+\label{si:text:disambiguation}
+{\bf Author name dismabiguation.}
+
+Author-name disambiguation, the problem of associating names on papers with individuals authors, remains difficult for the use of bibliometric data~\autocite{dangelo2020disambiguation}. 
+Authors in our dataset have been disambiguated using a rule-based algortihm that makes use of author and paper metadata, such as physica, addresses, co-authors, and journal, to score papers on the likelihood of belonging to an author cluster—a cluster of publications belived to have been authored by the same individual~\autocite{caron2014disambiguation}.
+We limit our period of analysis until after 2008, as this is when the Web of Science began indexing additional author-level metadata such as full names and email addresses. 
+The disambiguation algorithm is conservative, favoring splitting clusters. 
+Past studies have validated this data, demonstrating it comparable to ground-truth records such as those from ORCID and useful for a wide range of bibliometric studies~\cite{sugimoto2017mostimpact, robinson2019mobility, chinchilla2018global, chinchilla2018travelban}.
+
+\newpage
 
@@
 %
-% Figure - publications over time
+% Figure - descriptives
 %
@@
 	}
-	\label{fig:supp:pubs_over_time}
+	\label{fig:supp:descriptives}
 \end{figure}

### 2020-04-02 workflow/visualize_embedding/script/draw_california_figure_si.py
typo

@@ -68,7 +68,7 @@ def draw_figure(
         edgecolor="white",
     )
 
-    plt.text(3, -3.7, "San Franciso\nBay Area", c="black", fontproperties=large_prop)
+    plt.text(3, -3.7, "San Francisco\nBay Area", c="black", fontproperties=large_prop)
     plt.text(-3, 0.6, "Los Angeles", c="black", fontproperties=large_prop)
     plt.text(-4.6, -3.6, "San Diego", c="black", fontproperties=large_prop)
 
@@ -92,7 +92,7 @@ def draw_figure(
     plt.text(-3.1, -0.64, "UCLA\nHealth", c=c, fontproperties=prop)
     plt.text(2.5, -2.4, "UCSF\nMedical\nCenter", c=c, fontproperties=prop)
     plt.text(-1.95, -0.1, "Cedars-Sinai\nMedical Center", c=c, fontproperties=prop)
-    plt.text(1.6, -1.8, "Standfoard\nHealth Care", c=c, fontproperties=prop)
+    plt.text(1.6, -1.8, "Standford\nHealth Care", c=c, fontproperties=prop)
     plt.text(-3.4, -3.3, "UCSD\nHealth", c=c, fontproperties=prop)
 
     ## Inst annoate

### 2020-04-02 paper/current/main.tex
added org label table to the manuscript

@@
 \usepackage{url}
+
+\usepackage{changepage}
 
@@
 		Points correspond to organizations, and a sample of individual states are highlighted.
+		Full organization names listed in Table~\ref{table:supp:orglabels}.
 		\textbf{b.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity to the \textit{Elite} end of the axis prestige axis \textit{a}.
@@
 
+% latex table generated in R 3.5.1 by xtable 1.8-2 package
+% Thu Apr  2 13:43:00 2020
+\begin{table}[ht]
+\centering
+\caption{\textbf{Full organization names}}
+\label{table:supp:orglabels}
+\begin{adjustwidth}{-2cm}{}
+\begingroup\scriptsize
+\begin{tabular}{llll}
+  \hline
+Short & Full & Short & Full \\ 
+  \hline
+Stanford & Stanford Univ & Northwestern & Northwestern Univ \\ 
+  Columbia & Columbia Univ & Ball State & Ball State Univ \\ 
+  Harvard & Harvard Univ & IU Bloomington & Indiana Univ, Bloomington \\ 
+  UCLA & Univ of California, Los Angeles & Stevens Institute & Stevens Institute of Technology \\ 
+  Cal State Long Beach & California State Univ, Long Beach & NJIT & New Jersey Institute of Technology \\ 
+  Wright State & Wright State Univ & NYU & New York Univ \\ 
+  U Toledo & Univ of Toledo & SUNY Albany & Univ at Albany, The State Univ of New York \\ 
+  Boston U & Boston Univ & NY Medical College & New York Medical College \\ 
+  Suffolk & Suffolk Univ & Miami University & Miami Univ \\ 
+  CUNY & City Univ of New York (CUNY) & IU Pennsylvania & Indiana Univ of Pennsylvania \\ 
+  U Arizona & Univ of Arizona & Baylor & Baylor College of Medicine \\ 
+  OSU & Ohio State Univ & UT Health Center & Univ of Texas Health Science Center \\ 
+  MIT & Massachusetts Institute of Technology & Bard College & Bard College \\ 
+  Princeton & Princeton Univ & Stonehill College & Stonehill College \\ 
+  GCU & Grand Canyon Univ & Carleton College & Carleton College \\ 
+  Northcentral & Northcentral Univ & Hanover College & Hanover College \\ 
+  UCSF & Univ of California, San Francisco & Queens College & Queens College \\ 
+  Fielding & Fielding Graduate Univ & DePauw & DePauw College \\ 
+  Pepperdine & Pepperdine Univ & Naval Academy & United States Naval Academy \\ 
+  Argosy & Argosy Univ & Cal State San Marcos & California State Univeristy San Marcos \\ 
+  Yale & Yale Univ & Broad Inst & Broad Institute \\ 
+  U Hartford & Univ of Hartford & Forsyth Inst & Forsyth Institute \\ 
+  FAU & Florida Atlantic Univ & U Alaska Museum & Univ of Alaska Museum of the North \\ 
+  U Miami & Univ of Miami & Lawrence Berkeley & Lawrence Berkeley Natl Laboratory \\ 
+  UWF & The Univ of West Florida & Allen Institute & Allen Institute for Brain Science \\ 
+  FIT & Florida Institute of Technology & RTI International & RTI InterNatl \\ 
+  Purdue & Purdue Univ, West Lafayette & Fermilab & Fermilab \\ 
+  Notre Dame & Univ of Notre Dame & State of NY & State of New York \\ 
+  Indiana State & Indiana State Univ & Mayo Clinic & Mayo Clinic \\ 
+  Saint Mary's & Saint Mary's College & Fish and Wildlife & Fish and Wildlife Research Institute \\ 
+  Tufts & Tufts Univ & EPA & United States Emvironmental Protection Agency \\ 
+  Mattel & Mattel Children's Hospital & US Army & United States Army \\ 
+  Clark & Clark Univ & NSF & Natl Science Foundation \\ 
+  UMass Amherst & Univ of Massachusetts Amherst & US Navy & United States Navy \\ 
+  Montclair & Montclair State Univ & US Air Force & United States Air Force \\ 
+  Farleigh Dickinson & Fairleigh Dickinson Univ-Metro Campus & Ames Laboratory & Ames Laboratory \\ 
+  Rockefeller & Rockefeller Univ & Olin College & Oin College of Engineering \\ 
+  Adelphi & Adelphi Univ & Scripss Institute & Scripss Institute \\ 
+  Barnard & Barnard College & Idaho Natl Lab & Idaho Natl Laboratory \\ 
+  Saint John Fisher & Saint John Fisher College & Dana Faber & Dana Faber Cancer Institute \\ 
+  U Penn & Univ of Pennsylvania & Dept of Agriculture & United States Department of Agriculture \\ 
+  Villanova & Villanova Univ & DOE & United States Department of Energy \\ 
+  Widener & Widener Univ-Main Campus & NIAMS & Natl Institute of Arthritis, Skin Diseases \\ 
+  Robert Morris & Robert Morris Univ & JMI Labs & JMI Laboratories \\ 
+  U Cincinnati & Univ of Cincinnati & Whitehead Inst & Whitehead Institute of Biomedical Research \\ 
+  Case Western & Case Western Reserve Univ & Wellesley & Wellesley Univeristy \\ 
+  Ashland & Ashland Univ & UT Health, San Antonio & Univ of Texas Health Science Center, San Antonio \\ 
+  Texas A\&M & Texas A\&M Univ-Commerce & UNT & Univ of North Texas \\ 
+  Texas Southern & Texas Southern Univ & UT Southwestern Med & Univ of Texas Southwestern Medical Center \\ 
+  Baylor & Univ of Mary Hardin-Baylor & UT El Paso & Univ of Texas, El Paso \\ 
+  U Washington & Univ of Washington - Seattle & USF & Univ of South Florida, Tampa \\ 
+  Washington State & Washington State Univ & Florida A\&M & Florida Agricultural and Mechanical Univ \\ 
+  Seattle Pacific & Seattle Pacific Univ & Barry & Barry Univ \\ 
+  Cal State Fresno & California State Univ-Fresno & UMass Dartmouth & Univ of Massachusetts Dartmouth \\ 
+  Northern Arizona & Northern Arizona Univ & Worcester Poly & Worcester Polytechnic Institute \\ 
+  IUPUI & Indiana Univ - Purdue Univ Indianapolis & Umass Boston & Univ of Massachusetts Boston \\ 
+  U Dayton & Univ of Dayton & MGH Inst & MGH Institute of Health Professions \\ 
+  U Conn & Univ of Connecticut & Joseph W. Jones Center & Joseph W. Jones Ecological Research Center \\ 
+  ASU & Arizona State Univ & Vaccine Research Center & Vaccine Research Center, San Diego \\ 
+  U Florida & Univ of Florida & LA Ag Center & Lousianna Agricultural Center \\ 
+  Northern Illinois & Northern Illinois Univ & FL Fish and Wildlife & Florida Fish and Wildlife Conservation Commission \\ 
+  Condordia Chicago & Concordia Univ-Chicago & NHLBI & Natl Heart, Lung, and Blood Institute \\ 
+  U Chicago & Univ of Chicago & NY Dept. of Health & New York Department of Health \\ 
+  SIU Edwardsville & Southern Illinois Univ, Edwardsville & St Michaels & Saint Michaels College \\ 
+  SIU Carbondale & Southern Illinois Univ, Carbondale &  &  \\ 
+   \hline
+\end{tabular}
+\endgroup
+\end{adjustwidth}
+\end{table}
+
+\newpage
 %
@@
 		Grey points correspond to all other U.S. universities.
+		Full organization names listed in Table~\ref{table:supp:orglabels}.
 	}
@@
 		Grey points correspond to all U.S. universities.
+	    	Full organization names listed in Table~\ref{table:supp:orglabels}.
 	}

### 2020-04-02 workflow/visualize_embedding/script/draw_pennsylvania_figure_si.py
add_pen_figure

@@ -1,0 +1,129 @@
+import pickle
+import sys
+
+import matplotlib.font_manager as font_manager
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+from pylab import rcParams
+
+from py_scimobility.core import get_awesome_c_list
+
+
+def draw_figure(
+    INPUT_UMAP_COORD_FILE,
+    INPUT_META_INFO_FILE,
+    INPUT_SIMPLIFITED_ORGS_FILE,
+    INPUT_SIZE_FILE,
+    FONT_PATH,
+    OUTPUT_FILE,
+):
+    umap_result = pickle.load(open(INPUT_UMAP_COORD_FILE, "rb"))
+    institute_list = np.array(list(umap_result.keys()))
+    umap_coords = np.array([umap_result[inst] for inst in institute_list])
+
+    meta_info = pd.read_csv(INPUT_META_INFO_FILE, sep="\t")
+    meta_info = meta_info.set_index("cwts_org_no")
+    code_to_org_type = meta_info["org_type"].to_dict()
+
+    simple_orgs_file = pd.read_csv(INPUT_SIMPLIFITED_ORGS_FILE)
+    simple_orgs_file = simple_orgs_file.set_index("org_type")
+    orgs_to_simple_orgs = simple_orgs_file["org_type_simplified"].to_dict()
+    orgs_list = np.array(
+        [orgs_to_simple_orgs[code_to_org_type[int(inst)]] for inst in institute_list]
+    )
+
+    size_data = pd.read_csv(INPUT_SIZE_FILE, sep="\t", dtype={"cwts_org_no": str})
+    size_data = size_data.drop(size_data.index[len(size_data) - 1])
+    size_data.person_count = size_data.person_count.astype(int)
+    mean_size_dict = (
+        size_data.groupby("cwts_org_no")["person_count"].apply(np.mean).to_dict()
+    )
+    size_list = np.array([mean_size_dict[inst] for inst in institute_list])
+
+    rcParams["figure.figsize"] = 20, 18
+    if FONT_PATH:
+        prop = font_manager.FontProperties(fname=FONT_PATH, size=28)
+        large_prop = font_manager.FontProperties(fname=FONT_PATH, size=40)
+    else:
+        prop = font_manager.FontProperties(size=28)
[…]

### 2020-04-02 workflow/visualize_embedding/script/draw_pennsylvania_figure_si.py
black

@@ -61,10 +61,9 @@ def draw_figure(
         linewidth=0.4,
         edgecolor="white",
     )
-    
+
     plt.text(1.3, 3.8, "Pittsburgh", c="black", fontproperties=large_prop)
     plt.text(2.4, 1.5, "Philadelphia", c="black", fontproperties=large_prop)
-
 
     ## Univ annoate
     c = awesome_c_list[4]
@@ -73,27 +72,38 @@ def draw_figure(
     plt.text(3.65, 0.88, "Villanova", c=c, fontproperties=prop)
     plt.text(2.82, -1.35, "Lehigh", c=c, fontproperties=prop)
     plt.text(3, -2.7, "Pennsylvania\nState System", c=c, fontproperties=prop)
-    plt.text(1.35, 5.05,  "Pittsburgh", c=c, fontproperties=prop)
+    plt.text(1.35, 5.05, "Pittsburgh", c=c, fontproperties=prop)
     plt.text(2.78, 2.45, "Drexel", c=c, fontproperties=prop)
     plt.text(4.17, 2.8, "Temple", c=c, fontproperties=prop)
     plt.text(2.2, 4.6, "Duquesne", c=c, fontproperties=prop)
-    plt.text(1.23, .9, "Thomas\nJefferson", c=c, fontproperties=prop)
-    
+    plt.text(1.23, 0.9, "Thomas\nJefferson", c=c, fontproperties=prop)
+
     ## Hospital annoate
     c = awesome_c_list[3]
-    plt.text(4.7,0.84, "UPenn\nHealth\nSystem", c=c, fontproperties=prop)
+    plt.text(4.7, 0.84, "UPenn\nHealth\nSystem", c=c, fontproperties=prop)
     plt.text(0.88, 2.1, "Thomas Jefferson\nU. Hospital", c=c, fontproperties=prop)
-    plt.text(2.3, -3.3, "Penn State Health Milton\nS. Hershey Medical Center", c=c, fontproperties=prop)
+    plt.text(
+        2.3,
+        -3.3,
+        "Penn State Health Milton\nS. Hershey Medical Center",
+        c=c,
+        fontproperties=prop,
+    )
     plt.text(1.4, 5.6, "U.Pittsburgh\nMedical Center", c=c, fontproperties=prop)
-    plt.text(1.5,4.2, "UPMC Presbyterian", c=c, fontproperties=prop)
+    plt.text(1.5, 4.2, "UPMC Presbyterian", c=c, fontproperties=prop)
[…]

### 2020-04-02 workflow/visualize_embedding/script/draw_texas_figure_si.py
add_texas_fig

@@ -1,0 +1,132 @@
+import pickle
+import sys
+
+import matplotlib.font_manager as font_manager
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+from pylab import rcParams
+
+from py_scimobility.core import get_awesome_c_list
+
+
+def draw_figure(
+    INPUT_UMAP_COORD_FILE,
+    INPUT_META_INFO_FILE,
+    INPUT_SIMPLIFITED_ORGS_FILE,
+    INPUT_SIZE_FILE,
+    FONT_PATH,
+    OUTPUT_FILE,
+):
+    umap_result = pickle.load(open(INPUT_UMAP_COORD_FILE, "rb"))
+    institute_list = np.array(list(umap_result.keys()))
+    umap_coords = np.array([umap_result[inst] for inst in institute_list])
+
+    meta_info = pd.read_csv(INPUT_META_INFO_FILE, sep="\t")
+    meta_info = meta_info.set_index("cwts_org_no")
+    code_to_org_type = meta_info["org_type"].to_dict()
+
+    simple_orgs_file = pd.read_csv(INPUT_SIMPLIFITED_ORGS_FILE)
+    simple_orgs_file = simple_orgs_file.set_index("org_type")
+    orgs_to_simple_orgs = simple_orgs_file["org_type_simplified"].to_dict()
+    orgs_list = np.array(
+        [orgs_to_simple_orgs[code_to_org_type[int(inst)]] for inst in institute_list]
+    )
+
+    size_data = pd.read_csv(INPUT_SIZE_FILE, sep="\t", dtype={"cwts_org_no": str})
+    size_data = size_data.drop(size_data.index[len(size_data) - 1])
+    size_data.person_count = size_data.person_count.astype(int)
+    mean_size_dict = (
+        size_data.groupby("cwts_org_no")["person_count"].apply(np.mean).to_dict()
+    )
+    size_list = np.array([mean_size_dict[inst] for inst in institute_list])
+
+    rcParams["figure.figsize"] = 20, 18
+    if FONT_PATH:
+        prop = font_manager.FontProperties(fname=FONT_PATH, size=28)
+        large_prop = font_manager.FontProperties(fname=FONT_PATH, size=40)
+    else:
+        prop = font_manager.FontProperties(size=28)
[…]

### 2020-04-02 workflow/visualize_embedding/script/draw_texas_figure_si.py
black

@@ -61,11 +61,10 @@ def draw_figure(
         linewidth=0.4,
         edgecolor="white",
     )
-    
+
     plt.text(-1.9, 5.5, "Houston", c="black", fontproperties=large_prop)
     plt.text(-2.9, 1.9, "Austin", c="black", fontproperties=large_prop)
     plt.text(-2.3, 0.1, "Dallas", c="black", fontproperties=large_prop)
-
 
     ## Univ annoate
     c = awesome_c_list[4]
@@ -74,29 +73,36 @@ def draw_figure(
     plt.text(-2.25, 1.3, "Southern\nMethodist", c=c, fontproperties=prop)
     plt.text(-3.4, -5.7, "Texas A&M System", c=c, fontproperties=prop)
     plt.text(-2.95, -3.65, "Baylor", c=c, fontproperties=prop)
-    plt.text(-2.3, -1.9,  "Texas\nChristian", c=c, fontproperties=prop)
+    plt.text(-2.3, -1.9, "Texas\nChristian", c=c, fontproperties=prop)
     plt.text(-2.78, 1.1, "UT Dallas", c=c, fontproperties=prop)
     plt.text(-2.5, 5.5, "U.Houston", c=c, fontproperties=prop)
-    plt.text(-.6, 0, "UT System", c=c, fontproperties=prop)
+    plt.text(-0.6, 0, "UT System", c=c, fontproperties=prop)
     plt.text(-3.75, -2.4, "Texas Tech", c=c, fontproperties=prop)
-    plt.text(-3.1, -.8, "U.North Texas", c=c, fontproperties=prop)
+    plt.text(-3.1, -0.8, "U.North Texas", c=c, fontproperties=prop)
     plt.text(-2.9, 3.6, "UT Health", c=c, fontproperties=prop)
-    
+
     ## Hospital annoate
     c = awesome_c_list[3]
-    plt.text(-.7,5, "Methodist\nHospital,\nHouston", c=c, fontproperties=prop)
+    plt.text(-0.7, 5, "Methodist\nHospital,\nHouston", c=c, fontproperties=prop)
     plt.text(-2.75, -4.3, "Baylor Scott and\nWhite Health", c=c, fontproperties=prop)
-    plt.text(-2.15, 2.8, "Memorial\nHermann-\nTexas\nMedical Center", c=c, fontproperties=prop)
-    plt.text(-.9,4.5, "Texas Children's Hospital", c=c, fontproperties=prop)
[…]

### 2020-04-02 workflow/visualize_embedding/script/draw_california_figure_si.py
for kavli foundation

@@ -29,6 +29,8 @@ def draw_figure(
     simple_orgs_file = pd.read_csv(INPUT_SIMPLIFITED_ORGS_FILE)
     simple_orgs_file = simple_orgs_file.set_index("org_type")
     orgs_to_simple_orgs = simple_orgs_file["org_type_simplified"].to_dict()
+    # for missclassfied kavil foundation
+    orgs_to_simple_orgs['Funding Organisation'] = 'Institute'
     orgs_list = np.array(
         [orgs_to_simple_orgs[code_to_org_type[int(inst)]] for inst in institute_list]
     )
@@ -118,10 +120,9 @@ def draw_figure(
         ls="",
         marker="o",
     )[0]
-    handles = [
-        lp(k) for k in ["Institute", "Hospital", "University", "Teaching", "Government"]
-    ]
-    plt.legend(handles=handles, bbox_to_anchor=(0.86, 0.24), prop=prop, frameon=False)
+    
+    handles = [lp(k) for k in ["Institute", "Hospital", "University", "Teaching"]]
+    plt.legend(handles=handles, bbox_to_anchor=(1.08, 0.21), prop=prop, frameon=False)
     plt.savefig(OUTPUT_FILE, bbox_inches="tight")
 
 

### 2020-04-02 workflow/visualize_embedding/script/draw_california_figure_si.py
black

@@ -30,7 +30,7 @@ def draw_figure(
     simple_orgs_file = simple_orgs_file.set_index("org_type")
     orgs_to_simple_orgs = simple_orgs_file["org_type_simplified"].to_dict()
     # for missclassfied kavil foundation
-    orgs_to_simple_orgs['Funding Organisation'] = 'Institute'
+    orgs_to_simple_orgs["Funding Organisation"] = "Institute"
     orgs_list = np.array(
         [orgs_to_simple_orgs[code_to_org_type[int(inst)]] for inst in institute_list]
     )
@@ -120,7 +120,7 @@ def draw_figure(
         ls="",
         marker="o",
     )[0]
-    
+
     handles = [lp(k) for k in ["Institute", "Hospital", "University", "Teaching"]]
     plt.legend(handles=handles, bbox_to_anchor=(1.08, 0.21), prop=prop, frameon=False)
     plt.savefig(OUTPUT_FILE, bbox_inches="tight")

### 2020-04-02 workflow/visualize_embedding/script/draw_pennsylvania_figure_si.py
typo

@@ -89,7 +89,7 @@ def draw_figure(
         c=c,
         fontproperties=prop,
     )
-    plt.text(1.4, 5.6, "U.Pittsburgh\nMedical Center", c=c, fontproperties=prop)
+    plt.text(1.4, 5.6, "U. Pittsburgh\nMedical Center", c=c, fontproperties=prop)
     plt.text(1.5, 4.2, "UPMC Presbyterian", c=c, fontproperties=prop)
 
     ## Inst annoate
@@ -99,7 +99,7 @@ def draw_figure(
     plt.text(
         3.75,
         -2.75,
-        "The Sigfried and\nJanet Weis\nCenter for Research",
+        "The Siegfried and\nJanet Weis\nCenter for Research",
         c=c,
         fontproperties=prop,
     )

### 2020-04-02 workflow/visualize_embedding/script/draw_texas_figure_si.py
typo

@@ -100,7 +100,7 @@ def draw_figure(
     plt.text(-2.85, 4.3, "M.D. Anderson\nCancer Center", c=c, fontproperties=prop)
     plt.text(-0.7, 1.82, "Southwest Research\nInstitute", c=c, fontproperties=prop)
     plt.text(
-        -1.85, 2.2, "US Army Institue\nof Surgircal Research", c=c, fontproperties=prop
+        -1.85, 2.2, "US Army Institute\nof Surgircal Research", c=c, fontproperties=prop
     )
     plt.text(-3.9, -4.2, "Texas AgriLife", c=c, fontproperties=prop)
 

### 2020-04-02 paper/current/main.tex
Added supporting state-level projections to maunscript

@@
 Even though UMass Boston is located in Boston, it clusters near other universities in the UMass System rather than the typically more elite and research-focused universities in Boston, reflecting a relative lack of mobility between the two systems, even within the same state.
-Similar structures can be observed in many states (New York, California, etc.), such that prestigious university systems are separate from more regional ones (SI~TBD).
+Similar structures can be observed in other states such as among New York's CUNY and SUNY systems (Fig.~\ref{fig:supp:proj_newyork}), Pennsylvania's state system (Fig.~\ref{fig:supp:proj_pennsylvania}), Texas's Agricultural and Mechanical universities(Fig.~\ref{fig:supp:proj_texas}), and between the University of California and State University of California systems (Fig.~\ref{fig:supp:proj_california}).
 
@@
 %
+% Figure - New York Projection
+%
+\begin{figure}[hp!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_New_York.pdf}
+	\caption{
+		\textbf{UMAP Projection of organizations in New York.}
+		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019. 
+		Color indicates the sector. 
+	}
+	\label{fig:supp:proj_newyork}
+\end{figure}
+
+%
+% Figure - Pennsylvania Projection
+%
+\begin{figure}[hp!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_Pennsylvania.pdf}
+	\caption{
+		\textbf{UMAP Projection of organizations in Pennsylvania.}
+		UMAP projection of the embedding space of organizations in Pennsylvania reveal clustering based on geography, sector, and academic prestige.
+		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019. 
+		Color indicates the sector. 
+	}
+	\label{fig:supp:proj_pennsylvania}
+\end{figure}
+
+%
+% Figure - Texas Projection
+%
+\begin{figure}[hp!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_Texas.pdf}
+	\caption{
+		\textbf{UMAP Projection of organizations in Texas.}
+		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019. 
+		Color indicates the sector. 
+	}
+	\label{fig:supp:proj_texas}
+\end{figure}
+
+%
+% Figure - California Projection
+%
+\begin{figure}[hp!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_California.pdf}
+	\caption{
+		\textbf{UMAP Projection of organizations in California.}
+		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019. 
+		Color indicates the sector. 
+	}
+	\label{fig:supp:proj_california}
+\end{figure}
+
+%
 % Figure - SemAxis results

### 2020-04-06 paper/current/main.tex

@@
 In addition to encoding national characteristics, the embedding also encodes domestic geography and latent hierarchy.
-Employing the SemAxis approach~\autocite{an2018semaxis} we define two axes.
+Leveraging the unique semantic properties of the organization embedding, we employ the SemAxis approach~\autocite{an2018semaxis} and define two semantic axes.
 The first is the California--Massachusetts axis defined by the mean vector of universities in California on one end, and in Massachusetts on the other. 
@@
 A university projected onto the axis corresponds to their nearness to the mean vector defining each pole (Fig.~\ref{fig:semaxis}a).
+
 Generally, universities in Western states, such as Arizona (Fig.~\ref{fig:supp:semaxis_states}b) are nearer to the California end of the axis, whereas states in the Northeast such as New York (Fig.~\ref{fig:supp:semaxis_states}f) and Connecticut (Fig.~\ref{fig:supp:semaxis_states}e) are nearer the Massachusetts end.
-Universities geographically distance from both California and Massahcussets are less aligned with either, such as Texas (Fig.~\ref{fig:supp:semaxis_states}g)s and Florida (Fig.~\ref{fig:supp:semaxis_states}i).
+Universities geographically distant from both California and Massahcussets are less aligned with either, such as Texas (Fig.~\ref{fig:supp:semaxis_states}g)s and Florida (Fig.~\ref{fig:supp:semaxis_states}i).
 
@@
 Universities at the bottom of this axis tend to be regional universities with lower national profiles.
-
-Once these axes are constructed using university rankings, we can even relate other types of organizations that would not typically be fit onto university rankings.
-For example, among Government institutions, we see that the U.S.
-Department of Energy is more aligned with Californian universities, whereas the Mayo Clinic is more aligned with Massachusetts and organizations like the National Institute of Arthritis, Musculoskeletal, and Skin Disease and more aligned with elite universities than is the U.S.
-Department of Agriculture (Fig.~\ref{fig:supp:semaxis_sectors}a).
-Among research institutes, the most aligned with elite universities are typically those prestigious university-adjacent institutes such as the Whitehead Institute, the Broad Institute, and the Dana Faber institute (Fig.~\ref{fig:supp:semaxis_sectors}b); those institutes aligned with low-ranked universities tend to be ecological or agricultural institutes such as the Joseph W.
-Jones Ecological Research Center and the Louisiana Agriculture Center.
-Among teaching organizations, the top-ranked tend to be notable private liberal arts colleges such as Wellesley College and Carleton College, whereas community colleges and military colleges tend to be more aligned with low-ranked universities (Fig.~\ref{fig:supp:semaxis_sectors}c).
+By considering mobility between all organization types, organization embeddings offer a new means of reasoning about the prestige of organizations typically excluded from rankings such as government organizatioss (Fig.~\ref{fig:supp:semaxis_sectors}a), research institutes (Fig.~\ref{fig:supp:semaxis_sectors}b), and teaching colleges (Fig.~\ref{fig:supp:semaxis_sectors}c)
 
@@
 
-Globally, science has experienced many changes, from gradual globalization~\autocite{czaika2018globalisation} to the more sudden 2016 Brexit and 2017 U.S. travel bans.
+Globally, science has experienced many changes, from gradual globalization~\autocite{czaika2018globalisation} to the more sudden 2016 Brexit and 2017 U.S.
+travel bans, and more recently the Covid19 global pandemic.
 The consequences of these changes are far-reaching, and how nations respond to them will shape the future of the scientific enterprise~\autocite{chinchilla2018travelban, wagner2017open, sugimoto2017mostimpact, whetsell2019democracy}.

### 2020-04-10 paper/current/main.tex
new_math_part

@@
 \begin{equation}
+	\label{eq:approxi_mass_term}
     \mu_{i} = \sum_{k \in N} T_{ik} \propto M_i
@@
 
-with the hypothesis that a similar fraction of the scholars are mobile in each organization.
-It can be checked in Fig.~\ref{fig:math_part}a.
-Then, our gravity model can be written with only terms from mobility data,
-
-\begin{equation}
-    \label{eq:gravity_model_approx}
-    \frac{T_{ij}}{\mu_i  \mu_j} \propto \exp(\cos(v_i,v_j))
-\end{equation}
-
-The embedding that best represents the data should closely approximate the true conditional probability defined in
-Eq.~\ref{eq:flux_conditional_prob},
-
-\begin{equation}
-    \label{eq:flux_conditional_prob}
-    p(j|i) = \frac{T_{ij}}{\mu_i}
-\end{equation}
-
-We can then rewrite Eq.~\ref{eq:gravity_model_approx} as,
-
-\begin{equation}
-    \label{eq:gravity_relationship}
-    \frac{T_{ij}}{\mu_i  \mu_j} = \frac{\mu_i  p(j|i)}{\mu_i\mu_j} =  \frac{p(j|i)}{\mu_j} \propto \exp(\cos(v_i,v_j))
-\end{equation}
-
-Then, the word embedding model will learns vectors under the condition,
-
-\begin{equation}
-    \label{eq:conditional probability}
-      p(j|i) \propto {\mu_j} \exp(\cos(v_i,v_j))
-\end{equation}
-
-which is restricted to, sum of the conditional probability should be one,
-
-\begin{equation}
-    \label{eq:sum of the conditional probabiitliy}
-    \sum_{j \in N} p(j|i) = 1
-\end{equation}
-
-Then, we can write $p(j|i)$ with $\mu_{j}$
-
-\begin{equation}
-    p(j|i) \propto \frac{{\mu_j}\exp(\cos(v_i,v_j)}{\sum_{k \in N} {\mu_k}\exp(\cos(v_i,v_k))}
-\end{equation}
-
-And, if we remove ${\mu_*}$ for simplicity (or for the special case with $\mu_{i} = \mu_{j} = \mu_*$), then $p(j|i)$ can be written as,
-
-\begin{equation}
-    \label{eq:real_embedding_relationship}
-    p(j|i) \propto \frac{\exp(\cos(v_j, v_i))}{\sum_{k \in N} \exp(\cos(v_k,v_i))}
-\end{equation}
-
-We can check the evidence that Eq.\ref{eq:real_embedding_relationship} is a good approximation functional form of is $p(i|j)$ in Fig.~\ref{fig:math_part}b, as high values of flow correspond to high Eq.\ref{eq:real_embedding_relationship} values.
+Then, we can rewrite the \ref{eq:gravity_model},
+\begin{equation}
+   \frac{T_{ij}}{\mu_{i} \mu_{j}} \propto \exp(\cos(v_i,v_j))
+\end{equation}
 
@@
 
-This finding relates to the objective function of the neural embedding model.
+This mathematical form relates to the objective function of the neural embedding model.
 The model attempts to maximize the average log probability of observing a target word in a sentence, $w_{t}$, given the words in the surrounding context window, $w_{t + k}$.
@@
 where $v_w$ and $v'_w$ are ``input'' and ``output'' vector representations of each word in the vocabulary.
-With facts that the cosine similarity of in-vectors is used as a measure of affinity in general, Eq.
-\ref{eq:skipgram_conditional_expanded} and Eq.
-\ref{eq:real_embedding_relationship} share a similar functional form, or exact same if vectors are normalized.
-
+We use Skip-gram negative sampling, and following the work by Levy and Goldberg, it is implicitly factorizing
+
+\begin{equation}
+    \label{eq:sgns_relation}
+    \log \left(\frac{\#(w,c) |D|}{\#(w) \#(c)} \right) - \log k
+\end{equation}
+where $\#(w)\text{,} \#(w) \text{ and } \#(c)$ denote the number of times word w, c and word-context-pair (w,c) in the corpus respectively.
+$k$ is the number of negative samples and $|D|$ is the size of the corpus.
+Eq.
+\ref{eq:sgns_relation} is symmetry matrix, result vector representation  $v_w$ and $v'_w$ are identical.
+With these relations, for a specific pair of words $(w_i, w_j)$,
+
+\begin{equation}
+    \label{eq:sgns_relation_w,i, w_j}
+    v_{w_i} \cdot v_{w_j} =  \log \left(\frac{\#(w_i, w_j) |D|}{\#(w_i) \#(w_j)} \right) - \log k
+\end{equation}
+
+$|D|$ and k is constant, then it can be rewritten as
+
+\begin{equation}
+    \label{eq:sgns_relation_w,i, w_j}
+     \frac{\#(w_i, w_j)}{\#(w_i) \#(w_j)}  \propto  \exp(v_{w_i} \cdot v_{w_j} )
+\end{equation}
+
+Combining Eq. \ref{eq:approxi_mass_term}, we have
+
+\begin{equation}
+    \label{eq:sgns_relation_w,i, w_j_combining}
+     \frac{T_{ij}}{\mu_{i} \mu_{j}}  \propto  \exp(v_{w_i} \cdot v_{w_j} )
+\end{equation}
+
+It is consistent with the finding on our model, we can say that there is a mathematical link between the neural embedding model and the gravity model.
 Hence, the neural embedding model can be an effective model for investigating any kind of mobility trajectory data, stemming from the mathematical relationship between it and the gravity model of mobility.

### 2020-04-10 paper/current/main.tex
add_ref
minor math edits

@@
 
-Then, we can rewrite the \ref{eq:gravity_model},
+Then, we can rewrite Eq.~\ref{eq:gravity_model} as,
 \begin{equation}
@@
 where $v_w$ and $v'_w$ are ``input'' and ``output'' vector representations of each word in the vocabulary.
-We use Skip-gram negative sampling, and following the work by Levy and Goldberg, it is implicitly factorizing
+We use Skip-gram negative sampling, and following the work by Levy and Goldberg \cite{levy2014neural}, consider the model as implicitely performing matrix factorization as shown below,
 
@@
 \end{equation}
-where $\#(w)\text{,} \#(w) \text{ and } \#(c)$ denote the number of times word w, c and word-context-pair (w,c) in the corpus respectively.
+
+where $\#(w)\text{, } \#(w) \text{ and } \#(c)$ denotes the number of times word $w$, $c$ and word-context-pair ($w$, $c$) in the corpus respectively.
 $k$ is the number of negative samples and $|D|$ is the size of the corpus.
@@
 
-$|D|$ and k is constant, then it can be rewritten as
+Where $|D|$ and $k$ are constants, such that the functional form can be re-written as,
 
@@
 
-Combining Eq. \ref{eq:approxi_mass_term}, we have
+Combining Eq.~\ref{eq:approxi_mass_term}, we have
 
@@
 
-It is consistent with the finding on our model, we can say that there is a mathematical link between the neural embedding model and the gravity model.
+This proportionality relationship is consistent with findings from our model, and so we can say that there is a mathematical link between the neural embedding model and the gravity model.
 Hence, the neural embedding model can be an effective model for investigating any kind of mobility trajectory data, stemming from the mathematical relationship between it and the gravity model of mobility.

### 2020-04-10 paper/current/main.tex

@@
 
-Then, we can rewrite Eq.~\ref{eq:gravity_model} as,
+It can be checked in Fig.\ref{fig:math_part}. With this approximation, we can rewrite Eq.~\ref{eq:gravity_model} as,
 \begin{equation}
@@
     \centering
-    \includegraphics[width=0.8\columnwidth]{\figdir/Math/use_all_log.pdf}
-    \caption{
-    \textbf{a}.   Relationship between $M_i$ and $\mu_i$.
-    \textbf{b}.
-Relationship between the conditional probability $p(j|i)$, Eq.
-\ref{eq:flux_conditional_prob} which is measured in the data and approximate functional form Eq.
-\ref{eq:real_embedding_relationship}}.
+    \includegraphics[width=0.4\columnwidth]{\figdir/Math/m_and_M.pdf}
+    \caption{
+    Relationship between $M_i$ and $\mu_i$.}.
     \label{fig:math_part}

### 2020-04-10 paper/current/main.tex

@@
 
-Let $T_{ij}$ represents the total \textbf{flux}, the number of people who moved between organizations $i$ and $j$.
+Let $T_{ij}$ represents the \textbf{flux}, the number of people who moved between organizations $i$ and $j$.
 $M_{i}$ and $M_{j}$ represent the size of an organization.
@@
 
-Combining Eq.~\ref{eq:approxi_mass_term}, we have
+In or model, $\#(w_i)$ and $\#(w_j)$ are total flux $M_i$ and $M_j$ respectively,  and $\#(w_i,w_j)$ is just  $T_{ij}$, flux between i and j. Then, we have same expression with gravity model,
 

### 2020-04-12 paper/current/main.tex
reflect_sada's comment

--- 2020-04-10 paper/current/main.tex
@@
 
-Let $T_{ij}$ represents the total \textbf{flux}, the number of people who moved between organizations $i$ and $j$.
-$M_{i}$ and $M_{j}$ represent the size of an organization.
-According to our gravity model on the embedding space,
+According to our observation on the embedding space,
 
@@
     \label{eq:gravity_model}
-    \frac{T_{ij}}{M_{i} M_{j}} \propto \exp(\cos(v_i,v_j))
-\end{equation}
-
-where the cosine similarity between two vectors, $\cos(v_{i}, v_{j})$, is defined as,
-
-\begin{equation}
-    \cos(v_i, v_j) = \frac{v_i \cdot v_j}{\Vert v_j \Vert \Vert v_i  \Vert}
-\end{equation}
-
-In the case of scientific co-affiliation, all movements are without direction (symmetric), meaning that  $T_{ij} = T_{ji}$.
-Let's denote $N$ as set of organizations in the data.
-Then, the total flux to or from $i$ can be written as
+    \frac{T_{ij}}{M_{i} M_{j}} \propto -\exp(d_{ij}) = - \exp(1 - \cos(v_i,v_j)) \propto \exp(\cos(v_i,v_j)),
+\end{equation}
+
+where $T_{ij}$ represents the \textbf{flux}, the number of people who moved between organizations $i$ and $j$,  $M_{i}$ and $M_{j}$ represent the size of an organization,  $d_{ij} = 1 - \cos(v_{i}, v_{j})$ is the embedding distance, and $\cos(v_{i}, v_{j})=\frac{v_{i} \cdot v_{j}}{\lVert v_{i} \rVert \lVert v_{j} \rVert}$  is the cosine similarity between two vectors.
+In the case of scientific co-affiliation, we assume all movements are without direction (symmetric), meaning that  $T_{ij} = T_{ji}$.
+
+To convert Eq. \ref{eq:gravity_model} to a flux-related term only, we replace  $M_*$ with $\mu_{i*}$, the total flux to or from $i$ which can be written as
 
@@
 	\label{eq:approxi_mass_term}
-    \mu_{i} = \sum_{k \in N} T_{ik} \propto M_i
-\end{equation}
-
-It can be checked in Fig.\ref{fig:math_part}. With this approximation, we can rewrite Eq.~\ref{eq:gravity_model} as,
-\begin{equation}
-   \frac{T_{ij}}{\mu_{i} \mu_{j}} \propto \exp(\cos(v_i,v_j))
+    \mu_{i} = \sum_{k \in N} T_{ik} \propto M_i,
+\end{equation}
+where $N$ as set of organizations in the data. It can be checked in Fig.\ref{fig:math_part}. With this approximation, we can rewrite Eq.~\ref{eq:gravity_model} as,
+\begin{equation}
+   \frac{T_{ij}}{\mu_{i} \mu_{j}} \propto \exp(\cos(v_i,v_j)).
 \end{equation}
@@
 
-where the conditional probability of observing one word, $w_{0}$, given another, $w_{1}$, is defined as,
+where the conditional probability of observing one word, $w_{O}$, given another, $w_{I}$, is defined as,
 
@@
 where $v_w$ and $v'_w$ are ``input'' and ``output'' vector representations of each word in the vocabulary.
-We use Skip-gram negative sampling, and following the work by Levy and Goldberg \cite{levy2014neural}, consider the model as implicitely performing matrix factorization as shown below,
+We use Skip-gram negative sampling, and following the work by Levy and Goldberg \autocite{levy2014neural}, consider the model as implicitly performing matrix factorization as shown below,
 
@@
     \label{eq:sgns_relation}
-    \log \left(\frac{\#(w,c) |D|}{\#(w) \#(c)} \right) - \log k
-\end{equation}
-
-where $\#(w)\text{, } \#(w) \text{ and } \#(c)$ denotes the number of times word $w$, $c$ and word-context-pair ($w$, $c$) in the corpus respectively.
-$k$ is the number of negative samples and $|D|$ is the size of the corpus.
-Eq.
-\ref{eq:sgns_relation} is symmetry matrix, result vector representation  $v_w$ and $v'_w$ are identical.
-With these relations, for a specific pair of words $(w_i, w_j)$,
+    \log \left(\frac{\#(w,c) |D|}{\#(w) \#(c)} \right) - \log k,
+\end{equation}
+
+where $\#(w)\text{, } \#(c) \text{ and } \#(w, c)$ denotes the number of times word $w$, $c$, and word-context-pair ($w$, $c$) in the corpus respectively.
+Variable $k$ is the number of negative samples and $|D|$ is the size of the corpus.
+
+Mathematically, the maximization of the objective function of the model yields $V=L$ and $V'=R$ where L and R are the left and right singular vectors of the matrix Eq.\ref{eq:sgns_relation}, respectively.
+Note that $V=L=R=V'$ because Eq.\ref{eq:sgns_relation} is a real symmetric matrix.
+With these relations, for a specific pair of words $(w_i ,w_j )$,
 
@@
     \label{eq:sgns_relation_w,i, w_j}
-    v_{w_i} \cdot v_{w_j} =  \log \left(\frac{\#(w_i, w_j) |D|}{\#(w_i) \#(w_j)} \right) - \log k
-\end{equation}
-
-Where $|D|$ and $k$ are constants, such that the functional form can be re-written as,
+    v_{w_i} \cdot v_{w_j} =  \log \left(\frac{\#(w_i, w_j) |D|}{\#(w_i) \#(w_j)} \right) - \log k,
+\end{equation}
+
+where $|D|$ and $k$ are constants, such that the functional form can be re-written as,
 
@@
     \label{eq:sgns_relation_w,i, w_j}
-     \frac{\#(w_i, w_j)}{\#(w_i) \#(w_j)}  \propto  \exp(v_{w_i} \cdot v_{w_j} )
-\end{equation}
-
-Combining Eq.~\ref{eq:approxi_mass_term}, we have
+     \frac{\#(w_i, w_j)}{\#(w_i) \#(w_j)}  \propto  \exp(v_{w_i} \cdot v_{w_j} ).
+\end{equation}
+
+In our model, $\#(w_i)$ and $\#(w_j)$ are total flux $M_i$ and $M_j$ respectively,  and $\#(w_i,w_j)$ is just  $T_{ij}$, flux between $i$ and $j$. Then, we have the same expression with gravity model,
 
@@
     \label{eq:sgns_relation_w,i, w_j_combining}
-     \frac{T_{ij}}{\mu_{i} \mu_{j}}  \propto  \exp(v_{w_i} \cdot v_{w_j} )
+     \frac{T_{ij}}{\mu_{i} \mu_{j}}  \propto  \exp(v_{i} \cdot v_{j} ).
 \end{equation}

### 2020-04-12 paper/current/main.tex
typo

@@
 When less than one kilometer, a distance of one is imputed.
-The embedding distance, $d_{ij}$, is calculated as the pairwise cosine distance between vectors from the learned organization embedding, where $v_{i}$ and $v_{j}$ represent the vectors and $d_{ij} = 1 - \frac{v_{i} \dot v_{j}}{\lVert v_{i} \rVert \lVert v_{j} \rVert}$.
+The embedding distance, $d_{ij}$, is calculated as the pairwise cosine distance between vectors from the learned organization embedding, where $v_{i}$ and $v_{j}$ represent the vectors and $d_{ij} = 1 - \frac{v_{i} \cdot v_{j}}{\lVert v_{i} \rVert \lVert v_{j} \rVert}$.
 

### 2020-04-13 paper/current/main.tex

@@
 Why does the word embedding model, originally designed for natural language processing, produce a reasonable distance that models gravity relationships between organizations?
-We find evidence of a theoretical connection between the two models, one that makes the skip-gram model applicable to embedding many forms of mobility trajectories.
-
-According to our observation on the embedding space,
+We find evidence of a theoretical connection between the two models, one that makes the neural embedding model applicable to embedding many forms of mobility trajectories.
+
+According to our observation on the embedding space from Eq.\ref{eq:linear_flux_emb},
 
@@
     \label{eq:gravity_model}
-    \frac{T_{ij}}{M_{i} M_{j}} \propto -\exp(d_{ij}) = - \exp(1 - \cos(v_i,v_j)) \propto \exp(\cos(v_i,v_j)),
-\end{equation}
-
+    \frac{T_{ij}}{M_{i} M_{j}} \propto \exp(-d_{ij}) = - \exp(- (1 - \cos(v_i,v_j))) \propto \exp(\cos(v_i,v_j)),
+\end{equation}
 where $T_{ij}$ represents the \textbf{flux}, the number of people who moved between organizations $i$ and $j$,  $M_{i}$ and $M_{j}$ represent the size of an organization,  $d_{ij} = 1 - \cos(v_{i}, v_{j})$ is the embedding distance, and $\cos(v_{i}, v_{j})=\frac{v_{i} \cdot v_{j}}{\lVert v_{i} \rVert \lVert v_{j} \rVert}$  is the cosine similarity between two vectors.
@@
 
-To convert Eq. \ref{eq:gravity_model} to a flux-related term only, we replace  $M_*$ with $\mu_{i*}$, the total flux to or from $i$ which can be written as
+To rewrite  Eq.\ref{eq:gravity_model} in terms of $T_{ij}$, we replace  $M_*$ with $\mu_{i*}$, the total flux to or from $i$ which can be written as
 
@@
 \end{equation}
-
 where the conditional probability of observing one word, $w_{O}$, given another, $w_{I}$, is defined as,
@@
 \end{equation}
-
 where $v_w$ and $v'_w$ are ``input'' and ``output'' vector representations of each word in the vocabulary.
-We use Skip-gram negative sampling, and following the work by Levy and Goldberg \autocite{levy2014neural}, consider the model as implicitly performing matrix factorization as shown below,
+We use Skip-gram negative sampling model, and following the work by Levy and Goldberg \autocite{levy2014neural}, consider the model as implicitly performing matrix factorization as shown below,
 
@@
     \label{eq:sgns_relation}
-    \log \left(\frac{\#(w,c) |D|}{\#(w) \#(c)} \right) - \log k,
-\end{equation}
-
-where $\#(w)\text{, } \#(c) \text{ and } \#(w, c)$ denotes the number of times word $w$, $c$, and word-context-pair ($w$, $c$) in the corpus respectively.
+    A = \left(a_{ij}\right)_{W*W} = \log \left(\frac{N(i, j) |D|}{N(i) N(j)} \right) - \log k,
+\end{equation}
+
+where $N(i)\text{, } N(j) \text{ and } N(i,j)$ denotes the number of times word $i$, $j$, and word-context-pair ($i$, $j$) in the corpus respectively.
 Variable $k$ is the number of negative samples and $|D|$ is the size of the corpus.
 
-Mathematically, the maximization of the objective function of the model yields $V=L$ and $V'=R$ where L and R are the left and right singular vectors of the matrix Eq.\ref{eq:sgns_relation}, respectively.
-Note that $V=L=R=V'$ because Eq.\ref{eq:sgns_relation} is a real symmetric matrix.
-With these relations, for a specific pair of words $(w_i ,w_j )$,
+From Matrix Eq.\ref{eq:sgns_relation}, we can get embedding vector with rank-d approximation by SVD, $A=L_d \Sigma_d R_d$.
+Mathematically, the maximization of the objective function of the model yields $V=L_d \sqrt{\Sigma_d}$ and $V'=\sqrt{\Sigma_d}R_d$ where L and R are the left and right singular vectors of the matrix Eq.\ref{eq:sgns_relation}, respectively.
+Note that $V=L_d \sqrt{\Sigma_d}=\sqrt{\Sigma_d}R_d=V'$ because Eq.\ref{eq:sgns_relation} is a real symmetric matrix.
+With these relations, for a specific pair of words $(i ,j )$,
 
@@
     \label{eq:sgns_relation_w,i, w_j}
-    v_{w_i} \cdot v_{w_j} =  \log \left(\frac{\#(w_i, w_j) |D|}{\#(w_i) \#(w_j)} \right) - \log k,
-\end{equation}
-
+    v_{i} \cdot v_{j} =  \log \left(\frac{N(i, j) |D|}{N(i) N(j)} \right) - \log k,
+\end{equation}
 where $|D|$ and $k$ are constants, such that the functional form can be re-written as,
@@
     \label{eq:sgns_relation_w,i, w_j}
-     \frac{\#(w_i, w_j)}{\#(w_i) \#(w_j)}  \propto  \exp(v_{w_i} \cdot v_{w_j} ).
-\end{equation}
-
-In our model, $\#(w_i)$ and $\#(w_j)$ are total flux $M_i$ and $M_j$ respectively,  and $\#(w_i,w_j)$ is just  $T_{ij}$, flux between $i$ and $j$. Then, we have the same expression with gravity model,
+     \frac{N(i, j)}{N(i) N(j)}  \propto  \exp(v_{i} \cdot v_{j} ).
+\end{equation}
+
+In our model, $N(i)$ and $N(j)$ are total flux $M_i$ and $M_j$ respectively,  and $N(i,j)$ is just  $T_{ij}$, flux between $i$ and $j$. Then, we have the same expression with gravity model,
 

### 2020-04-13 workflow/scripts/PlotGravityLawRelationship.R
Calculate dot product distance alongside cosine similarity

@@ -74,7 +74,8 @@ if (opt$geo == "same-country") {
 
 # Reduce the size to save on memory
 dist <- dist %>%
-  select(geo_distance, emb_distance, pprcos_distance, pprjsd_distance, gravity)
+  select(geo_distance, emb_distance, dot_distance,
+         pprcos_distance, pprjsd_distance,  gravity)
 
 axislabel <- "DEFAULT"
 # Select the appropriate metric using the --distance command line argument
@@ -105,6 +106,12 @@ if (opt$distance == "geo") {
 
   # Provide axis label
   axislabel <- "PPR Jensen-Shannon"
+} else if (opt$distance == "dot") {
+  dist <- dist %>%
+    rename(distance = dot_distance)
+
+  # Provide axis label
+  axislabel <- "Dot product distance"
 }
 
 # Calculate the logged gravity and select only relevant columns
@@ -201,7 +208,7 @@ if (opt$showcoef) {
   plot <- plot +
     # Add the r-squared coefficient to the plot
     ggpmisc::stat_poly_eq(formula = y ~ x,
-                          geom = "text",
+                          geom = "text_npc",
                           aes(label = paste(..rr.label.., sep = "~~~")),
                           parse=TRUE,
                           label.x.npc = ifelse(grepl("ppr", opt$distance, fixed = TRUE), 0.25, 0.75),

### 2020-04-13 workflow/scripts/calculate_org_w2v_similarity.py

@@ -20,6 +20,8 @@ parser = argparse.ArgumentParser()
 # System arguments
 parser.add_argument("-mod", "--model", help = "Path to word2vec model",
                     type = str, required = True)
+parser.add_argument("--type", help = "Type of similarity, 'dot' or 'cos'",
+                    type = str, required = True)
 parser.add_argument("-o", "--output", help = "Output data path",
                     type = str, required = True)
 
@@ -33,10 +35,19 @@ vocab = model.wv.vocab
 
 # Construct the distnace matrix
 D = defaultdict(lambda: defaultdict(float))
-for word1, word2 in combinations(vocab, 2):
-    temp_sim = model.similarity(word1,word2)
-    D[word1][word2] = temp_sim
-    D[word2][word1] = temp_sim
+
+# There is some code repetition here, but its worth it to
+# not check the args.type every iteration of the loop
+if args.type == 'cos':
+    for word1, word2 in combinations(vocab, 2):
+        temp_sim = model.similarity(word1, word2)
+        D[word1][word2] = temp_sim
+        D[word2][word1] = temp_sim
+elif args.type == 'dot':
+    for word1, word2 in combinations(vocab, 2):
+        temp_sim = np.dot(model.wv[word1], model.wv[word2])
+        D[word1][word2] = temp_sim
+        D[word2][word1] = temp_sim
 
 # Convert distance matrix to a dataframe
 distance_df = pd.DataFrame(D)

### 2020-04-13 workflow/scripts/PlotDotCosineRelationship.R
Plot the relationship between cosine similarity and dot product

@@ -1,0 +1,124 @@
+#
+# PlotDotCosineRelationship.R
+#
+# author: Dakota Murray
+#
+
+# Plotting options
+NUM_HEX_BINS = 20
+NUM_DISTANCE_BINS = 30
+
+FILL_GRADIENT_MIN = "white"
+FILL_GRADIENT_MAX = "#7f8c8d"
+BIN_BORDER_COLOR = "white"
+
+LEGEND_POSITION = "right" # can be "right", "bottom", "left", or None
+
+REGRESSION_LINE_COLOR = "#c0392b"
+
+# Plot dimensions
+FIG_WIDTH = 3
+FIG_HEIGHT = 3
+
+library(ggplot2)
+library(dplyr)
+suppressPackageStartupMessages(require(optparse))
+
+# Command line arguments
+option_list = list(
+  make_option(c("-i", "--input"), action="store", default=NA, type='character',
+              help="Path to file containing aggregate organization distances"),
+  make_option(c("-o", "--output"), action="store", default=NA, type='character',
+              help="Path to save output image")
+) # end option_list
+opt = parse_args(OptionParser(option_list=option_list))
+
+# Read the aggregated distance file
+dist = readr::read_csv(opt$input, col_types = readr::cols()) %>%
+  filter(count > 0) %>%
+  select(dot_distance, emb_distance)
+
+# Create binned values that will be plotted over top
+dist_binned <- dist %>%
+  mutate(
+    bin = cut(round(emb_distance, 2), NUM_DISTANCE_BINS)
+  ) %>%
+  arrange(bin) %>%
+  group_by(bin) %>%
+  summarize(
+    # Plot the point at the midpoint in each bin
+    pos = min(emb_distance) + ((max(emb_distance) - min(emb_distance)) / 2),
+    #pos = (as.numeric(first(bin)) * 0.05) - 0.025,
+    mu = mean(dot_distance, na.rm = T),
+    ci = 2.576 * (sd(dot_distance, na.rm = T) / sqrt(n())) # using the 99th percentile CI
+  )
+
+# Build the plot object
+plot <- dist %>%
+  ggplot(aes(x = emb_distance, y = dot_distance)) +
+    geom_hex(bins = NUM_HEX_BINS,
+             aes(fill = stat(log10(count))),
+             size = 0 # remove boundary
+    ) +
+    # Draw a regression line
+    stat_smooth(method = "lm",
+                formula = y ~ x,
+                color = REGRESSION_LINE_COLOR,
[…]

### 2020-04-20 paper/current/main.tex
new_math_part

@@
 After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance globally (Fig.~\ref{fig:gravity_performance}c--d) and for domestic (Fig.~\ref{fig:supp:gravity_correlation}e--f) and international mobility(Fig.~\ref{fig:supp:gravity_correlation}g--h).
+We also examine gravity model with dot product in the embedding space, the amount of variance explain ($R^{2} = 0.34$) by dot product outperforms that of geographic distance .
 Similarly, embedding distance outperforms ``diffusion''  distances such as those derived from calculating personalized-page rank scores (see supporting materials) on the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
@@
 We find evidence of a theoretical connection between the two models, one that makes the neural embedding model applicable to embedding many forms of mobility trajectories.
+For this section, we relax the cosine similarity as a dot product for simplicity.
 
@@
     \label{eq:gravity_model}
-    \frac{T_{ij}}{M_{i} M_{j}} \propto \exp(-d_{ij}) = - \exp(- (1 - \cos(v_i,v_j))) \propto \exp(\cos(v_i,v_j)),
-\end{equation}
-where $T_{ij}$ represents the \textbf{flux}, the number of people who moved between organizations $i$ and $j$,  $M_{i}$ and $M_{j}$ represent the size of an organization,  $d_{ij} = 1 - \cos(v_{i}, v_{j})$ is the embedding distance, and $\cos(v_{i}, v_{j})=\frac{v_{i} \cdot v_{j}}{\lVert v_{i} \rVert \lVert v_{j} \rVert}$  is the cosine similarity between two vectors.
+    \frac{T_{ij}}{M_{i} M_{j}} \propto \exp(-d_{ij}) =  \exp(- (-v_i \cdot v_j) \propto \exp(v_i \cdot v_j) 
+\end{equation}
+where $T_{ij}$ represents the \textbf{flux}, the number of people who moved between organizations $i$ and $j$,  $M_{i}$ and $M_{j}$ represent the size of an organization,  $d_{ij} = - v_{i}, v_{j}$ is the embedding distance.
 In the case of scientific co-affiliation, we assume all movements are without direction (symmetric), meaning that  $T_{ij} = T_{ji}$.
@@
 \begin{equation}
-   \frac{T_{ij}}{\mu_{i} \mu_{j}} \propto \exp(\cos(v_i,v_j)).
+   \frac{T_{ij}}{\mu_{i} \mu_{j}} \propto \exp(v_i,v_j).
 \end{equation}
@@
 
-From Matrix Eq.\ref{eq:sgns_relation}, we can get embedding vector with rank-d approximation by SVD, $A=L_d \Sigma_d R_d$.
-Mathematically, the maximization of the objective function of the model yields $V=L_d \sqrt{\Sigma_d}$ and $V'=\sqrt{\Sigma_d}R_d$ where L and R are the left and right singular vectors of the matrix Eq.\ref{eq:sgns_relation}, respectively.
-Note that $V=L_d \sqrt{\Sigma_d}=\sqrt{\Sigma_d}R_d=V'$ because Eq.\ref{eq:sgns_relation} is a real symmetric matrix.
-With these relations, for a specific pair of words $(i ,j )$,
+From Matrix Eq.\ref{eq:sgns_relation}, we can get embedding vector with rank-d approximation by SVD.
+The rank-d SVD factorize matrix A into product of three matrices  $L_d \Sigma R_d^T$, where $L_d$ and $R_d$ is $n \times d$ real matrices, and $\Sigma$ is    $d \times d$ diagonal matrix.
+
+Mathematically, the maximization of the objective function of the model yields $A_d = L_d \Sigma R_d^T$ such that $A_d = \arg \ \min_{Rank(A')=d} \Vert A' - A  \Vert$, which is the best approximate of the original matrix $A$.
+If we set, $V=L_d \Sigma$ and $V'=R_d$, then dot product between the rows of $V$ are equal to the dot products between rows of $A_d$ because $V$ is orthogonal real matrix  \autocite{levy2014neural}.
+With this relationship, we can rewrite the equation in terms of $V$.
+For a specific word pair $(i,j)$,
 
@@
 
+In embedding space, we can consider two proximity measures: cosine similarity and dot product.
+Cosine similarity only consider about angle difference of two embedding vectors, while dot product cares about angle and magnitude at the same time.
+If vectors are normalized, they are the same.
+In general, which measure is good depends on the task.
+If the task is desirable to ignore the magnitude, then cosine similarity is better, otherwise, the dot product is better.
+
 %
@@
 When less than one kilometer, a distance of one is imputed.
-The embedding distance, $d_{ij}$, is calculated as the pairwise cosine distance between vectors from the learned organization embedding, where $v_{i}$ and $v_{j}$ represent the vectors and $d_{ij} = 1 - \frac{v_{i} \cdot v_{j}}{\lVert v_{i} \rVert \lVert v_{j} \rVert}$.
+The embedding distance with the cosine similarity, $d_{ij}$, is calculated as the pairwise cosine distance between vectors from the learned organization embedding, where $v_{i}$ and $v_{j}$ represent the vectors and $d_{ij} = 1 - \frac{v_{i} \cdot v_{j}}{\lVert v_{i} \rVert \lVert v_{j} \rVert}$.
+Additionally, the embedding distance with the dot product, we use  $d_{ij} =  -v_{i} \cdot v_{j}$.
 

### 2020-04-20 paper/current/main.tex
typo
Minor changes while skimming main-text

@@
 A basic component of mobility is distance--people are more likely to move nearby than to cross continents.
-Although many alternative ways to quantify the distance~\autocite{boschma2005proximity} exist, geographic distance remains an unambiguous and foundational quantity for the distance.
+Although many alternative ways to quantify the distance exist~\autocite{boschma2005proximity}, geographic distance remains the unambiguous and foundational quantity.
 In turn, models of human mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation models ~\autocite{simini2012universal}, rely almost exclusively on geographic distance.
 However, distance is not always so straightforward as simple geography. 
-Geographic distance fails to capture the host of historical, linguistic, cultural, and cognitive distance that also drive mobility. 
+Geographic distance alone fails to capture the host of historical, linguistic, cultural, and cognitive distances that also drive mobility. 
 For instance, Australia may be physically close to Indonesia, but in terms of language, history, and shared culture, they are essentially neighbors to the United Kingdom.
@@
 
-Here, we propose a neural embedding model as an efficient means of encoding an effective measure of distance using large-scale data on mobility trajectories.
 It has been demonstrated that the neural embedding model preserves semantic relationships between words in a dense, continuous and meaningful low-dimensional vector representation~\autocite{mikolov2013word2vec}, and has been applied to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
@@
         An author published five papers across five time periods, with only one affiliation listed in the byline of each paper.
-        To each organization, a unique identifier is assigned, and they are assembled into a mobility sentence.
+        To each organization, a unique identifier is assigned, and they are assembled into a mobility sentence ordered by year of publication.
         \textbf{b.}
         In a more complex case, an author lists several affiliations on the byline of papers in $t_{2}$, $t_{3}$, and $t_{4}$. 
-Here, organization ids are still ordered by year, however order within a single year is random.
+        In the case where multiple organizations are listed within the same year, then organization IDs within a single year are randomized across each training iteration or "epoch" of the \textit{word2vec} model.
     }
@@
 
-To rewrite  Eq.\ref{eq:gravity_model} in terms of $T_{ij}$, we replace  $M_*$ with $\mu_{i*}$, the total flux to or from $i$ which can be written as
+To rewrite  Eq.\ref{eq:gravity_model} in terms of $T_{ij}$, we replace  $M_i$ with $\mu_{i}$, the total flux to or from $i$ which can be written as
 
@@
 Variable $k$ is the number of negative samples and $|D|$ is the size of the corpus.
-
 From Matrix Eq.\ref{eq:sgns_relation}, we can get embedding vector with rank-d approximation by SVD.
@@
 
-Scientific mobility is complex and can be defined in many possible ways~\autocite{robinson2019mobility}.
+Scientific mobility is complex and can be defined in many possible ways~\autocite{robinson2019mobility} and at multiple levels of analysis.
 Here, authors are classified as mobile when they have at least two distinct organization ids in their trajectory, meaning that they have published using two or more distinct affiliations between 2008 and 2019.

### 2020-04-20 paper/current/main.tex
Added supporting material paragraph and skeleton of others

@@
 \section{Supporting Information}
+
+%
+%
+\paragraph*{S1 Text}
+\label{si:text:mobility_science}
+{\bf Mobility and science.}
+TODO: why is mobility important to science?
+
+%
+%
+\paragraph*{S1 Text}
+\label{si:text:mobility_models}
+{\bf Modeling scientific mobility.}
+There are many ways of modeling scientific mobility from bibliographic data, the first consideration being the unit of analysis. 
+Most studies of mobility have focused on \textit{country-level} mobility--the flows of researchers across nations~\autocite{sugimoto2017mostimpact, scellato2015migrant, robinson-garcia2018indicators, franzoni2012foreign-born}.
+Practically, country-level analyses benefit from higher reliability, such that such that idiosyncrasies and errors inherent to bibliographic databases are mitigated by this higher level of aggregation.
+Epistemically, country-level analysis is useful for national science governance who aim to understand the status of their country in the global landscape and make informed policy decisions. 
+Analyses at lower levels of analysis are far less common. 
+\textit{Regional}-level scientific mobility--the flow of researchers between regions or cities within or across countries, has been only minimally studied~\autocite{vaccario2019mobility}, possibly due to lack of reliable long-term data and lack of policy relevance to national-level lawmakers.
+\textit{Organization}-level mobility has potential to inform institutional policy and for understand the composition of mobility within a single country or region, especially as it relates to organization performance, prestige, and inequality~\autocite{albarran2017topeconomic, deville2014career, morgan2018prestige, clauset2015hierarchy}.
+However, affiliation disambiguation and noise in bibliometric data has makes large-scale organization-level analysis challenging.
+Here, we learn neural-network embeddings of scientific mobility at the level of organizations using a curated bibliographic database.
+These embeddings are robust to noise, and so are capable of representing clear structure even amid issues with organizational disambiguation. 
+In doing so, embeddings also capture a more detailed understanding of mobility than has been previously studied.
+
+Another consideration when analyzing scientific mobility are what kinds of mobility to study. 
+Typical understandings of mobility are directional, meaning that movement is always \textit{from} one place and \textit{to} another. 
+Scientific mobility, however, is more complicated.
+For example, scientists often hold multiple affiliations at a time~\autocite{markova2016synchronous}, listing them as co-affiliations on a single paper, or even choosing a subset of affiliations to use for multiple simultaneous projects~\autocite{robinson2019mobility}.
+Even clearly-directional migration to another institution is complex--researchers may continue to publish with an old affiliation for projects that began before their move, and they may maintain social and organizational links  to their old institution (e.g., collaborators, projects, graduate students) such that there is no clear breakage after migrating.
+There are also a whole range of short-term scientific mobility, such as visiting scholarships and short-term visits that are only visible through intensive efforts such as manual extraction from CVs~\autocite{woolley2009cv, sandstrom2009cv, canibano2011temporary}.
+Here, we focus on more long-term mobility that can be derived from bibliographic data. 
+Due to the complexity of scientific mobility, we make the simplifying assumption that all scientific mobility is \textit{symmetric} or without direction such that any move from organization $A$ to organization $B$ is equivalent to a move from $B$ to $A$.
+By assuming non-directional mobility, all mobility events are commensurate, meaning that they can be treated identically in our analysis--this allows us to represent the complexity of mobility without making decisions for individual researcher's about the directional of their mobility or which is their main affiliation.
+Moreover, this assumption has the practical advantage of matching the data format expected by the \textit{word2vec} model, as well as the theoretical advantage of adhering to the symmetricity assumption of the gravity model of mobility.
+
+%
+% S1 TEXT
+\paragraph*{S1 Text}
+\label{si:text:mobility_traj}
+{\bf Building mobility trajectories.}
+
+For example, a researcher listing the set of affiliations $\{A, B, C\}$ on papers published in three different years will be considered two distinct instances of mobility, ${A \leftrightarrow B}$ and ${B \leftrightarrow C}$, where ${A \leftrightarrow B} = {B \leftrightarrow A}$ and  ${B \leftrightarrow C} = {C \leftrightarrow B}$.
 

### 2020-04-20 paper/current/main.tex
Another small change in main text
added new SI text section

@@
 
+Here, we propose a neural embedding model as an efficient means of encoding an effective measure of distance using large-scale data on mobility trajectories, one that encodes complex latent structure.
 It has been demonstrated that the neural embedding model preserves semantic relationships between words in a dense, continuous and meaningful low-dimensional vector representation~\autocite{mikolov2013word2vec}, and has been applied to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
@@
 {\bf Mobility and science.}
-TODO: why is mobility important to science?
+
+Mobility is essential to the scientific enterprise.
 
@@
 
-For example, a researcher listing the set of affiliations $\{A, B, C\}$ on papers published in three different years will be considered two distinct instances of mobility, ${A \leftrightarrow B}$ and ${B \leftrightarrow C}$, where ${A \leftrightarrow B} = {B \leftrightarrow A}$ and  ${B \leftrightarrow C} = {C \leftrightarrow B}$.
+We adopt a data-driven approach to constructing mobility trajectories, making as little adjustment to the raw bibliometric data as possible. 
+For each mobile researcher (having at least two distinct affiliations), we construct a mobility trajectory based on the affiliations listed on their published papers indexed in the Web of Science database between 2008 and 2019.
+An author is considered mobile if they published with at least two distinct affiliations during the time period of study. 
+Affiliations map to disambiguated organizations, each of which matches to a unique identifier. 
+Affiliations in a trajectory are first ordered by year of publication.
+For example, if an author published with affiliation $A$ in $t_{0}$, affiliation $B$ in $t_{1}$, and $A$ again in $t_{2}$, then their ordered mobility trajectory would be $\{A, B, C\}$.
+
+In the case that multiple affiliations are used within a single year, affiliations listed on publications published in that year are shuffled between each stage of the \textit{word2vec} training process (each epoch).
+For example, an author who published with affiliation $A$ in $t_{0}$, and affiliations $B, C$ in $t_{1}$ could appear as one of $\{A, B, C\}$ or $\{A, C, B\}$ in each training iteration. 
+This effectively removes the effect of order within a year, as order cannot be meaningfully established based on co-affiliations in a single paper, or on different affiliations listed on separate papers, publication of which is not necessarily representative of the actual completion of the project.
+
+Other than restricting to only mobile researchers, we do not perform any filtering or reductions to mobility trajectories.
+For example, in the case than an author publishes with organization $A$ four times in $t_{0}$, and affiliation $B$ two times in $t_{1}$, then their trajectory will be $\{A, A, A, A, B, B\}$. 
+This means that mobile authors who publish more papers will have longer trajectories.
+However, \textit{word2vec} will skip duplicate consecutive organization IDs, effectively eliminating the impact of these long repetitive trajectories.
 

### 2020-04-20 paper/current/main.tex
Added supp text outlining importance of mobility

@@
 
-Mobility is essential to the scientific enterprise.
+As scholars move, they bring their knowledge, their skills, and their social connections with them--collectively the movements of researchers shapes the structure and direction of the global scientific enterprise.
+For example, prestige-driven mobility between doctoral-granting and employing institution is highly unequal~\autocite{clauset2015hierarchy, deville2014career}, which impacts the diffusion of ideas across academia~\autocite{morgan2018prestige}.
+By placing researchers in new social settings, mobility can lead to the formation of new collaborative relationships~\autocite{rodrigues2016mobility}, which in turn spur the further diffusion of knoweldge and new innovations~\autocite{braunerhjelm2020labor, azoulay2011diffusion, kaiser2018innovation, armano2017innovation}.
+Perhaps resulting from the selection effects of who gets to move, or the reconfiguring of social and epistemic networks, movement is associated with increased scientific impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}.
+At the national level, the understanding of mobility has progressed beyond simplistic narratives of brain drain and brain gain, and instead adopts a new perspective of \textit{flows} of talent~\autocite{meyer2001network, ioannidis2014braindrain, gaillard1998circulation}.
+Under this flow model, a mobile researcher is viewed as contributing to both their origin and destincation countries, a perspective that fosters that is evidenced by the strong science of open countires~\autocite{wagner2017open}.
+Perhaps because of these individual and national benefits, policy-makers have come to recognize the importance of global mobility~\autocite{box2008competition, oecd2010innovation}. 
+Movement is a key mechanism that has clear impacts on the composition and direction of the global scientific workforce and our collective scientific understanding. 
+Understanding the structure and dynamics of mobility is thus essential for understanding global science.
 

### 2020-04-20 paper/current/main.tex
updating SI text section numbers
other minor changes

@@
 Geographic distance alone fails to capture the host of historical, linguistic, cultural, and cognitive distances that also drive mobility. 
-For instance, Australia may be physically close to Indonesia, but in terms of language, history, and shared culture, they are essentially neighbors to the United Kingdom.
+For instance, Australia may be physically close to Indonesia, but in terms of shared language, history, and culture, they are essentially neighbors to the United Kingdom.
 Then, how can we quantify meaningful, useful distance between institutions, cities, and countries?
@@
         In a more complex case, an author lists several affiliations on the byline of papers in $t_{2}$, $t_{3}$, and $t_{4}$. 
-        In the case where multiple organizations are listed within the same year, then organization IDs within a single year are randomized across each training iteration or "epoch" of the \textit{word2vec} model.
+        In the case where multiple organizations are listed within the same year, then organization IDs within a single year are randomized across each training iteration or "epoch" of the \textit{word2vec} model (for more detail, see Supporting Materials).
     }
@@
 %
-%
-\paragraph*{S1 Text}
+% S2 Text
+\paragraph*{S2Text}
 \label{si:text:mobility_models}
 {\bf Modeling scientific mobility.}
+
 There are many ways of modeling scientific mobility from bibliographic data, the first consideration being the unit of analysis. 
@@
 %
-% S1 TEXT
-\paragraph*{S1 Text}
+% S3 TEXT
+\paragraph*{S3 Text}
 \label{si:text:mobility_traj}
@@
 %
-% S1 TEXT
-\paragraph*{S1 Text}
+% S4 TEXT
+\paragraph*{S4 Text}
 \label{si:text:ppr_dist}
@@
 %
-% S2 TEXT
-\paragraph*{S2 Text}
+% S5 TEXT
+\paragraph*{S5 Text}
 \label{si:text:organizations}
@@
 %
-% S3 TEXT
-\paragraph*{S3 Text}
+% S6 TEXT
+\paragraph*{S6 Text}
 \label{si:text:disambiguation}

### 2020-04-20 paper/current/main.tex
new supporting figures

@@
 Globally, the effect of geography is conspicuous; organizations tend to form clusters based on their national affiliations and national clusters tend to be near their geographic neighbors. 
-At the same time, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions.
+At the same time, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions much more clearly than altenrative network visualizations (Fig.~\ref{fig:supp:network_vis}).
 
@@
 	}
+	\label{fig:supp:cosdot}
+\end{figure}
+
+%
+% Figure - Dot product and cosine similarity
+%
+\begin{figure}[p!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/Math/d300_ws1_dot_cosine.pdf}
+	\caption{
+		\textbf{Cosine distance is correlated with dot product similarity.}
+		Calculated as the pairwise cosine distance (x-axis) and dot product similarity (y-axis) between organizational vectors. 
+		The two quantities are correlated with $R^{2} = 0.73$. 
+		Color indicates frequency of organizations in hex bin. 
+		Black dots are the mean dot product similarity for binned sets of embedding similarity and error bars correspond to 95\textsc{th} percentile confidence intervals. 
+		Red line is line of best fit.
+	}
 	\label{fig:supp:hyperparams}
@@
 	\label{fig:supp:gravity_prediction_subsets}
+\end{figure}
+
+%
+% Figure - Dot product distance
+%
+\begin{figure}[p!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_dot.pdf}
+	\caption{
+		\textbf{Personalized page rank with cosine distance.}
+		Performance of dot product similarities in explaining and predicting mobility.
+		Similarity scores are calculated as the pairwise dot product between organizational vectors. 
+		Dot product similarity performs better than geographic distance, though worse than cosine similarity in explaining global mobility (\textbf{a}), or domestic (\textbf{b}) or international (\textbf{c}) country mobility.
+		Red line is line of best fit.
+		Black dots are mean flux across binned distances.
+		Color indicates frequency of organization pairs within each hex bin.
+		Similarly, PPR distance performs comparably to geographic distance in predicting global (\textbf{d}), domestic (\textit{e}) and international (\textbf{f}) scientific mobility.
+		Boxplots show distribution of actual flux for binned values of predicted flux.
+		Box color corresponds to the degree to which the distribution overlaps $x = y$.
+	}
+	\label{fig:supp:gravity_dot}
 \end{figure}
@@
 %
+% Figure - Global Network Projection
+%
+\begin{figure}[hp!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/Projection/co_occur_with_label.pdf}
+	\caption{
+		\textbf{Visualization of global mobility network.}
+		The network demonstrates country-level structure, but not at the detail or the extent of the global UMAP projection (Fig.~\ref{fig:projection}a). 
+		Each node corresponds to an organization, whereas  weighted edges (not shown) correspond to the flow of mobile researchers between the two organization.
+		Nodes are colored by the country of the organization. 
+		Nodes are positioned using the force atlas layout algorithm. 
+	}
+	\label{fig:supp:proj_newyork}
+\end{figure}
+
+%
 % Figure - New York Projection
@@
 	}
-	\label{fig:supp:semaxis_sectors}
+	\label{fig:supp:network_vis}
 \end{figure}

### 2020-04-20 paper/current/main.tex
fix labels

@@
 
-Where the \textit{expected flux}, $\hat{T_{ij}}$, or expected number of authors co-affiliated with a pair organizations during the time period is proportional to the organization's sizes, $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+Where the \textit{expected flux}, $\hat{T_{ij}}$, or expected number of authors co-affiliated with a pair organizations during the time period is proportional to the organization's sizes (both mobile and non-mobile researchers, see Data and Methods), $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
 We consider two distances, the geographic distance between the organizations as a baseline, and the \textit{embedding distance} defined as the cosine distance between the organization's vector in the trained embedding space.
@@
 By considering mobility between all organization types, organization embeddings offer a new means of reasoning about the prestige of organizations typically excluded from rankings such as government organizatioss (Fig.~\ref{fig:supp:semaxis_sectors}a), research institutes (Fig.~\ref{fig:supp:semaxis_sectors}b), and teaching colleges (Fig.~\ref{fig:supp:semaxis_sectors}c)
-
+\ref{fig:supp:sem
 %
@@
 	}
-	\label{fig:supp:proj_newyork}
+	\label{fig:supp:network_vis}
 \end{figure}
@@
 	}
-	\label{fig:supp:network_vis}
+	\label{fig:supp:semaxis_sectors}
 \end{figure}

### 2020-04-20 paper/current/main.tex
additional language stressing linguistic properties of embeddings

--- 2020-04-20 paper/current/main.tex
@@
 By treating geo-located organizations analogously to words and trajectories analogously to sentences, we learn vector-space embedding of organizations using a neural embedding method (Fig.~\ref{fig:methods:mobility_sentence}).
-In the resulting embedding, each organization corresponds to a vector, and the \textit{cosine distance} between vectors represents the distance in the landscape of scientific mobility.
+In the resulting embedding, each organization corresponds to a vector, and vectors relate to one another \textit{semantically}--just as with language, organizations are \textit{semantically} similar when they share similar co-affiliation \textit{contexts}.
+We measure the semantic distance between organization vectors using \textit{cosine distance}, and use this to model distance in the landscape of scientific mobility.
 
@@
 
-Where the \textit{expected flux}, $\hat{T_{ij}}$, or expected number of authors co-affiliated with a pair organizations during the time period is proportional to the organization's sizes, $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+Where the \textit{expected flux}, $\hat{T_{ij}}$, or expected number of authors co-affiliated with a pair organizations during the time period is proportional to the organization's sizes (both mobile and non-mobile authors, see Data and Methods), $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
 We consider two distances, the geographic distance between the organizations as a baseline, and the \textit{embedding distance} defined as the cosine distance between the organization's vector in the trained embedding space.
@@
 Globally, the effect of geography is conspicuous; organizations tend to form clusters based on their national affiliations and national clusters tend to be near their geographic neighbors. 
-At the same time, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions much more clearly than altenrative network visualizations (Fig.~\ref{fig:supp:network_vis}).
+At the same time, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions much more clearly than alternative network visualizations (Fig.~\ref{fig:supp:network_vis}).
 
@@
 For instance, does the mobility embedding encode information about the prestige or universities?
-In addition to encoding national characteristics, the embedding also encodes domestic geography and latent hierarchy.
-Leveraging the unique semantic properties of the organization embedding, we employ the SemAxis approach~\autocite{an2018semaxis} and define two semantic axes.
+We show that, in addition to encoding national characteristics, the embedding also encodes domestic geography and latent hierarchy.
+
+By treating organizations analogously to words and trajectories to sentences, we embed organizations in a way that preserves \textit{semantic} relationships, meaning organizations that share similar co-affiliation \textit{contexts} will in turn be similar (see Data and Methods).
+Leveraging these unique semantic properties, we employ the SemAxis approach~\autocite{an2018semaxis} and define two axes.
 The first is the California--Massachusetts axis defined by the mean vector of universities in California on one end, and in Massachusetts on the other. 
@@
 census region) set of universities.
-A university projected onto the axis corresponds to their nearness to the mean vector defining each pole (Fig.~\ref{fig:semaxis}a).
+A university projected onto the axis corresponds to their relative nearness to the mean vector defining each pole (Fig.~\ref{fig:semaxis}a).
 
 Generally, universities in Western states, such as Arizona (Fig.~\ref{fig:supp:semaxis_states}b) are nearer to the California end of the axis, whereas states in the Northeast such as New York (Fig.~\ref{fig:supp:semaxis_states}f) and Connecticut (Fig.~\ref{fig:supp:semaxis_states}e) are nearer the Massachusetts end.
-Universities geographically distant from both California and Massahcussets are less aligned with either, such as Texas (Fig.~\ref{fig:supp:semaxis_states}g)s and Florida (Fig.~\ref{fig:supp:semaxis_states}i).
+Universities geographically distant from both California and Massachusetts are less aligned with either, such as Texas (Fig.~\ref{fig:supp:semaxis_states}g)s and Florida (Fig.~\ref{fig:supp:semaxis_states}i).
 
@@
 By considering mobility between all organization types, organization embeddings offer a new means of reasoning about the prestige of organizations typically excluded from rankings such as government organizatioss (Fig.~\ref{fig:supp:semaxis_sectors}a), research institutes (Fig.~\ref{fig:supp:semaxis_sectors}b), and teaching colleges (Fig.~\ref{fig:supp:semaxis_sectors}c)
+\ref{fig:supp:sem
 
@@
 		\textbf{b.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity to the \textit{Elite} end of the axis prestige axis \textit{a}.
-		White points are those top and bottom 20 universities aggregated to define the ends of the axis.
-		The grey box corresponds to the top 20 and bottom 20 ranks.
-	  	The estimate of the spearman rank correlation between the SemAxis and Times ranking is 0.81 (n = 145).
+		White points are those top and bottom 5 universities aggregated to define the ends of the axis.
+		The grey box corresponds to the top 5 and bottom 5 ranks.
+	  		  	Even when considering only a total of ten organization vectors, the estimate of the spearman rank correlation between the SemAxis and Times ranking is 0.73 (n = 145).
 	}
@@
 
-where $m_{i}$ and $m_{j}$ are the yearly-average size of each organization during the time window, and $f(r_{ij})$ is a distance-decaying function  between the two organizations.
+where $m_{i}$ and $m_{j}$ are the organization masses, or the yearly-average count of unique authors affiliated with each organization during the time window, and $f(r_{ij})$ is a distance-decaying function  between the two organizations.
 There are two popular forms of the $f(r_{ij})$.
@@
 responses and labeled historical data \autocite{kozlowski2018geometry}.
-In the case of scientific mobility, SemAxis offers a means of operationalizing abstract relationships between organizations.
+
+In this analysis, we embed organization identifiers and trajectories, rather than words and sentences, however mobility can be thought of semantically, just like language. 
+Under this view, organizations can be thought of as similar when they have similar \textit{contexts}--that is, authors affiliated with that organization also tend to co-affiliate the same set of other organizations.
+By treating organizations analogously to words and trajectories analogously to sentences, we can use SemAxis to leverage the semantic properties of the resulting embedding vectors to operationalize abstract relationships between organizations.
 

### 2020-04-20 paper/current/main.tex
removed extra incomplete reference

@@
 Universities at the bottom of this axis tend to be regional universities with lower national profiles.
-By considering mobility between all organization types, organization embeddings offer a new means of reasoning about the prestige of organizations typically excluded from rankings such as government organizatioss (Fig.~\ref{fig:supp:semaxis_sectors}a), research institutes (Fig.~\ref{fig:supp:semaxis_sectors}b), and teaching colleges (Fig.~\ref{fig:supp:semaxis_sectors}c)
-\ref{fig:supp:sem
+By considering mobility between all organization types, organization embeddings offer a new means of reasoning about the prestige of organizations typically excluded from rankings such as government organizatioss (Fig.~\ref{fig:supp:semaxis_sectors}a), research institutes (Fig.~\ref{fig:supp:semaxis_sectors}b), and teaching colleges (Fig.~\ref{fig:supp:semaxis_sectors}c).
 

### 2020-04-21 paper/current/main.tex

@@
 After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance globally (Fig.~\ref{fig:gravity_performance}c--d) and for domestic (Fig.~\ref{fig:supp:gravity_correlation}e--f) and international mobility(Fig.~\ref{fig:supp:gravity_correlation}g--h).
-We also examine gravity model with dot product in the embedding space, the amount of variance explain ($R^{2} = 0.34$) by dot product outperforms that of geographic distance .
+We also examine gravity model with dot product in the embedding space, the amount of variance explain ($R^{2} = 0.34$) by dot product outperforms that of geographic distance (Fig.~\ref{fig:supp:gravity_dot}).
 Similarly, embedding distance outperforms ``diffusion''  distances such as those derived from calculating personalized-page rank scores (see supporting materials) on the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
@@
 \end{equation}
+
 where $T_{ij}$ represents the \textbf{flux}, the number of people who moved between organizations $i$ and $j$,  $M_{i}$ and $M_{j}$ represent the size of an organization,  $d_{ij} = - v_{i}, v_{j}$ is the embedding distance.

### 2020-04-21 paper/current/notes/gm-vs-w2v/main.tex
Add a node on the word2ve and the gravity model

\documentclass[12pt]{article} %{{{
\usepackage[margin=1in]{geometry}

% Figures
\usepackage{graphicx}
\graphicspath{{../../figs/}}

% Math
\usepackage{amsmath}
\usepackage{amssymb}
\DeclareMathOperator*{\argmin}{\arg\!\min}
\DeclareMathOperator*{\argmax}{\arg\!\max}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\diag}{diag}
\def\given{\mid}

% abbreviations
\def\eg{e.g.,~}
\def\ie{i.e.,~}
\def\cf{cf.\ }
\def\viz{viz.\ }
\def\vs{vs.\ }

% math notation
\usepackage{bm}
\def\tnull{{\text{null}}}
\def\vec#1{{\bm #1}}
\def\mat#1{\mathbf{#1}}

% Refs
\usepackage{biblatex}
\addbibresource{main.bib}

\usepackage{url}

\newcommand{\secref}[1]{Section~\ref{sec:#1}}
\newcommand{\figref}[1]{Fig.~\ref{fig:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
%\newcommand{\eqnref}[1]{\eqref{eq:#1}}
%\newcommand{\thmref}[1]{Theorem~\ref{#1}}
%\newcommand{\prgref}[1]{Program~\ref{#1}}
%\newcommand{\algref}[1]{Algorithm~\ref{#1}}
%\newcommand{\clmref}[1]{Claim~\ref{#1}}
%\newcommand{\lemref}[1]{Lemma~\ref{#1}}
%\newcommand{\ptyref}[1]{Property~\ref{#1}}

% for quick author comments 
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\definecolor{light-gray}{gray}{0.8}
\definecolor{light-blue}{RGB}{33,150,243}
\definecolor{light-green}{RGB}{76, 175, 80}
\def\del#1{ {\color{light-gray}{#1}} }
\def\yy#1{\footnote{\color{red}\textbf{yy: #1}} }
\def\sada#1{\footnote{\color{light-blue}\textbf{sk: #1}} }
\def\jisung#1{\footnote{\color{light-green}\textbf{js: #1}} }

%}}}

\begin{document} %{{{

\title{Note on the word2vec and the gravity model} %{{{
\date{\today}
\author{Sadamori Kojaku}
\maketitle %}}}

\section{The word2vec and the euclidean distance}

With the word2vec, one writes the probability of target node $j$ given center node $i$ as 
\begin{align}
  \label{eq:model_node2vec}
    P_{\text{W2V}}\left(j \given i\right) := \frac{1}{Z_i}\exp\left(\vec{u} ^\top _{i} \vec{v}_{j}\right), 
\end{align}
where vectors $\vec{u}_i$ and $\vec{v}_i$ are the column vectors of length $K$ that represent the coordinates of $i$ and $j$ in the embedding space spanned by in-vectors and out-vectors, respectively.
Variable $Z_i$ is the normalization constant, i.e., $Z_i:= \sum_{\ell=1}^N \exp\left(\vec{u} ^\top _{i} \vec{v}_{\ell}\right)$. 
Denote by $d(\vec{u},\vec{u}')$ the distance between nodes $i$ and $j$ for the in-vector, i.e., 
\begin{align}
    \label{eq:distance}
    d(\vec{u},\vec{u}'):= \sqrt{\sum_{k=1}^K \left(u_{k} - u'_{k}\right)^2}.
\end{align}
We assume that the in-vectors are equal to the out-vectors, i.e., $\vec{v}_j = \vec{u}_j$.
Then, the dot similarity for $\vec{u}_i$ and $\vec{v}_j$ is given by 
\begin{align}
    \label{eq:dotsim}
    \vec{u}_i ^\top \vec{v}_j = \frac{1}{2}\left[ ||\vec{u}_i|| + ||\vec{u}_j|| - d\left(\vec{u}_i, \vec{u}_j\right)^2 \right],
\end{align}
which leads 
\begin{align}
    \exp\left( \vec{u}_i ^\top \vec{v}_j \right) &= \frac{\exp\left( ||\vec{u}_i||/2 + ||\vec{u}_j||/2 \right)}{\exp\left[ d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2 \right]} \nonumber \\
                                                 &= \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2\right]}, \label{eq:exp_distance_form}
\end{align}
where $s_i:=\exp(||\vec{u}_i||/2)$. 
Substituting Eq.~\eqref{eq:exp_distance_form} into Eq.~\eqref{eq:model_node2vec} yields
\begin{align}
    \label{eq:model_node2vec_distance}
    P_{\text{W2V}}\left(j \given i\right) &:= \frac{1}{Z_i}\cdot \frac{s_is_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2/2\right]}. 
\end{align}
The walkers in point $i$ tend to move to the points with a large $s_j$ more than those with a smaller $s_j$.
Thus, variable $s_j$ represents the {\it pulling force} for node $j$\sada{tentative naming}. 
It turns out that $s_j$ is a mass variable for the gravity model (see Section 2).

\section{The word2vec is a special case of the gravity model}

The gravity model generates the flow from $i$ to $j$ by 
\begin{align}
    \label{eq:gravity_model}
    T_{ij}:= G M_i M_j f\left(d(\vec{u}_i,\vec{u}_j)\right),
\end{align}
where $M_i$ ($M_i>0$) is the mass for the gravity model, $f$ is a function for the distance, and 
$G$ is the constant analogous to the gravitational constant in physics.

In migration study, $M_i$ is often fixed to the number of people at a point $i$ (e.g., city and country), which is a restricted version of the gravity model.
We show that the word2vec is free from the restriction and automatically learns the mass $M_i$ from data, which may not be equal to the number of people at a point.
To avoid the confusion, we denote by $n_i$ the number of people at a point $i$ in the followings.

We regard $P_{\text{W2V}}(j \vert i)$ as the transition probability from $i$ to $j$ in a Markov process.
Then, the number of people that move from $i$ to $j$ (i.e., flow) in one step is given by 
\begin{align}
    \label{eq:flow}
    T_{ij}:= n_i P_{\text{W2V}}(j \vert i).
\end{align}
We assume that the Markov process satisfies detailed balanced condition:  
\begin{align}
    \label{eq:detailed_balanced}
    n_i P_{\text{W2V}}\left(j \vert i \right) = n_j P_{\text{W2V}}\left(i \vert j \right).
\end{align}
In other words, the flow is symmetric (i.e., $T_{ij} = T_{ji}$) and $n_i$ is the stationary distribution for the Markov process.
Equation \eqref{eq:detailed_balanced} yields 
\begin{align}
    &\frac{n_i}{Z_i}\cdot \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2\right]} = \frac{n_j}{Z_j}\cdot \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2 \right]} \\
    &\iff \frac{n_i}{Z_i} = \frac{n_j}{Z_j} =: G', \label{eq:const}
\end{align}
where $G'$ is a constant. 
Substituting Eq.~\eqref{eq:model_node2vec_distance} into Eq.~\eqref{eq:flow} and exploiting Eq.~\eqref{eq:const} yield 
\begin{align}
    \label{eq:flow_gravity_model}
    T_{ij} &= n_i P_{\text{W2V}}\left(j \vert i \right)\nonumber \\
           &= \frac{n_i}{Z_i} \cdot \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2 \right]}\nonumber \\ 
           &= G' \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2 \right]}. 
\end{align}
Remind that $T_{ij}:= G M_i M_j f\left(d\left(\vec{u}_i,\vec{u}_j\right)\right)$ in the gravity model.
Thus, the word2vec is a gravity model with $M_i=s_i$ and $f\left(d\left(\vec{u}_i,\vec{u}_j\right)\right) = 1/\exp\left[d\left(\vec{u}_i,\vec{u}_j\right) ^ 2 /2\right]$.
Popularity $s_i$ corresponds to the mass in the gravity model but does not have a solid physical meaning.

\section{Population, pulling force and gravitational potential}

What is pulling force $s_i$? Is it related to the population $n_i$ in each point?
To answer these questions, we rewrite $n_i$ as a function of $s_i$ as follows. 
With Eq.~\eqref{eq:const}, we rewrite $n_i$ as 
\begin{align}
    n_i &= G' Z_i \nonumber \\
        &= G' s_i \sum_{\ell=1}^N s_\ell f\left(d\left(\vec{u}_i,\vec{u}_j\right)\right) \nonumber \\ 
        &= - s_i \Phi(\vec{u}_i), \label{eq:flow_gravity_model_2} %\nonumber \\ 
\end{align}
where $\Phi(\vec{u})$ is the potential given by 
\begin{align}
    \Phi(\vec{u}):=-G' \sum_{\ell=1}^N s_\ell f\left(d\left(\vec{u},\vec{u}_j\right)\right).
\end{align}
Potential $\Phi(\vec{u})$ is analogous to the gravitational potential, i.e., $GM/d$, where $m$ is the mass and $d$ is the distance from the mass.
In other words,  $\Phi(\vec{u})$ is the gravitational potential for the field, where 
each point $\ell$ has a mass $s_{\ell}$ and is away from $u$ with distance $d(\vec{u},\vec{u}_\ell)$, and the effect of the mass decays by the factor of $\exp\left[d(\vec{u},\vec{u}_\ell) ^2 /2\right]$.

Population $n_i$ is given by $-s_i\Phi(\vec{u}_i)$. What does it mean for the mobility for scientists?
Suppose two institutions A and B. They have many influx from other institutions for different reasons:
(i) A is indeed an attractive institution which everyone on the planet wants to go but isolated from other institutions;
(ii) B is not attractive but close to many attractive institutions (e.g., small universities in a big city) and thus gain many influx from surrounding institutions.
Pulling force $s_i$ indicates the first factor, i.e., how attractive the individual institution is. 
Potential $\Phi(\vec{u})$ indicates how attractive the field is, accounting for the second factor.
The population is large when pulling force $s_i$ is large or the potential $\Phi(\vec{u}_i)$ is small.

\section*{Random idea}
\begin{itemize}
    \item Compute the potential in the embedding and visualize it
    \item Does the potential predict the birth of new journals?
    \item What does $s_i$ indicate in the mobility data? Correlation to prestige?
    \item Use different kernel e.g., $f(d) = 1/exp(d)$, $f(d)=1/exp(\text{L1 norm})$ in the word2vec.
\end{itemize}
%\section*{Note}
%\begin{itemize}
%    \item The mass $m_i$ in this draft is different from $M_i$ in the manuscript. Variable $m_i$ is a parameter for the gravity model. 
%\end{itemize}

\printbibliography{}

\end{document} %}}}

### 2020-04-21 paper/current/notes/gm-vs-w2v/main.tex
fix typo

@@
 Variable $Z_i$ is the normalization constant, i.e., $Z_i:= \sum_{\ell=1}^N \exp\left(\vec{u} ^\top _{i} \vec{v}_{\ell}\right)$. 
-Denote by $d(\vec{u},\vec{u}')$ the distance between nodes $i$ and $j$ for the in-vector, i.e., 
+Denote by $d(\vec{u},\vec{u}')$ the distance between the in-vectors, i.e., 
 \begin{align}
@@
 Thus, the word2vec is a gravity model with $M_i=s_i$ and $f\left(d\left(\vec{u}_i,\vec{u}_j\right)\right) = 1/\exp\left[d\left(\vec{u}_i,\vec{u}_j\right) ^ 2 /2\right]$.
-Popularity $s_i$ corresponds to the mass in the gravity model but does not have a solid physical meaning.
+Pulling force $s_i$ corresponds to the mass in the gravity model but does not have a solid physical meaning.
 
@@
 What is pulling force $s_i$? Is it related to the population $n_i$ in each point?
-To answer these questions, we rewrite $n_i$ as a function of $s_i$ as follows. 
+To answer the questions, we rewrite $n_i$ as a function of $s_i$ as follows. 
 With Eq.~\eqref{eq:const}, we rewrite $n_i$ as 
@@
 \end{align}
-Potential $\Phi(\vec{u})$ is analogous to the gravitational potential, i.e., $GM/d$, where $m$ is the mass and $d$ is the distance from the mass.
+Potential $\Phi(\vec{u})$ is analogous to the gravitational potential, i.e., $-GM/d$, where $M$ is the mass and $d$ is the distance from the mass.
 In other words,  $\Phi(\vec{u})$ is the gravitational potential for the field, where 

### 2020-04-21 workflow/scripts/BuildAggregateDistanceFile.R
Compute and plot euclidean distances

@@ -28,6 +28,8 @@ option_list = list(
               help="Path to file containing organization PPR distances"),
   make_option(c("--dot"), action="store", default=NA, type='character',
               help="Path to file containing organization dot product similarities"),
+  make_option(c("--euclidean"), action="store", default=NA, type='character',
+              help="Path to file containing organization euclidean distances"),
   make_option(c("-o", "--out"), action="store", default=NA, type='character',
               help="Path to save aggregated distance file")
 ) # end option_list
@@ -149,6 +151,22 @@ distance_all <- data.table::rbindlist(list(dot1, dot2)) %>%
 
 remove("dot", "dot1", "dot2")
 
+# Now merge dot product similarities
+euclidean <- read_csv(opt$euclidean, col_types = cols()) %>%
+  select(org1, org2, similarity) %>%
+  rename(euclidean_distance = similarity)
+
+euclidean1 <- distance_all %>%
+  inner_join(euclidean, by = c("org1" = "org1", "org2" = "org2"))
+
+euclidean2 <- distance_all %>%
+  inner_join(euclidean, by = c("org2" = "org1", "org1" = "org2"))
+
+distance_all <- data.table::rbindlist(list(euclidean1, euclidean2)) %>%
+  distinct(org1, org2, .keep_all = TRUE)
+
+remove("euclidean", "euclidean1", "euclidean2")
+
 # PPR Cosine distnaces
 ppr <- read_csv(opt$pprcos, col_types = cols()) %>%
   select(org1, org2, distance) %>%
@@ -206,7 +224,7 @@ distance_all <- distance_all %>%
   # Select only relevant variables
   select(org1, org2, count,
          org1_size, org2_size,
-         geo_distance, emb_distance, dot_distance,
+         geo_distance, emb_distance, dot_distance, euclidean_distance,
          pprcos_distance, pprjsd_distance, gravity,
          org1_city, org1_region, org1_country,
          org2_city, org2_region, org2_country

### 2020-04-21 workflow/scripts/CalculatePredictedVsActual.R

@@ -30,7 +30,8 @@ agg <- readr::read_csv(opt$input, col_types = readr::cols()) %>%
   select(org1_size, org2_size,
          org1_country, org2_country,
          count, gravity,
-         geo_distance, pprcos_distance, pprjsd_distance, emb_distance, dot_distance) %>%
+         geo_distance, pprcos_distance, pprjsd_distance,
+         emb_distance, dot_distance, euclidean_distance) %>%
   rename(actual = count)
 
 # If the geographic constraint (--geo) is set, then filter the
@@ -51,32 +52,32 @@ if (opt$distance == "geo") {
   # Perform the regression
   agg <- agg %>%
     mutate(
-      distance = geo_distance,
-      distance.log = log(geo_distance)
+      distance = geo_distance
     )
 } else if (opt$distance == "emb") {
   agg <- agg %>%
     mutate(
-      distance = emb_distance,
-      distance.log = log(emb_distance)
+      distance = emb_distance
     )
 } else if (opt$distance == "pprcos") {
   agg <- agg %>%
     mutate(
-      distance = pprcos_distance,
-      distance.log = log(pprcos_distance)
+      distance = pprcos_distance
     )
 } else if (opt$distance == "pprjsd") {
   agg <- agg %>%
     mutate(
-      distance = pprjsd_distance,
-      distance.log = log(pprjsd_distance)
+      distance = pprjsd_distance
     )
 } else if (opt$distance == "dot") {
   agg <- agg %>%
     mutate(
-      distance = dot_distance,
-      distance.log = log(dot_distance)
+      distance = dot_distance
+    )
+} else if (opt$distance == "euclidean") {
+  agg <- agg %>%
+    mutate(
+      distance = euclidean_distance
     )
 }
 
@@ -99,7 +100,7 @@ agg <- agg %>%
 
 agg <- agg %>%
   select(-c(org1_size, org2_size,
-            gravity, geo_distance, emb_distance,
+            gravity, geo_distance, emb_distance, euclidean_distance,
             pprcos_distance, pprjsd_distance, dot_distance))
 
 print(head(agg))

### 2020-04-21 workflow/scripts/PlotGravityLawRelationship.R

@@ -74,7 +74,7 @@ if (opt$geo == "same-country") {
 
 # Reduce the size to save on memory
 dist <- dist %>%
-  select(geo_distance, emb_distance, dot_distance,
+  select(geo_distance, emb_distance, dot_distance, euclidean_distance,
          pprcos_distance, pprjsd_distance,  gravity)
 
 axislabel <- "DEFAULT"
@@ -112,6 +112,12 @@ if (opt$distance == "geo") {
 
   # Provide axis label
   axislabel <- "Dot product similarity"
+} else if (opt$distance == "euclidean") {
+  dist <- dist %>%
+    rename(distance = euclidean_distance)
+
+  # Provide axis label
+  axislabel <- "Euclidean distance"
 }
 
 # Calculate the logged gravity and select only relevant columns

### 2020-04-21 workflow/scripts/calculate_org_w2v_similarity.py

@@ -20,7 +20,7 @@ parser = argparse.ArgumentParser()
 # System arguments
 parser.add_argument("-mod", "--model", help = "Path to word2vec model",
                     type = str, required = True)
-parser.add_argument("--type", help = "Type of similarity, 'dot' or 'cos'",
+parser.add_argument("--type", help = "Type of similarity, 'dot', 'euclidean', or 'cos'",
                     type = str, required = True)
 parser.add_argument("-o", "--output", help = "Output data path",
                     type = str, required = True)
@@ -46,6 +46,13 @@ if args.type == 'cos':
 elif args.type == 'dot':
     for word1, word2 in combinations(vocab, 2):
         temp_sim = np.dot(model.wv[word1], model.wv[word2])
+        D[word1][word2] = temp_sim
+        D[word2][word1] = temp_sim
+elif args.type == 'euclidean':
+    for word1, word2 in combinations(vocab, 2):
+        w1 = model.wv[word1]
+        w2 = model.wv[word2]
+        temp_sim = np.power(np.linalg.norm(w1 - w2), 2) / 2
         D[word1][word2] = temp_sim
         D[word2][word1] = temp_sim
 

### 2020-04-22 paper/current/notes/gm-vs-w2v/main.tex

@@
 In other words,  $\Phi(\vec{u})$ is the gravitational potential for the field, where 
-each point $\ell$ has a mass $s_{\ell}$ and is away from $u$ with distance $d(\vec{u},\vec{u}_\ell)$, and the effect of the mass decays by the factor of $\exp\left[d(\vec{u},\vec{u}_\ell) ^2 /2\right]$.
+each point $\ell$ has a mass $s_{\ell}$ and is away from $\vec{u}$ with distance $d(\vec{u},\vec{u}_\ell)$, and the effect of the mass decays by the factor of $\exp\left[d(\vec{u},\vec{u}_\ell) ^2 /2\right]$.
 

### 2020-04-29 paper/current/notes/gm-vs-w2v/main.tex
correct a typo in the definition of the mass s_i

@@
     \label{eq:dotsim}
-    \vec{u}_i ^\top \vec{v}_j = \frac{1}{2}\left[ ||\vec{u}_i|| + ||\vec{u}_j|| - d\left(\vec{u}_i, \vec{u}_j\right)^2 \right],
+    \vec{u}_i ^\top \vec{v}_j = \frac{1}{2}\left[ ||\vec{u}_i||^2 + ||\vec{u}_j||^2 - d\left(\vec{u}_i, \vec{u}_j\right)^2 \right],
 \end{align}
@@
 \begin{align}
-    \exp\left( \vec{u}_i ^\top \vec{v}_j \right) &= \frac{\exp\left( ||\vec{u}_i||/2 + ||\vec{u}_j||/2 \right)}{\exp\left[ d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2 \right]} \nonumber \\
+    \exp\left( \vec{u}_i ^\top \vec{v}_j \right) &= \frac{\exp\left( ||\vec{u}_i||^2/2 + ||\vec{u}_j||^2/2 \right)}{\exp\left[ d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2 \right]} \nonumber \\
                                                  &= \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2\right]}, \label{eq:exp_distance_form}
 \end{align}
-where $s_i:=\exp(||\vec{u}_i||/2)$. 
+where $s_i:=\exp(||\vec{u} _i||^2/2)$. 
 Substituting Eq.~\eqref{eq:exp_distance_form} into Eq.~\eqref{eq:model_node2vec} yields
@@
 We show that the word2vec is free from the restriction and automatically learns the mass $M_i$ from data, which may not be equal to the number of people at a point.
-To avoid the confusion, we denote by $n_i$ the number of people at a point $i$ in the followings.
 
 We regard $P_{\text{W2V}}(j \vert i)$ as the transition probability from $i$ to $j$ in a Markov process.
-Then, the number of people that move from $i$ to $j$ (i.e., flow) in one step is given by 
+Denote by $\pi_i$ the number of scientists in institution who may move to different institutions, i.e., mobile scientists.
+We note that $\pi$ may not be equal to the number of scientists in the institution because some scientists always stay in the institutions.
+The number of scientists that move from $i$ to $j$ (i.e., flow) in one step is given by 
 \begin{align}
     \label{eq:flow}
-    T_{ij}:= n_i P_{\text{W2V}}(j \vert i).
+    T_{ij}:= \pi_i P_{\text{W2V}}(j \vert i).
 \end{align}
@@
     \label{eq:detailed_balanced}
-    n_i P_{\text{W2V}}\left(j \vert i \right) = n_j P_{\text{W2V}}\left(i \vert j \right).
+    \pi_i P_{\text{W2V}}\left(j \vert i \right) = \pi_j P_{\text{W2V}}\left(i \vert j \right).
 \end{align}
-In other words, the flow is symmetric (i.e., $T_{ij} = T_{ji}$) and $n_i$ is the stationary distribution for the Markov process.
+In other words, the flow is symmetric (i.e., $T_{ij} = T_{ji}$) and $\pi_i$ is the stationary distribution for the Markov process.
 Equation \eqref{eq:detailed_balanced} yields 
 \begin{align}
-    &\frac{n_i}{Z_i}\cdot \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2\right]} = \frac{n_j}{Z_j}\cdot \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2 \right]} \\
-    &\iff \frac{n_i}{Z_i} = \frac{n_j}{Z_j} =: G', \label{eq:const}
+    &\frac{\pi_i}{Z_i}\cdot \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2\right]} = \frac{\pi_j}{Z_j}\cdot \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2 \right]} \\
+    &\iff \frac{\pi_i}{Z_i} = \frac{\pi_j}{Z_j} =: G', \label{eq:const}
 \end{align}
@@
     \label{eq:flow_gravity_model}
-    T_{ij} &= n_i P_{\text{W2V}}\left(j \vert i \right)\nonumber \\
-           &= \frac{n_i}{Z_i} \cdot \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2 \right]}\nonumber \\ 
+    T_{ij} &= \pi_i P_{\text{W2V}}\left(j \vert i \right)\nonumber \\
+           &= \frac{\pi_i}{Z_i} \cdot \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2 \right]}\nonumber \\ 
            &= G' \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2 \right]}. 
@@
 
-What is pulling force $s_i$? Is it related to the population $n_i$ in each point?
-To answer the questions, we rewrite $n_i$ as a function of $s_i$ as follows. 
-With Eq.~\eqref{eq:const}, we rewrite $n_i$ as 
+What is pulling force $s_i$? Is it related to the mobile population $\pi_i$ in each point?
+To answer the questions, we rewrite $\pi_i$ as a function of $s_i$ as follows. 
+With Eq.~\eqref{eq:const}, we rewrite $\pi_i$ as 
 \begin{align}
-    n_i &= G' Z_i \nonumber \\
-        &= G' s_i \sum_{\ell=1}^N s_\ell f\left(d\left(\vec{u}_i,\vec{u}_j\right)\right) \nonumber \\ 
-        &= - s_i \Phi(\vec{u}_i), \label{eq:flow_gravity_model_2} %\nonumber \\ 
+    \pi_i &= G' Z_i \nonumber \\
+        &= G' s_i \sum_{\ell=1}^N s_\ell f\left(d\left(\vec{u}_i,\vec{u}_\ell\right)\right) \nonumber \\ 
+        &= G' s_i ^2 - s_i \Phi(\vec{u}_i), \label{eq:flow_gravity_model_2} %\nonumber \\ 
 \end{align}
@@
 \begin{align}
-    \Phi(\vec{u}):=-G' \sum_{\ell=1}^N s_\ell f\left(d\left(\vec{u},\vec{u}_j\right)\right).
+    \Phi(\vec{u}):=-G' \sum_{\ell=1, \vec{u}\neq \vec{u}_\ell}^N s_\ell f\left(d\left(\vec{u},\vec{u}_\ell\right)\right).
 \end{align}
@@
 
-Population $n_i$ is given by $-s_i\Phi(\vec{u}_i)$. What does it mean for the mobility for scientists?
+Population $\pi_i$ is given by $-s_i\Phi(\vec{u}_i)$. What does it mean for the mobility for scientists?
 Suppose two institutions A and B. They have many influx from other institutions for different reasons:

### 2020-06-10 paper/current/main.tex
Update abstract, new refs

@@
 
-\title{Unsupervised embeddings of organizations capture latent structure of scientific mobility} %{{{
+\title{Unsupervised embeddings of organizations capture the latent structure of scientific mobility} %{{{
 \date{\today}
@@
 
-Scientific mobility drives innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}.
+Human mobility and migration drives countless social phenomenon including the growth and evolution of cities~\autocite{bettencourt2007cities, bettencourt2013cities, wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity, hufnagel2004epidemics, eubank2004outbreaks}, economies~\autocite{kaluza2010cargo, kerr2011immigration, taylor2016refugees, pappalardo2015mobility}, innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation, liu2010spillovers},  and scientific research~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage, morgan2018prestige, rodrigues2016mobility}.
 Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity, xia2005measlesgravity, jung2008highwaygravity, barbosa2018human, curiel2018citygravity, lewer2008immigrationgravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity, simini2012universal}, describes mobility using the \textit{distance} between places.
-However, amid a globalizing scientific enterprise~\autocite{czaika2018globalisation}, geographic distance is losing its relevance for understanding mobility, whereas other abstract notions of distance~\autocite{boschma2005proximity} pose practical and theoretical challenges.
-%Accordingly, the complexity of factors shaping global scientific mobility~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics} necessitates simplified models for reasoning about and crafting effective policy.
-Leveraging the neural embedding model~\autocite{mikolov2013word2vec}, we demonstrate a data-driven approach for learning a vector-space representation that encodes an effective distance between places and captures the latent and multi-faceted structure of mobility.
-We train scientific mobility embedding using the organizational trajectories derived from the publications of disambiguated authors from the Web of Science database between 2008 and 2019.
-Distance between vectors in the learned embedding space explains and predicts mobility between organizations better than  geographic distance or network distance.
-We argue that such power emerges from an underlying connection between the neural embedding model and the gravity model.
-In addition to geography, these embeddings also capture latent religious, cultural, social, and linguistic, and even prestige of organizations at multiple levels of granularity.
+However, amid a globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization}, geographic distance has less relevance for understanding mobility, whereas other abstract notions of distance~\autocite{boschma2005proximity} pose practical and theoretical challenges.
+Using the case of scientific mobility, we leveragethe neural embedding model~\autocite{mikolov2013word2vec} to demonstrate a data-driven approach for learning a vector-space embedding that encodes a functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} between places and captures the latent and multi-faceted structure of human mobility.
+We train embeddings of scientific organizations using mobility trajectories derived from the publications of disambiguated authors from the Web of Science database between 2008 and 2019.
+Distance between vectors in the learned embedding space explains and predicts real mobility between organizations better than  geographic distance. 
+We argue that this explanatory power emerges from an underlying connection between the neural embedding model and the gravity model.
+In addition to geography, the embedding also captures latent factors related to culture, language, and prestige of organizations at multiple levels of granularity.
 With this approach, we can learn scalable, dense, and meaningful vector representations of scientific mobility directly from the data using a methodology that can be easily applied to all kinds of mobility data.

### 2020-06-10 paper/current/main.tex
revise introduction text

@@
 
-When scientists move, they bring their knowledge with them, and so understanding the flows of scientists allows us to understand the flow of knowledge around the world. 
+How far apart are two places?
+The question is surprisingly hard to answer when it involves human mobility.
+While geographic distance may have driven human movements in past eras, it holds less importance to a world connected by rapid transport, complex international relations, and global trade.
+For example, a person currently living in Australia is more likely to migrate to the United Kingdom, a country with similar language and culture, than to much closer and more populous countries like Indonesia and the Philippines.
+Similarly, a prospective student living in South Korea is more likely to attend university in Canada rather than the much closer though diplomatically isolated North Korea. 
+Despite its complexity, the ubiquitious models of human mobility such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} model continue to predict mobility as a function of geographic distance.
+Although alternatives exist to quantify \textit{functional} distances not based on geography~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional}, geographic distance remains the unambiguous and foundational quantity for modeling mobility.
+
+Here, we propose a neural embedding model that uses real-world mobility trajectories to encode the complex structure of mobility into a dense, continuous, and meaningful vector-space representation, from which a \textit{functional distance} between places can be derived.
+This approach, origionally designed to create embeddings of words~\autocite{mikolov2013word2vec} has been used to reveal insights in texts~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
+In addition to providing a data-driven functional distance, this approach is computationally efficient, scalable for large datasets, robust to noise, and allows for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.
+
+We use scientific mobility (scientific co-affiliation) as a case study to demonstrate the neural embedding approach. 
+Scientific mobility has become increasingly globalized over time~\autocite{czaika2018globalisation}, and has been shown to drive innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}.
 However,  given its complexity~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, new approaches are needed to make sense of landscape of global scientific mobility.
-A basic component of mobility is distance--people are more likely to move nearby than to cross continents.
-Although many alternative ways to quantify the distance exist~\autocite{boschma2005proximity}, geographic distance remains the unambiguous and foundational quantity.
-In turn, models of human mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation models ~\autocite{simini2012universal}, rely almost exclusively on geographic distance.
-However, distance is not always so straightforward as simple geography. 
-Geographic distance alone fails to capture the host of historical, linguistic, cultural, and cognitive distances that also drive mobility. 
-For instance, Australia may be physically close to Indonesia, but in terms of shared language, history, and culture, they are essentially neighbors to the United Kingdom.
-Then, how can we quantify meaningful, useful distance between institutions, cities, and countries?
-
-Here, we propose a neural embedding model as an efficient means of encoding an effective measure of distance using large-scale data on mobility trajectories, one that encodes complex latent structure.
-It has been demonstrated that the neural embedding model preserves semantic relationships between words in a dense, continuous and meaningful low-dimensional vector representation~\autocite{mikolov2013word2vec}, and has been applied to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
-In addition to encoding latent structure, this approach is computationally efficient, scalable for large datasets, robust to noise, and allows for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.
-
-As scientist's careers progress, they move between organizations or pick up additional affiliations, forming co-affiliation or \textit{mobility trajectories} that can be derived from their publication histories~\autocite{robinson2019mobility, sugimoto2017mostimpact}.
-By treating geo-located organizations analogously to words and trajectories analogously to sentences, we learn vector-space embedding of organizations using a neural embedding method (Fig.~\ref{fig:methods:mobility_sentence}).
-In the resulting embedding, each organization corresponds to a vector, and vectors relate to one another \textit{semantically}--just as with language, organizations are \textit{semantically} similar when they share similar co-affiliation \textit{contexts}.
-We measure the semantic distance between organization vectors using \textit{cosine distance}, and use this to model distance in the landscape of scientific mobility.
+
+As scientist's careers progress, they move between organizations or pick up additional simultaneous affiliations forming co-affiliation or \textit{mobility trajectories}.
+These mobility trajectories, represented as ordered lists of organizations, can be derived from affiliations listed on researcher's publication histories~\autocite{robinson2019mobility, sugimoto2017mostimpact} (Fig.~\ref{fig:methods:mobility_sentence}).
+We use the trajectories of the three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
+A vector-space embedding or organizations is learned by using mobility trajectories as input to the standard skip-gram negative sampling, or \textit{word2vec} neural-network architecture.
+In the resulting embedding, each organization corresponds to a vector, and vectors relate to one another based on the likelihood of organizations appearing near one another in the provided mobility trajectories.
+We calculate the pairwise \textit{embedding distance} between organization as the cosine distance between their correponding vectors in the embedding.
 
@@
 
-We use the trajectories of the three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
-We adopt the Gravity Model of mobility~\autocite{zipf1946gravity, barbosa2018human}, one of the most broadly applied mobility models~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} to assess how well the embedding captures mobility.
+We assess the performance of the embedding distance relative to geographic distance by evaluating their ability to explain and predict real-world mobility as parameters in the Gravity Model of mobility~\autocite{zipf1946gravity, barbosa2018human}.
+The Gravity Model, taking inspiration from Newton's law of gravity, is one of the most broadly applied mobility models~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} .
 After fitting the parameters of the gravity model, we use it to derive the \textit{expected flux} $\hat{T_{ij}}$ between organizations, defined as,
@@
 Where the \textit{expected flux}, $\hat{T_{ij}}$, or expected number of authors co-affiliated with a pair organizations during the time period is proportional to the organization's sizes (both mobile and non-mobile authors, see Data and Methods), $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
-We consider two distances, the geographic distance between the organizations as a baseline, and the \textit{embedding distance} defined as the cosine distance between the organization's vector in the trained embedding space.
-We argue that the performance of a distance measure can be observed from their ability to explain expected mobility between organizations and to make predictions using the gravity model.
+The distance function is defined in terms of either the geographic distance between organizations orthe embedding distance. 
 For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_emb_bymodel} and Fig.~\ref{fig:supp:predict_geo_bymodel}).
+We argue that the performance of a distance measure can be observed from its ability to explain expected mobility between organizations and to make predictions using the gravity model.
 

### 2020-06-10 paper/current/main.tex
update figure caption, sentence -> trajectory

@@
     \caption{
-        \textbf{Co-affiliation trajectories represented as sentences}
+        \textbf{Construction of mobility trajectories from publication records}
         \textbf{a.}
         An author published five papers across five time periods, with only one affiliation listed in the byline of each paper.
-        To each organization, a unique identifier is assigned, and they are assembled into a mobility sentence ordered by year of publication.
+        To each organization, a unique identifier is assigned, and they are assembled into a mobility trajectory ordered by year of publication.
         \textbf{b.}

### 2020-06-10 paper/current/main.tex
effective distance -> functional distance

@@
 %
-\subsection*{Embeddings estimate the effective distance between organizations}
-
-The effective distance estimated by our embedding model explains and predicts scientific mobility best.
+\subsection*{Embeddings provide a functional distance between organizations}
+
+The functional distance derived from the  embedding model explains and predicts scientific mobility best.
 The amount of variance explained by embedding distance ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) is more than twice that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
@@
 
-Given that embeddings capture effective distance between organizations, we can now examine the global structure of scientific mobility.
+Given that embeddings capture a functional distance between organizations, we can now examine the global structure of scientific mobility.
 Because the embeddings are defined in a high-dimensional space, we apply a widely-used dimensionality reduction technique (UMAP~\autocite{mcinnes2018umap}) to visualize the overall structure (Fig.~\ref{fig:projection}a).

### 2020-06-10 paper/current/main.tex
revise gravity performance text

@@
 %
+% TODO: remove the subsection label?
+%
 \subsection*{Embeddings provide a functional distance between organizations}
 
-The functional distance derived from the  embedding model explains and predicts scientific mobility best.
+The functional distance derived from the embedding explains and predicts scientific mobility better than geographic distance.
 The amount of variance explained by embedding distance ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) is more than twice that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
-This pattern holds for the variance of only domestic (Fig.~\ref{fig:supp:gravity_correlation}c) and international mobility flows (Fig.~\ref{fig:supp:gravity_correlation}d).
-After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance globally (Fig.~\ref{fig:gravity_performance}c--d) and for domestic (Fig.~\ref{fig:supp:gravity_correlation}e--f) and international mobility(Fig.~\ref{fig:supp:gravity_correlation}g--h).
-We also examine gravity model with dot product in the embedding space, the amount of variance explain ($R^{2} = 0.34$) by dot product outperforms that of geographic distance (Fig.~\ref{fig:supp:gravity_dot}).
-Similarly, embedding distance outperforms ``diffusion''  distances such as those derived from calculating personalized-page rank scores (see supporting materials) on the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-Geographic distance alone is a poor perspective for understanding international scientific mobility---rather, by learning a distance directly from the data, it is possible to better explain, and better predict flux between organizations.
+This pattern holds when considering the subset of only domestic (Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (Fig.~\ref{fig:supp:gravity_correlation}d).
+After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance (Fig.~\ref{fig:gravity_performance}c--d), which also holds for the subsets of only domestic (Fig.~\ref{fig:supp:gravity_correlation}e--f) and international mobility(Fig.~\ref{fig:supp:gravity_correlation}g--h).
+The embedding distance defined from the cosine distnace between vectors also outperforms that defined from their dot product ($R^{2} = 0.34$, Fig.~\ref{fig:supp:gravity_dot}).
+The embedding distance also out-performs alternative ``diffusion'' measures such as the personalized-page rank scores (see supporting materials) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+Geographic distance alone is a poor perspective for understanding international scientific mobility---rather, by learning a functional distance directly from the data, it is possible to better explain, and better predict flux between organizations.
 

### 2020-06-10 paper/current/main.tex
update caption
updated text around figs 4 and 5

@@
 	\caption{
-		\textbf{Embedding distance outperforms and is more robust than geographic distance.}
+		\textbf{Embedding distance outperforms geographic distance.}
 		\textbf{a.} embedding distance (cosine distance between organization vectors) explains more of the expected flux between organization pairs than does geographic distance (\textbf{b}).
@@
 
-Given that embeddings capture a functional distance between organizations, we can now examine the global structure of scientific mobility.
-Because the embeddings are defined in a high-dimensional space, we apply a widely-used dimensionality reduction technique (UMAP~\autocite{mcinnes2018umap}) to visualize the overall structure (Fig.~\ref{fig:projection}a).
+What kind of information is encoded in the embedding that allows embedding distance to outperform geographic distance?
+To explore the structure of the embedding space, we use a common dimensionality reduction technique (UMAP~\autocite{mcinnes2018umap}) to visualize it in two dimensions (Fig.~\ref{fig:projection}a).
+This projection constitutes the largest and highest resolution ``map'' of scientific mobility to date.
+
 Globally, the effect of geography is conspicuous; organizations tend to form clusters based on their national affiliations and national clusters tend to be near their geographic neighbors. 
-At the same time, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions much more clearly than alternative network visualizations (Fig.~\ref{fig:supp:network_vis}).
-
-By learning and leveraging the embedding space, these complex national and regional relationships can be quantified and visualized.  
-For example, by re-projecting or \textit{zooming into} organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries from majority-Muslim countries in the Middle East to South Asian countries of Pakistan, Bangladesh, and Indonesia, and finally towards Southeast-Asian nations with different religious majorities such as Vietnam, the Philippines, and Thailand.
+At the same time, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions much more clearly than alternative network representations (Fig.~\ref{fig:supp:network_vis}) that have dominated studies of scientific mobility~\autocite{chinchilla2018global, czaika2018globalisation}.
+
+An advantage of the embedding space is the ability to \textit{zoom in} on subsets of counties and re-project them in order to reveal more local relationships. 
+For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries ranging from Egypt to Phillipines that correponds to both geography but also cultural factors, such as the majority relitigion of each country;
+for example, the cluster for Malaysia, a majority-Muslim country, is nearer to other Middle Eastern nations than Thailand, a country that is geographically-nearer though with very different religious demographics.
 Linguistic and historical ties are also important.
@@
 Comparable structural patterns exist even within a single country.
-For example, organizations within Quebec in Canada are located near the French cluster rather than the rest of Canada.
-
-Just as the global embedding captures national-level geographic structure, so does a projection of organizations in the United States reflect organizational structure based on states (Fig.~\ref{fig:projection}d).
-By re-projecting at the state-level for Massachusetts (Fig.~\ref{fig:projection}e), we observe structure between urban Centers (Boston vs.
+For example, at the global level (Fig~\ref{fig:projection}a), organizations within Quebec in Canada are located near the French cluster rather than the rest of Canada.
+
+Just as the global embedding captures national-level geographic structure, so does a projection of organizations in the United States reflect organizational structure based on states and regions (Fig.~\ref{fig:projection}d).
+By re-projecting at the state-level for Massachusetts (Fig.~\ref{fig:projection}e), we observe structure between urban centers (Boston vs.
 Worcester), but also based on organization type (e.g., hospitals vs.
@@
 
-We can also examine high-level structure by estimating aggregate embeddings of countries. 
+Just as the embedding space makes it possible to "zoom in" on subsets of organizations, it is possible to "zoom out" to a higher level by aggregating organizational vectors. 
+For example, we can examine high-level structure by estimating the aggregate embeddings of countries. 
 Namely, we calculate the representative vector of each country by averaging organization vectors within the given country.
@@
 \ref{fig:clustering}a).
-The identified six clusters roughly correspond to: East-Asian (orange), Scandinavian (dark purple), British Commonwealth (light purple), Central and Eastern European countries (light blue), and then two cluster diverse clusters with a mix of European, Latin American, and Mediterranean countries.
-Countries are either grouped geographically or by linguistic or historical ties.
-
-We investigate the extent to which geography and language dictate the formation of clusters using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering by explicitly adjusting the relative importance of different levels of the hierarchy with scaling parameter $r$, acting like a ``zooming lens''.
+The six identified clusters roughly correspond to: East-Asian (orange), Scandinavian (dark purple), British Commonwealth (light purple), Central and Eastern European countries (light blue), and then two cluster diverse clusters with a mix of European, Latin American, and Mediterranean countries.
+These clusters demonstrate the importance of not only geography, but also linguistic ties between countries.
+
+We quantify the relative importance of geography (by continent), and language (by majority language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering by explicitly adjusting the relative importance of different levels of the hierarchy with scaling parameter $r$, acting like a ``zooming lens''.
 If $r$ is high, the similarity is based on the lower levels of the dendrogram, whereas when $r$ is low, similarity is based on higher levels.

### 2020-06-10 paper/current/main.tex
some revisions to the prestige hierarchy text

@@
 %
-\subsection*{Embeddings capture latent geography and hierarchy}
-
-The results demonstrating embeddings' ability to capture various features governing mobility raise the question of whether they can also capture semantic axes analogously to word embeddings. 
-For instance, does the mobility embedding encode information about the prestige or universities?
-We show that, in addition to encoding national characteristics, the embedding also encodes domestic geography and latent hierarchy.
-
-By treating organizations analogously to words and trajectories to sentences, we embed organizations in a way that preserves \textit{semantic} relationships, meaning organizations that share similar co-affiliation \textit{contexts} will in turn be similar (see Data and Methods).
-Leveraging these unique semantic properties, we employ the SemAxis approach~\autocite{an2018semaxis} and define two axes.
-The first is the California--Massachusetts axis defined by the mean vector of universities in California on one end, and in Massachusetts on the other. 
-The second axis is the low- to high- prestige axis;
-the elite end of the axis is defined as the top 20 U.S.
-universities according to the Times Ranking of World Universities, whereas the non-elite axis is defined as bottom-ranked and geographically matched (by U.S.
-census region) set of universities.
-A university projected onto the axis corresponds to their relative nearness to the mean vector defining each pole (Fig.~\ref{fig:semaxis}a).
-
-Generally, universities in Western states, such as Arizona (Fig.~\ref{fig:supp:semaxis_states}b) are nearer to the California end of the axis, whereas states in the Northeast such as New York (Fig.~\ref{fig:supp:semaxis_states}f) and Connecticut (Fig.~\ref{fig:supp:semaxis_states}e) are nearer the Massachusetts end.
-Universities geographically distant from both California and Massachusetts are less aligned with either, such as Texas (Fig.~\ref{fig:supp:semaxis_states}g)s and Florida (Fig.~\ref{fig:supp:semaxis_states}i).
+\subsection*{Embeddings capture latent prestige hierarchy}
+
+Prestige hierarchies underpin the dynamics of scientific mobility~\autocite{deville2014career, clauset2015hierarchy}, but are these hierarchies captured in the embedding space?
+We test this by exploting the geometric properties of the embedding space with the technique SemAxis~\autocite{an2018semaxis}, an approach originally designed for word embeddings but that is equally applicable here.
+SemAxis assumes the existence of an a user-defined axis, defined as the vector formed by the distance of some two vectors in the embedding space.
+The choice of the axis should represent a meaningful and coherent concept.
+Organization vectors are then projected onto this axis, and their position estimates their similarity to the concepts embodied by either end of the axis. 
+We define prestige using the Times Ranking of World Universities, including all ranked universities in the United States;
+the elite end is defined as the mean vector of the top five U.S.
+universities according to the rankings, whereas the non-elite axis is defined using the five bottom-ranked and geographically matched (by U.S.
+census region) universities.
+A geographic axis is also added to aid the visualization and reinforce the importance of geography, defined as the mean vector of all universities in California and then Massachusetts.
 
 Universities hiring and mobility networks are known to exhbit latent pretige hierarchies ~\autocite{deville2014career, clauset2015hierarchy} that should be encoded in the embedding space.
-Accordingly, prestigious universities such as Stanford, Colombia, MIT, Harvard, and NYU, group towards the top of the axis.
+Accordingly, prestigious universities such as Stanford, Colombia, MIT, Harvard, and NYU, group towards the top of the axis (Fig.~\ref{fig:semaxis}a).
 Universities at the bottom of this axis tend to be regional universities with lower national profiles.
@@
 		\textbf{Embedding captures latent geography and prestige hierarchy.}
-		\textbf{a.} illustrates SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S.
+		\textbf{a.} illustrates SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top five and geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S.
 Universities (bottom to top).
@@
 		\textbf{b.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity to the \textit{Elite} end of the axis prestige axis \textit{a}.
-		White points are those top and bottom 5 universities aggregated to define the ends of the axis.
-		The grey box corresponds to the top 5 and bottom 5 ranks.
+		White points are those top and bottom five universities aggregated to define the ends of the axis.
+		The grey box corresponds to the top five and bottom five ranks.
 	  	Even when considering only a total of ten organization vectors, the estimate of the spearman rank correlation between the SemAxis and Times ranking is 0.73 (n = 145).
@@
 
-In addition to capturing geography, the word embedding also encodes the well-known latent prestige hierarchies of academic mobility~\autocite{deville2014career, clauset2015hierarchy}.
+The embedding space captures prestige hierarchies to such a high resoltuion that they can be used to reconstruct academic rankings. 
 We derive a ranking using the prestige axis that we call \textit{SemRank}, and compare them to traditional university rankings.
 SemRank is defined from the position of organizations along the prestige axis, with the top ranked being the furthest towards the \textit{Elite} end of the axis.
-We find that SemRank derived is highly correlated with the Times ranking ($\rho = 0.81$, Fig.~\ref{fig:semaxis}b).
+We find that SemRank derived is highly correlated with the Times ranking ($\rho = 0.73$, Fig.~\ref{fig:semaxis}b).
 This correlation is robust with the number of organizations used to define the axes (Fig.
 SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities is strongly correlated with the Times Ranking ($\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
-For reference, SemRank achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking~\autocite{waltman2012leidenrankings}, a common and bibliometrically informed university ranking ($\rho = 0.87$, Fig.~\ref{fig:supp:times_vs_leiden}).
-This suggests that word embeddings, in addition to learning the latent geography of mobility, also capture more nuanced characteristics such as latent hierarchy in the axis of the embedding, which is a unique and fascinating characteristic of this approach.
+For reference, SemRank achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking~\autocite{waltman2012leidenrankings}, a common and bibliometrically-informed university ranking ($\rho = 0.87$, Fig.~\ref{fig:supp:times_vs_leiden}).
+This suggests that the organization embedding captures the latent prestige hierarchy inherent to academic mobility with a high degree of resolution and reliability.
 

### 2020-06-12 paper/current/main.tex
revise_math_part

@@
 \DeclareMathOperator*{\argmax}{\arg\!\max}
+\usepackage{bm}
+\def\tnull{{\text{null}}}
+\def\vec#1{{\bm #1}}
+\def\mat#1{\mathbf{#1}}
 
@@
 We find evidence of a theoretical connection between the two models, one that makes the neural embedding model applicable to embedding many forms of mobility trajectories.
-For this section, we relax the cosine similarity as a dot product for simplicity.
-
-According to our observation on the embedding space from Eq.\ref{eq:linear_flux_emb},
-
-\begin{equation}
+
+The gravity model generates the flow from $i$ to $j$ by 
+\begin{align}
     \label{eq:gravity_model}
-    \frac{T_{ij}}{M_{i} M_{j}} \propto \exp(-d_{ij}) =  \exp(- (-v_i \cdot v_j) \propto \exp(v_i \cdot v_j) 
-\end{equation}
-
-where $T_{ij}$ represents the \textbf{flux}, the number of people who moved between organizations $i$ and $j$,  $M_{i}$ and $M_{j}$ represent the size of an organization,  $d_{ij} = - v_{i}, v_{j}$ is the embedding distance.
-In the case of scientific co-affiliation, we assume all movements are without direction (symmetric), meaning that  $T_{ij} = T_{ji}$.
-
-To rewrite  Eq.\ref{eq:gravity_model} in terms of $T_{ij}$, we replace  $M_i$ with $\mu_{i}$, the total flux to or from $i$ which can be written as
-
-\begin{equation}
-	\label{eq:approxi_mass_term}
-    \mu_{i} = \sum_{k \in N} T_{ik} \propto M_i,
-\end{equation}
-where $N$ as set of organizations in the data. It can be checked in Fig.\ref{fig:math_part}. With this approximation, we can rewrite Eq.~\ref{eq:gravity_model} as,
-\begin{equation}
-   \frac{T_{ij}}{\mu_{i} \mu_{j}} \propto \exp(v_i,v_j).
-\end{equation}
-
-%
-% Figure - Conditional Probability
-%
-\begin{figure}
-    \centering
-    \includegraphics[width=0.4\columnwidth]{\figdir/Math/m_and_M.pdf}
-    \caption{
-    Relationship between $M_i$ and $\mu_i$.}.
-    \label{fig:math_part}
-\end{figure}
-
-This mathematical form relates to the objective function of the neural embedding model.
-The model attempts to maximize the average log probability of observing a target word in a sentence, $w_{t}$, given the words in the surrounding context window, $w_{t + k}$.
+    T_{ij}:= G M_i M_j f\left(d_{ij}\right),
+\end{align}
+where $M_i$ is the mass for the gravity model, $f\left(d_{ij}\right)$ is a function of the distance, and 
+$G$ is the constant analogous to the gravitational constant in physics.
+In migration study, any quantity that proportion to sum of flow from $i$ can be used as $M_i$, often population at a point $i$ (e.g., city and country) is popular choice.
+For the $d_{ij}$, geographical distance is often used.
+In other words, the gravity model inference most appropriate  $f\left(d_{ij}\right)$ with given $M_i, M_j, T_{ij},$ and $d_{ij}$.
+Here, we are going to show that \textit{word2vec} can be interpreted as generalized version of the gravity model, which preserved the original information into the scalable and meaningful embedding vector.
+
+Word embedding model \textit{word2vec} attempts to maximize the average log probability of observing a target word in a sentence, $w_{t}$, given the words in the surrounding context window, $w_{t + k}$.
 This can be written as follows, where $c$ is the size of the context window and $T$ iterates through possible target words:
@@
 \end{equation}
-where the conditional probability of observing one word, $w_{O}$, given another, $w_{I}$, is defined as,
-
-\begin{equation}
-    \label{eq:skipgram_conditional_expanded}
-    p(w_O|w_I) = \frac{\exp(v'_{w_O} \cdot v_{w_I})}{\sum_{w=1}^{W} \exp(v'_w \cdot v_{w_I})},
-\end{equation}
-where $v_w$ and $v'_w$ are ``input'' and ``output'' vector representations of each word in the vocabulary.
-We use Skip-gram negative sampling model, and following the work by Levy and Goldberg \autocite{levy2014neural}, consider the model as implicitly performing matrix factorization as shown below,
-
-\begin{equation}
-    \label{eq:sgns_relation}
-    A = \left(a_{ij}\right)_{W*W} = \log \left(\frac{N(i, j) |D|}{N(i) N(j)} \right) - \log k,
-\end{equation}
-
-where $N(i)\text{, } N(j) \text{ and } N(i,j)$ denotes the number of times word $i$, $j$, and word-context-pair ($i$, $j$) in the corpus respectively.
-Variable $k$ is the number of negative samples and $|D|$ is the size of the corpus.
-From Matrix Eq.\ref{eq:sgns_relation}, we can get embedding vector with rank-d approximation by SVD.
-The rank-d SVD factorize matrix A into product of three matrices  $L_d \Sigma R_d^T$, where $L_d$ and $R_d$ is $n \times d$ real matrices, and $\Sigma$ is    $d \times d$ diagonal matrix.
-
-Mathematically, the maximization of the objective function of the model yields $A_d = L_d \Sigma R_d^T$ such that $A_d = \arg \ \min_{Rank(A')=d} \Vert A' - A  \Vert$, which is the best approximate of the original matrix $A$.
-If we set, $V=L_d \Sigma$ and $V'=R_d$, then dot product between the rows of $V$ are equal to the dot products between rows of $A_d$ because $V$ is orthogonal real matrix  \autocite{levy2014neural}.
-With this relationship, we can rewrite the equation in terms of $V$.
-For a specific word pair $(i,j)$,
-
-\begin{equation}
-    \label{eq:sgns_relation_w,i, w_j}
-    v_{i} \cdot v_{j} =  \log \left(\frac{N(i, j) |D|}{N(i) N(j)} \right) - \log k,
-\end{equation}
-where $|D|$ and $k$ are constants, such that the functional form can be re-written as,
-
-\begin{equation}
-    \label{eq:sgns_relation_w,i, w_j}
-     \frac{N(i, j)}{N(i) N(j)}  \propto  \exp(v_{i} \cdot v_{j} ).
-\end{equation}
-
-In our model, $N(i)$ and $N(j)$ are total flux $M_i$ and $M_j$ respectively,  and $N(i,j)$ is just  $T_{ij}$, flux between $i$ and $j$. Then, we have the same expression with gravity model,
-
-\begin{equation}
-    \label{eq:sgns_relation_w,i, w_j_combining}
-     \frac{T_{ij}}{\mu_{i} \mu_{j}}  \propto  \exp(v_{i} \cdot v_{j} ).
-\end{equation}
-
-This proportionality relationship is consistent with findings from our model, and so we can say that there is a mathematical link between the neural embedding model and the gravity model.
+where the conditional probability of observing one word $i$, given word, $j$, is defined as,
+
+\begin{align}
+  \label{eq:model_node2vec}
+    P \left(j \mid i\right) = \frac{1}{Z_i}\exp\left(\vec{u} ^\top _{i} \vec{v}_{j}\right), 
+\end{align}
+where $u_i$ and $v_j$ are ``in-vector'' and ``out-vector'' respectively, which is K-dimensional vector representations of each word in the vocabulary.
+Variable $Z_i$ is the normalization constant or the partition function, i.e., $Z_i:= \sum_{\ell=1}^N \exp\left(\vec{u} ^\top _{i} \vec{v}_{\ell}\right)$.
+By the definition of the euclidean distance between the in-vectors,
+\begin{align}
+    \label{eq:distance}
+    d(\vec{u},\vec{u}'):= \sqrt{\sum_{k=1}^K \left(u_{k} - u'_{k}\right)^2}.
+\end{align}
+
+For simplicity, we assume that the $\vec{v}_j = \vec{u}_j$, it can be different practically.
+Exploiting $d^2 (\vec{u},\vec{u}')=||\vec{u}||^2 + ||\vec{u}'||^2 - 2\vec{u} ^\top \vec{u}'$, the dot similarity for $\vec{u}_i$ and $\vec{v}_j$ is given by
+\begin{align}
+    \label{eq:dotsim}
+    \vec{u}_i ^\top \vec{v}_j = \frac{1}{2}\left[ ||\vec{u}_i||^2 + ||\vec{u}_j||^2 - d\left(\vec{u}_i, \vec{u}_j\right)^2 \right],
+\end{align}
+which leads 
+\begin{align}
+    \exp\left( \vec{u}_i ^\top \vec{v}_j \right) &= \frac{\exp\left( ||\vec{u}_i||^2/2 + ||\vec{u}_j||^2/2 \right)}{\exp\left[ d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2 \right]} \nonumber \\
+                                                 &= \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2\right]}, \label{eq:exp_distance_form}
+\end{align}
+where $s_i:=\exp(||\vec{u} _i||^2/2)$. Substituting Eq.~\eqref{eq:exp_distance_form} into Eq.~\eqref{eq:model_node2vec} yields
+\begin{align}
+    \label{eq:model_node2vec_distance}
+    P \left(j \mid i\right) &:= \frac{1}{Z_i}\cdot \frac{s_is_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2/2\right]}. 
+\end{align}
+
+If we consider a stable Markov process with the transition probability from $i$ to $j$, $P_(j \vert i)$ and consider the stationary distribution for the Markov process  $\pi$, i.e., mobile scientists.
+Then, the flow from $i$ to $j$  in one step is given by
+\begin{align}
+    \label{eq:flow}
+    T_{ij}:= \pi_i P(j \vert i).
+\end{align}
+According to detailed balanced condition of Markov process, 
+\begin{align}
+    \pi_i P\left(j \vert i \right) = \pi_j P\left(i \vert j \right),
+\end{align}
+\begin{align}
+    \label{eq:detailed_balanced}
+    &\frac{\pi_i}{Z_i}\cdot \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2\right]} = \frac{\pi_j}{Z_j}\cdot \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2 \right]} \\
+    &\iff \frac{\pi_i}{Z_i} = \frac{\pi_j}{Z_j} =: G', \label{eq:const}
+\end{align}
+where $G'$ is a constant. 
+Substituting Eq.~\eqref{eq:model_node2vec_distance} into Eq.~\eqref{eq:flow} and exploiting Eq.~\eqref{eq:const} yield 
+\begin{align}
+    \label{eq:flow_gravity_model}
+    T_{ij} &= \pi_i P\left(j \vert i \right)\nonumber \\
+           &= \frac{\pi_i}{Z_i} \cdot \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2 \right]}\nonumber \\ 
+           &= G' \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2 \right]}. 
+\end{align}
+
+Remind that $T_{ij}:= G M_i M_j f\left(d_{ij}\right)$ in the gravity model.
+Thus, the word2vec is the generalized version of the gravity model with $M_i=s_i$ and $f\left(d_{ij} \right) = \exp\left[ - d\left(\vec{u}_i,\vec{u}_j\right) ^ 2 /2\right]$, which automatically learns the mass $M_i$ and map each entity into more abundant vector space with only given $T_{ij}$.
 Hence, the neural embedding model can be an effective model for investigating any kind of mobility trajectory data, stemming from the mathematical relationship between it and the gravity model of mobility.

### 2020-06-15 paper/current/main.tex
update math section

@@
 
-Why does the word embedding model, originally designed for natural language processing, produce a reasonable distance that models gravity relationships between organizations?
+Why does the neural embedding model (skip-gram with negative sampling, or \textit{word2vec}), originally designed for natural language processing~\autocite{mikolov2013word2vec}, produce a reasonable distance that models gravity relationships between organizations?
 We find evidence of a theoretical connection between the two models, one that makes the neural embedding model applicable to embedding many forms of mobility trajectories.
-
 The gravity model generates the flow from $i$ to $j$ by
+
 \begin{align}
@@
 \end{align}
-where $M_i$ is the mass for the gravity model, $f\left(d_{ij}\right)$ is a function of the distance, and 
-$G$ is the constant analogous to the gravitational constant in physics.
-In migration study, any quantity that proportion to sum of flow from $i$ can be used as $M_i$, often population at a point $i$ (e.g., city and country) is popular choice.
-For the $d_{ij}$, geographical distance is often used.
-In other words, the gravity model inference most appropriate  $f\left(d_{ij}\right)$ with given $M_i, M_j, T_{ij},$ and $d_{ij}$.
-Here, we are going to show that \textit{word2vec} can be interpreted as generalized version of the gravity model, which preserved the original information into the scalable and meaningful embedding vector.
-
-Word embedding model \textit{word2vec} attempts to maximize the average log probability of observing a target word in a sentence, $w_{t}$, given the words in the surrounding context window, $w_{t + k}$.
+
+where $M_i$ and $M_j$ are the masses of of the entities, $f\left(d_{ij}\right)$ is a function of the distance, and $G$ is the constant analogous to the gravitational constant in physics. 
+In mobility studies, any quantity proportional to the sum of flows from $i$ can be used as $M_i$; a common choice is the population at a point $i$ (e.g., city and country).
+For $d_{ij}$, geographical distance is often used. 
+We argue that the neural embedding model
+Here, we show that the neural embedding model can be interpreted as generalized version of the gravity model that efficiently encodes a functional distance into the dense, continuous, and meaningful embedding vector.
+
+In the case of language, the neural embedding model attempts to maximize the average log probability of observing a target word in a sentence, $w_{t}$, given the words in the surrounding context window, $w_{t + k}$.
 This can be written as follows, where $c$ is the size of the context window and $T$ iterates through possible target words:
@@
 \end{equation}
+
 where the conditional probability of observing one word $i$, given word, $j$, is defined as,
@@
 \end{align}
-where $u_i$ and $v_j$ are ``in-vector'' and ``out-vector'' respectively, which is K-dimensional vector representations of each word in the vocabulary.
+
+where $u_i$ and $v_j$ are `the `in-vector'' and ``out-vector'' respectively, which are K-dimensional vector representations of each word in the vocabulary. 
 Variable $Z_i$ is the normalization constant or the partition function, i.e., $Z_i:= \sum_{\ell=1}^N \exp\left(\vec{u} ^\top _{i} \vec{v}_{\ell}\right)$.
 By the definition of the euclidean distance between the in-vectors,
+
 \begin{align}
@@
 
-For simplicity, we assume that the $\vec{v}_j = \vec{u}_j$, it can be different practically.
-Exploiting $d^2 (\vec{u},\vec{u}')=||\vec{u}||^2 + ||\vec{u}'||^2 - 2\vec{u} ^\top \vec{u}'$, the dot similarity for $\vec{u}_i$ and $\vec{v}_j$ is given by
+For simplicity, we assume that  $\vec{v}_j = \vec{u}_j$, although they may differ in practice.
+Exploiting the fact that $d^2 (\vec{u},\vec{u}')=||\vec{u}||^2 + ||\vec{u}'||^2 - 2\vec{u} ^\top \vec{u}'$, the dot similarly between in and our vectors $\vec{u}_i$ and $\vec{v}_j$ is given by
+
 \begin{align}
@@
 \end{align}
-which leads 
+
+Using Eq.~\ref{eq:dotsim}, we can define $\exp\left( \vec{u}_i ^\top \vec{v}_j \right)$ as
+
 \begin{align}
@@
 \end{align}
-where $s_i:=\exp(||\vec{u} _i||^2/2)$. Substituting Eq.~\eqref{eq:exp_distance_form} into Eq.~\eqref{eq:model_node2vec} yields
+
+where $s_i:=\exp(||\vec{u} _i||^2/2)$. 
+Substituting Eq.~\eqref{eq:exp_distance_form} into Eq.~\eqref{eq:model_node2vec} yields
+
 \begin{align}
@@
 
-If we consider a stable Markov process with the transition probability from $i$ to $j$, $P_(j \vert i)$ and consider the stationary distribution for the Markov process  $\pi$, i.e., mobile scientists.
+If we consider a stable Markov process with the transition probability from $i$ to $j$, $P(j \vert i)$ and consider the stationary distribution for the Markov process  $\pi$, i.e., mobile scientists.
 Then, the flow from $i$ to $j$  in one step is given by
+
 \begin{align}
@@
 \end{align}
+
 According to detailed balanced condition of Markov process,
+
 \begin{align}
@@
 \end{align}
+
 \begin{align}
@@
 \end{align}
+
 where $G'$ is a constant. 
 Substituting Eq.~\eqref{eq:model_node2vec_distance} into Eq.~\eqref{eq:flow} and exploiting Eq.~\eqref{eq:const} yield
+
 \begin{align}
@@
 
-Remind that $T_{ij}:= G M_i M_j f\left(d_{ij}\right)$ in the gravity model.
-Thus, the word2vec is the generalized version of the gravity model with $M_i=s_i$ and $f\left(d_{ij} \right) = \exp\left[ - d\left(\vec{u}_i,\vec{u}_j\right) ^ 2 /2\right]$, which automatically learns the mass $M_i$ and map each entity into more abundant vector space with only given $T_{ij}$.
+The form of Eq.~\ref{eq:flow_gravity_model} maps to the gravity model $T_{ij}:= G M_i M_j f\left(d_{ij}\right)$.
+Therefore, we argue that the nerual embedding model is a generalized version of the gravity model with $M_i=s_i$ and $f\left(d_{ij} \right) = \exp\left[ - d\left(\vec{u}_i,\vec{u}_j\right) ^ 2 /2\right]$.
+Given flows $T_{ij}$ derived from mobility trajectories, this model attempts to learn the mass $M_i$ and map each entity into more abundant vector space . 
 Hence, the neural embedding model can be an effective model for investigating any kind of mobility trajectory data, stemming from the mathematical relationship between it and the gravity model of mobility.

### 2020-06-16 paper/current/main.tex

@@
 
-Human mobility and migration drives countless social phenomenon including the growth and evolution of cities~\autocite{bettencourt2007cities, bettencourt2013cities, wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity, hufnagel2004epidemics, eubank2004outbreaks}, economies~\autocite{kaluza2010cargo, kerr2011immigration, taylor2016refugees, pappalardo2015mobility}, innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation, liu2010spillovers},  and scientific research~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage, morgan2018prestige, rodrigues2016mobility}.
+Human mobility and migration drives major social phenomenon such as the growth and evolution of cities~\autocite{bettencourt2007cities, bettencourt2013cities, wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity, hufnagel2004epidemics, eubank2004outbreaks}, economies~\autocite{kaluza2010cargo, kerr2011immigration, taylor2016refugees, pappalardo2015mobility}, innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation, liu2010spillovers},  and scientific research~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage, morgan2018prestige, rodrigues2016mobility}.
 Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity, xia2005measlesgravity, jung2008highwaygravity, barbosa2018human, curiel2018citygravity, lewer2008immigrationgravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity, simini2012universal}, describes mobility using the \textit{distance} between places.
 However, amid a globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization}, geographic distance has less relevance for understanding mobility, whereas other abstract notions of distance~\autocite{boschma2005proximity} pose practical and theoretical challenges.
-Using the case of scientific mobility, we leveragethe neural embedding model~\autocite{mikolov2013word2vec} to demonstrate a data-driven approach for learning a vector-space embedding that encodes a functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} between places and captures the latent and multi-faceted structure of human mobility.
+Using the case of scientific mobility, we leverage the neural embedding model~\autocite{mikolov2013word2vec} to demonstrate a data-driven approach for learning a vector-space embedding that encodes a functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} between places and captures the latent and multi-faceted structure of human mobility.
 We train embeddings of scientific organizations using mobility trajectories derived from the publications of disambiguated authors from the Web of Science database between 2008 and 2019.
-Distance between vectors in the learned embedding space explains and predicts real mobility between organizations better than  geographic distance. 
-We argue that this explanatory power emerges from an underlying connection between the neural embedding model and the gravity model.
-In addition to geography, the embedding also captures latent factors related to culture, language, and prestige of organizations at multiple levels of granularity.
+Distance between vectors in the learned embedding space explains and predicts real mobility between organizations better than  geographic distance, emerging from an underlying connection between the neural embedding model and the gravity model.
+Exploiting their unique properties, we interpret the embedding space and observe how it captures latent factors related to culture, language, and prestige of organizations at multiple levels of granularity.
 With this approach, we can learn scalable, dense, and meaningful vector representations of scientific mobility directly from the data using a methodology that can be easily applied to all kinds of mobility data.
@@
 This approach, origionally designed to create embeddings of words~\autocite{mikolov2013word2vec} has been used to reveal insights in texts~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
-In addition to providing a data-driven functional distance, this approach is computationally efficient, scalable for large datasets, robust to noise, and allows for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.
+In addition to providing a data-driven functional distance, this approach is computationally efficient, scalable for large datasets, robust to noise, and are readily interpretable using an array of unique techniques based on simple vector arithmetic.
 

### 2020-06-16 paper/current/main.tex

@@
 For $d_{ij}$, geographical distance is often used. 
-We argue that the neural embedding model
-Here, we show that the neural embedding model can be interpreted as generalized version of the gravity model that efficiently encodes a functional distance into the dense, continuous, and meaningful embedding vector.
+Here, we show that the neural embedding model can be interpreted as a generalized version of the gravity model that efficiently encodes a functional distance into the dense, continuous, and meaningful embedding vector.
 
@@
 The form of Eq.~\ref{eq:flow_gravity_model} maps to the gravity model $T_{ij}:= G M_i M_j f\left(d_{ij}\right)$.
-Therefore, we argue that the nerual embedding model is a generalized version of the gravity model with $M_i=s_i$ and $f\left(d_{ij} \right) = \exp\left[ - d\left(\vec{u}_i,\vec{u}_j\right) ^ 2 /2\right]$.
-Given flows $T_{ij}$ derived from mobility trajectories, this model attempts to learn the mass $M_i$ and map each entity into more abundant vector space . 
+Therefore, we argue that the nerual embedding model can be interpreted as a generalized version of the gravity model with $M_i=s_i$ and $f\left(d_{ij} \right) = \exp\left[ - d\left(\vec{u}_i,\vec{u}_j\right) ^ 2 /2\right]$.
+Given flows $T_{ij}$ derived from mobility trajectories, neural embedding model attempts to learn the mass $M_i$, map each entity, and encode the functional distance into more abundant vector space . 
 Hence, the neural embedding model can be an effective model for investigating any kind of mobility trajectory data, stemming from the mathematical relationship between it and the gravity model of mobility.

### 2020-07-03 paper/current/main.tex
Update abstract and intro

--- 2020-06-16 paper/current/main.tex
@@
 
-\title{Unsupervised embeddings of organizations capture the latent structure of scientific mobility} %{{{
+\title{Unsupervised embeddings of organizations capture the latent structure of global scientific mobility} %{{{
 \date{\today}
@@
 However, amid a globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization}, geographic distance has less relevance for understanding mobility, whereas other abstract notions of distance~\autocite{boschma2005proximity} pose practical and theoretical challenges.
-Using the case of scientific mobility, we leverage the neural embedding model~\autocite{mikolov2013word2vec} to demonstrate a data-driven approach for learning a vector-space embedding that encodes a functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} between places and captures the latent and multi-faceted structure of human mobility.
-We train embeddings of scientific organizations using mobility trajectories derived from the publications of disambiguated authors from the Web of Science database between 2008 and 2019.
-Distance between vectors in the learned embedding space explains and predicts real mobility between organizations better than  geographic distance, emerging from an underlying connection between the neural embedding model and the gravity model.
+Using the case of scientific mobility, we leverage the neural embedding model~\autocite{mikolov2013word2vec} to demonstrate a data-driven approach for learning a vector-space embedding that encodes a functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} between organizations and captures the latent and multi-faceted structure of human mobility.
+We train neural embeddings of scientific organizations using mobility trajectories derived from the papers published between 2008 and 2019 of disambiguated authors from the Web of Science database.
+Functional distnace is derived as the cosine distance between vectors in the resulting embedding, and is shown to better explain and predict real mobility between organizations than geographic distance.
 Exploiting their unique properties, we interpret the embedding space and observe how it captures latent factors related to culture, language, and prestige of organizations at multiple levels of granularity.
-With this approach, we can learn scalable, dense, and meaningful vector representations of scientific mobility directly from the data using a methodology that can be easily applied to all kinds of mobility data.
+This approach can  learn scalable, dense, and meaningful vector representations of scientific mobility directly from the data, and can easily be generalized to other mobility data.
 \end{abstract}
@@
 The question is surprisingly hard to answer when it involves human mobility.
-While geographic distance may have driven human movements in past eras, it holds less importance to a world connected by rapid transport, complex international relations, and global trade.
-For example, a person currently living in Australia is more likely to migrate to the United Kingdom, a country with similar language and culture, than to much closer and more populous countries like Indonesia and the Philippines.
-Similarly, a prospective student living in South Korea is more likely to attend university in Canada rather than the much closer though diplomatically isolated North Korea. 
-Despite its complexity, the ubiquitious models of human mobility such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} model continue to predict mobility as a function of geographic distance.
-Although alternatives exist to quantify \textit{functional} distances not based on geography~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional}, geographic distance remains the unambiguous and foundational quantity for modeling mobility.
-
-Here, we propose a neural embedding model that uses real-world mobility trajectories to encode the complex structure of mobility into a dense, continuous, and meaningful vector-space representation, from which a \textit{functional distance} between places can be derived.
-This approach, origionally designed to create embeddings of words~\autocite{mikolov2013word2vec} has been used to reveal insights in texts~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
-In addition to providing a data-driven functional distance, this approach is computationally efficient, scalable for large datasets, robust to noise, and are readily interpretable using an array of unique techniques based on simple vector arithmetic.
+While geographic distance may have driven human movements in past eras, it holds less importance to a world connected by rapid transit, complex international relations, and global trade.
+For example, a person currently living in Australia is more likely to migrate to the United Kingdom, a country with similar language and culture, than to closer and more populous countries like Indonesia.
+Similarly, a prospective student living in South Korea is more likely to attend university in Canada rather than the closer though diplomatically isolated North Korea. 
+Despite its complexity, ubiquitious models of human mobility such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} model continue to predict mobility as a function of geographic distance.
+Although alternatives exist to quantify \textit{functional} distances based on factors other than geography~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional}, geographic distance remains the unambiguous and foundational quantity for modeling mobility.
+
+Here, we propose a neural embedding model that uses real-world mobility trajectories to encode the complex landscape of global mobility into a dense, continuous, and meaningful vector-space representation, from which a \textit{functional distance} between places can be derived.
+This approach, origionally designed for learning language models~\autocite{mikolov2013word2vec} has been used to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, e2014doc2vec, nakandala2016twitch} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
+In addition to providing a data-driven functional distance, this approach is computationally efficient, scalable for large datasets, robust to noise, and is readily interpretable through the application of simple vector arithmetic.
 
 We use scientific mobility (scientific co-affiliation) as a case study to demonstrate the neural embedding approach. 
-Scientific mobility has become increasingly globalized over time~\autocite{czaika2018globalisation}, and has been shown to drive innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}.
-However,  given its complexity~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, new approaches are needed to make sense of landscape of global scientific mobility.
-
-As scientist's careers progress, they move between organizations or pick up additional simultaneous affiliations forming co-affiliation or \textit{mobility trajectories}.
+Scientific mobility is a central aspect of the increasingly-globalized scientific system~\autocite{czaika2018globalisation}, being strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}.
+For nations and organizations hoping to win in the global competition for talent~\autocite{box2008competition}, understanding the landscape of global scientific mobility is essential. 
+However, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}.
+Neural embedding offers a means of capturing the complex global structure of scientific mobility in a dense and coherent representation that supports modeling and predicting mobility flows, mapping  patterns of mobility at multiple scales, and quantifying abstract notions such as academic prestige.
+
+The most fine-grained geographical unit of scientific production is the organization, such as an university, research institute, business, or government agency.
+As a scientist's careers progress, they move between organizations or pick up additional simultaneous affiliations forming co-affiliation or \textit{mobility trajectories}.
 These mobility trajectories, represented as ordered lists of organizations, can be derived from affiliations listed on researcher's publication histories~\autocite{robinson2019mobility, sugimoto2017mostimpact} (Fig.~\ref{fig:methods:mobility_sentence}).
 We use the trajectories of the three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
-A vector-space embedding or organizations is learned by using mobility trajectories as input to the standard skip-gram negative sampling, or \textit{word2vec} neural-network architecture.
-In the resulting embedding, each organization corresponds to a vector, and vectors relate to one another based on the likelihood of organizations appearing near one another in the provided mobility trajectories.
-We calculate the pairwise \textit{embedding distance} between organization as the cosine distance between their correponding vectors in the embedding.
+A vector-space embedding of organizations is learned by using mobility trajectories as input to the standard skip-gram with negative sampling, or \textit{word2vec} neural-network architecture.
+In the resulting embedding, each organization corresponds to a vector, and vectors relate to one another based on the likelihood of organizations appearing near together in the mobility trajectory data.
+The functional distance between two organizations is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}
 
@@
 
-Where the \textit{expected flux}, $\hat{T_{ij}}$, or expected number of authors co-affiliated with a pair organizations during the time period is proportional to the organization's sizes (both mobile and non-mobile authors, see Data and Methods), $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
-The distance function is defined in terms of either the geographic distance between organizations orthe embedding distance. 
+Where the \textit{expected flux}, $\hat{T_{ij}}$, or expected number of authors co-affiliated with a pair organizations during the time period is proportional to the organization's sizes (the sum of both mobile and non-mobile authors, see Data and Methods), $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+The distance function is defined in terms of either the geographic distance between organizations or the embedding distance. 
 For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_emb_bymodel} and Fig.~\ref{fig:supp:predict_geo_bymodel}).

### 2020-07-03 paper/current/main.tex
remove math section

@@
 The embedding distance also out-performs alternative ``diffusion'' measures such as the personalized-page rank scores (see supporting materials) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-Geographic distance alone is a poor perspective for understanding international scientific mobility---rather, by learning a functional distance directly from the data, it is possible to better explain, and better predict flux between organizations.
+Geographic distance alone is a poor perspective for understanding international scientific mobility---rather, by learning a functional distance directly from the data, it is possible to better explain, and better predict the flow of scientific mobility between organizations.
+We speculate that this results from an underlying mathematical connection between the neural embedding architecture and the gravity model of mobility.
 
@@
 \end{figure}
-
-%
-% Subsection: Mathematical Exploration
-%
-\subsection*{Mathematical connection between gravity model and neural embedding }
-
-Why does the neural embedding model (skip-gram with negative sampling, or \textit{word2vec}), originally designed for natural language processing~\autocite{mikolov2013word2vec}, produce a reasonable distance that models gravity relationships between organizations?
-We find evidence of a theoretical connection between the two models, one that makes the neural embedding model applicable to embedding many forms of mobility trajectories.
-The gravity model generates the flow from $i$ to $j$ by
-
-\begin{align}
-    \label{eq:gravity_model}
-    T_{ij}:= G M_i M_j f\left(d_{ij}\right),
-\end{align}
-
-where $M_i$ and $M_j$ are the masses of of the entities, $f\left(d_{ij}\right)$ is a function of the distance, and $G$ is the constant analogous to the gravitational constant in physics. 
-In mobility studies, any quantity proportional to the sum of flows from $i$ can be used as $M_i$; a common choice is the population at a point $i$ (e.g., city and country).
-For $d_{ij}$, geographical distance is often used. 
-We argue that the neural embedding model
-Here, we show that the neural embedding model can be interpreted as generalized version of the gravity model that efficiently encodes a functional distance into the dense, continuous, and meaningful embedding vector.
-
-In the case of language, the neural embedding model attempts to maximize the average log probability of observing a target word in a sentence, $w_{t}$, given the words in the surrounding context window, $w_{t + k}$.
-This can be written as follows, where $c$ is the size of the context window and $T$ iterates through possible target words:
-
-\begin{equation}
-    \label{eq:skipgram_log_prob_condensed}
-    \frac{1}{T}\sum_{t=1}^{T} \sum_{-c \le j \le c, j \neq 0} \log p(w_{t+j}|w_t),
-\end{equation}
-
-where the conditional probability of observing one word $i$, given word, $j$, is defined as,
-
-\begin{align}
-  \label{eq:model_node2vec}
-    P \left(j \mid i\right) = \frac{1}{Z_i}\exp\left(\vec{u} ^\top _{i} \vec{v}_{j}\right), 
-\end{align}
-
-where $u_i$ and $v_j$ are `the `in-vector'' and ``out-vector'' respectively, which are K-dimensional vector representations of each word in the vocabulary. 
-Variable $Z_i$ is the normalization constant or the partition function, i.e., $Z_i:= \sum_{\ell=1}^N \exp\left(\vec{u} ^\top _{i} \vec{v}_{\ell}\right)$.
-By the definition of the euclidean distance between the in-vectors,
-
-\begin{align}
-    \label{eq:distance}
-    d(\vec{u},\vec{u}'):= \sqrt{\sum_{k=1}^K \left(u_{k} - u'_{k}\right)^2}.
-\end{align}
-
-For simplicity, we assume that  $\vec{v}_j = \vec{u}_j$, although they may differ in practice.
-Exploiting the fact that $d^2 (\vec{u},\vec{u}')=||\vec{u}||^2 + ||\vec{u}'||^2 - 2\vec{u} ^\top \vec{u}'$, the dot similarly between in and our vectors $\vec{u}_i$ and $\vec{v}_j$ is given by
-
-\begin{align}
-    \label{eq:dotsim}
-    \vec{u}_i ^\top \vec{v}_j = \frac{1}{2}\left[ ||\vec{u}_i||^2 + ||\vec{u}_j||^2 - d\left(\vec{u}_i, \vec{u}_j\right)^2 \right],
-\end{align}
-
-Using Eq.~\ref{eq:dotsim}, we can define $\exp\left( \vec{u}_i ^\top \vec{v}_j \right)$ as
-
-\begin{align}
-    \exp\left( \vec{u}_i ^\top \vec{v}_j \right) &= \frac{\exp\left( ||\vec{u}_i||^2/2 + ||\vec{u}_j||^2/2 \right)}{\exp\left[ d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2 \right]} \nonumber \\
-                                                 &= \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2\right]}, \label{eq:exp_distance_form}
-\end{align}
-
-where $s_i:=\exp(||\vec{u} _i||^2/2)$. 
-Substituting Eq.~\eqref{eq:exp_distance_form} into Eq.~\eqref{eq:model_node2vec} yields
-
-\begin{align}
-    \label{eq:model_node2vec_distance}
-    P \left(j \mid i\right) &:= \frac{1}{Z_i}\cdot \frac{s_is_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2/2\right]}. 
-\end{align}
-
-If we consider a stable Markov process with the transition probability from $i$ to $j$, $P(j \vert i)$ and consider the stationary distribution for the Markov process  $\pi$, i.e., mobile scientists.
-Then, the flow from $i$ to $j$  in one step is given by
-
-\begin{align}
-    \label{eq:flow}
-    T_{ij}:= \pi_i P(j \vert i).
-\end{align}
-
-According to detailed balanced condition of Markov process,
-
-\begin{align}
-    \pi_i P\left(j \vert i \right) = \pi_j P\left(i \vert j \right),
-\end{align}
-
-\begin{align}
-    \label{eq:detailed_balanced}
-    &\frac{\pi_i}{Z_i}\cdot \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2\right]} = \frac{\pi_j}{Z_j}\cdot \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2 \right]} \\
-    &\iff \frac{\pi_i}{Z_i} = \frac{\pi_j}{Z_j} =: G', \label{eq:const}
-\end{align}
-
-where $G'$ is a constant. 
-Substituting Eq.~\eqref{eq:model_node2vec_distance} into Eq.~\eqref{eq:flow} and exploiting Eq.~\eqref{eq:const} yield
-
-\begin{align}
-    \label{eq:flow_gravity_model}
-    T_{ij} &= \pi_i P\left(j \vert i \right)\nonumber \\
-           &= \frac{\pi_i}{Z_i} \cdot \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2 \right]}\nonumber \\ 
-           &= G' \frac{s_i s_j}{\exp\left[d\left(\vec{u}_i, \vec{u}_j\right)^2 / 2 \right]}. 
-\end{align}
-
-The form of Eq.~\ref{eq:flow_gravity_model} maps to the gravity model $T_{ij}:= G M_i M_j f\left(d_{ij}\right)$.
-Therefore, we argue that the nerual embedding model is a generalized version of the gravity model with $M_i=s_i$ and $f\left(d_{ij} \right) = \exp\left[ - d\left(\vec{u}_i,\vec{u}_j\right) ^ 2 /2\right]$.
-Given flows $T_{ij}$ derived from mobility trajectories, this model attempts to learn the mass $M_i$ and map each entity into more abundant vector space . 
-Hence, the neural embedding model can be an effective model for investigating any kind of mobility trajectory data, stemming from the mathematical relationship between it and the gravity model of mobility.
 

### 2020-07-03 paper/current/main.tex
add new title possibility
updated conclusion

@@
 \begin{document} %{{{
-
+\title{Learning a functional distance between organizations with unsupervised embeddings of scientific mobility}
 \title{Unsupervised embeddings of organizations capture the latent structure of global scientific mobility} %{{{
@@
 In the resulting embedding, each organization corresponds to a vector, and vectors relate to one another based on the likelihood of organizations appearing near together in the mobility trajectory data.
-The functional distance between two organizations is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}
+The functional distance between two organizations is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.
 
@@
 
-What kind of information is encoded in the embedding that allows embedding distance to outperform geographic distance?
+What information is encoded in the embedding that allows embedding distance to outperform geographic distance?
 To explore the structure of the embedding space, we use a common dimensionality reduction technique (UMAP~\autocite{mcinnes2018umap}) to visualize it in two dimensions (Fig.~\ref{fig:projection}a).
-This projection constitutes the largest and highest resolution ``map'' of scientific mobility to date.
+By showing relationships between individual organizations, rather than aggregates such as nations or cities, this projection constitutes the largest and highest resolution ``map'' of scientific mobility to date.
 
@@
 An advantage of the embedding space is the ability to \textit{zoom in} on subsets of counties and re-project them in order to reveal more local relationships. 
-For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries ranging from Egypt to Phillipines that correponds to both geography but also cultural factors, such as the majority relitigion of each country;
+For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries ranging from Egypt to Phillipines that corresponds to both geography but also cultural factors, such as the majority religion of each country;
 for example, the cluster for Malaysia, a majority-Muslim country, is nearer to other Middle Eastern nations than Thailand, a country that is geographically-nearer though with very different religious demographics.
@@
 
-Just as the global embedding captures national-level geographic structure, so does a projection of organizations in the United States reflect organizational structure based on states and regions (Fig.~\ref{fig:projection}d).
+The geographic structure of the global embedding is mirrored in re-projection of the United States, wherein organizations are largely organized according to regions and states (Fig.~\ref{fig:projection}d).
 By re-projecting at the state-level for Massachusetts (Fig.~\ref{fig:projection}e), we observe structure between urban centers (Boston vs.
@@
 
-By learning a distance directly from data, word embeddings successfully  and efficiently captures a robust measure of semantic distance between entities, all with existing tools and minor data processing.
-This methodology is broadly applicable to studies of mobility.
-Its success also points to the broad applicability of ideas from language and graph embedding techniques such as GLoVE~\autocite{pennington2014glove}, BERT~\autocite{devlin2018bert}, hyperbolic embeddings~\autocite{nickel2017poincare, linzhuo2020hyperbolic}, and persona2vec () to other problem domains, such as the social sciences.
-In addition to their technical advantages and their unique suite of analytical tools, they are also readily transferable and can be trivially fit into a diverse array of analyses.
-
-Globally, science has experienced many changes, from gradual globalization~\autocite{czaika2018globalisation} to the more sudden 2016 Brexit and 2017 U.S.
-travel bans, and more recently the Covid19 global pandemic.
-The consequences of these changes are far-reaching, and how nations respond to them will shape the future of the scientific enterprise~\autocite{chinchilla2018travelban, wagner2017open, sugimoto2017mostimpact, whetsell2019democracy}.
-Given mobility's importance, its vital that we gain a better understanding of where, how, and why researchers move, and what the impact of these movements will be.
-With this new data-driven approach to learning distances relating to mobility, we capture the latent and nuanced structure of mobility at multiple scales;
-with this, predictive models can be improved and new insights gained, which in turn will inform more effective science and immigration policy, allowing global science to dictate the terms and leverage the benefits of our own migrations.
+Mobility and migration are central to the human experience~\autocite{shah2020migration}, but recent events threaten to upend patterns of human mobility that defined recent decades. 
+Within science, mobility has grown increasingly global~\autocite{czaika2018globalisation}, though the travel restrictions in the U.S.
+and U.K.
+brought by Brexit and the Trump administration~\autocite{chinchilla2018travelban}, and the rise of new scientific powers such as China~\autocite{tollefson2018china, cao2020returning} may lead to reorientation in who goes where.
+Similarly, the COVID19 pandemic threatens drastic change to travel and migration by tightening borders  and halting travel. 
+Now, more than ever, new tools and approaches are needed to understanding human mobility in order to inform sensible, effective, humane Immigration and Science and Technology policy.
+
+Neural embeddings offer a natural approach for learning an effective and robust functional distance between places based on mobility trajectory data. 
+Here, we demonstrated how the embedding space encodes complex aspects of scientific mobility, such as global and regional geography, national similarity, and organizational prestige.
+While scientific mobility is used as a case study, this approach can be broadly applied to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
+Moreover, this approach can be used to learn a functional distance between entities when no such analog to geographic distance exists, such as a functional distance between occupational categories based individual's career trajectories.
+In addition to providing a functional distance that supports modeling and predicting mobility patterns, the unique structure of neural embedding also allow for a range of methodological applications.
+For example, projecting the embedding space onto two dimensions using UMAP allows for the visualization of the complex structure of scientific mobility at high resolution and at multiple scales. 
+Other techniques, such as SemAxis, allow the the potential to quantify abstract notions in mobility such as academic prestige. 
+Neural embedding open the door for new approaches for representing and understanding patterns of global human mobility.
 

### 2020-07-03 paper/current/main.tex
updated SemAxis section

@@
 Prestige hierarchies underpin the dynamics of scientific mobility~\autocite{deville2014career, clauset2015hierarchy}, but are these hierarchies captured in the embedding space?
-We test this by exploting the geometric properties of the embedding space with the technique SemAxis~\autocite{an2018semaxis}, an approach originally designed for word embeddings but that is equally applicable here.
-SemAxis assumes the existence of an a user-defined axis, defined as the vector formed by the distance of some two vectors in the embedding space.
-The choice of the axis should represent a meaningful and coherent concept.
+We test this by exploting the geometric properties of the embedding space with the technique SemAxis~\autocite{an2018semaxis}, an approach originally designed for characterize the semantics of words in language embeddings, but is equally applicable here.
+In the context of organization vectors, this approach leverages the unique properties of the embedding space in order to quantify the nearness of an organization to the ends of some meaningful axis. 
+The axis is defined by the user and should represent some meaningful  and coherent concept. 
 Organization vectors are then projected onto this axis, and their position estimates their similarity to the concepts embodied by either end of the axis. 
+Here, we use SemAxis to operationalize the abstract notion of academic prestige, defining each end of the axis using known high- and low-ranked universities. 
 We define prestige using the Times Ranking of World Universities, including all ranked universities in the United States;
@@
 Universities hiring and mobility networks are known to exhbit latent pretige hierarchies ~\autocite{deville2014career, clauset2015hierarchy} that should be encoded in the embedding space.
-Accordingly, prestigious universities such as Stanford, Colombia, MIT, Harvard, and NYU, group towards the top of the axis (Fig.~\ref{fig:semaxis}a).
+Accordingly, prestigious universities such as Stanford, Colombia, MIT, Harvard, and NYU are positioned towards the top of the axis (Fig.~\ref{fig:semaxis}a).
 Universities at the bottom of this axis tend to be regional universities with lower national profiles.
-By considering mobility between all organization types, organization embeddings offer a new means of reasoning about the prestige of organizations typically excluded from rankings such as government organizatioss (Fig.~\ref{fig:supp:semaxis_sectors}a), research institutes (Fig.~\ref{fig:supp:semaxis_sectors}b), and teaching colleges (Fig.~\ref{fig:supp:semaxis_sectors}c).
+By considering mobility between all organization types, SemAxis applied to embeddings offers a new means of reasoning about the prestige of organizations typically excluded from rankings such as government organizatioss (Fig.~\ref{fig:supp:semaxis_sectors}a), research institutes (Fig.~\ref{fig:supp:semaxis_sectors}b), and teaching colleges (Fig.~\ref{fig:supp:semaxis_sectors}c).
 
@@
 
-The embedding space captures prestige hierarchies to such a high resoltuion that they can be used to reconstruct academic rankings. 
+The embedding space captures prestige hierarchies to such a high resolution that they can be used to reconstruct academic rankings. 
 We derive a ranking using the prestige axis that we call \textit{SemRank}, and compare them to traditional university rankings.
@@
 This suggests that the organization embedding captures the latent prestige hierarchy inherent to academic mobility with a high degree of resolution and reliability.
+
+While we use SemAxis to operationalize notions of prestige and geography, the approach can be easily generalized to other concepts so long as they can be meaningfully represented as an axis in the vector space.
+For example, axes could similarly be defined between teaching- and research-focused universities, between companies and government agencies, or between organizations in the U.S. and in China.
 

### 2020-07-06 paper/current/main.tex
minor typo
minor change

@@
 We train neural embeddings of scientific organizations using mobility trajectories derived from the papers published between 2008 and 2019 of disambiguated authors from the Web of Science database.
-Functional distnace is derived as the cosine distance between vectors in the resulting embedding, and is shown to better explain and predict real mobility between organizations than geographic distance.
+Functional distance is derived as the cosine distance between vectors in the resulting embedding and is shown to better explain and predict real mobility between organizations than geographic distance.
 Exploiting their unique properties, we interpret the embedding space and observe how it captures latent factors related to culture, language, and prestige of organizations at multiple levels of granularity.
@@
 While geographic distance may have driven human movements in past eras, it holds less importance to a world connected by rapid transit, complex international relations, and global trade.
-For example, a person currently living in Australia is more likely to migrate to the United Kingdom, a country with similar language and culture, than to closer and more populous countries like Indonesia.
+For instance, a person currently living in Australia is more likely to migrate to the United Kingdom, a country with similar language and culture, than to closer and more populous countries like Indonesia.
 Similarly, a prospective student living in South Korea is more likely to attend university in Canada rather than the closer though diplomatically isolated North Korea. 
-Despite its complexity, ubiquitious models of human mobility such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} model continue to predict mobility as a function of geographic distance.
+Despite its complexity, ubiquitous models of human mobility such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} model continue to predict mobility as a function of geographic distance.
 Although alternatives exist to quantify \textit{functional} distances based on factors other than geography~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional}, geographic distance remains the unambiguous and foundational quantity for modeling mobility.
@@
 Here, we propose a neural embedding model that uses real-world mobility trajectories to encode the complex landscape of global mobility into a dense, continuous, and meaningful vector-space representation, from which a \textit{functional distance} between places can be derived.
-This approach, origionally designed for learning language models~\autocite{mikolov2013word2vec} has been used to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, e2014doc2vec, nakandala2016twitch} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
+This approach, originally designed for learning language models~\autocite{mikolov2013word2vec} has been used to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
 In addition to providing a data-driven functional distance, this approach is computationally efficient, scalable for large datasets, robust to noise, and is readily interpretable through the application of simple vector arithmetic.
@@
 As a scientist's careers progress, they move between organizations or pick up additional simultaneous affiliations forming co-affiliation or \textit{mobility trajectories}.
-These mobility trajectories, represented as ordered lists of organizations, can be derived from affiliations listed on researcher's publication histories~\autocite{robinson2019mobility, sugimoto2017mostimpact} (Fig.~\ref{fig:methods:mobility_sentence}).
+These mobility trajectories, represented as ordered lists of organizations, can be derived from affiliations listed on the researcher's publication histories~\autocite{robinson2019mobility, sugimoto2017mostimpact} (Fig.~\ref{fig:methods:mobility_sentence}).
 We use the trajectories of the three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
@@
 
-%
-% Subsection: Applications
-%
 \subsection*{Embeddings capture global structure of mobility}

### 2020-07-06 paper/current/main.tex
minor change

@@
 A vector-space embedding of organizations is learned by using mobility trajectories as input to the standard skip-gram with negative sampling, or \textit{word2vec} neural-network architecture.
-In the resulting embedding, each organization corresponds to a vector, and vectors relate to one another based on the likelihood of organizations appearing near together in the mobility trajectory data.
+In the resulting embedding, each organization corresponds to a single vector, and vectors relate to one another based on the likelihood of organizations appearing near together in the mobility trajectory data.
 The functional distance between two organizations is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.
@@
 
-Mobility and migration are central to the human experience~\autocite{shah2020migration}, but recent events threaten to upend patterns of human mobility that defined recent decades. 
+Mobility and migration are central to the human experience~\autocite{shah2020migration}, but recent events threaten to upend patterns of human mobility that defined in recent decades. 
 Within science, mobility has grown increasingly global~\autocite{czaika2018globalisation}, though the travel restrictions in the U.S.
 and U.K.
-brought by Brexit and the Trump administration~\autocite{chinchilla2018travelban}, and the rise of new scientific powers such as China~\autocite{tollefson2018china, cao2020returning} may lead to reorientation in who goes where.
+brought by Brexit and the Trump administration~\autocite{chinchilla2018travelban}, and the rise of new scientific powers such as China~\autocite{tollefson2018china, cao2020returning} may lead to a reorientation in who goes where.
 Similarly, the COVID19 pandemic threatens drastic change to travel and migration by tightening borders and halting travel. 
@@
 While scientific mobility is used as a case study, this approach can be broadly applied to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
-Moreover, this approach can be used to learn a functional distance between entities when no such analog to geographic distance exists, such as a functional distance between occupational categories based individual's career trajectories.
-In addition to providing a functional distance that supports modeling and predicting mobility patterns, the unique structure of neural embedding also allow for a range of methodological applications.
-For example, projecting the embedding space onto two dimensions using UMAP allows for the visualization of the complex structure of scientific mobility at high resolution and at multiple scales. 
-Other techniques, such as SemAxis, allow the the potential to quantify abstract notions in mobility such as academic prestige. 
-Neural embedding open the door for new approaches for representing and understanding patterns of global human mobility.
+Moreover, this approach can be used to learn a functional distance between entities when no such analog to geographic distance exists, such as a functional distance between occupational categories based on individual's career trajectories.
+In addition to providing a functional distance that supports modeling and predicting mobility patterns, the unique structure of neural embedding also allows for a range of methodological applications.
+For instance, projecting the embedding space onto two dimensions using UMAP allows for the visualization of the complex structure of scientific mobility at high resolution and at multiple scales. 
+Other techniques, such as SemAxis, allow the potential to quantify abstract notions in mobility such as academic prestige. 
+Neural embedding opens the door for new approaches for representing and understanding patterns of global human mobility.
 

### 2020-07-14 paper/current/main.tex
update abstract

@@
 
-Human mobility and migration drives major social phenomenon such as the growth and evolution of cities~\autocite{bettencourt2007cities, bettencourt2013cities, wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity, hufnagel2004epidemics, eubank2004outbreaks}, economies~\autocite{kaluza2010cargo, kerr2011immigration, taylor2016refugees, pappalardo2015mobility}, innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation, liu2010spillovers},  and scientific research~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage, morgan2018prestige, rodrigues2016mobility}.
-Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity, xia2005measlesgravity, jung2008highwaygravity, barbosa2018human, curiel2018citygravity, lewer2008immigrationgravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity, simini2012universal}, describes mobility using the \textit{distance} between places.
-However, amid a globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization}, geographic distance has less relevance for understanding mobility, whereas other abstract notions of distance~\autocite{boschma2005proximity} pose practical and theoretical challenges.
-Using the case of scientific mobility, we leverage the neural embedding model~\autocite{mikolov2013word2vec} to demonstrate a data-driven approach for learning a vector-space embedding that encodes a functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} between organizations and captures the latent and multi-faceted structure of human mobility.
-We train neural embeddings of scientific organizations using mobility trajectories derived from the papers published between 2008 and 2019 of disambiguated authors from the Web of Science database.
-Functional distance is derived as the cosine distance between vectors in the resulting embedding and is shown to better explain and predict real mobility between organizations than geographic distance.
+Human mobility and migration drives major social phenomenon such as the growth and evolution of cities~\autocite{wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity}, economies~\autocite{kaluza2010cargo, kerr2011immigration}, innovation~\autocite{kaiser2018innovation, armano2017innovation},  and scientific research~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage, morgan2018prestige, rodrigues2016mobility}.
+Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity, xia2005measlesgravity, jung2008highwaygravity, barbosa2018human, curiel2018citygravity, lewer2008immigrationgravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity}, describes mobility using the \textit{distance} between places.
+However, geographic distance is less relevent in the increasingly-globalized globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization}, in which mobility is dependent less on geography than linguistic, economic, cultural, and historical similarity.
+Alternative and abstract notions of distance attempt to capture the latent landscape of mobility~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional} but pose practical and theoretical challenges.
+Here, using the case of scientific mobility, we leverage the neural embedding model~\autocite{mikolov2013word2vec} to demonstrate a data-driven approach for learning a vector-space embedding that encodes a functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} between organizations and captures the latent and multi-faceted structure of scientist's mobility.
+We demonstrate that the cosine distance between organization vectors in the embedding, constructed using the affiliation trajectories of scientists in the Web of Science database, better explain and predict real mobility than geographic distance.
 Exploiting their unique properties, we interpret the embedding space and observe how it captures latent factors related to culture, language, and prestige of organizations at multiple levels of granularity.

### 2020-07-14 paper/current/main.tex
update first section

@@
 The question is surprisingly hard to answer when it involves human mobility.
-While geographic distance may have driven human movements in past eras, it holds less importance to a world connected by rapid transit, complex international relations, and global trade.
+While geographic distance may have driven human movements in past eras, it holds less importance to a world connected by rapid transit, complex international relations, and dense airline networks.
 For instance, a person currently living in Australia is more likely to migrate to the United Kingdom, a country with similar language and culture, than to closer and more populous countries like Indonesia.
 Similarly, a prospective student living in South Korea is more likely to attend university in Canada rather than the closer though diplomatically isolated North Korea. 
-Despite its complexity, ubiquitous models of human mobility such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} model continue to predict mobility as a function of geographic distance.
-Although alternatives exist to quantify \textit{functional} distances based on factors other than geography~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional}, geographic distance remains the unambiguous and foundational quantity for modeling mobility.
+Despite its complexity, geographic distnace is used as the basis for the most prominent models of mobility such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal}.
+So-called \textit{functional distances}~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional} have been proposed that attempt to learn alternative notions of distance from real-world data or \textit{a priori} relationships between geographic entities.
 
@@
 This approach, originally designed for learning language models~\autocite{mikolov2013word2vec} has been used to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
-In addition to providing a data-driven functional distance, this approach is computationally efficient, scalable for large datasets, robust to noise, and is readily interpretable through the application of simple vector arithmetic.
-
-We use scientific mobility (scientific co-affiliation) as a case study to demonstrate the neural embedding approach. 
-Scientific mobility is a central aspect of the increasingly-globalized scientific system~\autocite{czaika2018globalisation}, being strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}.
+Neural embedding is also computationally efficient, scalable for large datasets, robust to noise, and is readily interpretable through the application of simple vector arithmetic.
+
+We use scientific mobility, inferred from affiliations, to demonstrate the neural embedding approach. 
+Scientific mobility is a central aspect of the increasingly-globalized scientific system~\autocite{czaika2018globalisation, altbach2004globalization}, being strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}.
 For nations and organizations hoping to win in the global competition for talent~\autocite{box2008competition}, understanding the landscape of global scientific mobility is essential. 
 However, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}.
-Neural embedding offers a means of capturing the complex global structure of scientific mobility in a dense and coherent representation that supports modeling and predicting mobility flows, mapping patterns of mobility at multiple scales, and quantifying abstract notions such as academic prestige.
-
-The most fine-grained geographical unit of scientific production is the organization, such as an university, research institute, business, or government agency.
-As a scientist's careers progress, they move between organizations or pick up additional simultaneous affiliations forming co-affiliation or \textit{mobility trajectories}.
-These mobility trajectories, represented as ordered lists of organizations, can be derived from affiliations listed on the researcher's publication histories~\autocite{robinson2019mobility, sugimoto2017mostimpact} (Fig.~\ref{fig:methods:mobility_sentence}).
+One roadblock is the lack of a meaningful measure of functional distance between countries, cities, and organizations.
+
+Here, scientific mobility is operationalized using researcher's organizational affiliations derived from their publication histories indexed in a large-scale bibliographic database. 
+The most fine-grained geographical unit in this data is the organization, such as an university, research institute, business, or government agency.
+As a scientist's careers progress, they move between organizations or pick up additional (simultaneous) affiliations forming \textit{affiliation trajectories} (Fig.~\ref{fig:methods:mobility_sentence}.
+These trajectories encodie both asynchronous migration, and synchronous mobility---the holding of multiple simultaneous co-affiliations involving the sharing of time and capital between locations---that is typical of scientific mobility~\autocite{rodrigues2016mobility, markova2016synchronous, sugimoto2017mostimpact} (see Supplementary Materials).
 We use the trajectories of the three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
+
 A vector-space embedding of organizations is learned by using mobility trajectories as input to the standard skip-gram with negative sampling, or \textit{word2vec} neural-network architecture.
@@
 
-Where the \textit{expected flux}, $\hat{T_{ij}}$, or expected number of authors co-affiliated with a pair organizations during the time period is proportional to the organization's sizes (the sum of both mobile and non-mobile authors, see Data and Methods), $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+Where the \textit{expected flux}, $\hat{T_{ij}}$, or expected number of authors who were affiliated with both organizations during the time period is proportional to the organization's sizes (the sum of both mobile and non-mobile authors, see Data and Methods), $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
 The distance function is defined in terms of either the geographic distance between organizations or the embedding distance. 

### 2020-07-14 paper/current/main.tex
updates to remaining results and conclusion

@@
 The embedding distance defined from the cosine distnace between vectors also outperforms that defined from their dot product ($R^{2} = 0.34$, Fig.~\ref{fig:supp:gravity_dot}).
-The embedding distance also out-performs alternative ``diffusion'' measures such as the personalized-page rank scores (see supporting materials) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-Geographic distance alone is a poor perspective for understanding international scientific mobility---rather, by learning a functional distance directly from the data, it is possible to better explain, and better predict the flow of scientific mobility between organizations.
+The embedding distance also out-performs alternative ``diffusion'' network distance measures such as the personalized-page rank scores (see supporting materials) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+Our results unequivecolly argue that the distance learned by the embedding method better capture actual mobility patterns than does geographic distance. 
 We speculate that this results from an underlying mathematical connection between the neural embedding architecture and the gravity model of mobility.
@@
 		\textbf{a.} embedding distance (cosine distance between organization vectors) explains more of the expected flux between organization pairs than does geographic distance (\textbf{b}).
-		Red line is line of best fit.
+		The red line is the line of best fit.
 		Black dots are mean flux across binned distances.
@@
 		Box color corresponds to the degree to which the distribution overlaps $x = y$.
-		``Err'' is calculated as the root-mean-squared error between the actual and predicted values.
+		``RMSE'' is calculated as the root-mean-squared error between the actual and predicted values.
 		\textbf{e-f.} Predictions made using model parameters learned from a subset of domestic (within-country) organization pairs.
@@
 
-What information is encoded in the embedding that allows embedding distance to outperform geographic distance?
-To explore the structure of the embedding space, we use a common dimensionality reduction technique (UMAP~\autocite{mcinnes2018umap}) to visualize it in two dimensions (Fig.~\ref{fig:projection}a).
+By encoding the complex landscape in a dense representation, embeddings also allow us to create informative visualizations of global scientific mobility.
+To explore the embedding, we use a common dimensionality reduction technique (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation of the embedding (Fig.~\ref{fig:projection}a).
 By showing relationships between individual organizations, rather than aggregates such as nations or cities, this projection constitutes the largest and highest resolution ``map'' of scientific mobility to date.
@@
 
-An advantage of the embedding space is the ability to \textit{zoom in} on subsets of counties and re-project them in order to reveal more local relationships. 
+The embedding space also allows us to to \textit{zoom in} on subsets of counties and re-project them in order to reveal more local relationships. 
 For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries ranging from Egypt to Phillipines that corresponds to both geography but also cultural factors, such as the majority religion of each country;
-for example, the cluster for Malaysia, a majority-Muslim country, is nearer to other Middle Eastern nations than Thailand, a country that is geographically-nearer though with very different religious demographics.
-Linguistic and historical ties are also important.
-For example, we observe that Spanish-speaking post-colonial Latin American nations (Mexico, Chile, Peru, etc.) are positioned near Spain, whereas Brazil is nearer to Portugal (Fig.~\ref{fig:projection}c).
+for example, the cluster for Malaysia, a majority-Muslim country, is nearer to other Middle Eastern nations than Thailand, a country that is geographically-nearer but religiously-distant. 
+Linguistic and historical ties are also conspicuous.
+For example, we observe that Spanish-speaking post-colonial Latin American nations (Mexico, Chile, Peru, etc.) are positioned near Spain, whereas Brazil is nearer to Portugal (Fig.~\ref{fig:projection}c) reflecting the role of language, culture, and colonial history that shapes scientific mobility.
 Similarly, Algeria and Morocco are near the French cluster (Fig.~\ref{fig:projection}a).
@@
 
-Just as the embedding space makes it possible to "zoom in" on subsets of organizations, it is possible to "zoom out" to a higher level by aggregating organizational vectors. 
+Just as the embedding space makes it possible to ``zoom in'' on subsets of organizations, it is possible to ``zoom out'' to a higher level by aggregating organizational vectors. 
 For example, we can examine high-level structure by estimating the aggregate embeddings of countries. 
@@
 \ref{fig:clustering}a).
-The six identified clusters roughly correspond to: East-Asian (orange), Scandinavian (dark purple), British Commonwealth (light purple), Central and Eastern European countries (light blue), and then two cluster diverse clusters with a mix of European, Latin American, and Mediterranean countries.
+The six identified clusters roughly correspond to: East-Asian (orange), Scandinavian (dark purple), British Commonwealth (light purple), Central and Eastern European countries (light blue), and then two remaining diverse clusters that contain a mix of European, Latin American, and Mediterranean countries.
 These clusters demonstrate the importance of not only geography, but also linguistic ties between countries.
@@
 		Color of three cell rows separated from the matrix correspond to, from left to right, the continent of the country, the language family~\autocite{ethnologue}, and the individual language.
-		\textbf{b.}	\textit{CluSim} \autocite{gates2019element} results demonstrating the factors dictating hierarchical clustering, varying by scaling parameter, $r$.
+		\textbf{b.}	Element-centric cluster similarity~\autocite{gates2019element} results demonstrating the factors dictating hierarchical clustering, varying by scaling parameter, $r$.
 		Continent better explains the grouping of country vectors at higher levels of the clustering processes.
@@
 Prestige hierarchies underpin the dynamics of scientific mobility~\autocite{deville2014career, clauset2015hierarchy}, but are these hierarchies captured in the embedding space?
-We test this by exploting the geometric properties of the embedding space with the technique SemAxis~\autocite{an2018semaxis}, an approach originally designed for characterize the semantics of words in language embeddings, but is equally applicable here.
-In the context of organization vectors, this approach leverages the unique properties of the embedding space in order to quantify the nearness of an organization to the ends of some meaningful axis. 
-The axis is defined by the user and should represent some meaningful  and coherent concept. 
-Organization vectors are then projected onto this axis, and their position estimates their similarity to the concepts embodied by either end of the axis. 
+We test this by exploiting the geometric properties of the embedding space with the technique SemAxis~\autocite{an2018semaxis}, an approach originally designed for characterize the semantics of words in language embeddings.
 Here, we use SemAxis to operationalize the abstract notion of academic prestige, defining each end of the axis using known high- and low-ranked universities. 
@@
 
-Universities hiring and mobility networks are known to exhbit latent pretige hierarchies ~\autocite{deville2014career, clauset2015hierarchy} that should be encoded in the embedding space.
-Accordingly, prestigious universities such as Stanford, Colombia, MIT, Harvard, and NYU are positioned towards the top of the axis (Fig.~\ref{fig:semaxis}a).
-Universities at the bottom of this axis tend to be regional universities with lower national profiles.
-By considering mobility between all organization types, SemAxis applied to embeddings offers a new means of reasoning about the prestige of organizations typically excluded from rankings such as government organizatioss (Fig.~\ref{fig:supp:semaxis_sectors}a), research institutes (Fig.~\ref{fig:supp:semaxis_sectors}b), and teaching colleges (Fig.~\ref{fig:supp:semaxis_sectors}c).
+Prestigious universities such as Stanford, Colombia, MIT, Harvard, and NYU are positioned towards the top of the axis (Fig.~\ref{fig:semaxis}a).
+Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education).
+SemAxis also offers a new means of reasoning about the prestige of organizations typically excluded from rankings such as government organizatioss (Fig.~\ref{fig:supp:semaxis_sectors}a), research institutes (Fig.~\ref{fig:supp:semaxis_sectors}b), and teaching colleges (Fig.~\ref{fig:supp:semaxis_sectors}c).
 
@@
 		\textbf{Embedding captures latent geography and prestige hierarchy.}
-		\textbf{a.} illustrates SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top five and geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S.
-Universities (bottom to top).
-		Points correspond to organizations, and a sample of individual states are highlighted.
+		\textbf{a.} Illustrates SemAxis projection along two axes,California and Massachusetts and for the top five-to geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S.
+Universities.
+		Points correspond to organizations, and a sample of states are highlighted.
 		Full organization names listed in Table~\ref{table:supp:orglabels}.
 		\textbf{b.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity to the \textit{Elite} end of the axis prestige axis \textit{a}.
-		White points are those top and bottom five universities aggregated to define the ends of the axis.
-		The grey box corresponds to the top five and bottom five ranks.
-	  	Even when considering only a total of ten organization vectors, the estimate of the spearman rank correlation between the SemAxis and Times ranking is 0.73 (n = 145).
+		White points are those top and bottom five universities used to define the poles of the axis.
+	  	Even when considering only a total of ten organization vectors, the estimate of the spearman rank correlation between the SemAxis and Times ranking is 0.73 (n = 145), and increases if controlling for the number of top-and-bottom ranked universities (Fig.~\ref{fig:supp:semaxis_compare}).
 	}
@@
 
-The embedding space captures prestige hierarchies to such a high resolution that they can be used to reconstruct academic rankings. 
-We derive a ranking using the prestige axis that we call \textit{SemRank}, and compare them to traditional university rankings.
-SemRank is defined from the position of organizations along the prestige axis, with the top ranked being the furthest towards the \textit{Elite} end of the axis.
-We find that SemRank derived is highly correlated with the Times ranking ($\rho = 0.73$, Fig.~\ref{fig:semaxis}b).
-This correlation is robust with the number of organizations used to define the axes (Fig.
-SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities is strongly correlated with the Times Ranking ($\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
-For reference, SemRank achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking~\autocite{waltman2012leidenrankings}, a common and bibliometrically-informed university ranking ($\rho = 0.87$, Fig.~\ref{fig:supp:times_vs_leiden}).
-This suggests that the organization embedding captures the latent prestige hierarchy inherent to academic mobility with a high degree of resolution and reliability.
-
-While we use SemAxis to operationalize notions of prestige and geography, the approach can be easily generalized to other concepts so long as they can be meaningfully represented as an axis in the vector space.
-For example, axes could similarly be defined between teaching- and research-focused universities, between companies and government agencies, or between organizations in the U.S. and in China.
+The embedding space captures prestige hierarchies can be used to reconstruct academic rankings. 
+We derive a ranking using the SemAxis prestige axis in Fig.~\ref{fig:semaxis}.a and compare them to traditional university rankings.
+The SemAxis ranking is defined from the position of organizations along the prestige axis, with the top ranked being the furthest towards the \textit{Elite} end of the axis.
+We find that the SemAxis ranking is highly correlated with the Times ranking (Spearman's $\rho = 0.73$, Fig.~\ref{fig:semaxis}b).
+The strongest outliers are universities that were ranked more highly in the Times Ranking than the SemAxis ranking and tended to be large universities such as Arizona State University and  University of Florida;
+Those ranked higher in the SemAxis ranking tended to be relatively-smaller universities such as the University of San Francisco and University of Maryland Baltimore County.
+
+The correlation between SemAxis and the Times ranking is robust with the number of organizations used to define the axes (Fig.
+SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities is strongly correlated with the Times Ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
+For reference, SemRank achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking~\autocite{waltman2012leidenrankings}, a common and bibliometrically-informed university ranking (Spearman's $\rho = 0.87$, Fig.~\ref{fig:supp:times_vs_leiden}).
+This suggests that the organization embedding surprisingly captures the latent prestige hierarchy inherent to academic mobility with a high degree of resolution and reliability~\autocite{deville2014career, clauset2015hierarchy}.
 
@@
 
-Mobility and migration are central to the human experience~\autocite{shah2020migration}, but recent events threaten to upend patterns of human mobility that defined in recent decades. 
+Neural embeddings offer a natural approach for learning an effective and robust functional distance between places based on mobility trajectory data. 
+Here, we demonstrated how the embedding space encodes complex aspects of scientific mobility, such as global and regional geography, national similarity, and organizational prestige.
+While scientific mobility is used as a case study, this approach can be broadly applied to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
+Moreover, this approach can be used to learn a functional distance between entities when no such analog to geographic distance exists, such as a functional distance between occupational categories based on individual's career trajectories.
+In addition to providing a functional distance that supports modeling and predicting mobility patterns, the unique structure of neural embedding also allows for a range of methodological applications.
+For instance, projecting the embedding space onto two dimensions using UMAP allows for the visualization of the complex structure of scientific mobility at high resolution and at multiple scales, which has implications.
+Other techniques, such as SemAxis, allow the potential to quantify abstract notions in mobility such as academic prestige, and can also be generalized to other abstract axes.
+Neural embedding opens the door for new approaches for representing and understanding patterns of global human mobility.
+
+In spire of its promise, this approach and analysis presents several limitations. 
+First, the standard neural embedding model non-directional, meaning that embedding will be less effective at capturing mobility for which directional is critical.
+Second, the neural embedding approach is most useful in cases of mobility between discrete geographic entities such as between countries, cities, and businesses; this approach is less useful in the case of mobility between arbitrary locations represented in geographic coordinates, such as in the modeling of animal movements.
+Neither of these methodological limitations are insurmountable, and future work can aim to incorporate directionality and identify meaningful representations of continuous mobility data. 
+Finally, the case of scientific mobility presents domain-specific limitations. 
+Reliance on bibliometric metadata means that we capture only long-term mobility such as migration, rather than the array or more frequent short-term mobility such as conference travel and temporary visits.
+The kinds of mobility we do capture—asynchronous migration and synchronous co-affiliation, are treated identically by our model even though they are qualitatively different.
+Scientific mobility is complex, and its study continues to pose challenges; neural embeddings do not solve many of these issues, but they create opportunities for new analyses and understanding
+Future work should aim to
+
+Mobility and migration is a core asepct of human nature and history~\autocite{shah2020migration}, driving social phenomena as diverse as epidemics\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity} and science and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage, morgan2018prestige, rodrigues2016mobility}.
 Within science, mobility has grown increasingly global~\autocite{czaika2018globalisation}, though the travel restrictions in the U.S.
@@
 Now, more than ever, new tools and approaches are needed to understanding human mobility in order to inform sensible, effective, humane Immigration and Science and Technology policy.
-
-Neural embeddings offer a natural approach for learning an effective and robust functional distance between places based on mobility trajectory data. 
-Here, we demonstrated how the embedding space encodes complex aspects of scientific mobility, such as global and regional geography, national similarity, and organizational prestige.
-While scientific mobility is used as a case study, this approach can be broadly applied to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
-Moreover, this approach can be used to learn a functional distance between entities when no such analog to geographic distance exists, such as a functional distance between occupational categories based on individual's career trajectories.
-In addition to providing a functional distance that supports modeling and predicting mobility patterns, the unique structure of neural embedding also allows for a range of methodological applications.
-For instance, projecting the embedding space onto two dimensions using UMAP allows for the visualization of the complex structure of scientific mobility at high resolution and at multiple scales. 
-Other techniques, such as SemAxis, allow the potential to quantify abstract notions in mobility such as academic prestige. 
-Neural embedding opens the door for new approaches for representing and understanding patterns of global human mobility.
 

### 2020-07-14 paper/current/main.tex
minor edits, throughout methods and supplementals

@@
 		White points are those top and bottom five universities used to define the poles of the axis.
-	  	Even when considering only a total of ten organization vectors, the estimate of the spearman rank correlation between the SemAxis and Times ranking is 0.73 (n = 145), and increases if controlling for the number of top-and-bottom ranked universities (Fig.~\ref{fig:supp:semaxis_compare}).
+	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the SemAxis and Times ranking is 0.73 (n = 145), and increases if controlling for the number of top-and-bottom ranked universities (Fig.~\ref{fig:supp:semaxis_compare}).
 	}
@@
 However, due to their size, the USA, accounted for nearly 40 percent of all mobile authors worldwide (Fig.~\ref{fig:supp:descriptives}a), with 10 countries accounting for 80 percent of all mobility (Fig.~\ref{fig:supp:descriptives}b).
-In most cases, countries with a high degree inter-organization mobility also had a high degree of international mobility;
-however, the USA and France had a high degree of inter-organization mobility with the corresponding international mobility (Fig.~\ref{fig:supp:descriptives}c).
+The countries with the highest proportion of mobile scientists are France, Qatar, the United States, and Iraq, whereas those with the lowest are Jamaica, Serbia, Bosnia \& Herzegovina, and North Macedonia\ref{fig:supp:descriptives}.c).
+In most cases, countries with a high degree of inter-organization mobility also have a high degree of international mobility, indicating a high proportion of their total mobility being international (Fig.~\ref{fig:supp:descriptives}.d);
+However, some countries such as France and the United States seem to have more domestic mobility than international mobility. 
 While the number of publications has increased year-to-year, the mobility and disciplinary makeup of the dataset has not significantly changed across the period of study (Fig.~\ref{fig:supp:pubs_over_time}).
@@
 We embed co-affiliation trajectories by treating them analogously to sentences, and organizations analogously to words.
-The trajectories of mobile authors were converted to ''mobility sentences`` by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:methods:mobility_sentence}.a.
+The trajectories of mobile authors were converted to ``affiliation trajectories'' by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:methods:mobility_sentence}.a.
 In more complex cases, such as listing multiple affiliations on the same paper or publishing with different affiliations on multiple affiliations in the same year, the order is randomized within that year, as shown in  Fig.~\ref{fig:methods:mobility_sentence}.b.
@@
 %% word2vec
-These mobility sentences are used as input to the standard skip-gram negative sampling model, for word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec} .
+These affiliation trajectories are used as input to the standard skip-gram negative sampling model, for word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec} .
 In natural-language processing, word embeddings are used to construct dense vector-space representations of words and phrases, in which distance relationships between words correspond to a notion of semantic distance.
-By embedding co-affiliation trajectories, we aim to learn a dense vector for every organization where distance between vectors relates to the tendency for two organizations to co-occur in a token window around the target term in the same career trajectory.
+By embedding affiliation trajectories, we aim to learn a dense vector for every organization where distance between vectors relates to the tendency for two organizations to co-occur in a token window around the target organization token in the same career trajectory.
 Vectors are learned by training a neural network to optimize the prediction of the so-called context term given a target, in our case using one organization to predict the others appearing in the same co-affiliation trajectory.
-The hidden layer of the trained neural network is used as the
+The hidden layer of the trained neural network is used as the final representation.
 
@@
 
-In embedding space, we can consider two proximity measures: cosine similarity and dot product.
-Cosine similarity only consider about angle difference of two embedding vectors, while dot product cares about angle and magnitude at the same time.
-If vectors are normalized, they are the same.
-In general, which measure is good depends on the task.
-If the task is desirable to ignore the magnitude, then cosine similarity is better, otherwise, the dot product is better.
-
 %
@@
 The embedding distance with the cosine similarity, $d_{ij}$, is calculated as the pairwise cosine distance between vectors from the learned organization embedding, where $v_{i}$ and $v_{j}$ represent the vectors and $d_{ij} = 1 - \frac{v_{i} \cdot v_{j}}{\lVert v_{i} \rVert \lVert v_{j} \rVert}$.
-Additionally, the embedding distance with the dot product, we use  $d_{ij} =  -v_{i} \cdot v_{j}$.
 
@@
 For geographic distance, we use the power-law function of the gravity law, with $f(g_{ij})= g^{-\alpha}_{ij}$, where $\alpha$ is estimated from the data.
-For embedding distance , we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data.
+For embedding distance, we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data.
 To estimate parameters $C$, $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_basic}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.
@@
 	\label{eq:linear_flux_geo}
-	\ln(\frac{T_{ij}}{m_im_j}) = \ln(C)  - \alpha \ln(g_{ij})
+	\ln\frac{T_{ij}}{m_im_j} = \ln(C)  - \alpha \ln(g_{ij})
 \end{equation}
@@
 	\label{eq:linear_flux_emb}
-	\ln(\frac{T_{ij}}{m_im_j}) = \ln(C) - \beta d_{ij}
+	\ln\frac{T_{ij}}{m_im_j} = \ln(C) - \beta d_{ij}
 \end{equation}
@@
 \subsection*{SemAxis}
-By constructing semantic embeddings from mobility trajectories, we allow for unique methodology for understanding the embedding space, such as SemAxis.
 SemAxis~\autocite{an2018semaxis} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these term to the concept.
-The precise axis is an antonym pair defined \textit{ad-hoc} for the specific use case.
-In the case of language, the ends of the axis could be ``good'' and ``bad'', ``surprising'' and ``unsurprising'', or ``masculine'' and ``feminine''.
-It is shown that projection of words to given specific axis fit well with widely shared cultural connotation from surveyed
-responses and labeled historical data \autocite{kozlowski2018geometry}.
-
-In this analysis, we embed organization identifiers and trajectories, rather than words and sentences, however mobility can be thought of semantically, just like language. 
-Under this view, organizations can be thought of as similar when they have similar \textit{contexts}--that is, authors affiliated with that organization also tend to co-affiliate the same set of other organizations.
+Each axis is an antonym pair defined for each specific use case.
+In the case of language, the poles of the axis could be ``good'' and ``bad'', ``surprising'' and ``unsurprising'', or ``masculine'' and ``feminine''. 
 By treating organizations analogously to words and trajectories analogously to sentences, we can use SemAxis to leverage the semantic properties of the resulting embedding vectors to operationalize abstract relationships between organizations.
 
-Here, we apply SemAxis to U.S. universities by defining two axes, one of geography and one of academic prestige.
+Given vectors representing the positive and negative poles of an axis, $v^{+}$ and $v^{-}$, the axis is defined as.$v_{\text{axis}} = v^{+} - v^{-}$.
+For each organization in the embedding space, $w$, a score is calculated relating the term to to the positive, $v^{+}$ or negative, $v^{-}$ pole, calculated as the cosine similarity of the organization's vector with the axis,
+
+$$
+score(w)v_{\text{axis}} = \cos(u_{w}, v_{\text{axis}})
+$$
+
+We apply SemAxis to U.S. universities by defining two axes, one of geography and one of academic prestige.
 The poles of the geographic axis are defined as the mean vector of all vectors corresponding to organizations in California, and then the mean of all vectors of organizations in Massachusetts.
@@
 For example, if 20 universities top-ranked universities are selected and six of them are in the Northeastern United States, then the bottom six universities according to the same ranking will be included in the low-ranked subset.
-From the prestige axis we also derive what we call \textit{SemRank}, a university ranking based on the nearness of universities to the \textit{Elite} end of the axis.
-We compare the SemAxis ranking to the traditional university rankings using Spearman rank correlations.
+From the prestige axis we derive a ranking of universities that we then compare to other formal university rankings using Spearman rank correlation.
 
@@
 	\label{eq:KL}
-	D_{KL} = \sum p(x)\log(\frac{p(x)}{q(x)})
+	D_{KL} = \sum p(x)\log\frac{p(x)}{q(x)}
 \end{equation}
@@
 		The grey box corresponds to the top 20 and bottom 20 ranks.
-	  	PCC details the estimate from Spearman correlation between the two rankings.
+	  	Spearman's rho details the estimate from Spearman correlation between the two rankings using all universities, including those used to define the ends of each axis. 
 	}

### 2020-07-14 workflow/clustering_figure/script/draw_clustering_figure_country_level.py
output country-level pairwise distnaces along with clustering figure

@@ -22,6 +22,7 @@ def draw_figure(
     COUNTRY_META_INFO_FILE,
     FONT_PATH,
     BOLD_FONT_PATH,
+    DISTANCE_DATA_PATH,
     DENDROGRAM_PART_PATH,
     HEATMAP_PART_PATH,
     CLUSIM_PART_PATH,
@@ -172,6 +173,15 @@ def draw_figure(
     bold_prop = font_manager.FontProperties(fname=BOLD_FONT_PATH, size=22)
     small_prop = font_manager.FontProperties(fname=FONT_PATH, size=20)
     tick_prop = font_manager.FontProperties(fname=FONT_PATH, size=16)
+
+    # Save the pairwise distances to a file
+    sim_df = pd.DataFrame(sim_mtx)
+    sim_df.columns = target_countries
+    sim_df.index = target_countries
+    upper_tri = sim_df.where(np.triu(np.ones(sim_df.shape)).astype(np.bool))
+    upper_tri = upper_tri.stack().reset_index()
+
+    upper_tri.to_csv(DISTANCE_DATA_PATH, index = False)
 
     # Draw heatmap part
     g = sns.clustermap(
@@ -366,9 +376,10 @@ if __name__ == "__main__":
     COUNTRY_META_INFO_FILE = sys.argv[3]
     FONT_PATH = sys.argv[4] if sys.argv[4] != "None" else None
     BOLD_FONT_PATH = sys.argv[5] if sys.argv[5] != "None" else None
-    DENDROGRAM_PART_PATH = sys.argv[6]
-    HEATMAP_PART_PATH = sys.argv[7]
-    CLUSIM_PART_PATH = sys.argv[8]
+    DISTANCE_DATA_PATH = sys.argv[6]
+    DENDROGRAM_PART_PATH = sys.argv[7]
+    HEATMAP_PART_PATH = sys.argv[8]
+    CLUSIM_PART_PATH = sys.argv[9]
 
     draw_figure(
         INPUT_EMBEDDING_FILE,
@@ -376,6 +387,7 @@ if __name__ == "__main__":
         COUNTRY_META_INFO_FILE,
         FONT_PATH,
         BOLD_FONT_PATH,
+        DISTANCE_DATA_PATH,
         DENDROGRAM_PART_PATH,
         HEATMAP_PART_PATH,
         CLUSIM_PART_PATH,

### 2020-07-14 paper/current/main.tex
added quantitative values to discussion of UMAP plot

@@
 The embedding space also allows us to to \textit{zoom in} on subsets of counties and re-project them in order to reveal more local relationships. 
-For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries ranging from Egypt to Phillipines that corresponds to both geography but also cultural factors, such as the majority religion of each country;
-for example, the cluster for Malaysia, a majority-Muslim country, is nearer to other Middle Eastern nations than Thailand, a country that is geographically-nearer but religiously-distant. 
+For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries ranging from Egypt to Philippines that corresponds largely to geography, but with some peculiar exceptions.
+For example, countries like Iraq are nearer to some southeast-Asian countries like Malaysia, with a cosine distance between the nation's aggregate vectors of $d = 0.29$, than to nearer and more religiously-similar nations like Saudi Arabia ($d = 0.50$ and Qatar ($d = 0.51$).
 Linguistic and historical ties are also conspicuous.
-For example, we observe that Spanish-speaking post-colonial Latin American nations (Mexico, Chile, Peru, etc.) are positioned near Spain, whereas Brazil is nearer to Portugal (Fig.~\ref{fig:projection}c) reflecting the role of language, culture, and colonial history that shapes scientific mobility.
-Similarly, Algeria and Morocco are near the French cluster (Fig.~\ref{fig:projection}a).
+For example, we observe that Spanish-speaking post-colonial Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), such as Mexico ($d = 0.34$) and Chile ($d = 0.39$) morose than to nearby Portuguese-speaking Brazil ($d = 0.52$ for Mexico and $d = 0.49$ for Chile).
+Similarly, North-African countries that were once under French rule such as Morocco are nearer to France ($d =0.35$) than to similarly-distant European countries as Spain ($d = 0.40$) and Italy ($d = 0.53$).
 Comparable structural patterns exist even within a single country.
-For example, at the global level (Fig~\ref{fig:projection}a), organizations within Quebec in Canada are located near the French cluster rather than the rest of Canada.
+For example, at the global level (Fig~\ref{fig:projection}a), organizations within Quebec in Canada are located nearer the French cluster ($d = 0.65$) than the rest of the Canadian universities Canada ($d = 0.88$).
 
@@
 universities) and university systems.
-Even though UMass Boston is located in Boston, it clusters near other universities in the UMass System rather than the typically more elite and research-focused universities in Boston, reflecting a relative lack of mobility between the two systems, even within the same state.
-Similar structures can be observed in other states such as among New York's CUNY and SUNY systems (Fig.~\ref{fig:supp:proj_newyork}), Pennsylvania's state system (Fig.~\ref{fig:supp:proj_pennsylvania}), Texas's Agricultural and Mechanical universities(Fig.~\ref{fig:supp:proj_texas}), and between the University of California and State University of California systems (Fig.~\ref{fig:supp:proj_california}).
+For example, even though UMass Boston is located in Boston, it clusters near other universities in the UMass System ($d = 0.34$) rather than the other typically more elite and research-focused universities in Boston ($d = 0.41$), reflecting a relative lack of mobility between the two systems, even within the same state.
+Similar structures can be observed in other states such as among New York's CUNY and SUNY systems (Fig.~\ref{fig:supp:proj_newyork}), Pennsylvania's state system (Fig.~\ref{fig:supp:proj_pennsylvania}), Texas's Agricultural and Mechanical universities (Fig.~\ref{fig:supp:proj_texas}), and between the University of California and State University of California systems (Fig.~\ref{fig:supp:proj_california}).
 

### 2020-07-14 workflow/clustering_figure/script/draw_clustering_figure_country_level.py

@@ -55,6 +55,28 @@ def draw_figure(
     target_countries = [
         k for k, v in Counter(country_list).items() if v >= 25 and k != "United States"
     ]
+
+    # First, get all pairwise distances and save to a file
+    representative_vector_all = [
+        embedding_list[country_list == country].mean(axis=0)
+        for country in country_list
+    ]
+    sim_mtx_all = mt.pairwise.cosine_similarity(representative_vector_all)
+
+    # Save the pairwise distances to a file
+    sim_df = pd.DataFrame(sim_mtx_all)
+
+    # set column names
+    sim_df.columns = country_list
+    sim_df.index = country_list
+
+    upper_tri = sim_df.where(np.triu(np.ones(sim_df.shape)).astype(np.bool))
+    upper_tri = upper_tri.stack().reset_index().drop_duplicates()
+
+    # save the file
+    upper_tri.to_csv(DISTANCE_DATA_PATH, index = False)
+
+    # Now shift to only the target countires
     representative_vector = [
         embedding_list[country_list == country].mean(axis=0)
         for country in target_countries
@@ -173,15 +195,6 @@ def draw_figure(
     bold_prop = font_manager.FontProperties(fname=BOLD_FONT_PATH, size=22)
     small_prop = font_manager.FontProperties(fname=FONT_PATH, size=20)
     tick_prop = font_manager.FontProperties(fname=FONT_PATH, size=16)
-
-    # Save the pairwise distances to a file
-    sim_df = pd.DataFrame(sim_mtx)
-    sim_df.columns = target_countries
-    sim_df.index = target_countries
-    upper_tri = sim_df.where(np.triu(np.ones(sim_df.shape)).astype(np.bool))
-    upper_tri = upper_tri.stack().reset_index()
-
-    upper_tri.to_csv(DISTANCE_DATA_PATH, index = False)
 
     # Draw heatmap part
     g = sns.clustermap(

### 2020-07-14 paper/current/main.tex
replace 'mobility' with 'affiliation' trajectory

@@
 The most fine-grained geographical unit in this data is the organization, such as an university, research institute, business, or government agency.
-As a scientist's careers progress, they move between organizations or pick up additional (simultaneous) affiliations forming \textit{affiliation trajectories} (Fig.~\ref{fig:methods:mobility_sentence}.
+As a scientist's careers progress, they move between organizations or pick up additional (simultaneous) affiliations forming \textit{affiliation trajectories} (Fig.~\ref{fig:methods:mobility_sentence}).
 These trajectories encodie both asynchronous migration, and synchronous mobility---the holding of multiple simultaneous co-affiliations involving the sharing of time and capital between locations---that is typical of scientific mobility~\autocite{rodrigues2016mobility, markova2016synchronous, sugimoto2017mostimpact} (see Supplementary Materials).
@@
 
-A vector-space embedding of organizations is learned by using mobility trajectories as input to the standard skip-gram with negative sampling, or \textit{word2vec} neural-network architecture.
-In the resulting embedding, each organization corresponds to a single vector, and vectors relate to one another based on the likelihood of organizations appearing near together in the mobility trajectory data.
+A vector-space embedding of organizations is learned by using affiliation trajectories as input to the standard skip-gram with negative sampling, or \textit{word2vec} neural-network architecture.
+In the resulting embedding, each organization corresponds to a single vector, and vectors relate to one another based on the likelihood of organizations appearing near together in the affiliation trajectory data.
 The functional distance between two organizations is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.
@@
     \caption{
-        \textbf{Construction of mobility trajectories from publication records}
+        \textbf{Construction of affiliation trajectories from publication records}
         \textbf{a.}
         An author published five papers across five time periods, with only one affiliation listed in the byline of each paper.
-        To each organization, a unique identifier is assigned, and they are assembled into a mobility trajectory ordered by year of publication.
+        To each organization, a unique identifier is assigned, and they are assembled into a affiliation trajectory ordered by year of publication.
         \textbf{b.}
@@
 
-Neural embeddings offer a natural approach for learning an effective and robust functional distance between places based on mobility trajectory data. 
+Neural embeddings offer a natural approach for learning an effective and robust functional distance between places based on affiliation trajectory data. 
 Here, we demonstrated how the embedding space encodes complex aspects of scientific mobility, such as global and regional geography, national similarity, and organizational prestige.
@@
 \label{si:text:mobility_traj}
-{\bf Building mobility trajectories.}
-
-We adopt a data-driven approach to constructing mobility trajectories, making as little adjustment to the raw bibliometric data as possible. 
-For each mobile researcher (having at least two distinct affiliations), we construct a mobility trajectory based on the affiliations listed on their published papers indexed in the Web of Science database between 2008 and 2019.
+{\bf Building affiliation trajectories.}
+
+We adopt a data-driven approach to constructing affiliation trajectories, making as little adjustment to the raw bibliometric data as possible. 
+For each mobile researcher (having at least two distinct affiliations), we construct an affiliation trajectory based on the affiliations listed on their published papers indexed in the Web of Science database between 2008 and 2019.
 An author is considered mobile if they published with at least two distinct affiliations during the time period of study. 
@@
 Affiliations in a trajectory are first ordered by year of publication.
-For example, if an author published with affiliation $A$ in $t_{0}$, affiliation $B$ in $t_{1}$, and $A$ again in $t_{2}$, then their ordered mobility trajectory would be $\{A, B, C\}$.
+For example, if an author published with affiliation $A$ in $t_{0}$, affiliation $B$ in $t_{1}$, and $A$ again in $t_{2}$, then their ordered affiliation trajectory would be $\{A, B, C\}$.
 
@@
 
-Other than restricting to only mobile researchers, we do not perform any filtering or reductions to mobility trajectories.
+Other than restricting to only mobile researchers, we do not perform any filtering or reductions to affiliation trajectories.
 For example, in the case than an author publishes with organization $A$ four times in $t_{0}$, and affiliation $B$ two times in $t_{1}$, then their trajectory will be $\{A, A, A, A, B, B\}$. 

### 2020-07-14 workflow/scripts/PlotDescriptive/PlotCountryMobilityDistribution.R
clean up descriptive files, fix bugs in workflow

@@ -1,9 +1,10 @@
 #
-# PlotProportionMobilityByCountry.R
+# PlotCountryMobilityDistribution.R
 #
 # author: Dakota Murray
 #
-# Plot the proportion of mobile vs. nonmobile researchers by country
+# Plot the distirbution of country's based on their contribution to
+# global mobility
 #
 
 # Plot dimensions
@@ -44,7 +45,7 @@ flows <- read_delim(opt$flows, delim = "\t", col_types = readr::cols())
 nonmobile <- read_delim(opt$nonmobile, delim = "\t", col_types = readr::cols())
 
 # Merge with nonmobile individuals
-flows <- data.table::rbindlist(list(flows, nonmobile))
+flows <- data.table::rbindlist(list(flows, nonmobile), fill = T)
 
 flows <- flows %>%
   select(-LR_main_field_no, -pub_year) %>%
@@ -69,36 +70,28 @@ plotdata <- flows %>%
     cumulative = cumsum(prop)
   )
 
-# Build separete dataframe for the labels
+# Get dataframe of labels for the plot
 labels = plotdata %>%
-  top_n(5, prop) %>%
+  top_n(10, prop) %>%
   mutate(
-    text = ifelse(country_iso_alpha == "USA", "USA", paste0("+", country_iso_alpha))
+    text = country_iso_alpha
   )
 
 # Build the plot
 plot <- plotdata %>%
-  ggplot(aes(x = index, y = cumulative)) +
-    geom_step() +
-    scale_x_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30, 50), expand = c(0, 0)) +
-    scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.7, 0.8, 0.9, 1.0), expand = c(0, 0)) +
-    geom_segment(x = 0, xend = 10, y = 0.80, yend = 0.80, linetype = "dashed", color = "darkgrey") +
-    geom_segment(x = 10, xend = 10, y = 0, yend = 0.80, linetype = "dashed", color = "darkgrey") +
-    geom_segment(x = 0, xend = 17, y = 0.90, yend = 0.90, linetype = "dashed", color = "darkgrey") +
-    geom_segment(x = 17, xend = 17, y = 0.0, yend = 0.90, linetype = "dashed", color = "darkgrey") +
[…]

### 2020-07-14 workflow/scripts/PlotDescriptive/PlotCountryMobilityECDF.R

@@ -38,17 +38,13 @@ lookup <- read_delim(opt$lookup, delim = "\t", col_types = readr::cols()) %>%
 researchers <- read_delim(opt$researchers, delim = "\t", col_types = readr::cols()) %>%
   select(cluster_id, org_mobile, country_mobile)
 
-# Calculate the expected mobility, or the world proportion of org-mobile researchers
-expected.mobility <- sum(researchers$org_mobile) / dim(researchers)[1]
-
-# Load the dataframe of all transitions, merge in other metainfo, and
-# aggregate across countries and organization mobility status
+# Load the flows and aggregate
 flows <- read_delim(opt$flows, delim = "\t", col_types = readr::cols())
 
 nonmobile <- read_delim(opt$nonmobile, delim = "\t", col_types = readr::cols())
 
 # Merge with nonmobile individuals
-flows <- data.table::rbindlist(list(flows, nonmobile))
+flows <- data.table::rbindlist(list(flows, nonmobile), fill = T)
 
 flows <- flows %>%
   select(-LR_main_field_no, -pub_year) %>%
@@ -59,56 +55,54 @@ flows <- flows %>%
     count = length(unique(cluster_id))
   )
 
-print(head(flows), 10)
-
-# Remove unecessary dataframes
-remove(researchers, lookup)
-
-# construct the data for the plot
+# Build data for the plot
 plotdata <- flows %>%
-  # spread the count of org_mobile across two columns
-  tidyr::spread(org_mobile, count) %>%
-  rename(mobile = `TRUE`, nonmobile = `FALSE`) %>%
-  mutate(
-    mobile = ifelse(is.na(mobile), 0, mobile),
-    total = mobile + nonmobile,
-    prop = mobile / total
-  ) %>%
-  filter(country_iso_alpha != "NULL" & total > 100) %>%
-  arrange(desc(prop)) %>% # Arrange in descending order by proportion mobile
+  filter(org_mobile) %>%
   ungroup() %>%
-  mutate(index = row_number()) # Index used for the x-axis
+  mutate(
+    prop = count / sum(count, na.rm = T),
+    country_iso_alpha = reorder(country_iso_alpha, desc(prop))
+  ) %>%
+  arrange(desc(prop)) %>%
+  mutate(
+    index = row_number(),
+    cumulative = cumsum(prop)
+  )
 
[…]

### 2020-07-14 workflow/scripts/PlotDescriptive/PlotProportionMobilityByCountry.R

@@ -1,10 +1,9 @@
 #
-# PlotCountryMobilityDistribution.R
+# PlotProportionMobilityByCountry.R
 #
 # author: Dakota Murray
 #
-# Plot the distirbution of country's based on their contribution to
-# global mobility
+# Plot the proportion of mobile vs. nonmobile researchers by country
 #
 
 # Plot dimensions
@@ -39,13 +38,17 @@ lookup <- read_delim(opt$lookup, delim = "\t", col_types = readr::cols()) %>%
 researchers <- read_delim(opt$researchers, delim = "\t", col_types = readr::cols()) %>%
   select(cluster_id, org_mobile, country_mobile)
 
-# Load the flows and aggregate
+# Calculate the expected mobility, or the world proportion of org-mobile researchers
+expected.mobility <- sum(researchers$org_mobile) / dim(researchers)[1]
+
+# Load the dataframe of all transitions, merge in other metainfo, and
+# aggregate across countries and organization mobility status
 flows <- read_delim(opt$flows, delim = "\t", col_types = readr::cols())
 
 nonmobile <- read_delim(opt$nonmobile, delim = "\t", col_types = readr::cols())
 
 # Merge with nonmobile individuals
-flows <- data.table::rbindlist(list(flows, nonmobile))
+flows <- data.table::rbindlist(list(flows, nonmobile), fill = T)
 
 flows <- flows %>%
   select(-LR_main_field_no, -pub_year) %>%
@@ -56,46 +59,56 @@ flows <- flows %>%
     count = length(unique(cluster_id))
   )
 
-# Build data for the plot
+print(head(flows), 10)
+
+# Remove unecessary dataframes
+remove(researchers, lookup)
+
+# construct the data for the plot
 plotdata <- flows %>%
-  filter(org_mobile) %>%
-  ungroup() %>%
+  # spread the count of org_mobile across two columns
+  tidyr::spread(org_mobile, count) %>%
+  rename(mobile = `TRUE`, nonmobile = `FALSE`) %>%
   mutate(
-    prop = count / sum(count, na.rm = T),
-    country_iso_alpha = reorder(country_iso_alpha, desc(prop))
+    mobile = ifelse(is.na(mobile), 0, mobile),
+    total = mobile + nonmobile,
+    prop = mobile / total
   ) %>%
-  arrange(desc(prop)) %>%
-  mutate(
-    index = row_number(),
[…]

### 2020-07-14 workflow/scripts/PlotPredictedVsActual.R
update to predicted vs. actual plot

@@ -89,7 +89,6 @@ binned <- data %>%
   )
 
 error <- sqrt(mean((log10(data$expected) - log10(data$actual)) ^ 2, na.rm = T))
-print(error)
 
 # Build the plot
 plot <- data %>%
@@ -133,9 +132,9 @@ plot <- data %>%
                      expand = c(0, 0)) +
   coord_fixed() +
   annotate(geom = "text",
-           x = 1.2,
+           x = 1.4,
            y = 6.2,
-           label = paste0("Err = ", sprintf("%.2f", round(error,3))),
+           label = paste0("RMSE = ", sprintf("%.2f", round(error,3))),
            size = 7
          ) +
   # Define the gradient

### 2020-07-15 paper/current/main.tex
update abstract, intro, first para

@@
 Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity, xia2005measlesgravity, jung2008highwaygravity, barbosa2018human, curiel2018citygravity, lewer2008immigrationgravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity}, describes mobility using the \textit{distance} between places.
-However, geographic distance is less relevent in the increasingly-globalized globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization}, in which mobility is dependent less on geography than linguistic, economic, cultural, and historical similarity.
+However, geographic distance is less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization}, in which mobility is dependent less on geography than linguistic, economic, cultural, and historical similarity.
 Alternative and abstract notions of distance attempt to capture the latent landscape of mobility~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional} but pose practical and theoretical challenges.
@@
 This approach can learn scalable, dense, and meaningful vector representations of scientific mobility directly from the data, and can easily be generalized to other mobility data.
+
 \end{abstract}
@@
 As a scientist's careers progress, they move between organizations or pick up additional (simultaneous) affiliations forming \textit{affiliation trajectories} (Fig.~\ref{fig:methods:mobility_sentence}).
-These trajectories encodie both asynchronous migration, and synchronous mobility---the holding of multiple simultaneous co-affiliations involving the sharing of time and capital between locations---that is typical of scientific mobility~\autocite{rodrigues2016mobility, markova2016synchronous, sugimoto2017mostimpact} (see Supplementary Materials).
+These trajectories encode both asynchronous migration, and synchronous mobility---the holding of multiple simultaneous co-affiliations involving the sharing of time and capital between locations---that is typical of scientific mobility~\autocite{rodrigues2016mobility, markova2016synchronous, sugimoto2017mostimpact} (see Supplementary Materials).
 We use the trajectories of the three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
@@
         In a more complex case, an author lists several affiliations on the byline of papers in $t_{2}$, $t_{3}$, and $t_{4}$. 
-        In the case where multiple organizations are listed within the same year, then organization IDs within a single year are randomized across each training iteration or "epoch" of the \textit{word2vec} model (for more detail, see Supporting Materials).
+        In the case where multiple organizations are listed within the same year, then organization IDs within a single year are randomized across each training iteration or ``epoch" of the \textit{word2vec} model (for more detail, see Supporting Materials).
     }
@@
 This pattern holds when considering the subset of only domestic (Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (Fig.~\ref{fig:supp:gravity_correlation}d).
-After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance (Fig.~\ref{fig:gravity_performance}c--d), which also holds for the subsets of only domestic (Fig.~\ref{fig:supp:gravity_correlation}e--f) and international mobility(Fig.~\ref{fig:supp:gravity_correlation}g--h).
+After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance (Fig.~\ref{fig:gravity_performance}c--d), which also holds for the subsets of only domestic (Fig.~\ref{fig:supp:gravity_correlation}e--f) and international mobility (Fig.~\ref{fig:supp:gravity_correlation}g--h).
 The embedding distance defined from the cosine distnace between vectors also outperforms that defined from their dot product ($R^{2} = 0.34$, Fig.~\ref{fig:supp:gravity_dot}).
-The embedding distance also out-performs alternative ``diffusion'' network distance measures such as the personalized-page rank scores (see supporting materials) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-Our results unequivecolly argue that the distance learned by the embedding method better capture actual mobility patterns than does geographic distance. 
+The embedding distance also out-performs alternative ``diffusion-based'' network distance measures such as the personalized-page rank scores (see supporting materials) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+Our results unequivocally argue that the distance learned by the embedding method better capture actual mobility patterns than does geographic distance. 
 We speculate that this results from an underlying mathematical connection between the neural embedding architecture and the gravity model of mobility.

### 2020-07-15 paper/current/main.tex
update till clustering

@@
 		\textbf{a.} embedding distance (cosine distance between organization vectors) explains more of the expected flux between organization pairs than does geographic distance (\textbf{b}).
-		The red line is the line of best fit.
+		The red line is the line of the best fit.
 		Black dots are mean flux across binned distances.
@@
 		Box color corresponds to the degree to which the distribution overlaps $x = y$.
-		``RMSE'' is calculated as the root-mean-squared error between the actual and predicted values.
+		``RMSE'' is root-mean-squared error between the actual and predicted values.
 		\textbf{e-f.} Predictions made using model parameters learned from a subset of domestic (within-country) organization pairs.
@@
 By encoding the complex landscape in a dense representation, embeddings also allow us to create informative visualizations of global scientific mobility.
-To explore the embedding, we use a common dimensionality reduction technique (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation of the embedding (Fig.~\ref{fig:projection}a).
+To explore the topological structure of the embedding, we use a common dimensionality reduction technique (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation of the embedding (Fig.~\ref{fig:projection}a).
 By showing relationships between individual organizations, rather than aggregates such as nations or cities, this projection constitutes the largest and highest resolution ``map'' of scientific mobility to date.
@@
 Globally, the effect of geography is conspicuous; organizations tend to form clusters based on their national affiliations and national clusters tend to be near their geographic neighbors. 
-At the same time, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions much more clearly than alternative network representations (Fig.~\ref{fig:supp:network_vis}) that have dominated studies of scientific mobility~\autocite{chinchilla2018global, czaika2018globalisation}.
+At the same time, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions much more clearly than alternative network representations (Fig.~\ref{fig:supp:network_vis}) that have been dominating studies of scientific mobility~\autocite{chinchilla2018global, czaika2018globalisation}.
 
@@
 Linguistic and historical ties are also conspicuous.
-For example, we observe that Spanish-speaking post-colonial Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), such as Mexico ($d = 0.34$) and Chile ($d = 0.39$) morose than to nearby Portuguese-speaking Brazil ($d = 0.52$ for Mexico and $d = 0.49$ for Chile).
+For example, we observe that Spanish-speaking post-colonial Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), such as Mexico ($d = 0.34$) and Chile ($d = 0.39$) morose than to nearby Portuguese-speaking nation ($d = 0.52$ for Mexico and $d = 0.49$ for Chile) reflecting language and culture constructed the nature of scientific mobility.
 Similarly, North-African countries that were once under French rule such as Morocco are nearer to France ($d =0.35$) than to similarly-distant European countries as Spain ($d = 0.40$) and Italy ($d = 0.53$).

### 2020-07-15 paper/current/main.tex
edit till right before conclution

@@
 		\textbf{Embedding captures latent geography and prestige hierarchy.}
-		\textbf{a.} Illustrates SemAxis projection along two axes,California and Massachusetts and for the top five-to geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S.
-Universities.
+		\textbf{a.} Illustration of SemAxis projection along two axes;  \textit{latent geographical axis}, from California to Massachusetts (left to right) and \textit{prestige axis}, from the top five to geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S.
+Universities (top to bottom).
 		Points correspond to organizations, and a sample of states are highlighted.
@@
 		White points are those top and bottom five universities used to define the poles of the axis.
-	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the SemAxis and Times ranking is 0.73 (n = 145), and increases if controlling for the number of top-and-bottom ranked universities (Fig.~\ref{fig:supp:semaxis_compare}).
+	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the SemAxis and Times ranking is 0.73 (n = 145), and it increases if we include more top-and-bottom ranked universities (Fig.~\ref{fig:supp:semaxis_compare}).
 	}

### 2020-07-15 paper/current/main.tex
edit conclusion

@@
 
-Neural embeddings offer a natural approach for learning an effective and robust functional distance between places based on affiliation trajectory data. 
+Neural embeddings offer a novel approach for learning an effective and robust functional distance between places based on affiliation trajectory data. 
 Here, we demonstrated how the embedding space encodes complex aspects of scientific mobility, such as global and regional geography, national similarity, and organizational prestige.
@@
 In addition to providing a functional distance that supports modeling and predicting mobility patterns, the unique structure of neural embedding also allows for a range of methodological applications.
-For instance, projecting the embedding space onto two dimensions using UMAP allows for the visualization of the complex structure of scientific mobility at high resolution and at multiple scales, which has implications.
-Other techniques, such as SemAxis, allow the potential to quantify abstract notions in mobility such as academic prestige, and can also be generalized to other abstract axes.
+As we shown, projecting the embedding space onto two dimensions using UMAP allows for the visualization of the complex structure of scientific mobility at high resolution and at multiple scales, which has implications in practice.
+Other techniques, such as SemAxis, also allow the potential to quantify abstract notions in mobility such as academic prestige, and can also be generalized to other abstract axes.
 Neural embedding opens the door for new approaches for representing and understanding patterns of global human mobility.
 
-In spire of its promise, this approach and analysis presents several limitations. 
-First, the standard neural embedding model non-directional, meaning that embedding will be less effective at capturing mobility for which directional is critical.
-Second, the neural embedding approach is most useful in cases of mobility between discrete geographic entities such as between countries, cities, and businesses; this approach is less useful in the case of mobility between arbitrary locations represented in geographic coordinates, such as in the modeling of animal movements.
-Neither of these methodological limitations are insurmountable, and future work can aim to incorporate directionality and identify meaningful representations of continuous mobility data. 
+In spite of its promise, this approach and analysis present several limitations. 
+First, the \textit{skip-gram word2vec} model can not encode directional information, meaning that embedding will be less effective at capturing mobility for which directional is critical.
+Second, the neural embedding approach is most useful in cases of mobility between discrete geographic units such as between countries, cities, and businesses; this approach is less useful in the case of mobility between arbitrary locations represented in geographic coordinates, such as in the modeling of animal movements.
+Neither of these methodological limitations is insurmountable, and future work can aim to incorporate directionality and identify meaningful representations of continuous mobility data. 
 Finally, the case of scientific mobility presents domain-specific limitations. 
@@
 The kinds of mobility we do capture—asynchronous migration and synchronous co-affiliation, are treated identically by our model even though they are qualitatively different.
+Also, our data can possess survivorship bias. Researchers at prestige organization tend to have more publications, inducing appear more in the mobility sentence.
 Scientific mobility is complex, and its study continues to pose challenges; neural embeddings do not solve many of these issues, but they create opportunities for new analyses and understanding
-Future work should aim to
+future work should aim to
 

### 2020-07-15 paper/current/main.tex
edit method part

@@
 There are two popular forms of the $f(r_{ij})$.
-The first one is power-law function with $f(r_{ij})= r^{-\alpha}_{ij}  (\alpha > 0)$, and the another one is exponential function with $f(r_{ij}) = e^{-\beta r_{ij}} (\beta > 0)$ \autocite{chen2015distance}.
+The first one is power-law function with $f(r_{ij})= r^{-\alpha}_{ij} \ (\alpha > 0)$, and the another one is exponential function with $f(r_{ij}) = e^{-\beta r_{ij}} \ (\beta > 0)$ \autocite{chen2015distance}.
 $f(r_{ij})$, $C$ can be chosen as to fit the data with the simple regression.
@@
 Each axis is an antonym pair defined for each specific use case.
-In the case of language, the poles of the axis could be ``good'' and ``bad'', ``surprising'' and ``unsurprising'', or ``masculine'' and ``feminine''. 
+In the case of natural language, the poles of the axis could be ``good'' and ``bad'', ``surprising'' and ``unsurprising'', or ``masculine'' and ``feminine''. 
 By treating organizations analogously to words and trajectories analogously to sentences, we can use SemAxis to leverage the semantic properties of the resulting embedding vectors to operationalize abstract relationships between organizations.
 
-Given vectors representing the positive and negative poles of an axis, $v^{+}$ and $v^{-}$, the axis is defined as.$v_{\text{axis}} = v^{+} - v^{-}$.
-For each organization in the embedding space, $w$, a score is calculated relating the term to to the positive, $v^{+}$ or negative, $v^{-}$ pole, calculated as the cosine similarity of the organization's vector with the axis,
+Let $S^+ = \{v_1^+, v_2^+ \cdots v_n^+\}$ and $S^- =\{v_1^-, v_2^- \cdots v_n^-\}$ be the sets of positive and negative poles organization vector respectively.
+Then, the average vectors of each set can be calculated as $V^{+} = \frac{1}{n}\sum^n_1 v_i^+$ and $V^{-} = \frac{1}{n}\sum^n_1 v_i^-$.
+From these average vectors of each set of poles, the semantic axis is defined as $V_{\text{axis}} = V^{+} - V^{-}$.
+Then,  a score of organization $w$ is calculated calculated as the cosine similarity of the organization's vector with the axis,
 
 $$
-score(w)v_{\text{axis}} = \cos(u_{w}, v_{\text{axis}})
+score(w)_{V_{\text{axis}}} = \cos(u_{w}, V_{\text{axis}}) = \frac{u_{w} \cdot V_{\text{axis}}}{\lVert v_{i} \rVert \lVert V_{\text{axis}} \rVert},
 $$
+
+where higher scores means that organization $w$ is more closely aligned to $S^+$ than $S^-$.
 

### 2020-07-15 paper/current/main.tex
edit typo from main paper

@@
 Similarly, a prospective student living in South Korea is more likely to attend university in Canada rather than the closer though diplomatically isolated North Korea. 
-Despite its complexity, geographic distnace is used as the basis for the most prominent models of mobility such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal}.
+Despite its complexity, geographic distance is used as the basis for the most prominent models of mobility such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal}.
 So-called \textit{functional distances}~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional} have been proposed that attempt to learn alternative notions of distance from real-world data or \textit{a priori} relationships between geographic entities.
@@
 However, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}.
-One roadblock is the lack of a meaningful measure of functional distance between countries, cities, and organizations.
+One roadblock is the lack of a meaningful measure of the functional distance between countries, cities, and organizations.
 
 Here, scientific mobility is operationalized using researcher's organizational affiliations derived from their publication histories indexed in a large-scale bibliographic database. 
-The most fine-grained geographical unit in this data is the organization, such as an university, research institute, business, or government agency.
+The most fine-grained geographical unit in this data is the organization, such as a university, research institute, business, or government agency.
 As a scientist's careers progress, they move between organizations or pick up additional (simultaneous) affiliations forming \textit{affiliation trajectories} (Fig.~\ref{fig:methods:mobility_sentence}).
@@
         An author published five papers across five time periods, with only one affiliation listed in the byline of each paper.
-        To each organization, a unique identifier is assigned, and they are assembled into a affiliation trajectory ordered by year of publication.
+        To each organization, a unique identifier is assigned, and they are assembled into an affiliation trajectory ordered by year of publication.
         \textbf{b.}
@@
 The embedding distance also out-performs alternative ``diffusion-based'' network distance measures such as the personalized-page rank scores (see supporting materials) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-Our results unequivocally argue that the distance learned by the embedding method better capture actual mobility patterns than does geographic distance. 
+Our results unequivocally argue that the distance learned by the embedding method better captures actual mobility patterns than does geographic distance. 
 We speculate that this results from an underlying mathematical connection between the neural embedding architecture and the gravity model of mobility.
@@
 
-The embedding space also allows us to to \textit{zoom in} on subsets of counties and re-project them in order to reveal more local relationships. 
+The embedding space also allows us to \textit{zoom in} on subsets of counties and re-project them in order to reveal more local relationships. 
 For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries ranging from Egypt to Philippines that corresponds largely to geography, but with some peculiar exceptions.
@@
 
-The geographic structure of the global embedding is mirrored in re-projection of the United States, wherein organizations are largely organized according to regions and states (Fig.~\ref{fig:projection}d).
+The geographic structure of the global embedding is mirrored in the re-projection of the United States, wherein organizations are largely organized according to regions and states (Fig.~\ref{fig:projection}d).
 By re-projecting at the state-level for Massachusetts (Fig.~\ref{fig:projection}e), we observe structure between urban centers (Boston vs.
-Worcester), but also based on organization type (e.g., hospitals vs.
+Worcester) but also based on organization type (e.g., hospitals vs.
 universities) and university systems.
@@
 		\textbf{b.} Zooming into (re-projecting) the area containing countries in the Middle East and South and Southeast Asia shows a geographic and cultural gradient of country clusters. 
-		\textbf{c.} Similarly, zooming into the area organizations in Spain, Portugal, South and Central America show clustering by majority language group--Spanish and Portuguese.
+		\textbf{c.} Similarly, zooming into the area organizations in Spain, Portugal, South, and Central America show clustering by majority language group--Spanish and Portuguese.
 		\textbf{d.} Doing the same for organizations in the United States reveals geographic clustering based on state, roughly grouped by Census Bureau-designated regions,
@@
 Just as the embedding space makes it possible to ``zoom in'' on subsets of organizations, it is possible to ``zoom out'' to a higher level by aggregating organizational vectors. 
-For example, we can examine high-level structure by estimating the aggregate embeddings of countries. 
+For example, we can examine the high-level structure by estimating the aggregate embeddings of countries. 
 Namely, we calculate the representative vector of each country by averaging organization vectors within the given country.
@@
 \ref{fig:clustering}a).
-The six identified clusters roughly correspond to: East-Asian (orange), Scandinavian (dark purple), British Commonwealth (light purple), Central and Eastern European countries (light blue), and then two remaining diverse clusters that contain a mix of European, Latin American, and Mediterranean countries.
-These clusters demonstrate the importance of not only geography, but also linguistic ties between countries.
+The six identified clusters roughly correspond to East-Asian (orange), Scandinavian (dark purple), British Commonwealth (light purple), Central and Eastern European countries (light blue), and then two remaining diverse clusters that contain a mix of European, Latin American, and Mediterranean countries.
+These clusters demonstrate the importance of not only geography but also linguistic ties between countries.
 
 We quantify the relative importance of geography (by continent), and language (by majority language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering by explicitly adjusting the relative importance of different levels of the hierarchy with scaling parameter $r$, acting like a ``zooming lens''.
-If $r$ is high, the similarity is based on the lower levels of the dendrogram, whereas when $r$ is low, similarity is based on higher levels.
+If $r$ is high, the similarity is based on the lower levels of the dendrogram, whereas when $r$ is low, the similarity is based on higher levels.
 Fig.
-\ref{fig:clustering}b demonstrates that continent plays a major role at higher levels of clustering process (low $r$), and language (family) explain the clustering more at the lower levels (high $r$).
+\ref{fig:clustering}b demonstrates that the continent plays a major role at higher levels of the clustering process (low $r$), and language (family) explains the clustering more at the lower levels (high $r$).
 This suggests that geography, then language, are important factors contributing to the structure of international scientific mobility.
@@
 		\textbf{Geography, then language, dictate international mobility.}
-		\textbf{a.} Hierarchically clustered similarity matrix of country vectors, aggregated as the mean of all organization vectors within the country that has a more than 25 organizations, excluding the United States.
-		Color of matrix cells corresponds to similarity between country vectors.
+		\textbf{a.} Hierarchically clustered similarity matrix of country vectors, aggregated as the mean of all organization vectors within the country that has more than 25 organizations, excluding the United States.
+		Color of matrix cells corresponds to the similarity between country vectors.
 		Color of country names corresponds to their cluster.
@@
 Prestige hierarchies underpin the dynamics of scientific mobility~\autocite{deville2014career, clauset2015hierarchy}, but are these hierarchies captured in the embedding space?
-We test this by exploiting the geometric properties of the embedding space with the technique SemAxis~\autocite{an2018semaxis}, an approach originally designed for characterize the semantics of words in language embeddings.
+We test this by exploiting the geometric properties of the embedding space with the technique SemAxis~\autocite{an2018semaxis}, an approach originally designed to characterize the semantics of words in language embeddings.
 Here, we use SemAxis to operationalize the abstract notion of academic prestige, defining each end of the axis using known high- and low-ranked universities. 
@@
 
-The embedding space captures prestige hierarchies can be used to reconstruct academic rankings. 
+The embedding space captures prestige hierarchies that can be used to reconstruct academic rankings. 
 We derive a ranking using the SemAxis prestige axis in Fig.~\ref{fig:semaxis}.a and compare them to traditional university rankings.
-The SemAxis ranking is defined from the position of organizations along the prestige axis, with the top ranked being the furthest towards the \textit{Elite} end of the axis.
+The SemAxis ranking is defined from the position of organizations along the prestige axis, with the top-ranked being the furthest towards the \textit{Elite} end of the axis.
 We find that the SemAxis ranking is highly correlated with the Times ranking (Spearman's $\rho = 0.73$, Fig.~\ref{fig:semaxis}b).
@@
 The correlation between SemAxis and the Times ranking is robust with the number of organizations used to define the axes (Fig.
-SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities is strongly correlated with the Times Ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
+SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities are strongly correlated with the Times Ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
 For reference, SemRank achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking~\autocite{waltman2012leidenrankings}, a common and bibliometrically-informed university ranking (Spearman's $\rho = 0.87$, Fig.~\ref{fig:supp:times_vs_leiden}).
@@
 In addition to providing a functional distance that supports modeling and predicting mobility patterns, the unique structure of neural embedding also allows for a range of methodological applications.
-As we shown, projecting the embedding space onto two dimensions using UMAP allows for the visualization of the complex structure of scientific mobility at high resolution and at multiple scales, which has implications in practice.
+As we have shown, projecting the embedding space onto two dimensions using UMAP allows for the visualization of the complex structure of scientific mobility at high resolution and at multiple scales, which has implications in practice.
 Other techniques, such as SemAxis, also allow the potential to quantify abstract notions in mobility such as academic prestige, and can also be generalized to other abstract axes.
@@
 The kinds of mobility we do capture—asynchronous migration and synchronous co-affiliation, are treated identically by our model even though they are qualitatively different.
-Also, our data can possess survivorship bias. Researchers at prestige organization tend to have more publications, inducing appear more in the mobility sentence.
+Also, our data can possess survivorship bias. Researchers at prestigious organizations tend to have more publications, inducing appear more in the mobility sentence.
 Scientific mobility is complex, and its study continues to pose challenges; neural embeddings do not solve many of these issues, but they create opportunities for new analyses and understanding
@@
 Trajectories are constructed from author affiliations listed on the byline of publications for a given author.
-Given the limitations of author-name disambiguation, we limit to papers published after 2008, when the Web of Science began providing full names and institutional affiliations~\autocite{caron2014disambiguation} that improved disambigatuon (see supporting materials).
+Given the limitations of author-name disambiguation, we limit to papers published after 2008, when the Web of Science began providing full names and institutional affiliations~\autocite{caron2014disambiguation} that improved disambiguation (see supporting materials).
 This yields 33,934,672 author-affiliation combinations representing 12,963,792 authors.
-Each author-affiliation combination is associated with the publication year and an ID linking it to one of 8,661 a dismabiguated organizational affiliation (see supporting materials for more detail)
+Each author-affiliation combination is associated with the publication year and an ID linking it to one of 8,661 a disambiguated organizational affiliation (see supporting materials for more detail)
 Trajectories are represented as the list of author-affiliation combinations, ordered by year of publication, and randomly ordered for combinations within the same year.
@@
 Here, authors are classified as mobile when they have at least two distinct organization ids in their trajectory, meaning that they have published using two or more distinct affiliations between 2008 and 2019.
-Under this definition, mobile authors constitute 3,007,192 or 23.2 percent of all authors, and 17,700,095 author-affiliation combinations.
+Under this definition, mobile authors constitute 3,007,192 or 23.2 percent of all authors and 17,700,095 author-affiliation combinations.
 Mobile authors were associated with, on average, 2.5 distinct organizational affiliations.
-Rates of mobility tended to differ across country.
+Rates of mobility tended to differ across countries.
 For example, France, Qatar, the USA, Iraq, and Luxembourg had the most mobile authors (Fig.~\ref{fig:supp:descriptives}c).
@@
 In natural-language processing, word embeddings are used to construct dense vector-space representations of words and phrases, in which distance relationships between words correspond to a notion of semantic distance.
-By embedding affiliation trajectories, we aim to learn a dense vector for every organization where distance between vectors relates to the tendency for two organizations to co-occur in a token window around the target organization token in the same career trajectory.
+By embedding affiliation trajectories, we aim to learn a dense vector for every organization where the distance between vectors relates to the tendency for two organizations to co-occur in a token window around the target organization token in the same career trajectory.
 Vectors are learned by training a neural network to optimize the prediction of the so-called context term given a target, in our case using one organization to predict the others appearing in the same co-affiliation trajectory.
@@
 The skip-gram model has several tunable hyper-parameters, including the size of the learned vectors, the size of the token window considered when training, the minimum frequency threshold for including an organization, and the number of iterations.
-We iterate through several values of vector size and window size, repeating analysis for each combination.
+We iterate through several values of vector size and window size, repeating the analysis for each combination.
 To mitigate the effect of less common organizations, only organizations appearing at least 50 times in mobility sentences are included in the embedding;
@@
 SI~\ref{fig:supp:hyperparams}).
-We note that this performance and the outcomes of analysis was robust to hyperparemeters settings.
+We note that this performance and the outcomes of the analysis were robust to hyper-parameters settings.
 
@@
 
-We also calculate two forms of distance between organizations.
+We also calculate two forms of the distance between organizations.
 The geographic distance, $g_{ij}$, is the pairwise geographic distance between organizations.
@@
 
-where $T_{ij}$ is the real flux from dataset. The gravity law of mobility is known to be sensitive to the case where $T_{ij} = 0$, or zero movement between organizations.
+where $T_{ij}$ is the real flux from the dataset. The gravity law of mobility is known to be sensitive to the case where $T_{ij} = 0$, or zero movement between organizations.
 Here, non-zero flows account for only 4.2 percent of all possible pairs of the 6,580 organizations represented in the embedding.
 This value is comparable to other common applications of the gravity law, such as to hone calls, commuting, and migration \autocite{simini2012universal}.
-We follow standard practice and exclude from our analysis zero flows.
+We follow standard practice and exclude zero flows from our analysis.
 
@@
 \subsection*{SemAxis}
-SemAxis~\autocite{an2018semaxis} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these term to the concept.
+SemAxis~\autocite{an2018semaxis} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these terms to the concept.
 Each axis is an antonym pair defined for each specific use case.
@@
 
-Let $S^+ = \{v_1^+, v_2^+ \cdots v_n^+\}$ and $S^- =\{v_1^-, v_2^- \cdots v_n^-\}$ be the sets of positive and negative poles organization vector respectively.
+Let $S^+ = \{v_1^+, v_2^+ \cdots v_n^+\}$ and $S^- =\{v_1^-, v_2^- \cdots v_n^-\}$ be the set of positive and negative pole organization vectors respectively.
 Then, the average vectors of each set can be calculated as $V^{+} = \frac{1}{n}\sum^n_1 v_i^+$ and $V^{-} = \frac{1}{n}\sum^n_1 v_i^-$.
 From these average vectors of each set of poles, the semantic axis is defined as $V_{\text{axis}} = V^{+} - V^{-}$.
-Then,  a score of organization $w$ is calculated calculated as the cosine similarity of the organization's vector with the axis,
+Then,  a score of organization $w$ is calculated as the cosine similarity of the organization's vector with the axis,
 
 $$
-score(w)_{V_{\text{axis}}} = \cos(u_{w}, V_{\text{axis}}) = \frac{u_{w} \cdot V_{\text{axis}}}{\lVert v_{i} \rVert \lVert V_{\text{axis}} \rVert},
+score(w)_{V_{\text{axis}}} = \cos(v_{w}, V_{\text{axis}}) = \frac{u_{w} \cdot V_{\text{axis}}}{\lVert v_{w} \rVert \lVert V_{\text{axis}} \rVert},
 $$
 
-where higher scores means that organization $w$ is more closely aligned to $S^+$ than $S^-$.
+where higher scores mean that organization $w$ is more closely aligned to $S^+$ than $S^-$.
 
@@
 For example, if 20 universities top-ranked universities are selected and six of them are in the Northeastern United States, then the bottom six universities according to the same ranking will be included in the low-ranked subset.
-From the prestige axis we derive a ranking of universities that we then compare to other formal university rankings using Spearman rank correlation.
+From the prestige axis, we derive a ranking of universities that we then compare to other formal university rankings using Spearman rank correlation.
 

### 2020-07-16 paper/current/main.tex
edit typo on supp

@@
 
-As scholars move, they bring their knowledge, their skills, and their social connections with them--collectively the movements of researchers shapes the structure and direction of the global scientific enterprise.
+As scholars move, they bring their knowledge, their skills, and their social connections with them--collectively the movements of researchers shape the structure and direction of the global scientific enterprise.
 For example, prestige-driven mobility between doctoral-granting and employing institution is highly unequal~\autocite{clauset2015hierarchy, deville2014career}, which impacts the diffusion of ideas across academia~\autocite{morgan2018prestige}.
-By placing researchers in new social settings, mobility can lead to the formation of new collaborative relationships~\autocite{rodrigues2016mobility}, which in turn spur the further diffusion of knoweldge and new innovations~\autocite{braunerhjelm2020labor, azoulay2011diffusion, kaiser2018innovation, armano2017innovation}.
+By placing researchers in new social settings, mobility can lead to the formation of new collaborative relationships~\autocite{rodrigues2016mobility}, which in turn spur the further diffusion of knowledge and new innovations~\autocite{braunerhjelm2020labor, azoulay2011diffusion, kaiser2018innovation, armano2017innovation}.
 Perhaps resulting from the selection effects of who gets to move, or the reconfiguring of social and epistemic networks, movement is associated with increased scientific impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}.
 At the national level, the understanding of mobility has progressed beyond simplistic narratives of brain drain and brain gain, and instead adopts a new perspective of \textit{flows} of talent~\autocite{meyer2001network, ioannidis2014braindrain, gaillard1998circulation}.
-Under this flow model, a mobile researcher is viewed as contributing to both their origin and destincation countries, a perspective that fosters that is evidenced by the strong science of open countires~\autocite{wagner2017open}.
+Under this flow model, a mobile researcher is viewed as contributing to both their origin and destination countries, a perspective that fosters that is evidenced by the strong science of open countires~\autocite{wagner2017open}.
 Perhaps because of these individual and national benefits, policy-makers have come to recognize the importance of global mobility~\autocite{box2008competition, oecd2010innovation}. 
@@
 Most studies of mobility have focused on \textit{country-level} mobility--the flows of researchers across nations~\autocite{sugimoto2017mostimpact, scellato2015migrant, robinson-garcia2018indicators, franzoni2012foreign-born}.
-Practically, country-level analyses benefit from higher reliability, such that such that idiosyncrasies and errors inherent to bibliographic databases are mitigated by this higher level of aggregation.
-Epistemically, country-level analysis is useful for national science governance who aim to understand the status of their country in the global landscape and make informed policy decisions. 
+Practically, country-level analyses benefit from higher reliability, such that idiosyncrasies and errors inherent to bibliographic databases are mitigated by this higher level of aggregation.
+Epistemically, country-level analysis is useful for national science governance who aims to understand the status of their country in the global landscape and make informed policy decisions. 
 Analyses at lower levels of analysis are far less common. 
 \textit{Regional}-level scientific mobility--the flow of researchers between regions or cities within or across countries, has been only minimally studied~\autocite{vaccario2019mobility}, possibly due to lack of reliable long-term data and lack of policy relevance to national-level lawmakers.
-\textit{Organization}-level mobility has potential to inform institutional policy and for understand the composition of mobility within a single country or region, especially as it relates to organization performance, prestige, and inequality~\autocite{albarran2017topeconomic, deville2014career, morgan2018prestige, clauset2015hierarchy}.
-However, affiliation disambiguation and noise in bibliometric data has makes large-scale organization-level analysis challenging.
+\textit{Organization}-level mobility has the potential to inform institutional policy and to understand the composition of mobility within a single country or region, especially as it relates to organization performance, prestige, and inequality~\autocite{albarran2017topeconomic, deville2014career, morgan2018prestige, clauset2015hierarchy}.
+However, affiliation disambiguation and noise in bibliometric data have makes large-scale organization-level analysis challenging.
 Here, we learn neural-network embeddings of scientific mobility at the level of organizations using a curated bibliographic database.
@@
 
-Another consideration when analyzing scientific mobility are what kinds of mobility to study. 
+Another consideration when analyzing scientific mobility is what kinds of mobility to study. 
 Typical understandings of mobility are directional, meaning that movement is always \textit{from} one place and \textit{to} another. 
@@
 Even clearly-directional migration to another institution is complex--researchers may continue to publish with an old affiliation for projects that began before their move, and they may maintain social and organizational links to their old institution (e.g., collaborators, projects, graduate students) such that there is no clear breakage after migrating.
-There are also a whole range of short-term scientific mobility, such as visiting scholarships and short-term visits that are only visible through intensive efforts such as manual extraction from CVs~\autocite{woolley2009cv, sandstrom2009cv, canibano2011temporary}.
+There is also a whole range of short-term scientific mobility, such as visiting scholarships and short-term visits that are only visible through intensive efforts such as manual extraction from CVs~\autocite{woolley2009cv, sandstrom2009cv, canibano2011temporary}.
 Here, we focus on more long-term mobility that can be derived from bibliographic data. 
-Due to the complexity of scientific mobility, we make the simplifying assumption that all scientific mobility is \textit{symmetric} or without direction such that any move from organization $A$ to organization $B$ is equivalent to a move from $B$ to $A$.
-By assuming non-directional mobility, all mobility events are commensurate, meaning that they can be treated identically in our analysis--this allows us to represent the complexity of mobility without making decisions for individual researcher's about the directional of their mobility or which is their main affiliation.
+Due to the complexity of scientific mobility, we make the simplifying assumption that all scientific mobility is \textit{symmetric} or without direction such that any move from an organization $A$ to organization $B$ is equivalent to a move from $B$ to $A$.
+By assuming non-directional mobility, all mobility events are commensurate, meaning that they can be treated identically in our analysis--this allows us to represent the complexity of mobility without making decisions about the directional of their mobility or which is their main affiliation.
 Moreover, this assumption has the practical advantage of matching the data format expected by the \textit{word2vec} model, as well as the theoretical advantage of adhering to the symmetricity assumption of the gravity model of mobility.
@@
 
-We adopt a data-driven approach to constructing affiliation trajectories, making as little adjustment to the raw bibliometric data as possible. 
+We adopt a data-driven approach to constructing affiliation trajectories, making an as little adjustment to the raw bibliometric data as possible. 
 For each mobile researcher (having at least two distinct affiliations), we construct an affiliation trajectory based on the affiliations listed on their published papers indexed in the Web of Science database between 2008 and 2019.
@@
 For example, an author who published with affiliation $A$ in $t_{0}$, and affiliations $B, C$ in $t_{1}$ could appear as one of $\{A, B, C\}$ or $\{A, C, B\}$ in each training iteration. 
-This effectively removes the effect of order within a year, as order cannot be meaningfully established based on co-affiliations in a single paper, or on different affiliations listed on separate papers, publication of which is not necessarily representative of the actual completion of the project.
+This effectively removes the effect of order within a year, as the order cannot be meaningfully established based on co-affiliations in a single paper, or on different affiliations listed on separate papers, the publication of which is not necessarily representative of the actual completion of the project.
 
@@
 Even though the length of the PPR vectors is extremely larger than the length of our embedding vectors, our result on the embedding outperforms than network approach.
-Moreover, it is also computationally efficient and salable for large dataset.
+Moreover, it is also computationally efficient and salable for large datasets.
 
@@
 
-Affiliations mapped to one of 8,661 organizations, disambiguated following that origionally designed for the Leiden Rankings of World Universities~\autocite{waltman2012leidenrankings}.
+Affiliations mapped to one of 8,661 organizations, disambiguated following that originally designed for the Leiden Rankings of World Universities~\autocite{waltman2012leidenrankings}.
 Organizational records were associated with a full name, a type indicating the sector (e.g., University, Government, Industry), and an identifier for the country and city of the organization.
 Sixteen different sector types were included in the analysis, which we aggregated to a four high-level codes: \textit{University}, \textit{Hospital}, \textit{Government}, and \textit{Other}.
-Each record was also associated with a latitude and longitude, however for many organizations these were missing or incorrect.
+Each record was also associated with a latitude and longitude, however, for many organizations, these were missing or incorrect.
 We manually updated the coordinates of 2,267 organizations by searching the institution name and city on Google Maps;
@@
 The data was further enriched with country-level information, including continent, majority language spoken, and language family of the majority language (e.g., the language family of \textit{Spanish} is \textit{Italic}).
-State/province level  information were added using the reverse geocoding service LocationIQ using each organization's latitude and longitude as input.
+State/province-level information was added using the reverse geocoding service LocationIQ using each organization's latitude and longitude as input.
 Regional census classifications were also added for states in the United States.
-For each organization, we also calculated a size as the average number of unique authors (mobile and non-mobile) who published with that organization across each year of our dataset;
+For each organization, we also calculated size as the average number of unique authors (mobile and non-mobile) who published with that organization across each year of our dataset;
 in the case that authors publish with multiple affiliations in a single year, they are counted towards each.
@@
 		The number of papers published by mobile authors has been steadily increasing from 2008 to 2017, with a small decrease in 2018,  likely an artifact of the Web of Science indexing process.
-		Lines corresponds to publications by mobile authors (org, purple), by authors with affiliations in at least two cities (blue), at least two regions (green), and at least two countries (yellow).
-		There is no evidence of major changes in publication patterns of mobile authors during this time period.
+		Lines correspond to publications by mobile authors (org, purple), by authors with affiliations in at least two cities (blue), at least two regions (green), and at least two countries (yellow).
+		There is no evidence of major changes in the publication patterns of mobile authors during this time period.
 		\textbf{b.}
@@
 		\textbf{d.}
-		The proportion of authors publications across fields has largely remained steady.
-		Biology and Health Science has comprised the majority of publications across nearly all years, but has steadily declined in proportion.
+		The proportion of authors' publications across fields has largely remained steady.
+		Biology and Health Science has comprised the majority of publications across nearly all years but has steadily declined in proportion.
 		However, the proportion of Social Science and Humanities publications has been steadily increasing.
@@
 		\textbf{a.}
-		Proportion of researchers in each country classified as mobile, meaning that they have at least two organization affiliations within the period of study.
+		The proportion of researchers in each country classified as mobile, meaning that they have at least two organization affiliations within the period of study.
 		The countries with the most mobile researchers are the United States, China, France, Great Britain, and Germany.
@@
 		The same information, arranged into a cumulative distribution.
-		The five countires with the highest mobility account for approximately 70 percent of all mobility.
+		The five countries with the highest mobility account for approximately 70 percent of all mobility.
 		\textbf{c.} The proportion of researchers labeled as mobile by country.
 		\textbf{d.} First two principal components of four variables: proportion in each country mobile across organizations, proportion mobile across cities, proportion mobile across regions, and proportion mobile across countries.
-		First component captures overall degree of mobile, whereas the second compares within-country against across-country mobility.
+		The first component captures the overall degree of mobile, whereas the second compares within-country against across-country mobility.
 	}
@@
 		\textbf{a.}
-		Proportion of mobile authors by how many organizations are represented 	in their career trajectories.
+		The proportion of mobile authors by how many organizations are represented in their career trajectories.
 		For example, for mobile authors, 100 percent of authors held an affiliation with at least two organizations, whereas about 35 percent were affiliated with 3 ore more organizations between 2008 and 2019.
@@
 	\caption{
-		\textbf{Personalized page rank with cosine distance.}
+		\textbf{Examine gravity model with dot product on the embedding space.}
 		Performance of dot product similarities in explaining and predicting mobility.
@@
 		Black points show spearman correlation using all organizations; white points show correlation using only universalizes not aggregated in the poles. 
-		More universities improves performance, but quickly saturates after around five universities.
-		\textbf{b - f.} Comparison between the Times and SemAxis ranks of universities, by number of universities used to define the poles (n).
+		Including more universities improves performance, but quickly saturates after around five universities.
+		\textbf{b - f.} Comparison between the Times and SemAxis ranks of universities, by the number of universities used to define the poles (n).
 		White points are those top and bottom 20 universities aggregated to define the ends of the axis.
@@
 		Here, the Leiden Ranking is operationalized as the mean normalized fractional citation impact for each university~\autocite{waltman2012leidenrankings}. 
-	  	PCC details the estimate from Spearman correlation between the two rankings.
+	  	PCC details the estimate from the Spearman correlation between the two rankings.
 	}

### 2020-07-16 paper/current/main.tex
adjust math

@@
 	\label{eq:gravity_basic}
-	\hat{T_{ij}} = Cm_{i}m_{j}f(r_{ij})
+	\hat{T_{ij}} = Cm_{i}m_{j}f(r_{ij}),
 \end{equation}
-
-Where the \textit{expected flux}, $\hat{T_{ij}}$, or expected number of authors who were affiliated with both organizations during the time period is proportional to the organization's sizes (the sum of both mobile and non-mobile authors, see Data and Methods), $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+where the \textit{expected flux}, $\hat{T_{ij}}$, or expected number of authors who were affiliated with both organizations during the time period is proportional to the organization's sizes (the sum of both mobile and non-mobile authors, see Data and Methods), $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
 The distance function is defined in terms of either the geographic distance between organizations or the embedding distance. 
@@
 	\label{eq:gravity_basic}
-	\hat{T_{ij}} = Cm_{i}m_{j}f(r_{ij})
+	\hat{T_{ij}} = Cm_{i}m_{j}f(r_{ij}),
 \end{equation}
-
 where $m_{i}$ and $m_{j}$ are the organization masses, or the yearly-average count of unique authors affiliated with each organization during the time window, and $f(r_{ij})$ is a distance-decaying function  between the two organizations.
@@
 For embedding distance, we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data.
-To estimate parameters $C$, $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_basic}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.
+To estimate parameters $C$, $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_basic}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression
 
@@
 $$
-
 where higher scores mean that organization $w$ is more closely aligned to $S^+$ than $S^-$.

### 2020-07-16 workflow/clustering_figure/script/draw_clustering_figure_country_level.py
adjust label

@@ -282,14 +282,14 @@ def draw_figure(
     ]
     continent_legend = plt.legend(
         handles=handles,
-        bbox_to_anchor=(0.5, 1.74),
+        bbox_to_anchor=(-0.2, 1.74),
         prop=prop,
         frameon=False,
         ncol=6,
         handlelength=0,
         handletextpad=1,
     )
-    plt.text(-11.2, 1.07, "Continent", fontproperties=bold_prop)
+    plt.text(-11.2, 1.07, "Region", fontproperties=bold_prop)
 
     lp = lambda i: plt.plot(
         [],
@@ -365,20 +365,22 @@ def draw_figure(
     similiarties_language_family = [
         sim.element_sim(hierarchical_clu, language_family_clu, r=r) for r in r_list
     ]
-
+    
+    prop = font_manager.FontProperties(fname=FONT_PATH, size=30)
+    small_prop = font_manager.FontProperties(fname=FONT_PATH, size=25)
     sns.set_style("white")
     fig, ax = plt.subplots(1, figsize=(10, 6))
-    ax.plot(r_list, similiarties_continent, "-", label="Continent")
+    ax.plot(r_list, similiarties_continent, "-", label="Region")
     ax.plot(r_list, similiarties_language_family, "-", label="Language Family")
     ax.plot(r_list, similiarties_language, "-", label="Language")
     ax.set_xlabel("r, Scaling parameter", fontproperties=prop)
     ax.set_ylabel("Similarity", fontproperties=prop)
-    ax.legend(bbox_to_anchor=(0.43, 0.68), prop=small_prop, frameon=False)
+    ax.legend(bbox_to_anchor=(0.53, 0.61), prop=small_prop, frameon=False)
 
     for label in ax.get_xticklabels():
-        label.set_fontproperties(tick_prop)
+        label.set_fontproperties(small_prop)
     for label in ax.get_yticklabels():
-        label.set_fontproperties(tick_prop)
+        label.set_fontproperties(small_prop)
 
     plt.savefig(CLUSIM_PART_PATH, bbox_inches="tight")
 

### 2020-07-16 paper/current/main.tex
revise abstract

@@
 Human mobility and migration drives major social phenomenon such as the growth and evolution of cities~\autocite{wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity}, economies~\autocite{kaluza2010cargo, kerr2011immigration}, innovation~\autocite{kaiser2018innovation, armano2017innovation},  and scientific research~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage, morgan2018prestige, rodrigues2016mobility}.
-Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity, xia2005measlesgravity, jung2008highwaygravity, barbosa2018human, curiel2018citygravity, lewer2008immigrationgravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity}, describes mobility using the \textit{distance} between places.
-However, geographic distance is less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization}, in which mobility is dependent less on geography than linguistic, economic, cultural, and historical similarity.
-Alternative and abstract notions of distance attempt to capture the latent landscape of mobility~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional} but pose practical and theoretical challenges.
-Here, using the case of scientific mobility, we leverage the neural embedding model~\autocite{mikolov2013word2vec} to demonstrate a data-driven approach for learning a vector-space embedding that encodes a functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} between organizations and captures the latent and multi-faceted structure of scientist's mobility.
-We demonstrate that the cosine distance between organization vectors in the embedding, constructed using the affiliation trajectories of scientists in the Web of Science database, better explain and predict real mobility than geographic distance.
+Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity, xia2005measlesgravity, jung2008highwaygravity, barbosa2018human, curiel2018citygravity, lewer2008immigrationgravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity}, often successfully capture mobility between places using their population and the \textit{distance} between them.
+However, geographic distance is less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization} where the physical distance barrier shrinks while the impact of linguistic, economic, cultural, and historical similarity increases.
+Alternative notions of functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} attempt to re-define distance by using some of the aforementioned factor~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional} but suffer from practical and theoretical challenges.
+Here, using a rich dataset of scientific mobility, we demonstrate that a data-driven neural embedding approach~\autocite{mikolov2013word2vec} can successfully encodes a functional distance between organizations and captures the latent and multi-faceted structure of scientist's mobility.
+We demonstrate that the cosine distance between organization embedding vectors, constructed using the affiliation trajectories of scientists in the Web of Science database, better explain and predict real mobility than geographic distance.
 Exploiting their unique properties, we interpret the embedding space and observe how it captures latent factors related to culture, language, and prestige of organizations at multiple levels of granularity.
-This approach can learn scalable, dense, and meaningful vector representations of scientific mobility directly from the data, and can easily be generalized to other mobility data.
+The ability yo learn scalable, dense, and meaningful vector representations of mobility directly from the data can open up a new avenue of studying human mobility.
 

### 2020-07-16 paper/current/main.tex
typo

@@
 Exploiting their unique properties, we interpret the embedding space and observe how it captures latent factors related to culture, language, and prestige of organizations at multiple levels of granularity.
-The ability yo learn scalable, dense, and meaningful vector representations of mobility directly from the data can open up a new avenue of studying human mobility.
+The ability to learn scalable, dense, and meaningful vector representations of mobility directly from the data can open up a new avenue of studying human mobility.
 

### 2020-07-16 paper/current/main.tex
update intro and first para

@@
 The question is surprisingly hard to answer when it involves human mobility.
-While geographic distance may have driven human movements in past eras, it holds less importance to a world connected by rapid transit, complex international relations, and dense airline networks.
-For instance, a person currently living in Australia is more likely to migrate to the United Kingdom, a country with similar language and culture, than to closer and more populous countries like Indonesia.
-Similarly, a prospective student living in South Korea is more likely to attend university in Canada rather than the closer though diplomatically isolated North Korea. 
-Despite its complexity, geographic distance is used as the basis for the most prominent models of mobility such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal}.
-So-called \textit{functional distances}~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional} have been proposed that attempt to learn alternative notions of distance from real-world data or \textit{a priori} relationships between geographic entities.
+While geographic distance may have driven human movements in the past, it holds less importance to a world connected by rapid transit, complex international relations, and dense airline networks.
+For instance, a person living in Australia is more likely to migrate to the United Kingdom, a country with similar language and culture, than to closer and more populous countries like Indonesia. 
+Similarly, a prospective student living in South Korea is more likely to attend universities in Canada than those in North Korea. 
+While geographic distance is still used as the basis for the most prominent models of mobility such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} model, so-called \textit{functional distances}~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional} have been proposed to learn alternative notions of distance from real-world data or \textit{a priori} relationships between geographic entities.
+Yet, limitations of the existing functional distance measure still are not being overcome.
 
@@
 This approach, originally designed for learning language models~\autocite{mikolov2013word2vec} has been used to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
-Neural embedding is also computationally efficient, scalable for large datasets, robust to noise, and is readily interpretable through the application of simple vector arithmetic.
-
-We use scientific mobility, inferred from affiliations, to demonstrate the neural embedding approach. 
+Neural embedding is also computationally efficient, scalable for large datasets, robust to noise, and can extract rich relationship between the entities through the application of simple vector arithmetic.
+
+We use scientific mobility, inferred from affiliations, to demonstrate the effectiveness of our approach
 Scientific mobility is a central aspect of the increasingly-globalized scientific system~\autocite{czaika2018globalisation, altbach2004globalization}, being strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}.
@@
 However, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}.
-One roadblock is the lack of a meaningful measure of the functional distance between countries, cities, and organizations.
-
-Here, scientific mobility is operationalized using researcher's organizational affiliations derived from their publication histories indexed in a large-scale bibliographic database. 
+Underlying these challenges is the lack of a meaningful functional distance measure between countries, cities, and organizations.
+
+Here, scientific mobility is operationalized using researcher's organizational affiliations derived from their publication histories indexed in a comprehensive bibliographic database. 
 The most fine-grained geographical unit in this data is the organization, such as a university, research institute, business, or government agency.
@@
 For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_emb_bymodel} and Fig.~\ref{fig:supp:predict_geo_bymodel}).
-We argue that the performance of a distance measure can be observed from its ability to explain expected mobility between organizations and to make predictions using the gravity model.
 
@@
 Our results unequivocally argue that the distance learned by the embedding method better captures actual mobility patterns than does geographic distance.
-We speculate that this results from an underlying mathematical connection between the neural embedding architecture and the gravity model of mobility.
 

### 2020-07-16 paper/current/main.tex
edit second main para

@@
 
-By encoding the complex landscape in a dense representation, embeddings also allow us to create informative visualizations of global scientific mobility.
-To explore the topological structure of the embedding, we use a common dimensionality reduction technique (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation of the embedding (Fig.~\ref{fig:projection}a).
+The embedding also allows us to create informative visualizations of global scientific mobility.
+To explore the topological structure of the embedding, we use a standard dimensionality reduction technique (UMAP~\autocite{mcinnes2018umap}) for embedding to obtain a two-dimensional representation of the embedding (Fig.~\ref{fig:projection}a).
 By showing relationships between individual organizations, rather than aggregates such as nations or cities, this projection constitutes the largest and highest resolution ``map'' of scientific mobility to date.
 
-Globally, the effect of geography is conspicuous; organizations tend to form clusters based on their national affiliations and national clusters tend to be near their geographic neighbors. 
+Globally, the geographical constraints are conspicuous; organizations tend to form clusters based on their national affiliations and national clusters tend to be near their geographic neighbors. 
 At the same time, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions much more clearly than alternative network representations (Fig.~\ref{fig:supp:network_vis}) that have been dominating studies of scientific mobility~\autocite{chinchilla2018global, czaika2018globalisation}.
@@
 For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries ranging from Egypt to Philippines that corresponds largely to geography, but with some peculiar exceptions.
-For example, countries like Iraq are nearer to some southeast-Asian countries like Malaysia, with a cosine distance between the nation's aggregate vectors of $d = 0.29$, than to nearer and more religiously-similar nations like Saudi Arabia ($d = 0.50$ and Qatar ($d = 0.51$).
+For example, countries like Iraq are nearer to some southeast-Asian countries like Malaysia, with a cosine distance between the nation's aggregate vectors of $d = 0.29$, than to nearer and more religiously-similar nations like Saudi Arabia ($d = 0.50$) and Qatar ($d = 0.51$).
 Linguistic and historical ties are also conspicuous.
-For example, we observe that Spanish-speaking post-colonial Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), such as Mexico ($d = 0.34$) and Chile ($d = 0.39$) morose than to nearby Portuguese-speaking nation ($d = 0.52$ for Mexico and $d = 0.49$ for Chile) reflecting language and culture constructed the nature of scientific mobility.
+For example, we observe that Spanish-speaking post-colonial Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), such as Mexico ($d = 0.34$) and Chile ($d = 0.39$) more than to nearby Portuguese-speaking nation ($d = 0.52$ for Mexico and $d = 0.49$ for Chile) reflecting languatic and cultural constraints.
 Similarly, North-African countries that were once under French rule such as Morocco are nearer to France ($d =0.35$) than to similarly-distant European countries as Spain ($d = 0.40$) and Italy ($d = 0.53$).
 Comparable structural patterns exist even within a single country.
-For example, at the global level (Fig~\ref{fig:projection}a), organizations within Quebec in Canada are located nearer the French cluster ($d = 0.65$) than the rest of the Canadian universities Canada ($d = 0.88$).
+For example, at the global level (Fig~\ref{fig:projection}a), organizations within Quebec in Canada are located nearer the French cluster ($d = 0.65$) than the rest of the Canadian universities ($d = 0.88$).
 
 The geographic structure of the global embedding is mirrored in the re-projection of the United States, wherein organizations are largely organized according to regions and states (Fig.~\ref{fig:projection}d).
-By re-projecting at the state-level for Massachusetts (Fig.~\ref{fig:projection}e), we observe structure between urban centers (Boston vs.
-Worcester) but also based on organization type (e.g., hospitals vs.
+By re-projecting Massachusetts (Fig.~\ref{fig:projection}e), we observe structure  based on urban centers (Boston vs.
+Worcester) as well as on organization type (e.g., hospitals vs.
 universities) and university systems.

### 2020-07-16 paper/current/main.tex
conclution part

@@
 universities) and university systems.
-For example, even though UMass Boston is located in Boston, it clusters near other universities in the UMass System ($d = 0.34$) rather than the other typically more elite and research-focused universities in Boston ($d = 0.41$), reflecting a relative lack of mobility between the two systems, even within the same state.
+For example, even though UMass Boston is located in Boston, it clusters with  other universities in the UMass System ($d = 0.34$) rather than the other typically more elite and research-focused universities in Boston ($d = 0.41$), reflecting a relative lack of mobility between the two systems, even within the same state.
 Similar structures can be observed in other states such as among New York's CUNY and SUNY systems (Fig.~\ref{fig:supp:proj_newyork}), Pennsylvania's state system (Fig.~\ref{fig:supp:proj_pennsylvania}), Texas's Agricultural and Mechanical universities (Fig.~\ref{fig:supp:proj_texas}), and between the University of California and State University of California systems (Fig.~\ref{fig:supp:proj_california}).
@@
 Namely, we calculate the representative vector of each country by averaging organization vectors within the given country.
-We then perform hierarchical clustering of nations that have at least 25 organizations represented in the embedding space, excluding the United States which has high similarity with most other countries (see Fig.
+We then perform hierarchical clustering of nations that have at least 25 organizations represented in the embedding space, excluding the United States which is a dominant hub well connected to most other countries (see Fig.
 \ref{fig:clustering}a).
@@
 
-Prestige hierarchies underpin the dynamics of scientific mobility~\autocite{deville2014career, clauset2015hierarchy}, but are these hierarchies captured in the embedding space?
-We test this by exploiting the geometric properties of the embedding space with the technique SemAxis~\autocite{an2018semaxis}, an approach originally designed to characterize the semantics of words in language embeddings.
-Here, we use SemAxis to operationalize the abstract notion of academic prestige, defining each end of the axis using known high- and low-ranked universities. 
+Prestige hierarchies underpin the dynamics of scientific mobility~\autocite{deville2014career, clauset2015hierarchy}, but are these hierarchies captured in the embedding space, to which no explicit information on the prestige is given?
+We test this by exploiting the geometric properties of the embedding space with the  SemAxis~\autocite{an2018semaxis}, an approach originally designed to characterize the semantics of words in word embeddings.
+Here, we use SemAxis to operationalize the abstract notion of academic prestige, defining each pole of the axis using known high- and low-ranked universities. 
 We define prestige using the Times Ranking of World Universities, including all ranked universities in the United States;
-the elite end is defined as the mean vector of the top five U.S.
-universities according to the rankings, whereas the non-elite axis is defined using the five bottom-ranked and geographically matched (by U.S.
+the ``elite" pole is defined as the mean vector of the top five U.S.
+universities according to the rankings, whereas the non-elite pole is defined using the five bottom-ranked and geographically matched (by U.S.
 census region) universities.
@@
 The embedding space captures prestige hierarchies that can be used to reconstruct academic rankings. 
-We derive a ranking using the SemAxis prestige axis in Fig.~\ref{fig:semaxis}.a and compare them to traditional university rankings.
+We derive a ranking using the SemAxis prestige axis in Fig.~\ref{fig:semaxis}a and compare them to traditional university rankings.
 The SemAxis ranking is defined from the position of organizations along the prestige axis, with the top-ranked being the furthest towards the \textit{Elite} end of the axis.
-We find that the SemAxis ranking is highly correlated with the Times ranking (Spearman's $\rho = 0.73$, Fig.~\ref{fig:semaxis}b).
-The strongest outliers are universities that were ranked more highly in the Times Ranking than the SemAxis ranking and tended to be large universities such as Arizona State University and  University of Florida;
-Those ranked higher in the SemAxis ranking tended to be relatively-smaller universities such as the University of San Francisco and University of Maryland Baltimore County.
+We find that the SemAxis ranking is correlated with the Times ranking (Spearman's $\rho = 0.73$, Fig.~\ref{fig:semaxis}b).
+The strongest outliers that were ranked more highly in the Times Ranking than the SemAxis ranking tend to be large state universities such as Arizona State University and  University of Florida;
+Those ranked higher in the SemAxis ranking tend to be relatively-smaller universities such as the University of San Francisco and University of Maryland Baltimore County that are close to other prestigious universities.
 
 The correlation between SemAxis and the Times ranking is robust with the number of organizations used to define the axes (Fig.
-SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities are strongly correlated with the Times Ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
-For reference, SemRank achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking~\autocite{waltman2012leidenrankings}, a common and bibliometrically-informed university ranking (Spearman's $\rho = 0.87$, Fig.~\ref{fig:supp:times_vs_leiden}).
-This suggests that the organization embedding surprisingly captures the latent prestige hierarchy inherent to academic mobility with a high degree of resolution and reliability~\autocite{deville2014career, clauset2015hierarchy}.
+SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities are significantly correlated with the Times Ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
+For reference, our result achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking~\autocite{waltman2012leidenrankings}, a common and bibliometrically-informed university ranking (Spearman's $\rho = 0.87$, Fig.~\ref{fig:supp:times_vs_leiden}).
+This suggests that the organization embedding captures the latent prestige hierarchy inherent to academic mobility, even without providing any explicit information on prestige, with a high degree of resolution and reliability~\autocite{deville2014career, clauset2015hierarchy}.
 
@@
 In spite of its promise, this approach and analysis present several limitations. 
-First, the \textit{skip-gram word2vec} model can not encode directional information, meaning that embedding will be less effective at capturing mobility for which directional is critical.
+First, the current \textit{skip-gram word2vec} model can not encode directional information, meaning that embedding will be less effective at capturing mobility for which directional is critical.
 Second, the neural embedding approach is most useful in cases of mobility between discrete geographic units such as between countries, cities, and businesses; this approach is less useful in the case of mobility between arbitrary locations represented in geographic coordinates, such as in the modeling of animal movements.
@@
 The kinds of mobility we do capture—asynchronous migration and synchronous co-affiliation, are treated identically by our model even though they are qualitatively different.
-Also, our data can possess survivorship bias. Researchers at prestigious organizations tend to have more publications, inducing appear more in the mobility sentence.
-Scientific mobility is complex, and its study continues to pose challenges; neural embeddings do not solve many of these issues, but they create opportunities for new analyses and understanding
-future work should aim to
-
-Mobility and migration is a core asepct of human nature and history~\autocite{shah2020migration}, driving social phenomena as diverse as epidemics\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity} and science and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage, morgan2018prestige, rodrigues2016mobility}.
+Also, our data can possess survivorship bias. Researchers at prestigious organizations tend to have more publications, inducing these organizations appear more in the mobility sentence.
+
+Mobility and migration is a core asepct of human nature and history~\autocite{shah2020migration}, driving social phenomena as diverse as epidemics\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity} and science and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage, morgan2018prestige, rodrigues2016mobility}, and that there have been lots of politically motivated policy changes that affect scientific mobility.
 Within science, mobility has grown increasingly global~\autocite{czaika2018globalisation}, though the travel restrictions in the U.S.
@@
 	\label{eq:linear_flux_geo}
-	\ln\frac{T_{ij}}{m_im_j} = \ln(C)  - \alpha \ln(g_{ij})
+	\ln\frac{T_{ij}}{m_im_j} = \ln C  - \alpha \ln g_{ij}
 \end{equation}
@@
 	\label{eq:linear_flux_emb}
-	\ln\frac{T_{ij}}{m_im_j} = \ln(C) - \beta d_{ij}
+	\ln\frac{T_{ij}}{m_im_j} = \ln C - \beta d_{ij}
 \end{equation}

### 2020-07-16 paper/current/main.tex
change continent to region

@@
 		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019. 
-		Color indicates the continent.
+		Color indicates the region.
 		\textbf{b.} Zooming into (re-projecting) the area containing countries in the Middle East and South and Southeast Asia shows a geographic and cultural gradient of country clusters. 
@@
 
-We quantify the relative importance of geography (by continent), and language (by majority language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering by explicitly adjusting the relative importance of different levels of the hierarchy with scaling parameter $r$, acting like a ``zooming lens''.
+We quantify the relative importance of geography (by region), and language (by majority language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering by explicitly adjusting the relative importance of different levels of the hierarchy with scaling parameter $r$, acting like a ``zooming lens''.
 If $r$ is high, the similarity is based on the lower levels of the dendrogram, whereas when $r$ is low, the similarity is based on higher levels.
 Fig.
-\ref{fig:clustering}b demonstrates that the continent plays a major role at higher levels of the clustering process (low $r$), and language (family) explains the clustering more at the lower levels (high $r$).
+\ref{fig:clustering}b demonstrates that the region plays a major role at higher levels of the clustering process (low $r$), and language (family) explains the clustering more at the lower levels (high $r$).
 This suggests that geography, then language, are important factors contributing to the structure of international scientific mobility.

### 2020-07-16 paper/current/main.tex
change to region

@@
 		Color of country names corresponds to their cluster.
-		Color of three cell rows separated from the matrix correspond to, from left to right, the continent of the country, the language family~\autocite{ethnologue}, and the individual language.
+		Color of three cell rows separated from the matrix correspond to, from left to right, the region of the country, the language family~\autocite{ethnologue}, and the individual language.
 		\textbf{b.}	Element-centric cluster similarity~\autocite{gates2019element} results demonstrating the factors dictating hierarchical clustering, varying by scaling parameter, $r$.
-		Continent better explains the grouping of country vectors at higher levels of the clustering processes.
+		Region better explains the grouping of country vectors at higher levels of the clustering processes.
 		Language family, and then majority spoken language, better explain the grouping of countries at more granular.
@@
 in cases where a precise location of the organization could not be identified, we used the coordinates returned when searching the name of the city.
-The data was further enriched with country-level information, including continent, majority language spoken, and language family of the majority language (e.g., the language family of \textit{Spanish} is \textit{Italic}).
+The data was further enriched with country-level information, including region, majority language spoken, and language family of the majority language (e.g., the language family of \textit{Spanish} is \textit{Italic}).
 State/province-level information was added using the reverse geocoding service LocationIQ using each organization's latitude and longitude as input.

### 2020-07-16 workflow/clustering_figure/script/draw_clustering_figure_country_level.py
update figure

@@ -366,8 +366,8 @@ def draw_figure(
         sim.element_sim(hierarchical_clu, language_family_clu, r=r) for r in r_list
     ]
     
-    prop = font_manager.FontProperties(fname=FONT_PATH, size=30)
-    small_prop = font_manager.FontProperties(fname=FONT_PATH, size=25)
+    
+    prop = font_manager.FontProperties(fname=FONT_PATH, size=40)
     sns.set_style("white")
     fig, ax = plt.subplots(1, figsize=(10, 6))
     ax.plot(r_list, similiarties_continent, "-", label="Region")
@@ -375,12 +375,12 @@ def draw_figure(
     ax.plot(r_list, similiarties_language, "-", label="Language")
     ax.set_xlabel("r, Scaling parameter", fontproperties=prop)
     ax.set_ylabel("Similarity", fontproperties=prop)
-    ax.legend(bbox_to_anchor=(0.53, 0.61), prop=small_prop, frameon=False)
+    ax.set_yticks([.1, .3, .5, .7])
 
     for label in ax.get_xticklabels():
-        label.set_fontproperties(small_prop)
+        label.set_fontproperties(prop)
     for label in ax.get_yticklabels():
-        label.set_fontproperties(small_prop)
+        label.set_fontproperties(prop)
 
     plt.savefig(CLUSIM_PART_PATH, bbox_inches="tight")
 

### 2020-07-20 paper/current/main.tex
add additional globalization ref

@@
 Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity, xia2005measlesgravity, jung2008highwaygravity, barbosa2018human, curiel2018citygravity, lewer2008immigrationgravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity}, often successfully capture mobility between places using their population and the \textit{distance} between them.
-However, geographic distance is less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization} where the physical distance barrier shrinks while the impact of linguistic, economic, cultural, and historical similarity increases.
+However, geographic distance is less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} where the physical distance barrier shrinks while the impact of linguistic, economic, cultural, and historical similarity increases.
 Alternative notions of functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} attempt to re-define distance by using some of the aforementioned factor~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional} but suffer from practical and theoretical challenges.

### 2020-07-20 paper/current/main.tex
minor text edits

@@
 While geographic distance is still used as the basis for the most prominent models of mobility such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} model, so-called \textit{functional distances}~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional} have been proposed to learn alternative notions of distance from real-world data or \textit{a priori} relationships between geographic entities.
-Yet, limitations of the existing functional distance measure still are not being overcome.
+Yet, limitations of the existing functional distance measure have yet to be overcome.
 
@@
 This approach, originally designed for learning language models~\autocite{mikolov2013word2vec} has been used to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
-Neural embedding is also computationally efficient, scalable for large datasets, robust to noise, and can extract rich relationship between the entities through the application of simple vector arithmetic.
-
-We use scientific mobility, inferred from affiliations, to demonstrate the effectiveness of our approach
+Neural embedding is also computationally efficient, scalable for large datasets, robust to noise, and can extract rich relationship between the entities through the application of simple vector arithmetic~\autocite{levy2014neural}.
+
+We use scientific mobility, inferred from affiliations, to demonstrate the effectiveness of our approach.
 Scientific mobility is a central aspect of the increasingly-globalized scientific system~\autocite{czaika2018globalisation, altbach2004globalization}, being strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}.
@@
 These trajectories encode both asynchronous migration, and synchronous mobility---the holding of multiple simultaneous co-affiliations involving the sharing of time and capital between locations---that is typical of scientific mobility~\autocite{rodrigues2016mobility, markova2016synchronous, sugimoto2017mostimpact} (see Supplementary Materials).
-We use the trajectories of the three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
+We use the trajectories of more than three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
 
@@
 Linguistic and historical ties are also conspicuous.
-For example, we observe that Spanish-speaking post-colonial Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), such as Mexico ($d = 0.34$) and Chile ($d = 0.39$) more than to nearby Portuguese-speaking nation ($d = 0.52$ for Mexico and $d = 0.49$ for Chile) reflecting languatic and cultural constraints.
+For example, we observe that Spanish-speaking post-colonial Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), such as Mexico ($d = 0.34$) and Chile ($d = 0.39$) more than to nearby Portuguese-speaking nation ($d = 0.52$ for Mexico and $d = 0.49$ for Chile) reflecting linguistic and cultural constraints.
 Similarly, North-African countries that were once under French rule such as Morocco are nearer to France ($d =0.35$) than to similarly-distant European countries as Spain ($d = 0.40$) and Italy ($d = 0.53$).
@@
 
-Just as the embedding space makes it possible to ``zoom in'' on subsets of organizations, it is possible to ``zoom out'' to a higher level by aggregating organizational vectors. 
+Just as the embedding space makes it possible to ``zoom in'' on subsets of organizations, it is also possible to ``zoom out'' to a higher level by aggregating organizational vectors. 
 For example, we can examine the high-level structure by estimating the aggregate embeddings of countries. 
-Namely, we calculate the representative vector of each country by averaging organization vectors within the given country.
+Namely, we calculate the representative vector of each country as the average of their organizational vectors.
 We then perform hierarchical clustering of nations that have at least 25 organizations represented in the embedding space, excluding the United States which is a dominant hub well connected to most other countries (see Fig.
 \ref{fig:clustering}a).
-The six identified clusters roughly correspond to East-Asian (orange), Scandinavian (dark purple), British Commonwealth (light purple), Central and Eastern European countries (light blue), and then two remaining diverse clusters that contain a mix of European, Latin American, and Mediterranean countries.
+The six identified clusters roughly correspond to countries in East-Asia (orange), Scandinavia (dark purple), the British Commonwealth (light purple), and Central and Eastern Europe (light blue), and then two remaining diverse clusters contain a mix of European, Latin American, and Mediterranean countries.
 These clusters demonstrate the importance of not only geography but also linguistic ties between countries.
@@
 Prestige hierarchies underpin the dynamics of scientific mobility~\autocite{deville2014career, clauset2015hierarchy}, but are these hierarchies captured in the embedding space, to which no explicit information on the prestige is given?
-We test this by exploiting the geometric properties of the embedding space with the  SemAxis~\autocite{an2018semaxis}, an approach originally designed to characterize the semantics of words in word embeddings.
+We test this by exploiting the geometric properties of the embedding space with SemAxis~\autocite{an2018semaxis}, an approach originally designed to characterize the semantics of words in word embeddings.
 Here, we use SemAxis to operationalize the abstract notion of academic prestige, defining each pole of the axis using known high- and low-ranked universities. 
-We define prestige using the Times Ranking of World Universities, including all ranked universities in the United States;
-the ``elite" pole is defined as the mean vector of the top five U.S.
-universities according to the rankings, whereas the non-elite pole is defined using the five bottom-ranked and geographically matched (by U.S.
+We define prestige using the Times Ranking of World Universities (and using research impact from the Leiden Rankings~\autocite{waltman2012leidenrankings} in Supplementary Materials), including all ranked universities in the United States;
+the high-ranked pole is defined as the mean vector of the top five U.S.
+universities according to the rankings, whereas the low-ranked pole is defined using the five bottom-ranked and geographically matched (by U.S.
 census region) universities.
@@
 
-Prestigious universities such as Stanford, Colombia, MIT, Harvard, and NYU are positioned towards the top of the axis (Fig.~\ref{fig:semaxis}a).
-Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education).
-SemAxis also offers a new means of reasoning about the prestige of organizations typically excluded from rankings such as government organizatioss (Fig.~\ref{fig:supp:semaxis_sectors}a), research institutes (Fig.~\ref{fig:supp:semaxis_sectors}b), and teaching colleges (Fig.~\ref{fig:supp:semaxis_sectors}c).
+Prestigious universities such as Colombia, Stanford, MIT, Harvard, and Rockefeller are positioned towards the top of the axis (Fig.~\ref{fig:semaxis}a).
+Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphesis on teaching, such as Barry Univeristy and California State University at Long Beach.
+SemAxis also offers a new means of reasoning about the prestige of organizations typically excluded from rankings such as government organizations (Fig.~\ref{fig:supp:semaxis_sectors}a), research institutes (Fig.~\ref{fig:supp:semaxis_sectors}b), and teaching colleges (Fig.~\ref{fig:supp:semaxis_sectors}c).
 
@@
 		Full organization names listed in Table~\ref{table:supp:orglabels}.
-		\textbf{b.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity to the \textit{Elite} end of the axis prestige axis \textit{a}.
+		\textbf{b.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity high-ranked end of the axis prestige axis \textit{a}.
 		White points are those top and bottom five universities used to define the poles of the axis.
-	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the SemAxis and Times ranking is 0.73 (n = 145), and it increases if we include more top-and-bottom ranked universities (Fig.~\ref{fig:supp:semaxis_compare}).
+	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the SemAxis and Times ranking is $rho = 0.73$ (n = 145), and it increases if we include more top-and-bottom ranked universities (Fig.~\ref{fig:supp:semaxis_compare}).
 	}
@@
 SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities are significantly correlated with the Times Ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
-For reference, our result achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking~\autocite{waltman2012leidenrankings}, a common and bibliometrically-informed university ranking (Spearman's $\rho = 0.87$, Fig.~\ref{fig:supp:times_vs_leiden}).
+For reference, the SemAxis-derived ranking achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking~\autocite{waltman2012leidenrankings}, a common and bibliometrically-informed university ranking (Spearman's $\rho = 0.87$, Fig.~\ref{fig:supp:times_vs_leiden}).
 This suggests that the organization embedding captures the latent prestige hierarchy inherent to academic mobility, even without providing any explicit information on prestige, with a high degree of resolution and reliability~\autocite{deville2014career, clauset2015hierarchy}.
@@
 The kinds of mobility we do capture—asynchronous migration and synchronous co-affiliation, are treated identically by our model even though they are qualitatively different.
-Also, our data can possess survivorship bias. Researchers at prestigious organizations tend to have more publications, inducing these organizations appear more in the mobility sentence.
-
-Mobility and migration is a core asepct of human nature and history~\autocite{shah2020migration}, driving social phenomena as diverse as epidemics\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity} and science and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage, morgan2018prestige, rodrigues2016mobility}, and that there have been lots of politically motivated policy changes that affect scientific mobility.
-Within science, mobility has grown increasingly global~\autocite{czaika2018globalisation}, though the travel restrictions in the U.S.
+Also, our data can possess survivorship bias: researchers at prestigious organizations tend to have more publications, inducing these organizations appear more in the mobility sentence.
+
+Mobility and migration is a core asepct of human nature and history~\autocite{shah2020migration}, driving social phenomena as diverse as epidemics\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity} and science and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage, morgan2018prestige, rodrigues2016mobility}.
+However, the paradigm of scientific migration may be changing.
+Traditional hubs of migration have enacted many politially-motivated policy changes that affect scientific mobility, such as travel restrictions in the U.S.
 and U.K.
-brought by Brexit and the Trump administration~\autocite{chinchilla2018travelban}, and the rise of new scientific powers such as China~\autocite{tollefson2018china, cao2020returning} may lead to a reorientation in who goes where.
-Similarly, the COVID19 pandemic threatens drastic change to travel and migration by tightening borders and halting travel. 
-Now, more than ever, new tools and approaches are needed to understanding human mobility in order to inform sensible, effective, humane Immigration and Science and Technology policy.
+brought by Brexit and the Trump administration~\autocite{chinchilla2018travelban}.
+Other nations, such as China, are growing into major scientific powers and attractors of talent~\autocite{tollefson2018china, cao2020returning}.
+Global crises such as COVID19 pandemic threaten drastic change to travel and migration by tightening borders and halting travel. 
+Now, more than ever, new tools and approaches are needed to understanding human mobility in order to inform sensible, effective, and humane Immigration and Science and Technology policy.
 

### 2020-07-20 workflow/scripts/PlotPrestigeRankCorrelation.R
replace "rho" with actual symbol

@@ -70,7 +70,7 @@ plot <- corr %>%
     legend.title = element_blank()
   ) +
   xlab("Num orgs in axis") +
-  ylab("Spearman's Rho")
+  ylab(latex2exp::TeX("Spearman's $\\rho"))
 
 # Save the plot
 ggsave(opt$output, plot, width = FIG_WIDTH, height = FIG_HEIGHT)

### 2020-07-20 workflow/scripts/PlotPrestigeSimVsRank.R

@@ -162,8 +162,8 @@ plot <- sims %>%
     panel.grid.minor = element_blank(),
   ) +
   # Add the Spearman's Rho to the plot
-  annotate("text", x = 45, y = 145,
-           label = paste("Spearman's Rho = ", round(cor$estimate, 2)),
+  annotate("text", x = 40, y = 145,
+           label = latex2exp::TeX(paste("Spearman's $\\rho = ", round(cor$estimate, 2))),
            size = 7,
            fontface = 2) +
   ylab(axis_title) +

### 2020-07-20 paper/current/main.tex
remove "elite" naming

@@
 universities) and university systems.
-For example, even though UMass Boston is located in Boston, it clusters with  other universities in the UMass System ($d = 0.34$) rather than the other typically more elite and research-focused universities in Boston ($d = 0.41$), reflecting a relative lack of mobility between the two systems, even within the same state.
+For example, even though UMass Boston is located in Boston, it clusters with  other universities in the UMass System ($d = 0.34$) rather than the other typically more highly-ranked and research-focused universities in Boston ($d = 0.41$), reflecting a relative lack of mobility between the two systems, even within the same state.
 Similar structures can be observed in other states such as among New York's CUNY and SUNY systems (Fig.~\ref{fig:supp:proj_newyork}), Pennsylvania's state system (Fig.~\ref{fig:supp:proj_pennsylvania}), Texas's Agricultural and Mechanical universities (Fig.~\ref{fig:supp:proj_texas}), and between the University of California and State University of California systems (Fig.~\ref{fig:supp:proj_california}).
@@
 We derive a ranking using the SemAxis prestige axis in Fig.~\ref{fig:semaxis}a and compare them to traditional university rankings.
-The SemAxis ranking is defined from the position of organizations along the prestige axis, with the top-ranked being the furthest towards the \textit{Elite} end of the axis.
+The SemAxis ranking is defined from the position of organizations along the prestige axis, with the top-ranked being the furthest towards the high-ranked end of the axis.
 We find that the SemAxis ranking is correlated with the Times ranking (Spearman's $\rho = 0.73$, Fig.~\ref{fig:semaxis}b).
@@
 Scientific mobility is complex and can be defined in many possible ways~\autocite{robinson2019mobility} and at multiple levels of analysis.
-Here, authors are classified as mobile when they have at least two distinct organization ids in their trajectory, meaning that they have published using two or more distinct affiliations between 2008 and 2019.
+Here, authors are classified as mobile when they have at least two distinct organization IDs in their trajectory, meaning that they have published using two or more distinct affiliations between 2008 and 2019.
 Under this definition, mobile authors constitute 3,007,192 or 23.2 percent of all authors and 17,700,095 author-affiliation combinations.

### 2020-07-20 paper/current/main.tex
fix cases where rho was not the proper symbol

@@
 		White points are those top and bottom five universities used to define the poles of the axis.
-	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the SemAxis and Times ranking is $rho = 0.73$ (n = 145), and it increases if we include more top-and-bottom ranked universities (Fig.~\ref{fig:supp:semaxis_compare}).
+	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the SemAxis and Times ranking is $\rho = 0.73$ (n = 145), and it increases if we include more top-and-bottom ranked universities (Fig.~\ref{fig:supp:semaxis_compare}).
 	}
@@
 		The grey box corresponds to the top 20 and bottom 20 ranks.
-	  	Spearman's rho details the estimate from Spearman correlation between the two rankings using all universities, including those used to define the ends of each axis. 
+	  	Spearman's $\rho$ details the estimate from Spearman correlation between the two rankings using all universities, including those used to define the ends of each axis. 
 	}

### 2020-07-20 workflow/scripts/Plot2DSemAxis.R
replace "elite" with "high-ranked" in 2d semaxis plots

@@ -15,8 +15,8 @@ NOT_HIGHLIGHTED_ALPHA = 0.9
 
 MASS_LABEL = "Massachusetts"
 CALI_LABEL = "California"
-TOP_LABEL = "Elite"
-BOT_LABEL = "Non elite"
+TOP_LABEL = "High-ranked"
+BOT_LABEL = "Low-ranked"
 
 STATES_TO_PLOT <- c("Connecticut", "New York", "Arizona", "California", "Massachusetts", "Florida")
 STATE_COLORS <- c("#7fc97f", "#beaed4", "#fdc086", "#ffff99", "#386cb0", "#f0027f")
@@ -181,8 +181,8 @@ y_floor <- floor(min(unis$sim.y) * 50) / 50
 
 plot <- plotdata %>%
   ggplot() +
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  geom_hline(yintercept = 0, linetype = "dashed") +
+  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
+  geom_hline(yintercept = 0, linetype = "dashed", color = "grey") +
   geom_point(aes(x = sim.x, y = sim.y),
              size = 3.5,
              shape = 16,

### 2020-07-20 workflow/scripts/PlotPredictedVsActual.R
move around labels on gravity law plots

@@ -132,7 +132,7 @@ plot <- data %>%
                      expand = c(0, 0)) +
   coord_fixed() +
   annotate(geom = "text",
-           x = 1.4,
+           x = 1.6,
            y = 6.2,
            label = paste0("RMSE = ", sprintf("%.2f", round(error,3))),
            size = 7

### 2020-07-20 paper/current/main.tex
update figure 5 & surrounding text

@@
 Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphesis on teaching, such as Barry Univeristy and California State University at Long Beach.
-SemAxis also offers a new means of reasoning about the prestige of organizations typically excluded from rankings such as government organizations (Fig.~\ref{fig:supp:semaxis_sectors}a), research institutes (Fig.~\ref{fig:supp:semaxis_sectors}b), and teaching colleges (Fig.~\ref{fig:supp:semaxis_sectors}c).
+SemAxis also offers a new means of reasoning about the prestige of organizations typically excluded from rankings such as government organizations (Fig.~\ref{fig:semaxis}b), research institutes (Fig.~\ref{fig:semaxis}c), and teaching colleges (Fig.~\ref{fig:semaxis}d).
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_fig.pdf}
+	\includegraphics[width=0.7\textwidth]{\figdir/SemAxis/semaxis_fig.pdf}
 	\caption{
 		\textbf{Embedding captures latent geography and prestige hierarchy.}
-		\textbf{a.} Illustration of SemAxis projection along two axes;  \textit{latent geographical axis}, from California to Massachusetts (left to right) and \textit{prestige axis}, from the top five to geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S.
+		\textbf{a-d.} Illustration of SemAxis projection along two axes;  \textit{latent geographical axis}, from California to Massachusetts (left to right) and \textit{prestige axis}, from the top five to geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S.
 Universities (top to bottom).
-		Points correspond to organizations, and a sample of states are highlighted.
+		Shown for U.S. Universities (\textbf{a}), Teaching colleges (\textbf{b}), Research institutes (\textbf{c}), and Government organizations (\textbf{d}).
 		Full organization names listed in Table~\ref{table:supp:orglabels}.
-		\textbf{b.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity high-ranked end of the axis prestige axis \textit{a}.
+		\textbf{e.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity high-ranked end of the axis prestige axis \textit{a}.
 		White points are those top and bottom five universities used to define the poles of the axis.
 	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the SemAxis and Times ranking is $\rho = 0.73$ (n = 145), and it increases if we include more top-and-bottom ranked universities (Fig.~\ref{fig:supp:semaxis_compare}).
+	  	\textbf{f.} Times ranking is correlated with Leiden Ranking of U.S. universities with Spearman's $\rho = 0.87$
 	}
@@
 The embedding space captures prestige hierarchies that can be used to reconstruct academic rankings. 
-We derive a ranking using the SemAxis prestige axis in Fig.~\ref{fig:semaxis}a and compare them to traditional university rankings.
+We derive a ranking for universities using the SemAxis prestige axis in Fig.~\ref{fig:semaxis}a and compare them to traditional university rankings.
 The SemAxis ranking is defined from the position of organizations along the prestige axis, with the top-ranked being the furthest towards the high-ranked end of the axis.
-We find that the SemAxis ranking is correlated with the Times ranking (Spearman's $\rho = 0.73$, Fig.~\ref{fig:semaxis}b).
+We find that the SemAxis ranking is correlated with the Times ranking (Spearman's $\rho = 0.73$, Fig.~\ref{fig:semaxis}e).
 The strongest outliers that were ranked more highly in the Times Ranking than the SemAxis ranking tend to be large state universities such as Arizona State University and  University of Florida;
@@
 SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities are significantly correlated with the Times Ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
-For reference, the SemAxis-derived ranking achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking~\autocite{waltman2012leidenrankings}, a common and bibliometrically-informed university ranking (Spearman's $\rho = 0.87$, Fig.~\ref{fig:supp:times_vs_leiden}).
+For reference, the SemAxis-derived ranking achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking~\autocite{waltman2012leidenrankings}, a common and bibliometrically-informed university ranking (Spearman's $\rho = 0.87$, Fig.~\ref{fig:semaxis}f).
 This suggests that the organization embedding captures the latent prestige hierarchy inherent to academic mobility, even without providing any explicit information on prestige, with a high degree of resolution and reliability~\autocite{deville2014career, clauset2015hierarchy}.
@@
 %
-\begin{figure}[hp!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/SemAxis/times_leiden_compare.pdf}
-	\caption{
-		\textbf{Correlation between Times and Leiden Ranking.}
-		Comparison between the Times and Leiden rankings of universities.
-		Here, the Leiden Ranking is operationalized as the mean normalized fractional citation impact for each university~\autocite{waltman2012leidenrankings}. 
-	  	PCC details the estimate from the Spearman correlation between the two rankings.
-	}
-	\label{fig:supp:times_vs_leiden}
-\end{figure}
+%\begin{figure}[hp!]
+%	\centering
+%	\includegraphics[width=\textwidth]{\figdir/SemAxis/times_leiden_compare.pdf}
+%	\caption{
+%		\textbf{Correlation between Times and Leiden Ranking.}
+%		Comparison between the Times and Leiden rankings of universities.
+%		Here, the Leiden Ranking is operationalized as the mean normalized fractional citation impact for each university~\autocite{waltman2012leidenrankings}. 
+%	  	PCC details the estimate from the Spearman correlation between the two rankings.
+%	}
+%	\label{fig:supp:times_vs_leiden}
+%\end{figure}
 
@@
 %
-\begin{figure}[hp!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_sectors_fig.pdf}
-	\caption{
-		\textbf{Geography and prestige SemAxis in U.S. by Sector.}
-		SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S.
+%\begin{figure}[hp!]
+%	\centering
+%	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_sectors_fig.pdf}
+%	\caption{
+%		\textbf{Geography and prestige SemAxis in U.S. by Sector.}
+%		SemAxis projection along two axes, comparing California to Massachusetts universities (left to r%ight), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 %Times Higher Education ranking of U.S.
 Universities (bottom to top).
-		Points correspond to organizations labeled as Government (\textbf{a}), Institute (\textbf{b}), and Teaching (\textbf{c}), corresponding to government organizations, research institutes, and teaching organizations, respectively.
-		Grey points correspond to all U.S. universities.
-	    	Full organization names listed in Table~\ref{table:supp:orglabels}.
-	}
-	\label{fig:supp:semaxis_sectors}
-\end{figure}
+%		Points correspond to organizations labeled as Government (\textbf{a}), Institute (\textbf{b}), and %Teaching (\textbf{c}), corresponding to government organizations, research institutes, and teaching o%rganizations, respectively.
+%		Grey points correspond to all U.S. universities.
+%	    	Full organization names listed in Table~\ref{table:supp:orglabels}.
+%	}
+%	\label{fig:supp:semaxis_sectors}
+%\end{figure}
 

### 2020-07-20 workflow/scripts/Plot2DSemAxis.R

@@ -244,14 +244,14 @@ if (opt$overall) {
     plotlabel <- opt$sector
   }
 
-  plot <- plot +
-    annotate(geom = "text",
-             x = 0.28,
-             y = -0.4,
-             label = plotlabel,
-             size = 7,
-             fontface = 2
-           )
+  # plot <- plot +
+  #   annotate(geom = "text",
+  #            x = 0.28,
+  #            y = -0.4,
+  #            label = plotlabel,
+  #            size = 7,
+  #            fontface = 2
+  #          )
 }
 
 # Save the plot

### 2020-07-20 paper/current/main.tex
edit and add s_i factors plot

@@
 %
+% Figure - s_i by factors
+%
+\begin{figure}[hp!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/Math/si_factors.pdf}
+	\caption{
+		\textbf{Factors relating to $s_{i}$ among universities}
+		Correlation between various organization-level factors for U.S. universities and the value $s_{i}$.
+		Dots correspond to organizations.	
+		The red line is the line of  the best fit. 
+		Red text is the regression estimate.
+		Number of authors is the average annual count of unique mobile and non-mobile authors.
+		Rankings are derived from the Times Ranking of World Universities, and the Leiden Rankings of Universities. 
+		Remaining variables come from the Carnegie Classification of Higher Education Institutions.
+		The factors that best explain $s_i$ are the number of authors, the rank, the amount of Science and Engineering (S\&E) funding, and the number of doctorates granted. 
+	}
+	\label{fig:supp:semaxis_states}
+\end{figure}
+
+%
 % Figure - SemAxis By Sector

### 2020-07-20 workflow/scripts/PlotFactors/PlotContinuousFactorsByMeta.R

@@ -30,6 +30,8 @@ option_list = list(
               help="Path to file containing carnegie classification"),
   make_option(c("--unicw"), action="store", default=NA, type='character',
               help="Path to file containing university crosswalk"),
+  make_option(c("--times"), action="store", default=NA, type='character',
+              help="Path to file containing Times information"),
   make_option(c("--leiden"), action="store", default=NA, type='character',
               help="Path to file containing leiden information"),
   make_option(c("--sizes"), action="store", default=NA, type='character',
@@ -56,6 +58,8 @@ cw <- read_csv(opt$unicw, col_types = cols())
 # Load the leiden rankings
 leiden <- read_csv(opt$leiden, col_types = cols())
 
+times <- read_csv(opt$times, col_types = cols())
+
 # Load the organization sizes
 inst_sizes = readr::read_delim(opt$sizes, delim = "\t", col_types = cols()) %>%
   group_by(cwts_org_no) %>%
@@ -69,11 +73,13 @@ factors.ext <- factors %>%
   left_join(cw, by = "cwts_org_no") %>%
   left_join(carnegie, by = c("cc_id" = "UNITID")) %>%
   left_join(leiden, by = "cwts_org_no") %>%
+  left_join(times, by = "cwts_org_no") %>%
   left_join(inst_sizes, by = "cwts_org_no") %>%
   # Construct the factors
   mutate(
     # Log transform some of the main continuous variables
     s_i = log10(s_i),
+    pubs = log10(impact_frac_p),
     gravity_potential = log10(gravity_potential),
     count = log10(count),
     research = recode(BASIC2018, `15` = "R1", `16` = "R2", `17` = "R3", .default = "Other"),
@@ -85,21 +91,26 @@ factors.ext <- factors %>%
   ) %>%
   arrange(desc(impact_frac_mncs)) %>%
   mutate(
-    leiden_rank = row_number()
+    leiden_rank = ifelse(is.na(impact_frac_mncs), NA, row_number())
+  ) %>%
+  arrange(desc(total_score)) %>%
+  mutate(
+    times_rank = ifelse(is.na(total_score), NA, row_number())
   )
 
 if (opt$toplot == "pull") {
   var.yaxis <- "s_i"
-  varname.yaxis <- "Log10(pulling force)"
+  varname.yaxis <- latex2exp::TeX("$\\log_{10}(s_{i})")
[…]

### 2020-07-21 notebooks/embedding_boomerang_plots.rmd
update text with new figure

---
title: "Mobility Boomerang Plots"
output: html_notebook
---

```{r}
library(tidyverse)
library(readr)

df <- read_csv("/Users/dakotamurray/Desktop/l2-norm_vs_size.csv")
meta <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t")
types <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/org_types.csv")

country <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/country_metadata.csv")
leiden <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/leiden_ranking.csv")
times <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/times_ranking.csv")
head(df)

```

```{r}

df %>%
  left_join(meta, by = c("name" = "full_name")) %>%
  left_join(leiden, by = c("cwts_org_no"))

```

```{r}
plotdata <- df %>%
  filter(country == "United States") %>%
  left_join(types) %>%
  filter(org_type_simplified %in% c("University", "Government", "Institute", "Teaching")) %>%
  mutate(
    org_type_simplified = factor(org_type_simplified,
                                 levels = c("University", "Teaching", "Institute", "Government"))
  )

plotdata %>%
  ggplot(aes(x = size, y = `l2-norm`, color = org_type_simplified, shape = org_type_simplified, label = name)) +
  geom_point() +
  scale_x_log10(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
  scale_shape_manual(values = c(16, 1, 1, 1)) +
  #scale_color_manual(values = c(""))
  scale_color_manual(values = c("#2c3e50", "#c0392b", "#8e44ad", "#27ae60")) +
  theme_minimal() +
  theme(
    text = element_text(size = 12, family = "Helvetica"),
    panel.grid.minor = element_blank()
  ) +
  annotation_logticks(sides = "b") +
  xlab("Organization size") +
  ylab("L2 Norm")

plotly::ggplotly()
```

```{r}

labels <- c("Harvard University", "University of Alaska, Fairbanks", "Reykjavik University",
            "University of Oxford", "Princeton University", "Shanghai Jiao Tong University", "Novosibirsk State University", "University of Louisville",  "University of Tennessee, Knoxville", "Barry University", "Appalachian State University", "University of Michigan-Flint", "New York Medical College")

plotdata <- df %>%
  filter(country == "United States") %>%
  filter(org_type == "University") %>%
  left_join(meta, by = c("name" = "full_name")) %>%
  #left_join(leiden, by = c("cwts_org_no"))
  left_join(times, by = c("cwts_org_no")) %>%
  arrange(desc(total_score)) %>%
  mutate(
    rank = ifelse(!is.na(total_score), row_number(), NA)
  )

set.seed(117)
plotlabs <- plotdata %>%
  filter(name %in% labels) %>%
  mutate(
    label = gsub('University', 'Univ', name),
    label = gsub('(.{1,24})(\\s|$)', '\\1\n', label),
    label = trimws(label)
  )

plot <- plotdata %>%
  ggplot(aes(x = size, y = `l2-norm`, color = rank, shape = is.na(rank), label = name)) +
  geom_point() +
  scale_x_log10(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
  scale_y_continuous(
    limits = c(0, 7),
    breaks = c(2, 4, 6)
  ) +
  viridis::scale_color_viridis(
    name = "Times Rank", 
    option = "C",
    breaks = c(1, 50, 100)) +
  scale_shape_manual(values = c(16, 1)) +
  #ggrepel::geom_label_repel(
  #  data = plotlabs,
  #  aes(label = label),
  #  color = "black",
  #  force = 50,
  #  min.segment.length = 0.1,
  #  alpha = 0.9,
  #  size = 3.5
  #) +
  guides(shape = F) +
  theme_minimal() +
  annotate(geom = "label", x = 1.5e4, y = 3.5, label = "Harvard", size = 3.5) +
  annotate(geom = "label", x = 1.6e3, y = 3.69, label = "Princeton", size = 3.5) +
  annotate(geom = "label", x = 8.5e3, y = 5.9, label = "Univ Tennessee\nKnoxville", size = 3.5) +
  annotate(geom = "label", x = 4.9e2, y = 2.15, label = "Univ Alaska\nFairbanks", size = 3.5) +
  annotate(geom = "label", x = 4e2, y = 5.75, label = "NY Medical College", size = 3.5) +
  annotate(geom = "label", x = 2e1, y = 4.6, label = "Univ Michigan\nFlint", size = 3.4) +
  annotate(geom = "label", x = 6.4e1, y = 2.48, label = "Barry University", size = 3.5) +
  theme(
    text = element_text(family = "Helvetica", size = 12),
    axis.title.x = element_text(angle = 0, size = 14, face = "bold", vjust = 0.5),
    axis.title.x.top = element_text(angle = 0, size = 14, face = "bold", vjust = 0.5),
    axis.text.x.top = element_blank(),
    axis.title.y = element_text(angle = 90, size = 14, face = "bold"),
    axis.title.y.right = element_text(angle = 90, size = 14, face = "bold"),
    axis.text.y.right = element_blank(),
    legend.text = element_text(size = 12),
    legend.position = c(0.85, 0.20),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    axis.line = element_line(color="black", size = 0.3),
    legend.box.background = element_rect(color="black", size=0.1, fill = "white")
  ) +
  annotation_logticks(sides = "b") +
  xlab("# Researchers") +
  ylab("L2 Norm")

plot

ggsave("/Users/dakotamurray/Dropbox/SME-dropbox/Figures/boomerang_ranking_times.pdf", plot, width = 6, height = 6)
```

```{r}
plot <- df %>%
  mutate(
    highlight = ifelse(country %in% c("China", "United States", "Germany"), country, "Other"),
    highlight = factor(highlight, levels = c("United States", "China", "Germany", "Other"))
  ) %>%
  ggplot(aes(x = size, y = `l2-norm`, label = name, alpha = highlight, shape = highlight, color = highlight)) +
  geom_point(alpha = 0.5) +
  stat_smooth(
    method = "loess",
    se = F
  ) +
  scale_shape_manual(values = c(16, 16, 16, 16, 16,  1)) +
  scale_color_manual(values = c("#66c2a5", "#fc8d62", "#8da0cb", "#e78ac3", "#a6d854", "grey")) +
  scale_alpha_manual(values = c(1, 1, 1, 1, 1,  0.6)) +
  scale_x_log10(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
  scale_y_continuous(
    limits = c(0, 7),
    breaks = c(2, 4, 6)
  ) +
  guides(shape = F) +
  theme_minimal() +
  theme(
    text = element_text(family = "Helvetica", size = 12),
    axis.title.x = element_text(angle = 0, size = 14, face = "bold", vjust = 0.5),
    axis.title.x.top = element_text(angle = 0, size = 14, face = "bold", vjust = 0.5),
    axis.text.x.top = element_blank(),
    axis.title.y = element_text(angle = 90, size = 14, face = "bold"),
    axis.title.y.right = element_text(angle = 90, size = 14, face = "bold"),
    axis.text.y.right = element_blank(),
    legend.text = element_text(size = 10),
    legend.position = c(0.14, 0.82),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    legend.title = element_blank(),
    axis.line = element_line(color="black", size = 0.3),
    legend.box.background = element_rect(color="black", size=0.1, fill = "white")
  ) +
  annotation_logticks(sides = "b") +
  xlab("# Researchers") +
  ylab("L2 Norm")

plot

ggsave("/Users/dakotamurray/Dropbox/SME-dropbox/Figures/boomerang_global.pdf", plot, width = 6, height = 6)
```

```{r}
ratio <- read_csv("/Users/dakotamurray/Desktop/data_with_ratio.csv")
plot <- ratio %>%
  mutate(ratio = log10(ratio)) %>%
  ggplot(aes(x = ratio, y = `l2-norm`)) +
  geom_hex(
    aes(fill = stat(log10(count)))
  ) +
  # Draw a regression line
  stat_smooth(method = "lm",
              formula = y ~ x,
              color = "#c0392b",
              alpha = 0.6,
              se = T,
              level = 0.99,
              size = 1.5,
              fullrange = T)  +
  # Add the r-squared coefficient to the plot
  ggpmisc::stat_poly_eq(formula = y ~ x,
                        geom = "text_npc",
                        aes(label = paste(..rr.label.., sep = "~~~")),
                        parse=TRUE,
                        label.x.npc = 0.95,
                        label.y.npc = 0.96,
                        rr.digits = 2,
                        size = 7
  ) +
  scale_fill_gradientn(colours=c("white", "#7f8c8d"),
                         name = "Freq",
                         breaks = c(0, 1, 2),
                         limits = c(0, 2),
                         labels = function(x) { parse(text=paste0("10^", x)) },
                         na.value=NA
    ) +
  theme_minimal() +
  theme(
    text = element_text(family = "Helvetica", size = 12),
    axis.title.x = element_text(angle = 0, size = 14, face = "bold", vjust = 0.5),
    axis.title.x.top = element_text(angle = 0, size = 14, face = "bold", vjust = 0.5),
    axis.text.x.top = element_blank(),
    axis.title.y = element_text(angle = 90, size = 14, face = "bold"),
    axis.title.y.right = element_text(angle = 90, size = 14, face = "bold"),
    axis.text.y.right = element_blank(),
    legend.text = element_text(size = 12),
    #legend.position = c(0.16, 0.35),
    legend.position = "right",
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    panel.border = element_rect(size = 0.5, color = "black", fill = NA),
    legend.title = element_text(face = "bold"),
    legend.box.background = element_rect(color="black", size=0.1, fill = "white")
  ) +
  annotation_logticks(sides = "b") +
  xlab("Expexted reach") +
  ylab("L2 Norm")

plot 
ggsave("/Users/dakotamurray/Dropbox/SME-dropbox/Figures/ratio_l2.png", plot, width = 4, height = 3)
```

```{r}
leiden

```

### 2020-07-21 paper/current/main.tex
update text with new figure

@@
 This suggests that the organization embedding captures the latent prestige hierarchy inherent to academic mobility, even without providing any explicit information on prestige, with a high degree of resolution and reliability~\autocite{deville2014career, clauset2015hierarchy}.
+
+%
+% Figure - SemAxis results
+%
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/Math/boomerang.pdf}
+	\caption{
+		\textbf{Lengh of organization vectors captures the reach of organizations.}
+		\textbf{a} L2 norm of organization vectors compared to their number of researchers for U.S. universities.
+		The L2 norm corresponds to the distance to the origin of the vector space.
+		Color indicates the rank of the university from the Times ranking, with 1 being the highest rank university.
+		Uncolored points are universities without a times rank.
+		A "boomerang"-shape emerges, wherein larger universities are more distant from the origin (large L2 norm), however the more prestigious the university, the closer it is to the origin (small L2 norm).
+		\textbf{b} This boomerang pattern repeats globally for all organizations across all countries, shown for the United States, Germany, China, and others (loess regression line shown). 
+		The L2 norm is correlated weakly with the expected reach or organizations, that is, the number of total flows an organization has with others given its size ($R^{2} = 0.17$, \textbf{inset});
+		The red line is the line of best fit.
+	}
+	\label{fig:semaxis}
+\end{figure}
 

### 2020-07-21 notebooks/embedding_boomerang_plots.rmd
other small tweaks to figure

@@
     method = "loess",
+    size = 1.25,
     se = F
   ) +
-  scale_shape_manual(values = c(16, 16, 16, 16, 16,  1)) +
-  scale_color_manual(values = c("#66c2a5", "#fc8d62", "#8da0cb", "#e78ac3", "#a6d854", "grey")) +
-  scale_alpha_manual(values = c(1, 1, 1, 1, 1,  0.6)) +
+  scale_shape_manual(values = c(16, 16, 16, 1)) +
+  scale_color_manual(values = c("#66c2a5", "#fc8d62", "#8da0cb", "darkgrey")) +
+  scale_fill_manual(values = c("#66c2a5", "#fc8d62", "#8da0cb", "grey")) +
+  scale_alpha_manual(values = c(1, 1, 1,  0.6)) +
   scale_x_log10(

### 2020-07-21 paper/current/main.tex
update figure caption

--- 2020-07-20 paper/current/main.tex
@@
 This suggests that the organization embedding captures the latent prestige hierarchy inherent to academic mobility, even without providing any explicit information on prestige, with a high degree of resolution and reliability~\autocite{deville2014career, clauset2015hierarchy}.
+
+%
+% Figure - SemAxis results
+%
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/Math/boomerang.pdf}
+	\caption{
+		\textbf{Length of organization vectors captures the connection diversity of organizations.}
+		\textbf{a} L2 norm of organization vectors compared to their number of researchers for U.S. universities.
+		The L2 norm corresponds to the distance from the origin of the vector space.
+		Color indicates the rank of the university from the Times ranking, with 1 being the highest rank university.
+		Uncolored points are universities not listed on a times rank.
+		A "boomerang"-shape emerges, wherein larger universities tend to more distant from the origin (large L2 norm), however the more prestigious the university, the closer it is to the origin (small L2 norm).
+		\textbf{b} This boomerang pattern repeats globally for all organizations across all countries, shown for the United States, Germany, China, and others (loess regression line shown). 
+		The L2 norm is correlated weakly with the number of connection divided by the number of researchers in organization, which can be interpreted diversity of the connection compared to their size ($R^{2} = 0.17$, \textbf{inset}).
+		The red line is the line of the best fit.
+	}
+	\label{fig:semaxis}
+\end{figure}
 

### 2020-07-22 paper/current/main.tex
update caption

@@
 	\caption{
-		\textbf{Length of organization vectors captures the connection diversity of organizations.}
+		\textbf{Length of organization vectors captures a connection diversity of organizations.}
 		\textbf{a} L2 norm of organization vectors compared to their number of researchers for U.S. universities.
@@
 		\textbf{b} This boomerang pattern repeats globally for all organizations across all countries, shown for the United States, Germany, China, and others (loess regression line shown). 
-		The L2 norm is correlated weakly with the number of connection divided by the number of researchers in organization, which can be interpreted diversity of the connection compared to their size ($R^{2} = 0.17$, \textbf{inset}).
+		The L2 norm is correlated weakly with the number of connections divided by the number of researchers in the organization, which can be interpreted diversity of the connection compared to their size ($R^{2} = 0.17$, \textbf{inset}).
 		The red line is the line of the best fit.
+
 	}

### 2020-07-22 paper/current/main.tex
add additional para

--- 2020-07-21 paper/current/main.tex
@@
 
+Also, we take one step further and find that the length of the organization vector, distance from the origin of the vector space, provides additional insight into the characteristics of the organization.
+The length of the vector tends to increase proportion to the number of unique researchers in the organization and it decreases after a certain point, yield ``boomerang" -shape curve (Fig.~\ref{fig:length}a).
+Almost the prestigious university vector is close to the origin compared to the number of the researcher and this pattern is consistent for all organizations (Fig.~\ref{fig:length}b).
+This pattern also observed in natural language suggesting the length of the vector represents the word significance~\autocite{schakel2015measuring}.
+
+We find that the length of the vector captures the connection diversity of the organization compare to its size.
+The length of the vector is correlated with the number of connections to other organizations divided by the number of researchers, which can be interpreted as connection diversity compared to their size.
+This suggests that researchers in the organization with a long vector have less freedom to move to other organizations compare to their size while researchers in the organization with short vector have more freedom to move.
+This observation can also be related to the organization's strategy.
+Most prestigious universities have policies that can enhance their collaboration with other organizations such as visiting program, giving additional affiliation to the researcher.
+We also show a correlation between the length of the vector and various organization-level factors such as diverse rankings,  amount of the funding, number of doctorates granted (Fig.~\ref{fig:supp:length_vs_metaInfo}), indicating the length of the organization vector capture diverse characteristics of the organization.
+
 %
@@
 	\caption{
-		\textbf{Length of organization vectors captures the connection diversity of organizations.}
-		\textbf{a} L2 norm of organization vectors compared to their number of researchers for U.S. universities.
+		\textbf{Length of organization vectors captures connection diversity of organizations.}
+		\textbf{a.} L2 norm of organization vectors compared to their number of researchers for U.S. universities.
 		The L2 norm corresponds to the distance from the origin of the vector space.
@@
 		A "boomerang"-shape emerges, wherein larger universities tend to more distant from the origin (large L2 norm), however the more prestigious the university, the closer it is to the origin (small L2 norm).
-		\textbf{b} This boomerang pattern repeats globally for all organizations across all countries, shown for the United States, Germany, China, and others (loess regression line shown). 
+		\textbf{b.} This boomerang pattern repeats globally for all organizations across all countries, shown for the United States, Germany, China, and others (loess regression line shown). 
 		The L2 norm is correlated weakly with the number of connection divided by the number of researchers in organization, which can be interpreted diversity of the connection compared to their size ($R^{2} = 0.17$, \textbf{inset}).
@@
 	}
-	\label{fig:semaxis}
+	\label{fig:length}
 \end{figure}
@@
 However, due to their size, the USA, accounted for nearly 40 percent of all mobile authors worldwide (Fig.~\ref{fig:supp:descriptives}a), with 10 countries accounting for 80 percent of all mobility (Fig.~\ref{fig:supp:descriptives}b).
-The countries with the highest proportion of mobile scientists are France, Qatar, the United States, and Iraq, whereas those with the lowest are Jamaica, Serbia, Bosnia \& Herzegovina, and North Macedonia\ref{fig:supp:descriptives}.c).
+The countries with the highest proportion of mobile scientists are France, Qatar, the United States, and Iraq, whereas those with the lowest are Jamaica, Serbia, Bosnia \& Herzegovina, and North Macedonia Fig.~\ref{fig:supp:descriptives}.c).
 In most cases, countries with a high degree of inter-organization mobility also have a high degree of international mobility, indicating a high proportion of their total mobility being international (Fig.~\ref{fig:supp:descriptives}.d);
@@
 	}
-	\label{fig:supp:semaxis_states}
+	\label{fig:supp:length_vs_metaInfo}
 \end{figure}

### 2020-07-22 paper/current/main.tex

@@
 We find that the length of the vector captures the connection diversity of the organization compare to its size.
-The length of the vector is correlated with the number of connections to other organizations divided by the number of researchers, which can be interpreted as connection diversity compared to their size.
+The length of the vector is correlated with the number of connections to other organizations divided by the number of researchers, which can be interpreted as connection diversity compared to their size (Fig.~\ref{fig:length}b, inset).
 This suggests that researchers in the organization with a long vector have less freedom to move to other organizations compare to their size while researchers in the organization with short vector have more freedom to move.

### 2020-07-22 workflow/scripts/calculate_word2vec_decomposition.py
update factor plots

@@ -47,6 +47,8 @@ out_emb = {word: model.syn1neg[index] for index, word in enumerate(vocab_list_)}
 in_si = [np.exp(np.power(np.linalg.norm(embedding_dict[vocab]), 2) / 2) for vocab in vocab_list]
 out_si = [np.exp(np.power(np.linalg.norm(out_emb[vocab]), 2) / 2) for vocab in vocab_list]
 
+l2norm = [np.linalg.norm(embedding_dict[vocab]) for vocab in vocab_list]
+
 # Calculate the gravitation potential, defined as the product of the
 # pulling force and the distance between the embedding vectors
 matrix_for_potential = np.zeros((len(vocab_list), len(vocab_list)))
@@ -77,6 +79,7 @@ partition_function_array = dot_product_matrix.sum(axis=1)
 # construct a dataframe from the w2v factors
 df = pd.DataFrame({
     'cwts_org_no': list(vocab_list),
+    'l2norm': list(l2norm),
     'gravity_potential': list(negative_gravity_potential),
     's_i': list(in_si),
     's_j': list(out_si),

### 2020-07-22 paper/current/main.tex
update text relating to vector length plot

--- 2020-07-22 paper/current/main.tex
@@
 
+What is it about the organization embedding that captures prestige so effectively?
+We find that the length of organization vectors---that is, the distance from the origin of the vector space---provides provides insight into the characteristics of organizations. 
+Up to a point, the length of U.S. organization's vectors tends to increase proportional to its number of researchers (both mobile and non-mobile) who published with that organization;
+these organizations are primarily teaching-focused institutions, agencies, and hospitals that either are not ranked or have a low ranking. 
+However, at around 1,000 researchers, the length of the vector decreases with increase in the number of researchers;
+organizations here are primarily research-intensive and prestigious universities with higher rankings, research outputs, R\&D funding, and doctoral students (Fig.~\ref{fig:supp:length_vs_metaInfo}).
+This same convex-curve repeats irrespective of country, such as China and Germany, though the curve may be shifted based on the typical size and vector length of their organizations (Fig.~\ref{fig:length}b).
+
+This pattern has been observed in applications of neural embedding to natural language, wherein the length of word vectors were found to represent word "significance"~\autocite{schakel2015measuring
+Here, interpret the vector length instead as a measure of an organization's connectedness to other organizations given its size, where a connection is defined as a non-zero flow between organizations.
+for example, organizations with a small L2 norm tend to also have a lower number of connections given their size (Fig.~\ref{fig:length}b, inset, $R^{2} = 0.17$). 
+Large and prestigious universities can be considered as having a shorter vector length than expected given their size, reflecting their ability to attract researchers from many places, to place graduates in positions around the world, and the capacity to encourage mobility by offering temporary and visiting researcher positions.
+At the national level, the relative position of the convex-curves can reveal characteristics of their scientific organizations—for example, compared to the United States, Chinese organizations have a longer typical vector length (Fig.~\ref{fig:length}b) reflecting lower overall connectedness in the embedding space.
+Prestige is a key component academic mobility—by encoding information relating to prestige, neural embeddings offer a means of better representing functional distance between organizations and capturing the global landscape of mobility.
+
 %
@@
 	\caption{
-		\textbf{Length of organization vectors captures a connection diversity of organizations.}
-		\textbf{a} L2 norm of organization vectors compared to their number of researchers for U.S. universities.
+		\textbf{Length of organization vectors captures connection diversity of organizations.}
+		\textbf{a.} L2 norm of organization vectors compared to their number of researchers for U.S. universities.
 		The L2 norm corresponds to the distance from the origin of the vector space.
-		Color indicates the rank of the university from the Times ranking, with 1 being the highest rank university.
-		Uncolored points are universities not listed on a times rank.
-		A "boomerang"-shape emerges, wherein larger universities tend to more distant from the origin (large L2 norm), however the more prestigious the university, the closer it is to the origin (small L2 norm).
-		\textbf{b} This boomerang pattern repeats globally for all organizations across all countries, shown for the United States, Germany, China, and others (loess regression line shown). 
-		The L2 norm is correlated weakly with the number of connections divided by the number of researchers in the organization, which can be interpreted diversity of the connection compared to their size ($R^{2} = 0.17$, \textbf{inset}).
+		Color indicates the rank of the university from the Times ranking, with 1 being the highest ranked university.
+		Uncolored points are universities not listed on a Times ranking.
+		A convex-shape emerges, wherein larger universities tend to more distant from the origin (large L2 norm), however the more prestigious the university, the closer it is to the origin (small L2 norm).
+		\textbf{b.} This convex pattern repeats globally for all organizations across all countries, shown for the United States, Germany, China, and others (loess regression line shown). 
+		The L2 norm is correlated weakly with the number of connection divided by the number of researchers in organization, which can be interpreted diversity of the connection compared to their size ($R^{2} = 0.17$, \textbf{inset}).
 		The red line is the line of the best fit.
-
-	}
-	\label{fig:semaxis}
+	}
+	\label{fig:length}
 \end{figure}
@@
 %
-% Figure - s_i by factors
-%
-\begin{figure}[hp!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/Math/si_factors.pdf}
-	\caption{
-		\textbf{Factors relating to $s_{i}$ among universities}
-		Correlation between various organization-level factors for U.S. universities and the value $s_{i}$.
-		Dots correspond to organizations.	
-		The red line is the line of  the best fit. 
-		Red text is the regression estimate.
-		Number of authors is the average annual count of unique mobile and non-mobile authors.
-		Rankings are derived from the Times Ranking of World Universities, and the Leiden Rankings of Universities. 
-		Remaining variables come from the Carnegie Classification of Higher Education Institutions.
-		The factors that best explain $s_i$ are the number of authors, the rank, the amount of Science and Engineering (S\&E) funding, and the number of doctorates granted. 
-	}
-	\label{fig:supp:semaxis_states}
-\end{figure}
-
-%
 % Figure - SemAxis By Sector
@@
 
+%
+% Figure - length by factors
+%
+\begin{figure}[hp!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/Math/si_factors.pdf}
+	\caption{
+		\textbf{Factors relating to the L2 norm of vectors for U.S. universities}
+		Correlation between the L2 norm of organization embedding vectors of U.S. universities and characteristics of U.S. universities. 
+		Dots correspond to organizations.	
+		The red line is the line of  the best fit. 
+		Red text is the regression estimate.
+		Number of authors is the average annual count of unique mobile and non-mobile authors.
+		Rankings are derived from the Times Ranking of World Universities, and the Leiden Rankings of Universities. 
+		Remaining variables come from the Carnegie Classification of Higher Education Institutions.
+		The factors that best explain $s_i$ are the number of authors, the rank, the amount of Science and Engineering (S\&E) funding, and the number of doctorates granted. 
+	}
+	\label{fig:supp:length_vs_metaInfo}
+\end{figure}
+
 \clearpage

### 2020-07-22 paper/current/main.tex
add missing citation bracket

@@
 
-This pattern has been observed in applications of neural embedding to natural language, wherein the length of word vectors were found to represent word "significance"~\autocite{schakel2015measuring
+This pattern has been observed in applications of neural embedding to natural language, wherein the length of word vectors were found to represent word "significance"~\autocite{schakel2015measuring}
 Here, interpret the vector length instead as a measure of an organization's connectedness to other organizations given its size, where a connection is defined as a non-zero flow between organizations.

### 2020-07-22 paper/current/main.tex
updates throughout

@@
 Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity, xia2005measlesgravity, jung2008highwaygravity, barbosa2018human, curiel2018citygravity, lewer2008immigrationgravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity}, often successfully capture mobility between places using their population and the \textit{distance} between them.
-However, geographic distance is less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} where the physical distance barrier shrinks while the impact of linguistic, economic, cultural, and historical similarity increases.
-Alternative notions of functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} attempt to re-define distance by using some of the aforementioned factor~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional} but suffer from practical and theoretical challenges.
+However, geographic distance is less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} wherein the physical distance barrier shrinks while the impact of inter-related linguistic, economic, cultural, and historical similarities increases.
+Alternative notions of functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} attempt to re-define distance by using some of the aforementioned factor~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional} but are often low resolution, arbitrary, and consider only single isolated facets of mobility.
 Here, using a rich dataset of scientific mobility, we demonstrate that a data-driven neural embedding approach~\autocite{mikolov2013word2vec} can successfully encodes a functional distance between organizations and captures the latent and multi-faceted structure of scientist's mobility.
 We demonstrate that the cosine distance between organization embedding vectors, constructed using the affiliation trajectories of scientists in the Web of Science database, better explain and predict real mobility than geographic distance.
-Exploiting their unique properties, we interpret the embedding space and observe how it captures latent factors related to culture, language, and prestige of organizations at multiple levels of granularity.
-The ability to learn scalable, dense, and meaningful vector representations of mobility directly from the data can open up a new avenue of studying human mobility.
+Exploiting their unique properties, we interpret the embedding space and observe that it captures not only geographic relations between organizations, but also relations based on culture, language, and academic prestige at multiple levels of granularity.
+Also encoded in the embedding space is a universal pattern capturing the relationship between organization's size and their connectedness.
+The ability to learn scalable, dense, and meaningful high-resolution vector representations of mobility directly from the data can open up a new avenue of studying human mobility.
 
@@
 While geographic distance is still used as the basis for the most prominent models of mobility such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} model, so-called \textit{functional distances}~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional} have been proposed to learn alternative notions of distance from real-world data or \textit{a priori} relationships between geographic entities.
-Yet, limitations of the existing functional distance measure have yet to be overcome.
+Yet, functional distances are often low-resolution and rely on somewhat arbitrary decisions about what factors are most important.
+Moreover, functional distances typically only focus on one facet of mobility at a time, whereas real-world mobility is multi-faceted, influenced simultaneously by geography, language, culture, history, and economic opportunity.
+Mobility is complex, and so new approaches are needed to merge its many facets into a single high-resolution measure of functional distance.
 
@@
 This approach, originally designed for learning language models~\autocite{mikolov2013word2vec} has been used to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
-Neural embedding is also computationally efficient, scalable for large datasets, robust to noise, and can extract rich relationship between the entities through the application of simple vector arithmetic~\autocite{levy2014neural}.
+Neural embedding is also computationally efficient, scalable for large datasets, robust to noise, and can extract rich relationships between the entities through the application of simple vector arithmetic~\autocite{levy2014neural}.
 
@@
 Scientific mobility is a central aspect of the increasingly-globalized scientific system~\autocite{czaika2018globalisation, altbach2004globalization}, being strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}.
+Moreover, scientific mobility has known structure, such as the centrality of the United States and the United Kingdom, and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career} that should be captured in a representation.
 For nations and organizations hoping to win in the global competition for talent~\autocite{box2008competition}, understanding the landscape of global scientific mobility is essential. 
@@
 %
-\subsection*{Embeddings provide a functional distance between organizations}
+\subsection*{Embeddings provide both geographical and functional distance between organizations}
 
@@
 \ref{fig:clustering}b demonstrates that the region plays a major role at higher levels of the clustering process (low $r$), and language (family) explains the clustering more at the lower levels (high $r$).
-This suggests that geography, then language, are important factors contributing to the structure of international scientific mobility.
+This suggests that the embedding space captures a hierarchy of facets of mobility---at the highest level, geography defines the  embedding space, followed then by language.
 
@@
 
-Prestige hierarchies underpin the dynamics of scientific mobility~\autocite{deville2014career, clauset2015hierarchy}, but are these hierarchies captured in the embedding space, to which no explicit information on the prestige is given?
+Prestige hierarchies underpin the dynamics of scientific mobility~\autocite{deville2014career, clauset2015hierarchy}, but are these hierarchies captured in the embedding space, to which no explicit information on prestige is given?
 We test this by exploiting the geometric properties of the embedding space with SemAxis~\autocite{an2018semaxis}, an approach originally designed to characterize the semantics of words in word embeddings.
@@
 		A convex-shape emerges, wherein larger universities tend to more distant from the origin (large L2 norm), however the more prestigious the university, the closer it is to the origin (small L2 norm).
-		\textbf{b.} This convex pattern repeats globally for all organizations across all countries, shown for the United States, Germany, China, and others (loess regression line shown). 
+		\textbf{b.} This convex pattern repeats globally for all organizations across all countries, shown for the United States, Germany, China, and others,
+		The loess regression lines are shown for each selected country, and for the aggregate of remaining countries. 
 		The L2 norm is correlated weakly with the number of connection divided by the number of researchers in organization, which can be interpreted diversity of the connection compared to their size ($R^{2} = 0.17$, \textbf{inset}).
@@
 
-Neural embeddings offer a novel approach for learning an effective and robust functional distance between places based on affiliation trajectory data. 
-Here, we demonstrated how the embedding space encodes complex aspects of scientific mobility, such as global and regional geography, national similarity, and organizational prestige.
+Neural embeddings offer a novel approach for learning an effective and robust functional distance between places based on affiliation trajectory data that captures the complex and multi-faceted nature of mobility.
+Here, we demonstrated how the embedding space encodes aspects scientific mobility, such as the  global and regional geography, national shared languages, and the hierarchy of organizational prestige. 
 While scientific mobility is used as a case study, this approach can be broadly applied to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
-Moreover, this approach can be used to learn a functional distance between entities when no such analog to geographic distance exists, such as a functional distance between occupational categories based on individual's career trajectories.
-In addition to providing a functional distance that supports modeling and predicting mobility patterns, the unique structure of neural embedding also allows for a range of methodological applications.
-As we have shown, projecting the embedding space onto two dimensions using UMAP allows for the visualization of the complex structure of scientific mobility at high resolution and at multiple scales, which has implications in practice.
-Other techniques, such as SemAxis, also allow the potential to quantify abstract notions in mobility such as academic prestige, and can also be generalized to other abstract axes.
-Neural embedding opens the door for new approaches for representing and understanding patterns of global human mobility.
+Moreover, this approach can be used to learn a functional distance between entities for which no geographic analog exists, such as between occupational categories based on individual's career trajectories.
+In addition to providing a functional distance that supports modeling and predicting mobility patterns, the unique structure of the neural embedding space is amenable to a range of unique applications for studying mobility.
+As we have shown, projecting the embedding space onto two dimensions using UMAP~\autocite{mcinnes2018umap} allows for the visualization of the complex structure of scientific mobility at high resolution and at multiple scales, providing the largest and most detailed map of global scientific mobility to date.
+Other techniques, such as SemAxis~\autocite{an2018semaxis}, also allow the potential to quantify abstract notions in mobility such as academic prestige, and can also be generalized to other abstract axes.
+Investigation of the structure of the embedding space, such as the vector length, reveals unique and universal patterns based on organization's size and connectedness, and could contribute to deeper understandings of scientific mobility.
+Neural embedding opens the door for new approaches to represent and study scientific mobility, and also mobility more generally.
 
@@
 and U.K.
-brought by Brexit and the Trump administration~\autocite{chinchilla2018travelban}.
+brought by Trump administration and enacted as part of Brexit~\autocite{chinchilla2018travelban}.
 Other nations, such as China, are growing into major scientific powers and attractors of talent~\autocite{tollefson2018china, cao2020returning}.
 Global crises such as COVID19 pandemic threaten drastic change to travel and migration by tightening borders and halting travel. 
-Now, more than ever, new tools and approaches are needed to understanding human mobility in order to inform sensible, effective, and humane Immigration and Science and Technology policy.
+The paradigm of global mobility is changing, and now, more than ever, new tools and approaches are needed to understanding human mobility in order to inform sensible, effective, and humane Immigration and Science and Technology policy.
 

### 2020-07-22 paper/current/main.tex
minor typo

@@
 What is it about the organization embedding that captures prestige so effectively?
-We find that the length of organization vectors---that is, the distance from the origin of the vector space---provides provides insight into the characteristics of organizations. 
+We find that the length of organization vectors---that is, the distance from the origin of the vector space---provides insight into the characteristics of organizations. 
 Up to a point, the length of U.S. organization's vectors tends to increase proportional to its number of researchers (both mobile and non-mobile) who published with that organization;
 these organizations are primarily teaching-focused institutions, agencies, and hospitals that either are not ranked or have a low ranking. 
-However, at around 1,000 researchers, the length of the vector decreases with increase in the number of researchers;
+However, at around 1,000 researchers, the length of the vector decreases with increment in the number of researchers;
 organizations here are primarily research-intensive and prestigious universities with higher rankings, research outputs, R\&D funding, and doctoral students (Fig.~\ref{fig:supp:length_vs_metaInfo}).
-This same convex-curve repeats irrespective of country, such as China and Germany, though the curve may be shifted based on the typical size and vector length of their organizations (Fig.~\ref{fig:length}b).
-
-This pattern has been observed in applications of neural embedding to natural language, wherein the length of word vectors were found to represent word "significance"~\autocite{schakel2015measuring}
+This same convex-curve repeats irrespective of countries, such as China and Germany, though the curve may be shifted based on the typical size and vector length of their organizations (Fig.~\ref{fig:length}b).
+
+This pattern has been observed in applications of neural embedding to natural language, wherein the length of word vectors was found to represent the word "significance"~\autocite{schakel2015measuring}
 Here, interpret the vector length instead as a measure of an organization's connectedness to other organizations given its size, where a connection is defined as a non-zero flow between organizations.
@@
 At the national level, the relative position of the convex-curves can reveal characteristics of their scientific organizations—for example, compared to the United States, Chinese organizations have a longer typical vector length (Fig.~\ref{fig:length}b) reflecting lower overall connectedness in the embedding space.
-Prestige is a key component academic mobility—by encoding information relating to prestige, neural embeddings offer a means of better representing functional distance between organizations and capturing the global landscape of mobility.
+Prestige is a key component of academic mobility—by encoding information relating to prestige, neural embeddings offer a means of better representing the functional distance between organizations and capturing the global landscape of mobility.
 

### 2020-07-22 paper/current/main.tex
add_average_length_in_paper

@@
 What is it about the organization embedding that captures prestige so effectively?
-We find that the length of organization vectors---that is, the distance from the origin of the vector space---provides insight into the characteristics of organizations. 
+We find that the length of organization vectors--- the distance from the origin of the vector space---provides insight into the characteristics of organizations. 
 Up to a point, the length of U.S. organization's vectors tends to increase proportional to its number of researchers (both mobile and non-mobile) who published with that organization;
@@
 
-This pattern has been observed in applications of neural embedding to natural language, wherein the length of word vectors was found to represent the word "significance"~\autocite{schakel2015measuring}
+This pattern has been observed in applications of neural embedding on natural language, wherein the length of word vectors was found to represent the word "significance"~\autocite{schakel2015measuring}
 Here, interpret the vector length instead as a measure of an organization's connectedness to other organizations given its size, where a connection is defined as a non-zero flow between organizations.
@@
 Large and prestigious universities can be considered as having a shorter vector length than expected given their size, reflecting their ability to attract researchers from many places, to place graduates in positions around the world, and the capacity to encourage mobility by offering temporary and visiting researcher positions.
-At the national level, the relative position of the convex-curves can reveal characteristics of their scientific organizations—for example, compared to the United States, Chinese organizations have a longer typical vector length (Fig.~\ref{fig:length}b) reflecting lower overall connectedness in the embedding space.
+At the national level, the relative position of the convex-curves can reveal characteristics of their scientific organizations—for example, Chinese organizations have a longer average and typical vector length ($\overline{l}=4.81 $, Fig.~\ref{fig:length}b) compared to organizations in United States ($\overline{l}=4.21$), reflecting lower overall connectedness in the embedding space.
 Prestige is a key component of academic mobility—by encoding information relating to prestige, neural embeddings offer a means of better representing the functional distance between organizations and capturing the global landscape of mobility.

### 2020-07-22 paper/current/main.tex
typo

@@
 Here, we propose a neural embedding model that uses real-world mobility trajectories to encode the complex landscape of global mobility into a dense, continuous, and meaningful vector-space representation, from which a \textit{functional distance} between places can be derived.
-This approach, originally designed for learning language models~\autocite{mikolov2013word2vec} has been used to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
+This approach, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been used to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
 Neural embedding is also computationally efficient, scalable for large datasets, robust to noise, and can extract rich relationships between the entities through the application of simple vector arithmetic~\autocite{levy2014neural}.
@@
 Large and prestigious universities can be considered as having a shorter vector length than expected given their size, reflecting their ability to attract researchers from many places, to place graduates in positions around the world, and the capacity to encourage mobility by offering temporary and visiting researcher positions.
-At the national level, the relative position of the convex-curves can reveal characteristics of their scientific organizations—for example, Chinese organizations have a longer average and typical vector length ($\overline{l}=4.81 $, Fig.~\ref{fig:length}b) compared to organizations in United States ($\overline{l}=4.21$), reflecting lower overall connectedness in the embedding space.
+At the national level, the relative position of the convex-curves can reveal characteristics of their scientific organization.
+For instance, Chinese organizations have a longer average and typical vector length ($\overline{l}=4.81 $, Fig.~\ref{fig:length}b) compared to organizations in United States ($\overline{l}=4.21$), reflecting lower overall connectedness in the embedding space.
 Prestige is a key component of academic mobility—by encoding information relating to prestige, neural embeddings offer a means of better representing the functional distance between organizations and capturing the global landscape of mobility.

### 2020-07-23 paper/current/main.tex
yy revisions: abstract

--- 2020-07-22 paper/current/main.tex
@@
 
-Human mobility and migration drives major social phenomenon such as the growth and evolution of cities~\autocite{wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity}, economies~\autocite{kaluza2010cargo, kerr2011immigration}, innovation~\autocite{kaiser2018innovation, armano2017innovation},  and scientific research~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage, morgan2018prestige, rodrigues2016mobility}.
-Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity, xia2005measlesgravity, jung2008highwaygravity, barbosa2018human, curiel2018citygravity, lewer2008immigrationgravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity}, often successfully capture mobility between places using their population and the \textit{distance} between them.
-However, geographic distance is less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} wherein the physical distance barrier shrinks while the impact of inter-related linguistic, economic, cultural, and historical similarities increases.
-Alternative notions of functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} attempt to re-define distance by using some of the aforementioned factor~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional} but are often low resolution, arbitrary, and consider only single isolated facets of mobility.
+Human mobility and migration drives major social phenomena such as the growth and evolution of cities~\autocite{wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity}, economies~\autocite{kaluza2010cargo, kerr2011immigration}, innovation~\autocite{kaiser2018innovation, armano2017innovation},  and scientific research~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage, morgan2018prestige, rodrigues2016mobility}.
+Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity, xia2005measlesgravity, jung2008highwaygravity, barbosa2018human, curiel2018citygravity, lewer2008immigrationgravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} aim to capture mobility between places using their population and the \textit{distance} between them.
+However, geographic distance is less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} wherein the physical barrier shrinks while linguistic, economic, cultural, and historical similarities matter more.
+Alternative notions of functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} attempt to re-define distance by using some of the aforementioned factor~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional} but are often arbitrary, and consider only single isolated facets.
 Here, using a rich dataset of scientific mobility, we demonstrate that a data-driven neural embedding approach~\autocite{mikolov2013word2vec} can successfully encodes a functional distance between organizations and captures the latent and multi-faceted structure of scientist's mobility.
 We demonstrate that the cosine distance between organization embedding vectors, constructed using the affiliation trajectories of scientists in the Web of Science database, better explain and predict real mobility than geographic distance.
-Exploiting their unique properties, we interpret the embedding space and observe that it captures not only geographic relations between organizations, but also relations based on culture, language, and academic prestige at multiple levels of granularity.
-Also encoded in the embedding space is a universal pattern capturing the relationship between organization's size and their connectedness.
+Exploiting their unique properties, we idemonstrate that the embedding space encodes not only geographic relations between organizations, but also relations based on culture, language, and academic prestige at multiple levels of granularity.
+Also captured in the embedding space is a universal pattern capturing the relationship between organization's size and their connectedness.
 The ability to learn scalable, dense, and meaningful high-resolution vector representations of mobility directly from the data can open up a new avenue of studying human mobility.
@@
 What is it about the organization embedding that captures prestige so effectively?
-We find that the length of organization vectors---that is, the distance from the origin of the vector space---provides insight into the characteristics of organizations. 
+We find that the length of organization vectors---that is, the distance from the origin of the vector space---provides provides insight into the characteristics of organizations. 
 Up to a point, the length of U.S. organization's vectors tends to increase proportional to its number of researchers (both mobile and non-mobile) who published with that organization;
 these organizations are primarily teaching-focused institutions, agencies, and hospitals that either are not ranked or have a low ranking. 
-However, at around 1,000 researchers, the length of the vector decreases with increment in the number of researchers;
+However, at around 1,000 researchers, the length of the vector decreases with increase in the number of researchers;
 organizations here are primarily research-intensive and prestigious universities with higher rankings, research outputs, R\&D funding, and doctoral students (Fig.~\ref{fig:supp:length_vs_metaInfo}).
-This same convex-curve repeats irrespective of countries, such as China and Germany, though the curve may be shifted based on the typical size and vector length of their organizations (Fig.~\ref{fig:length}b).
-
-This pattern has been observed in applications of neural embedding to natural language, wherein the length of word vectors was found to represent the word "significance"~\autocite{schakel2015measuring}
+This same convex-curve repeats irrespective of country, such as China and Germany, though the curve may be shifted based on the typical size and vector length of their organizations (Fig.~\ref{fig:length}b).
+
+This pattern has been observed in applications of neural embedding to natural language, wherein the length of word vectors were found to represent word "significance"~\autocite{schakel2015measuring}
 Here, interpret the vector length instead as a measure of an organization's connectedness to other organizations given its size, where a connection is defined as a non-zero flow between organizations.
@@
 At the national level, the relative position of the convex-curves can reveal characteristics of their scientific organizations—for example, compared to the United States, Chinese organizations have a longer typical vector length (Fig.~\ref{fig:length}b) reflecting lower overall connectedness in the embedding space.
-Prestige is a key component of academic mobility—by encoding information relating to prestige, neural embeddings offer a means of better representing the functional distance between organizations and capturing the global landscape of mobility.
+Prestige is a key component academic mobility—by encoding information relating to prestige, neural embeddings offer a means of better representing functional distance between organizations and capturing the global landscape of mobility.
 

### 2020-07-23 paper/current/main.tex
update text relating to figs 2-4

@@
 While geographic distance may have driven human movements in the past, it holds less importance to a world connected by rapid transit, complex international relations, and dense airline networks.
-For instance, a person living in Australia is more likely to migrate to the United Kingdom, a country with similar language and culture, than to closer and more populous countries like Indonesia. 
-Similarly, a prospective student living in South Korea is more likely to attend universities in Canada than those in North Korea. 
-While geographic distance is still used as the basis for the most prominent models of mobility such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} model, so-called \textit{functional distances}~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional} have been proposed to learn alternative notions of distance from real-world data or \textit{a priori} relationships between geographic entities.
-Yet, functional distances are often low-resolution and rely on somewhat arbitrary decisions about what factors are most important.
-Moreover, functional distances typically only focus on one facet of mobility at a time, whereas real-world mobility is multi-faceted, influenced simultaneously by geography, language, culture, history, and economic opportunity.
-Mobility is complex, and so new approaches are needed to merge its many facets into a single high-resolution measure of functional distance.
+For instance, a person living in Australia is more likely to migrate to the United Kingdom, a far-away country with similar language and culture, than to much closer countries like Indonesia. 
+Similarly, a student in South Korea is more likely to attend universities in Canada than those in North Korea. 
+Although geographic distance has still been used as the basis for the most prominent models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} model,  \textit{functional distances}~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional} have been proposed to learn alternative notions of distance from real-world data or \textit{a priori} relationships between geographic entities.
+Yet, functional distances are often low-resolution and rely on somewhat arbitrary decisions about the importance of each factor.
+Moreover, functional distances typically only focus on a single facet of mobility at a time, whereas real-world mobility is multi-faceted, influenced simultaneously by geography, language, culture, history, and economic opportunity.
+To capture the complexity of human mobility, and so new approaches are needed to incorporate its many facets into a single high-resolution measure of functional distance.
 
 Here, we propose a neural embedding model that uses real-world mobility trajectories to encode the complex landscape of global mobility into a dense, continuous, and meaningful vector-space representation, from which a \textit{functional distance} between places can be derived.
-This approach, originally designed for learning language models~\autocite{mikolov2013word2vec} has been used to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
-Neural embedding is also computationally efficient, scalable for large datasets, robust to noise, and can extract rich relationships between the entities through the application of simple vector arithmetic~\autocite{levy2014neural}.
+The neural embedding, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been used to reveal insights into texts~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
+Neural embedding is also computationally efficient, scalable for large datasets, robust to noise, and can extract rich relationships between entities through the application of simple vector arithmetic~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.
 
 We use scientific mobility, inferred from affiliations, to demonstrate the effectiveness of our approach.
-Scientific mobility is a central aspect of the increasingly-globalized scientific system~\autocite{czaika2018globalisation, altbach2004globalization}, being strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}.
+Scientific mobility is a central driver of the increasingly-globalized scientific enterprise~\autocite{czaika2018globalisation, altbach2004globalization, box2008competition}, being strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}.
 Moreover, scientific mobility has known structure, such as the centrality of the United States and the United Kingdom, and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career} that should be captured in a representation.
-For nations and organizations hoping to win in the global competition for talent~\autocite{box2008competition}, understanding the landscape of global scientific mobility is essential. 
 However, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}.
-Underlying these challenges is the lack of a meaningful functional distance measure between countries, cities, and organizations.
+Underlying these challenges is the diminishing role of geography and geographic distance in shaping the landscape of scientific mobility.
 
@@
 The most fine-grained geographical unit in this data is the organization, such as a university, research institute, business, or government agency.
-As a scientist's careers progress, they move between organizations or pick up additional (simultaneous) affiliations forming \textit{affiliation trajectories} (Fig.~\ref{fig:methods:mobility_sentence}).
+As a scientist's career progresses, they move between organizations or pick up additional (simultaneous) affiliations forming \textit{affiliation trajectories} (Fig.~\ref{fig:methods:mobility_sentence}).
 These trajectories encode both asynchronous migration, and synchronous mobility---the holding of multiple simultaneous co-affiliations involving the sharing of time and capital between locations---that is typical of scientific mobility~\autocite{rodrigues2016mobility, markova2016synchronous, sugimoto2017mostimpact} (see Supplementary Materials).
@@
 %
-\subsection*{Embeddings provide both geographical and functional distance between organizations}
-
-The functional distance derived from the embedding explains and predicts scientific mobility better than geographic distance.
+\subsection*{Embeddings provide both functional distance between organizations}
+
+The embedding distance explains and predicts scientific mobility better than geographic distance.
 The amount of variance explained by embedding distance ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) is more than twice that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
@@
 After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance (Fig.~\ref{fig:gravity_performance}c--d), which also holds for the subsets of only domestic (Fig.~\ref{fig:supp:gravity_correlation}e--f) and international mobility (Fig.~\ref{fig:supp:gravity_correlation}g--h).
-The embedding distance defined from the cosine distnace between vectors also outperforms that defined from their dot product ($R^{2} = 0.34$, Fig.~\ref{fig:supp:gravity_dot}).
+The embedding distance defined from the cosine distance between vectors also outperforms that defined from their dot product ($R^{2} = 0.34$, Fig.~\ref{fig:supp:gravity_dot}).
 The embedding distance also out-performs alternative ``diffusion-based'' network distance measures such as the personalized-page rank scores (see supporting materials) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
@@
 		\textbf{Embedding distance outperforms geographic distance.}
-		\textbf{a.} embedding distance (cosine distance between organization vectors) explains more of the expected flux between organization pairs than does geographic distance (\textbf{b}).
+		\textbf{a.} embedding distance (cosine distance between organization vectors) better explains the expected flux between organization pairs than geographic distance (\textbf{b}).
 		The red line is the line of the best fit.
@@
 		Error bars are 99\% confidence intervals.
-		Color indicates the frequency of organization pairs within each hex bin.
+		The lightness of each hex bin indicates the frequency of organization pairs within it.
 		\textbf{c-d.} Predictions of flux between organization pairs made using embedding distance outperform those made using geographic distance.
 		Boxplots show distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps $x = y$.
+		Box color corresponds to the degree to which the distribution overlaps $y = x$.
 		``RMSE'' is root-mean-squared error between the actual and predicted values.
@@
 		Predictions are not meaningfully different if estimates are learned on all pairs of organizations (Fig. \ref{fig:supp:gravity_prediction_subsets}).
-		These predictions are robust whether the model is fit on the global data, or on the domestic (Fig.~\ref{fig:gravity_performance}e-h) or international Fig.~\ref{fig:supp:gravity_prediction_subsets}) subsets .
+		These predictions are robust whether the model is fit on the global data, or on the domestic (Fig.~\ref{fig:gravity_performance}e-h) or international (Fig.~\ref{fig:supp:gravity_prediction_subsets}) subsets.
 	}
@@
 The embedding also allows us to create informative visualizations of global scientific mobility.
-To explore the topological structure of the embedding, we use a standard dimensionality reduction technique (UMAP~\autocite{mcinnes2018umap}) for embedding to obtain a two-dimensional representation of the embedding (Fig.~\ref{fig:projection}a).
+To explore the topological structure of the embedding, we use a standard dimensionality reduction technique (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation of the embedding (Fig.~\ref{fig:projection}a).
 By showing relationships between individual organizations, rather than aggregates such as nations or cities, this projection constitutes the largest and highest resolution ``map'' of scientific mobility to date.
@@
 
-The embedding space also allows us to \textit{zoom in} on subsets of counties and re-project them in order to reveal more local relationships. 
-For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries ranging from Egypt to Philippines that corresponds largely to geography, but with some peculiar exceptions.
+The embedding space also allows us to \textit{zoom in} on subsets and re-project them in order to reveal more local relationships. 
+For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries between Egypt to Philippines that corresponds largely to geography, but with some peculiar exceptions.
 For example, countries like Iraq are nearer to some southeast-Asian countries like Malaysia, with a cosine distance between the nation's aggregate vectors of $d = 0.29$, than to nearer and more religiously-similar nations like Saudi Arabia ($d = 0.50$) and Qatar ($d = 0.51$).
 Linguistic and historical ties are also conspicuous.
-For example, we observe that Spanish-speaking post-colonial Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), such as Mexico ($d = 0.34$) and Chile ($d = 0.39$) more than to nearby Portuguese-speaking nation ($d = 0.52$ for Mexico and $d = 0.49$ for Chile) reflecting linguistic and cultural constraints.
+For example, we observe that Spanish-speaking post-colonial Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), rather than nearby Portuguese-speaking nation ($d = 0.34$ vs.
+$d = 0.52$ for Mexico and $d = 0.39$ vs.
+$d = 0.49$ for Chile) reflecting linguistic and cultural constraints.
 Similarly, North-African countries that were once under French rule such as Morocco are nearer to France ($d =0.35$) than to similarly-distant European countries as Spain ($d = 0.40$) and Italy ($d = 0.53$).
@@
 
-The geographic structure of the global embedding is mirrored in the re-projection of the United States, wherein organizations are largely organized according to regions and states (Fig.~\ref{fig:projection}d).
+The geographic structure of the global embedding is mirrored in the re-projection of the United States, wherein organizations are largely organized according to geography (Fig.~\ref{fig:projection}d).
 By re-projecting Massachusetts (Fig.~\ref{fig:projection}e), we observe structure based on urban centers (Boston vs.
@@
 universities) and university systems.
-For example, even though UMass Boston is located in Boston, it clusters with  other universities in the UMass System ($d = 0.34$) rather than the other typically more highly-ranked and research-focused universities in Boston ($d = 0.41$), reflecting a relative lack of mobility between the two systems, even within the same state.
+For example, even though UMass Boston is located in Boston, it clusters with  other universities in the UMass System ($d = 0.34$) rather than the other typically more highly-ranked and research-focused universities in Boston ($d = 0.41$), reflecting a relative lack of mobility between the two systems.
 Similar structures can be observed in other states such as among New York's CUNY and SUNY systems (Fig.~\ref{fig:supp:proj_newyork}), Pennsylvania's state system (Fig.~\ref{fig:supp:proj_pennsylvania}), Texas's Agricultural and Mechanical universities (Fig.~\ref{fig:supp:proj_texas}), and between the University of California and State University of California systems (Fig.~\ref{fig:supp:proj_california}).
@@
 
-Just as the embedding space makes it possible to ``zoom in'' on subsets of organizations, it is also possible to ``zoom out'' to a higher level by aggregating organizational vectors. 
+Just as the embedding space makes it possible to ``zoom in'' on subsets of organizations, it is also possible to ``zoom out'' by aggregating organizational vectors. 
 For example, we can examine the high-level structure by estimating the aggregate embeddings of countries. 
-Namely, we calculate the representative vector of each country as the average of their organizational vectors.
+Namely, we define the representative vector of each country as the average of their organizational vectors.
 We then perform hierarchical clustering of nations that have at least 25 organizations represented in the embedding space, excluding the United States which is a dominant hub well connected to most other countries (see Fig.
@@
 \ref{fig:clustering}b demonstrates that the region plays a major role at higher levels of the clustering process (low $r$), and language (family) explains the clustering more at the lower levels (high $r$).
-This suggests that the embedding space captures a hierarchy of facets of mobility---at the highest level, geography defines the  embedding space, followed then by language.
+This suggests that the embedding space captures the hierarchical structure of mobility---at the highest level, geography defines the embedding space, followed then by language.
 

### 2020-07-23 paper/current/main.tex
update fig 4 caption

@@
 		Color of three cell rows separated from the matrix correspond to, from left to right, the region of the country, the language family~\autocite{ethnologue}, and the individual language.
-		\textbf{b.}	Element-centric cluster similarity~\autocite{gates2019element} results demonstrating the factors dictating hierarchical clustering, varying by scaling parameter, $r$.
-		Region better explains the grouping of country vectors at higher levels of the clustering processes.
-		Language family, and then majority spoken language, better explain the grouping of countries at more granular.
+		\textbf{b.}	Element-centric cluster similarity~\autocite{gates2019element} reveals the factors dictating hierarchical clustering.
+		Region better explains the grouping of country vectors at higher levels of the clustering.
+		Language family, and then majority spoken language, better explain the grouping of countries at more fine-grained level.
 	}

### 2020-07-23 paper/current/main.tex

@@
 
-Prestige hierarchies underpin the dynamics of scientific mobility~\autocite{deville2014career, clauset2015hierarchy}, but are these hierarchies captured in the embedding space, to which no explicit information on prestige is given?
+Prestige hierarchy is known to underpin the dynamics of scientific mobility~\autocite{deville2014career, clauset2015hierarchy}, but can this hierarchy be encoded in the embedding space, to which no explicit information on prestige is given?
 We test this by exploiting the geometric properties of the embedding space with SemAxis~\autocite{an2018semaxis}, an approach originally designed to characterize the semantics of words in word embeddings.
-Here, we use SemAxis to operationalize the abstract notion of academic prestige, defining each pole of the axis using known high- and low-ranked universities. 
+Here, we use SemAxis to operationalize the abstract notion of academic prestige, defining each pole of the axis using high- and low-ranked universities. 
 We define prestige using the Times Ranking of World Universities (and using research impact from the Leiden Rankings~\autocite{waltman2012leidenrankings} in Supplementary Materials), including all ranked universities in the United States;
@@
 Prestigious universities such as Colombia, Stanford, MIT, Harvard, and Rockefeller are positioned towards the top of the axis (Fig.~\ref{fig:semaxis}a).
-Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphesis on teaching, such as Barry Univeristy and California State University at Long Beach.
+Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphasis on teaching, such as Barry University and California State University at Long Beach.
 SemAxis also offers a new means of reasoning about the prestige of organizations typically excluded from rankings such as government organizations (Fig.~\ref{fig:semaxis}b), research institutes (Fig.~\ref{fig:semaxis}c), and teaching colleges (Fig.~\ref{fig:semaxis}d).
@@
 
-The embedding space captures prestige hierarchies that can be used to reconstruct academic rankings. 
+The embedding space captures the prestige hierarchy and can be used to reconstruct academic rankings. 
 We derive a ranking for universities using the SemAxis prestige axis in Fig.~\ref{fig:semaxis}a and compare them to traditional university rankings.
 The SemAxis ranking is defined from the position of organizations along the prestige axis, with the top-ranked being the furthest towards the high-ranked end of the axis.
-We find that the SemAxis ranking is correlated with the Times ranking (Spearman's $\rho = 0.73$, Fig.~\ref{fig:semaxis}e).
+We find that the embedding-based ranking is strongly correlated with the Times ranking (Spearman's $\rho = 0.73$, Fig.~\ref{fig:semaxis}e).
 The strongest outliers that were ranked more highly in the Times Ranking than the SemAxis ranking tend to be large state universities such as Arizona State University and  University of Florida;
@@
 SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities are significantly correlated with the Times Ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
-For reference, the SemAxis-derived ranking achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking~\autocite{waltman2012leidenrankings}, a common and bibliometrically-informed university ranking (Spearman's $\rho = 0.87$, Fig.~\ref{fig:semaxis}f).
+For reference, the SemAxis-derived ranking achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking~\autocite{waltman2012leidenrankings}, a well-known and bibliometrically-informed university ranking (Spearman's $\rho = 0.87$, Fig.~\ref{fig:semaxis}f).
 This suggests that the organization embedding captures the latent prestige hierarchy inherent to academic mobility, even without providing any explicit information on prestige, with a high degree of resolution and reliability~\autocite{deville2014career, clauset2015hierarchy}.
@@
 What is it about the organization embedding that captures prestige so effectively?
-We find that the length of organization vectors---that is, the distance from the origin of the vector space---provides provides insight into the characteristics of organizations. 
-Up to a point, the length of U.S. organization's vectors tends to increase proportional to its number of researchers (both mobile and non-mobile) who published with that organization;
+We find that the size (L2 norm) of the organization embedding vectors provides insights into the characteristics of organizations. 
+Up to a point, the size of U.S. organization's vectors tends to increase proportional to its number of researchers (both mobile and non-mobile) who published with that organization;
 these organizations are primarily teaching-focused institutions, agencies, and hospitals that either are not ranked or have a low ranking. 
-However, at around 1,000 researchers, the length of the vector decreases with increase in the number of researchers;
+However, at around 1,000 researchers, the size of the vector decreases as the number of researchers increases;
 organizations here are primarily research-intensive and prestigious universities with higher rankings, research outputs, R\&D funding, and doctoral students (Fig.~\ref{fig:supp:length_vs_metaInfo}).
+A similar pattern has been observed in applications of neural embedding to natural language, wherein the length of word vectors were found to represent word "significance"~\autocite{schakel2015measuring}.
+If a word appears frequently in a specific context, the norm of the word vector is likely to be large, because a large norm is associated with how predictably the word occurs given a context.
+However, if the word in question is universal, appearing frequently in many different contexts, it cannot have a large norm as it lacks a strong association with a particular context. 
+Likewise, an organization such as Harvard with a small norm appears in many contexts, that is, alongside many different organizations in affiliation trajectories. 
+The concavity emerges in part from the relationship between the size of the vector and the expected connectedness of the organization given its size (Fig.~\ref{fig:length}a, inset, $R^{2} = 0.17$).
+Large, prestigious, and well-funded research universities such as Princeton and Harvard have smaller vector sizes because they appear in many different contexts compared to more teaching-focused organizations such as NY Medical College, and University of Michigan at Flint.
+Some universities, such as the University of Alaska at Fairbanks, have surprisingly small vectors, perhaps as a result of its remote location and unique circumstances.
+
 This same convex-curve repeats irrespective of country, such as China and Germany, though the curve may be shifted based on the typical size and vector length of their organizations (Fig.~\ref{fig:length}b).
-
-This pattern has been observed in applications of neural embedding to natural language, wherein the length of word vectors were found to represent word "significance"~\autocite{schakel2015measuring}
+The relative position of these curves can reveal characteristics about the scientific systems in each country. 
+For example,
+
+This 
 Here, interpret the vector length instead as a measure of an organization's connectedness to other organizations given its size, where a connection is defined as a non-zero flow between organizations.
@@
 	\caption{
-		\textbf{Length of organization vectors captures connection diversity of organizations.}
-		\textbf{a.} L2 norm of organization vectors compared to their number of researchers for U.S. universities.
-		The L2 norm corresponds to the distance from the origin of the vector space.
+		\textbf{Size of organization embedding vectors captures connection diversity of organizations.}
+		\textbf{a.} Size (L2 norm) of organization embedding vectors compared to their number of researchers for U.S. universities.
 		Color indicates the rank of the university from the Times ranking, with 1 being the highest ranked university.
@@
 		A convex-shape emerges, wherein larger universities tend to more distant from the origin (large L2 norm), however the more prestigious the university, the closer it is to the origin (small L2 norm).
-		\textbf{b.} This convex pattern repeats globally for all organizations across all countries, shown for the United States, Germany, China, and others,
+		The L2 norm is correlated weakly with the number of connection divided by the number of researchers in organization, which can be interpreted diversity of the connection compared to their size ($R^{2} = 0.17$, \textbf{inset}).
+		The red line is the line of the best fit, and 99\% confidence intervals are shown. 
+		\textbf{b.} This convex pattern repeats globally for all organizations across all countries, shown for the United States, China, and others,
 		The loess regression lines are shown for each selected country, and for the aggregate of remaining countries. 
-		The L2 norm is correlated weakly with the number of connection divided by the number of researchers in organization, which can be interpreted diversity of the connection compared to their size ($R^{2} = 0.17$, \textbf{inset}).
-		The red line is the line of the best fit.
 	}

### 2020-07-23 notebooks/embedding_boomerang_plots.rmd
update to figure 6 and surrounding text. added new supp figure

--- 2020-07-21 notebooks/embedding_boomerang_plots.rmd
@@
     option = "C",
-    breaks = c(1, 50, 100)) +
+    breaks = c(1, 50, 100)
+  ) +
   scale_shape_manual(values = c(16, 1)) +
@@
   #) +
-  guides(shape = F) +
+  guides(shape = F,
+         color = guide_colorbar(reverse = T)) +
   theme_minimal() +
-  annotate(geom = "label", x = 1.5e4, y = 3.5, label = "Harvard", size = 3.5) +
-  annotate(geom = "label", x = 1.6e3, y = 3.69, label = "Princeton", size = 3.5) +
+  annotate(geom = "label", x = 1.5e4, y = 3.6, label = "Harvard", size = 3.5) +
+  annotate(geom = "label", x = 1.6e3, y = 3.65, label = "Princeton", size = 3.5) +
   annotate(geom = "label", x = 8.5e3, y = 5.9, label = "Univ Tennessee\nKnoxville", size = 3.5) +
-  annotate(geom = "label", x = 4.9e2, y = 2.15, label = "Univ Alaska\nFairbanks", size = 3.5) +
-  annotate(geom = "label", x = 4e2, y = 5.75, label = "NY Medical College", size = 3.5) +
+  annotate(geom = "label", x = 1.8e2, y = 1.55, label = "Univ Alaska\nFairbanks", size = 3.5) +
+  annotate(geom = "label", x = 4e2, y = 6.2, label = "NY Medical College", size = 3.5) +
   annotate(geom = "label", x = 2e1, y = 4.6, label = "Univ Michigan\nFlint", size = 3.4) +
-  annotate(geom = "label", x = 6.4e1, y = 2.48, label = "Barry University", size = 3.5) +
+  annotate(geom = "label", x = 6.8e1, y = 2.48, label = "Barry University", size = 3.5) +
   theme(
@@
     legend.text = element_text(size = 12),
-    legend.position = c(0.85, 0.20),
+    legend.title = element_text(face = "bold"),
+    legend.position = c(0.11, 0.852),
     panel.grid.minor = element_blank(),
@@
   mutate(
-    highlight = ifelse(country %in% c("China", "United States", "Germany"), country, "Other"),
-    highlight = factor(highlight, levels = c("United States", "China", "Germany", "Other"))
+    highlight = ifelse(country %in% c("China", "United States"), country, "Other"),
+    highlight = factor(highlight, levels = c("United States", "China", "Other"))
   ) %>%
-  ggplot(aes(x = size, y = `l2-norm`, label = name, alpha = highlight, shape = highlight, color = highlight)) +
-  geom_point(alpha = 0.5) +
+  ggplot(aes(x = size, y = `l2-norm`, fill = highlight, shape = highlight, color = highlight, linetype = highlight)) +
+  geom_point(alpha = 0.2) +
   stat_smooth(
     method = "loess",
-    se = F
+    size = 1.5,
+    level = 0.99,
+    se = T,
+    alpha = 0.6
   ) +
-  scale_shape_manual(values = c(16, 16, 16, 16, 16,  1)) +
-  scale_color_manual(values = c("#66c2a5", "#fc8d62", "#8da0cb", "#e78ac3", "#a6d854", "grey")) +
-  scale_alpha_manual(values = c(1, 1, 1, 1, 1,  0.6)) +
+  scale_shape_manual(values = c(16, 16, 1)) +
+  scale_color_manual(values = c("#d35400", "#2980b9", "darkgrey")) +
+  scale_linetype_manual(values = c(2, 2, 1)) +
+  scale_fill_manual(values = c("#d35400", "#2980b9", "grey")) +
   scale_x_log10(
@@
     axis.text.y.right = element_blank(),
-    legend.text = element_text(size = 10),
-    legend.position = c(0.14, 0.82),
+    legend.text = element_text(size = 12, face = "bold"),
+    legend.position = c(0.15, 0.912),
     panel.grid.minor = element_blank(),
@@
 ```{r}
+plot <- df %>%
+  mutate(
+    highlight = ifelse(country %in% c("Brazil", "United States"), country, "Other"),
+    highlight = factor(highlight, levels = c("United States", "Brazil", "Other"))
+  ) %>%
+  filter(highlight != "Other") %>%
+  ggplot(aes(x = size, y = `l2-norm`, label = name, fill = highlight, color = highlight, linetype = highlight)) +
+  stat_smooth(
+    method = "loess",
+    size = 2,
+    level = 0.99,
+    se = T,
+    alpha = 0.6
+  ) +
+  scale_color_manual(values = c("#d35400", "#27ae60")) +
+  scale_fill_manual(values = c("#d35400", "#27ae60")) +
+  scale_linetype_manual(values = c(2, 1)) +
+  scale_x_log10(
+    breaks = scales::trans_breaks("log10", function(x) 10^x),
+    labels = scales::trans_format("log10", scales::math_format(10^.x))
+  ) +
+  scale_y_continuous(
+    limits = c(0, 7),
+    breaks = c(2, 4, 6)
+  ) +
+  guides(shape = F) +
+  theme_minimal() +
+  theme(
+    text = element_text(family = "Helvetica", size = 14),
+    axis.title.x = element_text(angle = 0, size = 16, face = "bold", vjust = 0.5),
+    axis.title.x.top = element_text(angle = 0, size = 16, face = "bold", vjust = 0.5),
+    axis.text.x.top = element_blank(),
+    axis.title.y = element_text(angle = 90, size = 16, face = "bold"),
+    axis.title.y.right = element_text(angle = 90, size = 16, face = "bold"),
+    axis.text.y.right = element_blank(),
+    legend.text = element_text(size = 16, face = "bold"),
+    legend.position = c(0.5, 0.2),
+    panel.grid.minor = element_blank(),
+    panel.grid.major = element_blank(),
+    panel.background = element_rect(size = 0.5),
+    legend.title = element_blank(),
+    axis.line = element_line(color="black", size = 0.3),
+    legend.box.background = element_rect(color=NA, fill = NA)
+  ) +
+  annotation_logticks(sides = "b") +
+  xlab("# Researchers") +
+  ylab("L2 Norm")
+
+plot
+
+ggsave("/Users/dakotamurray/Dropbox/SME-dropbox/Figures/boomerang_brazil.pdf", plot, width = 3, height = 3)
+```
+
+```{r}
+plot <- df %>%
+  mutate(
+    highlight = ifelse(country %in% c("Sweden", "United States"), country, "Other"),
+    highlight = factor(highlight, levels = c("United States", "Sweden", "Other"))
+  ) %>%
+  filter(highlight != "Other") %>%
+  ggplot(aes(x = size, y = `l2-norm`, label = name, fill = highlight, color = highlight, linetype = highlight)) +
+  stat_smooth(
+    method = "loess",
+    alpha = 0.6,
+    level = 0.99,
+    size = 2,
+    se = T
+  ) +
+  scale_color_manual(values = c("#d35400", "#8e44ad")) +
+  scale_fill_manual(values = c("#d35400", "#8e44ad")) +
+  scale_linetype_manual(values = c(2, 1)) +
+  scale_x_log10(
+    breaks = scales::trans_breaks("log10", function(x) 10^x),
+    labels = scales::trans_format("log10", scales::math_format(10^.x))
+  ) +
+  scale_y_continuous(
+    limits = c(0, 7),
+    breaks = c(2, 4, 6)
+  ) +
+  guides(shape = F) +
+  theme_minimal() +
+  theme(
+    text = element_text(family = "Helvetica", size = 14),
+    axis.title.x = element_text(angle = 0, size = 16, face = "bold", vjust = 0.5),
+    axis.title.x.top = element_text(angle = 0, size = 16, face = "bold", vjust = 0.5),
+    axis.text.x.top = element_blank(),
+    axis.title.y = element_text(angle = 90, size = 16, face = "bold"),
+    axis.title.y.right = element_text(angle = 90, size = 16, face = "bold"),
+    axis.text.y.right = element_blank(),
+    legend.text = element_text(size = 16, face = "bold"),
+    legend.position = c(0.5, 0.2),
+    panel.grid.minor = element_blank(),
+    panel.background = element_rect(size = 0.5),
+    panel.grid.major = element_blank(),
+    legend.title = element_blank(),
+    axis.line = element_line(color="black", size = 0.3),
+    legend.box.background = element_rect(color=NA, fill = NA)
+  ) +
+  annotation_logticks(sides = "b") +
+  xlab("# Researchers") +
+  ylab("L2 Norm")
+
+plot
+
+ggsave("/Users/dakotamurray/Dropbox/SME-dropbox/Figures/boomerang_sweden.pdf", plot, width = 3, height = 3)
+```
+
+```{r}
+plot <- df %>%
+  mutate(
+    highlight = ifelse(country %in% c("Egypt", "United States"), country, "Other"),
+    highlight = factor(highlight, levels = c("United States", "Egypt", "Other"))
+  ) %>%
+  filter(highlight != "Other") %>%
+  ggplot(aes(x = size, y = `l2-norm`, label = name, fill = highlight, color = highlight, linetype = highlight)) +
+  stat_smooth(
+    method = "loess",
+    size = 2,
+    level = 0.99,
+    fill = "lightgrey",
+    alpha = 0.6,
+    se = T
+  ) +
+  scale_color_manual(values = c("#d35400", "black")) +
+  scale_linetype_manual(values = c(2, 1)) +
+  scale_x_log10(
+    breaks = scales::trans_breaks("log10", function(x) 10^x),
+    labels = scales::trans_format("log10", scales::math_format(10^.x))
+  ) +
+  scale_y_continuous(
+    limits = c(0, 7),
+    breaks = c(2, 4, 6)
+  ) +
+  guides(shape = F) +
+  theme_minimal() +
+  theme(
+    text = element_text(family = "Helvetica", size = 14),
+    axis.title.x = element_text(angle = 0, size = 16, face = "bold", vjust = 0.5),
+    axis.title.x.top = element_text(angle = 0, size = 16, face = "bold", vjust = 0.5),
+    axis.text.x.top = element_blank(),
+    axis.title.y = element_text(angle = 90, size = 16, face = "bold"),
+    axis.title.y.right = element_text(angle = 90, size = 16, face = "bold"),
+    axis.text.y.right = element_blank(),
+    legend.text = element_text(size = 16, face = "bold"),
+    legend.position = c(0.5, 0.2),
+    panel.grid.minor = element_blank(),
+    panel.background = element_rect(size = 0.5),
+    panel.grid.major = element_blank(),
+    legend.title = element_blank(),
+    axis.line = element_line(color="black", size = 0.3),
+    legend.box.background = element_rect(color=NA, fill = NA)
+  ) +
+  annotation_logticks(sides = "b") +
+  xlab("# Researchers") +
+  ylab("L2 Norm")
+
+plot
+
+ggsave("/Users/dakotamurray/Dropbox/SME-dropbox/Figures/boomerang_egypt.pdf", plot, width = 3, height = 3)
+```
+
+```{r}
+selected <- (df %>%
+  group_by(country) %>%
+  summarize(total = sum(size)) %>%
+  top_n(20, total))$country
+
+plot <- df %>%
+  filter(!is.na(`l2-norm`)) %>%
+  filter(country %in% c(selected)) %>%
+  ggplot(aes(x = size, y = `l2-norm`)) +
+  stat_smooth(
+    method = "loess",
+    size = 2,
+    se = T,
+    level = 0.99,
+    color = "black",
+    fill = "black",
+    alpha = 0.4,
+
+  ) +
+  scale_x_log10(
+    breaks = scales::trans_breaks("log10", function(x) 10^x),
+    labels = scales::trans_format("log10", scales::math_format(10^.x))
+  ) +
+  scale_y_continuous(
+    limits = c(0, 7),
+    breaks = c(2, 4, 6)
+  ) +
+  facet_wrap(~country) +
+  theme_minimal() +
+  theme(
+    text = element_text(family = "Helvetica", size = 14),
+    axis.title.x = element_text(angle = 0, size = 16, face = "bold", vjust = 0.5),
+    axis.title.x.top = element_text(angle = 0, size = 16, face = "bold", vjust = 0.5),
+    axis.text.x.top = element_blank(),
+    axis.title.y = element_text(angle = 90, size = 16, face = "bold"),
+    axis.title.y.right = element_text(angle = 90, size = 16, face = "bold"),
+    axis.text.y.right = element_blank(),
+    panel.grid.minor = element_blank(),
+    panel.background = element_rect(size = 0.5),
+    panel.grid.major = element_blank(),
+    strip.text = element_text(face = "bold"),
+    axis.line = element_line(color="black", size = 0.3),
+  ) +
+  annotation_logticks(sides = "b") +
+  xlab("# Researchers") +
+  ylab("L2 Norm")
+
+plot
+
+ggsave("/Users/dakotamurray/Dropbox/SME-dropbox/Figures/boomerang_20_countries.pdf", plot, width = 7, height = 7)
+```
+
+```{r}
 ratio <- read_csv("/Users/dakotamurray/Desktop/data_with_ratio.csv")
@@
               formula = y ~ x,
-              color = "#c0392b",
-              alpha = 0.6,
+              color = "darkred",
+              alpha = 0.4,
+              fill = "darkred",
               se = T,
               level = 0.99,
-              size = 1.5,
+              size = 0.75,
               fullrange = T)  +
@@
     ) +
+  scale_x_continuous(breaks = c(-1.5, 0, 1)) +
   theme_minimal() +
   theme(
-    text = element_text(family = "Helvetica", size = 12),
-    axis.title.x = element_text(angle = 0, size = 14, face = "bold", vjust = 0.5),
-    axis.title.x.top = element_text(angle = 0, size = 14, face = "bold", vjust = 0.5),
+    text = element_text(family = "Helvetica", size = 14),
+    axis.title.x = element_text(angle = 0, size = 16, face = "bold", vjust = 0.5),
+    axis.title.x.top = element_text(angle = 0, size = 16, face = "bold", vjust = 0.5),
     axis.text.x.top = element_blank(),
-    axis.title.y = element_text(angle = 90, size = 14, face = "bold"),
-    axis.title.y.right = element_text(angle = 90, size = 14, face = "bold"),
+    axis.title.y = element_text(angle = 90, size = 16, face = "bold"),
+    axis.title.y.right = element_text(angle = 90, size = 16, face = "bold"),
     axis.text.y.right = element_blank(),
-    legend.text = element_text(size = 12),
+    legend.text = element_text(size = 14),
     #legend.position = c(0.16, 0.35),
@@
   annotation_logticks(sides = "b") +
-  xlab("Expexted reach") +
+  xlab("# connections / # researchers") +
   ylab("L2 Norm")
@@
 plot 
-ggsave("/Users/dakotamurray/Dropbox/SME-dropbox/Figures/ratio_l2.png", plot, width = 4, height = 3)
+ggsave("/Users/dakotamurray/Dropbox/SME-dropbox/Figures/ratio_l2.pdf", plot, width = 4, height = 3)
 ```

### 2020-07-23 paper/current/main.tex
update to figure 6 and surrounding text. added new supp figure

@@
 organizations here are primarily research-intensive and prestigious universities with higher rankings, research outputs, R\&D funding, and doctoral students (Fig.~\ref{fig:supp:length_vs_metaInfo}).
-A similar pattern has been observed in applications of neural embedding to natural language, wherein the length of word vectors were found to represent word "significance"~\autocite{schakel2015measuring}.
+A similar pattern has been observed in applications of neural embedding to natural language, wherein the size of word vectors were found to represent word ``significance''~\autocite{schakel2015measuring}.
 If a word appears frequently in a specific context, the norm of the word vector is likely to be large, because a large norm is associated with how predictably the word occurs given a context.
 However, if the word in question is universal, appearing frequently in many different contexts, it cannot have a large norm as it lacks a strong association with a particular context. 
-Likewise, an organization such as Harvard with a small norm appears in many contexts, that is, alongside many different organizations in affiliation trajectories. 
+Likewise, an organization such as Harvard with a small norm appears in many contexts, alongside many different organizations in affiliation trajectories. 
 The concavity emerges in part from the relationship between the size of the vector and the expected connectedness of the organization given its size (Fig.~\ref{fig:length}a, inset, $R^{2} = 0.17$).
@@
 
-This same convex-curve repeats irrespective of country, such as China and Germany, though the curve may be shifted based on the typical size and vector length of their organizations (Fig.~\ref{fig:length}b).
-The relative position of these curves can reveal characteristics about the scientific systems in each country. 
-For example,
-
-This 
-Here, interpret the vector length instead as a measure of an organization's connectedness to other organizations given its size, where a connection is defined as a non-zero flow between organizations.
-for example, organizations with a small L2 norm tend to also have a lower number of connections given their size (Fig.~\ref{fig:length}b, inset, $R^{2} = 0.17$). 
-Large and prestigious universities can be considered as having a shorter vector length than expected given their size, reflecting their ability to attract researchers from many places, to place graduates in positions around the world, and the capacity to encourage mobility by offering temporary and visiting researcher positions.
-At the national level, the relative position of the convex-curves can reveal characteristics of their scientific organizations—for example, compared to the United States, Chinese organizations have a longer typical vector length (Fig.~\ref{fig:length}b) reflecting lower overall connectedness in the embedding space.
-Prestige is a key component academic mobility—by encoding information relating to prestige, neural embeddings offer a means of better representing functional distance between organizations and capturing the global landscape of mobility.
+This same convex-curve repeats across many countries, though with variations that can reveal characteristics about the scientific systems of each country (Fig.~\ref{fig:length}b). 
+For example, Chinese organizations have a longer average embedding vector length ($\bar{l} = 4.81$) than organizations in the United States ($\bar{l} = 0.421$), reflecting the tendency for organizations in the United States to appear more frequently in more different contexts than Chinese organizations.
+Smaller but scientifically advanced countries such as Sweden, and other large populous countries like Brazil exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset), a pattern repeated across most of the 20 countries with the most researchers (Fig.~\ref{fig:concave20}).
+Other nations exhibit different curves, such as Egypt which has an "S"-shaped curve---their largest organizations do not have smaller vectors, as in many other countries. 
+Other nations such as Poland and Turkey demonstrate a linear relationship between an organization's number of researchers and the vector size, indicating that their largest organizations belong to very specific contexts (Fig.~\ref{fig:concave20}).
+By encoding whether an organization will appear in specific or many different contexts, organization embeddings offer a way to characterize universal and particularistic patterns of mobility across countries.
 
@@
 		\textbf{b.} This convex pattern repeats globally for all organizations across all countries, shown for the United States, China, and others,
-		The loess regression lines are shown for each selected country, and for the aggregate of remaining countries. 
+		The loess regression lines are shown for each selected country, and for the aggregate of remaining countries, with 99\% confidence intervals. 
+		Loess lines are also shown for organizations in Sweden, Brazil, and Egypt (inset).
 	}
@@
 		Dots correspond to organizations.	
-		The red line is the line of  the best fit. 
+		The red line is the line of  the best fit with corresponding 99\% confidence intervals. 
 		Red text is the regression estimate.
+		The blue line is the loess regression line with 99\% confidence intervals.
 		Number of authors is the average annual count of unique mobile and non-mobile authors.
@@
 
+%
+% Figure - Concave-curves countries
+%
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/Math/boomerang_20_countries.pdf}
+	\caption{
+		\textbf{Concave-curve repeats across most of 20 countries with most researchers.}
+		Size (L2 norm) of organization embedding vectors compared to their number of researchers for U.S. universities.
+		Loess regression line is shown for each country with 99\% confidence intervals. 
+		Countries shown are the top 20 countries with the largest number of total unique researchers, as derived from our bibliographic data. 
+	}
+	\label{fig:concave20}
+\end{figure}
+
 \clearpage

### 2020-07-23 paper/current/main.tex
updates to conclusion

@@
 This same convex-curve repeats across many countries, though with variations that can reveal characteristics about the scientific systems of each country (Fig.~\ref{fig:length}b). 
-For example, Chinese organizations have a longer average embedding vector length ($\bar{l} = 4.81$) than organizations in the United States ($\bar{l} = 0.421$), reflecting the tendency for organizations in the United States to appear more frequently in more different contexts than Chinese organizations.
+For example, Chinese organizations have a longer average embedding vector size ($\bar{l} = 4.81$) than organizations in the United States ($\bar{l} = 0.421$), reflecting the tendency for organizations in the United States to appear more frequently in more different contexts than Chinese organizations.
 Smaller but scientifically advanced countries such as Sweden, and other large populous countries like Brazil exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset), a pattern repeated across most of the 20 countries with the most researchers (Fig.~\ref{fig:concave20}).
@@
 %
-% Figure - SemAxis results
+% Figure - Boomerang
 %
@@
 		A convex-shape emerges, wherein larger universities tend to more distant from the origin (large L2 norm), however the more prestigious the university, the closer it is to the origin (small L2 norm).
-		The L2 norm is correlated weakly with the number of connection divided by the number of researchers in organization, which can be interpreted diversity of the connection compared to their size ($R^{2} = 0.17$, \textbf{inset}).
+		The L2 norm is correlated weakly with the ratio between organization's of number of connected organizations and its number of researchers ($R^{2} = 0.17$, \textbf{inset}).
 		The red line is the line of the best fit, and 99\% confidence intervals are shown. 
@@
 
-Neural embeddings offer a novel approach for learning an effective and robust functional distance between places based on affiliation trajectory data that captures the complex and multi-faceted nature of mobility.
-Here, we demonstrated how the embedding space encodes aspects scientific mobility, such as the  global and regional geography, national shared languages, and the hierarchy of organizational prestige. 
+Neural embeddings offer a novel, data-driven solution for learning an effective and robust functional distance between places based on trajectory data.
+By virtue of being data-driven, and by the nature of neural embedding, it encodes the complex and multi-faceted nature of mobility. 
+Here, we demonstrated how the embedding space encodes various aspects of scientific mobility, such as the  global and regional geography, national shared languages, and the hierarchy of organizational prestige, even without explicit information of these factors.
 While scientific mobility is used as a case study, this approach can be broadly applied to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
@@
 In addition to providing a functional distance that supports modeling and predicting mobility patterns, the unique structure of the neural embedding space is amenable to a range of unique applications for studying mobility.
-As we have shown, projecting the embedding space onto two dimensions using UMAP~\autocite{mcinnes2018umap} allows for the visualization of the complex structure of scientific mobility at high resolution and at multiple scales, providing the largest and most detailed map of global scientific mobility to date.
-Other techniques, such as SemAxis~\autocite{an2018semaxis}, also allow the potential to quantify abstract notions in mobility such as academic prestige, and can also be generalized to other abstract axes.
-Investigation of the structure of the embedding space, such as the vector length, reveals unique and universal patterns based on organization's size and connectedness, and could contribute to deeper understandings of scientific mobility.
+As we have shown allows the visualization of the complex structure of scientific mobility at high resolution across multiple scales, providing the largest and most detailed map of global scientific mobility to date.
+Other techniques, such as SemAxis~\autocite{an2018semaxis}, also allow us to quantify abstract notions in mobility such as academic prestige, and can also be generalized to other abstract axes.
+Investigation of the structure of the embedding space, such as the vector size, reveals unique and universal patterns based on organization's size and connectedness, and could contribute to deeper understandings of scientific mobility.
 Neural embedding opens the door for new approaches to represent and study scientific mobility, and also mobility more generally.

### 2020-07-23 notebooks/embedding_boomerang_plots.rmd
added points to 20 country plot, changed line color

@@
   ggplot(aes(x = size, y = `l2-norm`)) +
+  geom_point(alpha = 0.3) +
   stat_smooth(
     method = "loess",
-    size = 2,
+    size = 1,
     se = T,
     level = 0.99,
-    color = "black",
-    fill = "black",
+    color = "#2980b9",
+    fill = "#2980b9",
     alpha = 0.4,

### 2020-07-24 paper/current/main.tex
edit abstrct minor

@@
 However, geographic distance is less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} wherein the physical barrier shrinks while linguistic, economic, cultural, and historical similarities matter more.
-Alternative notions of functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} attempt to re-define distance by using some of the aforementioned factor~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional} but are often arbitrary, and consider only single isolated facets.
+Alternative notions of functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} attempt to re-define distance by using some of aforementioned factors~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional} but are often arbitrary and consider only single isolated facets.
 Here, using a rich dataset of scientific mobility, we demonstrate that a data-driven neural embedding approach~\autocite{mikolov2013word2vec} can successfully encodes a functional distance between organizations and captures the latent and multi-faceted structure of scientist's mobility.
 We demonstrate that the cosine distance between organization embedding vectors, constructed using the affiliation trajectories of scientists in the Web of Science database, better explain and predict real mobility than geographic distance.
-Exploiting their unique properties, we idemonstrate that the embedding space encodes not only geographic relations between organizations, but also relations based on culture, language, and academic prestige at multiple levels of granularity.
+Exploiting their unique properties, we demonstrate that the embedding space encodes not only geographic relations between organizations, but also relations based on culture, language, and academic prestige at multiple levels of granularity.
 Also captured in the embedding space is a universal pattern capturing the relationship between organization's size and their connectedness.

### 2020-07-24 paper/current/main.tex
edit introduction and figure out in-vector and out-vector things in method section

@@
 Moreover, functional distances typically only focus on a single facet of mobility at a time, whereas real-world mobility is multi-faceted, influenced simultaneously by geography, language, culture, history, and economic opportunity.
-To capture the complexity of human mobility, and so new approaches are needed to incorporate its many facets into a single high-resolution measure of functional distance.
+To capture such complexity of human mobility, new approaches are needed to incorporate its many facets into a single high-resolution functional distance.
 
@@
 Moreover, scientific mobility has known structure, such as the centrality of the United States and the United Kingdom, and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career} that should be captured in a representation.
-However, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}.
-Underlying these challenges is the diminishing role of geography and geographic distance in shaping the landscape of scientific mobility.
+However, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics} and one of the underlying these challenges is the diminishing role of geography in shaping the landscape of scientific mobility.
 
@@
 %% Mobility sentences
-We embed co-affiliation trajectories by treating them analogously to sentences, and organizations analogously to words.
+We embed co-affiliation trajectories by treating them analogously to sentences and organizations analogously to words.
 The trajectories of mobile authors were converted to ``affiliation trajectories'' by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:methods:mobility_sentence}.a.
@@
 %% word2vec
-These affiliation trajectories are used as input to the standard skip-gram negative sampling model, for word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec} .
-In natural-language processing, word embeddings are used to construct dense vector-space representations of words and phrases, in which distance relationships between words correspond to a notion of semantic distance.
+These affiliation trajectories are used as input to the standard skip-gram negative sampling word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec} .
+\textit{word2vec} constructs dense vector representations of words and phrases, in which distance relationships between words correspond to a notion of semantic distance.
+There are two types of embedding vectors in the model; in-vector and out-vector.
+In-vector is usually mainly used as a representation vector of each word \autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch} and we also used in-vector in this study.
 By embedding affiliation trajectories, we aim to learn a dense vector for every organization where the distance between vectors relates to the tendency for two organizations to co-occur in a token window around the target organization token in the same career trajectory.

### 2020-07-24 paper/current/main.tex
edit first main para and cover comment on page 4

@@
 The embedding distance also out-performs alternative ``diffusion-based'' network distance measures such as the personalized-page rank scores (see supporting materials) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+A reasonable explanation behind these results is that raw network distance measures cannot capture high-order interaction because the network is the first-order Markov process model of the system, while the neural embedding can leverage it.
+Also, raw network distance measures are well-known for vulnerable on random error \autocite{holme2002attack}.
 Our results unequivocally argue that the distance learned by the embedding method better captures actual mobility patterns than does geographic distance.

### 2020-07-24 paper/current/main.tex
edit figure 2 caption
cover comment on page 5

@@
 		Black dots are mean flux across binned distances.
-		Error bars are 99\% confidence intervals.
+		Error bars represent 99\% confidence intervals.
 		The lightness of each hex bin indicates the frequency of organization pairs within it.
@@
 The embedding space also allows us to \textit{zoom in} on subsets and re-project them in order to reveal more local relationships. 
-For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries between Egypt to Philippines that corresponds largely to geography, but with some peculiar exceptions.
+For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries between Egypt to Philippines that corresponds largely to geography, but with some peculiar exceptions based on cultural and religious spectrum.
 For example, countries like Iraq are nearer to some southeast-Asian countries like Malaysia, with a cosine distance between the nation's aggregate vectors of $d = 0.29$, than to nearer and more religiously-similar nations like Saudi Arabia ($d = 0.50$) and Qatar ($d = 0.51$).
 Linguistic and historical ties are also conspicuous.
-For example, we observe that Spanish-speaking post-colonial Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), rather than nearby Portuguese-speaking nation ($d = 0.34$ vs.
+For example, we observe that Spanish-speaking post-colonial Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), rather than nearby Portuguese-speaking nations ($d = 0.34$ vs.
 $d = 0.52$ for Mexico and $d = 0.39$ vs.

### 2020-07-24 paper/current/main.tex
update 2nd para
edit final main para

@@
 For example, we can examine the high-level structure by estimating the aggregate embeddings of countries. 
-Namely, we define the representative vector of each country as the average of their organizational vectors.
+Namely, we can define the representative vector of each country as the average of their organizational vectors.
 We then perform hierarchical clustering of nations that have at least 25 organizations represented in the embedding space, excluding the United States which is a dominant hub well connected to most other countries (see Fig.
@@
 
-Prestige hierarchy is known to underpin the dynamics of scientific mobility~\autocite{deville2014career, clauset2015hierarchy}, but can this hierarchy be encoded in the embedding space, to which no explicit information on prestige is given?
+Prestige hierarchy is known to underpin the dynamics of scientific mobility~\autocite{deville2014career, clauset2015hierarchy}, but can the hierarchy be encoded in the embedding space, to which no explicit information on prestige is given?
 We test this by exploiting the geometric properties of the embedding space with SemAxis~\autocite{an2018semaxis}, an approach originally designed to characterize the semantics of words in word embeddings.
@@
 We define prestige using the Times Ranking of World Universities (and using research impact from the Leiden Rankings~\autocite{waltman2012leidenrankings} in Supplementary Materials), including all ranked universities in the United States;
-the high-ranked pole is defined as the mean vector of the top five U.S.
+the high-rank pole is defined as the mean vector of the top five U.S.
 universities according to the rankings, whereas the low-ranked pole is defined using the five bottom-ranked and geographically matched (by U.S.
@@
 We derive a ranking for universities using the SemAxis prestige axis in Fig.~\ref{fig:semaxis}a and compare them to traditional university rankings.
-The SemAxis ranking is defined from the position of organizations along the prestige axis, with the top-ranked being the furthest towards the high-ranked end of the axis.
+The embedding based ranking is defined from the position of organizations along the prestige axis, with the top-ranked being the furthest towards the high-ranked end of the axis.
 We find that the embedding-based ranking is strongly correlated with the Times ranking (Spearman's $\rho = 0.73$, Fig.~\ref{fig:semaxis}e).
-The strongest outliers that were ranked more highly in the Times Ranking than the SemAxis ranking tend to be large state universities such as Arizona State University and  University of Florida;
-Those ranked higher in the SemAxis ranking tend to be relatively-smaller universities such as the University of San Francisco and University of Maryland Baltimore County that are close to other prestigious universities.
-
-The correlation between SemAxis and the Times ranking is robust with the number of organizations used to define the axes (Fig.
+The strongest outliers that were ranked more highly in the Times Ranking than the embedding based ranking tend to be large state universities such as Arizona State University and  University of Florida;
+Those ranked higher in the embedding based ranking tend to be relatively-smaller universities such as the University of San Francisco and University of Maryland Baltimore County that are close to other prestigious universities.
+
+The correlation between the embedding based ranking and the Times ranking is robust with the number of organizations used to define the axes (Fig.
 SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities are significantly correlated with the Times Ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
-For reference, the SemAxis-derived ranking achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking~\autocite{waltman2012leidenrankings}, a well-known and bibliometrically-informed university ranking (Spearman's $\rho = 0.87$, Fig.~\ref{fig:semaxis}f).
+For reference, the embedding-based ranking achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking~\autocite{waltman2012leidenrankings}, a well-known bibliometrically-informed university ranking (Spearman's $\rho = 0.87$, Fig.~\ref{fig:semaxis}f).
 This suggests that the organization embedding captures the latent prestige hierarchy inherent to academic mobility, even without providing any explicit information on prestige, with a high degree of resolution and reliability~\autocite{deville2014career, clauset2015hierarchy}.
@@
 organizations here are primarily research-intensive and prestigious universities with higher rankings, research outputs, R\&D funding, and doctoral students (Fig.~\ref{fig:supp:length_vs_metaInfo}).
-A similar pattern has been observed in applications of neural embedding to natural language, wherein the size of word vectors were found to represent word ``significance''~\autocite{schakel2015measuring}.
+A similar pattern has been observed in applications of neural embedding to natural language, wherein the size of word vectors was found to represent the word ``significance''~\autocite{schakel2015measuring}.
 If a word appears frequently in a specific context, the norm of the word vector is likely to be large, because a large norm is associated with how predictably the word occurs given a context.
@@
 Likewise, an organization such as Harvard with a small norm appears in many contexts, alongside many different organizations in affiliation trajectories. 
-The concavity emerges in part from the relationship between the size of the vector and the expected connectedness of the organization given its size (Fig.~\ref{fig:length}a, inset, $R^{2} = 0.17$).
-Large, prestigious, and well-funded research universities such as Princeton and Harvard have smaller vector sizes because they appear in many different contexts compared to more teaching-focused organizations such as NY Medical College, and University of Michigan at Flint.
-Some universities, such as the University of Alaska at Fairbanks, have surprisingly small vectors, perhaps as a result of its remote location and unique circumstances.
+The concavity can overlap into a single line, implying the size of the vector is related to the connectedness of the organization given its size (Fig.~\ref{fig:length}a, inset, $R^{2} = 0.17$).
+Large, prestigious, and well-funded research universities such as Princeton and Harvard have smaller vector sizes because they appear in many different contexts compared to more teaching-focused organizations such as NY Medical College, and the University of Michigan at Flint.
+% Some universities, such as the University of Alaska at Fairbanks, have surprisingly small vectors, perhaps as a result of its remote location and unique circumstances. (I think it hurts the context)
 
 This same convex-curve repeats across many countries, though with variations that can reveal characteristics about the scientific systems of each country (Fig.~\ref{fig:length}b). 
-For example, Chinese organizations have a longer average embedding vector size ($\bar{l} = 4.81$) than organizations in the United States ($\bar{l} = 0.421$), reflecting the tendency for organizations in the United States to appear more frequently in more different contexts than Chinese organizations.
+For example, Chinese organizations have a longer average embedding vector size ($\bar{l} = 4.81$) than organizations in the United States ($\bar{l} = 4.21$), reflecting the tendency for organizations in the United States to appear more frequently in more different contexts than Chinese organizations.
 Smaller but scientifically advanced countries such as Sweden, and other large populous countries like Brazil exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset), a pattern repeated across most of the 20 countries with the most researchers (Fig.~\ref{fig:concave20}).
-Other nations exhibit different curves, such as Egypt which has an "S"-shaped curve---their largest organizations do not have smaller vectors, as in many other countries. 
-Other nations such as Poland and Turkey demonstrate a linear relationship between an organization's number of researchers and the vector size, indicating that their largest organizations belong to very specific contexts (Fig.~\ref{fig:concave20}).
-By encoding whether an organization will appear in specific or many different contexts, organization embeddings offer a way to characterize universal and particularistic patterns of mobility across countries.
+Other nations exhibit different curves, such as Egypt which has an ``S"-shaped curve---their largest organizations do not have smaller vectors, as in many other countries. 
+Other nations such as Poland and Turkey demonstrate a linear relationship between an organization's number of researchers and the vector size, indicating that their largest organizations belong to specific contexts (Fig.~\ref{fig:concave20}).
+%By encoding whether an organization will appear in specific or many different contexts, organization embeddings offer a way to characterize universal and particularistic patterns of mobility across countries.
 

### 2020-07-24 paper/current/main.tex

@@
 By virtue of being data-driven, and by the nature of neural embedding, it encodes the complex and multi-faceted nature of mobility. 
-Here, we demonstrated how the embedding space encodes various aspects of scientific mobility, such as the  global and regional geography, national shared languages, and the hierarchy of organizational prestige, even without explicit information of these factors.
+Here, we demonstrated how the embedding space encodes various aspects of scientific mobility, such as the global and regional geography, national shared languages, and the hierarchy of organizational prestige, even without explicit information on these factors.
 While scientific mobility is used as a case study, this approach can be broadly applied to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
@@
 In addition to providing a functional distance that supports modeling and predicting mobility patterns, the unique structure of the neural embedding space is amenable to a range of unique applications for studying mobility.
-As we have shown allows the visualization of the complex structure of scientific mobility at high resolution across multiple scales, providing the largest and most detailed map of global scientific mobility to date.
+As we have shown, the embedding space allows the visualization of the complex structure of scientific mobility at high resolution across multiple scales, providing the largest and most detailed map of global scientific mobility to date.
 Other techniques, such as SemAxis~\autocite{an2018semaxis}, also allow us to quantify abstract notions in mobility such as academic prestige, and can also be generalized to other abstract axes.
-Investigation of the structure of the embedding space, such as the vector size, reveals unique and universal patterns based on organization's size and connectedness, and could contribute to deeper understandings of scientific mobility.
+Investigation of the structure of the embedding space, such as the vector size, reveals unique and universal patterns based on organization's size and connectedness and could contribute to deeper understandings of scientific mobility.
 Neural embedding opens the door for new approaches to represent and study scientific mobility, and also mobility more generally.

### 2020-07-24 workflow/scripts/PlotBoomerangCompare.R
code to plot all boomerang compare-to-usa figures

@@ -1,0 +1,130 @@
+#
+# PlotBoomerangCompare.R
+#
+# author: Dakota Murray
+#
+# Plot the comparison of the Boomerang plot between two countries
+#
+
+# Preset colors for specific countries, other defaults to grey
+col_list <- list(
+  "USA" = "#d35400",
+  "BRA" = "#27ae60",
+  "SWD" = "#8e44ad",
+  "EGY" = "black"
+)
+
+# Plot dimensions
+FIG_WIDTH = 3
+FIG_HEIGHT = 3
+
+library(ggplot2)
+library(dplyr)
+suppressPackageStartupMessages(require(optparse))
+
+# Command line arguments
+option_list = list(
+  make_option(c("-i", "--input"), action="store", default=NA, type='character',
+              help="Path to file containing the factor orgs for each org"),
+  make_option(c("--lookup"), action="store", default="none",
+              help="Path to organization-level metadata"),
+  make_option(c("--sizes"), action="store", default="none",
+              help="Path to organization sizes"),
+  make_option(c("--country1"), action="store", default="none",
+              help="Country 1 to comapre"),
+  make_option(c("--country2"), action="store", default="none",
+              help="Country 2 to comapre"),
+  make_option(c("-o", "--output"), action="store", default=NA, type='character',
+              help="Path to save distances")
+) # end option_list
+opt = parse_args(OptionParser(option_list=option_list))
+
+# Read the aggregated distance file
+df = readr::read_csv(opt$input, col_types = readr::cols()) %>%
+  select(cwts_org_no, l2norm)
+
+# Load the sizes and aggregate by org
+sizes <- readr::read_delim(opt$sizes, delim = "\t", col_types = readr::cols()) %>%
+  group_by(cwts_org_no) %>%
+  summarize(size = mean(person_count))
+
+
+# Load the metadata and filter to the select countries
+meta <- readr::read_delim(opt$lookup, delim = "\t", col_types = readr::cols()) %>%
+  filter(country_iso_alpha %in% c(opt$country1, opt$country2)) %>%
+  rename(country = country_iso_name) %>%
+  # rename countries to smaller, simpler versions, if necessary
+  mutate(
+    country = ifelse(country == "Russian Federation", "Russia", country),
+    country = ifelse(country == "Korea, Republic of", "South Korea", country),
[…]

### 2020-07-24 workflow/scripts/calculate_l2norm_country.py
gen file with l2 norm of mean vector by country

@@ -1,0 +1,65 @@
+"""
+
+calculate_l2norm_country.py
+
+author: Dakota Murray
+
+Calculate the l2 norm using the aggregate vector of a
+country's organizations
+
+"""
+
+from gensim.models import Word2Vec
+import pandas as pd
+import numpy as np
+
+import argparse
+parser = argparse.ArgumentParser()
+
+# System arguments
+parser.add_argument("--model", help = "the gensim word2vec model to decompose",
+                    type = str, required = True)
+parser.add_argument("--lookup", help = "Path to the organization lookup file")
+parser.add_argument("-o", "--output", help = "Output data path",
+                    type = str, required = True)
+
+args = parser.parse_args()
+
+# Load the word2vec model
+model = Word2Vec.load(args.model)
+
+meta = pd.read_csv(args.lookup, sep = "\t")
+
+# pre-process the metadata file
+meta = meta.fillna(-1)
+meta = meta.astype({'cwts_org_no': int})
+meta = meta.astype({'cwts_org_no': str})
+
+# Limit the metadata to orgs that are actually in the w2v model vocabulary
+vocab = list(model.wv.vocab.keys())
+meta = meta.loc[meta.cwts_org_no.isin(vocab)]
+
+
+l2_vals = []
+counts = []
+countries = list(set(meta.country_iso_alpha))
+
+# Iterate over countries, calculate mean vector of orgs, and calculate norm
+for country in countries:
+    # Get all the orgs per country
+    orgs = list(meta.loc[meta.country_iso_alpha == country]['cwts_org_no'])
+    # Get the mean vector
+    mu_vec = np.array([model.wv[x] for x in orgs]).mean(axis = 0)
+
+    l2_vals.append(np.linalg.norm(mu_vec))
+    counts.append(len(orgs))
+
+# Build the dataframe
+df = pd.DataFrame({
+    'country': countries,
+    'l2norm': l2_vals,
+    'count': counts,
+})
+
+# Write the output
+df.to_csv(args.output, index = False)

### 2020-07-24 workflow/scripts/PlotBoomerangAllCountries.R
plot aggregate boomerang figure across countries

@@ -1,0 +1,105 @@
+#
+# PlotBoomerangAllCountries.R
+#
+# author: Dakota Murray
+#
+# Plot the boomerang pattern across many countries
+#
+
+# Plot dimensions
+FIG_WIDTH = 7
+FIG_HEIGHT = 9
+
+NUM_COUNTRIES = 30
+
+library(ggplot2)
+library(dplyr)
+suppressPackageStartupMessages(require(optparse))
+
+# Command line arguments
+option_list = list(
+  make_option(c("-i", "--input"), action="store", default=NA, type='character',
+              help="Path to file containing the factor orgs for each org"),
+  make_option(c("--lookup"), action="store", default="none",
+              help="Path to organization-level metadata"),
+  make_option(c("--sizes"), action="store", default="none",
+              help="Path to organization sizes"),
+  make_option(c("-o", "--output"), action="store", default=NA, type='character',
+              help="Path to save distances")
+) # end option_list
+opt = parse_args(OptionParser(option_list=option_list))
+
+# Read the aggregated distance file
+df = readr::read_csv(opt$input, col_types = readr::cols()) %>%
+  select(cwts_org_no, l2norm)
+
+# Load the sizes and aggregate by org
+sizes <- readr::read_delim(opt$sizes, delim = "\t", col_types = readr::cols()) %>%
+  group_by(cwts_org_no) %>%
+  summarize(size = mean(person_count))
+
+# Load the metadata and filter to the select countries
+meta <- readr::read_delim(opt$lookup, delim = "\t", col_types = readr::cols()) %>%
+  rename(country = country_iso_name) %>%
+  # rename countries to smaller, simpler versions, if necessary
+  mutate(
+    country = ifelse(country == "Russian Federation", "Russia", country),
+    country = ifelse(country == "Korea, Republic of", "South Korea", country),
+    country = ifelse(country == "Taiwan, Province of China", "Taiwan", country),
+    country = ifelse(country == "Iran, Islamic Republic of", "Iran", country),
+  )
+
+df <- df %>%
+  # join metadata, filtering to select orgs in the process
+  inner_join(meta, by = "cwts_org_no") %>%
+  # join the sizes
+  left_join(sizes, by = "cwts_org_no") %>%
+
+print(head(df))
+# Get the countries to plot
[…]

### 2020-07-24 notebooks/embedding_boomerang_plots.rmd
cleanup redundant code from boomerang notebook

--- 2020-07-21 notebooks/embedding_boomerang_plots.rmd
@@
 
-df <- read_csv("/Users/dakotamurray/Desktop/l2-norm_vs_size.csv")
+#df <- read_csv("/Users/dakotamurray/Desktop/l2-norm_vs_size.csv")
+
 meta <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t")
+
+df <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Embeddings/precedence/factors/d300_ws1_precedence_w2vfactors.csv") %>%
+  select(cwts_org_no, l2norm) %>%
+  left_join(meta, by = "cwts_org_no")
+
 types <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/org_types.csv")
 
+sizes <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/raw/2008-2019_inst_sizes.txt", delim = "\t") %>%
+  group_by(cwts_org_no) %>%
+  summarize(
+    size = mean(person_count)
+  )
+
+df <- df %>% left_join(sizes, by = "cwts_org_no")
 country <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/country_metadata.csv")
@@
 
-df %>%
-  left_join(meta, by = c("name" = "full_name")) %>%
-  left_join(leiden, by = c("cwts_org_no"))
-
-```
-
-```{r}
-plotdata <- df %>%
-  filter(country == "United States") %>%
-  left_join(types) %>%
-  filter(org_type_simplified %in% c("University", "Government", "Institute", "Teaching")) %>%
-  mutate(
-    org_type_simplified = factor(org_type_simplified,
-                                 levels = c("University", "Teaching", "Institute", "Government"))
-  )
-
-plotdata %>%
-  ggplot(aes(x = size, y = `l2-norm`, color = org_type_simplified, shape = org_type_simplified, label = name)) +
-  geom_point() +
-  scale_x_log10(
-    breaks = scales::trans_breaks("log10", function(x) 10^x),
-    labels = scales::trans_format("log10", scales::math_format(10^.x))
-  ) +
-  scale_shape_manual(values = c(16, 1, 1, 1)) +
-  #scale_color_manual(values = c(""))
-  scale_color_manual(values = c("#2c3e50", "#c0392b", "#8e44ad", "#27ae60")) +
-  theme_minimal() +
-  theme(
-    text = element_text(size = 12, family = "Helvetica"),
-    panel.grid.minor = element_blank()
-  ) +
-  annotation_logticks(sides = "b") +
-  xlab("Organization size") +
-  ylab("L2 Norm")
-
-plotly::ggplotly()
-```
-
-```{r}
-
 labels <- c("Harvard University", "University of Alaska, Fairbanks", "Reykjavik University",
@@
 plotdata <- df %>%
-  filter(country == "United States") %>%
+  filter(country_iso_alpha == "USA") %>%
   filter(org_type == "University") %>%
-  left_join(meta, by = c("name" = "full_name")) %>%
+  #left_join(meta, by = c("name" = "full_name")) %>%
   #left_join(leiden, by = c("cwts_org_no"))
@@
 plotlabs <- plotdata %>%
-  filter(name %in% labels) %>%
+  filter(full_name %in% labels) %>%
   mutate(
-    label = gsub('University', 'Univ', name),
+    label = gsub('University', 'Univ', full_name),
     label = gsub('(.{1,24})(\\s|$)', '\\1\n', label),
@@
 plot <- plotdata %>%
-  ggplot(aes(x = size, y = `l2-norm`, color = rank, shape = is.na(rank), label = name)) +
+  ggplot(aes(x = size, y = l2norm, color = rank, shape = is.na(rank), label = full_name)) +
   geom_point() +
@@
   mutate(
-    highlight = ifelse(country %in% c("China", "United States", "Germany"), country, "Other"),
-    highlight = factor(highlight, levels = c("United States", "China", "Germany", "Other"))
+    highlight = ifelse(country_iso_name %in% c("China", "United States"), country_iso_name, "Other"),
+    highlight = factor(highlight, levels = c("United States", "China", "Other"))
   ) %>%
-  ggplot(aes(x = size, y = `l2-norm`, label = name, alpha = highlight, shape = highlight, color = highlight)) +
-  geom_point(alpha = 0.5) +
+  ggplot(aes(x = size, y = l2norm, fill = highlight, shape = highlight, color = highlight, linetype = highlight)) +
+  geom_point(alpha = 0.2) +
   stat_smooth(
     method = "loess",
-    size = 1.25,
-    se = F
+    size = 1.5,
+    level = 0.99,
+    se = T,
+    alpha = 0.6
   ) +
-  scale_shape_manual(values = c(16, 16, 16, 1)) +
-  scale_color_manual(values = c("#66c2a5", "#fc8d62", "#8da0cb", "darkgrey")) +
-  scale_fill_manual(values = c("#66c2a5", "#fc8d62", "#8da0cb", "grey")) +
-  scale_alpha_manual(values = c(1, 1, 1,  0.6)) +
+  scale_shape_manual(values = c(16, 16, 1)) +
+  scale_color_manual(values = c("#d35400", "#2980b9", "darkgrey")) +
+  scale_linetype_manual(values = c(2, 2, 1)) +
+  scale_fill_manual(values = c("#d35400", "#2980b9", "grey")) +
   scale_x_log10(
@@
 ```{r}
-leiden
+selected <- (df %>%
+  group_by(country_iso_alpha) %>%
+  summarize(total = sum(size)) %>%
+  top_n(30, total))$country_iso_alpha
 
+tab <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Embeddings/precedence/norm/d300_ws1_precedence_norm_by_country.csv")
+
+tab <- tab %>%
+  filter(country %in% selected) %>%
+  mutate(
+    country = ifelse(country == "Russian Federation", "Russia", country),
+    country = ifelse(country == "Korea, Republic of", "South Korea", country),
+    country = ifelse(country == "Taiwan, Province of China", "Taiwan", country),
+    country = ifelse(country == "Iran, Islamic Republic of", "Iran", country),
+  ) %>%
+  arrange((l2norm))
+
+write_csv(tab, "~/Desktop/norm_by_country.csv")
 ```

### 2020-07-24 notebooks/semaxis_notebook.rmd
updated with table, new supp figure, and new text related to fig 6

---
title: "SemAxis plotting"
output: html_notebook
---

```{r}
org_types <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/org_types.csv")
lookup <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t", col_types = readr::cols()) %>%
  filter(country_iso_alpha == "USA") %>%
  left_join(org_types, by = c("org_type")) %>%
  filter(org_type_simplified == "Government") %>%
  select(cwts_org_no, org_type, full_name)

lookup %>%
  filter(org_type == "Funding Organisation")
```

```{r}
library(readr)
library(tidyverse)
org_types <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/org_types.csv")
# Load organization meta-info
lookup <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t", col_types = readr::cols()) %>%
  filter(country_iso_alpha == "USA") %>% # select only the specified country
  select(cwts_org_no, country_iso_alpha, region, org_type, org_type_code, full_name) %>%
  left_join(org_types, by = "org_type")
  #filter(org_type_simplified == "Institute") # select only universities
  #filter(org_type_simplified == "Institute" | org_type_simplified == "Government") # select only universities

axis2 <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/SemAxis/precedence/prestige/times_d300_ws1_n20_precedence_semaxis.csv", col_types = readr::cols())

# Load the axis data and filter to only specified countries
sims <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/SemAxis/precedence/geography/coasts_d300_ws1_n20_semaxis.csv", col_types = readr::cols()) %>%
  inner_join(lookup, by = "cwts_org_no") %>%
  inner_join(axis2, by = "cwts_org_no")

```

```{r}
plotdata <- sims
library(plotly)

plotdata %>%
  filter(org_type_simplified == "Institute") %>%
  top_n(-1, sim.y)

p <- plotdata %>%
  ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(x = sim.x, y = sim.y, label1 = full_name, label2 = cwts_org_no),
             size = 3.5,
             shape = 16,
             fill = "lightgrey",
             alpha = 0.2,
             data = subset(plotdata, org_type_simplified == "Government")
           ) +
  #geom_point(aes(x = sim.x, y = sim.y, label = full_name),
  #           size = 3.5,
  #           shape = 21,
  #           fill = "#f39c12",
  #           alpha = 1.0,
  #           data = subset(plotdata, org_type_simplified == "Government")
  #         ) +
  theme_minimal() +
  theme(
    text = element_text(family = "Helvetica", size = 11),
    axis.title.x = element_text(angle = 0, size = 12, face = "bold", vjust = 0.5),
    axis.title.x.top = element_text(angle = 0, size = 12, face = "bold", vjust = 0.5),
    axis.title.y = element_text(angle = 0, size = 12, face = "bold", vjust = 0.5),
    axis.title.y.right = element_text(angle = 0, size = 12, face = "bold", vjust = 0.5),
    legend.text = element_text(size = 12),
    legend.title = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "bottom"
  )

p

widget <- ggplotly(p, tooltip = c("full_name", "cwts_org_no", "region", "city"))
widget
```

```{r}
# Load organization meta-info
lookup <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t", col_types = readr::cols()) %>%
  filter(country_iso_alpha == "GBR" & org_type_code == "U") %>% # select only the specified country
  select(cwts_org_no, country_iso_alpha, region, org_type, org_type_code, full_name)

axis2 <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/SemAxis/precedence/prestige/leiden_d300_ws1_n20_precedence_semaxis.csv", col_types = readr::cols())

# Load the axis data and filter to only specified countries
sims <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/SemAxis/precedence/geography/coasts_d300_ws1_n20_semaxis.csv", col_types = readr::cols()) %>%
  inner_join(lookup, by = "cwts_org_no") %>%
  inner_join(axis2, by = "cwts_org_no")

```

```{r}
plotdata <- sims
library(plotly)

p <- plotdata %>%
  ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(x = sim.x, y = sim.y, label = full_name),
             size = 3.5,
             shape = 16,
             fill = "lightgrey",
             alpha = 0.2,
             #data = subset(plotdata, org_type_simplified == "Institute")
           ) +
  theme_minimal() +
  theme(
    text = element_text(family = "Helvetica", size = 11),
    axis.title.x = element_text(angle = 0, size = 12, face = "bold", vjust = 0.5),
    axis.title.x.top = element_text(angle = 0, size = 12, face = "bold", vjust = 0.5),
    axis.title.y = element_text(angle = 0, size = 12, face = "bold", vjust = 0.5),
    axis.title.y.right = element_text(angle = 0, size = 12, face = "bold", vjust = 0.5),
    legend.text = element_text(size = 12),
    legend.title = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "bottom"
  )

p

widget <- ggplotly(p, tooltip = c("full_name", "region", "city"))
widget
```

```{r}
# Load organization meta-info
lookup <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t", col_types = readr::cols()) %>%
  filter(country_iso_alpha %in% c("GBR", "JPN") & org_type_code == "U") %>% # select only the specified country
  select(cwts_org_no, country_iso_alpha, region, org_type, org_type_code, full_name)

axis2 <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/SemAxis/precedence/prestige/leiden_d100_ws1_n1_precedence_semaxis.csv", col_types = readr::cols())

# Load the axis data and filter to only specified countries
sims <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/SemAxis/precedence/geography/coasts_d100_ws1_n20_semaxis.csv", col_types = readr::cols()) %>%
  inner_join(lookup, by = "cwts_org_no") %>%
  inner_join(axis2, by = "cwts_org_no")

```

```{r}
plotdata <- sims
library(plotly)

p <- plotdata %>%
  ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(x = sim.x, y = sim.y, label = full_name, fill = country_iso_alpha),
             size = 3.5,
             shape = 21,
             #fill = "lightgrey",
             alpha = 0.8,
             #data = subset(plotdata, org_type_simplified == "Institute")
           ) +
  theme_minimal() +
  theme(
    text = element_text(family = "Helvetica", size = 11),
    axis.title.x = element_text(angle = 0, size = 12, face = "bold", vjust = 0.5),
    axis.title.x.top = element_text(angle = 0, size = 12, face = "bold", vjust = 0.5),
    axis.title.y = element_text(angle = 0, size = 12, face = "bold", vjust = 0.5),
    axis.title.y.right = element_text(angle = 0, size = 12, face = "bold", vjust = 0.5),
    legend.text = element_text(size = 12),
    legend.title = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "bottom"
  )

p

widget <- ggplotly(p, tooltip = c("full_name", "region", "city"))
widget
```

```{r}

times <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/times_ranking.csv")
leiden <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/leiden_ranking.csv")

lookups <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/institution_lookup_with_states.txt")

sims <- lookup %>%
  filter(country_iso_alpha == "USA") %>%
  left_join(times, by = c("cwts_org_no")) %>%
  inner_join(leiden, by = c("cwts_org_no")) %>%
  select(full_name, cwts_org_no, total_score, impact_frac_mncs) %>%
  arrange(desc(total_score)) %>%
  mutate(
    times_rank = row_number()
  ) %>%
  arrange(desc(impact_frac_mncs)) %>%
  mutate(
    leiden_rank = row_number()
  )

# Build the plot
plot <- sims %>%
  ggplot(aes(x = times_rank, y = leiden_rank)) +
  geom_abline() +
  geom_point(size = 3.5, stroke = 0.5) +
  # Add a fake top axis title, just to ensure that its the same size as the 2d fig
  scale_x_continuous(limits = c(0, 150), sec.axis = dup_axis(name = "")) +
  scale_y_continuous(limits = c(0, 150)) +
  scale_shape_manual(values = c(1, 16)) +
  guides(shape = F) +
  theme_minimal() +
  theme(
    text = element_text(size = 12, family = "Helvetica"),
    axis.text.x.top = element_blank(),
    axis.title = element_text(size = 14, face = "bold"),
    panel.grid.minor = element_blank(),
  ) +
  ylab("") +
  xlab("SemAxis Rank")

plot

```

### 2020-07-24 paper/current/main.tex
updated with table, new supp figure, and new text related to fig 6

--- 2020-07-24 paper/current/main.tex
@@
 However, geographic distance is less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} wherein the physical barrier shrinks while linguistic, economic, cultural, and historical similarities matter more.
-Alternative notions of functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} attempt to re-define distance by using some of aforementioned factors~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional} but are often arbitrary and consider only single isolated facets.
+Alternative notions of functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} attempt to re-define distance by using some of the aforementioned factor~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional} but are often arbitrary, and consider only single isolated facets.
 Here, using a rich dataset of scientific mobility, we demonstrate that a data-driven neural embedding approach~\autocite{mikolov2013word2vec} can successfully encodes a functional distance between organizations and captures the latent and multi-faceted structure of scientist's mobility.
 We demonstrate that the cosine distance between organization embedding vectors, constructed using the affiliation trajectories of scientists in the Web of Science database, better explain and predict real mobility than geographic distance.
-Exploiting their unique properties, we demonstrate that the embedding space encodes not only geographic relations between organizations, but also relations based on culture, language, and academic prestige at multiple levels of granularity.
+Exploiting their unique properties, we idemonstrate that the embedding space encodes not only geographic relations between organizations, but also relations based on culture, language, and academic prestige at multiple levels of granularity.
 Also captured in the embedding space is a universal pattern capturing the relationship between organization's size and their connectedness.
@@
 Moreover, functional distances typically only focus on a single facet of mobility at a time, whereas real-world mobility is multi-faceted, influenced simultaneously by geography, language, culture, history, and economic opportunity.
-To capture such complexity of human mobility, new approaches are needed to incorporate its many facets into a single high-resolution functional distance.
+To capture the complexity of human mobility, and so new approaches are needed to incorporate its many facets into a single high-resolution measure of functional distance.
 
@@
 Moreover, scientific mobility has known structure, such as the centrality of the United States and the United Kingdom, and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career} that should be captured in a representation.
-However, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics} and one of the underlying these challenges is the diminishing role of geography in shaping the landscape of scientific mobility.
+However, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}.
+Underlying these challenges is the diminishing role of geography and geographic distance in shaping the landscape of scientific mobility.
 
@@
 The embedding distance also out-performs alternative ``diffusion-based'' network distance measures such as the personalized-page rank scores (see supporting materials) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-A reasonable explanation behind these results is that raw network distance measures cannot capture high-order interaction because the network is the first-order Markov process model of the system, while the neural embedding can leverage it.
-Also, raw network distance measures are well-known for vulnerable on random error \autocite{holme2002attack}.
 Our results unequivocally argue that the distance learned by the embedding method better captures actual mobility patterns than does geographic distance.
@@
 		Black dots are mean flux across binned distances.
-		Error bars represent 99\% confidence intervals.
+		Error bars are 99\% confidence intervals.
 		The lightness of each hex bin indicates the frequency of organization pairs within it.
@@
 The embedding space also allows us to \textit{zoom in} on subsets and re-project them in order to reveal more local relationships. 
-For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries between Egypt to Philippines that corresponds largely to geography, but with some peculiar exceptions based on cultural and religious spectrum.
+For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries between Egypt to Philippines that corresponds largely to geography, but with some peculiar exceptions.
 For example, countries like Iraq are nearer to some southeast-Asian countries like Malaysia, with a cosine distance between the nation's aggregate vectors of $d = 0.29$, than to nearer and more religiously-similar nations like Saudi Arabia ($d = 0.50$) and Qatar ($d = 0.51$).
 Linguistic and historical ties are also conspicuous.
-For example, we observe that Spanish-speaking post-colonial Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), rather than nearby Portuguese-speaking nations ($d = 0.34$ vs.
+For example, we observe that Spanish-speaking post-colonial Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), rather than nearby Portuguese-speaking nation ($d = 0.34$ vs.
 $d = 0.52$ for Mexico and $d = 0.39$ vs.
@@
 However, if the word in question is universal, appearing frequently in many different contexts, it cannot have a large norm as it lacks a strong association with a particular context. 
-Likewise, an organization such as Harvard with a small norm appears in many contexts, alongside many different organizations in affiliation trajectories. 
+Likewise, an organization such as Harvard with a small norm appears in many contexts, alongside many different organizations in affiliation trajectories---it is well-connected. 
 The concavity emerges in part from the relationship between the size of the vector and the expected connectedness of the organization given its size (Fig.~\ref{fig:length}a, inset, $R^{2} = 0.17$).
@@
 This same convex-curve repeats across many countries, though with variations that can reveal characteristics about the scientific systems of each country (Fig.~\ref{fig:length}b). 
-For example, Chinese organizations have a longer average embedding vector size ($\bar{l} = 4.81$) than organizations in the United States ($\bar{l} = 0.421$), reflecting the tendency for organizations in the United States to appear more frequently in more different contexts than Chinese organizations.
-Smaller but scientifically advanced countries such as Sweden, and other large populous countries like Brazil exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset), a pattern repeated across most of the 20 countries with the most researchers (Fig.~\ref{fig:concave20}).
-Other nations exhibit different curves, such as Egypt which has an "S"-shaped curve---their largest organizations do not have smaller vectors, as in many other countries. 
-Other nations such as Poland and Turkey demonstrate a linear relationship between an organization's number of researchers and the vector size, indicating that their largest organizations belong to very specific contexts (Fig.~\ref{fig:concave20}).
-By encoding whether an organization will appear in specific or many different contexts, organization embeddings offer a way to characterize universal and particularistic patterns of mobility across countries.
+For example, the representative vector of Chinese organizations are larger than that of the United States ($\bar{l} = 2.97$ vs $\bar{l} = 2.39$, Table~\ref{table:supp:norm}), reflecting the tendency for organizations in the United States to appear more frequently in more different contexts than Chinese organizations.
+Smaller but scientifically advanced countries such as Sweden, and other large populous countries like Brazil exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset), a pattern repeated across most countries with large scientific systems (Fig.~\ref{fig:concave30}).
+Other nations exhibit different curves, such as Egypt which has an "S"-shaped curve---their largest organizations do not as well connected as other country's largest organizations. 
+Other nations such as Poland, Iran, and Turkey demonstrate a linear relationship between an organization's number of researchers and the vector size, indicating that their largest organizations belong to very specific contexts (Fig.~\ref{fig:concave30}).
+The organization-level distribution of embedding vector norms reveals even deeper heterogeneity---
+for example, whereas the United States has the smallest representative vector, skewness of the sizes of its organization vectors suggest that this is driven by a small number of especially-well-connected organizations ($s = -0.82$, Fig.~\ref{fig:norm_dist}).
+Germany and the United Kingdom have comparable representative vector sizes to the United States ($\bar{l} = 2.6$ and $\bar{l} = 2.61$, respectively), though they are much less skewed ($s = -0.63$ and $s = -0.55$), suggesting less inequality in the connectedness of organizations in these countries.
+The vector sizes of organizations in some countries are even more skewed, such as in Iran ($\bar{l} = 3.57$, $s = -2.13$), and China ($\bar{l} = 2.97$, $s = -1.08$), indicating the strong difference between their most- and least-connected organizations.
+For some countries, their organizations are positively-skewed, though seemingly for different reasons---
+Austria, for example, has a balanced distribution of organization vector sizes, suggesting a diverse range of organizations with most being well connected ($\bar{l} =2.64$, $s = 0.18$);
+Russia, in contrast, has a high number of organization vectors of moderate size, but also several very isolated organizations with large vector sizes ($\bar{l} = 3.08$, $s = 0.67$). 
+By capturing the connectedness of organizations in the embedding vector size, the embedding space can be used to characterize universal and particularistic patterns of mobility across countries.
 
@@
 		The loess regression lines are shown for each selected country, and for the aggregate of remaining countries, with 99\% confidence intervals. 
-		Loess lines are also shown for organizations in Sweden, Brazil, and Egypt (inset).
+		Loess lines are also shown for organizations in Sweden, Brazil, and Egypt (\textbf{inset}).
 	}
@@
 %% Mobility sentences
-We embed co-affiliation trajectories by treating them analogously to sentences and organizations analogously to words.
+We embed co-affiliation trajectories by treating them analogously to sentences, and organizations analogously to words.
 The trajectories of mobile authors were converted to ``affiliation trajectories'' by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:methods:mobility_sentence}.a.
@@
 %% word2vec
-These affiliation trajectories are used as input to the standard skip-gram negative sampling word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec} .
-\textit{word2vec} constructs dense vector representations of words and phrases, in which distance relationships between words correspond to a notion of semantic distance.
-There are two types of embedding vectors in the model; in-vector and out-vector.
-In-vector is usually mainly used as a representation vector of each word \autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch} and we also used in-vector in this study.
+These affiliation trajectories are used as input to the standard skip-gram negative sampling model, for word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec} .
+In natural-language processing, word embeddings are used to construct dense vector-space representations of words and phrases, in which distance relationships between words correspond to a notion of semantic distance.
 By embedding affiliation trajectories, we aim to learn a dense vector for every organization where the distance between vectors relates to the tendency for two organizations to co-occur in a token window around the target organization token in the same career trajectory.
@@
 \newpage
+
+\begin{table}[]
+\centering
+\caption{\textbf{L2 Norm of country's representative vectors}.
+			 Shown for top 30 countries with the most unique mobile and non-mobile researchers}
+\label{table:supp:norm}
+\begin{tabular}{lrr}
+\textbf{Country} & \textbf{L2 Norm} & \textbf{\# Organizations} \\ \hline
+United States    & 2.39             & 1281                      \\
+Germany          & 2.6              & 485                       \\
+United Kingdom   & 2.61             & 514                       \\
+Austria          & 2.64             & 74                        \\
+France           & 2.83             & 688                       \\
+Belgium          & 2.84             & 84                        \\
+Switzerland      & 2.85             & 66                        \\
+Spain            & 2.94             & 322                       \\
+China            & 2.97             & 497                       \\
+India            & 2.99             & 114                       \\
+Poland           & 3.02             & 145                       \\
+Canada           & 3.02             & 147                       \\
+Italy            & 3.04             & 386                       \\
+Russia           & 3.08             & 187                       \\
+Norway           & 3.1              & 122                       \\
+Netherlands      & 3.11             & 136                       \\
+Sweden           & 3.16             & 75                        \\
+Brazil           & 3.16             & 286                       \\
+Finland          & 3.17             & 66                        \\
+Denmark          & 3.21             & 54                        \\
+Czech Republic   & 3.23             & 97                        \\
+Greece           & 3.24             & 62                        \\
+Australia        & 3.24             & 90                        \\
+Turkey           & 3.28             & 99                        \\
+South Korea      & 3.28             & 156                       \\
+Israel           & 3.32             & 71                        \\
+Portugal         & 3.33             & 57                        \\
+Japan            & 3.35             & 465                       \\
+Iran             & 3.57             & 68                        \\
+Taiwan           & 3.67             & 72                       
+\end{tabular}
+\end{table}
+
+\newpage
+
 %
@@
 	\centering
-	\includegraphics[width=\textwidth]{\figdir/Math/boomerang_20_countries.pdf}
-	\caption{
-		\textbf{Concave-curve repeats across most of 20 countries with most researchers.}
+	\includegraphics[width=\textwidth]{\figdir/Math/boomerang_30_countries.pdf}
+	\caption{
+		\textbf{Concave-curve repeats across most of 30 countries with most researchers.}
 		Size (L2 norm) of organization embedding vectors compared to their number of researchers for U.S. universities.
 		Loess regression line is shown for each country with 99\% confidence intervals. 
-		Countries shown are the top 20 countries with the largest number of total unique researchers, as derived from our bibliographic data. 
-	}
-	\label{fig:concave20}
+		Countries shown are the 30 with the largest number of total unique mobile and non-mobile researchers.
+	}
+	\label{fig:concave30}
+\end{figure}
+
+%
+% Figure - Norm distribution by country
+%
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/Math/l2_org_dist.pdf}
+	\caption{
+		\textbf{Distribution of organization embedding vector norms by country.}
+		Histogram showing the distribution of L2 norm values of organization embedding vectors in each of the 30 countries with the largest number of total unique mobile and non-mobile researchers. 
+		Text in each panel shows the number of organizations in the country (n) and the GINI index of inequality of the distribution (g); 
+		a small GINI index indicates that the L2 norms of organizations are more balanced, whereas a high GINI value indicates that they are more unequal. 
+	}
+	\label{fig:norm_dist}
 \end{figure}

### 2020-07-24 paper/current/main.tex

--- 2020-07-24 paper/current/main.tex
@@
 However, if the word in question is universal, appearing frequently in many different contexts, it cannot have a large norm as it lacks a strong association with a particular context.
-Likewise, an organization such as Harvard with a small norm appears in many contexts, alongside many different organizations in affiliation trajectories. 
-The concavity can overlap into a single line, implying the size of the vector is related to the connectedness of the organization given its size (Fig.~\ref{fig:length}a, inset, $R^{2} = 0.17$).
-Large, prestigious, and well-funded research universities such as Princeton and Harvard have smaller vector sizes because they appear in many different contexts compared to more teaching-focused organizations such as NY Medical College, and the University of Michigan at Flint.
-% Some universities, such as the University of Alaska at Fairbanks, have surprisingly small vectors, perhaps as a result of its remote location and unique circumstances. (I think it hurts the context)
+Likewise, an organization such as Harvard with a small norm appears in many contexts, alongside many different organizations in affiliation trajectories---it is well-connected.
+The concavity emerges in part from the relationship between the size of the vector and the expected connectedness of the organization given its size (Fig.~\ref{fig:length}a, inset, $R^{2} = 0.17$).
+Large, prestigious, and well-funded research universities such as Princeton and Harvard have smaller vector sizes because they appear in many different contexts compared to more teaching-focused organizations such as NY Medical College, and University of Michigan at Flint.
+Some universities, such as the University of Alaska at Fairbanks, have surprisingly small vectors, perhaps as a result of its remote location and unique circumstances.
 
 This same convex-curve repeats across many countries, though with variations that can reveal characteristics about the scientific systems of each country (Fig.~\ref{fig:length}b).
-For example, Chinese organizations have a longer average embedding vector size ($\bar{l} = 4.81$) than organizations in the United States ($\bar{l} = 4.21$), reflecting the tendency for organizations in the United States to appear more frequently in more different contexts than Chinese organizations.
-Smaller but scientifically advanced countries such as Sweden, and other large populous countries like Brazil exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset), a pattern repeated across most of the 20 countries with the most researchers (Fig.~\ref{fig:concave20}).
-Other nations exhibit different curves, such as Egypt which has an ``S"-shaped curve---their largest organizations do not have smaller vectors, as in many other countries. 
-Other nations such as Poland and Turkey demonstrate a linear relationship between an organization's number of researchers and the vector size, indicating that their largest organizations belong to specific contexts (Fig.~\ref{fig:concave20}).
-%By encoding whether an organization will appear in specific or many different contexts, organization embeddings offer a way to characterize universal and particularistic patterns of mobility across countries.
+For example, the representative vector of Chinese organizations are larger than that of the United States ($\bar{l} = 2.97$ vs $\bar{l} = 2.39$, Table~\ref{table:supp:norm}), reflecting the tendency for organizations in the United States to appear more frequently in more different contexts than Chinese organizations.
+Smaller but scientifically advanced countries such as Sweden, and other large populous countries like Brazil exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset), a pattern repeated across most countries with large scientific systems (Fig.~\ref{fig:concave30}).
+Other nations exhibit different curves, such as Egypt which has an "S"-shaped curve---their largest organizations do not as well connected as other country's largest organizations. 
+Other nations such as Poland, Iran, and Turkey demonstrate a linear relationship between an organization's number of researchers and the vector size, indicating that their largest organizations belong to very specific contexts (Fig.~\ref{fig:concave30}).
+The organization-level distribution of embedding vector norms reveals even deeper heterogeneity---
+for example, whereas the United States has the smallest representative vector, skewness of the sizes of its organization vectors suggest that this is driven by a small number of especially-well-connected organizations ($s = -0.82$, Fig.~\ref{fig:norm_dist}).
+Germany and the United Kingdom have comparable representative vector sizes to the United States ($\bar{l} = 2.6$ and $\bar{l} = 2.61$, respectively), though they are much less skewed ($s = -0.63$ and $s = -0.55$), suggesting less inequality in the connectedness of organizations in these countries.
+The vector sizes of organizations in some countries are even more skewed, such as in Iran ($\bar{l} = 3.57$, $s = -2.13$), and China ($\bar{l} = 2.97$, $s = -1.08$), indicating the strong difference between their most- and least-connected organizations.
+For some countries, their organizations are positively-skewed, though seemingly for different reasons---
+Austria, for example, has a balanced distribution of organization vector sizes, suggesting a diverse range of organizations with most being well connected ($\bar{l} =2.64$, $s = 0.18$);
+Russia, in contrast, has a high number of organization vectors of moderate size, but also several very isolated organizations with large vector sizes ($\bar{l} = 3.08$, $s = 0.67$).
+By capturing the connectedness of organizations in the embedding vector size, the embedding space can be used to characterize universal and particularistic patterns of mobility across countries.
 
@@
 		The loess regression lines are shown for each selected country, and for the aggregate of remaining countries, with 99\% confidence intervals.
-		Loess lines are also shown for organizations in Sweden, Brazil, and Egypt (inset).
+		Loess lines are also shown for organizations in Sweden, Brazil, and Egypt (\textbf{inset}).
 	}
@@
 \newpage
+
+\begin{table}[]
+\centering
+\caption{\textbf{L2 Norm of country's representative vectors}.
+			 Shown for top 30 countries with the most unique mobile and non-mobile researchers}
+\label{table:supp:norm}
+\begin{tabular}{lrr}
+\textbf{Country} & \textbf{L2 Norm} & \textbf{\# Organizations} \\ \hline
+United States    & 2.39             & 1281                      \\
+Germany          & 2.6              & 485                       \\
+United Kingdom   & 2.61             & 514                       \\
+Austria          & 2.64             & 74                        \\
+France           & 2.83             & 688                       \\
+Belgium          & 2.84             & 84                        \\
+Switzerland      & 2.85             & 66                        \\
+Spain            & 2.94             & 322                       \\
+China            & 2.97             & 497                       \\
+India            & 2.99             & 114                       \\
+Poland           & 3.02             & 145                       \\
+Canada           & 3.02             & 147                       \\
+Italy            & 3.04             & 386                       \\
+Russia           & 3.08             & 187                       \\
+Norway           & 3.1              & 122                       \\
+Netherlands      & 3.11             & 136                       \\
+Sweden           & 3.16             & 75                        \\
+Brazil           & 3.16             & 286                       \\
+Finland          & 3.17             & 66                        \\
+Denmark          & 3.21             & 54                        \\
+Czech Republic   & 3.23             & 97                        \\
+Greece           & 3.24             & 62                        \\
+Australia        & 3.24             & 90                        \\
+Turkey           & 3.28             & 99                        \\
+South Korea      & 3.28             & 156                       \\
+Israel           & 3.32             & 71                        \\
+Portugal         & 3.33             & 57                        \\
+Japan            & 3.35             & 465                       \\
+Iran             & 3.57             & 68                        \\
+Taiwan           & 3.67             & 72
+\end{tabular}
+\end{table}
+
+\newpage
+
 %
@@
 	\centering
-	\includegraphics[width=\textwidth]{\figdir/Math/boomerang_20_countries.pdf}
-	\caption{
-		\textbf{Concave-curve repeats across most of 20 countries with most researchers.}
+	\includegraphics[width=\textwidth]{\figdir/Math/boomerang_30_countries.pdf}
+	\caption{
+		\textbf{Concave-curve repeats across most of 30 countries with most researchers.}
 		Size (L2 norm) of organization embedding vectors compared to their number of researchers for U.S. universities.
 		Loess regression line is shown for each country with 99\% confidence intervals.
-		Countries shown are the top 20 countries with the largest number of total unique researchers, as derived from our bibliographic data. 
-	}
-	\label{fig:concave20}
+		Countries shown are the 30 with the largest number of total unique mobile and non-mobile researchers.
+	}
+	\label{fig:concave30}
+\end{figure}
+
+%
+% Figure - Norm distribution by country
+%
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/Math/l2_org_dist.pdf}
+	\caption{
+		\textbf{Distribution of organization embedding vector norms by country.}
+		Histogram showing the distribution of L2 norm values of organization embedding vectors in each of the 30 countries with the largest number of total unique mobile and non-mobile researchers.
+		Text in each panel shows the number of organizations in the country (n) and the GINI index of inequality of the distribution (g);
+		a small GINI index indicates that the L2 norms of organizations are more balanced, whereas a high GINI value indicates that they are more unequal.
+	}
+	\label{fig:norm_dist}
 \end{figure}

### 2020-07-24 notebooks/embedding_boomerang_plots.rmd
commited the wrong notebook last time

@@
 
+df %>%
+  filter(country_iso_alpha %in% selected) %>%
+  group_by(country_iso_name) %>%
+  summarize(
+    mu = mean(l2norm)
+  ) %>%
+  arrange(mu)
+
+plotdata <- df %>%
+  filter(country_iso_name != "NULL") %>%
+  filter(country_iso_alpha %in% selected) %>%
+  rename(country = country_iso_name) %>%
+  mutate(
+    country = ifelse(country == "Russian Federation", "Russia", country),
+    country = ifelse(country == "Korea, Republic of", "South Korea", country),
+    country = ifelse(country == "Taiwan, Province of China", "Taiwan", country),
+    country = ifelse(country == "Iran, Islamic Republic of", "Iran", country),
+  )
+
+mu <- plotdata %>%
+  group_by(country) %>%
+  summarize(
+    mu = mean(l2norm)
+  )
+
+plotdata %>%
+  left_join(mu, by = "country") %>%
+  ggplot(aes(l2norm, group = country)) +
+  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) +
+  geom_vline(aes(xintercept = mu)) +
+  geom_text(
+    data = mu,
+    aes(label = paste0("mu==", round(mu, 1))), 
+    parse = T,
+    x = 1.5, 
+    y = 0.18, 
+    size = 3
+  ) +
+  facet_wrap(~country) +
+  scale_y_continuous(breaks = c(0, 0.2)) +
+  theme_minimal() +
+  theme(
+      text = element_text(family = "Helvetica", size = 14),
+      axis.title.x = element_text(angle = 0, size = 16, face = "bold", vjust = 0.5),
+      axis.title.y = element_text(angle = 90, size = 16, face = "bold"),
+      panel.grid.minor = element_blank(),
+      panel.grid.major = element_blank(),
+      panel.border = element_rect(size = 0.5, color = "black", fill = NA),
+  ) +
+  xlab("L2 Norm of Organization Vectors by Country") +
+  ylab("Proportion")
+
+```
+
+```{r}
 tab <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Embeddings/precedence/norm/d300_ws1_precedence_norm_by_country.csv")
@@
 
+tab
 write_csv(tab, "~/Desktop/norm_by_country.csv")

### 2020-07-25 paper/current/main.tex
small edits

@@
 Moreover, scientific mobility has known structure, such as the centrality of the United States and the United Kingdom, and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career} that should be captured in a representation.
-However, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics} and one of the underlying these challenges is the diminishing role of geography in shaping the landscape of scientific mobility.
+However, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, and one of the underlying these challenges is the diminishing role of geography in shaping the landscape of scientific mobility.
 
 Here, scientific mobility is operationalized using researcher's organizational affiliations derived from their publication histories indexed in a comprehensive bibliographic database.
-The most fine-grained geographical unit in this data is the organization, such as a university, research institute, business, or government agency.
+The most fine-grained geographical unit in this data is the organization, such as a ``university'', ``research institute'', ``business'', or ``government agency''.
 As a scientist's career progresses, they move between organizations or pick up additional (simultaneous) affiliations forming \textit{affiliation trajectories} (Fig.~\ref{fig:methods:mobility_sentence}).
@@
 
-Prestige hierarchy is known to underpin the dynamics of scientific mobility~\autocite{deville2014career, clauset2015hierarchy}, but can the hierarchy be encoded in the embedding space, to which no explicit information on prestige is given?
+Prestige hierarchy is known to underpin the dynamics of scientific mobility~\autocite{deville2014career, clauset2015hierarchy}, but can the hierarchy be encoded in the embedding space, to which no explicit information on prestige is given and for which the direction of mobility not known?
 We test this by exploiting the geometric properties of the embedding space with SemAxis~\autocite{an2018semaxis}, an approach originally designed to characterize the semantics of words in word embeddings.
@@
 While scientific mobility is used as a case study, this approach can be broadly applied to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
-Moreover, this approach can be used to learn a functional distance between entities for which no geographic analog exists, such as between occupational categories based on individual's career trajectories.
+Moreover, this approach can be used to learn a functional distance between entities for which no physical analog exists, such as between occupational categories based on individual's career trajectories.
 In addition to providing a functional distance that supports modeling and predicting mobility patterns, the unique structure of the neural embedding space is amenable to a range of unique applications for studying mobility.

### 2020-07-26 paper/current/main.tex
update abstract

@@
 
-Human mobility and migration drives major social phenomena such as the growth and evolution of cities~\autocite{wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity}, economies~\autocite{kaluza2010cargo, kerr2011immigration}, innovation~\autocite{kaiser2018innovation, armano2017innovation},  and scientific research~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage, morgan2018prestige, rodrigues2016mobility}.
-Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity, xia2005measlesgravity, jung2008highwaygravity, barbosa2018human, curiel2018citygravity, lewer2008immigrationgravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} aim to capture mobility between places using their population and the \textit{distance} between them.
+Human mobility and migration drives major social phenomena such as the growth and evolution of cities~\autocite{wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity}, economies~\autocite{kaluza2010cargo, kerr2011immigration}, and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}.
+Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity} aim to capture mobility between places using their population and the \textit{distance} between them.
 However, geographic distance is less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} wherein the physical barrier shrinks while linguistic, economic, cultural, and historical similarities matter more.

### 2020-07-26 workflow/scripts/PlotSemAxisVsCentralityRank.R
plot semaxis rank vs. centrality rank

@@ -1,0 +1,120 @@
+#
+# PlotTimesVsCentralityRank.R
+#
+# author: Dakota Murray
+#
+# Plot the comparison between the ranking derived from the simularity
+# projection and the standard university ranking
+#
+
+# Plot dimensions
+FIG_WIDTH = 6
+FIG_HEIGHT = 6
+
+
+library(readr)
+library(ggplot2)
+library(dplyr)
+suppressPackageStartupMessages(require(optparse))
+
+# Command line arguments
+option_list = list(
+  make_option(c("--centrality"), action="store", default=NA, type='character',
+              help="Path to file containing centrality ranking"),
+  make_option(c("--semaxis"), action="store", default=NA, type='character',
+              help="Path to file containing semaxis ranking"),
+  make_option(c("--times"), action="store", default=NA, type='character',
+              help="Path to file containing times ranking"),
+  make_option(c("--measure"), action="store", default=NA, type='character',
+              help="Name of the centrality measure to use for the rank"),
+  make_option(c("--lookup"), action="store", default=NA, type='character',
+              help="Path to file containing organizational metadata"),
+  make_option(c("-o", "--output"), action="store", default=NA, type='character',
+              help="Path to save output image")
+) # end option_list
+opt = parse_args(OptionParser(option_list=option_list))
+
+semaxis <- read_csv(opt$semaxis, col_types = cols())
+centrality <- read_csv(opt$centrality, col_types = cols())
+
+# Load the times rankings also, as these are used to filter US orgs
+times <- read_csv(opt$times, col_types = cols())
+
+# Begin by loading the formal univeristy ranking
+ranks <- read_delim(opt$lookup, col_types = cols(), delim = "\t") %>%
+  filter(country_iso_alpha == "USA") %>% # Limit to USA universities
+  inner_join(times, by = c("cwts_org_no")) %>%
+  left_join(semaxis, by = c("cwts_org_no")) %>%
+  left_join(centrality, by = c("cwts_org_no")) %>%
+  rename(centrality = opt$measure) %>%
+  select(full_name, cwts_org_no, sim, centrality) %>%
+  filter(!is.na(sim) & !is.na(centrality)) %>%
+  arrange(desc(centrality)) %>%
+  mutate(
+    centrality_rank = row_number()
+  ) %>%
[…]

### 2020-07-26 paper/current/main.tex
update text throughout

@@
 While geographic distance may have driven human movements in the past, it holds less importance to a world connected by rapid transit, complex international relations, and dense airline networks.
-For instance, a person living in Australia is more likely to migrate to the United Kingdom, a far-away country with similar language and culture, than to much closer countries like Indonesia.
-Similarly, a student in South Korea is more likely to attend universities in Canada than those in North Korea.
-Although geographic distance has still been used as the basis for the most prominent models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} model,  \textit{functional distances}~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional} have been proposed to learn alternative notions of distance from real-world data or \textit{a priori} relationships between geographic entities.
+For instance, a person living in Australia is more likely to migrate to the United Kingdom, a far-away country with similar language and culture, than to much closer countries like Indonesia~\autocite{pew2018migration}.
+Similarly, a student in South Korea is more likely to attend universities in Canada than those in North Korea~\autocite{unesco2019students}.
+Although geographic distance has been used as the most prominent basis for models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} model, there have been attempts to define alternative notions of distance, or ~ \textit{functional distances}~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional} from real-world data or \textit{a priori} relationships between geographic entities.
 Yet, functional distances are often low-resolution and rely on somewhat arbitrary decisions about the importance of each factor.
 Moreover, functional distances typically only focus on a single facet of mobility at a time, whereas real-world mobility is multi-faceted, influenced simultaneously by geography, language, culture, history, and economic opportunity.
-To capture such complexity of human mobility, new approaches are needed to incorporate its many facets into a single high-resolution functional distance.
+To capture such complexity of human mobility, new approaches that incorporate its many facets into a single high-resolution functional distance are needed.
 
 Here, we propose a neural embedding model that uses real-world mobility trajectories to encode the complex landscape of global mobility into a dense, continuous, and meaningful vector-space representation, from which a \textit{functional distance} between places can be derived.
-The neural embedding, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been used to reveal insights into texts~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
-Neural embedding is also computationally efficient, scalable for large datasets, robust to noise, and can extract rich relationships between entities through the application of simple vector arithmetic~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.
+The neural embedding, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been  making breakthroughs by revealing novel insights into texts~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
+Neural embedding is also computationally efficient, robust to noise, and can encode reasonably rich relations between entities as geomemetric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.
 
@@
 Moreover, scientific mobility has known structure, such as the centrality of the United States and the United Kingdom, and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career} that should be captured in a representation.
-However, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, and one of the underlying these challenges is the diminishing role of geography in shaping the landscape of scientific mobility.
-
-Here, scientific mobility is operationalized using researcher's organizational affiliations derived from their publication histories indexed in a comprehensive bibliographic database.
+However, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, one underlying challenges being the diminishing role of geography in shaping the landscape of scientific mobility.
+
+Here, scientific mobility is operationalized using researcher's organizational affiliations derived from their publication histories indexed in a comprehensive bibliographic database (see Methods).
 The most fine-grained geographical unit in this data is the organization, such as a ``university'', ``research institute'', ``business'', or ``government agency''.
 As a scientist's career progresses, they move between organizations or pick up additional (simultaneous) affiliations forming \textit{affiliation trajectories} (Fig.~\ref{fig:methods:mobility_sentence}).
-These trajectories encode both asynchronous migration, and synchronous mobility---the holding of multiple simultaneous co-affiliations involving the sharing of time and capital between locations---that is typical of scientific mobility~\autocite{rodrigues2016mobility, markova2016synchronous, sugimoto2017mostimpact} (see Supplementary Materials).
+These trajectories encode both migration and co-affiliation---the holding of multiple simultaneous co-affiliations involving the sharing of time and capital between locations---that is typical of scientific mobility~\autocite{rodrigues2016mobility, markova2016synchronous, sugimoto2017mostimpact} (see Supplementary Materials).
 We use the trajectories of more than three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
 
-A vector-space embedding of organizations is learned by using affiliation trajectories as input to the standard skip-gram with negative sampling, or \textit{word2vec} neural-network architecture.
+A vector-space embedding of organizations is learned by using affiliation trajectories as input to the standard skip-gram with negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
 In the resulting embedding, each organization corresponds to a single vector, and vectors relate to one another based on the likelihood of organizations appearing near together in the affiliation trajectory data.
@@
     \centering
-    \includegraphics[width=\textwidth]{\figdir/mobility_example_combined.pdf}
+    \includegraphics[width=0.5\textwidth]{\figdir/mobility_example_combined.pdf}
     \caption{
@@
 %
-\subsection*{Embeddings provide both functional distance between organizations}
+\subsection*{Embeddings provide functional distance between organizations}
 
@@
 The embedding distance defined from the cosine distance between vectors also outperforms that defined from their dot product ($R^{2} = 0.34$, Fig.~\ref{fig:supp:gravity_dot}).
-The embedding distance also out-performs alternative ``diffusion-based'' network distance measures such as the personalized-page rank scores (see supporting materials) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-A reasonable explanation behind these results is that raw network distance measures cannot capture high-order interaction because the network is the first-order Markov process model of the system, while the neural embedding can leverage it.
-Also, raw network distance measures are well-known for vulnerable on random error \autocite{holme2002attack}.
-Our results unequivocally argue that the distance learned by the embedding method better captures actual mobility patterns than does geographic distance.
+The embedding distance also out-performs alternative ``diffusion-based'' network distance measures such as the personalized-page rank scores (see Supporting Materials) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+Our results unequivocally argue that the embedding distance better captures actual mobility patterns than does geographic distance.
 
@@
 		Boxplots show distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps $y = x$.
-		``RMSE'' is root-mean-squared error between the actual and predicted values.
+		Box color corresponds to the degree to which the distribution overlaps with $y = x$.
+		``RMSE'' is the root-mean-squared error between the actual and predicted values.
 		\textbf{e-f.} Predictions made using model parameters learned from a subset of domestic (within-country) organization pairs.
@@
 	\caption{
-		\textbf{Geography, then language, dictate international mobility.}
+		\textbf{Geography, then language, conditions international mobility.}
 		\textbf{a.} Hierarchically clustered similarity matrix of country vectors, aggregated as the mean of all organization vectors within the country that has more than 25 organizations, excluding the United States.
@@
 census region) universities.
-A geographic axis is also added to aid the visualization and reinforce the importance of geography, defined as the mean vector of all universities in California and then Massachusetts.
-
-Prestigious universities such as Colombia, Stanford, MIT, Harvard, and Rockefeller are positioned towards the top of the axis (Fig.~\ref{fig:semaxis}a).
-Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphasis on teaching, such as Barry University and California State University at Long Beach.
-SemAxis also offers a new means of reasoning about the prestige of organizations typically excluded from rankings such as government organizations (Fig.~\ref{fig:semaxis}b), research institutes (Fig.~\ref{fig:semaxis}c), and teaching colleges (Fig.~\ref{fig:semaxis}d).
-
-%
-% Figure - SemAxis results
-%
-\begin{figure}[hp!]
-	\centering
-	\includegraphics[width=0.7\textwidth]{\figdir/SemAxis/semaxis_fig.pdf}
-	\caption{
-		\textbf{Embedding captures latent geography and prestige hierarchy.}
-		\textbf{a-d.} Illustration of SemAxis projection along two axes;  \textit{latent geographical axis}, from California to Massachusetts (left to right) and \textit{prestige axis}, from the top five to geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S.
-Universities (top to bottom).
-		Shown for U.S. Universities (\textbf{a}), Teaching colleges (\textbf{b}), Research institutes (\textbf{c}), and Government organizations (\textbf{d}).
-		Full organization names listed in Table~\ref{table:supp:orglabels}.
-		\textbf{e.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity high-ranked end of the axis prestige axis \textit{a}.
-		White points are those top and bottom five universities used to define the poles of the axis.
-	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the SemAxis and Times ranking is $\rho = 0.73$ (n = 145), and it increases if we include more top-and-bottom ranked universities (Fig.~\ref{fig:supp:semaxis_compare}).
-	  	\textbf{f.} Times ranking is correlated with Leiden Ranking of U.S. universities with Spearman's $\rho = 0.87$
-	}
-	\label{fig:semaxis}
-\end{figure}
-
-The embedding space captures the prestige hierarchy and can be used to reconstruct academic rankings.
-We derive a ranking for universities using the SemAxis prestige axis in Fig.~\ref{fig:semaxis}a and compare them to traditional university rankings.
-The embedding based ranking is defined from the position of organizations along the prestige axis, with the top-ranked being the furthest towards the high-ranked end of the axis.
-We find that the embedding-based ranking is strongly correlated with the Times ranking (Spearman's $\rho = 0.73$, Fig.~\ref{fig:semaxis}e).
-The strongest outliers that were ranked more highly in the Times Ranking than the embedding based ranking tend to be large state universities such as Arizona State University and  University of Florida;
-Those ranked higher in the embedding based ranking tend to be relatively-smaller universities such as the University of San Francisco and University of Maryland Baltimore County that are close to other prestigious universities.
-
+
+The embedding space encodes the prestige hierarchy of U.S. universities well enough to re-construct university rankings. 
+We derive a ranking for universities using the SemAxis prestige axis and compare them to traditional university rankings.
+The embedding-based ranking is defined from the position of organizations along the prestige axis, with the top-ranked being the nearest to the high-ranked pole.
+The embedding-based ranking is strongly correlated with the Times ranking (Spearman's $\rho = 0.73$, Fig.~\ref{fig:semaxis}a).
+For reference, the embedding-based ranking achieves correlation with the Times Ranking comparable to that between the Times ranking and the publication impact scores from the Leiden Ranking~\autocite{waltman2012leidenrankings}, a well-known bibliometrically-informed university ranking (Spearman's $\rho = 0.87$, Fig.~\ref{fig:semaxis}b).
 The correlation between the embedding based ranking and the Times ranking is robust with the number of organizations used to define the axes (Fig.
 SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities are significantly correlated with the Times Ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
-For reference, the embedding-based ranking achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking~\autocite{waltman2012leidenrankings}, a well-known bibliometrically-informed university ranking (Spearman's $\rho = 0.87$, Fig.~\ref{fig:semaxis}f).
-This suggests that the organization embedding captures the latent prestige hierarchy inherent to academic mobility, even without providing any explicit information on prestige, with a high degree of resolution and reliability~\autocite{deville2014career, clauset2015hierarchy}.
+The strongest outliers that were ranked more highly in the Times Ranking than the embedding based ranking tend to be large state universities such as Arizona State University and  University of Florida;
+Those ranked higher in the embedding based ranking tend to be relatively-small universities such as the University of San Francisco and University of Maryland Baltimore County near major urban areas.
+This suggests that the organization embedding captures the latent prestige hierarchy inherent to academic mobility with a high degree of resolution and reliability, even without providing any explicit information on prestige~\autocite{deville2014career, clauset2015hierarchy}.
+
+The performance of the embedding ranking in reconstructing the Times ranking is comparable to that of network-derived measures such as weighted degree (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_times_compare}a) and eigencentrality centrality (Spearman's $\rho = 0.76$, Fig.~\ref{fig:supp:centrality_times_compare}b).
+However, while both embedding- and network-based measures relate to university prestige, they are qualitatively and quantitatively different.
+The embedding-ranking of U.S.
+universities is less correlated with weighted degree (Spearman's $\rho = 45$, Fig.~\ref{fig:supp:centrality_semaxis_compare}a) and eigenvector  centrality (Spearman's $\rho = 0.55$) than with the Times Ranking itself (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_semaxis_compare}b).
+The embedding ranking over-ranks large research-intensive universities such as North Carolina State University, University of Florida, and Texas A\&M University, whereas the network-derived ranking over-ranks smaller, more specialized universities such as Brandeis University, Yeshiva University, and University of San Francisco.
+This suggests that the embedding encodes encodes information on prestige hierarchy at least as well as a network representation, but that the information encoded is something different from centrality.
+
+The axes can further be visualized to examine the the relative position of organizations along the prestige axis, and along a geographic axis between California and Massachusetts that aids visualization.
+Prestigious universities such as Colombia, Stanford, MIT, Harvard, and Rockefeller are positioned towards the top of the axis (Fig.~\ref{fig:semaxis}c).
+Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphasis on teaching, such as Barry University and California State University at Long Beach.
+By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations typically excluded from rankings such as government organizations (Fig.~\ref{fig:semaxis}d), research institutes (Fig.~\ref{fig:semaxis}e), and teaching colleges (Fig.~\ref{fig:semaxis}f).
+
+%
+% Figure - SemAxis results
+%
+\begin{figure}[hp!]
+	\centering
+	\includegraphics[width=0.7\textwidth]{\figdir/SemAxis/semaxis_fig.pdf}
+	\caption{
+		\textbf{Embedding captures latent geography and prestige hierarchy.}
+		\textbf{a.} Comparison between the ranking of organizations by their rank in the Times ranking and the embedding rank derived using SemAxis with the poles defined using the top five, and geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S.
+Universities .
+		Un-filled points are those top and bottom five universities used to define the poles of the axis.
+	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the embedding and Times ranking is $\rho = 0.73$ (n = 145), and it increases if we include more top-and-bottom ranked universities (Fig.~\ref{fig:supp:semaxis_compare}).
+	  	\textbf{b.} Times ranking is correlated with Leiden Ranking of U.S. universities with Spearman's $\rho = 0.87$
+		\textbf{c-f.} Illustration of SemAxis projection along two axes;  \textit{latent geographical axis}, from California to Massachusetts (left to right) and the \textit{prestige axis}.
+		Shown for U.S. Universities (\textbf{c}), Teaching colleges (\textbf{d}), Research institutes (\textbf{e}), and Government organizations (\textbf{f}).
+		Full organization names listed in Table~\ref{table:supp:orglabels}.
+	}
+	\label{fig:semaxis}
+\end{figure}
 
@@
 
-This same convex-curve repeats across many countries, though with variations that can reveal characteristics about the scientific systems of each country (Fig.~\ref{fig:length}b).
+This same convex-curve repeats across many countries (Fig.~\ref{fig:concave30})., though with variations that can reveal characteristics about the scientific systems of each country (Fig.~\ref{fig:length}b).
 For example, the representative vector of Chinese organizations are larger than that of the United States ($\bar{l} = 2.97$ vs $\bar{l} = 2.39$, Table~\ref{table:supp:norm}), reflecting the tendency for organizations in the United States to appear more frequently in more different contexts than Chinese organizations.
-Smaller but scientifically advanced countries such as Sweden, and other large populous countries like Brazil exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset), a pattern repeated across most countries with large scientific systems (Fig.~\ref{fig:concave30}).
+Smaller but scientifically advanced countries such as Australia, and other large populous countries like Brazil exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset), though their exact position and size varies between countries.
 Other nations exhibit different curves, such as Egypt which has an "S"-shaped curve---their largest organizations do not as well connected as other country's largest organizations. 
@@
 	\caption{
-		\textbf{Size of organization embedding vectors captures connection diversity of organizations.}
+		\textbf{Size of organization embedding vectors captures prestige and size of organizations.}
 		\textbf{a.} Size (L2 norm) of organization embedding vectors compared to their number of researchers for U.S. universities.
@@
 		Uncolored points are universities not listed on a Times ranking.
-		A convex-shape emerges, wherein larger universities tend to more distant from the origin (large L2 norm), however the more prestigious the university, the closer it is to the origin (small L2 norm).
+		A convex-shape emerges, wherein larger universities tend to more distant from the origin (large L2 norm); however, the more prestigious the university, the closer it is to the origin (small L2 norm).
 		The L2 norm is correlated weakly with the ratio between organization's of number of connected organizations and its number of researchers ($R^{2} = 0.17$, \textbf{inset}).
@@
 		The loess regression lines are shown for each selected country, and for the aggregate of remaining countries, with 99\% confidence intervals.
-		Loess lines are also shown for organizations in Sweden, Brazil, and Egypt (\textbf{inset}).
+		Loess lines are also shown for organizations in Australia, Brazil, and Egypt (\textbf{inset}).
 	}
@@
 
-Scientific mobility is complex and can be defined in many possible ways~\autocite{robinson2019mobility} and at multiple levels of analysis.
+Scientific mobility is complex and can be defined in many ways~\autocite{robinson2019mobility} and at multiple levels of analysis.
 Here, authors are classified as mobile when they have at least two distinct organization IDs in their trajectory, meaning that they have published using two or more distinct affiliations between 2008 and 2019.
@@
 Mobile authors were associated with, on average, 2.5 distinct organizational affiliations.
-Rates of mobility tended to differ across countries.
+Rates of mobility differ across countries.
 For example, France, Qatar, the USA, Iraq, and Luxembourg had the most mobile authors (Fig.~\ref{fig:supp:descriptives}c).
@@
 We embed co-affiliation trajectories by treating them analogously to sentences and organizations analogously to words.
-The trajectories of mobile authors were converted to ``affiliation trajectories'' by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:methods:mobility_sentence}.a.
-In more complex cases, such as listing multiple affiliations on the same paper or publishing with different affiliations on multiple affiliations in the same year, the order is randomized within that year, as shown in  Fig.~\ref{fig:methods:mobility_sentence}.b.
+The trajectories of mobile authors were converted to ``affiliation trajectories'' by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:methods:mobility_sentence}a.
+In more complex cases, such as listing multiple affiliations on the same paper or publishing with different affiliations on multiple affiliations in the same year, the order is randomized within that year, as shown in  Fig.~\ref{fig:methods:mobility_sentence}b.
 
 %% word2vec
-These affiliation trajectories are used as input to the standard skip-gram negative sampling word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec} .
-\textit{word2vec} constructs dense vector representations of words and phrases, in which distance relationships between words correspond to a notion of semantic distance.
+These affiliation trajectories are used as input to the standard skip-gram negative sampling word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec}.
+\textit{word2vec} constructs dense and continuous vector representations of words and phrases, in which distance between words correspond to a notion of semantic distance.
 There are two types of embedding vectors in the model; in-vector and out-vector.
 In-vector is usually mainly used as a representation vector of each word \autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch} and we also used in-vector in this study.
-By embedding affiliation trajectories, we aim to learn a dense vector for every organization where the distance between vectors relates to the tendency for two organizations to co-occur in a token window around the target organization token in the same career trajectory.
-Vectors are learned by training a neural network to optimize the prediction of the so-called context term given a target, in our case using one organization to predict the others appearing in the same co-affiliation trajectory.
+By embedding affiliation trajectories, we aim to learn a dense vector for every organization where the distance between vectors relates to the tendency for two organizations to occur in similar contexts.
+Embedding vectors are learned by training a neural network to following average log probability using as input an affiliation trajectory---a sequence of tokens identifying organizations $a_{1}, a_{2}, ...
+a_{T}$,
+
+$$
+\frac{1}{T}\sum_{t = 1}^{T} \sum_{-c \leq j \leq c, j \neq 0} \log p(a_{t + j} \vert a_{t})
+$$
+
+where T is the total size of the training sequence, $c$ is the window size before and after the target organization token $a_{t}$ that is used to define the context, $a_{t + j}$~\autocite{mikolov2013word2vec}.
 The hidden layer of the trained neural network is used as the final representation.
@@
 %% Word2vec parameters and training procedure
-The skip-gram model has several tunable hyper-parameters, including the size of the learned vectors, the size of the token window considered when training, the minimum frequency threshold for including an organization, and the number of iterations.
-We iterate through several values of vector size and window size, repeating the analysis for each combination.
 To mitigate the effect of less common organizations, only organizations appearing at least 50 times in mobility sentences are included in the embedding;
@@
 We iterate the skip-gram training for five epochs over all mobility sentences.
-All word embeddings are trained using the \textit{gensim} python implementation of the skip-gram \textit{word2vec} model.
-We visualize embeddings by projecting into two dimensions using UMAP~\autocite{mcinnes2018umap}.
-
+The skip-gram negative sampling model has several tunable hyper-parameters, including the dimension of the learned vectors, the size of the token window considered when training, the minimum frequency threshold for including an organization, and the number of iterations.
 Results are reported for embeddings with a dimensionality of 300 and a window size of one, which were the parameters that produced that best explained the flux between organizations (Fig.
@@
 We note that this performance and the outcomes of the analysis were robust to hyper-parameters settings.
+All word embeddings are trained using the \textit{gensim} python implementation of the skip-gram \textit{word2vec} model.
 
@@
 For example, $T_{ij} = 10$ indicates that ten authors were co-affiliated with both organization $i$ and $j$ between 2008 and 2019, as evidenced from their publications.
-In contrast to traditional mobility studies, all co-affiliations are symmetric, meaning that $T_{ij} = T_{ji}$.
+We treat all co-affiliations are symmetric, meaning that $T_{ij} = T_{ji}$.
 
@@
 The embedding distance with the cosine similarity, $d_{ij}$, is calculated as the pairwise cosine distance between vectors from the learned organization embedding, where $v_{i}$ and $v_{j}$ represent the vectors and $d_{ij} = 1 - \frac{v_{i} \cdot v_{j}}{\lVert v_{i} \rVert \lVert v_{j} \rVert}$.
+Negative cosine distances, caused by cosine similarities greater than one, are truncated at zero. 
+Note that this distance derived from the embedding space is not a formal metric, as it does not satisfy the triangle inequality, however such distnaces have still proved practically useful in make tasks~\autocite{lerman2007embedding, brown1970migration, brown1970functional, kim2018functional}.
 
@@
 \end{equation}
-where $m_{i}$ and $m_{j}$ are the organization masses, or the yearly-average count of unique authors affiliated with each organization during the time window, and $f(r_{ij})$ is a distance-decaying function  between the two organizations.
+
+where $m_{i}$ and $m_{j}$ are the organization masses, or the yearly-average count of unique mobile and non-mobile authors affiliated with each organization during the time window, and $f(r_{ij})$ is a distance-decaying function  between the two organizations.
 There are two popular forms of the $f(r_{ij})$.
@@
 \subsection*{SemAxis}
-SemAxis~\autocite{an2018semaxis} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these terms to the concept.
+SemAxis~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these terms to the concept.
 Each axis is an antonym pair defined for each specific use case.
@@
 		\textbf{SemRank hierarchy is robust.}
-		\textbf{a.} Spearman correlation (n = 143) between Times prestige rank and SemAxis rank, by the number of high and bottom-ranked (geographically matched) universities aggregated to form the poles.
+		\textbf{a.} Spearman's $rho$ (n = 143) between Times prestige rank and embedding rank derived using SemAxis, with poles defined using the top and bottom (geographically matched) ranked universities.
 		Black points show spearman correlation using all organizations; white points show correlation using only universalizes not aggregated in the poles.
@@
 %
-% Figure - Times Ranking vs. Leiden Ranking
-%
-%\begin{figure}[hp!]
-%	\centering
-%	\includegraphics[width=\textwidth]{\figdir/SemAxis/times_leiden_compare.pdf}
-%	\caption{
-%		\textbf{Correlation between Times and Leiden Ranking.}
-%		Comparison between the Times and Leiden rankings of universities.
-%		Here, the Leiden Ranking is operationalized as the mean normalized fractional citation impact for each university~\autocite{waltman2012leidenrankings}.
-%	  	PCC details the estimate from the Spearman correlation between the two rankings.
-%	}
-%	\label{fig:supp:times_vs_leiden}
-%\end{figure}
+% Figure - Network Centrality vs. Times
+%
+\begin{figure}[hp!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/SemAxis/centrality_times_compare.pdf}
+	\caption{
+		\textbf{Network centrality is strongly correlated with Times ranking.}
+		Comparison between the ranking of organizations by their network-centrality rank and their rank in the 2018 Times Higher Education ranking of U.S. Universities .
+		The Times rank is correlated with degree centrality rank (\textbf{a}) with a Spearman's $\rho = 0.73$, and is correlated with the eigenvector centrality rank (\textbf{b}) with a Spearman's $\rho = 0.76$.
+	}
+	\label{fig:supp:centrality_times_compare}
+\end{figure}
+
+%
+% Figure - Network Centrality vs. SemAxis
+%
+\begin{figure}[hp!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_network_compare.pdf}
+	\caption{
+		\textbf{Network centrality less correlated with Embedding rank.}
+		Comparison between the ranking of organizations by their network-centrality rank and the embedding rank derived with SemAxis with poles defined using the top five to geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S.
+Universities .
+		Embedding rank is correlated with degree centrality rank (\textbf{a}) with a Spearman's $\rho = 0.45$, and is correlated with the eigenvector centrality rank (\textbf{b}) with a Spearman's $\rho = 0.55$.
+	}
+	\label{fig:supp:centrality_semaxis_compare}
+\end{figure}
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{\figdir/Math/si_factors.pdf}
+	\includegraphics[width=\textwidth]{\figdir/Math/l2_org_meta.pdf}
 	\caption{

### 2020-07-27 paper/current/main.tex
various edits

@@
 \textit{word2vec} constructs dense and continuous vector representations of words and phrases, in which distance between words correspond to a notion of semantic distance.
-There are two types of embedding vectors in the model; in-vector and out-vector.
-In-vector is usually mainly used as a representation vector of each word \autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch} and we also used in-vector in this study.
 By embedding affiliation trajectories, we aim to learn a dense vector for every organization where the distance between vectors relates to the tendency for two organizations to occur in similar contexts.
-Embedding vectors are learned by training a neural network to following average log probability using as input an affiliation trajectory---a sequence of tokens identifying organizations $a_{1}, a_{2}, ...
-a_{T}$,
-
+Formally, model attempt to maximize average log probability a target organization  in an affiliation trajectory $a_{t}$, given organizations in the surrounding context window, $a_{t+k}$.
+This can be written as follow, where $w$ is the size of the window and $T$ iterates through possible target organizations:
 $$
-\frac{1}{T}\sum_{t = 1}^{T} \sum_{-c \leq j \leq c, j \neq 0} \log p(a_{t + j} \vert a_{t})
+\frac{1}{T}\sum_{t = 1}^{T} \sum_{-w \leq j \leq w, j \neq 0} \log p(a_{t + j} \vert a_{t}),
 $$
-
-where T is the total size of the training sequence, $c$ is the window size before and after the target organization token $a_{t}$ that is used to define the context, $a_{t + j}$~\autocite{mikolov2013word2vec}.
-The hidden layer of the trained neural network is used as the final representation.
+where the conditional probability of observing one organization $a_{i}$, given another $a_{j}$, is defined as, 
+$$
+p(a_{i} \vert a_{j}) = \frac{\exp(u_{a_{i}} \cdot v_{a_{j}})}{\sum_{n=1}^N \exp(u_{a_{n}} \cdot v_{a_{j}})},
+$$
+where $N$ is the total number of organizations and $v$ and $u$ are ``in-vector" and ``out-vector" respectively~\autocite{mikolov2013word2vec}.
+Usually, in-vector $v$ is used as a final representation vector~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch}, we used in-vector in this study as well.
 
 %% Word2vec parameters and training procedure
-To mitigate the effect of less common organizations, only organizations appearing at least 50 times in mobility sentences are included in the embedding;
-this yields 6,580, or 76 percent of all organizations.
-We iterate the skip-gram training for five epochs over all mobility sentences.
-The skip-gram negative sampling model has several tunable hyper-parameters, including the dimension of the learned vectors, the size of the token window considered when training, the minimum frequency threshold for including an organization, and the number of iterations.
-Results are reported for embeddings with a dimensionality of 300 and a window size of one, which were the parameters that produced that best explained the flux between organizations (Fig.
-SI~\ref{fig:supp:hyperparams}).
-We note that this performance and the outcomes of the analysis were robust to hyper-parameters settings.
-All word embeddings are trained using the \textit{gensim} python implementation of the skip-gram \textit{word2vec} model.
+We used  \textit{gensim} python implementation of the \textit{word2vec} model.
+The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{min}$, initial learning rage $\alpha$, and the number of iterations.
+For main results, we used $d=300$ and $w=1$, which were the parameters that produced the best explained the flux between organizations (Fig. SI~\ref{fig:supp:hyperparams}).
+To mitigate the effect of less common organizations, we set the $f_{min}$ as  50.
+It means organizations with at least 50 appearances in mobility sentences are included in the final embedding, as a result, 6,580 organizations, 76 percent of all organizations, are remained.
+For $\alpha$, we used the default setting 0.025 and we iterates five times over whole affiliation trajectories.
+We checked results were robust across various hyper-parameters settings, while aforementioned settings yield the best result.
 
@@
 \end{equation}
-
 where $m_{i}$ and $m_{j}$ are the organization masses, or the yearly-average count of unique mobile and non-mobile authors affiliated with each organization during the time window, and $f(r_{ij})$ is a distance-decaying function  between the two organizations.
@@
 	\label{eq:linear_flux_geo}
-	\ln\frac{T_{ij}}{m_im_j} = \ln C  - \alpha \ln g_{ij}
+	\ln\frac{T_{ij}}{m_im_j} = \ln C  - \alpha \ln g_{ij},
 \end{equation}
@@
 	\label{eq:linear_flux_emb}
-	\ln\frac{T_{ij}}{m_im_j} = \ln C - \beta d_{ij}
+	\ln\frac{T_{ij}}{m_im_j} = \ln C - \beta d_{ij},
 \end{equation}
-
 where $T_{ij}$ is the real flux from the dataset. The gravity law of mobility is known to be sensitive to the case where $T_{ij} = 0$, or zero movement between organizations.

### 2020-07-27 paper/current/main.tex
typo

@@
 The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{min}$, initial learning rage $\alpha$, and the number of iterations.
-For main results, we used $d=300$ and $w=1$, which were the parameters that produced the best explained the flux between organizations (Fig. SI~\ref{fig:supp:hyperparams}).
+For main results, we used $d=300$ and $w=1$, which were the parameters that explained the flux between organizations most (Fig. SI~\ref{fig:supp:hyperparams}).
 To mitigate the effect of less common organizations, we set the $f_{min}$ as  50.
-It means organizations with at least 50 appearances in mobility sentences are included in the final embedding, as a result, 6,580 organizations, 76 percent of all organizations, are remained.
+It means organizations with at least 50 appearances in affiliation trajectories are included in the final embedding, as a result, 6,580 organizations, 76 percent of all organizations, are remained.
 For $\alpha$, we used the default setting 0.025 and we iterates five times over whole affiliation trajectories.

### 2020-07-27 workflow/scripts/PlotSemAxisVsCentralityRank.R
flip semaxis figure axes

@@ -86,7 +86,7 @@ max_val <- max(c(ranks$leiden_rank, ranks$semaxis_rank))
 
 # Build the plot
 plot <- ranks %>%
-  ggplot(aes(x = centrality_rank, y = semaxis_rank)) +
+  ggplot(aes(x = semaxis_rank, y = centrality_rank)) +
   geom_abline() +
   geom_point(size = 3.5, stroke = 0.5) +
   ggrepel::geom_label_repel(
@@ -98,7 +98,7 @@ plot <- ranks %>%
     size = 3.5) +
   # Add a fake top axis title, just to ensure that its the same size as the 2d fig
   scale_x_continuous(limits = c(0, max_val), sec.axis = dup_axis(name = "")) +
-  scale_y_continuous(limits = c(0, max_val + 10)) +
+  scale_y_continuous(limits = c(0, max_val + 15)) +
   guides(shape = F) +
   theme_minimal() +
   theme(
@@ -108,12 +108,13 @@ plot <- ranks %>%
     panel.grid.minor = element_blank(),
   ) +
   # Add the Spearman's Rho to the plot
-  annotate("text", x = 35, y = 150,
+  annotate("text", x = 35, y = 155,
            label = latex2exp::TeX(paste("Spearman's $\\rho = ", round(cor$estimate, 2))),
            size = 7,
            fontface = 2) +
-  xlab(axis.title) +
-  ylab("Embedding rank")
+  xlab("Embedding rank") +
+  ylab(axis.title)
+
 
 
 # Save the plot

### 2020-07-27 paper/current/main.tex
small edits. move network centrlaity to SI

@@
 Alternative notions of functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} attempt to re-define distance by using some of aforementioned factors~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional} but are often arbitrary and consider only single isolated facets.
-Here, using a rich dataset of scientific mobility, we demonstrate that a data-driven neural embedding approach~\autocite{mikolov2013word2vec} can successfully encodes a functional distance between organizations and captures the latent and multi-faceted structure of scientist's mobility.
+Here, using a rich dataset of scientific mobility, we demonstrate that a data-driven neural embedding~\autocite{mikolov2013word2vec} can successfully encodes a functional distance between organizations and captures the latent and multi-faceted structure of scientist's mobility.
 We demonstrate that the cosine distance between organization embedding vectors, constructed using the affiliation trajectories of scientists in the Web of Science database, better explain and predict real mobility than geographic distance.
@@
 SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities are significantly correlated with the Times Ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
+Performance is also comparable to network-driven measures such as degree strength (Spearman's $\rho = 0.73$) and eigenvector centrality (Spearman's $\rho = 0.76$, see Supporting Information). 
 The strongest outliers that were ranked more highly in the Times Ranking than the embedding based ranking tend to be large state universities such as Arizona State University and  University of Florida;
@@
 
-The performance of the embedding ranking in reconstructing the Times ranking is comparable to that of network-derived measures such as weighted degree (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_times_compare}a) and eigencentrality centrality (Spearman's $\rho = 0.76$, Fig.~\ref{fig:supp:centrality_times_compare}b).
-However, while both embedding- and network-based measures relate to university prestige, they are qualitatively and quantitatively different.
-The embedding-ranking of U.S.
-universities is less correlated with weighted degree (Spearman's $\rho = 45$, Fig.~\ref{fig:supp:centrality_semaxis_compare}a) and eigenvector  centrality (Spearman's $\rho = 0.55$) than with the Times Ranking itself (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_semaxis_compare}b).
-The embedding ranking over-ranks large research-intensive universities such as North Carolina State University, University of Florida, and Texas A\&M University, whereas the network-derived ranking over-ranks smaller, more specialized universities such as Brandeis University, Yeshiva University, and University of San Francisco.
-This suggests that the embedding encodes encodes information on prestige hierarchy at least as well as a network representation, but that the information encoded is something different from centrality.
-
 The axes can further be visualized to examine the the relative position of organizations along the prestige axis, and along a geographic axis between California and Massachusetts that aids visualization.
@@
 Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphasis on teaching, such as Barry University and California State University at Long Beach.
-By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations typically excluded from rankings such as government organizations (Fig.~\ref{fig:semaxis}d), research institutes (Fig.~\ref{fig:semaxis}e), and teaching colleges (Fig.~\ref{fig:semaxis}f).
+By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations which are typically not ranked, such as government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e), or for which rankings are often low-resolution and idiosyncratic, such as for regional and liberal arts universities (Fig.~\ref{fig:semaxis}f).
 
@@
 Past studies have validated this data, demonstrating it comparable to ground-truth records such as those from ORCID and useful for a wide range of bibliometric studies~\cite{sugimoto2017mostimpact, robinson2019mobility, chinchilla2018global, chinchilla2018travelban}.
+
+%
+% S7 TEXT
+\paragraph*{S7 Text}
+\label{si:text:network_ranking}
+{\bf Reconstructing Times ranking with network measure.}
+
+The performance of the embedding ranking in reconstructing the Times ranking is comparable to that of network-derived measures such as degree strength (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_times_compare}a) and eigencentrality centrality (Spearman's $\rho = 0.76$, Fig.~\ref{fig:supp:centrality_times_compare}b).
+However, while both embedding- and network-based measures relate to university prestige, they are qualitatively and quantitatively different.
+The embedding-ranking of U.S.
+universities is less correlated with weighted degree (Spearman's $\rho = 0.45$, Fig.~\ref{fig:supp:centrality_semaxis_compare}a) and eigenvector  centrality (Spearman's $\rho = 0.55$) than with the Times Ranking itself (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_semaxis_compare}b).
+The embedding ranking over-ranks large research-intensive universities such as North Carolina State University, University of Florida, and Texas A\&M University, whereas the network-derived ranking over-ranks smaller, more specialized universities such as Brandeis University, Yeshiva University, and University of San Francisco.
+This suggests that the embedding encodes information on prestige hierarchy at least as well as a network representation, but that the information encoded is something different from centrality
 

### 2020-07-27 paper/current/main.tex
move speculation to SI, other minor edits

@@
 
-What is it about the organization embedding that captures prestige so effectively?
-We find that the size (L2 norm) of the organization embedding vectors provides insights into the characteristics of organizations.
+We also find that the size (L2 norm) of the organization embedding vectors provides insights into the characteristics of organizations.
 Up to a point, the size of U.S. organization's vectors tends to increase proportional to its number of researchers (both mobile and non-mobile) who published with that organization;
@@
 
-This same convex-curve repeats across many countries (Fig.~\ref{fig:concave30})., though with variations that can reveal characteristics about the scientific systems of each country (Fig.~\ref{fig:length}b).
-For example, the representative vector of Chinese organizations are larger than that of the United States ($\bar{l} = 2.97$ vs $\bar{l} = 2.39$, Table~\ref{table:supp:norm}), reflecting the tendency for organizations in the United States to appear more frequently in more different contexts than Chinese organizations.
+This same convex-curve repeats across many countries such as with China, which closely mirrors that of the United States (Fig.~\ref{fig:length}b).
 Smaller but scientifically advanced countries such as Australia, and other large populous countries like Brazil exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset), though their exact position and size varies between countries.
-Other nations exhibit different curves, such as Egypt which has an "S"-shaped curve---their largest organizations do not as well connected as other country's largest organizations. 
-Other nations such as Poland, Iran, and Turkey demonstrate a linear relationship between an organization's number of researchers and the vector size, indicating that their largest organizations belong to very specific contexts (Fig.~\ref{fig:concave30}).
-The organization-level distribution of embedding vector norms reveals even deeper heterogeneity---
-for example, whereas the United States has the smallest representative vector, skewness of the sizes of its organization vectors suggest that this is driven by a small number of especially-well-connected organizations ($s = -0.82$, Fig.~\ref{fig:norm_dist}).
-Germany and the United Kingdom have comparable representative vector sizes to the United States ($\bar{l} = 2.6$ and $\bar{l} = 2.61$, respectively), though they are much less skewed ($s = -0.63$ and $s = -0.55$), suggesting less inequality in the connectedness of organizations in these countries.
-The vector sizes of organizations in some countries are even more skewed, such as in Iran ($\bar{l} = 3.57$, $s = -2.13$), and China ($\bar{l} = 2.97$, $s = -1.08$), indicating the strong difference between their most- and least-connected organizations.
-For some countries, their organizations are positively-skewed, though seemingly for different reasons---
-Austria, for example, has a balanced distribution of organization vector sizes, suggesting a diverse range of organizations with most being well connected ($\bar{l} =2.64$, $s = 0.18$);
-Russia, in contrast, has a high number of organization vectors of moderate size, but also several very isolated organizations with large vector sizes ($\bar{l} = 3.08$, $s = 0.67$).
-By capturing the connectedness of organizations in the embedding vector size, the embedding space can be used to characterize universal and particularistic patterns of mobility across countries.
+Other nations exhibit different curves, such as Egypt which has an``S''-shaped curve---their largest organizations do not as well connected as other country's largest organizations. 
+Similar patterns can be found across many of the 30 of the countries with the most total researchers (Fig.~\ref{fig:concave30}), though we can only speculate on what their variations mean (see Supporting Information).
+Neural embeddings encode a relationship between organization size and vector length that is universal across countries but with potentially meaningful nuances, helping the embedding to capture the landscape of global scientific mobility.
 
@@
 Here, we demonstrated how the embedding space encodes various aspects of scientific mobility, such as the global and regional geography, national shared languages, and the hierarchy of organizational prestige, even without explicit information on these factors.
-While scientific mobility is used as a case study, this approach can be broadly applied to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
+While scientific mobility is used as a case study, this approach may be broadly applicable to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
 Moreover, this approach can be used to learn a functional distance between entities for which no physical analog exists, such as between occupational categories based on individual's career trajectories.
@@
 This suggests that the embedding encodes information on prestige hierarchy at least as well as a network representation, but that the information encoded is something different from centrality
+
+%
+% S8 TEXT
+\paragraph*{S8 Text}
+\label{si:text:network_ranking}
+{\bf Speculation on variations of the convex-curve pattern.}
+
+The convex-curve pattern observed in Fig.~\ref{fig:length} repeats across many countries, but with variations.
+For example, the representative vector of Chinese organizations are larger than that of the United States ($\bar{l} = 2.97$ vs $\bar{l} = 2.39$, Table~\ref{table:supp:norm}),  causing its curve to be shifted upwards with a larger peak vector size;
+this may reflect a tendency for organizations in the United States to appear more frequently in more different contexts than Chinese organizations.
+Other nations such as Poland, Iran, and Turkey demonstrate a linear relationship between an organization's number of researchers and the vector size, indicating that their largest organizations belong to very specific contexts (Fig.~\ref{fig:concave30}).
+The organization-level distribution of embedding vector norms reveals even deeper heterogeneity---
+for example, whereas the United States has the smallest representative vector, skewness of the sizes of its organization vectors suggest that this is driven by a small number of especially-well-connected organizations ($s = -0.82$, Fig.~\ref{fig:norm_dist}).
+Germany and the United Kingdom have comparable representative vector sizes to the United States ($\bar{l} = 2.6$ and $\bar{l} = 2.61$, respectively), though they are much less skewed ($s = -0.63$ and $s = -0.55$), suggesting less inequality in the connectedness of organizations in these countries.
+The vector sizes of organizations in some countries are even more skewed, such as in Iran ($\bar{l} = 3.57$, $s = -2.13$), and China ($\bar{l} = 2.97$, $s = -1.08$), indicating the strong difference between their most- and least-connected organizations.
+For some countries, their organizations are positively-skewed, though seemingly for different reasons---
+Austria, for example, has a balanced distribution of organization vector sizes, suggesting a diverse range of organizations with most being well connected ($\bar{l} =2.64$, $s = 0.18$);
+Russia, in contrast, has a high number of organization vectors of moderate size, but also several very isolated organizations with large vector sizes ($\bar{l} = 3.08$, $s = 0.67$).
+By capturing the connectedness of organizations in the embedding vector size, the embedding space can be used to characterize universal and particularistic patterns of mobility across countries.
 

### 2020-07-27 paper/current/main.tex
weighted degree -> degree strength

@@
 The embedding-ranking of U.S.
-universities is less correlated with weighted degree (Spearman's $\rho = 0.45$, Fig.~\ref{fig:supp:centrality_semaxis_compare}a) and eigenvector  centrality (Spearman's $\rho = 0.55$) than with the Times Ranking itself (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_semaxis_compare}b).
+universities is less correlated with degree strength (Spearman's $\rho = 0.45$, Fig.~\ref{fig:supp:centrality_semaxis_compare}a) and eigenvector  centrality (Spearman's $\rho = 0.55$) than with the Times Ranking itself (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_semaxis_compare}b).
 The embedding ranking over-ranks large research-intensive universities such as North Carolina State University, University of Florida, and Texas A\&M University, whereas the network-derived ranking over-ranks smaller, more specialized universities such as Brandeis University, Yeshiva University, and University of San Francisco.

### 2020-07-27 paper/current/main.tex
define macro for SI, replace throughout text

@@
 
+% Define the supporting information name
+\def\SI{Supporting Information}
+
 %}}}
@@
 As a scientist's career progresses, they move between organizations or pick up additional (simultaneous) affiliations forming \textit{affiliation trajectories} (Fig.~\ref{fig:methods:mobility_sentence}).
-These trajectories encode both migration and co-affiliation---the holding of multiple simultaneous co-affiliations involving the sharing of time and capital between locations---that is typical of scientific mobility~\autocite{rodrigues2016mobility, markova2016synchronous, sugimoto2017mostimpact} (see Supplementary Materials).
+These trajectories encode both migration and co-affiliation---the holding of multiple simultaneous co-affiliations involving the sharing of time and capital between locations---that is typical of scientific mobility~\autocite{rodrigues2016mobility, markova2016synchronous, sugimoto2017mostimpact} (see \SI).
 We use the trajectories of more than three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
@@
         In a more complex case, an author lists several affiliations on the byline of papers in $t_{2}$, $t_{3}$, and $t_{4}$.
-        In the case where multiple organizations are listed within the same year, then organization IDs within a single year are randomized across each training iteration or ``epoch" of the \textit{word2vec} model (for more detail, see Supporting Materials).
+        In the case where multiple organizations are listed within the same year, then organization IDs within a single year are randomized across each training iteration or ``epoch" of the \textit{word2vec} model (for more detail, see \SI).
     }
@@
 The embedding distance defined from the cosine distance between vectors also outperforms that defined from their dot product ($R^{2} = 0.34$, Fig.~\ref{fig:supp:gravity_dot}).
-The embedding distance also out-performs alternative ``diffusion-based'' network distance measures such as the personalized-page rank scores (see Supporting Materials) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+The embedding distance also out-performs alternative ``diffusion-based'' network distance measures such as the personalized-page rank scores (see \SI) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
 Our results unequivocally argue that the embedding distance better captures actual mobility patterns than does geographic distance.
@@
 Here, we use SemAxis to operationalize the abstract notion of academic prestige, defining each pole of the axis using high- and low-ranked universities.
-We define prestige using the Times Ranking of World Universities (and using research impact from the Leiden Rankings~\autocite{waltman2012leidenrankings} in Supplementary Materials), including all ranked universities in the United States;
+We define prestige using the Times Ranking of World Universities (and using research impact from the Leiden Rankings~\autocite{waltman2012leidenrankings}, see \SI), including all ranked universities in the United States;
 the high-rank pole is defined as the mean vector of the top five U.S.
@@
 SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities are significantly correlated with the Times Ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
-Performance is also comparable to network-driven measures such as degree strength (Spearman's $\rho = 0.73$) and eigenvector centrality (Spearman's $\rho = 0.76$, see Supporting Information). 
+Performance is also comparable to network-driven measures such as degree strength (Spearman's $\rho = 0.73$) and eigenvector centrality (Spearman's $\rho = 0.76$, see \SI). 
 The strongest outliers that were ranked more highly in the Times Ranking than the embedding based ranking tend to be large state universities such as Arizona State University and  University of Florida;
@@
 Other nations exhibit different curves, such as Egypt which has an``S''-shaped curve---their largest organizations do not as well connected as other country's largest organizations. 
-Similar patterns can be found across many of the 30 of the countries with the most total researchers (Fig.~\ref{fig:concave30}), though we can only speculate on what their variations mean (see Supporting Information).
+Similar patterns can be found across many of the 30 of the countries with the most total researchers (Fig.~\ref{fig:concave30}), though we can only speculate on what their variations mean (see \SI).
 Neural embeddings encode a relationship between organization size and vector length that is universal across countries but with potentially meaningful nuances, helping the embedding to capture the landscape of global scientific mobility.
@@
 Trajectories are constructed from author affiliations listed on the byline of publications for a given author.
-Given the limitations of author-name disambiguation, we limit to papers published after 2008, when the Web of Science began providing full names and institutional affiliations~\autocite{caron2014disambiguation} that improved disambiguation (see supporting materials).
+Given the limitations of author-name disambiguation, we limit to papers published after 2008, when the Web of Science began providing full names and institutional affiliations~\autocite{caron2014disambiguation} that improved disambiguation (see \SI).
 This yields 33,934,672 author-affiliation combinations representing 12,963,792 authors.
-Each author-affiliation combination is associated with the publication year and an ID linking it to one of 8,661 a disambiguated organizational affiliation (see supporting materials for more detail)
+Each author-affiliation combination is associated with the publication year and an ID linking it to one of 8,661 a disambiguated organizational affiliation (see \SI for more detail)
 Trajectories are represented as the list of author-affiliation combinations, ordered by year of publication, and randomly ordered for combinations within the same year.

### 2020-07-27 paper/current/main.tex
percent -> %

@@
 This yields 33,934,672 author-affiliation combinations representing 12,963,792 authors.
-Each author-affiliation combination is associated with the publication year and an ID linking it to one of 8,661 a disambiguated organizational affiliation (see \SI for more detail)
+Each author-affiliation combination is associated with the publication year and an ID linking it to one of 8,661 disambiguated organizational affiliations (see \SI for more detail)
 Trajectories are represented as the list of author-affiliation combinations, ordered by year of publication, and randomly ordered for combinations within the same year.
 
-Scientific mobility is complex and can be defined in many ways~\autocite{robinson2019mobility} and at multiple levels of analysis.
 Here, authors are classified as mobile when they have at least two distinct organization IDs in their trajectory, meaning that they have published using two or more distinct affiliations between 2008 and 2019.
-Under this definition, mobile authors constitute 3,007,192 or 23.2 percent of all authors and 17,700,095 author-affiliation combinations.
+Under this definition, mobile authors constitute 3,007,192 or 23.2 \% of all authors and 17,700,095 author-affiliation combinations.
 Mobile authors were associated with, on average, 2.5 distinct organizational affiliations.
@@
 For example, France, Qatar, the USA, Iraq, and Luxembourg had the most mobile authors (Fig.~\ref{fig:supp:descriptives}c).
-However, due to their size, the USA, accounted for nearly 40 percent of all mobile authors worldwide (Fig.~\ref{fig:supp:descriptives}a), with 10 countries accounting for 80 percent of all mobility (Fig.~\ref{fig:supp:descriptives}b).
+However, due to their size, the USA, accounted for nearly 40 \% of all mobile authors worldwide (Fig.~\ref{fig:supp:descriptives}a), with 10 countries accounting for 80 \% of all mobility (Fig.~\ref{fig:supp:descriptives}b).
 The countries with the highest proportion of mobile scientists are France, Qatar, the United States, and Iraq, whereas those with the lowest are Jamaica, Serbia, Bosnia \& Herzegovina, and North Macedonia Fig.~\ref{fig:supp:descriptives}.c).
@@
 To mitigate the effect of less common organizations, we set the $f_{min}$ as  50.
-It means organizations with at least 50 appearances in affiliation trajectories are included in the final embedding, as a result, 6,580 organizations, 76 percent of all organizations, are remained.
+It means organizations with at least 50 appearances in affiliation trajectories are included in the final embedding, as a result, 6,580 organizations, 76 \% of all organizations, are remained.
 For $\alpha$, we used the default setting 0.025 and we iterates five times over whole affiliation trajectories.
@@
 where $T_{ij}$ is the real flux from the dataset. The gravity law of mobility is known to be sensitive to the case where $T_{ij} = 0$, or zero movement between organizations.
-Here, non-zero flows account for only 4.2 percent of all possible pairs of the 6,580 organizations represented in the embedding.
+Here, non-zero flows account for only 4.2 \% of all possible pairs of the 6,580 organizations represented in the embedding.
 This value is comparable to other common applications of the gravity law, such as to hone calls, commuting, and migration \autocite{simini2012universal}.
@@
 		The same information, arranged into a cumulative distribution.
-		The five countries with the highest mobility account for approximately 70 percent of all mobility.
+		The five countries with the highest mobility account for approximately 70 \% of all mobility.
 		\textbf{c.} The proportion of researchers labeled as mobile by country.
@@
 		The proportion of mobile authors by how many organizations are represented in their career trajectories.
-		For example, for mobile authors, 100 percent of authors held an affiliation with at least two organizations, whereas about 35 percent were affiliated with 3 ore more organizations between 2008 and 2019.
+		For example, for mobile authors, 100 \% of authors held an affiliation with at least two organizations, whereas about 35 \% were affiliated with 3 ore more organizations between 2008 and 2019.
 		Mobile authors are defined as those with at least two distinct organizational affiliations represented in our data.
-		\textbf{b.} 68 percent of mobile authors have at least two cities represented in their career trajectories.
-		\textbf{c.} 45 percent of mobile authors have 2 or more regions represented in their career trajectories.
-		\textbf{d.} Only 14 percent of mobile authors had 2 or more countries represented in their career trajectories.
+		\textbf{b.} 68 \% of mobile authors have at least two cities represented in their career trajectories.
+		\textbf{c.} 45 \% of mobile authors have 2 or more regions represented in their career trajectories.
+		\textbf{d.} Only 14 \% of mobile authors had 2 or more countries represented in their career trajectories.
 	}

### 2020-07-27 paper/current/main.tex
update embedding math section

@@
 However, due to their size, the USA, accounted for nearly 40 \% of all mobile authors worldwide (Fig.~\ref{fig:supp:descriptives}a), with 10 countries accounting for 80 \% of all mobility (Fig.~\ref{fig:supp:descriptives}b).
-The countries with the highest proportion of mobile scientists are France, Qatar, the United States, and Iraq, whereas those with the lowest are Jamaica, Serbia, Bosnia \& Herzegovina, and North Macedonia Fig.~\ref{fig:supp:descriptives}.c).
+The countries with the highest proportion of mobile scientists are France, Qatar, the United States, and Iraq, whereas those with the lowest are Jamaica, Serbia, Bosnia \& Herzegovina, and North Macedonia (Fig.~\ref{fig:supp:descriptives}.c).
 In most cases, countries with a high degree of inter-organization mobility also have a high degree of international mobility, indicating a high proportion of their total mobility being international (Fig.~\ref{fig:supp:descriptives}.d);
@@
 This can be written as follow, where $w$ is the size of the window and $T$ iterates through possible target organizations:
+
+%
+% MAIN W2V Equation
+%
 $$
@@
 $$
+
 where the conditional probability of observing one organization $a_{i}$, given another $a_{j}$, is defined as,
+
+%
+% CONDITIONAL PROBABILITY EQ
+%
 $$
-p(a_{i} \vert a_{j}) = \frac{\exp(u_{a_{i}} \cdot v_{a_{j}})}{\sum_{n=1}^N \exp(u_{a_{n}} \cdot v_{a_{j}})},
+p(a_{i} \vert a_{j}) = \frac{\exp(\bm{u}_{a_{i}} \cdot \bm{v}_{a_{j}})}{\sum_{n=1}^N \exp(\bm{u}_{a_{n}} \cdot \bm{v}_{a_{j}})},
 $$
-where $N$ is the total number of organizations and $v$ and $u$ are ``in-vector" and ``out-vector" respectively~\autocite{mikolov2013word2vec}.
+
+where $N$ is the total number of organizations and $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively~\autocite{mikolov2013word2vec}.
 Usually, in-vector $v$ is used as a final representation vector~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch}, we used in-vector in this study as well.
@@
 %% Word2vec parameters and training procedure
-We used  \textit{gensim} python implementation of the \textit{word2vec} model.
-The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{min}$, initial learning rage $\alpha$, and the number of iterations.
-For main results, we used $d=300$ and $w=1$, which were the parameters that explained the flux between organizations most (Fig. SI~\ref{fig:supp:hyperparams}).
-To mitigate the effect of less common organizations, we set the $f_{min}$ as  50.
-It means organizations with at least 50 appearances in affiliation trajectories are included in the final embedding, as a result, 6,580 organizations, 76 \% of all organizations, are remained.
-For $\alpha$, we used the default setting 0.025 and we iterates five times over whole affiliation trajectories.
-We checked results were robust across various hyper-parameters settings, while aforementioned settings yield the best result.
+We used  \texttt{gensim} python implementation of the \textit{word2vec} model.
+The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{\min}$, initial learning rage $\alpha$, and the number of iterations.
+For main results, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between organizations, though results were robust across different settings (Fig.~\ref{fig:supp:hyperparams}).
+To mitigate the effect of less common organizations, we set the $f_{\min}$ as 50, limiting to organizations appearing at least 50 times across the training trajectories, or 6,580 organizations (76 \%) unique organizations.
+We set $\alpha$ as the default value of 0.025 and iterate five times over all training affiliation trajectories.
 

### 2020-07-27 paper/current/main.tex
update remaining methods section

@@
 %% Distance calculations
-We calculate $T_{ij}$, the pairwise number of co-affiliations between organizations, calculated as the number of co-occurrences of organizations within author co-affiliation trajectories.
-For example, $T_{ij} = 10$ indicates that ten authors were co-affiliated with both organization $i$ and $j$ between 2008 and 2019, as evidenced from their publications.
+$T_{ij}$, is the number of co-occurrences of organizations within author affiliation trajectories.
+For example, $T_{ij} = 10$ indicates that ten authors were affiliated with both organization $i$ and $j$ between 2008 and 2019, as evidenced from their publications.
 We treat all co-affiliations are symmetric, meaning that $T_{ij} = T_{ji}$.
@@
 Geographic distance is calculated as the great circle distance, in kilometers, between pairs of organizations.
-When less than one kilometer, a distance of one is imputed.
-The embedding distance with the cosine similarity, $d_{ij}$, is calculated as the pairwise cosine distance between vectors from the learned organization embedding, where $v_{i}$ and $v_{j}$ represent the vectors and $d_{ij} = 1 - \frac{v_{i} \cdot v_{j}}{\lVert v_{i} \rVert \lVert v_{j} \rVert}$.
-Negative cosine distances, caused by cosine similarities greater than one, are truncated at zero. 
-Note that this distance derived from the embedding space is not a formal metric, as it does not satisfy the triangle inequality, however such distnaces have still proved practically useful in make tasks~\autocite{lerman2007embedding, brown1970migration, brown1970functional, kim2018functional}.
+When less than one kilometer, a distance of 1 km is imputed.
+The embedding distance with the cosine similarity, $d_{ij}$, is calculated as the pairwise cosine distance between vectors from the learned organization embedding, where $v_{i}$ and $v_{j}$ represent the vectors and $d_{ij} = 1 - \frac{\bm{v}_{i} \cdot \bm{v}_{j}}{\lVert \bm{v}_{i} \rVert \lVert \bm{v}_{j} \rVert}$.
+Note that this distance derived from the embedding space is not a formal metric, as it does not satisfy the triangle inequality, however such distances have still proved practically useful in many tasks~\autocite{lerman2007embedding, brown1970migration, brown1970functional, kim2018functional}.
 
@@
 
+%
+% Gravity law EQ
+%
 \begin{equation}
@@
 \end{equation}
-where $m_{i}$ and $m_{j}$ are the organization masses, or the yearly-average count of unique mobile and non-mobile authors affiliated with each organization during the time window, and $f(r_{ij})$ is a distance-decaying function  between the two organizations.
+
+where $m_{i}$ and $m_{j}$ are the organization masses, or the yearly-average count of unique authors, both mobile and non-mobile, affiliated with each organization during the time window, and $f(r_{ij})$ is a distance-decaying function  between the two organizations.
 There are two popular forms of the $f(r_{ij})$.
 The first one is power-law function with $f(r_{ij})= r^{-\alpha}_{ij} \ (\alpha > 0)$, and the another one is exponential function with $f(r_{ij}) = e^{-\beta r_{ij}} \ (\beta > 0)$ \autocite{chen2015distance}.
-$f(r_{ij})$, $C$ can be chosen as to fit the data with the simple regression.
+$f(r_{ij})$ and $C$ can be fit with the data.
 
@@
 For embedding distance, we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data.
-To estimate parameters $C$, $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_basic}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression
+Following past studies~\autocite{simini2012universal}, parameters $C$, $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_basic}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression
 
@@
 
-Let $S^+ = \{v_1^+, v_2^+ \cdots v_n^+\}$ and $S^- =\{v_1^-, v_2^- \cdots v_n^-\}$ be the set of positive and negative pole organization vectors respectively.
-Then, the average vectors of each set can be calculated as $V^{+} = \frac{1}{n}\sum^n_1 v_i^+$ and $V^{-} = \frac{1}{n}\sum^n_1 v_i^-$.
-From these average vectors of each set of poles, the semantic axis is defined as $V_{\text{axis}} = V^{+} - V^{-}$.
-Then,  a score of organization $w$ is calculated as the cosine similarity of the organization's vector with the axis,
+Let $S^+ = \{\bm{v}_1^+, \bm{v}_2^+ \cdots \bm{v}_n^+\}$ and $S^- =\{\bm{v}_1^-, \bm{v}_2^- \cdots \bm{v}_n^-\}$ be the set of positive and negative pole organization vectors respectively.
+Then, the average vectors of each set can be calculated as $\bm{V}^{+} = \frac{1}{n}\sum^n_1 \bm{v}_i^+$ and $\bm{V}^{-} = \frac{1}{n}\sum^n_1 \bm{v}_i^-$.
+From these average vectors of each set of poles, the semantic axis is defined as $\bm{V}_{\text{axis}} = \bm{V}^{+} - \bm{V}^{-}$.
+Then,  a score of organization $a$ is calculated as the cosine similarity of the organization's vector with the axis,
 
 $$
-score(w)_{V_{\text{axis}}} = \cos(v_{w}, V_{\text{axis}}) = \frac{u_{w} \cdot V_{\text{axis}}}{\lVert v_{w} \rVert \lVert V_{\text{axis}} \rVert},
+score(a)_{\bm{V}_{\text{axis}}} = \cos(\bm{v}_{a}, \bm{V}_{\text{axis}}) = \frac{\bm{u}_{a} \cdot \bm{V}_{\text{axis}}}{\lVert \bm{v}_{a} \rVert \lVert \bm{V}_{\text{axis}} \rVert},
 $$
-where higher scores mean that organization $w$ is more closely aligned to $S^+$ than $S^-$.
-
-We apply SemAxis to U.S. universities by defining two axes, one of geography and one of academic prestige.
+
+where higher scores mean that organization $a$ is more closely aligned to $S^+$ than $S^-$.
+
+We apply SemAxis to U.S. universities by defining two axes that capture geography and academic prestige, respectively.
 The poles of the geographic axis are defined as the mean vector of all vectors corresponding to organizations in California, and then the mean of all vectors of organizations in Massachusetts.
@@
 \paragraph*{S8 Text}
-\label{si:text:network_ranking}
+\label{si:text:boomerang_speculation}
 {\bf Speculation on variations of the convex-curve pattern.}

### 2020-07-28 paper/current/main.tex
my pass

@@
 This yields 33,934,672 author-affiliation combinations representing 12,963,792 authors.
-Each author-affiliation combination is associated with the publication year and an ID linking it to one of 8,661 disambiguated organizational affiliations (see \SI for more detail)
+Each author-affiliation combination is associated with the publication year and an ID linking it to one of 8,661 disambiguated organizational affiliations (see \SI for more detail).
 Trajectories are represented as the list of author-affiliation combinations, ordered by year of publication, and randomly ordered for combinations within the same year.
@@
 $$
-
 where the conditional probability of observing one organization $a_{i}$, given another $a_{j}$, is defined as,
@@
 $$
-
 where $N$ is the total number of organizations and $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively~\autocite{mikolov2013word2vec}.
-Usually, in-vector $v$ is used as a final representation vector~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch}, we used in-vector in this study as well.
+Usually, in-vector $\bm{v}$ is used as a final representation vector~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch}, we used in-vector in this study as well.
 
@@
 We used  \texttt{gensim} python implementation of the \textit{word2vec} model.
-The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{\min}$, initial learning rage $\alpha$, and the number of iterations.
+The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{\min}$, initial learning rate $\alpha$, and the number of iterations.
 For main results, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between organizations, though results were robust across different settings (Fig.~\ref{fig:supp:hyperparams}).
-To mitigate the effect of less common organizations, we set the $f_{\min}$ as 50, limiting to organizations appearing at least 50 times across the training trajectories, or 6,580 organizations (76 \%) unique organizations.
+To mitigate the effect of less common organizations, we set the $f_{\min}$ as 50, limiting to organizations appearing at least 50 times across the training trajectories,  6,580 organizations (76 \%) unique organizations are kept in the result embedding .
 We set $\alpha$ as the default value of 0.025 and iterate five times over all training affiliation trajectories.
@@
 %% Distance calculations
-$T_{ij}$, is the number of co-occurrences of organizations within author affiliation trajectories.
+$T_{ij}$ is the number of co-occurrences of organizations within author affiliation trajectories.
 For example, $T_{ij} = 10$ indicates that ten authors were affiliated with both organization $i$ and $j$ between 2008 and 2019, as evidenced from their publications.
@@
 The embedding distance with the cosine similarity, $d_{ij}$, is calculated as the pairwise cosine distance between vectors from the learned organization embedding, where $v_{i}$ and $v_{j}$ represent the vectors and $d_{ij} = 1 - \frac{\bm{v}_{i} \cdot \bm{v}_{j}}{\lVert \bm{v}_{i} \rVert \lVert \bm{v}_{j} \rVert}$.
-Note that this distance derived from the embedding space is not a formal metric, as it does not satisfy the triangle inequality, however such distances have still proved practically useful in many tasks~\autocite{lerman2007embedding, brown1970migration, brown1970functional, kim2018functional}.
+Note that cosine distance derived from the embedding space is not a formal metric, as it does not satisfy the triangle inequality, however cosine distance have still proved practically useful across many tasks~\autocite{lerman2007embedding, brown1970migration, brown1970functional, kim2018functional}.
 
@@
 \end{equation}
-
 where $m_{i}$ and $m_{j}$ are the organization masses, or the yearly-average count of unique authors, both mobile and non-mobile, affiliated with each organization during the time window, and $f(r_{ij})$ is a distance-decaying function  between the two organizations.
@@
 For embedding distance, we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data.
-Following past studies~\autocite{simini2012universal}, parameters $C$, $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_basic}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression
+Following past studies~\autocite{simini2012universal}, parameters $C$, $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_basic}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression \autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}
 
@@
 $$
-
 where higher scores mean that organization $a$ is more closely aligned to $S^+$ than $S^-$.
@@
 % S2 Text
-\paragraph*{S2Text}
+\paragraph*{S2 Text}
 \label{si:text:mobility_models}

### 2020-07-28 paper/current/main.tex
minor edit

@@
 
-Data, analysis, and associated code have been made publicly available and can be found at \url{https://github.com/murrayds/sci-mobility-emb}
+Data, analysis, and associated code have been made publicly available and can be found at \url{https://github.com/murrayds/sci-mobility-emb}.
 
@@
 For main results, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between organizations, though results were robust across different settings (Fig.~\ref{fig:supp:hyperparams}).
-To mitigate the effect of less common organizations, we set the $f_{\min}$ as 50, limiting to organizations appearing at least 50 times across the training trajectories,  6,580 organizations (76 \%) unique organizations are kept in the result embedding .
+To mitigate the effect of less common organizations, we set the $f_{\min}$ as 50, limiting to organizations appearing at least 50 times across the training trajectories,  6,580 unique organizations are kept in the result embedding .
 We set $\alpha$ as the default value of 0.025 and iterate five times over all training affiliation trajectories.
@@
 For embedding distance, we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data.
-Following past studies~\autocite{simini2012universal}, parameters $C$, $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_basic}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression \autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}
+Following past studies~\autocite{simini2012universal}, parameters $C$, $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_basic}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression \autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity, simini2012universal}
 

### 2020-07-28 paper/current/main.tex
removing dots

@@
 However, due to their size, the USA, accounted for nearly 40 \% of all mobile authors worldwide (Fig.~\ref{fig:supp:descriptives}a), with 10 countries accounting for 80 \% of all mobility (Fig.~\ref{fig:supp:descriptives}b).
-The countries with the highest proportion of mobile scientists are France, Qatar, the United States, and Iraq, whereas those with the lowest are Jamaica, Serbia, Bosnia \& Herzegovina, and North Macedonia (Fig.~\ref{fig:supp:descriptives}.c).
-In most cases, countries with a high degree of inter-organization mobility also have a high degree of international mobility, indicating a high proportion of their total mobility being international (Fig.~\ref{fig:supp:descriptives}.d);
+The countries with the highest proportion of mobile scientists are France, Qatar, the United States, and Iraq, whereas those with the lowest are Jamaica, Serbia, Bosnia \& Herzegovina, and North Macedonia (Fig.~\ref{fig:supp:descriptives}c).
+In most cases, countries with a high degree of inter-organization mobility also have a high degree of international mobility, indicating a high proportion of their total mobility being international (Fig.~\ref{fig:supp:descriptives}d);
 However, some countries such as France and the United States seem to have more domestic mobility than international mobility.

### 2020-07-28 paper/current/main.tex
minor edits

@@
 Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphasis on teaching, such as Barry University and California State University at Long Beach.
-By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations which are typically not ranked, such as government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e), or for which rankings are often low-resolution and idiosyncratic, such as for regional and liberal arts universities (Fig.~\ref{fig:semaxis}f).
+By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations for which rankings are often low-resolution or incomplete, such as regional and liberal arts universities (Fig.~\ref{fig:semaxis}d), or for which no such rankings exist, such as government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).
 
@@
 		\textbf{c-f.} Illustration of SemAxis projection along two axes;  \textit{latent geographical axis}, from California to Massachusetts (left to right) and the \textit{prestige axis}.
-		Shown for U.S. Universities (\textbf{c}), Teaching colleges (\textbf{d}), Research institutes (\textbf{e}), and Government organizations (\textbf{f}).
+		Shown for U.S. Universities (\textbf{c}), regional and liberal arts universities (\textbf{d}), Research institutes (\textbf{e}), and Government organizations (\textbf{f}).
 		Full organization names listed in Table~\ref{table:supp:orglabels}.
@@
 By embedding affiliation trajectories, we aim to learn a dense vector for every organization where the distance between vectors relates to the tendency for two organizations to occur in similar contexts.
-Formally, model attempt to maximize average log probability a target organization  in an affiliation trajectory $a_{t}$, given organizations in the surrounding context window, $a_{t+k}$.
+Formally,  the model attempt to maximize average log probability of a target organization appearing in an affiliation trajectory $a_{t}$, given organizations in the surrounding context window, $a_{t+k}$.
 This can be written as follow, where $w$ is the size of the window and $T$ iterates through possible target organizations:
@@
 where $N$ is the total number of organizations and $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively~\autocite{mikolov2013word2vec}.
-Usually, in-vector $\bm{v}$ is used as a final representation vector~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch}, we used in-vector in this study as well.
+We follow past studies and use the in-vector, $\bm{v}$, as the final representation~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch}.
 
 %% Word2vec parameters and training procedure
-We used  \texttt{gensim} python implementation of the \textit{word2vec} model.
+We used the \texttt{gensim} python implementation of the \textit{word2vec} model. 
 The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{\min}$, initial learning rate $\alpha$, and the number of iterations.
 For main results, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between organizations, though results were robust across different settings (Fig.~\ref{fig:supp:hyperparams}).
-To mitigate the effect of less common organizations, we set the $f_{\min}$ as 50, limiting to organizations appearing at least 50 times across the training trajectories,  6,580 unique organizations are kept in the result embedding .
-We set $\alpha$ as the default value of 0.025 and iterate five times over all training affiliation trajectories.
+To mitigate the effect of less common organizations, we set the $f_{\min}$ as 50, limiting to organizations appearing at least 50 times across the training trajectories;
+6,580 unique organizations appear in the resulting embedding.
+We set $\alpha$ to its default value of 0.025 and iterate five times over all training affiliation trajectories.
 

### 2020-07-28 paper/current/main.tex
minor edit, highlight community college, seminaries, etc.

@@
 Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphasis on teaching, such as Barry University and California State University at Long Beach.
-By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations for which rankings are often low-resolution or incomplete, such as regional and liberal arts universities (Fig.~\ref{fig:semaxis}d), or for which no such rankings exist, such as government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).
+By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations for which rankings are often low-resolution or incomplete, such as regional and liberal arts universities, seminaries, musical schools, and community colleges (Fig.~\ref{fig:semaxis}d), or for which no such rankings exist, such as government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).
 
@@
 		\textbf{c-f.} Illustration of SemAxis projection along two axes;  \textit{latent geographical axis}, from California to Massachusetts (left to right) and the \textit{prestige axis}.
-		Shown for U.S. Universities (\textbf{c}), regional and liberal arts universities (\textbf{d}), Research institutes (\textbf{e}), and Government organizations (\textbf{f}).
+		Shown for U.S. Universities (\textbf{c}), regional and liberal arts colleges (\textbf{d}), Research institutes (\textbf{e}), and Government organizations (\textbf{f}).
 		Full organization names listed in Table~\ref{table:supp:orglabels}.

### 2020-07-31 paper/current/main.tex
stat comments—up to pg 4

@@
 
-Human mobility and migration drives major social phenomena such as the growth and evolution of cities~\autocite{wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity}, economies~\autocite{kaluza2010cargo, kerr2011immigration}, and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}.
+Human mobility and migration drive major societal phenomena such as the growth and evolution of cities~\autocite{wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity}, economies~\autocite{kaluza2010cargo, kerr2011immigration}, and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}.
 Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity} aim to capture mobility between places using their population and the \textit{distance} between them.
-However, geographic distance is less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} wherein the physical barrier shrinks while linguistic, economic, cultural, and historical similarities matter more.
+However, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} wherein physical barriers are shrinking while linguistic, economic, cultural, and historical similarities are becoming more important.
 Alternative notions of functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} attempt to re-define distance by using some of aforementioned factors~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional} but are often arbitrary and consider only single isolated facets.
-Here, using a rich dataset of scientific mobility, we demonstrate that a data-driven neural embedding~\autocite{mikolov2013word2vec} can successfully encodes a functional distance between organizations and captures the latent and multi-faceted structure of scientist's mobility.
+Here, using a rich dataset of scientific mobility, we demonstrate that a data-driven neural embedding~\autocite{mikolov2013word2vec} can successfully encode a functional distance between organizations and capture the latent and multi-faceted structure of scientist's mobility.
 We demonstrate that the cosine distance between organization embedding vectors, constructed using the affiliation trajectories of scientists in the Web of Science database, better explain and predict real mobility than geographic distance.
-Exploiting their unique properties, we demonstrate that the embedding space encodes not only geographic relations between organizations, but also relations based on culture, language, and academic prestige at multiple levels of granularity.
-Also captured in the embedding space is a universal pattern capturing the relationship between organization's size and their connectedness.
+We demonstrate that the embedding space encodes not only geographic relations between organizations, but also relations based on culture, language, and academic prestige at multiple levels of granularity.
+The embedding space also captures the relationship between organization's size and their connectedness that repeats across most countries.
 The ability to learn scalable, dense, and meaningful high-resolution vector representations of mobility directly from the data can open up a new avenue of studying human mobility.
@@
 While geographic distance may have driven human movements in the past, it holds less importance to a world connected by rapid transit, complex international relations, and dense airline networks.
-For instance, a person living in Australia is more likely to migrate to the United Kingdom, a far-away country with similar language and culture, than to much closer countries like Indonesia~\autocite{pew2018migration}.
-Similarly, a student in South Korea is more likely to attend universities in Canada than those in North Korea~\autocite{unesco2019students}.
-Although geographic distance has been used as the most prominent basis for models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} model, there have been attempts to define alternative notions of distance, or ~ \textit{functional distances}~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional} from real-world data or \textit{a priori} relationships between geographic entities.
+For instance, a person living in Australia is more likely to migrate to the United Kingdom, a far-away country with similar language and culture, than to a much closer country such as Indonesia~\autocite{pew2018migration}.
+Similarly, a student in South Korea is more likely to attend a university in Canada than one in North Korea~\autocite{unesco2019students}.
+Although geographic distance has been used as the most prominent basis for models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} models, there have been attempts to define alternative notions of distance, or ~ \textit{functional distances}~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional} from real-world data or \textit{a priori} relationships between geographic entities.
 Yet, functional distances are often low-resolution and rely on somewhat arbitrary decisions about the importance of each factor.
@@
 The neural embedding, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been  making breakthroughs by revealing novel insights into texts~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
-Neural embedding is also computationally efficient, robust to noise, and can encode reasonably rich relations between entities as geomemetric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.
-
-We use scientific mobility, inferred from affiliations, to demonstrate the effectiveness of our approach.
+They are also computationally efficient, robust to noise, and can encode reasonably rich relations between entities as geomemetric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.
+
+We use scientific mobility, inferred from researcher's affiliations, to demonstrate the effectiveness of our approach.
 Scientific mobility is a central driver of the increasingly-globalized scientific enterprise~\autocite{czaika2018globalisation, altbach2004globalization, box2008competition}, being strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}.
 Moreover, scientific mobility has known structure, such as the centrality of the United States and the United Kingdom, and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career} that should be captured in a representation.
-However, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, one underlying challenges being the diminishing role of geography in shaping the landscape of scientific mobility.
-
-Here, scientific mobility is operationalized using researcher's organizational affiliations derived from their publication histories indexed in a comprehensive bibliographic database (see Methods).
+However, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, being further confounded by the diminishing role of geography in shaping the landscape of scientific mobility.
+
+Here, scientific mobility is operationalized using a researcher's organizational affiliations derived from their publication histories indexed in a comprehensive bibliographic database (see Methods).
 The most fine-grained geographical unit in this data is the organization, such as a ``university'', ``research institute'', ``business'', or ``government agency''.
 As a scientist's career progresses, they move between organizations or pick up additional (simultaneous) affiliations forming \textit{affiliation trajectories} (Fig.~\ref{fig:methods:mobility_sentence}).
-These trajectories encode both migration and co-affiliation---the holding of multiple simultaneous co-affiliations involving the sharing of time and capital between locations---that is typical of scientific mobility~\autocite{rodrigues2016mobility, markova2016synchronous, sugimoto2017mostimpact} (see \SI).
+Thus, the trajectories encode both migration and co-affiliation---the holding of multiple simultaneous co-affiliations involving the sharing of time and capital between locations---that is typical of scientific mobility~\autocite{rodrigues2016mobility, markova2016synchronous, sugimoto2017mostimpact} (see \SI).
 We use the trajectories of more than three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
@@
 A vector-space embedding of organizations is learned by using affiliation trajectories as input to the standard skip-gram with negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
-In the resulting embedding, each organization corresponds to a single vector, and vectors relate to one another based on the likelihood of organizations appearing near together in the affiliation trajectory data.
+In the resulting embedding, each organization corresponds to a single vector, and vectors relate to one another based on the likelihood of organizations appearing adjacent to one another in the same affiliation trajectory.
 The functional distance between two organizations is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.
@@
         An author published five papers across five time periods, with only one affiliation listed in the byline of each paper.
-        To each organization, a unique identifier is assigned, and they are assembled into an affiliation trajectory ordered by year of publication.
+        A unique identifier is assigned to each each organization and they are assembled into an affiliation trajectory ordered by year of publication.
         \textbf{b.}
@@
 
-We assess the performance of the embedding distance relative to geographic distance by evaluating their ability to explain and predict real-world mobility as parameters in the Gravity Model of mobility~\autocite{zipf1946gravity, barbosa2018human}.
+To assess the performance of the embedding distance relative to geographic distance, we evaluate their correlation with real-world mobility data and their performance in predicting real-world mobility flows as parameters to the Gravity Model~\autocite{zipf1946gravity, barbosa2018human}.
 The Gravity Model, taking inspiration from Newton's law of gravity, is one of the most broadly applied mobility models~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} .
@@
 \end{equation}
-where the \textit{expected flux}, $\hat{T_{ij}}$, or expected number of authors who were affiliated with both organizations during the time period is proportional to the organization's sizes (the sum of both mobile and non-mobile authors, see Data and Methods), $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+where the \textit{expected flux}, $\hat{T_{ij}}$, or expected number of authors who were affiliated with both organizations during the time period, is proportional to the organizations' sizes (the sum of both mobile and non-mobile authors, see Data and Methods), $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
 The distance function is defined in terms of either the geographic distance between organizations or the embedding distance.
@@
 The amount of variance explained by embedding distance ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) is more than twice that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
-This pattern holds when considering the subset of only domestic (Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (Fig.~\ref{fig:supp:gravity_correlation}d).
-After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance (Fig.~\ref{fig:gravity_performance}c--d), which also holds for the subsets of only domestic (Fig.~\ref{fig:supp:gravity_correlation}e--f) and international mobility (Fig.~\ref{fig:supp:gravity_correlation}g--h).
+This pattern holds when considering the subset of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d).
+After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance (Fig.~\ref{fig:gravity_performance}c--d), which also holds for the subsets of only domestic (Fig.~\ref{fig:supp:gravity_correlation}e--f) and only international mobility (Fig.~\ref{fig:supp:gravity_correlation}g--h).
 The embedding distance defined from the cosine distance between vectors also outperforms that defined from their dot product ($R^{2} = 0.34$, Fig.~\ref{fig:supp:gravity_dot}).
 The embedding distance also out-performs alternative ``diffusion-based'' network distance measures such as the personalized-page rank scores (see \SI) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-Our results unequivocally argue that the embedding distance better captures actual mobility patterns than does geographic distance.
+Our results unequivocally demonstrate that the embedding distance better captures actual mobility patterns than does geographic distance.
 

### 2020-07-31 paper/current/main.tex
stasa comments—up to page 7

@@
 The embedding also allows us to create informative visualizations of global scientific mobility.
-To explore the topological structure of the embedding, we use a standard dimensionality reduction technique (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation of the embedding (Fig.~\ref{fig:projection}a).
+To explore the topological structure of the embedding, we use a standard dimensionality reduction technique (UMAP~\autocite{mcinnes2018umap}) to obtain its two-dimensional representation (Fig.~\ref{fig:projection}a).
 By showing relationships between individual organizations, rather than aggregates such as nations or cities, this projection constitutes the largest and highest resolution ``map'' of scientific mobility to date.
@@
 The embedding space also allows us to \textit{zoom in} on subsets and re-project them in order to reveal more local relationships.
-For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries between Egypt to Philippines that corresponds largely to geography, but with some peculiar exceptions based on cultural and religious spectrum.
-For example, countries like Iraq are nearer to some southeast-Asian countries like Malaysia, with a cosine distance between the nation's aggregate vectors of $d = 0.29$, than to nearer and more religiously-similar nations like Saudi Arabia ($d = 0.50$) and Qatar ($d = 0.51$).
+For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries between Egypt and the Philippines that corresponds largely to geography, but with some peculiar exceptions along the cultural and religious spectrums.
+For example, Iraq is nearer to some southeast-Asian countries such as Malaysia, with a cosine distance between the nation's aggregate vectors of $d = 0.29$, than to closer and more religiously-similar nations such as Saudi Arabia ($d = 0.50$) and Qatar ($d = 0.51$).
 Linguistic and historical ties are also conspicuous.
@@
 $d = 0.52$ for Mexico and $d = 0.39$ vs.
-$d = 0.49$ for Chile) reflecting linguistic and cultural constraints.
-Similarly, North-African countries that were once under French rule such as Morocco are nearer to France ($d =0.35$) than to similarly-distant European countries as Spain ($d = 0.40$) and Italy ($d = 0.53$).
+$d = 0.49$ for Chile) reflecting linguistic and cultural ties.
+Similarly, North-African countries that were once under French rule such as Morocco are nearer to France ($d =0.35$) than to similarly-distant European countries such as Spain ($d = 0.40$) and Italy ($d = 0.53$).
 Comparable structural patterns exist even within a single country.
-For example, at the global level (Fig~\ref{fig:projection}a), organizations within Quebec in Canada are located nearer the French cluster ($d = 0.65$) than the rest of the Canadian universities ($d = 0.88$).
+For example, at the global level (Fig~\ref{fig:projection}a), organizations within Quebec in Canada are located nearer the French cluster ($d = 0.65$) than the rest of the Canadian organizations ($d = 0.88$).
 
 The geographic structure of the global embedding is mirrored in the re-projection of the United States, wherein organizations are largely organized according to geography (Fig.~\ref{fig:projection}d).
-By re-projecting Massachusetts (Fig.~\ref{fig:projection}e), we observe structure based on urban centers (Boston vs.
-Worcester) as well as on organization type (e.g., hospitals vs.
-universities) and university systems.
+By re-projecting Massachusetts (Fig.~\ref{fig:projection}e), we observe structure based on: urban centers (Boston vs.
+Worcester), organization type (e.g., hospitals vs.
+universities) and university systems (UMass vs.
+Harvard \& MIT).
 For example, even though UMass Boston is located in Boston, it clusters with  other universities in the UMass System ($d = 0.34$) rather than the other typically more highly-ranked and research-focused universities in Boston ($d = 0.41$), reflecting a relative lack of mobility between the two systems.
@@
 		\textbf{b.} Zooming into (re-projecting) the area containing countries in the Middle East and South and Southeast Asia shows a geographic and cultural gradient of country clusters.
-		\textbf{c.} Similarly, zooming into the area organizations in Spain, Portugal, South, and Central America show clustering by majority language group--Spanish and Portuguese.
+		\textbf{c.} Similarly, zooming into the area organizations in Spain, Portugal, South, and Central America shows clustering by most widely-spoken majority language group--Spanish and Portuguese.
 		\textbf{d.} Doing the same for organizations in the United States reveals geographic clustering based on state, roughly grouped by Census Bureau-designated regions,
@@
 
-We quantify the relative importance of geography (by region), and language (by majority language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering by explicitly adjusting the relative importance of different levels of the hierarchy with scaling parameter $r$, acting like a ``zooming lens''.
+We quantify the relative importance of geography (by region), and language (by most widely-spoken language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering by explicitly adjusting the relative importance of different levels of the hierarchy with scaling parameter $r$, acting like a ``zooming lens''.
 If $r$ is high, the similarity is based on the lower levels of the dendrogram, whereas when $r$ is low, the similarity is based on higher levels.
@@
 \ref{fig:clustering}b demonstrates that the region plays a major role at higher levels of the clustering process (low $r$), and language (family) explains the clustering more at the lower levels (high $r$).
-This suggests that the embedding space captures the hierarchical structure of mobility---at the highest level, geography defines the embedding space, followed then by language.
+This suggests that the embedding space captures the hierarchical structure of mobility---at the highest level, geography defines the embedding space, followed by language.
 

### 2020-07-31 paper/current/main.tex
finished stasa's comments

@@
 		Color of country names corresponds to their cluster.
-		Color of three cell rows separated from the matrix correspond to, from left to right, the region of the country, the language family~\autocite{ethnologue}, and the individual language.
+		Color of three cell rows separated from the matrix corresponds to, from left to right, the region of the country, the language family~\autocite{ethnologue}, and the individual language.
 		\textbf{b.}	Element-centric cluster similarity~\autocite{gates2019element} reveals the factors dictating hierarchical clustering.
 		Region better explains the grouping of country vectors at higher levels of the clustering.
-		Language family, and then majority spoken language, better explain the grouping of countries at more fine-grained level.
+		Language family, and then the most widely-spoken language, better explain the grouping of countries at more fine-grained level.
 	}
@@
 
-Prestige hierarchy is known to underpin the dynamics of scientific mobility~\autocite{deville2014career, clauset2015hierarchy}, but can the hierarchy be encoded in the embedding space, to which no explicit information on prestige is given and for which the direction of mobility not known?
+Prestige hierarchy is known to underpin the dynamics of scientific mobility~\autocite{deville2014career, clauset2015hierarchy}, but can the hierarchy be encoded in the embedding space, to which no explicit information on prestige is given and for which the direction of mobility is not known?
 We test this by exploiting the geometric properties of the embedding space with SemAxis~\autocite{an2018semaxis}, an approach originally designed to characterize the semantics of words in word embeddings.
 Here, we use SemAxis to operationalize the abstract notion of academic prestige, defining each pole of the axis using high- and low-ranked universities.
-We define prestige using the Times Ranking of World Universities (and using research impact from the Leiden Rankings~\autocite{waltman2012leidenrankings}, see \SI), including all ranked universities in the United States;
+To define prestige of ranked U.S.
+ranked univeristies, we use the Times Ranking of World Universities (we also use research impact from the Leiden Rankings~\autocite{waltman2012leidenrankings}, see \SI);
 the high-rank pole is defined as the mean vector of the top five U.S.
-universities according to the rankings, whereas the low-ranked pole is defined using the five bottom-ranked and geographically matched (by U.S.
+universities according to the rankings, whereas the low-ranked pole is defined using the five bottom-ranked (geographically-matched by U.S.
 census region) universities.
@@
 For reference, the embedding-based ranking achieves correlation with the Times Ranking comparable to that between the Times ranking and the publication impact scores from the Leiden Ranking~\autocite{waltman2012leidenrankings}, a well-known bibliometrically-informed university ranking (Spearman's $\rho = 0.87$, Fig.~\ref{fig:semaxis}b).
-The correlation between the embedding based ranking and the Times ranking is robust with the number of organizations used to define the axes (Fig.
-SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities are significantly correlated with the Times Ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
+The correlation between the embedding-based ranking and the Times ranking is robust regardless of the number of organizations used to define the axes (Fig.
+SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities produces a ranking that is significantly correlated with the Times Ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
 Performance is also comparable to network-driven measures such as degree strength (Spearman's $\rho = 0.73$) and eigenvector centrality (Spearman's $\rho = 0.76$, see \SI). 
-The strongest outliers that were ranked more highly in the Times Ranking than the embedding based ranking tend to be large state universities such as Arizona State University and  University of Florida;
-Those ranked higher in the embedding based ranking tend to be relatively-small universities such as the University of San Francisco and University of Maryland Baltimore County near major urban areas.
+The strongest outliers that were ranked more highly in the Times Ranking than in the embedding-based ranking tend to be large state universities such as Arizona State University and  University of Florida.
+Those ranked higher in the embedding based ranking tend to be relatively-small universities near major urban areas such as the University of San Francisco and University of Maryland Baltimore County.
 This suggests that the organization embedding captures the latent prestige hierarchy inherent to academic mobility with a high degree of resolution and reliability, even without providing any explicit information on prestige~\autocite{deville2014career, clauset2015hierarchy}.
 
-The axes can further be visualized to examine the the relative position of organizations along the prestige axis, and along a geographic axis between California and Massachusetts that aids visualization.
-Prestigious universities such as Colombia, Stanford, MIT, Harvard, and Rockefeller are positioned towards the top of the axis (Fig.~\ref{fig:semaxis}c).
+The axes can further be visualized to examine the relative position of organizations along the prestige axis, and along a geographic axis between California and Massachusetts that aids visualization.
+Prestigious universities such as Columbia, Stanford, MIT, Harvard, and Rockefeller are positioned towards the top of the axis (Fig.~\ref{fig:semaxis}c).
 Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphasis on teaching, such as Barry University and California State University at Long Beach.
@@
 We also find that the size (L2 norm) of the organization embedding vectors provides insights into the characteristics of organizations.
-Up to a point, the size of U.S. organization's vectors tends to increase proportional to its number of researchers (both mobile and non-mobile) who published with that organization;
+Up to a point (around 1,000 researchers), the size of U.S.
+organization's vectors tends to increase proportional to the number of researchers (both mobile and non-mobile) within that organization with published work;
 these organizations are primarily teaching-focused institutions, agencies, and hospitals that either are not ranked or have a low ranking.
-However, at around 1,000 researchers, the size of the vector decreases as the number of researchers increases;
-organizations here are primarily research-intensive and prestigious universities with higher rankings, research outputs, R\&D funding, and doctoral students (Fig.~\ref{fig:supp:length_vs_metaInfo}).
+However, at around 1,000 researchers, the size of the vector decreases as the number of researchers increases.
+These organizations are primarily research-intensive and prestigious universities with higher rankings, research outputs, R\&D funding, and doctoral students (Fig.~\ref{fig:supp:length_vs_metaInfo}).
 A similar pattern has been observed in applications of neural embedding to natural language, wherein the size of word vectors was found to represent the word ``significance''~\autocite{schakel2015measuring}.
@@
 
-This same convex-curve repeats across many countries such as with China, which closely mirrors that of the United States (Fig.~\ref{fig:length}b).
-Smaller but scientifically advanced countries such as Australia, and other large populous countries like Brazil exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset), though their exact position and size varies between countries.
-Other nations exhibit different curves, such as Egypt which has an``S''-shaped curve---their largest organizations do not as well connected as other country's largest organizations. 
+This same convex-curve repeats across many countries such as China, which closely mirrors that of the United States (Fig.~\ref{fig:length}b).
+Smaller but scientifically advanced countries such as Australia, and other large populous countries such as Brazil exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset), though their exact position and size varies.
+Other nations exhibit different curves, such as Egypt which has an``S''-shaped curve---meaning that their largest organizations are not as well connected as other countries' largest organizations. 
 Similar patterns can be found across many of the 30 of the countries with the most total researchers (Fig.~\ref{fig:concave30}), though we can only speculate on what their variations mean (see \SI).
@@
 		\textbf{Size of organization embedding vectors captures prestige and size of organizations.}
-		\textbf{a.} Size (L2 norm) of organization embedding vectors compared to their number of researchers for U.S. universities.
+		\textbf{a.} Size (L2 norm) of organization embedding vectors compared to the number of researchers for U.S. universities.
 		Color indicates the rank of the university from the Times ranking, with 1 being the highest ranked university.
 		Uncolored points are universities not listed on a Times ranking.
-		A convex-shape emerges, wherein larger universities tend to more distant from the origin (large L2 norm); however, the more prestigious the university, the closer it is to the origin (small L2 norm).
-		The L2 norm is correlated weakly with the ratio between organization's of number of connected organizations and its number of researchers ($R^{2} = 0.17$, \textbf{inset}).
-		The red line is the line of the best fit, and 99\% confidence intervals are shown.
+		A convex-shape emerges, wherein larger universities tend to be more distant from the origin (large L2 norm); however, the more prestigious the university, the closer it is to the origin (small L2 norm).
+		The L2 norm is correlated weakly with the ratio of organizations' number of connections (non-zero flows) to the number of researchers ($R^{2} = 0.17$, \textbf{inset}).
+		The red line is the line of the best fit, and 99\% confidence intervals are shown, though are too small to be visible.
 		\textbf{b.} This convex pattern repeats globally for all organizations across all countries, shown for the United States, China, and others,
@@
 
-Neural embeddings offer a novel, data-driven solution for learning an effective and robust functional distance between places based on trajectory data.
-By virtue of being data-driven, and by the nature of neural embedding, it encodes the complex and multi-faceted nature of mobility.
-Here, we demonstrated how the embedding space encodes various aspects of scientific mobility, such as the global and regional geography, national shared languages, and the hierarchy of organizational prestige, even without explicit information on these factors.
+Neural embeddings offer a novel, data-driven solution for learning an effective and robust functional distance between places based on trajectory data, encoding the complex and multi-faceted nature of mobility.
+We demonstrated how the embedding space encodes various aspects of scientific mobility, such as the global and regional geography, shared languages, and the hierarchy of organizational prestige, even without explicit information on these factors.
 While scientific mobility is used as a case study, this approach may be broadly applicable to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
 Moreover, this approach can be used to learn a functional distance between entities for which no physical analog exists, such as between occupational categories based on individual's career trajectories.
-In addition to providing a functional distance that supports modeling and predicting mobility patterns, the unique structure of the neural embedding space is amenable to a range of unique applications for studying mobility.
+In addition to providing a functional distance that supports modeling and predicting mobility patterns, the structure of the neural embedding space is amenable to a range of unique applications for studying mobility.
 As we have shown, the embedding space allows the visualization of the complex structure of scientific mobility at high resolution across multiple scales, providing the largest and most detailed map of global scientific mobility to date.
@@
 
-In spite of its promise, this approach and analysis present several limitations.
-First, the current \textit{skip-gram word2vec} model can not encode directional information, meaning that embedding will be less effective at capturing mobility for which directional is critical.
-Second, the neural embedding approach is most useful in cases of mobility between discrete geographic units such as between countries, cities, and businesses; this approach is less useful in the case of mobility between arbitrary locations represented in geographic coordinates, such as in the modeling of animal movements.
+In spite of its promise, this approach and analysis has several limitations.
+First, the current \textit{skip-gram word2vec} model can not encode directional information, meaning that embedding will be less effective at capturing mobility for which directionality is critical.
+Second, the neural embedding approach is most useful in cases of mobility between discrete geographic units such as between countries, cities, and businesses; this approach is less useful in the case of mobility between locations represented using geographic coordinates, such as in the modeling of animal movements.
 Neither of these methodological limitations is insurmountable, and future work can aim to incorporate directionality and identify meaningful representations of continuous mobility data.
@@
 Reliance on bibliometric metadata means that we capture only long-term mobility such as migration, rather than the array or more frequent short-term mobility such as conference travel and temporary visits.
-The kinds of mobility we do capture—asynchronous migration and synchronous co-affiliation, are treated identically by our model even though they are qualitatively different.
-Also, our data can possess survivorship bias: researchers at prestigious organizations tend to have more publications, inducing these organizations appear more in the mobility sentence.
-
-Mobility and migration is a core asepct of human nature and history~\autocite{shah2020migration}, driving social phenomena as diverse as epidemics\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity} and science and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage, morgan2018prestige, rodrigues2016mobility}.
+The kinds of mobility we do capture—migration and co-affiliation, are treated identically by our model even though they are qualitatively different.
+Also, our data might further suffer from survivorship bias: researchers at prestigious organizations tend to have more publications, leading to these organizations appearing more frequently in affiliation trajectories.
+
+Mobility and migration are at the core of human nature and history~\autocite{shah2020migration}, driving societal phenomena as diverse as epidemics\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity} and science and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage, morgan2018prestige, rodrigues2016mobility}.
 However, the paradigm of scientific migration may be changing.
-Traditional hubs of migration have enacted many politially-motivated policy changes that affect scientific mobility, such as travel restrictions in the U.S.
-and U.K.
-brought by Trump administration and enacted as part of Brexit~\autocite{chinchilla2018travelban}.
-Other nations, such as China, are growing into major scientific powers and attractors of talent~\autocite{tollefson2018china, cao2020returning}.
-Global crises such as COVID19 pandemic threaten drastic change to travel and migration by tightening borders and halting travel.
-The paradigm of global mobility is changing, and now, more than ever, new tools and approaches are needed to understanding human mobility in order to inform sensible, effective, and humane Immigration and Science and Technology policy.
+Traditional hubs of migration have experienced many politially-motivated policy changes that affect scientific mobility, such as travel restrictions in the U.S.
+and U.K.~\autocite{chinchilla2018travelban}.
+At the same time, other nations, such as China, are growing into major scientific powers and attractors of talent~\autocite{tollefson2018china, cao2020returning}.
+Unprecedented health crises such as COVID-19 pandemic threaten to bring drastic global changes to travel and migration by tightening borders and halting travel.
+With the changing paradigm of global mobility we need now, more than ever, new tools and approaches to capture and understand human mobility in order to inform sensible, effective, sustainable, and humane policies.
 
@@
 Trajectories are constructed from author affiliations listed on the byline of publications for a given author.
-Given the limitations of author-name disambiguation, we limit to papers published after 2008, when the Web of Science began providing full names and institutional affiliations~\autocite{caron2014disambiguation} that improved disambiguation (see \SI).
+Given the limitations of author-name disambiguation, we limit our analyses to papers published after 2008, when the Web of Science began providing full names and institutional affiliations~\autocite{caron2014disambiguation} that improved disambiguation (see \SI).
 This yields 33,934,672 author-affiliation combinations representing 12,963,792 authors.
@@
 Under this definition, mobile authors constitute 3,007,192 or 23.2 \% of all authors and 17,700,095 author-affiliation combinations.
-Mobile authors were associated with, on average, 2.5 distinct organizational affiliations.
+Mobile authors were associated with 2.5 distinct organizational affiliations on average.
 Rates of mobility differ across countries.
@@
 The countries with the highest proportion of mobile scientists are France, Qatar, the United States, and Iraq, whereas those with the lowest are Jamaica, Serbia, Bosnia \& Herzegovina, and North Macedonia (Fig.~\ref{fig:supp:descriptives}c).
-In most cases, countries with a high degree of inter-organization mobility also have a high degree of international mobility, indicating a high proportion of their total mobility being international (Fig.~\ref{fig:supp:descriptives}d);
+In most cases, countries with a high degree of inter-organization mobility also have a high degree of international mobility, indicating that a high proportion of their total mobility is international (Fig.~\ref{fig:supp:descriptives}d);
 However, some countries such as France and the United States seem to have more domestic mobility than international mobility.
@@
 The trajectories of mobile authors were converted to ``affiliation trajectories'' by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:methods:mobility_sentence}a.
-In more complex cases, such as listing multiple affiliations on the same paper or publishing with different affiliations on multiple affiliations in the same year, the order is randomized within that year, as shown in  Fig.~\ref{fig:methods:mobility_sentence}b.
+In more complex cases, such as listing multiple affiliations on the same paper or publishing with different affiliations on multiple publications in the same year, the order is randomized within that year, as shown in  Fig.~\ref{fig:methods:mobility_sentence}b.
 
@@
 These affiliation trajectories are used as input to the standard skip-gram negative sampling word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec}.
-\textit{word2vec} constructs dense and continuous vector representations of words and phrases, in which distance between words correspond to a notion of semantic distance.
+\textit{word2vec} constructs dense and continuous vector representations of words and phrases, in which distance between words corresponds to a notion of semantic distance.
 By embedding affiliation trajectories, we aim to learn a dense vector for every organization where the distance between vectors relates to the tendency for two organizations to occur in similar contexts.
-Formally,  the model attempt to maximize average log probability of a target organization appearing in an affiliation trajectory $a_{t}$, given organizations in the surrounding context window, $a_{t+k}$.
+Formally,  the model attempts to maximize average log probability of a target organization appearing in an affiliation trajectory $a_{t}$, given organizations in the surrounding context window, $a_{t+k}$.
 This can be written as follow, where $w$ is the size of the window and $T$ iterates through possible target organizations:
@@
 For example, $T_{ij} = 10$ indicates that ten authors were affiliated with both organization $i$ and $j$ between 2008 and 2019, as evidenced from their publications.
-We treat all co-affiliations are symmetric, meaning that $T_{ij} = T_{ji}$.
+We treat all co-affiliations as symmetric, meaning that $T_{ij} = T_{ji}$.
 
@@
 We model the flux of authors between organizations, $T_{ij}$, using the gravity law.
-the gravity law of mobility loosely derives from the physical law of gravity, whereby the attraction between two objects is a function of their mass and the distance between them.
+The gravity law of mobility loosely derives from the physical law of gravity, whereby the attraction between two objects is a function of their mass and the distance between them.
 Given its simplicity and flexibility, this formulation and variants have proven incredibly useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
@@
 Here, non-zero flows account for only 4.2 \% of all possible pairs of the 6,580 organizations represented in the embedding.
-This value is comparable to other common applications of the gravity law, such as to hone calls, commuting, and migration \autocite{simini2012universal}.
+This value is comparable to other common applications of the gravity law, such as to phone calls, commuting, and migration \autocite{simini2012universal}.
 We follow standard practice and exclude zero flows from our analysis.
@@
 \subsection*{SemAxis}
-SemAxis~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these terms to the concept.
+SemAxis~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these terms to a corresponding concept.
 Each axis is an antonym pair defined for each specific use case.
@@
 The other end of the prestige axis is the geographically-matched (according to census region) set of universities ranked at the bottom of these rankings.
-For example, if 20 universities top-ranked universities are selected and six of them are in the Northeastern United States, then the bottom six universities according to the same ranking will be included in the low-ranked subset.
+For example, if 20 top-ranked universities are selected and six of them are in the Northeastern United States, then the bottom six universities according to the same ranking will be included in the low-ranked subset.
 From the prestige axis, we derive a ranking of universities that we then compare to other formal university rankings using Spearman rank correlation.

### 2020-07-31 paper/current/main.tex
sadamori's edits up to page 7

@@
 Human mobility and migration drive major societal phenomena such as the growth and evolution of cities~\autocite{wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity}, economies~\autocite{kaluza2010cargo, kerr2011immigration}, and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}.
-Common models of mobility, such as the Gravity Model~\autocite{zipf1946gravity} aim to capture mobility between places using their population and the \textit{distance} between them.
-However, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} wherein physical barriers are shrinking while linguistic, economic, cultural, and historical similarities are becoming more important.
-Alternative notions of functional distance~\autocite{brown1970migration, brown1970functional, kim2018functional} attempt to re-define distance by using some of aforementioned factors~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional} but are often arbitrary and consider only single isolated facets.
-Here, using a rich dataset of scientific mobility, we demonstrate that a data-driven neural embedding~\autocite{mikolov2013word2vec} can successfully encode a functional distance between organizations and capture the latent and multi-faceted structure of scientist's mobility.
-We demonstrate that the cosine distance between organization embedding vectors, constructed using the affiliation trajectories of scientists in the Web of Science database, better explain and predict real mobility than geographic distance.
-We demonstrate that the embedding space encodes not only geographic relations between organizations, but also relations based on culture, language, and academic prestige at multiple levels of granularity.
-The embedding space also captures the relationship between organization's size and their connectedness that repeats across most countries.
+Geographic distance and population have been considered as leading factors of human mobilit~\autocite{zipf1946gravity}.
+However, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important, which calls for alternative \textit{functional distances} that take these factors into account~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional}.
+However, existing functional distance are often arbitrary and consider only single isolated facets of mobility.
+Using the case study of scientific mobility, we demonstrate the a neural embedding model can successfully encode the affiliation trajectories of scientists into a vector-space representation of organizations~\autocite{mikolov2013word2vec} from which a functional distance can be derived.
+We show that the proposed functional distance reflects the multi-faced structure of scientists' mobility that is not explained by geographic distance alone, capturing relations based on culture, language, and academic prestige at multiple levels of granularity.
+The vector representations of organizations themselves also reveal insights into the landscape of global scientific mobility, such as a relationship between organizations' size and their connectedness that is consistent across most countries.
 The ability to learn scalable, dense, and meaningful high-resolution vector representations of mobility directly from the data can open up a new avenue of studying human mobility.
@@
 The question is surprisingly hard to answer when it involves human mobility.
-While geographic distance may have driven human movements in the past, it holds less importance to a world connected by rapid transit, complex international relations, and dense airline networks.
+Geographic distance has underpinned human movements, however it is becoming less relevant in a world connected by rapid transit and global airline networks.
 For instance, a person living in Australia is more likely to migrate to the United Kingdom, a far-away country with similar language and culture, than to a much closer country such as Indonesia~\autocite{pew2018migration}.
 Similarly, a student in South Korea is more likely to attend a university in Canada than one in North Korea~\autocite{unesco2019students}.
-Although geographic distance has been used as the most prominent basis for models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} models, there have been attempts to define alternative notions of distance, or ~ \textit{functional distances}~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional} from real-world data or \textit{a priori} relationships between geographic entities.
-Yet, functional distances are often low-resolution and rely on somewhat arbitrary decisions about the importance of each factor.
-Moreover, functional distances typically only focus on a single facet of mobility at a time, whereas real-world mobility is multi-faceted, influenced simultaneously by geography, language, culture, history, and economic opportunity.
+Although geographic distance has been used as the most prominent basis for models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} models, there have been attempts to define alternative notions of distance, or ~\textit{functional distances}~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional} from real-world data or \textit{a priori} relationships between geographic entities.
+Yet, functional distances are often low-resolution, at the level of countries rather than regions, cities, or organizations, and rely on somewhat arbitrary decisions about which factors are most relevant.
+Moreover, functional distances have focused on only a single facet of mobility at a time, whereas real-world mobility is multi-faceted, influenced simultaneously by geography, language, culture, history, and economic opportunity.
 To capture such complexity of human mobility, new approaches that incorporate its many facets into a single high-resolution functional distance are needed.
 
-Here, we propose a neural embedding model that uses real-world mobility trajectories to encode the complex landscape of global mobility into a dense, continuous, and meaningful vector-space representation, from which a \textit{functional distance} between places can be derived.
-The neural embedding, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been  making breakthroughs by revealing novel insights into texts~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
-They are also computationally efficient, robust to noise, and can encode reasonably rich relations between entities as geomemetric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.
-
-We use scientific mobility, inferred from researcher's affiliations, to demonstrate the effectiveness of our approach.
+Here, we propose using a neural embedding model that draws from real-world mobility trajectories to encode the complex landscape of global mobility into a dense, continuous, and meaningful vector-space representation, from which a \textit{functional distance} between places is derived.
+Using the case of scientific mobility, we demonstrate that the functional distance captures relations based on culture, language, and academic prestige, along with geographic relations, at multiple levels of granularity
+
 Scientific mobility is a central driver of the increasingly-globalized scientific enterprise~\autocite{czaika2018globalisation, altbach2004globalization, box2008competition}, being strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}.
@@
 A vector-space embedding of organizations is learned by using affiliation trajectories as input to the standard skip-gram with negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
-In the resulting embedding, each organization corresponds to a single vector, and vectors relate to one another based on the likelihood of organizations appearing adjacent to one another in the same affiliation trajectory.
+This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
+They are also computationally efficient, robust to noise, and can encode relations between entities as geomemetric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.
+In the organization embedding, each organization is encoded into a single vector, and vectors relate to one another based on the likelihood of organizations appearing adjacent to one another in the same affiliation trajectory.
 The functional distance between two organizations is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.
@@
         \textbf{b.}
-        In a more complex case, an author lists several affiliations on the byline of papers in $t_{2}$, $t_{3}$, and $t_{4}$.
-        In the case where multiple organizations are listed within the same year, then organization IDs within a single year are randomized across each training iteration or ``epoch" of the \textit{word2vec} model (for more detail, see \SI).
+        If an author lists multiple organization affiliations within the same year, then organization IDs within that year are placed in random order in each training iteration of the \textit{word2vec} model (for more detail, see \SI).
     }
@@
 
-To assess the performance of the embedding distance relative to geographic distance, we evaluate their correlation with real-world mobility data and their performance in predicting real-world mobility flows as parameters to the Gravity Model~\autocite{zipf1946gravity, barbosa2018human}.
-The Gravity Model, taking inspiration from Newton's law of gravity, is one of the most broadly applied mobility models~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} .
-After fitting the parameters of the gravity model, we use it to derive the \textit{expected flux} $\hat{T_{ij}}$ between organizations, defined as,
+To assess the performance of the embedding distance relative to geographic distance, we evaluate their correlation with real-world mobility data and their performance in predicting real-world mobility flows as parameters to the gravity model~\autocite{zipf1946gravity, barbosa2018human}.
+The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} that calculates the \textit{expected flux}, $\hat{T}_{ij}$, of scientists between organizations based on their populations and distance:
 
@@
 \end{equation}
-where the \textit{expected flux}, $\hat{T_{ij}}$, or expected number of authors who were affiliated with both organizations during the time period, is proportional to the organizations' sizes (the sum of both mobile and non-mobile authors, see Data and Methods), $m_{i}$ and $m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
-The distance function is defined in terms of either the geographic distance between organizations or the embedding distance.
+where $m_{i}$ is the population of mobile and non-mobile authors who affiliated with institution $i$, $f(r_{ij})$ is a decay function with respect to distance between organizations, and $C$ is a constant estimated from data (see Data and Methods).
+$\hat{T}_{ij}$, which is often referred to as ``expected flux''~\autocite{simini2012universal}, is the expected frequency of the co-occurrence of organizations $i$ and $j$ in the trajectory of affiliations in the gravity model.
+The gravity model dictates that the expected flow, $\hat{T}_{ij}$, is symmetric (\ie $\hat{T}_{ij }= \hat{T}_{ji})$, is proportional to the organizations' sizes, $\hat{T}_{ij} \propto m_{i}, m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+We define the distance function in terms of either the geographic distance between organizations or their embedding distance.
 For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_emb_bymodel} and Fig.~\ref{fig:supp:predict_geo_bymodel}).
@@
 
-The embedding distance explains and predicts scientific mobility better than geographic distance.
-The amount of variance explained by embedding distance ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) is more than twice that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
+The embedding distance correlates with and can be used to predict real-wold mobility flows better than geographic distance. 
+The amount of variance in the expected flux explained by embedding distance ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) is more than twice that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
 This pattern holds when considering the subset of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d).
-After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance (Fig.~\ref{fig:gravity_performance}c--d), which also holds for the subsets of only domestic (Fig.~\ref{fig:supp:gravity_correlation}e--f) and only international mobility (Fig.~\ref{fig:supp:gravity_correlation}g--h).
+We fit the gravity model given by Eq.~\ref{eq:gravity_basic} (see Data and Methods) and computed the expected flux  $\hat{T}_{ij}$ using geographic distance and embedding distance as parameters.
+The embedding distance produces better predictions of actual flux than does geographic distance (Fig.~\ref{fig:gravity_performance}c--d), which also holds for the subsets of only domestic (Fig.~\ref{fig:supp:gravity_correlation}e--f) and only international mobility (Fig.~\ref{fig:supp:gravity_correlation}g--h).
 The embedding distance defined from the cosine distance between vectors also outperforms that defined from their dot product ($R^{2} = 0.34$, Fig.~\ref{fig:supp:gravity_dot}).
@@
 		\textbf{Embedding distance outperforms geographic distance.}
-		\textbf{a.} embedding distance (cosine distance between organization vectors) better explains the expected flux between organization pairs than geographic distance (\textbf{b}).
+		\textbf{a-b.} Embedding distance (cosine distance between organization vectors) better explains the expected flux between organization pairs than geographic distance.
 		The red line is the line of the best fit.
 		Black dots are mean flux across binned distances.
-		Error bars represent 99\% confidence intervals.
+		99\% confidence intervals are plotted, but are too small to be visible.
+		Correlation is calculated on the data in the $log$-$log$ scale. 
 		The lightness of each hex bin indicates the frequency of organization pairs within it.
@@
 		Boxplots show distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps with $y = x$.
+		Box color corresponds to the degree to which the distribution overlaps with $y = x$;
+		a perfect prediction yields all points on the black line.
 		``RMSE'' is the root-mean-squared error between the actual and predicted values.
@@
 		\textbf{g-h.} Embedding distance also outperforms geographic distance when predicting flux using model parameters estimated from only international mobility (across-country organization pairs).
-		Predictions are not meaningfully different if estimates are learned on all pairs of organizations (Fig. \ref{fig:supp:gravity_prediction_subsets}).
-		These predictions are robust whether the model is fit on the global data, or on the domestic (Fig.~\ref{fig:gravity_performance}e-h) or international (Fig.~\ref{fig:supp:gravity_prediction_subsets}) subsets.
+		Predictions of domestic and international mobility are qualitatively similar whether predicted using models with only within- or across-country pairs (\textbf{e-h}), or all organizations pairs (Fig.
+\ref{fig:supp:gravity_prediction_subsets}).
 	}
@@
 
-The embedding also allows us to create informative visualizations of global scientific mobility.
-To explore the topological structure of the embedding, we use a standard dimensionality reduction technique (UMAP~\autocite{mcinnes2018umap}) to obtain its two-dimensional representation (Fig.~\ref{fig:projection}a).
+The geometric space generated by the neural embedding methods sheds light on the multi-faceted relationships between organizations.
+To explore the topological structure of the embedding, we use a standard dimensionality reduction method (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation (Fig.~\ref{fig:projection}a).
 By showing relationships between individual organizations, rather than aggregates such as nations or cities, this projection constitutes the largest and highest resolution ``map'' of scientific mobility to date.
@@
 
-The embedding space also allows us to \textit{zoom in} on subsets and re-project them in order to reveal more local relationships.
-For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries between Egypt and the Philippines that corresponds largely to geography, but with some peculiar exceptions along the cultural and religious spectrums.
-For example, Iraq is nearer to some southeast-Asian countries such as Malaysia, with a cosine distance between the nation's aggregate vectors of $d = 0.29$, than to closer and more religiously-similar nations such as Saudi Arabia ($d = 0.50$) and Qatar ($d = 0.51$).
+The embedding space also allows us to \textit{zoom in} on subsets and re-project them using UMAP to reveal local relationships.
+For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries between Egypt and the Philippines that largely corresponds to geography, but with some exceptions along the cultural and religious spectrums;
+Iraq is nearer to Malaysia in southeast-Asian than closer and more religiously-similar Saudi Arabia and Qatar.
+In fact, we compute the distance, $d$, between nations in the original embedding space as the cosine distance between the centroids of organizations vectors belonging to that country. 
+Then, Malaysia ($d=0.29$) is closer to Iraq more than Arabia ($d=0.50$) and Qatar ($d=0.51$).
 Linguistic and historical ties are also conspicuous.
-For example, we observe that Spanish-speaking post-colonial Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), rather than nearby Portuguese-speaking nations ($d = 0.34$ vs.
+We observe that Spanish-speaking post-colonial Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), rather than nearby Portuguese-speaking nations ($d = 0.34$ vs.
 $d = 0.52$ for Mexico and $d = 0.39$ vs.
 $d = 0.49$ for Chile) reflecting linguistic and cultural ties.
-Similarly, North-African countries that were once under French rule such as Morocco are nearer to France ($d =0.35$) than to similarly-distant European countries such as Spain ($d = 0.40$) and Italy ($d = 0.53$).
+Similarly, North-African countries that were once under French rule such as Morocco are closer to France ($d =0.35$) than to similarly-distant European countries such as Spain ($d = 0.40$) and Italy ($d = 0.53$).
 Comparable structural patterns exist even within a single country.
@@
 
-The geographic structure of the global embedding is mirrored in the re-projection of the United States, wherein organizations are largely organized according to geography (Fig.~\ref{fig:projection}d).
-By re-projecting Massachusetts (Fig.~\ref{fig:projection}e), we observe structure based on: urban centers (Boston vs.
+Mirroring the global pattern, organizations in the United States are largely arranged according to geography (Fig.~\ref{fig:projection}d).
+Re-projecting organizations located in Massachusetts (Fig.~\ref{fig:projection}e) reveals structure based on: urban centers (Boston vs.
 Worcester), organization type (e.g., hospitals vs.
-universities) and university systems (UMass vs.
+universities), and university systems (UMass vs.
 Harvard \& MIT).
-For example, even though UMass Boston is located in Boston, it clusters with  other universities in the UMass System ($d = 0.34$) rather than the other typically more highly-ranked and research-focused universities in Boston ($d = 0.41$), reflecting a relative lack of mobility between the two systems.
+For example, even though UMass Boston is located in Boston, it clusters with  other universities in the UMass System ($d = 0.34$) rather than the other typically more highly-ranked and research-focused universities in Boston ($d = 0.41$), implying a relative lack of mobility between the two systems.
 Similar structures can be observed in other states such as among New York's CUNY and SUNY systems (Fig.~\ref{fig:supp:proj_newyork}), Pennsylvania's state system (Fig.~\ref{fig:supp:proj_pennsylvania}), Texas's Agricultural and Mechanical universities (Fig.~\ref{fig:supp:proj_texas}), and between the University of California and State University of California systems (Fig.~\ref{fig:supp:proj_california}).
@@
 	\caption{
-		\textbf{Projection of embedding demonstrates complex multi-scale structure.}
+		\textbf{Projection of embedding space reveals complex multi-scale structure of organizations.}
 		\textbf{a.}
-		UMAP projection \autocite{mcinnes2018umap} of the embedding space reveals strong country-level clustering.
+		UMAP projection \autocite{mcinnes2018umap} of the embedding space reveals country-level clustering.
 		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019.
@@
 Just as the embedding space makes it possible to ``zoom in'' on subsets of organizations, it is also possible to ``zoom out'' by aggregating organizational vectors.
-For example, we can examine the high-level structure by estimating the aggregate embeddings of countries.
-Namely, we can define the representative vector of each country as the average of their organizational vectors.
-We then perform hierarchical clustering of nations that have at least 25 organizations represented in the embedding space, excluding the United States which is a dominant hub well connected to most other countries (see Fig.
+We can examine the country-level structure that governs scientific mobility.
+To this end, we define the representative vector of each country as the average of their organizational vectors.
+We then perform hierarchical clustering of nations that have at least 25 organizations represented in the embedding space based on their cosine similarity, excluding the United States which is a dominant hub well connected to most other countries (see Fig.
 \ref{fig:clustering}a).
@@
 		\textbf{a.} Hierarchically clustered similarity matrix of country vectors, aggregated as the mean of all organization vectors within the country that has more than 25 organizations, excluding the United States.
-		Color of matrix cells corresponds to the similarity between country vectors.
+		Color of matrix cells corresponds to the cosine similarity between country vectors.
 		Color of country names corresponds to their cluster.

### 2020-07-31 paper/current/main.tex
remainder of Sadamori's comments

@@
 The six identified clusters roughly correspond to countries in East-Asia (orange), Scandinavia (dark purple), the British Commonwealth (light purple), and Central and Eastern Europe (light blue), and then two remaining diverse clusters contain a mix of European, Latin American, and Mediterranean countries.
-These clusters demonstrate the importance of not only geography but also linguistic ties between countries.
+The cluster structure shows that not only geography but also linguistic ties between countries are related to scientific mobility.
 
@@
 		\textbf{Geography, then language, conditions international mobility.}
-		\textbf{a.} Hierarchically clustered similarity matrix of country vectors, aggregated as the mean of all organization vectors within the country that has more than 25 organizations, excluding the United States.
+		\textbf{a.} Hierarchically clustered similarity matrix of country vectors aggregated as the mean of all organization vectors within the country, excluding the United States and countries with less than or equal to 25 organizations.
 		Color of matrix cells corresponds to the cosine similarity between country vectors.
@@
 
-Prestige hierarchy is known to underpin the dynamics of scientific mobility~\autocite{deville2014career, clauset2015hierarchy}, but can the hierarchy be encoded in the embedding space, to which no explicit information on prestige is given and for which the direction of mobility is not known?
-We test this by exploiting the geometric properties of the embedding space with SemAxis~\autocite{an2018semaxis}, an approach originally designed to characterize the semantics of words in word embeddings.
-Here, we use SemAxis to operationalize the abstract notion of academic prestige, defining each pole of the axis using high- and low-ranked universities.
+Prestige hierarchy is known to underpin the dynamics of scientific mobility, where researchers tend to move to similar or less prestigious organizations~\autocite{deville2014career, clauset2015hierarchy}.
+Does the embedding space, to which no prestige information is given, encode a prestige hierarchy?
+We test this by exploiting the geometric properties of the embedding space with SemAxis~\autocite{an2018semaxis}.
+Here, we use SemAxis to operationalize the abstract notion of academic prestige, defining an axis in the embedding space where poles are defined using known high- and low-ranked universities.
 To define prestige of ranked U.S.
@@
 census region) universities.
-
-The embedding space encodes the prestige hierarchy of U.S. universities well enough to re-construct university rankings. 
-We derive a ranking for universities using the SemAxis prestige axis and compare them to traditional university rankings.
-The embedding-based ranking is defined from the position of organizations along the prestige axis, with the top-ranked being the nearest to the high-ranked pole.
+We derive an embedding-based ranking for universities based on their nearness to the high-ranked pole.
+
+The embedding space encodes the prestige hierarchy of U.S. universities that are coherent with real-world university rankings.
 The embedding-based ranking is strongly correlated with the Times ranking (Spearman's $\rho = 0.73$, Fig.~\ref{fig:semaxis}a).
-For reference, the embedding-based ranking achieves correlation with the Times Ranking comparable to that between the Times ranking and the publication impact scores from the Leiden Ranking~\autocite{waltman2012leidenrankings}, a well-known bibliometrically-informed university ranking (Spearman's $\rho = 0.87$, Fig.~\ref{fig:semaxis}b).
+For reference, the embedding-based ranking achieves correlation with the Times ranking comparable to that between the Times ranking and the publication impact scores from the Leiden Ranking~\autocite{waltman2012leidenrankings}, a bibliometrically-based university ranking (Spearman's $\rho = 0.87$, Fig.~\ref{fig:semaxis}b).
 The correlation between the embedding-based ranking and the Times ranking is robust regardless of the number of organizations used to define the axes (Fig.
-SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities produces a ranking that is significantly correlated with the Times Ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
-Performance is also comparable to network-driven measures such as degree strength (Spearman's $\rho = 0.73$) and eigenvector centrality (Spearman's $\rho = 0.76$, see \SI). 
-The strongest outliers that were ranked more highly in the Times Ranking than in the embedding-based ranking tend to be large state universities such as Arizona State University and  University of Florida.
+SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities produces a ranking that is significantly correlated with the Times ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
+The correlation is also comparable to network-driven measures such as degree strength (sum of edge weights, Spearman's $\rho = 0.73$) and eigenvector centrality (Spearman's $\rho = 0.76$, see \SI). 
+The strongest outliers that were ranked more highly in the Times ranking than in the embedding-based ranking tend to be large state universities such as Arizona State University and  University of Florida.
 Those ranked higher in the embedding based ranking tend to be relatively-small universities near major urban areas such as the University of San Francisco and University of Maryland Baltimore County.
-This suggests that the organization embedding captures the latent prestige hierarchy inherent to academic mobility with a high degree of resolution and reliability, even without providing any explicit information on prestige~\autocite{deville2014career, clauset2015hierarchy}.
-
-The axes can further be visualized to examine the relative position of organizations along the prestige axis, and along a geographic axis between California and Massachusetts that aids visualization.
+This suggests that organizations in the embedding space are arranged according to prestige, even when the erepresentation is learned using data without explicit infomration on the direction of mobility (as in other formal models~\autocite{clauset2015hierarchy}), or prestige.
+
+The axes can further be visualized to examine the relative position of organizations along the prestige axis, and along a geographic axis between California and Massachusetts to aid visualization.
 Prestigious universities such as Columbia, Stanford, MIT, Harvard, and Rockefeller are positioned towards the top of the axis (Fig.~\ref{fig:semaxis}c).
@@
 		\textbf{Embedding captures latent geography and prestige hierarchy.}
-		\textbf{a.} Comparison between the ranking of organizations by their rank in the Times ranking and the embedding rank derived using SemAxis with the poles defined using the top five, and geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S.
-Universities .
-		Un-filled points are those top and bottom five universities used to define the poles of the axis.
-	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the embedding and Times ranking is $\rho = 0.73$ (n = 145), and it increases if we include more top-and-bottom ranked universities (Fig.~\ref{fig:supp:semaxis_compare}).
+		\textbf{a.} Comparison between the ranking of organizations by their rank in the Times ranking and the embedding rank derived using SemAxis pointing from the top five to geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S.
+Universities.
+		Un-filled points are those top and bottom five universities used span the axis.
+	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the embedding and Times ranking is $\rho = 0.73$ ($n = 145$), which increases when more top-and-bottom ranked universities are included (Fig.~\ref{fig:supp:semaxis_compare}).
 	  	\textbf{b.} Times ranking is correlated with Leiden Ranking of U.S. universities with Spearman's $\rho = 0.87$
@@
 Up to a point (around 1,000 researchers), the size of U.S.
-organization's vectors tends to increase proportional to the number of researchers (both mobile and non-mobile) within that organization with published work;
+organization's vectors tends to increase proportionally to the number of researchers (both mobile and non-mobile) within that organization with published work;
 these organizations are primarily teaching-focused institutions, agencies, and hospitals that either are not ranked or have a low ranking.
@@
 These organizations are primarily research-intensive and prestigious universities with higher rankings, research outputs, R\&D funding, and doctoral students (Fig.~\ref{fig:supp:length_vs_metaInfo}).
-A similar pattern has been observed in applications of neural embedding to natural language, wherein the size of word vectors was found to represent the word ``significance''~\autocite{schakel2015measuring}.
-If a word appears frequently in a specific context, the norm of the word vector is likely to be large, because a large norm is associated with how predictably the word occurs given a context.
-However, if the word in question is universal, appearing frequently in many different contexts, it cannot have a large norm as it lacks a strong association with a particular context.
+A similar pattern has been observed in applications of neural embedding to natural language, in which the size of word vectors was found to represent the word's specificity.
+Roughly speaking, for word embeddings, the size of a vector indicates a specificity, i.e., the word associated with the vector frequently co-appears with particular context words\autocite{schakel2015measuring}.
+If the word in question is universal, appearing frequently in many different contexts, it would not have a large norm due to a lack of strong association with a particular context.
 Likewise, an organization such as Harvard with a small norm appears in many contexts, alongside many different organizations in affiliation trajectories---it is well-connected.
@@
 Large, prestigious, and well-funded research universities such as Princeton and Harvard have smaller vector sizes because they appear in many different contexts compared to more teaching-focused organizations such as NY Medical College, and University of Michigan at Flint.
-Some universities, such as the University of Alaska at Fairbanks, have surprisingly small vectors, perhaps as a result of its remote location and unique circumstances.
-
-This same convex-curve repeats across many countries such as China, which closely mirrors that of the United States (Fig.~\ref{fig:length}b).
+Some universities, such as the University of Alaska at Fairbanks, have considerably small vectors, which may be a result of its remote location and unique circumstances.
+
+This find a similar convex-curve across many countries such as China, which closely mirrors that of the United States (Fig.~\ref{fig:length}b).
 Smaller but scientifically advanced countries such as Australia, and other large populous countries such as Brazil exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset), though their exact position and size varies.
-Other nations exhibit different curves, such as Egypt which has an``S''-shaped curve---meaning that their largest organizations are not as well connected as other countries' largest organizations. 
-Similar patterns can be found across many of the 30 of the countries with the most total researchers (Fig.~\ref{fig:concave30}), though we can only speculate on what their variations mean (see \SI).
+Other nations exhibit different curves, such as Egypt which has an``S''-shaped curve, meaning that their largest organizations are not as well connected as other countries' largest organizations. 
+Similar patterns can be found across many of the 30 of the countries with the most total researchers (Fig.~\ref{fig:concave30}), however we can only speculate on what their variations mean (see \SI).
 Neural embeddings encode a relationship between organization size and vector length that is universal across countries but with potentially meaningful nuances, helping the embedding to capture the landscape of global scientific mobility.
@@
 		Uncolored points are universities not listed on a Times ranking.
-		A convex-shape emerges, wherein larger universities tend to be more distant from the origin (large L2 norm); however, the more prestigious the university, the closer it is to the origin (small L2 norm).
+		A convex-shape emerges, wherein larger universities tend to be more distant from the origin (large L2 norm); however, the more prestigious universities tend to have a small L2 norm.
 		The L2 norm is correlated weakly with the ratio of organizations' number of connections (non-zero flows) to the number of researchers ($R^{2} = 0.17$, \textbf{inset}).
 		The red line is the line of the best fit, and 99\% confidence intervals are shown, though are too small to be visible.
-		\textbf{b.} This convex pattern repeats globally for all organizations across all countries, shown for the United States, China, and others,
+		\textbf{b.} We find a simliar convex-curve pattern across many countries such as the United States, China, Australia, Brazil, and others (\textit{inset}, and Fig.~\ref{fig:concave30}). 
+		Some countries exhibit variants of this pattern, such as Egypt 's ``S''-shaped curve (\textbf{inset}).
 		The loess regression lines are shown for each selected country, and for the aggregate of remaining countries, with 99\% confidence intervals.
@@
 We demonstrated how the embedding space encodes various aspects of scientific mobility, such as the global and regional geography, shared languages, and the hierarchy of organizational prestige, even without explicit information on these factors.
+
 While scientific mobility is used as a case study, this approach may be broadly applicable to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
-Moreover, this approach can be used to learn a functional distance between entities for which no physical analog exists, such as between occupational categories based on individual's career trajectories.
+Moreover, this approach can be used to learn a functional distance between entities for which no physical analog exists, such as between occupational categories based on individuals' career trajectories.
 In addition to providing a functional distance that supports modeling and predicting mobility patterns, the structure of the neural embedding space is amenable to a range of unique applications for studying mobility.
-As we have shown, the embedding space allows the visualization of the complex structure of scientific mobility at high resolution across multiple scales, providing the largest and most detailed map of global scientific mobility to date.
-Other techniques, such as SemAxis~\autocite{an2018semaxis}, also allow us to quantify abstract notions in mobility such as academic prestige, and can also be generalized to other abstract axes.
+As we have shown, the embedding space allows the visualization of the complex structure of scientific mobility at high resolution across multiple scales, providing a large and detailed map of the landscape of global scientific mobility.
+SemAxis~\autocite{an2018semaxis} allows us to quantify abstract notions in mobility such as academic prestige, and can also be generalized to other abstract axes.
 Investigation of the structure of the embedding space, such as the vector size, reveals unique and universal patterns based on organization's size and connectedness and could contribute to deeper understandings of scientific mobility.
@@
 Reliance on bibliometric metadata means that we capture only long-term mobility such as migration, rather than the array or more frequent short-term mobility such as conference travel and temporary visits.
-The kinds of mobility we do capture—migration and co-affiliation, are treated identically by our model even though they are qualitatively different.
+The kinds of mobility we do capture---migration and co-affiliation---are treated identically by our model although they are qualitatively different.
 Also, our data might further suffer from survivorship bias: researchers at prestigious organizations tend to have more publications, leading to these organizations appearing more frequently in affiliation trajectories.
@@
 However, the paradigm of scientific migration may be changing.
-Traditional hubs of migration have experienced many politially-motivated policy changes that affect scientific mobility, such as travel restrictions in the U.S.
+Traditional hubs of migration have experienced many politically-motivated policy changes that affect scientific mobility, such as travel restrictions in the U.S.
 and U.K.~\autocite{chinchilla2018travelban}.
 At the same time, other nations, such as China, are growing into major scientific powers and attractors of talent~\autocite{tollefson2018china, cao2020returning}.
-Unprecedented health crises such as COVID-19 pandemic threaten to bring drastic global changes to travel and migration by tightening borders and halting travel.
+Unprecedented health crises such as the COVID-19 pandemic threaten to bring drastic global changes to travel and migration by tightening borders and halting travel.
 With the changing paradigm of global mobility we need now, more than ever, new tools and approaches to capture and understand human mobility in order to inform sensible, effective, sustainable, and humane policies.
@@
 The embedding-ranking of U.S.
-universities is less correlated with degree strength (Spearman's $\rho = 0.45$, Fig.~\ref{fig:supp:centrality_semaxis_compare}a) and eigenvector  centrality (Spearman's $\rho = 0.55$) than with the Times Ranking itself (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_semaxis_compare}b).
+universities is less correlated with degree strength (Spearman's $\rho = 0.45$, Fig.~\ref{fig:supp:centrality_semaxis_compare}a) and eigenvector  centrality (Spearman's $\rho = 0.55$) than with the Times ranking itself (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_semaxis_compare}b).
 The embedding ranking over-ranks large research-intensive universities such as North Carolina State University, University of Florida, and Texas A\&M University, whereas the network-derived ranking over-ranks smaller, more specialized universities such as Brandeis University, Yeshiva University, and University of San Francisco.

### 2020-08-03 paper/current/main.tex
implenet sada comments—data and methods

@@
 By embedding affiliation trajectories, we aim to learn a dense vector for every organization where the distance between vectors relates to the tendency for two organizations to occur in similar contexts.
-Formally,  the model attempts to maximize average log probability of a target organization appearing in an affiliation trajectory $a_{t}$, given organizations in the surrounding context window, $a_{t+k}$.
-This can be written as follow, where $w$ is the size of the window and $T$ iterates through possible target organizations:
+Suppose an affiliation trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), where $a_{t}$ is the $t$th organization in the trajectory.
+An organization, $a_{t}$, is considered to have context organizations, $a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}$, that appear in the window surrounding $a_t$ up to a time lag of $w$, where $w$ is the window size parameter truncated at $t - w \geq 0$ and $t + w \leq T$.
+Then, the model learns probability $p(a_{t + \tau} \vert a_{t})$, where $-w\leq \tau\leq w$ and $\tau \neq 0$,  by maximizing its log likelihood given by
 
@@
 %
-$$
-\frac{1}{T}\sum_{t = 1}^{T} \sum_{-w \leq j \leq w, j \neq 0} \log p(a_{t + j} \vert a_{t}),
-$$
-where the conditional probability of observing one organization $a_{i}$, given another $a_{j}$, is defined as,
+\begin{equation}
+\frac{1}{T}\sum_{t = 1}^{T} \sum_{-w \leq \tau \leq w, \tau \neq 0} \log p(a_{t + \tau} \vert a_{t}),
+\end{equation}
+where,
 
@@
 %
-$$
-p(a_{i} \vert a_{j}) = \frac{\exp(\bm{u}_{a_{i}} \cdot \bm{v}_{a_{j}})}{\sum_{n=1}^N \exp(\bm{u}_{a_{n}} \cdot \bm{v}_{a_{j}})},
-$$
-where $N$ is the total number of organizations and $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively~\autocite{mikolov2013word2vec}.
-We follow past studies and use the in-vector, $\bm{v}$, as the final representation~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch}.
+\begin{equation}
+p(a_{i} \vert a_{j}) = \frac{\exp(\bm{u}_{i} \cdot \bm{v}_{a_{j}})}{\sum_{n=1}^N \exp(\bm{u}_{n} \cdot \bm{v}_{a_{j}})},
+\end{equation}
+where $a_{t+\tau} = j \vert a_{t+\tau} = i$, and $N$ is the number of unique organizations represented in the data, and $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively.
+The in-vector and out-vectors are different kinds of vector representations for organizations.
+We only use the in-vector, $v$, because the in-vector is more widely used and often superiors to the out-vector in link prediction benchmarks~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch}.
 
 %% Word2vec parameters and training procedure
-We used the \texttt{gensim} python implementation of the \textit{word2vec} model. 
+We used the \textit{word2vec}  implenetation in the python package \texttt{gensim}. 
 The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{\min}$, initial learning rate $\alpha$, and the number of iterations.
 For main results, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between organizations, though results were robust across different settings (Fig.~\ref{fig:supp:hyperparams}).
-To mitigate the effect of less common organizations, we set the $f_{\min}$ as 50, limiting to organizations appearing at least 50 times across the training trajectories;
+To mitigate the effect of less common organizations, we set $f_{\min} = 50$, limiting to organizations appearing at least 50 times across the training trajectories;
 6,580 unique organizations appear in the resulting embedding.

### 2020-08-03 paper/current/main.tex
address sada comments up through SI text

@@
 To define prestige of ranked U.S.
-ranked univeristies, we use the Times Ranking of World Universities (we also use research impact from the Leiden Rankings~\autocite{waltman2012leidenrankings}, see \SI);
+ranked universities, we use the Times Ranking of World Universities (we also use research impact from the Leiden Rankings~\autocite{waltman2012leidenrankings}, see \SI);
 the high-rank pole is defined as the mean vector of the top five U.S.
@@
 The concavity emerges in part from the relationship between the size of the vector and the expected connectedness of the organization given its size (Fig.~\ref{fig:length}a, inset, $R^{2} = 0.17$).
-Large, prestigious, and well-funded research universities such as Princeton and Harvard have smaller vector sizes because they appear in many different contexts compared to more teaching-focused organizations such as NY Medical College, and University of Michigan at Flint.
+Large, prestigious, and well-funded research universities such as Princeton and Harvard have smaller vector norms because they appear in many different contexts compared to more teaching-focused organizations such as NY Medical College, and University of Michigan at Flint.
 Some universities, such as the University of Alaska at Fairbanks, have considerably small vectors, which may be a result of its remote location and unique circumstances.
@@
 SemAxis~\autocite{an2018semaxis} allows us to quantify abstract notions in mobility such as academic prestige, and can also be generalized to other abstract axes.
-Investigation of the structure of the embedding space, such as the vector size, reveals unique and universal patterns based on organization's size and connectedness and could contribute to deeper understandings of scientific mobility.
+Investigation of the structure of the embedding space, such as the vector norm, reveals unique and universal patterns based on organization's size and connectedness and could contribute to deeper understandings of scientific mobility.
 Neural embedding opens the door for new approaches to represent and study scientific mobility, and also mobility more generally.
@@
 %% Distance calculations
-$T_{ij}$ is the number of co-occurrences of organizations within author affiliation trajectories.
+We calculate $T_{ij}$ as the number of trajectories in which two organizations $i$ and $j$ appear together.
 For example, $T_{ij} = 10$ indicates that ten authors were affiliated with both organization $i$ and $j$ between 2008 and 2019, as evidenced from their publications.
-We treat all co-affiliations as symmetric, meaning that $T_{ij} = T_{ji}$.
-
-We also calculate two forms of the distance between organizations.
+Organizations appearing multiple times in an affiliation trajectory are only counted once. 
+In affiliation trajectories where an organization appears multiple times, 
+We note that $T_{ij} = T_{ji}$.
+
+We calculate two forms of the distance between organizations.
 The geographic distance, $g_{ij}$, is the pairwise geographic distance between organizations.
@@
 When less than one kilometer, a distance of 1 km is imputed.
-The embedding distance with the cosine similarity, $d_{ij}$, is calculated as the pairwise cosine distance between vectors from the learned organization embedding, where $v_{i}$ and $v_{j}$ represent the vectors and $d_{ij} = 1 - \frac{\bm{v}_{i} \cdot \bm{v}_{j}}{\lVert \bm{v}_{i} \rVert \lVert \bm{v}_{j} \rVert}$.
-Note that cosine distance derived from the embedding space is not a formal metric, as it does not satisfy the triangle inequality, however cosine distance have still proved practically useful across many tasks~\autocite{lerman2007embedding, brown1970migration, brown1970functional, kim2018functional}.
+The embedding distance with the cosine distance, $d_{ij}$, is calculated as $d_{ij} = 1 - \frac{\bm{v}_{i} \cdot \bm{v}_{j}}{\lVert \bm{v}_{i} \rVert \lVert \bm{v}_{j} \rVert}$,
+where $v_i$ and $v_j$ are the embedding vectors for organizations $i$ and $j$, respectively.
+Note that $d_{ij}$ is not a formal metric because it does not satisfy the triangle inequality.
+Nevertheless, cosine distance is often shown to be useful in practice~\autocite{lerman2007embedding, brown1970migration, brown1970functional, kim2018functional}.
 
@@
 
-We model the flux of authors between organizations, $T_{ij}$, using the gravity law.
-The gravity law of mobility loosely derives from the physical law of gravity, whereby the attraction between two objects is a function of their mass and the distance between them.
-Given its simplicity and flexibility, this formulation and variants have proven incredibly useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
-Following the gravity law, the \textit{expected flux} $\hat{T_{ij}}$ between two organizations is defined as follows,
+We model co-occurences $T_{ij$} for organizations $i$, and $j$, often referred to as flux, using the gravity law of mobility~\autocite{zipf1946gravity}.
+The gravity law of mobility loosely derives from the physical law of gravity, in which the attraction between two objects is a function of their mass and the distance between them.
+This formulation and variants have proven useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
+In the gravity law of mobility, the \textit{expected flux}, $\hat{T_{ij}}$ between two organizations $i$ and $j$ is defined as,
 
@@
 \end{equation}
-where $m_{i}$ and $m_{j}$ are the organization masses, or the yearly-average count of unique authors, both mobile and non-mobile, affiliated with each organization during the time window, and $f(r_{ij})$ is a distance-decaying function  between the two organizations.
-There are two popular forms of the $f(r_{ij})$.
-The first one is power-law function with $f(r_{ij})= r^{-\alpha}_{ij} \ (\alpha > 0)$, and the another one is exponential function with $f(r_{ij}) = e^{-\beta r_{ij}} \ (\beta > 0)$ \autocite{chen2015distance}.
-$f(r_{ij})$ and $C$ can be fit with the data.
+where $m_{i}$ and $m_{j}$ are the organization masses, or the yearly-average count of unique authors, both mobile and non-mobile, affiliated with each organization during the time window, and $f(r_{ij})$ is a decay function of distance $r_{ij}$ between organizations $i$ and $j$.
+There are two popular forms of the $f(r_{ij})$:
+one is a power law function in the form $f(r_{ij})= r^{-\alpha}_{ij} \ (\alpha > 0$, which we call the power decay model;
+the other and the another one is an exponential function in the form $f(r_{ij}) = e^{-\beta r_{ij}} \ (\beta > 0)$ \autocite{chen2015distance}, which we call the exponential model.  
+The parameters for $f(r_{ij})$ and $C$ are fit to given mobility data using a log-linear regression~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity, simini2012universal}.
 
 We consider separate variants of $f(r_{ij})$ for geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$, report the best-fit model of each distance.
-For geographic distance, we use the power-law function of the gravity law, with $f(g_{ij})= g^{-\alpha}_{ij}$, where $\alpha$ is estimated from the data.
-For embedding distance, we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data.
-Following past studies~\autocite{simini2012universal}, parameters $C$, $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_basic}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression \autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity, simini2012universal}
+For geographic distance, we use the power-law function of the gravity law, $f(g_{ij})= g^{-\alpha}_{ij}$ (Eq.~\ref{eq:linear_flux_geo}).
+For embedding distance, we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$ (Eq.~\ref{eq:linear_flux_emb}).
 
@@
 \end{equation}
-where $T_{ij}$ is the real flux from the dataset. The gravity law of mobility is known to be sensitive to the case where $T_{ij} = 0$, or zero movement between organizations.
-Here, non-zero flows account for only 4.2 \% of all possible pairs of the 6,580 organizations represented in the embedding.
+where $T_{ij}$ is the real flux from the data. 
+The gravity law of mobility is sensitive to $T_{ij} = 0$, or zero movement between organizations.
+In our dataset, non-zero flows account for only 4.2 \% of all possible pairs of the 6,580 organizations represented in the embedding.
 This value is comparable to other common applications of the gravity law, such as to phone calls, commuting, and migration \autocite{simini2012universal}.
@@
 \subsection*{SemAxis}
-SemAxis~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these terms to a corresponding concept.
+SemAxis~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these terms to a corresponding concept.
 Each axis is an antonym pair defined for each specific use case.
@@
 Let $S^+ = \{\bm{v}_1^+, \bm{v}_2^+ \cdots \bm{v}_n^+\}$ and $S^- =\{\bm{v}_1^-, \bm{v}_2^- \cdots \bm{v}_n^-\}$ be the set of positive and negative pole organization vectors respectively. 
-Then, the average vectors of each set can be calculated as $\bm{V}^{+} = \frac{1}{n}\sum^n_1 \bm{v}_i^+$ and $\bm{V}^{-} = \frac{1}{n}\sum^n_1 \bm{v}_i^-$.
+Then, the average vectors of each set can be calculated as $\bm{V}^{+} = \frac{1}{n}\sum^n_{i=1} \bm{v}_i^+$ and $\bm{V}^{-} = \frac{1}{n}\sum^n_{i=1} \bm{v}_i^-$. 
 From these average vectors of each set of poles, the semantic axis is defined as $\bm{V}_{\text{axis}} = \bm{V}^{+} - \bm{V}^{-}$.
@@
 
-$$
-score(a)_{\bm{V}_{\text{axis}}} = \cos(\bm{v}_{a}, \bm{V}_{\text{axis}}) = \frac{\bm{u}_{a} \cdot \bm{V}_{\text{axis}}}{\lVert \bm{v}_{a} \rVert \lVert \bm{V}_{\text{axis}} \rVert},
-$$
-where higher scores mean that organization $a$ is more closely aligned to $S^+$ than $S^-$.
-
-We apply SemAxis to U.S. universities by defining two axes that capture geography and academic prestige, respectively.
+\begin{equation}
+\frac{\bm{u}_{a} \cdot \bm{V}_{\text{axis}}}{\lVert \bm{v}_{a} \rVert \lVert \bm{V}_{\text{axis}} \rVert},
+\end{equation}
+where a higher score for organization $a$ indicates that $a$ is more closely aligned to $V^+$ than $V^-$.
+
+We define two axes to capture geography and academic prestige, respectively.
 The poles of the geographic axis are defined as the mean vector of all vectors corresponding to organizations in California, and then the mean of all vectors of organizations in Massachusetts.
@@
 The other end of the prestige axis is the geographically-matched (according to census region) set of universities ranked at the bottom of these rankings.
-For example, if 20 top-ranked universities are selected and six of them are in the Northeastern United States, then the bottom six universities according to the same ranking will be included in the low-ranked subset.
+For example, if 20 top-ranked universities are selected and six of them are in the Northeastern U.S., then the bottom twenty will be chosen to also include six from the Northeastern U.S..
 From the prestige axis, we derive a ranking of universities that we then compare to other formal university rankings using Spearman rank correlation.
@@
 For example, prestige-driven mobility between doctoral-granting and employing institution is highly unequal~\autocite{clauset2015hierarchy, deville2014career}, which impacts the diffusion of ideas across academia~\autocite{morgan2018prestige}.
-By placing researchers in new social settings, mobility can lead to the formation of new collaborative relationships~\autocite{rodrigues2016mobility}, which in turn spur the further diffusion of knowledge and new innovations~\autocite{braunerhjelm2020labor, azoulay2011diffusion, kaiser2018innovation, armano2017innovation}.
+By placing researchers in new social settings, mobility can lead to the formation of new collaborative relationships~\autocite{rodrigues2016mobility}, which in turn spurs the further diffusion of knowledge and innovations~\autocite{braunerhjelm2020labor, azoulay2011diffusion, kaiser2018innovation, armano2017innovation}.
 Perhaps resulting from the selection effects of who gets to move, or the reconfiguring of social and epistemic networks, movement is associated with increased scientific impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}.
@@
 Analyses at lower levels of analysis are far less common.
-\textit{Regional}-level scientific mobility--the flow of researchers between regions or cities within or across countries, has been only minimally studied~\autocite{vaccario2019mobility}, possibly due to lack of reliable long-term data and lack of policy relevance to national-level lawmakers.
+\textit{Regional}-level scientific mobility--the flow of researchers between regions or cities within or across countries has been only minimally studied~\autocite{vaccario2019mobility}, possibly due to lack of reliable long-term data and lack of policy relevance to national-level lawmakers.
 \textit{Organization}-level mobility has the potential to inform institutional policy and to understand the composition of mobility within a single country or region, especially as it relates to organization performance, prestige, and inequality~\autocite{albarran2017topeconomic, deville2014career, morgan2018prestige, clauset2015hierarchy}.
@@
 Another consideration when analyzing scientific mobility is what kinds of mobility to study.
-Typical understandings of mobility are directional, meaning that movement is always \textit{from} one place and \textit{to} another.
-Scientific mobility, however, is more complicated.
+Typical understandings of mobility are directional: movement is always \textit{from} one place and \textit{to} another.
+However, scientific mobility is more complicated.
 For example, scientists often hold multiple affiliations at a time~\autocite{markova2016synchronous}, listing them as co-affiliations on a single paper, or even choosing a subset of affiliations to use for multiple simultaneous projects~\autocite{robinson2019mobility}.
@@
 
-We adopt a data-driven approach to constructing affiliation trajectories, making an as little adjustment to the raw bibliometric data as possible.
-For each mobile researcher (having at least two distinct affiliations), we construct an affiliation trajectory based on the affiliations listed on their published papers indexed in the Web of Science database between 2008 and 2019.
+For each mobile researcher who has at least two distinct affiliations, we construct an affiliation trajectory based on the affiliations listed on their published papers indexed in the Web of Science database between 2008 and 2019.
 An author is considered mobile if they published with at least two distinct affiliations during the time period of study.
-Affiliations map to disambiguated organizations, each of which matches to a unique identifier.
-Affiliations in a trajectory are first ordered by year of publication.
-For example, if an author published with affiliation $A$ in $t_{0}$, affiliation $B$ in $t_{1}$, and $A$ again in $t_{2}$, then their ordered affiliation trajectory would be $\{A, B, C\}$.
-
-In the case that multiple affiliations are used within a single year, affiliations listed on publications published in that year are shuffled between each stage of the \textit{word2vec} training process (each epoch).
-For example, an author who published with affiliation $A$ in $t_{0}$, and affiliations $B, C$ in $t_{1}$ could appear as one of $\{A, B, C\}$ or $\{A, C, B\}$ in each training iteration.
-This effectively removes the effect of order within a year, as the order cannot be meaningfully established based on co-affiliations in a single paper, or on different affiliations listed on separate papers, the publication of which is not necessarily representative of the actual completion of the project.
+Affiliation names were manually disambiguated, and each was mapped to a unique organization identifier.
+An affiliation trajectory for an individual researcher is a sequence of organizations in ascending order of year of publication.
+if a researcher published papers with affiliation $A$ in year $t$, $B$ in $t+1$, $C$ in $t+2$ and $A$ again in $t+3$, then the affiliation trajectory is expressed as $(A, B, C, A)$.
+
+In the case that an individual lists multiple affiliations in a single year, affiliations listed on publications published in that year are shuffled between each iteration of the \textit{word2vec} training process (each epoch).
+For example, an author who published with affiliation $A$ in $t_{0}$, and affiliations $B$ and $C$ in $t_{1}$ could appear as one of $(A, B, C)$ or $(A, C, B)$ in each training iteration.
+This effectively removes the effect of order within a year, as the order cannot be meaningfully established based on co-affiliations in a single paper, or on different affiliations listed on separate papers, for which its date of publication may not be representative of the actual completion of the project.
 
 Other than restricting to only mobile researchers, we do not perform any filtering or reductions to affiliation trajectories.
-For example, in the case than an author publishes with organization $A$ four times in $t_{0}$, and affiliation $B$ two times in $t_{1}$, then their trajectory will be $\{A, A, A, A, B, B\}$.
-This means that mobile authors who publish more papers will have longer trajectories.
-However, \textit{word2vec} will skip duplicate consecutive organization IDs, effectively eliminating the impact of these long repetitive trajectories.
+In the case than an author publishes with organization $A$ four times in $t_{0}$, and affiliation $B$ two times in $t_{1}$, then their trajectory will be $(A, A, A, A, B, B)$.
+Although mobile authors who publish more papers will have longer trajectories, \textit{word2vec} will skip duplicate consecutive organization IDs, mitigating the impact of long repetitive trajectories.
 
@@
 Organizational records were associated with a full name, a type indicating the sector (e.g., University, Government, Industry), and an identifier for the country and city of the organization.
-Sixteen different sector types were included in the analysis, which we aggregated to a four high-level codes: \textit{University}, \textit{Hospital}, \textit{Government}, and \textit{Other}.
-Each record was also associated with a latitude and longitude, however, for many organizations, these were missing or incorrect.
+Sixteen different sector types were included in the analysis, which we aggregated to four high-level codes: \textit{University}, \textit{Hospital}, \textit{Government}, and \textit{Other}.
+Each record was also associated with a latitude and longitude. 
+However, for many organizations, these geographic coordinates were missing or incorrect. 
 We manually updated the coordinates of 2,267 organizations by searching the institution name and city on Google Maps;
 in cases where a precise location of the organization could not be identified, we used the coordinates returned when searching the name of the city.
-The data was further enriched with country-level information, including region, majority language spoken, and language family of the majority language (e.g., the language family of \textit{Spanish} is \textit{Italic}).
+The data was further enriched with country-level information, including region, most widely-spoken language, and its language family (e.g., the language family of \textit{Spanish} is \textit{Italic}).
 State/province-level information was added using the reverse geocoding service LocationIQ using each organization's latitude and longitude as input.
-Regional census classifications were also added for states in the United States.
-For each organization, we also calculated size as the average number of unique authors (mobile and non-mobile) who published with that organization across each year of our dataset;
+Regional census classifications were added for states in the United States.
+For each organization, we calculated size as the average number of unique authors (mobile and non-mobile) who published with that organization across each year of our dataset;
 in the case that authors publish with multiple affiliations in a single year, they are counted towards each.
@@
 Author-name disambiguation, the problem of associating names on papers with individuals authors, remains difficult for the use of bibliometric data~\autocite{dangelo2020disambiguation}.
-Authors in our dataset have been disambiguated using a rule-based algortihm that makes use of author and paper metadata, such as physica, addresses, co-authors, and journal, to score papers on the likelihood of belonging to an author cluster—a cluster of publications belived to have been authored by the same individual~\autocite{caron2014disambiguation}.
-We limit our period of analysis until after 2008, as this is when the Web of Science began indexing additional author-level metadata such as full names and email addresses.
-The disambiguation algorithm is conservative, favoring splitting clusters.
-Past studies have validated this data, demonstrating it comparable to ground-truth records such as those from ORCID and useful for a wide range of bibliometric studies~\cite{sugimoto2017mostimpact, robinson2019mobility, chinchilla2018global, chinchilla2018travelban}.
+Authors in our dataset have been disambiguated using a rule-based algorithm that makes use of author and paper metadata, such as physical addresses, co-authors, and journal, to score papers on the likelihood of belonging to an author cluster---a cluster of publications believed to have been authored by the same individual~\autocite{caron2014disambiguation}.
+We limit our period of analysis to the period of 2008 to 2019, as in 2008 the Web of Science began indexing additional author-level metadata such as full names and email addresses.
+The disambiguation algorithm is conservative, favoring splitting clusters over merging.
+Past studies have validated this data and shown that the disambiguated authors are comparable to ground-truth records such as those from ORCID and useful for a wide range of bibliometric studies~\autocite{sugimoto2017mostimpact, robinson2019mobility, chinchilla2018global, chinchilla2018travelban}.
 
@@
 The embedding ranking over-ranks large research-intensive universities such as North Carolina State University, University of Florida, and Texas A\&M University, whereas the network-derived ranking over-ranks smaller, more specialized universities such as Brandeis University, Yeshiva University, and University of San Francisco.
-This suggests that the embedding encodes information on prestige hierarchy at least as well as a network representation, but that the information encoded is something different from centrality
+This suggests that the embedding encodes information on prestige hierarchy at least as well as a network representation, with some noticeable qualitative differences.
 
@@
 
-The convex-curve pattern observed in Fig.~\ref{fig:length} repeats across many countries, but with variations.
-For example, the representative vector of Chinese organizations are larger than that of the United States ($\bar{l} = 2.97$ vs $\bar{l} = 2.39$, Table~\ref{table:supp:norm}),  causing its curve to be shifted upwards with a larger peak vector size;
-this may reflect a tendency for organizations in the United States to appear more frequently in more different contexts than Chinese organizations.
-Other nations such as Poland, Iran, and Turkey demonstrate a linear relationship between an organization's number of researchers and the vector size, indicating that their largest organizations belong to very specific contexts (Fig.~\ref{fig:concave30}).
-The organization-level distribution of embedding vector norms reveals even deeper heterogeneity---
-for example, whereas the United States has the smallest representative vector, skewness of the sizes of its organization vectors suggest that this is driven by a small number of especially-well-connected organizations ($s = -0.82$, Fig.~\ref{fig:norm_dist}).
-Germany and the United Kingdom have comparable representative vector sizes to the United States ($\bar{l} = 2.6$ and $\bar{l} = 2.61$, respectively), though they are much less skewed ($s = -0.63$ and $s = -0.55$), suggesting less inequality in the connectedness of organizations in these countries.
-The vector sizes of organizations in some countries are even more skewed, such as in Iran ($\bar{l} = 3.57$, $s = -2.13$), and China ($\bar{l} = 2.97$, $s = -1.08$), indicating the strong difference between their most- and least-connected organizations.
-For some countries, their organizations are positively-skewed, though seemingly for different reasons---
-Austria, for example, has a balanced distribution of organization vector sizes, suggesting a diverse range of organizations with most being well connected ($\bar{l} =2.64$, $s = 0.18$);
-Russia, in contrast, has a high number of organization vectors of moderate size, but also several very isolated organizations with large vector sizes ($\bar{l} = 3.08$, $s = 0.67$).
-By capturing the connectedness of organizations in the embedding vector size, the embedding space can be used to characterize universal and particularistic patterns of mobility across countries.
+The convex-curve pattern observed in Fig.~\ref{fig:length} repeats across many countries, with variations.
+For example, the representative vector of Chinese organizations has a larger norm than that of the U.S.
+($\bar{l} = 2.97$ vs $\bar{l} = 2.39$, Table~\ref{table:supp:norm}), causing its curve to be shifted upwards with a larger peak vector norm;
+this may reflect a tendency for organizations in the U.S. to appear more frequently in different contexts than Chinese organizations.
+Other nations such as Poland, Iran, and Turkey show a linear relationship between an organization's number of researchers and the vector norm, indicating that their largest organizations belong to very specific contexts (Fig.~\ref{fig:concave30}).
+The organization-level distribution of vector norms reveals deeper heterogeneity.
+The distribution of the vector norms for the U.S.
+is relatively skewed, suggesting their large norm is driven by a small and tight community of organizations (\textit{skew}$ = -0.82$, Fig.~\ref{fig:norm_dist}).
+Germany and the U.K.
+have comparable representative vector norms to the U.S.
+($\bar{l} = 2.6$ and $\bar{l} = 2.61$, respectively), with lower skewness (\textit{skew}$ = -0.63$ and \textit{skew}$ = -0.55$), suggesting more tight community of organizations.
+The vector norms of organizations in some countries are even more skewed, such as in Iran ($\bar{l} = 3.57$, \textit{skew}$ = -2.13$) and China ($\bar{l} = 2.97$, \textit{skew}$ = -1.08$), indicating the strong difference between their most- and least-connected organizations.
+For some countries, their organizations are positively-skewed, though seemingly for different reasons.
+For example, Austria has a balanced distribution of organization vector norms, suggesting a diverse range of organizations with most being well connected ($\bar{l} =2.64$, $s = 0.18$);
+Russia, in contrast, has a number of organization vectors of moderate norms, but also several isolated organizations with large vector norms ($\bar{l} = 3.08$, $s = 0.67$).
 
@@
   Pepperdine & Pepperdine Univ & Naval Academy & United States Naval Academy \\
-  Argosy & Argosy Univ & Cal State San Marcos & California State Univeristy San Marcos \\
+  Argosy & Argosy Univ & Cal State San Marcos & California State Univ San Marcos \\
   Yale & Yale Univ & Broad Inst & Broad Institute \\
@@
   Saint Mary's & Saint Mary's College & Fish and Wildlife & Fish and Wildlife Research Institute \\
-  Tufts & Tufts Univ & EPA & United States Emvironmental Protection Agency \\
+  Tufts & Tufts Univ & EPA & United States Environmental Protection Agency \\
   Mattel & Mattel Children's Hospital & US Army & United States Army \\
@@
   Rockefeller & Rockefeller Univ & Olin College & Oin College of Engineering \\
-  Adelphi & Adelphi Univ & Scripss Institute & Scripss Institute \\
+  Adelphi & Adelphi Univ & Scrips Institute & Scrips Institute \\
   Barnard & Barnard College & Idaho Natl Lab & Idaho Natl Laboratory \\
@@
   U Cincinnati & Univ of Cincinnati & Whitehead Inst & Whitehead Institute of Biomedical Research \\
-  Case Western & Case Western Reserve Univ & Wellesley & Wellesley Univeristy \\
+  Case Western & Case Western Reserve Univ & Wellesley & Wellesley Univ\\
   Ashland & Ashland Univ & UT Health, San Antonio & Univ of Texas Health Science Center, San Antonio \\
@@
   Northern Illinois & Northern Illinois Univ & FL Fish and Wildlife & Florida Fish and Wildlife Conservation Commission \\
-  Condordia Chicago & Concordia Univ-Chicago & NHLBI & Natl Heart, Lung, and Blood Institute \\
+  Concordia Chicago & Concordia Univ-Chicago & NHLBI & Natl Heart, Lung, and Blood Institute \\
   U Chicago & Univ of Chicago & NY Dept. of Health & New York Department of Health \\

### 2020-08-03 paper/current/main.tex
edits s1 fig

@@
 
-We model co-occurences $T_{ij$} for organizations $i$, and $j$, often referred to as flux, using the gravity law of mobility~\autocite{zipf1946gravity}.
+We model co-occurences $T_{ij}$ for organizations $i$, and $j$, often referred to as flux, using the gravity law of mobility~\autocite{zipf1946gravity}.
 The gravity law of mobility loosely derives from the physical law of gravity, in which the attraction between two objects is a function of their mass and the distance between them.
@@
 		\textbf{a.}
-		The number of papers published by mobile authors has been steadily increasing from 2008 to 2017, with a small decrease in 2018,  likely an artifact of the Web of Science indexing process.
-		Lines correspond to publications by mobile authors (org, purple), by authors with affiliations in at least two cities (blue), at least two regions (green), and at least two countries (yellow).
-		There is no evidence of major changes in the publication patterns of mobile authors during this time period.
+		The number of papers published by mobile authors has been steadily increasing from 2008 to 2017, with a small decrease in 2018,  which may be due to an artifact of the Web of Science indexing process.
+		Lines correspond to publications by mobile authors, by authors with affiliations in at least two cities, at least two regions, and at least two countries.
+		We did not find major changes in the publication patterns of mobile authors during this time period.
 		\textbf{b.}
@@
 		\textbf{c.}
-		Despite increasing absolute counts, the percentage of mobile scholars, and those with at least two city, regional, or country affiliations, as a proportion of all publications, has decreased over time.
+		While the absolute count of publications has increased, the percentage of mobile scholars, and those with affiliations in at least least two cities, regions, or countries, as a proportion of all publications, has decreased over time.
 		\textbf{d.}

### 2020-08-03 paper/current/main.tex
edits s2 fig

@@
 		\textbf{a.}
-		The proportion of researchers in each country classified as mobile, meaning that they have at least two organization affiliations within the period of study.
-		The countries with the most mobile researchers are the United States, China, France, Great Britain, and Germany.
+		The proportion of all mobile researchers contributed by each country. 
+		Over 30\% of all mobile researchers have been affiliated with organizations in the U.S. during the period of study.
 		\textbf{b.}
-		The same information, arranged into a cumulative distribution.
-		The five countries with the highest mobility account for approximately 70 \% of all mobility.
-		\textbf{c.} The proportion of researchers labeled as mobile by country.
-		\textbf{d.} First two principal components of four variables: proportion in each country mobile across organizations, proportion mobile across cities, proportion mobile across regions, and proportion mobile across countries.
-		The first component captures the overall degree of mobile, whereas the second compares within-country against across-country mobility.
+		Cumulative distribution of data shown in (\textbf{a}).
+		The U.S., China, and France, the U.K., and Germany comprise about 70\% of all mobile researchers. 
+		\textbf{c.} 
+		The proportion of each country's researchers who are mobile.
+		The dashed line indicates the proportion of all researchers in the data who are mobile. 
+		France, followed by Qatar and the U.S. have the highest proportion of mobile researchers. 
+		\textbf{d.} First two principal components of four variables: proportion of researchers in each country mobile across organizations, proportion mobile across cities, proportion mobile across regions, and proportion mobile across countries.
+		The countries are roughly sorted in order of the number of mobile researchers and the fraction of international mobile researchers in the first and second principal components, which are indicated by PC1 and PC2, respectively.
+		PC1 explains 88.3\% of the total variance, whereas PC2 explains 9.5\% of the total variance. 
 	}

### 2020-08-03 workflow/scripts/PlotDescriptive/PlotCountryMobilityDistribution.R

@@ -84,13 +84,14 @@ plot <- plotdata %>%
   ggrepel::geom_label_repel(data = labels, aes(label = country_iso_alpha), nudge_x = 5, size = 3, force = 2, direction = "y") +
   theme_minimal() +
   theme(
-    text = element_text(family = "Helvetica"),
+    text = element_text(size = 12, family = "Helvetica"),
     axis.title = element_text(size = 12, face = "bold"),
     axis.text = element_text(size = 11),
-    panel.grid.major = element_blank()
+    panel.grid.minor = element_blank(),
+    panel.background = element_rect(size = 0.5),
   ) +
   xlab("Rank") +
-  ylab("Proportion of global mobile researchers")
+  ylab("% all mobile researchers by country")
 
 
 p <- egg::set_panel_size(plot,

### 2020-08-03 workflow/scripts/PlotDescriptive/PlotCountryMobilityECDF.R

@@ -91,14 +91,15 @@ plot <- plotdata %>%
     geom_label(data = labels, aes(x = index, y = cumulative, label = text), size = 3, nudge_x = 6) +
     theme_minimal() +
     theme(
-      text = element_text(family = "Helvetica"),
+      text = element_text(family = "Helvetica", size = 12),
       axis.title = element_text(face = "bold", size = 12),
       axis.text = element_text(size = 11),
       axis.text.y = element_text(face = c(rep("plain", 9), "bold", "bold", "plain")),
-      panel.grid.major = element_blank()
+      panel.grid.minor = element_blank(),
+      panel.background = element_rect(size = 0.5),
     ) +
     xlab("Rank") +
-    ylab("Cumulative proportion")
+    ylab("Cumulative % of all mobile researchers by country")
 
 p <- egg::set_panel_size(plot,
                          width  = unit(FIG_WIDTH, "in"),

### 2020-08-03 workflow/scripts/PlotDescriptive/PlotProportionMobilityByCountry.R

@@ -99,13 +99,14 @@ plot <- plotdata %>%
     scale_x_continuous(expand = c(0, 0)) +
     theme_minimal() +
     theme(
-      panel.grid.major = element_blank(),
-      text = element_text(family = "Helvetica"),
+      panel.background = element_rect(size = 0.5),
+      panel.grid.minor = element_blank(),
+      text = element_text(family = "Helvetica", size = 12),
       axis.title = element_text(size = 12, face = "bold"),
       axis.text = element_text(size = 11),
     ) +
     xlab("Rank") +
-    ylab("Proportion mobile")
+    ylab("% mobility in each country")
 
 p <- egg::set_panel_size(plot,
                          width  = unit(FIG_WIDTH, "in"),

### 2020-08-03 workflow/scripts/PlotDescriptive/PlotCountryMobilityDistribution.R
minor changes to s2 fig

@@ -91,7 +91,7 @@ plot <- plotdata %>%
     panel.background = element_rect(size = 0.5),
   ) +
   xlab("Rank") +
-  ylab("% all mobile researchers by country")
+  ylab("Proportion all mobile researchers by country")
 
 
 p <- egg::set_panel_size(plot,

### 2020-08-03 workflow/scripts/PlotDescriptive/PlotCountryMobilityECDF.R

@@ -99,7 +99,7 @@ plot <- plotdata %>%
       panel.background = element_rect(size = 0.5),
     ) +
     xlab("Rank") +
-    ylab("Cumulative % of all mobile researchers by country")
+    ylab("Cumulative proportion of mobile researchers by country")
 
 p <- egg::set_panel_size(plot,
                          width  = unit(FIG_WIDTH, "in"),

### 2020-08-03 workflow/scripts/PlotDescriptive/PlotProportionMobilityByCountry.R

@@ -106,7 +106,7 @@ plot <- plotdata %>%
       axis.text = element_text(size = 11),
     ) +
     xlab("Rank") +
-    ylab("% mobility in each country")
+    ylab("Proportion mobility in each country")
 
 p <- egg::set_panel_size(plot,
                          width  = unit(FIG_WIDTH, "in"),

### 2020-08-03 paper/current/main.tex
edits up to s17 fig

@@
 There are two popular forms of the $f(r_{ij})$:
-one is a power law function in the form $f(r_{ij})= r^{-\alpha}_{ij} \ (\alpha > 0$, which we call the power decay model;
-the other and the another one is an exponential function in the form $f(r_{ij}) = e^{-\beta r_{ij}} \ (\beta > 0)$ \autocite{chen2015distance}, which we call the exponential model.  
+one is a power law function in the form $f(r_{ij})= r^{-\alpha}_{ij} \ (\alpha > 0$, and the other and the another one is an exponential function in the form $f(r_{ij}) = e^{-\beta r_{ij}} \ (\beta > 0)$ \autocite{chen2015distance}.
 The parameters for $f(r_{ij})$ and $C$ are fit to given mobility data using a log-linear regression~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity, simini2012universal}.
@@
 	\caption{
-		\textbf{Reverse cumulative-distribution function of mobile authors by geographic scale.}
+		\textbf{Reverse cumulative-distribution function of mobile researchers by geographic scale.}
 		\textbf{a.}
-		The proportion of mobile authors by how many organizations are represented in their career trajectories.
-		For example, for mobile authors, 100 \% of authors held an affiliation with at least two organizations, whereas about 35 \% were affiliated with 3 ore more organizations between 2008 and 2019.
-		Mobile authors are defined as those with at least two distinct organizational affiliations represented in our data.
-		\textbf{b.} 68 \% of mobile authors have at least two cities represented in their career trajectories.
-		\textbf{c.} 45 \% of mobile authors have 2 or more regions represented in their career trajectories.
-		\textbf{d.} Only 14 \% of mobile authors had 2 or more countries represented in their career trajectories.
+		Survival probability of mobile researchers with respect to the number of organizations in the their affiliation trajectory.
+		All mobile authors were affiliated with at least two organizations (i.e., survival probability of one) and about 35.0\% were affiliated with three or more. 
+		\textbf{b.} About 68\% of mobile authors listed at least two cities represented in their career trajectories.
+		\textbf{c.} 45\% of mobile authors have two or more regions represented in their career trajectories.
+		\textbf{d.} Only 14\% of mobile authors had two or more countries represented in their career trajectories.
 	}
@@
 		The correlation, or amount of flux explained by the embedding distance with varying skip-gram negative sampling hyperparameters.
-		Window size refers to the window, on either side of the target token, to use as context for training.
-		Smaller window sizes results in an embedding that explain more of the flux.
-		Embedding dimensions refer to the size of the organization vector.
+		Window size refers to $w$, the size of the context window that defines the context in a trajectory.
+		Smaller window sizes result in an embedding that explain more flux.
+		Embedding dimensions refer to the size of the embedding vector.
 		Larger vectors perform better, though little difference between 200 and 300.
@@
 		All variants perform worse on different-country pairs on organizations.
-		Larger embeddings outperform mid-size embeddings for the different-country case.
+		Embeddings with larger dimensions outperform mid-size embeddings for the different-country case.
 	}
@@
 		\textbf{Cosine distance is correlated with dot product similarity.}
-		Calculated as the pairwise cosine distance (x-axis) and dot product similarity (y-axis) between organizational vectors.
-		The two quantities are correlated with $R^{2} = 0.73$.
-		Color indicates frequency of organizations in hex bin.
-		Black dots are the mean dot product similarity for binned sets of embedding similarity and error bars correspond to 95\textsc{th} percentile confidence intervals.
+		We find a relatively high correlation between the embedding distance---one minus the cosine similarity---and the dot product similarity between organization vectors ($R^2 = 0.73$).
+		Color of each hex bin indicates the frequency of organization pairs. 
+		Black dots indicate the mean dot product similarity averaged over binned sets at the same embedding distance.
 		Red line is line of best fit.
@@
 		\textbf{For geographic distance, the power-decay gravity model is better.}
-		Predictions of flux between organization pairs made using geographic distance the exponential gravity model (top), and the power-law decay model (bottom).
+		Flux between organization pairs predicted by the gravity model with different distance decay functions, i.e., exponential decay function (\textbf{a}) and power-law decay function (\textbf{b}) using geographic distance.
 		Boxplots show distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps $x = y$.
-		Shown using all pairs of organization (\textbf{a-b}), domestic (\textbf{c-d}), and international only (\textbf{e-f}) mobility.
-		The power-decay model outperforms the exponential gravity model.
+		Box color corresponds to the degree to which the distribution overlaps with $x = y$; 
+		a perfect prediction yields all points on the black line.
+		Shown for all pairs of organization (\textbf{a-b}), domestic (\textbf{c-d}), and international only (\textbf{e-f}) mobility.
+		The gravity model with the power-decay function outperforms that with an exponential decay function.
 	}
@@
 	\caption{
-		\textbf{For embedding distance, the exponential gravity model is better.}
-		Predictions of flux between organization pairs made using embedding distance the exponential gravity model (top), and the power-law decay model (bottom).
+		\textbf{For geographic distance, the power-decay gravity model is better.}
+		Flux between organization pairs predicted by the gravity model with different distance decay functions, i.e., exponential decay function (\textbf{a}) and power-law decay function (\textbf{b}) using embedding distance.
 		Boxplots show distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps $x = y$.
-		Shown using all pairs of organization (\textbf{a-b}), domestic (\textbf{c-d}), and international only (\textbf{e-f}) mobility.
-		The exponential gravity model out-performs the power-decay model.
+		Box color corresponds to the degree to which the distribution overlaps with $x = y$; 
+		a perfect prediction yields all points on the black line.
+		Shown for all pairs of organization (\textbf{a-b}), domestic (\textbf{c-d}), and international only (\textbf{e-f}) mobility.
+		The gravity model with the exponential decay function outperforms that with a power-decay function.
 	}
@@
 	\caption{
-		\textbf{Embedding distance explains more variance for global, within, and between country flux than geographic distance.}
+		\textbf{Embedding distance explains more variance for global, within, and across country flux than geographic distance.}
 		\textbf{a.}
-		Embedding distance (cosine distance between vectors) explains more of the total distance than does geographic distance (\textbf{b}).
-		Red line is line of best fit.
+		Embedding distance explains more flux than geographic distance (\textbf{b}).
+		Red line is the line of best fit.
 		Black dots are mean flux across binned distances.
-		Color indicates frequency of organization pairs within each hex bin.
+		Color of each hex bin indicates frequency of organization pairs.
 		Results here are identical to those shown in Fig.~\ref{fig:gravity_performance}a and Fig.~\ref{fig:gravity_performance}.
-		\textbf{c-d.}	embedding distance explains more variance when considering only pairs of organizations within the same country.
-		\textbf{e-f.} embedding distance is more robust than geographic distance for pairs of organizations in different countries.
+		\textbf{c-d.}	embedding distance explains more variance when considering only within-country organization pairs.
+		\textbf{e-f.} embedding distance is more robust than geographic distance when considering only across-country organization pairs.
 	}
@@
 		Boxplots show distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps $x = y$.
-		\textbf{a-b.} Predictions are made with parameter, estimating parameters from all pairs of organizations, making global predictions (as in Fig.~\ref{fig:gravity_performance}c), and showing only subsets of predictions for organization pairs in the same country (\textbf{a}) and in different countries (\textbf{b}).
-		\textbf{c-d.} Predictions made by estimating gravity law parameters on subset of organizations in the same country (\textbf{c}) and different country \textbf{d});
+		Box color corresponds to the degree to which the distribution overlaps the line $x = y$; 
+		a perfect prediction yields all points on the black line.
+		\textbf{a-b.} Predictions are made with parameters estimated from all pairs of organizations (as in Fig.~\ref{fig:gravity_performance}c), and showing only the subsets of predictions for organization pairs in the same country (\textbf{a}) and in different countries (\textbf{b}).
+		\textbf{c-d.} Predictions made using parameters estimated from the subset of organizations in the same country (\textbf{c}) and different country \textbf{d});
 		this is the same data as shown in Fig.~\ref{fig:gravity_performance}f and Fig.~\ref{fig:gravity_performance}h.
@@
 		Boxplots show distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps $x = y$.
+		Box color corresponds to the degree to which the distribution overlaps $x = y$;
+		a perfect prediction yields all points on the black line.
 	}
@@
 		Personalized page rank is calculated for the underlying mobility network, and distance measured as the cosine distnace between PPR probability distribution vectors.
-		PPR cosine distance performs roughly similar to geographic distance in explaining global mobility (\textbf{a}), or domestic (\textbf{b}) or international (\textbf{c}) country mobility.
-		Red line is line of best fit.
-		Black dots are mean flux across binned distances.
-		Color indicates frequency of organization pairs within each hex bin.
+		PPR cosine distance performs roughly similar to geographic distance in explaining global(\textbf{a}), domestic (\textbf{b}), or international (\textbf{c}) country mobility.
+		Red line is the line of best fit.
+		Black dots indicate the mean flux across binned distances.
+		Color of hex bind indicates frequency of organization pairs.
 		Similarly, PPR distance performs comparably to geographic distance in predicting global (\textbf{d}), domestic (\textit{e}) and international (\textbf{f}) scientific mobility.
 		Boxplots show distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps $x = y$.
+		Box color corresponds to the degree to which the distribution overlaps $x = y$;
+		a perfect prediction yields all points on the black line.
 	}
@@
 		PPR JSD performs roughly similar to geographic distance in explaining global mobility (\textbf{a}), or domestic (\textbf{b}) or international (\textbf{c}) country mobility.
-		Overall, PPR JSD explains more vairance in mobility than using cosine distance (Fig.~\ref{fig:supp:gravity_pprcos}), except for international mobility, for which cosine similarity out-performs JSD.
-		Red line is line of best fit.
+		Overall, PPR JSD explains more variance in mobility than using cosine distance (Fig.~\ref{fig:supp:gravity_pprcos}), except for international mobility, for which cosine similarity out-performs JSD.
+		Red line is the line of best fit.
 		Black dots are mean flux across binned distances.
-		Color indicates frequency of organization pairs within each hex bin.
+		Color of hex bind indicates frequency of organization pairs.
 		Similarly, PPR JSD performs comparably to geographic distance in predicting global (\textbf{d}), domestic (\textit{e}) and international (\textbf{f}) scientific mobility.
 		Boxplots show distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps $x = y$.
+		Box color corresponds to the degree to which the distribution overlaps $x = y$;
+		a perfect prediction yields all points on the black line. 
 	}

### 2020-08-03 paper/current/main.tex
edits through si figs

@@
 		Nodes are colored by the country of the organization.
-		Nodes are positioned using the force atlas layout algorithm.
+		Nodes are positioned using the Force Atlas layout algorithm.
 	}
@@
 		\textbf{UMAP Projection of organizations in Pennsylvania.}
-		UMAP projection of the embedding space of organizations in Pennsylvania reveal clustering based on geography, sector, and academic prestige.
+		UMAP projection of the embedding space of organizations in Pennsylvania reveals clustering based on geography, sector, and academic prestige.
 		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019.
@@
 		\textbf{SemRank hierarchy is robust.}
-		\textbf{a.} Spearman's $rho$ (n = 143) between Times prestige rank and embedding rank derived using SemAxis, with poles defined using the top and bottom (geographically matched) ranked universities.
+		\textbf{a.} Spearman's $\rho$ ($n = 143$) between Times prestige rank and embedding rank derived using SemAxis, with poles defined using the top and bottom (geographically matched) ranked universities.
 		Black points show spearman correlation using all organizations; white points show correlation using only universalizes not aggregated in the poles.
@@
 		Comparison between the ranking of organizations by their network-centrality rank and their rank in the 2018 Times Higher Education ranking of U.S. Universities .
-		The Times rank is correlated with degree centrality rank (\textbf{a}) with a Spearman's $\rho = 0.73$, and is correlated with the eigenvector centrality rank (\textbf{b}) with a Spearman's $\rho = 0.76$.
+		The Times rank is correlated with degree centrality rank (\textbf{a}) with Spearman's $\rho = 0.73$, and is correlated with the eigenvector centrality rank (\textbf{b}) with Spearman's $\rho = 0.76$.
 	}
@@
 Universities .
-		Embedding rank is correlated with degree centrality rank (\textbf{a}) with a Spearman's $\rho = 0.45$, and is correlated with the eigenvector centrality rank (\textbf{b}) with a Spearman's $\rho = 0.55$.
+		Embedding rank is correlated with degree centrality rank (\textbf{a}) with Spearman's $\rho = 0.45$, and is correlated with the eigenvector centrality rank (\textbf{b}) with Spearman's $\rho = 0.55$.
 	}

### 2020-08-03 paper/current/main.tex
bib fixed

@@
 A vector-space embedding of organizations is learned by using affiliation trajectories as input to the standard skip-gram with negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
-This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
+This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
 They are also computationally efficient, robust to noise, and can encode relations between entities as geomemetric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.
@@
 The in-vector and out-vectors are different kinds of vector representations for organizations.
-We only use the in-vector, $v$, because the in-vector is more widely used and often superiors to the out-vector in link prediction benchmarks~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2016twitch}.
+We only use the in-vector, $v$, because the in-vector is more widely used and often superiors to the out-vector in link prediction benchmarks~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}.
 

### 2020-08-03 paper/current/main.tex
small abstract edit-no longer talking about connectedness

@@
 We show that the proposed functional distance reflects the multi-faced structure of scientists' mobility that is not explained by geographic distance alone, capturing relations based on culture, language, and academic prestige at multiple levels of granularity.
-The vector representations of organizations themselves also reveal insights into the landscape of global scientific mobility, such as a relationship between organizations' size and their connectedness that is consistent across most countries.
+The vector representations of organizations themselves also reveal insights into the landscape of global scientific mobility, such as a relationship between organizations' size and the norm of its vector that is consistent across most countries.
 The ability to learn scalable, dense, and meaningful high-resolution vector representations of mobility directly from the data can open up a new avenue of studying human mobility.

### 2020-08-04 paper/current/main.tex

@@
 SemAxis~\autocite{an2018semaxis} allows us to quantify abstract notions in mobility such as academic prestige, and can also be generalized to other abstract axes.
-Investigation of the structure of the embedding space, such as the vector norm, reveals unique and universal patterns based on organization's size and connectedness and could contribute to deeper understandings of scientific mobility.
+Investigation of the structure of the embedding space, such as the vector norm, reveals unique and universal patterns based on organization's size and their vector norm that could be leveraged in future studies of mobility.
 Neural embedding opens the door for new approaches to represent and study scientific mobility, and also mobility more generally.

### 2020-08-11 paper/current/main.tex

@@
 Human mobility and migration drive major societal phenomena such as the growth and evolution of cities~\autocite{wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity}, economies~\autocite{kaluza2010cargo, kerr2011immigration}, and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}.
-Geographic distance and population have been considered as leading factors of human mobilit~\autocite{zipf1946gravity}.
+Geographic distance and population have been considered as leading factors of human mobility~\autocite{zipf1946gravity}.
 However, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important, which calls for alternative \textit{functional distances} that take these factors into account~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional}.
@@
 Here, we propose using a neural embedding model that draws from real-world mobility trajectories to encode the complex landscape of global mobility into a dense, continuous, and meaningful vector-space representation, from which a \textit{functional distance} between places is derived.
-Using the case of scientific mobility, we demonstrate that the functional distance captures relations based on culture, language, and academic prestige, along with geographic relations, at multiple levels of granularity
+Using the case of scientific mobility, we demonstrate that the functional distance captures relations based on culture, language, and academic prestige, along with geographic relations, at multiple levels of granularity.
 
@@
 Iraq is nearer to Malaysia in southeast-Asian than closer and more religiously-similar Saudi Arabia and Qatar.
-In fact, we compute the distance, $d$, between nations in the original embedding space as the cosine distance between the centroids of organizations vectors belonging to that country. 
+We also validate this finding quantitatively with the distance between nations  in the embedding space $d$,  cosine distance between the centroids of organizations vectors belonging to that country. 
 Then, Malaysia ($d=0.29$) is closer to Iraq more than Arabia ($d=0.50$) and Qatar ($d=0.51$).
-Linguistic and historical ties are also conspicuous.
+
+Linguistic and historical ties also effect the scientific mobility.
 We observe that Spanish-speaking post-colonial Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), rather than nearby Portuguese-speaking nations ($d = 0.34$ vs.
@@
 
-Just as the embedding space makes it possible to ``zoom in'' on subsets of organizations, it is also possible to ``zoom out'' by aggregating organizational vectors.
+Just as the embedding space makes it possible to \textit{zoom in} on subsets of organizations, it is also possible to \textit{zoom out}  by aggregating organizational vectors.
 We can examine the country-level structure that governs scientific mobility.
-To this end, we define the representative vector of each country as the average of their organizational vectors.
-We then perform hierarchical clustering of nations that have at least 25 organizations represented in the embedding space based on their cosine similarity, excluding the United States which is a dominant hub well connected to most other countries (see Fig.
+For the purpose, we define the representative vector of each country as the average of their organizational vector and perform hierarchical clustering of nations that have at least 25 organizations represented in the embedding space based on their cosine similarity, excluding the United States which is a dominant hub well connected to most other countries (see Fig.
 \ref{fig:clustering}a).
@@
 
-We quantify the relative importance of geography (by region), and language (by most widely-spoken language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering by explicitly adjusting the relative importance of different levels of the hierarchy with scaling parameter $r$, acting like a ``zooming lens''.
+We quantify the relative importance of geography (by region), and language (by most widely-spoken language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering by explicitly adjusting the relative importance of different levels of the hierarchy with scaling parameter $r$, acting like a \textit{zooming lens}.
 If $r$ is high, the similarity is based on the lower levels of the dendrogram, whereas when $r$ is low, the similarity is based on higher levels.
@@
 ranked universities, we use the Times Ranking of World Universities (we also use research impact from the Leiden Rankings~\autocite{waltman2012leidenrankings}, see \SI);
-the high-rank pole is defined as the mean vector of the top five U.S.
+the high-rank pole is defined as the average vector of the top five U.S.
 universities according to the rankings, whereas the low-ranked pole is defined using the five bottom-ranked (geographically-matched by U.S.
@@
 The correlation between the embedding-based ranking and the Times ranking is robust regardless of the number of organizations used to define the axes (Fig.
-SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities produces a ranking that is significantly correlated with the Times ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
+~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities produces a ranking that is significantly correlated with the Times ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
 The correlation is also comparable to network-driven measures such as degree strength (sum of edge weights, Spearman's $\rho = 0.73$) and eigenvector centrality (Spearman's $\rho = 0.76$, see \SI). 
@@
 In the case of natural language, the poles of the axis could be ``good'' and ``bad'', ``surprising'' and ``unsurprising'', or ``masculine'' and ``feminine''.
-By treating organizations analogously to words and trajectories analogously to sentences, we can use SemAxis to leverage the semantic properties of the resulting embedding vectors to operationalize abstract relationships between organizations.
+By treating organizations analogously to words and trajectories analogously to sentences, we can use SemAxis to leverage the semantic properties of the embedding vectors to operationalize abstract relationships between organizations.
 

### 2020-08-11 paper/current/main.tex
PPR part

@@
 
-We also examine the gravity model on the Personalized Page Rank (PPR)\autocite{jeh2003scaling} as a benchmark on the network.
-We construct the co-occurrence network whose nodes are organization and edges are co-occurrence between two organizations.
-We use 0.9 in here.
+We examine the gravity model on the Personalized Page Rank (PPR)\autocite{jeh2003scaling} as a benchmark on the network.
+We construct the co-occurrence network of $N$ organizations, in which each edge between organizations $i$ and $j$ represents a co-occurence of $i$ and $j$ in the same affiliation trajectory, with weight $W_{ij}$ given by the sum of the co-occurences over all researchers.
+and edges are co-occurrence between two organizations.
+The Personalized Page Rank is a ranking algorithm for nodes based on a random walk process on networks.
+The walker visiting at a node moves to a neighboring node chosen randomly with a probability proportionally to the weight of the edge in one step.
+Furthermore, with probability $\alpha$, the walker is teleported back to the starting node.
+The rank of a node is determined by the probability that the walker visits the node in the stationary state.
+The stationary distribution of the random walker starting from node $i$, denoted by $p_i=(p_{ik})$, is given by
 
@@
 	\label{eq:ppr}
-	p_i = (1.0 - \alpha) v_i + \alpha p_i W,
+	p_i = (1 - \alpha) v_i + \alpha p_i W,
 \end{equation}
-
-where $v_i$ is a vector with 1 in the ith entry, whose length is the N, the number of nodes in the network, W is the weighted adjacency matrix, and $\alpha$ is the hyper-parameter is called the teleportation parameter that controls the probability that random walker revisits the original node i.
-We can think of this PPR vector as a representation of a node, which is N-length embedding.
-For examining the gravity law, we use two distance measures for PPR.
-The first one is cosine distance which is used for our embedding method, and the second one is the Jensen–Shannon divergence (JSD).
+where $v_i$ is a column vector of length $N$ with entries that are all zero except the $i$th entry that equals to one, $W = (W_{ij})$ is the weighted adjacency matrix. We used $\alpha=0.9$ here.
+
+ We can think $p_i$ as a representation vector of the organization $i$, and calculate the distance between organizations $i$ and $j$, $d_{ij}$ with measuring distance between $p_i$ and $p_j$ to examine the gravity law.
+We consider two distance measures in this analysis.
+The first one is cosine distance which is used for our embedding method, $d_{ij} = 1 - \frac{\bm{p}_{i} \cdot \bm{p}_{j}}{\lVert \bm{p}_{i} \rVert \lVert \bm{p}_{j} \rVert}$.
+Also, if we think $p_i$ as a discrete probability distribution, then we can consider Jensen–Shannon divergence (JSD), can be written as,
 
@@
 	\label{eq:JSD}
-	JSD(P||Q) = \frac{1}{2}D_{KL}(P||M) + \frac{1}{2}D_{KL}(Q||M),
+	d_{ij} = JSD(p_i||p_j) = \frac{1}{2}D_{KL}(p_i||m) + \frac{1}{2}D_{KL}(p_j||m),
 \end{equation}
@@
 	\label{eq:KL}
-	D_{KL} = \sum p(x)\log\frac{p(x)}{q(x)}
+	D_{KL}(p_i||m) = \sum^x p_{ix}\log\frac{p_{ix}}{m_x},
 \end{equation}
-
-where $M=\frac{1}{2}(P+Q)$.
-We report the both results, PPR with cosine distance (Fig.
-\ref{fig:supp:gravity_pprcos}) and (Fig.
+where $m=\frac{1}{2}(p_i+p_j)$.
+We report the result with cosine distance ($R^2=0.14$, Fig.
+\ref{fig:supp:gravity_pprcos}) and  Jensen–Shannon divergence ($R^2=0.19$, Fig.
 \ref{fig:supp:gravity_pprjsd}).
 In both cases, the performance is under the performance of the model with geographical distance.
-Even though the length of the PPR vectors is extremely larger than the length of our embedding vectors, our result on the embedding outperforms than network approach.
-Moreover, it is also computationally efficient and salable for large datasets.
+Even though the length of the PPR vectors is extremely larger than the length of our embedding vectors, result with the embedding distance outperforms both of them.
 

### 2020-08-13 paper/current/main.tex
change_title
revised abstract and introduction

@@
 \title{Learning a functional distance between organizations with unsupervised embeddings of scientific mobility}
-\title{Unsupervised embeddings of organizations capture the latent structure of global scientific mobility} %{{{
+\title{Unsupervised embeddings of career trajectories capture the latent structure of global scientific mobility} %{{{
 \date{\today}
@@
 Human mobility and migration drive major societal phenomena such as the growth and evolution of cities~\autocite{wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity}, economies~\autocite{kaluza2010cargo, kerr2011immigration}, and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}.
-Geographic distance and population have been considered as leading factors of human mobility~\autocite{zipf1946gravity}.
-However, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important, which calls for alternative \textit{functional distances} that take these factors into account~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional}.
-However, existing functional distance are often arbitrary and consider only single isolated facets of mobility.
-Using the case study of scientific mobility, we demonstrate the a neural embedding model can successfully encode the affiliation trajectories of scientists into a vector-space representation of organizations~\autocite{mikolov2013word2vec} from which a functional distance can be derived.
-We show that the proposed functional distance reflects the multi-faced structure of scientists' mobility that is not explained by geographic distance alone, capturing relations based on culture, language, and academic prestige at multiple levels of granularity.
-The vector representations of organizations themselves also reveal insights into the landscape of global scientific mobility, such as a relationship between organizations' size and the norm of its vector that is consistent across most countries.
-The ability to learn scalable, dense, and meaningful high-resolution vector representations of mobility directly from the data can open up a new avenue of studying human mobility.
+Historically, human mobility is strongly constrained by the physical separation-geographical distance~\autocite{zipf1946gravity}.
+Recently, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important, which calls for alternative modeling framework for human mobility take these factors into account~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional}.
+Here, using a massive dataset of scientific mobility, we demonstrate a neural embedding model can successfully encode nuanced relationships between locations into a vector-space ~\autocite{mikolov2013word2vec}, providing an effective functional distance that reflects the multi-faced structure of scientists' mobility and capturing cultural, linguistic relations and even academic prestige at multiple levels of granularity as well as implicit hierarchical mobility structure.
+Furthermore, vector representations of organizations themselves also reveal insights into the landscape of global scientific mobility, such as a relationship between organizations' size and the norm of its vector that is consistent across most countries.
+The ability to learn scalable, dense, and meaningful high-resolution vector representations of mobility directly derived from the data can open up a new avenue of studying human mobility.
 
@@
 The question is surprisingly hard to answer when it involves human mobility.
-Geographic distance has underpinned human movements, however it is becoming less relevant in a world connected by rapid transit and global airline networks.
+Although geographic distance has been constraining  human movements throughout history, it is becoming less relevant in a world connected by rapid transit and global airline networks.
 For instance, a person living in Australia is more likely to migrate to the United Kingdom, a far-away country with similar language and culture, than to a much closer country such as Indonesia~\autocite{pew2018migration}.
@@
 
-Here, we propose using a neural embedding model that draws from real-world mobility trajectories to encode the complex landscape of global mobility into a dense, continuous, and meaningful vector-space representation, from which a \textit{functional distance} between places is derived.
-Using the case of scientific mobility, we demonstrate that the functional distance captures relations based on culture, language, and academic prestige, along with geographic relations, at multiple levels of granularity.
+Here, we propose using a neural embedding model that draws from real-world mobility trajectories can encode the complex landscape of human mobility into a dense, continuous, and meaningful vector-space representation, from which not only a meaningful \textit{functional distance} between places but also relationship based on culture, language, and even prestige along with geographic relationship can be probed.
 
@@
 
-Here, scientific mobility is operationalized using a researcher's organizational affiliations derived from their publication histories indexed in a comprehensive bibliographic database (see Methods).
+Here, each trajectory is operationalized using a researcher's organizational affiliations derived from their publication histories indexed in a comprehensive bibliographic database (see Methods).
 The most fine-grained geographical unit in this data is the organization, such as a ``university'', ``research institute'', ``business'', or ``government agency''.
@@
 To assess the performance of the embedding distance relative to geographic distance, we evaluate their correlation with real-world mobility data and their performance in predicting real-world mobility flows as parameters to the gravity model~\autocite{zipf1946gravity, barbosa2018human}.
-The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} that calculates the \textit{expected flux}, $\hat{T}_{ij}$, of scientists between organizations based on their populations and distance:
+The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} that calculates the \textit{expected flux}, $\hat{T}_{ij}$, of peoples between locations(organizations) based on their populations and distance:
 
@@
 $\hat{T}_{ij}$, which is often referred to as ``expected flux''~\autocite{simini2012universal}, is the expected frequency of the co-occurrence of organizations $i$ and $j$ in the trajectory of affiliations in the gravity model.
-The gravity model dictates that the expected flow, $\hat{T}_{ij}$, is symmetric (\ie $\hat{T}_{ij }= \hat{T}_{ji})$, is proportional to the organizations' sizes, $\hat{T}_{ij} \propto m_{i}, m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+The gravity model dictates that the expected flow, $\hat{T}_{ij}$, is symmetric (\ie $\hat{T}_{ij }= \hat{T}_{ji})$, is proportional to the organizations' sizes, $\hat{T}_{ij} \propto m_{i} m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
 We define the distance function in terms of either the geographic distance between organizations or their embedding distance.

### 2020-08-13 paper/current/main.tex
put comma

@@
 Recently, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important, which calls for alternative modeling framework for human mobility take these factors into account~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional}.
-Here, using a massive dataset of scientific mobility, we demonstrate a neural embedding model can successfully encode nuanced relationships between locations into a vector-space ~\autocite{mikolov2013word2vec}, providing an effective functional distance that reflects the multi-faced structure of scientists' mobility and capturing cultural, linguistic relations and even academic prestige at multiple levels of granularity as well as implicit hierarchical mobility structure.
+Here, using a massive dataset of scientific mobility, we demonstrate a neural embedding model can successfully encode nuanced relationships between locations into a vector-space ~\autocite{mikolov2013word2vec}, providing an effective functional distance that reflects the multi-faced structure of scientists' mobility and capturing cultural, linguistic relations, and even academic prestige at multiple levels of granularity as well as implicit hierarchical mobility structure.
 Furthermore, vector representations of organizations themselves also reveal insights into the landscape of global scientific mobility, such as a relationship between organizations' size and the norm of its vector that is consistent across most countries.

### 2020-08-13 paper/current/main.tex
merge paragraphs

@@
 Although geographic distance has been used as the most prominent basis for models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} models, there have been attempts to define alternative notions of distance, or ~\textit{functional distances}~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional} from real-world data or \textit{a priori} relationships between geographic entities.
-Yet, functional distances are often low-resolution, at the level of countries rather than regions, cities, or organizations, and rely on somewhat arbitrary decisions about which factors are most relevant.
-Moreover, functional distances have focused on only a single facet of mobility at a time, whereas real-world mobility is multi-faceted, influenced simultaneously by geography, language, culture, history, and economic opportunity.
-To capture such complexity of human mobility, new approaches that incorporate its many facets into a single high-resolution functional distance are needed.
+
+Yet, functional distances are often low-resolution, at the level of countries rather than regions, cities, or organizations, and have focused on only a specific single facet of mobility at a time, whereas real-world mobility is multi-faceted, influenced simultaneously by geography, language, culture, history, and economic opportunity.
+Furthermore, even though the network has been using a powerful unifying approach for understanding human mobility, discrete characteristic of the network makes hard to apply simple algebraic operations or common algorithms directly, which can be easily solved with a fine-grained representation of each entity.
+To capture such complexity of human mobility and overcome these limitations, new approaches that can produce an coherent representation and incorporate its many facets into a single high-resolution functional distance are needed.
 
 Here, we propose using a neural embedding model that draws from real-world mobility trajectories can encode the complex landscape of human mobility into a dense, continuous, and meaningful vector-space representation, from which not only a meaningful \textit{functional distance} between places but also relationship based on culture, language, and even prestige along with geographic relationship can be probed.
-
-Scientific mobility is a central driver of the increasingly-globalized scientific enterprise~\autocite{czaika2018globalisation, altbach2004globalization, box2008competition}, being strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}.
-Moreover, scientific mobility has known structure, such as the centrality of the United States and the United Kingdom, and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career} that should be captured in a representation.
-However, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, being further confounded by the diminishing role of geography in shaping the landscape of scientific mobility.
+We leverage a massive dataset that documents scientific mobility captured in bibliometric records.
+Scientific mobility, which is central driver of the increasingly-globalized scientific enterprise~\autocite{czaika2018globalisation, altbach2004globalization, box2008competition}, being strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}, is not only an important topic on science of science  but also ideal for our study thanks to its richness and well-known structural properties such as the centrality to scientific-advance country, and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career}.
+In spite of the importance of the problem, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, being further confounded by the diminishing role of geography in shaping the landscape of scientific mobility.
 

### 2020-08-24 paper/current/main.tex

@@
 We leverage a massive dataset that documents scientific mobility captured in bibliometric records.
-Scientific mobility, which is central driver of the increasingly-globalized scientific enterprise~\autocite{czaika2018globalisation, altbach2004globalization, box2008competition}, being strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}, is not only an important topic on science of science  but also ideal for our study thanks to its richness and well-known structural properties such as the centrality to scientific-advance country, and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career}.
-In spite of the importance of the problem, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, being further confounded by the diminishing role of geography in shaping the landscape of scientific mobility.
-
-Here, each trajectory is operationalized using a researcher's organizational affiliations derived from their publication histories indexed in a comprehensive bibliographic database (see Methods).
-The most fine-grained geographical unit in this data is the organization, such as a ``university'', ``research institute'', ``business'', or ``government agency''.
+Scientific mobility, which is central driver of the globalized scientific enterprise~\autocite{czaika2018globalisation, altbach2004globalization, box2008competition} and strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}, is not only an important topic on science of science  but also ideal for our study thanks to its richness and well-known structural properties such as the centrality to scientific-advance country, and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career}.
+In spite of the its importance, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, being further confounded by the diminishing role of geography in shaping the landscape of scientific mobility.
+
+For the purpose, we use the trajectories of more than three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
+Each trajectory is operationalized using a researcher's organizational affiliations derived from their publication histories indexed in a comprehensive bibliographic database (see Methods).
 As a scientist's career progresses, they move between organizations or pick up additional (simultaneous) affiliations forming \textit{affiliation trajectories} (Fig.~\ref{fig:methods:mobility_sentence}).
 Thus, the trajectories encode both migration and co-affiliation---the holding of multiple simultaneous co-affiliations involving the sharing of time and capital between locations---that is typical of scientific mobility~\autocite{rodrigues2016mobility, markova2016synchronous, sugimoto2017mostimpact} (see \SI).
-We use the trajectories of more than three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
-
-A vector-space embedding of organizations is learned by using affiliation trajectories as input to the standard skip-gram with negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
+
+A vector-space embedding of organizations is learned by using affiliation trajectories as input to the standard skip-gram negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
 This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
-They are also computationally efficient, robust to noise, and can encode relations between entities as geomemetric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.
-In the organization embedding, each organization is encoded into a single vector, and vectors relate to one another based on the likelihood of organizations appearing adjacent to one another in the same affiliation trajectory.
-The functional distance between two organizations is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.
+They are also computationally efficient, robust to noise, and can encode relations between entities as geometric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.
+As a result, each organization is encoded into a single vector representation, and vectors relate to one another based on the likelihood of organizations appearing adjacent to one another in the same affiliation trajectory.
 
@@
 
-To assess the performance of the embedding distance relative to geographic distance, we evaluate their correlation with real-world mobility data and their performance in predicting real-world mobility flows as parameters to the gravity model~\autocite{zipf1946gravity, barbosa2018human}.
-The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} that calculates the \textit{expected flux}, $\hat{T}_{ij}$, of peoples between locations(organizations) based on their populations and distance:
+To validate our approach, we evaluate the quality of result vector representations with their performance in predicting real-world mobility flows as parameters to the gravity model~\autocite{zipf1946gravity, barbosa2018human}.
+The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} that calculates the \textit{expected flux}, $\hat{T}_{ij}$, of peoples between locations (organizations) based on their populations and distance:
 
@@
 The gravity model dictates that the expected flow, $\hat{T}_{ij}$, is symmetric (\ie $\hat{T}_{ij }= \hat{T}_{ji})$, is proportional to the organizations' sizes, $\hat{T}_{ij} \propto m_{i} m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
-We define the distance function in terms of either the geographic distance between organizations or their embedding distance.
+We define the distance function in terms of either the geographic distance between organizations or their functional distance in the vector space, which is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.
 For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_emb_bymodel} and Fig.~\ref{fig:supp:predict_geo_bymodel}).
@@
 Trajectories are represented as the list of author-affiliation combinations, ordered by year of publication, and randomly ordered for combinations within the same year.
+The most fine-grained geographical unit in this data is the organization, such as a ``university'', ``research institute'', ``business'', or ``government agency''.
 

### 2020-09-07 workflow/scripts/PlotSemAxisVsImpactCorrByThreshold.R
add new semaxis rankings and impact plot comparison for sectors

@@ -1,0 +1,135 @@
+#
+# PlotSemAxisVsImpactCorrByThreshold.R
+#
+# author: Dakota Murray
+#
+# Plot the comparison between the ranking derived from the simularity
+# projection and the standard university ranking
+#
+# Plot dimensions
+FIG_WIDTH = 12
+FIG_HEIGHT = 4
+
+# The thresholds to plot
+thresholds <- c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100, 110, 120, 130, 140, 150)
+
+library(readr)
+library(ggplot2)
+library(dplyr)
+suppressPackageStartupMessages(require(optparse))
+
+# Command line arguments
+option_list = list(
+  make_option(c("--semaxis"), action="store", default=NA, type='character',
+              help="Path to file containing semaxis ranking"),
+  make_option(c("--impact"), action="store", default=NA, type='character',
+              help="Path to file containing times ranking"),
+  make_option(c("--types"), action="store", default=NA, type='character',
+              help="Path to file containing org types"),
+  make_option(c("--lookup"), action="store", default=NA, type='character',
+              help="Path to file containing organizational metadata"),
+  make_option(c("--sizes"), action="store", default="none", type='character',
+              help="Path to organization sizes"),
+  make_option(c("-o", "--output"), action="store", default=NA, type='character',
+              help="Path to save output image")
+) # end option_list
+opt = parse_args(OptionParser(option_list=option_list))
+
+# Semaxis data
+semaxis <- read_csv(opt$semaxis, col_types = cols())
+
+# Impact data from the Leiden database
+impact <- read_delim(opt$impact, delim = "\t", col_types = cols())
+
+# Organization types
+org_types <- read_csv(opt$types, col_types = cols())
+
+# Organization lookup table, metadata
+lookup <- read_delim(opt$lookup, delim = "\t", col_types = readr::cols()) %>%
+  filter(country_iso_alpha == "USA") # select only the specified country
+
+# Information on the sizes of organizations
+sizes <- readr::read_delim(opt$sizes, delim = "\t", col_types = readr::cols()) %>%
+  group_by(cwts_org_no) %>%
+  summarize(size = mean(person_count))
+
+base_data <- impact %>%
+  # Make sure the impact is set to a numeric
[…]

### 2020-09-07 paper/current/main.tex
incorperate new plots into text

--- 2020-08-13 paper/current/main.tex
@@
 \title{Learning a functional distance between organizations with unsupervised embeddings of scientific mobility}
-\title{Unsupervised embeddings of career trajectories capture the latent structure of global scientific mobility} %{{{
+\title{Unsupervised embeddings of organizations capture the latent structure of global scientific mobility} %{{{
 \date{\today}
@@
 Human mobility and migration drive major societal phenomena such as the growth and evolution of cities~\autocite{wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity}, economies~\autocite{kaluza2010cargo, kerr2011immigration}, and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}.
-Historically, human mobility is strongly constrained by the physical separation-geographical distance~\autocite{zipf1946gravity}.
-Recently, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important, which calls for alternative modeling framework for human mobility take these factors into account~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional}.
-Here, using a massive dataset of scientific mobility, we demonstrate a neural embedding model can successfully encode nuanced relationships between locations into a vector-space ~\autocite{mikolov2013word2vec}, providing an effective functional distance that reflects the multi-faced structure of scientists' mobility and capturing cultural, linguistic relations, and even academic prestige at multiple levels of granularity as well as implicit hierarchical mobility structure.
-Furthermore, vector representations of organizations themselves also reveal insights into the landscape of global scientific mobility, such as a relationship between organizations' size and the norm of its vector that is consistent across most countries.
-The ability to learn scalable, dense, and meaningful high-resolution vector representations of mobility directly derived from the data can open up a new avenue of studying human mobility.
+Geographic distance and population have been considered as leading factors of human mobilit~\autocite{zipf1946gravity}.
+However, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important, which calls for alternative \textit{functional distances} that take these factors into account~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional}.
+However, existing functional distance are often arbitrary and consider only single isolated facets of mobility.
+Using the case study of scientific mobility, we demonstrate the a neural embedding model can successfully encode the affiliation trajectories of scientists into a vector-space representation of organizations~\autocite{mikolov2013word2vec} from which a functional distance can be derived.
+We show that the proposed functional distance reflects the multi-faced structure of scientists' mobility that is not explained by geographic distance alone, capturing relations based on culture, language, and academic prestige at multiple levels of granularity.
+The vector representations of organizations themselves also reveal insights into the landscape of global scientific mobility, such as a relationship between organizations' size and the norm of its vector that is consistent across most countries.
+The ability to learn scalable, dense, and meaningful high-resolution vector representations of mobility directly from the data can open up a new avenue of studying human mobility.
 
@@
 The question is surprisingly hard to answer when it involves human mobility.
-Although geographic distance has been constraining  human movements throughout history, it is becoming less relevant in a world connected by rapid transit and global airline networks.
+Geographic distance has underpinned human movements, however it is becoming less relevant in a world connected by rapid transit and global airline networks.
 For instance, a person living in Australia is more likely to migrate to the United Kingdom, a far-away country with similar language and culture, than to a much closer country such as Indonesia~\autocite{pew2018migration}.
@@
 
-Here, we propose using a neural embedding model that draws from real-world mobility trajectories can encode the complex landscape of human mobility into a dense, continuous, and meaningful vector-space representation, from which not only a meaningful \textit{functional distance} between places but also relationship based on culture, language, and even prestige along with geographic relationship can be probed.
+Here, we propose using a neural embedding model that draws from real-world mobility trajectories to encode the complex landscape of global mobility into a dense, continuous, and meaningful vector-space representation, from which a \textit{functional distance} between places is derived.
+Using the case of scientific mobility, we demonstrate that the functional distance captures relations based on culture, language, and academic prestige, along with geographic relations, at multiple levels of granularity
 
@@
 
-Here, each trajectory is operationalized using a researcher's organizational affiliations derived from their publication histories indexed in a comprehensive bibliographic database (see Methods).
+Here, scientific mobility is operationalized using a researcher's organizational affiliations derived from their publication histories indexed in a comprehensive bibliographic database (see Methods).
 The most fine-grained geographical unit in this data is the organization, such as a ``university'', ``research institute'', ``business'', or ``government agency''.
@@
 To assess the performance of the embedding distance relative to geographic distance, we evaluate their correlation with real-world mobility data and their performance in predicting real-world mobility flows as parameters to the gravity model~\autocite{zipf1946gravity, barbosa2018human}.
-The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} that calculates the \textit{expected flux}, $\hat{T}_{ij}$, of peoples between locations(organizations) based on their populations and distance:
+The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} that calculates the \textit{expected flux}, $\hat{T}_{ij}$, of scientists between organizations based on their populations and distance:
 
@@
 $\hat{T}_{ij}$, which is often referred to as ``expected flux''~\autocite{simini2012universal}, is the expected frequency of the co-occurrence of organizations $i$ and $j$ in the trajectory of affiliations in the gravity model.
-The gravity model dictates that the expected flow, $\hat{T}_{ij}$, is symmetric (\ie $\hat{T}_{ij }= \hat{T}_{ji})$, is proportional to the organizations' sizes, $\hat{T}_{ij} \propto m_{i} m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+The gravity model dictates that the expected flow, $\hat{T}_{ij}$, is symmetric (\ie $\hat{T}_{ij }= \hat{T}_{ji})$, is proportional to the organizations' sizes, $\hat{T}_{ij} \propto m_{i}, m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
 We define the distance function in terms of either the geographic distance between organizations or their embedding distance.
@@
 Iraq is nearer to Malaysia in southeast-Asian than closer and more religiously-similar Saudi Arabia and Qatar.
-We also validate this finding quantitatively with the distance between nations  in the embedding space $d$,  cosine distance between the centroids of organizations vectors belonging to that country. 
+In fact, we compute the distance, $d$, between nations in the original embedding space as the cosine distance between the centroids of organizations vectors belonging to that country. 
 Then, Malaysia ($d=0.29$) is closer to Iraq more than Arabia ($d=0.50$) and Qatar ($d=0.51$).
-
-Linguistic and historical ties also effect the scientific mobility.
+Linguistic and historical ties are also conspicuous.
 We observe that Spanish-speaking post-colonial Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), rather than nearby Portuguese-speaking nations ($d = 0.34$ vs.
@@
 
-Just as the embedding space makes it possible to \textit{zoom in} on subsets of organizations, it is also possible to \textit{zoom out}  by aggregating organizational vectors.
+Just as the embedding space makes it possible to ``zoom in'' on subsets of organizations, it is also possible to ``zoom out'' by aggregating organizational vectors.
 We can examine the country-level structure that governs scientific mobility.
-For the purpose, we define the representative vector of each country as the average of their organizational vector and perform hierarchical clustering of nations that have at least 25 organizations represented in the embedding space based on their cosine similarity, excluding the United States which is a dominant hub well connected to most other countries (see Fig.
+To this end, we define the representative vector of each country as the average of their organizational vectors.
+We then perform hierarchical clustering of nations that have at least 25 organizations represented in the embedding space based on their cosine similarity, excluding the United States which is a dominant hub well connected to most other countries (see Fig.
 \ref{fig:clustering}a).
@@
 
-We quantify the relative importance of geography (by region), and language (by most widely-spoken language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering by explicitly adjusting the relative importance of different levels of the hierarchy with scaling parameter $r$, acting like a \textit{zooming lens}.
+We quantify the relative importance of geography (by region), and language (by most widely-spoken language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering by explicitly adjusting the relative importance of different levels of the hierarchy with scaling parameter $r$, acting like a ``zooming lens''.
 If $r$ is high, the similarity is based on the lower levels of the dendrogram, whereas when $r$ is low, the similarity is based on higher levels.
@@
 ranked universities, we use the Times Ranking of World Universities (we also use research impact from the Leiden Rankings~\autocite{waltman2012leidenrankings}, see \SI);
-the high-rank pole is defined as the average vector of the top five U.S.
+the high-rank pole is defined as the mean vector of the top five U.S.
 universities according to the rankings, whereas the low-ranked pole is defined using the five bottom-ranked (geographically-matched by U.S.
@@
 The correlation between the embedding-based ranking and the Times ranking is robust regardless of the number of organizations used to define the axes (Fig.
-~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities produces a ranking that is significantly correlated with the Times ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
+SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities produces a ranking that is significantly correlated with the Times ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
 The correlation is also comparable to network-driven measures such as degree strength (sum of edge weights, Spearman's $\rho = 0.73$) and eigenvector centrality (Spearman's $\rho = 0.76$, see \SI). 
@@
 Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphasis on teaching, such as Barry University and California State University at Long Beach.
-By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations for which rankings are often low-resolution or incomplete, such as regional and liberal arts universities, seminaries, musical schools, and community colleges (Fig.~\ref{fig:semaxis}d), or for which no such rankings exist, such as government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).
+By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations for which rankings are often low-resolution, incomplete, or entirely absent such as regional and liberal arts universities, seminaries, musical schools, and community colleges (Fig.~\ref{fig:semaxis}d), government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).
+Using SemAxis, we can even construct quantitative rankings for these types of organizations that correlate with their citation impact (Fig.~\ref{fig:supp:sector_semaxis_impact}.
 
@@
 In the case of natural language, the poles of the axis could be ``good'' and ``bad'', ``surprising'' and ``unsurprising'', or ``masculine'' and ``feminine''.
-By treating organizations analogously to words and trajectories analogously to sentences, we can use SemAxis to leverage the semantic properties of the embedding vectors to operationalize abstract relationships between organizations.
+By treating organizations analogously to words and trajectories analogously to sentences, we can use SemAxis to leverage the semantic properties of the resulting embedding vectors to operationalize abstract relationships between organizations.
 
@@
 
-We examine the gravity model on the Personalized Page Rank (PPR)\autocite{jeh2003scaling} as a benchmark on the network.
-We construct the co-occurrence network of $N$ organizations, in which each edge between organizations $i$ and $j$ represents a co-occurence of $i$ and $j$ in the same affiliation trajectory, with weight $W_{ij}$ given by the sum of the co-occurences over all researchers.
-and edges are co-occurrence between two organizations.
-The Personalized Page Rank is a ranking algorithm for nodes based on a random walk process on networks.
-The walker visiting at a node moves to a neighboring node chosen randomly with a probability proportionally to the weight of the edge in one step.
-Furthermore, with probability $\alpha$, the walker is teleported back to the starting node.
-The rank of a node is determined by the probability that the walker visits the node in the stationary state.
-The stationary distribution of the random walker starting from node $i$, denoted by $p_i=(p_{ik})$, is given by
+We also examine the gravity model on the Personalized Page Rank (PPR)\autocite{jeh2003scaling} as a benchmark on the network.
+We construct the co-occurrence network whose nodes are organization and edges are co-occurrence between two organizations.
+We use 0.9 in here.
 
@@
 	\label{eq:ppr}
-	p_i = (1 - \alpha) v_i + \alpha p_i W,
+	p_i = (1.0 - \alpha) v_i + \alpha p_i W,
 \end{equation}
-where $v_i$ is a column vector of length $N$ with entries that are all zero except the $i$th entry that equals to one, $W = (W_{ij})$ is the weighted adjacency matrix. We used $\alpha=0.9$ here.
-
- We can think $p_i$ as a representation vector of the organization $i$, and calculate the distance between organizations $i$ and $j$, $d_{ij}$ with measuring distance between $p_i$ and $p_j$ to examine the gravity law.
-We consider two distance measures in this analysis.
-The first one is cosine distance which is used for our embedding method, $d_{ij} = 1 - \frac{\bm{p}_{i} \cdot \bm{p}_{j}}{\lVert \bm{p}_{i} \rVert \lVert \bm{p}_{j} \rVert}$.
-Also, if we think $p_i$ as a discrete probability distribution, then we can consider Jensen–Shannon divergence (JSD), can be written as,
+
+where $v_i$ is a vector with 1 in the ith entry, whose length is the N, the number of nodes in the network, W is the weighted adjacency matrix, and $\alpha$ is the hyper-parameter is called the teleportation parameter that controls the probability that random walker revisits the original node i.
+We can think of this PPR vector as a representation of a node, which is N-length embedding.
+For examining the gravity law, we use two distance measures for PPR.
+The first one is cosine distance which is used for our embedding method, and the second one is the Jensen–Shannon divergence (JSD).
 
@@
 	\label{eq:JSD}
-	d_{ij} = JSD(p_i||p_j) = \frac{1}{2}D_{KL}(p_i||m) + \frac{1}{2}D_{KL}(p_j||m),
+	JSD(P||Q) = \frac{1}{2}D_{KL}(P||M) + \frac{1}{2}D_{KL}(Q||M),
 \end{equation}
@@
 	\label{eq:KL}
-	D_{KL}(p_i||m) = \sum^x p_{ix}\log\frac{p_{ix}}{m_x},
+	D_{KL} = \sum p(x)\log\frac{p(x)}{q(x)}
 \end{equation}
-where $m=\frac{1}{2}(p_i+p_j)$.
-We report the result with cosine distance ($R^2=0.14$, Fig.
-\ref{fig:supp:gravity_pprcos}) and  Jensen–Shannon divergence ($R^2=0.19$, Fig.
+
+where $M=\frac{1}{2}(P+Q)$.
+We report the both results, PPR with cosine distance (Fig.
+\ref{fig:supp:gravity_pprcos}) and (Fig.
 \ref{fig:supp:gravity_pprjsd}).
 In both cases, the performance is under the performance of the model with geographical distance.
-Even though the length of the PPR vectors is extremely larger than the length of our embedding vectors, result with the embedding distance outperforms both of them.
+Even though the length of the PPR vectors is extremely larger than the length of our embedding vectors, our result on the embedding outperforms than network approach.
+Moreover, it is also computationally efficient and salable for large datasets.
 
@@
 %
+% Figure - SemAxis By State
+%
+\begin{figure}[hp!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/SemAxis/sector_rank_comparison.pdf}
+	\caption{
+		\textbf{SemAxis reconstructs publication impact in non-university sectors.}
+		Comparison between the ranking of organizations in each non-university sector by their citation impact and the embedding rank.
+		Citation impact is calculated as the mean-normalized citation score using papers published in the Web of Science database between 2008 and 2019. 
+		The embedding rank is derived by first projecting non-university organizations onto the SemAxis axis formed with poles defined using the top five to geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S.
+Universities.
+		\textbf{a} Shows how the correlation between the citation impact and SemAxis rankings differ while varying the size threshold for including an organization.
+		Size is calculated as the mean annualized number of unique authors publishing with that organization. 
+		Annotations show the number of organizations remaining at thresholds pf 0, 50, and 100. 
+		\textbf{b}. Comparison of organizations using a size threshold of 10 for regional and liberal arts colleges, and 50 for research institutes and government organizations;
+		these thresholds were chosen as points thresholds of stability in \textbf{a}. 		
+		The impact rank is correlated with the embedding rank for regional and liberal arts colleges with Spearman's $\rho = 0.49 (n = 48)$, research institutes with Spearman's $\rho = 0.58 (n = 159)$, and for government organizations with Spearman's $\rho = 0.36 (n = 55)$.
+	}
+	\label{fig:supp:sector_semaxis_impact}
+\end{figure}
+
+%
 % Figure - SemAxis By Sector

### 2020-09-07 paper/current/main.tex
updated text

@@
 Human mobility and migration drive major societal phenomena such as the growth and evolution of cities~\autocite{wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity}, economies~\autocite{kaluza2010cargo, kerr2011immigration}, and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}.
-Historically, human mobility is strongly constrained by the physical separation-geographical distance~\autocite{zipf1946gravity}.
-Recently, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important, which calls for alternative modeling framework for human mobility take these factors into account~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional}.
-Here, using a massive dataset of scientific mobility, we demonstrate a neural embedding model can successfully encode nuanced relationships between locations into a vector-space ~\autocite{mikolov2013word2vec}, providing an effective functional distance that reflects the multi-faced structure of scientists' mobility and capturing cultural, linguistic relations, and even academic prestige at multiple levels of granularity as well as implicit hierarchical mobility structure.
+Historically, human mobility is strongly constrained by physical separation---geographical distance~\autocite{zipf1946gravity}.
+However, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important, which calls for an alternative modeling framework for human mobility that take these factors into account~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional}.
+Here, using a massive dataset of scientific mobility, we demonstrate a neural embedding model can successfully encode nuanced relationships between locations into a vector-space ~\autocite{mikolov2013word2vec}, providing an effective functional distance that reflects the multi-faced structure of scientists' mobility and capturing cultural, linguistic relations, and even academic prestige at multiple levels of granularity, as well as implicit hierarchical structure.
 Furthermore, vector representations of organizations themselves also reveal insights into the landscape of global scientific mobility, such as a relationship between organizations' size and the norm of its vector that is consistent across most countries.
@@
 
-Yet, functional distances are often low-resolution, at the level of countries rather than regions, cities, or organizations, and have focused on only a specific single facet of mobility at a time, whereas real-world mobility is multi-faceted, influenced simultaneously by geography, language, culture, history, and economic opportunity.
-Furthermore, even though the network has been using a powerful unifying approach for understanding human mobility, discrete characteristic of the network makes hard to apply simple algebraic operations or common algorithms directly, which can be easily solved with a fine-grained representation of each entity.
-To capture such complexity of human mobility and overcome these limitations, new approaches that can produce an coherent representation and incorporate its many facets into a single high-resolution functional distance are needed.
+Yet, functional distances are often low-resolution, computed at the level of countries rather than regions, cities, or organizations, and have focused on only a single facets of mobility at a time, whereas real-world mobility is multi-faceted, influenced simultaneously by geography, language, culture, history, and economic opportunity.
+Low dimensional distance alone cannot represent the multitude of inter-related factors that derive mobility. 
+Networks offer a solution to representing the many dimensions of mobility, yet they only represent flows between discrete entities, and so cannot easily capture the relationships between entities themselves.
+Overcoming the complexity of mobility requires moving beyond simple functional distances and networks, to instead learning high-dimensional landscapes of mobility that incorporates the many facets of mobility into a single fine-grained and continuous representation.
 
@@
 We leverage a massive dataset that documents scientific mobility captured in bibliometric records.
-Scientific mobility, which is central driver of the globalized scientific enterprise~\autocite{czaika2018globalisation, altbach2004globalization, box2008competition} and strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}, is not only an important topic on science of science  but also ideal for our study thanks to its richness and well-known structural properties such as the centrality to scientific-advance country, and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career}.
-In spite of the its importance, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, being further confounded by the diminishing role of geography in shaping the landscape of scientific mobility.
-
-For the purpose, we use the trajectories of more than three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
+Scientific mobility, which is central driver of the globalized scientific enterprise~\autocite{czaika2018globalisation, altbach2004globalization, box2008competition} and strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}, is not only an important topic on science of science but also ideal for our study thanks to its richness and well-known structural properties such as the centrality of scientifically advanced countries and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career}.
+In spite of its importance, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, being further confounded by the diminishing role of geography in shaping the landscape of scientific mobility.
+
+In our approach, we use trajectories of more than three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
 Each trajectory is operationalized using a researcher's organizational affiliations derived from their publication histories indexed in a comprehensive bibliographic database (see Methods).
@@
 To validate our approach, we evaluate the quality of result vector representations with their performance in predicting real-world mobility flows as parameters to the gravity model~\autocite{zipf1946gravity, barbosa2018human}.
-The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} that calculates the \textit{expected flux}, $\hat{T}_{ij}$, of peoples between locations (organizations) based on their populations and distance:
+The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} that calculates the \textit{expected flux}, $\hat{T}_{ij}$, of people between locations (organizations) based on their populations and distance:
 
@@
 	\caption{
-		\textbf{Embedding distance outperforms geographic distance.}
+		\textbf{Embedding distance encodes functional distance and better predicts mobility.}
 		\textbf{a-b.} Embedding distance (cosine distance between organization vectors) better explains the expected flux between organization pairs than geographic distance.
@@
 		99\% confidence intervals are plotted, but are too small to be visible.
-		Correlation is calculated on the data in the $log$-$log$ scale. 
+		Correlation is calculated on the data in the $\log-\log$ scale. 
 		The lightness of each hex bin indicates the frequency of organization pairs within it.
@@
 
+%
+% BIG PROJECTION
+%
 \begin{figure}[hp!]
@@
 		Color indicates the region.
+		The separation of organizations in Quebec and the rest of Canada is highlighted. 
 		\textbf{b.} Zooming into (re-projecting) the area containing countries in the Middle East and South and Southeast Asia shows a geographic and cultural gradient of country clusters.
@@
 By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations for which rankings are often low-resolution, incomplete, or entirely absent such as regional and liberal arts universities, seminaries, musical schools, and community colleges (Fig.~\ref{fig:semaxis}d), government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).
-Using SemAxis, we can even construct quantitative rankings for these types of organizations that correlate with their citation impact (Fig.~\ref{fig:supp:sector_semaxis_impact}.
+Using SemAxis, we can even construct quantitative rankings for these types of organizations that correlate with their citation impact (Fig.~\ref{fig:supp:sector_semaxis_impact}).
 

### 2020-09-08 paper/current/main.tex
merge

--- 2020-09-07 paper/current/main.tex
@@
 	\caption{
-		\textbf{Embedding distance outperforms geographic distance.}
+		\textbf{Embedding distance encodes functional distance and better predict mobility.}
 		\textbf{a-b.} Embedding distance (cosine distance between organization vectors) better explains the expected flux between organization pairs than geographic distance.
@@
 		99\% confidence intervals are plotted, but are too small to be visible.
-		Correlation is calculated on the data in the $log$-$log$ scale. 
+		Correlation is calculated on the data in the log-log scale. 
 		The lightness of each hex bin indicates the frequency of organization pairs within it.
@@
 Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphasis on teaching, such as Barry University and California State University at Long Beach.
-By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations for which rankings are often low-resolution, incomplete, or entirely absent such as regional and liberal arts universities, seminaries, musical schools, and community colleges (Fig.~\ref{fig:semaxis}d), government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).
-Using SemAxis, we can even construct quantitative rankings for these types of organizations that correlate with their citation impact (Fig.~\ref{fig:supp:sector_semaxis_impact}.
+By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations for which rankings are often low-resolution or incomplete, such as regional and liberal arts universities, seminaries, musical schools, and community colleges (Fig.~\ref{fig:semaxis}d), or for which no such rankings exist, such as government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).
 
@@
 %
-% Figure - SemAxis By State
-%
-\begin{figure}[hp!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/SemAxis/sector_rank_comparison.pdf}
-	\caption{
-		\textbf{SemAxis reconstructs publication impact in non-university sectors.}
-		Comparison between the ranking of organizations in each non-university sector by their citation impact and the embedding rank.
-		Citation impact is calculated as the mean-normalized citation score using papers published in the Web of Science database between 2008 and 2019. 
-		The embedding rank is derived by first projecting non-university organizations onto the SemAxis axis formed with poles defined using the top five to geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S.
-Universities.
-		\textbf{a} Shows how the correlation between the citation impact and SemAxis rankings differ while varying the size threshold for including an organization.
-		Size is calculated as the mean annualized number of unique authors publishing with that organization. 
-		Annotations show the number of organizations remaining at thresholds pf 0, 50, and 100. 
-		\textbf{b}. Comparison of organizations using a size threshold of 10 for regional and liberal arts colleges, and 50 for research institutes and government organizations;
-		these thresholds were chosen as points thresholds of stability in \textbf{a}. 		
-		The impact rank is correlated with the embedding rank for regional and liberal arts colleges with Spearman's $\rho = 0.49 (n = 48)$, research institutes with Spearman's $\rho = 0.58 (n = 159)$, and for government organizations with Spearman's $\rho = 0.36 (n = 55)$.
-	}
-	\label{fig:supp:sector_semaxis_impact}
-\end{figure}
-
-%
 % Figure - SemAxis By Sector

### 2020-09-14 paper/current/main.tex
add data part

--- 2020-09-07 paper/current/main.tex
@@
 		99\% confidence intervals are plotted, but are too small to be visible.
-		Correlation is calculated on the data in the $\log-\log$ scale. 
+		Correlation is calculated on the data in the log-log scale. 
 		The lightness of each hex bin indicates the frequency of organization pairs within it.
@@
 
-\subsection*{Data}
+\subsection*{Data - Scientific mobility}
 %% Main dataset
@@
 While the number of publications has increased year-to-year, the mobility and disciplinary makeup of the dataset has not significantly changed across the period of study (Fig.~\ref{fig:supp:pubs_over_time}).
+
+\subsection*{Data -US Airport Itinerary data}
+We use US airport itinerary data from the Bureau of Transportation statistics provided by the United States Department of Transportation.
+Origin and Destination Survey (DB1B) is a 10\% sample of domestic airline tickets, including origin, destination, and other itinerary details.
+Trajectories are represented as the list of airport code, cover itinerary between 1993 to 2020 and 30,776,0841 trajectory in total and the unique number of airports is 838.
 

### 2020-09-14 paper/current/main.tex
change a little bit

--- 2020-09-07 paper/current/main.tex
@@
 While the number of publications has increased year-to-year, the mobility and disciplinary makeup of the dataset has not significantly changed across the period of study (Fig.~\ref{fig:supp:pubs_over_time}).
+
+\subsection*{Data -US Airport Itinerary}
+We use US airport itinerary data from the Bureau of Transportation statistics provided by the United States Department of Transportation.
+Origin and Destination Survey (DB1B) is a 10\% sample of domestic airline tickets, including origin, destination, and other itinerary details.
+Trajectories are represented as the list of airport code and cover itinerary between 1993 to 2020.
+There are 30,776,0841 trajectories in total and the unique number of airports is 838.
 

### 2020-09-24 workflow/scripts/CalculatePredictedVsActualAirport.R
code to plot airport gravity, predicted vs. actual plots

@@ -1,0 +1,75 @@
+#
+# CalculatePredictedVsActual.R
+#
+# author: Dakota Murray
+#
+# Represents the organization flows as a single network and calculates shortest
+# paths between all pairs of points
+#
+
+library(dplyr)
+# Parse command line argument
+suppressPackageStartupMessages(require(optparse))
+
+# Command line arguments
+option_list = list(
+  make_option(c("-i", "--input"), action="store", default=NA, type='character',
+              help="Path to file containing aggregate distance information"),
+  make_option(c("--distance"), action="store", default="none",
+              help="One of 'geo' or 'emb', specifying which distance metric of the dataframe to use"),
+  make_option(c("-o", "--output"), action="store", default=NA, type='character',
+              help="Path to save distances")
+) # end option_list
+opt = parse_args(OptionParser(option_list=option_list))
+
+# Load the data, select relevant columns
+agg <- readr::read_csv(opt$input, col_types = readr::cols()) %>%
+  select(org1_size, org2_size,
+         count, gravity,
+         geo_distance, emb_distance) %>%
+  rename(actual = count)
+
+
+#
+# Calculate the expected value. We use two different equations depending on
+# whether we are calculating it on geographic distance, or embedding similarity
+#
+if (opt$distance == "geo") {
+  # Perform the regression
+  agg <- agg %>%
+    mutate(
+      distance = geo_distance,
+      distance.log = log(geo_distance)
+    )
+} else if (opt$distance == "emb") {
+  agg <- agg %>%
+    mutate(
+      distance = emb_distance,
+      distance.log = log(emb_distance)
+    )
+}
+
+fit.power <- summary(lm(log(gravity) ~ log(distance), data = agg))
+intercept.power <- fit.power$coefficients["(Intercept)", "Estimate"]
+coef.power <- fit.power$coefficients["log(distance)", "Estimate"]
+
+fit.exp <- summary(lm(log(gravity) ~ distance, data = agg))
+# Save the coefficients for use later
+intercept.exp <- fit.exp$coefficients["(Intercept)", "Estimate"]
+coef.exp <- fit.exp$coefficients["distance", "Estimate"]
+
+agg <- agg %>%
+  mutate(
+    # Calculate the expected value using the geographic distance formula
+    expected.power = (org1_size * org2_size) * (distance ^ (coef.power)) * exp(intercept.power),
+    # Calculate the expected value using the embedding similarity formula
[…]

### 2020-09-24 workflow/scripts/PlotPredictedVsActualAirport.R

@@ -1,0 +1,157 @@
+#
+# PlotPredictedVsActualAirport.R
+#
+# author: Dakota Murray
+#
+# Plot the relationship between predicted and actual flows
+# for the airport dataset
+#
+
+# Plotting options
+NUM_BINS = 36
+
+COLOR_BAD_FIT = "white"
+COLOR_GOOD_FIT = "#1E88E5"
+
+FILL_GRADIENT_MIN = "white"
+FILL_GRADIENT_MAX = "#7f8c8d"
+BIN_BORDER_COLOR = "white"
+
+# Plot dimensions
+FIG_WIDTH = 3
+FIG_HEIGHT = 3
+
+library(ggplot2)
+library(dplyr)
+suppressPackageStartupMessages(require(optparse))
+
+# Command line arguments
+option_list = list(
+  make_option(c("-i", "--input"), action="store", default=NA, type='character',
+              help="Path to file containing predicted vs. actual flows"),
+  make_option(c("--model"), action="store", default="none",
+              help="Model type, either exponential (exp) or power decay (power)"),
+  make_option(c("-o", "--output"), action="store", default=NA, type='character',
+              help="Path to save distances")
+) # end option_list
+opt = parse_args(OptionParser(option_list=option_list))
+
+# Read the aggregated distance file
+data = readr::read_csv(opt$input, col_types = readr::cols())
+
+# Set the correct distance variable based on input parameter
+if (opt$model == "exp") {
+  data <- data %>%
+    mutate(expected = expected.exp)
+} else if (opt$model == "power") {
+  data <- data %>%
+    mutate(expected = expected.power)
+}
+
+# Create bins for epected values within which we will calculate
+# aggregate information about the actual values.
+binned <- data %>%
+  # Filter to within a specific range to avoid outlier issues
+  filter(log10(expected) < 6 & log10(expected) >= 0) %>%
+  filter(log10(actual) < 6 & log10(actual) >= 0) %>%
+  mutate(
+    expected = log10(expected),
+    actual = log10(actual),
+    bin = cut(expected, NUM_BINS)
+  ) %>%
+  arrange(bin) %>%
+  group_by(bin) %>%
+  summarize(
+    # Plot the point at the midpoint in each bin
+    bin_char = first(gsub("(?![,.])[[:punct:]]", "", as.character(bin), perl=TRUE)),
+    bin_min = as.numeric(unlist(strsplit(bin_char, ","))[1]),
+    bin_max = as.numeric(unlist(strsplit(bin_char, ","))[2]),
[…]

### 2020-09-26 paper/current/main.tex
Add the new airport figure into the paper, adjust extant results text accordingly

@@
 We fit the gravity model given by Eq.~\ref{eq:gravity_basic} (see Data and Methods) and computed the expected flux  $\hat{T}_{ij}$ using geographic distance and embedding distance as parameters.
-The embedding distance produces better predictions of actual flux than does geographic distance (Fig.~\ref{fig:gravity_performance}c--d), which also holds for the subsets of only domestic (Fig.~\ref{fig:supp:gravity_correlation}e--f) and only international mobility (Fig.~\ref{fig:supp:gravity_correlation}g--h).
+The embedding distance produces better predictions of actual flux than does geographic distance (Fig.~\ref{fig:supp:predict_emb_bymodel} and Fig.~\ref{fig:supp:predict_geo_bymodel}), which also holds for the subsets of only domestic and only international mobility.
 The embedding distance defined from the cosine distance between vectors also outperforms that defined from their dot product ($R^{2} = 0.34$, Fig.~\ref{fig:supp:gravity_dot}).
 The embedding distance also out-performs alternative ``diffusion-based'' network distance measures such as the personalized-page rank scores (see \SI) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-Our results unequivocally demonstrate that the embedding distance better captures actual mobility patterns than does geographic distance.
+Our results unequivocally demonstrate that the embedding distance better captures patterns of actual scientific mobility than does geographic distance.
 
@@
 	\caption{
-		\textbf{Embedding distance encodes functional distance and better predicts mobility.}
-		\textbf{a-b.} Embedding distance (cosine distance between organization vectors) better explains the expected flux between organization pairs than geographic distance.
+		\textbf{Embedding distance encodes functional distance and better predicts global scientific mobility and U.S flight itineraries.}
+		\textbf{a-b.} Embedding distance (cosine distance between organization vectors) better explains the expected flux of researchers between organization pairs than geographic distance.
 		The red line is the line of the best fit.
@@
 		``RMSE'' is the root-mean-squared error between the actual and predicted values.
-		\textbf{e-f.} Predictions made using model parameters learned from a subset of domestic (within-country) organization pairs.
-		Embedding distance outperforms those made for geographic distance.
-		\textbf{g-h.} Embedding distance also outperforms geographic distance when predicting flux using model parameters estimated from only international mobility (across-country organization pairs).
-		Predictions of domestic and international mobility are qualitatively similar whether predicted using models with only within- or across-country pairs (\textbf{e-h}), or all organizations pairs (Fig.
-\ref{fig:supp:gravity_prediction_subsets}).
+		\textbf{e-f.} Embedding distance better explains the expected flux of passengers between U.S. airports than does geographic distance. 
+		\textbf{g-h.} Predictions of flux between airport pairs made using embedding distance outperform those made using geographic distance. 
 	}
@@
 Trajectories are represented as the list of airport code and cover itinerary between 1993 to 2020.
-There are 30,776,0841 trajectories in total and the unique number of airports is 838.
+There are 307,760,841 trajectories in total and the unique number of airports is 838.
 

### 2020-09-30 paper/current/main.tex

@@
 However, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important, which calls for an alternative modeling framework for human mobility that take these factors into account~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional}.
-Here, using a massive dataset of scientific mobility, we demonstrate a neural embedding model can successfully encode nuanced relationships between locations into a vector-space ~\autocite{mikolov2013word2vec}, providing an effective functional distance that reflects the multi-faced structure of scientists' mobility and capturing cultural, linguistic relations, and even academic prestige at multiple levels of granularity, as well as implicit hierarchical structure.
+Here, using a massive dataset of scientific mobility and U.S.
+flight itineraries, we demonstrate a neural embedding model that successfully encodes nuanced relationships between locations into a vector-space ~\autocite{mikolov2013word2vec}, providing an effective functional distance that reflects the multi-faced structure of human mobility.
+Focusing on the case of scientific mobility between organizations, we show that the embedding captures cultural and linguistic relations, and even academic prestige at multiple levels of granularity, as well as implicit hierarchical structure.
 Furthermore, vector representations of organizations themselves also reveal insights into the landscape of global scientific mobility, such as a relationship between organizations' size and the norm of its vector that is consistent across most countries.
@@
 As a result, each organization is encoded into a single vector representation, and vectors relate to one another based on the likelihood of organizations appearing adjacent to one another in the same affiliation trajectory.
+
+This procedure is repeated for a dataset of U.S.
+flight itinerary data, in which trajectories were formed from the unique identifiers of Airports in more than 300 million passenger flight itineraries between 1993 and 2020.
+As with scientific mobility, we use a neural embedding model to learn a vector-space representation of 828 U.S. airports from passenger trajectories (see Data and Methods).
 
@@
 We fit the gravity model given by Eq.~\ref{eq:gravity_basic} (see Data and Methods) and computed the expected flux  $\hat{T}_{ij}$ using geographic distance and embedding distance as parameters.
-The embedding distance produces better predictions of actual flux than does geographic distance (Fig.~\ref{fig:supp:predict_emb_bymodel} and Fig.~\ref{fig:supp:predict_geo_bymodel}), which also holds for the subsets of only domestic and only international mobility.
+The embedding distance produces better predictions of actual flux than does geographic distance (Fig.~\ref{fig:gravity_performance}c-d), which also holds for the subsets of only domestic and only international mobility (Fig.~\ref{fig:supp:predict_emb_bymodel} and Fig.~\ref{fig:supp:predict_geo_bymodel}).
 The embedding distance defined from the cosine distance between vectors also outperforms that defined from their dot product ($R^{2} = 0.34$, Fig.~\ref{fig:supp:gravity_dot}).
@@
 Our results unequivocally demonstrate that the embedding distance better captures patterns of actual scientific mobility than does geographic distance.
+
+This approach is generalizable to other domains, such as learning a functional distance between airports. 
+We learned an embedding of U.S. airports following a similar procedure as scientific mobility, using trajectories formed by the flight itineraries of individual passengers (see Data and Methods).
+As with scientific mobility, the embedding approach better predicts real-world flows of airline passengers than does geographic distance. 
+Embedding distance explains more of the expected flux between U.S.
+airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}e) than does geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}f).
+Fitting the data to the gravity model given by Eq.~\ref{eq:gravity_basic} using each of embedding and geographic distance as parameters, and we find that predictions made using embedding distance out-performed those made using geographic distnace (Fig.~\ref{fig:gravity_performance}g-h).
+These results demonstrate that embeddings are applicable to a diverse range of mobility trajectory data.
 
@@
 		``RMSE'' is the root-mean-squared error between the actual and predicted values.
+		We show the generalizability of this approach by repeating it on a a dataset of U.S. flight itineraries. 
 		\textbf{e-f.} Embedding distance better explains the expected flux of passengers between U.S. airports than does geographic distance. 
@@
 
-The geometric space generated by the neural embedding methods sheds light on the multi-faceted relationships between organizations.
+We focus on the case of scientific mobility, and investigate how the geometric space generated by the neural embedding method sheds light on the multi-faceted relationships between organizations. 
 To explore the topological structure of the embedding, we use a standard dimensionality reduction method (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation (Fig.~\ref{fig:projection}a).
@@
 \subsection*{Data -US Airport Itinerary}
-We use US airport itinerary data from the Bureau of Transportation statistics provided by the United States Department of Transportation.
-Origin and Destination Survey (DB1B) is a 10\% sample of domestic airline tickets, including origin, destination, and other itinerary details.
-Trajectories are represented as the list of airport code and cover itinerary between 1993 to 2020.
-There are 307,760,841 trajectories in total and the unique number of airports is 838.
+We source US airport itinerary data from the Origin and Destination Survey (DB1B), provided by the Bureau of Transportation Statistics at the United States Department of Transportation. 
+DB1B is a sample of 10 percent of domestic airline tickets between 1993 and 2020, comprising 307,760,841 passenger itineraries between 828 U.S. airports. 
+Each itinerary is associated with an origin, destination, and associated metadata.
 

### 2020-09-30 paper/current/main.tex
abstract and introduction

@@
 \title{Learning a functional distance between organizations with unsupervised embeddings of scientific mobility}
-\title{Unsupervised embeddings of career trajectories capture the latent structure of global scientific mobility} %{{{
+\title{Unsupervised embeddings of trajectories captures the latent structure of mobility} %{{{
 \date{\today}
@@
 Historically, human mobility is strongly constrained by physical separation---geographical distance~\autocite{zipf1946gravity}.
-However, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important, which calls for an alternative modeling framework for human mobility that take these factors into account~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional}.
+However, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important, which calls for an alternative modeling framework for human mobility that takes these factors into account~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional}.
 Here, using a massive dataset of scientific mobility and U.S.
-flight itineraries, we demonstrate a neural embedding model that successfully encodes nuanced relationships between locations into a vector-space ~\autocite{mikolov2013word2vec}, providing an effective functional distance that reflects the multi-faced structure of human mobility.
-Focusing on the case of scientific mobility between organizations, we show that the embedding captures cultural and linguistic relations, and even academic prestige at multiple levels of granularity, as well as implicit hierarchical structure.
-Furthermore, vector representations of organizations themselves also reveal insights into the landscape of global scientific mobility, such as a relationship between organizations' size and the norm of its vector that is consistent across most countries.
-The ability to learn scalable, dense, and meaningful high-resolution vector representations of mobility directly derived from the data can open up a new avenue of studying human mobility.
+flight itineraries, we demonstrate that a neural embedding model can successfully encode nuanced relationships between locations into a vector-space ~\autocite{mikolov2013word2vec}, providing an effective functional distance that reflects the multi-faced structure of human mobility.
+Focusing on the case of scientific mobility, we show that the embedding captures cultural and linguistic relations at multiple levels of granularity, and even academic prestige.
+Furthermore, embedding vectors themselves also reveal insights on the role of the organization in the landscape of global scientific mobility universally.
+The ability to learn scalable, dense and meaningful high-resolution vector representations of mobility directly from the data can open up a new avenue of studying mobility across domains.
 
@@
 
-Yet, functional distances are often low-resolution, computed at the level of countries rather than regions, cities, or organizations, and have focused on only a single facets of mobility at a time, whereas real-world mobility is multi-faceted, influenced simultaneously by geography, language, culture, history, and economic opportunity.
+Yet, functional distances are often low-resolution, computed at the level of countries rather than regions, cities, or organizations, and have focused on only a single facet of mobility at a time, whereas real-world mobility is multi-faceted, influenced simultaneously by geography, language, culture, history, and economic opportunity.
 Low dimensional distance alone cannot represent the multitude of inter-related factors that derive mobility. 
-Networks offer a solution to representing the many dimensions of mobility, yet they only represent flows between discrete entities, and so cannot easily capture the relationships between entities themselves.
+Networks offer a solution to representing many dimensions of mobility, yet they only represent flows between discrete entities, and so cannot easily capture the relationships between entities themselves.
 Overcoming the complexity of mobility requires moving beyond simple functional distances and networks, to instead learning high-dimensional landscapes of mobility that incorporates the many facets of mobility into a single fine-grained and continuous representation.
 
-Here, we propose using a neural embedding model that draws from real-world mobility trajectories can encode the complex landscape of human mobility into a dense, continuous, and meaningful vector-space representation, from which not only a meaningful \textit{functional distance} between places but also relationship based on culture, language, and even prestige along with geographic relationship can be probed.
-We leverage a massive dataset that documents scientific mobility captured in bibliometric records.
-Scientific mobility, which is central driver of the globalized scientific enterprise~\autocite{czaika2018globalisation, altbach2004globalization, box2008competition} and strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}, is not only an important topic on science of science but also ideal for our study thanks to its richness and well-known structural properties such as the centrality of scientifically advanced countries and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career}.
+Here, we propose to apply a neural embedding framework to real-world mobility trajectories and demonstrate that it can encode the complex landscape of human mobility into a dense, continuous, and meaningful vector-space representation, from which not only a meaningful \textit{functional distance} between places but also relationships based on culture, language, and even prestige along with geographic relationship can be probed.
+We leverage two massive datasets: a dataset of scientific mobility captured in bibliometric records and a dataset of US airport itinerary records.
+In particular, we focus on scientific mobility throughout the paper due to its richness and importance.
+Scientific mobility, which is a central driver of the globalized scientific enterprise~\autocite{czaika2018globalisation, altbach2004globalization, box2008competition} and strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}, is not only an important topic on the science of science but also ideal for our study thanks to its richness and well-known structural properties such as the centrality of scientifically advanced countries and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career}.
 In spite of its importance, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, being further confounded by the diminishing role of geography in shaping the landscape of scientific mobility.

### 2020-10-01 paper/current/main.tex
revise introduction

@@
 Here, we propose to apply a neural embedding framework to real-world mobility trajectories and demonstrate that it can encode the complex landscape of human mobility into a dense, continuous, and meaningful vector-space representation, from which not only a meaningful \textit{functional distance} between places but also relationships based on culture, language, and even prestige along with geographic relationship can be probed.
-We leverage two massive datasets: a dataset of scientific mobility captured in bibliometric records and a dataset of US airport itinerary records.
+We leverage two massive datasets: a dataset of U.S.
+airport itinerary records and  scientific mobility captured in bibliometric records.
 In particular, we focus on scientific mobility throughout the paper due to its richness and importance.
@@
 
-In our approach, we use trajectories of more than three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
+For U.S.
+airport itinerary data, we use trajectories consists of the 828 unique identifier of U.S.
+airport in more than 300 million passenger flight itineraries between 1993 and 2020 from the Airline Origin and Destination Survey.
+Each trajectory includes origin, destination, and other itinerary details of passengers transported.
+ For scientific mobility, we use trajectories of more than three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
 Each trajectory is operationalized using a researcher's organizational affiliations derived from their publication histories indexed in a comprehensive bibliographic database (see Methods).
@@
 
-A vector-space embedding of organizations is learned by using affiliation trajectories as input to the standard skip-gram negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
+A vector-space embedding of locations (airports and organizations) is learned by using trajectories as input to the standard skip-gram negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
 This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
 They are also computationally efficient, robust to noise, and can encode relations between entities as geometric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.
-As a result, each organization is encoded into a single vector representation, and vectors relate to one another based on the likelihood of organizations appearing adjacent to one another in the same affiliation trajectory.
-
-This procedure is repeated for a dataset of U.S.
-flight itinerary data, in which trajectories were formed from the unique identifiers of Airports in more than 300 million passenger flight itineraries between 1993 and 2020.
-As with scientific mobility, we use a neural embedding model to learn a vector-space representation of 828 U.S. airports from passenger trajectories (see Data and Methods).
+As a result, each location is encoded into a single vector representation, and vectors relate to one another based on the likelihood of locations appearing adjacent to one another in the same trajectory.
 
@@
 
-To validate our approach, we evaluate the quality of result vector representations with their performance in predicting real-world mobility flows as parameters to the gravity model~\autocite{zipf1946gravity, barbosa2018human}.
-The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} that calculates the \textit{expected flux}, $\hat{T}_{ij}$, of people between locations (organizations) based on their populations and distance:
+To validate our approach, we evaluate the quality of vector representations with their performance in predicting real-world mobility flows using the gravity model framework~\autocite{zipf1946gravity, barbosa2018human}.
+The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} that models the \textit{expected flux}, $\hat{T}_{ij}$ between locations (organizations) based on their populations and distance:
 
@@
 \end{equation}
-where $m_{i}$ is the population of mobile and non-mobile authors who affiliated with institution $i$, $f(r_{ij})$ is a decay function with respect to distance between organizations, and $C$ is a constant estimated from data (see Data and Methods).
-$\hat{T}_{ij}$, which is often referred to as ``expected flux''~\autocite{simini2012universal}, is the expected frequency of the co-occurrence of organizations $i$ and $j$ in the trajectory of affiliations in the gravity model.
-The gravity model dictates that the expected flow, $\hat{T}_{ij}$, is symmetric (\ie $\hat{T}_{ij }= \hat{T}_{ji})$, is proportional to the organizations' sizes, $\hat{T}_{ij} \propto m_{i} m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
-We define the distance function in terms of either the geographic distance between organizations or their functional distance in the vector space, which is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.
+where $m_{i}$ is the population of locations $i$,  $f(r_{ij})$ is a decay function with respect to distance between locations, and $C$ is a constant estimated from data (see Data and Methods).
+For the U.S.
+airport itinerary, we use population $m_{i}$ as the total number of unique passenger on each airport and  for scientific mobility, we use the total number of mobile and non-mobile authors who affiliated with organization.
+$\hat{T}_{ij}$, which is often referred to as ``expected flux''~\autocite{simini2012universal}, is the expected frequency of the co-occurrence of location $i$ and $j$ in the trajectory in the gravity model.
+The gravity model dictates that the expected flow, $\hat{T}_{ij}$, is symmetric (\ie $\hat{T}_{ij }= \hat{T}_{ji})$, is proportional to the locations' population, $\hat{T}_{ij} \propto m_{i} m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+We define the distance function in terms of either the geographic distance between locations or their functional distance in the vector space, which is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.
 For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_emb_bymodel} and Fig.~\ref{fig:supp:predict_geo_bymodel}).
@@
 %
-\subsection*{Embeddings provide functional distance between organizations}
+\subsection*{Embeddings provide functional distance between locations}
 

### 2020-10-01 paper/current/main.tex
edit first main para

@@
         An author published five papers across five time periods, with only one affiliation listed in the byline of each paper.
-        A unique identifier is assigned to each each organization and they are assembled into an affiliation trajectory ordered by year of publication.
+        A unique identifier is assigned to each organization and they are assembled into an affiliation trajectory ordered by year of publication.
         \textbf{b.}
@@
 
-The embedding distance correlates with and can be used to predict real-wold mobility flows better than geographic distance. 
-The amount of variance in the expected flux explained by embedding distance ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) is more than twice that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
+We show that the embedding distance, compared with the geographical distances, predicts actual mobility flows. 
+For the case of scientific mobility, the amount of variance in the expected flux explained by the embedding distance ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) is more than twice that of the geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
 This pattern holds when considering the subset of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d).
-We fit the gravity model given by Eq.~\ref{eq:gravity_basic} (see Data and Methods) and computed the expected flux  $\hat{T}_{ij}$ using geographic distance and embedding distance as parameters.
-The embedding distance produces better predictions of actual flux than does geographic distance (Fig.~\ref{fig:gravity_performance}c-d), which also holds for the subsets of only domestic and only international mobility (Fig.~\ref{fig:supp:predict_emb_bymodel} and Fig.~\ref{fig:supp:predict_geo_bymodel}).
+We fit the gravity model given by Eq.~\ref{eq:gravity_basic} (see Data and Methods) and computed the expected flux  $\hat{T}_{ij}$ using the geographic distance and the embedding distance as parameters.
+The embedding distance produces better predictions of actual flux than does the geographic distance (Fig.~\ref{fig:gravity_performance}c-d), which also holds for the subsets of only domestic and only international mobility (Fig.~\ref{fig:supp:predict_emb_bymodel} and Fig.~\ref{fig:supp:predict_geo_bymodel}).
 The embedding distance defined from the cosine distance between vectors also outperforms that defined from their dot product ($R^{2} = 0.34$, Fig.~\ref{fig:supp:gravity_dot}).
 The embedding distance also out-performs alternative ``diffusion-based'' network distance measures such as the personalized-page rank scores (see \SI) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-Our results unequivocally demonstrate that the embedding distance better captures patterns of actual scientific mobility than does geographic distance.
-
-This approach is generalizable to other domains, such as learning a functional distance between airports. 
-We learned an embedding of U.S. airports following a similar procedure as scientific mobility, using trajectories formed by the flight itineraries of individual passengers (see Data and Methods).
-As with scientific mobility, the embedding approach better predicts real-world flows of airline passengers than does geographic distance. 
-Embedding distance explains more of the expected flux between U.S.
-airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}e) than does geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}f).
-Fitting the data to the gravity model given by Eq.~\ref{eq:gravity_basic} using each of embedding and geographic distance as parameters, and we find that predictions made using embedding distance out-performed those made using geographic distnace (Fig.~\ref{fig:gravity_performance}g-h).
-These results demonstrate that embeddings are applicable to a diverse range of mobility trajectory data.
+These results are consistent in the U.S.
+flight itinerary data.
+As with scientific mobility, the embedding approach better predicts actual flows of airline passengers than the geographic distance. 
+The embedding distance explains more of the expected flux between U.S.
+airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}e) than does the geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}f).
+By fitting the gravity model given by Eq.~\ref{eq:gravity_basic} using each of the embedding distance and the geographic distance as parameters, and we find that predictions with embedding distance out-performed those with the geographic distance (Fig.~\ref{fig:gravity_performance}g-h).
+Our results demonstrate that the embedding distance better captures patterns of actual mobility than does the geographic distance across datasets.
 

### 2020-10-01 paper/current/main.tex
edit second main para

@@
 
-We focus on the case of scientific mobility, and investigate how the geometric space generated by the neural embedding method sheds light on the multi-faceted relationships between organizations. 
-To explore the topological structure of the embedding, we use a standard dimensionality reduction method (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation (Fig.~\ref{fig:projection}a).
+From here, we focus on the case of scientific mobility leveraging its richness and investigate how the geometric space generated by the neural embedding method sheds light on the multi-faceted relationships between organizations.
+To explore the topological structure of the embedding, we use a topology-based dimensionality reduction method (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation (Fig.~\ref{fig:projection}a).
 By showing relationships between individual organizations, rather than aggregates such as nations or cities, this projection constitutes the largest and highest resolution ``map'' of scientific mobility to date.
@@
 The embedding space also allows us to \textit{zoom in} on subsets and re-project them using UMAP to reveal local relationships.
-For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries between Egypt and the Philippines that largely corresponds to geography, but with some exceptions along the cultural and religious spectrums;
-Iraq is nearer to Malaysia in southeast-Asian than closer and more religiously-similar Saudi Arabia and Qatar.
+For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries between Egypt and the Philippines that largely corresponds to geography, but with some exceptions along with the cultural and religious spectra;
+Malaysia is nearer to Middle Eastern countries than closer South Asia countries
 We also validate this finding quantitatively with the distance between nations in the embedding space $d$,  cosine distance between the centroids of organizations vectors belonging to that country. 
@@
 
-Linguistic and historical ties also effect the scientific mobility.
+Linguistic and historical ties also affect scientific mobility.
 We observe that Spanish-speaking post-colonial Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), rather than nearby Portuguese-speaking nations ($d = 0.34$ vs.
@@
 Mirroring the global pattern, organizations in the United States are largely arranged according to geography (Fig.~\ref{fig:projection}d).
-Re-projecting organizations located in Massachusetts (Fig.~\ref{fig:projection}e) reveals structure based on: urban centers (Boston vs.
+Re-projecting organizations located in Massachusetts (Fig.~\ref{fig:projection}e) reveals structure based on urban centers (Boston vs.
 Worcester), organization type (e.g., hospitals vs.
@@
 Fig.
-\ref{fig:clustering}b demonstrates that the region plays a major role at higher levels of the clustering process (low $r$), and language (family) explains the clustering more at the lower levels (high $r$).
-This suggests that the embedding space captures the hierarchical structure of mobility---at the highest level, geography defines the embedding space, followed by language.
+\ref{fig:clustering}b demonstrates that the regional relationship plays a major role at higher levels of the clustering process (low $r$), and language (family) explains the clustering more at the lower levels (high $r$).
+This suggests that the embedding space captures the hierarchical structure of mobility.
 

### 2020-10-01 paper/current/main.tex
edit final main para

@@
 		\textbf{Geography, then language, conditions international mobility.}
-		\textbf{a.} Hierarchically clustered similarity matrix of country vectors aggregated as the mean of all organization vectors within the country, excluding the United States and countries with less than or equal to 25 organizations.
+		\textbf{a.} Hierarchically clustered similarity matrix of country vectors aggregated as the mean of all organization vectors within the country, excluding the United States and countries with at most 25 organizations.
 		Color of matrix cells corresponds to the cosine similarity between country vectors.
 		Color of country names corresponds to their cluster.
-		Color of three cell rows separated from the matrix corresponds to, from left to right, the region of the country, the language family~\autocite{ethnologue}, and the individual language.
+		Color of three cell rows separated from the matrix corresponds to, from left to right, the region of the country, the language family~\autocite{ethnologue}, and the dominant language.
 		\textbf{b.}	Element-centric cluster similarity~\autocite{gates2019element} reveals the factors dictating hierarchical clustering.
 		Region better explains the grouping of country vectors at higher levels of the clustering.
-		Language family, and then the most widely-spoken language, better explain the grouping of countries at more fine-grained level.
+		Language family, and then the most widely-spoken language, better explain the fine-grained grouping of countries.
 	}
@@
 Prestige hierarchy is known to underpin the dynamics of scientific mobility, where researchers tend to move to similar or less prestigious organizations~\autocite{deville2014career, clauset2015hierarchy}.
-Does the embedding space, to which no prestige information is given, encode a prestige hierarchy?
+Could the embedding space, to which no explicit prestige information is given, encode a prestige hierarchy?
 We test this by exploiting the geometric properties of the embedding space with SemAxis~\autocite{an2018semaxis}.
 Here, we use SemAxis to operationalize the abstract notion of academic prestige, defining an axis in the embedding space where poles are defined using known high- and low-ranked universities.
-To define prestige of ranked U.S.
-ranked universities, we use the Times Ranking of World Universities (we also use research impact from the Leiden Rankings~\autocite{waltman2012leidenrankings}, see \SI);
+As an external measure of prestige, we use the Times Ranking of World Universities (we also use research impact from the Leiden Rankings~\autocite{waltman2012leidenrankings}, see \SI);
 the high-rank pole is defined as the average vector of the top five U.S.
@@
 census region) universities.
-We derive an embedding-based ranking for universities based on their nearness to the high-ranked pole.
+We derive an embedding-based ranking for universities based on the spectrum from the high-ranked to low-ranked poles (see Data and Methods).
 
@@
 The embedding-based ranking is strongly correlated with the Times ranking (Spearman's $\rho = 0.73$, Fig.~\ref{fig:semaxis}a).
-For reference, the embedding-based ranking achieves correlation with the Times ranking comparable to that between the Times ranking and the publication impact scores from the Leiden Ranking~\autocite{waltman2012leidenrankings}, a bibliometrically-based university ranking (Spearman's $\rho = 0.87$, Fig.~\ref{fig:semaxis}b).
+For reference, the correlation between the Times ranking and the publication impact scores from the Leiden Ranking~\autocite{waltman2012leidenrankings}, a bibliometrically-based university ranking is 0.87 (Spearman's $\rho$, Fig.~\ref{fig:semaxis}b).
 The correlation between the embedding-based ranking and the Times ranking is robust regardless of the number of organizations used to define the axes (Fig.
@@
 The correlation is also comparable to network-driven measures such as degree strength (sum of edge weights, Spearman's $\rho = 0.73$) and eigenvector centrality (Spearman's $\rho = 0.76$, see \SI). 
-The strongest outliers that were ranked more highly in the Times ranking than in the embedding-based ranking tend to be large state universities such as Arizona State University and  University of Florida.
-Those ranked higher in the embedding based ranking tend to be relatively-small universities near major urban areas such as the University of San Francisco and University of Maryland Baltimore County.
-This suggests that organizations in the embedding space are arranged according to prestige, even when the erepresentation is learned using data without explicit infomration on the direction of mobility (as in other formal models~\autocite{clauset2015hierarchy}), or prestige.
-
-The axes can further be visualized to examine the relative position of organizations along the prestige axis, and along a geographic axis between California and Massachusetts to aid visualization.
+The strongest outliers that were ranked more highly in the Times ranking than in the embedding-based ranking tend to be large state universities such as Arizona State University and the University of Florida.
+Those ranked higher in the embedding-based ranking tend to be relatively-small universities near major urban areas such as the University of San Francisco and the University of Maryland Baltimore County.
+In sum, our result suggests that the embedding space is capable of capturing information about academic prestige, even when the presentation is learned using data without explicit information on the direction of mobility (as in other formal models~\autocite{clauset2015hierarchy}), or prestige.
+
+The axes can further be visualized to examine the relative position of organizations along the prestige axis, and along a geographic axis between California and Massachusetts.
 Prestigious universities such as Columbia, Stanford, MIT, Harvard, and Rockefeller are positioned towards the top of the axis (Fig.~\ref{fig:semaxis}c).
 Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphasis on teaching, such as Barry University and California State University at Long Beach.
-By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations for which rankings are often low-resolution, incomplete, or entirely absent such as regional and liberal arts universities, seminaries, musical schools, and community colleges (Fig.~\ref{fig:semaxis}d), government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).
-Using SemAxis, we can even construct quantitative rankings for these types of organizations that correlate with their citation impact (Fig.~\ref{fig:supp:sector_semaxis_impact}).
+By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations for which rankings are often low-resolution, incomplete, or entirely absent, such as regional and liberal arts universities, seminaries, musical schools, community colleges (Fig.~\ref{fig:semaxis}d), government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).
+Their estimatee prestige has a significant correlation with their citation impact (Fig.~\ref{fig:supp:sector_semaxis_impact}).
 
@@
 We also find that the size (L2 norm) of the organization embedding vectors provides insights into the characteristics of organizations.
-Up to a point (around 1,000 researchers), the size of U.S.
-organization's vectors tends to increase proportionally to the number of researchers (both mobile and non-mobile) within that organization with published work;
+Up to a point (around 1,000 researchers), the size of U.S. organization's vectors tends to increase proportionally to the number of researchers (both mobile and non-mobile) with published work;
 these organizations are primarily teaching-focused institutions, agencies, and hospitals that either are not ranked or have a low ranking.
@@
 These organizations are primarily research-intensive and prestigious universities with higher rankings, research outputs, R\&D funding, and doctoral students (Fig.~\ref{fig:supp:length_vs_metaInfo}).
-A similar pattern has been observed in applications of neural embedding to natural language, in which the size of word vectors was found to represent the word's specificity.
+A similar pattern has been observed in applications of neural embedding to natural language, in which the size of word vectors was found to represent the word's \emph{specificity}.
 Roughly speaking, for word embeddings, the size of a vector indicates a specificity, i.e., the word associated with the vector frequently co-appears with particular context words\autocite{schakel2015measuring}.
@@
 The concavity emerges in part from the relationship between the size of the vector and the expected connectedness of the organization given its size (Fig.~\ref{fig:length}a, inset, $R^{2} = 0.17$).
-Large, prestigious, and well-funded research universities such as Princeton and Harvard have smaller vector norms because they appear in many different contexts compared to more teaching-focused organizations such as NY Medical College, and University of Michigan at Flint.
+Large, prestigious, and well-funded research universities such as Princeton and Harvard have smaller vector norms because they appear in many different contexts compared to more teaching-focused organizations such as NY Medical College, and the University of Michigan at Flint.
 Some universities, such as the University of Alaska at Fairbanks, have considerably small vectors, which may be a result of its remote location and unique circumstances.
 
-This find a similar convex-curve across many countries such as China, which closely mirrors that of the United States (Fig.~\ref{fig:length}b).
-Smaller but scientifically advanced countries such as Australia, and other large populous countries such as Brazil exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset), though their exact position and size varies.
+We report that this curve is almost universal. For instance, China closely mirrors that of the United States (Fig.~\ref{fig:length}b).
+Smaller but scientifically advanced countries such as Australia, and other populous countries such as Brazil exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset), though their exact position and size vary.
 Other nations exhibit different curves, such as Egypt which has an``S''-shaped curve, meaning that their largest organizations are not as well connected as other countries' largest organizations. 
-Similar patterns can be found across many of the 30 of the countries with the most total researchers (Fig.~\ref{fig:concave30}), however we can only speculate on what their variations mean (see \SI).
-Neural embeddings encode a relationship between organization size and vector length that is universal across countries but with potentially meaningful nuances, helping the embedding to capture the landscape of global scientific mobility.
+Similar patterns can be found across many of the 30 of the countries with the most total researchers (Fig.~\ref{fig:concave30}), however, we can only speculate on what their variations mean (see \SI).
+See Supporting Information for more discussion.
 

### 2020-10-01 paper/current/main.tex
conclusion

@@
 		\textbf{Embedding captures latent geography and prestige hierarchy.}
-		\textbf{a.} Comparison between the ranking of organizations by their rank in the Times ranking and the embedding rank derived using SemAxis pointing from the top five to geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S.
-Universities.
+		\textbf{a.} Comparison between the ranking of organizations in the Times ranking and the embedding ranking derived using SemAxis.
 		Un-filled points are those top and bottom five universities used span the axis.
 	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the embedding and Times ranking is $\rho = 0.73$ ($n = 145$), which increases when more top-and-bottom ranked universities are included (Fig.~\ref{fig:supp:semaxis_compare}).
-	  	\textbf{b.} Times ranking is correlated with Leiden Ranking of U.S. universities with Spearman's $\rho = 0.87$
+	  	\textbf{b.} Times ranking is correlated with Leiden Ranking of U.S. universities with Spearman's $\rho = 0.87$.
 		\textbf{c-f.} Illustration of SemAxis projection along two axes;  \textit{latent geographical axis}, from California to Massachusetts (left to right) and the \textit{prestige axis}.
@@
 		Color indicates the rank of the university from the Times ranking, with 1 being the highest ranked university.
-		Uncolored points are universities not listed on a Times ranking.
-		A convex-shape emerges, wherein larger universities tend to be more distant from the origin (large L2 norm); however, the more prestigious universities tend to have a small L2 norm.
+		Uncolored points are universities not listed on the Times ranking.
+		A convex-shape emerges, wherein larger universities tend to be more distant from the origin (large L2 norm); however, the more prestigious universities tend to have smaller L2 norms.
 		The L2 norm is correlated weakly with the ratio of organizations' number of connections (non-zero flows) to the number of researchers ($R^{2} = 0.17$, \textbf{inset}).
 		The red line is the line of the best fit, and 99\% confidence intervals are shown, though are too small to be visible.
-		\textbf{b.} We find a simliar convex-curve pattern across many countries such as the United States, China, Australia, Brazil, and others (\textit{inset}, and Fig.~\ref{fig:concave30}). 
-		Some countries exhibit variants of this pattern, such as Egypt 's ``S''-shaped curve (\textbf{inset}).
+		\textbf{b.} We find a similar convex-curve pattern across many countries such as the United States, China, Australia, Brazil, and others (\textit{inset}, and Fig.~\ref{fig:concave30}). 
+		Some countries exhibit variants of this pattern, such as Egypt's case with missing the right side of the curve.
 		The loess regression lines are shown for each selected country, and for the aggregate of remaining countries, with 99\% confidence intervals.
@@
 
-Neural embeddings offer a novel, data-driven solution for learning an effective and robust functional distance between places based on trajectory data, encoding the complex and multi-faceted nature of mobility.
+Neural embedding approach offers a novel, data-driven solution for learning an effective and robust representation of locations based on trajectory data, encoding the complex and multi-faceted nature of mobility.
 We demonstrated how the embedding space encodes various aspects of scientific mobility, such as the global and regional geography, shared languages, and the hierarchy of organizational prestige, even without explicit information on these factors.
@@
 As we have shown, the embedding space allows the visualization of the complex structure of scientific mobility at high resolution across multiple scales, providing a large and detailed map of the landscape of global scientific mobility.
-SemAxis~\autocite{an2018semaxis} allows us to quantify abstract notions in mobility such as academic prestige, and can also be generalized to other abstract axes.
-Investigation of the structure of the embedding space, such as the vector norm, reveals unique and universal patterns based on organization's size and their vector norm that could be leveraged in future studies of mobility.
-Neural embedding opens the door for new approaches to represent and study scientific mobility, and also mobility more generally.
-
-In spite of its promise, this approach and analysis has several limitations.
-First, the current \textit{skip-gram word2vec} model can not encode directional information, meaning that embedding will be less effective at capturing mobility for which directionality is critical.
+Embedding also allows us to quantify abstract notions in mobility such as academic prestige, and can also be generalized to other abstract axes.
+Investigation of the structure of the embedding space, such as the vector norm, reveals unique and universal patterns based on the organization's size and their vector norm that could be leveraged in future studies of mobility.
+
+In spite of its promise, our study has several limitations.
+First, the current skip-gram word2vec model cannot encode directional information, meaning that embedding will be less effective at capturing mobility for which directionality is critical.
 Second, the neural embedding approach is most useful in cases of mobility between discrete geographic units such as between countries, cities, and businesses; this approach is less useful in the case of mobility between locations represented using geographic coordinates, such as in the modeling of animal movements.
@@
 Reliance on bibliometric metadata means that we capture only long-term mobility such as migration, rather than the array or more frequent short-term mobility such as conference travel and temporary visits.
-The kinds of mobility we do capture---migration and co-affiliation---are treated identically by our model although they are qualitatively different.
+The kinds of mobility we do capture---migration, and co-affiliation---are ,although they are qualitatively different, treated identically by our model.
 Also, our data might further suffer from survivorship bias: researchers at prestigious organizations tend to have more publications, leading to these organizations appearing more frequently in affiliation trajectories.
@@
 Unprecedented health crises such as the COVID-19 pandemic threaten to bring drastic global changes to travel and migration by tightening borders and halting travel.
-With the changing paradigm of global mobility we need now, more than ever, new tools and approaches to capture and understand human mobility in order to inform sensible, effective, sustainable, and humane policies.
+With the changing paradigm of global mobility, we need now, more than ever, new tools and approaches to capture and understand human mobility in order to inform sensible, effective, sustainable, and humane policies.
 

### 2020-10-01 paper/current/main.tex
data and method

@@
 
-Neural embedding approach offers a novel, data-driven solution for learning an effective and robust representation of locations based on trajectory data, encoding the complex and multi-faceted nature of mobility.
+Neural embedding approaches offer a novel, data-driven solution for learning an effective and robust representation of locations based on trajectory data, encoding the complex and multi-faceted nature of mobility.
 We demonstrated how the embedding space encodes various aspects of scientific mobility, such as the global and regional geography, shared languages, and the hierarchy of organizational prestige, even without explicit information on these factors.
@@
 
-\subsection*{Data - Scientific mobility}
+\subsection*{Scientific mobility data}
 %% Main dataset
@@
 
-\subsection*{Data -US Airport Itinerary}
-We source US airport itinerary data from the Origin and Destination Survey (DB1B), provided by the Bureau of Transportation Statistics at the United States Department of Transportation. 
+\subsection*{U.S. Airport Itinerary data}
+We source U.S. airport itinerary data from the Origin and Destination Survey (DB1B), provided by the Bureau of Transportation Statistics at the United States Department of Transportation. 
 DB1B is a sample of 10 percent of domestic airline tickets between 1993 and 2020, comprising 307,760,841 passenger itineraries between 828 U.S. airports. 
@@
 %% Mobility sentences
-We embed co-affiliation trajectories by treating them analogously to sentences and organizations analogously to words. 
-The trajectories of mobile authors were converted to ``affiliation trajectories'' by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:methods:mobility_sentence}a.
+We embed trajectories by treating them analogously to sentences and locations analogously to words. 
+For U.S. airport itinerary, trajectories are formed by the flight itineraries of individual passenger and each location is unique airport code.
+For scientific mobility, the trajectories of mobile authors were converted to ``affiliation trajectories'' by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:methods:mobility_sentence}a.
 In more complex cases, such as listing multiple affiliations on the same paper or publishing with different affiliations on multiple publications in the same year, the order is randomized within that year, as shown in  Fig.~\ref{fig:methods:mobility_sentence}b.
@@
 %% word2vec
-These affiliation trajectories are used as input to the standard skip-gram negative sampling word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec}.
+These trajectories are used as input to the standard skip-gram negative sampling word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec}.
 \textit{word2vec} constructs dense and continuous vector representations of words and phrases, in which distance between words corresponds to a notion of semantic distance.
-By embedding affiliation trajectories, we aim to learn a dense vector for every organization where the distance between vectors relates to the tendency for two organizations to occur in similar contexts.
-Suppose an affiliation trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), where $a_{t}$ is the $t$th organization in the trajectory.
-An organization, $a_{t}$, is considered to have context organizations, $a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}$, that appear in the window surrounding $a_t$ up to a time lag of $w$, where $w$ is the window size parameter truncated at $t - w \geq 0$ and $t + w \leq T$.
+By embedding trajectories, we aim to learn a dense vector for every locations where the distance between vectors relates to the tendency for two locations to occur in similar contexts.
+Suppose an trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), where $a_{t}$ is the $t$th location in the trajectory.
+An location, $a_{t}$, is considered to have context locations, $a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}$, that appear in the window surrounding $a_t$ up to a time lag of $w$, where $w$ is the window size parameter truncated at $t - w \geq 0$ and $t + w \leq T$.
 Then, the model learns probability $p(a_{t + \tau} \vert a_{t})$, where $-w\leq \tau\leq w$ and $\tau \neq 0$,  by maximizing its log likelihood given by
@@
 \end{equation}
-where $a_{t+\tau} = j \vert a_{t+\tau} = i$, and $N$ is the number of unique organizations represented in the data, and $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively.
-The in-vector and out-vectors are different kinds of vector representations for organizations.
+where $a_{t+\tau} = j \vert a_{t+\tau} = i$, and $N$ is the number of unique locations represented in the data, and $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively.
+The in-vector and out-vectors are different kinds of vector representations for locations.
 We only use the in-vector, $v$, because the in-vector is more widely used and often superiors to the out-vector in link prediction benchmarks~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}.
@@
 %% Word2vec parameters and training procedure
-We used the \textit{word2vec}  implenetation in the python package \texttt{gensim}. 
+We used the \textit{word2vec}  implementation in the python package \texttt{gensim}. 
 The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{\min}$, initial learning rate $\alpha$, and the number of iterations.
-For main results, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between organizations, though results were robust across different settings (Fig.~\ref{fig:supp:hyperparams}).
-To mitigate the effect of less common organizations, we set $f_{\min} = 50$, limiting to organizations appearing at least 50 times across the training trajectories;
-6,580 unique organizations appear in the resulting embedding.
-We set $\alpha$ to its default value of 0.025 and iterate five times over all training affiliation trajectories.
+For main results, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig.~\ref{fig:supp:hyperparams}).
+To mitigate the effect of less common locations, we set $f_{\min} = 50$, limiting to locations appearing at least 50 times across the training trajectories;
+744 unique airport for U.S. airport itinerary  and 6,580 unique organizations for scientific mobility appear in the resulting embedding.
+We set $\alpha$ to its default value of 0.025 and iterate five times over all training trajectories.
 
@@
 %% Distance calculations
-We calculate $T_{ij}$ as the number of trajectories in which two organizations $i$ and $j$ appear together.
-For example, $T_{ij} = 10$ indicates that ten authors were affiliated with both organization $i$ and $j$ between 2008 and 2019, as evidenced from their publications.
-Organizations appearing multiple times in an affiliation trajectory are only counted once. 
-In affiliation trajectories where an organization appears multiple times, 
-We note that $T_{ij} = T_{ji}$.
-
-We calculate two forms of the distance between organizations.
-The geographic distance, $g_{ij}$, is the pairwise geographic distance between organizations.
-Geographic distance is calculated as the great circle distance, in kilometers, between pairs of organizations.
+We calculate $T_{ij}$ as the total number of co-occurrence between two locations $i$ and $j$ across the data-set.
+For case in scientific mobility, $T_{ij} = 10$ indicates that the number of co-occurrence between both organization $i$ and $j$ between 2008 and 2019 is 10, as evidenced from their publications.
+We treat $T_{ij} = T_{ji}$ because directional information is not informative.
+
+We calculate two forms of the distance between locations.
+The geographic distance, $g_{ij}$, is the pairwise geographic distance between locations.
+Geographic distance is calculated as the great circle distance, in kilometers, between pairs of locations.
 When less than one kilometer, a distance of 1 km is imputed.
 The embedding distance with the cosine distance, $d_{ij}$, is calculated as $d_{ij} = 1 - \frac{\bm{v}_{i} \cdot \bm{v}_{j}}{\lVert \bm{v}_{i} \rVert \lVert \bm{v}_{j} \rVert}$,
-where $v_i$ and $v_j$ are the embedding vectors for organizations $i$ and $j$, respectively.
+where $v_i$ and $v_j$ are the embedding vectors for locations $i$ and $j$, respectively.
 Note that $d_{ij}$ is not a formal metric because it does not satisfy the triangle inequality.
@@
 
-We model co-occurences $T_{ij}$ for organizations $i$, and $j$, often referred to as flux, using the gravity law of mobility~\autocite{zipf1946gravity}.
+We model co-occurences $T_{ij}$ for locations $i$, and $j$, often referred to as flux, using the gravity law of mobility~\autocite{zipf1946gravity}.
 The gravity law of mobility loosely derives from the physical law of gravity, in which the attraction between two objects is a function of their mass and the distance between them.
@@
 \end{equation}
-where $m_{i}$ and $m_{j}$ are the organization masses, or the yearly-average count of unique authors, both mobile and non-mobile, affiliated with each organization during the time window, and $f(r_{ij})$ is a decay function of distance $r_{ij}$ between organizations $i$ and $j$.
-There are two popular forms of the $f(r_{ij})$:
+where $m_{i}$ and $m_{j}$ are the population of locations which is the total number of passenger on each airport for U.S.
+airport itinerary and the yearly-average count of unique authors, both mobile and non-mobile, affiliated with each organization for scientific mobility.
+$f(r_{ij})$ is a decay function of distance $r_{ij}$ between locations $i$ and $j$.
+There are two popular forms for the $f(r_{ij})$:
 one is a power law function in the form $f(r_{ij})= r^{-\alpha}_{ij} \ (\alpha > 0$, and the other and the another one is an exponential function in the form $f(r_{ij}) = e^{-\beta r_{ij}} \ (\beta > 0)$ \autocite{chen2015distance}.
@@
 
-We consider separate variants of $f(r_{ij})$ for geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$, report the best-fit model of each distance.
-For geographic distance, we use the power-law function of the gravity law, $f(g_{ij})= g^{-\alpha}_{ij}$ (Eq.~\ref{eq:linear_flux_geo}).
-For embedding distance, we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$ (Eq.~\ref{eq:linear_flux_emb}).
+We consider separate variants of $f(r_{ij})$ for the geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$, report the best-fit model of each distance.
+For the geographic distance, we use the power-law function of the gravity law, $f(g_{ij})= g^{-\alpha}_{ij}$ (Eq.~\ref{eq:linear_flux_geo}).
+For the embedding distance, we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$ (Eq.~\ref{eq:linear_flux_emb}).
 
@@
 \end{equation}
-where $T_{ij}$ is the real flux from the data. 
-The gravity law of mobility is sensitive to $T_{ij} = 0$, or zero movement between organizations.
-In our dataset, non-zero flows account for only 4.2 \% of all possible pairs of the 6,580 organizations represented in the embedding.
+where $T_{ij}$ is the actual flow from the data. 
+The gravity law of mobility is sensitive to $T_{ij} = 0$, or zero movement  between locations.
+In our dataset, non-zero flows account for only 4.2 \% of all possible pairs of the 6,580 organizations for scientific mobility, while 76.4\% of all possible pairs of the 744 airports for U.S.
+airport Itinerary.
 This value is comparable to other common applications of the gravity law, such as to phone calls, commuting, and migration \autocite{simini2012universal}.
@@
 \subsection*{SemAxis}
-SemAxis~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these terms to a corresponding concept.
+SemAxis~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} and similar studies demonstrated that ``semantic axes'' can be found from an embedding space by defining the ``poles'' and the latent semantic relationship along semantic axis can be extracted with the simple arithmetic.
 Each axis is an antonym pair defined for each specific use case.

### 2020-10-01 paper/current/main.tex
abstract edits

@@
 \begin{document} %{{{
-\title{Learning a functional distance between organizations with unsupervised embeddings of scientific mobility}
-\title{Unsupervised embeddings of trajectories captures the latent structure of mobility} %{{{
+\title{Unsupervised embedding of trajectories captures the latent structure of mobility} %{{{
 \date{\today}
@@
 Here, using a massive dataset of scientific mobility and U.S.
-flight itineraries, we demonstrate that a neural embedding model can successfully encode nuanced relationships between locations into a vector-space ~\autocite{mikolov2013word2vec}, providing an effective functional distance that reflects the multi-faced structure of human mobility.
-Focusing on the case of scientific mobility, we show that the embedding captures cultural and linguistic relations at multiple levels of granularity, and even academic prestige.
-Furthermore, embedding vectors themselves also reveal insights on the role of the organization in the landscape of global scientific mobility universally.
+flight itineraries, we demonstrate that a neural embedding model can successfully encode nuanced relationships between locations into a vector-space~\autocite{mikolov2013word2vec}, providing an effective functional distance that reflects the multi-faced structure of human mobility.
+Focusing on the case of scientific mobility, we show that embeddings of scientific organizations captures cultural and linguistic relations at multiple levels of granularity, and even academic prestige.
+Furthermore, the embedding vectors themselves reveal universal relationships between organizational characteristics, and their place in the global landscape of scientific mobility. 
 The ability to learn scalable, dense and meaningful high-resolution vector representations of mobility directly from the data can open up a new avenue of studying mobility across domains.

### 2020-10-01 paper/current/main.tex
intro edits

@@
 
-Here, we propose to apply a neural embedding framework to real-world mobility trajectories and demonstrate that it can encode the complex landscape of human mobility into a dense, continuous, and meaningful vector-space representation, from which not only a meaningful \textit{functional distance} between places but also relationships based on culture, language, and even prestige along with geographic relationship can be probed.
-We leverage two massive datasets: a dataset of U.S.
-airport itinerary records and  scientific mobility captured in bibliometric records.
+Here, we propose to apply a neural embedding framework to real-world mobility trajectories and demonstrate that it can encode the complex landscape of human mobility into a dense, continuous, and meaningful vector-space representation, from which we can not only derive a meaningful \textit{functional distance} between places but also probe relationships based on culture, language, and even prestige along with geographic relationship.
+We leverage two massive datasets: a dataset of U.S. passenger flight itinerary records, and a dataset of scientific mobility between organizations captured in bibliometric records. 
 In particular, we focus on scientific mobility throughout the paper due to its richness and importance.
@@
 
-For U.S.
-airport itinerary data, we use trajectories consists of the 828 unique identifier of U.S.
-airport in more than 300 million passenger flight itineraries between 1993 and 2020 from the Airline Origin and Destination Survey.
-Each trajectory includes origin, destination, and other itinerary details of passengers transported.
- For scientific mobility, we use trajectories of more than three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
+The flight itinerary data, from the Airline Origin and Destination Survey, consists of records of more than 300 million itineraries between 1993 and 2020 documenting domestic flights between 828 airports in the United States.
+A trajectory is constructed for each passenger flight itinerary, forming an ordered sequence of unique identifiers of the origin and destination airports. 
+Although more complex, trajectories of scientific mobility are constructed in a similar fashion. 
+Trajectories are constructed using more than three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
 Each trajectory is operationalized using a researcher's organizational affiliations derived from their publication histories indexed in a comprehensive bibliographic database (see Methods).
@@
 To validate our approach, we evaluate the quality of vector representations with their performance in predicting real-world mobility flows using the gravity model framework~\autocite{zipf1946gravity, barbosa2018human}.
-The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} that models the \textit{expected flux}, $\hat{T}_{ij}$ between locations (organizations) based on their populations and distance:
+The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} that models the \textit{expected flux}, $\hat{T}_{ij}$ between locations (airports and organizations) based on their populations and distance:
 
@@
 \end{equation}
+
 where $m_{i}$ is the population of locations $i$,  $f(r_{ij})$ is a decay function with respect to distance between locations, and $C$ is a constant estimated from data (see Data and Methods). 
-For the U.S.
-airport itinerary, we use population $m_{i}$ as the total number of unique passenger on each airport and  for scientific mobility, we use the total number of mobile and non-mobile authors who affiliated with organization.
+For the flight itinerary data, we use population $m_{i}$ as the total number of unique passenger on each airport, and for scientific mobility, we use the mean annual number of of unique mobile and non-mobile authors who affiliated with each organization.
 $\hat{T}_{ij}$, which is often referred to as ``expected flux''~\autocite{simini2012universal}, is the expected frequency of the co-occurrence of location $i$ and $j$ in the trajectory in the gravity model.
-The gravity model dictates that the expected flow, $\hat{T}_{ij}$, is symmetric (\ie $\hat{T}_{ij }= \hat{T}_{ji})$, is proportional to the locations' population, $\hat{T}_{ij} \propto m_{i} m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+The gravity model dictates that the expected flow, $\hat{T}_{ij}$, is symmetric (\ie $\hat{T}_{ij }= \hat{T}_{ji})$), is proportional to the locations' population, $\hat{T}_{ij} \propto m_{i} m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
 We define the distance function in terms of either the geographic distance between locations or their functional distance in the vector space, which is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.

### 2020-10-01 paper/current/main.tex
performance results

@@
 
-We show that the embedding distance, compared with the geographical distances, predicts actual mobility flows. 
-For the case of scientific mobility, the amount of variance in the expected flux explained by the embedding distance ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) is more than twice that of the geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
+We show that the embedding distance, compared with the geographical distance, predicts actual mobility flows. 
+In the case flight itineraries, the embedding distance explains more than twice the expected flux between airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}a) than does geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
+We fit the gravity model given by Eq.~\ref{eq:gravity_basic} (see Data and Methods) and computed the expected flux  $\hat{T}_{ij}$ using the geographic distance and the embedding distance as parameters.
+The embedding distance produces better predictions of actual flux between airports than does the geographic distance (Fig.~\ref{fig:gravity_performance}c-d).
+These results are consistent in the case of scientific mobility. 
+the amount of variance in the expected flux explained by the embedding distance ($R^{2} = 0.48$, Fig.~\ref{fig:gravity_performance}e) is again more than double that explained by the geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}f).
 This pattern holds when considering the subset of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d).
-We fit the gravity model given by Eq.~\ref{eq:gravity_basic} (see Data and Methods) and computed the expected flux  $\hat{T}_{ij}$ using the geographic distance and the embedding distance as parameters.
-The embedding distance produces better predictions of actual flux than does the geographic distance (Fig.~\ref{fig:gravity_performance}c-d), which also holds for the subsets of only domestic and only international mobility (Fig.~\ref{fig:supp:predict_emb_bymodel} and Fig.~\ref{fig:supp:predict_geo_bymodel}).
-The embedding distance defined from the cosine distance between vectors also outperforms that defined from their dot product ($R^{2} = 0.34$, Fig.~\ref{fig:supp:gravity_dot}).
+As with flight itineraries, we fit the gravity model on the scientific mobility data using the gravity model.
+Predictions made using the embedding distance outperform those made using the geographic distance (Fig.~\ref{fig:gravity_performance}g-h), which also holds for the subsets of only domestic and only international mobility (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}).
+For scientific mobility, the embedding distance defined from the cosine distance between vectors also outperforms that defined from their dot product ($R^{2} = 0.34$, Fig.~\ref{fig:supp:gravity_dot}).
 The embedding distance also out-performs alternative ``diffusion-based'' network distance measures such as the personalized-page rank scores (see \SI) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-These results are consistent in the U.S.
-flight itinerary data.
-As with scientific mobility, the embedding approach better predicts actual flows of airline passengers than the geographic distance. 
-The embedding distance explains more of the expected flux between U.S.
-airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}e) than does the geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}f).
-By fitting the gravity model given by Eq.~\ref{eq:gravity_basic} using each of the embedding distance and the geographic distance as parameters, and we find that predictions with embedding distance out-performed those with the geographic distance (Fig.~\ref{fig:gravity_performance}g-h).
 Our results demonstrate that the embedding distance better captures patterns of actual mobility than does the geographic distance across datasets.
@@
 	\caption{
-		\textbf{Embedding distance encodes functional distance and better predicts global scientific mobility and U.S flight itineraries.}
-		\textbf{a-b.} Embedding distance (cosine distance between organization vectors) better explains the expected flux of researchers between organization pairs than geographic distance.
+		\textbf{Embedding distance encodes functional distance and better predicts U.S flights and global scientific mobility.}
+		\textbf{a-b.} Embedding distance (cosine distance between organization vectors) better explains the expected flux of passengers between U.S. airports than does geographic distance. 
 		The red line is the line of the best fit.
@@
 		The lightness of each hex bin indicates the frequency of organization pairs within it.
-		\textbf{c-d.} Predictions of flux between organization pairs made using embedding distance outperform those made using geographic distance.
+		\textbf{c-d.} Predictions of flux between airport pairs made using embedding distance outperform those made using geographic distance. 
 		Boxplots show distribution of actual flux for binned values of predicted flux.
@@
 		``RMSE'' is the root-mean-squared error between the actual and predicted values.
-		We show the generalizability of this approach by repeating it on a a dataset of U.S. flight itineraries. 
-		\textbf{e-f.} Embedding distance better explains the expected flux of passengers between U.S. airports than does geographic distance. 
-		\textbf{g-h.} Predictions of flux between airport pairs made using embedding distance outperform those made using geographic distance. 
+		Results are consistent in the case of scientific mobility. 
+		\textbf{e-f.} Embedding distance better explains the expected flux of researchers between organization pairs than geographic distance.
+		\textbf{g-h.} Predictions of flux between organization pairs made using embedding distance outperform those made using geographic distance.
 	}

### 2020-10-01 paper/current/main.tex
projection edits

@@
 
-From here, we focus on the case of scientific mobility leveraging its richness and investigate how the geometric space generated by the neural embedding method sheds light on the multi-faceted relationships between organizations.
-To explore the topological structure of the embedding, we use a topology-based dimensionality reduction method (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation (Fig.~\ref{fig:projection}a).
+From here, we focus on the case of scientific mobility, leveraging its richness to investigate how the geometric space generated by the neural embedding method sheds light on the multi-faceted relationships between organizations.
+To explore the topological structure of the embedding, we use a topology-based dimensionality reduction method (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation of the embedding space (Fig.~\ref{fig:projection}a).
 By showing relationships between individual organizations, rather than aggregates such as nations or cities, this projection constitutes the largest and highest resolution ``map'' of scientific mobility to date.
@@
 For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries between Egypt and the Philippines that largely corresponds to geography, but with some exceptions along with the cultural and religious spectra;
-Malaysia is nearer to Middle Eastern countries than closer South Asia countries
+Malaysia, with its official religion of Islam, is nearer to Middle Eastern countries in the embedding space than many geographically-closer but South Asia countries.
 We also validate this finding quantitatively with the distance between nations in the embedding space $d$,  cosine distance between the centroids of organizations vectors belonging to that country. 
-Then, Malaysia ($d=0.29$) is closer to Iraq more than Arabia ($d=0.50$) and Qatar ($d=0.51$).
+Then, in the embedding space, Malaysia is nearer to many Islamic countries such as Iraq ($d = 0.29$), Pakistan ($d = 0.31$), and Saudi Arabia ($d = 0.41$)  than neighboring but Buddhist Thailand ($d = 0.43$) and predominantly-secular Vietnam ($d = 0.48$).
 
@@
 Fig.
-\ref{fig:clustering}b demonstrates that the regional relationship plays a major role at higher levels of the clustering process (low $r$), and language (family) explains the clustering more at the lower levels (high $r$).
+\ref{fig:clustering}b demonstrates that regional relationships play a major role at higher levels of the clustering process (low $r$), and language (family) explains the clustering more at the lower levels (high $r$).
 This suggests that the embedding space captures the hierarchical structure of mobility.
@@
 		Color of country names corresponds to their cluster.
-		Color of three cell rows separated from the matrix corresponds to, from left to right, the region of the country, the language family~\autocite{ethnologue}, and the dominant language.
+		Color of three cell columns separated from the matrix corresponds to, from left to right, the region of the country, the language family~\autocite{ethnologue}, and the dominant language.
 		\textbf{b.}	Element-centric cluster similarity~\autocite{gates2019element} reveals the factors dictating hierarchical clustering.

### 2020-10-01 paper/current/main.tex
hierarchy result edits

@@
 The strongest outliers that were ranked more highly in the Times ranking than in the embedding-based ranking tend to be large state universities such as Arizona State University and the University of Florida.
-Those ranked higher in the embedding-based ranking tend to be relatively-small universities near major urban areas such as the University of San Francisco and the University of Maryland Baltimore County.
-In sum, our result suggests that the embedding space is capable of capturing information about academic prestige, even when the presentation is learned using data without explicit information on the direction of mobility (as in other formal models~\autocite{clauset2015hierarchy}), or prestige.
+Those ranked higher in the embedding-based ranking tend to be relatively-small universities near major urban areas such as the University of San Francisco and the University of Maryland Baltimore County, possibly reflecting exchanges of scholars with nearby high-ranked institutions at these locations.
+In sum, our result suggests that the embedding space is capable of capturing information about academic prestige, even when the representation is learned using data without explicit information on the direction of mobility (as in other formal models~\autocite{clauset2015hierarchy}), or prestige.
 
@@
 By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations for which rankings are often low-resolution, incomplete, or entirely absent, such as regional and liberal arts universities, seminaries, musical schools, community colleges (Fig.~\ref{fig:semaxis}d), government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).
-Their estimatee prestige has a significant correlation with their citation impact (Fig.~\ref{fig:supp:sector_semaxis_impact}).
+Their estimated prestige has a significant correlation with their citation impact (Fig.~\ref{fig:supp:sector_semaxis_impact}).
 
@@
 
-We report that this curve is almost universal. For instance, China closely mirrors that of the United States (Fig.~\ref{fig:length}b).
-Smaller but scientifically advanced countries such as Australia, and other populous countries such as Brazil exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset), though their exact position and size vary.
+We report that this curve is almost universal across many countries. 
+For instance, China's curve closely mirrors that of the United States (Fig.~\ref{fig:length}b).
+Smaller but scientifically advanced countries such as Australia, and other populous countries such as Brazil also exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset), though their exact position and size vary.
 Other nations exhibit different curves, such as Egypt which has an``S''-shaped curve, meaning that their largest organizations are not as well connected as other countries' largest organizations. 
-Similar patterns can be found across many of the 30 of the countries with the most total researchers (Fig.~\ref{fig:concave30}), however, we can only speculate on what their variations mean (see \SI).
-See Supporting Information for more discussion.
+Similar patterns can be found across many of the 30 of the countries with the most total researchers (Fig.~\ref{fig:concave30}), however, we can only speculate on what their variations mean (see \SI for more discussion).
 
@@
 		\textbf{b.} We find a similar convex-curve pattern across many countries such as the United States, China, Australia, Brazil, and others (\textit{inset}, and Fig.~\ref{fig:concave30}). 
-		Some countries exhibit variants of this pattern, such as Egypt's case with missing the right side of the curve.
+		Some countries exhibit variants of this pattern, such as Egypt, which is missing the right side of the curve.
 		The loess regression lines are shown for each selected country, and for the aggregate of remaining countries, with 99\% confidence intervals.

### 2020-10-01 paper/current/main.tex
conclusion edits

@@
 Neural embedding approaches offer a novel, data-driven solution for learning an effective and robust representation of locations based on trajectory data, encoding the complex and multi-faceted nature of mobility.
-We demonstrated how the embedding space encodes various aspects of scientific mobility, such as the global and regional geography, shared languages, and the hierarchy of organizational prestige, even without explicit information on these factors.
-
-While scientific mobility is used as a case study, this approach may be broadly applicable to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
+We demonstrated that a functional distance derived from the embedding can be used with the gravity model of mobility to better predicts real-world mobility than does geographic distance.
+Embedding distance outperformed geographic distance both in the case of U.S. flight itineraries and global scientific mobility domains of mobility with very different characteristics. 
+Focusing on scientific mobility, we find that neural embedding's performance is driven by its ability to encode many aspects of scientific mobility into a single representation, including global and regional geography, shared languages, and prestige hierarchies, even without explicit information on these factors.
+
+While we focus on data of U.S.
+flight itineraries and scientific mobility, this approach may be broadly applicable to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
 Moreover, this approach can be used to learn a functional distance between entities for which no physical analog exists, such as between occupational categories based on individuals' career trajectories.
@@
 Reliance on bibliometric metadata means that we capture only long-term mobility such as migration, rather than the array or more frequent short-term mobility such as conference travel and temporary visits.
-The kinds of mobility we do capture---migration, and co-affiliation---are ,although they are qualitatively different, treated identically by our model.
+The kinds of mobility we do capture---migration, and co-affiliation---although qualitatively different, are treated identically by our model.
 Also, our data might further suffer from survivorship bias: researchers at prestigious organizations tend to have more publications, leading to these organizations appearing more frequently in affiliation trajectories.

### 2020-10-01 paper/current/main.tex
data&methods edits

@@
 
-Data, analysis, and associated code have been made publicly available and can be found at \url{https://github.com/murrayds/sci-mobility-emb}.
+Processed data, analysis, and associated code have been made publicly available and can be found at \url{https://github.com/murrayds/sci-mobility-emb}.
+
+\subsection*{U.S. flight itinerary data}
+We source U.S. airport itinerary data from the Origin and Destination Survey (DB1B), provided by the Bureau of Transportation Statistics at the United States Department of Transportation. 
+DB1B is a sample of 10 percent of domestic airline tickets between 1993 and 2020, comprising 307,760,841 passenger itineraries between 828 U.S. airports. 
+Each itinerary is associated with an origin, destination, and passenger and ticket metadata.
 
@@
 
-\subsection*{U.S. Airport Itinerary data}
-We source U.S. airport itinerary data from the Origin and Destination Survey (DB1B), provided by the Bureau of Transportation Statistics at the United States Department of Transportation. 
-DB1B is a sample of 10 percent of domestic airline tickets between 1993 and 2020, comprising 307,760,841 passenger itineraries between 828 U.S. airports. 
-Each itinerary is associated with an origin, destination, and associated metadata.
-
 \subsection*{Embedding}
@@
 We embed trajectories by treating them analogously to sentences and locations analogously to words. 
-For U.S. airport itinerary, trajectories are formed by the flight itineraries of individual passenger and each location is unique airport code.
-For scientific mobility, the trajectories of mobile authors were converted to ``affiliation trajectories'' by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:methods:mobility_sentence}a.
+For U.S. airport itinerary, trajectories are formed from the flight itineraries of individual passenger, in which airports correspond to unique identifiers. 
+For scientific mobility, an``affiliation trajectories'' is constructed for each mobile author, which is built by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:methods:mobility_sentence}a.
 In more complex cases, such as listing multiple affiliations on the same paper or publishing with different affiliations on multiple publications in the same year, the order is randomized within that year, as shown in  Fig.~\ref{fig:methods:mobility_sentence}b.

### 2020-10-05 paper/current/main.tex
abstract + intro edits

@@
 Historically, human mobility is strongly constrained by physical separation---geographical distance~\autocite{zipf1946gravity}.
-However, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important, which calls for an alternative modeling framework for human mobility that takes these factors into account~\autocite{boschma2005proximity,  brown1970functional, brown1970migration, kim2018functional}.
+However, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important.
+The critical importance of understanding mobility in many socio-economic phenomena thus compel alternative frameworks for mobility.
 Here, using a massive dataset of scientific mobility and U.S.
-flight itineraries, we demonstrate that a neural embedding model can successfully encode nuanced relationships between locations into a vector-space~\autocite{mikolov2013word2vec}, providing an effective functional distance that reflects the multi-faced structure of human mobility.
-Focusing on the case of scientific mobility, we show that embeddings of scientific organizations captures cultural and linguistic relations at multiple levels of granularity, and even academic prestige.
+flight itineraries, we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective functional distance that reflects the multi-faced structure of human mobility.
+Focusing on the case of scientific mobility, we show that embeddings of scientific organizations discovers cultural and linguistic relations at multiple levels of granularity, and even academic prestige.
 Furthermore, the embedding vectors themselves reveal universal relationships between organizational characteristics, and their place in the global landscape of scientific mobility. 
@@
 
-Here, we propose to apply a neural embedding framework to real-world mobility trajectories and demonstrate that it can encode the complex landscape of human mobility into a dense, continuous, and meaningful vector-space representation, from which we can not only derive a meaningful \textit{functional distance} between places but also probe relationships based on culture, language, and even prestige along with geographic relationship.
+Here, we apply a neural embedding framework to real-world mobility trajectories and demonstrate that it can encode the complex landscape of human mobility into a dense, continuous, and meaningful vector-space representation, from which we can not only derive a meaningful \textit{functional distance} between places but also probe relationships based on culture, language, and even prestige along with geographic relationship.
 We leverage two massive datasets: a dataset of U.S. passenger flight itinerary records, and a dataset of scientific mobility between organizations captured in bibliometric records. 

### 2020-10-05 paper/current/main.tex
projection figure edits. ALso fixed bugs in in-text results, updated accordingly

@@
 
-The embedding space also allows us to \textit{zoom in} on subsets and re-project them using UMAP to reveal local relationships.
-For example, re-projecting organizations located in Western, Southern, and Southeastern Asia (Fig.~\ref{fig:projection}b) reveals a gradient of countries between Egypt and the Philippines that largely corresponds to geography, but with some exceptions along with the cultural and religious spectra;
-Malaysia, with its official religion of Islam, is nearer to Middle Eastern countries in the embedding space than many geographically-closer but South Asia countries.
-We also validate this finding quantitatively with the distance between nations in the embedding space $d$,  cosine distance between the centroids of organizations vectors belonging to that country. 
-Then, in the embedding space, Malaysia is nearer to many Islamic countries such as Iraq ($d = 0.29$), Pakistan ($d = 0.31$), and Saudi Arabia ($d = 0.41$)  than neighboring but Buddhist Thailand ($d = 0.43$) and predominantly-secular Vietnam ($d = 0.48$).
+The embedding space also allows us to \textit{zoom in} on subsets and re-project them to reveal local relationships.
+For example, re-projecting organizations located in Western, Southern, and Southeastern Asia with UMAP (Fig.~\ref{fig:projection}b) reveals a gradient of countries between Egypt and the Philippines that largely corresponds to geography, but with some exceptions along with the cultural and religious spectra;
+Malaysia, with its official religion of Islam, is nearer to Middle Eastern countries in the embedding space than many geographically-closer South Asian countries.
+We also validate this finding quantitatively with the cosine distance between nations (the centroids of organizations vectors belonging to that country). 
+Malaysia is nearer to many Islamic countries such as Iraq ($d = 0.29$), Pakistan ($d = 0.31$), and Saudi Arabia ($d = 0.41$)  than neighboring but Buddhist Thailand ($d = 0.43$) and predominantly-secular Vietnam ($d = 0.48$).
 
@@
 Comparable structural patterns exist even within a single country.
-For example, at the global level (Fig~\ref{fig:projection}a), organizations within Quebec in Canada are located nearer the French cluster ($d = 0.65$) than the rest of the Canadian organizations ($d = 0.88$).
+For example, organizations within Quebec in Canada are located nearer the French cluster ($d = 0365$) than the United States cluster ($d = 0.49$).
 
@@
 Harvard \& MIT).
-For example, even though UMass Boston is located in Boston, it clusters with other universities in the UMass System ($d = 0.34$) rather than the other typically more highly-ranked and research-focused universities in Boston ($d = 0.41$), implying a relative lack of mobility between the two systems.
+For example, even though UMass Boston is located in Boston, it clusters with other universities in the UMass System ($d = 0.33$) rather than the other typically more highly-ranked and research-focused organizations in Boston ($d = 0.38$), implying a relative lack of mobility between the two systems.
 Similar structures can be observed in other states such as among New York's CUNY and SUNY systems (Fig.~\ref{fig:supp:proj_newyork}), Pennsylvania's state system (Fig.~\ref{fig:supp:proj_pennsylvania}), Texas's Agricultural and Mechanical universities (Fig.~\ref{fig:supp:proj_texas}), and between the University of California and State University of California systems (Fig.~\ref{fig:supp:proj_california}).

### 2020-10-05 paper/current/main.tex
edits to just before conlusion

@@
 Could the embedding space, to which no explicit prestige information is given, encode a prestige hierarchy?
-We test this by exploiting the geometric properties of the embedding space with SemAxis~\autocite{an2018semaxis}.
+This question is tested by exploiting the geometric properties of the embedding space with SemAxis~\autocite{an2018semaxis}.
 Here, we use SemAxis to operationalize the abstract notion of academic prestige, defining an axis in the embedding space where poles are defined using known high- and low-ranked universities.
@@
 the high-rank pole is defined as the average vector of the top five U.S.
-universities according to the rankings, whereas the low-ranked pole is defined using the five bottom-ranked (geographically-matched by U.S.
+universities according to the rankings, whereas the low-rank pole is defined using the five bottom-ranked (geographically-matched by U.S.
 census region) universities.
-We derive an embedding-based ranking for universities based on the spectrum from the high-ranked to low-ranked poles (see Data and Methods).
+We derive an embedding-based ranking for universities based on the geometrical spectrum from the high-ranked to low-ranked poles (see Data and Methods).
 
@@
 ~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities produces a ranking that is significantly correlated with the Times ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
-The correlation is also comparable to network-driven measures such as degree strength (sum of edge weights, Spearman's $\rho = 0.73$) and eigenvector centrality (Spearman's $\rho = 0.76$, see \SI). 
+The correlation is also comparable to more direct measures such as node strength (sum of edge weights, Spearman's $\rho = 0.73$) and eigenvector centrality (Spearman's $\rho = 0.76$, see \SI) from the mobility network.
 The strongest outliers that were ranked more highly in the Times ranking than in the embedding-based ranking tend to be large state universities such as Arizona State University and the University of Florida.
@@
 
-The axes can further be visualized to examine the relative position of organizations along the prestige axis, and along a geographic axis between California and Massachusetts.
+The axes can be visualized to examine the relative position of organizations along the prestige axis, and along a geographic axis between California and Massachusetts.
 Prestigious universities such as Columbia, Stanford, MIT, Harvard, and Rockefeller are positioned towards the top of the axis (Fig.~\ref{fig:semaxis}c).
 Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphasis on teaching, such as Barry University and California State University at Long Beach.
-By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations for which rankings are often low-resolution, incomplete, or entirely absent, such as regional and liberal arts universities, seminaries, musical schools, community colleges (Fig.~\ref{fig:semaxis}d), government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).
-Their estimated prestige has a significant correlation with their citation impact (Fig.~\ref{fig:supp:sector_semaxis_impact}).
+By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reason about the prestige of organizations for which rankings are often low-resolution, incomplete, or entirely absent, such as regional and liberal arts universities, seminaries, musical schools, community colleges (Fig.~\ref{fig:semaxis}d), government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).
+Their estimated prestige is speculative, though we find that it significantly correlates with their citation impact (Fig.~\ref{fig:supp:sector_semaxis_impact}).
 
@@
 these organizations are primarily teaching-focused institutions, agencies, and hospitals that either are not ranked or have a low ranking.
-However, at around 1,000 researchers, the size of the vector decreases as the number of researchers increases.
+However, at around 1,000 researchers, the size of the vector \emph{decreases} as the number of researchers increases.
 These organizations are primarily research-intensive and prestigious universities with higher rankings, research outputs, R\&D funding, and doctoral students (Fig.~\ref{fig:supp:length_vs_metaInfo}).
 A similar pattern has been observed in applications of neural embedding to natural language, in which the size of word vectors was found to represent the word's \emph{specificity}.
-Roughly speaking, for word embeddings, the size of a vector indicates a specificity, i.e., the word associated with the vector frequently co-appears with particular context words\autocite{schakel2015measuring}.
+Roughly speaking, for word embeddings, the size of a vector reflects its specificity, i.e., the word associated with the vector frequently co-appears with particular context words\autocite{schakel2015measuring}.
 If the word in question is universal, appearing frequently in many different contexts, it would not have a large norm due to a lack of strong association with a particular context.
 Likewise, an organization such as Harvard with a small norm appears in many contexts, alongside many different organizations in affiliation trajectories---it is well-connected.
-The concavity emerges in part from the relationship between the size of the vector and the expected connectedness of the organization given its size (Fig.~\ref{fig:length}a, inset, $R^{2} = 0.17$).
+The concavity emerges in part from the relationship between the size of the vector and the expected connectedness of the organization given its size ($R^{2} = 0.17$).
 Large, prestigious, and well-funded research universities such as Princeton and Harvard have smaller vector norms because they appear in many different contexts compared to more teaching-focused organizations such as NY Medical College, and the University of Michigan at Flint.
@@
 Other nations exhibit different curves, such as Egypt which has an``S''-shaped curve, meaning that their largest organizations are not as well connected as other countries' largest organizations. 
-Similar patterns can be found across many of the 30 of the countries with the most total researchers (Fig.~\ref{fig:concave30}), however, we can only speculate on what their variations mean (see \SI for more discussion).
+Similar patterns can be found across many of the 30 of the countries with the most total researchers (Fig.~\ref{fig:concave30}) see \SI{} for more discussion).
 
@@
 		A convex-shape emerges, wherein larger universities tend to be more distant from the origin (large L2 norm); however, the more prestigious universities tend to have smaller L2 norms.
-		The L2 norm is correlated weakly with the ratio of organizations' number of connections (non-zero flows) to the number of researchers ($R^{2} = 0.17$, \textbf{inset}).
-		The red line is the line of the best fit, and 99\% confidence intervals are shown, though are too small to be visible.
 		\textbf{b.} We find a similar convex-curve pattern across many countries such as the United States, China, Australia, Brazil, and others (\textit{inset}, and Fig.~\ref{fig:concave30}). 

### 2020-10-05 paper/current/main.tex
conclusion edits

@@
 We demonstrated that a functional distance derived from the embedding can be used with the gravity model of mobility to better predicts real-world mobility than does geographic distance.
-Embedding distance outperformed geographic distance both in the case of U.S. flight itineraries and global scientific mobility domains of mobility with very different characteristics. 
+Embedding distance outperformed geographic distance both in the case of U.S. flight itineraries and global scientific mobility, which represent two domains with disparate nature. 
 Focusing on scientific mobility, we find that neural embedding's performance is driven by its ability to encode many aspects of scientific mobility into a single representation, including global and regional geography, shared languages, and prestige hierarchies, even without explicit information on these factors.
@@
 flight itineraries and scientific mobility, this approach may be broadly applicable to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
-Moreover, this approach can be used to learn a functional distance between entities for which no physical analog exists, such as between occupational categories based on individuals' career trajectories.
+Moreover, this approach can be used to learn a functional distance even between entities for which no physical analog exists, such as between occupational categories based on individuals' career trajectories.
 In addition to providing a functional distance that supports modeling and predicting mobility patterns, the structure of the neural embedding space is amenable to a range of unique applications for studying mobility.
 As we have shown, the embedding space allows the visualization of the complex structure of scientific mobility at high resolution across multiple scales, providing a large and detailed map of the landscape of global scientific mobility.
-Embedding also allows us to quantify abstract notions in mobility such as academic prestige, and can also be generalized to other abstract axes.
-Investigation of the structure of the embedding space, such as the vector norm, reveals unique and universal patterns based on the organization's size and their vector norm that could be leveraged in future studies of mobility.
+Embedding also allows us to quantitatively explore abstract notions such as academic prestige, and can potentially be generalized to other abstract axes.
+Investigation of the structure of the embedding space, such as the vector norm, reveals universal patterns based on the organization's size and their vector norm that could be leveraged in future studies of mobility.
 
 In spite of its promise, our study has several limitations.
-First, the current skip-gram word2vec model cannot encode directional information, meaning that embedding will be less effective at capturing mobility for which directionality is critical.
+First, the skip-gram word2vec model does not leverage directionality, meaning that embedding will be less effective at capturing mobility for which directionality is critical.
 Second, the neural embedding approach is most useful in cases of mobility between discrete geographic units such as between countries, cities, and businesses; this approach is less useful in the case of mobility between locations represented using geographic coordinates, such as in the modeling of animal movements.
@@
 
-Mobility and migration are at the core of human nature and history~\autocite{shah2020migration}, driving societal phenomena as diverse as epidemics\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity} and science and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage, morgan2018prestige, rodrigues2016mobility}.
+Mobility and migration are at the core of human nature and history~\autocite{shah2020migration}, driving societal phenomena as diverse as epidemics\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity} and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage, morgan2018prestige, rodrigues2016mobility}.
 However, the paradigm of scientific migration may be changing.

### 2020-10-05 paper/current/main.tex
edits to data and methods

@@
 Suppose an trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), where $a_{t}$ is the $t$th location in the trajectory.
-An location, $a_{t}$, is considered to have context locations, $a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}$, that appear in the window surrounding $a_t$ up to a time lag of $w$, where $w$ is the window size parameter truncated at $t - w \geq 0$ and $t + w \leq T$.
+A location, $a_{t}$, is considered to have context locations, $a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}$, that appear in the window surrounding $a_t$ up to a time lag of $w$, where $w$ is the window size parameter truncated at $t - w \geq 0$ and $t + w \leq T$.
 Then, the model learns probability $p(a_{t + \tau} \vert a_{t})$, where $-w\leq \tau\leq w$ and $\tau \neq 0$,  by maximizing its log likelihood given by
@@
 \subsection*{SemAxis}
-SemAxis~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} and similar studies demonstrated that ``semantic axes'' can be found from an embedding space by defining the ``poles'' and the latent semantic relationship along semantic axis can be extracted with the simple arithmetic.
+SemAxis and similar studies~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} demonstrated that ``semantic axes'' can be found from an embedding space by defining the ``poles'' and the latent semantic relationship along semantic axis can be extracted with the simple arithmetic.
 Each axis is an antonym pair defined for each specific use case.
@@
 As scholars move, they bring their knowledge, their skills, and their social connections with them--collectively the movements of researchers shape the structure and direction of the global scientific enterprise.
-For example, prestige-driven mobility between doctoral-granting and employing institution is highly unequal~\autocite{clauset2015hierarchy, deville2014career}, which impacts the diffusion of ideas across academia~\autocite{morgan2018prestige}.
+For example, prestige-driven mobility between doctoral-granting and employing institution is highly unequal~\autocite{clauset2015hierarchy, deville2014career}, which affects the diffusion of ideas across academia~\autocite{morgan2018prestige}.
 By placing researchers in new social settings, mobility can lead to the formation of new collaborative relationships~\autocite{rodrigues2016mobility}, which in turn spurs the further diffusion of knowledge and innovations~\autocite{braunerhjelm2020labor, azoulay2011diffusion, kaiser2018innovation, armano2017innovation}.
@@
 At the national level, the understanding of mobility has progressed beyond simplistic narratives of brain drain and brain gain, and instead adopts a new perspective of \textit{flows} of talent~\autocite{meyer2001network, ioannidis2014braindrain, gaillard1998circulation}.
-Under this flow model, a mobile researcher is viewed as contributing to both their origin and destination countries, a perspective that fosters that is evidenced by the strong science of open countires~\autocite{wagner2017open}.
+Under this flow model, a mobile researcher is viewed as contributing to both their origin and destination countries, a perspective that fosters that is evidenced by the strong science of open countries~\autocite{wagner2017open}.
 Perhaps because of these individual and national benefits, policy-makers have come to recognize the importance of global mobility~\autocite{box2008competition, oecd2010innovation}.

### 2020-10-05 paper/current/main.tex
update to biber, which better captures special characters

@@
 \usepackage[margin=1in]{geometry}
+\usepackage[utf8]{inputenc}
 \usepackage{graphicx}
@@
 \usepackage[style=nature,
-					backend=bibtex,
+					backend=biber,
 					sortcites=true,
@@
 Here, we apply a neural embedding framework to real-world mobility trajectories and demonstrate that it can encode the complex landscape of human mobility into a dense, continuous, and meaningful vector-space representation, from which we can not only derive a meaningful \textit{functional distance} between places but also probe relationships based on culture, language, and even prestige along with geographic relationship.
-We leverage two massive datasets: a dataset of U.S. passenger flight itinerary records, and a dataset of scientific mobility between organizations captured in bibliometric records. 
-In particular, we focus on scientific mobility throughout the paper due to its richness and importance.
-Scientific mobility, which is a central driver of the globalized scientific enterprise~\autocite{czaika2018globalisation, altbach2004globalization, box2008competition} and strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}, is not only an important topic on the science of science but also ideal for our study thanks to its richness and well-known structural properties such as the centrality of scientifically advanced countries and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career}.
+We leverage two massive datasets: a dataset of U.S. passenger flight itinerary records, and a dataset of scientists' career mobility between organizations captured in bibliometric records. 
+In particular, we focus on scientific mobility due to its richness and importance.
+Scientific mobility, which is a central driver of the globalized scientific enterprise~\autocite{czaika2018globalisation, altbach2004globalization, box2008competition} and strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}, is not only an important topic in the Science of Science but also ideal for our study thanks to its richness and well-known structural properties such as the centrality of scientifically advanced countries and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career}.
 In spite of its importance, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, being further confounded by the diminishing role of geography in shaping the landscape of scientific mobility.
@@
 These results are consistent in the case of scientific mobility. 
-the amount of variance in the expected flux explained by the embedding distance ($R^{2} = 0.48$, Fig.~\ref{fig:gravity_performance}e) is again more than double that explained by the geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}f).
+The amount of variance in the expected flux explained by the embedding distance ($R^{2} = 0.48$, Fig.~\ref{fig:gravity_performance}e) is again more than double that explained by the geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}f).
 This pattern holds when considering the subset of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d).
@@
 Linguistic and historical ties also affect scientific mobility.
-We observe that Spanish-speaking post-colonial Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), rather than nearby Portuguese-speaking nations ($d = 0.34$ vs.
+We observe that Spanish-speaking Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), rather than Portuguese-speaking Brazil ($d = 0.34$ vs.
 $d = 0.52$ for Mexico and $d = 0.39$ vs.
 $d = 0.49$ for Chile) reflecting linguistic and cultural ties.
-Similarly, North-African countries that were once under French rule such as Morocco are closer to France ($d =0.35$) than to similarly-distant European countries such as Spain ($d = 0.40$) and Italy ($d = 0.53$).
+Similarly, North-African countries that were once under French rule such as Morocco are closer to France ($d =0.35$) than to similarly geographically-distant European countries such as Spain ($d = 0.40$), Portugal ($d = 0.55$), and Italy ($d = 0.53$).
 Comparable structural patterns exist even within a single country.
@@
 Worcester), organization type (e.g., hospitals vs.
-universities), and university systems (UMass vs.
+universities), and university systems (Univeristy of  Massachusetts system vs.
 Harvard \& MIT).
@@
 Here, we use SemAxis to operationalize the abstract notion of academic prestige, defining an axis in the embedding space where poles are defined using known high- and low-ranked universities.
-As an external measure of prestige, we use the Times Ranking of World Universities (we also use research impact from the Leiden Rankings~\autocite{waltman2012leidenrankings}, see \SI);
+As an external proxy of prestige, we use the Times Ranking of World Universities (we also use research impact from the Leiden Ranking~\autocite{waltman2012leidenrankings}, see \SI);
 the high-rank pole is defined as the average vector of the top five U.S.
@@
 Reliance on bibliometric metadata means that we capture only long-term mobility such as migration, rather than the array or more frequent short-term mobility such as conference travel and temporary visits.
-The kinds of mobility we do capture---migration, and co-affiliation---although qualitatively different, are treated identically by our model.
+The kinds of mobility we do capture---migration, and co-affiliation---although conceptually different, are treated identically by our model.
 Also, our data might further suffer from survivorship bias: researchers at prestigious organizations tend to have more publications, leading to these organizations appearing more frequently in affiliation trajectories.

### 2020-10-06 paper/current/main.tex

@@
 
-As scholars move, they bring their knowledge, their skills, and their social connections with them--collectively the movements of researchers shape the structure and direction of the global scientific enterprise.
-For example, prestige-driven mobility between doctoral-granting and employing institution is highly unequal~\autocite{clauset2015hierarchy, deville2014career}, which affects the diffusion of ideas across academia~\autocite{morgan2018prestige}.
-By placing researchers in new social settings, mobility can lead to the formation of new collaborative relationships~\autocite{rodrigues2016mobility}, which in turn spurs the further diffusion of knowledge and innovations~\autocite{braunerhjelm2020labor, azoulay2011diffusion, kaiser2018innovation, armano2017innovation}.
-Perhaps resulting from the selection effects of who gets to move, or the reconfiguring of social and epistemic networks, movement is associated with increased scientific impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}.
-At the national level, the understanding of mobility has progressed beyond simplistic narratives of brain drain and brain gain, and instead adopts a new perspective of \textit{flows} of talent~\autocite{meyer2001network, ioannidis2014braindrain, gaillard1998circulation}.
-Under this flow model, a mobile researcher is viewed as contributing to both their origin and destination countries, a perspective that fosters that is evidenced by the strong science of open countries~\autocite{wagner2017open}.
-Perhaps because of these individual and national benefits, policy-makers have come to recognize the importance of global mobility~\autocite{box2008competition, oecd2010innovation}.
-Movement is a key mechanism that has clear impacts on the composition and direction of the global scientific workforce and our collective scientific understanding.
-Understanding the structure and dynamics of mobility is thus essential for understanding global science.
-
 %
@@
 
-There are many ways of modeling scientific mobility from bibliographic data, the first consideration being the unit of analysis.
-Most studies of mobility have focused on \textit{country-level} mobility--the flows of researchers across nations~\autocite{sugimoto2017mostimpact, scellato2015migrant, robinson-garcia2018indicators, franzoni2012foreign-born}.
-Practically, country-level analyses benefit from higher reliability, such that idiosyncrasies and errors inherent to bibliographic databases are mitigated by this higher level of aggregation.
-Epistemically, country-level analysis is useful for national science governance who aims to understand the status of their country in the global landscape and make informed policy decisions.
-Analyses at lower levels of analysis are far less common.
-\textit{Regional}-level scientific mobility--the flow of researchers between regions or cities within or across countries has been only minimally studied~\autocite{vaccario2019mobility}, possibly due to lack of reliable long-term data and lack of policy relevance to national-level lawmakers.
-\textit{Organization}-level mobility has the potential to inform institutional policy and to understand the composition of mobility within a single country or region, especially as it relates to organization performance, prestige, and inequality~\autocite{albarran2017topeconomic, deville2014career, morgan2018prestige, clauset2015hierarchy}.
-However, affiliation disambiguation and noise in bibliometric data have makes large-scale organization-level analysis challenging.
-Here, we learn neural-network embeddings of scientific mobility at the level of organizations using a curated bibliographic database.
-These embeddings are robust to noise, and so are capable of representing clear structure even amid issues with organizational disambiguation.
-In doing so, embeddings also capture a more detailed understanding of mobility than has been previously studied.
-
-Another consideration when analyzing scientific mobility is what kinds of mobility to study.
-Typical understandings of mobility are directional: movement is always \textit{from} one place and \textit{to} another.
-However, scientific mobility is more complicated.
-For example, scientists often hold multiple affiliations at a time~\autocite{markova2016synchronous}, listing them as co-affiliations on a single paper, or even choosing a subset of affiliations to use for multiple simultaneous projects~\autocite{robinson2019mobility}.
-Even clearly-directional migration to another institution is complex--researchers may continue to publish with an old affiliation for projects that began before their move, and they may maintain social and organizational links to their old institution (e.g., collaborators, projects, graduate students) such that there is no clear breakage after migrating.
-There is also a whole range of short-term scientific mobility, such as visiting scholarships and short-term visits that are only visible through intensive efforts such as manual extraction from CVs~\autocite{woolley2009cv, sandstrom2009cv, canibano2011temporary}.
-Here, we focus on more long-term mobility that can be derived from bibliographic data.
-Due to the complexity of scientific mobility, we make the simplifying assumption that all scientific mobility is \textit{symmetric} or without direction such that any move from an organization $A$ to organization $B$ is equivalent to a move from $B$ to $A$.
-By assuming non-directional mobility, all mobility events are commensurate, meaning that they can be treated identically in our analysis--this allows us to represent the complexity of mobility without making decisions about the directional of their mobility or which is their main affiliation.
-Moreover, this assumption has the practical advantage of matching the data format expected by the \textit{word2vec} model, as well as the theoretical advantage of adhering to the symmetricity assumption of the gravity model of mobility.
-
 %
@@
 
-For each mobile researcher who has at least two distinct affiliations, we construct an affiliation trajectory based on the affiliations listed on their published papers indexed in the Web of Science database between 2008 and 2019.
-An author is considered mobile if they published with at least two distinct affiliations during the time period of study.
-Affiliation names were manually disambiguated, and each was mapped to a unique organization identifier.
-An affiliation trajectory for an individual researcher is a sequence of organizations in ascending order of year of publication.
-if a researcher published papers with affiliation $A$ in year $t$, $B$ in $t+1$, $C$ in $t+2$ and $A$ again in $t+3$, then the affiliation trajectory is expressed as $(A, B, C, A)$.
-
-In the case that an individual lists multiple affiliations in a single year, affiliations listed on publications published in that year are shuffled between each iteration of the \textit{word2vec} training process (each epoch).
-For example, an author who published with affiliation $A$ in $t_{0}$, and affiliations $B$ and $C$ in $t_{1}$ could appear as one of $(A, B, C)$ or $(A, C, B)$ in each training iteration.
-This effectively removes the effect of order within a year, as the order cannot be meaningfully established based on co-affiliations in a single paper, or on different affiliations listed on separate papers, for which its date of publication may not be representative of the actual completion of the project.
-
-Other than restricting to only mobile researchers, we do not perform any filtering or reductions to affiliation trajectories.
-In the case than an author publishes with organization $A$ four times in $t_{0}$, and affiliation $B$ two times in $t_{1}$, then their trajectory will be $(A, A, A, A, B, B)$.
-Although mobile authors who publish more papers will have longer trajectories, \textit{word2vec} will skip duplicate consecutive organization IDs, mitigating the impact of long repetitive trajectories.
-
 %
@@
 
-We examine the gravity model on the Personalized Page Rank (PPR)\autocite{jeh2003scaling} as a benchmark on the network.
-We construct the co-occurrence network of $N$ organizations, in which each edge between organizations $i$ and $j$ represents a co-occurence of $i$ and $j$ in the same affiliation trajectory, with weight $W_{ij}$ given by the sum of the co-occurences over all researchers.
-and edges are co-occurrence between two organizations.
-The Personalized Page Rank is a ranking algorithm for nodes based on a random walk process on networks.
-The walker visiting at a node moves to a neighboring node chosen randomly with a probability proportionally to the weight of the edge in one step.
-Furthermore, with probability $\alpha$, the walker is teleported back to the starting node.
-The rank of a node is determined by the probability that the walker visits the node in the stationary state.
-The stationary distribution of the random walker starting from node $i$, denoted by $p_i=(p_{ik})$, is given by
-
-\begin{equation}
-	\label{eq:ppr}
-	p_i = (1 - \alpha) v_i + \alpha p_i W,
-\end{equation}
-where $v_i$ is a column vector of length $N$ with entries that are all zero except the $i$th entry that equals to one, $W = (W_{ij})$ is the weighted adjacency matrix. We used $\alpha=0.9$ here.
-
- We can think $p_i$ as a representation vector of the organization $i$, and calculate the distance between organizations $i$ and $j$, $d_{ij}$ with measuring distance between $p_i$ and $p_j$ to examine the gravity law.
-We consider two distance measures in this analysis.
-The first one is cosine distance which is used for our embedding method, $d_{ij} = 1 - \frac{\bm{p}_{i} \cdot \bm{p}_{j}}{\lVert \bm{p}_{i} \rVert \lVert \bm{p}_{j} \rVert}$.
-Also, if we think $p_i$ as a discrete probability distribution, then we can consider Jensen–Shannon divergence (JSD), can be written as,
-
-\begin{equation}
-	\label{eq:JSD}
-	d_{ij} = JSD(p_i||p_j) = \frac{1}{2}D_{KL}(p_i||m) + \frac{1}{2}D_{KL}(p_j||m),
-\end{equation}
-
-\begin{equation}
-	\label{eq:KL}
-	D_{KL}(p_i||m) = \sum^x p_{ix}\log\frac{p_{ix}}{m_x},
-\end{equation}
-where $m=\frac{1}{2}(p_i+p_j)$.
-We report the result with cosine distance ($R^2=0.14$, Fig.
-\ref{fig:supp:gravity_pprcos}) and  Jensen–Shannon divergence ($R^2=0.19$, Fig.
-\ref{fig:supp:gravity_pprjsd}).
-In both cases, the performance is under the performance of the model with geographical distance.
-Even though the length of the PPR vectors is extremely larger than the length of our embedding vectors, result with the embedding distance outperforms both of them.
-
 %
@@
 
-Affiliations mapped to one of 8,661 organizations, disambiguated following that originally designed for the Leiden Rankings of World Universities~\autocite{waltman2012leidenrankings}.
-Organizational records were associated with a full name, a type indicating the sector (e.g., University, Government, Industry), and an identifier for the country and city of the organization.
-Sixteen different sector types were included in the analysis, which we aggregated to four high-level codes: \textit{University}, \textit{Hospital}, \textit{Government}, and \textit{Other}.
-Each record was also associated with a latitude and longitude. 
-However, for many organizations, these geographic coordinates were missing or incorrect. 
-We manually updated the coordinates of 2,267 organizations by searching the institution name and city on Google Maps;
-in cases where a precise location of the organization could not be identified, we used the coordinates returned when searching the name of the city.
-The data was further enriched with country-level information, including region, most widely-spoken language, and its language family (e.g., the language family of \textit{Spanish} is \textit{Italic}).
-State/province-level information was added using the reverse geocoding service LocationIQ using each organization's latitude and longitude as input.
-Regional census classifications were added for states in the United States.
-For each organization, we calculated size as the average number of unique authors (mobile and non-mobile) who published with that organization across each year of our dataset;
-in the case that authors publish with multiple affiliations in a single year, they are counted towards each.
-
-As a result of our disambiguation procedure, some affiliations are mapped to two organizations, one specific, and one more general.
-For example, any author affiliated with ``Indiana University Bloomington'' will also be listed as being affiliated with the ``Indiana University System'', a more general designation for all public universities in Indiana.
-However, a more general organization may not always occur alongside the more specific one.
-For example, a researcher affiliated with the smaller regional school ``Indiana University South Bend'' will be listed as affiliated with only the ``Indiana University System''.
-We identify all specific organizations that always co-occur along with a more general one.
-For every career trajectory that includes one of these specific organizations, we remove all occurrences of the more general organization;
-trajectories containing only a general designation are not altered.
-
 %
@@
 
-Author-name disambiguation, the problem of associating names on papers with individuals authors, remains difficult for the use of bibliometric data~\autocite{dangelo2020disambiguation}.
-Authors in our dataset have been disambiguated using a rule-based algorithm that makes use of author and paper metadata, such as physical addresses, co-authors, and journal, to score papers on the likelihood of belonging to an author cluster---a cluster of publications believed to have been authored by the same individual~\autocite{caron2014disambiguation}.
-We limit our period of analysis to the period of 2008 to 2019, as in 2008 the Web of Science began indexing additional author-level metadata such as full names and email addresses.
-The disambiguation algorithm is conservative, favoring splitting clusters over merging.
-Past studies have validated this data and shown that the disambiguated authors are comparable to ground-truth records such as those from ORCID and useful for a wide range of bibliometric studies~\autocite{sugimoto2017mostimpact, robinson2019mobility, chinchilla2018global, chinchilla2018travelban}.
-
 %
@@
 
-The performance of the embedding ranking in reconstructing the Times ranking is comparable to that of network-derived measures such as degree strength (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_times_compare}a) and eigencentrality centrality (Spearman's $\rho = 0.76$, Fig.~\ref{fig:supp:centrality_times_compare}b).
-However, while both embedding- and network-based measures relate to university prestige, they are qualitatively and quantitatively different.
-The embedding-ranking of U.S.
-universities is less correlated with degree strength (Spearman's $\rho = 0.45$, Fig.~\ref{fig:supp:centrality_semaxis_compare}a) and eigenvector  centrality (Spearman's $\rho = 0.55$) than with the Times ranking itself (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_semaxis_compare}b).
-The embedding ranking over-ranks large research-intensive universities such as North Carolina State University, University of Florida, and Texas A\&M University, whereas the network-derived ranking over-ranks smaller, more specialized universities such as Brandeis University, Yeshiva University, and University of San Francisco.
-This suggests that the embedding encodes information on prestige hierarchy at least as well as a network representation, with some noticeable qualitative differences.
-
 %
@@
 
-The convex-curve pattern observed in Fig.~\ref{fig:length} repeats across many countries, with variations.
-For example, the representative vector of Chinese organizations has a larger norm than that of the U.S.
-($\bar{l} = 2.97$ vs $\bar{l} = 2.39$, Table~\ref{table:supp:norm}), causing its curve to be shifted upwards with a larger peak vector norm;
-this may reflect a tendency for organizations in the U.S. to appear more frequently in different contexts than Chinese organizations.
-Other nations such as Poland, Iran, and Turkey show a linear relationship between an organization's number of researchers and the vector norm, indicating that their largest organizations belong to very specific contexts (Fig.~\ref{fig:concave30}).
-The organization-level distribution of vector norms reveals deeper heterogeneity.
-The distribution of the vector norms for the U.S.
-is relatively skewed, suggesting their large norm is driven by a small and tight community of organizations (\textit{skew}$ = -0.82$, Fig.~\ref{fig:norm_dist}).
-Germany and the U.K.
-have comparable representative vector norms to the U.S.
-($\bar{l} = 2.6$ and $\bar{l} = 2.61$, respectively), with lower skewness (\textit{skew}$ = -0.63$ and \textit{skew}$ = -0.55$), suggesting more tight community of organizations.
-The vector norms of organizations in some countries are even more skewed, such as in Iran ($\bar{l} = 3.57$, \textit{skew}$ = -2.13$) and China ($\bar{l} = 2.97$, \textit{skew}$ = -1.08$), indicating the strong difference between their most- and least-connected organizations.
-For some countries, their organizations are positively-skewed, though seemingly for different reasons.
-For example, Austria has a balanced distribution of organization vector norms, suggesting a diverse range of organizations with most being well connected ($\bar{l} =2.64$, $s = 0.18$);
-Russia, in contrast, has a number of organization vectors of moderate norms, but also several isolated organizations with large vector norms ($\bar{l} = 3.08$, $s = 0.67$).
-
+\clearpage
 \newpage
 
-% latex table generated in R 3.5.1 by xtable 1.8-2 package
-% Thu Apr  2 13:43:00 2020
-\begin{table}[ht]
-\centering
+% S1 Table
+\begin{table}
 \caption{\textbf{Full organization names}}
 \label{table:supp:orglabels}
-\begin{adjustwidth}{-2cm}{}
-\begingroup\scriptsize
-\begin{tabular}{llll}
-  \hline
-Short & Full & Short & Full \\
-  \hline
-Stanford & Stanford Univ & Northwestern & Northwestern Univ \\
-  Columbia & Columbia Univ & Ball State & Ball State Univ \\
-  Harvard & Harvard Univ & IU Bloomington & Indiana Univ, Bloomington \\
-  UCLA & Univ of California, Los Angeles & Stevens Institute & Stevens Institute of Technology \\
-  Cal State Long Beach & California State Univ, Long Beach & NJIT & New Jersey Institute of Technology \\
-  Wright State & Wright State Univ & NYU & New York Univ \\
-  U Toledo & Univ of Toledo & SUNY Albany & Univ at Albany, The State Univ of New York \\
-  Boston U & Boston Univ & NY Medical College & New York Medical College \\
-  Suffolk & Suffolk Univ & Miami University & Miami Univ \\
-  CUNY & City Univ of New York (CUNY) & IU Pennsylvania & Indiana Univ of Pennsylvania \\
-  U Arizona & Univ of Arizona & Baylor & Baylor College of Medicine \\
-  OSU & Ohio State Univ & UT Health Center & Univ of Texas Health Science Center \\
-  MIT & Massachusetts Institute of Technology & Bard College & Bard College \\
-  Princeton & Princeton Univ & Stonehill College & Stonehill College \\
-  GCU & Grand Canyon Univ & Carleton College & Carleton College \\
-  Northcentral & Northcentral Univ & Hanover College & Hanover College \\
-  UCSF & Univ of California, San Francisco & Queens College & Queens College \\
-  Fielding & Fielding Graduate Univ & DePauw & DePauw College \\
-  Pepperdine & Pepperdine Univ & Naval Academy & United States Naval Academy \\
-  Argosy & Argosy Univ & Cal State San Marcos & California State Univ San Marcos \\
-  Yale & Yale Univ & Broad Inst & Broad Institute \\
-  U Hartford & Univ of Hartford & Forsyth Inst & Forsyth Institute \\
-  FAU & Florida Atlantic Univ & U Alaska Museum & Univ of Alaska Museum of the North \\
-  U Miami & Univ of Miami & Lawrence Berkeley & Lawrence Berkeley Natl Laboratory \\
-  UWF & The Univ of West Florida & Allen Institute & Allen Institute for Brain Science \\
-  FIT & Florida Institute of Technology & RTI International & RTI InterNatl \\
-  Purdue & Purdue Univ, West Lafayette & Fermilab & Fermilab \\
-  Notre Dame & Univ of Notre Dame & State of NY & State of New York \\
-  Indiana State & Indiana State Univ & Mayo Clinic & Mayo Clinic \\
-  Saint Mary's & Saint Mary's College & Fish and Wildlife & Fish and Wildlife Research Institute \\
-  Tufts & Tufts Univ & EPA & United States Environmental Protection Agency \\
-  Mattel & Mattel Children's Hospital & US Army & United States Army \\
-  Clark & Clark Univ & NSF & Natl Science Foundation \\
-  UMass Amherst & Univ of Massachusetts Amherst & US Navy & United States Navy \\
-  Montclair & Montclair State Univ & US Air Force & United States Air Force \\
-  Farleigh Dickinson & Fairleigh Dickinson Univ-Metro Campus & Ames Laboratory & Ames Laboratory \\
-  Rockefeller & Rockefeller Univ & Olin College & Oin College of Engineering \\
-  Adelphi & Adelphi Univ & Scrips Institute & Scrips Institute \\
-  Barnard & Barnard College & Idaho Natl Lab & Idaho Natl Laboratory \\
-  Saint John Fisher & Saint John Fisher College & Dana Faber & Dana Faber Cancer Institute \\
-  U Penn & Univ of Pennsylvania & Dept of Agriculture & United States Department of Agriculture \\
-  Villanova & Villanova Univ & DOE & United States Department of Energy \\
-  Widener & Widener Univ-Main Campus & NIAMS & Natl Institute of Arthritis, Skin Diseases \\
-  Robert Morris & Robert Morris Univ & JMI Labs & JMI Laboratories \\
-  U Cincinnati & Univ of Cincinnati & Whitehead Inst & Whitehead Institute of Biomedical Research \\
-  Case Western & Case Western Reserve Univ & Wellesley & Wellesley Univ\\
-  Ashland & Ashland Univ & UT Health, San Antonio & Univ of Texas Health Science Center, San Antonio \\
-  Texas A\&M & Texas A\&M Univ-Commerce & UNT & Univ of North Texas \\
-  Texas Southern & Texas Southern Univ & UT Southwestern Med & Univ of Texas Southwestern Medical Center \\
-  Baylor & Univ of Mary Hardin-Baylor & UT El Paso & Univ of Texas, El Paso \\
-  U Washington & Univ of Washington - Seattle & USF & Univ of South Florida, Tampa \\
-  Washington State & Washington State Univ & Florida A\&M & Florida Agricultural and Mechanical Univ \\
-  Seattle Pacific & Seattle Pacific Univ & Barry & Barry Univ \\
-  Cal State Fresno & California State Univ-Fresno & UMass Dartmouth & Univ of Massachusetts Dartmouth \\
-  Northern Arizona & Northern Arizona Univ & Worcester Poly & Worcester Polytechnic Institute \\
-  IUPUI & Indiana Univ - Purdue Univ Indianapolis & Umass Boston & Univ of Massachusetts Boston \\
-  U Dayton & Univ of Dayton & MGH Inst & MGH Institute of Health Professions \\
-  U Conn & Univ of Connecticut & Joseph W. Jones Center & Joseph W. Jones Ecological Research Center \\
-  ASU & Arizona State Univ & Vaccine Research Center & Vaccine Research Center, San Diego \\
-  U Florida & Univ of Florida & LA Ag Center & Lousianna Agricultural Center \\
-  Northern Illinois & Northern Illinois Univ & FL Fish and Wildlife & Florida Fish and Wildlife Conservation Commission \\
-  Concordia Chicago & Concordia Univ-Chicago & NHLBI & Natl Heart, Lung, and Blood Institute \\
-  U Chicago & Univ of Chicago & NY Dept. of Health & New York Department of Health \\
-  SIU Edwardsville & Southern Illinois Univ, Edwardsville & St Michaels & Saint Michaels College \\
-  SIU Carbondale & Southern Illinois Univ, Carbondale &  &  \\
-   \hline
-\end{tabular}
-\endgroup
-\end{adjustwidth}
 \end{table}
 
+% S2 Table
+\begin{table}
+\caption{\textbf{L2 Norm of country's representative vectors}.}
+\label{table:supp:norm}
+\end{table}
+
+\clearpage
 \newpage
 
-\begin{table}[]
-\centering
-\caption{\textbf{L2 Norm of country's representative vectors}.
-			 Shown for top 30 countries with the most unique mobile and non-mobile researchers}
-\label{table:supp:norm}
-\begin{tabular}{lrr}
-\textbf{Country} & \textbf{L2 Norm} & \textbf{\# Organizations} \\ \hline
-United States    & 2.39             & 1281                      \\
-Germany          & 2.6              & 485                       \\
-United Kingdom   & 2.61             & 514                       \\
-Austria          & 2.64             & 74                        \\
-France           & 2.83             & 688                       \\
-Belgium          & 2.84             & 84                        \\
-Switzerland      & 2.85             & 66                        \\
-Spain            & 2.94             & 322                       \\
-China            & 2.97             & 497                       \\
-India            & 2.99             & 114                       \\
-Poland           & 3.02             & 145                       \\
-Canada           & 3.02             & 147                       \\
-Italy            & 3.04             & 386                       \\
-Russia           & 3.08             & 187                       \\
-Norway           & 3.1              & 122                       \\
-Netherlands      & 3.11             & 136                       \\
-Sweden           & 3.16             & 75                        \\
-Brazil           & 3.16             & 286                       \\
-Finland          & 3.17             & 66                        \\
-Denmark          & 3.21             & 54                        \\
-Czech Republic   & 3.23             & 97                        \\
-Greece           & 3.24             & 62                        \\
-Australia        & 3.24             & 90                        \\
-Turkey           & 3.28             & 99                        \\
-South Korea      & 3.28             & 156                       \\
-Israel           & 3.32             & 71                        \\
-Portugal         & 3.33             & 57                        \\
-Japan            & 3.35             & 465                       \\
-Iran             & 3.57             & 68                        \\
-Taiwan           & 3.67             & 72
-\end{tabular}
-\end{table}
-
-\newpage
-
 %
@@
 %
-\begin{figure}[p!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/Descriptive/pubs_over_time.pdf}
+\begin{figure}[]
+\begin{flushleft}
+	%\includegraphics[width=\textwidth]{\figdir/Descriptive/pubs_over_time.pdf}
 	\caption{
 		\textbf{Publications over time.}
-		\textbf{a.}
-		The number of papers published by mobile authors has been steadily increasing from 2008 to 2017, with a small decrease in 2018,  which may be due to an artifact of the Web of Science indexing process.
-		Lines correspond to publications by mobile authors, by authors with affiliations in at least two cities, at least two regions, and at least two countries.
-		We did not find major changes in the publication patterns of mobile authors during this time period.
-		\textbf{b.}
-		Lines correspond to the proportion of publications classified as Biology and Health (black), Physics and Engineering (purple), Life and Earth Science (magenta), Social Science and Humanities (orange), and Math and Computer Science (yellow).
-		The rate of publication in Biology and Health has leveled since about 2013, whereas the rate of publication in other fields has steadily increased.
-		\textbf{c.}
-		While the absolute count of publications has increased, the percentage of mobile scholars, and those with affiliations in at least least two cities, regions, or countries, as a proportion of all publications, has decreased over time.
-		\textbf{d.}
-		The proportion of authors' publications across fields has largely remained steady.
-		Biology and Health Science has comprised the majority of publications across nearly all years but has steadily declined in proportion.
-		However, the proportion of Social Science and Humanities publications has been steadily increasing.
-	}
+		}
+\end{flushleft}
 	\label{fig:supp:pubs_over_time}
@@
 %
-\begin{figure}[p!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/Descriptive/mobility_by_country.pdf}
-	\caption{
-		\textbf{Extent and nature of mobility by country.}
-		\textbf{a.}
-		The proportion of all mobile researchers contributed by each country. 
-		Over 30\% of all mobile researchers have been affiliated with organizations in the U.S. during the period of study.
-		\textbf{b.}
-		Cumulative distribution of data shown in (\textbf{a}).
-		The U.S., China, and France, the U.K., and Germany comprise about 70\% of all mobile researchers. 
-		\textbf{c.} 
-		The proportion of each country's researchers who are mobile.
-		The dashed line indicates the proportion of all researchers in the data who are mobile. 
-		France, followed by Qatar and the U.S. have the highest proportion of mobile researchers. 
-		\textbf{d.} First two principal components of four variables: proportion of researchers in each country mobile across organizations, proportion mobile across cities, proportion mobile across regions, and proportion mobile across countries.
-		The countries are roughly sorted in order of the number of mobile researchers and the fraction of international mobile researchers in the first and second principal components, which are indicated by PC1 and PC2, respectively.
-		PC1 explains 88.3\% of the total variance, whereas PC2 explains 9.5\% of the total variance. 
-	}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/Descriptive/mobility_by_country.pdf}
+	\caption{\textbf{Extent and nature of mobility by country.}}
 	\label{fig:supp:descriptives}
@@
 
-\newpage
 %
@@
 %
-\begin{figure}[p!]
-	\centering
-	\includegraphics[width=0.8\textwidth]{\figdir/Descriptive/rcdf_by_scale.pdf}
+\begin{figure}[]
+	%\includegraphics[width=0.8\textwidth]{\figdir/Descriptive/rcdf_by_scale.pdf}
 	\caption{
 		\textbf{Reverse cumulative-distribution function of mobile researchers by geographic scale.}
-		\textbf{a.}
-		Survival probability of mobile researchers with respect to the number of organizations in the their affiliation trajectory.
-		All mobile authors were affiliated with at least two organizations (i.e., survival probability of one) and about 35.0\% were affiliated with three or more. 
-		\textbf{b.} About 68\% of mobile authors listed at least two cities represented in their career trajectories.
-		\textbf{c.} 45\% of mobile authors have two or more regions represented in their career trajectories.
-		\textbf{d.} Only 14\% of mobile authors had two or more countries represented in their career trajectories.
 	}
@@
 %
-\begin{figure}[p!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/Descriptive/hyperparameter_performance.pdf}
-	\caption{
-		\textbf{Larger dimensions, smaller window size improves embedding performance.}
-		The correlation, or amount of flux explained by the embedding distance with varying skip-gram negative sampling hyperparameters.
-		Window size refers to $w$, the size of the context window that defines the context in a trajectory.
-		Smaller window sizes result in an embedding that explain more flux.
-		Embedding dimensions refer to the size of the embedding vector.
-		Larger vectors perform better, though little difference between 200 and 300.
-		All variants perform better on same-country pairs of organizations than on all organizations.
-		All variants perform worse on different-country pairs on organizations.
-		Embeddings with larger dimensions outperform mid-size embeddings for the different-country case.
-	}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/Descriptive/hyperparameter_performance.pdf}
+	\caption{\textbf{Larger dimensions, smaller window size improves embedding performance.}}
 	\label{fig:supp:cosdot}
@@
 %
-\begin{figure}[p!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/Math/d300_ws1_dot_cosine.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/Math/d300_ws1_dot_cosine.pdf}
 	\caption{
 		\textbf{Cosine distance is correlated with dot product similarity.}
-		We find a relatively high correlation between the embedding distance---one minus the cosine similarity---and the dot product similarity between organization vectors ($R^2 = 0.73$).
-		Color of each hex bin indicates the frequency of organization pairs. 
-		Black dots indicate the mean dot product similarity averaged over binned sets at the same embedding distance.
-		Red line is line of best fit.
 	}
@@
 %
-\begin{figure}[p!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance_geo_bymodel.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance_geo_bymodel.pdf}
 	\caption{
 		\textbf{For geographic distance, the power-decay gravity model is better.}
-		Flux between organization pairs predicted by the gravity model with different distance decay functions, i.e., exponential decay function (\textbf{a}) and power-law decay function (\textbf{b}) using geographic distance.
-		Boxplots show distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps with $x = y$; 
-		a perfect prediction yields all points on the black line.
-		Shown for all pairs of organization (\textbf{a-b}), domestic (\textbf{c-d}), and international only (\textbf{e-f}) mobility.
-		The gravity model with the power-decay function outperforms that with an exponential decay function.
 	}
@@
 %
-\begin{figure}[p!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance_emb_bymodel.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance_emb_bymodel.pdf}
 	\caption{
 		\textbf{For geographic distance, the power-decay gravity model is better.}
-		Flux between organization pairs predicted by the gravity model with different distance decay functions, i.e., exponential decay function (\textbf{a}) and power-law decay function (\textbf{b}) using embedding distance.
-		Boxplots show distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps with $x = y$; 
-		a perfect prediction yields all points on the black line.
-		Shown for all pairs of organization (\textbf{a-b}), domestic (\textbf{c-d}), and international only (\textbf{e-f}) mobility.
-		The gravity model with the exponential decay function outperforms that with a power-decay function.
 	}
@@
 %
-\begin{figure}[p!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_correlations.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_correlations.pdf}
 	\caption{
 		\textbf{Embedding distance explains more variance for global, within, and across country flux than geographic distance.}
-		\textbf{a.}
-		Embedding distance explains more flux than geographic distance (\textbf{b}).
-		Red line is the line of best fit.
-		Black dots are mean flux across binned distances.
-		Color of each hex bin indicates frequency of organization pairs.
-		Results here are identical to those shown in Fig.~\ref{fig:gravity_performance}a and Fig.~\ref{fig:gravity_performance}.
-		\textbf{c-d.}	embedding distance explains more variance when considering only within-country organization pairs.
-		\textbf{e-f.} embedding distance is more robust than geographic distance when considering only across-country organization pairs.
 	}
@@
 %
-\begin{figure}[p!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_different_fits.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_different_fits.pdf}
 	\caption{
 		\textbf{Little difference between gravity predictions fit on all or subsets of data.}
-		Predictions of flux between organization pairs made using embedding distance out-performs those made using geographic distance.
-		Boxplots show distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps the line $x = y$; 
-		a perfect prediction yields all points on the black line.
-		\textbf{a-b.} Predictions are made with parameters estimated from all pairs of organizations (as in Fig.~\ref{fig:gravity_performance}c), and showing only the subsets of predictions for organization pairs in the same country (\textbf{a}) and in different countries (\textbf{b}).
-		\textbf{c-d.} Predictions made using parameters estimated from the subset of organizations in the same country (\textbf{c}) and different country \textbf{d});
-		this is the same data as shown in Fig.~\ref{fig:gravity_performance}f and Fig.~\ref{fig:gravity_performance}h.
 	}
@@
 %
-\begin{figure}[p!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_dot.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_dot.pdf}
 	\caption{
 		\textbf{Examine gravity model with dot product on the embedding space.}
-		Performance of dot product similarities in explaining and predicting mobility.
-		Similarity scores are calculated as the pairwise dot product between organizational vectors.
-		Dot product similarity performs better than geographic distance, though worse than cosine similarity in explaining global mobility (\textbf{a}), or domestic (\textbf{b}) or international (\textbf{c}) country mobility.
-		Red line is line of best fit.
-		Black dots are mean flux across binned distances.
-		Color indicates frequency of organization pairs within each hex bin.
-		Similarly, PPR distance performs comparably to geographic distance in predicting global (\textbf{d}), domestic (\textit{e}) and international (\textbf{f}) scientific mobility.
-		Boxplots show distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps $x = y$;
-		a perfect prediction yields all points on the black line.
 	}
@@
 %
-\begin{figure}[p!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_pprcos.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_pprcos.pdf}
 	\caption{
 		\textbf{Personalized page rank with cosine distance.}
-		Performance of personalized page rank scores in explaining and predicting mobility.
-		Personalized page rank is calculated for the underlying mobility network, and distance measured as the cosine distnace between PPR probability distribution vectors.
-		PPR cosine distance performs roughly similar to geographic distance in explaining global(\textbf{a}), domestic (\textbf{b}), or international (\textbf{c}) country mobility.
-		Red line is the line of best fit.
-		Black dots indicate the mean flux across binned distances.
-		Color of hex bind indicates frequency of organization pairs.
-		Similarly, PPR distance performs comparably to geographic distance in predicting global (\textbf{d}), domestic (\textit{e}) and international (\textbf{f}) scientific mobility.
-		Boxplots show distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps $x = y$;
-		a perfect prediction yields all points on the black line.
 	}
@@
 
-\begin{figure}[p!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_pprjsd.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_pprjsd.pdf}
 	\caption{
 		\textbf{Personalized page rank with Jensen-Shannon Divergence.}
-		Performance of personalized page rank scores in explaining and predicting mobility.
-		Personalized page rank is calculated for the underlying mobility network, and distance measured as the Jensen-Shannon Divergence (JSD) between PPR probability distribution vectors.
-		PPR JSD performs roughly similar to geographic distance in explaining global mobility (\textbf{a}), or domestic (\textbf{b}) or international (\textbf{c}) country mobility.
-		Overall, PPR JSD explains more variance in mobility than using cosine distance (Fig.~\ref{fig:supp:gravity_pprcos}), except for international mobility, for which cosine similarity out-performs JSD.
-		Red line is the line of best fit.
-		Black dots are mean flux across binned distances.
-		Color of hex bind indicates frequency of organization pairs.
-		Similarly, PPR JSD performs comparably to geographic distance in predicting global (\textbf{d}), domestic (\textit{e}) and international (\textbf{f}) scientific mobility.
-		Boxplots show distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps $x = y$;
-		a perfect prediction yields all points on the black line. 
 	}
@@
 %
-\begin{figure}[hp!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/Projection/co_occur_with_label.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/Projection/co_occur_with_label.pdf}
 	\caption{
 		\textbf{Visualization of global mobility network.}
-		The network demonstrates country-level structure, but not at the detail or the extent of the global UMAP projection (Fig.~\ref{fig:projection}a).
-		Each node corresponds to an organization, whereas  weighted edges (not shown) correspond to the flow of mobile researchers between the two organization.
-		Nodes are colored by the country of the organization.
-		Nodes are positioned using the Force Atlas layout algorithm.
 	}
@@
 %
-\begin{figure}[hp!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_New_York.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_New_York.pdf}
 	\caption{
 		\textbf{UMAP Projection of organizations in New York.}
-		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019.
-		Color indicates the sector.
 	}
@@
 %
-\begin{figure}[hp!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_Pennsylvania.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_Pennsylvania.pdf}
 	\caption{
 		\textbf{UMAP Projection of organizations in Pennsylvania.}
-		UMAP projection of the embedding space of organizations in Pennsylvania reveals clustering based on geography, sector, and academic prestige.
-		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019.
-		Color indicates the sector.
 	}
@@
 %
-\begin{figure}[hp!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_Texas.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_Texas.pdf}
 	\caption{
 		\textbf{UMAP Projection of organizations in Texas.}
-		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019.
-		Color indicates the sector.
 	}
@@
 %
-\begin{figure}[hp!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_California.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_California.pdf}
 	\caption{
 		\textbf{UMAP Projection of organizations in California.}
-		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019.
-		Color indicates the sector.
 	}
@@
 %
-\begin{figure}[hp!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_compare_fig.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_compare_fig.pdf}
 	\caption{
 		\textbf{SemRank hierarchy is robust.}
-		\textbf{a.} Spearman's $\rho$ ($n = 143$) between Times prestige rank and embedding rank derived using SemAxis, with poles defined using the top and bottom (geographically matched) ranked universities.
-		Black points show spearman correlation using all organizations; white points show correlation using only universalizes not aggregated in the poles.
-		Including more universities improves performance, but quickly saturates after around five universities.
-		\textbf{b - f.} Comparison between the Times and SemAxis ranks of universities, by the number of universities used to define the poles (n).
-		White points are those top and bottom 20 universities aggregated to define the ends of the axis.
-		The grey box corresponds to the top 20 and bottom 20 ranks.
-	  	Spearman's $\rho$ details the estimate from Spearman correlation between the two rankings using all universities, including those used to define the ends of each axis.
 	}
@@
 %
-\begin{figure}[hp!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/SemAxis/centrality_times_compare.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/SemAxis/centrality_times_compare.pdf}
 	\caption{
 		\textbf{Network centrality is strongly correlated with Times ranking.}
-		Comparison between the ranking of organizations by their network-centrality rank and their rank in the 2018 Times Higher Education ranking of U.S. Universities .
-		The Times rank is correlated with degree centrality rank (\textbf{a}) with Spearman's $\rho = 0.73$, and is correlated with the eigenvector centrality rank (\textbf{b}) with Spearman's $\rho = 0.76$.
 	}
@@
 %
-\begin{figure}[hp!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_network_compare.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_network_compare.pdf}
 	\caption{
 		\textbf{Network centrality less correlated with Embedding rank.}
-		Comparison between the ranking of organizations by their network-centrality rank and the embedding rank derived with SemAxis with poles defined using the top five to geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S.
-Universities .
-		Embedding rank is correlated with degree centrality rank (\textbf{a}) with Spearman's $\rho = 0.45$, and is correlated with the eigenvector centrality rank (\textbf{b}) with Spearman's $\rho = 0.55$.
 	}
@@
 %
-\begin{figure}[hp!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_states_fig.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_states_fig.pdf}
 	\caption{
 		\textbf{Geography and prestige SemAxis by U.S. state.}
-		SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S.
-Universities (bottom to top).
-		Points correspond to universities shown for California (\textbf{a}), Arizona (\textbf{b}), Washington (\textbf{c}), Massachusetts (\textbf{d}), Connecticut (\textbf{e}), New York (\textbf{f}), Texas (\textbf{g}), Pennsylvania (\textbf{h}), and Florida (\textbf{i}).
-		Grey points correspond to all other U.S. universities.
-		Full organization names listed in Table~\ref{table:supp:orglabels}.
 	}
@@
 %
-\begin{figure}[hp!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/SemAxis/sector_rank_comparison.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/SemAxis/sector_rank_comparison.pdf}
 	\caption{
 		\textbf{SemAxis reconstructs publication impact in non-university sectors.}
-		Comparison between the ranking of organizations in each non-university sector by their citation impact and the embedding rank.
-		Citation impact is calculated as the mean-normalized citation score using papers published in the Web of Science database between 2008 and 2019. 
-		The embedding rank is derived by first projecting non-university organizations onto the SemAxis axis formed with poles defined using the top five to geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S.
-Universities.
-		\textbf{a} Shows how the correlation between the citation impact and SemAxis rankings differ while varying the size threshold for including an organization.
-		Size is calculated as the mean annualized number of unique authors publishing with that organization. 
-		Annotations show the number of organizations remaining at thresholds pf 0, 50, and 100. 
-		\textbf{b}. Comparison of organizations using a size threshold of 10 for regional and liberal arts colleges, and 50 for research institutes and government organizations;
-		these thresholds were chosen as points thresholds of stability in \textbf{a}. 		
-		The impact rank is correlated with the embedding rank for regional and liberal arts colleges with Spearman's $\rho = 0.49 (n = 48)$, research institutes with Spearman's $\rho = 0.58 (n = 159)$, and for government organizations with Spearman's $\rho = 0.36 (n = 55)$.
 	}
@@
 %
-% Figure - SemAxis By Sector
-%
-%\begin{figure}[hp!]
-%	\centering
-%	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_sectors_fig.pdf}
-%	\caption{
-%		\textbf{Geography and prestige SemAxis in U.S. by Sector.}
-%		SemAxis projection along two axes, comparing California to Massachusetts universities (left to r%ight), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 %Times Higher Education ranking of U.S.
-Universities (bottom to top).
-%		Points correspond to organizations labeled as Government (\textbf{a}), Institute (\textbf{b}), and %Teaching (\textbf{c}), corresponding to government organizations, research institutes, and teaching o%rganizations, respectively.
-%		Grey points correspond to all U.S. universities.
-%	    	Full organization names listed in Table~\ref{table:supp:orglabels}.
-%	}
-%	\label{fig:supp:semaxis_sectors}
-%\end{figure}
-
-%
 % Figure - length by factors
 %
-\begin{figure}[hp!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/Math/l2_org_meta.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/Math/l2_org_meta.pdf}
 	\caption{
 		\textbf{Factors relating to the L2 norm of vectors for U.S. universities}
-		Correlation between the L2 norm of organization embedding vectors of U.S. universities and characteristics of U.S. universities.
-		Dots correspond to organizations.
-		The red line is the line of  the best fit with corresponding 99\% confidence intervals.
-		Red text is the regression estimate.
-		The blue line is the loess regression line with 99\% confidence intervals.
-		Number of authors is the average annual count of unique mobile and non-mobile authors.
-		Rankings are derived from the Times Ranking of World Universities, and the Leiden Rankings of Universities.
-		Remaining variables come from the Carnegie Classification of Higher Education Institutions.
-		The factors that best explain $s_i$ are the number of authors, the rank, the amount of Science and Engineering (S\&E) funding, and the number of doctorates granted.
 	}
@@
 %
-\begin{figure}[h!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/Math/boomerang_30_countries.pdf}
+\begin{figure}[]
+	%\includegraphics[width=\textwidth]{\figdir/Math/boomerang_30_countries.pdf}
 	\caption{
 		\textbf{Concave-curve repeats across most of 30 countries with most researchers.}
-		Size (L2 norm) of organization embedding vectors compared to their number of researchers for U.S. universities.
-		Loess regression line is shown for each country with 99\% confidence intervals.
-		Countries shown are the 30 with the largest number of total unique mobile and non-mobile researchers.
 	}
@@
 %
-\begin{figure}[h!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/Math/l2_org_dist.pdf}
+\begin{figure}[]
+	% \includegraphics[width=\textwidth]{\figdir/Math/l2_org_dist.pdf}
 	\caption{
 		\textbf{Distribution of organization embedding vector norms by country.}
-		Histogram showing the distribution of L2 norm values of organization embedding vectors in each of the 30 countries with the largest number of total unique mobile and non-mobile researchers.
-		Text in each panel shows the number of organizations in the country (n) and the GINI index of inequality of the distribution (g);
-		a small GINI index indicates that the L2 norms of organizations are more balanced, whereas a high GINI value indicates that they are more unequal.
 	}

### 2020-10-06 paper/current/supp.tex

\documentclass[12pt]{article} %{{{

% Text
\setlength{\marginparwidth}{2.3cm}

% Figures
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\def\figdir{../Figs}

% define a command to setup the format of supporting infomration figures and tables.
% source: http://bytesizebio.net/2013/03/11/adding-supplementary-tables-and-figures-in-latex/
\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{S\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{S\arabic{figure}}%
     }

% Math
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{newtxmath}
\DeclareMathAlphabet{\mathpzc}{T1}{pzc}{m}{it}
\DeclareMathOperator*{\argmin}{\arg\!\min}
\DeclareMathOperator*{\argmax}{\arg\!\max}
\usepackage{bm}
\def\tnull{{\text{null}}}
\def\vec#1{{\bm #1}}
\def\mat#1{\mathbf{#1}}

% abbreviations
\def\etal{\emph{et~al}.\ }
\def\eg{e.g.,~}
\def\ie{i.e.,~}
\def\cf{cf.\ }
\def\viz{viz.\ }
\def\vs{vs.\ }

% Refs
\usepackage[style=nature,
					backend=biber,
					sortcites=true,
					autocite=superscript
]{biblatex}
\addbibresource{mobility.bib}

\usepackage{url}

\usepackage{changepage}

% Figure caption
\usepackage{setspace}
\usepackage[font=small,labelfont=bf]{caption}
\captionsetup[subfigure]{font={bf,small}, skip=1pt, singlelinecheck=false}

\newcommand{\secref}[1]{Section~\ref{sec:#1}}
\newcommand{\figref}[1]{Fig.~\ref{fig:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
%\newcommand{\eqnref}[1]{\eqref{eq:#1}}
%\newcommand{\thmref}[1]{Theorem~\ref{#1}}
%\newcommand{\prgref}[1]{Program~\ref{#1}}
%\newcommand{\algref}[1]{Algorithm~\ref{#1}}
%\newcommand{\clmref}[1]{Claim~\ref{#1}}
%\newcommand{\lemref}[1]{Lemma~\ref{#1}}
%\newcommand{\ptyref}[1]{Property~\ref{#1}}

% for quick author comments
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\definecolor{light-gray}{gray}{0.8}
\def\del#1{ {\color{light-gray}{#1}} }
\def\yy#1{ {\color{red}\textbf{yy: #1}} }
\def\dk#1{ {\color{red}\textbf{dk: #1}} }
\def\js#1{ {\color{red}\textbf{js: #1}} }

%}}}

\begin{document} %{{{

\title{Supporting Information: Unsupervised embedding of trajectories captures the latent structure of mobility} %{{{
\date{\today}
\maketitle %}}}

%
%
\paragraph*{S1 Text}
\label{si:text:mobility_science}
{\bf Mobility and science.}

As scholars move, they bring their knowledge, their skills, and their social connections with them--collectively the movements of researchers shape the structure and direction of the global scientific enterprise.
For example, prestige-driven mobility between doctoral-granting and employing institution is highly unequal~\autocite{clauset2015hierarchy, deville2014career}, which affects the diffusion of ideas across academia~\autocite{morgan2018prestige}.
By placing researchers in new social settings, mobility can lead to the formation of new collaborative relationships~\autocite{rodrigues2016mobility}, which in turn spurs the further diffusion of knowledge and innovations~\autocite{braunerhjelm2020labor, azoulay2011diffusion, kaiser2018innovation, armano2017innovation}.
Perhaps resulting from the selection effects of who gets to move, or the reconfiguring of social and epistemic networks, movement is associated with increased scientific impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, jonkers2013return, franzoni2014advantage}.
At the national level, the understanding of mobility has progressed beyond simplistic narratives of brain drain and brain gain, and instead adopts a new perspective of \textit{flows} of talent~\autocite{meyer2001network, ioannidis2014braindrain, gaillard1998circulation}.
Under this flow model, a mobile researcher is viewed as contributing to both their origin and destination countries, a perspective that fosters that is evidenced by the strong science of open countries~\autocite{wagner2017open}.
Perhaps because of these individual and national benefits, policy-makers have come to recognize the importance of global mobility~\autocite{box2008competition, oecd2010innovation}.
Movement is a key mechanism that has clear impacts on the composition and direction of the global scientific workforce and our collective scientific understanding.
Understanding the structure and dynamics of mobility is thus essential for understanding global science.

%
% S2 Text
\paragraph*{S2 Text}
\label{si:text:mobility_models}
{\bf Modeling scientific mobility.}

There are many ways of modeling scientific mobility from bibliographic data, the first consideration being the unit of analysis.
Most studies of mobility have focused on \textit{country-level} mobility--the flows of researchers across nations~\autocite{sugimoto2017mostimpact, scellato2015migrant, robinson-garcia2018indicators, franzoni2012foreign-born}.
Practically, country-level analyses benefit from higher reliability, such that idiosyncrasies and errors inherent to bibliographic databases are mitigated by this higher level of aggregation.
Epistemically, country-level analysis is useful for national science governance who aims to understand the status of their country in the global landscape and make informed policy decisions.
Analyses at lower levels of analysis are far less common.
\textit{Regional}-level scientific mobility--the flow of researchers between regions or cities within or across countries has been only minimally studied~\autocite{vaccario2019mobility}, possibly due to lack of reliable long-term data and lack of policy relevance to national-level lawmakers.
\textit{Organization}-level mobility has the potential to inform institutional policy and to understand the composition of mobility within a single country or region, especially as it relates to organization performance, prestige, and inequality~\autocite{albarran2017topeconomic, deville2014career, morgan2018prestige, clauset2015hierarchy}.
However, affiliation disambiguation and noise in bibliometric data have makes large-scale organization-level analysis challenging.
Here, we learn neural-network embeddings of scientific mobility at the level of organizations using a curated bibliographic database.
These embeddings are robust to noise, and so are capable of representing clear structure even amid issues with organizational disambiguation.
In doing so, embeddings also capture a more detailed understanding of mobility than has been previously studied.

Another consideration when analyzing scientific mobility is what kinds of mobility to study.
Typical understandings of mobility are directional: movement is always \textit{from} one place and \textit{to} another.
However, scientific mobility is more complicated.
For example, scientists often hold multiple affiliations at a time~\autocite{markova2016synchronous}, listing them as co-affiliations on a single paper, or even choosing a subset of affiliations to use for multiple simultaneous projects~\autocite{robinson2019mobility}.
Even clearly-directional migration to another institution is complex--researchers may continue to publish with an old affiliation for projects that began before their move, and they may maintain social and organizational links to their old institution (e.g., collaborators, projects, graduate students) such that there is no clear breakage after migrating.
There is also a whole range of short-term scientific mobility, such as visiting scholarships and short-term visits that are only visible through intensive efforts such as manual extraction from CVs~\autocite{woolley2009cv, sandstrom2009cv, canibano2011temporary}.
Here, we focus on more long-term mobility that can be derived from bibliographic data.
Due to the complexity of scientific mobility, we make the simplifying assumption that all scientific mobility is \textit{symmetric} or without direction such that any move from an organization $A$ to organization $B$ is equivalent to a move from $B$ to $A$.
By assuming non-directional mobility, all mobility events are commensurate, meaning that they can be treated identically in our analysis--this allows us to represent the complexity of mobility without making decisions about the directional of their mobility or which is their main affiliation.
Moreover, this assumption has the practical advantage of matching the data format expected by the \textit{word2vec} model, as well as the theoretical advantage of adhering to the symmetricity assumption of the gravity model of mobility.

%
% S3 TEXT
\paragraph*{S3 Text}
\label{si:text:mobility_traj}
{\bf Building affiliation trajectories.}

For each mobile researcher who has at least two distinct affiliations, we construct an affiliation trajectory based on the affiliations listed on their published papers indexed in the Web of Science database between 2008 and 2019.
An author is considered mobile if they published with at least two distinct affiliations during the time period of study.
Affiliation names were manually disambiguated, and each was mapped to a unique organization identifier.
An affiliation trajectory for an individual researcher is a sequence of organizations in ascending order of year of publication.
if a researcher published papers with affiliation $A$ in year $t$, $B$ in $t+1$, $C$ in $t+2$ and $A$ again in $t+3$, then the affiliation trajectory is expressed as $(A, B, C, A)$.

In the case that an individual lists multiple affiliations in a single year, affiliations listed on publications published in that year are shuffled between each iteration of the \textit{word2vec} training process (each epoch).
For example, an author who published with affiliation $A$ in $t_{0}$, and affiliations $B$ and $C$ in $t_{1}$ could appear as one of $(A, B, C)$ or $(A, C, B)$ in each training iteration.
This effectively removes the effect of order within a year, as the order cannot be meaningfully established based on co-affiliations in a single paper, or on different affiliations listed on separate papers, for which its date of publication may not be representative of the actual completion of the project.

Other than restricting to only mobile researchers, we do not perform any filtering or reductions to affiliation trajectories.
In the case than an author publishes with organization $A$ four times in $t_{0}$, and affiliation $B$ two times in $t_{1}$, then their trajectory will be $(A, A, A, A, B, B)$.
Although mobile authors who publish more papers will have longer trajectories, \textit{word2vec} will skip duplicate consecutive organization IDs, mitigating the impact of long repetitive trajectories.

%
% S4 TEXT
\paragraph*{S4 Text}
\label{si:text:ppr_dist}
{\bf Network-based personalized page rank distances.}

We examine the gravity model on the Personalized Page Rank (PPR)\autocite{jeh2003scaling} as a benchmark on the network. We construct the co-occurrence network of $N$ organizations, in which each edge between organizations $i$ and $j$ represents a co-occurence of $i$ and $j$ in the same affiliation trajectory, with weight $W_{ij}$ given by the sum of the co-occurences over all researchers. and edges are co-occurrence between two organizations. The Personalized Page Rank is a ranking algorithm for nodes based on a random walk process on networks. 
The walker visiting at a node moves to a neighboring node chosen randomly with a probability proportionally to the weight of the edge in one step. Furthermore, with probability $\alpha$, the walker is teleported back to the starting node. The rank of a node is determined by the probability that the walker visits the node in the stationary state. The stationary distribution of the random walker starting from node $i$, denoted by $p_i=(p_{ik})$, is given by

\begin{equation}
	\label{eq:ppr}
	p_i = (1 - \alpha) v_i + \alpha p_i W,
\end{equation}
where $v_i$ is a column vector of length $N$ with entries that are all zero except the $i$th entry that equals to one, $W = (W_{ij})$ is the weighted adjacency matrix. We used $\alpha=0.9$ here.

 We can think $p_i$ as a representation vector of the organization $i$, and calculate the distance between organizations $i$ and $j$, $d_{ij}$ with measuring distance between $p_i$ and $p_j$ to examine the gravity law. We consider two distance measures in this analysis. The first one is cosine distance which is used for our embedding method, $d_{ij} = 1 - \frac{\bm{p}_{i} \cdot \bm{p}_{j}}{\lVert \bm{p}_{i} \rVert \lVert \bm{p}_{j} \rVert}$. Also, if we think $p_i$ as a discrete probability distribution, then we can consider Jensen–Shannon divergence (JSD), can be written as,

\begin{equation}
	\label{eq:JSD}
	d_{ij} = JSD(p_i||p_j) = \frac{1}{2}D_{KL}(p_i||m) + \frac{1}{2}D_{KL}(p_j||m),
\end{equation}

\begin{equation}
	\label{eq:KL}
	D_{KL}(p_i||m) = \sum^x p_{ix}\log\frac{p_{ix}}{m_x},
\end{equation}
where $m=\frac{1}{2}(p_i+p_j)$. We report the result with cosine distance ($R^2=0.14$, Fig. \ref{fig:supp:gravity_pprcos}) and  Jensen–Shannon divergence ($R^2=0.19$, Fig. \ref{fig:supp:gravity_pprjsd}). In both cases, the performance is under the performance of the model with geographical distance. Even though the length of the PPR vectors is extremely larger than the length of our embedding vectors, result with the embedding distance outperforms both of them.

%
% S5 TEXT
\paragraph*{S5 Text}
\label{si:text:organizations}
{\bf Organization disambiguation and metadata.}

Affiliations mapped to one of 8,661 organizations, disambiguated following that originally designed for the Leiden Rankings of World Universities~\autocite{waltman2012leidenrankings}.
Organizational records were associated with a full name, a type indicating the sector (e.g., University, Government, Industry), and an identifier for the country and city of the organization.
Sixteen different sector types were included in the analysis, which we aggregated to four high-level codes: \textit{University}, \textit{Hospital}, \textit{Government}, and \textit{Other}.
Each record was also associated with a latitude and longitude. 
However, for many organizations, these geographic coordinates were missing or incorrect. 
We manually updated the coordinates of 2,267 organizations by searching the institution name and city on Google Maps;
in cases where a precise location of the organization could not be identified, we used the coordinates returned when searching the name of the city.
The data was further enriched with country-level information, including region, most widely-spoken language, and its language family (e.g., the language family of \textit{Spanish} is \textit{Italic}).
State/province-level information was added using the reverse geocoding service LocationIQ using each organization's latitude and longitude as input.
Regional census classifications were added for states in the United States.
For each organization, we calculated size as the average number of unique authors (mobile and non-mobile) who published with that organization across each year of our dataset;
in the case that authors publish with multiple affiliations in a single year, they are counted towards each.

As a result of our disambiguation procedure, some affiliations are mapped to two organizations, one specific, and one more general.
For example, any author affiliated with ``Indiana University Bloomington'' will also be listed as being affiliated with the ``Indiana University System'', a more general designation for all public universities in Indiana.
However, a more general organization may not always occur alongside the more specific one.
For example, a researcher affiliated with the smaller regional school ``Indiana University South Bend'' will be listed as affiliated with only the ``Indiana University System''.
We identify all specific organizations that always co-occur along with a more general one.
For every career trajectory that includes one of these specific organizations, we remove all occurrences of the more general organization;
trajectories containing only a general designation are not altered.

%
% S6 TEXT
\paragraph*{S6 Text}
\label{si:text:disambiguation}
{\bf Author name dismabiguation.}

Author-name disambiguation, the problem of associating names on papers with individuals authors, remains difficult for the use of bibliometric data~\autocite{dangelo2020disambiguation}.
Authors in our dataset have been disambiguated using a rule-based algorithm that makes use of author and paper metadata, such as physical addresses, co-authors, and journal, to score papers on the likelihood of belonging to an author cluster---a cluster of publications believed to have been authored by the same individual~\autocite{caron2014disambiguation}.
We limit our period of analysis to the period of 2008 to 2019, as in 2008 the Web of Science began indexing additional author-level metadata such as full names and email addresses.
The disambiguation algorithm is conservative, favoring splitting clusters over merging.
Past studies have validated this data and shown that the disambiguated authors are comparable to ground-truth records such as those from ORCID and useful for a wide range of bibliometric studies~\autocite{sugimoto2017mostimpact, robinson2019mobility, chinchilla2018global, chinchilla2018travelban}.

%
% S7 TEXT
\paragraph*{S7 Text}
\label{si:text:network_ranking}
{\bf Reconstructing Times ranking with network measure.}

The performance of the embedding ranking in reconstructing the Times ranking is comparable to that of network-derived measures such as degree strength (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_times_compare}a) and eigencentrality centrality (Spearman's $\rho = 0.76$, Fig.~\ref{fig:supp:centrality_times_compare}b).
However, while both embedding- and network-based measures relate to university prestige, they are qualitatively and quantitatively different.
The embedding-ranking of U.S. universities is less correlated with degree strength (Spearman's $\rho = 0.45$, Fig.~\ref{fig:supp:centrality_semaxis_compare}a) and eigenvector  centrality (Spearman's $\rho = 0.55$) than with the Times ranking itself (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_semaxis_compare}b). 
The embedding ranking over-ranks large research-intensive universities such as North Carolina State University, University of Florida, and Texas A\&M University, whereas the network-derived ranking over-ranks smaller, more specialized universities such as Brandeis University, Yeshiva University, and University of San Francisco. 
This suggests that the embedding encodes information on prestige hierarchy at least as well as a network representation, with some noticeable qualitative differences.

%
% S8 TEXT
\paragraph*{S8 Text}
\label{si:text:boomerang_speculation}
{\bf Speculation on variations of the convex-curve pattern.}

The convex-curve pattern observed in Fig.~\ref{fig:length} repeats across many countries, with variations.
For example, the representative vector of Chinese organizations has a larger norm than that of the U.S. ($\bar{l} = 2.97$ vs $\bar{l} = 2.39$, Table~\ref{table:supp:norm}), causing its curve to be shifted upwards with a larger peak vector norm;
this may reflect a tendency for organizations in the U.S. to appear more frequently in different contexts than Chinese organizations.
Other nations such as Poland, Iran, and Turkey show a linear relationship between an organization's number of researchers and the vector norm, indicating that their largest organizations belong to very specific contexts (Fig.~\ref{fig:concave30}).
The organization-level distribution of vector norms reveals deeper heterogeneity.
The distribution of the vector norms for the U.S. is relatively skewed, suggesting their large norm is driven by a small and tight community of organizations (\textit{skew}$ = -0.82$, Fig.~\ref{fig:norm_dist}).
Germany and the U.K. have comparable representative vector norms to the U.S. ($\bar{l} = 2.6$ and $\bar{l} = 2.61$, respectively), with lower skewness (\textit{skew}$ = -0.63$ and \textit{skew}$ = -0.55$), suggesting more tight community of organizations.
The vector norms of organizations in some countries are even more skewed, such as in Iran ($\bar{l} = 3.57$, \textit{skew}$ = -2.13$) and China ($\bar{l} = 2.97$, \textit{skew}$ = -1.08$), indicating the strong difference between their most- and least-connected organizations.
For some countries, their organizations are positively-skewed, though seemingly for different reasons.
For example, Austria has a balanced distribution of organization vector norms, suggesting a diverse range of organizations with most being well connected ($\bar{l} =2.64$, $s = 0.18$);
Russia, in contrast, has a number of organization vectors of moderate norms, but also several isolated organizations with large vector norms ($\bar{l} = 3.08$, $s = 0.67$).

\newpage

% latex table generated in R 3.5.1 by xtable 1.8-2 package
% Thu Apr  2 13:43:00 2020
\begin{table}[ht]
\centering
\caption{\textbf{Full organization names}}
\label{table:supp:orglabels}
\begin{adjustwidth}{-2cm}{}
\begingroup\scriptsize
\begin{tabular}{llll}
  \hline
Short & Full & Short & Full \\
  \hline
Stanford & Stanford Univ & Northwestern & Northwestern Univ \\
  Columbia & Columbia Univ & Ball State & Ball State Univ \\
  Harvard & Harvard Univ & IU Bloomington & Indiana Univ, Bloomington \\
  UCLA & Univ of California, Los Angeles & Stevens Institute & Stevens Institute of Technology \\
  Cal State Long Beach & California State Univ, Long Beach & NJIT & New Jersey Institute of Technology \\
  Wright State & Wright State Univ & NYU & New York Univ \\
  U Toledo & Univ of Toledo & SUNY Albany & Univ at Albany, The State Univ of New York \\
  Boston U & Boston Univ & NY Medical College & New York Medical College \\
  Suffolk & Suffolk Univ & Miami University & Miami Univ \\
  CUNY & City Univ of New York (CUNY) & IU Pennsylvania & Indiana Univ of Pennsylvania \\
  U Arizona & Univ of Arizona & Baylor & Baylor College of Medicine \\
  OSU & Ohio State Univ & UT Health Center & Univ of Texas Health Science Center \\
  MIT & Massachusetts Institute of Technology & Bard College & Bard College \\
  Princeton & Princeton Univ & Stonehill College & Stonehill College \\
  GCU & Grand Canyon Univ & Carleton College & Carleton College \\
  Northcentral & Northcentral Univ & Hanover College & Hanover College \\
  UCSF & Univ of California, San Francisco & Queens College & Queens College \\
  Fielding & Fielding Graduate Univ & DePauw & DePauw College \\
  Pepperdine & Pepperdine Univ & Naval Academy & United States Naval Academy \\
  Argosy & Argosy Univ & Cal State San Marcos & California State Univ San Marcos \\
  Yale & Yale Univ & Broad Inst & Broad Institute \\
  U Hartford & Univ of Hartford & Forsyth Inst & Forsyth Institute \\
  FAU & Florida Atlantic Univ & U Alaska Museum & Univ of Alaska Museum of the North \\
  U Miami & Univ of Miami & Lawrence Berkeley & Lawrence Berkeley Natl Laboratory \\
  UWF & The Univ of West Florida & Allen Institute & Allen Institute for Brain Science \\
  FIT & Florida Institute of Technology & RTI International & RTI InterNatl \\
  Purdue & Purdue Univ, West Lafayette & Fermilab & Fermilab \\
  Notre Dame & Univ of Notre Dame & State of NY & State of New York \\
  Indiana State & Indiana State Univ & Mayo Clinic & Mayo Clinic \\
  Saint Mary's & Saint Mary's College & Fish and Wildlife & Fish and Wildlife Research Institute \\
  Tufts & Tufts Univ & EPA & United States Environmental Protection Agency \\
  Mattel & Mattel Children's Hospital & US Army & United States Army \\
  Clark & Clark Univ & NSF & Natl Science Foundation \\
  UMass Amherst & Univ of Massachusetts Amherst & US Navy & United States Navy \\
  Montclair & Montclair State Univ & US Air Force & United States Air Force \\
  Farleigh Dickinson & Fairleigh Dickinson Univ-Metro Campus & Ames Laboratory & Ames Laboratory \\
  Rockefeller & Rockefeller Univ & Olin College & Oin College of Engineering \\
  Adelphi & Adelphi Univ & Scrips Institute & Scrips Institute \\
  Barnard & Barnard College & Idaho Natl Lab & Idaho Natl Laboratory \\
  Saint John Fisher & Saint John Fisher College & Dana Faber & Dana Faber Cancer Institute \\
  U Penn & Univ of Pennsylvania & Dept of Agriculture & United States Department of Agriculture \\
  Villanova & Villanova Univ & DOE & United States Department of Energy \\
  Widener & Widener Univ-Main Campus & NIAMS & Natl Institute of Arthritis, Skin Diseases \\
  Robert Morris & Robert Morris Univ & JMI Labs & JMI Laboratories \\
  U Cincinnati & Univ of Cincinnati & Whitehead Inst & Whitehead Institute of Biomedical Research \\
  Case Western & Case Western Reserve Univ & Wellesley & Wellesley Univ\\
  Ashland & Ashland Univ & UT Health, San Antonio & Univ of Texas Health Science Center, San Antonio \\
  Texas A\&M & Texas A\&M Univ-Commerce & UNT & Univ of North Texas \\
  Texas Southern & Texas Southern Univ & UT Southwestern Med & Univ of Texas Southwestern Medical Center \\
  Baylor & Univ of Mary Hardin-Baylor & UT El Paso & Univ of Texas, El Paso \\
  U Washington & Univ of Washington - Seattle & USF & Univ of South Florida, Tampa \\
  Washington State & Washington State Univ & Florida A\&M & Florida Agricultural and Mechanical Univ \\
  Seattle Pacific & Seattle Pacific Univ & Barry & Barry Univ \\
  Cal State Fresno & California State Univ-Fresno & UMass Dartmouth & Univ of Massachusetts Dartmouth \\
  Northern Arizona & Northern Arizona Univ & Worcester Poly & Worcester Polytechnic Institute \\
  IUPUI & Indiana Univ - Purdue Univ Indianapolis & Umass Boston & Univ of Massachusetts Boston \\
  U Dayton & Univ of Dayton & MGH Inst & MGH Institute of Health Professions \\
  U Conn & Univ of Connecticut & Joseph W. Jones Center & Joseph W. Jones Ecological Research Center \\
  ASU & Arizona State Univ & Vaccine Research Center & Vaccine Research Center, San Diego \\
  U Florida & Univ of Florida & LA Ag Center & Lousianna Agricultural Center \\
  Northern Illinois & Northern Illinois Univ & FL Fish and Wildlife & Florida Fish and Wildlife Conservation Commission \\
  Concordia Chicago & Concordia Univ-Chicago & NHLBI & Natl Heart, Lung, and Blood Institute \\
  U Chicago & Univ of Chicago & NY Dept. of Health & New York Department of Health \\
  SIU Edwardsville & Southern Illinois Univ, Edwardsville & St Michaels & Saint Michaels College \\
  SIU Carbondale & Southern Illinois Univ, Carbondale &  &  \\
   \hline
\end{tabular}
\endgroup
\end{adjustwidth}
\end{table}

\newpage

\begin{table}[]
\centering
\caption{\textbf{L2 Norm of country's representative vectors}.
			 Shown for top 30 countries with the most unique mobile and non-mobile researchers}
\label{table:supp:norm}
\begin{tabular}{lrr}
\textbf{Country} & \textbf{L2 Norm} & \textbf{\# Organizations} \\ \hline
United States    & 2.39             & 1281                      \\
Germany          & 2.6              & 485                       \\
United Kingdom   & 2.61             & 514                       \\
Austria          & 2.64             & 74                        \\
France           & 2.83             & 688                       \\
Belgium          & 2.84             & 84                        \\
Switzerland      & 2.85             & 66                        \\
Spain            & 2.94             & 322                       \\
China            & 2.97             & 497                       \\
India            & 2.99             & 114                       \\
Poland           & 3.02             & 145                       \\
Canada           & 3.02             & 147                       \\
Italy            & 3.04             & 386                       \\
Russia           & 3.08             & 187                       \\
Norway           & 3.1              & 122                       \\
Netherlands      & 3.11             & 136                       \\
Sweden           & 3.16             & 75                        \\
Brazil           & 3.16             & 286                       \\
Finland          & 3.17             & 66                        \\
Denmark          & 3.21             & 54                        \\
Czech Republic   & 3.23             & 97                        \\
Greece           & 3.24             & 62                        \\
Australia        & 3.24             & 90                        \\
Turkey           & 3.28             & 99                        \\
South Korea      & 3.28             & 156                       \\
Israel           & 3.32             & 71                        \\
Portugal         & 3.33             & 57                        \\
Japan            & 3.35             & 465                       \\
Iran             & 3.57             & 68                        \\
Taiwan           & 3.67             & 72
\end{tabular}
\end{table}

\newpage

%
% Figure - publications over time
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Descriptive/pubs_over_time.pdf}
	\caption{
		\textbf{Publications over time.}
		\textbf{a.}
		The number of papers published by mobile authors has been steadily increasing from 2008 to 2017, with a small decrease in 2018,  which may be due to an artifact of the Web of Science indexing process.
		Lines correspond to publications by mobile authors, by authors with affiliations in at least two cities, at least two regions, and at least two countries.
		We did not find major changes in the publication patterns of mobile authors during this time period.
		\textbf{b.}
		Lines correspond to the proportion of publications classified as Biology and Health (black), Physics and Engineering (purple), Life and Earth Science (magenta), Social Science and Humanities (orange), and Math and Computer Science (yellow).
		The rate of publication in Biology and Health has leveled since about 2013, whereas the rate of publication in other fields has steadily increased.
		\textbf{c.}
		While the absolute count of publications has increased, the percentage of mobile scholars, and those with affiliations in at least least two cities, regions, or countries, as a proportion of all publications, has decreased over time.
		\textbf{d.}
		The proportion of authors' publications across fields has largely remained steady.
		Biology and Health Science has comprised the majority of publications across nearly all years but has steadily declined in proportion.
		However, the proportion of Social Science and Humanities publications has been steadily increasing.
	}
	\label{fig:supp:pubs_over_time}
\end{figure}

%
% Figure - descriptives
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Descriptive/mobility_by_country.pdf}
	\caption{
		\textbf{Extent and nature of mobility by country.}
		\textbf{a.}
		The proportion of all mobile researchers contributed by each country. 
		Over 30\% of all mobile researchers have been affiliated with organizations in the U.S. during the period of study.
		\textbf{b.}
		Cumulative distribution of data shown in (\textbf{a}).
		The U.S., China, and France, the U.K., and Germany comprise about 70\% of all mobile researchers. 
		\textbf{c.} 
		The proportion of each country's researchers who are mobile.
		The dashed line indicates the proportion of all researchers in the data who are mobile. 
		France, followed by Qatar and the U.S. have the highest proportion of mobile researchers. 
		\textbf{d.} First two principal components of four variables: proportion of researchers in each country mobile across organizations, proportion mobile across cities, proportion mobile across regions, and proportion mobile across countries.
		The countries are roughly sorted in order of the number of mobile researchers and the fraction of international mobile researchers in the first and second principal components, which are indicated by PC1 and PC2, respectively. 
		PC1 explains 88.3\% of the total variance, whereas PC2 explains 9.5\% of the total variance. 
	}
	\label{fig:supp:descriptives}
\end{figure}

\newpage
%
% Figure - reverse CDF by scale
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=0.8\textwidth]{\figdir/Descriptive/rcdf_by_scale.pdf}
	\caption{
		\textbf{Reverse cumulative-distribution function of mobile researchers by geographic scale.}
		\textbf{a.}
		Survival probability of mobile researchers with respect to the number of organizations in the their affiliation trajectory.
		All mobile authors were affiliated with at least two organizations (i.e., survival probability of one) and about 35.0\% were affiliated with three or more. 
		\textbf{b.} About 68\% of mobile authors listed at least two cities represented in their career trajectories.
		\textbf{c.} 45\% of mobile authors have two or more regions represented in their career trajectories.
		\textbf{d.} Only 14\% of mobile authors had two or more countries represented in their career trajectories.
	}
	\label{fig:supp:rcdf_by_scale}
\end{figure}

%
% Figure - Hyperparameter performance
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Descriptive/hyperparameter_performance.pdf}
	\caption{
		\textbf{Larger dimensions, smaller window size improves embedding performance.}
		The correlation, or amount of flux explained by the embedding distance with varying skip-gram negative sampling hyperparameters.
		Window size refers to $w$, the size of the context window that defines the context in a trajectory.
		Smaller window sizes result in an embedding that explain more flux.
		Embedding dimensions refer to the size of the embedding vector.
		Larger vectors perform better, though little difference between 200 and 300.
		All variants perform better on same-country pairs of organizations than on all organizations.
		All variants perform worse on different-country pairs on organizations.
		Embeddings with larger dimensions outperform mid-size embeddings for the different-country case.
	}
	\label{fig:supp:cosdot}
\end{figure}

%
% Figure - Dot product and cosine similarity
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Math/d300_ws1_dot_cosine.pdf}
	\caption{
		\textbf{Cosine distance is correlated with dot product similarity.}
		We find a relatively high correlation between the embedding distance---one minus the cosine similarity---and the dot product similarity between organization vectors ($R^2 = 0.73$).
		Color of each hex bin indicates the frequency of organization pairs. 
		Black dots indicate the mean dot product similarity averaged over binned sets at the same embedding distance.
		Red line is line of best fit.
	}
	\label{fig:supp:hyperparams}
\end{figure}

%
% Figure - Geographic predictions, by model
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance_geo_bymodel.pdf}
	\caption{
		\textbf{For geographic distance, the power-decay gravity model is better.}
		Flux between organization pairs predicted by the gravity model with different distance decay functions, i.e., exponential decay function (\textbf{a}) and power-law decay function (\textbf{b}) using geographic distance.
		Boxplots show distribution of actual flux for binned values of predicted flux.
		Box color corresponds to the degree to which the distribution overlaps with $x = y$; 
		a perfect prediction yields all points on the black line.
		Shown for all pairs of organization (\textbf{a-b}), domestic (\textbf{c-d}), and international only (\textbf{e-f}) mobility.
		The gravity model with the power-decay function outperforms that with an exponential decay function.
	}
	\label{fig:supp:predict_geo_bymodel}
\end{figure}

%
% Figure - Embedding predictions, by model
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance_emb_bymodel.pdf}
	\caption{
		\textbf{For geographic distance, the power-decay gravity model is better.}
		Flux between organization pairs predicted by the gravity model with different distance decay functions, i.e., exponential decay function (\textbf{a}) and power-law decay function (\textbf{b}) using embedding distance.
		Boxplots show distribution of actual flux for binned values of predicted flux.
		Box color corresponds to the degree to which the distribution overlaps with $x = y$; 
		a perfect prediction yields all points on the black line.
		Shown for all pairs of organization (\textbf{a-b}), domestic (\textbf{c-d}), and international only (\textbf{e-f}) mobility.
		The gravity model with the exponential decay function outperforms that with a power-decay function.
	}
	\label{fig:supp:predict_emb_bymodel}
\end{figure}

%
% Figure - gravity correlation
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_correlations.pdf}
	\caption{
		\textbf{Embedding distance explains more variance for global, within, and across country flux than geographic distance.}
		\textbf{a.}
		Embedding distance explains more flux than geographic distance (\textbf{b}).
		Red line is the line of best fit.
		Black dots are mean flux across binned distances.
		Color of each hex bin indicates frequency of organization pairs.
		Results here are identical to those shown in Fig.~\ref{fig:gravity_performance}a and Fig.~\ref{fig:gravity_performance}.
		\textbf{c-d.}	embedding distance explains more variance when considering only within-country organization pairs.
		\textbf{e-f.} embedding distance is more robust than geographic distance when considering only across-country organization pairs.
	}
	\label{fig:supp:gravity_correlation}
\end{figure}

%
% Figure - gravity predictions based on subset or global
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_different_fits.pdf}
	\caption{
		\textbf{Little difference between gravity predictions fit on all or subsets of data.}
		Predictions of flux between organization pairs made using embedding distance out-performs those made using geographic distance.
		Boxplots show distribution of actual flux for binned values of predicted flux.
		Box color corresponds to the degree to which the distribution overlaps the line $x = y$; 
		a perfect prediction yields all points on the black line.
		\textbf{a-b.} Predictions are made with parameters estimated from all pairs of organizations (as in Fig.~\ref{fig:gravity_performance}c), and showing only the subsets of predictions for organization pairs in the same country (\textbf{a}) and in different countries (\textbf{b}).
		\textbf{c-d.} Predictions made using parameters estimated from the subset of organizations in the same country (\textbf{c}) and different country \textbf{d});
		this is the same data as shown in Fig.~\ref{fig:gravity_performance}f and Fig.~\ref{fig:gravity_performance}h.
	}
	\label{fig:supp:gravity_prediction_subsets}
\end{figure}

%
% Figure - Dot product distance
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_dot.pdf}
	\caption{
		\textbf{Examine gravity model with dot product on the embedding space.}
		Performance of dot product similarities in explaining and predicting mobility.
		Similarity scores are calculated as the pairwise dot product between organizational vectors.
		Dot product similarity performs better than geographic distance, though worse than cosine similarity in explaining global mobility (\textbf{a}), or domestic (\textbf{b}) or international (\textbf{c}) country mobility.
		Red line is line of best fit.
		Black dots are mean flux across binned distances.
		Color indicates frequency of organization pairs within each hex bin.
		Similarly, PPR distance performs comparably to geographic distance in predicting global (\textbf{d}), domestic (\textit{e}) and international (\textbf{f}) scientific mobility.
		Boxplots show distribution of actual flux for binned values of predicted flux.
		Box color corresponds to the degree to which the distribution overlaps $x = y$;
		a perfect prediction yields all points on the black line.
	}
	\label{fig:supp:gravity_dot}
\end{figure}

%
% Figure - PPR with COSINE DISTANCE gravity model and predictions
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_pprcos.pdf}
	\caption{
		\textbf{Personalized page rank with cosine distance.}
		Performance of personalized page rank scores in explaining and predicting mobility.
		Personalized page rank is calculated for the underlying mobility network, and distance measured as the cosine distnace between PPR probability distribution vectors.
		PPR cosine distance performs roughly similar to geographic distance in explaining global(\textbf{a}), domestic (\textbf{b}), or international (\textbf{c}) country mobility.
		Red line is the line of best fit.
		Black dots indicate the mean flux across binned distances.
		Color of hex bind indicates frequency of organization pairs.
		Similarly, PPR distance performs comparably to geographic distance in predicting global (\textbf{d}), domestic (\textit{e}) and international (\textbf{f}) scientific mobility.
		Boxplots show distribution of actual flux for binned values of predicted flux.
		Box color corresponds to the degree to which the distribution overlaps $x = y$;
		a perfect prediction yields all points on the black line.
	}
	\label{fig:supp:gravity_pprcos}
\end{figure}

%
% Figure - PPR with JSD gravity model and predictions
%

\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_pprjsd.pdf}
	\caption{
		\textbf{Personalized page rank with Jensen-Shannon Divergence.}
		Performance of personalized page rank scores in explaining and predicting mobility.
		Personalized page rank is calculated for the underlying mobility network, and distance measured as the Jensen-Shannon Divergence (JSD) between PPR probability distribution vectors.
		PPR JSD performs roughly similar to geographic distance in explaining global mobility (\textbf{a}), or domestic (\textbf{b}) or international (\textbf{c}) country mobility.
		Overall, PPR JSD explains more variance in mobility than using cosine distance (Fig.~\ref{fig:supp:gravity_pprcos}), except for international mobility, for which cosine similarity out-performs JSD.
		Red line is the line of best fit.
		Black dots are mean flux across binned distances.
		Color of hex bind indicates frequency of organization pairs.
		Similarly, PPR JSD performs comparably to geographic distance in predicting global (\textbf{d}), domestic (\textit{e}) and international (\textbf{f}) scientific mobility.
		Boxplots show distribution of actual flux for binned values of predicted flux.
		Box color corresponds to the degree to which the distribution overlaps $x = y$;
		a perfect prediction yields all points on the black line. 
	}
	\label{fig:supp:gravity_pprjsd}
\end{figure}

%
% Figure - Global Network Projection
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Projection/co_occur_with_label.pdf}
	\caption{
		\textbf{Visualization of global mobility network.}
		The network demonstrates country-level structure, but not at the detail or the extent of the global UMAP projection (Fig.~\ref{fig:projection}a).
		Each node corresponds to an organization, whereas  weighted edges (not shown) correspond to the flow of mobile researchers between the two organization.
		Nodes are colored by the country of the organization.
		Nodes are positioned using the Force Atlas layout algorithm.
	}
	\label{fig:supp:network_vis}
\end{figure}

%
% Figure - New York Projection
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_New_York.pdf}
	\caption{
		\textbf{UMAP Projection of organizations in New York.}
		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019.
		Color indicates the sector.
	}
	\label{fig:supp:proj_newyork}
\end{figure}

%
% Figure - Pennsylvania Projection
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_Pennsylvania.pdf}
	\caption{
		\textbf{UMAP Projection of organizations in Pennsylvania.}
		UMAP projection of the embedding space of organizations in Pennsylvania reveals clustering based on geography, sector, and academic prestige.
		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019.
		Color indicates the sector.
	}
	\label{fig:supp:proj_pennsylvania}
\end{figure}

%
% Figure - Texas Projection
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_Texas.pdf}
	\caption{
		\textbf{UMAP Projection of organizations in Texas.}
		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019.
		Color indicates the sector.
	}
	\label{fig:supp:proj_texas}
\end{figure}

%
% Figure - California Projection
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_California.pdf}
	\caption{
		\textbf{UMAP Projection of organizations in California.}
		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019.
		Color indicates the sector.
	}
	\label{fig:supp:proj_california}
\end{figure}

%
% Figure - SemAxis results
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_compare_fig.pdf}
	\caption{
		\textbf{SemRank hierarchy is robust.}
		\textbf{a.} Spearman's $\rho$ ($n = 143$) between Times prestige rank and embedding rank derived using SemAxis, with poles defined using the top and bottom (geographically matched) ranked universities.
		Black points show spearman correlation using all organizations; white points show correlation using only universalizes not aggregated in the poles.
		Including more universities improves performance, but quickly saturates after around five universities.
		\textbf{b - f.} Comparison between the Times and SemAxis ranks of universities, by the number of universities used to define the poles (n).
		White points are those top and bottom 20 universities aggregated to define the ends of the axis.
		The grey box corresponds to the top 20 and bottom 20 ranks.
	  	Spearman's $\rho$ details the estimate from Spearman correlation between the two rankings using all universities, including those used to define the ends of each axis.
	}
	\label{fig:supp:semaxis_compare}
\end{figure}

%
% Figure - Network Centrality vs. Times
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/centrality_times_compare.pdf}
	\caption{
		\textbf{Network centrality is strongly correlated with Times ranking.}
		Comparison between the ranking of organizations by their network-centrality rank and their rank in the 2018 Times Higher Education ranking of U.S. Universities .
		The Times rank is correlated with degree centrality rank (\textbf{a}) with Spearman's $\rho = 0.73$, and is correlated with the eigenvector centrality rank (\textbf{b}) with Spearman's $\rho = 0.76$.
	}
	\label{fig:supp:centrality_times_compare}
\end{figure}

%
% Figure - Network Centrality vs. SemAxis
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_network_compare.pdf}
	\caption{
		\textbf{Network centrality less correlated with Embedding rank.}
		Comparison between the ranking of organizations by their network-centrality rank and the embedding rank derived with SemAxis with poles defined using the top five to geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S. Universities .
		Embedding rank is correlated with degree centrality rank (\textbf{a}) with Spearman's $\rho = 0.45$, and is correlated with the eigenvector centrality rank (\textbf{b}) with Spearman's $\rho = 0.55$.
	}
	\label{fig:supp:centrality_semaxis_compare}
\end{figure}

%
% Figure - SemAxis By State
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_states_fig.pdf}
	\caption{
		\textbf{Geography and prestige SemAxis by U.S. state.}
		SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S. Universities (bottom to top).
		Points correspond to universities shown for California (\textbf{a}), Arizona (\textbf{b}), Washington (\textbf{c}), Massachusetts (\textbf{d}), Connecticut (\textbf{e}), New York (\textbf{f}), Texas (\textbf{g}), Pennsylvania (\textbf{h}), and Florida (\textbf{i}).
		Grey points correspond to all other U.S. universities.
		Full organization names listed in Table~\ref{table:supp:orglabels}.
	}
	\label{fig:supp:semaxis_states}
\end{figure}

%
% Figure - SemAxis By State
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/sector_rank_comparison.pdf}
	\caption{
		\textbf{SemAxis reconstructs publication impact in non-university sectors.}
		Comparison between the ranking of organizations in each non-university sector by their citation impact and the embedding rank.
		Citation impact is calculated as the mean-normalized citation score using papers published in the Web of Science database between 2008 and 2019. 
		The embedding rank is derived by first projecting non-university organizations onto the SemAxis axis formed with poles defined using the top five to geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S. Universities.
		\textbf{a} Shows how the correlation between the citation impact and SemAxis rankings differ while varying the size threshold for including an organization.
		Size is calculated as the mean annualized number of unique authors publishing with that organization. 
		Annotations show the number of organizations remaining at thresholds pf 0, 50, and 100. 
		\textbf{b}. Comparison of organizations using a size threshold of 10 for regional and liberal arts colleges, and 50 for research institutes and government organizations;
		these thresholds were chosen as points thresholds of stability in \textbf{a}. 		
		The impact rank is correlated with the embedding rank for regional and liberal arts colleges with Spearman's $\rho = 0.49 (n = 48)$, research institutes with Spearman's $\rho = 0.58 (n = 159)$, and for government organizations with Spearman's $\rho = 0.36 (n = 55)$. 
	}
	\label{fig:supp:sector_semaxis_impact}
\end{figure}

%
% Figure - SemAxis By Sector
%
%\begin{figure}[hp!]
%	\centering
%	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_sectors_fig.pdf}
%	\caption{
%		\textbf{Geography and prestige SemAxis in U.S. by Sector.}
%		SemAxis projection along two axes, comparing California to Massachusetts universities (left to r%ight), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 %Times Higher Education ranking of U.S. Universities (bottom to top).
%		Points correspond to organizations labeled as Government (\textbf{a}), Institute (\textbf{b}), and %Teaching (\textbf{c}), corresponding to government organizations, research institutes, and teaching o%rganizations, respectively.
%		Grey points correspond to all U.S. universities.
%	    	Full organization names listed in Table~\ref{table:supp:orglabels}.
%	}
%	\label{fig:supp:semaxis_sectors}
%\end{figure}

%
% Figure - length by factors
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Math/l2_org_meta.pdf}
	\caption{
		\textbf{Factors relating to the L2 norm of vectors for U.S. universities}
		Correlation between the L2 norm of organization embedding vectors of U.S. universities and characteristics of U.S. universities.
		Dots correspond to organizations.
		The red line is the line of  the best fit with corresponding 99\% confidence intervals.
		Red text is the regression estimate.
		The blue line is the loess regression line with 99\% confidence intervals.
		Number of authors is the average annual count of unique mobile and non-mobile authors.
		Rankings are derived from the Times Ranking of World Universities, and the Leiden Rankings of Universities.
		Remaining variables come from the Carnegie Classification of Higher Education Institutions.
		The factors that best explain $s_i$ are the number of authors, the rank, the amount of Science and Engineering (S\&E) funding, and the number of doctorates granted.
	}
	\label{fig:supp:length_vs_metaInfo}
\end{figure}

%
% Figure - Concave-curves countries
%
\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Math/boomerang_30_countries.pdf}
	\caption{
		\textbf{Concave-curve repeats across most of 30 countries with most researchers.}
		Size (L2 norm) of organization embedding vectors compared to their number of researchers for U.S. universities.
		Loess regression line is shown for each country with 99\% confidence intervals.
		Countries shown are the 30 with the largest number of total unique mobile and non-mobile researchers.
	}
	\label{fig:concave30}
\end{figure}

%
% Figure - Norm distribution by country
%
\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Math/l2_org_dist.pdf}
	\caption{
		\textbf{Distribution of organization embedding vector norms by country.}
		Histogram showing the distribution of L2 norm values of organization embedding vectors in each of the 30 countries with the largest number of total unique mobile and non-mobile researchers.
		Text in each panel shows the number of organizations in the country (n) and the GINI index of inequality of the distribution (g);
		a small GINI index indicates that the L2 norms of organizations are more balanced, whereas a high GINI value indicates that they are more unequal.
	}
	\label{fig:norm_dist}
\end{figure}

\clearpage
\printbibliography{}

\end{document} %}}}

### 2020-10-08 paper/current/main.tex
add korea dataset

@@
 The critical importance of understanding mobility in many socio-economic phenomena thus compel alternative frameworks for mobility.
-Here, using a massive dataset of scientific mobility and U.S.
-flight itineraries, we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective functional distance that reflects the multi-faced structure of human mobility.
+Here, using a massive dataset of scientific mobility, U.S.
+flight itineraries and Korean accommodation reservation, we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective functional distance that reflects the multi-faced structure of human mobility.
 Focusing on the case of scientific mobility, we show that embeddings of scientific organizations discovers cultural and linguistic relations at multiple levels of granularity, and even academic prestige.
@@
 Each itinerary is associated with an origin, destination, and passenger and ticket metadata.
+
+\subsection*{Korean accommodation reservation data}
+We source Korean accommodation reservation data from collaboration with Good Choice Company in Korea.
+Each trajectory is the sequence of reserved accommodation in Seoul, South Korea between 2018.08.01 ~ 2020.07.31, comprising 938,962 trajectories between 1,038 unique accommodations.
 

### 2020-10-08 paper/current/main.tex
add  korea dataset on maintext

@@
 Here, we apply a neural embedding framework to real-world mobility trajectories and demonstrate that it can encode the complex landscape of human mobility into a dense, continuous, and meaningful vector-space representation, from which we can not only derive a meaningful \textit{functional distance} between places but also probe relationships based on culture, language, and even prestige along with geographic relationship.
-We leverage two massive datasets: a dataset of U.S. passenger flight itinerary records, and a dataset of scientists' career mobility between organizations captured in bibliometric records. 
+We leverage three massive datasets: a dataset of U.S.
+passenger flight itinerary records, Korean accommodation reservation records, and a dataset of scientists' career mobility between organizations captured in bibliometric records.
 In particular, we focus on scientific mobility due to its richness and importance.
@@
 A trajectory is constructed for each passenger flight itinerary, forming an ordered sequence of unique identifiers of the origin and destination airports. 
+The Korean accommodation reservation records consist of accommodation reservation history between 2018 and 2020 between 1,038 unique accommodation in Seoul, South Korea.
+A trajectory is constructed for each customer's accommodation reservation history, constructing an ordered sequence of unique commendation with accurate location information.
 Although more complex, trajectories of scientific mobility are constructed in a similar fashion. 
@@
 We source Korean accommodation reservation data from collaboration with Good Choice Company in Korea.
-Each trajectory is the sequence of reserved accommodation in Seoul, South Korea between 2018.08.01 ~ 2020.07.31, comprising 938,962 trajectories between 1,038 unique accommodations.
+Each trajectory is the sequence of reserved accommodation in Seoul, South Korea between 2018.08.01 ~ 2020.07.31, comprising 938,962 trajectories consist of  1,038 unique accommodations.
 

### 2020-10-08 paper/current/main.tex
adding authors"

@@
 \def\SI{Supporting Information}
-
+\usepackage{authblk}
 %}}}
@@
 \title{Unsupervised embedding of trajectories captures the latent structure of mobility} %{{{
+\author[1,4]{Dakota Murray}
+\author[1, 2, 4]{Jisung Yoon}
+\author[1]{Sadamori Kojaku}
+\author[3]{Rodrigo Costas}
+\author[2]{Woo-Sung Jung}
+\author[1]{Staša Milojević \thanks{smilojev@indiana.edu}}
+\author[1]{Yong-Yeol Ahn \thanks{yyahn@iu.edu}}
+
+\affil[1]{Center for Complex Networks and Systems Research, Luddy School of Informatics, Computing, and Engineering, Indiana University, Bloomington, IN 47408, USA}
+\affil[2]{Department of Industrial and Management Engineering, Pohang University of Science and Technology,
+Pohang 37673, Republic of Korea.}
+\affil[3]{Centre for Science and Technology Studies (CWTS), Leiden University, P.O. Box 905,
+2300 AX Leiden, The Netherlands}
+\affil[4]{These authors contributed equally: Jisung Yoon, Dakota Murray.}
+
 \date{\today}

### 2020-10-08 workflow/scripts/PlotGravityLawRelationshipSecondary.R
generalize secondary data plotting

@@ -141,9 +141,10 @@ plot <- dist %>%
 # Add an x-axis scale based on the type of distance metric being used
 #
 if (opt$distance == "geo") {
+  max.dist = max(dist$distance)
   plot <- plot +
-    scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5),
-                       limits = c(0, 5),
+    scale_x_continuous(breaks = seq(0, ceiling(max.dist), 1),
+                       limits = c(0, ceiling(max.dist)),
                        labels = function(x) { parse(text=paste0("10^", x)) },
                        expand = c(0, 0)
                      )

### 2020-10-08 paper/current/main.tex
minor tweaks

--- 2020-10-08 paper/current/main.tex
@@
 \def\mat#1{\mathbf{#1}}
+
+% Figure captions
+\usepackage{caption}
+\captionsetup{justification=raggedright,singlelinecheck=false,font=small}
 
@@
 The critical importance of understanding mobility in many socio-economic phenomena thus compel alternative frameworks for mobility.
-Here, using a massive dataset of scientific mobility, U.S.
-flight itineraries and Korean accommodation reservation, we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective functional distance that reflects the multi-faced structure of human mobility.
+Here, using a massive dataset of scientific mobility and U.S.
+flight itineraries, we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective functional distance that reflects the multi-faced structure of human mobility.
 Focusing on the case of scientific mobility, we show that embeddings of scientific organizations discovers cultural and linguistic relations at multiple levels of granularity, and even academic prestige.
@@
 
-where $m_{i}$ is the population of locations $i$,  $f(r_{ij})$ is a decay function with respect to distance between locations, and $C$ is a constant estimated from data (see Data and Methods). 
+where $m_{i}$ is the population of locations $i$,  $f(r_{ij})$ is a decay function with respect to distance between locations, and $C$ is a constant estimated from data (see Methods). 
 For the flight itinerary data, we use population $m_{i}$ as the total number of unique passenger on each airport, and for scientific mobility, we use the mean annual number of of unique mobile and non-mobile authors who affiliated with each organization.
@@
 In the case flight itineraries, the embedding distance explains more than twice the expected flux between airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}a) than does geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
-We fit the gravity model given by Eq.~\ref{eq:gravity_basic} (see Data and Methods) and computed the expected flux  $\hat{T}_{ij}$ using the geographic distance and the embedding distance as parameters.
+We fit the gravity model given by Eq.~\ref{eq:gravity_basic} (see Methods) and computed the expected flux  $\hat{T}_{ij}$ using the geographic distance and the embedding distance as parameters.
 The embedding distance produces better predictions of actual flux between airports than does the geographic distance (Fig.~\ref{fig:gravity_performance}c-d).
@@
 %
-\section*{Data and Methods}
+\section*{Methods}
 \label{sec:datamethods} %{{{
@@
 Each itinerary is associated with an origin, destination, and passenger and ticket metadata.
-
-\subsection*{Korean accommodation reservation data}
-We source Korean accommodation reservation data from collaboration with Good Choice Company in Korea.
-Each trajectory is the sequence of reserved accommodation in Seoul, South Korea between 2018.08.01 ~ 2020.07.31, comprising 938,962 trajectories between 1,038 unique accommodations.
 
@@
 
+\clearpage 
+\newpage
+
 %

### 2020-10-08 paper/current/main.tex
formatting author block
adjust supplemental formatting
edit intro, update results

@@
 % CUSTOM MACROS
+\usepackage{ marvosym }
 
@@
 
+\renewcommand\Authfont{\fontsize{12}{14.4}\selectfont}
+\renewcommand\Affilfont{\fontsize{9}{10.8}\itshape}
+
 \begin{document} %{{{
 \title{Unsupervised embedding of trajectories captures the latent structure of mobility} %{{{
-\author[1,4]{Dakota Murray}
-\author[1, 2, 4]{Jisung Yoon}
+\author[1,\Yinyang]{Dakota Murray}
+\author[1,2,\Yinyang]{Jisung Yoon}
 \author[1]{Sadamori Kojaku}
@@
 2300 AX Leiden, The Netherlands}
-\affil[4]{These authors contributed equally: Jisung Yoon, Dakota Murray.}
+\affil[\Yinyang]{These authors contributed equally: Jisung Yoon, Dakota Murray.}
 
@@
 Here, using a massive dataset of scientific mobility, U.S.
-flight itineraries and Korean accommodation reservation, we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective functional distance that reflects the multi-faced structure of human mobility.
+flight itineraries, and South Korean accommodation reservations, we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective functional distance that reflects the multi-faced structure of human mobility.
 Focusing on the case of scientific mobility, we show that embeddings of scientific organizations discovers cultural and linguistic relations at multiple levels of granularity, and even academic prestige.
@@
 Here, we apply a neural embedding framework to real-world mobility trajectories and demonstrate that it can encode the complex landscape of human mobility into a dense, continuous, and meaningful vector-space representation, from which we can not only derive a meaningful \textit{functional distance} between places but also probe relationships based on culture, language, and even prestige along with geographic relationship.
-We leverage three massive datasets: a dataset of U.S.
-passenger flight itinerary records, Korean accommodation reservation records, and a dataset of scientists' career mobility between organizations captured in bibliometric records.
+We leverage three massive datasets: U.S.
+passenger flight itinerary records, South Korean accommodation reservations, and a dataset of scientists' career mobility between organizations captured in bibliometric records.
 In particular, we focus on scientific mobility due to its richness and importance.
@@
 A trajectory is constructed for each passenger flight itinerary, forming an ordered sequence of unique identifiers of the origin and destination airports. 
-The Korean accommodation reservation records consist of accommodation reservation history between 2018 and 2020 between 1,038 unique accommodation in Seoul, South Korea.
+The Korean accommodation reservations consist of accommodation reservation history between 2018 and 2020 between 1,038 unique accommodation locations in Seoul, South Korea.
 A trajectory is constructed for each customer's accommodation reservation history, constructing an ordered sequence of unique commendation with accurate location information.
@@
 We show that the embedding distance, compared with the geographical distance, predicts actual mobility flows. 
-In the case flight itineraries, the embedding distance explains more than twice the expected flux between airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}a) than does geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
+In the case flight itineraries, the embedding distance explains more than twice the expected flux between airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}a) than does geographic distance ($R^{2} = 0.22$).
 We fit the gravity model given by Eq.~\ref{eq:gravity_basic} (see Methods) and computed the expected flux  $\hat{T}_{ij}$ using the geographic distance and the embedding distance as parameters.
-The embedding distance produces better predictions of actual flux between airports than does the geographic distance (Fig.~\ref{fig:gravity_performance}c-d).
+The embedding distance produces better predictions of actual flux between airports than does the geographic distance (Fig.~\ref{fig:gravity_performance}b).
+The neural embedding also performs well in a smaller geographic context:
+In the case of South Korean hotel accommodations, such that the embedding distance better explains the expected flux ($R^{2} = 0.57$, Fig.~\ref{fig:gravity_performance}c) than does geographic distance ($R^{2} = 0.25$), and predictions made using embedding distance outperform those made with geographic distance (Fig.~\ref{fig:gravity_performance}d).
 These results are consistent in the case of scientific mobility. 
-The amount of variance in the expected flux explained by the embedding distance ($R^{2} = 0.48$, Fig.~\ref{fig:gravity_performance}e) is again more than double that explained by the geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}f).
+The amount of variance in the expected flux explained by the embedding distance ($R^{2} = 0.48$, Fig.~\ref{fig:gravity_performance}e) is again more than double that explained by the geographic distance ($R^{2} = 0.22$).
 This pattern holds when considering the subset of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d).
 As with flight itineraries, we fit the gravity model on the scientific mobility data using the gravity model.
-Predictions made using the embedding distance outperform those made using the geographic distance (Fig.~\ref{fig:gravity_performance}g-h), which also holds for the subsets of only domestic and only international mobility (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}).
+Predictions made using the embedding distance outperform those made using the geographic distance (Fig.~\ref{fig:gravity_performance}f), which also holds for the subsets of only domestic and only international mobility (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}).
 For scientific mobility, the embedding distance defined from the cosine distance between vectors also outperforms that defined from their dot product ($R^{2} = 0.34$, Fig.~\ref{fig:supp:gravity_dot}).
 The embedding distance also out-performs alternative ``diffusion-based'' network distance measures such as the personalized-page rank scores (see \SI) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-Our results demonstrate that the embedding distance better captures patterns of actual mobility than does the geographic distance across datasets.
+Our results demonstrate that the embedding distance better captures patterns of actual mobility than does the geographic distance across domains.
 
@@
 	\caption{
-		\textbf{Embedding distance encodes functional distance and better predicts U.S flights and global scientific mobility.}
-		\textbf{a-b.} Embedding distance (cosine distance between organization vectors) better explains the expected flux of passengers between U.S. airports than does geographic distance. 
+		\textbf{Embedding distance encodes functional distance and better predicts U.S flights, accommodation reservations, and global scientific mobility.}
+		\textbf{a} Embedding distance (cosine distance between organization vectors, top) better explains the expected flux of passengers between U.S. airports than does geographic distance (bottom). 
 		The red line is the line of the best fit.
@@
 		The lightness of each hex bin indicates the frequency of organization pairs within it.
-		\textbf{c-d.} Predictions of flux between airport pairs made using embedding distance outperform those made using geographic distance. 
+		\textbf{b} Predictions of flux between airport pairs made using embedding distance (top) outperform those made using geographic distance (bottom). 
 		Boxplots show distribution of actual flux for binned values of predicted flux.
@@
 		Results are consistent in the case of scientific mobility. 
-		\textbf{e-f.} Embedding distance better explains the expected flux of researchers between organization pairs than geographic distance.
-		\textbf{g-h.} Predictions of flux between organization pairs made using embedding distance outperform those made using geographic distance.
+		For South Korean hotel reservations, embedding distance better explains the expected flux than does geographic distance (\textbf{c}), and produces better predictions (\textbf{d}).
+		Similarly, in the case of global scientific mobility, embedding distance explains the expected flux between organizations (\textbf{e)} and allows for better predictions (\textbf{f}) than geographic distance.
 	}
@@
 DB1B is a sample of 10 percent of domestic airline tickets between 1993 and 2020, comprising 307,760,841 passenger itineraries between 828 U.S. airports. 
-Each itinerary is associated with an origin, destination, and passenger and ticket metadata.
+Each itinerary is associated with a a trajectory of airports including an origin, destination, and intermediary stops.
 
 \subsection*{Korean accommodation reservation data}
-We source Korean accommodation reservation data from collaboration with Good Choice Company in Korea.
-Each trajectory is the sequence of reserved accommodation in Seoul, South Korea between 2018.08.01 ~ 2020.07.31, comprising 938,962 trajectories consist of  1,038 unique accommodations.
+We source Korean accommodation reservation data from collaboration with Good Choice Company in Korea, containing 938,962 trajectories spanning the time period of August 2018 through July 2020,  comprising 1,038 unique accommodation locations in Seoul, South Korea.
 
@@
 \clearpage
-\newpage
-
+%
+% SUPP TABLES
+%
 % S1 Table
-\begin{table}
+\begin{table}[]
 \caption{\textbf{Full organization names}}
@@
 % S2 Table
-\begin{table}
+\begin{table}[]
 \caption{\textbf{L2 Norm of country's representative vectors}.}
@@
 %
+% SUPP FIGURES
+%
+
+%
 % Figure - publications over time
@@
 \begin{figure}[]
-\begin{flushleft}
 	%\includegraphics[width=\textwidth]{\figdir/Descriptive/pubs_over_time.pdf}
@@
 		}
-\end{flushleft}
 	\label{fig:supp:pubs_over_time}

### 2020-10-09 workflow/scripts/PlotGravityLawRelationshipSecondary.R
update scale of gravity plots

@@ -143,7 +143,7 @@ plot <- dist %>%
 if (opt$distance == "geo") {
   max.dist = max(dist$distance)
   plot <- plot +
-    scale_x_continuous(breaks = seq(0, ceiling(max.dist), 1),
+    scale_x_continuous(breaks = seq(0, ceiling(max.dist) - 1, 1),
                        limits = c(0, ceiling(max.dist)),
                        labels = function(x) { parse(text=paste0("10^", x)) },
                        expand = c(0, 0)

### 2020-10-09 paper/current/main.tex
added necessary statements; tidied supplemental; other small tweaks

@@
 \usepackage{caption}
-\captionsetup{justification=raggedright,singlelinecheck=false,font=small}
+\captionsetup{font=small}
+
+% External file referencing
+\usepackage{xr}
+\externaldocument{supp}
 
@@
 Trajectories are represented as the list of author-affiliation combinations, ordered by year of publication, and randomly ordered for combinations within the same year.
-The most fine-grained geographical unit in this data is the organization, such as a ``university'', ``research institute'', ``business'', or ``government agency''.
+The most fine-grained geographical unit in this data is the organization, such as a university, research institute, business, or government agency.
 
@@
 For U.S. airport itinerary, trajectories are formed from the flight itineraries of individual passenger, in which airports correspond to unique identifiers. 
+In the case of South Korean accommodation reservations, trajectories comprise a sequence of accommodations reserved over a customer's history.
 For scientific mobility, an``affiliation trajectories'' is constructed for each mobile author, which is built by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:methods:mobility_sentence}a.
@@
 The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{\min}$, initial learning rate $\alpha$, and the number of iterations.
-For main results, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig.~\ref{fig:supp:hyperparams}).
+For main results regarding scientific mobility, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig.~\ref{fig:supp:hyperparams}).
 To mitigate the effect of less common locations, we set $f_{\min} = 50$, limiting to locations appearing at least 50 times across the training trajectories;
@@
 We set $\alpha$ to its default value of 0.025 and iterate five times over all training trajectories.
+For scientific mobility, across each training iteration, the order of organizations within a single year is randomized.
 
@@
 
-\clearpage
-\beginsupplement
-\section{Supporting Information}
+%
+% Acknowledgements
+%
+\subsection*{Acknowledgements}
+We thank the Center for Science and Technology Studies at Leiden University for managing and making available the dataset of scientific mobility. 
+For their comments, we thank Guillaume Cabanac, Cassidy R. Sugimoto, Vincent Lariviére, Alessandro Flammini, Filippo Menczer, Lili Miao, Xiaoran Yan, and Inho Hong. 
+This material is based upon work supported by the Air Force Office of Scientific Research under award number FA9550-19-1-0391.
 
 %
+% Author Contributions
 % 
-\paragraph*{S1 Text}
-\label{si:text:mobility_science}
-{\bf Mobility and science.}
+\subsection*{Author Contributions}
+Dakota Murray and Jisung Yoon were involved in all stages of data handling, analysis, and writing
+Sadamori Kojaku contributed to the development of the mathematical framework used in this paper.
+Rodrigo Costas provided access to and knowledge of the dataset of scientific mobility.
+Woo-Sung Jung, Staša Milojević , and Yong-Yeol Ahn provided guidance, mentorship, and conceptualization.
+All authors contributed to the preparation of this manuscript.
 
 %
-% S2 Text
-\paragraph*{S2 Text}
-\label{si:text:mobility_models}
-{\bf Modeling scientific mobility.}
+% Supporting Information
+% 
+\subsection*{Additional Information}
+Supplementary Information is available for this paper.
+Correspondence and requests for materials should be addressed to Dr. Staša Milojević and Dr. Yong-Yeol Ahn”.
+Reprints and permissions information is available at www.nature.com/reprints”
 
-%
-% S3 TEXT
-\paragraph*{S3 Text}
-\label{si:text:mobility_traj}
-{\bf Building affiliation trajectories.}
+\subsection*{Data Availability}
+The U.S. airline itinerary dataset can be found at XYZ. 
+The South Korean accommodation reservation dataset can be found at XYZ.
+Due to its proprietary nature, the global scientific mobility dataset, sourced from the Web of Science, cannot be provided;
+however, we have made available all metadata and trained neural embeddings available at XYZ.
 
-%
-% S4 TEXT
-\paragraph*{S4 Text}
-\label{si:text:ppr_dist}
-{\bf Network-based personalized page rank distances.}
+\subsection*{Code Availability}
+Code used in this analysis can be found at \url{https://github.com/murrayds/sci-mobility-emb}
 
-%
-% S5 TEXT
-\paragraph*{S5 Text}
-\label{si:text:organizations}
-{\bf Organization disambiguation and metadata.}
-
-%
-% S6 TEXT
-\paragraph*{S6 Text}
-\label{si:text:disambiguation}
-{\bf Author name dismabiguation.}
-
-%
-% S7 TEXT
-\paragraph*{S7 Text}
-\label{si:text:network_ranking}
-{\bf Reconstructing Times ranking with network measure.}
-
-%
-% S8 TEXT
-\paragraph*{S8 Text}
-\label{si:text:boomerang_speculation}
-{\bf Speculation on variations of the convex-curve pattern.}
-
-\clearpage
-%
-% SUPP TABLES
-%
-% S1 Table
-\begin{table}[]
-\caption{\textbf{Full organization names}}
-\label{table:supp:orglabels}
-\end{table}
-
-% S2 Table
-\begin{table}[]
-\caption{\textbf{L2 Norm of country's representative vectors}.}
-\label{table:supp:norm}
-\end{table}
-
-\clearpage
-\newpage
-
-%
-% SUPP FIGURES
-%
-
-%
-% Figure - publications over time
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/Descriptive/pubs_over_time.pdf}
-	\caption{
-		\textbf{Publications over time.}
-		}
-	\label{fig:supp:pubs_over_time}
-\end{figure}
-
-%
-% Figure - descriptives
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/Descriptive/mobility_by_country.pdf}
-	\caption{\textbf{Extent and nature of mobility by country.}}
-	\label{fig:supp:descriptives}
-\end{figure}
-
-%
-% Figure - reverse CDF by scale
-%
-\begin{figure}[]
-	%\includegraphics[width=0.8\textwidth]{\figdir/Descriptive/rcdf_by_scale.pdf}
-	\caption{
-		\textbf{Reverse cumulative-distribution function of mobile researchers by geographic scale.}
-	}
-	\label{fig:supp:rcdf_by_scale}
-\end{figure}
-
-%
-% Figure - Hyperparameter performance
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/Descriptive/hyperparameter_performance.pdf}
-	\caption{\textbf{Larger dimensions, smaller window size improves embedding performance.}}
-	\label{fig:supp:cosdot}
-\end{figure}
-
-%
-% Figure - Dot product and cosine similarity
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/Math/d300_ws1_dot_cosine.pdf}
-	\caption{
-		\textbf{Cosine distance is correlated with dot product similarity.}
-	}
-	\label{fig:supp:hyperparams}
-\end{figure}
-
-%
-% Figure - Geographic predictions, by model
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance_geo_bymodel.pdf}
-	\caption{
-		\textbf{For geographic distance, the power-decay gravity model is better.}
-	}
-	\label{fig:supp:predict_geo_bymodel}
-\end{figure}
-
-%
-% Figure - Embedding predictions, by model
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance_emb_bymodel.pdf}
-	\caption{
-		\textbf{For geographic distance, the power-decay gravity model is better.}
-	}
-	\label{fig:supp:predict_emb_bymodel}
-\end{figure}
-
-%
-% Figure - gravity correlation
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_correlations.pdf}
-	\caption{
-		\textbf{Embedding distance explains more variance for global, within, and across country flux than geographic distance.}
-	}
-	\label{fig:supp:gravity_correlation}
-\end{figure}
-
-%
-% Figure - gravity predictions based on subset or global
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_different_fits.pdf}
-	\caption{
-		\textbf{Little difference between gravity predictions fit on all or subsets of data.}
-	}
-	\label{fig:supp:gravity_prediction_subsets}
-\end{figure}
-
-%
-% Figure - Dot product distance
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_dot.pdf}
-	\caption{
-		\textbf{Examine gravity model with dot product on the embedding space.}
-	}
-	\label{fig:supp:gravity_dot}
-\end{figure}
-
-%
-% Figure - PPR with COSINE DISTANCE gravity model and predictions
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_pprcos.pdf}
-	\caption{
-		\textbf{Personalized page rank with cosine distance.}
-	}
-	\label{fig:supp:gravity_pprcos}
-\end{figure}
-
-%
-% Figure - PPR with JSD gravity model and predictions
-%
-
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_pprjsd.pdf}
-	\caption{
-		\textbf{Personalized page rank with Jensen-Shannon Divergence.}
-	}
-	\label{fig:supp:gravity_pprjsd}
-\end{figure}
-
-%
-% Figure - Global Network Projection
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/Projection/co_occur_with_label.pdf}
-	\caption{
-		\textbf{Visualization of global mobility network.}
-	}
-	\label{fig:supp:network_vis}
-\end{figure}
-
-\clearpage 
-\newpage
-
-%
-% Figure - New York Projection
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_New_York.pdf}
-	\caption{
-		\textbf{UMAP Projection of organizations in New York.}
-	}
-	\label{fig:supp:proj_newyork}
-\end{figure}
-
-%
-% Figure - Pennsylvania Projection
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_Pennsylvania.pdf}
-	\caption{
-		\textbf{UMAP Projection of organizations in Pennsylvania.}
-	}
-	\label{fig:supp:proj_pennsylvania}
-\end{figure}
-
-%
-% Figure - Texas Projection
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_Texas.pdf}
-	\caption{
-		\textbf{UMAP Projection of organizations in Texas.}
-	}
-	\label{fig:supp:proj_texas}
-\end{figure}
-
-%
-% Figure - California Projection
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_California.pdf}
-	\caption{
-		\textbf{UMAP Projection of organizations in California.}
-	}
-	\label{fig:supp:proj_california}
-\end{figure}
-
-%
-% Figure - SemAxis results
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_compare_fig.pdf}
-	\caption{
-		\textbf{SemRank hierarchy is robust.}
-	}
-	\label{fig:supp:semaxis_compare}
-\end{figure}
-
-%
-% Figure - Network Centrality vs. Times
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/SemAxis/centrality_times_compare.pdf}
-	\caption{
-		\textbf{Network centrality is strongly correlated with Times ranking.}
-	}
-	\label{fig:supp:centrality_times_compare}
-\end{figure}
-
-%
-% Figure - Network Centrality vs. SemAxis
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_network_compare.pdf}
-	\caption{
-		\textbf{Network centrality less correlated with Embedding rank.}
-	}
-	\label{fig:supp:centrality_semaxis_compare}
-\end{figure}
-
-%
-% Figure - SemAxis By State
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_states_fig.pdf}
-	\caption{
-		\textbf{Geography and prestige SemAxis by U.S. state.}
-	}
-	\label{fig:supp:semaxis_states}
-\end{figure}
-
-%
-% Figure - SemAxis By State
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/SemAxis/sector_rank_comparison.pdf}
-	\caption{
-		\textbf{SemAxis reconstructs publication impact in non-university sectors.}
-	}
-	\label{fig:supp:sector_semaxis_impact}
-\end{figure}
-
-%
-% Figure - length by factors
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/Math/l2_org_meta.pdf}
-	\caption{
-		\textbf{Factors relating to the L2 norm of vectors for U.S. universities}
-	}
-	\label{fig:supp:length_vs_metaInfo}
-\end{figure}
-
-%
-% Figure - Concave-curves countries
-%
-\begin{figure}[]
-	%\includegraphics[width=\textwidth]{\figdir/Math/boomerang_30_countries.pdf}
-	\caption{
-		\textbf{Concave-curve repeats across most of 30 countries with most researchers.}
-	}
-	\label{fig:concave30}
-\end{figure}
-
-%
-% Figure - Norm distribution by country
-%
-\begin{figure}[]
-	% \includegraphics[width=\textwidth]{\figdir/Math/l2_org_dist.pdf}
-	\caption{
-		\textbf{Distribution of organization embedding vector norms by country.}
-	}
-	\label{fig:norm_dist}
-\end{figure}
-
-\clearpage
 \printbibliography{}

### 2020-10-19 paper/current/main.tex

@@
 Human mobility and migration drive major societal phenomena such as the growth and evolution of cities~\autocite{wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity}, economies~\autocite{kaluza2010cargo, kerr2011immigration}, and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}.
-Historically, human mobility is strongly constrained by physical separation---geographical distance~\autocite{zipf1946gravity}.
+Historically, human mobility has been strongly constrained by physical separation---geographic distance~\autocite{zipf1946gravity}.
 However, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important.
-The critical importance of understanding mobility in many socio-economic phenomena thus compel alternative frameworks for mobility.
-Here, using a massive dataset of scientific mobility, U.S.
-flight itineraries, and South Korean accommodation reservations, we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective functional distance that reflects the multi-faced structure of human mobility.
-Focusing on the case of scientific mobility, we show that embeddings of scientific organizations discovers cultural and linguistic relations at multiple levels of granularity, and even academic prestige.
-Furthermore, the embedding vectors themselves reveal universal relationships between organizational characteristics, and their place in the global landscape of scientific mobility. 
+As the mobility and migration are becoming more complex and more critical for contemporary society, finding frameworks that will allow for capturing this complexity are of paramount importance.
+Here, using three massive dataasets: U.S.
+flight itineraries, South Korean accommodation reservations, and global scientific mobility,  we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faced structure of human mobility.
+Focusing on the case of scientific mobility, we show that embeddings of scientific organizations uncovers cultural and linguistic relations at multiple levels of granularity, and even academic prestige.
+Furthermore, the embedding vectors reveal universal relationships between organizational characteristics, and their place in the global landscape of scientific mobility. 
 The ability to learn scalable, dense and meaningful high-resolution vector representations of mobility directly from the data can open up a new avenue of studying mobility across domains.
@@
 Yet, functional distances are often low-resolution, computed at the level of countries rather than regions, cities, or organizations, and have focused on only a single facet of mobility at a time, whereas real-world mobility is multi-faceted, influenced simultaneously by geography, language, culture, history, and economic opportunity.
-Low dimensional distance alone cannot represent the multitude of inter-related factors that derive mobility. 
-Networks offer a solution to representing many dimensions of mobility, yet they only represent flows between discrete entities, and so cannot easily capture the relationships between entities themselves.
-Overcoming the complexity of mobility requires moving beyond simple functional distances and networks, to instead learning high-dimensional landscapes of mobility that incorporates the many facets of mobility into a single fine-grained and continuous representation.
+Low dimensional distance alone cannot represent the multitude of inter-related factors that drive mobility. 
+Networks offer a solution to representing many dimensions of mobility, yet edges only encode simple relationships between connected entities, and cannot easily capture the rich landscape of mobility. 
+Thus, capturing the complexity of mobility requires moving beyond simple functional distances and networks, to learning high-dimensional landscapes of mobility that incorporate the many facets of mobility into a single fine-grained and continuous representation.
 
-Here, we apply a neural embedding framework to real-world mobility trajectories and demonstrate that it can encode the complex landscape of human mobility into a dense, continuous, and meaningful vector-space representation, from which we can not only derive a meaningful \textit{functional distance} between places but also probe relationships based on culture, language, and even prestige along with geographic relationship.
-We leverage three massive datasets: U.S.
+Here, we apply a neural embedding framework to real-world mobility trajectories and demonstrate that it can encode the complex landscape of human mobility into a dense and continuous vector-space representation, from which we can not only derive a meaningful \textit{functional distance} between places but also probe relationships based on culture, language, and even prestige along with geographic relationship.
+We embed trajectories from three massive datasets: U.S.
 passenger flight itinerary records, South Korean accommodation reservations, and a dataset of scientists' career mobility between organizations captured in bibliometric records.
-In particular, we focus on scientific mobility due to its richness and importance.
-Scientific mobility, which is a central driver of the globalized scientific enterprise~\autocite{czaika2018globalisation, altbach2004globalization, box2008competition} and strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}, is not only an important topic in the Science of Science but also ideal for our study thanks to its richness and well-known structural properties such as the centrality of scientifically advanced countries and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career}.
-In spite of its importance, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, being further confounded by the diminishing role of geography in shaping the landscape of scientific mobility.
 
@@
 The Korean accommodation reservations consist of accommodation reservation history between 2018 and 2020 between 1,038 unique accommodation locations in Seoul, South Korea.
-A trajectory is constructed for each customer's accommodation reservation history, constructing an ordered sequence of unique commendation with accurate location information.
-Although more complex, trajectories of scientific mobility are constructed in a similar fashion. 
-Trajectories are constructed using more than three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database.
-Each trajectory is operationalized using a researcher's organizational affiliations derived from their publication histories indexed in a comprehensive bibliographic database (see Methods).
+A trajectory is constructed for each customer's accommodation reservation history, constructing an ordered sequence of accommodations reserved over time.
+We focus in more detail on scientific mobility due to its richness and importance. 
+Scientific mobility, which is a central driver of the globalized scientific enterprise~\autocite{czaika2018globalisation, altbach2004globalization, box2008competition} and strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}, is not only an important topic in the Science of Science but also ideal for our study thanks to its richness and well-known structural properties such as the centrality of scientifically advanced countries and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career}.
+In spite of its importance, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, being further confounded by the diminishing role of geography in shaping the landscape of scientific mobility.
+Trajectories of scientific mobility are constructed using more than three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database (see Methods).
 As a scientist's career progresses, they move between organizations or pick up additional (simultaneous) affiliations forming \textit{affiliation trajectories} (Fig.~\ref{fig:methods:mobility_sentence}).
@@
 This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
-They are also computationally efficient, robust to noise, and can encode relations between entities as geometric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.
+The model is also computationally efficient, robust to noise, and can encode relations between entities as geometric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.
 As a result, each location is encoded into a single vector representation, and vectors relate to one another based on the likelihood of locations appearing adjacent to one another in the same trajectory.
@@
 where $m_{i}$ is the population of locations $i$,  $f(r_{ij})$ is a decay function with respect to distance between locations, and $C$ is a constant estimated from data (see Methods). 
-For the flight itinerary data, we use population $m_{i}$ as the total number of unique passenger on each airport, and for scientific mobility, we use the mean annual number of of unique mobile and non-mobile authors who affiliated with each organization.
+For the flight itinerary data, we use population $m_{i}$ as the total number of unique passengers on each airport, and for scientific mobility, we use the mean annual number of unique mobile and non-mobile authors who were affiliated with each organization.
 $\hat{T}_{ij}$, which is often referred to as ``expected flux''~\autocite{simini2012universal}, is the expected frequency of the co-occurrence of location $i$ and $j$ in the trajectory in the gravity model.
@@
 
-We show that the embedding distance, compared with the geographical distance, predicts actual mobility flows. 
+We show that the embedding distance better predicts actual mobility flows than the geographic distance.
 In the case flight itineraries, the embedding distance explains more than twice the expected flux between airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}a) than does geographic distance ($R^{2} = 0.22$).
-We fit the gravity model given by Eq.~\ref{eq:gravity_basic} (see Methods) and computed the expected flux  $\hat{T}_{ij}$ using the geographic distance and the embedding distance as parameters.
+We fit the gravity model given by Eq.~\ref{eq:gravity_basic} (see Methods) and compute the expected flux $\hat{T}_{ij}$ using the geographic distance and the embedding distance as parameters.
 The embedding distance produces better predictions of actual flux between airports than does the geographic distance (Fig.~\ref{fig:gravity_performance}b).
@@
 In the case of South Korean hotel accommodations, such that the embedding distance better explains the expected flux ($R^{2} = 0.57$, Fig.~\ref{fig:gravity_performance}c) than does geographic distance ($R^{2} = 0.25$), and predictions made using embedding distance outperform those made with geographic distance (Fig.~\ref{fig:gravity_performance}d).
-These results are consistent in the case of scientific mobility. 
-The amount of variance in the expected flux explained by the embedding distance ($R^{2} = 0.48$, Fig.~\ref{fig:gravity_performance}e) is again more than double that explained by the geographic distance ($R^{2} = 0.22$).
-This pattern holds when considering the subset of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d).
-As with flight itineraries, we fit the gravity model on the scientific mobility data using the gravity model.
-Predictions made using the embedding distance outperform those made using the geographic distance (Fig.~\ref{fig:gravity_performance}f), which also holds for the subsets of only domestic and only international mobility (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}).
+This performance is consistent in the case of scientific mobility:
+the embedding distance explains more than twice the expected flux ($R^{2} = 0.48$, Fig.~\ref{fig:gravity_performance}e) than does the geographic distance ($R^{2} = 0.22$), and predictions made using the embedding distance outperform those using the geographic distance (Fig.~\ref{fig:gravity_performance}f).
+These patterns hold for the subsets of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}c and Fig.~\ref{fig:supp:predict_geo_bymodel}) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d and  Fig.~\ref{fig:supp:predict_emb_bymodel}).
 For scientific mobility, the embedding distance defined from the cosine distance between vectors also outperforms that defined from their dot product ($R^{2} = 0.34$, Fig.~\ref{fig:supp:gravity_dot}).
@@
 
-From here, we focus on the case of scientific mobility, leveraging its richness to investigate how the geometric space generated by the neural embedding method sheds light on the multi-faceted relationships between organizations.
+In the remaidner of the paper, we focus only on scientific mobility, leveraging its richness to investigate how the geometric space generated by the neural embedding method sheds light on the multi-faceted relationships between organizations.
 To explore the topological structure of the embedding, we use a topology-based dimensionality reduction method (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation of the embedding space (Fig.~\ref{fig:projection}a).
@@
 
-Globally, the geographical constraints are conspicuous; organizations tend to form clusters based on their national affiliations and national clusters tend to be near their geographic neighbors.
+Globally, the geographic constraints are conspicuous; organizations tend to form clusters based on their national affiliations and national clusters tend to be near their geographic neighbors.
 At the same time, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions much more clearly than alternative network representations (Fig.~\ref{fig:supp:network_vis}) that have been dominating studies of scientific mobility~\autocite{chinchilla2018global, czaika2018globalisation}.
@@
 	  	\textbf{b.} Times ranking is correlated with Leiden Ranking of U.S. universities with Spearman's $\rho = 0.87$.
-		\textbf{c-f.} Illustration of SemAxis projection along two axes;  \textit{latent geographical axis}, from California to Massachusetts (left to right) and the \textit{prestige axis}.
+		\textbf{c-f.} Illustration of SemAxis projection along two axes;  \textit{latent geographic axis}, from California to Massachusetts (left to right) and the \textit{prestige axis}.
 		Shown for U.S. Universities (\textbf{c}), regional and liberal arts colleges (\textbf{d}), Research institutes (\textbf{e}), and Government organizations (\textbf{f}).
@@
 These organizations are primarily research-intensive and prestigious universities with higher rankings, research outputs, R\&D funding, and doctoral students (Fig.~\ref{fig:supp:length_vs_metaInfo}).
-A similar pattern has been observed in applications of neural embedding to natural language, in which the size of word vectors was found to represent the word's \emph{specificity}.
-Roughly speaking, for word embeddings, the size of a vector reflects its specificity, i.e., the word associated with the vector frequently co-appears with particular context words\autocite{schakel2015measuring}.
+A similar pattern has been observed in applications of neural embedding to natural language, in which the size of word vectors were found to represent the word's \emph{specificity}, i.e., the word associated with the vector frequently co-appears with particular context words\autocite{schakel2015measuring}.
 If the word in question is universal, appearing frequently in many different contexts, it would not have a large norm due to a lack of strong association with a particular context.
 Likewise, an organization such as Harvard with a small norm appears in many contexts, alongside many different organizations in affiliation trajectories---it is well-connected.
-The concavity emerges in part from the relationship between the size of the vector and the expected connectedness of the organization given its size ($R^{2} = 0.17$).
+The concavity of the curve emerges in part from the relationship between the size of the vector and the expected connectedness of the organization, given its size ($R^{2} = 0.17$).
 Large, prestigious, and well-funded research universities such as Princeton and Harvard have smaller vector norms because they appear in many different contexts compared to more teaching-focused organizations such as NY Medical College, and the University of Michigan at Flint.
-Some universities, such as the University of Alaska at Fairbanks, have considerably small vectors, which may be a result of its remote location and unique circumstances.
+Some universities, such as the University of Alaska at Fairbanks, have considerably small vectors, which may be a result of their remote locations and unique circumstances.
 
@@
 		A convex-shape emerges, wherein larger universities tend to be more distant from the origin (large L2 norm); however, the more prestigious universities tend to have smaller L2 norms.
-		\textbf{b.} We find a similar convex-curve pattern across many countries such as the United States, China, Australia, Brazil, and others (\textit{inset}, and Fig.~\ref{fig:concave30}). 
+		\textbf{b.} We find a similar convex-curve pattern across many countries such as the United States, China, Australia, Brazil, and others (\textbf{inset}, and Fig.~\ref{fig:concave30}). 
 		Some countries exhibit variants of this pattern, such as Egypt, which is missing the right side of the curve.
@@
 Neural embedding approaches offer a novel, data-driven solution for learning an effective and robust representation of locations based on trajectory data, encoding the complex and multi-faceted nature of mobility.
-We demonstrated that a functional distance derived from the embedding can be used with the gravity model of mobility to better predicts real-world mobility than does geographic distance.
+We demonstrated that a functional distance derived from the embedding can be used with the gravity model of mobility to better predict real-world mobility than does geographic distance.
 Embedding distance outperformed geographic distance both in the case of U.S. flight itineraries and global scientific mobility, which represent two domains with disparate nature. 
@@
 Trajectories are represented as the list of author-affiliation combinations, ordered by year of publication, and randomly ordered for combinations within the same year.
-The most fine-grained geographical unit in this data is the organization, such as a university, research institute, business, or government agency.
+The most fine-grained geographic unit in this data is the organization, such as a university, research institute, business, or government agency.
 

### 2020-10-19 paper/current/main.tex
add affiliation
abstract and introduction

@@
 \author[1]{Staša Milojević \thanks{smilojev@indiana.edu}}
-\author[1]{Yong-Yeol Ahn \thanks{yyahn@iu.edu}}
+\author[1,4,5]{Yong-Yeol Ahn \thanks{yyahn@iu.edu}}
 
@@
 2300 AX Leiden, The Netherlands}
+\affil[4]{Network Science Institute, Indiana University, Bloomington (IUNI), IN 47408, USA}
+\affil[5]{Connection Science, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
+
 \affil[\Yinyang]{These authors contributed equally: Jisung Yoon, Dakota Murray.}
@@
 However, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important.
-As the mobility and migration are becoming more complex and more critical for contemporary society, finding frameworks that will allow for capturing this complexity are of paramount importance.
-Here, using three massive dataasets: U.S.
-flight itineraries, South Korean accommodation reservations, and global scientific mobility,  we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faced structure of human mobility.
+As understanding mobility is becoming critical for contemporary society, finding frameworks that can capture this complexity are of paramount importance.
+Here, using three datasets that capture human trajectories,  we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
 Focusing on the case of scientific mobility, we show that embeddings of scientific organizations uncovers cultural and linguistic relations at multiple levels of granularity, and even academic prestige.
 Furthermore, the embedding vectors reveal universal relationships between organizational characteristics, and their place in the global landscape of scientific mobility. 
-The ability to learn scalable, dense and meaningful high-resolution vector representations of mobility directly from the data can open up a new avenue of studying mobility across domains.
+The ability to learn scalable, dense and meaningful representations of mobility directly from the data can open up a new avenue of studying mobility across domains.
 
@@
 Similarly, a student in South Korea is more likely to attend a university in Canada than one in North Korea~\autocite{unesco2019students}.
-Although geographic distance has been used as the most prominent basis for models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} models, there have been attempts to define alternative notions of distance, or ~\textit{functional distances}~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional} from real-world data or \textit{a priori} relationships between geographic entities.
+Although geographic distance has been used as the most prominent basis for models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} models, there have been attempts to define alternative notions of distance, or functional distances~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional} from real-world data or \textit{a priori} relationships between geographic entities.
 
@@
 A trajectory is constructed for each customer's accommodation reservation history, constructing an ordered sequence of accommodations reserved over time.
+Finally, we use scientific mobility data that capture the affiliation trajectory of 12,963,792 scientists across ten years.
 We focus in more detail on scientific mobility due to its richness and importance. 
@@
 In spite of its importance, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, being further confounded by the diminishing role of geography in shaping the landscape of scientific mobility.
+
 Trajectories of scientific mobility are constructed using more than three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database (see Methods).

### 2020-10-19 paper/current/main.tex
first main para

@@
 We show that the embedding distance better predicts actual mobility flows than the geographic distance.
-In the case flight itineraries, the embedding distance explains more than twice the expected flux between airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}a) than does geographic distance ($R^{2} = 0.22$).
-We fit the gravity model given by Eq.~\ref{eq:gravity_basic} (see Methods) and compute the expected flux $\hat{T}_{ij}$ using the geographic distance and the embedding distance as parameters.
-The embedding distance produces better predictions of actual flux between airports than does the geographic distance (Fig.~\ref{fig:gravity_performance}b).
-The neural embedding also performs well in a smaller geographic context:
+In the case of flight itineraries, the embedding distance explains more than twice the expected flux between airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}a) than does geographic distance ($R^{2} = 0.22$).
+Also, the embedding distance produces better predictions of actual flux between airports than does the geographic distance (Fig.~\ref{fig:gravity_performance}b).
 In the case of South Korean hotel accommodations, such that the embedding distance better explains the expected flux ($R^{2} = 0.57$, Fig.~\ref{fig:gravity_performance}c) than does geographic distance ($R^{2} = 0.25$), and predictions made using embedding distance outperform those made with geographic distance (Fig.~\ref{fig:gravity_performance}d).
@@
 These patterns hold for the subsets of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}c and Fig.~\ref{fig:supp:predict_geo_bymodel}) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d and  Fig.~\ref{fig:supp:predict_emb_bymodel}).
-For scientific mobility, the embedding distance defined from the cosine distance between vectors also outperforms that defined from their dot product ($R^{2} = 0.34$, Fig.~\ref{fig:supp:gravity_dot}).
-The embedding distance also out-performs alternative ``diffusion-based'' network distance measures such as the personalized-page rank scores (see \SI) calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-Our results demonstrate that the embedding distance better captures patterns of actual mobility than does the geographic distance across domains.
+The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores  calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+In sum, our results demonstrate that the embedding distance better captures patterns of actual mobility than does the geographic distance consistently.
 

### 2020-10-19 paper/current/main.tex
one more thing on first main para
some minor issues

@@
 
-We show that the embedding distance better predicts actual mobility flows than the geographic distance.
+We show that the embedding distance better predicts actual mobility flows than the geographic distance across three disparate datasets.
 In the case of flight itineraries, the embedding distance explains more than twice the expected flux between airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}a) than does geographic distance ($R^{2} = 0.22$).
@@
 For instance, China's curve closely mirrors that of the United States (Fig.~\ref{fig:length}b).
-Smaller but scientifically advanced countries such as Australia, and other populous countries such as Brazil also exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset), though their exact position and size vary.
-Other nations exhibit different curves, such as Egypt which has an``S''-shaped curve, meaning that their largest organizations are not as well connected as other countries' largest organizations. 
+Smaller but scientifically advanced countries such as Australia, and other populous countries such as Brazil also exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset).
+Other nations exhibit different curves which lacks the portions with decreasing norm, probably indicating the lack of highly prestigious institutions.
 Similar patterns can be found across many of the 30 of the countries with the most total researchers (Fig.~\ref{fig:concave30}) see \SI{} for more discussion).
@@
 \label{sec:datamethods} %{{{
-
-Processed data, analysis, and associated code have been made publicly available and can be found at \url{https://github.com/murrayds/sci-mobility-emb}.
 
@@
 \subsection*{Author Contributions}
-Dakota Murray and Jisung Yoon were involved in all stages of data handling, analysis, and writing
+Dakota Murray and Jisung Yoon were involved in all stages of data handling, analysis, and writing.
 Sadamori Kojaku contributed to the development of the mathematical framework used in this paper.
 Rodrigo Costas provided access to and knowledge of the dataset of scientific mobility.
-Woo-Sung Jung, Staša Milojević , and Yong-Yeol Ahn provided guidance, mentorship, and conceptualization.
+Woo-Sung Jung, Staša Milojević, and Yong-Yeol Ahn provided guidance, mentorship, and conceptualization.
 All authors contributed to the preparation of this manuscript.
@@
 Supplementary Information is available for this paper.
-Correspondence and requests for materials should be addressed to Dr. Staša Milojević and Dr. Yong-Yeol Ahn”.
-Reprints and permissions information is available at www.nature.com/reprints”
+Correspondence and requests for materials should be addressed to Dr. Staša Milojević and Dr. Yong-Yeol Ahn.
+Reprints and permissions information is available at www.nature.com/reprints
 

### 2020-10-19 paper/current/main.tex
add impute statements

@@
 Geographic distance is calculated as the great circle distance, in kilometers, between pairs of locations.
-When less than one kilometer, a distance of 1 km is imputed.
+In the case of U.S.
+flight itinerary and scientific mobility, we impute distance to 1 km when their distance is less than one kilometer.
+In the case of Korean accommodation reservation data, because this data is intra-city mobility trajectory, we impute distance to 0.01 km when their distance is less than 0.01 km.
 The embedding distance with the cosine distance, $d_{ij}$, is calculated as $d_{ij} = 1 - \frac{\bm{v}_{i} \cdot \bm{v}_{j}}{\lVert \bm{v}_{i} \rVert \lVert \bm{v}_{j} \rVert}$,

### 2020-10-19 paper/current/main.tex
data availabiltiy

@@
 Correspondence and requests for materials should be addressed to Dr. Staša Milojević and Dr. Yong-Yeol Ahn.
-Reprints and permissions information is available at www.nature.com/reprints
+Reprints and permissions information is available at 
+\url{www.nature.com/reprints}.
 
 \subsection*{Data Availability}
-The U.S. airline itinerary dataset can be found at XYZ. 
-The South Korean accommodation reservation dataset can be found at XYZ.
+The U.S. airline itinerary dataset can be found at \url{https://www.transtats.bts.gov/DataIndex.asp}. 
+In case of the South Korean accommodation reservation dataset, due to the nature of the dataset, participants of this study did not agree for their data to be shared publicly.
 Due to its proprietary nature, the global scientific mobility dataset, sourced from the Web of Science, cannot be provided;

### 2020-10-19 paper/current/supp.tex
fixed supp figure numbering
minor comments on suppliment

@@
 
+\beginsupplement
+
 %
@@
 
-As scholars move, they bring their knowledge, their skills, and their social connections with them--collectively the movements of researchers shape the structure and direction of the global scientific enterprise.
+As scholars move, they bring their knowledge, skills, and social connections with them---collectively the movements of researchers shape the structure and direction of the global scientific enterprise.
 For example, prestige-driven mobility between doctoral-granting and employing institution is highly unequal~\autocite{clauset2015hierarchy, deville2014career}, which affects the diffusion of ideas across academia~\autocite{morgan2018prestige}.
@@
 \textit{Organization}-level mobility has the potential to inform institutional policy and to understand the composition of mobility within a single country or region, especially as it relates to organization performance, prestige, and inequality~\autocite{albarran2017topeconomic, deville2014career, morgan2018prestige, clauset2015hierarchy}.
-However, affiliation disambiguation and noise in bibliometric data have makes large-scale organization-level analysis challenging.
+However, affiliation disambiguation and noise in bibliometric data makes large-scale organization-level analysis challenging.
 Here, we learn neural-network embeddings of scientific mobility at the level of organizations using a curated bibliographic database.
@@
 However, scientific mobility is more complicated.
-For example, scientists often hold multiple affiliations at a time~\autocite{markova2016synchronous}, listing them as co-affiliations on a single paper, or even choosing a subset of affiliations to use for multiple simultaneous projects~\autocite{robinson2019mobility}.
+For example, scientists often hold multiple affiliations at a time~\autocite{markova2016synchronous}, listing them as co-affiliations on a single paper, or even choosing a subset of affiliations to use fohabeultiple simultaneous projects~\autocite{robinson2019mobility}.
 Even clearly-directional migration to another institution is complex--researchers may continue to publish with an old affiliation for projects that began before their move, and they may maintain social and organizational links to their old institution (e.g., collaborators, projects, graduate students) such that there is no clear breakage after migrating.
@@
 		Color of each hex bin indicates frequency of organization pairs.
-		Results here are identical to those shown in Fig.~\ref{fig:gravity_performance}a and Fig.~\ref{fig:gravity_performance}.
+		Results here are identical to those shown in Fig.2.
 		\textbf{c-d.}	embedding distance explains more variance when considering only within-country organization pairs.
@@
 		a perfect prediction yields all points on the black line.
-		\textbf{a-b.} Predictions are made with parameters estimated from all pairs of organizations (as in Fig.~\ref{fig:gravity_performance}c), and showing only the subsets of predictions for organization pairs in the same country (\textbf{a}) and in different countries (\textbf{b}).
+		\textbf{a-b.} Predictions are made with parameters estimated from all pairs of organizations (as in Fig.2e), and showing only the subsets of predictions for organization pairs in the same country (\textbf{a}) and in different countries (\textbf{b}).
 		\textbf{c-d.} Predictions made using parameters estimated from the subset of organizations in the same country (\textbf{c}) and different country \textbf{d});
-		this is the same data as shown in Fig.~\ref{fig:gravity_performance}f and Fig.~\ref{fig:gravity_performance}h.
+		this is the same data as shown in Fig.2f and Fig.2h.
 	}
@@
 		these thresholds were chosen as points thresholds of stability in \textbf{a}. 		
-		The impact rank is correlated with the embedding rank for regional and liberal arts colleges with Spearman's $\rho = 0.49 (n = 48)$, research institutes with Spearman's $\rho = 0.58 (n = 159)$, and for government organizations with Spearman's $\rho = 0.36 (n = 55)$.
+		The impact rank is correlated with the embedding rank for regional and liberal arts colleges with Spearman's $\rho = 0.49\,(n = 48)$, research institutes with Spearman's $\rho = 0.58\,(n = 159)$, and for government organizations with Spearman's $\rho = 0.36\,(n = 55)$.
 	}

### 2020-10-19 paper/current/main.tex
author contribution statement update

@@
 \subsection*{Author Contributions}
-Dakota Murray and Jisung Yoon were involved in all stages of data handling, analysis, and writing.
-Sadamori Kojaku contributed to the development of the mathematical framework used in this paper.
-Rodrigo Costas provided access to and knowledge of the dataset of scientific mobility.
-Woo-Sung Jung, Staša Milojević, and Yong-Yeol Ahn provided guidance, mentorship, and conceptualization.
-All authors contributed to the preparation of this manuscript.
+All authors contributed extensively to the work presented in this paper.
+D.
+M.
+and J.Y.
+were involved in all stages of conceptualization, analysis, and writing, S.K.
+developed the theoretical framework, R.C.
+assembled input data, and W.J., S.M., and Y.A.
+contributed to conceptualization.
+All authors discussed the results and commented on the manuscript at all stages.
 

### 2020-10-19 paper/current/main.tex
added figshare record to data availability statement

@@
 Due to its proprietary nature, the global scientific mobility dataset, sourced from the Web of Science, cannot be provided;
-however, we have made available all metadata and trained neural embeddings available at XYZ.
+however, metadata and trained neural embeddings have been published at \url{https://doi.org/10.6084/m9.figshare.13072790.v1}
 

### 2020-10-19 paper/current/main.tex
cut references :(

@@
 
-Human mobility and migration drive major societal phenomena such as the growth and evolution of cities~\autocite{wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity}, economies~\autocite{kaluza2010cargo, kerr2011immigration}, and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}.
+Human mobility and migration drive major societal phenomena such as the growth and evolution of cities~\autocite{wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity}, economies~\autocite{kaluza2010cargo, kerr2011immigration}, and innovation~\autocite{kaiser2018innovation, sugimoto2017mostimpact, petersen2018multiscale}.
 Historically, human mobility has been strongly constrained by physical separation---geographic distance~\autocite{zipf1946gravity}.
-However, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018migration, czaika2018globalisation, buchan2009globalization, altbach2004globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important.
+However, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018globalisation, buchan2009globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important.
 As understanding mobility is becoming critical for contemporary society, finding frameworks that can capture this complexity are of paramount importance.
@@
 Similarly, a student in South Korea is more likely to attend a university in Canada than one in North Korea~\autocite{unesco2019students}.
-Although geographic distance has been used as the most prominent basis for models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} models, there have been attempts to define alternative notions of distance, or functional distances~\autocite{boschma2005proximity, brown1970functional, brown1970migration, kim2018functional} from real-world data or \textit{a priori} relationships between geographic entities.
+Although geographic distance has been used as the most prominent basis for models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} models, there have been attempts to define alternative notions of distance, or functional distances~\autocite{boschma2005proximity, brown1970migration, kim2018functional} from real-world data or \textit{a priori} relationships between geographic entities.
 
@@
 We focus in more detail on scientific mobility due to its richness and importance. 
-Scientific mobility, which is a central driver of the globalized scientific enterprise~\autocite{czaika2018globalisation, altbach2004globalization, box2008competition} and strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation, armano2017innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, azoulay2011diffusion, morgan2018prestige}, is not only an important topic in the Science of Science but also ideal for our study thanks to its richness and well-known structural properties such as the centrality of scientifically advanced countries and the strong prestige hierarchy~\autocite{auriol2010careers, clauset2015hierarchy, deville2014career}.
-In spite of its importance, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, being further confounded by the diminishing role of geography in shaping the landscape of scientific mobility.
+Scientific mobility, which is a central driver of the globalized scientific enterprise~\autocite{czaika2018globalisation, box2008competition} and strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, morgan2018prestige}, is not only an important topic in the Science of Science but also ideal for our study thanks to its richness and well-known structural properties such as the centrality of scientifically advanced countries and the strong prestige hierarchy~\autocite{clauset2015hierarchy, deville2014career}.
+In spite of its importance, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, deville2014career}, being further confounded by the diminishing role of geography in shaping the landscape of scientific mobility.
 
@@
 As a scientist's career progresses, they move between organizations or pick up additional (simultaneous) affiliations forming \textit{affiliation trajectories} (Fig.~\ref{fig:methods:mobility_sentence}).
-Thus, the trajectories encode both migration and co-affiliation---the holding of multiple simultaneous co-affiliations involving the sharing of time and capital between locations---that is typical of scientific mobility~\autocite{rodrigues2016mobility, markova2016synchronous, sugimoto2017mostimpact} (see \SI).
+Thus, the trajectories encode both migration and co-affiliation---the holding of multiple simultaneous co-affiliations involving the sharing of time and capital between locations---that is typical of scientific mobility~\autocite{rodrigues2016mobility, sugimoto2017mostimpact} (see \SI).
 
@@
 To validate our approach, we evaluate the quality of vector representations with their performance in predicting real-world mobility flows using the gravity model framework~\autocite{zipf1946gravity, barbosa2018human}.
-The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity, xia2005measlesgravity} that models the \textit{expected flux}, $\hat{T}_{ij}$ between locations (airports and organizations) based on their populations and distance:
+The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity} that models the \textit{expected flux}, $\hat{T}_{ij}$ between locations (airports and organizations) based on their populations and distance:
 
@@
 
-Mobility and migration are at the core of human nature and history~\autocite{shah2020migration}, driving societal phenomena as diverse as epidemics\autocite{kraemer2020covid, truscott2012epidemicgravity, xia2005measlesgravity} and innovation~\autocite{kaiser2018innovation, armano2017innovation, sugimoto2017mostimpact, petersen2018multiscale, franzoni2014advantage, morgan2018prestige, rodrigues2016mobility}.
+Mobility and migration are at the core of human nature and history, driving societal phenomena as diverse as epidemics\autocite{kraemer2020covid, truscott2012epidemicgravity} and innovation~\autocite{kaiser2018innovation, sugimoto2017mostimpact, petersen2018multiscale, morgan2018prestige, rodrigues2016mobility}.
 However, the paradigm of scientific migration may be changing.
@@
 and U.K.~\autocite{chinchilla2018travelban}.
-At the same time, other nations, such as China, are growing into major scientific powers and attractors of talent~\autocite{tollefson2018china, cao2020returning}.
+At the same time, other nations, such as China, are growing into major scientific powers and attractors of talent~\autocite{cao2020returning}.
 Unprecedented health crises such as the COVID-19 pandemic threaten to bring drastic global changes to travel and migration by tightening borders and halting travel.
@@
 Note that $d_{ij}$ is not a formal metric because it does not satisfy the triangle inequality.
-Nevertheless, cosine distance is often shown to be useful in practice~\autocite{lerman2007embedding, brown1970migration, brown1970functional, kim2018functional}.
+Nevertheless, cosine distance is often shown to be useful in practice~\autocite{lerman2007embedding, brown1970migration, kim2018functional}.
 
@@
 The gravity law of mobility loosely derives from the physical law of gravity, in which the attraction between two objects is a function of their mass and the distance between them.
-This formulation and variants have proven useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
+This formulation and variants have proven useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, truscott2012epidemicgravity, hong2016busgravity}.
 In the gravity law of mobility, the \textit{expected flux}, $\hat{T_{ij}}$ between two organizations $i$ and $j$ is defined as,
@@
 one is a power law function in the form $f(r_{ij})= r^{-\alpha}_{ij} \ (\alpha > 0$, and the other and the another one is an exponential function in the form $f(r_{ij}) = e^{-\beta r_{ij}} \ (\beta > 0)$ \autocite{chen2015distance}.
-The parameters for $f(r_{ij})$ and $C$ are fit to given mobility data using a log-linear regression~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity, simini2012universal}.
+The parameters for $f(r_{ij})$ and $C$ are fit to given mobility data using a log-linear regression~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity,  truscott2012epidemicgravity, hong2016busgravity, simini2012universal}.
 

### 2020-10-19 paper/current/main.tex
more cut references :(

@@
 A vector-space embedding of locations (airports and organizations) is learned by using trajectories as input to the standard skip-gram negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
-This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered} and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
+This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered} and networks~\autocite{grover2016node2vec}.
 The model is also computationally efficient, robust to noise, and can encode relations between entities as geometric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.
@@
 
-To validate our approach, we evaluate the quality of vector representations with their performance in predicting real-world mobility flows using the gravity model framework~\autocite{zipf1946gravity, barbosa2018human}.
-The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, lewer2008immigrationgravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity} that models the \textit{expected flux}, $\hat{T}_{ij}$ between locations (airports and organizations) based on their populations and distance:
+To validate our approach, we evaluate the quality of vector representations with their performance in predicting real-world mobility flows using the gravity model framework~\autocite{zipf1946gravity}.
+The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity} that models the \textit{expected flux}, $\hat{T}_{ij}$ between locations (airports and organizations) based on their populations and distance:
 
@@
 The gravity law of mobility loosely derives from the physical law of gravity, in which the attraction between two objects is a function of their mass and the distance between them.
-This formulation and variants have proven useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, truscott2012epidemicgravity, hong2016busgravity}.
+This formulation and variants have proven useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, truscott2012epidemicgravity, hong2016busgravity}.
 In the gravity law of mobility, the \textit{expected flux}, $\hat{T_{ij}}$ between two organizations $i$ and $j$ is defined as,
@@
 one is a power law function in the form $f(r_{ij})= r^{-\alpha}_{ij} \ (\alpha > 0$, and the other and the another one is an exponential function in the form $f(r_{ij}) = e^{-\beta r_{ij}} \ (\beta > 0)$ \autocite{chen2015distance}.
-The parameters for $f(r_{ij})$ and $C$ are fit to given mobility data using a log-linear regression~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity,  truscott2012epidemicgravity, hong2016busgravity, simini2012universal}.
+The parameters for $f(r_{ij})$ and $C$ are fit to given mobility data using a log-linear regression~\autocite{jung2008highwaygravity, curiel2018citygravity, truscott2012epidemicgravity, hong2016busgravity, simini2012universal}.
 

### 2020-10-19 paper/current/main.tex
main body tweaks

@@
 
-Here, we apply a neural embedding framework to real-world mobility trajectories and demonstrate that it can encode the complex landscape of human mobility into a dense and continuous vector-space representation, from which we can not only derive a meaningful \textit{functional distance} between places but also probe relationships based on culture, language, and even prestige along with geographic relationship.
+Here, we apply a neural embedding framework to real-world mobility trajectories and demonstrate that it can encode the complex landscape of human mobility into a dense and continuous vector-space representation, from which we can not only derive a meaningful functional distance between places but also probe relationships based on culture, language, and even prestige along with geographic relationship.
 We embed trajectories from three massive datasets: U.S.
@@
 A trajectory is constructed for each customer's accommodation reservation history, constructing an ordered sequence of accommodations reserved over time.
-Finally, we use scientific mobility data that capture the affiliation trajectory of 12,963,792 scientists across ten years.
+Finally, we use scientific mobility data that captures the affiliation trajectories of nearly 13 million scientists across ten years.
 We focus in more detail on scientific mobility due to its richness and importance. 
@@
 Also, the embedding distance produces better predictions of actual flux between airports than does the geographic distance (Fig.~\ref{fig:gravity_performance}b).
-In the case of South Korean hotel accommodations, such that the embedding distance better explains the expected flux ($R^{2} = 0.57$, Fig.~\ref{fig:gravity_performance}c) than does geographic distance ($R^{2} = 0.25$), and predictions made using embedding distance outperform those made with geographic distance (Fig.~\ref{fig:gravity_performance}d).
+In the case of South Korean accommodation reservations, such that the embedding distance better explains the expected flux ($R^{2} = 0.57$, Fig.~\ref{fig:gravity_performance}c) than does geographic distance ($R^{2} = 0.25$), and predictions made using embedding distance outperform those made with geographic distance (Fig.~\ref{fig:gravity_performance}d).
 This performance is consistent in the case of scientific mobility:
@@
 The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores  calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-In sum, our results demonstrate that the embedding distance better captures patterns of actual mobility than does the geographic distance consistently.
+In sum, our results demonstrate that, consistently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
 
@@
 		Results are consistent in the case of scientific mobility. 
-		For South Korean hotel reservations, embedding distance better explains the expected flux than does geographic distance (\textbf{c}), and produces better predictions (\textbf{d}).
+		For South Korean accommodation reservations, embedding distance better explains the expected flux than does geographic distance (\textbf{c}), and produces better predictions (\textbf{d}).
 		Similarly, in the case of global scientific mobility, embedding distance explains the expected flux between organizations (\textbf{e)} and allows for better predictions (\textbf{f}) than geographic distance.

### 2020-10-20 paper/current/main.tex
change to legal name

@@
 \subsection*{Korean accommodation reservation data}
-We source Korean accommodation reservation data from collaboration with Good Choice Company in Korea, containing 938,962 trajectories spanning the time period of August 2018 through July 2020,  comprising 1,038 unique accommodation locations in Seoul, South Korea.
+We source Korean accommodation reservation data from collaboration with Goodchoice Company LTD.
+in Korea, containing 938,962 trajectories spanning the time period of August 2018 through July 2020,  comprising 1,038 unique accommodation locations in Seoul, South Korea.
 

### 2020-10-21 paper/current/main.tex
add more affiliation

@@
 \author[3]{Rodrigo Costas}
-\author[2]{Woo-Sung Jung}
+\author[2,4,5]{Woo-Sung Jung}
 \author[1]{Staša Milojević \thanks{smilojev@indiana.edu}}
-\author[1,4,5]{Yong-Yeol Ahn \thanks{yyahn@iu.edu}}
+\author[1,6,7]{Yong-Yeol Ahn \thanks{yyahn@iu.edu}}
 
@@
 2300 AX Leiden, The Netherlands}
-\affil[4]{Network Science Institute, Indiana University, Bloomington (IUNI), IN 47408, USA}
-\affil[5]{Connection Science, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
+\affil[4]{Department of Physics, Pohang University of Science and Technology,
+Pohang 37673, Republic of Korea.}
+\affil[5]{Asia Pacific Center for Theoretical Physics, Pohang 37673, Republic of Korea.}
+
+\affil[6]{Network Science Institute, Indiana University, Bloomington (IUNI), IN 47408, USA}
+\affil[7]{Connection Science, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
 

### 2020-10-21 paper/current/supp.tex
allow supp to reference main figures
some errors on suppl

@@
 \usepackage{changepage}
+
+% External file referencing
+\usepackage{xr}
+\externaldocument{main}
 
@@
 	\caption{
-		\textbf{For geographic distance, the power-decay gravity model is better.}
+		\textbf{For embedding distance, the exponential=decay gravity model is better.}
 		Flux between organization pairs predicted by the gravity model with different distance decay functions, i.e., exponential decay function (\textbf{a}) and power-law decay function (\textbf{b}) using embedding distance.

### 2020-10-21 paper/current/supp.tex
revert refernece part

@@
 		Color of each hex bin indicates frequency of organization pairs.
-		Results here are identical to those shown in Fig.2.
+		Results here are identical to those shown in Fig.~\ref{fig:gravity_performance}.
 		\textbf{c-d.}	embedding distance explains more variance when considering only within-country organization pairs.
@@
 		a perfect prediction yields all points on the black line.
-		\textbf{a-b.} Predictions are made with parameters estimated from all pairs of organizations (as in Fig.2e), and showing only the subsets of predictions for organization pairs in the same country (\textbf{a}) and in different countries (\textbf{b}).
+		\textbf{a-b.} Predictions are made with parameters estimated from all pairs of organizations (as in Fig.~\ref{fig:gravity_performance}e), and showing only the subsets of predictions for organization pairs in the same country (\textbf{a}) and in different countries (\textbf{b}).
 		\textbf{c-d.} Predictions made using parameters estimated from the subset of organizations in the same country (\textbf{c}) and different country \textbf{d});
-		this is the same data as shown in Fig.2f and Fig.2h.
+		this is the same data as shown in Fig.~\ref{fig:gravity_performance}f and Fig.~\ref{fig:gravity_performance}h.
 	}

### 2020-10-21 paper/current/main.tex
edit on sk data

@@
 \author[3]{Rodrigo Costas}
-\author[2,4,5]{Woo-Sung Jung}
+\author[2,4]{Woo-Sung Jung}
 \author[1]{Staša Milojević \thanks{smilojev@indiana.edu}}
@@
 We source Korean accommodation reservation data from collaboration with Goodchoice Company LTD.
-in Korea, containing 938,962 trajectories spanning the time period of August 2018 through July 2020,  comprising 1,038 unique accommodation locations in Seoul, South Korea.
+in Korea, The data contain reservation trajectories of each customer spanning the time period of August 2018 through July 2020, and comprising 1,038 unique accommodation locations in Seoul, South Korea.
 

### 2020-10-23 paper/current/main.tex
ackwoldgement
implement stasa's comments

@@
 Low dimensional distance alone cannot represent the multitude of inter-related factors that drive mobility. 
-Networks offer a solution to representing many dimensions of mobility, yet edges only encode simple relationships between connected entities, and cannot easily capture the rich landscape of mobility. 
+Networks offer a solution to representing many dimensions of mobility, yet edges only encode simple relationships between connected entities.
 Thus, capturing the complexity of mobility requires moving beyond simple functional distances and networks, to learning high-dimensional landscapes of mobility that incorporate the many facets of mobility into a single fine-grained and continuous representation.
@@
 A trajectory is constructed for each customer's accommodation reservation history, constructing an ordered sequence of accommodations reserved over time.
-Finally, we use scientific mobility data that captures the affiliation trajectories of nearly 13 million scientists across ten years.
+Finally, we use scientific mobility data that captures the affiliation trajectories of nearly 3 million scientists across ten years.
 We focus in more detail on scientific mobility due to its richness and importance. 
@@
 Also, the embedding distance produces better predictions of actual flux between airports than does the geographic distance (Fig.~\ref{fig:gravity_performance}b).
-In the case of South Korean accommodation reservations, such that the embedding distance better explains the expected flux ($R^{2} = 0.57$, Fig.~\ref{fig:gravity_performance}c) than does geographic distance ($R^{2} = 0.25$), and predictions made using embedding distance outperform those made with geographic distance (Fig.~\ref{fig:gravity_performance}d).
+In the case of South Korean accommodation reservations, embedding distance better explains the expected flux ($R^{2} = 0.57$, Fig.~\ref{fig:gravity_performance}c) than does geographic distance ($R^{2} = 0.25$), and predictions made using the embedding distance outperform those made with geographic distance (Fig.~\ref{fig:gravity_performance}d).
 This performance is consistent in the case of scientific mobility:
@@
 	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the embedding and Times ranking is $\rho = 0.73$ ($n = 145$), which increases when more top-and-bottom ranked universities are included (Fig.~\ref{fig:supp:semaxis_compare}).
-	  	\textbf{b.} Times ranking is correlated with Leiden Ranking of U.S. universities with Spearman's $\rho = 0.87$.
+	  	\textbf{b.} The Times ranking is correlated with Leiden Ranking of U.S. universities with Spearman's $\rho = 0.87$.
 		\textbf{c-f.} Illustration of SemAxis projection along two axes;  \textit{latent geographic axis}, from California to Massachusetts (left to right) and the \textit{prestige axis}.
@@
 However, at around 1,000 researchers, the size of the vector \emph{decreases} as the number of researchers increases.
-These organizations are primarily research-intensive and prestigious universities with higher rankings, research outputs, R\&D funding, and doctoral students (Fig.~\ref{fig:supp:length_vs_metaInfo}).
+These organizations are primarily research-intensive and prestigious universities with higher rank, research outputs, R\&D funding, and doctoral students (Fig.~\ref{fig:supp:length_vs_metaInfo}).
 A similar pattern has been observed in applications of neural embedding to natural language, in which the size of word vectors were found to represent the word's \emph{specificity}, i.e., the word associated with the vector frequently co-appears with particular context words\autocite{schakel2015measuring}.
@@
 However, some countries such as France and the United States seem to have more domestic mobility than international mobility.
-While the number of publications has increased year-to-year, the mobility and disciplinary makeup of the dataset has not significantly changed across the period of study (Fig.~\ref{fig:supp:pubs_over_time}).
+While the number of publications has increased year-to-year, the mobility and disciplinary makeup of the dataset has not notably changed across the period of study (Fig.~\ref{fig:supp:pubs_over_time}).
 
@@
 The poles of the geographic axis are defined as the mean vector of all vectors corresponding to organizations in California, and then the mean of all vectors of organizations in Massachusetts.
-For the prestige axis, we define a subset of top-ranked universities according to either the Times World University Rankings or based on the mean normalized research impact sourced from the Leiden Rankings.
+For the prestige axis, we define a subset of top-ranked universities according to either the Times World University Ranking or based on the mean normalized research impact sourced from the Leiden Ranking.
 The other end of the prestige axis is the geographically-matched (according to census region) set of universities ranked at the bottom of these rankings.
@@
 We thank the Center for Science and Technology Studies at Leiden University for managing and making available the dataset of scientific mobility.
+We also thank the  Goodchoice Company LTD for making  available the dataset of Korean accommodation reservation data.
 For their comments, we thank Guillaume Cabanac, Cassidy R. Sugimoto, Vincent Lariviére, Alessandro Flammini, Filippo Menczer, Lili Miao, Xiaoran Yan, and Inho Hong. 

### 2020-10-23 paper/current/main.tex
added word
tweaks to SK data

@@
 		Shown for U.S. Universities (\textbf{c}), regional and liberal arts colleges (\textbf{d}), Research institutes (\textbf{e}), and Government organizations (\textbf{f}).
-		Full organization names listed in Table~\ref{table:supp:orglabels}.
+		Full organization names are listed in Table~\ref{table:supp:orglabels}.
 	}
@@
 \subsection*{Korean accommodation reservation data}
-We source Korean accommodation reservation data from collaboration with Goodchoice Company LTD.
-in Korea, The data contain reservation trajectories of each customer spanning the time period of August 2018 through July 2020, and comprising 1,038 unique accommodation locations in Seoul, South Korea.
+We source South Korean accommodation reservation data from collaboration with Goodchoice Company LTD. 
+The data contains customer-level reservation trajectories spanning the time period of August 2018 through July 2020, and comprising 1,038 unique accommodation locations in Seoul, South Korea.
 

### 2020-10-24 paper/current/main.tex
main text, yy comments

@@
 As understanding mobility is becoming critical for contemporary society, finding frameworks that can capture this complexity are of paramount importance.
-Here, using three datasets that capture human trajectories,  we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
+Here, using three discrete human trajectory datasets,  we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
 Focusing on the case of scientific mobility, we show that embeddings of scientific organizations uncovers cultural and linguistic relations at multiple levels of granularity, and even academic prestige.
@@
 $\hat{T}_{ij}$, which is often referred to as ``expected flux''~\autocite{simini2012universal}, is the expected frequency of the co-occurrence of location $i$ and $j$ in the trajectory in the gravity model.
-The gravity model dictates that the expected flow, $\hat{T}_{ij}$, is symmetric (\ie $\hat{T}_{ij }= \hat{T}_{ji})$), is proportional to the locations' population, $\hat{T}_{ij} \propto m_{i} m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+The gravity model dictates that the expected flow, $\hat{T}_{ij}$, ($\hat{T}_{ij }= \hat{T}_{ji}$), is proportional to the locations' population, $\hat{T}_{ij} \propto m_{i} m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
 We define the distance function in terms of either the geographic distance between locations or their functional distance in the vector space, which is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.
@@
 
-In the remaidner of the paper, we focus only on scientific mobility, leveraging its richness to investigate how the geometric space generated by the neural embedding method sheds light on the multi-faceted relationships between organizations.
+In the remainder of the paper, we focus on scientific mobility, leveraging its richness to investigate how the geometric space generated by the neural embedding method sheds light on the multi-faceted relationships between organizations.
 To explore the topological structure of the embedding, we use a topology-based dimensionality reduction method (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation of the embedding space (Fig.~\ref{fig:projection}a).
@@
 Smaller but scientifically advanced countries such as Australia, and other populous countries such as Brazil also exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset).
-Other nations exhibit different curves which lacks the portions with decreasing norm, probably indicating the lack of highly prestigious institutions.
-Similar patterns can be found across many of the 30 of the countries with the most total researchers (Fig.~\ref{fig:concave30}) see \SI{} for more discussion).
+Other nations exhibit different curves which lacks the portions with decreasing norm, probably indicating the lack of internationally-prestigious institutions.
+Similar patterns can be found across many of the 30 of the countries with the most total researchers (Fig.~\ref{fig:concave30}; see \SI{} for more discussion).
 

### 2020-10-25 paper/current/main.tex
methods, implement YY edits

@@
 where $a_{t+\tau} = j \vert a_{t+\tau} = i$, and $N$ is the number of unique locations represented in the data, and $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively.
-The in-vector and out-vectors are different kinds of vector representations for locations.
-We only use the in-vector, $v$, because the in-vector is more widely used and often superiors to the out-vector in link prediction benchmarks~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}.
+We follow the standard practice and only use the in-vector, $v$,  which is known to be superior to the out-vector in link prediction benchmarks~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}.
 
@@
 We calculate $T_{ij}$ as the total number of co-occurrence between two locations $i$ and $j$ across the data-set.
-For case in scientific mobility, $T_{ij} = 10$ indicates that the number of co-occurrence between both organization $i$ and $j$ between 2008 and 2019 is 10, as evidenced from their publications.
-We treat $T_{ij} = T_{ji}$ because directional information is not informative.
+In scientific mobility, $T_{ij} = 10$ indicates that the number of co-occurrence between both organization $i$ and $j$ between 2008 and 2019 is 10, as evidenced from their publications.
+Here, we treat $T_{ij} = T_{ji}$ for the sake of simplicity, and, in the case of scientific mobility, because  directionalality cannot easily be derived from bibliometric records, or may not be particularly affirmative (see \SI).
 
@@
 
-We model co-occurences $T_{ij}$ for locations $i$, and $j$, often referred to as flux, using the gravity law of mobility~\autocite{zipf1946gravity}.
-The gravity law of mobility loosely derives from the physical law of gravity, in which the attraction between two objects is a function of their mass and the distance between them.
+We model co-occurences $T_{ij}$ for locations $i$ and $j$ (referred to as flux), using the gravity law of mobility~\autocite{zipf1946gravity}.
+The gravity law of mobility, which was inspired by Newton's law of gravity, postulates that attraction between two locations is a function of their population and the distance between them.
 This formulation and variants have proven useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, truscott2012epidemicgravity, hong2016busgravity}.
-In the gravity law of mobility, the \textit{expected flux}, $\hat{T_{ij}}$ between two organizations $i$ and $j$ is defined as,
+In the gravity law of mobility, the \textit{expected flux}, $\hat{T_{ij}}$ between two locations $i$ and $j$ is defined as,
 
@@
 \end{equation}
-where $m_{i}$ and $m_{j}$ are the population of locations which is the total number of passenger on each airport for U.S.
-airport itinerary and the yearly-average count of unique authors, both mobile and non-mobile, affiliated with each organization for scientific mobility.
+where $m_{i}$ and $m_{j}$ are the population of locations (\eg the total number of passenger on each airport for U.S.
+airport itinerary and the yearly-average count of unique authors, both mobile and non-mobile, affiliated with each organization for scientific mobility).
 $f(r_{ij})$ is a decay function of distance $r_{ij}$ between locations $i$ and $j$. 
@@
 In the case of natural language, the poles of the axis could be ``good'' and ``bad'', ``surprising'' and ``unsurprising'', or ``masculine'' and ``feminine''.
-By treating organizations analogously to words and trajectories analogously to sentences, we can use SemAxis to leverage the semantic properties of the embedding vectors to operationalize abstract relationships between organizations.
+We can use SemAxis to leverage the semantic properties of the embedding vectors to operationalize abstract relationships between organizations.
 

### 2020-10-25 paper/current/main.tex
data availability, yy comments
fixed references
proofreading, main text

@@
 ]{biblatex}
+
+% Ignore irrelevant biblatex fields
+\AtEveryBibitem{%
+ \clearfield{url}%
+   \clearfield{month}%
+ \clearfield{issn}%
+ \clearfield{doi}%%
+}
+
 \addbibresource{mobility.bib}
@@
 As understanding mobility is becoming critical for contemporary society, finding frameworks that can capture this complexity are of paramount importance.
-Here, using three discrete human trajectory datasets,  we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
-Focusing on the case of scientific mobility, we show that embeddings of scientific organizations uncovers cultural and linguistic relations at multiple levels of granularity, and even academic prestige.
+Here, using three datasets of discrete human trajectories, we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
+Focusing on the case of scientific mobility, we show that embeddings of scientific organizations uncovers cultural and linguistic relations, and even academic prestige, at multiple levels of granularity.
 Furthermore, the embedding vectors reveal universal relationships between organizational characteristics, and their place in the global landscape of scientific mobility. 
@@
 Similarly, a student in South Korea is more likely to attend a university in Canada than one in North Korea~\autocite{unesco2019students}.
-Although geographic distance has been used as the most prominent basis for models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} models, there have been attempts to define alternative notions of distance, or functional distances~\autocite{boschma2005proximity, brown1970migration, kim2018functional} from real-world data or \textit{a priori} relationships between geographic entities.
+Although geographic distance has been used as the most prominent basis for models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} models, there have been attempts to define alternative notions of distance, or functional distances~\autocite{boschma2005proximity, brown1970migration, kim2018functional}, from real-world data or \textit{a priori} relationships between geographic entities.
 
@@
 Networks offer a solution to representing many dimensions of mobility, yet edges only encode simple relationships between connected entities.
-Thus, capturing the complexity of mobility requires moving beyond simple functional distances and networks, to learning high-dimensional landscapes of mobility that incorporate the many facets of mobility into a single fine-grained and continuous representation.
+Capturing the complexity of mobility requires moving beyond simple functional distances and networks, to learning high-dimensional landscapes of mobility that incorporate the many facets of mobility into a single fine-grained and continuous representation.
 
-Here, we apply a neural embedding framework to real-world mobility trajectories and demonstrate that it can encode the complex landscape of human mobility into a dense and continuous vector-space representation, from which we can not only derive a meaningful functional distance between places but also probe relationships based on culture, language, and even prestige along with geographic relationship.
+Here, we apply a neural embedding framework to real-world mobility trajectories and demonstrate that it can encode the complex landscape of human mobility into a dense and continuous vector-space representation, from which we can not only derive a meaningful functional distance between locations but also probe relationships based on culture, language, and even prestige along with geographic relationship.
 We embed trajectories from three massive datasets: U.S.
@@
 A trajectory is constructed for each passenger flight itinerary, forming an ordered sequence of unique identifiers of the origin and destination airports. 
-The Korean accommodation reservations consist of accommodation reservation history between 2018 and 2020 between 1,038 unique accommodation locations in Seoul, South Korea.
-A trajectory is constructed for each customer's accommodation reservation history, constructing an ordered sequence of accommodations reserved over time.
+The South Korean accommodation reservations consist of customer reservation histories across 2018 and 2020 for 1,038 unique accommodation locations in Seoul, South Korea.
+A trajectory is constructed for each customer, containing the ordered sequences of accommodations they reserved over time.
 Finally, we use scientific mobility data that captures the affiliation trajectories of nearly 3 million scientists across ten years.
 We focus in more detail on scientific mobility due to its richness and importance. 
-Scientific mobility, which is a central driver of the globalized scientific enterprise~\autocite{czaika2018globalisation, box2008competition} and strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, morgan2018prestige}, is not only an important topic in the Science of Science but also ideal for our study thanks to its richness and well-known structural properties such as the centrality of scientifically advanced countries and the strong prestige hierarchy~\autocite{clauset2015hierarchy, deville2014career}.
+Scientific mobility---which is a central driver of the globalized scientific enterprise~\autocite{czaika2018globalisation, box2008competition} and strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, morgan2018prestige}---is not only an important topic in the Science of Science but also ideal for our study thanks to its well-known structural properties such as the centrality of scientifically advanced countries and the strong prestige hierarchy~\autocite{clauset2015hierarchy, deville2014career}.
 In spite of its importance, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, deville2014career}, being further confounded by the diminishing role of geography in shaping the landscape of scientific mobility.
@@
 
-A vector-space embedding of locations (airports and organizations) is learned by using trajectories as input to the standard skip-gram negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
+A vector-space embedding of locations (airports, accommodations, and organizations) is learned by using trajectories as input to the standard with skip-gram negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
 This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered} and networks~\autocite{grover2016node2vec}.
@@
     \caption{
-        \textbf{Construction of affiliation trajectories from publication records}
+        \textbf{Construction of affiliation trajectories from publication records.}
         \textbf{a.}
@@
 To validate our approach, we evaluate the quality of vector representations with their performance in predicting real-world mobility flows using the gravity model framework~\autocite{zipf1946gravity}.
-The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity} that models the \textit{expected flux}, $\hat{T}_{ij}$ between locations (airports and organizations) based on their populations and distance:
+The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity} that models the \textit{expected flux}, $\hat{T}_{ij}$, between locations based on their populations and distance:
 
@@
 We define the distance function in terms of either the geographic distance between locations or their functional distance in the vector space, which is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.
-For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_emb_bymodel} and Fig.~\ref{fig:supp:predict_geo_bymodel}).
+For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}).
 
@@
 %
-% TODO: remove the subsection label?
 %
@@
 the embedding distance explains more than twice the expected flux ($R^{2} = 0.48$, Fig.~\ref{fig:gravity_performance}e) than does the geographic distance ($R^{2} = 0.22$), and predictions made using the embedding distance outperform those using the geographic distance (Fig.~\ref{fig:gravity_performance}f).
-These patterns hold for the subsets of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}c and Fig.~\ref{fig:supp:predict_geo_bymodel}) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d and  Fig.~\ref{fig:supp:predict_emb_bymodel}).
+These patterns hold for the subsets of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d and  Fig.~\ref{fig:supp:predict_emb_bymodel}).
 The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores  calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
@@
 	\caption{
-		\textbf{Embedding distance encodes functional distance and better predicts U.S flights, accommodation reservations, and global scientific mobility.}
+		\textbf{Embedding distance encodes functional distance and better predicts mobility in flights, accommodation reservations, and global scientific mobility.}
 		\textbf{a} Embedding distance (cosine distance between organization vectors, top) better explains the expected flux of passengers between U.S. airports than does geographic distance (bottom). 
@@
 Globally, the geographic constraints are conspicuous; organizations tend to form clusters based on their national affiliations and national clusters tend to be near their geographic neighbors.
-At the same time, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions much more clearly than alternative network representations (Fig.~\ref{fig:supp:network_vis}) that have been dominating studies of scientific mobility~\autocite{chinchilla2018global, czaika2018globalisation}.
+At the same time, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions much more clearly than alternative network representations (Fig.~\ref{fig:supp:network_vis}) that have been common in studies of scientific mobility~\autocite{chinchilla2018global, czaika2018globalisation}.
 
 The embedding space also allows us to \textit{zoom in} on subsets and re-project them to reveal local relationships.
-For example, re-projecting organizations located in Western, Southern, and Southeastern Asia with UMAP (Fig.~\ref{fig:projection}b) reveals a gradient of countries between Egypt and the Philippines that largely corresponds to geography, but with some exceptions along with the cultural and religious spectra;
+For example, re-projecting organizations located in Western, Southern, and Southeastern Asia with UMAP (Fig.~\ref{fig:projection}b) reveals a gradient of countries between Egypt and the Philippines that largely corresponds to geography, but with some exceptions seemingly stemming from cultural and religious similarity;
 Malaysia, with its official religion of Islam, is nearer to Middle Eastern countries in the embedding space than many geographically-closer South Asian countries.
-We also validate this finding quantitatively with the cosine distance between nations (the centroids of organizations vectors belonging to that country). 
+We validate this finding quantitatively with the cosine distance between nations (the centroids of organizations vectors belonging to that country). 
 Malaysia is nearer to many Islamic countries such as Iraq ($d = 0.29$), Pakistan ($d = 0.31$), and Saudi Arabia ($d = 0.41$)  than neighboring but Buddhist Thailand ($d = 0.43$) and predominantly-secular Vietnam ($d = 0.48$).
@@
 Similarly, North-African countries that were once under French rule such as Morocco are closer to France ($d =0.35$) than to similarly geographically-distant European countries such as Spain ($d = 0.40$), Portugal ($d = 0.55$), and Italy ($d = 0.53$).
-Comparable structural patterns exist even within a single country.
-For example, organizations within Quebec in Canada are located nearer the French cluster ($d = 0365$) than the United States cluster ($d = 0.49$).
+Comparable patterns exist even within a single country.
+For example, organizations within Quebec in Canada are located nearer France ($d = 0.37$) than the United States ($d = 0.49$).
 
@@
 		The separation of organizations in Quebec and the rest of Canada is highlighted. 
-		\textbf{b.} Zooming into (re-projecting) the area containing countries in the Middle East and South and Southeast Asia shows a geographic and cultural gradient of country clusters.
-		\textbf{c.} Similarly, zooming into the area organizations in Spain, Portugal, South, and Central America shows clustering by most widely-spoken majority language group--Spanish and Portuguese.
+		\textbf{b.} Zooming into (re-projecting) the area containing countries in Western, South, and Southeast Asia shows a geographic and cultural gradient of country clusters.
+		\textbf{c.} Similarly, zooming into the area containing organizations in Spain, Portugal, South, and Central America shows clustering by most widely-spoken majority language group: Spanish and Portuguese.
 		\textbf{d.} Doing the same for organizations in the United States reveals geographic clustering based on state, roughly grouped by Census Bureau-designated regions,
@@
 We can examine the country-level structure that governs scientific mobility.
-For the purpose, we define the representative vector of each country as the average of their organizational vector and perform hierarchical clustering of nations that have at least 25 organizations represented in the embedding space based on their cosine similarity, excluding the United States which is a dominant hub well connected to most other countries (see Fig.
+For the purpose, we define the representative vector of each country as the average of their organizational vectors and, using their cosine similarities, perform hierarchical clustering of nations that have at least 25 organizations represented in the embedding space, excluding the United States which is a dominant hub well connected to most other countries (see Fig.
 \ref{fig:clustering}a).
@@
 
-We quantify the relative importance of geography (by region), and language (by most widely-spoken language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering by explicitly adjusting the relative importance of different levels of the hierarchy with scaling parameter $r$, acting like a \textit{zooming lens}.
+We quantify the relative importance of geography (by region), and language (by the most widely-spoken language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering by explicitly adjusting the relative importance of different levels of the hierarchy with a scaling parameter $r$, acting like a \textit{zooming lens}.
 If $r$ is high, the similarity is based on the lower levels of the dendrogram, whereas when $r$ is low, the similarity is based on higher levels.
@@
 
-Prestige hierarchy is known to underpin the dynamics of scientific mobility, where researchers tend to move to similar or less prestigious organizations~\autocite{deville2014career, clauset2015hierarchy}.
+Prestige hierarchy is known to underpin the dynamics of scientific mobility, in which researchers tend to move to similar or less prestigious organizations~\autocite{deville2014career, clauset2015hierarchy}.
 Could the embedding space, to which no explicit prestige information is given, encode a prestige hierarchy?
@@
 The embedding-based ranking is strongly correlated with the Times ranking (Spearman's $\rho = 0.73$, Fig.~\ref{fig:semaxis}a).
-For reference, the correlation between the Times ranking and the publication impact scores from the Leiden Ranking~\autocite{waltman2012leidenrankings}, a bibliometrically-based university ranking is 0.87 (Spearman's $\rho$, Fig.~\ref{fig:semaxis}b).
-The correlation between the embedding-based ranking and the Times ranking is robust regardless of the number of organizations used to define the axes (Fig.
-~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities produces a ranking that is significantly correlated with the Times ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
+For reference, the correlation between the Times ranking and the publication impact scores from the Leiden Ranking~\autocite{waltman2012leidenrankings}, a bibliometrically-based university ranking, is 0.87 (Spearman's $\rho$, Fig.~\ref{fig:semaxis}b).
+The correlation between the embedding-based ranking and the Times ranking is robust regardless of the number of organizations used to define the axes (Fig.~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities produces a ranking that is significantly correlated with the Times ranking (Spearman's $\rho = 0.46$, Fig.~\ref{fig:supp:semaxis_compare}a).
 The correlation is also comparable to more direct measures such as node strength (sum of edge weights, Spearman's $\rho = 0.73$) and eigenvector centrality (Spearman's $\rho = 0.76$, see \SI) from the mobility network.
@@
 Those ranked higher in the embedding-based ranking tend to be relatively-small universities near major urban areas such as the University of San Francisco and the University of Maryland Baltimore County, possibly reflecting exchanges of scholars with nearby high-ranked institutions at these locations.
-In sum, our result suggests that the embedding space is capable of capturing information about academic prestige, even when the representation is learned using data without explicit information on the direction of mobility (as in other formal models~\autocite{clauset2015hierarchy}), or prestige.
+In sum, our results suggest that the embedding space is capable of capturing information about academic prestige, even when the representation is learned using data without explicit information on the direction of mobility (as in other formal models~\autocite{clauset2015hierarchy}), or prestige.
 
@@
 Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphasis on teaching, such as Barry University and California State University at Long Beach.
-By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reason about the prestige of organizations for which rankings are often low-resolution, incomplete, or entirely absent, such as regional and liberal arts universities, seminaries, musical schools, community colleges (Fig.~\ref{fig:semaxis}d), government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).
+By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reason about the prestige of organizations for which rankings are often low-resolution, incomplete, or entirely absent, such as regional and liberal arts universities (Fig.~\ref{fig:semaxis}d), government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).
 Their estimated prestige is speculative, though we find that it significantly correlates with their citation impact (Fig.~\ref{fig:supp:sector_semaxis_impact}).
@@
 		\textbf{a.} Comparison between the ranking of organizations in the Times ranking and the embedding ranking derived using SemAxis.
-		Un-filled points are those top and bottom five universities used span the axis.
+		Un-filled points are those top and bottom five universities used to span the axis.
 	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the embedding and Times ranking is $\rho = 0.73$ ($n = 145$), which increases when more top-and-bottom ranked universities are included (Fig.~\ref{fig:supp:semaxis_compare}).
 	  	\textbf{b.} The Times ranking is correlated with Leiden Ranking of U.S. universities with Spearman's $\rho = 0.87$.
-		\textbf{c-f.} Illustration of SemAxis projection along two axes;  \textit{latent geographic axis}, from California to Massachusetts (left to right) and the \textit{prestige axis}.
-		Shown for U.S. Universities (\textbf{c}), regional and liberal arts colleges (\textbf{d}), Research institutes (\textbf{e}), and Government organizations (\textbf{f}).
+		\textbf{c-f.} Illustration of SemAxis projection along two axes;  the \textit{latent geographic axis}, from California to Massachusetts (left to right) and the \textit{prestige axis}.
+		Shown for U.S. Universities (\textbf{c}), Regional and liberal arts colleges (\textbf{d}), Research institutes (\textbf{e}), and Government organizations (\textbf{f}).
 		Full organization names are listed in Table~\ref{table:supp:orglabels}.
@@
 If the word in question is universal, appearing frequently in many different contexts, it would not have a large norm due to a lack of strong association with a particular context.
-Likewise, an organization such as Harvard with a small norm appears in many contexts, alongside many different organizations in affiliation trajectories---it is well-connected.
+Likewise, an organization with a small norm, such as Harvard, appears in many contexts alongside many different organizations in affiliation trajectories---it is well-connected.
 The concavity of the curve emerges in part from the relationship between the size of the vector and the expected connectedness of the organization, given its size ($R^{2} = 0.17$).
@@
 Other nations exhibit different curves which lacks the portions with decreasing norm, probably indicating the lack of internationally-prestigious institutions.
-Similar patterns can be found across many of the 30 of the countries with the most total researchers (Fig.~\ref{fig:concave30}; see \SI{} for more discussion).
+Similar patterns can be found across many of the 30 countries with the most total researchers (Fig.~\ref{fig:concave30}; see \SI{} for more discussion).
 
@@
 		Uncolored points are universities not listed on the Times ranking.
-		A convex-shape emerges, wherein larger universities tend to be more distant from the origin (large L2 norm); however, the more prestigious universities tend to have smaller L2 norms.
-		\textbf{b.} We find a similar convex-curve pattern across many countries such as the United States, China, Australia, Brazil, and others (\textbf{inset}, and Fig.~\ref{fig:concave30}). 
+		A concave-shape emerges, wherein larger universities tend to be more distant from the origin (large L2 norm); however, the more prestigious universities tend to have smaller L2 norms.
+		\textbf{b.} We find a similar concave-curve pattern across many countries such as the United States, China, Australia, Brazil, and others (\textbf{inset}, and Fig.~\ref{fig:concave30}). 
 		Some countries exhibit variants of this pattern, such as Egypt, which is missing the right side of the curve.
@@
 We demonstrated that a functional distance derived from the embedding can be used with the gravity model of mobility to better predict real-world mobility than does geographic distance.
-Embedding distance outperformed geographic distance both in the case of U.S. flight itineraries and global scientific mobility, which represent two domains with disparate nature. 
+Embedding distance outperformed geographic distance across distinct and disparate domains, including U.S.
+flight itineraries, South Korean hotel accommodation reservations, and global scientific mobility.
 Focusing on scientific mobility, we find that neural embedding's performance is driven by its ability to encode many aspects of scientific mobility into a single representation, including global and regional geography, shared languages, and prestige hierarchies, even without explicit information on these factors.
 
-While we focus on data of U.S.
-flight itineraries and scientific mobility, this approach may be broadly applicable to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
+While we focus on three domains of mobility, this approach may be broadly applicable to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
 Moreover, this approach can be used to learn a functional distance even between entities for which no physical analog exists, such as between occupational categories based on individuals' career trajectories.
@@
 The kinds of mobility we do capture---migration, and co-affiliation---although conceptually different, are treated identically by our model.
-Also, our data might further suffer from survivorship bias: researchers at prestigious organizations tend to have more publications, leading to these organizations appearing more frequently in affiliation trajectories.
+Also, our data might further suffer from bias based on publication rates: researchers at prestigious organizations tend to have more publications, leading to these organizations appearing more frequently in affiliation trajectories.
 
@@
 DB1B is a sample of 10 percent of domestic airline tickets between 1993 and 2020, comprising 307,760,841 passenger itineraries between 828 U.S. airports. 
-Each itinerary is associated with a a trajectory of airports including an origin, destination, and intermediary stops.
+Each itinerary is associated with a a trajectory of airports including the origin, destination, and intermediary stops.
 
@@
 We source co-affiliation trajectories of authors from the Web of Science database hosted by the Center for Science and Technology Studies at Leiden University.
-Trajectories are constructed from author affiliations listed on the byline of publications for a given author.
+Trajectories are constructed from author affiliations listed on the byline of publications for an author.
 Given the limitations of author-name disambiguation, we limit our analyses to papers published after 2008, when the Web of Science began providing full names and institutional affiliations~\autocite{caron2014disambiguation} that improved disambiguation (see \SI).
 This yields 33,934,672 author-affiliation combinations representing 12,963,792 authors.
-Each author-affiliation combination is associated with the publication year and an ID linking it to one of 8,661 disambiguated organizational affiliations (see \SI for more detail).
+Each author-affiliation combination is associated with the publication year and an ID linking it to one of 8,661 disambiguated organizational affiliations (see \SI{} for more detail).
 Trajectories are represented as the list of author-affiliation combinations, ordered by year of publication, and randomly ordered for combinations within the same year.
@@
 Here, authors are classified as mobile when they have at least two distinct organization IDs in their trajectory, meaning that they have published using two or more distinct affiliations between 2008 and 2019.
-Under this definition, mobile authors constitute 3,007,192 or 23.2 \% of all authors and 17,700,095 author-affiliation combinations.
+Under this definition, mobile authors constitute 3,007,192 or 23.2\% of all authors and 17,700,095 author-affiliation combinations.
 Mobile authors were associated with 2.5 distinct organizational affiliations on average.
@@
 \textit{word2vec} constructs dense and continuous vector representations of words and phrases, in which distance between words corresponds to a notion of semantic distance. 
-By embedding trajectories, we aim to learn a dense vector for every locations where the distance between vectors relates to the tendency for two locations to occur in similar contexts.
-Suppose an trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), where $a_{t}$ is the $t$th location in the trajectory.
+By embedding trajectories, we aim to learn a dense vector for every location, for which the distance between vectors relates to the tendency for two locations to occur in similar contexts.
+Suppose a trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), where $a_{t}$ is the $t$th location in the trajectory.
 A location, $a_{t}$, is considered to have context locations, $a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}$, that appear in the window surrounding $a_t$ up to a time lag of $w$, where $w$ is the window size parameter truncated at $t - w \geq 0$ and $t + w \leq T$.
@@
 In scientific mobility, $T_{ij} = 10$ indicates that the number of co-occurrence between both organization $i$ and $j$ between 2008 and 2019 is 10, as evidenced from their publications.
-Here, we treat $T_{ij} = T_{ji}$ for the sake of simplicity, and, in the case of scientific mobility, because  directionalality cannot easily be derived from bibliometric records, or may not be particularly affirmative (see \SI).
+Here, we treat $T_{ij} = T_{ji}$ for the sake of simplicity and, in the case of scientific mobility, because  directionalality cannot easily be derived from bibliometric records, or may not be particularly informative (see \SI).
 
@@
 Geographic distance is calculated as the great circle distance, in kilometers, between pairs of locations.
-In the case of U.S.
-flight itinerary and scientific mobility, we impute distance to 1 km when their distance is less than one kilometer.
-In the case of Korean accommodation reservation data, because this data is intra-city mobility trajectory, we impute distance to 0.01 km when their distance is less than 0.01 km.
+In the case of U.S. flight itinerary and scientific mobility, we impute distance to 1 km when their distance is less than one kilometer. 
+In the case of South Korean accommodation reservation data, because this data is intra-city mobility trajectory, we impute distance to 0.01 km when their distance is less than 0.01 km. 
 The embedding distance with the cosine distance, $d_{ij}$, is calculated as $d_{ij} = 1 - \frac{\bm{v}_{i} \cdot \bm{v}_{j}}{\lVert \bm{v}_{i} \rVert \lVert \bm{v}_{j} \rVert}$,
@@
 There are two popular forms for the $f(r_{ij})$:
-one is a power law function in the form $f(r_{ij})= r^{-\alpha}_{ij} \ (\alpha > 0$, and the other and the another one is an exponential function in the form $f(r_{ij}) = e^{-\beta r_{ij}} \ (\beta > 0)$ \autocite{chen2015distance}.
+one is a power law function in the form $f(r_{ij})= r^{-\alpha}_{ij} \ (\alpha > 0)$, and the other is an exponential function in the form $f(r_{ij}) = e^{-\beta r_{ij}} \ (\beta > 0)$ \autocite{chen2015distance}.
 The parameters for $f(r_{ij})$ and $C$ are fit to given mobility data using a log-linear regression~\autocite{jung2008highwaygravity, curiel2018citygravity, truscott2012epidemicgravity, hong2016busgravity, simini2012universal}.
@@
 SemAxis and similar studies~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} demonstrated that ``semantic axes'' can be found from an embedding space by defining the ``poles'' and the latent semantic relationship along semantic axis can be extracted with the simple arithmetic.
-Each axis is an antonym pair defined for each specific use case.
 In the case of natural language, the poles of the axis could be ``good'' and ``bad'', ``surprising'' and ``unsurprising'', or ``masculine'' and ``feminine''.
@@
 The U.S. airline itinerary dataset can be found at \url{https://www.transtats.bts.gov/DataIndex.asp}. 
-In case of the South Korean accommodation reservation dataset, due to the nature of the dataset, participants of this study did not agree for their data to be shared publicly.
+The raw South Korean accommodation reservation dataset, due to privacy concerns, cannot be shared publicly. 
 Due to its proprietary nature, the global scientific mobility dataset, sourced from the Web of Science, cannot be provided;

### 2020-10-25 paper/current/main.tex
add Rodgido's affiliation and ack.

@@
 \author[1]{Sadamori Kojaku}
-\author[3]{Rodrigo Costas}
-\author[2,4]{Woo-Sung Jung}
+\author[3,4]{Rodrigo Costas}
+\author[2,5,6]{Woo-Sung Jung}
 \author[1]{Staša Milojević \thanks{smilojev@indiana.edu}}
-\author[1,6,7]{Yong-Yeol Ahn \thanks{yyahn@iu.edu}}
+\author[1,7,8]{Yong-Yeol Ahn \thanks{yyahn@iu.edu}}
 
@@
 2300 AX Leiden, The Netherlands}
-\affil[4]{Department of Physics, Pohang University of Science and Technology,
+\affil{DST-NRF Centre of Excellence in Scientometrics and Science, Technology and Innovation Policy, Stellenbosch University, Stellenbosch, South Africa}
+\affil[5]{Department of Physics, Pohang University of Science and Technology,
 Pohang 37673, Republic of Korea.}
-\affil[5]{Asia Pacific Center for Theoretical Physics, Pohang 37673, Republic of Korea.}
+\affil[6]{Asia Pacific Center for Theoretical Physics, Pohang 37673, Republic of Korea.}
 
-\affil[6]{Network Science Institute, Indiana University, Bloomington (IUNI), IN 47408, USA}
-\affil[7]{Connection Science, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
+\affil[7]{Network Science Institute, Indiana University, Bloomington (IUNI), IN 47408, USA}
+\affil[8]{Connection Science, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
 
@@
 This material is based upon work supported by the Air Force Office of Scientific Research under award number FA9550-19-1-0391.
+Rodrigo Costas is partially funded by the South African DST-NRF Centre of Excellence in Scientometrics and Science, Technology and Innovation Policy (SciSTIP)
 

### 2020-10-26 paper/current/main.tex
add population info on page 1

@@
 where $m_{i}$ is the population of locations $i$,  $f(r_{ij})$ is a decay function with respect to distance between locations, and $C$ is a constant estimated from data (see Methods). 
-For the flight itinerary data, we use population $m_{i}$ as the total number of unique passengers on each airport, and for scientific mobility, we use the mean annual number of unique mobile and non-mobile authors who were affiliated with each organization.
+For the flight itinerary data, we use population $m_{i}$ as the total number of unique passengers on each airport, for the South Korean accommodation reservation data, we use population $m_{i}$ as the total number of unique customers on each accommodation, and for scientific mobility, we use the mean annual number of unique mobile and non-mobile authors who were affiliated with each organization.
 $\hat{T}_{ij}$, which is often referred to as ``expected flux''~\autocite{simini2012universal}, is the expected frequency of the co-occurrence of location $i$ and $j$ in the trajectory in the gravity model.

### 2020-10-26 paper/current/main.tex
fix affilation error

@@
 2300 AX Leiden, The Netherlands}
-\affil{DST-NRF Centre of Excellence in Scientometrics and Science, Technology and Innovation Policy, Stellenbosch University, Stellenbosch, South Africa}
+\affil[4]{DST-NRF Centre of Excellence in Scientometrics and Science, Technology and Innovation Policy, Stellenbosch University, Stellenbosch, South Africa}
 \affil[5]{Department of Physics, Pohang University of Science and Technology,

### 2020-10-26 paper/current/main.tex
add number of unique locations after trainig
change southkorean to korean:

@@
 We embed trajectories from three massive datasets: U.S.
-passenger flight itinerary records, South Korean accommodation reservations, and a dataset of scientists' career mobility between organizations captured in bibliometric records.
+passenger flight itinerary records,  Korean accommodation reservations, and a dataset of scientists' career mobility between organizations captured in bibliometric records.
 
@@
 A trajectory is constructed for each passenger flight itinerary, forming an ordered sequence of unique identifiers of the origin and destination airports. 
-The South Korean accommodation reservations consist of customer reservation histories across 2018 and 2020 for 1,038 unique accommodation locations in Seoul, South Korea.
+The Korean accommodation reservations consist of customer reservation histories across 2018 and 2020 for 1,038 unique accommodation locations in Seoul, South Korea.
 A trajectory is constructed for each customer, containing the ordered sequences of accommodations they reserved over time.
@@
 where $m_{i}$ is the population of locations $i$,  $f(r_{ij})$ is a decay function with respect to distance between locations, and $C$ is a constant estimated from data (see Methods). 
-For the flight itinerary data, we use population $m_{i}$ as the total number of unique passengers on each airport, for the South Korean accommodation reservation data, we use population $m_{i}$ as the total number of unique customers on each accommodation, and for scientific mobility, we use the mean annual number of unique mobile and non-mobile authors who were affiliated with each organization.
+For the flight itinerary data, we use population $m_{i}$ as the total number of unique passengers on each airport, for the Korean accommodation reservation data, we use population $m_{i}$ as the total number of unique customers on each accommodation, and for scientific mobility, we use the mean annual number of unique mobile and non-mobile authors who were affiliated with each organization.
 $\hat{T}_{ij}$, which is often referred to as ``expected flux''~\autocite{simini2012universal}, is the expected frequency of the co-occurrence of location $i$ and $j$ in the trajectory in the gravity model.
@@
 Also, the embedding distance produces better predictions of actual flux between airports than does the geographic distance (Fig.~\ref{fig:gravity_performance}b).
-In the case of South Korean accommodation reservations, embedding distance better explains the expected flux ($R^{2} = 0.57$, Fig.~\ref{fig:gravity_performance}c) than does geographic distance ($R^{2} = 0.25$), and predictions made using the embedding distance outperform those made with geographic distance (Fig.~\ref{fig:gravity_performance}d).
+In the case of Korean accommodation reservations, embedding distance better explains the expected flux ($R^{2} = 0.57$, Fig.~\ref{fig:gravity_performance}c) than does geographic distance ($R^{2} = 0.25$), and predictions made using the embedding distance outperform those made with geographic distance (Fig.~\ref{fig:gravity_performance}d).
 This performance is consistent in the case of scientific mobility:
@@
 		Results are consistent in the case of scientific mobility. 
-		For South Korean accommodation reservations, embedding distance better explains the expected flux than does geographic distance (\textbf{c}), and produces better predictions (\textbf{d}).
+		For Korean accommodation reservations, embedding distance better explains the expected flux than does geographic distance (\textbf{c}), and produces better predictions (\textbf{d}).
 		Similarly, in the case of global scientific mobility, embedding distance explains the expected flux between organizations (\textbf{e)} and allows for better predictions (\textbf{f}) than geographic distance.
@@
 We demonstrated that a functional distance derived from the embedding can be used with the gravity model of mobility to better predict real-world mobility than does geographic distance.
-Embedding distance outperformed geographic distance across distinct and disparate domains, including U.S.
-flight itineraries, South Korean hotel accommodation reservations, and global scientific mobility.
+Embedding distance outperformed geographic distance across distinct and disparate domains, including U.S. flight itineraries, Korean hotel accommodation reservations, and global scientific mobility.
 Focusing on scientific mobility, we find that neural embedding's performance is driven by its ability to encode many aspects of scientific mobility into a single representation, including global and regional geography, shared languages, and prestige hierarchies, even without explicit information on these factors.
@@
 For U.S. airport itinerary, trajectories are formed from the flight itineraries of individual passenger, in which airports correspond to unique identifiers. 
-In the case of South Korean accommodation reservations, trajectories comprise a sequence of accommodations reserved over a customer's history.
+In the case of Korean accommodation reservations, trajectories comprise a sequence of accommodations reserved over a customer's history.
 For scientific mobility, an``affiliation trajectories'' is constructed for each mobile author, which is built by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:methods:mobility_sentence}a.
@@
 To mitigate the effect of less common locations, we set $f_{\min} = 50$, limiting to locations appearing at least 50 times across the training trajectories;
-744 unique airport for U.S. airport itinerary  and 6,580 unique organizations for scientific mobility appear in the resulting embedding.
+744 unique airport for U.S.
+airport itinerary , 1004 unique accommodations for korean accomdation reservationd data and 6,580 unique organizations for scientific mobility appear in the resulting embedding.
 We set $\alpha$ to its default value of 0.025 and iterate five times over all training trajectories.
@@
 In the case of U.S. flight itinerary and scientific mobility, we impute distance to 1 km when their distance is less than one kilometer. 
-In the case of South Korean accommodation reservation data, because this data is intra-city mobility trajectory, we impute distance to 0.01 km when their distance is less than 0.01 km. 
+In the case of Korean accommodation reservation data, because this data is intra-city mobility trajectory, we impute distance to 0.01 km when their distance is less than 0.01 km. 
 The embedding distance with the cosine distance, $d_{ij}$, is calculated as $d_{ij} = 1 - \frac{\bm{v}_{i} \cdot \bm{v}_{j}}{\lVert \bm{v}_{i} \rVert \lVert \bm{v}_{j} \rVert}$,
@@
 	\label{eq:linear_flux_geo}
-	\ln\frac{T_{ij}}{m_im_j} = \ln C  - \alpha \ln g_{ij},
+	\ln\frac{T_{ij}}{m_im_j} = \ln C  - \alpha \ln g_{ij},S
 \end{equation}
@@
 In our dataset, non-zero flows account for only 4.2 \% of all possible pairs of the 6,580 organizations for scientific mobility, while 76.4\% of all possible pairs of the 744 airports for U.S.
-airport Itinerary.
+airport Itinerary and 62.5 \% of all possible pairs of the 1,004 accommodations for Korean accommodation reservation data.
 This value is comparable to other common applications of the gravity law, such as to phone calls, commuting, and migration \autocite{simini2012universal}.
@@
 The U.S. airline itinerary dataset can be found at \url{https://www.transtats.bts.gov/DataIndex.asp}. 
-The raw South Korean accommodation reservation dataset, due to privacy concerns, cannot be shared publicly. 
+The raw Korean accommodation reservation dataset, due to privacy concerns, cannot be shared publicly. 
 Due to its proprietary nature, the global scientific mobility dataset, sourced from the Web of Science, cannot be provided;

### 2020-10-26 paper/current/main.tex
add info on korean data

@@
 where $m_{i}$ and $m_{j}$ are the population of locations (\eg the total number of passenger on each airport for U.S.
-airport itinerary and the yearly-average count of unique authors, both mobile and non-mobile, affiliated with each organization for scientific mobility).
+airport itinerary  the total number of customer on each accommodation for Korean accommodation reservation, and the yearly-average count of unique authors, both mobile and non-mobile, affiliated with each organization for scientific mobility).
 $f(r_{ij})$ is a decay function of distance $r_{ij}$ between locations $i$ and $j$. 

### 2020-10-26 paper/current/main.tex
add comma

--- 2020-10-26 paper/current/main.tex
@@
 where $m_{i}$ and $m_{j}$ are the population of locations (\eg the total number of passenger on each airport for U.S.
-airport itinerary and the yearly-average count of unique authors, both mobile and non-mobile, affiliated with each organization for scientific mobility).
+airport itinerary,  the total number of customer on each accommodation for Korean accommodation reservation, and the yearly-average count of unique authors, both mobile and non-mobile, affiliated with each organization for scientific mobility).
 $f(r_{ij})$ is a decay function of distance $r_{ij}$ between locations $i$ and $j$. 

### 2020-10-26 paper/current/main.tex
grammar spell check

@@
 However, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018globalisation, buchan2009globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important.
-As understanding mobility is becoming critical for contemporary society, finding frameworks that can capture this complexity are of paramount importance.
+As understanding mobility is becoming critical for contemporary society, finding frameworks that can capture this complexity is of paramount importance.
 Here, using three datasets of discrete human trajectories, we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
-Focusing on the case of scientific mobility, we show that embeddings of scientific organizations uncovers cultural and linguistic relations, and even academic prestige, at multiple levels of granularity.
-Furthermore, the embedding vectors reveal universal relationships between organizational characteristics, and their place in the global landscape of scientific mobility. 
-The ability to learn scalable, dense and meaningful representations of mobility directly from the data can open up a new avenue of studying mobility across domains.
+Focusing on the case of scientific mobility, we show that embeddings of scientific organizations uncover cultural and linguistic relations, and even academic prestige, at multiple levels of granularity.
+Furthermore, the embedding vectors reveal universal relationships between organizational characteristics and their place in the global landscape of scientific mobility. 
+The ability to learn scalable, dense, and meaningful representations of mobility directly from the data can open up a new avenue of studying mobility across domains.
 
@@
 
-Here, we apply a neural embedding framework to real-world mobility trajectories and demonstrate that it can encode the complex landscape of human mobility into a dense and continuous vector-space representation, from which we can not only derive a meaningful functional distance between locations but also probe relationships based on culture, language, and even prestige along with geographic relationship.
+Here, we apply a neural embedding framework to real-world mobility trajectories and demonstrate that it can encode the complex landscape of human mobility into a dense and continuous vector-space representation, from which we can not only derive a meaningful functional distance between locations but also probe relationships based on culture, language, and even prestige along with the geographic relationship.
 We embed trajectories from three massive datasets: U.S.
@@
 		Black dots are mean flux across binned distances.
-		99\% confidence intervals are plotted, but are too small to be visible.
+		99\% confidence intervals are plotted but are too small to be visible.
 		Correlation is calculated on the data in the log-log scale. 
@@
 		\textbf{b} Predictions of flux between airport pairs made using embedding distance (top) outperform those made using geographic distance (bottom). 
-		Boxplots show distribution of actual flux for binned values of predicted flux.
+		Boxplots show the distribution of actual flux for binned values of predicted flux.
 		Box color corresponds to the degree to which the distribution overlaps with $y = x$;
@@
 Worcester), organization type (e.g., hospitals vs.
-universities), and university systems (Univeristy of  Massachusetts system vs.
+universities), and university systems (University of  Massachusetts system vs.
 Harvard \& MIT).
@@
 For instance, China's curve closely mirrors that of the United States (Fig.~\ref{fig:length}b).
-Smaller but scientifically advanced countries such as Australia, and other populous countries such as Brazil also exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset).
-Other nations exhibit different curves which lacks the portions with decreasing norm, probably indicating the lack of internationally-prestigious institutions.
+Smaller but scientifically advanced countries such as Australia and other populous countries such as Brazil also exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset).
+Other nations exhibit different curves which lack the portions with decreasing norm, probably indicating the lack of internationally-prestigious institutions.
 Similar patterns can be found across many of the 30 countries with the most total researchers (Fig.~\ref{fig:concave30}; see \SI{} for more discussion).
@@
 DB1B is a sample of 10 percent of domestic airline tickets between 1993 and 2020, comprising 307,760,841 passenger itineraries between 828 U.S. airports. 
-Each itinerary is associated with a a trajectory of airports including the origin, destination, and intermediary stops.
+Each itinerary is associated with a trajectory of airports including the origin, destination, and intermediary stops.
 
@@
 We source South Korean accommodation reservation data from collaboration with Goodchoice Company LTD. 
-The data contains customer-level reservation trajectories spanning the time period of August 2018 through July 2020, and comprising 1,038 unique accommodation locations in Seoul, South Korea.
+The data contains customer-level reservation trajectories spanning the period of August 2018 through July 2020 and comprising 1,038 unique accommodation locations in Seoul, South Korea.
 
@@
 \subsection*{Embedding}
+
 %% Mobility sentences
@@
 Then, the model learns probability $p(a_{t + \tau} \vert a_{t})$, where $-w\leq \tau\leq w$ and $\tau \neq 0$,  by maximizing its log likelihood given by
-
 %
@@
 744 unique airport for U.S.
-airport itinerary , 1004 unique accommodations for korean accomdation reservationd data and 6,580 unique organizations for scientific mobility appear in the resulting embedding.
+airport itinerary, 1004 unique accommodations for Korean accommodation reservation data, and 6,580 unique organizations for scientific mobility appear in the resulting embedding.
 We set $\alpha$ to its default value of 0.025 and iterate five times over all training trajectories.
@@
 In scientific mobility, $T_{ij} = 10$ indicates that the number of co-occurrence between both organization $i$ and $j$ between 2008 and 2019 is 10, as evidenced from their publications.
-Here, we treat $T_{ij} = T_{ji}$ for the sake of simplicity and, in the case of scientific mobility, because  directionalality cannot easily be derived from bibliometric records, or may not be particularly informative (see \SI).
+Here, we treat $T_{ij} = T_{ji}$ for the sake of simplicity and, in the case of scientific mobility, because directionality cannot easily be derived from bibliometric records, or may not be particularly informative (see \SI).
 
-We calculate two forms of the distance between locations.
+We calculate two forms of distance between locations.
 The geographic distance, $g_{ij}$, is the pairwise geographic distance between locations.
@@
 airport Itinerary and 62.5 \% of all possible pairs of the 1,004 accommodations for Korean accommodation reservation data.
-This value is comparable to other common applications of the gravity law, such as to phone calls, commuting, and migration \autocite{simini2012universal}.
+This value is comparable to other common applications of the gravity law, such as phone calls, commuting, and migration \autocite{simini2012universal}.
 We follow standard practice and exclude zero flows from our analysis.
@@
 \subsection*{SemAxis}
-SemAxis and similar studies~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} demonstrated that ``semantic axes'' can be found from an embedding space by defining the ``poles'' and the latent semantic relationship along semantic axis can be extracted with the simple arithmetic.
+SemAxis and similar studies~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} demonstrated that ``semantic axes'' can be found SemAxis and similar studies~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} demonstrated that ``semantic axes'' can be found from an embedding space by defining the ``poles'' and the latent semantic relationship along the semantic axis can be extracted with simple arithmetic.
 In the case of natural language, the poles of the axis could be ``good'' and ``bad'', ``surprising'' and ``unsurprising'', or ``masculine'' and ``feminine''.
@@
 %
-\subsection*{Acknowledgements}
+\subsection*{Acknowledgments}
 We thank the Center for Science and Technology Studies at Leiden University for managing and making available the dataset of scientific mobility.
@@
 This material is based upon work supported by the Air Force Office of Scientific Research under award number FA9550-19-1-0391.
-Rodrigo Costas is partially funded by the South African DST-NRF Centre of Excellence in Scientometrics and Science, Technology and Innovation Policy (SciSTIP)
+Rodrigo Costas is partially funded by the South African DST-NRF Centre of Excellence in Scientometrics and Science, Technology and Innovation Policy (SciSTIP).
 

### 2020-10-26 paper/current/main.tex
remove space after eq

@@
 \end{equation}
-
 where $m_{i}$ is the population of locations $i$,  $f(r_{ij})$ is a decay function with respect to distance between locations, and $C$ is a constant estimated from data (see Methods). 

### 2020-10-26 paper/current/main.tex
introduction update

@@
 \affil[6]{Asia Pacific Center for Theoretical Physics, Pohang 37673, Republic of Korea.}
-
 \affil[7]{Network Science Institute, Indiana University, Bloomington (IUNI), IN 47408, USA}
@@
 As understanding mobility is becoming critical for contemporary society, finding frameworks that can capture this complexity is of paramount importance.
-Here, using three datasets of discrete human trajectories, we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
+Here, using three distinct human trajectory datasets, we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
 Focusing on the case of scientific mobility, we show that embeddings of scientific organizations uncover cultural and linguistic relations, and even academic prestige, at multiple levels of granularity.

### 2020-10-26 paper/current/main.tex
update unclear math part

@@
 \begin{equation}
-p(a_{i} \vert a_{j}) = \frac{\exp(\bm{u}_{i} \cdot \bm{v}_{a_{j}})}{\sum_{n=1}^N \exp(\bm{u}_{n} \cdot \bm{v}_{a_{j}})},
+p(a_{i} \vert a_{j}) = \frac{\exp(\bm{u}_{a_i} \cdot \bm{v}_{a_{j}})}{\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{a_{j}})},
 \end{equation}
-where $a_{t+\tau} = j \vert a_{t+\tau} = i$, and $N$ is the number of unique locations represented in the data, and $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively.
+where $a_i = a_{t + \tau}$, $ a_j=a_{t}$, $\mathcal{A}$ is the entire set of unique locations represented in the data, and  $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively.
 We follow the standard practice and only use the in-vector, $v$,  which is known to be superior to the out-vector in link prediction benchmarks~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}.
@@
 For main results regarding scientific mobility, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig.~\ref{fig:supp:hyperparams}).
+We also use same setting for U.S.
+airport itinerary and Korean accommodation reservation data.
 To mitigate the effect of less common locations, we set $f_{\min} = 50$, limiting to locations appearing at least 50 times across the training trajectories;
@@
 We set $\alpha$ to its default value of 0.025 and iterate five times over all training trajectories.
-For scientific mobility, across each training iteration, the order of organizations within a single year is randomized.
+For scientific mobility, across each training iteration, the order of organizations within a single year is randomized to remove unclear sequential order..
 

### 2020-10-26 paper/current/main.tex
edit equation:
add dot on LTD

@@
 \subsection*{Korean accommodation reservation data}
-We source South Korean accommodation reservation data from collaboration with Goodchoice Company LTD. 
+We source South Korean accommodation reservation data from collaboration with Goodchoice Company LTD.. 
 The data contains customer-level reservation trajectories spanning the period of August 2018 through July 2020 and comprising 1,038 unique accommodation locations in Seoul, South Korea.
@@
 \begin{equation}
-\frac{\bm{u}_{a} \cdot \bm{V}_{\text{axis}}}{\lVert \bm{v}_{a} \rVert \lVert \bm{V}_{\text{axis}} \rVert},
+\frac{\bm{v}_{a} \cdot \bm{V}_{\text{axis}}}{\lVert \bm{v}_{a} \rVert \lVert \bm{V}_{\text{axis}} \rVert},
 \end{equation}
@@
 We thank the Center for Science and Technology Studies at Leiden University for managing and making available the dataset of scientific mobility.
-We also thank the  Goodchoice Company LTD for making available the dataset of Korean accommodation reservation data.
+We also thank the  Goodchoice Company LTD.
+for making available the dataset of Korean accommodation reservation data.
 For their comments, we thank Guillaume Cabanac, Cassidy R. Sugimoto, Vincent Lariviére, Alessandro Flammini, Filippo Menczer, Lili Miao, Xiaoran Yan, and Inho Hong. 

### 2020-10-26 paper/current/main.tex
small text tweaks

@@
 where $m_{i}$ is the population of locations $i$,  $f(r_{ij})$ is a decay function with respect to distance between locations, and $C$ is a constant estimated from data (see Methods). 
-For the flight itinerary data, we use population $m_{i}$ as the total number of unique passengers on each airport, for the Korean accommodation reservation data, we use population $m_{i}$ as the total number of unique customers on each accommodation, and for scientific mobility, we use the mean annual number of unique mobile and non-mobile authors who were affiliated with each organization.
+For the flight itinerary data, we use population $m_{i}$ as the total number of unique passengers who passed through each airport, for the Korean accommodation reservation data, we use the total number of unique customers who booked with each accommodation, and for scientific mobility, we use the mean annual number of unique mobile and non-mobile authors who were affiliated with each organization.
 $\hat{T}_{ij}$, which is often referred to as ``expected flux''~\autocite{simini2012universal}, is the expected frequency of the co-occurrence of location $i$ and $j$ in the trajectory in the gravity model.
@@
 \subsection*{Korean accommodation reservation data}
-We source South Korean accommodation reservation data from collaboration with Goodchoice Company LTD.. 
+We source Korean accommodation reservation data from collaboration with Goodchoice Company LTD.. 
 The data contains customer-level reservation trajectories spanning the period of August 2018 through July 2020 and comprising 1,038 unique accommodation locations in Seoul, South Korea.
@@
 \end{equation}
-where $m_{i}$ and $m_{j}$ are the population of locations (\eg the total number of passenger on each airport for U.S.
-airport itinerary,  the total number of customer on each accommodation for Korean accommodation reservation, and the yearly-average count of unique authors, both mobile and non-mobile, affiliated with each organization for scientific mobility).
+where $m_{i}$ and $m_{j}$ are the population of locations, defined as the total number of passenger who passed through each airport for U.S.
+airport itineraries,  the total number of customer who booked with each accommodation for Korean accommodation reservations, and the yearly-average count of unique authors, both mobile and non-mobile, affiliated with each organization for scientific mobility.
 $f(r_{ij})$ is a decay function of distance $r_{ij}$ between locations $i$ and $j$. 

### 2020-10-26 paper/current/supp.tex

@@
 ]{biblatex}
+
+% Ignore irrelevant biblatex fields
+\AtEveryBibitem{%
+ \clearfield{url}%
+  \clearfield{month}%
+ \clearfield{issn}%
+ \clearfield{doi}%%
+}
+
 \addbibresource{mobility.bib}
@@
 	\caption{
-		\textbf{For embedding distance, the exponential=decay gravity model is better.}
+		\textbf{For embedding distance, the exponential-decay gravity model is better.}
 		Flux between organization pairs predicted by the gravity model with different distance decay functions, i.e., exponential decay function (\textbf{a}) and power-law decay function (\textbf{b}) using embedding distance.

### 2020-11-01 paper/current/main.tex
update linzhou2020 in-text reference

@@
 A vector-space embedding of locations (airports, accommodations, and organizations) is learned by using trajectories as input to the standard with skip-gram negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
-This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered} and networks~\autocite{grover2016node2vec}.
+This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered} and networks~\autocite{grover2016node2vec, linzhuo2020hyperbolic}.
 The model is also computationally efficient, robust to noise, and can encode relations between entities as geometric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.

### 2020-12-03 paper/current/main.tex
implement Sada's corrections

@@
 \subsection*{Korean accommodation reservation data}
-We source Korean accommodation reservation data from collaboration with Goodchoice Company LTD.. 
+We source Korean accommodation reservation data from collaboration with Goodchoice Company LTD.
 The data contains customer-level reservation trajectories spanning the period of August 2018 through July 2020 and comprising 1,038 unique accommodation locations in Seoul, South Korea.
@@
 	\label{eq:linear_flux_geo}
-	\ln\frac{T_{ij}}{m_im_j} = \ln C  - \alpha \ln g_{ij},S
+	\ln\frac{T_{ij}}{m_im_j} = \ln C  - \alpha \ln g_{ij},
 \end{equation}
@@
 \subsection*{SemAxis}
-SemAxis and similar studies~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} demonstrated that ``semantic axes'' can be found SemAxis and similar studies~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} demonstrated that ``semantic axes'' can be found from an embedding space by defining the ``poles'' and the latent semantic relationship along the semantic axis can be extracted with simple arithmetic.
+SemAxis and similar studies~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} demonstrated that ``semantic axes'' can be found from an embedding space by defining the ``poles'' and the latent semantic relationship along the semantic axis can be extracted with simple arithmetic.
 In the case of natural language, the poles of the axis could be ``good'' and ``bad'', ``surprising'' and ``unsurprising'', or ``masculine'' and ``feminine''.

### 2021-01-05 paper/current/notes/2021-0105-word2vec-vs-gravity-model/main.tex
add note on gravity model vs word2vec

\documentclass[12pt]{article} %{{{

% Figures
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\def\figdir{figs}

% Math
\usepackage{amsmath}
\usepackage{amssymb}
\DeclareMathOperator*{\argmin}{\arg\!\min}
\DeclareMathOperator*{\argmax}{\arg\!\max}
\def\given{\mid}

% abbreviations
\def\etal{\emph{et~al}.\ }
\def\eg{e.g.,~}
\def\ie{i.e.,~}
\def\cf{cf.\ }
\def\viz{viz.\ }
\def\vs{vs.\ }

% Refs
\usepackage{biblatex}
\addbibresource{main.bib}

\usepackage{url}

\newcommand{\secref}[1]{Section~\ref{sec:#1}}
\newcommand{\figref}[1]{Fig.~\ref{fig:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
%\newcommand{\eqnref}[1]{\eqref{eq:#1}}
%\newcommand{\thmref}[1]{Theorem~\ref{#1}}
%\newcommand{\prgref}[1]{Program~\ref{#1}}
%\newcommand{\algref}[1]{Algorithm~\ref{#1}}
%\newcommand{\clmref}[1]{Claim~\ref{#1}}
%\newcommand{\lemref}[1]{Lemma~\ref{#1}}
%\newcommand{\ptyref}[1]{Property~\ref{#1}}

% for quick author comments 
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\definecolor{light-gray}{gray}{0.8}
\def\del#1{ {\color{light-gray}{#1}} }
\def\yy#1{ {\color{red}\textbf{yy: #1}} }

%}}}

\begin{document} %{{{

\title{Gravity model and word2vec} %{{{
\date{\today}
\maketitle %}}}

\section{Introduction}\label{sec:introduction}

The word2vec fits well to a wide range of mobilities, which prompts us to ask: why does the word2vec fit well to the mobility data?
It turns out that the word2vec is tied to a gravity model, a widespread and long-standing model that well explains human mobility.
While the gravity model predicts a flow from given locations and populations, the word2vec is a reverse engineering model that estimates the location and population from flows.

Let us approach the connection by initially focusing on the gravity model.
Suppose that flow of people between $N$ locations. The gravity model models the flow by
\begin{align}
    T_{ij} = G M_i M_j f(d_{ij}), \label{eq:gravity_model}
\end{align}
where $T_{ij}$ is the flow from location $i$ to $j$, $M_i$ is a mass term corresponding to population of $i$, $d_{ij}$ is a distance between locations $i$ and $j$,
$f$ is a decreasing function with respect to $d_{ij}$, and $G$ is a constant.
Note that the gravity model implicitly assumes that the flow is symmetric, \ie $T_{ij}=T_{ji}$, which eads to a stationality in population $M_{i}$.

Now, let us move our focus to the word2vec.
The word2vec takes a sequence of locations (\ie trajectory) and models the co-occurrence of center word $i$ and context word $j$ by
\begin{align}
    P(j\given i) = \frac{\exp(u_i ^\top v_j)}{Z_i},
\end{align}
where $u_i$ and $v_{j}$ are embedding vectors for node $i$, which are referred to as in-vecvtor and out-vector, respectivey, and $Z_i$ is a normalization constant.
The co-occurrence \emph{frequency} of center and context word is given by
\begin{align}
    \pi_i P(j\given i) = \frac{\pi_i\exp(u_i ^\top v_j)}{Z_i},
\end{align}
where $\pi_i$ is the frequency of word $i$ in the sentence. When restricting window size to be one, the co-occurence frequency corresponds to the flow, \ie
\begin{align}
    T_{ij} = \frac{\pi_i\exp(u_i ^\top v_j)}{Z_i}. \label{eq:flow_w2v}
\end{align}
Additionally, because the window covers the preceding and succeeding words from a center word, the co-occurence is symmetric, $T_{ij} = T_{ji}$, which echoes the gravity model.
Exploiting the symmetry in flows (\ie $T_{ij} = T_{ji}$), we have
\begin{align}
    \frac{\pi_i}{Z_i}  = \frac{\pi_j}{Z_j}
    \Rightarrow Z_i   = \pi_i / c \label{eq:Z}
\end{align}
where $c$ is a positive constant. Substituting \eqref{eq:Z} into \eqref{eq:flow_w2v}, we have
\begin{align}
    T_{ij} = c \exp(u_i ^\top v_j). \label{eq:flow_w2v2}
\end{align}
Both word2vec and the gravity model assume that the flow is determined by the locations.
Yet, they have some notable differences.
For example, the gravity model measures the distance by the euclidean distance while the word2vec measures by a dot similarity.
Additionally, the word2vec does not have a mass term for locations.

%The word2vecs flow between locations based on a dot similarity while the gravity model does baesd on eucliden distance.
%Although the two models differ in many respects, 
The gap between two models can be filled by using euclidean distance for the word2vec, \ie
\begin{align}
    P(j\given i) = \frac{\exp(-||u_i - u_j||^2)}{Z_i}.
\end{align}
The flow is then given by
\begin{align}
    T_{ij} = c \exp(-||u_i - u_j||^2).
\end{align}
Now, this modified word2vec has a functional form similar to the gravity model, \ie the flow is decreasing with respective to the euclidean distance.

Although the mass terms are still missing in the modified wod2vec, they come into the model when using a commonly-used optimization algorithm---\emph{the negative sampling}.
The negative sampling is an optimization method widely used for training the word2vec.
An overlooked fact is that the negative sampling is a biased estimator that optimizes a slightly different objective function~\cite{Gutmann2010}.

The negative sampling finds the embedding vectors as follows.
For each center--context word pair $(i,j)$, one generates $k$ noise center--context word pairs, denoted by $(i, \ell)$, where context word $\ell$ for the noise pair is sampled from a noise distribution, denoted by $p_{0}(\ell)$.
Given a center-context word pair, $(i,j)$, as an input, one predicts whether it comes from the original data or noise distribution based on
a similarity between two words, \eg dot similarity in case of the word2vec.

Note that the negative sampling does not directly fit the word2vec to the given data but with the synthetic classification task.
As a consequence, it does not fit the original model but a different model given by \cite{Gutmann2010}
\begin{align}
    P\left(j \given i \right):= \frac{p_0(j)\exp(u^\top _i v_j)}{Z_i}.
\end{align}
Although the negative sampling optimizes a different model, it has computational advantages and works well in practice.

Let us return to the modified word2vec and optimize it using the negative sampling.
The flow between $i$ and $j$ is given by
\begin{align}
    T_{ij}=\pi_i\frac{p_0(j)\exp(-||u_i - u_j||^2)}{Z_i}.
\end{align}
The original word2vec uses a noise distribution given by $p_{0}(\ell) = \pi^{\gamma} _\ell / \sum_{\ell'} \pi^{\gamma}_{\ell'}$, where $\gamma$ is a free parameter typicall set to $3/4$ or $1$.
%We set $\gamma = 1$.
Setting $\gamma=1$, we have
\begin{align}
    T_{ij}=c\pi_i \pi_j\exp(-||u_i - u_j||^2).
\end{align}
which reveals the mass $M_i$ for the modified word2vec model.
In fact, the mass term $M_i$ for location $i$ corresponds to its frequency in the trajetory in the modified word2vec model.

\printbibliography{}

\end{document} %}}}

### 2021-01-06 notebooks/20210105_euclidean_word2vec/utils.py
add notebook to demonstrate the euclidean word2vec

@@ -1,0 +1,675 @@
+import networkx as nx
+import numba
+import numpy as np
+from numba import prange
+from scipy import sparse
+
+
+#
+# Random walks
+#
+def calc_cum_trans_prob(A):
+    P = A.copy()
+    P.data = _calc_cum_trans_prob(A.indptr, A.indices, A.data.astype(float), A.shape[0])
+    return P
+
+
+@numba.jit(nopython=True, parallel=True)
+def _calc_cum_trans_prob(
+    A_indptr,
+    A_indices,
+    A_data_,
+    num_nodes,  # should be cumulative
+):
+    A_data = A_data_.copy()
+    for i in prange(num_nodes):
+        # Compute the out-deg
+        outdeg = np.sum(A_data[A_indptr[i] : A_indptr[i + 1]])
+        A_data[A_indptr[i] : A_indptr[i + 1]] = np.cumsum(
+            A_data[A_indptr[i] : A_indptr[i + 1]]
+        ) / np.maximum(outdeg, 1e-8)
+    return A_data
+
+
+def simulate_simple_walk(
+    A,
+    num_walk,
+    walk_length,
+    restart_prob,
+    start_node_ids=None,
+    restart_at_dangling=False,
+):
+    """Wrapper for."""
+
+    if A.getformat() != "csr":
+        raise TypeError("A should be in the scipy.sparse.csc_matrix")
+
+    # Extract the information on the csr matrix
+    P = calc_cum_trans_prob(A)
+    if start_node_ids is None:
+        start_node_ids = np.arange(A.shape[0])
+    return _simulate_simple_walk(
+        P.indptr,
+        P.indices,
+        P.data,
+        P.shape[0],
+        restart_prob,
+        np.repeat(start_node_ids, num_walk),
+        walk_length,
+        restart_at_dangling,
+    )
+
+
+@numba.jit(nopython=True, cache=True, parallel=True)
+def _simulate_simple_walk(
+    A_indptr,
+    A_indices,
+    A_data,  # should be cumulative
+    num_nodes,
+    restart_prob,
+    start_node_ids,
+    walk_length,
+    restart_at_dangling,
+):
+    """Sampler based on a simple walk. A random walker chooses a neighbor with
+    proportional to edge weights. For a fast simulation of random walks, we
+    exploit scipy.sparse.csr_matrix data structure. In scipy.sparse.csr_matrix
+    A, there are 3 attributes:
+
+    - A.indices : column ID
[…]

### 2021-01-06 paper/current/notes/2021-0105-word2vec-vs-gravity-model/main.tex
add optimization algorithm

@@
 $f$ is a decreasing function with respect to $d_{ij}$, and $G$ is a constant.
-Note that the gravity model implicitly assumes that the flow is symmetric, \ie $T_{ij}=T_{ji}$, which eads to a stationality in population $M_{i}$.
+Note that the gravity model implicitly assumes that the flow is symmetric, \ie $T_{ij}=T_{ji}$, which ensures the stationarity in population $M_{i}$.
 
@@
 \end{align}
-where $u_i$ and $v_{j}$ are embedding vectors for node $i$, which are referred to as in-vecvtor and out-vector, respectivey, and $Z_i$ is a normalization constant.
+where $u_i$ and $v_{j}$ are embedding vectors for node $i$, which are referred to as in-vector and out-vector, respectively, and $Z_i$ is a normalization constant.
 The co-occurrence \emph{frequency} of center and context word is given by
@@
 \end{align}
-where $\pi_i$ is the frequency of word $i$ in the sentence. When restricting window size to be one, the co-occurence frequency corresponds to the flow, \ie
+where $\pi_i$ is the frequency of word $i$ in the sentence. When restricting window size to be one, the co-occurrence frequency corresponds to the flow, \ie
 \begin{align}
@@
 \end{align}
-Additionally, because the window covers the preceding and succeeding words from a center word, the co-occurence is symmetric, $T_{ij} = T_{ji}$, which echoes the gravity model.
+Additionally, because the window covers the preceding and succeeding words from a center word, the co-occurrence is symmetric, $T_{ij} = T_{ji}$, which echoes the gravity model.
 Exploiting the symmetry in flows (\ie $T_{ij} = T_{ji}$), we have
@@
 \begin{align}
-    P(j\given i) = \frac{\exp(-||u_i - u_j||^2)}{Z_i}.
+    P(j\given i) = \frac{\exp(-||u_i - u_j||)}{Z_i}.
 \end{align}
@@
 \begin{align}
-    T_{ij} = c \exp(-||u_i - u_j||^2).
+    T_{ij} = c \exp(-||u_i - u_j||).
 \end{align}
-Now, this modified word2vec has a functional form similar to the gravity model, \ie the flow is decreasing with respective to the euclidean distance.
+Now, this Euclidean word2vec has a functional form similar to the gravity model, \ie the flow is decreasing with respective to the euclidean distance.
 
-Although the mass terms are still missing in the modified wod2vec, they come into the model when using a commonly-used optimization algorithm---\emph{the negative sampling}.
+Although the mass terms are still missing in the modified word2vec, they come into the model when using a commonly-used optimization algorithm---\emph{the negative sampling}.
 The negative sampling is an optimization method widely used for training the word2vec.
@@
 
-Let us return to the modified word2vec and optimize it using the negative sampling.
+Let us return to the Euclidean word2vec and optimize it using the negative sampling.
 The flow between $i$ and $j$ is given by
 \begin{align}
-    T_{ij}=\pi_i\frac{p_0(j)\exp(-||u_i - u_j||^2)}{Z_i}.
+    T_{ij}=\pi_i\frac{p_0(j)\exp(-||u_i - u_j||)}{Z_i}.
 \end{align}
-The original word2vec uses a noise distribution given by $p_{0}(\ell) = \pi^{\gamma} _\ell / \sum_{\ell'} \pi^{\gamma}_{\ell'}$, where $\gamma$ is a free parameter typicall set to $3/4$ or $1$.
+The original word2vec uses a noise distribution given by $p_{0}(\ell) = \pi^{\gamma} _\ell / \sum_{\ell'} \pi^{\gamma}_{\ell'}$, where $\gamma$ is a free parameter typically set to $3/4$ or $1$.
 %We set $\gamma = 1$.
@@
 \begin{align}
-    T_{ij}=c\pi_i \pi_j\exp(-||u_i - u_j||^2).
+    T_{ij}=c\pi_i \pi_j\exp(-||u_i - u_j||). \label{eq:flow_w2v_ng}
 \end{align}
-which reveals the mass $M_i$ for the modified word2vec model.
-In fact, the mass term $M_i$ for location $i$ corresponds to its frequency in the trajetory in the modified word2vec model.
+which reveals the mass $M_i$ for the Euclidean word2vec model.
+In fact, the mass term $M_i$ for location $i$ corresponds to its frequency in the trajectory in the Euclidean word2vec model.
+
+\section{Optimization based on the multidimensional scaling}
+
+The euclidean word2vec takes flow as input and outputs the location and population at each location.
+This algorithm is reminiscent of the multidimensional scaling (MDS), which maps entities onto a Euclidean space by preserving their dissimilarity as distance as much as possible.
+Specifically, given a dissimilarity matrix $D=(D_{ij})$, MDS aims to map entities such that $D_{ij} \approx ||u_i - u_j||$ for all $i$ and $j$.
+This connection allows us to optimize the euclidean word2vec using the MDS algorithm, as we will see in the following.
+
+For a moment, let us consider an ideal situation in which the given data is generated from Eq~\eqref{eq:flow_w2v_ng} and how we can fit the model.
+Denoted by $T_{ij} ^\text{data}$ as the actual flow, and $T^{\text{model}}_ij$ by the flow modeled by the word2vec.
+When embedding dimension $K$ is small, the word2vec has a limited expression power and thus the modeled flow can be considerably different to the actual flow.
+As we increase $K$, however, the model gains more expression power and eventually achieves an exact fit, $T_{ij} ^\text{data} = T_{ij} ^\text{model}$, just like fitting a high-order polynomial function (\eg quadratic function) to two data points.
+In this case, the distance is given by solving Eq.~\eqref{eq:flow_w2v_ng}, or
+\begin{align}
+    ||u_i - u_j|| = - \log \frac{T^\text{data}_{ij}}{\pi_i \pi_j} + \log c.
+\end{align}
+This problem is equivalent to the MDS problem, taking $R=(R_ij)$ with entries $R_{ij}= - \log \frac{T_{ij}}{\pi_i \pi_j} + \log c$ as the dissimilarity matrix.
+It should be noted that MDS problem does not have a unique solution.
+
+In practice, we may want a compact embedding space, $K\ll N$.
+Furthermore, given data may not be generated from the same model.
+Yet, solving the MDS problem would provide a good approximate for embedding.
+
+An implementation issue is that the dissimilarity $R_{ij}$ can be infinity because flow $T_{ij}$ can be zero, making the MDS problem invalid.
+To circumvent this problem, we add a small synthetic flow $\tilde \epsilon_{ij}$ to the actual flow given by $\epsilon_{ij} = \alpha \pi_i \pi_j$, where $\alpha = 1e-3$.
 

### 2021-01-07 paper/current/notes/2021-0105-word2vec-vs-gravity-model/main.tex
make assumption explicit and use the cosine

--- 2021-01-05 paper/current/notes/2021-0105-word2vec-vs-gravity-model/main.tex
@@
 $f$ is a decreasing function with respect to $d_{ij}$, and $G$ is a constant.
-Note that the gravity model implicitly assumes that the flow is symmetric, \ie $T_{ij}=T_{ji}$, which eads to a stationality in population $M_{i}$.
+That the gravity model implicitly assumes that the flow is symmetric, \ie $T_{ij}=T_{ji}$, which ensures the stationarity in population $M_{i}$.
+The choice of distance measure $d_{ij}$ is entirely unconstrained; it can be the euclidean distance, or even pseudo distance measure that does not satisfy the axioms for metric space.
+In the following, we refer to a measure of dissimilarity as distance.
 
@@
 \end{align}
-where $\pi_i$ is the frequency of word $i$ in the sentence. When restricting window size to be one, the co-occurence frequency corresponds to the flow, \ie
+where $\pi_i$ is the frequency of word $i$ in the sentence.
+When restricting window size to be one, the co-occurrence frequency corresponds to the flow, \ie
 \begin{align}
@@
 \end{align}
-Additionally, because the window covers the preceding and succeeding words from a center word, the co-occurence is symmetric, $T_{ij} = T_{ji}$, which echoes the gravity model.
-Exploiting the symmetry in flows (\ie $T_{ij} = T_{ji}$), we have
-\begin{align}
-    \frac{\pi_i}{Z_i}  = \frac{\pi_j}{Z_j}
-    \Rightarrow Z_i   = \pi_i / c \label{eq:Z}
-\end{align}
-where $c$ is a positive constant. Substituting \eqref{eq:Z} into \eqref{eq:flow_w2v}, we have
-\begin{align}
-    T_{ij} = c \exp(u_i ^\top v_j). \label{eq:flow_w2v2}
-\end{align}
-Both word2vec and the gravity model assume that the flow is determined by the locations.
-Yet, they have some notable differences.
-For example, the gravity model measures the distance by the euclidean distance while the word2vec measures by a dot similarity.
-Additionally, the word2vec does not have a mass term for locations.
+The co-occurrence frequency has a similar functional form with the gravity model, \ie $d_{ij} = -u_i ^\top v_j$ and $f(x) = \exp(-x)$.
+Yet, they have some apparent differences.
+For example, the word2vec does not have a mass term $M_i$.
+In addition, the dot similarity $u_i ^\top v_j$ can be asymmetric, \ie $u_i ^\top v_j \neq u_j ^\top v_i$.
+In practice, however, this gap is filled due to the effect of optimization algorithm---\emph{the negative sampling}.
 
-%The word2vecs flow between locations based on a dot similarity while the gravity model does baesd on eucliden distance.
-%Although the two models differ in many respects, 
-The gap between two models can be filled by using euclidean distance for the word2vec, \ie
-\begin{align}
-    P(j\given i) = \frac{\exp(-||u_i - u_j||^2)}{Z_i}.
-\end{align}
-The flow is then given by
-\begin{align}
-    T_{ij} = c \exp(-||u_i - u_j||^2).
-\end{align}
-Now, this modified word2vec has a functional form similar to the gravity model, \ie the flow is decreasing with respective to the euclidean distance.
-
-Although the mass terms are still missing in the modified wod2vec, they come into the model when using a commonly-used optimization algorithm---\emph{the negative sampling}.
-The negative sampling is an optimization method widely used for training the word2vec.
-An overlooked fact is that the negative sampling is a biased estimator that optimizes a slightly different objective function~\cite{Gutmann2010}.
-
-The negative sampling finds the embedding vectors as follows.
+The negative sampling is an optimization method widely used for training the word2vec, which operates as follows.
 For each center--context word pair $(i,j)$, one generates $k$ noise center--context word pairs, denoted by $(i, \ell)$, where context word $\ell$ for the noise pair is sampled from a noise distribution, denoted by $p_{0}(\ell)$.
@@
 
-Note that the negative sampling does not directly fit the word2vec to the given data but with the synthetic classification task.
+An overlooked fact is that the negative sampling is a biased estimator that optimizes a slightly different objective function~\cite{Gutmann2010}.
+The negative sampling does not directly fit the word2vec to the given data but with the synthetic classification task.
 As a consequence, it does not fit the original model but a different model given by \cite{Gutmann2010}
@@
 \end{align}
-Although the negative sampling optimizes a different model, it has computational advantages and works well in practice.
+By taking into the bias, the flow between $i$ and $j$ is given by
+\begin{align}
+    T_{ij}=\pi_i\frac{p_0(j)\exp(u_i ^\top v_j)}{Z_i}. \label{eq:flow_w2v_ng0}
+\end{align}
+The word2vec uses a noise distribution given by $p_{0}(\ell) = \pi^{\gamma} _\ell / \sum_{\ell'} \pi^{\gamma}_{\ell'}$, where $\gamma$ is a free parameter typically set to $3/4$ or $1$.
+Notably, $\gamma=1$ is a special choice that ensures that the in-vector and out-vector are the same, \ie $u_i = v_i$.
+Setting $\gamma = 1$ and substituting $p_0 (\ell) = \pi_\ell$ into Eq~\eqref{eq:flow_w2v_ng0} yields
+\begin{align}
+    T_{ij}=c\pi_i \pi_j\exp(u_i ^\top u_j). \label{eq:flow_w2v_ng}
+\end{align}
+where $c$ is a positive constant, and we have exploited $\pi_i/Z_i = c$ derived from $T_{ij} = T_{ji}$.
+Equation~\eqref{eq:flow_w2v_ng} reveals the connection between the word2vec and the gravity model.
+For example, the word2vec is a special case of the gravity model, in which the mass of location $i$ is its frequency in the trajectory data, and the distance between locations is measured by their dot similarities.
 
-Let us return to the modified word2vec and optimize it using the negative sampling.
-The flow between $i$ and $j$ is given by
-\begin{align}
-    T_{ij}=\pi_i\frac{p_0(j)\exp(-||u_i - u_j||^2)}{Z_i}.
-\end{align}
-The original word2vec uses a noise distribution given by $p_{0}(\ell) = \pi^{\gamma} _\ell / \sum_{\ell'} \pi^{\gamma}_{\ell'}$, where $\gamma$ is a free parameter typicall set to $3/4$ or $1$.
-%We set $\gamma = 1$.
-Setting $\gamma=1$, we have
-\begin{align}
-    T_{ij}=c\pi_i \pi_j\exp(-||u_i - u_j||^2).
-\end{align}
-which reveals the mass $M_i$ for the modified word2vec model.
-In fact, the mass term $M_i$ for location $i$ corresponds to its frequency in the trajetory in the modified word2vec model.
+%\section{Optimization based on the multidimensional scaling}
+%
+%The euclidean word2vec takes flow as input and outputs the location and population at each location.
+%This algorithm is reminiscent of the multidimensional scaling (MDS), which maps entities onto a Euclidean space by preserving their dissimilarity as distance as much as possible.
+%Specifically, given a dissimilarity matrix $D=(D_{ij})$, MDS aims to map entities such that $D_{ij} \approx ||u_i - u_j||$ for all $i$ and $j$.
+%This connection allows us to optimize the euclidean word2vec using the MDS algorithm, as we will see in the following.
+%
+%For a moment, let us consider an ideal situation in which the given data is generated from Eq~\eqref{eq:flow_w2v_ng} and how we can fit the model.
+%Denoted by $T_{ij} ^\text{data}$ as the actual flow, and $T^{\text{model}}_ij$ by the flow modeled by the word2vec.
+%When embedding dimension $K$ is small, the word2vec has a limited expression power and thus the modeled flow can be considerably different to the actual flow.
+%As we increase $K$, however, the model gains more expression power and eventually achieves an exact fit, $T_{ij} ^\text{data} = T_{ij} ^\text{model}$, just like fitting a high-order polynomial function (\eg quadratic function) to two data points.
+%In this case, the distance is given by solving Eq.~\eqref{eq:flow_w2v_ng}, or
+%\begin{align}
+%    ||u_i - u_j|| = - \log \frac{T^\text{data}_{ij}}{\pi_i \pi_j} + \log c.
+%\end{align}
+%This problem is equivalent to the MDS problem, taking $R=(R_ij)$ with entries $R_{ij}= - \log \frac{T_{ij}}{\pi_i \pi_j} + \log c$ as the dissimilarity matrix.
+%It should be noted that MDS problem does not have a unique solution.
+%
+%In practice, we may want a compact embedding space, $K\ll N$.
+%Furthermore, given data may not be generated from the same model.
+%Yet, solving the MDS problem would provide a good approximate for embedding.
+%
+%An implementation issue is that the dissimilarity $R_{ij}$ can be infinity because flow $T_{ij}$ can be zero, making the MDS problem invalid.
+%To circumvent this problem, we add a small synthetic flow $\tilde \epsilon_{ij}$ to the actual flow given by $\epsilon_{ij} = \alpha \pi_i \pi_j$, where $\alpha = 1e-3$.
 

### 2021-01-07 paper/current/notes/2021-0105-word2vec-vs-gravity-model/main.tex
edit the terms that we have been used in the main paper

@@
 \begin{align}
-    T_{ij} = G M_i M_j f(d_{ij}), \label{eq:gravity_model}
+    \hat{T_{ij}} = C m_i m_j f(r_{ij}), \label{eq:gravity_model}
 \end{align}
-where $T_{ij}$ is the flow from location $i$ to $j$, $M_i$ is a mass term corresponding to population of $i$, $d_{ij}$ is a distance between locations $i$ and $j$,
-$f$ is a decreasing function with respect to $d_{ij}$, and $G$ is a constant.
+where $\hat{T_{ij}}$ is the expected flow from location $i$ to $j$, $m_i$ is the population of locations of $i$, $r_{ij}$ is a distance between locations $i$ and $j$, $f$ is a decreasing function with respect to $r_{ij}$, and $C$ is a constant.
 That the gravity model implicitly assumes that the flow is symmetric, \ie $T_{ij}=T_{ji}$, which ensures the stationarity in population $M_{i}$.
-The choice of distance measure $d_{ij}$ is entirely unconstrained; it can be the euclidean distance, or even pseudo distance measure that does not satisfy the axioms for metric space.
+The choice of distance measure $d_{ij}$ is entirely unconstrained; it can be the euclidean distance, or any kind of general distance measure.
 In the following, we refer to a measure of dissimilarity as distance.

### 2021-01-08 paper/current/main.tex
edit math eq more easily in the maintext

@@
 \begin{equation}
-p(a_{i} \vert a_{j}) = \frac{\exp(\bm{u}_{a_i} \cdot \bm{v}_{a_{j}})}{\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{a_{j}})},
+p(a_{j} \vert a_{i}) = \frac{\exp(\bm{u}_{a_j} \cdot \bm{v}_{a_{i}})}{\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{a_{i}})},
 \end{equation}
-where $a_i = a_{t + \tau}$, $ a_j=a_{t}$, $\mathcal{A}$ is the entire set of unique locations represented in the data, and  $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively.
+where $a_i =a_{t} $, $ a_j=a_{t + \tau}$, $\mathcal{A}$ is the entire set of unique locations represented in the data, and  $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively.
 We follow the standard practice and only use the in-vector, $v$,  which is known to be superior to the out-vector in link prediction benchmarks~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}.

### 2021-01-11 paper/current/notes/2021-0105-word2vec-vs-gravity-model/main.tex
edit notes

@@
 \def\vs{vs.\ }
+
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{newtxmath}
+\DeclareMathAlphabet{\mathpzc}{T1}{pzc}{m}{it}
+\usepackage{bm}
+\def\tnull{{\text{null}}}
+\def\vec#1{{\bm #1}}
+\def\mat#1{\mathbf{#1}}
 
@@
 
-\title{Gravity model and word2vec} %{{{
+\title{Gravity model and \textit{\textit{word2vec}}} %{{{
 \date{\today}
@@
 
-\section{Introduction}\label{sec:introduction}
+\section{From \textit{word2vec} to gravity model}
 
-The word2vec fits well to a wide range of mobilities, which prompts us to ask: why does the word2vec fit well to the mobility data?
-It turns out that the word2vec is tied to a gravity model, a widespread and long-standing model that well explains human mobility.
-While the gravity model predicts a flow from given locations and populations, the word2vec is a reverse engineering model that estimates the location and population from flows.
+The \textit{word2vec} fits well to a wide range of mobilities, which prompts us to ask: why does the \textit{word2vec} fit well to the mobility data?
+It turns out that the \textit{word2vec} is tied to a gravity model, a widespread and long-standing model that well explains human mobility.
+While the gravity model predicts a flow from given locations and populations, the \textit{word2vec} is a reverse engineering model that estimates the location and population from flows.
 
@@
 where $\hat{T_{ij}}$ is the expected flow from location $i$ to $j$, $m_i$ is the population of locations of $i$, $r_{ij}$ is a distance between locations $i$ and $j$, $f$ is a decreasing function with respect to $r_{ij}$, and $C$ is a constant.
-That the gravity model implicitly assumes that the flow is symmetric, \ie $T_{ij}=T_{ji}$, which ensures the stationarity in population $M_{i}$.
+That the gravity model implicitly assumes that the flow is symmetric, \ie $\hat{T_{ij}}=\hat{T_{ji}}$, which ensures the stationarity in population $m_{i}$.
 The choice of distance measure $d_{ij}$ is entirely unconstrained; it can be the euclidean distance, or any kind of general distance measure.
@@
 
-Now, let us move our focus to the word2vec.
-The word2vec takes a sequence of locations (\ie trajectory) and models the co-occurrence of center word $i$ and context word $j$ by
+Now, let us move our focus to the \textit{\textit{word2vec}}.
+In out setting, the model takes a sequence of locations and models the co-occurrence of center location $i$ and context location $j$ by
+\begin{equation}
+p(j \given i) = \frac{\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
+\end{equation}
+where $\mathcal{A}$ is the entire set of unique locations represented in the data, and  $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively.
+$Z_i=\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{i})$ is a normalization constant.
+Under the stationary condition and restricting window size to be one , the expected flow between center location $a_i$ and context location $a_j$ is given by
 \begin{align}
-    P(j\given i) = \frac{\exp(u_i ^\top v_j)}{Z_i},
+	  \label{eq:flow_w2v}
+        \hat{T_{ij}}=\pi_i P(j\given i) = \frac{\pi_i\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
 \end{align}
-where $u_i$ and $v_{j}$ are embedding vectors for node $i$, which are referred to as in-vector and out-vector, respectively, and $Z_i$ is a normalization constant.
-The co-occurrence \emph{frequency} of center and context word is given by
-\begin{align}
-    \pi_i P(j\given i) = \frac{\pi_i\exp(u_i ^\top v_j)}{Z_i},
-\end{align}
-where $\pi_i$ is the frequency of word $i$ in the sentence.
-When restricting window size to be one, the co-occurrence frequency corresponds to the flow, \ie
-\begin{align}
-    T_{ij} = \frac{\pi_i\exp(u_i ^\top v_j)}{Z_i}. \label{eq:flow_w2v}
-\end{align}
-The co-occurrence frequency has a similar functional form with the gravity model, \ie $d_{ij} = -u_i ^\top v_j$ and $f(x) = \exp(-x)$.
-Yet, they have some apparent differences.
-For example, the word2vec does not have a mass term $M_i$.
-In addition, the dot similarity $u_i ^\top v_j$ can be asymmetric, \ie $u_i ^\top v_j \neq u_j ^\top v_i$.
+where $\pi_i$ is the frequency of location $i$ over the dataset
+
+Interestingly, Eq.~\ref{eq:flow_w2v} has a similar functional form with the gravity model, \ie $d_{ij} = - \bm{u}_{j} \cdot \bm{v}_{i}$ and $f(x) = \exp(-x)$.
+Yet, the Eq.~\ref{eq:flow_w2v}  does not have a population term $m_i$, and the distance can be asymmetric,$d_{ij}=- \bm{u}_{j} \cdot \bm{v}_{i} \neq - \bm{u}_{i} \cdot \bm{v}_{j}=d_{ji}$.
 In practice, however, this gap is filled due to the effect of optimization algorithm---\emph{the negative sampling}.
 
-The negative sampling is an optimization method widely used for training the word2vec, which operates as follows.
+The negative sampling is an optimization method widely used for training the \textit{word2vec}, which operates as follows.
 For each center--context word pair $(i,j)$, one generates $k$ noise center--context word pairs, denoted by $(i, \ell)$, where context word $\ell$ for the noise pair is sampled from a noise distribution, denoted by $p_{0}(\ell)$.
 Given a center-context word pair, $(i,j)$, as an input, one predicts whether it comes from the original data or noise distribution based on
-a similarity between two words, \eg dot similarity in case of the word2vec.
+a similarity between two words, \eg dot similarity in case of the \textit{word2vec}.
 
-An overlooked fact is that the negative sampling is a biased estimator that optimizes a slightly different objective function~\cite{Gutmann2010}.
-The negative sampling does not directly fit the word2vec to the given data but with the synthetic classification task.
-As a consequence, it does not fit the original model but a different model given by \cite{Gutmann2010}
+The negative sampling is a biased estimator that optimizes a slightly different objective function~\autocite{Gutmann2010}, not directly fit the \textit{word2vec} with the the synthetic classification task.
+As a consequence, the model optimized following conditional probability,
 \begin{align}
-    P\left(j \given i \right):= \frac{p_0(j)\exp(u^\top _i v_j)}{Z_i}.
+    P\left(j \given i \right):= \frac{p_0(j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z'_i}, \label{eq:prob_w2v_ng0}
 \end{align}
-By taking into the bias, the flow between $i$ and $j$ is given by
+where $Z'_i=\sum_{x \in \mathcal{A}} p_0(x) \exp(\bm{u}_{x} \cdot \bm{v}_{i})$ is a new biased normalization constant.
+
+The \textit{word2vec} uses a noise distribution given by $p_{0}(j) = \pi^{\gamma} _j / \sum_{\ell'} \pi^{\gamma}_{\ell'}$, where $\gamma$ is a free parameter typically set to $3/4$ or $1$.
+Notably, $\gamma=1$ is a special choice that ensures that the in-vector and out-vector are the same, \ie $u_i = v_i$ \autocite{levy2014neural}.
+Setting $\gamma = 1$ and substituting $p_{0}(j) = \pi^{\gamma} _j / \sum_{\ell'} \pi^{\gamma}_{\ell'}$ into Eq~\eqref{eq:flow_w2v_ng0} yields
+
 \begin{align}
-    T_{ij}=\pi_i\frac{p_0(j)\exp(u_i ^\top v_j)}{Z_i}. \label{eq:flow_w2v_ng0}
+    P\left(j \given i \right):= \frac{\pi^{\gamma} _j  \exp(\bm{u}_j \cdot \bm{v}_{i})}{ \sum_{\ell'} \pi^{\gamma}_{\ell'} Z'_i} =  \frac{\pi _j  \exp(\bm{v}_j \cdot \bm{v}_{i})}{ \sum_{\ell'} \pi_{\ell'} Z'_i},
 \end{align}
-The word2vec uses a noise distribution given by $p_{0}(\ell) = \pi^{\gamma} _\ell / \sum_{\ell'} \pi^{\gamma}_{\ell'}$, where $\gamma$ is a free parameter typically set to $3/4$ or $1$.
-Notably, $\gamma=1$ is a special choice that ensures that the in-vector and out-vector are the same, \ie $u_i = v_i$.
-Setting $\gamma = 1$ and substituting $p_0 (\ell) = \pi_\ell$ into Eq~\eqref{eq:flow_w2v_ng0} yields
+
 \begin{align}
-    T_{ij}=c\pi_i \pi_j\exp(u_i ^\top u_j). \label{eq:flow_w2v_ng}
+    \hat{T_{ij}}=\pi_i P(j\given i) =  \frac{\pi_i \pi _j  \exp(\bm{v}_j \cdot \bm{v}_{i})}{ \sum_{\ell'} \pi_{\ell'} Z'_i}. \label{eq:flow_w2v_ng0}
 \end{align}
-where $c$ is a positive constant, and we have exploited $\pi_i/Z_i = c$ derived from $T_{ij} = T_{ji}$.
-Equation~\eqref{eq:flow_w2v_ng} reveals the connection between the word2vec and the gravity model.
-For example, the word2vec is a special case of the gravity model, in which the mass of location $i$ is its frequency in the trajectory data, and the distance between locations is measured by their dot similarities.
+
+Also, deriving form $\hat{T_{ij}}=\hat{T_{ji}}$ yields
+\begin{align}
+    \frac{\pi_i \pi _j  \exp(\bm{v}_j \cdot \bm{v}_{i})}{ \sum_{\ell'} \pi_{\ell'} Z'_i} =  \frac{\pi_j \pi _i  \exp(\bm{v}_i \cdot \bm{v}_{j})}{ \sum_{\ell'} \pi_{\ell'} Z'_j},
+\end{align}
+\begin{align}
+    Z'_j = Z'_i. \label{eq:euqal_rel}
+\end{align}
+
+Combining Eq. \eqref{eq:flow_w2v_ng0} and Eq. \eqref{eq:euqal_rel} yields
+\begin{align}
+\hat{T_{ij}}=\pi_i P(j\given i) =  C \pi_i \pi _j  \exp(\bm{v}_j \cdot \bm{v}_{i}),
+\end{align}
+where $C$ is a positive constant.
+Eq.~\eqref{eq:flow_w2v_ng0} reveals the connection between the \textit{word2vec} and the gravity model Eq.~\eqref{eq:gravity_model} with $d_{ij} = - \bm{u}_{j} \cdot \bm{v}_{i}$ and $f(x) = \exp(-x)$.
+For example, the \textit{word2vec} is a special case of the gravity model, in which the mass of location $i$ is its frequency in the trajectory data, and the distance between locations is measured by their dot similarities.
+
+\section{From gravity model to \textit{word2vec}}
+In gravity model,  the probability that a person moves from location i to j is given by
+\begin{align}
+P\left(j \given i \right) = T_{ij} / m_i = C m_j f(d_{ij}). \label{eq:gravity_prob}
+\end{align}
+
+Because, the sum of conditional probability should be one,
+\begin{align}
+ C \sum_{k} m_k f(d_{ik}) = 1, \label{eq:gravity_constant}
+\end{align}
+which means $\sum_{j} m_j f(d_{ij})$ is constant. Substituting Eq.~\eqref{eq:gravity_prob} into \eqref{eq:gravity_constant} yields
+\begin{align}
+P\left(j \given i \right) = \frac{m_i f(d_{ij})}{\sum_{k} m_j f(d_{ik})}. \label{eq:gravity_prob},
+\end{align}
+which is similar functional form of  Eq.~\eqref{eq:prob_w2v_ng0}.
 
@@
 %
-%The euclidean word2vec takes flow as input and outputs the location and population at each location.
+%The euclidean \textit{word2vec} takes flow as input and outputs the location and population at each location.
 %This algorithm is reminiscent of the multidimensional scaling (MDS), which maps entities onto a Euclidean space by preserving their dissimilarity as distance as much as possible.
 %Specifically, given a dissimilarity matrix $D=(D_{ij})$, MDS aims to map entities such that $D_{ij} \approx ||u_i - u_j||$ for all $i$ and $j$.
-%This connection allows us to optimize the euclidean word2vec using the MDS algorithm, as we will see in the following.
+%This connection allows us to optimize the euclidean \textit{word2vec} using the MDS algorithm, as we will see in the following.
 %
 %For a moment, let us consider an ideal situation in which the given data is generated from Eq~\eqref{eq:flow_w2v_ng} and how we can fit the model.
-%Denoted by $T_{ij} ^\text{data}$ as the actual flow, and $T^{\text{model}}_ij$ by the flow modeled by the word2vec.
-%When embedding dimension $K$ is small, the word2vec has a limited expression power and thus the modeled flow can be considerably different to the actual flow.
+%Denoted by $T_{ij} ^\text{data}$ as the actual flow, and $T^{\text{model}}_ij$ by the flow modeled by the \textit{word2vec}.
+%When embedding dimension $K$ is small, the \textit{word2vec} has a limited expression power and thus the modeled flow can be considerably different to the actual flow.
 %As we increase $K$, however, the model gains more expression power and eventually achieves an exact fit, $T_{ij} ^\text{data} = T_{ij} ^\text{model}$, just like fitting a high-order polynomial function (\eg quadratic function) to two data points.

### 2021-01-11 paper/current/notes/2021-0105-word2vec-vs-gravity-model/main.tex
add additional proof for equation 4

@@
 
-The \textit{word2vec} fits well to a wide range of mobilities, which prompts us to ask: why does the \textit{word2vec} fit well to the mobility data?
-It turns out that the \textit{word2vec} is tied to a gravity model, a widespread and long-standing model that well explains human mobility.
-While the gravity model predicts a flow from given locations and populations, the \textit{word2vec} is a reverse engineering model that estimates the location and population from flows.
+Our results show that the \textit{word2vec} better explain a wide range of mobilities than conventional embedding methods, which prompts us to ask: why does the \textit{word2vec} work well for the mobility data?
+Here, we show that the \textit{word2vec} is tied to a gravity model, a widespread and long-standing model that well explains human mobility.
+%While the gravity model predicts a flow from given locations and populations, the \textit{word2vec} is a reverse engineering model that estimates the location and population from flows.
 
 Let us approach the connection by initially focusing on the gravity model.
-Suppose that flow of people between $N$ locations. The gravity model models the flow by
+Suppose that flow of people between $N$ locations. The gravity model models the expected flow $\hat{T_{ij}}$ from location $i$ to $j$ by
 \begin{align}
@@
 \end{align}
-where $\hat{T_{ij}}$ is the expected flow from location $i$ to $j$, $m_i$ is the population of locations of $i$, $r_{ij}$ is a distance between locations $i$ and $j$, $f$ is a decreasing function with respect to $r_{ij}$, and $C$ is a constant.
-That the gravity model implicitly assumes that the flow is symmetric, \ie $\hat{T_{ij}}=\hat{T_{ji}}$, which ensures the stationarity in population $m_{i}$.
-The choice of distance measure $d_{ij}$ is entirely unconstrained; it can be the euclidean distance, or any kind of general distance measure.
-In the following, we refer to a measure of dissimilarity as distance.
+where $m_i$ is the population of locations of $i$, $r_{ij}$ is their distance, $f$ is a decreasing function of $r_{ij}$, and $C$ is a constant.
+The choice of distance measure is not entirely unconstrained; it should have symmetricity (\ie $r_{ij} = r_{ji}$).
+Apart from that, the distance measure $r_{ij}$ can be any dissimilarity measure even if it does not satisfy the axiom of metric space (such as triangle inequality $r_{ij}  + r_{jk} > r_{ik}$).
+In the following, we refer to a measure of dissimilarity as distance for brevity.
+In gravity model, the flow is symmetric, \ie $\hat{T_{ij}}=\hat{T_{ji}}$, which ensures the stationarity in population $m_{i}$.
 
-Now, let us move our focus to the \textit{\textit{word2vec}}.
+Now, let us move our focus to the \textit{word2vec}.
 In out setting, the model takes a sequence of locations and models the co-occurrence of center location $i$ and context location $j$ by
@@
 \end{equation}
-where $\mathcal{A}$ is the entire set of unique locations represented in the data, and  $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively.
-$Z_i=\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{i})$ is a normalization constant.
-Under the stationary condition and restricting window size to be one , the expected flow between center location $a_i$ and context location $a_j$ is given by
+where $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector", respectively, and $Z_i=\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{i})$ is a normalization constant,
+and $\mathcal{A}$ is the set of all locations.
+Under restricting window size to be one, the expected flow between center location $a_i$ and context location $a_j$ is given by
 \begin{align}
     \label{eq:flow_w2v}
-        \hat{T_{ij}}=\pi_i P(j\given i) = \frac{\pi_i\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
+    \hat{T_{ij}}=s_i P(j\given i) = \frac{s_i\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
 \end{align}
-where $\pi_i$ is the frequency of location $i$ over the dataset
+where $s_i$ is the frequency of location $i$ summed for all trajectories in the dataset.
+Although there are some similarities, Eq.~\ref{eq:flow_w2v} does not have a population term $m_i$.
+In additionm the distance can be asymmetric,$r_{ij}=- \bm{u}_{j} \cdot \bm{v}_{i} \neq - \bm{u}_{i} \cdot \bm{v}_{j}=r_{ji}$.
 
-Interestingly, Eq.~\ref{eq:flow_w2v} has a similar functional form with the gravity model, \ie $d_{ij} = - \bm{u}_{j} \cdot \bm{v}_{i}$ and $f(x) = \exp(-x)$.
-Yet, the Eq.~\ref{eq:flow_w2v}  does not have a population term $m_i$, and the distance can be asymmetric,$d_{ij}=- \bm{u}_{j} \cdot \bm{v}_{i} \neq - \bm{u}_{i} \cdot \bm{v}_{j}=d_{ji}$.
-In practice, however, this gap is filled due to the effect of optimization algorithm---\emph{the negative sampling}.
-
+The gap between the gravity model and {\it word2vec} is filled by taking into account how we train the word2vec---\emph{the negative sampling}.
 The negative sampling is an optimization method widely used for training the \textit{word2vec}, which operates as follows.
 For each center--context word pair $(i,j)$, one generates $k$ noise center--context word pairs, denoted by $(i, \ell)$, where context word $\ell$ for the noise pair is sampled from a noise distribution, denoted by $p_{0}(\ell)$.
-Given a center-context word pair, $(i,j)$, as an input, one predicts whether it comes from the original data or noise distribution based on
-a similarity between two words, \eg dot similarity in case of the \textit{word2vec}.
+Given a center-context word pair, $(i,j)$, as an input, one predicts whether it comes from the original data or noise distribution based on a similarity between two words, \eg dot similarity in case of the \textit{word2vec}.
 
-The negative sampling is a biased estimator that optimizes a slightly different objective function~\autocite{Gutmann2010}, not directly fit the \textit{word2vec} with the the synthetic classification task.
-As a consequence, the model optimized following conditional probability,
+The negative sampling does not directly fit the word2vec to the data but through the synthetic classification task.
+An often underappreciated fact is that the negative sampling has a bias and maximizes a different objective function~\autocite{Gutmann2010}.
+With the negative sampling, the correct expression for the conditional probability is given by
 \begin{align}
@@
 \end{align}
-where $Z'_i=\sum_{x \in \mathcal{A}} p_0(x) \exp(\bm{u}_{x} \cdot \bm{v}_{i})$ is a new biased normalization constant.
+where $Z'_i=\sum_{x \in \mathcal{A}} p_0(x) \exp(\bm{u}_{x} \cdot \bm{v}_{i})$ is a normalization constant.
+See Section \ref{sec:correct_word2vec} for full calculations.
 
-The \textit{word2vec} uses a noise distribution given by $p_{0}(j) = \pi^{\gamma} _j / \sum_{\ell'} \pi^{\gamma}_{\ell'}$, where $\gamma$ is a free parameter typically set to $3/4$ or $1$.
-Notably, $\gamma=1$ is a special choice that ensures that the in-vector and out-vector are the same, \ie $u_i = v_i$ \autocite{levy2014neural}.
-Setting $\gamma = 1$ and substituting $p_{0}(j) = \pi^{\gamma} _j / \sum_{\ell'} \pi^{\gamma}_{\ell'}$ into Eq~\eqref{eq:flow_w2v_ng0} yields
-
+The \textit{word2vec} uses a noise distribution given by $p_{0}(j) = s^{\gamma} _j / \sum_{\ell'} s^{\gamma}_{\ell'}$, where $\gamma$ is a free parameter typically set to $3/4$ or $1$.
+Parameter $\gamma=1$ is a special choice that ensures that the in-vector and out-vector are the same, \ie $\bm{u}_i = \bm{v}_i$ \autocite{levy2014neural}.
+Setting $\gamma = 1$, and substituting $\bm{u}_i = \bm{v}_j$ and $p_0(j) = s_j / \sum_{\ell'} s_{\ell'}$ into Eq~\eqref{eq:flow_w2v_ng0}, we have
 \begin{align}
-    P\left(j \given i \right):= \frac{\pi^{\gamma} _j  \exp(\bm{u}_j \cdot \bm{v}_{i})}{ \sum_{\ell'} \pi^{\gamma}_{\ell'} Z'_i} =  \frac{\pi _j  \exp(\bm{v}_j \cdot \bm{v}_{i})}{ \sum_{\ell'} \pi_{\ell'} Z'_i},
+    P\left(j \given i \right) & := \frac{ p_0 (j) \exp(\bm{v}_j \cdot \bm{v}_{i})}{ Z'_i}                      \\
+                              & =  \frac{s _j  \exp(\bm{v}_j \cdot \bm{v}_{i})}{ Z' _i\sum_{\ell'} s_{\ell'}},
 \end{align}
-
+which leads to the expected flow for the word2vec model, \ie
 \begin{align}
-    \hat{T_{ij}}=\pi_i P(j\given i) =  \frac{\pi_i \pi _j  \exp(\bm{v}_j \cdot \bm{v}_{i})}{ \sum_{\ell'} \pi_{\ell'} Z'_i}. \label{eq:flow_w2v_ng0}
+    \hat{T_{ij}}=s_i P(j\given i) =  \frac{s_i s _j  \exp(\bm{v}_j \cdot \bm{v}_{i})}{  Z'_i\sum_{\ell'} s_{\ell'}}. \label{eq:flow_w2v_ng0}
 \end{align}
-
-Also, deriving form $\hat{T_{ij}}=\hat{T_{ji}}$ yields
+In the word2vec, the flow $\hat{T_{ij}}_{ij}$ is symmetric by design (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because the word2vec neglects whether the context $j$ appears later or earlier from center $i$.
+Therefore, we have
 \begin{align}
-    \frac{\pi_i \pi _j  \exp(\bm{v}_j \cdot \bm{v}_{i})}{ \sum_{\ell'} \pi_{\ell'} Z'_i} =  \frac{\pi_j \pi _i  \exp(\bm{v}_i \cdot \bm{v}_{j})}{ \sum_{\ell'} \pi_{\ell'} Z'_j},
+    T_{ij} = T_{ji}
+     & \Rightarrow
+    \frac{s_i s _j  \exp(\bm{v}_j \cdot \bm{v}_{i})}{  Z'_i\sum_{\ell'} s_{\ell'}} =  \frac{s_j s _i  \exp(\bm{v}_i \cdot \bm{v}_{j})}{  Z'_j\sum_{\ell'} s_{\ell'}} \\
+     & \Rightarrow
+    Z'_i = Z'_j, \label{eq:euqal_rel}
 \end{align}
+suggesting that the normalization constant $Z' _i$ is constant.
+Combining Eqs.~\eqref{eq:flow_w2v_ng0} and \eqref{eq:euqal_rel}, we have
 \begin{align}
-    Z'_j = Z'_i. \label{eq:euqal_rel}
-\end{align}
-
-Combining Eq. \eqref{eq:flow_w2v_ng0} and Eq. \eqref{eq:euqal_rel} yields
-\begin{align}
-\hat{T_{ij}}=\pi_i P(j\given i) =  C \pi_i \pi _j  \exp(\bm{v}_j \cdot \bm{v}_{i}),
+    \hat{T_{ij}}=  C s_i s _j  \exp(\bm{v}_j \cdot \bm{v}_{i}),
 \end{align}
 where $C$ is a positive constant.
-Eq.~\eqref{eq:flow_w2v_ng0} reveals the connection between the \textit{word2vec} and the gravity model Eq.~\eqref{eq:gravity_model} with $d_{ij} = - \bm{u}_{j} \cdot \bm{v}_{i}$ and $f(x) = \exp(-x)$.
-For example, the \textit{word2vec} is a special case of the gravity model, in which the mass of location $i$ is its frequency in the trajectory data, and the distance between locations is measured by their dot similarities.
+Eq.~\eqref{eq:flow_w2v_ng0} reveals the connection between the \textit{word2vec} and the gravity model, with with $d_{ij} = - \bm{u}_{j} \cdot \bm{v}_{i}$ and $f(x) = \exp(-x)$.
+In sum, the \textit{word2vec} is a gravity model, in which the mass of location $i$ is its frequency in the trajectory data, and the distance between locations is measured by their dot similarities.
 
 \section{From gravity model to \textit{word2vec}}
-In gravity model,  the probability that a person moves from location i to j is given by
+\label{sec:from_gravity_to_word2vec}
+
+Let us approach from the gravity model to the word2vec.
+In the gravity model, the probability that a person moves from location $i$ to $j$ is given by
 \begin{align}
@@
 \end{align}
+Because, the sum of probabilities should be one,
+\begin{align}
+     & \sum_{j} P(j \given i) = 1 \nonumber                                     \\
+     & \Rightarrow C \sum_{k} m_k f(d_{ik}) = 1 \nonumber                       \\
+     & \Rightarrow C  = 1 / \sum_{k} m_k f(d_{ik}), \label{eq:gravity_constant}
+\end{align}
+which ensures that $\sum_{j} m_j f(d_{ij})$ is constant.
+Substituting \eqref{eq:gravity_constant}  into Eq.~\eqref{eq:gravity_prob} yields a model having the same functional form with the word2vec, \ie
+\begin{align}
+    P\left(j \given i \right) = \frac{m_i f(d_{ij})}{\sum_{k} m_k f(d_{ik})}. \label{eq:gravity_prob2}
+\end{align}
 
-Because, the sum of conditional probability should be one,
+\section{Correct representation of word2vec section}
+\label{sec:correct_word2vec}
+
+Many probability models including the word2vec can be represented in form
 \begin{align}
- C \sum_{k} m_k f(d_{ik}) = 1, \label{eq:gravity_constant}
+    f(x) / \sum_{x' \in {\cal X}} f(x'),
 \end{align}
-which means $\sum_{j} m_j f(d_{ij})$ is constant. Substituting Eq.~\eqref{eq:gravity_prob} into \eqref{eq:gravity_constant} yields
+where $f$ is a nonnegative function.
+Fitting the probability models are computationally expensive as its denominator involves a sum over all possible entities ${\cal X}$ in data.
+The negative sampling is introduced as a way to avoid computing the denominator.
+To this end, the negative sampling solves a synthetic binary classification task, in which
+we are asked to classify an actual data $x$ and a noise data $\tilde x$ using a sigmoid function
 \begin{align}
-P\left(j \given i \right) = \frac{m_i f(d_{ij})}{\sum_{k} m_j f(d_{ik})}. \label{eq:gravity_prob},
+    \label{eq:sigmoid}
+    \frac{1}{1 + \exp\left( -\log f(z) \right)}.
 \end{align}
-which is similar functional form of  Eq.~\eqref{eq:prob_w2v_ng0}.
+Because this sigmoid function does not involve the normalization constant, the model fitting can be done with less computational burden.
+
+The negative sampling does not directly fits a probability model to data but does so through the synthetic classification task.
+This has a side effect: the negative sampling has a bias, and hence does not correctly train the model \cite{Dyer2014}.
+The bias can be corrected using the noise contrastive estimation (NCE) \cite{Chia2010}, which solves the
+same classification task but with a bias-corrected sigmoid function, \ie
+\begin{align}
+    \label{eq:sigmoid2}
+    \frac{1}{1 + \exp\left( -\log f(z) + \log p_0(z) \right)}.
+\end{align}
+Note that Eq.~\eqref{eq:sigmoid2} has an additional term $\log p_0(z)$, which is the log-probability of $z$ for a noise distribution.
+
+If the bias is not corrected, what model does the negative sampling actually fit?
+To see this, we rewrite the sigmoid function (Eq.~\eqref{eq:sigmoid}) in form of the bias-corrected sigmoid function, \ie
+\begin{align}
+    \label{eq:sigmoid3}
+    \frac{1}{1 + \exp\left[ - \log \tilde f(z) + \log p_0(z)  \right]},
+\end{align}
+where we have defined
+\begin{align}
+    \label{eq:unnormalized}
+    \tilde f(z) = f(z) p_0(z).
+\end{align}
+This sigmoid function correctly fits a probability model:
+\begin{align}
+    f'(x) / \sum_{x' \in {\cal X}} f'(x),
+\end{align}
+or, by substituting Eq.~\eqref{eq:unnormalized},
+\begin{align}
+    p_0(x)f(x) / \sum_{x' \in {\cal X}} p_0(x')f(x').
+\end{align}
+For the word2vec, the correct expression of word2vec optimized with the negative sampling is given by
+\begin{align}
+    P\left(j \given i \right):= \frac{p_0(j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z'_i}.
+\end{align}
+
+%What if we train the word2vec without the correction?
 
 %\section{Optimization based on the multidimensional scaling}
+
 %

### 2021-01-12 paper/current/notes/2021-0105-word2vec-vs-gravity-model/main.tex
edit some para

@@
 where $m_i$ is the population of locations of $i$, $r_{ij}$ is their distance, $f$ is a decreasing function of $r_{ij}$, and $C$ is a constant.
-The choice of distance measure is not entirely unconstrained; it should have symmetricity (\ie $r_{ij} = r_{ji}$).
-Apart from that, the distance measure $r_{ij}$ can be any dissimilarity measure even if it does not satisfy the axiom of metric space (such as triangle inequality $r_{ij}  + r_{jk} > r_{ik}$).
-In the following, we refer to a measure of dissimilarity as distance for brevity.
+In the following, we refer to a measure of dissimilarity as a distance for brevity.
 In gravity model, the flow is symmetric, \ie $\hat{T_{ij}}=\hat{T_{ji}}$, which ensures the stationarity in population $m_{i}$.
@@
 Although there are some similarities, Eq.~\ref{eq:flow_w2v} does not have a population term $m_i$.
-In additionm the distance can be asymmetric,$r_{ij}=- \bm{u}_{j} \cdot \bm{v}_{i} \neq - \bm{u}_{i} \cdot \bm{v}_{j}=r_{ji}$.
+In additionm the distance can be asymmetric, $r_{ij}=- \bm{u}_{j} \cdot \bm{v}_{i} \neq - \bm{u}_{i} \cdot \bm{v}_{j}=r_{ji}$.
 
-The gap between the gravity model and {\it word2vec} is filled by taking into account how we train the word2vec---\emph{the negative sampling}.
-The negative sampling is an optimization method widely used for training the \textit{word2vec}, which operates as follows.
+The gap between the gravity model and {\it word2vec} is filled by taking into account how we train the \textit{word2vec}---\emph{the negative sampling}.
+The negative sampling is an optimization method widely used for training the machine learning model, which operates as follows.
 For each center--context word pair $(i,j)$, one generates $k$ noise center--context word pairs, denoted by $(i, \ell)$, where context word $\ell$ for the noise pair is sampled from a noise distribution, denoted by $p_{0}(\ell)$.
@@
 
-The negative sampling does not directly fit the word2vec to the data but through the synthetic classification task.
-An often underappreciated fact is that the negative sampling has a bias and maximizes a different objective function~\autocite{Gutmann2010}.
+The negative sampling does not directly fit the \textit{word2vec} to the data but through the synthetic classification task.
+An often underappreciated fact is that negative sampling has a bias and maximizes a different objective function~\autocite{Gutmann2010}.
 With the negative sampling, the correct expression for the conditional probability is given by
@@
 \end{align}
-where $Z'_i=\sum_{x \in \mathcal{A}} p_0(x) \exp(\bm{u}_{x} \cdot \bm{v}_{i})$ is a normalization constant.
+where $Z'_i=\sum_{x \in \mathcal{A}} p_0(x) \exp(\bm{u}_{x} \cdot \bm{v}_{i})$ is a normalization constant, and a noise distribution given by $p_{0}(j) = s^{\gamma} _j / \sum_{\ell'} s^{\gamma}_{\ell'}$, where $\gamma$ is a free parameter typically set to $3/4$ or $1$.
 See Section \ref{sec:correct_word2vec} for full calculations.
 
-The \textit{word2vec} uses a noise distribution given by $p_{0}(j) = s^{\gamma} _j / \sum_{\ell'} s^{\gamma}_{\ell'}$, where $\gamma$ is a free parameter typically set to $3/4$ or $1$.
 Parameter $\gamma=1$ is a special choice that ensures that the in-vector and out-vector are the same, \ie $\bm{u}_i = \bm{v}_i$ \autocite{levy2014neural}.
@@
 \end{align}
-In the word2vec, the flow $\hat{T_{ij}}_{ij}$ is symmetric by design (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because the word2vec neglects whether the context $j$ appears later or earlier from center $i$.
+In the \textit{word2vec}, the flow $\hat{T_{ij}}_{ij}$ is symmetric by design (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because the word2vec neglects whether the context $j$ appears later or earlier from center $i$.
 Therefore, we have
@@
 
-The negative sampling does not directly fits a probability model to data but does so through the synthetic classification task.
-This has a side effect: the negative sampling has a bias, and hence does not correctly train the model \cite{Dyer2014}.
+The negative sampling does not directly fit a probability model to data but does so through the synthetic classification task.
+This has a side effect: the negative sampling has a bias and hence does not correctly train the model \cite{Dyer2014}.
 The bias can be corrected using the noise contrastive estimation (NCE) \cite{Chia2010}, which solves the

### 2021-01-14 paper/current/main.tex

@@
 \begin{equation}
-p(a_{j} \vert a_{i}) = \frac{\exp(\bm{u}_{a_j} \cdot \bm{v}_{a_{i}})}{\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{a_{i}})},
+p(j \vert i) = \frac{\exp(\bm{u}_{j} \cdot \bm{v}_{i})}{\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{i})},
 \end{equation}
-where $a_i =a_{t} $, $ a_j=a_{t + \tau}$, $\mathcal{A}$ is the entire set of unique locations represented in the data, and  $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively.
+where $i =a_{t} $, $ j=a_{t + \tau}$, $\mathcal{A}$ is the entire set of unique locations represented in the data, and  $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively.
 We follow the standard practice and only use the in-vector, $v$,  which is known to be superior to the out-vector in link prediction benchmarks~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}.

### 2021-01-15 workflow/scripts/PlotHyperparameterPerformance.R
add gamma to hyperparameters plot

@@ -8,8 +8,8 @@
 #
 
 # Plot dimensions
-FIG_WIDTH = 7
-FIG_HEIGHT = 4
+FIG_WIDTH = 6
+FIG_HEIGHT = 6
 
 
 library(readr)
@@ -32,43 +32,49 @@ params <- read_csv(opt$input, col_types = readr::cols())
 plotdata <- params %>%
   filter(metric == "emb") %>%
   filter(sizetype == "mobile") %>%
-  filter(gamma == 1.0) %>%
+  filter(traj == "precedence") %>%
   mutate(
     dim = factor(dim),
+    ws = factor(ws),
     case = factor(case,
                   levels = c("global", "same-country", "diff-country"),
                   labels = c("All Organizations", "Same Country", "Different Country")
-                  )
-    )
+                ),
+    gamma = factor(gamma),
+    gamma = factor(gamma,
+                   levels = c(0.75, 1.0),
+                   labels = c("gamma = 0.75", "gamma = 1.0")
+            )
+  )
 
 
 plot <- plotdata %>%
-  ggplot(aes(x = ws, y = r2, color = dim, shape = dim, group = dim)) +
+  ggplot(aes(x = dim, y = r2, color = ws, shape = ws, group = ws)) +
     geom_point(size = 3) +
     geom_line() +
     geom_linerange(aes(ymin = ci.lower, ymax = ci.upper)) +
-    facet_grid(traj~case) +
-    scale_x_continuous(breaks = unique(plotdata$ws)) +
+    facet_grid(case~gamma) +
     scale_y_continuous(
       limits = c(0.2, 0.6),
       breaks = c(0.2, 0.4, 0.6)
     ) +
     scale_color_manual(
-      name = "Embedding Dimension",
+      name = "Window size",
       values = c("#b2bec3", "#636e72", "#2d3436")
     ) +
-    scale_shape_discrete(name = "Embedding Dimension") +
+    scale_shape_discrete(name = "Window size") +
     theme_minimal() +
     theme(
       text = element_text(size = 11, family = "Helvetica"),
       strip.text = element_text(size = 12, face = "bold"),
+      strip.text.y.right = element_text(angle = 0, hjust = 0),
       axis.title = element_text(size = 12),
       legend.title = element_text(size = 12, face = "bold"),
       legend.position = "bottom",
       panel.grid.minor = element_blank(),
       panel.spacing = unit(1.5, "lines")
     ) +
[…]

### 2021-01-15 workflow/scripts/PlotDistanceMetricPerformance.R
create plot of R2 across distance metrics, cases. population definitions

@@ -1,0 +1,76 @@
+#
+# PlotDistanceMetricPerformance.R
+#
+# author: Dakota Murray
+#
+# Plots the performance of various distance metrics and definitions
+# of population size
+#
+
+# Plot dimensions
+FIG_WIDTH = 6
+FIG_HEIGHT = 7
+
+
+library(readr)
+library(ggplot2)
+library(dplyr)
+suppressPackageStartupMessages(require(optparse))
+
+# Command line arguments
+option_list = list(
+  make_option(c("-i", "--input"), action="store", default=NA, type='character',
+              help="Path to file containing the aggregated hyperameter values"),
+  make_option(c("-o", "--output"), action="store", default=NA, type='character',
+              help="Path to save output image")
+) # end option_list
+opt = parse_args(OptionParser(option_list=option_list))
+
+# Read the aggregate R2 data
+params <- read_csv(opt$input, col_types = readr::cols())
+
+plotdata <- params %>%
+  filter(dim == 300) %>%
+  filter(ws == 1) %>%
+  filter(gamma == 1.0) %>%
+  mutate(
+    sizetype = gsub(".csv", "", sizetype, fixed = T),
+    metric = factor(metric,
+                    levels = c("geo", "emb", "dot", "pprcos", "pprjsd", "lapcos", "svdcos"),
+                    labels = c("Geographic\ndistance", "Embedding\ncosine distance", "Embedding\ndot product", "PPR cosine\ndistance", "PPR JSD", "Laplacian\nEigenmap\ndistance", "SVD distance")),
+    case = factor(case,
+                  levels = c("global", "same-country", "diff-country"),
+                  labels = c("All", "Domestic", "International")),
+    sizetype = factor(sizetype,
+                      levels = c("all", "mobile", "freq"),
+                      labels = c("All", "Mobile only", "Raw frequency"))
+
+  )
+
+
+plot <- plotdata %>%
+  ggplot(aes(x = sizetype, y = r2)) +
+  geom_point(stroke = 0.2, size = 2.5, alpha = 0.8, position = position_dodge(0.5)) +
+  facet_grid(metric~case) +
+  scale_y_continuous(
+    limits = c(0, 0.52),
+    breaks = c(0, 0.25, 0.5)
+  ) +
+  scale_shape_manual(values = c(23, 21)) +
+  scale_fill_manual(values = c("darkgrey", "black")) +
+  theme_minimal() +
+  theme(
[…]

### 2021-01-15 workflow/scripts/PlotHyperparameterPerformance.R
make hyperparameter plot prettier

@@ -65,14 +65,15 @@ plot <- plotdata %>%
     scale_shape_discrete(name = "Window size") +
     theme_minimal() +
     theme(
+      panel.grid.minor = element_blank(),
+      panel.grid.major.x = element_blank(),
+      panel.border = element_rect(size = 0.5, color = "black", fill = NA),
       text = element_text(size = 11, family = "Helvetica"),
       strip.text = element_text(size = 12, face = "bold"),
       strip.text.y.right = element_text(angle = 0, hjust = 0),
       axis.title = element_text(size = 12),
       legend.title = element_text(size = 12, face = "bold"),
       legend.position = "bottom",
-      panel.grid.minor = element_blank(),
-      panel.spacing = unit(1.5, "lines")
     ) +
     xlab("Embedding dimension") +
     ylab("Correlation with flux (R2)")

### 2021-01-15 workflow/scripts/PlotDistanceMetricPerformance.R
sort the vertical panels (distance) by performance

@@ -38,6 +38,8 @@ plotdata <- params %>%
     metric = factor(metric,
                     levels = c("geo", "emb", "dot", "pprcos", "pprjsd", "lapcos", "svdcos"),
                     labels = c("Geographic\ndistance", "Embedding\ncosine distance", "Embedding\ndot product", "PPR cosine\ndistance", "PPR JSD", "Laplacian\nEigenmap\ndistance", "SVD distance")),
+    # Reorder the metric variable with 
+    metric = reorder(metric, desc(r2)),
     case = factor(case,
                   levels = c("global", "same-country", "diff-country"),
                   labels = c("All", "Domestic", "International")),

### 2021-01-15 paper/current/main.tex
add bew figures to manuscript. Add mentions in the text

--- 2020-12-03 paper/current/main.tex
@@
 These patterns hold for the subsets of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d and  Fig.~\ref{fig:supp:predict_emb_bymodel}).
-The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores  calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores  calculated from the underlying mobility network (Fig.~\ref{fig:supp:distancemetrics}, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+The embedding distance derived from neural embedding also explains more of the flux than simpler embedding baselines, such as distances derived from a singular-value decomposition and from a Laplacian Eigenmap embedding of the underlying data (Fig.~\ref{fig:supp:distancemetrics}).
 In sum, our results demonstrate that, consistently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
@@
 We used the \textit{word2vec}  implementation in the python package \texttt{gensim}. 
-The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{\min}$, initial learning rate $\alpha$, and the number of iterations.
+The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{\min}$, initial learning rate $\alpha$, shape of negative sampling distribution $\gamma$, and the number of iterations.
 For main results regarding scientific mobility, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig.~\ref{fig:supp:hyperparams}).
-We also use same setting for U.S.
-airport itinerary and Korean accommodation reservation data.
+Although the original \textit{word2vec } paper uses $\gamma = 0.75$\autocite{mikolov2013word2vec}, here we set $\gamma = 1.0$, though results are only trivially different at different values of $\gamma$ (Fig.~\ref{fig:supp:distancemetrics}).
+We also use same setting for U.S. airport itinerary and Korean accommodation reservation data.
 To mitigate the effect of less common locations, we set $f_{\min} = 50$, limiting to locations appearing at least 50 times across the training trajectories;

### 2021-01-15 paper/current/supp.tex
add bew figures to manuscript. Add mentions in the text

@@
 		Larger vectors perform better, though little difference between 200 and 300.
+		Gamma refers to the $\gamma$ parameter in word2vec, which shapes the negative sampling distribution. 
+		A value of $\gamma = 0.75$ is the default for word2vec.
+		There is virtually no difference in performance based on $\gamma$.
 		All variants perform better on same-country pairs of organizations than on all organizations.
@@
 	}
-	\label{fig:supp:cosdot}
+	\label{fig:supp:hyperparameter}
+\end{figure}
+
+%
+% Figure - Distance metric performance
+%
+\begin{figure}[p!]
+	\centering
+	\includegraphics[width=0.9\textwidth]{\figdir/Descriptive/distance_metric_performance.pdf}
+	\caption{
+		\textbf{Cosine distance between embedding vectors explains more flux in scientific mobility than geographic distance, baselines.}
+		The correlation, or amount of flux explained by the embedding distance across distance metrics and other experimental parameters. 
+		Distance metrics are ordered, from top to bottom, by the highest correlation ($r^{2}$). 
+		All distance metrics explain more of the flux than does geographic distance.
+		The cosine distance between embedding vectors explains more flux than all other distance metrics. 
+		The x-axis differentiates between three strategies for defining the organization population used to calculate the flux. 
+		``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
+		population is defined in the same way for ``mobile-only'', except only using unique mobile researchers;
+		``Raw frequency'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding. 
+		Generally, ``All'' explains more of the flux, however there is little difference between definitions of mobility.
+		All distance metrics tend to explain more of the flux when describing all or domestic (same-country) mobility.	
+		}
+	\label{fig:supp:distancemetrics}
 \end{figure}
@@
 	}
-	\label{fig:supp:hyperparams}
+	\label{fig:supp:cosdot}
 \end{figure}

### 2021-01-18 paper/current/main.tex
incoperating math part

--- 2021-01-14 paper/current/main.tex
@@
 \DeclareMathAlphabet{\mathpzc}{T1}{pzc}{m}{it}
-\DeclareMathOperator*{\argmin}{\arg\!\min}
-\DeclareMathOperator*{\argmax}{\arg\!\max}
+\def\given{\mid}
 \usepackage{bm}
@@
 As understanding mobility is becoming critical for contemporary society, finding frameworks that can capture this complexity is of paramount importance.
-Here, using three distinct human trajectory datasets, we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
+Here, we show the  mathematical  connection  between  neural embedding models and the gravity model of human mobility and, using three distinct human trajectory datasets, demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
 Focusing on the case of scientific mobility, we show that embeddings of scientific organizations uncover cultural and linguistic relations, and even academic prestige, at multiple levels of granularity.
@@
 \end{figure}
+
+\subsection*{Mathematical connection between neural embedding model and gravity model}
+
+Our results show that the neural embedding better explains a wide range of mobilities than conventional embedding methods, which prompts us to ask: why does the \textit{word2vec} work well for the mobility data?
+We show that the \textit{word2vec} is tied to a gravity model, a widespread and long-standing model that well explains human mobility.
+
+Let us approach the connection by initially focusing on the gravity model.
+Suppose that flow of people between $N$ locations. The gravity model models the expected flow $\hat{T_{ij}}$ from location $i$ to $j$ by
+\begin{align}
+    \hat{T_{ij}} = C m_i m_j f(r_{ij}), \label{eq:gravity_model}
+\end{align}
+where $m_i$ is the population of locations of $i$, $r_{ij}$ is their distance, $f$ is a decreasing function of $r_{ij}$, and $C$ is a constant.
+%In the following, we refer to a measure of dissimilarity as a distance for brevity.
+%In gravity model, the flow is symmetric, \ie $\hat{T_{ij}}=\hat{T_{ji}}$, which ensures the stationarity in population $m_{i}$.
+
+%Now, let us move our focus to the \textit{word2vec}.
+The skip-gram negative sampling \textit{word2vec} takes a sequence of locations and models the co-occurrence of center location $i$ and context location $j$ by (See Methods)
+\begin{align}
+    P\left(j \given i \right):= \frac{p_0(j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z'_i}, \label{eq:prob_w2v_ng0}
+\end{align}
+where $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector", respectively,  $Z'_i=\sum_{x \in \mathcal{A}} p_0(x) \exp(\bm{u}_{x} \cdot \bm{v}_{i})$  is a normalization constant, and $\mathcal{A}$ is the set of all locations, and a noise distribution given by $p_{0}(j) = s^{\gamma} _j / \sum_{\ell'} s^{\gamma}_{\ell'}$, where $\gamma$ is a free parameter typically set to $3/4$ or $1$.
+Under restricting window size to be one, the expected flow between center location $i$ and context location $j$ is given by
+\begin{align}
+    \label{eq:flow_w2v}
+    \hat{T_{ij}}=s_i P(j\given i) = \frac{s_i\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z'_i},
+\end{align}
+where $s_i$ is the frequency of location $i$ summed for all trajectories in the dataset.
+
+Parameter $\gamma=1$ is a special choice that ensures that the in-vector and out-vector are the same, \ie $\bm{u}_i = \bm{v}_i$ \autocite{levy2014neural}.
+Setting $\gamma = 1$, and substituting $\bm{u}_i = \bm{v}_j$ and $p_0(j) = s_j / \sum_{\ell'} s_{\ell'}$ into Eq~\eqref{eq:flow_w2v_ng0}, we have
+\begin{align}
+    P\left(j \given i \right) & := \frac{ p_0 (j) \exp(\bm{v}_j \cdot \bm{v}_{i})}{ Z'_i}                      \\
+                              & =  \frac{s _j  \exp(\bm{v}_j \cdot \bm{v}_{i})}{ Z' _i\sum_{\ell'} s_{\ell'}},
+\end{align}
+which leads to the expected flow for the word2vec model, \ie
+\begin{align}
+    \hat{T_{ij}}=s_i P(j\given i) =  \frac{s_i s _j  \exp(\bm{v}_j \cdot \bm{v}_{i})}{  Z'_i\sum_{\ell'} s_{\ell'}}. \label{eq:flow_w2v_ng0}
+\end{align}
+
+In the \textit{word2vec}, the flow $\hat{T_{ij}}$ is symmetric by design (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because the model neglects whether the context $j$ appears later or earlier from center $i$.
+Then, we have
+\begin{align}
+    T_{ij} = T_{ji}
+     & \Rightarrow
+    \frac{s_i s _j  \exp(\bm{v}_j \cdot \bm{v}_{i})}{  Z'_i\sum_{\ell'} s_{\ell'}} =  \frac{s_j s _i  \exp(\bm{v}_i \cdot \bm{v}_{j})}{  Z'_j\sum_{\ell'} s_{\ell'}} \\
+     & \Rightarrow
+    Z'_i = Z'_j, \label{eq:euqal_rel}
+\end{align}
+suggesting that the normalization constant $Z' _i$ is constant.
+Combining Eqs.~\eqref{eq:flow_w2v_ng0} and \eqref{eq:euqal_rel}, we have
+\begin{align}
+    \hat{T_{ij}}=  C s_i s _j  \exp(\bm{v}_j \cdot \bm{v}_{i}),
+\end{align}
+where $C$ is a positive constant.
+Eq.~\eqref{eq:flow_w2v_ng0} reveals the connection between the \textit{word2vec} and the gravity model, with with $d_{ij} = - \bm{u}_{j} \cdot \bm{v}_{i}$ and $f(x) = \exp(-x)$.
+In sum, the \textit{word2vec} is a gravity model, in which the population of location $i$ is its frequency in the trajectory data, and the distance between locations is measured by their dot similarities.
+
+We also shows the reverse way of derivation (from gravity model to the \textit{word2vec}).
+In the gravity model, the probability that a person moves from location $i$ to $j$ is given by
+\begin{align}
+    P\left(j \given i \right) = T_{ij} / m_i = C m_j f(d_{ij}). \label{eq:gravity_prob}
+\end{align}
+
+Because, the sum of probabilities should be one,
+\begin{align}
+     & \sum_{j} P(j \given i) = 1 \nonumber                                     \\
+     & \Rightarrow C \sum_{k} m_k f(d_{ik}) = 1 \nonumber                       \\
+     & \Rightarrow C  = 1 / \sum_{k} m_k f(d_{ik}), \label{eq:gravity_constant}
+\end{align}
+which ensures that $\sum_{j} m_j f(d_{ij})$ is constant.
+Substituting \eqref{eq:gravity_constant}  into Eq.~\eqref{eq:gravity_prob} yields a model having the same functional form with the word2vec, \ie
+\begin{align}
+    P\left(j \given i \right) = \frac{m_i f(d_{ij})}{\sum_{k} m_k f(d_{ik})}. \label{eq:gravity_prob2}
+\end{align}
 
@@
 \begin{equation}
-p(j \vert i) = \frac{\exp(\bm{u}_{j} \cdot \bm{v}_{i})}{\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{i})},
+p(j \given i) = \frac{\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:cond_prob_w2v}
 \end{equation}
-where $i =a_{t} $, $ j=a_{t + \tau}$, $\mathcal{A}$ is the entire set of unique locations represented in the data, and  $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively.
+where $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector", respectively,  $Z_i=\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
 We follow the standard practice and only use the in-vector, $v$,  which is known to be superior to the out-vector in link prediction benchmarks~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}.
 
-%% Word2vec parameters and training procedure
+Fitting the Eq.~\ref{eq:cond_prob_w2v} are computationally expensive as its denominator involves a sum over all possible entities in data.
+Commonly, the negative sampling is introduced as a way to avoid computing the denominator.
+The negative sampling is an optimization method widely used for training the machine learning model, which operates as follows.
+For each center--context word pair $(i,j)$, one generates $k$ noise center--context word pairs, denoted by $(i, \ell)$, where context word $\ell$ for the noise pair is sampled from a noise distribution, denoted by $p_{0}(\ell)$.
+Given a center-context word pair, $(i,j)$, as an input, one predicts whether it comes from the original data or noise distribution based on a similarity between two words, \eg dot similarity in case of the \textit{word2vec}.
+
+ Due to the negative sampling, the correct expression optimized with the negative sampling is given by (see Methods:Skip-gram and \textit{word2vec})
+\begin{align}
+    P\left(j \given i \right):= \frac{p_0(j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z'_i},
+\end{align}
+where $Z'_i=\sum_{x \in \mathcal{A}} p_0(x) \exp(\bm{u}_{x} \cdot \bm{v}_{i})$.
+
 We used the \textit{word2vec}  implementation in the python package \texttt{gensim}. 
@@
 We set $\alpha$ to its default value of 0.025 and iterate five times over all training trajectories.
-For scientific mobility, across each training iteration, the order of organizations within a single year is randomized to remove unclear sequential order..
+For scientific mobility, across each training iteration, the order of organizations within a single year is randomized to remove unclear sequential order.
+
+\subsection*{Skip-gram and \textit{word2vec}} 
+\label{sec:sg_and_word2vec}
+Many probability models including the \textit{word2vec} can be represented in form
+\begin{align}
+    f(x) / \sum_{x' \in {\cal X}} f(x'),
+\end{align}
+where $f$ is a nonnegative function. Fitting the probability models are computationally expensive as its denominator involves a sum over all possible entities ${\cal X}$ in data.
+The negative sampling is introduced as a way to avoid computing the denominator.
+The negative sampling solves a synthetic binary classification task, classifying an actual data $x$ and a noise data $\tilde x$ using a sigmoid function
+\begin{align}
+    \label{eq:sigmoid}
+    \frac{1}{1 + \exp\left( -\log f(z) \right)}.
+\end{align}
+Because this sigmoid function does not involve the normalization constant, the model fitting can be done with less computational burden.
+Besides , this has a side effect: the negative sampling has a bias and hence does not correctly train the model \cite{Dyer2014}.
+The bias can be corrected using the noise contrastive estimation (NCE) \cite{Chia2010}, which solves the
+same classification task but with a bias-corrected sigmoid function, \ie
+\begin{align}
+    \label{eq:sigmoid2}
+    \frac{1}{1 + \exp\left( -\log f(z) + \log p_0(z) \right)}.
+\end{align}
+Note that Eq.~\eqref{eq:sigmoid2} has an additional term $\log p_0(z)$, which is the log-probability of $z$ for a noise distribution.
+
+If the bias is not corrected, what model does the negative sampling actually fit? We rewrite the sigmoid function (Eq.~\eqref{eq:sigmoid}) in form of the bias-corrected sigmoid function, \ie
+\begin{align}
+    \label{eq:sigmoid3}
+    \frac{1}{1 + \exp\left[ - \log \tilde f(z) + \log p_0(z)  \right]},
+\end{align}
+where we have defined
+\begin{align}
+    \label{eq:unnormalized}
+    \tilde f(z) = f(z) p_0(z).
+\end{align}
+This sigmoid function correctly fits a probability model:
+\begin{align}
+    f'(x) / \sum_{x' \in {\cal X}} f'(x),
+\end{align}
+or, by substituting Eq.~\eqref{eq:unnormalized},
+\begin{align}
+    p_0(x)f(x) / \sum_{x' \in {\cal X}} p_0(x')f(x').
+\end{align}
+
+For the \textit{word2vec}, the correct expression optimized with the negative sampling is given by
+\begin{align}
+    P\left(j \given i \right):= \frac{p_0(j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z'_i}.
+\end{align}
+where $Z'_i=\sum_{x \in \mathcal{A}} p_0(x) \exp(\bm{u}_{x} \cdot \bm{v}_{i})$.
 
@@
 $f(r_{ij})$ is a decay function of distance $r_{ij}$ between locations $i$ and $j$. 
+Here, we used the most basic gravity model which assumes symmetry of the flow $\hat{T_{ij}} =\hat{T_{ji}}$ and distance $r_{ij} = r_{ji}$, while there are four proposed variants \autocite{wilson2011entropy}.
 There are two popular forms for the $f(r_{ij})$:

### 2021-01-21 paper/current/main.tex
math section: sk

@@
-\documentclass[12pt]{article} %{{{
+\documentclass[draft,12pt]{article} %{{{
 
@@
 \def\js#1{ {\color{red}\textbf{js: #1}} }
+\def\sk#1{ {\color{red}\textbf{sk: #1}} }
 
@@
 
-\subsection*{Mathematical connection between neural embedding model and gravity model}
+\subsection*{word2vec and gravity model}
 
-Our results show that the neural embedding better explains a wide range of mobilities than conventional embedding methods, which prompts us to ask: why does the \textit{word2vec} work well for the mobility data?
-We show that the \textit{word2vec} is tied to a gravity model, a widespread and long-standing model that well explains human mobility.
+Why does the embedding distance better predicts actual mobility flows than the geographic distance?
+One plausible explanation is that an embedding is constructed based on mobility flows, making embedding distance useful for prediction.
+However, there remains a question of why the embedding generated by the {\it word2vec} explains the flow exceptionally well.
+We show that the {\it word2vec} can be translated into a gravity model, with mass and locations estimated from location trajectories.
+It is this connection that gives rise to the {\it word2vec}'s exceptional ability to predict the flow.
 
-Let us approach the connection by initially focusing on the gravity model.
-Suppose that flow of people between $N$ locations. The gravity model models the expected flow $\hat{T_{ij}}$ from location $i$ to $j$ by
+Let us approach the question by initially focusing on how the {\it word2vec} generates the embedding.
+The {\it word2vec} takes a location trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), as an input.
+A location $a_t=i$ is considered to have a context location $a_{t'}=j$ that appears in its succeeding and proceeding $w$ locations in the trajectory, \ie  $j \in [a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}]$.
+The {\it word2vec} learns an embedding by estimating a probability that location $i$ has context $j$ by
 \begin{align}
-    \hat{T_{ij}} = C m_i m_j f(r_{ij}), \label{eq:gravity_model}
+	P\left(j \given i \right):= \frac{\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:prob_w2v_ng}
 \end{align}
-where $m_i$ is the population of locations of $i$, $r_{ij}$ is their distance, $f$ is a decreasing function of $r_{ij}$, and $C$ is a constant.
-%In the following, we refer to a measure of dissimilarity as a distance for brevity.
-%In gravity model, the flow is symmetric, \ie $\hat{T_{ij}}=\hat{T_{ji}}$, which ensures the stationarity in population $m_{i}$.
+where denominator $Z_i=\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
+Although the {\it word2vec} generates two embedding vectors $\bm{v_i}$ and $\bm{u}_i$---which are referred to as in-vector and out-vector, respectively, many studies, as well as our experiments, adopt in-vector $\bm{v}_i$ as an embedding of location $i$.
 
-%Now, let us move our focus to the \textit{word2vec}.
-The skip-gram negative sampling \textit{word2vec} takes a sequence of locations and models the co-occurrence of center location $i$ and context location $j$ by (See Methods)
-\begin{align}
-    P\left(j \given i \right):= \frac{p_0(j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z'_i}, \label{eq:prob_w2v_ng0}
-\end{align}
-where $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector", respectively,  $Z'_i=\sum_{x \in \mathcal{A}} p_0(x) \exp(\bm{u}_{x} \cdot \bm{v}_{i})$  is a normalization constant, and $\mathcal{A}$ is the set of all locations, and a noise distribution given by $p_{0}(j) = s^{\gamma} _j / \sum_{\ell'} s^{\gamma}_{\ell'}$, where $\gamma$ is a free parameter typically set to $3/4$ or $1$.
-Under restricting window size to be one, the expected flow between center location $i$ and context location $j$ is given by
+Our results show that the {\it word2vec} best explains the mobility flow across different datasets when $w=1$, with the flow is predicted by
 \begin{align}
 	\label{eq:flow_w2v}
-    \hat{T_{ij}}=s_i P(j\given i) = \frac{s_i\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z'_i},
+	\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
 \end{align}
-where $s_i$ is the frequency of location $i$ summed for all trajectories in the dataset.
+where $P(i)$ is the probability that location $i$ appears in the trajectory.
+Apparently, there is no direct correspondence between the flow predicted by the {\it word2vec} and gravity model (Eq.~\eqref{eq:gravity_basic}).
+The gap between the two models, however, can be filled by taking into account the effect of how the {\it word2vec} is trained.
 
-Parameter $\gamma=1$ is a special choice that ensures that the in-vector and out-vector are the same, \ie $\bm{u}_i = \bm{v}_i$ \autocite{levy2014neural}.
-Setting $\gamma = 1$, and substituting $\bm{u}_i = \bm{v}_j$ and $p_0(j) = s_j / \sum_{\ell'} s_{\ell'}$ into Eq~\eqref{eq:flow_w2v_ng0}, we have
+A widespread training method for the {\it word2vec} is the {\it negative sampling} \cite{mikolov2013word2vec}.
+The negative sampling finds the embedding vectors by solving a binary classification task, in which one is given a center-context location pair $(i, j)$ and classifies whether the pair comes from the data or an artificially generated ``fake'' data.
+The fake pair $(i,j)$ is sampled based on the power $\gamma$ of the frequency of $j$, \ie $P^\gamma(j)$, where $\gamma$ is a parameter.
+%typically sets to $\gamma=3/4$ or $\gamma = 1$.
+
+The negative sampling does not fit the \textit{word2vec} directly to the data but indirectly through the synthetic classification task.
+This has a side effect: the negative sampling has a bias and maximizes a different objective function~\autocite{Gutmann2010}.
+When taking into account the bias, the {\it word2vec} with the negative sampling fits a probabiliy model given by
 \begin{align}
-    P\left(j \given i \right) & := \frac{ p_0 (j) \exp(\bm{v}_j \cdot \bm{v}_{i})}{ Z'_i}                      \\
-                              & =  \frac{s _j  \exp(\bm{v}_j \cdot \bm{v}_{i})}{ Z' _i\sum_{\ell'} s_{\ell'}},
+	P\left(j \given i \right):= \frac{P^ \gamma(j) \exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:prob_w2v_ng0}
 \end{align}
-which leads to the expected flow for the word2vec model, \ie
+where we have redefined the normalization constant, \ie $Z_i=\sum_{x \in \mathcal{A}} P^ \gamma (j) \exp(\bm{u}_{x} \cdot \bm{v}_{i})$. (See Skip-gram and word2vecc section for the full calculation).
+
+Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists  optimial in-vectors and out-vectors such that $\bm{u}_i = \bm{v}_i$ \autocite{levy2014neural}.
+Setting $\gamma = 1$ and substituting $\bm{u}_i = \bm{v}_j$ into Eq.~\eqref{eq:prob_w2v_ng0}, the flow predicted by the {\it word2vec} is given by
 \begin{align}
-    \hat{T_{ij}}=s_i P(j\given i) =  \frac{s_i s _j  \exp(\bm{v}_j \cdot \bm{v}_{i})}{  Z'_i\sum_{\ell'} s_{\ell'}}. \label{eq:flow_w2v_ng0}
+	\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)P(j)\exp(\bm{v}_j \cdot \bm{v}_{i})}{Z_i}. \label{eq:flow_w2v_ng1}
 \end{align}
+The flow $\hat{T_{ij}}$ is symmetric (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because the model neglects whether the context $j$ appears later or earlier from center $i$.
+In the righ-hand side of Eq.~\eqref{eq:flow_w2v_ng1}, the numerator remains the same even if we swap center and context locations $i$ and $j$.
+Thus, to ensure the symmetry $T_{ij} = T_{ji}$, the denominator $Z_i$ should be a constant.
 
-In the \textit{word2vec}, the flow $\hat{T_{ij}}$ is symmetric by design (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because the model neglects whether the context $j$ appears later or earlier from center $i$.
-Then, we have
+Taken altogether, the {\it word2vec} with the negative sampling predicts a flow in the same form as in the gravity model:
 \begin{align}
-    T_{ij} = T_{ji}
-     & \Rightarrow
-    \frac{s_i s _j  \exp(\bm{v}_j \cdot \bm{v}_{i})}{  Z'_i\sum_{\ell'} s_{\ell'}} =  \frac{s_j s _i  \exp(\bm{v}_i \cdot \bm{v}_{j})}{  Z'_j\sum_{\ell'} s_{\ell'}} \\
-     & \Rightarrow
-    Z'_i = Z'_j, \label{eq:euqal_rel}
-\end{align}
-suggesting that the normalization constant $Z' _i$ is constant.
-Combining Eqs.~\eqref{eq:flow_w2v_ng0} and \eqref{eq:euqal_rel}, we have
-\begin{align}
-    \hat{T_{ij}}=  C s_i s _j  \exp(\bm{v}_j \cdot \bm{v}_{i}),
+	\hat{T_{ij}}=  C P(i) P(j)  \exp(\bm{v}_j \cdot \bm{v}_{i}), \label{eq:flow_w2v_ng0}
 \end{align}
 where $C$ is a positive constant.
-Eq.~\eqref{eq:flow_w2v_ng0} reveals the connection between the \textit{word2vec} and the gravity model, with with $d_{ij} = - \bm{u}_{j} \cdot \bm{v}_{i}$ and $f(x) = \exp(-x)$.
-In sum, the \textit{word2vec} is a gravity model, in which the population of location $i$ is its frequency in the trajectory data, and the distance between locations is measured by their dot similarities.
-
-We also shows the reverse way of derivation (from gravity model to the \textit{word2vec}).
-In the gravity model, the probability that a person moves from location $i$ to $j$ is given by
-\begin{align}
-    P\left(j \given i \right) = T_{ij} / m_i = C m_j f(d_{ij}). \label{eq:gravity_prob}
-\end{align}
-
-Because, the sum of probabilities should be one,
-\begin{align}
-     & \sum_{j} P(j \given i) = 1 \nonumber                                     \\
-     & \Rightarrow C \sum_{k} m_k f(d_{ik}) = 1 \nonumber                       \\
-     & \Rightarrow C  = 1 / \sum_{k} m_k f(d_{ik}), \label{eq:gravity_constant}
-\end{align}
-which ensures that $\sum_{j} m_j f(d_{ij})$ is constant.
-Substituting \eqref{eq:gravity_constant}  into Eq.~\eqref{eq:gravity_prob} yields a model having the same functional form with the word2vec, \ie
-\begin{align}
-    P\left(j \given i \right) = \frac{m_i f(d_{ij})}{\sum_{k} m_k f(d_{ik})}. \label{eq:gravity_prob2}
-\end{align}
+In other words, the \textit{word2vec} is a gravity model, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
+While the gravity model generates the flow from the given mass and locations, the {\it word2vec} finds the mass and locations that best explain the given trajectories.
+Therefore, the embedding distance is inherently tied to the flow, and hence, has greater predictive power than the geographic distance.
 

### 2021-01-21 paper/current/main.tex
minor edit
reflect YY's comment and edit

@@
 	As understanding mobility is becoming critical for contemporary society, finding frameworks that can capture this complexity is of paramount importance.
-	Here, we show the  mathematical  connection  between  neural embedding models and the gravity model of human mobility and, using three distinct human trajectory datasets, demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
+	Here, we show the  mathematical  connection  between  neural embedding models ~\autocite{mikolov2013word2vec} and the gravity model of human mobility and, using three distinct human trajectory datasets, demonstrate that a neural embedding model can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
 	Focusing on the case of scientific mobility, we show that embeddings of scientific organizations uncover cultural and linguistic relations, and even academic prestige, at multiple levels of granularity.
@@
 
-Why does the embedding distance better predicts actual mobility flows than the geographic distance?
-One plausible explanation is that an embedding is constructed based on mobility flows, making embedding distance useful for prediction.
-However, there remains a question of why the embedding generated by the {\it word2vec} explains the flow exceptionally well.
-We show that the {\it word2vec} can be translated into a gravity model, with mass and locations estimated from location trajectories.
-It is this connection that gives rise to the {\it word2vec}'s exceptional ability to predict the flow.
+Why does the embedding distance predict actual mobility flows better than the geographic distance?
+Here, we show that the objective function of {\it word2vec} is equivalent to the gravity model.
 
-Let us approach the question by initially focusing on how the {\it word2vec} generates the embedding.
 The {\it word2vec} takes a location trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), as an input.
-A location $a_t=i$ is considered to have a context location $a_{t'}=j$ that appears in its succeeding and proceeding $w$ locations in the trajectory, \ie  $j \in [a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}]$.
-The {\it word2vec} learns an embedding by estimating a probability that location $i$ has context $j$ by
+A location $a_t=i$ is considered to have a context location $a_{t'}=j$ that appears in its succeeding or proceeding $w$ locations in the trajectory, \ie  $j \in [a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}]$.
+The {\it word2vec} learns an embedding by estimating a probability that location $i$ has context $j$:
 \begin{align}
@@
 \end{align}
-where denominator $Z_i=\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
+where denominator $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
 Although the {\it word2vec} generates two embedding vectors $\bm{v_i}$ and $\bm{u}_i$---which are referred to as in-vector and out-vector, respectively, many studies, as well as our experiments, adopt in-vector $\bm{v}_i$ as an embedding of location $i$.
 
-Our results show that the {\it word2vec} best explains the mobility flow across different datasets when $w=1$, with the flow is predicted by
+Our results show that the {\it word2vec} best explains the mobility flow across different datasets when $w=1$, with the flow predicted by
 \begin{align}
@@
 where $P(i)$ is the probability that location $i$ appears in the trajectory.
-Apparently, there is no direct correspondence between the flow predicted by the {\it word2vec} and gravity model (Eq.~\eqref{eq:gravity_basic}).
-The gap between the two models, however, can be filled by taking into account the effect of how the {\it word2vec} is trained.
+Because computing $Z_i$ is computationally demanding, multiple approximation methods have been proposed with the most  popular being the negative sampling~\autocite{mikolov2013word2vec}.
 
-A widespread training method for the {\it word2vec} is the {\it negative sampling} \cite{mikolov2013word2vec}.
-The negative sampling finds the embedding vectors by solving a binary classification task, in which one is given a center-context location pair $(i, j)$ and classifies whether the pair comes from the data or an artificially generated ``fake'' data.
-The fake pair $(i,j)$ is sampled based on the power $\gamma$ of the frequency of $j$, \ie $P^\gamma(j)$, where $\gamma$ is a parameter.
-%typically sets to $\gamma=3/4$ or $\gamma = 1$.
+The negative sampling finds the embedding vectors by solving a binary classification task, in which one is given a center-context location pair $(i, j)$ and classifies whether the pair comes from the data or an artificially generated ``negative'' samples.
+The negative pair $(i,j)$ is sampled proportional to $P^\gamma(j)$ with parameter $\gamma \geq 0$.
 
-The negative sampling does not fit the \textit{word2vec} directly to the data but indirectly through the synthetic classification task.
-This has a side effect: the negative sampling has a bias and maximizes a different objective function~\autocite{Gutmann2010}.
+As a heuristic, the negative sampling has a bias and maximizes a different objective function~\autocite{Gutmann2010}.
 When taking into account the bias, the {\it word2vec} with the negative sampling fits a probabiliy model given by
@@
 \end{align}
-where we have redefined the normalization constant, \ie $Z_i=\sum_{x \in \mathcal{A}} P^ \gamma (j) \exp(\bm{u}_{x} \cdot \bm{v}_{i})$. (See Skip-gram and word2vecc section for the full calculation).
+where we have redefined the normalization constant, \ie $Z_i=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$. (See Methods section for the full calculation).
 
@@
 \end{align}
-The flow $\hat{T_{ij}}$ is symmetric (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because the model neglects whether the context $j$ appears later or earlier from center $i$.
-In the righ-hand side of Eq.~\eqref{eq:flow_w2v_ng1}, the numerator remains the same even if we swap center and context locations $i$ and $j$.
-Thus, to ensure the symmetry $T_{ij} = T_{ji}$, the denominator $Z_i$ should be a constant.
+The flow $\hat{T_{ij}}$ is symmetric (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because the {\it word2vec} neglects whether the context $j$ appears later or earlier from center $i$.
+If we swap $i$ and $j$ in Eq.~\eqref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
+Therefore, to ensure $T_{ij} = T_{ji}$, the denominator $Z_i$ should be a constant.
 
-Taken altogether, the {\it word2vec} with the negative sampling predicts a flow in the same form as in the gravity model:
+Taken altogether, the {\it word2ve}c with the negative sampling predicts a flow in the same form as in the gravity model:
 \begin{align}
@@
 where $C$ is a positive constant.
-In other words, the \textit{word2vec} is a gravity model, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
+In other words, the \emph{word2vec with the negative sampling is a gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
 While the gravity model generates the flow from the given mass and locations, the {\it word2vec} finds the mass and locations that best explain the given trajectories.

### 2021-01-21 paper/current/main.tex
first edit in the Methods

@@
 
-Due to the negative sampling, the correct expression optimized with the negative sampling is given by (see Methods:Skip-gram and \textit{word2vec})
+Due to the negative sampling, the correct expression optimized with the negative sampling is given by
 \begin{align}
-	P\left(j \given i \right):= \frac{p_0(j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z'_i},
+	P\left(j \given i \right):= \frac{P(j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
 \end{align}
-where $Z'_i=\sum_{x \in \mathcal{A}} p_0(x) \exp(\bm{u}_{x} \cdot \bm{v}_{i})$.
+where $Z_i=\sum_{j' \in \mathcal{A}} P(j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
 
@@
 \label{sec:sg_and_word2vec}
-Many probability models including the \textit{word2vec} can be represented in form
+
+The \textit{word2vec} takes a form
 \begin{align}
-	f(x) / \sum_{x' \in {\cal X}} f(x'),
+	\frac{ f(\bm{u}_{j'}, \bm{v}_i) }{ \sum_{j' \in {\cal A}} f(\bm{u}_{j'}, \bm{v}_i)},
 \end{align}
-where $f$ is a nonnegative function. Fitting the probability models are computationally expensive as its denominator involves a sum over all possible entities ${\cal X}$ in data.
-The negative sampling is introduced as a way to avoid computing the denominator.
-The negative sampling solves a synthetic binary classification task, classifying an actual data $x$ and a noise data $\tilde x$ using a sigmoid function
+where $f$ is a nonnegative function.
+Fitting the probability model is computationally expensive as its denominator involves a sum over all possible entities ${\cal A}$ in data.
+To circumvent this problem, the negative sampling solves a binary classification task,
+in which one is given an instance $z$ and asked whether $z$ is sampled from an actual data $x$ or a noise data $\tilde x$,
 \begin{align}
@@
 Because this sigmoid function does not involve the normalization constant, the model fitting can be done with less computational burden.
-Besides , this has a side effect: the negative sampling has a bias and hence does not correctly train the model \cite{Dyer2014}.
+Besides, this has a side effect: the negative sampling has a bias and hence does not correctly train the model \cite{Dyer2014}.
 The bias can be corrected using the noise contrastive estimation (NCE) \cite{Chia2010}, which solves the

### 2021-01-22 paper/current/main.tex
edit the Method section

@@
 \end{equation}
-where $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector", respectively,  $Z_i=\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
-We follow the standard practice and only use the in-vector, $v$,  which is known to be superior to the out-vector in link prediction benchmarks~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}.
-
-Fitting the Eq.~\ref{eq:cond_prob_w2v} are computationally expensive as its denominator involves a sum over all possible entities in data.
-Commonly, the negative sampling is introduced as a way to avoid computing the denominator.
-The negative sampling is an optimization method widely used for training the machine learning model, which operates as follows.
-For each center--context word pair $(i,j)$, one generates $k$ noise center--context word pairs, denoted by $(i, \ell)$, where context word $\ell$ for the noise pair is sampled from a noise distribution, denoted by $p_{0}(\ell)$.
-Given a center-context word pair, $(i,j)$, as an input, one predicts whether it comes from the original data or noise distribution based on a similarity between two words, \eg dot similarity in case of the \textit{word2vec}.
-
-Due to the negative sampling, the correct expression optimized with the negative sampling is given by
-\begin{align}
-	P\left(j \given i \right):= \frac{P(j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
-\end{align}
-where $Z_i=\sum_{j' \in \mathcal{A}} P(j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
+where $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector", respectively,  $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
+We follow the standard practice and only use the in-vector, $\bm{v}$,  which is known to be superior to the out-vector in link prediction benchmarks~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}.
 
@@
 
-\subsection*{Skip-gram and \textit{word2vec}}
+\subsection*{An implicit bias in the negative sampling}
 \label{sec:sg_and_word2vec}
 
-The \textit{word2vec} takes a form
-\begin{align}
-	\frac{ f(\bm{u}_{j'}, \bm{v}_i) }{ \sum_{j' \in {\cal A}} f(\bm{u}_{j'}, \bm{v}_i)},
-\end{align}
-where $f$ is a nonnegative function.
-Fitting the probability model is computationally expensive as its denominator involves a sum over all possible entities ${\cal A}$ in data.
-To circumvent this problem, the negative sampling solves a binary classification task,
-in which one is given an instance $z$ and asked whether $z$ is sampled from an actual data $x$ or a noise data $\tilde x$,
+The negative sampling is a biased estimator~\autocite{Chia2010,Dyer2014} that optimizes a model different from the {\it word2vec}.
+What is the correct model for the word2vec with the negative sampling?
+
+The negative sampling trains the word2vec by a binary classification task as follows.
+One samples a center-context word pair $(i,j)$ from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$.
+The negative context $\ell$ is sampled from noise distribution $p_0(\ell)=P^\gamma(\ell)$, where $P(j)$ is the
+fraction of $j$ in the given data, and $\gamma>0$ is a parameter.
+Then, given a center-context word pair $(i,j)$, one predicts whether it is a positive or negative sample using sigmoid function:
 \begin{align}
 	\label{eq:sigmoid}
-	\frac{1}{1 + \exp\left( -\log f(z) \right)}.
+	\frac{1}{1 + \exp\left( - \bm{u}_j \cdot \bm{v}_i \right)}.
 \end{align}
-Because this sigmoid function does not involve the normalization constant, the model fitting can be done with less computational burden.
-Besides, this has a side effect: the negative sampling has a bias and hence does not correctly train the model \cite{Dyer2014}.
-The bias can be corrected using the noise contrastive estimation (NCE) \cite{Chia2010}, which solves the
-same classification task but with a bias-corrected sigmoid function, \ie
+
+The negative sampling does not guaranteed that, even if one increases the number of training samples and iterations, the embedding is not guaranteed to converge to the optimial one~\autocite{Chia2010,Dyer2014}.
+This inconsistency problem is addressed by the noise contrastive estimation (NCE) \autocite{Chia2010}, which fits a probability model in form:
+\begin{align}
+	\label{eq:nce}
+	f(x) / \sum_{x'} f(x'),
+\end{align}
+where $f(x)$ is the unnormalized probability for an instance $x$.
+As is the case for the negative sampling, the NCE fits the model based on a binary classification task, with positive and negative samples randomly drawn from the given data and a noise distribution $p_0$, respectively, using a bias-corrected sigmoid function, \ie
 \begin{align}
 	\label{eq:sigmoid2}
-	\frac{1}{1 + \exp\left( -\log f(z) + \log p_0(z) \right)}.
+	\frac{1}{1 + \exp\left( -f(x) + \log p_0(x) \right)}.
 \end{align}
-Note that Eq.~\eqref{eq:sigmoid2} has an additional term $\log p_0(z)$, which is the log-probability of $z$ for a noise distribution.
+In case of the word2vec, the instance is the dot similarity $x=\bm{u}_i \cdot \bm{v}_j$,  $f(x)=\exp(x)$, and $p_0(j)=P^\gamma(j)$.
 
-If the bias is not corrected, what model does the negative sampling actually fit? We rewrite the sigmoid function (Eq.~\eqref{eq:sigmoid}) in form of the bias-corrected sigmoid function, \ie
+Rewriting the sigmoid function for the negative sampling (Eq.~\eqref{eq:sigmoid}) in form of the bias-corrected sigmoid function yields
 \begin{align}
 	\label{eq:sigmoid3}
-	\frac{1}{1 + \exp\left[ - \log \tilde f(z) + \log p_0(z)  \right]},
+	\frac{1}{1 + \exp\left[ - \tilde f(x) + \log p_0(x)  \right]},
 \end{align}
@@
 	\label{eq:unnormalized}
-	\tilde f(z) = f(z) p_0(z).
+	\tilde f(x) = f(x) p_0(x).
 \end{align}
-This sigmoid function correctly fits a probability model:
+This bias-corrected sigmoid function fits a probability model:
 \begin{align}
-	f'(x) / \sum_{x' \in {\cal X}} f'(x),
+	f'(x) / \sum_{x'} f'(x),
 \end{align}
-or, by substituting Eq.~\eqref{eq:unnormalized},
+or, by substituting $x=\bm{u}_i \cdot \bm{v}_j$, $f(x)=\exp(x)$, and $p_0(j)=P^\gamma (j)$,
 \begin{align}
-	p_0(x)f(x) / \sum_{x' \in {\cal X}} p_0(x')f(x').
+	P\left(j \given i \right):= \frac{P^\gamma (j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}.
 \end{align}
-
-For the \textit{word2vec}, the correct expression optimized with the negative sampling is given by
-\begin{align}
-	P\left(j \given i \right):= \frac{p_0(j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z'_i}.
-\end{align}
-where $Z'_i=\sum_{x \in \mathcal{A}} p_0(x) \exp(\bm{u}_{x} \cdot \bm{v}_{i})$.
+where $Z_i=\sum_{j' \in \mathcal{A}} P^\gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
 

### 2021-01-22 paper/current/main.tex
minor correction

@@
 The negative sampling is a biased estimator~\autocite{Chia2010,Dyer2014} that optimizes a model different from the {\it word2vec}.
-What is the correct model for the word2vec with the negative sampling?
+What is the different model?
 
 The negative sampling trains the word2vec by a binary classification task as follows.
-One samples a center-context word pair $(i,j)$ from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$.
-The negative context $\ell$ is sampled from noise distribution $p_0(\ell)=P^\gamma(\ell)$, where $P(j)$ is the
-fraction of $j$ in the given data, and $\gamma>0$ is a parameter.
+One samples a center-context word pair $(i,j)$ from the given data as a positive pair, and sample $k$ negative pairs $(i,\ell)$ from noise distribution $p_0(\ell)=P^\gamma(\ell)$.
+(Remind that $P(j)$ is the
+fraction of $j$ in the given data, and $\gamma>0$ is a parameter).
 Then, given a center-context word pair $(i,j)$, one predicts whether it is a positive or negative sample using sigmoid function:
@@
 
-The negative sampling does not guaranteed that, even if one increases the number of training samples and iterations, the embedding is not guaranteed to converge to the optimial one~\autocite{Chia2010,Dyer2014}.
+The negative sampling does not guarantee that the embedding converges to the optimal one, even if one increases the number of training samples and iterations~\autocite{Chia2010,Dyer2014}.
 This inconsistency problem is addressed by the noise contrastive estimation (NCE) \autocite{Chia2010}, which fits a probability model in form:
@@
 \begin{align}
-	P\left(j \given i \right):= \frac{P^\gamma (j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}.
+	P\left(j \given i \right):= \frac{P^\gamma (j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
 \end{align}

### 2021-01-22 paper/current/main.tex
small edits to abstract & intro

@@
 	As understanding mobility is becoming critical for contemporary society, finding frameworks that can capture this complexity is of paramount importance.
-	Here, we show the  mathematical  connection  between  neural embedding models ~\autocite{mikolov2013word2vec} and the gravity model of human mobility and, using three distinct human trajectory datasets, demonstrate that a neural embedding model can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
+	Here, we illustrate a mathematical connection between neural embedding models ~\autocite{mikolov2013word2vec} and the gravity model of human mobility and, using three distinct human trajectory datasets, demonstrate that a neural embedding model can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
 	Focusing on the case of scientific mobility, we show that embeddings of scientific organizations uncover cultural and linguistic relations, and even academic prestige, at multiple levels of granularity.
@@
 The question is surprisingly hard to answer when it involves human mobility.
-Although geographic distance has been constraining human movements throughout history, it is becoming less relevant in a world connected by rapid transit and global airline networks.
+Although geographic distance has historically constrained human movements, it is becoming less relevant in a world connected by rapid transit and global airline networks.
 For instance, a person living in Australia is more likely to migrate to the United Kingdom, a far-away country with similar language and culture, than to a much closer country such as Indonesia~\autocite{pew2018migration}.

### 2021-01-22 paper/current/main.tex
edits to new math section

@@
 	As understanding mobility is becoming critical for contemporary society, finding frameworks that can capture this complexity is of paramount importance.
-	Here, we illustrate a mathematical connection between neural embedding models ~\autocite{mikolov2013word2vec} and the gravity model of human mobility and, using three distinct human trajectory datasets, demonstrate that a neural embedding model can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
+	Here, we illustrate a mathematical connection between the neural embedding model \textit{word2ec}~\autocite{mikolov2013word2vec} and the gravity model of mobility and, using three distinct human trajectory datasets, demonstrate that a neural embedding model can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
 	Focusing on the case of scientific mobility, we show that embeddings of scientific organizations uncover cultural and linguistic relations, and even academic prestige, at multiple levels of granularity.
@@
 
-The {\it word2vec} takes a location trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), as an input.
+The {\it word2vec} model takes a location trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), as an input.
 A location $a_t=i$ is considered to have a context location $a_{t'}=j$ that appears in its succeeding or proceeding $w$ locations in the trajectory, \ie  $j \in [a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}]$.
-The {\it word2vec} learns an embedding by estimating a probability that location $i$ has context $j$:
+ {\it Word2vec} learns an embedding by estimating the probability that location $i$ has context $j$:
 \begin{align}
@@
 \end{align}
-where denominator $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
-Although the {\it word2vec} generates two embedding vectors $\bm{v_i}$ and $\bm{u}_i$---which are referred to as in-vector and out-vector, respectively, many studies, as well as our experiments, adopt in-vector $\bm{v}_i$ as an embedding of location $i$.
+where the denominator $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
+Although {\it word2vec} generates two embedding vectors $\bm{v_i}$ and $\bm{u}_i$---which are referred to as the in-vector and out-vector, respectively, we follow many studies by adopting the in-vector $\bm{v}_i$ as an embedding of location $i$.
 
-Our results show that the {\it word2vec} best explains the mobility flow across different datasets when $w=1$, with the flow predicted by
+Our experiments show that {\it word2vec} best explains real-world mobility flow when $w=1$ (Fig.~\ref{fig:supp:hyperparams}), with the flow predicted by
 \begin{align}
@@
 where $P(i)$ is the probability that location $i$ appears in the trajectory.
-Because computing $Z_i$ is computationally demanding, multiple approximation methods have been proposed with the most  popular being the negative sampling~\autocite{mikolov2013word2vec}.
-
-The negative sampling finds the embedding vectors by solving a binary classification task, in which one is given a center-context location pair $(i, j)$ and classifies whether the pair comes from the data or an artificially generated ``negative'' samples.
-The negative pair $(i,j)$ is sampled proportional to $P^\gamma(j)$ with parameter $\gamma \geq 0$.
+Because computing $Z_i$ is computationally demanding, multiple approximation methods have been proposed, the most  popular being negative sampling~\autocite{mikolov2013word2vec}. 
+Negative sampling finds the embedding vectors by solving a binary classification task, in which the model classifies whether a given center-context location pair $(i, j)$ comes from the data or artificially generated ``negative'' samples.
+The negative pair $(i,j)$ is sampled in proportion to $P^\gamma(j)$ with parameter $\gamma \geq 0$.
 
 As a heuristic, the negative sampling has a bias and maximizes a different objective function~\autocite{Gutmann2010}.
-When taking into account the bias, the {\it word2vec} with the negative sampling fits a probabiliy model given by
+When taking into account this bias, {\it word2vec} with the negative sampling fits a probability model given by
 \begin{align}
@@
 \end{align}
-where we have redefined the normalization constant, \ie $Z_i=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$. (See Methods section for the full calculation).
+where we redefine the normalization constant as $Z_i=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$. (See Methods section for the full calculation).
 
 Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimial in-vectors and out-vectors such that $\bm{u}_i = \bm{v}_i$ \autocite{levy2014neural}.
-Setting $\gamma = 1$ and substituting $\bm{u}_i = \bm{v}_j$ into Eq.~\eqref{eq:prob_w2v_ng0}, the flow predicted by the {\it word2vec} is given by
+Setting $\gamma = 1$ and substituting $\bm{u}_i = \bm{v}_j$ into Eq.~\eqref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
 \begin{align}
@@
 \end{align}
-The flow $\hat{T_{ij}}$ is symmetric (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because the {\it word2vec} neglects whether the context $j$ appears later or earlier from center $i$.
+The flow $\hat{T_{ij}}$ is symmetric (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because {\it word2vec} neglects whether the context $j$ appears before or after the center $i$ in the trajectory.
 If we swap $i$ and $j$ in Eq.~\eqref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
@@
 
-Taken altogether, the {\it word2ve}c with the negative sampling predicts a flow in the same form as in the gravity model:
+Taken altogether, the {\it word2vec} model with the negative sampling predicts a flow in the same form as in the gravity model:
 \begin{align}
@@
 where $C$ is a positive constant.
-In other words, the \emph{word2vec with the negative sampling is a gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
-While the gravity model generates the flow from the given mass and locations, the {\it word2vec} finds the mass and locations that best explain the given trajectories.
+In other words, \emph{word2vec with the negative sampling is a gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
+While the gravity model generates the flow from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given trajectories.
 Therefore, the embedding distance is inherently tied to the flow, and hence, has greater predictive power than the geographic distance.
@@
 
-In the remainder of the paper, we focus on scientific mobility, leveraging its richness to investigate how the geometric space generated by the neural embedding method sheds light on the multi-faceted relationships between organizations.
+In the remainder of the paper, we focus on scientific mobility and interrogate the geometric space generated by the neural embedding to sheds light on the multi-faceted relationships between organizations.
 To explore the topological structure of the embedding, we use a topology-based dimensionality reduction method (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation of the embedding space (Fig.~\ref{fig:projection}a).

### 2021-01-22 paper/current/main.tex
edits to methods new math

@@
 
-The negative sampling is a biased estimator~\autocite{Chia2010,Dyer2014} that optimizes a model different from the {\it word2vec}.
+Negative sampling is a biased estimator~\autocite{Chia2010,Dyer2014} that optimizes a distinct model  from {\it word2vec}.
 What is the different model?
 
-The negative sampling trains the word2vec by a binary classification task as follows.
-One samples a center-context word pair $(i,j)$ from the given data as a positive pair, and sample $k$ negative pairs $(i,\ell)$ from noise distribution $p_0(\ell)=P^\gamma(\ell)$.
-(Remind that $P(j)$ is the
-fraction of $j$ in the given data, and $\gamma>0$ is a parameter).
-Then, given a center-context word pair $(i,j)$, one predicts whether it is a positive or negative sample using sigmoid function:
+Negative sampling trains {\oit word2vec} using a binary classification task as follows.
+A center-context word pair $(i,j)$ is sampled from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$ are sampled from a noise distribution $p_0(\ell)=P^\gamma(\ell)$.
+($P(j)$ is the fraction of $j$ in the data, and $\gamma>0$ is a parameter).
+Then, given a center-context word pair $(i,j)$, the model predicts whether it is a positive or negative sample using sigmoid function:
 \begin{align}
@@
 
-The negative sampling does not guarantee that the embedding converges to the optimal one, even if one increases the number of training samples and iterations~\autocite{Chia2010,Dyer2014}.
-This inconsistency problem is addressed by the noise contrastive estimation (NCE) \autocite{Chia2010}, which fits a probability model in form:
+This procedure does not guarantee that the embedding optimally converges, even when increasing the training samples and iterations~\autocite{Chia 2010,Dyer2014}.
+This problem is addressed by the noise contrastive estimation (NCE) \autocite{Chia2010}, which fits a probability model in the form:
 \begin{align}
@@
 where $f(x)$ is the unnormalized probability for an instance $x$.
-As is the case for the negative sampling, the NCE fits the model based on a binary classification task, with positive and negative samples randomly drawn from the given data and a noise distribution $p_0$, respectively, using a bias-corrected sigmoid function, \ie
+As in negative sampling, NCE fits the model based on a binary classification task, with positive and negative samples randomly drawn from the given data and a noise distribution $p_0$, respectively, using a bias-corrected sigmoid function:
 \begin{align}
@@
 \end{align}
-In case of the word2vec, the instance is the dot similarity $x=\bm{u}_i \cdot \bm{v}_j$,  $f(x)=\exp(x)$, and $p_0(j)=P^\gamma(j)$.
+In case of the {\it word2vec}, the instance is the dot similarity $x=\bm{u}_i \cdot \bm{v}_j$,  $f(x)=\exp(x)$, and $p_0(j)=P^\gamma(j)$.
 

### 2021-01-22 paper/current/main.tex
addressing reviewer2 minor comments

@@
 We embed trajectories from three massive datasets: U.S.
-passenger flight itinerary records, Korean accommodation reservations, and a dataset of scientists' career mobility between organizations captured in bibliometric records.
+passenger flight itinerary records, Korean accommodation reservations, and a dataset of scientists' career mobility between organizations captured in bibliometric records (Detailed descriptions are available in the Methods).
 
@@
 Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphasis on teaching, such as Barry University and California State University at Long Beach.
-By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reason about the prestige of organizations for which rankings are often low-resolution, incomplete, or entirely absent, such as regional and liberal arts universities (Fig.~\ref{fig:semaxis}d), government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).
+By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reason about the prestige of organizations for which rankings are often low-resolution, incomplete, or entirely absent, such as regional and liberal arts universities (Fig.~\ref{fig:semaxis}d), research institutes (Fig.~\ref{fig:semaxis}e), and government organizations (Fig.~\ref{fig:semaxis}f).
 Their estimated prestige is speculative, though we find that it significantly correlates with their citation impact (Fig.~\ref{fig:supp:sector_semaxis_impact}).
@@
 
-We also find that the size (L2 norm) of the organization embedding vectors provides insights into the characteristics of organizations.
+We also find that the size (L2 norm) of the organization embedding vectors provides insights into the characteristics of organizations (Fig.~\ref{fig:length}).
 Up to a point (around 1,000 researchers), the size of U.S. organization's vectors tends to increase proportionally to the number of researchers (both mobile and non-mobile) with published work;
@@
 The other end of the prestige axis is the geographically-matched (according to census region) set of universities ranked at the bottom of these rankings.
-For example, if 20 top-ranked universities are selected and six of them are in the Northeastern U.S., then the bottom twenty will be chosen to also include six from the Northeastern U.S..
+For example, if 20 top-ranked universities are selected and six of them are in the Northeastern U.S., then the bottom twenty will be chosen to also include six from the Northeastern U.S.
 From the prestige axis, we derive a ranking of universities that we then compare to other formal university rankings using Spearman rank correlation.

### 2021-01-22 paper/current/supp.tex
fixed swapped links in supp
addressing reviewer2 minor comments

--- 2020-10-26 paper/current/supp.tex
@@
 An affiliation trajectory for an individual researcher is a sequence of organizations in ascending order of year of publication.
-if a researcher published papers with affiliation $A$ in year $t$, $B$ in $t+1$, $C$ in $t+2$ and $A$ again in $t+3$, then the affiliation trajectory is expressed as $(A, B, C, A)$.
+If a researcher published papers with affiliation $A$ in year $t$, $B$ in $t+1$, $C$ in $t+2$ and $A$ again in $t+3$, then the affiliation trajectory is expressed as $(A, B, C, A)$.
 
@@
 	}
-	\label{fig:supp:cosdot}
+	\label{fig:supp:hyperparams}
 \end{figure}

### 2021-01-22 workflow/scripts/PlotDescriptive/PlotPropOverTimeByDiscipline.R
reviewer2 comment: add grid to s1 fig

@@ -59,7 +59,6 @@ plot <- plotdata %>%
     theme(
       text = element_text(size = 12, family = "Helvetica"),
       panel.grid.minor = element_blank(),
-      panel.grid.major = element_blank(),
       panel.background = element_rect(size = 0.5),
       axis.title.x = element_blank(),
       axis.title.y = element_text(size = 12, face = "bold"),

### 2021-01-22 workflow/scripts/PlotDescriptive/PlotPubsOverTime.R

@@ -76,7 +76,6 @@ plot <- plotdata %>%
   theme(
     text = element_text(size = 12, family = "Helvetica"),
     panel.grid.minor = element_blank(),
-    panel.grid.major = element_blank(),
     panel.background = element_rect(size = 0.5),
     axis.title.x = element_blank(),
     axis.title.y = element_text(size = 12, face = "bold"),

### 2021-01-22 paper/current/supp.tex
finished addressing reviewer2 minor comments

@@
 		\textbf{c.}
-		While the absolute count of publications has increased, the percentage of mobile scholars, and those with affiliations in at least least two cities, regions, or countries, as a proportion of all publications, has decreased over time.
+		While the absolute count of publications has increased, the percentage of mobile scholars, and those with affiliations in at least least two cities, regions, or countries, as a proportion of all publications, has remained stable over time.
 		\textbf{d.}
@@
 		Survival probability of mobile researchers with respect to the number of organizations in the their affiliation trajectory.
-		All mobile authors were affiliated with at least two organizations (i.e., survival probability of one) and about 35.0\% were affiliated with three or more. 
-		\textbf{b.} About 68\% of mobile authors listed at least two cities represented in their career trajectories.
-		\textbf{c.} 45\% of mobile authors have two or more regions represented in their career trajectories.
-		\textbf{d.} Only 14\% of mobile authors had two or more countries represented in their career trajectories.
+		All mobile authors were affiliated with at least two organizations (i.e., survival probability of one) and about 25.0\% were affiliated with three or more. 
+		\textbf{b.} About 70\% of mobile authors listed at least two cities represented in their career trajectories.
+		\textbf{c.} 50\% of mobile authors have two or more regions represented in their career trajectories.
+		\textbf{d.} Only 17\% of mobile authors had two or more countries represented in their career trajectories.
 	}
@@
 		a perfect prediction yields all points on the black line.
+		``RMSE'' is the root-mean-squared error between the actual and predicted values.
 		Shown for all pairs of organization (\textbf{a-b}), domestic (\textbf{c-d}), and international only (\textbf{e-f}) mobility.
@@
 	\caption{
-		\textbf{For embedding distance, the exponential-decay gravity model is better.}
+		\textbf{For embedding distance, the exponential-decay gravity model is slightly better.}
 		Flux between organization pairs predicted by the gravity model with different distance decay functions, i.e., exponential decay function (\textbf{a}) and power-law decay function (\textbf{b}) using embedding distance.
-		Boxplots show distribution of actual flux for binned values of predicted flux.
+		Boxplots show the distribution of actual flux for binned values of predicted flux.
 		Box color corresponds to the degree to which the distribution overlaps with $x = y$; 
 		a perfect prediction yields all points on the black line.
+		``RMSE'' is the root-mean-squared error between the actual and predicted values.
 		Shown for all pairs of organization (\textbf{a-b}), domestic (\textbf{c-d}), and international only (\textbf{e-f}) mobility.
-		The gravity model with the exponential decay function outperforms that with a power-decay function.
+		The gravity model with the exponential decay function slightly outperforms that with a power-decay function except in the case of international-only mobility, for which power-decay performs slightly better.
 	}
@@
 		a perfect prediction yields all points on the black line.
+		``RMSE'' is the root-mean-squared error between the actual and predicted values.
 		\textbf{a-b.} Predictions are made with parameters estimated from all pairs of organizations (as in Fig.~\ref{fig:gravity_performance}e), and showing only the subsets of predictions for organization pairs in the same country (\textbf{a}) and in different countries (\textbf{b}).
@@
 		a perfect prediction yields all points on the black line.
+		``RMSE'' is the root-mean-squared error between the actual and predicted values.
 	}
@@
 		a perfect prediction yields all points on the black line. 
+		``RMSE'' is the root-mean-squared error between the actual and predicted values.
 	}

### 2021-01-22 paper/current/main.tex
fixed typo error in main text
add line to satisfy comment of reviewer2

@@
 This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered} and networks~\autocite{grover2016node2vec, linzhuo2020hyperbolic}.
+It works under the notion that a good representation should facilitate prediction, and so learns a mapping of target locations (words) that best predict locations that co-appear in the same trajectory (sentence).
 The model is also computationally efficient, robust to noise, and can encode relations between entities as geometric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.
@@
 
-\subsection*{word2vec and gravity model}
+\subsection*{word2vec and the gravity model}
 
@@
 Just as the embedding space makes it possible to \textit{zoom in} on subsets of organizations, it is also possible to \textit{zoom out} by aggregating organizational vectors.
-We can examine the country-level structure that governs scientific mobility.
-For the purpose, we define the representative vector of each country as the average of their organizational vectors and, using their cosine similarities, perform hierarchical clustering of nations that have at least 25 organizations represented in the embedding space, excluding the United States which is a dominant hub well connected to most other countries (see Fig.
+In doing so, we can examine the country-level structure that governs scientific mobility.
+We define the representative vector of each country as the average of their organizational vectors and, using their cosine similarities, perform hierarchical clustering of nations that have at least 25 organizations represented in the embedding space, excluding the United States which is a dominant hub well connected to most other countries (see Fig.
 \ref{fig:clustering}a).
@@
 
-Negative sampling trains {\oit word2vec} using a binary classification task as follows.
+Negative sampling trains {\it word2vec} using a binary classification task as follows.
 A center-context word pair $(i,j)$ is sampled from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$ are sampled from a noise distribution $p_0(\ell)=P^\gamma(\ell)$.

### 2021-01-22 paper/current/main.tex
added a limitation about stochasticity to the conclusion

@@
 Neither of these methodological limitations is insurmountable, and future work can aim to incorporate directionality and identify meaningful representations of continuous mobility data.
+Third, neural embeddings are an inherently stochastic procedure, and so results may change across different iterations. 
+We however, note that all results shown here are robust to this stochasticity, likely emerging from the limited "vocabulary" of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories).
+Applications of \textit{word2vec }to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random artifacts. 
 Finally, the case of scientific mobility presents domain-specific limitations.

### 2021-01-27 workflow/scripts/PlotDistanceMetricPerformance.R
add asteriks to best performing distance method

@@ -38,7 +38,7 @@ plotdata <- params %>%
     metric = factor(metric,
                     levels = c("geo", "emb", "dot", "pprcos", "pprjsd", "lapcos", "svdcos"),
                     labels = c("Geographic\ndistance", "Embedding\ncosine distance", "Embedding\ndot product", "PPR cosine\ndistance", "PPR JSD", "Laplacian\nEigenmap\ndistance", "SVD distance")),
-    # Reorder the metric variable with 
+    # Reorder the metric variable with
     metric = reorder(metric, desc(r2)),
     case = factor(case,
                   levels = c("global", "same-country", "diff-country"),
@@ -50,15 +50,26 @@ plotdata <- params %>%
   )
 
 
+# Get the top-performing for each set of parameters
+top <- plotdata %>%
+  group_by(sizetype, case) %>%
+  filter(r2 == max(r2))
+
+
+print(top)
+
+# build the plot
 plot <- plotdata %>%
   ggplot(aes(x = sizetype, y = r2)) +
-  geom_point(stroke = 0.2, size = 2.5, alpha = 0.8, position = position_dodge(0.5)) +
+  geom_point(size = 2.5, alpha = 0.8, position = position_dodge(0.5), shape = 17) +
+  geom_point(data = top, size = 1,
+             aes(x = as.numeric(sizetype) + 0.15, y = r2 + 0.05),
+             shape = 8, position = position_dodge(0.5)) +
   facet_grid(metric~case) +
   scale_y_continuous(
-    limits = c(0, 0.52),
+    limits = c(0, 0.55),
     breaks = c(0, 0.25, 0.5)
   ) +
-  scale_shape_manual(values = c(23, 21)) +
   scale_fill_manual(values = c("darkgrey", "black")) +
   theme_minimal() +
   theme(

### 2021-01-27 workflow/scripts/PlotDistanceMetricPerformance.R
remove test print statement

@@ -55,9 +55,6 @@ top <- plotdata %>%
   group_by(sizetype, case) %>%
   filter(r2 == max(r2))
 
-
-print(top)
-
 # build the plot
 plot <- plotdata %>%
   ggplot(aes(x = sizetype, y = r2)) +

### 2021-01-28 workflow/scripts/PlotDistancePredictionPerformance.R
Plot the aggregate prediction RMSE values

@@ -1,0 +1,100 @@
+#
+# PlotDistancePredictionPerformance.R
+#
+# author: Dakota Murray
+#
+# Plots the error of predictions made with various distance metrics
+# and measures of population size
+#
+
+# Plot dimensions
+FIG_WIDTH = 6
+FIG_HEIGHT = 7
+
+
+library(readr)
+library(ggplot2)
+library(dplyr)
+suppressPackageStartupMessages(require(optparse))
+
+# Command line arguments
+option_list = list(
+  make_option(c("-i", "--input"), action="store", default=NA, type='character',
+              help="Path to file containing the aggregated hyperameter values"),
+  make_option(c("-o", "--output"), action="store", default=NA, type='character',
+              help="Path to save output image")
+) # end option_list
+opt = parse_args(OptionParser(option_list=option_list))
+
+# Read the aggregate R2 data
+errors <- read_csv(opt$input, col_types = readr::cols())
+
+plotdata <- errors %>%
+  filter(dim == 300) %>%
+  filter(ws == 1) %>%
+  filter(gamma == 1.0) %>%
+  tidyr::gather(model, rmse, error.exp, error.power) %>%
+  mutate(
+    model = gsub("(error.)", "", model),
+    sizetype = gsub(".csv", "", sizetype, fixed = T),
+    metric = factor(metric,
+                    levels = c("geo", "emb", "dot", "pprcos", "pprjsd", "lapcos", "svdcos"),
+                    labels = c("Geographic\ndistance", "Embedding\ncosine distance", "Embedding\ndot product", "PPR cosine\ndistance", "PPR JSD", "Laplacian\nEigenmap\ndistance", "SVD distance")),
+    # Reorder the metric variable with
+    metric = reorder(metric, desc(rmse)),
+    case = factor(case,
+                  levels = c("global", "same", "different"),
+                  labels = c("All", "Domestic", "International")),
+    sizetype = factor(sizetype,
+                      levels = c("all", "mobile", "freq"),
+                      labels = c("All", "Mobile only", "Raw frequency")),
+    model = factor(model,
+                    levels = c("exp", "power"),
+                    labels = c("Exponential", "Power-law"))
+
+  )
+
+# Get the top-performing for each set of parameters
+# Now, this is a little hacky, becuase position_dodge below requires a point
[…]

### 2021-01-28 workflow/scripts/PlotDistancePredictionPerformance.R
visual tweaks to prediction performance plot

@@ -41,7 +41,7 @@ plotdata <- errors %>%
                     levels = c("geo", "emb", "dot", "pprcos", "pprjsd", "lapcos", "svdcos"),
                     labels = c("Geographic\ndistance", "Embedding\ncosine distance", "Embedding\ndot product", "PPR cosine\ndistance", "PPR JSD", "Laplacian\nEigenmap\ndistance", "SVD distance")),
     # Reorder the metric variable with
-    metric = reorder(metric, desc(rmse)),
+    metric = reorder(metric, rmse),
     case = factor(case,
                   levels = c("global", "same", "different"),
                   labels = c("All", "Domestic", "International")),
@@ -68,16 +68,16 @@ plot <- plotdata %>%
   ggplot(aes(x = sizetype, y = rmse, fill = model, group = model)) +
   geom_point(size = 2.5, alpha = 0.8, shape = 25, position = position_dodge(0.5)) +
   geom_point(data = top, size = 1,
-             aes(x = as.numeric(sizetype) + 0.08, y = rmse + 0.15, color = model2),
+             aes(x = as.numeric(sizetype) + 0.08, y = rmse + 0.1, color = model2, fill = NULL),
              position = position_dodge2(0.5, preserve = "total"),
-             shape = 8) +
+             shape = 8, show.legend = FALSE) +
   facet_grid(metric~case) +
   scale_y_continuous(
-    limits = c(0, 1),
-    breaks = c(0, 0.5, 1.0)
+    limits = c(0.5, 1.1),
+    breaks = c(0.5, 0.75, 1.0)
   ) +
   scale_fill_manual(values = c("darkgrey", "black")) +
-  scale_color_manual(values = c("darkgrey", "black", "white")) +
+  scale_color_manual(values = c("darkgrey", "black", "white"), guide = F) +
   scale_alpha_manual(values = c(1.0, 1.0, 0)) +
   guides(alpha = F, color = F) +
   theme_minimal() +

### 2021-01-28 paper/current/main.tex
added new RMSE figure into the SI and reference text to main paper

--- 2021-01-22 paper/current/main.tex
@@
-\documentclass[draft,12pt]{article} %{{{
+\documentclass[12pt]{article} %{{{
 
@@
 \DeclareMathAlphabet{\mathpzc}{T1}{pzc}{m}{it}
-\def\given{\mid}
+\DeclareMathOperator*{\argmin}{\arg\!\min}
+\DeclareMathOperator*{\argmax}{\arg\!\max}
 \usepackage{bm}
@@
 \def\js#1{ {\color{red}\textbf{js: #1}} }
-\def\sk#1{ {\color{red}\textbf{sk: #1}} }
 
@@
 As understanding mobility is becoming critical for contemporary society, finding frameworks that can capture this complexity is of paramount importance.
-	Here, we illustrate a mathematical connection between the neural embedding model \textit{word2ec}~\autocite{mikolov2013word2vec} and the gravity model of mobility and, using three distinct human trajectory datasets, demonstrate that a neural embedding model can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
+Here, using three distinct human trajectory datasets, we demonstrate that a neural embedding model~\autocite{mikolov2013word2vec} can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
 Focusing on the case of scientific mobility, we show that embeddings of scientific organizations uncover cultural and linguistic relations, and even academic prestige, at multiple levels of granularity.
@@
 The question is surprisingly hard to answer when it involves human mobility.
-Although geographic distance has historically constrained human movements, it is becoming less relevant in a world connected by rapid transit and global airline networks.
+Although geographic distance has been constraining human movements throughout history, it is becoming less relevant in a world connected by rapid transit and global airline networks.
 For instance, a person living in Australia is more likely to migrate to the United Kingdom, a far-away country with similar language and culture, than to a much closer country such as Indonesia~\autocite{pew2018migration}.
@@
 We embed trajectories from three massive datasets: U.S.
-passenger flight itinerary records, Korean accommodation reservations, and a dataset of scientists' career mobility between organizations captured in bibliometric records (Detailed descriptions are available in the Methods).
+passenger flight itinerary records,  Korean accommodation reservations, and a dataset of scientists' career mobility between organizations captured in bibliometric records.
 
@@
 We define the distance function in terms of either the geographic distance between locations or their functional distance in the vector space, which is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.
-For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}).
+For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}), though the embedding distance outperforms geographic distance regardless of the type of gravity model used (Fig.~\ref{fig:supp:distancermse}).
 
@@
 the embedding distance explains more than twice the expected flux ($R^{2} = 0.48$, Fig.~\ref{fig:gravity_performance}e) than does the geographic distance ($R^{2} = 0.22$), and predictions made using the embedding distance outperform those using the geographic distance (Fig.~\ref{fig:gravity_performance}f).
-These patterns hold for the subsets of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d and  Fig.~\ref{fig:supp:predict_emb_bymodel}).
-The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores  calculated from the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+These patterns hold for the subsets of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d).
+The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores  calculated from the underlying mobility network (Fig.~\ref{fig:supp:distancemetrics}, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and from a Laplacian Eigenmap embedding of the underlying data (Fig.~\ref{fig:supp:distancemetrics} and Fig.~\ref{fig:supp:distancermse}).
 In sum, our results demonstrate that, consistently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
@@
 
-\subsection*{word2vec and gravity model}
-
-Why does the embedding distance predict actual mobility flows better than the geographic distance?
-Here, we show that the objective function of {\it word2vec} is equivalent to the gravity model.
-
-The {\it word2vec} model takes a location trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), as an input.
-A location $a_t=i$ is considered to have a context location $a_{t'}=j$ that appears in its succeeding or proceeding $w$ locations in the trajectory, \ie  $j \in [a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}]$.
- {\it Word2vec} learns an embedding by estimating the probability that location $i$ has context $j$:
-\begin{align}
-	P\left(j \given i \right):= \frac{\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:prob_w2v_ng}
-\end{align}
-where the denominator $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
-Although {\it word2vec} generates two embedding vectors $\bm{v_i}$ and $\bm{u}_i$---which are referred to as the in-vector and out-vector, respectively, we follow many studies by adopting the in-vector $\bm{v}_i$ as an embedding of location $i$.
-
-Our experiments show that {\it word2vec} best explains real-world mobility flow when $w=1$ (Fig.~\ref{fig:supp:hyperparams}), with the flow predicted by
-\begin{align}
-	\label{eq:flow_w2v}
-	\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
-\end{align}
-where $P(i)$ is the probability that location $i$ appears in the trajectory.
-Because computing $Z_i$ is computationally demanding, multiple approximation methods have been proposed, the most  popular being negative sampling~\autocite{mikolov2013word2vec}. 
-Negative sampling finds the embedding vectors by solving a binary classification task, in which the model classifies whether a given center-context location pair $(i, j)$ comes from the data or artificially generated ``negative'' samples.
-The negative pair $(i,j)$ is sampled in proportion to $P^\gamma(j)$ with parameter $\gamma \geq 0$.
-
-As a heuristic, the negative sampling has a bias and maximizes a different objective function~\autocite{Gutmann2010}.
-When taking into account this bias, {\it word2vec} with the negative sampling fits a probability model given by
-\begin{align}
-	P\left(j \given i \right):= \frac{P^ \gamma(j) \exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:prob_w2v_ng0}
-\end{align}
-where we redefine the normalization constant as $Z_i=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$. (See Methods section for the full calculation).
-
-Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimial in-vectors and out-vectors such that $\bm{u}_i = \bm{v}_i$ \autocite{levy2014neural}.
-Setting $\gamma = 1$ and substituting $\bm{u}_i = \bm{v}_j$ into Eq.~\eqref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
-\begin{align}
-	\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)P(j)\exp(\bm{v}_j \cdot \bm{v}_{i})}{Z_i}. \label{eq:flow_w2v_ng1}
-\end{align}
-The flow $\hat{T_{ij}}$ is symmetric (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because {\it word2vec} neglects whether the context $j$ appears before or after the center $i$ in the trajectory.
-If we swap $i$ and $j$ in Eq.~\eqref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
-Therefore, to ensure $T_{ij} = T_{ji}$, the denominator $Z_i$ should be a constant.
-
-Taken altogether, the {\it word2vec} model with the negative sampling predicts a flow in the same form as in the gravity model:
-\begin{align}
-	\hat{T_{ij}}=  C P(i) P(j)  \exp(\bm{v}_j \cdot \bm{v}_{i}), \label{eq:flow_w2v_ng0}
-\end{align}
-where $C$ is a positive constant.
-In other words, \emph{word2vec with the negative sampling is a gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
-While the gravity model generates the flow from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given trajectories.
-Therefore, the embedding distance is inherently tied to the flow, and hence, has greater predictive power than the geographic distance.
-
 \subsection*{Embeddings capture global structure of mobility}
 
-In the remainder of the paper, we focus on scientific mobility and interrogate the geometric space generated by the neural embedding to sheds light on the multi-faceted relationships between organizations.
+In the remainder of the paper, we focus on scientific mobility, leveraging its richness to investigate how the geometric space generated by the neural embedding method sheds light on the multi-faceted relationships between organizations.
 To explore the topological structure of the embedding, we use a topology-based dimensionality reduction method (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation of the embedding space (Fig.~\ref{fig:projection}a).
@@
 Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphasis on teaching, such as Barry University and California State University at Long Beach.
-By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reason about the prestige of organizations for which rankings are often low-resolution, incomplete, or entirely absent, such as regional and liberal arts universities (Fig.~\ref{fig:semaxis}d), research institutes (Fig.~\ref{fig:semaxis}e), and government organizations (Fig.~\ref{fig:semaxis}f).
+By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reason about the prestige of organizations for which rankings are often low-resolution, incomplete, or entirely absent, such as regional and liberal arts universities (Fig.~\ref{fig:semaxis}d), government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).
 Their estimated prestige is speculative, though we find that it significantly correlates with their citation impact (Fig.~\ref{fig:supp:sector_semaxis_impact}).
@@
 
-We also find that the size (L2 norm) of the organization embedding vectors provides insights into the characteristics of organizations (Fig.~\ref{fig:length}).
+We also find that the size (L2 norm) of the organization embedding vectors provides insights into the characteristics of organizations.
 Up to a point (around 1,000 researchers), the size of U.S. organization's vectors tends to increase proportionally to the number of researchers (both mobile and non-mobile) with published work;
@@
 \begin{equation}
-	p(j \given i) = \frac{\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:cond_prob_w2v}
+p(a_{i} \vert a_{j}) = \frac{\exp(\bm{u}_{a_i} \cdot \bm{v}_{a_{j}})}{\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{a_{j}})},
 \end{equation}
-where $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector", respectively,  $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
-We follow the standard practice and only use the in-vector, $\bm{v}$,  which is known to be superior to the out-vector in link prediction benchmarks~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}.
+where $a_i = a_{t + \tau}$, $ a_j=a_{t}$, $\mathcal{A}$ is the entire set of unique locations represented in the data, and  $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively.
+We follow the standard practice and only use the in-vector, $v$,  which is known to be superior to the out-vector in link prediction benchmarks~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}.
 
+%% Word2vec parameters and training procedure
 We used the \textit{word2vec}  implementation in the python package \texttt{gensim}. 
-The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{\min}$, initial learning rate $\alpha$, and the number of iterations.
+The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{\min}$, initial learning rate $\alpha$, shape of negative sampling distribution $\gamma$, and the number of iterations.
 For main results regarding scientific mobility, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig.~\ref{fig:supp:hyperparams}).
-We also use same setting for U.S.
-airport itinerary and Korean accommodation reservation data.
+Although the original \textit{word2vec } paper uses $\gamma = 0.75$\autocite{mikolov2013word2vec}, here we set $\gamma = 1.0$, though results are only trivially different at different values of $\gamma$ (Fig.~\ref{fig:supp:distancemetrics}).
+We also use same setting for U.S. airport itinerary and Korean accommodation reservation data.
 To mitigate the effect of less common locations, we set $f_{\min} = 50$, limiting to locations appearing at least 50 times across the training trajectories;
@@
 We set $\alpha$ to its default value of 0.025 and iterate five times over all training trajectories.
-For scientific mobility, across each training iteration, the order of organizations within a single year is randomized to remove unclear sequential order.
-
-\subsection*{An implicit bias in the negative sampling}
-\label{sec:sg_and_word2vec}
-
-Negative sampling is a biased estimator~\autocite{Chia2010,Dyer2014} that optimizes a distinct model  from {\it word2vec}.
-What is the different model?
-
-Negative sampling trains {\oit word2vec} using a binary classification task as follows.
-A center-context word pair $(i,j)$ is sampled from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$ are sampled from a noise distribution $p_0(\ell)=P^\gamma(\ell)$.
-($P(j)$ is the fraction of $j$ in the data, and $\gamma>0$ is a parameter).
-Then, given a center-context word pair $(i,j)$, the model predicts whether it is a positive or negative sample using sigmoid function:
-\begin{align}
-	\label{eq:sigmoid}
-	\frac{1}{1 + \exp\left( - \bm{u}_j \cdot \bm{v}_i \right)}.
-\end{align}
-
-This procedure does not guarantee that the embedding optimally converges, even when increasing the training samples and iterations~\autocite{Chia 2010,Dyer2014}.
-This problem is addressed by the noise contrastive estimation (NCE) \autocite{Chia2010}, which fits a probability model in the form:
-\begin{align}
-	\label{eq:nce}
-	f(x) / \sum_{x'} f(x'),
-\end{align}
-where $f(x)$ is the unnormalized probability for an instance $x$.
-As in negative sampling, NCE fits the model based on a binary classification task, with positive and negative samples randomly drawn from the given data and a noise distribution $p_0$, respectively, using a bias-corrected sigmoid function:
-\begin{align}
-	\label{eq:sigmoid2}
-	\frac{1}{1 + \exp\left( -f(x) + \log p_0(x) \right)}.
-\end{align}
-In case of the {\it word2vec}, the instance is the dot similarity $x=\bm{u}_i \cdot \bm{v}_j$,  $f(x)=\exp(x)$, and $p_0(j)=P^\gamma(j)$.
-
-Rewriting the sigmoid function for the negative sampling (Eq.~\eqref{eq:sigmoid}) in form of the bias-corrected sigmoid function yields
-\begin{align}
-	\label{eq:sigmoid3}
-	\frac{1}{1 + \exp\left[ - \tilde f(x) + \log p_0(x)  \right]},
-\end{align}
-where we have defined
-\begin{align}
-	\label{eq:unnormalized}
-	\tilde f(x) = f(x) p_0(x).
-\end{align}
-This bias-corrected sigmoid function fits a probability model:
-\begin{align}
-	f'(x) / \sum_{x'} f'(x),
-\end{align}
-or, by substituting $x=\bm{u}_i \cdot \bm{v}_j$, $f(x)=\exp(x)$, and $p_0(j)=P^\gamma (j)$,
-\begin{align}
-	P\left(j \given i \right):= \frac{P^\gamma (j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
-\end{align}
-where $Z_i=\sum_{j' \in \mathcal{A}} P^\gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
+For scientific mobility, across each training iteration, the order of organizations within a single year is randomized to remove unclear sequential order..
 
@@
 $f(r_{ij})$ is a decay function of distance $r_{ij}$ between locations $i$ and $j$. 
-Here, we used the most basic gravity model which assumes symmetry of the flow $\hat{T_{ij}} =\hat{T_{ji}}$ and distance $r_{ij} = r_{ji}$, while there are four proposed variants \autocite{wilson2011entropy}.
 There are two popular forms for the $f(r_{ij})$:
@@
 The other end of the prestige axis is the geographically-matched (according to census region) set of universities ranked at the bottom of these rankings.
-For example, if 20 top-ranked universities are selected and six of them are in the Northeastern U.S., then the bottom twenty will be chosen to also include six from the Northeastern U.S.
+For example, if 20 top-ranked universities are selected and six of them are in the Northeastern U.S., then the bottom twenty will be chosen to also include six from the Northeastern U.S..
 From the prestige axis, we derive a ranking of universities that we then compare to other formal university rankings using Spearman rank correlation.

### 2021-01-28 paper/current/supp.tex
added description of astericks to the caption
added new RMSE figure into the SI and reference text to main paper

--- 2021-01-15 paper/current/supp.tex
@@
 		Distance metrics are ordered, from top to bottom, by the highest correlation ($r^{2}$). 
+		The asterisk denotes the top-performing distance metric for every case. 
 		All distance metrics explain more of the flux than does geographic distance.
@@
 	\label{fig:supp:distancemetrics}
+\end{figure}
+
+%
+% Figure - Distance metric prediction RMSE performance 
+%
+\begin{figure}[p!]
+	\centering
+	\includegraphics[width=0.85\textwidth]{\figdir/Descriptive/distance_prediction_performance_rmse.pdf}
+	\caption{
+		\textbf{Using cosine distance between embedding vectors as input to the gravity model results in better predictions of scientific mobility compared to geographic distance, baselines.}
+		Shown is the Root Mean Squared Error (RMSE), or the accuracy of predictions made with the gravity model of mobility using the embedding distance and other experimental parameters.
+		The RMSE is shown using both the exponential and power-law forms of the gravity model. 
+		For each distance metric and set of parameters, the RMSE is shown for 
+		Distance metrics are ordered, from top to bottom, by the lowest RMSE, where a lower error indicates better predictions. 
+		The asterisk denotes the best-performing distance metric for every case. 
+		All distance metrics result in better predictions than does geographic distance.
+		In nearly every case, the embedding distance results in the best predictions, no matter the model. 
+		When considering international mobility alone, SVD distance performs best when using the power-law definition of the gravity model. 
+		The x-axis differentiates between three strategies for defining the organization population used to calculate the flux. 
+		``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
+		population is defined in the same way for ``mobile-only'', except only using unique mobile researchers;
+		``Raw frequency'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding. 
+		Generally, ``All'' results in better prediction.
+		}
+	\label{fig:supp:distancermse}
 \end{figure}

### 2021-01-28 paper/current/main.tex

@@
 \begin{equation}
-p(a_{i} \vert a_{j}) = \frac{\exp(\bm{u}_{a_i} \cdot \bm{v}_{a_{j}})}{\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{a_{j}})},
+p(j \vert i) = \frac{\exp(\bm{u}_{j} \cdot \bm{v}_{i})}{\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{i})},
 \end{equation}
-where $a_i = a_{t + \tau}$, $ a_j=a_{t}$, $\mathcal{A}$ is the entire set of unique locations represented in the data, and  $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively.
+where $i =a_{t} $, $ j=a_{t + \tau}$, $\mathcal{A}$ is the entire set of unique locations represented in the data, and  $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively.
 We follow the standard practice and only use the in-vector, $v$,  which is known to be superior to the out-vector in link prediction benchmarks~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}.

### 2021-01-29 paper/current/main.tex
resolving copyedits comment from reviwer #3

--- 2021-01-22 paper/current/main.tex
@@
 
-We quantify the relative importance of geography (by region), and language (by the most widely-spoken language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering by explicitly adjusting the relative importance of different levels of the hierarchy with a scaling parameter $r$, acting like a \textit{zooming lens}.
+We quantify the relative importance of geography (by region), and language (by the most widely-spoken language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering and disjoint clustering (geography, language...) at the different level of hierarchy by explicitly adjusting a scaling parameter $r$, acting like a \textit{zooming lens}.
 If $r$ is high, the similarity is based on the lower levels of the dendrogram, whereas when $r$ is low, the similarity is based on higher levels.

### 2021-01-29 paper/current/main.tex

@@
 $\hat{T}_{ij}$, which is often referred to as ``expected flux''~\autocite{simini2012universal}, is the expected frequency of the co-occurrence of location $i$ and $j$ in the trajectory in the gravity model.
+
 The gravity model dictates that the expected flow, $\hat{T}_{ij}$, ($\hat{T}_{ij }= \hat{T}_{ji}$), is proportional to the locations' population, $\hat{T}_{ij} \propto m_{i} m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
 We define the distance function in terms of either the geographic distance between locations or their functional distance in the vector space, which is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.
-For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}).
+For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}), though the embedding distance outperforms geographic distance regardless of the type of gravity model used (Fig.~\ref{fig:supp:distancermse}).
 
@@
 
+%% Word2vec parameters and training procedure
 We used the \textit{word2vec}  implementation in the python package \texttt{gensim}. 
-The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{\min}$, initial learning rate $\alpha$, and the number of iterations.
+The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{\min}$, initial learning rate $\alpha$, shape of negative sampling distribution $\gamma$, and the number of iterations.
 For main results regarding scientific mobility, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig.~\ref{fig:supp:hyperparams}).
-We also use same setting for U.S.
-airport itinerary and Korean accommodation reservation data.
+Although the original \textit{word2vec } paper uses $\gamma = 0.75$\autocite{mikolov2013word2vec}, here we set $\gamma = 1.0$, though results are only trivially different at different values of $\gamma$ (Fig.~\ref{fig:supp:distancemetrics}).
+We also use same setting for U.S. airport itinerary and Korean accommodation reservation data.
+
 To mitigate the effect of less common locations, we set $f_{\min} = 50$, limiting to locations appearing at least 50 times across the training trajectories;

### 2021-01-29 paper/current/supp.tex

@@
 	}
+
 	\label{fig:supp:hyperparameter}

### 2021-01-29 paper/current/main.tex
add missed references

@@
 A vector-space embedding of locations (airports, accommodations, and organizations) is learned by using trajectories as input to the standard with skip-gram negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
-This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered} and networks~\autocite{grover2016node2vec, linzhuo2020hyperbolic}.
+This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}, networks~\autocite{grover2016node2vec, linzhuo2020hyperbolic} and trajectories\autocite{liu2016exploring, feng2017poi2vec, yao2018representing, cao2019habit2vec, crivellari2019motion, solomon2018predict}.
 It works under the notion that a good representation should facilitate prediction, and so learns a mapping of target locations (words) that best predict locations that co-appear in the same trajectory (sentence).
@@
 For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}), though the embedding distance outperforms geographic distance regardless of the type of gravity model used (Fig.~\ref{fig:supp:distancermse}).
+We would like to note that different decay function $f(r_{ij})$, which is the effect of space, can be due to fundamentally different mechanism \autocite{barthelemy2011spatial} such as the different cost function for a given distance and the spatial granularity of the observation.
 
@@
 The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores  calculated from the underlying mobility network (Fig.~\ref{fig:supp:distancemetrics}, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and from a Laplacian Eigenmap embedding of the underlying data (Fig.~\ref{fig:supp:distancemetrics} and Fig.~\ref{fig:supp:distancermse}).
+The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baseline, such as distances derived from a singular-value decomposition on flow matrix and from a Laplacian Eigenmap embedding  \autocite{belkin2003laplacian} of the underlying data (Fig.~\ref{fig:supp:distancemetrics} and Fig.~\ref{fig:supp:distancermse}).
 In sum, our results demonstrate that, consistently, the embedding distance better captures patterns of actual mobility than does the geographic distance.

### 2021-01-29 paper/current/main.tex
add some reasoing on the choice of decay function with refernece

@@
 We define the distance function in terms of either the geographic distance between locations or their functional distance in the vector space, which is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.
+A different decay function $f(r_{ij})$, which is the effect of space, can be due to fundamentally different mechanism \autocite{barthelemy2011spatial} such as the different cost function for a given distance and the spatial granularity of the observation.
 For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}), though the embedding distance outperforms geographic distance regardless of the type of gravity model used (Fig.~\ref{fig:supp:distancermse}).
-We would like to note that different decay function $f(r_{ij})$, which is the effect of space, can be due to fundamentally different mechanism \autocite{barthelemy2011spatial} such as the different cost function for a given distance and the spatial granularity of the observation.
+Beyond the fitting on the data, we would like to argue that geographical distance fits well with the power-law decay function because it is is more suitable for analyzing large, complex, and scale-free spatial systems, while, embedding distance fits well with the exponential decay function, which we will show later in the section of mathematical relation between word2vec and the gravity model.
 

### 2021-01-29 paper/current/main.tex
add missing figures

@@
 For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}), though the embedding distance outperforms geographic distance regardless of the type of gravity model used (Fig.~\ref{fig:supp:distancermse}).
-Beyond the fitting on the data, we would like to argue that geographical distance fits well with the power-law decay function because it is is more suitable for analyzing large, complex, and scale-free spatial systems, while, embedding distance fits well with the exponential decay function, which we will show later in the section of mathematical relation between word2vec and the gravity model.
+Beyond the fitting on the data, we would like to argue that geographical distance fits well with the power-law decay function because it is is more suitable for analyzing large, complex, and scale-free spatial systems\autocite{chen2015distance}, while embedding distance fits well with the exponential decay function, which we will show later in the section of mathematical relation between \textit{word2vec}and the gravity model.
 
@@
 
-Our experiments show that {\it word2vec} best explains real-world mobility flow when $w=1$ (Fig.~\ref{fig:supp:hyperparams}), with the flow predicted by
+Our experiments show that {\it word2vec} best explains real-world mobility flow when $w=1$ (Fig.~\ref{fig:supp:hyperparameter}), with the flow predicted by
 \begin{align}
@@
 The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{\min}$, initial learning rate $\alpha$, shape of negative sampling distribution $\gamma$, and the number of iterations.
-For main results regarding scientific mobility, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig.~\ref{fig:supp:hyperparams}).
+For main results regarding scientific mobility, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig.~\ref{fig:supp:hyperparameter}).
 Although the original \textit{word2vec } paper uses $\gamma = 0.75$\autocite{mikolov2013word2vec}, here we set $\gamma = 1.0$, though results are only trivially different at different values of $\gamma$ (Fig.~\ref{fig:supp:distancemetrics}).

### 2021-01-29 paper/rebuttal/rebuttal.tex
add rebuttal tex files

\documentclass[12pt,a4paper]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{pslatex}
\usepackage{color}
\usepackage{bm}
\usepackage{cite}
\usepackage{xcolor}
\usepackage[normalem]{ulem}
\definecolor{orange}{RGB}{230, 81, 0}
\definecolor{purple}{RGB}{170, 0, 255}
\definecolor{mygreen}{RGB}{76, 175, 80}
\usepackage{framed}
\definecolor{shadecolor}{RGB}{210, 210, 210}

\def\figdir{../Figs}

\usepackage[most]{tcolorbox}
\newcommand{\sada}[1]{{\leavevmode\color{orange}[SK: #1]}}
\newcommand{\sadaadded}[1]{{\leavevmode\color{orange}{#1}}}
\newcommand{\todo}[1]{{\leavevmode\color{orange}[TODO: #1]}}
\newcommand{\add}[1]{{\leavevmode\color{blue}#1}}
\newcommand{\del}[1]{{\leavevmode\color{red}\sout{#1}}}
\newcommand{\response}[1]{{\leavevmode\noindent #1}}
%\newcommand{\rcomment}[1]{{\bigskip\begin{snugshade}\begin{quotation}\noindent #1 \end{quotation}\end{snugshade} }}
\newcommand{\rcomment}[1]{%
\vspace{10pt}
\begin{tcolorbox}[colback=black!3,colframe=white!45!black]
#1
\end{tcolorbox}
}
\newcommand{\correction}[2]{{\begin{quotation}\noindent {#1}{\it #2} \end{quotation} }}
%\newcommand{\correction}[2]{{\bigskip\begin{quotation}\noindent {#1}{\it #2} \end{quotation} }}

% comment out when submitting
\definecolor{myblue}{RGB}{33,150,243}
\definecolor{mygreen}{RGB}{76, 175, 80}
\definecolor{purple}{RGB}{170, 0, 255}

\makeatletter
\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
\begin{flushleft}
\Large  \textbf{\@title}
\end{flushleft}\egroup
}
\makeatother
\title{Response to the review of submission\\  ``Unsupervised embedding of trajectories captures the latent structure of mobility''}
\date{}
\begin{document}
\maketitle

We would like to thank all reviewers. 
Their comments have authentically helped us improve the quality of our manuscript.
In the following, we provide detailed responses to the issues raised by the reviewer.
The added and deleted sections of the main text are indicated by blue and red, respectively, in the annotated revised manuscript.

\section*{Response to Referee \#1}

\rcomment{%
A. Summary of the key results:

This manuscript proposes to use latent embeddings to represent human mobility data. The key idea is to embed traces of mobility data using the skip-gram with negative sampling (SGNS, i.e., “word2vec”) methodology. These embeddings can then be used to represent the distance between locations (e.g., via the cosine distance between embeddings), and, perhaps more importantly, these embeddings can also be interpreted in terms of how their properties capture various aspects of mobility.

The authors demonstrate three key findings, with their empirical analysis based on datasets of flight itineraries, academic career trajectories, and Korean accommodation reservations.
The authors show that the distance implicitly defined by the embedding space better reflects the flux between locations, compared to geographic distance (and personalized PageRank, in the appendix). More concretely, the authors show that the embedding distance explains more variance for the flow when using a gravity model approach.
The authors show how the “global” structure of the embedding space can be visualized and interpreted by using UMAP to generate two-dimensional visualizations. Notably, the authors demonstrate interesting and non-trivial organization of the data at multiple scales, based on the embeddings.
Finally, the authors show that the embeddings encode a latent “prestige” hierarchy over the academic data (e.g., with the L2 norm having an interesting non-linear relationship with institution size that appears to be mediated by prestige).
}

\response{%
Thank you for the valuable comments. 
In the following, we go through the review point-by-point and address the reviewer's concerns one by one.
}

\rcomment{%
To the best of my knowledge, this is the first work providing a thorough analysis of the structure encoded by latent mobility embeddings (e.g., the prestige hierarchy), and this is the first work I am aware of to propose embeddings as an explanatory/exploratory tool in this context. In this way, the work has some originality and significance.

However, the novelty of this work is quite narrow, as there are several prior works that develop trajectory-based embeddings of human mobility based on the word2vec algorithm. For example, the following references all propose word2vec-inspired embeddings of human mobility data:

Liu, Xin, Yong Liu, and Xiaoli Li. "Exploring the Context of Locations for Personalized Location Recommendations." IJCAI. 2016.
Feng, Shanshan, et al. "POI2Vec: geographical latent representation for predicting future visitors." AAAI. 2017.
Yao, Zijun, et al. "Representing Urban Functions through Zone Embedding with Human Mobility Patterns." IJCAI. 2018.
Cao, Hancheng, et al. "Habit2vec: Trajectory semantic embedding for living pattern recognition in population." IEEE Transactions on Mobile Computing 19.5 (2019): 1096-1108.

Notably, the location embedding methodology in Liu et al (2016) (see Section 3.1) is essentially the same as the approach used in the submitted manuscript, and the work by Liu et al (2016) is well-known with over 100 citations.
}

\response{%
Thank you for pointing out the missing references. We carefully read the papers and add them into introduction section.
}

\rcomment{
Put simply, there are no original scientific insights about mobility granted by the analysis of the submitted manuscript. There is a clear argument that embeddings can be a useful tool to explore mobility data, but in my opinion, this methodological insight is not sufficiently significant to warrant publication in a general-interest venue such as Nature. In its current state, this work would be more appropriate for a mobility-focused or methodological venue.

I found the specific use of the SGNS algorithm unmotivated. There are many ways to generate useful low-dimensional embeddings, so why is the SGNS method prioritized above others? This method is popular, but popularity alone is not sufficient justification and I see no theoretical reason why it should be the most appropriate method. For example, a key point in this manuscript is the fact that the the SGNS embeddings capture the flux between locations better than geographic distance. However, if this is such an important point, then why not simply learn a low-dimensional embedding approximation of the flux metric directly? SVD. In my view, such a direct low-dimensional approximation of flux using a well-understood and fundamental approach (i.e., SVD) would be simpler and more theoretically motivated as a direct approximation of the flux between locations. Of course, it is possible that SVD-based embeddings would not have the same interesting properties that the SGNS embeddings have, but in my opinion, the manuscript would need to justify this. Again, the core underlying issue—which relates to the above point on reproducibility—is the element of arbitrariness in the methodology. Given that the methodology is somewhat arbitrary and essentially chosen based on popularity, it is difficult to treat some findings (e.g., the correlation with prestige) as deeply meaningful rather than just a neat happenstance. E.g., is there something special about SGNS-style embeddings that gives rise to the prestige hierarchy, or is this a common feature of embeddings that approximate pairwise location co-occurrence statistics? The supplementary material does include some results using a personalized PageRank approach, but this appears to be a weak and over-complicated baseline (e.g., compared to a direct low-dimensional approximation of flux).

Overall, my concerns about the methodology center around the fact that the embedding technique is treated as a “black box” of sorts. There is no theoretical justification for why the particular embedding method is used, no thorough comparison between different strong embedding methods, and no thorough acknowledgement or treatment of the stochasticity/arbitrariness in the learned embeddings. Together, these issues—combined with the lack of a clear constructive/predictive original result—weaken the overall claims about the universality and utility of the specific embedding approach. Indeed, it concerns me how the embeddings are essentially treated as something of a black box that supposedly generates "universal" structure. In this way, the manuscript blurs the line between actually studying human mobility and simply studying the dynamics/quirks of SGNS-style embedding methods, which is worrisome and runs the risk of generating supposed "insights" that are actually just
methodological artifacts.

For some references related to the theory and justification of embedding techniques, I suggest the following, all of which emphasize the close connection between matrix factorization and embedding methods which reinforces my concern/question about why a direct SVD method was not explored. These references would hopefully allow for a more theoretical and constructive justification for the embedding approach used and potentially explain some the trends that were observed:

}

\response{%
Thank you for the suggestion!

TODO:
We checked other, simpler approximations )like svd or laplacian eighmap
New mathematical understanding, why word2vec performs better
This new understanding motivates the use of word2vec for mobility data

}

\rcomment{%
The methodology has potential limitations in terms of reproducibility and robustness, which should be addressed. This is no specific fault of the authors, but both the SGNS/word2vec algorithm and the UMAP algorithm are inherently stochastic. This means that these approaches involve inherent randomness, and for researchers to replicate the exact effect seen in this manuscript, one would need to ensure the exact same random seeds etc. were used. In my view, this is a serious limitation, especially given that the UMAP results and learned embeddings are reified and treated as first-class objects of scientific study. In other words, this manuscript proposes that the embeddings encode meaningful information about mobility and that “universal” insights can be gleaned by studying the structure of the embedding space. If this is the argument, then it is critical that the manuscript demonstrates the the findings are robust to the stochasticity that is inherent in the algorithms used. While some concessions are made to this point (e.g., discussions regarding robustness to the SGNS hyperparameters), I think the issue of stochasticity in the techniques needs to be addressed more prominently, especially in terms of how these methods can be effectively used in reproducible work moving forward and how this stochasticity and arbitrariness impacts claims of “universality”.
}

\response{%
TODO…

Heeding this as a general concern, we have added the following sentence to our limitations paragraph in our conclusion:

“We however, note that all results shown here are robust to this stochasticity, likely emerging from the limited "vocabulary" of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories). Applications of word2vec to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random artifacts.”

}

\rcomment{%
Another interesting point in this work is that the authors chose to not report p-values or the results of statistical significance tests (except confidence intervals). I presume this was a conscious decision, which I do not necessarily agree with. I see no critical error in the approach used by the authors, but I would have found aspects of the manuscript easier to understand in places with results of statistical tests (e.g., associated with goodness-of-fit tests formally test that the embedding-based distances are more correlated with the flux values). Given the sample sizes involved, I have no doubt that the results are statistically significant. However, I personally do see value in rigorously performed frequentist hypothesis testing, and I felt that this manuscript could be improved by employing such techniques.

Lastly, the authors do not actually state how the 99 confidence intervals were constructed. (E.g., was this via a bootstrap approach?) This detail should be added.
}

\response{%
JS: Can we do this. I think for the regression on the gravity model, p value is nearly zeros, dakota can you specify how the confidence interval? I thnk it is pretty much clear, but reviewer want to specify it?
}

\rcomment{%
F. Suggested improvements:
References and discussion of prior work using word2vec-style embeddings of mobility data.
Additional experiments using alternative embedding methods, especially an SVD-based embedding method, as well as robustness/reproducibility studies across different runs of the SGNS would be essential to strengthen the paper.
In addition, some additional results demonstrating how the embeddings provide novel scientific insight, rather than just recapitulating known structures, would be essential to make this work above-the-bar for a high-impact publication such as Nature.

}

\response{
TODO: We believe that the mathematical breakthroughs made since our first submission improve the manuscript and extend its contribution and demonstrates novel scientific insight, and justifies the use of word2vec towards mobility data. By adding this, and addressing your other points (above), we believe that the revised manuscript sufficiently remedies your concerns.

}

\bigskip
\response{%
In summary, we have updated the manuscript by providing the appropriate context in the literature, clarifying the limitations of our study, and extending our approach to incorporate delays in contact tracing. We deeply appreciate the referee's careful reading of the paper and their constructive comments. 
%We hope that have correctly addressed the referee's concerns and comments.
}

%===================================================

\newpage

\bigskip
\section*{\bf Response to Reviewer \#2}

\rcomment{%
I have carefully read the manuscript by Murray and others entitled as “Unsupervised embedding of trajectories captures the latent structure of mobility”, submitted for publication in Nature. In this paper the authors modify a conventional embedding method originally developed for word embedding, the Word2Vec algorithm, to obtain low dimensional representation of individual mobility trajectories in different settings. They analysed an air transportation dataset describing 87)flight connections between domestic airport of the US, a South Korean hotel accommodation dataset, and a world wide scientific mobility dataset obtained from the affiliations of researchers, recorded in the ISI Web of Science corpus. Beyond the methodological advance the main result of the paper is about the latent geographical and hierarchical patterns of academic units, what the embedding built from short scientific trajectories is demonstrated to capture at once.paradox of friendship) and propose a viable way to exploit the first principle without knowing the directionality of the infections.
}

\response{%
We would like to thank the referee for helpful comments. 
In the following, we provide detailed responses to all issues raised by the referee.
}

\rcomment{%
Although the paper is well written and explores a very interesting problem, I have certain criticism for the used methodology. After obtaining a representation of each dataset, the authors defined an embedding distance as the cosine distance between vectors in the space, while defining distance as the geographical distance in the original, spatially embedded datasets. Subsequently they used the Gravity Law to estimate the flux between location pairs of vector pairs in the spatial and embedded space respectively. The Gravity Law, applied on mobility, assumes that the number of people moving between two populations is proportional to the multiplicative of the sizes of the populations and a deterrence function. Research during the last decades on transportation, spatial networks and human mobility suggests that this deterrence function may take a functional form of an inverse exponential or an inverse power-law, as it has been acknowledged by the authors. However, the emergence of these different deterrence functions can be due to fundamentally different mechanisms (for a review on the topic see Barthélemy, Physics Reports 499, 1, 2011, a paper not cited in the manuscript). For example, the different cost functions (linear or logarithmic) to create link at a given distance, the spatial granularity of the observation, or even the heterogeneity of the moving individuals in terms of various factors, just to mention a few examples. Instead, the authors of the actual paper arbitrarily assumed a power-law deterrence function in the spatial case and an exponential deterrence function in the embedding space without further arguing their choice (other than fitting on the data). Furthermore, assuming different deterrence functions for the flux estimation using Gravity Law makes the estimated fluxes incomparable, resulting the invalidation of results depicted in Figure 2.
}

\response{%
Thank you for pointing this out. 
TODO:
We carefully read out the Barthélemy, Physics Reports 499, 1, 2011 and other reference paper in draft.
Also, we also report the performance of the flux estimation with different deterrence functions, which shows Embedding distance with exponential decay function always produce the best result.

Beyond the ﬁtting on the data, we would like to argue that geographical distance ﬁts well with the power-law decay function because it is is more suitable for analyzing large, complex, and scale-free spatial systems , while embedding distance ﬁts well with the exponential decay function, which we will show later in the section of mathematical relation between word2vecand the gravity model.
}

\begin{figure}[p!]
	\centering
	\includegraphics[width=0.85\textwidth]{\figdir/Descriptive/distance_prediction_performance_rmse.pdf}
	\caption{
		\textbf{Using cosine distance between embedding vectors as input to the gravity model results in better predictions of scientific mobility compared to geographic distance, baselines.}
		Shown is the Root Mean Squared Error (RMSE), or the accuracy of predictions made with the gravity model of mobility using the embedding distance and other experimental parameters.
		The RMSE is shown using both the exponential and power-law forms of the gravity model. 
		For each distance metric and set of parameters, the RMSE is shown for 
		Distance metrics are ordered, from top to bottom, by the lowest RMSE, where a lower error indicates better predictions. 
		The asterisk denotes the best-performing distance metric for every case. 
		The x-axis differentiates between three strategies for defining the organization population used to calculate the flux. 
		``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
		population is defined in the same way for ``mobile-only'', except only using unique mobile researchers;
		``Raw frequency'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding. 
		Generally, ``All'' results in better prediction.
		}
	\label{fig:supp:distancermse}
\end{figure}

\rcomment{
I would suggest to the authors to carefully cite other papers applying Word2Vec embedding on spatial data, especially focusing on location embedding based on trajectory sequences. Examples are:
A. Solomon et al., Predict Demographic Information Using Word2Vec on Spatial Trajectories., ACM UMAP '18: Proceedings of the 26th Conference on User Modeling, Adaptation and Personalization, July 2018 Pages 331–339, https://doi.org/10.1145/3209219.3209224
A. Crivellari and E. Beinat, From Motion Activity to Geo-Embeddings: Generating and Exploring Vector Representations of Locations, Traces and Visitors through Large-Scale Mobility Data., ISPRS Int. J. Geo-Inf. 2019, 8(3), 134 (2019); https://doi.org/10.3390/ijgi8030134
The application of the Word2Vec method on the studied trajectory sequences is not well explained. Without explaining the embedding method briefly in the main text the reader has no idea how to interpret the embedding distance, which is in the hear of the study.

}

\response{
Thank you. We have added the following sentence to the introduction: “It works under the notion that a good representation should facilitate prediction, and so learns a mapping of target locations (words) that best predict locations that co-appear in the same trajectory (sentence).”

In addition, we provided more explicit mathematical detail of word2vec in the new subsection entitled “word2vec and the gravity model”.

We believe that these details are sufficient in the main text of the manuscript, and refer readers to the Methods for a deeper explanation.
}

\rcomment{

The original SkipGram method expects environments of locations (originally words) with fixed length, however this is not explained in the manuscript nor in Methods or the SI.
Related question to the previous one. Let’s assume that the authors used fixed window lengths and, as mentioned in Methods Embedding section (and demonstrate in Fig.S4 - not referenced in Methods), that the windows size w=1 gives the best correlations in case of scientific mobility. This might be true in absolute terms but it is an unfair comparison to larger window sizes, as there are way more short trajectories in the data than longer ones (see Fig.S3), thus the flux prediction of w=1 is based on a way larger sample than for w>1. Undersampling the ensemble of trajectories used for w=1 predictions might provide a fair way of comparing results of different window sizes.
The other very important parameter of the SkipGram method is the embedding dimension, which is explained in the Methods but it is not explored. E.g. to choose the ideal dimension for embedding one may sweep through a broad range of possible dimensions and not only explore three values as described in the SI (Fig.S4).
Their main observations in section “Embeddings provide functional distance between locations” is that “…our results demonstrate that, consistently, the embedding distance better captures patterns of actual mobility than does the geographic distance.”. This is a great verification of their method but it is somewhat expected from an embedding, which is built on mobility trajectories between places, as compared to cases based on simply geographic distance.

}
\response{
JS: HOw can we do this?
}

\rcomment{
When datasets in the intro are explained, it should be mentioned that the detailed descriptions are in the Methods section.
}
\response{
Thank you. We have added a parenthetical to the introduction after stating the datasets, as follows:

“We embed trajectories from three massive datasets: U.S. passenger flight itinerary records, Korean accommodation reservations, and a dataset of scientists' career mobility between organizations captured in bibliometric records (Detailed descriptions are available in the Methods).”
}
\rcomment{
There is no reference to Fig.5e and f in the text.

}
\response{
We have remedied this, including a reference to both figure panels.

}
\rcomment{
Second paragraph on page 10: the authors discuss Fig.6 here but missed to refer the figure.

}
\response{

Thank you, we have corrected this oversight and added a reference to the first sentence of the relevant paragraph.

}
\rcomment{
Page 15, last row: double point in the end of sentence.

}
\response{
The extra point has been deleted. 
}
\rcomment{
SI Page 2, S3: “. if” -> “. If”

}
\response{
This has been corrected. 
}

\rcomment{
SI Fig.S1c: Here the authors conclude that the proportions “decreased over time”. These proportions seem to be rather flat without strong decreasing trends. In any case, if the authors would like to indicate minor changes here, it would be helpful for the reader if a grid would be posted on the figure.

}
\response{

Thank you, we agree that the trend is flat, rather than decreasing. We have adjusted the text accordingly, and also added a grid to the figure so that it can be more easily read.

}

\rcomment{

SI Fig.S3: Posted numerical values on the figures and the values described in the caption do not match.

}
\response{

Thank you for pointing out this oversight. The caption values have been updated.

}

\rcomment{
SI Fig.S6: Please indicate what is RMSE in the caption. The authors defined it in the main text but the SI should be self consistent too.

}
\response{
We have added the line “RMSE is the root-mean-squared error between the actual and predicted values.” to Fig. S6 as well as all other SI figures that make use of the same visualization.
}

\rcomment{

SI Fig.S7: The authors state that “The gravity model with the exponential decay function outperforms that with a power-decay function.” - this does not seem to be true for the “International” case. Please specify this in the caption.

}
\response{
We have updated the relevant line of the caption to read as follows: 
“The gravity model with the exponential decay function slightly outperforms that with a power-decay function except in the case of international-only mobility, for which power-decay performs slightly better.”

}

\section*{Response to Referee \#3}

\rcomment{%
In this article manuscript, Murray et al demonstrate the power of “vanilla” embedding models based on undirected trajectories and co-affiliation to capture subtle, “functional” distances between establishments, airports, scientific universities and research institutes in terms of human mobility between them. Specifically, they embed these various institutions in a 300 dimensional Euclidean space with a shallow neural network (the very popular word2vec skip-gram architecture) that enables recovery of many subtle aspects of these spaces. For example, when the authors replace geographic distance in the well-known gravity model with cosine distance from their embedding model, they more than double their prediction of human flux between the institutions in each case as well as overall. Moreover, when they interrogate the case of scientific institutions, they show (1) through dimension-reduction (with the UMAP algorithm) on their 300D space, they can recover a high-resolution 2D map of science that captures many intrinsic dimensions of the scientific landscape (e.g., like institution types, because they are built from the mobility of people who are selected and selecting between the institutions), (2) through anchoring the dimensionality of the Euclidean space (e.g., high minus low status institutions) they can identify geographic location and status; (3) through hierarchical clustering and a measure of hierarchical “depth”, the similarity of national scientific enterprises, suggesting the multi-scale resolution of these representations. In short, they demonstrate the power of popular, easy-to-run, shallow embedding approaches to capture and represent structures related to human mobility, largely deploying interesting bespoke methods they have previously developed (and published) to navigate these representations (e.g., SemAxis and Element-Centric clustering).
}

\response{%
Thank you for the valuable comments. 
In the following, we go through the review point-by-point and address the reviewer's concerns one by one.
}

\rcomment{
The analysis does not compare embeddings, which would not be a problem if they were making
an inference other than we can embed micro-mobility to trace macro-mobility. They use an
efficient (Google engineers developed it), single-layer embedding from 2013, which produces
linear associations. But the paper doesn’t take advantage of the revolution in deep neural
network models that now produce powerful, nonlinear and noncontiguous (e.g., using the
attention architecture) models that now dominate analysis of language, and are making very
power inroads in machine vision. To be clear, deeper models require much data and computational power to tune—they are an engineering feat—but if developed in these settings, they would likely dramatically improve the prediction of flux. They take into account directionality (e.g., a person moving from one opportunity to another) and would independently capture people how people distinctly move up and down the hierarchy or from place to place (e.g., a in bi-directional model like BERT). A lack of discussion or demonstration of which model works best--and the unfounded inference that direction does not matter felt weak without a demonstration that they would not have worked better. They did and do work much better for language models and for image generation...why would they not work for analysis of human mobility? (I’m sure they would, but this would time and independent development.)

}

\response{
TODO: we introduce another simpler embedding also make some theorertical relationship between gravity model and word2vec. I think we can specify here.
}

\rcomment{
The paper does not compare human transition (or co-affiliation) data with any other kinds of
data that could be used for embedding. Does author byline data do better than the embedding
of collaborating institutions (almost certainly), than co-mention of the institutions in the press, as
with institutional collaborations (e.g, the Harvard-MIT Broad Institute, or joint university
conferences; these will be stronger signals, but there are fewer of them), than advisor-student
university pairs (although many of these will be captured by the authors’ approach when
students publish at their home institutions before securing jobs elsewhere).

}

\response{
I think dakota can answer this problem 
}

\rcomment{
The paper does not compare human transition (or co-affiliation) data with any other kinds of
data that could be used for embedding. Does author byline data do better than the embedding
of collaborating institutions (almost certainly), than co-mention of the institutions in the press, as
with institutional collaborations (e.g, the Harvard-MIT Broad Institute, or joint university
conferences; these will be stronger signals, but there are fewer of them), than advisor-student
university pairs (although many of these will be captured by the authors’ approach when
students publish at their home institutions before securing jobs elsewhere).

}

\response{
Is there any good reasoning about this?
}

\rcomment{
There are known concerns with clustering a 300 dimensional objects because of the curse of
dimensionality. Many have shown that reducing dimensionality with UMAP to a nontrivial
number of dimensions (e.g., 30), which preserves both local and some global distance, then
clustering on those dimensions are much more stable (e.g., this post). This was one
concern with the stability of the clustering analysis

}

\response{
Will test
}

\rcomment{
P6Para3: “For THEIR purpose…”
}

\response{
P8Para1: “by explicitly the relative importance of different level of the hierarchy with a scaling parameter r ” which is never described or explained. Considering it was derived by the authors in a very recent paper, no one will know what it is.
}

\rcomment{
Thank you, we have edited the text to read as “We quantify the relative importance of geography (by region), and language (by the most widely-spoken language of each country) using the element-centric clustering similarity, a method that can compare hierarchical clustering and disjoint clustering (geography, language...) at the different level of hierarchy by explicitly adjusting a scaling parameter $r$, acting like a zooming lens”
}

\section*{Response to Referee \#1}

\rcomment{%
A. Summary of the key results:
This is a very interesting paper, that takes a new look at the tools used to model human mobility, bringing it to the AI/ML age. It demonstrates that a neural embedding model can encode the relationships between locations into a vector-space, providing an much better measure of distance than the traditionally used physical distance. It then uses multiple datasets, from travel patterns to scientific mobility, to validate the approach, offering additional caveats—demonstrating that embeddings of scientific organizations uncover cultural, prestige and linguistic relations. Overall the findings are novel and open up new possibilities in modeling human mobility.
}

\response{%
Thank you for the valuable comments. 
In the following, we go through the review point-by-point and address the reviewer's concerns one by one.
}

\rcomment{
The authors define the distance function in terms of either the geographic distance between locations or their functional distance in the vector space. The increase in R2, as they switch to the embedding distance, is rather convincing. One of the models they use as a reference is the gravity model, but they also mention the radiation model. I am curious if they tried a comparison with that, and what was the outcome. I suspect that the radiation model would have a comparable performance to the gravity one. But as distance is not the only factor there, is a comparison at all feasible?
}
\response{
radiation model assumes directionality, but it is hard to define in scientific mobility.
@dakota can you specify the charactersitc of the scientific mobilty?
}

\rcomment{
  My second group of questions pertain to the prestige hierarchy, that really drives the dynamics of scientific mobility. The technical description addressed most of them. However, I was wondering, is it all possible to go beyond the descriptive part, and show cases where the more accurate embedding base distances do make a difference? That is, using them, we do not only obtain better correlations with the ranking data, but also allows us to address problems that we could not without the embedding distance? For example, some results have shown that a paper coauthored by two authors at different high prestige institutions has higher impact, than writing a paper with two authors of the same high prestige institution—would embedding help us pull apart such effects? Here I am not trying to make the authors to write a different paper, so maybe a little forward thinking may be enough, if doing the actual work is too time consuming, and goes beyond the current narrative.
}

\response{
 	I think idea itself is really interesting, but time consuming, can we skop this for the future reseathc?

}

\rcomment{
Finally, one cannot escape the fact that COVID changes our mobility patterns. Many groups have used mobile phone data to explore these changes. I wonder, how would the pre-covid embeddings apply to post-covid mobility? Once again, I am mindful that this would require access to such data, but I would not be surprised at all if the authors have access to such data—in which case this is remains an intriguing question.
}

\response{
 	I think it is doable if we have enough large number of publish sequence and tracing the difference of each institution borrowing idea of the histword. But, I think it is okay to leave it as a future work.

}

%\bibliographystyle{unsrt}
\bibliography{main.bib}

\end{document}

### 2021-01-29 paper/rebuttal/rebuttal.tex

@@
 
-\section*{Response to Referee \#1}
+\section*{Response to reviewer \#1}
 
@@
 In summary, we have updated the manuscript by providing the appropriate context in the literature, clarifying the limitations of our study, and extending our approach to incorporate delays in contact tracing.
-We deeply appreciate the referee's careful reading of the paper and their constructive comments.
-%We hope that have correctly addressed the referee's concerns and comments.
+We deeply appreciate the reviewer's careful reading of the paper and their constructive comments.
+%We hope that have correctly addressed the reviewer's concerns and comments.
 }
@@
 \response{%
-We would like to thank the referee for helpful comments. 
-In the following, we provide detailed responses to all issues raised by the referee.
+We would like to thank the reviewer for helpful comments. 
+In the following, we provide detailed responses to all issues raised by the reviewer.
 }
@@
 
-\section*{Response to Referee \#3}
+\section*{Response to reviewer \#3}
 

### 2021-01-29 paper/current/main.tex

@@
 For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}), though the embedding distance outperforms geographic distance regardless of the type of gravity model used (Fig.~\ref{fig:supp:distancermse}).
-Beyond the fitting on the data, we would like to argue that geographical distance fits well with the power-law decay function because it is is more suitable for analyzing large, complex, and scale-free spatial systems\autocite{chen2015distance}, while embedding distance fits well with the exponential decay function, which we will show later in the section of mathematical relation between \textit{word2vec}and the gravity model.
+Beyond the fitting on the data, we would like to argue that geographical distance fits well with the power-law decay function because it is more suitable for analyzing large, complex, and scale-free spatial systems\autocite{chen2015distance}, while embedding distance fits well with the exponential decay function, which we will show later in the section of mathematical relation between \textit{word2vec}and the gravity model.
 

### 2021-01-30 paper/rebuttal/rebuttal.tex
update text for rebuttal

@@
 \definecolor{shadecolor}{RGB}{210, 210, 210}
+
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=blue,
+    filecolor=magenta,      
+    urlcolor=cyan,
+}
+
+\usepackage{dirtytalk}
 
@@
 
-We would like to thank all reviewers. 
-Their comments have authentically helped us improve the quality of our manuscript.
-In the following, we provide detailed responses to the issues raised by the reviewer.
-The added and deleted sections of the main text are indicated by blue and red, respectively, in the annotated revised manuscript.
+We would like to thank all reviewers for their incredibly helpful and insight comments which have helped to improve the quality of our manuscript.
+In the following, we provide detailed responses to the issues raised by each reviewer.
+A version of our manuscript with changes annotated has also been provided to highlight changes made.
 
@@
 \response{%
-Thank you for the valuable comments. 
-In the following, we go through the review point-by-point and address the reviewer's concerns one by one.
+Thank you for your valuable comments. 
+In the following, we address each of your comments point-by-point.
 }
@@
 \response{%
-Thank you for pointing out the missing references. We carefully read the papers and add them into introduction section.
+Thank you for pointing out the missing references. 
+We have carefully read through all of your reccoemnded papers, learning a lot in the process, and have incorporated them into our manuscript's introduction.
 }
@@
 Thank you for the suggestion! 
+We split our response into two subsections concerning the theoretical justification, on one hand, and the comparison to simpler baselines, on the other.
 
-TODO:
-We checked other, simpler approximations )like svd or laplacian eighmap
-New mathematical understanding, why word2vec performs better
-This new understanding motivates the use of word2vec for mobility data
+\subsection*{Theoretical justification of \textit{word2vec} and the Gravity Model} 
+\todo {add text}
+
+\subsection*{Performance of \textit{word2vec} compared with baselines}
+\todo{add text}
 
@@
 \response{%
-TODO…
+Thank you for this comment.
+While robustness is a general concern for these methods, we found that their application to our datasets were in fact quite robust, and observed no evidence that findings were the result of methodological artefacts.
+This is confirmed in extra work done in response to these reviews.
 
+We re-ran all of our results using different starting seeds and found all results were qualitatively similar, and almost quantitatively identical. 
+In addition, we expanded the set of experimental parameters, training 18 different embeddings with different dimensions, window sizes, and now, $\gamma$. 
+We found that while performance varies across each combination of parameters, the main results remain qualitatively similar. 
+While we can run more combinations of parameters, and more iterations of \textit{word2vec}, we see no evidence that results will drastically vary.
+
+We believe that the ratio of the number of organizations represented in our dataset to the total number of mobility trajectories makes our results especially robust. 
+Only about 8,661 organizations are represented across over three million career trajectories of scientists, such that nearly every organization appears enough times, and in enough contexts, to produce a robust vector representation.
+However, this may not hold true for all problem domains—for example, natural language includes many millions of tokens, many of which will occur only a few times, allowing stochasticity to have a much stronger effect on the final representation.
 Heeding this as a general concern, we have added the following sentence to our limitations paragraph in our conclusion:
@@
 \response{%
-JS: Can we do this.
-I think for the regression on the gravity model, p value is nearly zeros, dakota can you specify how the confidence interval?
-I thnk it is pretty much clear, but reviewer want to specify it?
+
+Thank you for this feedback.
+You are correct that it was a conscious choice to not report statistical significance in the form of a P-value. 
+The use of statistical significance is contentious, and Nature itself has hosted some of this debate (\href{https://www.nature.com/articles/d41586-019-00857-9}{[link]}). 
+As such, we have a philosophy of avoiding p-values in research when it makes sense to do so. 
+In our analysis, all correlations and fits are significant at a level below 0.0001, or have a p-value  computationally indistinguishable from zero. 
+However, we recognize that p-values can help readers interpret results. 
+As such, we have opted to add to a sentence such as \say{\textit{Correlation is calculated on the data in the log-log scale ($p < 0.0001$ across all fits)}.} or similar to relevant figures in the main text and supporting materials.
+We believe that this solution strikes a balance between transparency while also avoiding extraneous detail and the common pitfalls of statistical reporting.
+
+We have also provided detail about how confidence intervals were calculated in relevant figure captions. 
+For example, we state in figure 2's caption that \say{\textit{99\% confidence intervals are plotted for the mean flux in each bin based on a normal distribution.}}, which should give readers enough information to reproduce the confidence intervals following their standard definition.
+Other confidence intervals, such as intervals for the loess regression line in figure 6, are calculated using the smoothing functions in the \texttt{ggplot2} package of R, and refer readers to the relevant documentation.
 }
@@
 
-\begin{figure}[p!]
-	\centering
-	\includegraphics[width=0.85\textwidth]{\figdir/Descriptive/distance_prediction_performance_rmse.pdf}
-	\caption{
-		\textbf{Using cosine distance between embedding vectors as input to the gravity model results in better predictions of scientific mobility compared to geographic distance, baselines.}
-		Shown is the Root Mean Squared Error (RMSE), or the accuracy of predictions made with the gravity model of mobility using the embedding distance and other experimental parameters.
-		The RMSE is shown using both the exponential and power-law forms of the gravity model. 
-		For each distance metric and set of parameters, the RMSE is shown for 
-		Distance metrics are ordered, from top to bottom, by the lowest RMSE, where a lower error indicates better predictions. 
-		The asterisk denotes the best-performing distance metric for every case. 
-		The x-axis differentiates between three strategies for defining the organization population used to calculate the flux. 
-		``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
-		population is defined in the same way for ``mobile-only'', except only using unique mobile researchers;
-		``Raw frequency'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding. 
-		Generally, ``All'' results in better prediction.
-		}
-	\label{fig:supp:distancermse}
-\end{figure}
-
 \rcomment{
@@
 \response{
-JS: HOw can we do this?
+\todo{need to finish this. Honestly, I have no idea what they are saying about the window length}
+Thank you for these comments.
+First, we added a line to the methods section detailing the \textit{word2vec} we used, and noting that these achieved the bst performance: \say{\textit{For main results regarding scientific mobility, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig....)}}.
+
 }
@@
 \response{
-Thank you. We have added a parenthetical to the introduction after stating the datasets, as follows:
-
-“We embed trajectories from three massive datasets: U.S.
-passenger flight itinerary records, Korean accommodation reservations, and a dataset of scientists' career mobility between organizations captured in bibliometric records (Detailed descriptions are available in the Methods).”
+Thank you.
+We have added a parenthetical to the introduction after stating the datasets, as follows:  \say{We embed trajectories from three massive datasets: U.S.
+passenger flight itinerary records, Korean accommodation reservations, and a dataset of scientists' career mobility between organizations captured in bibliometric records (Detailed descriptions are available in the Methods).}
 }
@@
 \response{
-TODO: we introduce another simpler embedding also make some theorertical relationship between gravity model and word2vec. I think we can specify here.
+Thank you for this insightful comment. 
+We think that there is a great deal of potential in methods like BERT for representing mobility data.
+What initially drew us to \textit{word2vec}, however, was its simplicity, its ubiquity, and its mathematical tractability (at least compared to other, more sophisticated approaches). 
+This last attribute proved very useful, as in exploring the mathematical properties of the model, we discovered a deep connection between \textit{word2vec} and the Gravity Model of Mobility, which explains why it learns such effective gravity-like relationships between entities.
+We believe hat this new discovery, not included in the manuscript (and illustrated below), justify our use of \textit{word2vec} here. 
+We agree that the revolution in neural embeddings offers great promise in mobility and look forward to reading and also working on these future studies; however we argue that our contribution is most well founded, and best serves the scientific community, by working with simpler and more established models, especially concerning the mathematical link we uncovered.
+To highlight the importance of altenrative models, however, we add the following line to our conclusion: \say{\textit{Future studies may also consider bi-directional embeddings, such as BERT~\cite{devlin2018bert}, to incorporate directionality.
+}}.
+
+\todo{Add complete theoretical discussion here}
+
 }
@@
 students publish at their home institutions before securing jobs elsewhere).
-
 }
@@
 \response{
-I think dakota can answer this problem 
-}
-
-\rcomment{
-The paper does not compare human transition (or co-affiliation) data with any other kinds of
-data that could be used for embedding. Does author byline data do better than the embedding
-of collaborating institutions (almost certainly), than co-mention of the institutions in the press, as
-with institutional collaborations (e.g, the Harvard-MIT Broad Institute, or joint university
-conferences; these will be stronger signals, but there are fewer of them), than advisor-student
-university pairs (although many of these will be captured by the authors’ approach when
-students publish at their home institutions before securing jobs elsewhere).
-
-}
-
-\response{
-Is there any good reasoning about this?
+\todo{I'm worry this sounds too dismissive. Edit please?}
+Thank you for this comment. 
+We feel that applying these embeddings to other areas of scientific activity would be incredibly enlightening! 
+Your recommendation of collaboration (based on the author byline) and advisor-student pairs are especially interesting, and we would aim to address these areas in future studies. 
+However, given the importance of mobility to science, the importance of human mobility more generally, and the connection we discovered between \textit{word2vec} and the gravity model, that a focus of co-affiliation, which most closely aligns with ideas of mobility, is the most reasonable data to use for this manuscript.
 }
@@
 \response{
-Will test
+\todo{will test. But what do we test exactly?}
 }
@@
 \response{
+Thank you, we have corrected this mistake. 
+}
+
+\rcomment{
 P8Para1: “by explicitly the relative importance of different level of the hierarchy with a scaling parameter r ” which is never described or explained.
@@
 
-\rcomment{
+\response{
 Thank you, we have edited the text to read as “We quantify the relative importance of geography (by region), and language (by the most widely-spoken language of each country) using the element-centric clustering similarity, a method that can compare hierarchical clustering and disjoint clustering (geography, language...) at the different level of hierarchy by explicitly adjusting a scaling parameter $r$, acting like a zooming lens”
@@
 
-\section*{Response to reviewer \#1}
+\section*{Response to reviewer \#4}
 
@@
 }
+
 \response{
-radiation model assumes directionality, but it is hard to define in scientific mobility.
-@dakota can you specify the charactersitc of the scientific mobilty?
+
+Thank you for this suggestion. 
+We agree that comparing the radiation model would be incredibly interesting.
+However, we originally did not use radiation model because our dataset on scientific mobility lacked clear directionality, which is required by the radiation model of mobility. 
+Scientific mobility is incredibly complex, the most common form of mobility being co-affiliation, or a researcher holding multiple affiliations simultaneously. 
+In these cases, it is difficult to discern a researcher's main affiliation (where they start), and eventual affiliation (where they end up).
+As such, we conceive of scientific mobility as having no direction (see S2 Text). 
+Given these considerations, we instead chose to use the standard gravity model of mobility, which models mobility as symmetric.
+Moreover, we have recently discovered an underlying mathematical relationship between \textit{word2vec} and the gravity model of mobility, further justifying our choice. 
+While we are excited to investigate the use of neural embeddings with the radiation model, we believe it to be outside the scope of our current submission. 
 }
@@
 \response{
+\todo{Respond to this}
  	I think idea itself is really interesting, but time consuming, can we skop this for the future reseathc?
@@
 \response{
- 	I think it is doable if we have enough large number of publish sequence and tracing the difference of each institution borrowing idea of the histword.
-But, I think it is okay to leave it as a future work.
+This is an excellent idea, and one that we have been interesting in addressing as well. 
+Unfortunately, however, we do not have access to such data, at least not in large enough quantiaties to be representative. 
+Publications are on a time lag, compared to actual events.
+For example, a researcher may write a paper while studying at university $A$, but then before the final paper is published, move to university $B$, so while they now have a $B$ affiliation, in our data all we see is the $A$ one.
+As such, we would not necessarily expect to  see the impact of COVID on bibliometric data until later in 2021 or early 2022, when researchers have had the chance to publich with their new institution.
+We also not that some activity will, of course, be visible, especially given the number of researchers rapidly publishing on the subject of COVID-19, however we consider this to be an unrepresentative sample, given that it is concentrated in a few disciplines.
 
+In the future, however, we hope to have access to a fully-representative sample of mobility data to study the effects of COVID-19 on global scientific labor flows. 
+We can use techniqeus developed by other researchers, such as those used by Hamilton, Leskovec, \& Jurafsky (\href{https://nlp.stanford.edu/projects/histwords/}{[link]}), to align embeddings trained on different data in order to quantify the changes in global mobility.
+We look forward to approaching this, as well as other exciting projects in the future. 
 }
 
+\clearpage
+\begin{figure}[p!]
+	\centering
+	\includegraphics[width=0.85\textwidth]{\figdir/Descriptive/distance_prediction_performance_rmse.pdf}
+	\caption{
+		\textbf{Using cosine distance between embedding vectors as input to the gravity model results in better predictions of scientific mobility compared to geographic distance, baselines.}
+		Shown is the Root Mean Squared Error (RMSE), or the accuracy of predictions made with the gravity model of mobility using the embedding distance and other experimental parameters.
+		The RMSE is shown using both the exponential and power-law forms of the gravity model. 
+		For each distance metric and set of parameters, the RMSE is shown for 
+		Distance metrics are ordered, from top to bottom, by the lowest RMSE, where a lower error indicates better predictions. 
+		The asterisk denotes the best-performing distance metric for every case. 
+		The x-axis differentiates between three strategies for defining the organization population used to calculate the flux. 
+		``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
+		population is defined in the same way for ``mobile-only'', except only using unique mobile researchers;
+		``Raw frequency'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding. 
+		Generally, ``All'' results in better prediction.
+		}
+	\label{fig:supp:distancermse}
+\end{figure}
+
 %\bibliographystyle{unsrt}
-\bibliography{main.bib}
+\bibliography{../main.bib}
 

### 2021-01-30 paper/current/main.tex
update text for rebuttal

@@
 		Black dots are mean flux across binned distances.
-		99\% confidence intervals are plotted but are too small to be visible.
-		Correlation is calculated on the data in the log-log scale.
+		99\% confidence intervals are plotted for the mean flux in each bin based on a normal distribution. 
+		Correlation is calculated on the data in the log-log scale ($p < 0.0001$ across all fits).
 		The lightness of each hex bin indicates the frequency of organization pairs within it.
@@
 		Un-filled points are those top and bottom five universities used to span the axis.
-		Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the embedding and Times ranking is $\rho = 0.73$ ($n = 145$), which increases when more top-and-bottom ranked universities are included (Fig.~\ref{fig:supp:semaxis_compare}).
-		\textbf{b.} The Times ranking is correlated with Leiden Ranking of U.S. universities with Spearman's $\rho = 0.87$.
+		Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the embedding and Times ranking is $\rho = 0.73$ ($n = 145$, $p < 0.0001$), which increases when more top-and-bottom ranked universities are included (Fig.~\ref{fig:supp:semaxis_compare}).
+		\textbf{b.} The Times ranking is correlated with Leiden Ranking of U.S. universities with Spearman's $\rho = 0.87$ and $p < 0001$.
 		\textbf{c-f.} Illustration of SemAxis projection along two axes;  the \textit{latent geographic axis}, from California to Massachusetts (left to right) and the \textit{prestige axis}.
@@
 		Some countries exhibit variants of this pattern, such as Egypt, which is missing the right side of the curve.
-		The loess regression lines are shown for each selected country, and for the aggregate of remaining countries, with 99\% confidence intervals.
+		The loess regression lines are shown for each selected country, and for the aggregate of remaining countries, with ribbons mapping to the 99\% confidence intervals based on a normal distribution.
 		Loess lines are also shown for organizations in Australia, Brazil, and Egypt (\textbf{inset}).
@@
 Embedding distance outperformed geographic distance across distinct and disparate domains, including U.S. flight itineraries, Korean hotel accommodation reservations, and global scientific mobility.
+We discover that this performance results from neural embeddings implicitly learning gravity law relationships between locations, making them particularly well suited to representing mobility.
 Focusing on scientific mobility, we find that neural embedding's performance is driven by its ability to encode many aspects of scientific mobility into a single representation, including global and regional geography, shared languages, and prestige hierarchies, even without explicit information on these factors.
@@
 In spite of its promise, our study has several limitations.
-First, the skip-gram word2vec model does not leverage directionality, meaning that embedding will be less effective at capturing mobility for which directionality is critical.
+First, the skip-gram \textit{word2vec} model does not leverage directionality, meaning that embedding will be less effective at capturing mobility for which directionality is critical.
+Future studies may also consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality. 
 Second, the neural embedding approach is most useful in cases of mobility between discrete geographic units such as between countries, cities, and businesses; this approach is less useful in the case of mobility between locations represented using geographic coordinates, such as in the modeling of animal movements.

### 2021-01-30 paper/current/supp.tex
update text for rebuttal

@@
 		The correlation, or amount of flux explained by the embedding distance across distance metrics and other experimental parameters. 
+		All correlations are significant at $p < 0.0001$). 
 		Distance metrics are ordered, from top to bottom, by the highest correlation ($r^{2}$). 
@@
 		Color of each hex bin indicates the frequency of organization pairs. 
-		Black dots indicate the mean dot product similarity averaged over binned sets at the same embedding distance.
-		Red line is line of best fit.
+				The red line is the line of the best fit.
+		Black dots are mean flux across binned distances.
+		99\% confidence intervals are plotted for the mean flux in each bin based on a normal distribution. 
+		Correlation is calculated on the data in the log-log scale ($p < 0.0001$).
 	}
@@
 		Embedding distance explains more flux than geographic distance (\textbf{b}).
-		Red line is the line of best fit.
+		The red line is the line of the best fit.
 		Black dots are mean flux across binned distances.
+		99\% confidence intervals are plotted for the mean flux in each bin based on a normal distribution. 
+		Correlation is calculated on the data in the log-log scale ($p < 0.0001$ across all fits).
 		Color of each hex bin indicates frequency of organization pairs.
@@
 		Dot product similarity performs better than geographic distance, though worse than cosine similarity in explaining global mobility (\textbf{a}), or domestic (\textbf{b}) or international (\textbf{c}) country mobility.
-		Red line is line of best fit.
+		The red line is the line of the best fit.
 		Black dots are mean flux across binned distances.
+		99\% confidence intervals are plotted for the mean flux in each bin based on a normal distribution. 
+		Correlation is calculated on the data in the log-log scale ($p < 0.0001$ across all fits).
 		Color indicates frequency of organization pairs within each hex bin.
@@
 		PPR cosine distance performs roughly similar to geographic distance in explaining global(\textbf{a}), domestic (\textbf{b}), or international (\textbf{c}) country mobility.
-		Red line is the line of best fit.
-		Black dots indicate the mean flux across binned distances.
+		The red line is the line of the best fit.
+		Black dots are mean flux across binned distances.
+		99\% confidence intervals are plotted for the mean flux in each bin based on a normal distribution. 
+		Correlation is calculated on the data in the log-log scale ($p < 0.0001$ across all fits).
 		Color of hex bind indicates frequency of organization pairs.
@@
 		Overall, PPR JSD explains more variance in mobility than using cosine distance (Fig.~\ref{fig:supp:gravity_pprcos}), except for international mobility, for which cosine similarity out-performs JSD.
-		Red line is the line of best fit.
+		The red line is the line of the best fit.
 		Black dots are mean flux across binned distances.
+		99\% confidence intervals are plotted for the mean flux in each bin based on a normal distribution. 
+		Correlation is calculated on the data in the log-log scale ($p < 0.0001$ across all fits).
 		Color of hex bind indicates frequency of organization pairs.
@@
 	  	Spearman's $\rho$ details the estimate from Spearman correlation between the two rankings using all universities, including those used to define the ends of each axis.
+	  	All correlations are significant with $p < 0.0001$. 
 	}
@@
 		The Times rank is correlated with degree centrality rank (\textbf{a}) with Spearman's $\rho = 0.73$, and is correlated with the eigenvector centrality rank (\textbf{b}) with Spearman's $\rho = 0.76$.
+		All correlations are significant with $p < 0.0001$. 
 	}
@@
 		Embedding rank is correlated with degree centrality rank (\textbf{a}) with Spearman's $\rho = 0.45$, and is correlated with the eigenvector centrality rank (\textbf{b}) with Spearman's $\rho = 0.55$.
+		All correlations are significant with $p < 0.0001$. 
 	}
@@
 		Size is calculated as the mean annualized number of unique authors publishing with that organization. 
-		Annotations show the number of organizations remaining at thresholds pf 0, 50, and 100. 
+		Annotations show the number of organizations remaining at thresholds of 0, 50, and 100. 
 		\textbf{b}. Comparison of organizations using a size threshold of 10 for regional and liberal arts colleges, and 50 for research institutes and government organizations;
@@
 		The impact rank is correlated with the embedding rank for regional and liberal arts colleges with Spearman's $\rho = 0.49\,(n = 48)$, research institutes with Spearman's $\rho = 0.58\,(n = 159)$, and for government organizations with Spearman's $\rho = 0.36\,(n = 55)$.
+		All correlations are significant with $p < 0.001$. 
 	}

### 2021-01-30 paper/rebuttal/rebuttal.tex
write my opinio on using reduced dimension

@@
 }
-
+\DeclareUnicodeCharacter{FB01}{fi}
 \usepackage{dirtytalk}
@@
 \todo{will test. But what do we test exactly?}
+\todo{JS: actually, can't agree with this opinion.
+For sure, curse of  conventionality exists.
+Many dimensional reduction technique do is reducing dimension with keeping pair-wise distance.
+So, it can be well matched with some clustering algorithm such as k-means algorithm.
+But, in our analysis, we used raw similarity score for hierarchical clustering.
+So, in this analysis, using projected similarity form umap(their suggestion) is kinda ridiculous.
+Approximation is approximation, not real similarity.
+}
 }

### 2021-01-30 paper/rebuttal/rebuttal.tex
make latter prettier

@@
 
+\begin{itemize}
+	\item Liu, Xin, Yong Liu, and Xiaoli Li. "Exploring the Context of Locations for Personalized Location Recommendations." IJCAI. 2016.
+\item Feng, Shanshan, et al. "POI2Vec: geographical latent representation for predicting future visitors." AAAI. 2017.
+\item Yao, Zijun, et al. "Representing Urban Functions through Zone Embedding with Human Mobility Patterns." IJCAI. 2018.
+\item Cao, Hancheng, et al. "Habit2vec: Trajectory semantic embedding for living pattern recognition in population." IEEE Transactions on Mobile Computing 19.5 (2019): 1096-1108.
+\end{itemize}
+
 However, the novelty of this work is quite narrow, as there are several prior works that develop trajectory-based embeddings of human mobility based on the word2vec algorithm.
 For example, the following references all propose word2vec-inspired embeddings of human mobility data:
-
-Liu, Xin, Yong Liu, and Xiaoli Li. "Exploring the Context of Locations for Personalized Location Recommendations." IJCAI. 2016.
-Feng, Shanshan, et al. "POI2Vec: geographical latent representation for predicting future visitors." AAAI. 2017.
-Yao, Zijun, et al. "Representing Urban Functions through Zone Embedding with Human Mobility Patterns." IJCAI. 2018.
-Cao, Hancheng, et al. "Habit2vec: Trajectory semantic embedding for living pattern recognition in population." IEEE Transactions on Mobile Computing 19.5 (2019): 1096-1108.
 
@@
 I would suggest to the authors to carefully cite other papers applying Word2Vec embedding on spatial data, especially focusing on location embedding based on trajectory sequences. Examples are:
-A.
+\begin{itemize}
+\item A.
 Solomon et al., Predict Demographic Information Using Word2Vec on Spatial Trajectories., ACM UMAP '18: Proceedings of the 26th Conference on User Modeling, Adaptation and Personalization, July 2018 Pages 331–339, https://doi.org/10.1145/3209219.3209224
-A.
+\item A.
 Crivellari and E.
@@
 2019, 8(3), 134 (2019); https://doi.org/10.3390/ijgi8030134
+
+\end{itemize}
+
 The application of the Word2Vec method on the studied trajectory sequences is not well explained.
@@
 \rcomment{
-SI Page 2, S3: “. if” -> “. If”
+SI Page 2, S3: “. if” $\rightarrow$ “. If”
 

### 2021-01-30 paper/current/main.tex
update main text with YY comments

@@
 	\label{eq:gravity_basic}
-	\hat{T_{ij}} = Cm_{i}m_{j}f(r_{ij}),
+	\hat{T}_{ij} = Cm_{i}m_{j}f(r_{ij}),
 \end{equation}
@@
 \begin{align}
-	P\left(j \given i \right):= \frac{\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:prob_w2v_ng}
+	P\left(j \given i \right):= \frac{\exp(\bm{u}_j \cdot \bm{v}_{i})}{\widetilde{Z_i}}, \label{eq:prob_w2v_ng}
 \end{align}
-where the denominator $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
+where the denominator $\widetilde{Z_i}=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
 Although {\it word2vec} generates two embedding vectors $\bm{v_i}$ and $\bm{u}_i$---which are referred to as the in-vector and out-vector, respectively, we follow many studies by adopting the in-vector $\bm{v}_i$ as an embedding of location $i$.
@@
 	\label{eq:flow_w2v}
-	\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
+	\hat{T}_{ij} = P(i) P(j\given i) = \frac{P(i)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
 \end{align}
@@
 \end{align}
-The flow $\hat{T_{ij}}$ is symmetric (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because {\it word2vec} neglects whether the context $j$ appears before or after the center $i$ in the trajectory.
+The flow $\hat{T}_{ij}$ is symmetric (\ie $\hat{T}_{ij}=\hat{T}_{ji}$) because {\it word2vec} neglects whether the context $j$ appears before or after the center $i$ in the trajectory.
 If we swap $i$ and $j$ in Eq.~\eqref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
-Therefore, to ensure $T_{ij} = T_{ji}$, the denominator $Z_i$ should be a constant.
+Therefore, to ensure $T_{ij} = T_{ji}$, the denominator $Z_i$ must be a constant.
 
@@
 \begin{align}
-	\hat{T_{ij}}=  C P(i) P(j)  \exp(\bm{v}_j \cdot \bm{v}_{i}), \label{eq:flow_w2v_ng0}
+	\hat{T}_{ij}=  C P(i) P(j)  \exp(\bm{v}_j \cdot \bm{v}_{i}), \label{eq:flow_w2v_ng0}
 \end{align}
@@
 Negative sampling is a biased estimator~\autocite{Chia2010,Dyer2014} that optimizes a distinct model  from {\it word2vec}.
-What is the different model?
-
 Negative sampling trains {\it word2vec} using a binary classification task as follows.
@@
 
-This procedure does not guarantee that the embedding optimally converges, even when increasing the training samples and iterations~\autocite{Chia 2010,Dyer2014}.
+This procedure does not guarantee that the embedding optimally converges, even when increasing the training samples and iterations~\autocite{Chia2010,Dyer2014}.
 This problem is addressed by the noise contrastive estimation (NCE) \autocite{Chia2010}, which fits a probability model in the form:
@@
 This formulation and variants have proven useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, truscott2012epidemicgravity, hong2016busgravity}.
-In the gravity law of mobility, the \textit{expected flux}, $\hat{T_{ij}}$ between two locations $i$ and $j$ is defined as,
+In the gravity law of mobility, the \textit{expected flux}, $\hat{T}_{ij}$ between two locations $i$ and $j$ is defined as,
 
@@
 $f(r_{ij})$ is a decay function of distance $r_{ij}$ between locations $i$ and $j$.
-Here, we used the most basic gravity model which assumes symmetry of the flow $\hat{T_{ij}} =\hat{T_{ji}}$ and distance $r_{ij} = r_{ji}$, while there are four proposed variants \autocite{wilson2011entropy}.
+Here, we used the most basic gravity model which assumes symmetry of the flow $\hat{T}_{ij} =\hat{T}_{ji}$ and distance $r_{ij} = r_{ji}$, while there are four proposed variants \autocite{wilson2011entropy}.
 There are two popular forms for the $f(r_{ij})$:

### 2021-02-01 paper/rebuttal/rebuttal.tex
update rebuttal

@@
 \response{
-TODO: We believe that the mathematical breakthroughs made since our first submission improve the manuscript and extend its contribution and demonstrates novel scientific insight, and justifies the use of word2vec towards mobility data.
+We believe that the mathematical breakthroughs made since our first submission improve the manuscript and extend its contribution and demonstrates novel scientific insight, and justifies the use of word2vec towards mobility data.
 By adding this, and addressing your other points (above), we believe that the revised manuscript sufficiently remedies your concerns.
@@
 Thank you for pointing this out. 
-TODO:
-We carefully read out the Barthélemy, Physics Reports 499, 1, 2011 and other reference paper in draft.
-Also, we also report the performance of the flux estimation with different deterrence functions, which shows Embedding distance with exponential decay function always produce the best result.
+We carefully read out the Barthélemy, Physics Reports 499, 1, 2011, and referenced it in our manuscript. 
+Also, we report the performance of the flux estimation (Fig.~\ref{fig:supp:distancemetrics}, this document) and prediction (Fig.~\ref{fig:supp:distancermse}, this document) using different deterrence functions, funding that while performance differs, that the embedding distance outperforms geographic
+distance no matter the function used. 
+We add the following line to the methods,
 
-Beyond the ﬁtting on the data, we would like to argue that geographical distance ﬁts well with the power-law decay function because it is is more suitable for analyzing large, complex, and scale-free spatial systems , while embedding distance ﬁts well with the exponential decay function, which we will show later in the section of mathematical relation between word2vecand the gravity model.
+\medskip
+\say{The decay function $f(r_{ij})$ defines the effect of distance, and so different decay functions can model fundamentally different mechanism [...] such as the cost functions for a given distance and the spatial granularity of the observation.
+For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case.
+though the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Supporting Information).}
+\medskip
+
+We also argue that geographical distance ﬁts well with the power-law decay function because it is is more suitable for analyzing large, complex, and scale-free spatial systems , while embedding distance ﬁts well with the exponential decay function, which we demonstrate to correspond to an underlying mathematical relationship between \textit{word2vec} and the gravity model, a connection we recently discovered and included as a major finding in this revision (see our response to Reviewer 1).
+
 }
@@
 \response{
-\todo{will test. But what do we test exactly?}
-\todo{JS: actually, can't agree with this opinion.
-For sure, curse of  conventionality exists.
-Many dimensional reduction technique do is reducing dimension with keeping pair-wise distance.
-So, it can be well matched with some clustering algorithm such as k-means algorithm.
-But, in our analysis, we used raw similarity score for hierarchical clustering.
-So, in this analysis, using projected similarity form umap(their suggestion) is kinda ridiculous.
-Approximation is approximation, not real similarity.
-}
+
+Thank you for this suggestion. 
+We looked into this, using UMAP to reduce the country-level embeddings from 300 down to 30 dimensions, however the results from this were incomprehensible, and inferior to those using 300 dimensions. 
+Many dimensionality reduction techniques reduce the number of dimensions by maintaining pairwise distances between vectors, so that the result can be well-suited for clustering algorithms. 
+However, our approach already uses raw pairwise similarities to perform hierarchical clustering, so approximating this distance in 30 dimensions, and then using the new distances to perform clustering is redundant.
+We also find that the curse of dimensional is not a major issue in our analysis, at least given the size of our data and the number of locations represented---\textit{word2vec} seems able to learn dense vector-space representations.
 }
@@
 
+\clearpage
 \section*{Response to reviewer \#4}
@@
 \response{
-\todo{Respond to this}
- 	I think idea itself is really interesting, but time consuming, can we skop this for the future reseathc?
 
+Thank you for this idea!
+We believe that this is an interesting topic and we hope to investigate it in the future. 
+In your particular example, an embedding distance trained using sequences of co-authorship on the same paper might be better to capture the \textit{collaborative} distance between institutions. 
+Then, using that distance, one could measure the "embedding distance" spanned by all authors in the byline, and relate this to questions impact to determine whether (a)typical collaborations relate to impact.
+This is certainly a topic that is in our mind for future study. 
+In the case of scientific mobility, we might also consider the "embedding distance" spanned by an individual's career, and relate this to their demographics and scientific impact.
+
+However, while these topics are exciting, we believe that that they fall outside the scope of the current manuscript, especially given the discoveries we made concerning a fundamental connection between the gravity law of mobility and \textit{word2vec}.
 }
@@
 }
+
+\clearpage
+%
+% Figure - Distance metric performance
+%
+\begin{figure}[p!]
+	\centering
+	\includegraphics[width=0.9\textwidth]{\figdir/Descriptive/distance_metric_performance.pdf}
+	\caption{
+		\textbf{Cosine distance between embedding vectors explains more flux in scientific mobility than geographic distance, baselines.}
+		The correlation, or amount of flux explained by the embedding distance across distance metrics and other experimental parameters. 
+		All correlations are significant at $p < 0.0001$). 
+		Distance metrics are ordered, from top to bottom, by the highest correlation ($r^{2}$). 
+		The asterisk denotes the top-performing distance metric for every case. 
+		All distance metrics explain more of the flux than does geographic distance.
+		The cosine distance between embedding vectors explains more flux than all other distance metrics. 
+		The x-axis differentiates between three strategies for defining the organization population used to calculate the flux. 
+		``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
+		population is defined in the same way for ``mobile-only'', except only using unique mobile researchers;
+		``Raw frequency'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding. 
+		Generally, ``All'' explains more of the flux, however there is little difference between definitions of mobility.
+		All distance metrics tend to explain more of the flux when describing all or domestic (same-country) mobility.	
+		}
+	\label{fig:supp:distancemetrics}
+\end{figure}
 

### 2021-02-01 paper/current/main.tex
update rebuttal

@@
 We define the distance function in terms of either the geographic distance between locations or their functional distance in the vector space, which is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.
-A different decay function $f(r_{ij})$, which is the effect of space, can be due to fundamentally different mechanism \autocite{barthelemy2011spatial} such as the different cost function for a given distance and the spatial granularity of the observation.
+The decay function $f(r_{ij})$ defines the effect of distance, and so different decay functions can model fundamentally different mechanism \autocite{barthelemy2011spatial} such as the cost functions for a given distance and the spatial granularity of the observation.
 For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}), though the embedding distance outperforms geographic distance regardless of the type of gravity model used (Fig.~\ref{fig:supp:distancermse}).

### 2021-02-04 paper/rebuttal/rebuttal.tex
formatting letters

@@
 
+\newcommand{\mycaption}[2]{%
+  \caption[#1]{\textbf{#1} \small#2}%
+}
 % comment out when submitting
@@
 
-We would like to thank all reviewers for their incredibly helpful and insight comments which have helped to improve the quality of our manuscript.
-In the following, we provide detailed responses to the issues raised by each reviewer.
+\noindent Dear Dr.editorname and Refrees,
+
+We would like to thank all Referees for their incredibly helpful and insight comments which have helped to improve the quality of our manuscript.
+In the following, we provide detailed responses to the issues raised by each Referee.
 A version of our manuscript with changes annotated has also been provided to highlight changes made.
 
-\section*{Response to reviewer \#1}
+\tableofcontents
+\listoffigures
+
+\section{List of changes}
+
+We have broken down the list of changes to the manuscript by referee.
+
+\section{Point-by-point discussion}
+
+\subsection{Response to Referee 1}
 
@@
 
-\subsection*{Theoretical justification of \textit{word2vec} and the Gravity Model} 
-\todo {add text}
-
-\subsection*{Performance of \textit{word2vec} compared with baselines}
-\todo{add text}
-
-}
-
 \rcomment{%
@@
 In summary, we have updated the manuscript by providing the appropriate context in the literature, clarifying the limitations of our study, and extending our approach to incorporate delays in contact tracing.
-We deeply appreciate the reviewer's careful reading of the paper and their constructive comments.
-%We hope that have correctly addressed the reviewer's concerns and comments.
+We deeply appreciate the Referee's careful reading of the paper and their constructive comments.
+%We hope that have correctly addressed the Referee's concerns and comments.
 }
@@
 \bigskip
-\section*{\bf Response to Reviewer \#2}
+\subsection{Response to Referee 2}
 
@@
 \response{%
-We would like to thank the reviewer for helpful comments. 
-In the following, we provide detailed responses to all issues raised by the reviewer.
+We would like to thank the Referee for helpful comments. 
+In the following, we provide detailed responses to all issues raised by the Referee.
 }
@@
 
-We also argue that geographical distance ﬁts well with the power-law decay function because it is is more suitable for analyzing large, complex, and scale-free spatial systems , while embedding distance ﬁts well with the exponential decay function, which we demonstrate to correspond to an underlying mathematical relationship between \textit{word2vec} and the gravity model, a connection we recently discovered and included as a major finding in this revision (see our response to Reviewer 1).
+We also argue that geographical distance ﬁts well with the power-law decay function because it is is more suitable for analyzing large, complex, and scale-free spatial systems , while embedding distance ﬁts well with the exponential decay function, which we demonstrate to correspond to an underlying mathematical relationship between \textit{word2vec} and the gravity model, a connection we recently discovered and included as a major finding in this revision (see our response to Referee 1).
 
@@
 
-\section*{Response to reviewer \#3}
+\subsection{Response to Referee 3}
 
@@
 Thank you for the valuable comments. 
-In the following, we go through the review point-by-point and address the reviewer's concerns one by one.
+In the following, we go through the review point-by-point and address the Referee's concerns one by one.
 }
@@
 \clearpage
-\section*{Response to reviewer \#4}
+\subsection{Response to Referee 4}
 
@@
 
+\section{Theoretical justification of \textit{word2vec} and the Gravity Model} 
+\todo {add text}
+
+\section{Performance of \textit{word2vec} compared with baselines}
+\todo{add text}
+
+}
+
 \clearpage
@@
 	\includegraphics[width=0.9\textwidth]{\figdir/Descriptive/distance_metric_performance.pdf}
-	\caption{
-		\textbf{Cosine distance between embedding vectors explains more flux in scientific mobility than geographic distance, baselines.}
-		The correlation, or amount of flux explained by the embedding distance across distance metrics and other experimental parameters. 
+		\mycaption
+		{Cosine distance between embedding vectors explains more flux in scientific mobility than geographic distance, baselines.}
+		{The correlation, or amount of flux explained by the embedding distance across distance metrics and other experimental parameters. 
 		All correlations are significant at $p < 0.0001$). 
@@
 	\includegraphics[width=0.85\textwidth]{\figdir/Descriptive/distance_prediction_performance_rmse.pdf}
-	\caption{
-		\textbf{Using cosine distance between embedding vectors as input to the gravity model results in better predictions of scientific mobility compared to geographic distance, baselines.}
-		Shown is the Root Mean Squared Error (RMSE), or the accuracy of predictions made with the gravity model of mobility using the embedding distance and other experimental parameters.
+		\mycaption
+		{Using cosine distance between embedding vectors as input to the gravity model results in better predictions of scientific mobility compared to geographic distance, baselines.}
+		{Shown is the Root Mean Squared Error (RMSE), or the accuracy of predictions made with the gravity model of mobility using the embedding distance and other experimental parameters.
 		The RMSE is shown using both the exponential and power-law forms of the gravity model. 

### 2021-02-04 paper/rebuttal/rebuttal.tex
editing frame and write on the math works

@@
 \usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
 \usepackage{amsthm}
@@
 \usepackage{bm}
-\usepackage{cite}
 \usepackage{xcolor}
@@
 
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{newtxmath}
+\DeclareMathAlphabet{\mathpzc}{T1}{pzc}{m}{it}
+\def\given{\mid}
+\usepackage{bm}
+\def\tnull{{\text{null}}}
+\def\vec#1{{\bm #1}}
+\def\mat#1{\mathbf{#1}}
+
+% abbreviations
+\def\etal{\emph{et~al}.\ }
+\def\eg{e.g.,~} 
+\def\ie{i.e.,~}
+\def\cf{cf.\ }
+\def\viz{viz.\ }
+\def\vs{vs.\ }
+
 \usepackage{hyperref}
@@
     colorlinks=true,
-    linkcolor=blue,
+    linkcolor=black,
     filecolor=magenta,      
@@
 }
+\usepackage[style=nature,
+					backend=biber,
+					sortcites=true,
+					autocite=superscript
+]{biblatex}
+\addbibresource{rebuttal.bib}
+
 \DeclareUnicodeCharacter{FB01}{fi}
@@
 We split our response into two subsections concerning the theoretical justification, on one hand, and the comparison to simpler baselines, on the other. 
+}
 
@@
 We agree that the revolution in neural embeddings offers great promise in mobility and look forward to reading and also working on these future studies; however we argue that our contribution is most well founded, and best serves the scientific community, by working with simpler and more established models, especially concerning the mathematical link we uncovered.
-To highlight the importance of altenrative models, however, we add the following line to our conclusion: \say{\textit{Future studies may also consider bi-directional embeddings, such as BERT~\cite{devlin2018bert}, to incorporate directionality.
+To highlight the importance of altenrative models, however, we add the following line to our conclusion: \say{\textit{Future studies may also consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality.
 }}.
@@
 \section{Theoretical justification of \textit{word2vec} and the Gravity Model} 
-\todo {add text}
+In here, we would like to answer a question: why we use SGNS algorithms and is there any theoretical justification on that? This document details:
+\begin{enumerate}
+	\item Details on \textit{word2vec} algorithm
+
+\end{enumerate}
+
+\subsection{ Details on \textit{word2vec} algorithm}
+We used standard skip-gram negative sampling word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec}.
+Suppose a trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), where $a_{t}$ is the $t$th location in the trajectory.
+A location, $a_{t}$, is considered to have context locations, $a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}$, that appear in the window surrounding $a_t$ up to a time lag of $w$, where $w$ is the window size parameter truncated at $t - w \geq 0$ and $t + w \leq T$.
+Then, the model learns probability $p(a_{t + \tau} \vert a_{t})$, where $-w\leq \tau\leq w$ and $\tau \neq 0$,  by maximizing its log likelihood given by
+%
+% MAIN W2V Equation
+%
+\begin{equation}
+	\frac{1}{T}\sum_{t = 1}^{T} \sum_{-w \leq \tau \leq w, \tau \neq 0} \log p(a_{t + \tau} \vert a_{t}),
+\end{equation}
+where,
+
+%
+% CONDITIONAL PROBABILITY EQ
+%
+\begin{equation}
+	p(j \given i) = \frac{\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:cond_prob_w2v}
+\end{equation}
+where $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector", respectively,  $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
+In general, calculating $Z_i$ is computationally expensive and there are two common approximation:
+ hierarchical softmax \autocite{morin2005hierarchical} and negative sampling \autocite{mikolov2013word2vec}.
+
+\subsection{An implicit bias in the negative sampling}
+
+In our paper, we employed a specific algorithm SGNS word embedding.
+However, it is well known that the negative sampling is a biased estimator~\autocite{Chia2010,Dyer2014} that optimizes a distinct model  from {\it word2vec}.
+
+Negative sampling trains {\it word2vec} using a binary classification task as follows.
+A center-context word pair $(i,j)$ is sampled from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$ are sampled from a noise distribution $p_0(\ell)=P^\gamma(\ell)$.
+($P(j)$ is the fraction of $j$ in the data, and $\gamma>0$ is a parameter).
+Then, given a center-context word pair $(i,j)$, the model predicts whether it is a positive or negative sample using sigmoid function:
+\begin{align}
+	\label{eq:sigmoid}
+	\frac{1}{1 + \exp\left( - \bm{u}_j \cdot \bm{v}_i \right)}.
+\end{align}
+
+This procedure does not guarantee that the embedding optimally converges to the original conditional probability eq.\ref{eq:cond_prob_w2v}, even when increasing the training samples and iterations~\autocite{Chia2010,Dyer2014} in the fact that negative sampling has implicit bias.
+This problem is addressed by the noise contrastive estimation (NCE) \autocite{Chia2010}, which fits a probability model in the form:
+\begin{align}
+	\label{eq:nce}
+	f(x) / \sum_{x'} f(x'),
+\end{align}
+where $f(x)$ is the unnormalized probability for an instance $x$.
+As in negative sampling, NCE fits the model based on a binary classification task, with positive and negative samples randomly drawn from the given data and a noise distribution $p_0$, respectively, using a bias-corrected sigmoid function:
+\begin{align}
+	\label{eq:sigmoid2}
+	\frac{1}{1 + \exp\left( -f(x) + \log p_0(x) \right)}.
+\end{align}
+
+Rewriting the sigmoid function for the negative sampling (Eq.~\eqref{eq:sigmoid}) in form of the bias-corrected sigmoid function yields
+\begin{align}
+	\label{eq:sigmoid3}
+	\frac{1}{1 + \exp\left[ - \tilde f(x) + \log p_0(x)  \right]},
+\end{align}
+where we have defined
+\begin{align}
+	\label{eq:unnormalized}
+	\tilde f(x) = f(x) p_0(x).
+\end{align}
+So, the model with the negative sampling optimize $\tilde f(x)$, not $f(x)$.
+In case of the {\it word2vec}, the instance is the dot similarity $x=\bm{u}_i \cdot \bm{v}_j$,  $f(x)=\exp(x)$, and $p_0(j)=P^\gamma(j)$, and the SGNS word2vec actually optimize the following conditional probability:
+\begin{align}
+	P\left(j \given i \right):= \frac{P^\gamma (j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{\widetilde{Z_i}},
+\end{align}
+where $\widetilde {Z_i}=\sum_{j' \in \mathcal{A}} P^\gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
+
+\subsection*{word2vec and the gravity model}
+
+Why does the embedding distance predict actual mobility flows better than the geographic distance?
+Here, we show that the objective function of {\it word2vec} is equivalent to the gravity model.
+ {\it Word2vec} learns an embedding by estimating the probability that location $i$ has context $j$:
+\begin{align}
+	P\left(j \given i \right):= \frac{\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:prob_w2v_ng}
+\end{align}
+where the denominator $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
+Although {\it word2vec} generates two embedding vectors $\bm{v_i}$ and $\bm{u}_i$---which are referred to as the in-vector and out-vector, respectively, we follow many studies by adopting the in-vector $\bm{v}_i$ as an embedding of location $i$.
+
+Our experiments show that {\it word2vec} best explains real-world mobility flow when $w=1$ (Fig.~\ref{fig:supp:hyperparameter}), with the flow predicted by
+\begin{align}
+	\label{eq:flow_w2v}
+	\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
+\end{align}
+where $P(i)$ is the probability that location $i$ appears in the trajectory.
+Because computing $Z_i$ is computationally demanding, multiple approximation methods have been proposed, the most  popular being negative sampling~\autocite{mikolov2013word2vec}. 
+Negative sampling finds the embedding vectors by solving a binary classification task, in which the model classifies whether a given center-context location pair $(i, j)$ comes from the data or artificially generated ``negative'' samples.
+The negative pair $(i,j)$ is sampled in proportion to $P^\gamma(j)$ with parameter $\gamma \geq 0$.
+
+As a heuristic, the negative sampling has a bias and maximizes a different objective function~\autocite{Gutmann2010}.
+When taking into account this bias, {\it word2vec} with the negative sampling fits a probability model given by
+\begin{align}
+	P\left(j \given i \right):= \frac{P^ \gamma(j) \exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:prob_w2v_ng0}
+\end{align}
+where we redefine the normalization constant as $Z_i=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$. (See Methods section for the full calculation).
+
+Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimial in-vectors and out-vectors such that $\bm{u}_i = \bm{v}_i$ \autocite{levy2014neural}.
+Setting $\gamma = 1$ and substituting $\bm{u}_i = \bm{v}_j$ into Eq.~\eqref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
+\begin{align}
+	\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)P(j)\exp(\bm{v}_j \cdot \bm{v}_{i})}{Z_i}. \label{eq:flow_w2v_ng1}
+\end{align}
+The flow $\hat{T_{ij}}$ is symmetric (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because {\it word2vec} neglects whether the context $j$ appears before or after the center $i$ in the trajectory.
+If we swap $i$ and $j$ in Eq.~\eqref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
+Therefore, to ensure $T_{ij} = T_{ji}$, the denominator $Z_i$ should be a constant.
+
+Taken altogether, the {\it word2vec} model with the negative sampling predicts a flow in the same form as in the gravity model:
+\begin{align}
+	\hat{T_{ij}}=  C P(i) P(j)  \exp(\bm{v}_j \cdot \bm{v}_{i}), \label{eq:flow_w2v_ng0}
+\end{align}
+where $C$ is a positive constant.
+In other words, \emph{word2vec with the negative sampling is a gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
+While the gravity model generates the flow from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given trajectories.
+Therefore, the embedding distance is inherently tied to the flow, and hence, has greater predictive power than the geographic distance.
 
@@
 \todo{add text}
-
-}
 
@@
 
-%\bibliographystyle{unsrt}
-\bibliography{../main.bib}
-
+\printbibliography{}
 \end{document}

### 2021-02-04 paper/rebuttal/rebuttal.tex
various edits

@@
 A version of our manuscript with changes annotated has also been provided to highlight changes made.
+\todo{write a letter}
 
@@
 \section{Point-by-point discussion}
+All of the referees presented us with excellent, insightful comments and we feel that the changes implemented as a consequence have signiﬁcantly strengthened the manuscript.
+Here we offer further discussion, and introduce several results and figures to support certain arguments.
 
 \subsection{Response to Referee 1}
-
-\rcomment{%
-A. Summary of the key results:
-
-This manuscript proposes to use latent embeddings to represent human mobility data.
-The key idea is to embed traces of mobility data using the skip-gram with negative sampling (SGNS, i.e., “word2vec”) methodology.
-These embeddings can then be used to represent the distance between locations (e.g., via the cosine distance between embeddings), and, perhaps more importantly, these embeddings can also be interpreted in terms of how their properties capture various aspects of mobility.
-
-The authors demonstrate three key findings, with their empirical analysis based on datasets of flight itineraries, academic career trajectories, and Korean accommodation reservations.
-The authors show that the distance implicitly defined by the embedding space better reflects the flux between locations, compared to geographic distance (and personalized PageRank, in the appendix).
-More concretely, the authors show that the embedding distance explains more variance for the flow when using a gravity model approach.
-The authors show how the “global” structure of the embedding space can be visualized and interpreted by using UMAP to generate two-dimensional visualizations.
-Notably, the authors demonstrate interesting and non-trivial organization of the data at multiple scales, based on the embeddings.
-Finally, the authors show that the embeddings encode a latent “prestige” hierarchy over the academic data (e.g., with the L2 norm having an interesting non-linear relationship with institution size that appears to be mediated by prestige).
-}
-
-\response{%
-Thank you for your valuable comments. 
-In the following, we address each of your comments point-by-point.
-}
 
@@
 Thank you for pointing out the missing references. 
-We have carefully read through all of your reccoemnded papers, learning a lot in the process, and have incorporated them into our manuscript's introduction.
+We have carefully read through all of your rec emended papers, learning a lot in the process, and have incorporated them into our manuscript's introduction.
 }
@@
 \rcomment{
-Put simply, there are no original scientific insights about mobility granted by the analysis of the submitted manuscript.
-There is a clear argument that embeddings can be a useful tool to explore mobility data, but in my opinion, this methodological insight is not sufficiently significant to warrant publication in a general-interest venue such as Nature.
-In its current state, this work would be more appropriate for a mobility-focused or methodological venue.
-
 I found the specific use of the SGNS algorithm unmotivated.
@@
 However, if this is such an important point, then why not simply learn a low-dimensional embedding approximation of the flux metric directly?
-SVD.
-In my view, such a direct low-dimensional approximation of flux using a well-understood and fundamental approach (i.e., SVD) would be simpler and more theoretically motivated as a direct approximation of the flux between locations.
-Of course, it is possible that SVD-based embeddings would not have the same interesting properties that the SGNS embeddings have, but in my opinion, the manuscript would need to justify this.
-Again, the core underlying issue—which relates to the above point on reproducibility—is the element of arbitrariness in the methodology.
-Given that the methodology is somewhat arbitrary and essentially chosen based on popularity, it is difficult to treat some findings (e.g., the correlation with prestige) as deeply meaningful rather than just a neat happenstance.
-E.g., is there something special about SGNS-style embeddings that gives rise to the prestige hierarchy, or is this a common feature of embeddings that approximate pairwise location co-occurrence statistics?
-The supplementary material does include some results using a personalized PageRank approach, but this appears to be a weak and over-complicated baseline (e.g., compared to a direct low-dimensional approximation of flux).
-
-Overall, my concerns about the methodology center around the fact that the embedding technique is treated as a “black box” of sorts.
-There is no theoretical justification for why the particular embedding method is used, no thorough comparison between different strong embedding methods, and no thorough acknowledgement or treatment of the stochasticity/arbitrariness in the learned embeddings.
-Together, these issues—combined with the lack of a clear constructive/predictive original result—weaken the overall claims about the universality and utility of the specific embedding approach.
-Indeed, it concerns me how the embeddings are essentially treated as something of a black box that supposedly generates "universal" structure.
-In this way, the manuscript blurs the line between actually studying human mobility and simply studying the dynamics/quirks of SGNS-style embedding methods, which is worrisome and runs the risk of generating supposed "insights" that are actually just
-methodological artifacts.
-
-For some references related to the theory and justification of embedding techniques, I suggest the following, all of which emphasize the close connection between matrix factorization and embedding methods which reinforces my concern/question about why a direct SVD method was not explored.
-These references would hopefully allow for a more theoretical and constructive justification for the embedding approach used and potentially explain some the trends that were observed:
-
+such as SVD?
 }
@@
 In my view, this is a serious limitation, especially given that the UMAP results and learned embeddings are reified and treated as first-class objects of scientific study.
-In other words, this manuscript proposes that the embeddings encode meaningful information about mobility and that “universal” insights can be gleaned by studying the structure of the embedding space.
-If this is the argument, then it is critical that the manuscript demonstrates the the findings are robust to the stochasticity that is inherent in the algorithms used.
-While some concessions are made to this point (e.g., discussions regarding robustness to the SGNS hyperparameters), I think the issue of stochasticity in the techniques needs to be addressed more prominently, especially in terms of how these methods can be effectively used in reproducible work moving forward and how this stochasticity and arbitrariness impacts claims of “universality”.
 }
@@
 
-\newpage
-
-\bigskip
 \subsection{Response to Referee 2}
-
-\rcomment{%
-I have carefully read the manuscript by Murray and others entitled as “Unsupervised embedding of trajectories captures the latent structure of mobility”, submitted for publication in Nature.
-In this paper the authors modify a conventional embedding method originally developed for word embedding, the Word2Vec algorithm, to obtain low dimensional representation of individual mobility trajectories in different settings.
-They analysed an air transportation dataset describing 87)flight connections between domestic airport of the US, a South Korean hotel accommodation dataset, and a world wide scientific mobility dataset obtained from the affiliations of researchers, recorded in the ISI Web of Science corpus.
-Beyond the methodological advance the main result of the paper is about the latent geographical and hierarchical patterns of academic units, what the embedding built from short scientific trajectories is demonstrated to capture at once.paradox of friendship) and propose a viable way to exploit the first principle without knowing the directionality of the infections.
-}
-
-\response{%
-We would like to thank the Referee for helpful comments. 
-In the following, we provide detailed responses to all issues raised by the Referee.
-}
 
@@
 Let’s assume that the authors used fixed window lengths and, as mentioned in Methods Embedding section (and demonstrate in Fig.S4 - not referenced in Methods), that the windows size w=1 gives the best correlations in case of scientific mobility.
-This might be true in absolute terms but it is an unfair comparison to larger window sizes, as there are way more short trajectories in the data than longer ones (see Fig.S3), thus the flux prediction of w=1 is based on a way larger sample than for w>1.
+This might be true in absolute terms but it is an unfair comparison to larger window sizes, as there are way more short trajectories in the data than longer ones (see Fig.S3), thus the flux prediction of w=1 is based on a way larger sample than for w$>$1.
 Undersampling the ensemble of trajectories used for w=1 predictions might provide a fair way of comparing results of different window sizes.
+}
+
+\response{
+\todo{need to finish this. Honestly, I have no idea what they are saying about the window length}
+\todo{Maybe related to length of the trajectory @dakoda could you check this?
+}
+}
+
+\rcomment{
 The other very important parameter of the SkipGram method is the embedding dimension, which is explained in the Methods but it is not explored.
@@
 \response{
-\todo{need to finish this. Honestly, I have no idea what they are saying about the window length}
+\todo{ Can we test this? likes  yy's paper on optimal dimension of embedding }
 Thank you for these comments.
 First, we added a line to the methods section detailing the \textit{word2vec} we used, and noting that these achieved the bst performance: \say{\textit{For main results regarding scientific mobility, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig....)}}.
-
 }
@@
 \rcomment{
-There is no reference to Fig.5e and f in the text.
-
+Some minors comments
+\begin{enumerate}
+\item There is no reference to Fig.5e and f in the text.
+\item Second paragraph on page 10: the authors discuss Fig.6 here but missed to refer the figure.
+\item Page 15, last row: double point in the end of sentence.
+\item SI Page 2, S3: “. if” $\rightarrow$ “. If”
+\end{enumerate}
 }
 \response{
-We have remedied this, including a reference to both figure panels.
-
-}
-\rcomment{
-Second paragraph on page 10: the authors discuss Fig.6 here but missed to refer the figure.
-
-}
-\response{
-
-Thank you, we have corrected this oversight and added a reference to the first sentence of the relevant paragraph.
-
-}
-\rcomment{
-Page 15, last row: double point in the end of sentence.
-
-}
-\response{
-The extra point has been deleted. 
-}
-\rcomment{
-SI Page 2, S3: “. if” $\rightarrow$ “. If”
-
-}
-\response{
-This has been corrected. 
+Thank you, we have remedied these comments and have updates the manuscript accordingly, 
 }
@@
 In any case, if the authors would like to indicate minor changes here, it would be helpful for the reader if a grid would be posted on the figure.
-
 }
@@
 \subsection{Response to Referee 3}
-
-\rcomment{%
-In this article manuscript, Murray et al demonstrate the power of “vanilla” embedding models based on undirected trajectories and co-affiliation to capture subtle, “functional” distances between establishments, airports, scientific universities and research institutes in terms of human mobility between them.
-Specifically, they embed these various institutions in a 300 dimensional Euclidean space with a shallow neural network (the very popular word2vec skip-gram architecture) that enables recovery of many subtle aspects of these spaces.
-For example, when the authors replace geographic distance in the well-known gravity model with cosine distance from their embedding model, they more than double their prediction of human flux between the institutions in each case as well as overall.
-Moreover, when they interrogate the case of scientific institutions, they show (1) through dimension-reduction (with the UMAP algorithm) on their 300D space, they can recover a high-resolution 2D map of science that captures many intrinsic dimensions of the scientific landscape (e.g., like institution types, because they are built from the mobility of people who are selected and selecting between the institutions), (2) through anchoring the dimensionality of the Euclidean space (e.g., high minus low status institutions) they can identify geographic location and status; (3) through hierarchical clustering and a measure of hierarchical “depth”, the similarity of national scientific enterprises, suggesting the multi-scale resolution of these representations.
-In short, they demonstrate the power of popular, easy-to-run, shallow embedding approaches to capture and represent structures related to human mobility, largely deploying interesting bespoke methods they have previously developed (and published) to navigate these representations (e.g., SemAxis and Element-Centric clustering).
-}
-
-\response{%
-Thank you for the valuable comments. 
-In the following, we go through the review point-by-point and address the Referee's concerns one by one.
-}
 
@@
 
-\clearpage
 \subsection{Response to Referee 4}
-
-\rcomment{%
-A. Summary of the key results:
-This is a very interesting paper, that takes a new look at the tools used to model human mobility, bringing it to the AI/ML age.
-It demonstrates that a neural embedding model can encode the relationships between locations into a vector-space, providing an much better measure of distance than the traditionally used physical distance.
-It then uses multiple datasets, from travel patterns to scientific mobility, to validate the approach, offering additional caveats—demonstrating that embeddings of scientific organizations uncover cultural, prestige and linguistic relations.
-Overall the findings are novel and open up new possibilities in modeling human mobility.
-}
-
-\response{%
-Thank you for the valuable comments. 
-In the following, we go through the review point-by-point and address the Referee's concerns one by one.
-}
 
@@
 \response{
-
 Thank you for this suggestion. 
@@
 \response{
-
 Thank you for this idea!
@@
 	\item Details on \textit{word2vec} algorithm
+	\item An implicit bias in the negative sampling
+	\item \textit{word2vec} and the gravity model
 
@@
 	P\left(j \given i \right):= \frac{P^\gamma (j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{\widetilde{Z_i}},
+	\label{eq:real_cond}
 \end{align}
@@
 
-\subsection*{word2vec and the gravity model}
+\subsection{\textit{word2vec} and the gravity model}
 
-Why does the embedding distance predict actual mobility flows better than the geographic distance?
-Here, we show that the objective function of {\it word2vec} is equivalent to the gravity model.
- {\it Word2vec} learns an embedding by estimating the probability that location $i$ has context $j$:
+Taking into an implicit bias in the negative sampling  and set $w=1$, the \textit{word2vec} predict the flow with
 \begin{align}
-	P\left(j \given i \right):= \frac{\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:prob_w2v_ng}
+\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)P^\gamma (j)\exp(\bm{v}_j \cdot \bm{v}_{i})}{Z_i}. \label{eq:prob_w2v_ng0}
 \end{align}
-where the denominator $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
-Although {\it word2vec} generates two embedding vectors $\bm{v_i}$ and $\bm{u}_i$---which are referred to as the in-vector and out-vector, respectively, we follow many studies by adopting the in-vector $\bm{v}_i$ as an embedding of location $i$.
-
-Our experiments show that {\it word2vec} best explains real-world mobility flow when $w=1$ (Fig.~\ref{fig:supp:hyperparameter}), with the flow predicted by
-\begin{align}
-	\label{eq:flow_w2v}
-	\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
-\end{align}
-where $P(i)$ is the probability that location $i$ appears in the trajectory.
-Because computing $Z_i$ is computationally demanding, multiple approximation methods have been proposed, the most  popular being negative sampling~\autocite{mikolov2013word2vec}. 
-Negative sampling finds the embedding vectors by solving a binary classification task, in which the model classifies whether a given center-context location pair $(i, j)$ comes from the data or artificially generated ``negative'' samples.
-The negative pair $(i,j)$ is sampled in proportion to $P^\gamma(j)$ with parameter $\gamma \geq 0$.
-
-As a heuristic, the negative sampling has a bias and maximizes a different objective function~\autocite{Gutmann2010}.
-When taking into account this bias, {\it word2vec} with the negative sampling fits a probability model given by
-\begin{align}
-	P\left(j \given i \right):= \frac{P^ \gamma(j) \exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:prob_w2v_ng0}
-\end{align}
-where we redefine the normalization constant as $Z_i=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$. (See Methods section for the full calculation).
+where  $\widetilde{Z_i}=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
 
@@
 \end{align}
-The flow $\hat{T_{ij}}$ is symmetric (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because {\it word2vec} neglects whether the context $j$ appears before or after the center $i$ in the trajectory.
+
+The flow $\hat{T_{ij}}$ is symmetric (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because {\it word2vec} neglects whether the context $j$ appears before or after the center $i$ in the trajectory -- the mechanism of skip-gram.
 If we swap $i$ and $j$ in Eq.~\eqref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
@@
 where $C$ is a positive constant.
+
 In other words, \emph{word2vec with the negative sampling is a gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
@@
 
+\subsection{Some concerns on this section??}
+\todo{
+Why cosine similarity is better? In-vector and out-vectors are different in our result}
+
 \section{Performance of \textit{word2vec} compared with baselines}
-\todo{add text}
+\subsection{The method we have used for the test}
+\todo{list methods in here}
+\subsection{Result}
+\todo{report the results and say our results are better
+Why SGD has a lower performance and SGNS yield better performance
+power of stochastic gradient descent algorithm \autocite{smith2020generalization}}
 
@@
 		\mycaption
-		{Cosine distance between embedding vectors explains more flux in scientific mobility than geographic distance, baselines.}
-		{The correlation, or amount of flux explained by the embedding distance across distance metrics and other experimental parameters. 
+		{Comparison a correlation with flux across various baselines}
+		{
+		Cosine distance between embedding vectors explains more flux in scientific mobility than geographic distance, baselines.
+		The correlation, or amount of flux explained by the embedding distance across distance metrics and other experimental parameters. 
 		All correlations are significant at $p < 0.0001$). 
@@
 		\mycaption
-		{Using cosine distance between embedding vectors as input to the gravity model results in better predictions of scientific mobility compared to geographic distance, baselines.}
-		{Shown is the Root Mean Squared Error (RMSE), or the accuracy of predictions made with the gravity model of mobility using the embedding distance and other experimental parameters.
+		{Comparison of prediction power across various baselines}
+		{Using cosine distance between embedding vectors as input to the gravity model results in better predictions of scientific mobility compared to geographic distance, baselines.
+		Shown is the Root Mean Squared Error (RMSE), or the accuracy of predictions made with the gravity model of mobility using the embedding distance and other experimental parameters.
 		The RMSE is shown using both the exponential and power-law forms of the gravity model. 

### 2021-02-04 paper/rebuttal/rebuttal.tex
update bib
framing the letter

@@
 \usepackage{hyperref}
-\hypersetup{
-    colorlinks=true,
-    linkcolor=black,
-    filecolor=magenta,      
-    urlcolor=cyan,
-}
+
 \usepackage[style=nature,
@@
 ]{biblatex}
+
+\AtEveryBibitem{%
+ \clearfield{url}%
+   \clearfield{month}%
+ \clearfield{issn}%
+ \clearfield{doi}%%
+}
+
 \addbibresource{rebuttal.bib}
@@
 We have broken down the list of changes to the manuscript by referee.
+
+\begin{itemize} 
+\item \textbf{Referee 1} 
+     \begin{itemize} 
+        \item blah
+        \item blah
+     \end{itemize}
+\item \textbf{Referee 2} 
+     \begin{itemize} 
+        \item blah
+        \item blah
+     \end{itemize}
+\item \textbf{Referee 3} 
+     \begin{itemize} 
+        \item blah
+        \item blah
+     \end{itemize}
+ \item \textbf{Referee 4} 
+     \begin{itemize} 
+        \item blah
+        \item blah
+     \end{itemize}
+\end{itemize}
 
@@
 \subsection{The method we have used for the test}
-\todo{list methods in here}
+We list baselines that we have used for the validation. For embedding baselines, we set $d=300$ for the pair comparison.\\\\
+\textbf{SVD-based embedding baselines}
+\begin{itemize}
+    \item Truncated SVD on the flow matrix
+	\item  Laplacian eigenmap
+	\item Levy's word2vec
+\end{itemize}
+\textbf{Network-based baselines}
+\begin{itemize}
+    \item Personalized Page Rank
+\end{itemize}
+\textbf{Geographical baselines}
+
 \subsection{Result}
@@
 power of stochastic gradient descent algorithm \autocite{smith2020generalization}}
+also, compare the speed?
 

### 2021-02-04 paper/rebuttal/rebuttal.tex
formatting the letters

@@
 \definecolor{shadecolor}{RGB}{210, 210, 210}
+\setlength{\parskip}{0.6em}
+
+\setlength{\parindent}{0em}
 
@@
 \newcommand{\del}[1]{{\leavevmode\color{red}\sout{#1}}}
-\newcommand{\response}[1]{{\leavevmode\noindent #1}}
+\newcommand{\response}[1]{{\noindent #1}}
 %\newcommand{\rcomment}[1]{{\bigskip\begin{snugshade}\begin{quotation}\noindent #1 \end{quotation}\end{snugshade} }}
@@
 \vspace{10pt}
-\begin{tcolorbox}[colback=black!3,colframe=white!45!black]
+\begin{tcolorbox}[colback=black!3,colframe=white!45!black, left=0pt, right=0pt, top=0pt, bottom=0pt, arc=0pt,outer arc=0pt, grow to left by=-0.5cm,grow to right by=-0.5cm]
 #1
@@
 
-\response{%
-Thank you for pointing out the missing references. 
+\response{Thank you for pointing out the missing references. 
 We have carefully read through all of your rec emended papers, learning a lot in the process, and have incorporated them into our manuscript's introduction.
@@
 
-\response{%
-Thank you for the suggestion! 
+\response{Thank you for the suggestion! 
 We split our response into two subsections concerning the theoretical justification, on one hand, and the comparison to simpler baselines, on the other. 
@@
 
-\response{%
-Thank you for this comment.
+\response{Thank you for this comment.
 While robustness is a general concern for these methods, we found that their application to our datasets were in fact quite robust, and observed no evidence that findings were the result of methodological artefacts.
@@
 
-We re-ran all of our results using different starting seeds and found all results were qualitatively similar, and almost quantitatively identical. 
+\noindent We re-ran all of our results using different starting seeds and found all results were qualitatively similar, and almost quantitatively identical. 
 In addition, we expanded the set of experimental parameters, training 18 different embeddings with different dimensions, window sizes, and now, $\gamma$. 
@@
 
-We believe that the ratio of the number of organizations represented in our dataset to the total number of mobility trajectories makes our results especially robust. 
+\noindent We believe that the ratio of the number of organizations represented in our dataset to the total number of mobility trajectories makes our results especially robust. 
 Only about 8,661 organizations are represented across over three million career trajectories of scientists, such that nearly every organization appears enough times, and in enough contexts, to produce a robust vector representation.
@@
 
-“We however, note that all results shown here are robust to this stochasticity, likely emerging from the limited "vocabulary" of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories).
+\noindent “We however, note that all results shown here are robust to this stochasticity, likely emerging from the limited "vocabulary" of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories).
 Applications of word2vec to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random artifacts.”
@@
 
-\response{%
-
-Thank you for this feedback.
+\response{Thank you for this feedback.
 You are correct that it was a conscious choice to not report statistical significance in the form of a P-value. 
@@
 
-\response{
-We believe that the mathematical breakthroughs made since our first submission improve the manuscript and extend its contribution and demonstrates novel scientific insight, and justifies the use of word2vec towards mobility data.
+\response{We believe that the mathematical breakthroughs made since our first submission improve the manuscript and extend its contribution and demonstrates novel scientific insight, and justifies the use of word2vec towards mobility data.
 By adding this, and addressing your other points (above), we believe that the revised manuscript sufficiently remedies your concerns.
@@
 \bigskip
-\response{%
-In summary, we have updated the manuscript by providing the appropriate context in the literature, clarifying the limitations of our study, and extending our approach to incorporate delays in contact tracing.
+\response{In summary, we have updated the manuscript by providing the appropriate context in the literature, clarifying the limitations of our study, and extending our approach to incorporate delays in contact tracing.
 We deeply appreciate the Referee's careful reading of the paper and their constructive comments.
@@
 
-\response{%
-Thank you for pointing this out. 
+\response{Thank you for pointing this out. 
 We carefully read out the Barthélemy, Physics Reports 499, 1, 2011, and referenced it in our manuscript. 
@@
 
-\response{
-Thank you.
+\response{Thank you.
 We have added the following sentence to the introduction: “It works under the notion that a good representation should facilitate prediction, and so learns a mapping of target locations (words) that best predict locations that co-appear in the same trajectory (sentence).”
@@
 
-\response{
-\todo{need to finish this. Honestly, I have no idea what they are saying about the window length}
+\response{\todo{need to finish this. Honestly, I have no idea what they are saying about the window length}
 \todo{Maybe related to length of the trajectory @dakoda could you check this?
@@
 }
-\response{
-\todo{ Can we test this? likes  yy's paper on optimal dimension of embedding }
+\response{\todo{ Can we test this? likes  yy's paper on optimal dimension of embedding }
 Thank you for these comments.
@@
 }
-\response{
-Thank you.
+\response{Thank you.
 We have added a parenthetical to the introduction after stating the datasets, as follows:  \say{We embed trajectories from three massive datasets: U.S.
@@
 }
-\response{
-Thank you, we have remedied these comments and have updates the manuscript accordingly, 
+\response{Thank you, we have remedied these comments and have updates the manuscript accordingly, 
 }
@@
 }
-\response{
-
-Thank you, we agree that the trend is flat, rather than decreasing. We have adjusted the text accordingly, and also added a grid to the figure so that it can be more easily read.
+\response{Thank you, we agree that the trend is flat, rather than decreasing. We have adjusted the text accordingly, and also added a grid to the figure so that it can be more easily read.
 
@@
 \rcomment{
-
 SI Fig.S3: Posted numerical values on the figures and the values described in the caption do not match.
-
 }
-\response{
-
-Thank you for pointing out this oversight. The caption values have been updated.
-
+\response{Thank you for pointing out this oversight. The caption values have been updated. 
 }
 
-\rcomment{
-SI Fig.S6: Please indicate what is RMSE in the caption. The authors defined it in the main text but the SI should be self consistent too.
-
+\rcomment{SI Fig.S6: Please indicate what is RMSE in the caption. The authors defined it in the main text but the SI should be self consistent too.
 }
-\response{
-We have added the line “RMSE is the root-mean-squared error between the actual and predicted values.” to Fig. S6 as well as all other SI figures that make use of the same visualization.
+\response{We have added the line “RMSE is the root-mean-squared error between the actual and predicted values.” to Fig. S6 as well as all other SI figures that make use of the same visualization.
 }
 
-\rcomment{
+\rcomment{SI Fig.S7: The authors state that “The gravity model with the exponential decay function outperforms that with a power-decay function.” - this does not seem to be true for the “International” case.
+Please specify this in the caption.
+}
 
-SI Fig.S7: The authors state that “The gravity model with the exponential decay function outperforms that with a power-decay function.” - this does not seem to be true for the “International” case.
-Please specify this in the caption.
-
-}
-\response{
-We have updated the relevant line of the caption to read as follows: 
+\response{We have updated the relevant line of the caption to read as follows: 
 “The gravity model with the exponential decay function slightly outperforms that with a power-decay function except in the case of international-only mobility, for which power-decay performs slightly better.”
-
 }
@@
 
-\rcomment{
-The analysis does not compare embeddings, which would not be a problem if they were making
+\rcomment{The analysis does not compare embeddings, which would not be a problem if they were making
 an inference other than we can embed micro-mobility to trace macro-mobility. They use an
@@
 (I’m sure they would, but this would time and independent development.)
-
 }
 
-\response{
-Thank you for this insightful comment. 
+\response{Thank you for this insightful comment. 
 We think that there is a great deal of potential in methods like BERT for representing mobility data.
@@
 
-\response{
-\todo{I'm worry this sounds too dismissive. Edit please?}
+\response{\todo{I'm worry this sounds too dismissive. Edit please?}
 Thank you for this comment. 
@@
 
-\response{
-
-Thank you for this suggestion. 
+\response{Thank you for this suggestion. 
 We looked into this, using UMAP to reduce the country-level embeddings from 300 down to 30 dimensions, however the results from this were incomprehensible, and inferior to those using 300 dimensions. 
@@
 
-\response{
-Thank you, we have corrected this mistake. 
+\response{Thank you, we have corrected this mistake. 
 }
@@
 
-\response{
-Thank you, we have edited the text to read as “We quantify the relative importance of geography (by region), and language (by the most widely-spoken language of each country) using the element-centric clustering similarity, a method that can compare hierarchical clustering and disjoint clustering (geography, language...) at the different level of hierarchy by explicitly adjusting a scaling parameter $r$, acting like a zooming lens”
+\response{Thank you, we have edited the text to read as “We quantify the relative importance of geography (by region), and language (by the most widely-spoken language of each country) using the element-centric clustering similarity, a method that can compare hierarchical clustering and disjoint clustering (geography, language...) at the different level of hierarchy by explicitly adjusting a scaling parameter $r$, acting like a zooming lens”
 }
@@
 
-\response{
-Thank you for this suggestion. 
+\response{Thank you for this suggestion. 
 We agree that comparing the radiation model would be incredibly interesting.
@@
 
-\response{
-Thank you for this idea!
+\response{Thank you for this idea!
 We believe that this is an interesting topic and we hope to investigate it in the future. 
@@
 
-\response{
-This is an excellent idea, and one that we have been interesting in addressing as well. 
+\response{This is an excellent idea, and one that we have been interesting in addressing as well. 
 Unfortunately, however, we do not have access to such data, at least not in large enough quantiaties to be representative. 
@@
 
-\subsection{ Details on \textit{word2vec} algorithm}
+\subsection{Details on \textit{word2vec} algorithm}
 We used standard skip-gram negative sampling word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec}.

### 2021-02-05 paper/rebuttal/rebuttal.tex
chang spacing
writing on problem on SVD and benfits of SGD

@@
 \definecolor{shadecolor}{RGB}{210, 210, 210}
-\setlength{\parskip}{0.6em}
 
@@
 \end{itemize}
+\setlength{\parskip}{0.6em}
 
@@
 \subsection{Result}
-\todo{report the results and say our results are better
-Why SGD has a lower performance and SGNS yield better performance
-power of stochastic gradient descent algorithm \autocite{smith2020generalization}}
-also, compare the speed?
+\todo{report the results and say our results are better @dakoda
+}
+
+% why sgd is better?
+An issue in the matrix factorization approach is that it is extremely sensitive to small flows between affiliations.
+The matrix factorization approach embeds affiliations $i$ and $j$ such that their dot similarity is as close as to $\log (T_{ij} / P(i) P(j))$.
+If the flow $T_{ij}$ is considerably small or zero, the dot similarity goes $-\infty$, pushing $i$ and $j$ too far from the other affiliations in the embedding space~\autocite{levy2014neural, Qui2018}.
+This is particularly problematic when the window size is small because most affiliation pairs would have no flow, which is indeed the case in our experiments.
+To circumvent this problem, the previous studies~\autocite{levy2014neural, Qui2018} add a constant flow between the affiliation pairs with no flow.
+However, this changes the data to which we fit the model, and small flows still have a considerably strong impact on the embedding.
+
+Also, it is well known that SVD by itself is very vulnerable to outliers \autocite{ xu2012robust, huber1981robust, xu1995robust, chandrasekaran2011rank, candes2011robust, }.
+Compared to SVD, a stochastic gradient descent algorithm (SGD) which is employed in SGNS \textit{word2vec} benefits from the noise in the model itself and can enhance generalization and effectiveness as well \autocite{ma2018power, smith2020generalization, zhang2019algorithmic,}.
 

### 2021-02-05 paper/rebuttal/rebuttal.tex
added header to rebuttal letter
update comment macro
added cover page letter

@@
 \setlength{\parindent}{0em}
+\setlength{\parskip}{0.5em}
 
@@
 
+%
+% HEADER
+%
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+\lhead{Nature---Response to Reviews}
+\rhead{\thepage}
+\chead{}
+
 \DeclareUnicodeCharacter{FB01}{fi}
@@
 \newcommand{\del}[1]{{\leavevmode\color{red}\sout{#1}}}
-\newcommand{\response}[1]{{\noindent #1}}
+\newcommand{\response}[1]{{\noindent \textbf{Response:} \\ \\ \noindent #1}}
 %\newcommand{\rcomment}[1]{{\bigskip\begin{snugshade}\begin{quotation}\noindent #1 \end{quotation}\end{snugshade} }}
@@
 \makeatother
-\title{Response to the review of submission\\  ``Unsupervised embedding of trajectories captures the latent structure of mobility''}
+\title{Re: Nature submission 2020-10-19515}
 \date{}
@@
 
-\noindent Dear Dr.editorname and Refrees,
+\bigskip
+\noindent Dear Dr. Mary Elizabeth Sutherland and Referees, \\
 
-We would like to thank all Referees for their incredibly helpful and insight comments which have helped to improve the quality of our manuscript.
-In the following, we provide detailed responses to the issues raised by each Referee.
-A version of our manuscript with changes annotated has also been provided to highlight changes made.
-\todo{write a letter}
+We thank all the referees for their incredibly thoughtful and helpful comments and critiques, all of which provided valuable insights. 
+Following these comments, we have made a breakthrough in our study, and have made substantial revisions to our manuscript to emphasize these new theoretical contributions and additional methodological comparisons.
+With these changes, we are confident that our paper is significantly stronger, and its contribution more wide-reaching and impactful. 
+Again, we are incredibly appreciative of these comments, which provided the insight and motivation needed to make these breakthroughs.
 
+We have developed the mathematical and theoretical basis of our approach for embedding mobility, and made additional updates to our experiments and manuscript, addressing the three main issues raised by referees:
+
+\begin{enumerate}
+    \itemsep0em 
+	\item Our approach and analysis lacked theoretical justification and grounding, and the application of \textit{word2vec} to mobility was arbitrary
+	\item Performance of \textit{word2vec} is not well understood in the context of other, simpler embedding techniques
+	\item Our findings were not sufficiently grounded in the literature of neural embeddings and mobility
+\end{enumerate}
+
+Addressing the first point, we have identified an underlying mathematical connection between the Gravity Model of Mobility and the neural embedding technique \textit{word2vec}. 
+Namely, we demonstrate that \textit{word2vec} implicitly learns gravity-like relationships between entities, whether it be language or locations. 
+This development constitutes a major breakthrough in our understanding of neural embeddings, and provides theoretical justification for their application to mobility.
+
+For the second point, we have also conducted experiments comparing the performance of neural embedding to distances from an embedding derived by a singular value decomposition of the mobility network, and of a Laplacian eigenmap embedding.
+Additionally, we compare \textit{word2vec} model to another matrix factorization approach, which \textit{word2vec} approximates.
+We find that the embedding distance from \textit{word2vec} outperforms all baselines in explaining and predicting real-world mobility.
+
+Finally, addressing the third point, we take steps to better ground our manuscript in the existing literature, integrating the reviewer's suggested articles into our manuscript.
+
+In the attached detailed response, we outline the connection between \textit{word2vec} and the gravity model (section 1), and comparisons to baselines (section 2).
+We then provide a point-by-point response to each of the reviewer's comments in section 3.
+
+We thank you for your time, attention, and insight, and look forward to hearing back from you!\\
+
+\\Kind Regards,\\
+
+Dakota, Jisung, Sadamori, Rodrigo, Woo-Sung, Staša, and YY
+
+\clearpage
 \tableofcontents

### 2021-02-05 paper/rebuttal/rebuttal.tex
re-oganize, bringing changes to front, flesh out math section

@@
 
-\\Kind Regards,\\
+Kind Regards,
 
@@
 \listoffigures
+\clearpage
 
-\section{List of changes}
+\section{Theoretical justification of \textit{word2vec} and the Gravity Model} 
+Here, we attempt to answer a question raised from our analysis: Why does the skip-gram model with negative sampling (SGNS), otherwise known as \textit{word2vec}, work so well to model human mobility?
+We demonstrate a fundamental connection between the SGNS model and the Gravity Model of Mobility, namely, that SGNS implicitly learns gravity-like relationships between locations. 
+This connection provides necessary theoretical justification to our choice of \textit{word2vec}, and constitutes a major breakthrough of our understanding of neural embeddings. 
+In addition, this motivates the use of SGNS for future study of human mobility.
 
-We have broken down the list of changes to the manuscript by referee.
+First, we outline of the \textit{word2vec} model. 
+Then, we introduce the specific SGNS model, which incorperates a procedure called negative sampling that is key to its connection with the gravity model. 
+Finally, we demonstrate the connection between SGNS and the gravity model of mobility.
 
+\subsection{Details on \textit{word2vec} algorithm}
+We used standard skip-gram negative sampling word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec}.
+Suppose a trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), where $a_{t}$ is the $t$th location in the trajectory.
+A location, $a_{t}$, is considered to have context locations, $a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}$, that appear in the window surrounding $a_t$ up to a time lag of $w$, where $w$ is the window size parameter truncated at $t - w \geq 0$ and $t + w \leq T$.
+Then, the model learns probability $p(a_{t + \tau} \vert a_{t})$, where $-w\leq \tau\leq w$ and $\tau \neq 0$,  by maximizing its log likelihood given by
+%
+% MAIN W2V Equation
+%
+\begin{equation}
+	\frac{1}{T}\sum_{t = 1}^{T} \sum_{-w \leq \tau \leq w, \tau \neq 0} \log p(a_{t + \tau} \vert a_{t}),
+\end{equation}
+where,
+
+%
+% CONDITIONAL PROBABILITY EQ
+%
+\begin{equation}
+	p(j \given i) = \frac{\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:cond_prob_w2v}
+\end{equation}
+where $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector", respectively,  $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
+In general, calculating $Z_i$ is computationally expensive and there are two common approximation:
+ hierarchical softmax \autocite{morin2005hierarchical} and negative sampling \autocite{mikolov2013word2vec}.
+
+\subsection{An implicit bias in the negative sampling}
+
+In our paper, we employed a specific algorithm SGNS word embedding.
+However, it is well known that the negative sampling is a biased estimator~\autocite{Chia2010,Dyer2014} that optimizes a distinct model  from {\it word2vec}.
+
+Negative sampling trains {\it word2vec} using a binary classification task as follows.
+A center-context word pair $(i,j)$ is sampled from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$ are sampled from a noise distribution $p_0(\ell)=P^\gamma(\ell)$.
+($P(j)$ is the fraction of $j$ in the data, and $\gamma>0$ is a parameter).
+Then, given a center-context word pair $(i,j)$, the model predicts whether it is a positive or negative sample using sigmoid function:
+\begin{align}
+	\label{eq:sigmoid}
+	\frac{1}{1 + \exp\left( - \bm{u}_j \cdot \bm{v}_i \right)}.
+\end{align}
+
+This procedure does not guarantee that the embedding optimally converges to the original conditional probability eq.\ref{eq:cond_prob_w2v}, even when increasing the training samples and iterations~\autocite{Chia2010,Dyer2014} in the fact that negative sampling has implicit bias.
+This problem is addressed by the noise contrastive estimation (NCE) \autocite{Chia2010}, which fits a probability model in the form:
+\begin{align}
+	\label{eq:nce}
+	f(x) / \sum_{x'} f(x'),
+\end{align}
+where $f(x)$ is the unnormalized probability for an instance $x$.
+As in negative sampling, NCE fits the model based on a binary classification task, with positive and negative samples randomly drawn from the given data and a noise distribution $p_0$, respectively, using a bias-corrected sigmoid function:
+\begin{align}
+	\label{eq:sigmoid2}
+	\frac{1}{1 + \exp\left( -f(x) + \log p_0(x) \right)}.
+\end{align}
+
+Rewriting the sigmoid function for the negative sampling (Eq.~\eqref{eq:sigmoid}) in form of the bias-corrected sigmoid function yields
+\begin{align}
+	\label{eq:sigmoid3}
+	\frac{1}{1 + \exp\left[ - \tilde f(x) + \log p_0(x)  \right]},
+\end{align}
+where we have defined
+\begin{align}
+	\label{eq:unnormalized}
+	\tilde f(x) = f(x) p_0(x).
+\end{align}
+So, the model with the negative sampling optimize $\tilde f(x)$, not $f(x)$.
+In case of the {\it word2vec}, the instance is the dot similarity $x=\bm{u}_i \cdot \bm{v}_j$,  $f(x)=\exp(x)$, and $p_0(j)=P^\gamma(j)$, and the SGNS word2vec actually optimize the following conditional probability:
+\begin{align}
+	P\left(j \given i \right):= \frac{P^\gamma (j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{\widetilde{Z_i}},
+	\label{eq:real_cond}
+\end{align}
+where $\widetilde {Z_i}=\sum_{j' \in \mathcal{A}} P^\gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
+
+\subsection{\textit{word2vec} and the gravity model}
+
+Taking into an implicit bias in the negative sampling  and set $w=1$, the \textit{word2vec} predict the flow with
+\begin{align}
+\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)P^\gamma (j)\exp(\bm{v}_j \cdot \bm{v}_{i})}{Z_i}. \label{eq:prob_w2v_ng0}
+\end{align}
+where  $\widetilde{Z_i}=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
+
+Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimial in-vectors and out-vectors such that $\bm{u}_i = \bm{v}_i$ \autocite{levy2014neural}.
+Setting $\gamma = 1$ and substituting $\bm{u}_i = \bm{v}_j$ into Eq.~\eqref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
+\begin{align}
+	\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)P(j)\exp(\bm{v}_j \cdot \bm{v}_{i})}{Z_i}. \label{eq:flow_w2v_ng1}
+\end{align}
+
+The flow $\hat{T_{ij}}$ is symmetric (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because {\it word2vec} neglects whether the context $j$ appears before or after the center $i$ in the trajectory -- the mechanism of skip-gram.
+If we swap $i$ and $j$ in Eq.~\eqref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
+Therefore, to ensure $T_{ij} = T_{ji}$, the denominator $Z_i$ should be a constant.
+
+Taken altogether, the {\it word2vec} model with the negative sampling predicts a flow in the same form as in the gravity model:
+\begin{align}
+	\hat{T_{ij}}=  C P(i) P(j)  \exp(\bm{v}_j \cdot \bm{v}_{i}), \label{eq:flow_w2v_ng0}
+\end{align}
+where $C$ is a positive constant.
+
+In other words, \emph{word2vec with the negative sampling is a gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
+While the gravity model generates the flow from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given trajectories.
+Therefore, the embedding distance is inherently tied to the flow, and hence, has greater predictive power than the geographic distance.
+
+\subsection{Some concerns on this section??}
+\todo{Why cosine similarity is better? Add speculation sentence to paper}
+One open question that remains is why the cosine distance between vectors leads to better performance than the dot product, which is what the formla~\ref{eq:flow_w2v_ng0} expect....
+
+\todo{In-vector and out-vectors are different in our result, add something to paper}
+Another deviation in our implementation of \textit{word2vec} to mobility is that the in-vector and out-vector is different in out result, whereas they are assumed to be the same in the above derivations...
+
+\subsection{Changes to the manuscript}
+\todo{detail addition of above formulas}
+\todo{add sentences to paper concerning above issues/speculations, concerns}
+\todo{mention re-doing figures with $\gamma = 1$}
+
+%
+% SECTION-PERFORMANCE COMPARISONS
+%
+\section{Performance of \textit{word2vec} compared with baselines}
+\subsection{The method we have used for the test}
+We list baselines that we have used for the validation. For embedding baselines, we set $d=300$ for the pair comparison.\\\\
+\textbf{SVD-based embedding baselines}
 \begin{itemize}
-\item \textbf{Referee 1} 
+    \item Truncated SVD on the flow matrix
+	\item  Laplacian eigenmap
+	\item Levy's word2vec
+\end{itemize}
+\textbf{Network-based baselines}
 \begin{itemize}
-        \item blah
-        \item blah
+    \item Personalized Page Rank
 \end{itemize}
-\item \textbf{Referee 2} 
-     \begin{itemize} 
-        \item blah
-        \item blah
-     \end{itemize}
-\item \textbf{Referee 3} 
-     \begin{itemize} 
-        \item blah
-        \item blah
-     \end{itemize}
- \item \textbf{Referee 4} 
-     \begin{itemize} 
-        \item blah
-        \item blah
-     \end{itemize}
-\end{itemize}
-\setlength{\parskip}{0.6em}
+\textbf{Geographical baselines}
 
+\subsection{Result}
+\todo{report the results and say our results are better @dakoda
+}
+
+% why sgd is better?
+An issue in the matrix factorization approach is that it is extremely sensitive to small flows between affiliations.
+The matrix factorization approach embeds affiliations $i$ and $j$ such that their dot similarity is as close as to $\log (T_{ij} / P(i) P(j))$.
+If the flow $T_{ij}$ is considerably small or zero, the dot similarity goes $-\infty$, pushing $i$ and $j$ too far from the other affiliations in the embedding space~\autocite{levy2014neural, Qui2018}.
+This is particularly problematic when the window size is small because most affiliation pairs would have no flow, which is indeed the case in our experiments.
+To circumvent this problem, the previous studies~\autocite{levy2014neural, Qui2018} add a constant flow between the affiliation pairs with no flow.
+However, this changes the data to which we fit the model, and small flows still have a considerably strong impact on the embedding.
+
+Also, it is well known that SVD by itself is very vulnerable to outliers \autocite{ xu2012robust, huber1981robust, xu1995robust, chandrasekaran2011rank, candes2011robust, }.
+Compared to SVD, a stochastic gradient descent algorithm (SGD) which is employed in SGNS \textit{word2vec} benefits from the noise in the model itself and can enhance generalization and effectiveness as well \autocite{ma2018power, smith2020generalization, zhang2019algorithmic,}.
+
+%
+% SECTION- \POINT-BY-POINT DISCUSSION
+%
 \section{Point-by-point discussion}
@@
 
-\section{Theoretical justification of \textit{word2vec} and the Gravity Model} 
-In here, we would like to answer a question: why we use SGNS algorithms and is there any theoretical justification on that? This document details:
-\begin{enumerate}
-	\item Details on \textit{word2vec} algorithm
-	\item An implicit bias in the negative sampling
-	\item \textit{word2vec} and the gravity model
-
-\end{enumerate}
-
-\subsection{Details on \textit{word2vec} algorithm}
-We used standard skip-gram negative sampling word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec}.
-Suppose a trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), where $a_{t}$ is the $t$th location in the trajectory.
-A location, $a_{t}$, is considered to have context locations, $a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}$, that appear in the window surrounding $a_t$ up to a time lag of $w$, where $w$ is the window size parameter truncated at $t - w \geq 0$ and $t + w \leq T$.
-Then, the model learns probability $p(a_{t + \tau} \vert a_{t})$, where $-w\leq \tau\leq w$ and $\tau \neq 0$,  by maximizing its log likelihood given by
-%
-% MAIN W2V Equation
-%
-\begin{equation}
-	\frac{1}{T}\sum_{t = 1}^{T} \sum_{-w \leq \tau \leq w, \tau \neq 0} \log p(a_{t + \tau} \vert a_{t}),
-\end{equation}
-where,
-
-%
-% CONDITIONAL PROBABILITY EQ
-%
-\begin{equation}
-	p(j \given i) = \frac{\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:cond_prob_w2v}
-\end{equation}
-where $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector", respectively,  $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
-In general, calculating $Z_i$ is computationally expensive and there are two common approximation:
- hierarchical softmax \autocite{morin2005hierarchical} and negative sampling \autocite{mikolov2013word2vec}.
-
-\subsection{An implicit bias in the negative sampling}
-
-In our paper, we employed a specific algorithm SGNS word embedding.
-However, it is well known that the negative sampling is a biased estimator~\autocite{Chia2010,Dyer2014} that optimizes a distinct model  from {\it word2vec}.
-
-Negative sampling trains {\it word2vec} using a binary classification task as follows.
-A center-context word pair $(i,j)$ is sampled from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$ are sampled from a noise distribution $p_0(\ell)=P^\gamma(\ell)$.
-($P(j)$ is the fraction of $j$ in the data, and $\gamma>0$ is a parameter).
-Then, given a center-context word pair $(i,j)$, the model predicts whether it is a positive or negative sample using sigmoid function:
-\begin{align}
-	\label{eq:sigmoid}
-	\frac{1}{1 + \exp\left( - \bm{u}_j \cdot \bm{v}_i \right)}.
-\end{align}
-
-This procedure does not guarantee that the embedding optimally converges to the original conditional probability eq.\ref{eq:cond_prob_w2v}, even when increasing the training samples and iterations~\autocite{Chia2010,Dyer2014} in the fact that negative sampling has implicit bias.
-This problem is addressed by the noise contrastive estimation (NCE) \autocite{Chia2010}, which fits a probability model in the form:
-\begin{align}
-	\label{eq:nce}
-	f(x) / \sum_{x'} f(x'),
-\end{align}
-where $f(x)$ is the unnormalized probability for an instance $x$.
-As in negative sampling, NCE fits the model based on a binary classification task, with positive and negative samples randomly drawn from the given data and a noise distribution $p_0$, respectively, using a bias-corrected sigmoid function:
-\begin{align}
-	\label{eq:sigmoid2}
-	\frac{1}{1 + \exp\left( -f(x) + \log p_0(x) \right)}.
-\end{align}
-
-Rewriting the sigmoid function for the negative sampling (Eq.~\eqref{eq:sigmoid}) in form of the bias-corrected sigmoid function yields
-\begin{align}
-	\label{eq:sigmoid3}
-	\frac{1}{1 + \exp\left[ - \tilde f(x) + \log p_0(x)  \right]},
-\end{align}
-where we have defined
-\begin{align}
-	\label{eq:unnormalized}
-	\tilde f(x) = f(x) p_0(x).
-\end{align}
-So, the model with the negative sampling optimize $\tilde f(x)$, not $f(x)$.
-In case of the {\it word2vec}, the instance is the dot similarity $x=\bm{u}_i \cdot \bm{v}_j$,  $f(x)=\exp(x)$, and $p_0(j)=P^\gamma(j)$, and the SGNS word2vec actually optimize the following conditional probability:
-\begin{align}
-	P\left(j \given i \right):= \frac{P^\gamma (j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{\widetilde{Z_i}},
-	\label{eq:real_cond}
-\end{align}
-where $\widetilde {Z_i}=\sum_{j' \in \mathcal{A}} P^\gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
-
-\subsection{\textit{word2vec} and the gravity model}
-
-Taking into an implicit bias in the negative sampling  and set $w=1$, the \textit{word2vec} predict the flow with
-\begin{align}
-\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)P^\gamma (j)\exp(\bm{v}_j \cdot \bm{v}_{i})}{Z_i}. \label{eq:prob_w2v_ng0}
-\end{align}
-where  $\widetilde{Z_i}=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
-
-Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimial in-vectors and out-vectors such that $\bm{u}_i = \bm{v}_i$ \autocite{levy2014neural}.
-Setting $\gamma = 1$ and substituting $\bm{u}_i = \bm{v}_j$ into Eq.~\eqref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
-\begin{align}
-	\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)P(j)\exp(\bm{v}_j \cdot \bm{v}_{i})}{Z_i}. \label{eq:flow_w2v_ng1}
-\end{align}
-
-The flow $\hat{T_{ij}}$ is symmetric (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because {\it word2vec} neglects whether the context $j$ appears before or after the center $i$ in the trajectory -- the mechanism of skip-gram.
-If we swap $i$ and $j$ in Eq.~\eqref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
-Therefore, to ensure $T_{ij} = T_{ji}$, the denominator $Z_i$ should be a constant.
-
-Taken altogether, the {\it word2vec} model with the negative sampling predicts a flow in the same form as in the gravity model:
-\begin{align}
-	\hat{T_{ij}}=  C P(i) P(j)  \exp(\bm{v}_j \cdot \bm{v}_{i}), \label{eq:flow_w2v_ng0}
-\end{align}
-where $C$ is a positive constant.
-
-In other words, \emph{word2vec with the negative sampling is a gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
-While the gravity model generates the flow from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given trajectories.
-Therefore, the embedding distance is inherently tied to the flow, and hence, has greater predictive power than the geographic distance.
-
-\subsection{Some concerns on this section??}
-\todo{
-Why cosine similarity is better? In-vector and out-vectors are different in our result}
-
-\section{Performance of \textit{word2vec} compared with baselines}
-\subsection{The method we have used for the test}
-We list baselines that we have used for the validation. For embedding baselines, we set $d=300$ for the pair comparison.\\\\
-\textbf{SVD-based embedding baselines}
-\begin{itemize}
-    \item Truncated SVD on the flow matrix
-	\item  Laplacian eigenmap
-	\item Levy's word2vec
-\end{itemize}
-\textbf{Network-based baselines}
-\begin{itemize}
-    \item Personalized Page Rank
-\end{itemize}
-\textbf{Geographical baselines}
-
-\subsection{Result}
-\todo{report the results and say our results are better @dakoda
-}
-
-% why sgd is better?
-An issue in the matrix factorization approach is that it is extremely sensitive to small flows between affiliations.
-The matrix factorization approach embeds affiliations $i$ and $j$ such that their dot similarity is as close as to $\log (T_{ij} / P(i) P(j))$.
-If the flow $T_{ij}$ is considerably small or zero, the dot similarity goes $-\infty$, pushing $i$ and $j$ too far from the other affiliations in the embedding space~\autocite{levy2014neural, Qui2018}.
-This is particularly problematic when the window size is small because most affiliation pairs would have no flow, which is indeed the case in our experiments.
-To circumvent this problem, the previous studies~\autocite{levy2014neural, Qui2018} add a constant flow between the affiliation pairs with no flow.
-However, this changes the data to which we fit the model, and small flows still have a considerably strong impact on the embedding.
-
-Also, it is well known that SVD by itself is very vulnerable to outliers \autocite{ xu2012robust, huber1981robust, xu1995robust, chandrasekaran2011rank, candes2011robust, }.
-Compared to SVD, a stochastic gradient descent algorithm (SGD) which is employed in SGNS \textit{word2vec} benefits from the noise in the model itself and can enhance generalization and effectiveness as well \autocite{ma2018power, smith2020generalization, zhang2019algorithmic,}.
-
 \clearpage

### 2021-02-05 paper/rebuttal/rebuttal.tex
add "alternatives considered" text to rebuttal

@@
 \section{Performance of \textit{word2vec} compared with baselines}
-\subsection{The method we have used for the test}
-We list baselines that we have used for the validation. For embedding baselines, we set $d=300$ for the pair comparison.\\\\
-\textbf{SVD-based embedding baselines}
-\begin{itemize}
-    \item Truncated SVD on the flow matrix
-	\item  Laplacian eigenmap
-	\item Levy's word2vec
-\end{itemize}
-\textbf{Network-based baselines}
-\begin{itemize}
-    \item Personalized Page Rank
-\end{itemize}
-\textbf{Geographical baselines}
+\subsection{Alternatives considered}
+In our original manuscript, we compared the performance of what we call the embedding distance---the cosine distance between vectors learned by \textit{word2vec}---to a range of alternatives. 
+These alternatives included the geographic distance between locations, the distance most commonly used in definitions of the gravity model of mobility, along with the dot product similarity between embedding vectors, and the cosine distance and Jensen-Shannon divergence between vectors obtained from a personalized-page-ranking procedure on the underlying mobility network.
+
+Following the advice of the referees, we also add additional baselines to illustrate how the embedding distance performs compared to simpler embedding alternatives. 
+The first of these baselines uses the distance between vectors in an embedding space produced through a singular-value decomposition of the underlying location co-occurrence matrix.
+The second baseline is the distance between vectors obtained through a Laplacian eigenmap embedding of the location of the matrix.
+
+In addition to these suggested baselines, we also consider distances derived from embeddings learned through matrix factorization following the procedure outlined by Levy \& Goldberg~\autocite{levy2014neural}.
+The \textit{word2vec} model  implicitly approximates this matrix-factorization procedure, and so comparison to these ``Levy'' distances can demonstrate whether the approximation of neural embeddings outperform direct-calculations.
 

### 2021-02-05 paper/rebuttal/rebuttal.tex
working with comment labels, not perfect, but better

@@
 
+%
+% COLORBOX
+%
+\usepackage{tcolorbox}
+\tcbuselibrary{breakable}
+\newtcolorbox[auto counter, 				  
+					  number within=subsection,
+ 				       list type=subsubsection, 
+ 				       list inside=toc]{sectionbox}[1]{colback=white, 
+ 				       												colframe=black, 
+ 				       												colbacktitle=white!50!gray,
+ 				       												coltitle=black,
+ 				       												fonttitle=\bfseries, title={Comment \thetcbcounter}, 
+ 				       												list entry={Comment \thetcbcounter\quad}, breakable}
+
 \DeclareUnicodeCharacter{FB01}{fi}
@@
 
-\usepackage[most]{tcolorbox}
+%\usepackage[most]{tcolorbox}
 \newcommand{\sada}[1]{{\leavevmode\color{orange}[SK: #1]}}
@@
 \vspace{10pt}
-\begin{tcolorbox}[colback=black!3,colframe=white!45!black, left=0pt, right=0pt, top=0pt, bottom=0pt, arc=0pt,outer arc=0pt, grow to left by=-0.5cm,grow to right by=-0.5cm]
+\begin{sectionbox}
 #1
-\end{tcolorbox}
+\end{sectionbox}
 }
@@
 \bigskip
-\noindent Dear Dr. Mary Elizabeth Sutherland and Referees, \\
+\noindent Dear Dr. Sutherland and Referees, \\
 
@@
 \subsection{Changes to the manuscript}
-\todo{detail addition of above formulas}
-\todo{add sentences to paper concerning above issues/speculations, concerns}
-\todo{mention re-doing figures with $\gamma = 1$}
+To reflect these breakthroughs, we have made the following changes to the manuscript:
+\begin{itemize}
+	\itemsep0em
+	\item Following results demonstrating the performance of the embedding distance compared to geographic distance, we add the section \textbf{word2vec and the gravity model}, which summarizes the link between the two models.
+	\item We also added the section \textbf{An implicit bias in the negative sampling} to the methods section of our manuscript.
+	\item Since the formulation of the gravity used in the above derivations assumes $\gamma = 1$, we use this value of $gamma$ for all reported results. No result substantively changes with this change.
+	\item \todo{We added a sentence to the paper speculating on why cosine similarity works best}
+	\item \todo{We also added a sentence noting the in-vector and out-vector issue, and speculating on reasons/consequences}
+\end{itemize}
 
@@
 
+\subsection{New experimental parameters}
+In addition to the new baselines, we have also incorporate additional experimental parameters into our analysis. 
+The first is $\gamma$, a hyper-parameter of the \textit{word2vec} model, which defines the exponent which shapes the negative sampling distribution.
+The default of the `\texttt{gensim} implementation of \textit{word2vec} is to set $\gamma = 0.75$, and this was the value used in our original manuscript. 
+However, to connect \textit{word2vec} to the gravity model of mobility, we assume $\gamma = 1.0$ (see section 1). 
+We now report all main results using $\gamma = 1.0$, however we also compare its performance to embeddings learned using $\gamma = 0.75$, as we do with the number of embedded dimensions and window size.
+
+We also consider an experimental parameter differentiating between definitions of \textit{population}, in the context of scientific mobility. 
+Our original manuscript defined the population of an organization as its average annual number of unique mobile and non-mobile authors who publish with that organizational affiliation. 
+However, because non-mobile authors do not have mobility trajectories, and are thus not included in training of the embedding, this definition of population introduces additional, potentially confounding information into the experiment.
+To tease apart the impact of population definitions, we consider two additional definitions.
+The first defines an organization's population as the average annual number of unique mobile authors, only, who publish with the organization. 
+The second definition defines the population akin to language, as simply its frequency across all mobility trajectories.
+
 \subsection{Result}
@@
 
-% why sgd is better?
+\subsection{Why do neural embeddings outperform direct matrix factorization?}% why sgd is better?
 An issue in the matrix factorization approach is that it is extremely sensitive to small flows between affiliations.
@@
 %
-% SECTION- \POINT-BY-POINT DISCUSSION
+% SECTION- POINT-BY-POINT DISCUSSION
 %
@@
 
-\bigskip
-\response{In summary, we have updated the manuscript by providing the appropriate context in the literature, clarifying the limitations of our study, and extending our approach to incorporate delays in contact tracing.
-We deeply appreciate the Referee's careful reading of the paper and their constructive comments.
-%We hope that have correctly addressed the Referee's concerns and comments.
-}
-
 %===================================================
 
+%
+% Response to reviewer 2
+%
 \subsection{Response to Referee 2}

### 2021-02-08 paper/rebuttal/rebuttal.tex
amend missing first charcater
about the gap between math and simulations

@@
 \begin{sectionbox}
-#1
+s #1
 \end{sectionbox}
@@
 
-\subsection{Some concerns on this section??}
-\todo{Why cosine similarity is better? Add speculation sentence to paper}
-One open question that remains is why the cosine distance between vectors leads to better performance than the dot product, which is what the formla~\ref{eq:flow_w2v_ng0} expect....
+\subsection{Gap between the mathematical analysis and numerical simulations}
 
-\todo{In-vector and out-vectors are different in our result, add something to paper}
-Another deviation in our implementation of \textit{word2vec} to mobility is that the in-vector and out-vector is different in out result, whereas they are assumed to be the same in the above derivations...
+In the mathematical analysis, we assumed that the embedding vectors are optimal in terms of the objective of {\it word2vec}, which, however, is not true in our numerical simulations.
+This violation of assumption leads to two substantial consequences for embedding vectors.
+First, although there exist optimal in-vector and out-vector that are identical, the in-vector and out-vector can be different in practice because they are sub-optimal.
+Second, while dot similarity is a formal distance measure in terms of its connection to the gravity model, our simulations show that dot similarity did not predict mobility flow better than cosine similarity (Figs.~\ref{fig:supp:distancemetrics} and \ref{fig:supp:distancemse}).
+It has been widely observed that cosine similarity is generally better than dot similarity in many applications of word embedding~\cite{} [Jisung, could you add citations?].
+Therefore, the superiority of cosine similarity is not a problem specific but general feature of word embedding.
+Nevertheless, dot similarity is the second best predictor among the 7 embedding distances. What makes cosine similarity superior to dot similarity warrants the future work.
 

### 2021-02-09 paper/rebuttal/rebuttal.tex
replaced "" with ``''

@@
 \end{equation}
-where $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector", respectively,  $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
+where $\bm{v}$ and $\bm{u}$ are the ``in-vector'' and ``out-vector'', respectively,  $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
 In general, calculating $Z_i$ is computationally expensive and there are two common approximation:
@@
 	\begin{itemize}
-		\item Liu, Xin, Yong Liu, and Xiaoli Li. "Exploring the Context of Locations for Personalized Location Recommendations." IJCAI. 2016.
-		\item Feng, Shanshan, et al. "POI2Vec: geographical latent representation for predicting future visitors." AAAI. 2017.
-		\item Yao, Zijun, et al. "Representing Urban Functions through Zone Embedding with Human Mobility Patterns." IJCAI. 2018.
-		\item Cao, Hancheng, et al. "Habit2vec: Trajectory semantic embedding for living pattern recognition in population." IEEE Transactions on Mobile Computing 19.5 (2019): 1096-1108.
+		\item Liu, Xin, Yong Liu, and Xiaoli Li. ``Exploring the Context of Locations for Personalized Location Recommendations.'' IJCAI. 2016.
+		\item Feng, Shanshan, et al. ``POI2Vec: geographical latent representation for predicting future visitors.'' AAAI. 2017.
+		\item Yao, Zijun, et al. ``Representing Urban Functions through Zone Embedding with Human Mobility Patterns.'' IJCAI. 2018.
+		\item Cao, Hancheng, et al. ``Habit2vec: Trajectory semantic embedding for living pattern recognition in population.'' IEEE Transactions on Mobile Computing 19.5 (2019): 1096-1108.
 	\end{itemize}
@@
 
-	\noindent “We however, note that all results shown here are robust to this stochasticity, likely emerging from the limited "vocabulary" of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories).
+	\noindent “We however, note that all results shown here are robust to this stochasticity, likely emerging from the limited ``vocabulary'' of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories).
 Applications of word2vec to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random artifacts.”
@@
 	In your particular example, an embedding distance trained using sequences of co-authorship on the same paper might be better to capture the \textit{collaborative} distance between institutions.
-	Then, using that distance, one could measure the "embedding distance" spanned by all authors in the byline, and relate this to questions impact to determine whether (a)typical collaborations relate to impact.
+	Then, using that distance, one could measure the ``embedding distance'' spanned by all authors in the byline, and relate this to questions impact to determine whether (a)typical collaborations relate to impact.
 	This is certainly a topic that is in our mind for future study.
-	In the case of scientific mobility, we might also consider the "embedding distance" spanned by an individual's career, and relate this to their demographics and scientific impact.
+	In the case of scientific mobility, we might also consider the ``embedding distance'' spanned by an individual's career, and relate this to their demographics and scientific impact.
 

### 2021-02-09 paper/rebuttal/rebuttal.tex
reflecting yy's comment

@@
 
-Addressing the first point, we have identified an underlying mathematical connection between the Gravity Model of Mobility and the neural embedding technique \textit{word2vec}.
-Namely, we demonstrate that \textit{word2vec} implicitly learns gravity-like relationships between entities, whether it be language or locations.
+Addressing the first point, we have identified an underlying mathematical equivalence between the Gravity Model of Mobility and the neural embedding technique \textit{word2vec}.
+Namely, we demonstrate that \textit{word2vec} 's objective function is same as the gravity law and thus \textit{word2vec} learns gravity-like relationships between entities, whether it be language or locations.
 This development constitutes a major breakthrough in our understanding of neural embeddings, and provides theoretical justification for their application to mobility.
@@
 \section{Theoretical justification of \textit{word2vec} and the Gravity Model}
-Here, we attempt to answer a question raised from our analysis: Why does the skip-gram model with negative sampling (SGNS), otherwise known as \textit{word2vec}, work so well to model human mobility?
+Here, we answer a following question:å Why does the skip-gram model with negative sampling (SGNS), otherwise known as \textit{word2vec}, work so well to model human mobility?
 We demonstrate a fundamental connection between the SGNS model and the Gravity Model of Mobility, namely, that SGNS implicitly learns gravity-like relationships between locations.
@@
 
-First, we outline of the \textit{word2vec} model.
+First, we outline  \textit{word2vec} model.
 Then, we introduce the specific SGNS model, which incorperates a procedure called negative sampling that is key to its connection with the gravity model.
@@
 \subsection{Details on \textit{word2vec} algorithm}
-We used standard skip-gram negative sampling word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec}.
+We used the standard skip-gram negative sampling (SGNS) word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec}.
 Suppose a trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), where $a_{t}$ is the $t$th location in the trajectory.
@@
 	However, we recognize that p-values can help readers interpret results.
-	As such, we have opted to add to a sentence such as \say{\textit{Correlation is calculated on the data in the log-log scale ($p < 0.0001$ across all fits)}.} or similar to relevant figures in the main text and supporting materials.
+	As such, we have opted to add to a sentence such as \say{\textit{Correlation is calculated on the data in the log-log scale ($p <<0.0001$ across all fits)}.} or similar to relevant figures in the main text and supporting materials.
 	We believe that this solution strikes a balance between transparency while also avoiding extraneous detail and the common pitfalls of statistical reporting.
@@
 	We carefully read out the Barthélemy, Physics Reports 499, 1, 2011, and referenced it in our manuscript.
-	Also, we report the performance of the flux estimation (Fig.~\ref{fig:supp:distancemetrics}, this document) and prediction (Fig.~\ref{fig:supp:distancermse}, this document) using different deterrence functions, funding that while performance differs, that the embedding distance outperforms geographic
+	Also, we report the performance of the flux estimation (Fig.~\ref{fig:supp:distancemetrics}, this document) and prediction (Fig.~\ref{fig:supp:distancermse}, this document) using different deterrence functions, founding that while performance differs, that the embedding distance outperforms geographic
 	distance no matter the function used.
@@
 	\say{The decay function $f(r_{ij})$ defines the effect of distance, and so different decay functions can model fundamentally different mechanism [...] such as the cost functions for a given distance and the spatial granularity of the observation.
-		For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case.
-though the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Supporting Information).}
+		For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case though the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Supporting Information).}
 	\medskip
 
-	We also argue that geographical distance ﬁts well with the power-law decay function because it is is more suitable for analyzing large, complex, and scale-free spatial systems , while embedding distance ﬁts well with the exponential decay function, which we demonstrate to correspond to an underlying mathematical relationship between \textit{word2vec} and the gravity model, a connection we recently discovered and included as a major finding in this revision (see our response to Referee 1).
+	We also argue that geographical distance ﬁts well with the power-law decay function because power-based gravity model can be more suitable for analyzing large, complex, and scale-free spatial systems and the exponential-based gravity model indicates simplicty rather than spatial complexity~\autocite{chen2015distance}.
+Meanwhile, embedding distance ﬁts well with the exponential decay function, which we demonstrate to correspond to an underlying mathematical relationship between \textit{word2vec} and the gravity model, a connection we recently discovered and included as a major finding in this revision (see our response to Referee 1).
 
@@
 	We believe hat this new discovery, not included in the manuscript (and illustrated below), justify our use of \textit{word2vec} here.
-	We agree that the revolution in neural embeddings offers great promise in mobility and look forward to reading and also working on these future studies; however we argue that our contribution is most well founded, and best serves the scientific community, by working with simpler and more established models, especially concerning the mathematical link we uncovered.
+
+	We agree that the revolution in neural embeddings offers great promise in mobility and look forward to reading and also working on these future studies; however, we argue that our contribution is most well-founded, and best serves the scientific community, by working with simpler and more established models, especially concerning the mathematical link we uncovered.
+Moreover, these deep models require a tremendous amount of training data ($\sim$3 billion words in Bert) and model parameters.
+
 	To highlight the importance of altenrative models, however, we add the following line to our conclusion: \say{\textit{Future studies may also consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality.
 }}.
-
-	\todo{Add complete theoretical discussion here}
 

### 2021-02-09 paper/rebuttal/rebuttal.tex
minor tweaks

--- 2021-02-08 paper/rebuttal/rebuttal.tex
@@
 \begin{sectionbox}
-s #1
+#1
 \end{sectionbox}
@@
 \section{Theoretical justification of \textit{word2vec} and the Gravity Model} 
+\label{sec:theory}
 Here, we attempt to answer a question raised from our analysis: Why does the skip-gram model with negative sampling (SGNS), otherwise known as \textit{word2vec}, work so well to model human mobility?
@@
 
-\subsection{Gap between the mathematical analysis and numerical simulations}
+\subsection{Some concerns on this section??}
+\todo{Why cosine similarity is better? Add speculation sentence to paper}
+One open question that remains is why the cosine distance between vectors leads to better performance than the dot product, which is what the formla~\ref{eq:flow_w2v_ng0} expect....
 
-In the mathematical analysis, we assumed that the embedding vectors are optimal in terms of the objective of {\it word2vec}, which, however, is not true in our numerical simulations.
-This violation of assumption leads to two substantial consequences for embedding vectors.
-First, although there exist optimal in-vector and out-vector that are identical, the in-vector and out-vector can be different in practice because they are sub-optimal.
-Second, while dot similarity is a formal distance measure in terms of its connection to the gravity model, our simulations show that dot similarity did not predict mobility flow better than cosine similarity (Figs.~\ref{fig:supp:distancemetrics} and \ref{fig:supp:distancemse}).
-It has been widely observed that cosine similarity is generally better than dot similarity in many applications of word embedding~\cite{} [Jisung, could you add citations?].
-Therefore, the superiority of cosine similarity is not a problem specific but general feature of word embedding.
-Nevertheless, dot similarity is the second best predictor among the 7 embedding distances. What makes cosine similarity superior to dot similarity warrants the future work.
+\todo{In-vector and out-vectors are different in our result, add something to paper}
+Another deviation in our implementation of \textit{word2vec} to mobility is that the in-vector and out-vector is different in out result, whereas they are assumed to be the same in the above derivations...
 
@@
 
-\response{Thank you for pointing out the missing references.
-	We have carefully read through all of your rec emended papers, learning a lot in the process, and have incorporated them into our manuscript's introduction.
+\response{Thank you for pointing out the missing references!
+We have carefully read through each, and learned a lot in the process.
+They have now been incorperated into our manuscript's introduction. 
 }
@@
 What initially drew us to \textit{word2vec}, however, was its simplicity, its ubiquity, and its mathematical tractability (at least compared to other, more sophisticated approaches). 
-	This last attribute proved very useful, as in exploring the mathematical properties of the model, we discovered a deep connection between \textit{word2vec} and the Gravity Model of Mobility, which explains why it learns such effective gravity-like relationships between entities.
+This last attribute proved very useful, as in exploring the mathematical properties of the model, we discovered a deep connection between \textit{word2vec} and the Gravity Model of Mobility, which explains why it learns such effective gravity-like relationships between entities (see Section~\ref{sec:theory} of this letter).
 We believe hat this new discovery, not included in the manuscript (and illustrated below), justify our use of \textit{word2vec} here. 
-	We agree that the revolution in neural embeddings offers great promise in mobility and look forward to reading and also working on these future studies; however we argue that our contribution is most well founded, and best serves the scientific community, by working with simpler and more established models, especially concerning the mathematical link we uncovered.
+We agree that the revolution in neural embeddings offers great promise in mobility and look forward to contributing to this nascent field in the future; 
+however we argue that our contribution is most well founded, and best serves the scientific community, by working with simpler and more established models, especially concerning the mathematical link we uncovered.
 To highlight the importance of altenrative models, however, we add the following line to our conclusion: \say{\textit{Future studies may also consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality.
 }}.
-
-	\todo{Add complete theoretical discussion here}
 
@@
 
-\response{\todo{I'm worry this sounds too dismissive. Edit please?}
+\response{
 Thank you for this comment. 
@@
 Your recommendation of collaboration (based on the author byline) and advisor-student pairs are especially interesting, and we would aim to address these areas in future studies. 
-	However, given the importance of mobility to science, the importance of human mobility more generally, and the connection we discovered between \textit{word2vec} and the gravity model, that a focus of co-affiliation, which most closely aligns with ideas of mobility, is the most reasonable data to use for this manuscript.
+However, given the importance of mobility to science, the importance of human mobility more generally, and the connection we discovered between \textit{word2vec} and the gravity model (see Section~\ref{sec:theory}), that a focus of co-affiliation, which most closely aligns with ideas of mobility, is the most reasonable data to use for this manuscript.
 }
@@
 
+\clearpage
 \printbibliography{}

### 2021-02-09 paper/rebuttal/rebuttal.tex

--- 2021-02-09 paper/rebuttal/rebuttal.tex
@@
 \section{Theoretical justification of \textit{word2vec} and the Gravity Model}
-Here, we answer a following question:å Why does the skip-gram model with negative sampling (SGNS), otherwise known as \textit{word2vec}, work so well to model human mobility?
+\label{sec:theory}
+Here, we attempt to answer a question raised from our analysis: Why does the skip-gram model with negative sampling (SGNS), otherwise known as \textit{word2vec}, work so well to model human mobility?
 We demonstrate a fundamental connection between the SGNS model and the Gravity Model of Mobility, namely, that SGNS implicitly learns gravity-like relationships between locations.
@@
 
-\response{Thank you for pointing out the missing references.
-	We have carefully read through all of your rec emended papers, learning a lot in the process, and have incorporated them into our manuscript's introduction.
+\response{Thank you for pointing out the missing references!
+We have carefully read through each, and learned a lot in the process.
+They have now been incorperated into our manuscript's introduction.
 }

### 2021-02-10 workflow/scripts/PlotDistanceMetricPerformance.R
combine r2 and rmse figures into one simpler one

@@ -9,81 +9,94 @@
 
 # Plot dimensions
 FIG_WIDTH = 6
-FIG_HEIGHT = 7
+FIG_HEIGHT = 3.5
 
 
 library(readr)
 library(ggplot2)
 library(dplyr)
+library(tidyr)
 suppressPackageStartupMessages(require(optparse))
 
 # Command line arguments
 option_list = list(
-  make_option(c("-i", "--input"), action="store", default=NA, type='character',
-              help="Path to file containing the aggregated hyperameter values"),
+  make_option(c("--r2"), action="store", default=NA, type='character',
+              help="Path to file containing the aggregated r2 values"),
+  make_option(c("--rmse"), action="store", default=NA, type='character',
+              help="Path to file containing the aggregated RMSE values"),
   make_option(c("-o", "--output"), action="store", default=NA, type='character',
               help="Path to save output image")
 ) # end option_list
 opt = parse_args(OptionParser(option_list=option_list))
 
 # Read the aggregate R2 data
-params <- read_csv(opt$input, col_types = readr::cols())
+r2 <- read_csv(opt$r2, col_types = readr::cols()) %>%
+  select(r2, traj, metric, case, dim, ws, gamma, sizetype) %>%
+  mutate(
+    type = "r2",
+    performance = "Flux explained (correlation)"
+  ) %>%
+  rename(value = r2)
 
-metric_levels <- c("geo", "emb", "pprjsd", "lapcos", "svdcos", 'levyeuc')
-plotdata <- params %>%
+rmse <- read_csv(opt$rmse, col_types = readr::cols()) %>%
+  select(error.exp, error.power, traj, metric, case, dim, ws, gamma, sizetype) %>%
+  gather(type, value, error.exp, error.power) %>%
+  mutate(performance = "Root mean squared error")
+
+# The metrics to focus on for this plot
+metric_levels <- c("emb", 'levyeuc', "svdcos", "lapcos", "pprjsd", "geo")
+
+plotdata <- data.table::rbindlist(list(r2, rmse), use.names = T) %>%
   filter(dim == 300) %>%
   filter(ws == 1) %>%
   filter(gamma == 1.0) %>%
+  filter(sizetype == "all") %>%
+  filter(case == "global") %>%
   filter(metric %in% metric_levels) %>%
   mutate(
-    sizetype = gsub(".csv", "", sizetype, fixed = T),
     metric = factor(metric,
-                    levels = metric_levels,
-                    labels = c("Geographic\ndistance", "Embedding\ncosine distance",
[…]

### 2021-02-10 paper/rebuttal/rebuttal.tex
add new figure, table to the rebuttal letter

@@
 \def\mat#1{\mathbf{#1}}
+
+%
+% Huxtable dependencies (see R package)
+\usepackage{array}
+\usepackage{caption}
+\usepackage{graphicx}
+\usepackage{siunitx}
+\usepackage{ulem}
+\usepackage{colortbl}
+\usepackage{multirow}
+\usepackage{hhline}
+\usepackage{calc}
+\usepackage{tabularx}
+\usepackage{threeparttable}
+\usepackage{wrapfig}
+\usepackage{adjustbox}
+\usepackage{hyperref}
+
+% Allow landscape rotation on table page
+\usepackage{lscape}
 
@@
 
-\response{\todo{need to finish this. Honestly, I have no idea what they are saying about the window length}
-	\todo{Maybe related to length of the trajectory @dakoda could you check this?
-	}
+\response{
+\todo{Thoughts on this response? Still not 100\% sure I follow the reviewer}
+Thank you for this comment.
+We however, do not believe that this is a problem in our analysis.
+Raw co-occurrence, which is used to define our 'flux' between organizations, is always calculated using all organizations in a trajectory, and so window size does not affect flux. 
+Window size does affect \textit{word2vec}, however setting a smaller/larger window size should not make results incomparable. 
+When we set $w = 1$, \textit{word2vec} will generate training pairs at most 1 position away from each target location, for all possible targets. 
+When we instead set $w = 2$, \textit{word2vec} will generate training pairs the same way, but at most 2 positions away from each target---this means that the data for $w = 2$ will be \textit{larger}, containing as a subset all training pairs used for $w = 1$.
+The same follows for all $w > 1$, each generating a larger and larger set of training examples up until $w$ is larger than the length of the longest trajectory.
+
+What is notable about our findings, therefore, is that even though a model trained with $w = 1$ generates fewer training samples, it still outperforms $w > 1$ settings, which use more training samples, and which should capture higher-order structures in the data.
+We speculate that this is because the word2vec model with $w = 1$ is equvelant to the gravity model of mobility (see Section 1). 
 }
@@
 }
-\response{\todo{ Can we test this? likes  yy's paper on optimal dimension of embedding }
+\response{
 	Thank you for these comments.
 First, we added a line to the methods section detailing the \textit{word2vec} we used, and noting that these achieved the bst performance: \say{\textit{For main results regarding scientific mobility, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig....)}}.
+	A full search of the parameter space would certainly be interesting and useful, however we believe that set of parameters we considered here is sufficient to establish the utility of the approach, and demonstrate that performance is only slightly different based on different parameters.
 }
@@
 
-\response{Thank you for this insightful comment.
+\response{Thank you for this insightful comment!
 	We think that there is a great deal of potential in methods like BERT for representing mobility data.
@@
 
-\response{\todo{I'm worry this sounds too dismissive. Edit please?}
-	Thank you for this comment.
+\response{
+	Thank you for this comment!
 	We feel that applying these embeddings to other areas of scientific activity would be incredibly enlightening!
@@
 
-\clearpage
 %
@@
 %
-\begin{figure}[p!]
+\begin{figure}[ht!]
 	\centering
-	\includegraphics[width=0.9\textwidth]{\figdir/Descriptive/distance_metric_performance.pdf}
+	\includegraphics[width=0.95\textwidth]{\figdir/Descriptive/distance_metric_performance.pdf}
 	\mycaption
-	{Comparison a correlation with flux across various baselines}
+	{Neural embeddings outperform baselines for scientific mobility.}
 	{
-		Cosine distance between embedding vectors explains more flux in scientific mobility than geographic distance, baselines.
-		The correlation, or amount of flux explained by the embedding distance across distance metrics and other experimental parameters.
-		All correlations are significant at $p < 0.0001$).
-		Distance metrics are ordered, from top to bottom, by the highest correlation ($r^{2}$).
-		The asterisk denotes the top-performing distance metric for every case.
-		All distance metrics explain more of the flux than does geographic distance.
-		The cosine distance between embedding vectors explains more flux than all other distance metrics.
-		The x-axis differentiates between three strategies for defining the organization population used to calculate the flux.
-		``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
-		population is defined in the same way for ``mobile-only'', except only using unique mobile researchers;
-		``Raw frequency'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
-		Generally, ``All'' explains more of the flux, however there is little difference between definitions of mobility.
-		All distance metrics tend to explain more of the flux when describing all or domestic (same-country) mobility.
+		Cosine distance between embedding vectors generated with \textit{word2vec} explains more of the flux, and better predicts flux when used in the gravity model of mobility than geographic distance and other baselines.
+		Shown is the correlation between the flux and embedding distances, measured with $r^{2}$ (left), and the prediction error when using the distance as input to the gravity model of mobility. 
+		For prediction error, we show results based on both the exponential and power-law forms of the gravity model. 
+		All embedding-based methods use dimensions of 300. 
+		Here, embedding distance is obtained from neural embeddings learned with window size of 1 and $\gamma = 1$.  
+		In all cases, organization population is defined as the mean annualized number of unique mobile and non-mobile authors, and flux is calculated for all global mobility. 
+		Baselines include the top-performing distance metrics calculated between vectors obtained by personalized-page rank (PPR), singular value decomposition (SVD), laplacian eigenmap, and direct-factorization~\autocite{levy2014neural} approaches, as well as the geographic distance between organizations.
+		Embedding distance better explains and predicts flux than any other baseline, though there is some variation by experimental parameters (Table~\ref{supp:table:r2_table}, Table~\ref{supp:table:rmse_exp_table}, and Table~\ref{supp:table:rmse_power_table}).
 	}
@@
 
+%
+% R2 Table
+%
+\clearpage
+\begin{landscape}
+
+  \providecommand{\huxb}[2]{\arrayrulecolor[RGB]{#1}\global\arrayrulewidth=#2pt}
+  \providecommand{\huxvb}[2]{\color[RGB]{#1}\vrule width #2pt}
+  \providecommand{\huxtpad}[1]{\rule{0pt}{#1}}
+  \providecommand{\huxbpad}[1]{\rule[-#1]{0pt}{#1}}
+
+\begin{table}[ht]
+\caption{
+	\textbf{Correlation between flux and distance over metrics, experimental parameters}.
+	Each cell corresponds to the correlation (measured with $r^{2}$) between the real-world flux between scientific organizations, comparing the embedding distance against baseline metrics, and across subsets of mobility data and by definitions of organization population.
+	The asterisk denotes the top-performing distance metric by column. 
+	Distance metrics are ordered from highest $r^{2}$ to lowest, based on global mobility with organization population defined using all mobile and non-mobile authors. 
+	``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
+		population is defined in the same way for ``Mobile only'', except only using unique mobile researchers;
+		``Raw freq'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
+		Embedding distance, measured as the cosine distance between embedding vectors, explains more of the flux than baselines in nearly every case, except using raw frequency population and domestic and international mobility, where direct-factorization approaches~\autocite{levy2014neural} work better.
+}
+\label{supp:table:r2_table}
+\begin{centerbox}
+\begin{threeparttable}
+ \setlength{\tabcolsep}{0pt}
+\begin{tabular}{l l l l l l l l l l}
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}c!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{} \hspace{6pt}\huxbpad{0pt}} &
+\multicolumn{3}{c!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{All} \hspace{6pt}\huxbpad{0pt}} &
+\multicolumn{3}{c!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{Mobile only} \hspace{6pt}\huxbpad{0pt}} &
+\multicolumn{3}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{Raw freq} \hspace{6pt}\huxbpad{0pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{ } \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}-}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.481 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.418 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.435 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.492 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.456 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.489 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.325 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.251 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.252 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.341 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.369 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.382 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.213 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.271 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.284 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.305 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.323 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.334 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.341 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.313 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.316 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.254 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.265 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.267 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.218 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.181 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.177 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.247 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.297 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.309 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.213 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.314 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.325 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.111 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.152 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.16 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Geographic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.219 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.174 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.197 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.188 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.157 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.176 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.04 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.019 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.03 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Laplacian cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.212 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.199 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.218 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.176 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.157 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.18 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.079 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.1 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.111 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.208 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.227 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.231 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.169 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.246 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.246 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.057 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.054 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.053 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR JSD} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.194 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.276 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.276 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.218 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.335 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.335 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.012 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.077 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.069 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.138 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.136 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.143 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.196 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.186 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.197 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.13 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.149 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.152 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.004 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.013 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.004 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.039 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.034 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.035 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+\end{tabular}
+\end{threeparttable}\par\end{centerbox}
+
+\end{table}
+
+\end{landscape} % End r2 table page
+
+%
+% RMSE TABLE --- Exponential model
+%
+\clearpage
+\begin{landscape}
+
+  \providecommand{\huxb}[2]{\arrayrulecolor[RGB]{#1}\global\arrayrulewidth=#2pt}
+  \providecommand{\huxvb}[2]{\color[RGB]{#1}\vrule width #2pt}
+  \providecommand{\huxtpad}[1]{\rule{0pt}{#1}}
+  \providecommand{\huxbpad}[1]{\rule[-#1]{0pt}{#1}}
+
+\begin{table}[ht]
+\caption{
+	\textbf{Prediction error between actual and predicted mobility with exponential gravity model, by metrics and experimental parameters}.
+	Each cell corresponds to the prediction error (measured with root mean squared error) between the real-world flux between scientific organizations and predictions made with the exponential form of the gravity model of mobility.
+	The prediction error is shown for the embedding distance compared against baselines, subsets of mobility data, and definitions of organization population. 
+	The asterisk denotes the top-performing distance metric by column (lowest prediction error). 
+	Distance metrics are ordered from lowest prediction error to highest, based on global mobility with organization population defined using all mobile and non-mobile authors. 
+	``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
+		population is defined in the same way for ``Mobile only'', except only using unique mobile researchers;
+		``Raw freq'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
+		Embedding distance, measured as the cosine distance between embedding vectors, results in better predictions of mobility than baselines in nearly every case, however direct-factorization approaches~\autocite{levy2014neural} perform better for domestic and international mobility when raw frequency is used to define populations.
+}
+\label{supp:table:rmse_exp_table}
+\begin{centerbox}
+\begin{threeparttable}
+ \setlength{\tabcolsep}{0pt}
+\begin{tabular}{l l l l l l l l l l}
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}c!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{} \hspace{6pt}\huxbpad{0pt}} &
+\multicolumn{3}{c!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{All} \hspace{6pt}\huxbpad{0pt}} &
+\multicolumn{3}{c!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{Mobile only} \hspace{6pt}\huxbpad{0pt}} &
+\multicolumn{3}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{Raw freq} \hspace{6pt}\huxbpad{0pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{ } \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}-}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.713 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.76 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.737 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.702 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.749 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.713 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.715 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.764 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.748 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.803 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.791 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.771 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.867 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.725 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.726 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.705 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.803 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.825 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.811 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.851 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.87 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.854 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.769 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.798 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.784 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.859 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.835 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.815 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.841 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.82 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.82 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.812 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.792 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Laplacian cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.878 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.891 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.867 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.894 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.933 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.904 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.835 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.837 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.815 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.881 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.875 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.86 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.898 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.882 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.866 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.858 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.841 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR JSD} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.888 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.847 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.835 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.871 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.828 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.814 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.865 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.847 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.834 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.918 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.925 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.908 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.884 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.916 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.894 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.812 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.814 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.796 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Geographic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.929 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.951 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.928 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.973 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.002 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.983 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.856 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.875 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.853 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.987 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.995 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.98 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.979 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.014 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.996 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.853 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.867 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.849 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+\end{tabular}
+\end{threeparttable}\par\end{centerbox}
+
+\end{table}
+
+\end{landscape}
+
+%
+% RMSE TABLE --- Power Law
+% 
+\clearpage
+\begin{landscape}
+
+  \providecommand{\huxb}[2]{\arrayrulecolor[RGB]{#1}\global\arrayrulewidth=#2pt}
+  \providecommand{\huxvb}[2]{\color[RGB]{#1}\vrule width #2pt}
+  \providecommand{\huxtpad}[1]{\rule{0pt}{#1}}
+  \providecommand{\huxbpad}[1]{\rule[-#1]{0pt}{#1}}
+
+\begin{table}[ht]
+\caption{
+	\textbf{Prediction error between actual and predicted mobility with power-law gravity model, by metrics and experimental parameters}.
+	Each cell corresponds to the prediction error (measured with root mean squared error) between the real-world flux between scientific organizations and predictions made with the power-law form of the gravity model of mobility.
+	The prediction error is shown for the embedding distance compared against baselines, subsets of mobility data, and definitions of organization population. 
+	The asterisk denotes the top-performing distance metric by column (lowest prediction error). 
+	Distance metrics are ordered from lowest prediction error to highest, based on global mobility with organization population defined using all mobile and non-mobile authors. 
+	``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
+		population is defined in the same way for ``Mobile only'', except only using unique mobile researchers;
+		``Raw freq'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
+		Embedding distance, measured as the cosine distance between embedding vectors, results in better predictions for global mobility with ``All'; and ``Mobile only'' definitions of population, though the direct-factorization approach~\autocite{levy2014neural} perform better for in other cases.
+}
+\label{supp:table:rmse_power_table}
+\begin{centerbox}
+\begin{threeparttable}
+ \setlength{\tabcolsep}{0pt}
+\begin{tabular}{l l l l l l l l l l}
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}c!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{} \hspace{6pt}\huxbpad{0pt}} &
+\multicolumn{3}{c!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{All} \hspace{6pt}\huxbpad{0pt}} &
+\multicolumn{3}{c!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{Mobile only} \hspace{6pt}\huxbpad{0pt}} &
+\multicolumn{3}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{Raw freq} \hspace{6pt}\huxbpad{0pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{ } \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}-}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.743 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.784 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.76 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.73 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.784 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.749 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.714 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.762 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.745 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.78 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.776 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.755 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.847 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.822 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.703 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.711 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.691 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.822 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.831 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.864 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.879 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.863 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.783 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.809 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.795 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.839 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.785 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.761 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.89 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.834 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.81 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.792 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.752 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.728 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Laplacian cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.87 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.837 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.801 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.937 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.919 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.886 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.804 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.772 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.735 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Geographic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.905 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.879 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.888 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.933 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.906 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.852 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.851 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR JSD} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.889 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.85 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.838 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.871 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.834 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.819 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.865 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.847 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.834 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.92 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.927 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.91 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.885 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.918 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.896 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.812 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.815 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.797 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.927 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.926 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.911 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.93 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.924 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.909 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.861 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.872 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.854 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.99 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.998 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.983 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.977 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.015 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.997 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.845 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.86 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.841 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+\end{tabular}
+\end{threeparttable}\par\end{centerbox}
+
+\end{table}
+
+\end{landscape}
+
+%
+% BIBLIOGRAPHY
+%
 \clearpage

### 2021-02-10 paper/rebuttal/rebuttal.tex
tweaks to rebuttal letter

@@
 \tableofcontents
-\listoffigures
 \clearpage
@@
 First, although there exist optimal in-vector and out-vector that are identical, the in-vector and out-vector can be different in practice because they are sub-optimal.
-Second, while dot similarity is a formal distance measure in terms of its connection to the gravity model, our simulations show that dot similarity did not predict mobility flow better than cosine similarity (Figs.~\ref{fig:supp:distancemetrics} and \ref{fig:supp:distancemse}).
-It has been widely observed that cosine similarity is generally better than dot similarity in many applications of word embedding~\cite{} [Jisung, could you add citations?].
-Therefore, the superiority of cosine similarity is not a problem specific but general feature of word embedding.
-Nevertheless, dot similarity is the second best predictor among the 7 embedding distances. What makes cosine similarity superior to dot similarity warrants the future work.
+Second, while dot similarity is a formal distance measure in terms of its connection to the gravity model, our simulations show that dot similarity did not predict mobility flow better than cosine similarity (Fig.~\ref{fig:supp:distancemetrics}).
+It has been widely observed that cosine similarity is generally better than dot similarity in many applications of word embedding~\cite{}
+\todo{[Jisung, could you add citations?]}. Therefore, the superiority of cosine similarity is not a problem specific to, but instead a general feature of word embedding.
+Nevertheless, dot similarity still outperformed geographic distance and some baselines (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+What makes cosine similarity superior to dot similarity warrants the future work.
 
@@
 \subsection{Result}
-\todo{report the results and say our results are better @dakoda
-}
-
-\subsection{Why do neural embeddings outperform direct matrix factorization?}% why sgd is better?
-An issue in the matrix factorization approach is that it is extremely sensitive to small flows between affiliations.
-The matrix factorization approach embeds affiliations $i$ and $j$ such that their dot similarity is as close as to $\log (T_{ij} / P(i) P(j))$.
-If the flow $T_{ij}$ is considerably small or zero, the dot similarity goes $-\infty$, pushing $i$ and $j$ too far from the other affiliations in the embedding space~\autocite{levy2014neural, Qui2018}.
-This is particularly problematic when the window size is small because most affiliation pairs would have no flow, which is indeed the case in our experiments.
-To circumvent this problem, the previous studies~\autocite{levy2014neural, Qui2018} add a constant flow between the affiliation pairs with no flow.
-However, this changes the data to which we fit the model, and small flows still have a considerably strong impact on the embedding.
-
-Also, it is well known that SVD by itself is very vulnerable to outliers \autocite{ xu2012robust, huber1981robust, xu1995robust, chandrasekaran2011rank, candes2011robust, }.
-Compared to SVD, a stochastic gradient descent algorithm (SGD) which is employed in SGNS \textit{word2vec} benefits from the noise in the model itself and can enhance generalization and effectiveness as well \autocite{ma2018power, smith2020generalization, zhang2019algorithmic,}.
-
-%
-% SECTION- POINT-BY-POINT DISCUSSION
-%
-\section{Point-by-point discussion}
-All of the referees presented us with excellent, insightful comments and we feel that the changes implemented as a consequence have signiﬁcantly strengthened the manuscript.
-Here we offer further discussion, and introduce several results and figures to support certain arguments.
-
-\subsection{Response to Referee 1}
-
-\rcomment{%
-	To the best of my knowledge, this is the first work providing a thorough analysis of the structure encoded by latent mobility embeddings (e.g., the prestige hierarchy), and this is the first work I am aware of to propose embeddings as an explanatory/exploratory tool in this context.
-In this way, the work has some originality and significance.
-
-	\begin{itemize}
-		\item Liu, Xin, Yong Liu, and Xiaoli Li. ``Exploring the Context of Locations for Personalized Location Recommendations.'' IJCAI. 2016.
-		\item Feng, Shanshan, et al. ``POI2Vec: geographical latent representation for predicting future visitors.'' AAAI. 2017.
-		\item Yao, Zijun, et al. ``Representing Urban Functions through Zone Embedding with Human Mobility Patterns.'' IJCAI. 2018.
-		\item Cao, Hancheng, et al. ``Habit2vec: Trajectory semantic embedding for living pattern recognition in population.'' IEEE Transactions on Mobile Computing 19.5 (2019): 1096-1108.
-	\end{itemize}
-
-	However, the novelty of this work is quite narrow, as there are several prior works that develop trajectory-based embeddings of human mobility based on the word2vec algorithm.
-For example, the following references all propose word2vec-inspired embeddings of human mobility data:
-
-	Notably, the location embedding methodology in Liu et al (2016) (see Section 3.1) is essentially the same as the approach used in the submitted manuscript, and the work by Liu et al (2016) is well-known with over 100 citations.
-}
-
-\response{Thank you for pointing out the missing references!
-We have carefully read through each, and learned a lot in the process.
-They have now been incorperated into our manuscript's introduction.
-}
-
-\rcomment{
-	I found the specific use of the SGNS algorithm unmotivated.
-There are many ways to generate useful low-dimensional embeddings, so why is the SGNS method prioritized above others?
-This method is popular, but popularity alone is not sufficient justification and I see no theoretical reason why it should be the most appropriate method.
-For example, a key point in this manuscript is the fact that the the SGNS embeddings capture the flux between locations better than geographic distance.
-However, if this is such an important point, then why not simply learn a low-dimensional embedding approximation of the flux metric directly?
-such as SVD?
-}
-
-\response{Thank you for the suggestion!
-	We split our response into two subsections concerning the theoretical justification, on one hand, and the comparison to simpler baselines, on the other.
-}
-
-\rcomment{%
-	The methodology has potential limitations in terms of reproducibility and robustness, which should be addressed.
-This is no specific fault of the authors, but both the SGNS/word2vec algorithm and the UMAP algorithm are inherently stochastic.
-This means that these approaches involve inherent randomness, and for researchers to replicate the exact effect seen in this manuscript, one would need to ensure the exact same random seeds etc.
-were used.
-In my view, this is a serious limitation, especially given that the UMAP results and learned embeddings are reified and treated as first-class objects of scientific study.
-}
-
-\response{Thank you for this comment.
-While robustness is a general concern for these methods, we found that their application to our datasets were in fact quite robust, and observed no evidence that findings were the result of methodological artefacts.
-This is confirmed in extra work done in response to these reviews.
-
-	\noindent We re-ran all of our results using different starting seeds and found all results were qualitatively similar, and almost quantitatively identical.
-	In addition, we expanded the set of experimental parameters, training 18 different embeddings with different dimensions, window sizes, and now, $\gamma$.
-	We found that while performance varies across each combination of parameters, the main results remain qualitatively similar.
-	While we can run more combinations of parameters, and more iterations of \textit{word2vec}, we see no evidence that results will drastically vary.
-
-	\noindent We believe that the ratio of the number of organizations represented in our dataset to the total number of mobility trajectories makes our results especially robust.
-	Only about 8,661 organizations are represented across over three million career trajectories of scientists, such that nearly every organization appears enough times, and in enough contexts, to produce a robust vector representation.
-	However, this may not hold true for all problem domains—for example, natural language includes many millions of tokens, many of which will occur only a few times, allowing stochasticity to have a much stronger effect on the final representation.
-	Heeding this as a general concern, we have added the following sentence to our limitations paragraph in our conclusion:
-
-	\noindent “We however, note that all results shown here are robust to this stochasticity, likely emerging from the limited ``vocabulary'' of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories).
-Applications of word2vec to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random artifacts.”
-
-}
-
-\rcomment{%
-	Another interesting point in this work is that the authors chose to not report p-values or the results of statistical significance tests (except confidence intervals).
-I presume this was a conscious decision, which I do not necessarily agree with.
-I see no critical error in the approach used by the authors, but I would have found aspects of the manuscript easier to understand in places with results of statistical tests (e.g., associated with goodness-of-fit tests formally test that the embedding-based distances are more correlated with the flux values).
-Given the sample sizes involved, I have no doubt that the results are statistically significant.
-However, I personally do see value in rigorously performed frequentist hypothesis testing, and I felt that this manuscript could be improved by employing such techniques.
-
-	Lastly, the authors do not actually state how the 99 confidence intervals were constructed. (E.g., was this via a bootstrap approach?) This detail should be added.
-}
-
-\response{Thank you for this feedback.
-	You are correct that it was a conscious choice to not report statistical significance in the form of a P-value.
-	The use of statistical significance is contentious, and Nature itself has hosted some of this debate (\href{https://www.nature.com/articles/d41586-019-00857-9}{[link]}).
-	As such, we have a philosophy of avoiding p-values in research when it makes sense to do so.
-	In our analysis, all correlations and fits are significant at a level below 0.0001, or have a p-value  computationally indistinguishable from zero.
-	However, we recognize that p-values can help readers interpret results.
-	As such, we have opted to add to a sentence such as \say{\textit{Correlation is calculated on the data in the log-log scale ($p <<0.0001$ across all fits)}.} or similar to relevant figures in the main text and supporting materials.
-	We believe that this solution strikes a balance between transparency while also avoiding extraneous detail and the common pitfalls of statistical reporting.
-
-	We have also provided detail about how confidence intervals were calculated in relevant figure captions.
-	For example, we state in figure 2's caption that \say{\textit{99\% confidence intervals are plotted for the mean flux in each bin based on a normal distribution.}}, which should give readers enough information to reproduce the confidence intervals following their standard definition.
-	Other confidence intervals, such as intervals for the loess regression line in figure 6, are calculated using the smoothing functions in the \texttt{ggplot2} package of R, and refer readers to the relevant documentation.
-}
-
-\rcomment{%
-	F. Suggested improvements:
-	References and discussion of prior work using word2vec-style embeddings of mobility data.
-	Additional experiments using alternative embedding methods, especially an SVD-based embedding method, as well as robustness/reproducibility studies across different runs of the SGNS would be essential to strengthen the paper.
-	In addition, some additional results demonstrating how the embeddings provide novel scientific insight, rather than just recapitulating known structures, would be essential to make this work above-the-bar for a high-impact publication such as Nature.
-
-}
-
-\response{We believe that the mathematical breakthroughs made since our first submission improve the manuscript and extend its contribution and demonstrates novel scientific insight, and justifies the use of word2vec towards mobility data.
-By adding this, and addressing your other points (above), we believe that the revised manuscript sufficiently remedies your concerns.
-
-}
-
-%===================================================
-
-%
-% Response to reviewer 2
-%
-\subsection{Response to Referee 2}
-
-\rcomment{%
-	Although the paper is well written and explores a very interesting problem, I have certain criticism for the used methodology.
-After obtaining a representation of each dataset, the authors defined an embedding distance as the cosine distance between vectors in the space, while defining distance as the geographical distance in the original, spatially embedded datasets.
-Subsequently they used the Gravity Law to estimate the flux between location pairs of vector pairs in the spatial and embedded space respectively.
-The Gravity Law, applied on mobility, assumes that the number of people moving between two populations is proportional to the multiplicative of the sizes of the populations and a deterrence function.
-Research during the last decades on transportation, spatial networks and human mobility suggests that this deterrence function may take a functional form of an inverse exponential or an inverse power-law, as it has been acknowledged by the authors.
-However, the emergence of these different deterrence functions can be due to fundamentally different mechanisms (for a review on the topic see Barthélemy, Physics Reports 499, 1, 2011, a paper not cited in the manuscript).
-For example, the different cost functions (linear or logarithmic) to create link at a given distance, the spatial granularity of the observation, or even the heterogeneity of the moving individuals in terms of various factors, just to mention a few examples.
-Instead, the authors of the actual paper arbitrarily assumed a power-law deterrence function in the spatial case and an exponential deterrence function in the embedding space without further arguing their choice (other than fitting on the data).
-Furthermore, assuming different deterrence functions for the flux estimation using Gravity Law makes the estimated fluxes incomparable, resulting the invalidation of results depicted in Figure 2.
-}
-
-\response{Thank you for pointing this out.
-	We carefully read out the Barthélemy, Physics Reports 499, 1, 2011, and referenced it in our manuscript.
-	Also, we report the performance of the flux estimation (Fig.~\ref{fig:supp:distancemetrics}, this document) and prediction (Fig.~\ref{fig:supp:distancermse}, this document) using different deterrence functions, founding that while performance differs, that the embedding distance outperforms geographic
-	distance no matter the function used.
-	We add the following line to the methods,
-
-	\medskip
-	\say{The decay function $f(r_{ij})$ defines the effect of distance, and so different decay functions can model fundamentally different mechanism [...] such as the cost functions for a given distance and the spatial granularity of the observation.
-		For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case though the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Supporting Information).}
-	\medskip
-
-	We also argue that geographical distance ﬁts well with the power-law decay function because power-based gravity model can be more suitable for analyzing large, complex, and scale-free spatial systems and the exponential-based gravity model indicates simplicty rather than spatial complexity~\autocite{chen2015distance}.
-Meanwhile, embedding distance ﬁts well with the exponential decay function, which we demonstrate to correspond to an underlying mathematical relationship between \textit{word2vec} and the gravity model, a connection we recently discovered and included as a major finding in this revision (see our response to Referee 1).
-
-}
-
-\rcomment{
-	I would suggest to the authors to carefully cite other papers applying Word2Vec embedding on spatial data, especially focusing on location embedding based on trajectory sequences. Examples are:
-	\begin{itemize}
-		\item A.
-Solomon et al., Predict Demographic Information Using Word2Vec on Spatial Trajectories., ACM UMAP '18: Proceedings of the 26th Conference on User Modeling, Adaptation and Personalization, July 2018 Pages 331–339, https://doi.org/10.1145/3209219.3209224
-		\item A.
-Crivellari and E.
-Beinat, From Motion Activity to Geo-Embeddings: Generating and Exploring Vector Representations of Locations, Traces and Visitors through Large-Scale Mobility Data., ISPRS Int.
-J.
-Geo-Inf.
-2019, 8(3), 134 (2019); https://doi.org/10.3390/ijgi8030134
-
-	\end{itemize}
-
-	The application of the Word2Vec method on the studied trajectory sequences is not well explained.
-Without explaining the embedding method briefly in the main text the reader has no idea how to interpret the embedding distance, which is in the hear of the study.
-
-}
-
-\response{Thank you.
-We have added the following sentence to the introduction: “It works under the notion that a good representation should facilitate prediction, and so learns a mapping of target locations (words) that best predict locations that co-appear in the same trajectory (sentence).”
-
-	In addition, we provided more explicit mathematical detail of word2vec in the new subsection entitled “word2vec and the gravity model”.
-
-	We believe that these details are sufficient in the main text of the manuscript, and refer readers to the Methods for a deeper explanation.
-}
-
-\rcomment{
-
-	The original SkipGram method expects environments of locations (originally words) with fixed length, however this is not explained in the manuscript nor in Methods or the SI.
-	Related question to the previous one.
-Let’s assume that the authors used fixed window lengths and, as mentioned in Methods Embedding section (and demonstrate in Fig.S4 - not referenced in Methods), that the windows size w=1 gives the best correlations in case of scientific mobility.
-This might be true in absolute terms but it is an unfair comparison to larger window sizes, as there are way more short trajectories in the data than longer ones (see Fig.S3), thus the flux prediction of w=1 is based on a way larger sample than for w$>$1.
-Undersampling the ensemble of trajectories used for w=1 predictions might provide a fair way of comparing results of different window sizes.
-}
-
-\response{
-\todo{Thoughts on this response? Still not 100\% sure I follow the reviewer}
-Thank you for this comment.
-We however, do not believe that this is a problem in our analysis.
-Raw co-occurrence, which is used to define our 'flux' between organizations, is always calculated using all organizations in a trajectory, and so window size does not affect flux. 
-Window size does affect \textit{word2vec}, however setting a smaller/larger window size should not make results incomparable. 
-When we set $w = 1$, \textit{word2vec} will generate training pairs at most 1 position away from each target location, for all possible targets. 
-When we instead set $w = 2$, \textit{word2vec} will generate training pairs the same way, but at most 2 positions away from each target---this means that the data for $w = 2$ will be \textit{larger}, containing as a subset all training pairs used for $w = 1$.
-The same follows for all $w > 1$, each generating a larger and larger set of training examples up until $w$ is larger than the length of the longest trajectory.
-
-What is notable about our findings, therefore, is that even though a model trained with $w = 1$ generates fewer training samples, it still outperforms $w > 1$ settings, which use more training samples, and which should capture higher-order structures in the data.
-We speculate that this is because the word2vec model with $w = 1$ is equvelant to the gravity model of mobility (see Section 1). 
-}
-
-\rcomment{
-	The other very important parameter of the SkipGram method is the embedding dimension, which is explained in the Methods but it is not explored.
-E.g.
-to choose the ideal dimension for embedding one may sweep through a broad range of possible dimensions and not only explore three values as described in the SI (Fig.S4).
-	Their main observations in section “Embeddings provide functional distance between locations” is that “…our results demonstrate that, consistently, the embedding distance better captures patterns of actual mobility than does the geographic distance.”.
-This is a great verification of their method but it is somewhat expected from an embedding, which is built on mobility trajectories between places, as compared to cases based on simply geographic distance.
-
-}
-\response{
-	Thank you for these comments.
-First, we added a line to the methods section detailing the \textit{word2vec} we used, and noting that these achieved the bst performance: \say{\textit{For main results regarding scientific mobility, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig....)}}.
-	A full search of the parameter space would certainly be interesting and useful, however we believe that set of parameters we considered here is sufficient to establish the utility of the approach, and demonstrate that performance is only slightly different based on different parameters.
-}
-
-\rcomment{
-	When datasets in the intro are explained, it should be mentioned that the detailed descriptions are in the Methods section.
-}
-\response{Thank you.
-We have added a parenthetical to the introduction after stating the datasets, as follows:  \say{We embed trajectories from three massive datasets: U.S.
-passenger flight itinerary records, Korean accommodation reservations, and a dataset of scientists' career mobility between organizations captured in bibliometric records (Detailed descriptions are available in the Methods).}
-}
-\rcomment{
-	Some minors comments
-	\begin{enumerate}
-		\item There is no reference to Fig.5e and f in the text.
-		\item Second paragraph on page 10: the authors discuss Fig.6 here but missed to refer the figure.
-		\item Page 15, last row: double point in the end of sentence.
-		\item SI Page 2, S3: “. if” $\rightarrow$ “. If”
-	\end{enumerate}
-}
-\response{Thank you, we have remedied these comments and have updates the manuscript accordingly,
-}
-
-\rcomment{
-	SI Fig.S1c: Here the authors conclude that the proportions “decreased over time”.
-These proportions seem to be rather flat without strong decreasing trends.
-In any case, if the authors would like to indicate minor changes here, it would be helpful for the reader if a grid would be posted on the figure.
-}
-\response{Thank you, we agree that the trend is flat, rather than decreasing. We have adjusted the text accordingly, and also added a grid to the figure so that it can be more easily read.
-
-}
-
-\rcomment{
-	SI Fig.S3: Posted numerical values on the figures and the values described in the caption do not match.
-}
-\response{Thank you for pointing out this oversight. The caption values have been updated.
-}
-
-\rcomment{SI Fig.S6: Please indicate what is RMSE in the caption. The authors defined it in the main text but the SI should be self consistent too.
-}
-\response{We have added the line “RMSE is the root-mean-squared error between the actual and predicted values.” to Fig. S6 as well as all other SI figures that make use of the same visualization.
-}
-
-\rcomment{SI Fig.S7: The authors state that “The gravity model with the exponential decay function outperforms that with a power-decay function.” - this does not seem to be true for the “International” case.
-Please specify this in the caption.
-}
-
-\response{We have updated the relevant line of the caption to read as follows:
-	“The gravity model with the exponential decay function slightly outperforms that with a power-decay function except in the case of international-only mobility, for which power-decay performs slightly better.”
-}
-
-\subsection{Response to Referee 3}
-
-\rcomment{The analysis does not compare embeddings, which would not be a problem if they were making
-	an inference other than we can embed micro-mobility to trace macro-mobility. They use an
-	efficient (Google engineers developed it), single-layer embedding from 2013, which produces
-	linear associations. But the paper doesn’t take advantage of the revolution in deep neural
-	network models that now produce powerful, nonlinear and noncontiguous (e.g., using the
-	attention architecture) models that now dominate analysis of language, and are making very
-	power inroads in machine vision.
-To be clear, deeper models require much data and computational power to tune—they are an engineering feat—but if developed in these settings, they would likely dramatically improve the prediction of flux.
-They take into account directionality (e.g., a person moving from one opportunity to another) and would independently capture people how people distinctly move up and down the hierarchy or from place to place (e.g., a in bi-directional model like BERT).
-A lack of discussion or demonstration of which model works best--and the unfounded inference that direction does not matter felt weak without a demonstration that they would not have worked better.
-They did and do work much better for language models and for image generation...why would they not work for analysis of human mobility?
-(I’m sure they would, but this would time and independent development.)
-}
-
-\response{Thank you for this insightful comment!
-	We think that there is a great deal of potential in methods like BERT for representing mobility data.
-	What initially drew us to \textit{word2vec}, however, was its simplicity, its ubiquity, and its mathematical tractability (at least compared to other, more sophisticated approaches).
-	This last attribute proved very useful, as in exploring the mathematical properties of the model, we discovered a deep connection between \textit{word2vec} and the Gravity Model of Mobility, which explains why it learns such effective gravity-like relationships between entities.
-	We believe hat this new discovery, not included in the manuscript (and illustrated below), justify our use of \textit{word2vec} here.
-
-	We agree that the revolution in neural embeddings offers great promise in mobility and look forward to reading and also working on these future studies; however, we argue that our contribution is most well-founded, and best serves the scientific community, by working with simpler and more established models, especially concerning the mathematical link we uncovered.
-Moreover, these deep models require a tremendous amount of training data ($\sim$3 billion words in Bert) and model parameters.
-
-	To highlight the importance of altenrative models, however, we add the following line to our conclusion: \say{\textit{Future studies may also consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality.
-}}.
-
-}
-
-\rcomment{
-	The paper does not compare human transition (or co-affiliation) data with any other kinds of
-	data that could be used for embedding. Does author byline data do better than the embedding
-	of collaborating institutions (almost certainly), than co-mention of the institutions in the press, as
-	with institutional collaborations (e.g, the Harvard-MIT Broad Institute, or joint university
-	conferences; these will be stronger signals, but there are fewer of them), than advisor-student
-	university pairs (although many of these will be captured by the authors’ approach when
-	students publish at their home institutions before securing jobs elsewhere).
-}
-
-\response{
-	Thank you for this comment!
-	We feel that applying these embeddings to other areas of scientific activity would be incredibly enlightening!
-	Your recommendation of collaboration (based on the author byline) and advisor-student pairs are especially interesting, and we would aim to address these areas in future studies.
-	However, given the importance of mobility to science, the importance of human mobility more generally, and the connection we discovered between \textit{word2vec} and the gravity model, that a focus of co-affiliation, which most closely aligns with ideas of mobility, is the most reasonable data to use for this manuscript.
-}
-
-\rcomment{
-	There are known concerns with clustering a 300 dimensional objects because of the curse of
-	dimensionality. Many have shown that reducing dimensionality with UMAP to a nontrivial
-	number of dimensions (e.g., 30), which preserves both local and some global distance, then
-	clustering on those dimensions are much more stable (e.g., this post). This was one
-	concern with the stability of the clustering analysis
-
-}
-
-\response{Thank you for this suggestion.
-	We looked into this, using UMAP to reduce the country-level embeddings from 300 down to 30 dimensions, however the results from this were incomprehensible, and inferior to those using 300 dimensions.
-	Many dimensionality reduction techniques reduce the number of dimensions by maintaining pairwise distances between vectors, so that the result can be well-suited for clustering algorithms.
-	However, our approach already uses raw pairwise similarities to perform hierarchical clustering, so approximating this distance in 30 dimensions, and then using the new distances to perform clustering is redundant.
-	We also find that the curse of dimensional is not a major issue in our analysis, at least given the size of our data and the number of locations represented---\textit{word2vec} seems able to learn dense vector-space representations.
-}
-
-\rcomment{
-	P6Para3: “For THEIR purpose…”
-}
-
-\response{Thank you, we have corrected this mistake.
-}
-
-\rcomment{
-	P8Para1: “by explicitly the relative importance of different level of the hierarchy with a scaling parameter r ” which is never described or explained.
-Considering it was derived by the authors in a very recent paper, no one will know what it is.
-}
-
-\response{Thank you, we have edited the text to read as “We quantify the relative importance of geography (by region), and language (by the most widely-spoken language of each country) using the element-centric clustering similarity, a method that can compare hierarchical clustering and disjoint clustering (geography, language...) at the different level of hierarchy by explicitly adjusting a scaling parameter $r$, acting like a zooming lens”
-}
-
-\subsection{Response to Referee 4}
-
-\rcomment{
-	The authors define the distance function in terms of either the geographic distance between locations or their functional distance in the vector space.
-The increase in R2, as they switch to the embedding distance, is rather convincing.
-One of the models they use as a reference is the gravity model, but they also mention the radiation model.
-I am curious if they tried a comparison with that, and what was the outcome.
-I suspect that the radiation model would have a comparable performance to the gravity one.
-But as distance is not the only factor there, is a comparison at all feasible?
-}
-
-\response{Thank you for this suggestion.
-	We agree that comparing the radiation model would be incredibly interesting.
-	However, we originally did not use radiation model because our dataset on scientific mobility lacked clear directionality, which is required by the radiation model of mobility.
-	Scientific mobility is incredibly complex, the most common form of mobility being co-affiliation, or a researcher holding multiple affiliations simultaneously.
-	In these cases, it is difficult to discern a researcher's main affiliation (where they start), and eventual affiliation (where they end up).
-	As such, we conceive of scientific mobility as having no direction (see S2 Text).
-	Given these considerations, we instead chose to use the standard gravity model of mobility, which models mobility as symmetric.
-	Moreover, we have recently discovered an underlying mathematical relationship between \textit{word2vec} and the gravity model of mobility, further justifying our choice.
-	While we are excited to investigate the use of neural embeddings with the radiation model, we believe it to be outside the scope of our current submission.
-}
-
-\rcomment{
-	My second group of questions pertain to the prestige hierarchy, that really drives the dynamics of scientific mobility.
-The technical description addressed most of them.
-However, I was wondering, is it all possible to go beyond the descriptive part, and show cases where the more accurate embedding base distances do make a difference?
-That is, using them, we do not only obtain better correlations with the ranking data, but also allows us to address problems that we could not without the embedding distance?
-For example, some results have shown that a paper coauthored by two authors at different high prestige institutions has higher impact, than writing a paper with two authors of the same high prestige institution—would embedding help us pull apart such effects?
-Here I am not trying to make the authors to write a different paper, so maybe a little forward thinking may be enough, if doing the actual work is too time consuming, and goes beyond the current narrative.
-}
-
-\response{Thank you for this idea!
-	We believe that this is an interesting topic and we hope to investigate it in the future.
-	In your particular example, an embedding distance trained using sequences of co-authorship on the same paper might be better to capture the \textit{collaborative} distance between institutions.
-	Then, using that distance, one could measure the ``embedding distance'' spanned by all authors in the byline, and relate this to questions impact to determine whether (a)typical collaborations relate to impact.
-	This is certainly a topic that is in our mind for future study.
-	In the case of scientific mobility, we might also consider the ``embedding distance'' spanned by an individual's career, and relate this to their demographics and scientific impact.
-
-	However, while these topics are exciting, we believe that that they fall outside the scope of the current manuscript, especially given the discoveries we made concerning a fundamental connection between the gravity law of mobility and \textit{word2vec}.
-}
-
-\rcomment{
-	Finally, one cannot escape the fact that COVID changes our mobility patterns.
-Many groups have used mobile phone data to explore these changes.
-I wonder, how would the pre-covid embeddings apply to post-covid mobility?
-Once again, I am mindful that this would require access to such data, but I would not be surprised at all if the authors have access to such data—in which case this is remains an intriguing question.
-}
-
-\response{This is an excellent idea, and one that we have been interesting in addressing as well.
-	Unfortunately, however, we do not have access to such data, at least not in large enough quantiaties to be representative.
-	Publications are on a time lag, compared to actual events.
-	For example, a researcher may write a paper while studying at university $A$, but then before the final paper is published, move to university $B$, so while they now have a $B$ affiliation, in our data all we see is the $A$ one.
-	As such, we would not necessarily expect to  see the impact of COVID on bibliometric data until later in 2021 or early 2022, when researchers have had the chance to publich with their new institution.
-	We also not that some activity will, of course, be visible, especially given the number of researchers rapidly publishing on the subject of COVID-19, however we consider this to be an unrepresentative sample, given that it is concentrated in a few disciplines.
-
-	In the future, however, we hope to have access to a fully-representative sample of mobility data to study the effects of COVID-19 on global scientific labor flows.
-	We can use techniqeus developed by other researchers, such as those used by Hamilton, Leskovec, \& Jurafsky (\href{https://nlp.stanford.edu/projects/histwords/}{[link]}), to align embeddings trained on different data in order to quantify the changes in global mobility.
-	We look forward to approaching this, as well as other exciting projects in the future.
-}
-
-%
-% Figure - Distance metric performance
+
+%
+% Figure---Metric performance
 %
@@
 
-\clearpage
-\begin{figure}[p!]
-	\centering
-	\includegraphics[width=0.85\textwidth]{\figdir/Descriptive/distance_prediction_performance_rmse.pdf}
-	\mycaption
-	{Comparison of prediction power across various baselines}
-	{Using cosine distance between embedding vectors as input to the gravity model results in better predictions of scientific mobility compared to geographic distance, baselines.
-		Shown is the Root Mean Squared Error (RMSE), or the accuracy of predictions made with the gravity model of mobility using the embedding distance and other experimental parameters.
-		The RMSE is shown using both the exponential and power-law forms of the gravity model.
-		For each distance metric and set of parameters, the RMSE is shown for
-		Distance metrics are ordered, from top to bottom, by the lowest RMSE, where a lower error indicates better predictions.
-		The asterisk denotes the best-performing distance metric for every case.
-		The x-axis differentiates between three strategies for defining the organization population used to calculate the flux.
-		``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
-		population is defined in the same way for ``mobile-only'', except only using unique mobile researchers;
-		``Raw frequency'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
-		Generally, ``All'' results in better prediction.
-	}
-	\label{fig:supp:distancermse}
-\end{figure}
+We find that, using the best performing dimensions (300) and window size (1),  $\gamma = 1.0$, and for default experimental parameters (global mobility, population defined using all mobile and non-mobile scholars), that the embedding distance, or cosine distance between vectors learned through neural embedding, explains more of the flux, and leads to better predictions than other baselines (Fig.~\ref{fig:supp:distancemetrics}).
+This performance held when considering both the exponential and the power-law forms of the gravity model of mobility. 
+The euclidean distance between directly-factorized vectors performs comparably, and even beats out the embedding distance under certain experimental conditions (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+
+\subsection{Why do neural embeddings outperform direct matrix factorization?}% why sgd is better?
+One question raised by these comparisons is, why do neural-embedding approaches, which rely on stochastic gradient descent, outperform direct matrix factorization, especially seeing as \textit{word2vec} implicitly approximates factorization?
+An issue in the matrix factorization approach is that it is extremely sensitive to small flows between affiliations.
+The matrix factorization approach embeds affiliations $i$ and $j$ such that their dot similarity is as close as to $\log (T_{ij} / P(i) P(j))$.
+If the flow $T_{ij}$ is considerably small or zero, the dot similarity goes $-\infty$, pushing $i$ and $j$ too far from the other affiliations in the embedding space~\autocite{levy2014neural, Qui2018}.
+This is particularly problematic when the window size is small because most affiliation pairs would have no flow, which is indeed the case in our experiments.
+To circumvent this problem, the previous studies~\autocite{levy2014neural, Qui2018} add a constant flow between the affiliation pairs with no flow.
+However, this changes the data to which we fit the model, and small flows still have a considerably strong impact on the embedding.
+
+Also, it is well known that SVD by itself is very vulnerable to outliers \autocite{ xu2012robust, huber1981robust, xu1995robust, chandrasekaran2011rank, candes2011robust, }.
+Compared to SVD, a stochastic gradient descent algorithm (SGD) which is employed in SGNS \textit{word2vec} benefits from the noise in the model itself and can enhance generalization and effectiveness as well \autocite{ma2018power, smith2020generalization, zhang2019algorithmic,}.
+
+\subsection{Changes to the manuscript}
+To reflect these additional experiments, we have made the following changes to our manuscript:
+\begin{itemize}
+	\item Added Fig~\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table} to the manuscript. 
+	\item \todo{add sentence speculating on SGD performance differences into text/supporting meterials}
+\end{itemize}
+
+%
+% SECTION- POINT-BY-POINT DISCUSSION
+%
+\section{Point-by-point discussion}
+All of the referees presented us with excellent, insightful comments and we feel that the changes implemented as a consequence have signiﬁcantly strengthened the manuscript.
+Here we offer further discussion, and introduce several results and figures to support certain arguments.
+
+\subsection{Response to Referee 1}
+
+\rcomment{%
+	To the best of my knowledge, this is the first work providing a thorough analysis of the structure encoded by latent mobility embeddings (e.g., the prestige hierarchy), and this is the first work I am aware of to propose embeddings as an explanatory/exploratory tool in this context.
+In this way, the work has some originality and significance.
+
+	\begin{itemize}
+		\item Liu, Xin, Yong Liu, and Xiaoli Li. ``Exploring the Context of Locations for Personalized Location Recommendations.'' IJCAI. 2016.
+		\item Feng, Shanshan, et al. ``POI2Vec: geographical latent representation for predicting future visitors.'' AAAI. 2017.
+		\item Yao, Zijun, et al. ``Representing Urban Functions through Zone Embedding with Human Mobility Patterns.'' IJCAI. 2018.
+		\item Cao, Hancheng, et al. ``Habit2vec: Trajectory semantic embedding for living pattern recognition in population.'' IEEE Transactions on Mobile Computing 19.5 (2019): 1096-1108.
+	\end{itemize}
+
+	However, the novelty of this work is quite narrow, as there are several prior works that develop trajectory-based embeddings of human mobility based on the word2vec algorithm.
+For example, the following references all propose word2vec-inspired embeddings of human mobility data:
+
+	Notably, the location embedding methodology in Liu et al (2016) (see Section 3.1) is essentially the same as the approach used in the submitted manuscript, and the work by Liu et al (2016) is well-known with over 100 citations.
+}
+
+\response{Thank you for pointing out the missing references!
+We have carefully read through each, and learned a lot in the process.
+They have now been incorperated into our manuscript's introduction.
+}
+
+\rcomment{
+	I found the specific use of the SGNS algorithm unmotivated.
+There are many ways to generate useful low-dimensional embeddings, so why is the SGNS method prioritized above others?
+This method is popular, but popularity alone is not sufficient justification and I see no theoretical reason why it should be the most appropriate method.
+For example, a key point in this manuscript is the fact that the the SGNS embeddings capture the flux between locations better than geographic distance.
+However, if this is such an important point, then why not simply learn a low-dimensional embedding approximation of the flux metric directly?
+such as SVD?
+}
+
+\response{
+	Thank you for the suggestion!
+	Since our original submission, we have made a breakthrough, uncovering a mathematical connection between the skip-gram model with negative sampling, and the gravity model of mobility.
+	Namely, we find that SGNS is a gravity model, and is learns gravity-like relationships between tokens in its vocabulary. 
+	This finding demonstrates why SGNS performs so well, and demonstrates the utility of the model for studying contexts where gravity relationships are expected, such as in human mobility. 
+	We refer you to Section 1 of this letter, above, for an investigation of this connection, and how we adjusted our manuscript given this breakthrough.
+
+	Additionally, we compared the performance of SGNS to several baselines, including the distances between vectors obtained with singular-value decomposition, Laplacian eigenmap, and also Levy 
+	\& Goldberg's~\autocite{levy2014neural} matrix factorization, the last of which directly calculates what SGNS only approximates. 
+	We find that in nearly every case, SGNS outperforms all of these baselines, furhter illustrating the potential of such models for embedding and studying mobility. 
+	We refer you to Section 2 of this rebuttal letter, above, for more detailed results and the changes we made to our manuscript. 
+}
+
+\rcomment{%
+	The methodology has potential limitations in terms of reproducibility and robustness, which should be addressed.
+This is no specific fault of the authors, but both the SGNS/word2vec algorithm and the UMAP algorithm are inherently stochastic.
+This means that these approaches involve inherent randomness, and for researchers to replicate the exact effect seen in this manuscript, one would need to ensure the exact same random seeds etc.
+were used.
+In my view, this is a serious limitation, especially given that the UMAP results and learned embeddings are reified and treated as first-class objects of scientific study.
+}
+
+\response{Thank you for this comment.
+While robustness is a general concern for these methods, we found that their application to our datasets were in fact quite robust, and observed no evidence that findings were the result of methodological artefacts.
+This is confirmed in extra work done in response to these reviews.
+
+We re-ran all of our results using different starting seeds and found all results were qualitatively similar, and almost quantitatively identical.
+	In addition, we expanded the set of experimental parameters, training 18 different embeddings with different dimensions, window sizes, and now, $\gamma$.
+	We found that while performance varies across each combination of parameters, the main results remain qualitatively similar.
+	While we can run more combinations of parameters, and more iterations of \textit{word2vec}, we see no evidence that results will drastically vary.
+
+We believe that the ratio of the number of organizations represented in our dataset to the total number of mobility trajectories makes our results especially robust.
+	Only about 8,661 organizations are represented across over three million career trajectories of scientists, such that nearly every organization appears enough times, and in enough contexts, to produce a robust vector representation.
+	However, this may not hold true for all problem domains—for example, natural language includes many millions of tokens, many of which will occur only a few times, allowing stochasticity to have a much stronger effect on the final representation.
+	Heeding this as a general concern, we have added the following sentence to our limitations paragraph in our conclusion:
+
+“We however, note that all results shown here are robust to this stochasticity, likely emerging from the limited ``vocabulary'' of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories).
+Applications of word2vec to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random artifacts.”
+
+}
+
+\rcomment{%
+	Another interesting point in this work is that the authors chose to not report p-values or the results of statistical significance tests (except confidence intervals).
+I presume this was a conscious decision, which I do not necessarily agree with.
+I see no critical error in the approach used by the authors, but I would have found aspects of the manuscript easier to understand in places with results of statistical tests (e.g., associated with goodness-of-fit tests formally test that the embedding-based distances are more correlated with the flux values).
+Given the sample sizes involved, I have no doubt that the results are statistically significant.
+However, I personally do see value in rigorously performed frequentist hypothesis testing, and I felt that this manuscript could be improved by employing such techniques.
+
+	Lastly, the authors do not actually state how the 99 confidence intervals were constructed. (E.g., was this via a bootstrap approach?) This detail should be added.
+}
+
+\response{Thank you for this feedback.
+	You are correct that it was a conscious choice to not report statistical significance in the form of a P-value.
+	The use of statistical significance is contentious, and Nature itself has hosted some of this debate (\href{https://www.nature.com/articles/d41586-019-00857-9}{[link]}).
+	As such, we have a philosophy of avoiding p-values in research when it makes sense to do so.
+	In our analysis, all correlations and fits are significant at a level below 0.0001, or have a p-value  computationally indistinguishable from zero.
+	However, we recognize that p-values can help readers interpret results.
+	As such, we have opted to add to a sentence such as \say{\textit{Correlation is calculated on the data in the log-log scale ($p <<0.0001$ across all fits)}.} or similar to relevant figures in the main text and supporting materials.
+	We believe that this solution strikes a balance between transparency while also avoiding extraneous detail and the common pitfalls of statistical reporting.
+
+	We have also provided detail about how confidence intervals were calculated in relevant figure captions.
+	For example, we state in figure 2's caption that \say{\textit{99\% confidence intervals are plotted for the mean flux in each bin based on a normal distribution.}}, which should give readers enough information to reproduce the confidence intervals following their standard definition.
+	Other confidence intervals, such as intervals for the loess regression line in figure 6, are calculated using the smoothing functions in the \texttt{ggplot2} package of R, and refer readers to the relevant documentation.
+}
+
+\rcomment{%
+	F. Suggested improvements:
+	References and discussion of prior work using word2vec-style embeddings of mobility data.
+	Additional experiments using alternative embedding methods, especially an SVD-based embedding method, as well as robustness/reproducibility studies across different runs of the SGNS would be essential to strengthen the paper.
+	In addition, some additional results demonstrating how the embeddings provide novel scientific insight, rather than just recapitulating known structures, would be essential to make this work above-the-bar for a high-impact publication such as Nature.
+
+}
+
+\response{We believe that the mathematical breakthroughs made since our first submission improve the manuscript and extend its contribution and demonstrates novel scientific insight, and justifies the use of word2vec towards mobility data.
+By adding this, and addressing your other points (above), we believe that the revised manuscript sufficiently remedies your concerns.
+
+}
+
+%===================================================
+
+%
+% Response to reviewer 2
+%
+\subsection{Response to Referee 2}
+
+\rcomment{%
+	Although the paper is well written and explores a very interesting problem, I have certain criticism for the used methodology.
+After obtaining a representation of each dataset, the authors defined an embedding distance as the cosine distance between vectors in the space, while defining distance as the geographical distance in the original, spatially embedded datasets.
+Subsequently they used the Gravity Law to estimate the flux between location pairs of vector pairs in the spatial and embedded space respectively.
+The Gravity Law, applied on mobility, assumes that the number of people moving between two populations is proportional to the multiplicative of the sizes of the populations and a deterrence function.
+Research during the last decades on transportation, spatial networks and human mobility suggests that this deterrence function may take a functional form of an inverse exponential or an inverse power-law, as it has been acknowledged by the authors.
+However, the emergence of these different deterrence functions can be due to fundamentally different mechanisms (for a review on the topic see Barthélemy, Physics Reports 499, 1, 2011, a paper not cited in the manuscript).
+For example, the different cost functions (linear or logarithmic) to create link at a given distance, the spatial granularity of the observation, or even the heterogeneity of the moving individuals in terms of various factors, just to mention a few examples.
+Instead, the authors of the actual paper arbitrarily assumed a power-law deterrence function in the spatial case and an exponential deterrence function in the embedding space without further arguing their choice (other than fitting on the data).
+Furthermore, assuming different deterrence functions for the flux estimation using Gravity Law makes the estimated fluxes incomparable, resulting the invalidation of results depicted in Figure 2.
+}
+
+\response{Thank you for pointing this out.
+	We carefully read out the Barthélemy, Physics Reports 499, 1, 2011, and referenced it in our manuscript.
+	Also, we report the performance of the flux estimation and prediction using different deterrence functions (see Section 2, above), finding that while performance differs, the embedding distance outperforms geographic distance no matter the function used.
+	We add the following line to the methods noting this point,
+
+	\medskip
+	\say{The decay function $f(r_{ij})$ defines the effect of distance, and so different decay functions can model fundamentally different mechanism [...] such as the cost functions for a given distance and the spatial granularity of the observation.
+		For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case though the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Supporting Information).}
+
+	We also argue that geographical distance ﬁts well with the power-law decay function because power-based gravity model can be more suitable for analyzing large, complex, and scale-free spatial systems and the exponential-based gravity model indicates simplicty rather than spatial complexity~\autocite{chen2015distance}.
+Meanwhile, embedding distance ﬁts well with the exponential decay function, which we demonstrate to correspond to an underlying mathematical relationship between \textit{word2vec} and the gravity model, a connection we recently discovered and included as a major finding in this revision (see our response to Referee 1).
+
+}
+
+\rcomment{
+	I would suggest to the authors to carefully cite other papers applying Word2Vec embedding on spatial data, especially focusing on location embedding based on trajectory sequences. Examples are:
+	\begin{itemize}
+		\item A.
+Solomon et al., Predict Demographic Information Using Word2Vec on Spatial Trajectories., ACM UMAP '18: Proceedings of the 26th Conference on User Modeling, Adaptation and Personalization, July 2018 Pages 331–339, https://doi.org/10.1145/3209219.3209224
+		\item A.
+Crivellari and E.
+Beinat, From Motion Activity to Geo-Embeddings: Generating and Exploring Vector Representations of Locations, Traces and Visitors through Large-Scale Mobility Data., ISPRS Int.
+J.
+Geo-Inf.
+2019, 8(3), 134 (2019); https://doi.org/10.3390/ijgi8030134
+
+	\end{itemize}
+
+	The application of the Word2Vec method on the studied trajectory sequences is not well explained.
+Without explaining the embedding method briefly in the main text the reader has no idea how to interpret the embedding distance, which is in the hear of the study.
+
+}
+
+\response{Thank you.
+We have added the following sentence to the introduction: “It works under the notion that a good representation should facilitate prediction, and so learns a mapping of target locations (words) that best predict locations that co-appear in the same trajectory (sentence).”
+
+	In addition, we provided more explicit mathematical detail of word2vec in the new subsection entitled “word2vec and the gravity model”.
+You can read about this connection in Section 1 of this letter, above.
+
+	We believe that these details are sufficient in the main text of the manuscript, and refer readers to the Methods for a deeper explanation.
+}
+
+\rcomment{
+
+	The original SkipGram method expects environments of locations (originally words) with fixed length, however this is not explained in the manuscript nor in Methods or the SI.
+	Related question to the previous one.
+Let’s assume that the authors used fixed window lengths and, as mentioned in Methods Embedding section (and demonstrate in Fig.S4 - not referenced in Methods), that the windows size w=1 gives the best correlations in case of scientific mobility.
+This might be true in absolute terms but it is an unfair comparison to larger window sizes, as there are way more short trajectories in the data than longer ones (see Fig.S3), thus the flux prediction of w=1 is based on a way larger sample than for w$>$1.
+Undersampling the ensemble of trajectories used for w=1 predictions might provide a fair way of comparing results of different window sizes.
+}
+
+\response{
+\todo{Thoughts on this response? Still not 100\% sure I follow the reviewer}
+Thank you for this comment.
+We however, do not believe that this is a problem in our analysis.
+Raw co-occurrence, which is used to define our 'flux' between organizations, is always calculated using all organizations in a trajectory, and so window size does not affect flux. 
+Window size does affect \textit{word2vec}, however setting a smaller/larger window size should not make results incomparable. 
+When we set $w = 1$, \textit{word2vec} will generate training pairs at most 1 position away from each target location, for all possible targets. 
+When we instead set $w = 2$, \textit{word2vec} will generate training pairs the same way, but at most 2 positions away from each target---this means that the data for $w = 2$ will be \textit{larger}, containing as a subset all training pairs used for $w = 1$.
+The same follows for all $w > 1$, each generating a larger and larger set of training examples up until $w$ is larger than the length of the longest trajectory.
+
+What is notable about our findings, therefore, is that even though a model trained with $w = 1$ generates fewer training samples, it still outperforms $w > 1$ settings, which use more training samples, and which should capture higher-order structures in the data.
+We speculate that this is because the word2vec model with $w = 1$ is equvelant to the gravity model of mobility (see Section 1). 
+}
+
+\rcomment{
+	The other very important parameter of the SkipGram method is the embedding dimension, which is explained in the Methods but it is not explored.
+E.g.
+to choose the ideal dimension for embedding one may sweep through a broad range of possible dimensions and not only explore three values as described in the SI (Fig.S4).
+	Their main observations in section “Embeddings provide functional distance between locations” is that “…our results demonstrate that, consistently, the embedding distance better captures patterns of actual mobility than does the geographic distance.”.
+This is a great verification of their method but it is somewhat expected from an embedding, which is built on mobility trajectories between places, as compared to cases based on simply geographic distance.
+
+}
+\response{
+	Thank you for these comments.
+First, we added a line to the methods section detailing the \textit{word2vec} we used, and noting that these achieved the bst performance: \say{\textit{For main results regarding scientific mobility, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig....)}}.
+	A full search of the parameter space would certainly be interesting and useful, however we believe that set of parameters we considered here is sufficient to establish the utility of the approach, and demonstrate that performance is only slightly different based on different parameters.
+}
+
+\rcomment{
+	When datasets in the intro are explained, it should be mentioned that the detailed descriptions are in the Methods section.
+}
+\response{Thank you.
+We have added a parenthetical to the introduction after stating the datasets, as follows:  \say{We embed trajectories from three massive datasets: U.S.
+passenger flight itinerary records, Korean accommodation reservations, and a dataset of scientists' career mobility between organizations captured in bibliometric records (Detailed descriptions are available in the Methods).}
+}
+\rcomment{
+	Some minors comments
+	\begin{enumerate}
+		\item There is no reference to Fig.5e and f in the text.
+		\item Second paragraph on page 10: the authors discuss Fig.6 here but missed to refer the figure.
+		\item Page 15, last row: double point in the end of sentence.
+		\item SI Page 2, S3: “. if” $\rightarrow$ “. If”
+	\end{enumerate}
+}
+\response{Thank you, we have remedied these comments and have updates the manuscript accordingly,
+}
+
+\rcomment{
+	SI Fig.S1c: Here the authors conclude that the proportions “decreased over time”.
+These proportions seem to be rather flat without strong decreasing trends.
+In any case, if the authors would like to indicate minor changes here, it would be helpful for the reader if a grid would be posted on the figure.
+}
+\response{Thank you, we agree that the trend is flat, rather than decreasing. We have adjusted the text accordingly, and also added a grid to the figure so that it can be more easily read.
+
+}
+
+\rcomment{
+	SI Fig.S3: Posted numerical values on the figures and the values described in the caption do not match.
+}
+\response{Thank you for pointing out this oversight. The caption values have been updated.
+}
+
+\rcomment{SI Fig.S6: Please indicate what is RMSE in the caption. The authors defined it in the main text but the SI should be self consistent too.
+}
+\response{We have added the line “RMSE is the root-mean-squared error between the actual and predicted values.” to Fig. S6 as well as all other SI figures that make use of the same visualization.
+}
+
+\rcomment{SI Fig.S7: The authors state that “The gravity model with the exponential decay function outperforms that with a power-decay function.” - this does not seem to be true for the “International” case.
+Please specify this in the caption.
+}
+
+\response{We have updated the relevant line of the caption to read as follows:
+	“The gravity model with the exponential decay function slightly outperforms that with a power-decay function except in the case of international-only mobility, for which power-decay performs slightly better.”
+}
+
+\subsection{Response to Referee 3}
+
+\rcomment{The analysis does not compare embeddings, which would not be a problem if they were making
+	an inference other than we can embed micro-mobility to trace macro-mobility. They use an
+	efficient (Google engineers developed it), single-layer embedding from 2013, which produces
+	linear associations. But the paper doesn’t take advantage of the revolution in deep neural
+	network models that now produce powerful, nonlinear and noncontiguous (e.g., using the
+	attention architecture) models that now dominate analysis of language, and are making very
+	power inroads in machine vision.
+To be clear, deeper models require much data and computational power to tune—they are an engineering feat—but if developed in these settings, they would likely dramatically improve the prediction of flux.
+They take into account directionality (e.g., a person moving from one opportunity to another) and would independently capture people how people distinctly move up and down the hierarchy or from place to place (e.g., a in bi-directional model like BERT).
+A lack of discussion or demonstration of which model works best--and the unfounded inference that direction does not matter felt weak without a demonstration that they would not have worked better.
+They did and do work much better for language models and for image generation...why would they not work for analysis of human mobility?
+(I’m sure they would, but this would time and independent development.)
+}
+
+\response{Thank you for this insightful comment!
+	We think that there is a great deal of potential in methods like BERT for representing mobility data.
+	What initially drew us to \textit{word2vec}, however, was its simplicity, its ubiquity, and its mathematical tractability (at least compared to other, more sophisticated approaches).
+	This last attribute proved very useful, as in exploring the mathematical properties of the model, we discovered a deep connection between \textit{word2vec} and the gravity model of mobility, which explains why it learns such effective gravity-like relationships between entities (see Section 1, this letter).
+	We believe hat this new discovery, now included in the manuscript, justifies our use of \textit{word2vec} here.
+
+	We agree that the revolution in neural embeddings offers great promise in mobility and look forward to reading and also working on these future studies; however, we argue that our contribution is most well-founded, and best serves the scientific community, by working with simpler and more established models (see Section 2, this letter), especially concerning the mathematical link we uncovered.
+Moreover, these deep models require a tremendous amount of training data ($\sim$3 billion words in Bert) and model parameters, making their use more cumbersome.
+
+	To highlight the importance of altenrative models, however, we add the following line to our conclusion: \say{\textit{Future studies may also consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality.
+}}.
+
+}
+
+\rcomment{
+	The paper does not compare human transition (or co-affiliation) data with any other kinds of
+	data that could be used for embedding. Does author byline data do better than the embedding
+	of collaborating institutions (almost certainly), than co-mention of the institutions in the press, as
+	with institutional collaborations (e.g, the Harvard-MIT Broad Institute, or joint university
+	conferences; these will be stronger signals, but there are fewer of them), than advisor-student
+	university pairs (although many of these will be captured by the authors’ approach when
+	students publish at their home institutions before securing jobs elsewhere).
+}
+
+\response{
+	Thank you for this comment!
+	We feel that applying these embeddings to other areas of scientific activity would be incredibly enlightening!
+	Your recommendation of collaboration (based on the author byline) and advisor-student pairs are especially interesting, and we would aim to address these areas in future studies.
+	However, given the importance of mobility to science, the importance of human mobility more generally, and the connection we discovered between \textit{word2vec} and the gravity model, that a focus of co-affiliation, which most closely aligns with ideas of mobility, is the most reasonable data to use for this manuscript.
+}
+
+\rcomment{
+	There are known concerns with clustering a 300 dimensional objects because of the curse of
+	dimensionality. Many have shown that reducing dimensionality with UMAP to a nontrivial
+	number of dimensions (e.g., 30), which preserves both local and some global distance, then
+	clustering on those dimensions are much more stable (e.g., this post). This was one
+	concern with the stability of the clustering analysis
+
+}
+
+\response{Thank you for this suggestion.
+	We looked into this, using UMAP to reduce the country-level embeddings from 300 down to 30 dimensions, however the results from this were incomprehensible, and inferior to those using 300 dimensions.
+	Many dimensionality reduction techniques reduce the number of dimensions by maintaining pairwise distances between vectors, so that the result can be well-suited for clustering algorithms.
+	However, our approach already uses raw pairwise similarities to perform hierarchical clustering, so approximating this distance in 30 dimensions, and then using the new distances to perform clustering is redundant.
+	We also find that the curse of dimensional is not a major issue in our analysis, at least given the size of our data and the number of locations represented---\textit{word2vec} seems able to learn dense vector-space representations.
+}
+
+\rcomment{
+	P6Para3: “For THEIR purpose…”
+}
+
+\response{Thank you, we have corrected this mistake.
+}
+
+\rcomment{
+	P8Para1: “by explicitly the relative importance of different level of the hierarchy with a scaling parameter r ” which is never described or explained.
+Considering it was derived by the authors in a very recent paper, no one will know what it is.
+}
+
+\response{Thank you, we have edited the text to read as “We quantify the relative importance of geography (by region), and language (by the most widely-spoken language of each country) using the element-centric clustering similarity, a method that can compare hierarchical clustering and disjoint clustering (geography, language...) at the different level of hierarchy by explicitly adjusting a scaling parameter $r$, acting like a zooming lens”
+}
+
+\subsection{Response to Referee 4}
+
+\rcomment{
+	The authors define the distance function in terms of either the geographic distance between locations or their functional distance in the vector space.
+The increase in R2, as they switch to the embedding distance, is rather convincing.
+One of the models they use as a reference is the gravity model, but they also mention the radiation model.
+I am curious if they tried a comparison with that, and what was the outcome.
+I suspect that the radiation model would have a comparable performance to the gravity one.
+But as distance is not the only factor there, is a comparison at all feasible?
+}
+
+\response{Thank you for this suggestion.
+	We agree that comparing the radiation model would be incredibly interesting.
+	However, we originally did not use radiation model because our dataset on scientific mobility lacked clear directionality, which is required by the radiation model of mobility.
+	Scientific mobility is incredibly complex, the most common form of mobility being co-affiliation, or a researcher holding multiple affiliations simultaneously.
+	In these cases, it is difficult to discern a researcher's main affiliation (where they start), and eventual affiliation (where they end up).
+	As such, we conceive of scientific mobility as having no direction (see S2 Text).
+	Given these considerations, we instead chose to use the standard gravity model of mobility, which models mobility as symmetric.
+	Moreover, we have recently discovered an underlying mathematical relationship between \textit{word2vec} and the gravity model of mobility, further justifying our choice.
+	While we are excited to investigate the use of neural embeddings with the radiation model, we believe it to be outside the scope of our current submission.
+}
+
+\rcomment{
+	My second group of questions pertain to the prestige hierarchy, that really drives the dynamics of scientific mobility.
+The technical description addressed most of them.
+However, I was wondering, is it all possible to go beyond the descriptive part, and show cases where the more accurate embedding base distances do make a difference?
+That is, using them, we do not only obtain better correlations with the ranking data, but also allows us to address problems that we could not without the embedding distance?
+For example, some results have shown that a paper coauthored by two authors at different high prestige institutions has higher impact, than writing a paper with two authors of the same high prestige institution—would embedding help us pull apart such effects?
+Here I am not trying to make the authors to write a different paper, so maybe a little forward thinking may be enough, if doing the actual work is too time consuming, and goes beyond the current narrative.
+}
+
+\response{Thank you for this idea!
+	We believe that this is an interesting topic and we hope to investigate it in the future.
+	In your particular example, an embedding distance trained using sequences of co-authorship on the same paper might be better to capture the \textit{collaborative} distance between institutions.
+	Then, using that distance, one could measure the ``embedding distance'' spanned by all authors in the byline, and relate this to questions impact to determine whether (a)typical collaborations relate to impact.
+	This is certainly a topic that is in our mind for future study.
+	In the case of scientific mobility, we might also consider the ``embedding distance'' spanned by an individual's career, and relate this to their demographics and scientific impact.
+
+	However, while these topics are exciting, we believe that that they fall outside the scope of the current manuscript, especially given the discoveries we made concerning a fundamental connection between the gravity law of mobility and \textit{word2vec}.
+}
+
+\rcomment{
+	Finally, one cannot escape the fact that COVID changes our mobility patterns.
+Many groups have used mobile phone data to explore these changes.
+I wonder, how would the pre-covid embeddings apply to post-covid mobility?
+Once again, I am mindful that this would require access to such data, but I would not be surprised at all if the authors have access to such data—in which case this is remains an intriguing question.
+}
+
+\response{This is an excellent idea, and one that we have been interesting in addressing as well.
+	Unfortunately, however, we do not have access to such data, at least not in large enough quantiaties to be representative.
+	Publications are on a time lag, compared to actual events.
+	For example, a researcher may write a paper while studying at university $A$, but then before the final paper is published, move to university $B$, so while they now have a $B$ affiliation, in our data all we see is the $A$ one.
+	As such, we would not necessarily expect to  see the impact of COVID on bibliometric data until later in 2021 or early 2022, when researchers have had the chance to publich with their new institution.
+	We also not that some activity will, of course, be visible, especially given the number of researchers rapidly publishing on the subject of COVID-19, however we consider this to be an unrepresentative sample, given that it is concentrated in a few disciplines.
+
+	In the future, however, we hope to have access to a fully-representative sample of mobility data to study the effects of COVID-19 on global scientific labor flows.
+	We can use techniqeus developed by other researchers, such as those used by Hamilton, Leskovec, \& Jurafsky (\href{https://nlp.stanford.edu/projects/histwords/}{[link]}), to align embeddings trained on different data in order to quantify the changes in global mobility.
+	We look forward to approaching this, as well as other exciting projects in the future.
+}
 

### 2021-02-10 paper/current/main.tex
add text about why cosine better and in/out are different

@@
 Therefore, the embedding distance is inherently tied to the flow, and hence, has greater predictive power than the geographic distance.
+
+A central assumption in our mathematical analysis is that the embedding vectors are optimum in terms of the {\it word2vec}'s objective function.
+However, the embedding vectors are sub-optimal in practice because the optimization algorithm is stochastic and can be trapped in a local optimum.
+This has two consequences.
+First, the suboptimal in- and out-vectors can be different, which goes against the premise that the (optimal) in-vectors and out-vectors are identical.
+Second, dot similarity should in principle predict the mobility flow better than cosine similarity because dot similarity includes cosine similarity as its special case.
+However, our simulations show that it is the cosine similarity that better predicted the mobility flow~[reference to a figure].
+This phenomenon---cosine similarity outperforms dot similarity---has been observed in many applications of word embedding~\cite{add citations}.
+Yet, why cosine similarity is superior to dot similarity has not been clearly understood.
+Nevertheless, among the 7(?) measures tested in our simulations, dot similarity is the second-best predictor of mobility flow following cosine similarity.
+Furthermore, unlike cosine similarity, dot similarity has a mathematical connection to the gravity model.
 

### 2021-02-10 paper/current/main.tex
add tables to main and supp text

--- 2021-02-01 paper/current/main.tex
@@
 \newcommand{\tabref}[1]{Table~\ref{tab:#1}}
+\newcommand{\todo}[1]{{\leavevmode\color{orange}[TODO: #1]}}
 %\newcommand{\eqnref}[1]{\eqref{eq:#1}}
@@
 The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores  calculated from the underlying mobility network (Fig.~\ref{fig:supp:distancemetrics}, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baseline, such as distances derived from a singular-value decomposition on flow matrix and from a Laplacian Eigenmap embedding  \autocite{belkin2003laplacian} of the underlying data (Fig.~\ref{fig:supp:distancemetrics} and Fig.~\ref{fig:supp:distancermse}).
+The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baseline, such as distances derived from a singular-value decomposition on flow matrix and from a Laplacian Eigenmap embedding  \autocite{belkin2003laplacian} of the underlying data (Fig.~\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), in many cases even putperforming a direct factorization approach~\cite{levy2014neural}), which \textit{word2vec} efficiently approximates.
 In sum, our results demonstrate that, consistently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
@@
 Therefore, the embedding distance is inherently tied to the flow, and hence, has greater predictive power than the geographic distance.
+
+\todo{add stuff about cosine distance performing better, SGD performing better}
 
@@
 
-Neural embedding approaches offer a novel, data-driven solution for learning an effective and robust representation of locations based on trajectory data, encoding the complex and multi-faceted nature of mobility.
+Neural embedding approaches offer a novel, data-driven solution for efficiently learning an effective and robust representation of locations based on trajectory data, encoding the complex and multi-faceted nature of mobility.
 We demonstrated that a functional distance derived from the embedding can be used with the gravity model of mobility to better predict real-world mobility than does geographic distance.
@@
 We discover that this performance results from neural embeddings implicitly learning gravity law relationships between locations, making them particularly well suited to representing mobility.
-Focusing on scientific mobility, we find that neural embedding's performance is driven by its ability to encode many aspects of scientific mobility into a single representation, including global and regional geography, shared languages, and prestige hierarchies, even without explicit information on these factors.
+Focusing on scientific mobility, we find that the embedding successfully encodes many aspects of scientific mobility into a single representation, including global and regional geography, shared languages, and prestige hierarchies, even without explicit information on these factors.
 
-While we focus on three domains of mobility, this approach may be broadly applicable to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
+While we focus on three domains of mobility, this approach may be broadly applicable to other kinds of mobility data that is expected to follow a gravity-like pattern, such as general human migration, transit-network mobility, and more.
 Moreover, this approach can be used to learn a functional distance even between entities for which no physical analog exists, such as between occupational categories based on individuals' career trajectories.
@@
 
-We calculate two forms of distance between locations.
+We calculate two main forms of distance between locations.
 The geographic distance, $g_{ij}$, is the pairwise geographic distance between locations.
@@
 Nevertheless, cosine distance is often shown to be useful in practice~\autocite{lerman2007embedding, brown1970migration, kim2018functional}.
+We compare the performance of this cosine-based embedding distance against those derived using dot product similarity and euclidean distance.
+
+We compare the performance of the embedding distance to many baselines. 
+These include distances derived from simpler embedding approaches, such as Singular Value Decomposition (SVD) and a Laplacian Eigenmap embedding performed on the underlying co-occurrence matrix. 
+We also use network-based distances, calculating vectors using a Personalized Page Rank approach and measuring the distance between them using cosine distance and Jensen-Shannon Divergence (see \SI).
+Finally, we compare the embedding distnace against embeddings calculated through direct matrix factorization, following the approach that \textit{word2vec} implicitley approximates~\cite{levy2014neural}.
 

### 2021-02-10 paper/current/main.tex
fix broken reference

@@
 The decay function $f(r_{ij})$ defines the effect of distance, and so different decay functions can model fundamentally different mechanism \autocite{barthelemy2011spatial} such as the cost functions for a given distance and the spatial granularity of the observation.
-For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}), though the embedding distance outperforms geographic distance regardless of the type of gravity model used (Fig.~\ref{fig:supp:distancermse}).
+For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}), though the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
 Beyond the fitting on the data, we would like to argue that geographical distance fits well with the power-law decay function because it is more suitable for analyzing large, complex, and scale-free spatial systems\autocite{chen2015distance}, while embedding distance fits well with the exponential decay function, which we will show later in the section of mathematical relation between \textit{word2vec}and the gravity model.

### 2021-02-11 paper/current/main.tex
re-edit the paragraph on the limitations in math

--- 2021-02-10 paper/current/main.tex
@@
 \newcommand{\tabref}[1]{Table~\ref{tab:#1}}
-\newcommand{\todo}[1]{{\leavevmode\color{orange}[TODO: #1]}}
 %\newcommand{\eqnref}[1]{\eqref{eq:#1}}
@@
 The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores  calculated from the underlying mobility network (Fig.~\ref{fig:supp:distancemetrics}, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baseline, such as distances derived from a singular-value decomposition on flow matrix and from a Laplacian Eigenmap embedding  \autocite{belkin2003laplacian} of the underlying data (Fig.~\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), in many cases even putperforming a direct factorization approach~\cite{levy2014neural}), which \textit{word2vec} efficiently approximates.
+The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baseline, such as distances derived from a singular-value decomposition on flow matrix and from a Laplacian Eigenmap embedding  \autocite{belkin2003laplacian} of the underlying data (Fig.~\ref{fig:supp:distancemetrics} and Fig.~\ref{fig:supp:distancermse}).
 In sum, our results demonstrate that, consistently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
@@
 
-\todo{add stuff about cosine distance performing better, SGD performing better}
+A central assumption in our mathematical analysis is that the embedding vectors are optimum in terms of the {\it word2vec}'s objective function.
+However, this premise is not practical because the optimization algorithm often finds sub-optimal embeddings due to its stochasticity and being trapped in a local optimum.
+This has two consequences.
+First, the in- and out-vectors can be different.
+Second, dot similarity should in principle predict the mobility flow better than cosine similarity because dot similarity includes cosine similarity as its special case.
+However, our simulations show that it is the cosine similarity that better predicted the mobility flow~[reference to a figure].
+This phenomenon---cosine similarity outperforms dot similarity---has been observed in many applications of word embedding~\cite{add citations}.
+Nevertheless, among the 7(?) measures tested in our simulations, dot similarity is the second-best predictor of mobility flow following cosine similarity.
+Furthermore, unlike cosine similarity, dot similarity has a mathematical connection to the gravity model.
 
@@
 
-Neural embedding approaches offer a novel, data-driven solution for efficiently learning an effective and robust representation of locations based on trajectory data, encoding the complex and multi-faceted nature of mobility.
+Neural embedding approaches offer a novel, data-driven solution for learning an effective and robust representation of locations based on trajectory data, encoding the complex and multi-faceted nature of mobility.
 We demonstrated that a functional distance derived from the embedding can be used with the gravity model of mobility to better predict real-world mobility than does geographic distance.
@@
 We discover that this performance results from neural embeddings implicitly learning gravity law relationships between locations, making them particularly well suited to representing mobility.
-Focusing on scientific mobility, we find that the embedding successfully encodes many aspects of scientific mobility into a single representation, including global and regional geography, shared languages, and prestige hierarchies, even without explicit information on these factors.
+Focusing on scientific mobility, we find that neural embedding's performance is driven by its ability to encode many aspects of scientific mobility into a single representation, including global and regional geography, shared languages, and prestige hierarchies, even without explicit information on these factors.
 
-While we focus on three domains of mobility, this approach may be broadly applicable to other kinds of mobility data that is expected to follow a gravity-like pattern, such as general human migration, transit-network mobility, and more.
+While we focus on three domains of mobility, this approach may be broadly applicable to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
 Moreover, this approach can be used to learn a functional distance even between entities for which no physical analog exists, such as between occupational categories based on individuals' career trajectories.
@@
 Third, neural embeddings are an inherently stochastic procedure, and so results may change across different iterations.
-We however, note that all results shown here are robust to this stochasticity, likely emerging from the limited "vocabulary" of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories).
+We however, note that all results shown here are robust to this stochasticity, likely emerging from the limited ``vocabulary'' of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories).
 Applications of \textit{word2vec }to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random artifacts.
@@
 
-We calculate two main forms of distance between locations.
+We calculate two forms of distance between locations.
 The geographic distance, $g_{ij}$, is the pairwise geographic distance between locations.
@@
 Nevertheless, cosine distance is often shown to be useful in practice~\autocite{lerman2007embedding, brown1970migration, kim2018functional}.
-We compare the performance of this cosine-based embedding distance against those derived using dot product similarity and euclidean distance.
-
-We compare the performance of the embedding distance to many baselines. 
-These include distances derived from simpler embedding approaches, such as Singular Value Decomposition (SVD) and a Laplacian Eigenmap embedding performed on the underlying co-occurrence matrix. 
-We also use network-based distances, calculating vectors using a Personalized Page Rank approach and measuring the distance between them using cosine distance and Jensen-Shannon Divergence (see \SI).
-Finally, we compare the embedding distnace against embeddings calculated through direct matrix factorization, following the approach that \textit{word2vec} implicitley approximates~\cite{levy2014neural}.
 

### 2021-02-11 paper/current/main.tex

--- 2021-02-10 paper/current/main.tex
@@
 A central assumption in our mathematical analysis is that the embedding vectors are optimum in terms of the {\it word2vec}'s objective function.
-However, the embedding vectors are sub-optimal in practice because the optimization algorithm is stochastic and can be trapped in a local optimum.
+However, this premise is not practical because the optimization algorithm often finds sub-optimal embeddings due to its stochasticity and being trapped in a local optimum.
 This has two consequences.
-First, the suboptimal in- and out-vectors can be different, which goes against the premise that the (optimal) in-vectors and out-vectors are identical.
+First, the in- and out-vectors can be different.
 Second, dot similarity should in principle predict the mobility flow better than cosine similarity because dot similarity includes cosine similarity as its special case.
@@
 This phenomenon---cosine similarity outperforms dot similarity---has been observed in many applications of word embedding~\cite{add citations}.
-Yet, why cosine similarity is superior to dot similarity has not been clearly understood.
 Nevertheless, among the 7(?) measures tested in our simulations, dot similarity is the second-best predictor of mobility flow following cosine similarity.

### 2021-02-11 paper/current/supp.tex

@@
 \def\mat#1{\mathbf{#1}}
+
+%
+% Huxtable dependencies (see R package)
+\usepackage{array}
+\usepackage{siunitx}
+%\usepackage{ulem}
+\usepackage{colortbl}
+\usepackage{multirow}
+\usepackage{hhline}
+\usepackage{calc}
+\usepackage{tabularx}
+\usepackage{threeparttable}
+\usepackage{adjustbox}
+
+% Allow landscape rotation on table page
+\usepackage{lscape}
 
@@
 
+%
+% R2 Table
+%
+\clearpage
+\begin{landscape}
+
+  \providecommand{\huxb}[2]{\arrayrulecolor[RGB]{#1}\global\arrayrulewidth=#2pt}
+  \providecommand{\huxvb}[2]{\color[RGB]{#1}\vrule width #2pt}
+  \providecommand{\huxtpad}[1]{\rule{0pt}{#1}}
+  \providecommand{\huxbpad}[1]{\rule[-#1]{0pt}{#1}}
+
+\begin{table}[ht]
+\caption{
+	\textbf{Correlation between flux and distance over metrics, experimental parameters}.
+	Each cell corresponds to the correlation (measured with $r^{2}$) between the real-world flux between scientific organizations, comparing the embedding distance against baseline metrics, and across subsets of mobility data and by definitions of organization population.
+	The asterisk denotes the top-performing distance metric by column. 
+	Distance metrics are ordered from highest $r^{2}$ to lowest, based on global mobility with organization population defined using all mobile and non-mobile authors. 
+	``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
+		population is defined in the same way for ``Mobile only'', except only using unique mobile researchers;
+		``Raw freq'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
+		Embedding distance, measured as the cosine distance between embedding vectors, explains more of the flux than baselines in nearly every case, except using raw frequency population and domestic and international mobility, where direct-factorization approaches~\autocite{levy2014neural} work better.
+}
+\label{supp:table:r2_table}
+\begin{centerbox}
+\begin{threeparttable}
+\small
+ \setlength{\tabcolsep}{0pt}
+\begin{tabular}{l l l l l l l l l l}
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}c!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{} \hspace{6pt}\huxbpad{0pt}} &
+\multicolumn{3}{c!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{All} \hspace{6pt}\huxbpad{0pt}} &
+\multicolumn{3}{c!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{Mobile only} \hspace{6pt}\huxbpad{0pt}} &
+\multicolumn{3}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{Raw freq} \hspace{6pt}\huxbpad{0pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{ } \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}-}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.481 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.418 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.435 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.492 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.456 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.489 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.325 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.251 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.252 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.341 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.369 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.382 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.213 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.271 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.284 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.305 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.323 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.334 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.341 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.313 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.316 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.254 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.265 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.267 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.218 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.181 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.177 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.247 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.297 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.309 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.213 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.314 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.325 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.111 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.152 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.16 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Geographic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.219 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.174 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.197 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.188 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.157 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.176 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.04 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.019 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.03 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Laplacian cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.212 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.199 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.218 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.176 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.157 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.18 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.079 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.1 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.111 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.208 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.227 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.231 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.169 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.246 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.246 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.057 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.054 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.053 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR JSD} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.194 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.276 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.276 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.218 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.335 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.335 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.012 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.077 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.069 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.138 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.136 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.143 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.196 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.186 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.197 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.13 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.149 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.152 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.004 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.013 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.004 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.039 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.034 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.035 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+\end{tabular}
+\end{threeparttable}\par\end{centerbox}
+
+\end{table}
+
+\end{landscape} % End r2 table page
+
+%
+% RMSE TABLE --- Exponential model
+%
+\clearpage
+\begin{landscape}
+
+  \providecommand{\huxb}[2]{\arrayrulecolor[RGB]{#1}\global\arrayrulewidth=#2pt}
+  \providecommand{\huxvb}[2]{\color[RGB]{#1}\vrule width #2pt}
+  \providecommand{\huxtpad}[1]{\rule{0pt}{#1}}
+  \providecommand{\huxbpad}[1]{\rule[-#1]{0pt}{#1}}
+
+\begin{table}[ht]
+\caption{
+	\textbf{Prediction error between actual and predicted mobility with exponential gravity model, by metrics and experimental parameters}.
+	Each cell corresponds to the prediction error (measured with root mean squared error) between the real-world flux between scientific organizations and predictions made with the exponential form of the gravity model of mobility.
+	The prediction error is shown for the embedding distance compared against baselines, subsets of mobility data, and definitions of organization population. 
+	The asterisk denotes the top-performing distance metric by column (lowest prediction error). 
+	Distance metrics are ordered from lowest prediction error to highest, based on global mobility with organization population defined using all mobile and non-mobile authors. 
+	``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
+		population is defined in the same way for ``Mobile only'', except only using unique mobile researchers;
+		``Raw freq'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
+		Embedding distance, measured as the cosine distance between embedding vectors, results in better predictions of mobility than baselines in nearly every case, however direct-factorization approaches~\autocite{levy2014neural} perform better for domestic and international mobility when raw frequency is used to define populations.
+}
+\label{supp:table:rmse_exp_table}
+\begin{centerbox}
+\begin{threeparttable}
+\small
+ \setlength{\tabcolsep}{0pt}
+\begin{tabular}{l l l l l l l l l l}
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}c!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{} \hspace{6pt}\huxbpad{0pt}} &
+\multicolumn{3}{c!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{All} \hspace{6pt}\huxbpad{0pt}} &
+\multicolumn{3}{c!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{Mobile only} \hspace{6pt}\huxbpad{0pt}} &
+\multicolumn{3}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{Raw freq} \hspace{6pt}\huxbpad{0pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{ } \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}-}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.713 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.76 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.737 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.702 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.749 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.713 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.715 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.764 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.748 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.803 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.791 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.771 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.867 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.725 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.726 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.705 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.803 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.825 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.811 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.851 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.87 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.854 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.769 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.798 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.784 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.859 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.835 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.815 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.841 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.82 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.82 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.812 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.792 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Laplacian cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.878 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.891 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.867 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.894 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.933 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.904 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.835 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.837 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.815 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.881 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.875 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.86 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.898 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.882 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.866 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.858 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.841 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR JSD} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.888 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.847 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.835 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.871 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.828 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.814 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.865 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.847 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.834 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.918 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.925 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.908 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.884 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.916 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.894 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.812 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.814 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.796 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Geographic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.929 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.951 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.928 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.973 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.002 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.983 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.856 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.875 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.853 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.987 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.995 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.98 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.979 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.014 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.996 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.853 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.867 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.849 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+\end{tabular}
+\end{threeparttable}\par\end{centerbox}
+
+\end{table}
+
+\end{landscape}
+
+%
+% RMSE TABLE --- Power Law
+% 
+\clearpage
+\begin{landscape}
+
+  \providecommand{\huxb}[2]{\arrayrulecolor[RGB]{#1}\global\arrayrulewidth=#2pt}
+  \providecommand{\huxvb}[2]{\color[RGB]{#1}\vrule width #2pt}
+  \providecommand{\huxtpad}[1]{\rule{0pt}{#1}}
+  \providecommand{\huxbpad}[1]{\rule[-#1]{0pt}{#1}}
+
+\begin{table}[ht]
+\caption{
+	\textbf{Prediction error between actual and predicted mobility with power-law gravity model, by metrics and experimental parameters}.
+	Each cell corresponds to the prediction error (measured with root mean squared error) between the real-world flux between scientific organizations and predictions made with the power-law form of the gravity model of mobility.
+	The prediction error is shown for the embedding distance compared against baselines, subsets of mobility data, and definitions of organization population. 
+	The asterisk denotes the top-performing distance metric by column (lowest prediction error). 
+	Distance metrics are ordered from lowest prediction error to highest, based on global mobility with organization population defined using all mobile and non-mobile authors. 
+	``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
+		population is defined in the same way for ``Mobile only'', except only using unique mobile researchers;
+		``Raw freq'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
+		Embedding distance, measured as the cosine distance between embedding vectors, results in better predictions for global mobility with ``All'; and ``Mobile only'' definitions of population, though the direct-factorization approach~\autocite{levy2014neural} perform better for in other cases.
+}
+\label{supp:table:rmse_power_table}
+\begin{centerbox}
+\begin{threeparttable}
+\small
+ \setlength{\tabcolsep}{0pt}
+\begin{tabular}{l l l l l l l l l l}
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}c!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{} \hspace{6pt}\huxbpad{0pt}} &
+\multicolumn{3}{c!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{All} \hspace{6pt}\huxbpad{0pt}} &
+\multicolumn{3}{c!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{Mobile only} \hspace{6pt}\huxbpad{0pt}} &
+\multicolumn{3}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{Raw freq} \hspace{6pt}\huxbpad{0pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{ } \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}-}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.743 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.784 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.76 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.73 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.784 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.749 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.714 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.762 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.745 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.78 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.776 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.755 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.847 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.822 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.703 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.711 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.691 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.822 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.831 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.864 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.879 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.863 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.783 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.809 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.795 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.839 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.785 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.761 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.89 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.834 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.81 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.792 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.752 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.728 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Laplacian cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.87 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.837 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.801 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.937 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.919 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.886 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.804 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.772 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.735 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Geographic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.905 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.879 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.888 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.933 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.906 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.852 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.851 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR JSD} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.889 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.85 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.838 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.871 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.834 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.819 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.865 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.847 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.834 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.92 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.927 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.91 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.885 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.918 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.896 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.812 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.815 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.797 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.927 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.926 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.911 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.93 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.924 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.909 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.861 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.872 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.854 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.99 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.998 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.983 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.977 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.015 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.997 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.845 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.86 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.841 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+\end{tabular}
+\end{threeparttable}\par\end{centerbox}
+
+\end{table}
+
+\end{landscape}
+
+%
+%
+%
+% FIGURES
+%
+%
+%
+%
+%
 \newpage
@@
 %
-% Figure - Distance metric performance
-%
-\begin{figure}[p!]
-	\centering
-	\includegraphics[width=0.9\textwidth]{\figdir/Descriptive/distance_metric_performance.pdf}
-	\caption{
-		\textbf{Cosine distance between embedding vectors explains more flux in scientific mobility than geographic distance, baselines.}
-		The correlation, or amount of flux explained by the embedding distance across distance metrics and other experimental parameters. 
-		All correlations are significant at $p < 0.0001$). 
-		Distance metrics are ordered, from top to bottom, by the highest correlation ($r^{2}$). 
-		The asterisk denotes the top-performing distance metric for every case. 
-		All distance metrics explain more of the flux than does geographic distance.
-		The cosine distance between embedding vectors explains more flux than all other distance metrics. 
-		The x-axis differentiates between three strategies for defining the organization population used to calculate the flux. 
-		``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
-		population is defined in the same way for ``mobile-only'', except only using unique mobile researchers;
-		``Raw frequency'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding. 
-		Generally, ``All'' explains more of the flux, however there is little difference between definitions of mobility.
-		All distance metrics tend to explain more of the flux when describing all or domestic (same-country) mobility.	
+% Figure---Metric performance
+%
+\begin{figure}[ht!]
+	\centering
+	\includegraphics[width=0.95\textwidth]{\figdir/Descriptive/distance_metric_performance.pdf}
+	\caption{ 
+	\textbf{Neural embeddings outperform baselines for scientific mobility.}
+		Cosine distance between embedding vectors generated with \textit{word2vec} explains more of the flux, and better predicts flux when used in the gravity model of mobility than geographic distance and other baselines.
+		Shown is the correlation between the flux and embedding distances, measured with $r^{2}$ (left), and the prediction error when using the distance as input to the gravity model of mobility. 
+		For prediction error, we show results based on both the exponential and power-law forms of the gravity model. 
+		All embedding-based methods use dimensions of 300. 
+		Here, embedding distance is obtained from neural embeddings learned with window size of 1 and $\gamma = 1$.  
+		In all cases, organization population is defined as the mean annualized number of unique mobile and non-mobile authors, and flux is calculated for all global mobility. 
+		Baselines include the top-performing distance metrics calculated between vectors obtained by personalized-page rank (PPR), singular value decomposition (SVD), laplacian eigenmap, and direct-factorization~\autocite{levy2014neural} approaches, as well as the geographic distance between organizations.
+		Embedding distance better explains and predicts flux than any other baseline, though there is some variation by experimental parameters (Table~\ref{supp:table:r2_table}, Table~\ref{supp:table:rmse_exp_table}, and Table~\ref{supp:table:rmse_power_table}).
 	}
 	\label{fig:supp:distancemetrics}
-\end{figure}
-
-%
-% Figure - Distance metric prediction RMSE performance 
-%
-\begin{figure}[p!]
-	\centering
-	\includegraphics[width=0.85\textwidth]{\figdir/Descriptive/distance_prediction_performance_rmse.pdf}
-	\caption{
-		\textbf{Using cosine distance between embedding vectors as input to the gravity model results in better predictions of scientific mobility compared to geographic distance, baselines.}
-		Shown is the Root Mean Squared Error (RMSE), or the accuracy of predictions made with the gravity model of mobility using the embedding distance and other experimental parameters.
-		The RMSE is shown using both the exponential and power-law forms of the gravity model. 
-		For each distance metric and set of parameters, the RMSE is shown for 
-		Distance metrics are ordered, from top to bottom, by the lowest RMSE, where a lower error indicates better predictions. 
-		The asterisk denotes the best-performing distance metric for every case. 
-		All distance metrics result in better predictions than does geographic distance.
-		In nearly every case, the embedding distance results in the best predictions, no matter the model. 
-		When considering international mobility alone, SVD distance performs best when using the power-law definition of the gravity model. 
-		The x-axis differentiates between three strategies for defining the organization population used to calculate the flux. 
-		``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
-		population is defined in the same way for ``mobile-only'', except only using unique mobile researchers;
-		``Raw frequency'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding. 
-		Generally, ``All'' results in better prediction.
-		}
-	\label{fig:supp:distancermse}
 \end{figure}

### 2021-02-11 paper/current/main.tex
write a paragraph on gensim vs matrix decomposition

@@
 
+There is an alternative implementation of \textit{word2vec} based on a matrix factorization~\cite{levy2014neural,Qiu2018}, which optimizes the same objective function as for \texttt{gensim} but in a different way.
+The matrix factorization approach generates embedding vectors such that the dot similarity for locations $i$ and $j$ is as close as $q_{ij}= \log(T_{ij} / s_i s_j) + \text{const}$.
+An issue is that the generated embedding vectors can be largely affected by small flows $T_{ij}$ in the data.
+For example, if there is no flow between locations $i$ and $j$ (\ie, $T_{ij} = 0$), then $Q_{ij} = -\infty$, pushing $i$ and $j$ to the infinite horizon of the embedding space.
+To remedy this problem, one can add a small amount of flow between such locations or exclude them from the embedding~\cite{levy2014neural,Qiu2018}.
+However, this may change the data to which we fit the model, and small flows may still have profound impact on the embedding space.
+Therefore, we adopt the \textt{gensim} implementation of the \textit{word2vec}.
+Our simulations show that, in the prediction task of mobility flow, \texttt{gensim}'s word2vec performs better than the matrix factorization approach in xxx out of the xxx datasets (Fig.~??).
+
+\texttt{gensim} adopts a stochastic gradient descent algorithm that is robust to some outliers.
+
+While both \texttt{gensim} and matrix factorization approaches maximize the same objective function, they do so based on different optimization strategies.
+\texttt{gensim} adopts a stochastic gradient descent algorithms.
+The matrix factoriztion approach employs
+
 \subsection*{An implicit bias in the negative sampling}

### 2021-02-11 paper/current/main.tex
fix typo

@@
 An issue is that the generated embedding vectors can be largely affected by small flows $T_{ij}$ in the data.
-For example, if there is no flow between locations $i$ and $j$ (\ie, $T_{ij} = 0$), then $Q_{ij} = -\infty$, pushing $i$ and $j$ to the infinite horizon of the embedding space.
+For example, if there is no flow between locations $i$ and $j$ (\ie, $T_{ij} = 0$), then $q_{ij} = -\infty$, pushing $i$ and $j$ to the infinite horizon of the embedding space.
 To remedy this problem, one can add a small amount of flow between such locations or exclude them from the embedding~\cite{levy2014neural,Qiu2018}.

### 2021-02-11 paper/current/main.tex
clean up

@@
 
-\texttt{gensim} adopts a stochastic gradient descent algorithm that is robust to some outliers.
-
-While both \texttt{gensim} and matrix factorization approaches maximize the same objective function, they do so based on different optimization strategies.
-\texttt{gensim} adopts a stochastic gradient descent algorithms.
-The matrix factoriztion approach employs
-
 \subsection*{An implicit bias in the negative sampling}

### 2021-02-15 paper/rebuttal/rebuttal.tex
add ref

@@
 \label{sec:theory}
-Here, we attempt to answer a question raised from our analysis: Why does the skip-gram model with negative sampling (SGNS), otherwise known as \textit{word2vec}, work so well to model human mobility?
+Here, we answer a question: Why does the skip-gram model with negative sampling (SGNS), otherwise known as \textit{word2vec}, work so well to model human mobility?
 We demonstrate a fundamental connection between the SGNS model and the Gravity Model of Mobility, namely, that SGNS implicitly learns gravity-like relationships between locations.
@@
 Second, while dot similarity is a formal distance measure in terms of its connection to the gravity model, our simulations show that dot similarity did not predict mobility flow better than cosine similarity (Fig.~\ref{fig:supp:distancemetrics}).
-It has been widely observed that cosine similarity is generally better than dot similarity in many applications of word embedding~\cite{}
-\todo{[Jisung, could you add citations?]}. Therefore, the superiority of cosine similarity is not a problem specific to, but instead a general feature of word embedding.
+It has been widely observed that cosine similarity is generally better than dot similarity in many applications of word embedding~\autocite{levy2015improving}.
+Therefore, the superiority of cosine similarity is not a problem specific to, but instead a general feature of word embedding.
 Nevertheless, dot similarity still outperformed geographic distance and some baselines (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).

### 2021-02-17 paper/current/main.tex
update main paper

@@
 This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}, networks~\autocite{grover2016node2vec, linzhuo2020hyperbolic} and trajectories\autocite{liu2016exploring, feng2017poi2vec, yao2018representing, cao2019habit2vec, crivellari2019motion, solomon2018predict}.
-It works under the notion that a good representation should facilitate prediction, and so learns a mapping of target locations (words) that best predict locations that co-appear in the same trajectory (sentence).
+It works under the notion that a good representation should facilitate prediction,  so learns a mapping of words that predicts the target word with surrounding words (context).
 The model is also computationally efficient, robust to noise, and can encode relations between entities as geometric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.
@@
 A central assumption in our mathematical analysis is that the embedding vectors are optimum in terms of the {\it word2vec}'s objective function.
-However, this premise is not practical because the optimization algorithm often finds sub-optimal embeddings due to its stochasticity and being trapped in a local optimum.
+However, this premise is not practical because the optimization algorithm (e.g.
+stochastic gradient descent algorithm) often finds sub-optimal embeddings due to its stochasticity and being trapped in a local optimum.
 This has two consequences.
@@
 Second, dot similarity should in principle predict the mobility flow better than cosine similarity because dot similarity includes cosine similarity as its special case.
-However, our simulations show that it is the cosine similarity that better predicted the mobility flow~[reference to a figure].
-This phenomenon---cosine similarity outperforms dot similarity---has been observed in many applications of word embedding~\cite{add citations}.
-Nevertheless, among the 7(?) measures tested in our simulations, dot similarity is the second-best predictor of mobility flow following cosine similarity.
-Furthermore, unlike cosine similarity, dot similarity has a mathematical connection to the gravity model.
-
-\todo{add stuff about cosine distance performing better, SGD performing better}
+However, our simulations show that it is the cosine similarity that better predicted the mobility flow~(Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+ It has been widely observed that cosine similarity (dot product with $l2$ normalization) is generally better than dot similarity and dot similarity with various normalization methods in capturing a similarity between two words ~\autocite{levy2015improving}.
+Nevertheless, among the ten measures tested in our simulations, dot similarity is the second-best predictor of mobility flow following cosine similarity.
 
@@
 However, this may change the data to which we fit the model, and small flows may still have profound impact on the embedding space.
-Therefore, we adopt the \textt{gensim} implementation of the \textit{word2vec}.
+Therefore, we adopt the \texttt{gensim} implementation of the \textit{word2vec}.
 Our simulations show that, in the prediction task of mobility flow, \texttt{gensim}'s word2vec performs better than the matrix factorization approach in xxx out of the xxx datasets (Fig.~??).

### 2021-02-17 paper/current/supp.tex
add texts on the supp

@@
 }
+\newcommand{\todo}[1]{{\leavevmode\color{orange}[TODO: #1]}}
 
@@
 
+\paragraph*{S5 Text}
+\label{si:text:Raw SVD}
+{\bf Singular vector decomposition distance.}
+
+We examine the gravity model on the embedding vector with applying truncated singular vector decomposition (SVD) on the co-occurrence matrix as the first benchmark on the matrix factorization method.
+Intuitively,  truncated SVD performs linear low rank approximation of the matrix with given dimension $d$.
+First, we construct the co-occurrence matrix of $N$ organization, $A_{ij}$ given by the co-occurence of $i$ and $j$ in the same affiliation trajectory.
+Then, we apply truncated singular vector decomposition with $d=300$ on the flow matrix $A$ directly.
+
+We report the result with cosine distance ($R^2=0.247$, Table~\ref{supp:table:r2_table}), which is the best performance among cosine distance, euclidean distances and dot product.
+The performance is slightly over the the performance of the model with geographical distance.
+\todo{@dakoda can you write down the performance with other distance measures simply here?}
+
+\paragraph*{S6 Text}
+\label{si:text:Laplacian}
+{\bf Laplacian eigenmap distance.}
+
+We also consider Laplacian eigenmaps \cite{belkin2003laplacian}, which is the most fundamental graph embedding method, as the second benchmark on the matrix factorization.
+First, we construct the co-occurrence matrix of $N$ organization, $A_{ij}$ given by the co-occurence of $i$ and $j$ in the same affiliation trajectory and degree matrix $D$ which is the diagonal matrix for which $D_{ii}=\sum_j {A_{ij}}$.
+Then we construct graph lapalcian matrix $L = D-A$  and apply  truncated singular vector decomposition in the matrix $L$ with $d=300$.
+
+We report the result with euclidean distance ($R^2=0.341$, Table~\ref{supp:table:r2_table}), which is the best performance among cosine distance, euclidean distances and dot product.
+The performance is much bettern that the performance of the model with geographical distance, still below the performance of our suggested way.
+\todo{@dakoda can you write down the performance with other distance measures simply here?}
+
+\paragraph*{S7 Text}
+\label{si:text:Laplacian}
+{\bf Levy's  symmetric SVD \textit{word2vec} distance}
+
+Furthermore, We examine the gravity model with embedding vector with the symmetric SVD  \textit{word2vec} method\cite{levy2014neural} as the third benchmark on the matrix factorization.
+Based on idea of \textit{word2vec} is just implciity matrix factorization, Levy proposed symmetric SVD \textit{word2vec} embedding.
+First, we construct the matrix of $N$ organization,
+
+\begin{equation}
+ M_{ij} = \log(\frac{N(i,j) |D|}{N(i) N(j)}) - \log(k)
+\end{equation}
+
+We report the result with euclidean distance ($R^2=0.341$, Table~\ref{supp:table:r2_table}), which is the best performance among cosine distance, euclidean distances and dot product.
+The performance is much bettern that the performance of the model with geographical distance, still below the performance of our suggested way.
+\todo{@dakoda can you write down the performance with other distance measures simply here?}
+
 %
 % S5 TEXT
-\paragraph*{S5 Text}
+\paragraph*{S8 Text}
 \label{si:text:organizations}
@@
 % S6 TEXT
-\paragraph*{S6 Text}
+\paragraph*{S9 Text}
 \label{si:text:disambiguation}
@@
 % S7 TEXT
-\paragraph*{S7 Text}
+\paragraph*{S10 Text}
 \label{si:text:network_ranking}
@@
 % S8 TEXT
-\paragraph*{S8 Text}
+\paragraph*{S11 Text}
 \label{si:text:boomerang_speculation}

### 2021-02-17 paper/rebuttal/rebuttal.tex
rewrite the limitation of math

@@
 
-\subsection{Gap between the mathematical analysis and numerical simulations}
-
-In the mathematical analysis, we assumed that the embedding vectors are optimal in terms of the objective of {\it word2vec}, which, however, is not true in our numerical simulations.
-This violation of assumption leads to two substantial consequences for embedding vectors.
-First, although there exist optimal in-vector and out-vector that are identical, the in-vector and out-vector can be different in practice because they are sub-optimal.
-Second, while dot similarity is a formal distance measure in terms of its connection to the gravity model, our simulations show that dot similarity did not predict mobility flow better than cosine similarity (Fig.~\ref{fig:supp:distancemetrics}).
-It has been widely observed that cosine similarity is generally better than dot similarity in many applications of word embedding~\autocite{levy2015improving}.
-Therefore, the superiority of cosine similarity is not a problem specific to, but instead a general feature of word embedding.
-Nevertheless, dot similarity still outperformed geographic distance and some baselines (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
-What makes cosine similarity superior to dot similarity warrants the future work.
+A central assumption in our mathematical analysis is that the embedding vectors are optimum in terms of the {\it word2vec}'s objective function.
+However, this premise is not practical because the optimization algorithm (e.g.
+stochastic gradient descent algorithm) often finds sub-optimal embeddings due to its stochasticity and being trapped in a local optimum.
+This has two consequences.
+First, the in- and out-vectors can be different.
+Second, dot similarity should in principle predict the mobility flow better than cosine similarity because dot similarity includes cosine similarity as its special case.
+However, our simulations show that it is the cosine similarity that better predicted the mobility flow~(Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+It has been widely observed that cosine similarity (dot product with $l2$ normalization) is generally better than dot similarity and dot similarity with various normalization methods in capturing a similarity between two words ~\autocite{levy2015improving}.
+Nevertheless, among the ten measures tested in our simulations, dot similarity is the second-best predictor of mobility flow following cosine similarity (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+%What makes cosine similarity superior to dot similarity warrants the future work.
 

### 2021-02-17 paper/rebuttal/rebuttal.tex
e.g. -> \eg

@@
 A central assumption in our mathematical analysis is that the embedding vectors are optimum in terms of the {\it word2vec}'s objective function.
-However, this premise is not practical because the optimization algorithm (e.g.
-stochastic gradient descent algorithm) often finds sub-optimal embeddings due to its stochasticity and being trapped in a local optimum.
+However, this premise is not practical because the optimization algorithm (\eg stochastic gradient descent algorithm) often finds sub-optimal embeddings due to its stochasticity and being trapped in a local optimum.
 This has two consequences.

### 2021-02-18 paper/rebuttal/rebuttal.tex
update rebuttal

@@
 	\item Since the formulation of the gravity used in the above derivations assumes $\gamma = 1$, we use this value of $gamma$ for all reported results. No result substantively changes with this change.
-	\item \todo{We added a sentence to the paper speculating on why cosine similarity works best}
-	\item \todo{We also added a sentence noting the in-vector and out-vector issue, and speculating on reasons/consequences}
+	\item We added a sentence to the paper speculating on why cosine similarity works best in the main text.
+	\item We also added a sentence noting the in-vector and out-vector issue, and speculating on reasons/consequences.
 \end{itemize}
@@
 	\item Added Fig~\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table} to the manuscript.
-	\item \todo{add sentence speculating on SGD performance differences into text/supporting meterials}
+	\item We have added sentence speculating on SGD performance differences into supporting materials
 \end{itemize}
@@
 
-	We also argue that geographical distance ﬁts well with the power-law decay function because power-based gravity model can be more suitable for analyzing large, complex, and scale-free spatial systems and the exponential-based gravity model indicates simplicty rather than spatial complexity~\autocite{chen2015distance}.
+	We find the article that geographical distance ﬁts well with the power-law decay function because power-based gravity model can be more suitable for analyzing large, complex, and scale-free spatial systems theoretically and the exp`onential-based gravity model indicates simplicty rather than spatial complexity~\autocite{chen2015distance}.
 Meanwhile, embedding distance ﬁts well with the exponential decay function, which we demonstrate to correspond to an underlying mathematical relationship between \textit{word2vec} and the gravity model, a connection we recently discovered and included as a major finding in this revision (see our response to Referee 1).
@@
 \response{
-	\todo{Thoughts on this response? Still not 100\% sure I follow the reviewer}
 	Thank you for this comment.

### 2021-02-18 paper/current/main.tex
re-edit the last paragraph of math

@@
 A central assumption in our mathematical analysis is that the embedding vectors are optimum in terms of the {\it word2vec}'s objective function.
-However, this premise is not practical because the optimization algorithm (\eg stochastic gradient descent algorithm) often finds sub-optimal embeddings due to its stochasticity and being trapped in a local optimum.
+However, this premise is not practical because the optimization algorithm (\eg stochastic gradient descent algorithm) often finds sub-optimal embeddings.
 This has two consequences.
 First, the in- and out-vectors can be different.
-Second, dot similarity should in principle predict the mobility flow better than cosine similarity because dot similarity includes cosine similarity as its special case.
-However, our simulations show that it is the cosine similarity that better predicted the mobility flow~(Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
-It has been widely observed that cosine similarity (dot product with $l2$ normalization) is generally better than dot similarity and dot similarity with various normalization methods in capturing a similarity between two words ~\autocite{levy2015improving}.
-Nevertheless, among the ten measures tested in our simulations, dot similarity is the second-best predictor of mobility flow following cosine similarity.
+Second, dot similarity calculated by {\it word2vec} is the distance metric tied to the gravity model, and hence, should capture the mobility flow well.
+However, in our numerical simulations, cosine similarity calculated by {\it word2vec} predicts better than the dot similarity~(Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+Cosine similarity is a special case of dot similarity, and thus, should be no better than dot similarity if the embedding vectors are optimal.
+In practice, cosine similarity often outperform dot similarity in many applications of word embedding such as word analogy test~\autocite{levy2015improving}.
+Nevertheless, among the ten measures tested in our simulations, dot similarity is the second-best predictor of mobility flow, can be even better than cosine similarity.
 

### 2021-02-18 paper/current/main.tex
fix minor typos

@@
 \begin{align}
-	P\left(j \given i \right):= \frac{\exp(\bm{u}_j \cdot \bm{v}_{i})}{\widetilde{Z_i}}, \label{eq:prob_w2v_ng}
+	P\left(j \given i \right):= \frac{\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:prob_w2v_ng}
 \end{align}
-where the denominator $\widetilde{Z_i}=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
-Although {\it word2vec} generates two embedding vectors $\bm{v_i}$ and $\bm{u}_i$---which are referred to as the in-vector and out-vector, respectively, we follow many studies by adopting the in-vector $\bm{v}_i$ as an embedding of location $i$.
+where the denominator $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
+Although {\it word2vec} generates two embedding vectors $\bm{v_i}$ and $\bm{u}_i$---which are referred to as the in-vector and out-vector, respectively, we follow convention to use the in-vector $\bm{v}_i$ as an embedding of location $i$.
 
@@
 
-Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimial in-vectors and out-vectors such that $\bm{u}_i = \bm{v}_i$ \autocite{levy2014neural}.
+Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimial in-vectors and out-vectors such that $\bm{u}_i = \bm{v}_i$~\autocite{levy2014neural}.
 Setting $\gamma = 1$ and substituting $\bm{u}_i = \bm{v}_j$ into Eq.~\eqref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
 \begin{align}
-	\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)P(j)\exp(\bm{v}_j \cdot \bm{v}_{i})}{Z_i}. \label{eq:flow_w2v_ng1}
+	\hat{T}_{ij}= P(i) P(j\given i) = \frac{P(i)P(j)\exp(\bm{v}_j \cdot \bm{v}_{i})}{Z_i}. \label{eq:flow_w2v_ng1}
 \end{align}
@@
 If we swap $i$ and $j$ in Eq.~\eqref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
-Therefore, to ensure $T_{ij} = T_{ji}$, the denominator $Z_i$ must be a constant.
+Therefore, to ensure $\hat{T}_{ij} = \hat{T}_{ji}$, the denominator $Z_i$ must be a constant.
 
@@
 In other words, \emph{word2vec with the negative sampling is a gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
-While the gravity model generates the flow from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given trajectories.
-Therefore, the embedding distance is inherently tied to the flow, and hence, has greater predictive power than the geographic distance.
+While the gravity model generates mobility flow from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given mobility flow.
+Therefore, the embedding distance is inherently tied to mobility flow, and hence, has greater predictive power than the geographic distance.
 
@@
 First, the in- and out-vectors can be different.
-Second, dot similarity calculated by {\it word2vec} is the distance metric tied to the gravity model, and hence, should capture the mobility flow well.
-However, in our numerical simulations, cosine similarity calculated by {\it word2vec} predicts better than the dot similarity~(Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+Second, although dot similarity calculated by {\it word2vec} is the distance metric tied to the gravity model, and hence, should capture the mobility flow well,
+it is cosine similarity that best predicted mobility flow in our numerical simulations~(Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
 Cosine similarity is a special case of dot similarity, and thus, should be no better than dot similarity if the embedding vectors are optimal.
 In practice, cosine similarity often outperform dot similarity in many applications of word embedding such as word analogy test~\autocite{levy2015improving}.
-Nevertheless, among the ten measures tested in our simulations, dot similarity is the second-best predictor of mobility flow, can be even better than cosine similarity.
+Nevertheless, among the ten embedding distance tested in our simulations, dot similarity is the second-best predictor of mobility flow, can be even better than cosine similarity by carefully turning the optimization algorithm.
 

### 2021-02-18 paper/rebuttal/rebuttal.tex
minor edit:SGD vs SVD

@@
 \begin{align}
-	P\left(j \given i \right):= \frac{P^\gamma (j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{\widetilde{Z_i}},
+	P\left(j \given i \right):= \frac{P^\gamma (j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
 	\label{eq:real_cond}
 \end{align}
-where $\widetilde {Z_i}=\sum_{j' \in \mathcal{A}} P^\gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
+where $Z_i=\sum_{j' \in \mathcal{A}} P^\gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
 
@@
 \end{align}
-where  $\widetilde{Z_i}=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
+where we have redefined $Z_i=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
 
@@
 
-The flow $\hat{T_{ij}}$ is symmetric (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because {\it word2vec} neglects whether the context $j$ appears before or after the center $i$ in the trajectory -- the mechanism of skip-gram.
+The flow $\hat{T_{ij}}$ is symmetric (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because {\it word2vec} neglects whether the context $j$ appears before or after the center $i$ in the trajectory---the mechanism of skip-gram.
 If we swap $i$ and $j$ in Eq.~\eqref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
-Therefore, to ensure $T_{ij} = T_{ji}$, the denominator $Z_i$ should be a constant.
+Therefore, to ensure $\hat{T}_{ij} = \hat{T}_{ji}$, the denominator $Z_i$ should be a constant.
 
@@
 In other words, \emph{word2vec with the negative sampling is a gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
-While the gravity model generates the flow from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given trajectories.
-Therefore, the embedding distance is inherently tied to the flow, and hence, has greater predictive power than the geographic distance.
+While the gravity model generates mobility flow from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given mobility flow.
+Therefore, the embedding distance is inherently tied to mobility flow, and hence, has greater predictive power than the geographic distance.
 
 A central assumption in our mathematical analysis is that the embedding vectors are optimum in terms of the {\it word2vec}'s objective function.
-However, this premise is not practical because the optimization algorithm (\eg stochastic gradient descent algorithm) often finds sub-optimal embeddings due to its stochasticity and being trapped in a local optimum.
+However, this premise is not practical because the optimization algorithm (\eg stochastic gradient descent algorithm) often finds sub-optimal embeddings.
 This has two consequences.
 First, the in- and out-vectors can be different.
-Second, dot similarity should in principle predict the mobility flow better than cosine similarity because dot similarity includes cosine similarity as its special case.
-However, our simulations show that it is the cosine similarity that better predicted the mobility flow~(Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
-It has been widely observed that cosine similarity (dot product with $l2$ normalization) is generally better than dot similarity and dot similarity with various normalization methods in capturing a similarity between two words ~\autocite{levy2015improving}.
-Nevertheless, among the ten measures tested in our simulations, dot similarity is the second-best predictor of mobility flow following cosine similarity (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
-%What makes cosine similarity superior to dot similarity warrants the future work.
+Second, although dot similarity calculated by {\it word2vec} is the distance metric tied to the gravity model, and hence, should capture the mobility flow well,
+it is cosine similarity that best predicted mobility flow in our numerical simulations~(Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+Cosine similarity is a special case of dot similarity, and thus, should be no better than dot similarity if the embedding vectors are optimal.
+In practice, cosine similarity often outperform dot similarity in many applications of word embedding such as word analogy test~\autocite{levy2015improving}.
+Nevertheless, among the ten embedding distance tested in our simulations, dot similarity is the second-best predictor of mobility flow, can be even better than cosine similarity by carefully turning the optimization algorithm.
 
@@
 The matrix factorization approach embeds affiliations $i$ and $j$ such that their dot similarity is as close as to $\log (T_{ij} / P(i) P(j))$.
-If the flow $T_{ij}$ is considerably small or zero, the dot similarity goes $-\infty$, pushing $i$ and $j$ too far from the other affiliations in the embedding space~\autocite{levy2014neural, Qui2018}.
+If the flow $T_{ij}$ is considerably small or zero, the dot similarity goes $-\infty$, pushing $i$ and $j$ very far from the other affiliations in the embedding space~\autocite{levy2014neural, Qui2018}.
 This is particularly problematic when the window size is small because most affiliation pairs would have no flow, which is indeed the case in our experiments.
@@
 
-Also, it is well known that SVD by itself is very vulnerable to outliers \autocite{ xu2012robust, huber1981robust, xu1995robust, chandrasekaran2011rank, candes2011robust, }.
-Compared to SVD, a stochastic gradient descent algorithm (SGD) which is employed in SGNS \textit{word2vec} benefits from the noise in the model itself and can enhance generalization and effectiveness as well \autocite{ma2018power, smith2020generalization, zhang2019algorithmic,}.
+Also, it is well known that SVD by itself is very vulnerable to outliers \autocite{xu2012robust, huber1981robust, xu1995robust, chandrasekaran2011rank, candes2011robust}.
+The stochastic gradient descent algorithm (SGD), which is employed in SGNS \textit{word2vec}, is more robust than SVD and can enhance generalization and effectiveness of {\it word2vec} model \autocite{ma2018power, smith2020generalization, zhang2019algorithmic}.
 

### 2021-02-18 paper/rebuttal/rebuttal.tex
re-edit: limitation of math

@@
 First, the in- and out-vectors can be different.
-Second, although dot similarity calculated by {\it word2vec} is the distance metric tied to the gravity model, and hence, should capture the mobility flow well,
-it is cosine similarity that best predicted mobility flow in our numerical simulations~(Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
-Cosine similarity is a special case of dot similarity, and thus, should be no better than dot similarity if the embedding vectors are optimal.
-In practice, cosine similarity often outperform dot similarity in many applications of word embedding such as word analogy test~\autocite{levy2015improving}.
-Nevertheless, among the ten embedding distance tested in our simulations, dot similarity is the second-best predictor of mobility flow, can be even better than cosine similarity by carefully turning the optimization algorithm.
+Second, dot similarity calculated by {\it word2vec} is the distance metric tied to the gravity model, and hence, should capture the mobility flow well.
+In fact, dot similarity calculated by {\it word2vec} is the second-best predictor of mobility flow among ten embedding distances in our numerical simulations~(Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+However, cosine similarity predicted mobility flow better than dot similarity.
+This result echos many applications of word embedding such as word analogy test~\autocite{levy2015improving}, in which cosine similarity outperforms dot similarity.
+In predicting mobility flow, if the embedding vectors are optimal, cosine similarity should be no better than dot similarity because cosine similarity is a special case of dot similarity.
+Therefore, the inferiority of dot similarity is attributed to the optimization process, and therefore, dot similarity can outperform cosine similarity by a careful tuning of the optimization algorithm.
+%Nevertheless, among the ten embedding distance measures tested in our simulations, dot similarity is the second-best predictor of mobility flow, can be even better than cosine similarity by carefully turning the optimization algorithm.
 

### 2021-02-18 paper/current/main.tex
re-edit: limitation of math

@@
 First, the in- and out-vectors can be different.
-Second, although dot similarity calculated by {\it word2vec} is the distance metric tied to the gravity model, and hence, should capture the mobility flow well,
-it is cosine similarity that best predicted mobility flow in our numerical simulations~(Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
-Cosine similarity is a special case of dot similarity, and thus, should be no better than dot similarity if the embedding vectors are optimal.
-In practice, cosine similarity often outperform dot similarity in many applications of word embedding such as word analogy test~\autocite{levy2015improving}.
-Nevertheless, among the ten embedding distance tested in our simulations, dot similarity is the second-best predictor of mobility flow, can be even better than cosine similarity by carefully turning the optimization algorithm.
+Second, dot similarity calculated by {\it word2vec} is the distance metric tied to the gravity model, and hence, should capture the mobility flow well.
+In fact, dot similarity calculated by {\it word2vec} is the second-best predictor of mobility flow among ten embedding distances in our numerical simulations~(Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+However, cosine similarity predicted mobility flow better than dot similarity.
+This result echos many applications of word embedding such as word analogy test~\autocite{levy2015improving}, in which cosine similarity outperforms dot similarity.
+In predicting mobility flow, if the embedding vectors are optimal, cosine similarity should be no better than dot similarity because cosine similarity is a special case of dot similarity.
+Therefore, the inferiority of dot similarity is attributed to the optimization process, and therefore, dot similarity can outperform cosine similarity by a careful tuning of the optimization algorithm.
 

### 2021-02-18 paper/rebuttal/rebuttal.tex
last sentence editted

@@
 Second, dot similarity calculated by {\it word2vec} is the distance metric tied to the gravity model, and hence, should capture the mobility flow well.
-In fact, dot similarity calculated by {\it word2vec} is the second-best predictor of mobility flow among ten embedding distances in our numerical simulations~(Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+Our numerical simulations show that dot similarity calculated by {\it word2vec} is the second-best predictor of mobility flow among the ten embedding distances~(Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
 However, cosine similarity predicted mobility flow better than dot similarity.
@@
 In predicting mobility flow, if the embedding vectors are optimal, cosine similarity should be no better than dot similarity because cosine similarity is a special case of dot similarity.
-Therefore, the inferiority of dot similarity is attributed to the optimization process, and therefore, dot similarity can outperform cosine similarity by a careful tuning of the optimization algorithm.
+Therefore, the inferiority of dot similarity is attributed to the optimization process, and therefore, a careful tuning of the optimization algorithm would close the gap between our mathematical and numerical results.
 %Nevertheless, among the ten embedding distance measures tested in our simulations, dot similarity is the second-best predictor of mobility flow, can be even better than cosine similarity by carefully turning the optimization algorithm.

### 2021-02-18 paper/current/main.tex
last sentence editted

@@
 In predicting mobility flow, if the embedding vectors are optimal, cosine similarity should be no better than dot similarity because cosine similarity is a special case of dot similarity.
-Therefore, the inferiority of dot similarity is attributed to the optimization process, and therefore, dot similarity can outperform cosine similarity by a careful tuning of the optimization algorithm.
+Therefore, the inferiority of dot similarity is attributed to the optimization process, and therefore, a careful tuning of the optimization algorithm would close the gap between our mathematical and numerical results.
 

### 2021-02-18 paper/rebuttal/rebuttal.tex
fix minot type: last sentence of math

@@
 In predicting mobility flow, if the embedding vectors are optimal, cosine similarity should be no better than dot similarity because cosine similarity is a special case of dot similarity.
-Therefore, the inferiority of dot similarity is attributed to the optimization process, and therefore, a careful tuning of the optimization algorithm would close the gap between our mathematical and numerical results.
-%Nevertheless, among the ten embedding distance measures tested in our simulations, dot similarity is the second-best predictor of mobility flow, can be even better than cosine similarity by carefully turning the optimization algorithm.
+Therefore, the inferiority of dot similarity is attributed to the optimization process, and a careful tuning of the optimization algorithm would close the gap between our mathematical and numerical results.
 

### 2021-02-18 paper/current/main.tex
fix minot type: last sentence of math

@@
 In predicting mobility flow, if the embedding vectors are optimal, cosine similarity should be no better than dot similarity because cosine similarity is a special case of dot similarity.
-Therefore, the inferiority of dot similarity is attributed to the optimization process, and therefore, a careful tuning of the optimization algorithm would close the gap between our mathematical and numerical results.
+Therefore, the inferiority of dot similarity is attributed to the optimization process, and a careful tuning of the optimization algorithm would close the gap between our mathematical and numerical results.
 

### 2021-02-18 paper/rebuttal/rebuttal.tex
rephrase: last sentence of the math

@@
 In predicting mobility flow, if the embedding vectors are optimal, cosine similarity should be no better than dot similarity because cosine similarity is a special case of dot similarity.
-Therefore, the inferiority of dot similarity is attributed to the optimization process, and a careful tuning of the optimization algorithm would close the gap between our mathematical and numerical results.
+Therefore, the inferiority of dot similarity is attributed to the optimization process.
+Although finding an optimal embedding is difficult in practice, a careful tuning of the optimization algorithm would close the gap between our mathematical and numerical results.
 

### 2021-02-18 paper/current/main.tex
change \cite to \autocite

@@
 The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores  calculated from the underlying mobility network (Fig.~\ref{fig:supp:distancemetrics}, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baseline, such as distances derived from a singular-value decomposition on flow matrix and from a Laplacian Eigenmap embedding  \autocite{belkin2003laplacian} of the underlying data (Fig.~\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), in many cases even putperforming a direct factorization approach~\cite{levy2014neural}), which \textit{word2vec} efficiently approximates.
+The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baseline, such as distances derived from a singular-value decomposition on flow matrix and from a Laplacian Eigenmap embedding  \autocite{belkin2003laplacian} of the underlying data (Fig.~\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), in many cases even putperforming a direct factorization approach~\autocite{levy2014neural}), which \textit{word2vec} efficiently approximates.
 In sum, our results demonstrate that, consistently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
@@
 
-There is an alternative implementation of \textit{word2vec} based on a matrix factorization~\cite{levy2014neural,Qiu2018}, which optimizes the same objective function as for \texttt{gensim} but in a different way.
+There is an alternative implementation of \textit{word2vec} based on a matrix factorization~\autocite{levy2014neural,Qiu2018}, which optimizes the same objective function as for \texttt{gensim} but in a different way.
 The matrix factorization approach generates embedding vectors such that the dot similarity for locations $i$ and $j$ is as close as $q_{ij}= \log(T_{ij} / s_i s_j) + \text{const}$.
@@
 For example, if there is no flow between locations $i$ and $j$ (\ie, $T_{ij} = 0$), then $q_{ij} = -\infty$, pushing $i$ and $j$ to the infinite horizon of the embedding space.
-To remedy this problem, one can add a small amount of flow between such locations or exclude them from the embedding~\cite{levy2014neural,Qiu2018}.
+To remedy this problem, one can add a small amount of flow between such locations or exclude them from the embedding~\autocite{levy2014neural,Qiu2018}.
 However, this may change the data to which we fit the model, and small flows may still have profound impact on the embedding space.
@@
 We also use network-based distances, calculating vectors using a Personalized Page Rank approach and measuring the distance between them using cosine distance and Jensen-Shannon Divergence (see \SI).
-Finally, we compare the embedding distnace against embeddings calculated through direct matrix factorization, following the approach that \textit{word2vec} implicitley approximates~\cite{levy2014neural}.
+Finally, we compare the embedding distnace against embeddings calculated through direct matrix factorization, following the approach that \textit{word2vec} implicitley approximates~\autocite{levy2014neural}.
 

### 2021-02-18 paper/current/main.tex
distance typo

@@
 We also use network-based distances, calculating vectors using a Personalized Page Rank approach and measuring the distance between them using cosine distance and Jensen-Shannon Divergence (see \SI).
-Finally, we compare the embedding distnace against embeddings calculated through direct matrix factorization, following the approach that \textit{word2vec} implicitley approximates~\autocite{levy2014neural}.
+Finally, we compare the embedding distance against embeddings calculated through direct matrix factorization, following the approach that \textit{word2vec} implicitley approximates~\autocite{levy2014neural}.
 

### 2021-02-18 paper/current/main.tex
minor tweaks

@@
 The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores calculated from the underlying mobility network (Fig.~\ref{fig:supp:distancemetrics}, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baseline, such as distances derived from a singular-value decomposition on flow matrix and from a Laplacian Eigenmap embedding  \autocite{belkin2003laplacian} of the underlying data (Fig.~\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), in many cases even putperforming a direct factorization approach~\autocite{levy2014neural}), which \textit{word2vec} efficiently approximates.
+The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurence data (Fig.~\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and , in most cases, even outperforms a direct factorization approach~\autocite{levy2014neural}), which \textit{word2vec} is meant to approximate.
 In sum, our results demonstrate that, consistently, the embedding distance better captures patterns of actual mobility than does the geographic distance.

### 2021-02-18 paper/current/main.tex
edit math section

@@
 Why does the embedding distance predict actual mobility flows better than the geographic distance?
-Here, we show that the objective function of {\it word2vec} is equivalent to the gravity model.
+Here, we show that the objective function of {\it word2vec} is equivalent to the gravity model, explaining its ability to learn gravity-like relationships between locations.
 
-The {\it word2vec} model takes a location trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), as an input.
-A location $a_t=i$ is considered to have a context location $a_{t'}=j$ that appears in its succeeding or proceeding $w$ locations in the trajectory, \ie  $j \in [a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}]$.
+The {\it word2vec} model takes a location trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), as input.
+A location $a_t=i$ is considered to have a context location $a_{t'}=j$ that appears in the previous or subsequent $w$ locations in the trajectory, \ie  $j \in [a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}]$.
 	{\it Word2vec} learns an embedding by estimating the probability that location $i$ has context $j$:
@@
 where the denominator $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
-Although {\it word2vec} generates two embedding vectors $\bm{v_i}$ and $\bm{u}_i$---which are referred to as the in-vector and out-vector, respectively, we follow convention to use the in-vector $\bm{v}_i$ as an embedding of location $i$.
+Although {\it word2vec} generates two embedding vectors $\bm{v_i}$ and $\bm{u}_i$---referred to as the in-vector and out-vector, respectively---we follow convention to use the in-vector $\bm{v}_i$ as an embedding of location $i$.
 
@@
 Because computing $Z_i$ is computationally demanding, multiple approximation methods have been proposed, the most popular being negative sampling~\autocite{mikolov2013word2vec}.
-Negative sampling finds the embedding vectors by solving a binary classification task, in which the model classifies whether a given center-context location pair $(i, j)$ comes from the data or artificially generated ``negative'' samples.
+Negative sampling finds the embedding vectors by solving a binary classification task, in which the model classifies whether a given target-context location pair $(i, j)$ comes from the data or from artificially generated ``negative'' samples.
 The negative pair $(i,j)$ is sampled in proportion to $P^\gamma(j)$ with parameter $\gamma \geq 0$.
@@
 \end{align}
-where we redefine the normalization constant as $Z_i=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$. (See Methods section for the full calculation).
+where we redefine the normalization constant as $Z_i=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$. (See Methods section for the full derivation).
 
@@
 \end{align}
-The flow $\hat{T}_{ij}$ is symmetric (\ie $\hat{T}_{ij}=\hat{T}_{ji}$) because {\it word2vec} neglects whether the context $j$ appears before or after the center $i$ in the trajectory.
+The flow $\hat{T}_{ij}$ is symmetric (\ie $\hat{T}_{ij}=\hat{T}_{ji}$) because {\it word2vec} neglects whether the context $j$ appears before or after the target $i$ in the trajectory.
 If we swap $i$ and $j$ in Eq.~\eqref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
@@
 While the gravity model generates mobility flow from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given mobility flow.
-Therefore, the embedding distance is inherently tied to mobility flow, and hence, has greater predictive power than the geographic distance.
+Therefore, the embedding distance is inherently tied to the mobility flow, and hence, has greater predictive power than the geographic distance and other baselines.
 
-A central assumption in our mathematical analysis is that the embedding vectors are optimum in terms of the {\it word2vec}'s objective function.
+A key assumption in our mathematical analysis is that the embedding vectors are optimum in terms of the {\it word2vec}'s objective function.
 However, this premise is not practical because the optimization algorithm (\eg stochastic gradient descent algorithm) often finds sub-optimal embeddings.
@@
 First, the in- and out-vectors can be different.
-Second, dot similarity calculated by {\it word2vec} is the distance metric tied to the gravity model, and hence, should capture the mobility flow well.
-Our numerical simulations show that dot similarity calculated by {\it word2vec} is the second-best predictor of mobility flow among the ten embedding distances~(Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
-However, cosine similarity predicted mobility flow better than dot similarity.
-This result echos many applications of word embedding such as word analogy test~\autocite{levy2015improving}, in which cosine similarity outperforms dot similarity.
-In predicting mobility flow, if the embedding vectors are optimal, cosine similarity should be no better than dot similarity because cosine similarity is a special case of dot similarity.
-Therefore, the inferiority of dot similarity is attributed to the optimization process.
-Although finding an optimal embedding is difficult in practice, a careful tuning of the optimization algorithm would close the gap between our mathematical and numerical results.
+Second, {\it word2vec} learns the dot distance between location vectors, and so this distance should best capture mobility flows. 
+However, our numerical simulations show that the dot similarity between vectors is outperformed by the cosine distance as a predictor of mobility flow between scientific organizations~(Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+This result echos other applications of word embedding, such as word analogy testing~\autocite{levy2015improving}, in which cosine distance also outperformed dot similarity.
+Given that cosine similarity is a special case of dot similarity, we speculate that the deviation in explanatory and predictive quality can be attributed to \textit{word2vec's} optimization process.
+Although finding an optimal embedding is difficult in practice, careful tuning of the optimization algorithm would close the gap between our mathematical and numerical results.
 

### 2021-02-18 paper/current/main.tex
methods edits

@@
 Negative sampling trains {\it word2vec} using a binary classification task as follows.
-A center-context word pair $(i,j)$ is sampled from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$ are sampled from a noise distribution $p_0(\ell)=P^\gamma(\ell)$.
+A target-context word pair $(i,j)$ is sampled from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$ are sampled from a noise distribution $p_0(\ell)=P^\gamma(\ell)$.
 ($P(j)$ is the fraction of $j$ in the data, and $\gamma>0$ is a parameter).
-Then, given a center-context word pair $(i,j)$, the model predicts whether it is a positive or negative sample using sigmoid function:
+Then, given a target-context word pair $(i,j)$, the model predicts whether it is a positive or negative sample using sigmoid function:
 \begin{align}
@@
 \end{align}
-where $f(x)$ is the unnormalized probability for an instance $x$.
+where $f(x)$ is the non-normalized probability for an instance $x$.
 As in negative sampling, NCE fits the model based on a binary classification task, with positive and negative samples randomly drawn from the given data and a noise distribution $p_0$, respectively, using a bias-corrected sigmoid function:
@@
 In the case of U.S. flight itinerary and scientific mobility, we impute distance to 1 km when their distance is less than one kilometer.
-In the case of Korean accommodation reservation data, because this data is intra-city mobility trajectory, we impute distance to 0.01 km when their distance is less than 0.01 km.
+In the case of Korean accommodation reservation data, because this data is intra-city mobility trajectory at a much smaller scale, we impute distance to 0.01 km when their distance is less than 0.01 km.
 The embedding distance with the cosine distance, $d_{ij}$, is calculated as $d_{ij} = 1 - \frac{\bm{v}_{i} \cdot \bm{v}_{j}}{\lVert \bm{v}_{i} \rVert \lVert \bm{v}_{j} \rVert}$,
@@
 We compare the performance of the embedding distance to many baselines.
-These include distances derived from simpler embedding approaches, such as Singular Value Decomposition (SVD) and a Laplacian Eigenmap embedding performed on the underlying co-occurrence matrix.
+These include distances derived from simpler embedding approaches, such as Singular Value Decomposition (SVD) and a Laplacian Eigenmap embedding performed on the underlying location co-occurrence matrix.
 We also use network-based distances, calculating vectors using a Personalized Page Rank approach and measuring the distance between them using cosine distance and Jensen-Shannon Divergence (see \SI).

### 2021-02-19 paper/current/supp.tex
\cite to \autocite in supp

@@
 
-We also consider Laplacian eigenmaps \cite{belkin2003laplacian}, which is the most fundamental graph embedding method, as the second benchmark on the matrix factorization.
+We also consider Laplacian eigenmaps \autocite{belkin2003laplacian}, which is the most fundamental graph embedding method, as the second benchmark on the matrix factorization.
 First, we construct the co-occurrence matrix of $N$ organization, $A_{ij}$ given by the co-occurence of $i$ and $j$ in the same affiliation trajectory and degree matrix $D$ which is the diagonal matrix for which $D_{ii}=\sum_j {A_{ij}}$.
@@
 
-Furthermore, We examine the gravity model with embedding vector with the symmetric SVD  \textit{word2vec} method\cite{levy2014neural} as the third benchmark on the matrix factorization.
+Furthermore, We examine the gravity model with embedding vector with the symmetric SVD  \textit{word2vec} method\autocite{levy2014neural} as the third benchmark on the matrix factorization.
 Based on idea of \textit{word2vec} is just implciity matrix factorization, Levy proposed symmetric SVD \textit{word2vec} embedding.

### 2021-02-19 paper/current/supp.tex
update SVD and Laplacian texts blocks

--- 2021-02-11 paper/current/supp.tex
@@
 
+\paragraph*{S5 Text}
+\label{si:text:Raw SVD}
+{\bf Singular vector decomposition distance.}
+
+We use the truncated singular vector decomposition (SVD) on the underlying mobility co-occurrence matrix as a baseline embedding. 
+In short, truncated SVD performs linear low-rank approximation of the matrix with given dimensions, $d$.
+First, we construct the co-occurrence matrix of $N$ organizations, $A_{ij}$ given by the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory. 
+Then, we apply truncated singular vector decomposition with $d=300$ on the flow matrix $A$ directly.
+
+We calculate distance between organizations in the SVD embedding space using cosine distance, finding that it explains slighly more of the flux between organizations than does geographic distance ($R^2=0.247$, Table~\ref{supp:table:r2_table}).
+When used as an input to the gravity model, this distance produces better predictions than geographic distance using both the exponential and power-law models.
+
+\paragraph*{S6 Text}
+\label{si:text:Laplacian}
+{\bf Laplacian Eigenmap distance.}
+
+We also consider Laplacian Eigenmap embeddings~\autocite{belkin2003laplacian} as a baseline, which is one of the most fundamental approaches for graph embedding. 
+First, we construct the co-occurrence matrix of $N$ organizations, $A_{ij}$ given by the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory and degree matrix $D$ which is the diagonal matrix for which $D_{ii}=\sum_j {A_{ij}}$.
+Then we construct graph Lapalcian matrix $L = D-A$  and apply truncated singular vector decomposition in the matrix $L$ with $d=300$.
+
+We only report results based on the cosine distance between Laplacian embedding vectors, finding that it explains less of the total flux than geographic distance ($R^{2} = 0.212$, Table~\ref{supp:table:r2_table}).
+When used as an input to the gravity model, the Laplacian cosine distance produces marginally-better predictions than geographic distance using both the exponential (RMSE $= 0.859$, Table~\ref{supp:table:rmse_exp_table}) and power-law models (RMSE = $0.839$, Table~\ref{supp:table:rmse_power_table}), performing slightly better with the power-law model.
+
+\paragraph*{S7 Text}
+\label{si:text:Laplacian}
+{\bf Levy's  symmetric SVD \textit{word2vec} distance}
+
+Furthermore, We examine the gravity model with embedding vector with the symmetric SVD  \textit{word2vec} method\autocite{levy2014neural} as the third benchmark on the matrix factorization.
+Based on idea of \textit{word2vec} is just implciity matrix factorization, Levy proposed symmetric SVD \textit{word2vec} embedding.
+First, we construct the matrix of $N$ organization,
+
+\begin{equation}
+ M_{ij} = \log(\frac{N(i,j) |D|}{N(i) N(j)}) - \log(k)
+\end{equation}
+
+We report the result with euclidean distance ($R^2=0.341$, Table~\ref{supp:table:r2_table}), which is the best performance among cosine distance, euclidean distances and dot product.
+The performance is much bettern that the performance of the model with geographical distance, still below the performance of our suggested way.
+\todo{@dakoda can you write down the performance with other distance measures simply here?}
+
 %
 % S5 TEXT
-\paragraph*{S5 Text}
+\paragraph*{S8 Text}
 \label{si:text:organizations}

### 2021-02-19 paper/current/supp.tex
random typo

@@
 		Performance of personalized page rank scores in explaining and predicting mobility.
-		Personalized page rank is calculated for the underlying mobility network, and distance measured as the cosine distnace between PPR probability distribution vectors.
+		Personalized page rank is calculated for the underlying mobility network, and distance measured as the cosine distance between PPR probability distribution vectors.
 		PPR cosine distance performs roughly similar to geographic distance in explaining global(\textbf{a}), domestic (\textbf{b}), or international (\textbf{c}) country mobility.

### 2021-02-19 paper/current/supp.tex
update S? text comments
finished up distance text

@@
 
+%
+% S5 Text
 \paragraph*{S5 Text}
@@
 We calculate distance between organizations in the SVD embedding space using cosine distance, finding that it explains slighly more of the flux between organizations than does geographic distance ($R^2=0.247$, Table~\ref{supp:table:r2_table}).
-When used as an input to the gravity model, this distance produces better predictions than geographic distance using both the exponential and power-law models.
-
+When used as an input to the gravity model, this distance produces better predictions than geographic distance using both the exponential (RMSE $= 0.859$, Table~\ref{supp:table:rmse_exp_table}) and power-law models (RMSE $= 0.839$, Table~\ref{supp:table:rmse_exp_table}), performing slightly better with the power-law formulation.
+
+%
+% S6 Text
 \paragraph*{S6 Text}
@@
 We only report results based on the cosine distance between Laplacian embedding vectors, finding that it explains less of the total flux than geographic distance ($R^{2} = 0.212$, Table~\ref{supp:table:r2_table}).
-When used as an input to the gravity model, the Laplacian cosine distance produces marginally-better predictions than geographic distance using both the exponential (RMSE $= 0.859$, Table~\ref{supp:table:rmse_exp_table}) and power-law models (RMSE = $0.839$, Table~\ref{supp:table:rmse_power_table}), performing slightly better with the power-law model.
-
+When used as an input to the gravity model, the Laplacian cosine distance produces marginally-better predictions than geographic distance using both the exponential (RMSE $= 0.878$, Table~\ref{supp:table:rmse_exp_table}) and power-law models (RMSE = $0.87$, Table~\ref{supp:table:rmse_power_table}), performing slightly better with the power-law formulation.
+
+%
+% S7 Text
 \paragraph*{S7 Text}
-\label{si:text:Laplacian}
+\label{si:text:levy}
 {\bf Levy's  symmetric SVD \textit{word2vec} distance}
 
-Furthermore, We examine the gravity model with embedding vector with the symmetric SVD  \textit{word2vec} method\autocite{levy2014neural} as the third benchmark on the matrix factorization.
-Based on idea of \textit{word2vec} is just implciity matrix factorization, Levy proposed symmetric SVD \textit{word2vec} embedding.
+Finally, we also compare the \textit{word2vec} embedding distnace against a baseline of direct matrix factorization approach, using the symmetric SVD  \textit{word2vec} method~\autocite{levy2014neural}.
+Based on idea of \textit{word2vec} is just implicit matrix factorization, Levy proposed symmetric SVD \textit{word2vec} embedding, which should directly compute the embedding that \textit{word2vec} only attempts to efficiently approximate.
 First, we construct the matrix of $N$ organization,
@@
 
-We report the result with euclidean distance ($R^2=0.341$, Table~\ref{supp:table:r2_table}), which is the best performance among cosine distance, euclidean distances and dot product.
-The performance is much bettern that the performance of the model with geographical distance, still below the performance of our suggested way.
-\todo{@dakoda can you write down the performance with other distance measures simply here?}
-
-%
-% S5 TEXT
+\todo{Finish the text here...}
+
+For this baseline, we report results using the cosine distance, euclidean distance, and dot product between the embedding vectors. 
+We find that the dot product performs by far the worst, worse than any other baseline considered $R^{2} = 0.004$, Table~\ref{supp:table:r2_table}). 
+The cosine distance performs better, but worse than geographic distance ($R^{2} = 0.212$, Table~\ref{supp:table:r2_table}). 
+The euclidean distance performs best, explaining more of the flux than geographic distance, and only being below the embedding distance ($R^{2} = 0.341$, Table~\ref{supp:table:r2_table}). 
+Focusing on the euclidean distance, we find that using it as input to the gravity model results in better predictions than geographic distance using both the exponential model (RMSE $= 0.803$, Table~\ref{supp:table:rmse_exp_table}) and power law models, (RMSE $= 0.78$, Table~\ref{supp:table:rmse_power_table}), though it performs slightly better with the power law formulation.
+
+%
+% S8 TEXT
 \paragraph*{S8 Text}
@@
 %
-% S6 TEXT
+% S9 TEXT
 \paragraph*{S9 Text}
@@
 %
-% S7 TEXT
+% S10 TEXT
 \paragraph*{S10 Text}
@@
 %
-% S8 TEXT
+% S11 TEXT
 \paragraph*{S11 Text}

### 2021-02-19 paper/current/main.tex
update number of netagive sample in main text

@@
 We used the \textit{word2vec}  implementation in the python package \texttt{gensim}.
-The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{\min}$, initial learning rate $\alpha$, shape of negative sampling distribution $\gamma$, and the number of iterations.
+The skip-gram negative sampling  \textit{word2vec} model has several tunable hyper-parameters, including the embedding dimension $d$, the size of the context window $w$, the minimum frequency threshold $f_{\min}$, initial learning rate $\alpha$, shape of negative sampling distribution $\gamma$, the number of the negative samples should be drawn $k$, and the number of iterations.
 For main results regarding scientific mobility, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig.~\ref{fig:supp:hyperparameter}).
 Although the original \textit{word2vec } paper uses $\gamma = 0.75$\autocite{mikolov2013word2vec}, here we set $\gamma = 1.0$, though results are only trivially different at different values of $\gamma$ (Fig.~\ref{fig:supp:distancemetrics}).
+We used $k=5$, which is suggested default of \textit{word2vec}.
 We also use same setting for U.S. airport itinerary and Korean accommodation reservation data.

### 2021-02-19 paper/current/supp.tex
add some text on levy

@@
 When used as an input to the gravity model, this distance produces better predictions than geographic distance using both the exponential (RMSE $= 0.859$, Table~\ref{supp:table:rmse_exp_table}) and power-law models (RMSE $= 0.839$, Table~\ref{supp:table:rmse_exp_table}), performing slightly better with the power-law formulation.
+\todo{@dakoda other distance measures?}
 
@@
 When used as an input to the gravity model, the Laplacian cosine distance produces marginally-better predictions than geographic distance using both the exponential (RMSE $= 0.878$, Table~\ref{supp:table:rmse_exp_table}) and power-law models (RMSE = $0.87$, Table~\ref{supp:table:rmse_power_table}), performing slightly better with the power-law formulation.
+\todo{@dakoda other distance measures?}
 
@@
 Based on idea of \textit{word2vec} is just implicit matrix factorization, Levy proposed symmetric SVD \textit{word2vec} embedding, which should directly compute the embedding that \textit{word2vec} only attempts to efficiently approximate.
-First, we construct the matrix of $N$ organization,
+First, we construct the matrix of $N$ organization
 
 \begin{equation}
- M_{ij} = \log(\frac{N(i,j) |D|}{N(i) N(j)}) - \log(k)
+ M_{ij} = \log(\frac{N(i,j) |D|}{N(i) N(j)}) - \log(k),
 \end{equation}
-
-\todo{Finish the text here...}
+where $N(i,j)$ is the number of times the location pair $(i,j)$ appears given the window size $w$ in the total corpus $D$ ,$N(i)=\sum_{j=N}^i N(i,j)$ as the number of items $i$ occurred given the window size $w$ in $D$, and k is the number of negative samples.
+We used $w=1$ and $k=5$ which is same setting in the our main result.
+Then, we factorized matrix $M$ with truncated singular vector decomposition in the matrix with $d=300$ into $U_d \Sigma_d V_d$, and used the embedding vector as $U_d\sqrt{\Sigma_d}$.
 

### 2021-02-19 paper/current/supp.tex
add paragraphs

@@
 Focusing on the euclidean distance, we find that using it as input to the gravity model results in better predictions than geographic distance using both the exponential model (RMSE $= 0.803$, Table~\ref{supp:table:rmse_exp_table}) and power law models, (RMSE $= 0.78$, Table~\ref{supp:table:rmse_power_table}), though it performs slightly better with the power law formulation.
+
+\paragraph*{S8 Text}
+\label{si:text:levy}
+{\bf Why do neural embedings outperform direct matrix factorization?}
+
+Why do neural-embedding approaches, which rely on stochastic gradient descent, outperform direct matrix factorization, especially seeing as \textit{word2vec} implicitly approximates factorization?
+An issue in the matrix factorization approach is that it is extremely sensitive to small flows between affiliations.
+The matrix factorization approach embeds affiliations $i$ and $j$ such that their dot similarity is as close as to $\log (T_{ij} / P(i) P(j))$.
+If the flow $T_{ij}$ is considerably small or zero, the dot similarity goes $-\infty$, pushing $i$ and $j$ very far from the other affiliations in the embedding space~\autocite{levy2014neural, Qui2018}.
+This is particularly problematic when the window size is small because most affiliation pairs would have no flow, which is indeed the case in our experiments.
+To circumvent this problem, the previous studies~\autocite{levy2014neural, Qui2018} add a constant flow between the affiliation pairs with no flow.
+However, this changes the data to which we fit the model, and small flows still have a considerably strong impact on the embedding.
+
+Also, it is well known that SVD itself is vulnerable to outliers \autocite{xu2012robust, huber1981robust, xu1995robust, chandrasekaran2011rank, candes2011robust}.
+The stochastic gradient descent algorithm (SGD), which is employed in SGNS \textit{word2vec}, is more robust than SVD and can enhance generalization and effectiveness of {\it word2vec} model \autocite{ma2018power, smith2020generalization, zhang2019algorithmic}.
 

### 2021-02-19 paper/rebuttal/rebuttal.tex
add speculation para

@@
 \subsection{Why do neural embeddings outperform direct matrix factorization?}% why sgd is better?
-One question raised by these comparisons is, why do neural-embedding approaches, which rely on stochastic gradient descent, outperform direct matrix factorization, especially seeing as \textit{word2vec} implicitly approximates factorization?
+Why do neural-embedding approaches, which rely on stochastic gradient descent, outperform direct matrix factorization, especially given that \textit{word2vec} \emph{is} implicitly approximating factorization?
 An issue in the matrix factorization approach is that it is extremely sensitive to small flows between affiliations.
@@
 
-Also, it is well known that SVD by itself is very vulnerable to outliers \autocite{xu2012robust, huber1981robust, xu1995robust, chandrasekaran2011rank, candes2011robust}.
+Also, it is well known that SVD itself is vulnerable to outliers \autocite{xu2012robust, huber1981robust, xu1995robust, chandrasekaran2011rank, candes2011robust}.
 The stochastic gradient descent algorithm (SGD), which is employed in SGNS \textit{word2vec}, is more robust than SVD and can enhance generalization and effectiveness of {\it word2vec} model \autocite{ma2018power, smith2020generalization, zhang2019algorithmic}.

### 2021-02-19 paper/current/supp.tex
add speculation para

@@
 \paragraph*{S8 Text}
-\label{si:text:levy}
+\label{si:text:whynueralbetter}
 {\bf Why do neural embedings outperform direct matrix factorization?}
 
-Why do neural-embedding approaches, which rely on stochastic gradient descent, outperform direct matrix factorization, especially seeing as \textit{word2vec} implicitly approximates factorization?
+Why do neural-embedding approaches, which rely on stochastic gradient descent, outperform direct matrix factorization, especially given that \textit{word2vec} \emph{is} implicitly approximating factorization?
 An issue in the matrix factorization approach is that it is extremely sensitive to small flows between affiliations.
@@
 % S8 TEXT
-\paragraph*{S8 Text}
+\paragraph*{S9 Text}
 \label{si:text:organizations}
@@
 % S9 TEXT
-\paragraph*{S9 Text}
+\paragraph*{S10 Text}
 \label{si:text:disambiguation}
@@
 % S10 TEXT
-\paragraph*{S10 Text}
+\paragraph*{S11 Text}
 \label{si:text:network_ranking}
@@
 % S11 TEXT
-\paragraph*{S11 Text}
+\paragraph*{S12 Text}
 \label{si:text:boomerang_speculation}

### 2021-02-19 paper/rebuttal/rebuttal.tex
yy comments: cover letter

@@
 
-We thank all the referees for their incredibly thoughtful and helpful comments and critiques, all of which provided valuable insights.
-Following these comments, we have made a breakthrough in our study, and have made substantial revisions to our manuscript to emphasize these new theoretical contributions and additional methodological comparisons.
-With these changes, we are confident that our paper is significantly stronger, and its contribution more wide-reaching and impactful.
+We thank all the referees for their thoughtful and helpful comments and critiques, all of which provided valuable insights.
+We acknowledge that our initial submission had a substantial gap regarding the choice of the \textit{word2vec} model, its connection with the gravity model of mobility, and its evaluation. 
+While reflecting on these comments and our manuscript, we have made a theoretical breakthrough that addresses the primary issues;
+namely, we have discovered a mathematical connection between the \textit{word2vec} (skip-gram) model and the gravity model. 
+Furthermore, our subsequent experiments show that our approach's performance is robust, exceeding other baselines. 
+Therefore, with these changes, we are confident that our paper is significantly stronger, and its contribution more wide-reaching and impactful.
+Thus, we would like to request a reconsideration of our manuscript. 
 Again, we are incredibly appreciative of these comments, which provided the insight and motivation needed to make these breakthroughs.
@@
 Addressing the first point, we have identified an underlying mathematical equivalence between the Gravity Model of Mobility and the neural embedding technique \textit{word2vec}.
-Namely, we demonstrate that \textit{word2vec} 's objective function is same as the gravity law and thus \textit{word2vec} learns gravity-like relationships between entities, whether it be language or locations.
+Namely, we demonstrate that \textit{word2vec} 's objective function is equivalent to the gravity law and thus \textit{word2vec} learns gravity-like relationships between entities, whether it be language or locations.
 This development constitutes a major breakthrough in our understanding of neural embeddings, and provides theoretical justification for their application to mobility.
 
-For the second point, we have also conducted experiments comparing the performance of neural embedding to distances from an embedding derived by a singular value decomposition of the mobility network, and of a Laplacian eigenmap embedding.
+For the second point, we have also conducted experiments comparing the performance of neural embedding to an embedding derived by a singular value decomposition of the mobility network, and of a Laplacian eigenmap embedding.
 Additionally, we compare \textit{word2vec} model to another matrix factorization approach, which \textit{word2vec} approximates.

### 2021-02-19 paper/rebuttal/rebuttal.tex
yy comments: section 1 rebuttal

@@
 \label{sec:theory}
-Here, we answer a question: Why does the skip-gram model with negative sampling (SGNS), otherwise known as \textit{word2vec}, work so well to model human mobility?
-We demonstrate a fundamental connection between the SGNS model and the Gravity Model of Mobility, namely, that SGNS implicitly learns gravity-like relationships between locations.
-This connection provides necessary theoretical justification to our choice of \textit{word2vec}, and constitutes a major breakthrough of our understanding of neural embeddings.
+Why does \textit{word2vec} with the skip-gram with negative sampling model (SGNS) work so well to model human mobility?
+Here, we demonstrate that the SGNS model and the gravity model of mobility are mathematically equivalent.
+This connection provides strong theoretical justification to our choice of \textit{word2vec}, and constitutes a major breakthrough of our understanding of neural embeddings.
 In addition, this motivates the use of SGNS for future study of human mobility.
 
-First, we outline  \textit{word2vec} model.
-Then, we introduce the specific SGNS model, which incorperates a procedure called negative sampling that is key to its connection with the gravity model.
-Finally, we demonstrate the connection between SGNS and the gravity model of mobility.
-
-\subsection{Details on \textit{word2vec} algorithm}
-We used the standard skip-gram negative sampling (SGNS) word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec}.
-Suppose a trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), where $a_{t}$ is the $t$th location in the trajectory.
+\subsection{\textit{word2vec} algorithm}
+Imagine a trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), where $a_{t}$ is the $t$th location in the trajectory.
 A location, $a_{t}$, is considered to have context locations, $a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}$, that appear in the window surrounding $a_t$ up to a time lag of $w$, where $w$ is the window size parameter truncated at $t - w \geq 0$ and $t + w \leq T$.
-Then, the model learns probability $p(a_{t + \tau} \vert a_{t})$, where $-w\leq \tau\leq w$ and $\tau \neq 0$,  by maximizing its log likelihood given by
+Then, the SGNS model learns probability $p(a_{t + \tau} \vert a_{t})$, where $-w\leq \tau\leq w$ and $\tau \neq 0$,  by maximizing its log likelihood given by
 %
@@
 hierarchical softmax \autocite{morin2005hierarchical} and negative sampling \autocite{mikolov2013word2vec}.
+Due to its simplicity and performance, negative sampling is the most widely used strategy, which we also adopt in our study.
 
 \subsection{An implicit bias in the negative sampling}
-
-In our paper, we employed a specific algorithm SGNS word embedding.
-However, it is well known that the negative sampling is a biased estimator~\autocite{Chia2010,Dyer2014} that optimizes a distinct model  from {\it word2vec}.
+Although negative sampling is the most common approximation, it is known that it is a biased estimator~\autocite{Chia2010,Dyer2014} that optimizes an objective function different from {\it word2vec}.
 
 Negative sampling trains {\it word2vec} using a binary classification task as follows.
-A center-context word pair $(i,j)$ is sampled from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$ are sampled from a noise distribution $p_0(\ell)=P^\gamma(\ell)$.
+A target-context word pair $(i,j)$ is sampled from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$ are sampled from a noise distribution $p_0(\ell)=P^\gamma(\ell)$.
 ($P(j)$ is the fraction of $j$ in the data, and $\gamma>0$ is a parameter).
-Then, given a center-context word pair $(i,j)$, the model predicts whether it is a positive or negative sample using sigmoid function:
+Then, given a target-context word pair $(i,j)$, the model predicts whether it is a positive or negative sample using a sigmoid function:
 \begin{align}
@@
 
-This procedure does not guarantee that the embedding optimally converges to the original conditional probability eq.\ref{eq:cond_prob_w2v}, even when increasing the training samples and iterations~\autocite{Chia2010,Dyer2014} in the fact that negative sampling has implicit bias.
-This problem is addressed by the noise contrastive estimation (NCE) \autocite{Chia2010}, which fits a probability model in the form:
+This procedure does not guarantee that the embedding optimally converges to the original conditional probability from Eq.~\ref{eq:cond_prob_w2v}, even when increasing the training samples and iterations~\autocite{Chia2010,Dyer2014} because negative sampling has implicit bias.
+This problem is addressed by the noise contrastive estimation (NCE) \autocite{Chia2010}, which fits the following probability model,
 \begin{align}
@@
 
-Rewriting the sigmoid function for the negative sampling (Eq.~\eqref{eq:sigmoid}) in form of the bias-corrected sigmoid function yields
+Rewriting the sigmoid function for the negative sampling (Eq.~\ref{eq:sigmoid}) where the bias-corrected sigmoid function yields
 \begin{align}
@@
 \end{align}
-So, the model with the negative sampling optimize $\tilde f(x)$, not $f(x)$.
+So, the model with the negative sampling optimizes $\tilde f(x)$, not $f(x)$.
 In case of the {\it word2vec}, the instance is the dot similarity $x=\bm{u}_i \cdot \bm{v}_j$,  $f(x)=\exp(x)$, and $p_0(j)=P^\gamma(j)$, and the SGNS word2vec actually optimize the following conditional probability:
@@
 
-Taking into an implicit bias in the negative sampling  and set $w=1$, the \textit{word2vec} predict the flow with
+Taking into account the implicit bias in the negative sampling  and setting $w=1$, the \textit{word2vec} predicts the flow between locations with
 \begin{align}
-	\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)P^\gamma (j)\exp(\bm{v}_j \cdot \bm{v}_{i})}{Z_i}. \label{eq:prob_w2v_ng0}
+	\hat{T}_{ij}= P(i) P(j\given i) = \frac{P(i)P^\gamma (j)\exp(\bm{v}_j \cdot \bm{v}_{i})}{Z_i}. \label{eq:prob_w2v_ng0}
 \end{align}
@@
 Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimial in-vectors and out-vectors such that $\bm{u}_i = \bm{v}_i$ \autocite{levy2014neural}.
-Setting $\gamma = 1$ and substituting $\bm{u}_i = \bm{v}_j$ into Eq.~\eqref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
+Setting $\gamma = 1$ and substituting $\bm{u}_i = \bm{v}_j$ into Eq.~\ref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
 \begin{align}
@@
 
-The flow $\hat{T_{ij}}$ is symmetric (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because {\it word2vec} neglects whether the context $j$ appears before or after the center $i$ in the trajectory---the mechanism of skip-gram.
-If we swap $i$ and $j$ in Eq.~\eqref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
+The flow $\hat{T}_{ij}$ is symmetric (\ie $\hat{T}_{ij}=\hat{T}_{ji}$) becausethe skip-gram model neglects whether the context $j$ appears before or after the target $i$ in the trajectory.
+If we swap $i$ and $j$ in Eq.~\ref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
 Therefore, to ensure $\hat{T}_{ij} = \hat{T}_{ji}$, the denominator $Z_i$ should be a constant.
 
-Taken altogether, the {\it word2vec} model with the negative sampling predicts a flow in the same form as in the gravity model:
+Taken together, the {\it word2vec} model with the negative sampling predicts a flow in the same form as in the gravity model:
 \begin{align}
@@
 
-In other words, \emph{word2vec with the negative sampling is a gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
-While the gravity model generates mobility flow from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given mobility flow.
+In other words, \emph{word2vec with the negative sampling is a equivalent to a gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
+While the gravity model predicts mobility flows from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given mobility flow.
 Therefore, the embedding distance is inherently tied to mobility flow, and hence, has greater predictive power than the geographic distance.
 
-A central assumption in our mathematical analysis is that the embedding vectors are optimum in terms of the {\it word2vec}'s objective function.
-However, this premise is not practical because the optimization algorithm (\eg stochastic gradient descent algorithm) often finds sub-optimal embeddings.
-This has two consequences.
-First, the in- and out-vectors can be different.
-Second, dot similarity calculated by {\it word2vec} is the distance metric tied to the gravity model, and hence, should capture the mobility flow well.
-Our numerical simulations show that dot similarity calculated by {\it word2vec} is the second-best predictor of mobility flow among the ten embedding distances~(Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
-However, cosine similarity predicted mobility flow better than dot similarity.
-This result echos many applications of word embedding such as word analogy test~\autocite{levy2015improving}, in which cosine similarity outperforms dot similarity.
-In predicting mobility flow, if the embedding vectors are optimal, cosine similarity should be no better than dot similarity because cosine similarity is a special case of dot similarity.
-Therefore, the inferiority of dot similarity is attributed to the optimization process.
-Although finding an optimal embedding is difficult in practice, a careful tuning of the optimization algorithm would close the gap between our mathematical and numerical results.
+In practice, because we do not have unlimited amounts of data (which is also noisy) and the optimization may not find the true optimum, the idealized result may not hold. 
+Indeed, we tend to find that the in- and out-vectors tend to be different and that the cosine similarity tends to better capture real-world mobility than the dot similarity.
+Nevertheless, a model with dot similarity is still the second best after cosine similarity (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and the embedding distance still outperforms all alternatives we considered.
 
 \subsection{Changes to the manuscript}
-To reflect these breakthroughs, we have made the following changes to the manuscript:
+To reflect our new findings, we have made the following changes to the manuscript:
 \begin{itemize}
@@
 	\item We also added the section \textbf{An implicit bias in the negative sampling} to the methods section of our manuscript.
-	\item Since the formulation of the gravity used in the above derivations assumes $\gamma = 1$, we use this value of $gamma$ for all reported results. No result substantively changes with this change.
-	\item We added a sentence to the paper speculating on why cosine similarity works best in the main text.
+	\item Since the formulation of the gravity used in the above derivations assumes $\gamma = 1$, we use $\gamma = 1$ for all reported results. No results have been substantively changed.
+	\item We added a sentence to the paper speculating on why cosine similarity works best.
 	\item We also added a sentence noting the in-vector and out-vector issue, and speculating on reasons/consequences.

### 2021-02-19 workflow/scripts/PlotDistanceMetricPerformance.R
add asterisk to best performing metric in fig

@@ -69,11 +69,20 @@ plotdata <- data.table::rbindlist(list(r2, rmse), use.names = T) %>%
                              "Prediction error\n(Exponential model)"))
   )
 
+# Get the top-performing for each set of parameters
+top <- plotdata %>%
+  group_by(type) %>%
+  filter((type == "Flux explained" & value == max(value)) | (type != "Flux explained" & value == min(value)))
+
 # build the plot
 plot <- plotdata %>%
   ggplot(aes(x = value, y = metric, fill = type, shape = type)) +
   geom_point(size = 2.5, alpha = 0.8,
              position = position_dodge(0.75)) +
+  geom_point(data = top, size = 1,
+             aes(y = as.numeric(metric) + 0.1, x = value + 0.05, fill = type, shape = type),
+             position = position_dodge(0.75),
+             shape = 8, show.legend = FALSE) +
   geom_text(aes(label = round(value, 2)), size = 2.5, hjust = -1,
             position = position_dodge(0.75)) +
   facet_wrap(~performance) +

### 2021-02-19 paper/rebuttal/rebuttal.tex
yy comments: section 2 of rebuttal

@@
 \subsection{New experimental parameters}
-In addition to the new baselines, we have also incorporate additional experimental parameters into our analysis.
+In addition to the new baselines, we have also incorporated additional experimental parameters into our analysis.
 The first is $\gamma$, a hyper-parameter of the \textit{word2vec} model, which defines the exponent which shapes the negative sampling distribution.
-The default of the `\texttt{gensim} implementation of \textit{word2vec} is to set $\gamma = 0.75$, and this was the value used in our original manuscript.
+The default of `\texttt{gensim's} implementation of \textit{word2vec} is to set $\gamma = 0.75$, and this was the value used in our original manuscript.
 However, to connect \textit{word2vec} to the gravity model of mobility, we assume $\gamma = 1.0$ (see section 1).
@@
 		Cosine distance between embedding vectors generated with \textit{word2vec} explains more of the flux, and better predicts flux when used in the gravity model of mobility than geographic distance and other baselines.
-		Shown is the correlation between the flux and embedding distances, measured with $r^{2}$ (left), and the prediction error when using the distance as input to the gravity model of mobility.
+		Shown is the correlation between the flux and embedding distances, measured with $R^{2}$ (left), and the prediction error when using the distance as input to the gravity model of mobility.
 		For prediction error, we show results based on both the exponential and power-law forms of the gravity model.
 		All embedding-based methods use dimensions of 300.
-		Here, embedding distance is obtained from neural embeddings learned with window size of 1 and $\gamma = 1$.
+		Embedding distance is obtained from neural embeddings learned with window size of 1 and $\gamma = 1$.
+		The metric with the highest correlation and lowest prediction error are marked with an asterisk. 
 		In all cases, organization population is defined as the mean annualized number of unique mobile and non-mobile authors, and flux is calculated for all global mobility.
@@
 We find that, using the best performing dimensions (300) and window size (1),  $\gamma = 1.0$, and for default experimental parameters (global mobility, population defined using all mobile and non-mobile scholars), that the embedding distance, or cosine distance between vectors learned through neural embedding, explains more of the flux, and leads to better predictions than other baselines (Fig.~\ref{fig:supp:distancemetrics}).
-This performance held when considering both the exponential and the power-law forms of the gravity model of mobility.
-The euclidean distance between directly-factorized vectors performs comparably, and even beats out the embedding distance under certain experimental conditions (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
-
-\subsection{Why do neural embeddings outperform direct matrix factorization?}% why sgd is better?
+This performance advantage holds when considering both the exponential and the power-law forms of the gravity model of mobility.
+Although the euclidean distance between directly-factorized vectors performs comparably, and even narrowly beats out the embedding distance under certain experimental conditions (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}); \textit{word2vec} shows the msot consistent and robust performance, as suggested by Levy \& Goldberg~\autocite{levy2014neural}.
+
+\subsection{Why do neural embeddings outperform direct matrix factorization?}
 Why do neural-embedding approaches, which rely on stochastic gradient descent, outperform direct matrix factorization, especially given that \textit{word2vec} \emph{is} implicitly approximating factorization?
@@
 %
+\clearpage
 \section{Point-by-point discussion}

### 2021-02-19 paper/rebuttal/rebuttal.tex
yy comments: section 3.1 rebuttal

@@
 	We have carefully read through each, and learned a lot in the process.
-	They have now been incorperated into our manuscript's introduction.
+	They have now been incorporated into our manuscript's introduction.
+	Although there are existing work on trajectory-based mobility embedding, we argue that our new result establishing the mathematical equivalence of \textit{word2vec} and the gravity law represents a novel and substantial contribution.
 }
@@
 	Thank you for the suggestion!
-	Since our original submission, we have made a breakthrough, uncovering a mathematical connection between the skip-gram model with negative sampling, and the gravity model of mobility.
-	Namely, we find that SGNS is a gravity model, and is learns gravity-like relationships between tokens in its vocabulary.
+	Since our original submission, we have uncovered a mathematical connection between the skip-gram model with negative sampling, and the gravity model of mobility.
+	Namely, we find that \emph{SGNS is a gravity model}.
 	This finding demonstrates why SGNS performs so well, and demonstrates the utility of the model for studying contexts where gravity relationships are expected, such as in human mobility.
@@
 	\& Goldberg's~\autocite{levy2014neural} matrix factorization, the last of which directly calculates what SGNS only approximates.
-	We find that in nearly every case, SGNS outperforms all of these baselines, furhter illustrating the potential of such models for embedding and studying mobility.
+	We find that in nearly every case, SGNS outperforms all of these baselines, further illustrating the potential of such models for embedding and studying mobility.
 	We refer you to Section 2 of this rebuttal letter, above, for more detailed results and the changes we made to our manuscript.
@@
 	We believe that the ratio of the number of organizations represented in our dataset to the total number of mobility trajectories makes our results especially robust.
-	Only about 8,661 organizations are represented across over three million career trajectories of scientists, such that nearly every organization appears enough times, and in enough contexts, to produce a robust vector representation.
+	About 8,661 organizations are represented across over three million career trajectories of scientists, such that nearly every organization appears enough times, and in enough contexts, to produce a robust vector representation.
 	However, this may not hold true for all problem domains—for example, natural language includes many millions of tokens, many of which will occur only a few times, allowing stochasticity to have a much stronger effect on the final representation.
@@
 	“We however, note that all results shown here are robust to this stochasticity, likely emerging from the limited ``vocabulary'' of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories).
-Applications of word2vec to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random artifacts.”
+Applications of word2vec to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random fluctuations.”
 
@@
 	You are correct that it was a conscious choice to not report statistical significance in the form of a P-value.
-	The use of statistical significance is contentious, and Nature itself has hosted some of this debate (\href{https://www.nature.com/articles/d41586-019-00857-9}{[link]}).
-	As such, we have a philosophy of avoiding p-values in research when it makes sense to do so.
-	In our analysis, all correlations and fits are significant at a level below 0.0001, or have a p-value  computationally indistinguishable from zero.
+	The use of statistical significance is contentious, and Nature itself has hosted some of this debate~\autocite{amrhein2019statistics}.
+	As such, we avoided p-values in our research when it made sense to do so.
+	In our analysis, all significance levels were below 0.0001, with most computationally indistinguishable from zero.
 	However, we recognize that p-values can help readers interpret results.
-	As such, we have opted to add to a sentence such as \say{\textit{Correlation is calculated on the data in the log-log scale ($p <<0.0001$ across all fits)}.} or similar to relevant figures in the main text and supporting materials.
-	We believe that this solution strikes a balance between transparency while also avoiding extraneous detail and the common pitfalls of statistical reporting.
+	As such, we have opted to add to a sentence such as \say{\textit{Correlation is calculated on the data in the log-log scale ($p < 0.0001$ across all fits)}.} or similar to relevant figures in the main text and supporting materials.
 
@@
 
-\response{We believe that the mathematical breakthroughs made since our first submission improve the manuscript and extend its contribution and demonstrates novel scientific insight, and justifies the use of word2vec towards mobility data.
+\response{We believe that our new mathematical results substantially improve the manuscript and extend its contribution and demonstrates novel scientific insight, and justifies the use of word2vec towards mobility data.
 By adding this, and addressing your other points (above), we believe that the revised manuscript sufficiently remedies your concerns.
@@
 %
+\clearpage
 \subsection{Response to Referee 2}

### 2021-02-19 paper/current/main.tex
yy comments: section 3.1 rebuttal

@@
 We however, note that all results shown here are robust to this stochasticity, likely emerging from the limited ``vocabulary'' of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories).
-Applications of \textit{word2vec }to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random artifacts.
+Applications of \textit{word2vec }to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random fluctuations.
 Finally, the case of scientific mobility presents domain-specific limitations.

### 2021-02-19 paper/rebuttal/rebuttal.tex
yy comments: section 3.2 rebuttal

@@
 	We carefully read out the Barthélemy, Physics Reports 499, 1, 2011, and referenced it in our manuscript.
-	Also, we report the performance of the flux estimation and prediction using different deterrence functions (see Section 2, above), finding that while performance differs, the embedding distance outperforms geographic distance no matter the function used.
+	Also, we report the performance of the flux estimation and prediction using different deterrence functions (see Section 2, above), finding that the absolute values vary, the pattern doesn't change---the embedding distance robustly outperforms geographic distance regardless of the function used.
 	We add the following line to the methods noting this point,
@@
 	\say{The decay function $f(r_{ij})$ defines the effect of distance, and so different decay functions can model fundamentally different mechanism [...] such as the cost functions for a given distance and the spatial granularity of the observation.
-		For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case though the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Supporting Information).}
-
-	We find the article that geographical distance ﬁts well with the power-law decay function because power-based gravity model can be more suitable for analyzing large, complex, and scale-free spatial systems theoretically and the exp`onential-based gravity model indicates simplicty rather than spatial complexity~\autocite{chen2015distance}.
-Meanwhile, embedding distance ﬁts well with the exponential decay function, which we demonstrate to correspond to an underlying mathematical relationship between \textit{word2vec} and the gravity model, a connection we recently discovered and included as a major finding in this revision (see our response to Referee 1).
+		For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case though there is no qualitative difference---the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Supporting Information).}
+
+	We find the article that geographical distance ﬁts well with the power-law decay function because power-based gravity model can be more suitable for analyzing large, complex, and scale-free spatial systems, complexity which the exponential-based gravity model is not able to capture~\autocite{chen2015distance}.
+	However, the embedding distance fits well with the exponential decay function, perhaps demonstrating that the real-world spatial complexity of mobility is encoded in the \textit{word2vec}embedding space as simpler pairwise distances, likely resulting from underlying connection we established between \textit{word2vec} and the gravity model (see section 1, above).
 
@@
 
-	In addition, we provided more explicit mathematical detail of word2vec in the new subsection entitled “word2vec and the gravity model”.
-You can read about this connection in Section 1 of this letter, above.
-
-	We believe that these details are sufficient in the main text of the manuscript, and refer readers to the Methods for a deeper explanation.
+	In addition, we provided more explicit mathematical detail of word2vec in the new subsection entitled “word2vec and the gravity model” (see section 1, above).
+
 }
@@
 	We however, do not believe that this is a problem in our analysis.
-	Raw co-occurrence, which is used to define our 'flux' between organizations, is always calculated using all organizations in a trajectory, and so window size does not affect flux.
+	Raw co-occurrence, which is used to define our ``flux'' between organizations, is always calculated using all organizations in a trajectory, and so window size does not affect flux.
 	Window size does affect \textit{word2vec}, however setting a smaller/larger window size should not make results incomparable.
 	When we set $w = 1$, \textit{word2vec} will generate training pairs at most 1 position away from each target location, for all possible targets.
-	When we instead set $w = 2$, \textit{word2vec} will generate training pairs the same way, but at most 2 positions away from each target---this means that the data for $w = 2$ will be \textit{larger}, containing as a subset all training pairs used for $w = 1$.
+	When we instead set $w = 2$, \textit{word2vec} will generate training pairs the same way, but at most 2 positions away from each target---this means that the data for $w = 2$ will be \textit{larger}, containing all training pairs used for $w = 1$ as a subset.
 	The same follows for all $w > 1$, each generating a larger and larger set of training examples up until $w$ is larger than the length of the longest trajectory.
 
-	What is notable about our findings, therefore, is that even though a model trained with $w = 1$ generates fewer training samples, it still outperforms $w > 1$ settings, which use more training samples, and which should capture higher-order structures in the data.
+	What is notable about our findings, therefore, is that even though a model trained with $w = 1$ generates fewer training samples, it still outperforms settings with $w > 1$, which use more training samples, and which should capture higher-order structures in the data.
 	We speculate that this is because the word2vec model with $w = 1$ is equvelant to the gravity model of mobility (see Section 1).
@@
 	Thank you for these comments. 
-First, we added a line to the methods section detailing the \textit{word2vec} we used, and noting that these achieved the bst performance: \say{\textit{For main results regarding scientific mobility, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig....)}}.
+	First, we added a line to the methods section detailing the \textit{word2vec} we used, and noting that these achieved the best performance: \say{\textit{For main results regarding scientific mobility, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig....)}}.
+
 	A full search of the parameter space would certainly be interesting and useful, however we believe that set of parameters we considered here is sufficient to establish the utility of the approach, and demonstrate that performance is only slightly different based on different parameters.
+	We note that in previous work from our group, we explored the optimal dimensions for graph embedding~\autocite{gu2020dimensions}, finding that while a minimum number of dimensions is necessary, increasing the dimensions does not detract from performance, a property common across deep learning methods.
+	Given that there is little performance difference between $d = 100$ and $d = 300$, we opt to use the larger embeddings at $d = 300$, which are large enough to capture the complexity of mobility, yet small enough to allow an efficient computational workflow.
 }
@@
 
+%
+%
+% Response to reviewer 3
+\clearpage
 \subsection{Response to Referee 3}

### 2021-02-19 paper/current/main.tex
yy comments: section 3.2 rebuttal

@@
 The decay function $f(r_{ij})$ defines the effect of distance, and so different decay functions can model fundamentally different mechanism \autocite{barthelemy2011spatial} such as the cost functions for a given distance and the spatial granularity of the observation.
-For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}), though the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}), though there is no qualitative difference---the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
 Beyond the fitting on the data, we would like to argue that geographical distance fits well with the power-law decay function because it is more suitable for analyzing large, complex, and scale-free spatial systems\autocite{chen2015distance}, while embedding distance fits well with the exponential decay function, which we will show later in the section of mathematical relation between \textit{word2vec}and the gravity model.

### 2021-02-19 paper/current/main.tex
tweak the theory section of main text

@@
 Why does the embedding distance predict actual mobility flows better than the geographic distance?
-Here, we show that the objective function of {\it word2vec} is equivalent to the gravity model, explaining its ability to learn gravity-like relationships between locations.
+Here, we demonstrate that the SGNS model and the gravity model of mobility are mathematically equivalent, explaining its ability to learn gravity-like relationships between locations.
 
 The {\it word2vec} model takes a location trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), as input.
-A location $a_t=i$ is considered to have a context location $a_{t'}=j$ that appears in the previous or subsequent $w$ locations in the trajectory, \ie  $j \in [a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}]$.
+A target location $a_t=i$ is considered to have a context location $a_{t'}=j$ that appears in the previous or subsequent $w$ locations in the trajectory, \ie  $j \in [a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}]$.
 	{\it Word2vec} learns an embedding by estimating the probability that location $i$ has context $j$:
@@
 Because computing $Z_i$ is computationally demanding, multiple approximation methods have been proposed, the most popular being negative sampling~\autocite{mikolov2013word2vec}.
-Negative sampling finds the embedding vectors by solving a binary classification task, in which the model classifies whether a given target-context location pair $(i, j)$ comes from the data or from artificially generated ``negative'' samples.
+Negative sampling finds embedding vectors by solving a binary classification task in which the model classifies whether a given target-context location pair $(i, j)$ comes from the data or from artificially generated ``negative'' samples.
 The negative pair $(i,j)$ is sampled in proportion to $P^\gamma(j)$ with parameter $\gamma \geq 0$.
@@
 \end{align}
-where we redefine the normalization constant as $Z_i=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$. (See Methods section for the full derivation).
+where we redefine the normalization constant as $Z_i=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$. (See the Methods for the full derivation).
 
-Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimial in-vectors and out-vectors such that $\bm{u}_i = \bm{v}_i$~\autocite{levy2014neural}.
+Parameter $\gamma=1$ is a choice that ensures that when the embedding dimension is sufficiently large, there exists optimial in-vectors and out-vectors such that $\bm{u}_i = \bm{v}_i$~\autocite{levy2014neural}.
 Setting $\gamma = 1$ and substituting $\bm{u}_i = \bm{v}_j$ into Eq.~\eqref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
@@
 
-Taken altogether, the {\it word2vec} model with the negative sampling predicts a flow in the same form as in the gravity model:
+Taken together, the {\it word2vec} model with the negative sampling predicts a flow in the same form as in the gravity model:
 \begin{align}
@@
 where $C$ is a positive constant.
-In other words, \emph{word2vec with the negative sampling is a gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
+In other words, \emph{word2vec with the negative sampling is equivalent to the gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
 While the gravity model generates mobility flow from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given mobility flow.
@@
 
-A key assumption in our mathematical analysis is that the embedding vectors are optimum in terms of the {\it word2vec}'s objective function.
-However, this premise is not practical because the optimization algorithm (\eg stochastic gradient descent algorithm) often finds sub-optimal embeddings.
-This has two consequences.
-First, the in- and out-vectors can be different.
-Second, {\it word2vec} learns the dot distance between location vectors, and so this distance should best capture mobility flows. 
-However, our numerical simulations show that the dot similarity between vectors is outperformed by the cosine distance as a predictor of mobility flow between scientific organizations~(Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+In practice, because we do not have unlimited amounts of data (which is also noisy) and the optimization may not find the true optimum, the idealized result may not hold. 
+Indeed, we tend to find that the in- and out-vectors tend to be different and that the cosine similarity tends to better capture real-world mobility than the dot similarity.
 This result echos other applications of word embedding, such as word analogy testing~\autocite{levy2015improving}, in which cosine distance also outperformed dot similarity.
-Given that cosine similarity is a special case of dot similarity, we speculate that the deviation in explanatory and predictive quality can be attributed to \textit{word2vec's} optimization process.
+Nevertheless, a model with dot similarity is still the second best after cosine similarity (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and the embedding distance still outperforms all alternatives we considered.
 Although finding an optimal embedding is difficult in practice, careful tuning of the optimization algorithm would close the gap between our mathematical and numerical results.

### 2021-02-23 paper/current/supp.tex
remove deprecated figure

@@
 %
-% Figure - gravity predictions based on subset or global
-%
-\begin{figure}[p!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_different_fits.pdf}
-	\caption{
-		\textbf{Little difference between gravity predictions fit on all or subsets of data.}
-		Predictions of flux between organization pairs made using embedding distance out-performs those made using geographic distance.
-		Boxplots show distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps the line $x = y$; 
-		a perfect prediction yields all points on the black line.
-		``RMSE'' is the root-mean-squared error between the actual and predicted values.
-		\textbf{a-b.} Predictions are made with parameters estimated from all pairs of organizations (as in Fig.~\ref{fig:gravity_performance}e), and showing only the subsets of predictions for organization pairs in the same country (\textbf{a}) and in different countries (\textbf{b}).
-		\textbf{c-d.} Predictions made using parameters estimated from the subset of organizations in the same country (\textbf{c}) and different country \textbf{d});
-		this is the same data as shown in Fig.~\ref{fig:gravity_performance}f and Fig.~\ref{fig:gravity_performance}h.
-	}
-	\label{fig:supp:gravity_prediction_subsets}
-\end{figure}
-
-%
 % Figure - Dot product distance

### 2021-02-23 workflow/scripts/PlotPrestigeRankCorrelation.R
fix error in plotting prestige-rank figs

@@ -33,12 +33,10 @@ opt = parse_args(OptionParser(option_list=option_list))
 
 # Read the trajectories
 corr <- read_csv(opt$input, col_types = readr::cols()) %>%
-  filter(traj == "precedence") %>%
   filter(dim == opt$dim) %>%
   filter(ws == opt$ws) %>%
   filter(ranking == opt$ranking) %>%
   tidyr::gather(key, value, rho, rho.excluded)
-
 
 plot <- corr %>%
   mutate(

### 2021-02-25 paper/rebuttal/rebuttal.tex
add asterisk
update some texts

@@
 
-The flow $\hat{T}_{ij}$ is symmetric (\ie $\hat{T}_{ij}=\hat{T}_{ji}$) becausethe skip-gram model neglects whether the context $j$ appears before or after the target $i$ in the trajectory.
+The flow $\hat{T}_{ij}$ is symmetric (\ie $\hat{T}_{ij}=\hat{T}_{ji}$) because the skip-gram model neglects whether the context $j$ appears before or after the target $i$ in the trajectory.
 If we swap $i$ and $j$ in Eq.~\ref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
@@
 The first of these baselines uses the distance between vectors in an embedding space produced through a singular-value decomposition of the underlying location co-occurrence matrix.
-The second baseline is the distance between vectors obtained through a Laplacian eigenmap embedding of the location of the matrix.
+The third baseline is the distance between vectors obtained through a Laplacian eigenmap embedding of the location of the matrix.
 
@@
 The \textit{word2vec} model  implicitly approximates this matrix-factorization procedure, and so comparison to these ``Levy'' distances can demonstrate whether the approximation of neural embeddings outperform direct-calculations.
+Furthermore, we examined the embedding with the direct optimization of gravity law.
 
@@
 Although the euclidean distance between directly-factorized vectors performs comparably, and even narrowly beats out the embedding distance under certain experimental conditions (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}); \textit{word2vec} shows the msot consistent and robust performance, as suggested by Levy \& Goldberg~\autocite{levy2014neural}.
+\todo{@dakoda please write the new result with direct optimization of gravity law}
 
@@
 
-	We find the article that geographical distance ﬁts well with the power-law decay function because power-based gravity model can be more suitable for analyzing large, complex, and scale-free spatial systems, complexity which the exponential-based gravity model is not able to capture~\autocite{chen2015distance}.
-	However, the embedding distance fits well with the exponential decay function, perhaps demonstrating that the real-world spatial complexity of mobility is encoded in the \textit{word2vec}embedding space as simpler pairwise distances, likely resulting from underlying connection we established between \textit{word2vec} and the gravity model (see section 1, above).
+	We find the article that geographical distance ﬁts well with the power-law decay function because power-based gravity model can be more suitable for analyzing large, complex, and scale-free spatial systems with long-range spatial memory, while exponential-based gravity model
+	fits well with the simple system with no spatial memory~\autocite{chen2015distance}. 
+	However, the embedding distance fits well with the exponential decay function, perhaps demonstrating that the real-world spatial complexity of mobility is encoded in the \textit{word2vec} embedding space as simpler pairwise distances, likely resulting from underlying connection we established between \textit{word2vec} and the gravity model (see section 1, above).
 

### 2021-02-25 paper/current/main.tex
add gravity model direct

@@
 The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores calculated from the underlying mobility network (Fig.~\ref{fig:supp:distancemetrics}, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurence data (Fig.~\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and , in most cases, even outperforms a direct factorization approach~\autocite{levy2014neural}), which \textit{word2vec} is meant to approximate.
+The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurence data (Fig.~\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and , in most cases, even outperforms a direct factorization approach~\autocite{levy2014neural}), which \textit{word2vec} is meant to approximate and even direct optimization of the gravity law.
 In sum, our results demonstrate that, consistently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
@@
 		\textbf{Embedding distance encodes functional distance and better predicts mobility in flights, accommodation reservations, and global scientific mobility.}
-		\textbf{a} Embedding distance (cosine distance between organization vectors, top) better explains the expected flux of passengers between U.S. airports than does geographic distance (bottom).
+		\textbf{a.} Embedding distance (cosine distance between organization vectors, top) better explains the expected flux of passengers between U.S. airports than does geographic distance (bottom).
 		The red line is the line of the best fit.
@@
 		The lightness of each hex bin indicates the frequency of organization pairs within it.
-		\textbf{b} Predictions of flux between airport pairs made using embedding distance (top) outperform those made using geographic distance (bottom).
+		\textbf{b.} Predictions of flux between airport pairs made using embedding distance (top) outperform those made using geographic distance (bottom).
 		Boxplots show the distribution of actual flux for binned values of predicted flux.

### 2021-02-25 paper/current/supp.tex
add asterisk
add gravity model direct

--- 2021-02-19 paper/current/supp.tex
@@
 In short, truncated SVD performs linear low-rank approximation of the matrix with given dimensions, $d$.
-First, we construct the co-occurrence matrix of $N$ organizations, $A_{ij}$ given by the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory. 
-Then, we apply truncated singular vector decomposition with $d=300$ on the flow matrix $A$ directly.
+First, we construct the co-occurrence matrix of $N$ organizations, $T_{ij}$ given by the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory. 
+Then, we apply truncated singular vector decomposition with $d=300$ on the flow matrix $T$ directly.
 
@@
 When used as an input to the gravity model, this distance produces better predictions than geographic distance using both the exponential (RMSE $= 0.859$, Table~\ref{supp:table:rmse_exp_table}) and power-law models (RMSE $= 0.839$, Table~\ref{supp:table:rmse_exp_table}), performing slightly better with the power-law formulation.
-\todo{@dakoda other distance measures?}
+
+\paragraph*{S6 Text}
+\label{si:text:direct}
+{\bf Direct optimization of gravity model}
+
+We also try the embedding with the direct optimization of the gravity model.
+First, we construct the gravity matrix of $N$ organizations, $T_{ij}/m_i m_j$, where $T_{ij}$ is occurrence of organizations $i$ and $j$ in the same affiliation trajectory divided by multiplication of each location's population (mean annual member of unique mobile and non-mobile author).
+
+Then, we try two approximation methods to get the embedding.
+The first method is  truncated singular vector decomposition (SVD) and the second method is a multi-dimensional scaling (MDS), which places each entity into N-dimensional space that the distance between entities preserved as well as possible.
+Usually, MDS uses the euclidean distance of original vector as a distance measure.
+
+\todo{@dakoda, please report the performace here}
 
@@
 % S6 Text
-\paragraph*{S6 Text}
+\paragraph*{S7 Text}
 \label{si:text:Laplacian}
@@
 % S7 Text
-\paragraph*{S7 Text}
+\paragraph*{S8 Text}
 \label{si:text:levy}
@@
 
-\paragraph*{S8 Text}
+\paragraph*{S9 Text}
 \label{si:text:whynueralbetter}
@@
 % S8 TEXT
-\paragraph*{S9 Text}
+\paragraph*{S10 Text}
 \label{si:text:organizations}
@@
 % S9 TEXT
-\paragraph*{S10 Text}
+\paragraph*{S11 Text}
 \label{si:text:disambiguation}
@@
 % S10 TEXT
-\paragraph*{S11 Text}
+\paragraph*{S12 Text}
 \label{si:text:network_ranking}
@@
 % S11 TEXT
-\paragraph*{S12 Text}
+\paragraph*{S13 Text}
 \label{si:text:boomerang_speculation}

### 2021-02-26 paper/current/main.tex

@@
 The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores calculated from the underlying mobility network (Fig.~\ref{fig:supp:distancemetrics}, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurence data (Fig.~\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and , in most cases, even outperforms a direct factorization approach~\autocite{levy2014neural}), which \textit{word2vec} is meant to approximate and even direct optimization of the gravity law.
-In sum, our results demonstrate that, consistently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
+The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurence matrix, Levy's symmetric \textit{word2vec}\autocite{levy2014neural}, and even direct optimization of the gravity model (Fig.~\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+In sum, our results demonstrate that, consistently and efficiently , the embedding distance better captures patterns of actual mobility than does the geographic distance.
 

### 2021-02-26 paper/current/supp.tex
update new result

--- 2021-02-23 paper/current/supp.tex
@@
 \paragraph*{S8 Text}
+\label{si:text:direct}
+{\bf Direct optimization of gravity model}
+
+We also try the embedding with the direct optimization of the gravity model.
+First, we construct the gravity matrix of $N$ organizations, $T_{ij}/m_i m_j$, where $T_{ij}$ is occurrence of organizations $i$ and $j$ in the same affiliation trajectory divided by multiplication of each location's population (mean annual member of unique mobile and non-mobile author).
+
+Then, we try two approximation methods to get the embedding.
+The first method is  truncated singular vector decomposition (SVD) and the second method is a multi-dimensional scaling (MDS), which places each entity into N-dimensional space that the distance between entities preserved as well as possible.
+Usually, MDS uses the euclidean distance of original vector as a distance measure.
+
+\todo{@dakoda, please report the performace here}
+
+\paragraph*{S9 Text}
 \label{si:text:whynueralbetter}
@@
 		Shown is the correlation between the flux and embedding distances, measured with $r^{2}$ (left), and the prediction error when using the distance as input to the gravity model of mobility.
+    The asterisk denotes the top-performing metric.
 		For prediction error, we show results based on both the exponential and power-law forms of the gravity model.

### 2021-02-26 workflow/scripts/BuildAggregateDistanceFile.R
add new distance metrics to workflow

@@ -38,6 +38,10 @@ option_list = list(
               help="Path to file containing organization euclidean distance, calculated using levy's factorization"),
   make_option(c("--levydot"), action="store", default=NA, type='character',
               help="Path to file containing organization dot product similarities, calculated using levy's factorization"),
+  make_option(c("--gravsvd"), action="store", default=NA, type='character',
+              help="Path to file containing organization direct gravity-optimized distances with SVD"),
+  make_option(c("--gravmds"), action="store", default=NA, type='character',
+              help="Path to file containing organization direct gravity-optimized distances with MDS"),
   make_option(c("-o", "--out"), action="store", default=NA, type='character',
               help="Path to save aggregated distance file")
 ) # end option_list
@@ -268,6 +272,38 @@ distance_all <- data.table::rbindlist(list(levydot1, levydot2)) %>%
 remove("levydot", "levydot1", "levydot2")
 
 
+# Gravity SVD COS
+gravsvd <- read_csv(opt$gravsvd, col_types = cols()) %>%
+  select(org1, org2, distance) %>%
+  rename(gravsvd_distance = distance)
+
+gravsvd1 <- distance_all %>%
+  inner_join(gravsvd, by = c("org1" = "org1", "org2" = "org2"))
+
+gravsvd2 <- distance_all %>%
+  inner_join(gravsvd, by = c("org2" = "org1", "org1" = "org2"))
+
+distance_all <- data.table::rbindlist(list(gravsvd1, gravsvd2)) %>%
+  distinct(org1, org2, .keep_all = TRUE)
+
+remove("gravsvd", "gravsvd1", "gravsvd2")
+
+
+# Gravity SVD COS
+gravmds <- read_csv(opt$gravmds, col_types = cols()) %>%
+  select(org1, org2, distance) %>%
+  rename(gravmds_distance = distance)
+
+gravmds1 <- distance_all %>%
+  inner_join(gravmds, by = c("org1" = "org1", "org2" = "org2"))
+
+gravmds2 <- distance_all %>%
+  inner_join(gravmds, by = c("org2" = "org1", "org1" = "org2"))
+
+distance_all <- data.table::rbindlist(list(gravmds1, gravmds2)) %>%
+  distinct(org1, org2, .keep_all = TRUE)
+
+remove("gravmds", "gravmds1", "gravmds2")
 
 #
 # ORG LOOKUP TABLES
@@ -295,6 +331,7 @@ distance_all <- distance_all %>%
[…]

### 2021-02-26 workflow/scripts/CalculatePredictedVsActual.R

@@ -32,6 +32,7 @@ agg <- readr::read_csv(opt$input, col_types = readr::cols()) %>%
          count, gravity,
          geo_distance, pprcos_distance, pprjsd_distance, emb_distance,
          dot_distance, svdcos_distance, lapcos_distance,
+         gravsvd_distance, gravmds_distance,
          levycos_distance, levyeuc_distance, levydot_distance) %>%
   rename(actual = count)
 
@@ -108,6 +109,18 @@ if (opt$distance == "geo") {
       distance = levydot_distance,
       distance.log = log(levydot_distance)
     )
+} else if (opt$distance == "gravsvd") {
+  agg <- agg %>%
+    mutate(
+      distance = gravsvd_distance,
+      distance.log = log(gravsvd_distance)
+    )
+} else if (opt$distance == "gravmds") {
+  agg <- agg %>%
+    mutate(
+      distance = gravmds_distance,
+      distance.log = log(gravmds_distance)
+    )
 }
 
 fit.power <- summary(lm(log(gravity) ~ log(distance), data = agg))
@@ -131,7 +144,9 @@ agg <- agg %>%
   select(-c(org1_size, org2_size,
             gravity, geo_distance, emb_distance,
             pprcos_distance, pprjsd_distance, dot_distance,
-            svdcos_distance, lapcos_distance))
+            svdcos_distance, lapcos_distance, levydot_distance,
+            levyeuc_distance, levycos_distance,
+            gravsvd_distance, gravmds_distance))
 
 print(head(agg))
 

### 2021-02-26 workflow/scripts/GetAggregateGravityR2.R

@@ -7,7 +7,7 @@
 # stores them all into a single file
 #
 
-NUM_REPLICATIONS = 10
+NUM_REPLICATIONS = 5
 NUM_WORKERS = 4
 
 
@@ -172,8 +172,27 @@ agg <- data.table::rbindlist(lapply(DISTANCE_FILES, function(path) {
   df10 <- get_correlations(distance_data)
   df10$metric = "levydot"
 
+
+  # Rename svdcos_distance to "distance", remove the old column
+  distance_data <- distance_data %>%
+    mutate(distance = log(gravsvd_distance)) %>%
+    select(-gravsvd_distance)
+
+  df11 <- get_correlations(distance_data)
+  df11$metric = "gravsvd"
+
+
+  # Rename svdcos_distance to "distance", remove the old column
+  distance_data <- distance_data %>%
+    mutate(distance = log(gravmds_distance)) %>%
+    select(-gravmds_distance)
+
+  df12 <- get_correlations(distance_data)
+  df12$metric = "gravmds"
+
+
   # merge the two mini data frames
-  df <- data.table::rbindlist(list(df1, df2, df3, df4, df5, df6, df7, df8, df9, df10))
+  df <- data.table::rbindlist(list(df1, df2, df3, df4, df5, df6, df7, df8, df9, df10, df11, df12))
 
   # Specity the parameters of the file, including the embedding dimensions
   # and window size

### 2021-02-26 workflow/scripts/PlotDistanceMetricPerformance.R

@@ -9,7 +9,7 @@
 
 # Plot dimensions
 FIG_WIDTH = 6
-FIG_HEIGHT = 3.5
+FIG_HEIGHT = 4.5
 
 
 library(readr)
@@ -44,7 +44,7 @@ rmse <- read_csv(opt$rmse, col_types = readr::cols()) %>%
   mutate(performance = "Root mean squared error")
 
 # The metrics to focus on for this plot
-metric_levels <- c("emb", 'levyeuc', "svdcos", "lapcos", "pprjsd", "geo")
+metric_levels <- c("emb", 'gravmds', 'levyeuc', "svdcos", "lapcos", "pprjsd", 'gravsvd', "geo")
 
 plotdata <- data.table::rbindlist(list(r2, rmse), use.names = T) %>%
   filter(dim == 300) %>%
@@ -57,10 +57,12 @@ plotdata <- data.table::rbindlist(list(r2, rmse), use.names = T) %>%
     metric = factor(metric,
                     levels = rev(metric_levels),
                     labels = rev(c("Embedding\ncosine distance",
+                               "Gravity MDS\neuc. distance",
                                "Factorized euc.\ndistance",
                                "SVD distance",
                                "Laplacian\neigenmap\ndistance",
                                "PPR JSD",
+                               "Gravity SVD\ncosine distance",
                                "Geographic\ndistance"))),
     type = factor(type,
                   levels = c("r2", "error.power", "error.exp"),
@@ -87,7 +89,7 @@ plot <- plotdata %>%
             position = position_dodge(0.75)) +
   facet_wrap(~performance) +
   scale_x_continuous(
-    limits = c(0, 1.1),
+    limits = c(0, 1.15),
     breaks = c(0, 0.25, 0.5, 0.75, 1.0)
   ) +
   scale_shape_manual(values = c(23, 24, 25)) +

### 2021-02-26 workflow/scripts/PlotGravityLawRelationship.R

@@ -76,7 +76,7 @@ if (opt$geo == "same-country") {
 dist <- dist %>%
   select(geo_distance, emb_distance, dot_distance,
          pprcos_distance, pprjsd_distance,
-         svdcos_distance, lapcos_distance,
+         svdcos_distance, lapcos_distance, gravsvd_distance, gravmds_distance,
          levycos_distance, levyeuc_distance, levydot_distance, gravity)
 
 axislabel <- "DEFAULT"
@@ -144,6 +144,18 @@ if (opt$distance == "geo") {
 
   # Provide axis label
   axislabel <- "Levy's dot distance"
+} else if (opt$distance == "gravsvd") {
+  dist <- dist %>%
+    rename(distance = gravsvd_distance)
+
+  # Provide axis label
+  axislabel <- "Gravity SVD cosine distance"
+} else if (opt$distance == "gravmds") {
+  dist <- dist %>%
+    rename(distance = gravmds_distance)
+
+  # Provide axis label
+  axislabel <- "Gravity MDS euclidean distance"
 }
 
 # Calculate the logged gravity and select only relevant columns

### 2021-02-26 paper/current/main.tex
add distance details to supp

@@
 The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores calculated from the underlying mobility network (Fig.~\ref{fig:supp:distancemetrics}, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurence matrix, Levy's symmetric \textit{word2vec}\autocite{levy2014neural}, and even direct optimization of the gravity model (Fig.~\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurence matrix, Levy's symmetric \textit{word2vec}\autocite{levy2014neural}, and even direct optimization of the gravity model (Fig.~supp\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
 In sum, our results demonstrate that, consistently and efficiently , the embedding distance better captures patterns of actual mobility than does the geographic distance.

### 2021-02-26 paper/current/supp.tex
add distance details to supp

--- 2021-02-23 paper/current/supp.tex
@@
 When used as an input to the gravity model, this distance produces better predictions than geographic distance using both the exponential (RMSE $= 0.859$, Table~\ref{supp:table:rmse_exp_table}) and power-law models (RMSE $= 0.839$, Table~\ref{supp:table:rmse_exp_table}), performing slightly better with the power-law formulation.
-\todo{@dakoda other distance measures?}
 
@@
 When used as an input to the gravity model, the Laplacian cosine distance produces marginally-better predictions than geographic distance using both the exponential (RMSE $= 0.878$, Table~\ref{supp:table:rmse_exp_table}) and power-law models (RMSE = $0.87$, Table~\ref{supp:table:rmse_power_table}), performing slightly better with the power-law formulation.
-\todo{@dakoda other distance measures?}
 
@@
 
-Finally, we also compare the \textit{word2vec} embedding distnace against a baseline of direct matrix factorization approach, using the symmetric SVD  \textit{word2vec} method~\autocite{levy2014neural}.
+We also compare the \textit{word2vec} embedding distnace against a baseline of direct matrix factorization approach, using the symmetric SVD  \textit{word2vec} method~\autocite{levy2014neural}.
 Based on idea of \textit{word2vec} is just implicit matrix factorization, Levy proposed symmetric SVD \textit{word2vec} embedding, which should directly compute the embedding that \textit{word2vec} only attempts to efficiently approximate.
@@
 
+%
+% S8 Text
 \paragraph*{S8 Text}
+\label{si:text:direct}
+{\bf Direct optimization of gravity model}
+
+Finally, we create an embedding by optimizing for the gravity law directly. 
+Specifically, we construct a gravity matrix of $N$ organizations, where each cell of the matrix is calculated as $T_{ij}/m_i m_j$, where $T_{ij}$ is co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory, and $m_i$ and $m_j$ are the organizations' populations, defined here as the mean annual member of unique mobile and non-mobile authors affiliated.
+
+We then embed the gravity matrix using two approaches: a truncated singular-vector decomposition (SVD), and with multidimensional scaling (MDS), which embeds each location in a N-dimensional space such that pairwise distances are preserved as well as possible.
+Typically, MDS uses euclidean distance to measure distance between vectors.
+
+For this result, we report results using the cosine distance between embedding vectors for the SVD embedding, and the logged euclidean distance for the MDS embedding. 
+We observe that the gravity-optimized SVD cosine distance has poor performance, more weakly correlated with actual flux than geographic distance ($R^{2} = 0.122$, Table~\ref{supp:table:r2_table}), and similarly poor prediction error when used as input to the gravity mode.
+In contrast, the cosine distance between MDS vectors has the second-highest correlation with actual flux, after only the embedding distance ($R^{2} = 0.355$, Table~\ref{supp:table:r2_table}), and third best for predicting actual flux using both the power-law version of the gravity model (RMSE = $0.795$, Table~\ref{supp:table:rmse_power_table}), though performance is much lower using the exponential form (RMSE = $0.904$, Table~\ref{supp:table:rmse_exp_table}).
+We note that the MDS embedding actually has the lowest prediction error when organizations' populations are defined as the raw frequency during prediction with the power-law model (RMSE = $0.691$, Table~\ref{supp:table:rmse_power_table});
+however, we note that the MDS distnace is defined with a population of``All'' mobile and non-mobile scholars, whereas the predictions made in Table~\ref{supp:table:rmse_power_table} use the raw frequency, which likely confounds this result.
+
+%
+% S9 Text
+\paragraph*{S9 Text}
 \label{si:text:whynueralbetter}
-{\bf Why do neural embedings outperform direct matrix factorization?}
-
-Why do neural-embedding approaches, which rely on stochastic gradient descent, outperform direct matrix factorization, especially given that \textit{word2vec} \emph{is} implicitly approximating factorization?
-An issue in the matrix factorization approach is that it is extremely sensitive to small flows between affiliations.
-The matrix factorization approach embeds affiliations $i$ and $j$ such that their dot similarity is as close as to $\log (T_{ij} / P(i) P(j))$.
-If the flow $T_{ij}$ is considerably small or zero, the dot similarity goes $-\infty$, pushing $i$ and $j$ very far from the other affiliations in the embedding space~\autocite{levy2014neural, Qui2018}.
+{\bf Why do neural embeddings outperform direct matrix factorization?}
+
+Why do neural-embedding approaches, which rely on stochastic gradient descent, outperform Levy's direct matrix factorization~\autocite{levy2014neural}, especially given that \textit{word2vec} \emph{is} implicitly approximating factorization?
+We speculate that is stems, in part, from the sensitivity of matrix factorization to small flows between locations.  
+Levy's matrix factorization embeds affiliations $i$ and $j$ such that their dot similarity is as close as possible to $\log (T_{ij} / P(i) P(j))$. 
+If the flow $T_{ij}$ is considerably small or zero, the dot similarity goes to $-\infty$, pushing $i$ and $j$ very far from other affiliations in the embedding space~\autocite{levy2014neural, Qui2018}.
 This is particularly problematic when the window size is small because most affiliation pairs would have no flow, which is indeed the case in our experiments. 
-To circumvent this problem, the previous studies~\autocite{levy2014neural, Qui2018} add a constant flow between the affiliation pairs with no flow.
-However, this changes the data to which we fit the model, and small flows still have a considerably strong impact on the embedding.
-
-Also, it is well known that SVD itself is vulnerable to outliers \autocite{xu2012robust, huber1981robust, xu1995robust, chandrasekaran2011rank, candes2011robust}.
-The stochastic gradient descent algorithm (SGD), which is employed in SGNS \textit{word2vec}, is more robust than SVD and can enhance generalization and effectiveness of {\it word2vec} model \autocite{ma2018power, smith2020generalization, zhang2019algorithmic}.
-
-%
-% S8 TEXT
-\paragraph*{S9 Text}
+To circumvent this problem, previous studies~\autocite{levy2014neural, Qui2018} added a constant flow between the affiliation pairs with no flow. 
+However, this alters the underlying data, and these small flows can still have a strong impact on the embedding.
+
+It is also well known that singular-vector decomposition (SVD) is vulnerable to outliers~\autocite{xu2012robust, huber1981robust, xu1995robust, chandrasekaran2011rank, candes2011robust}.
+The stochastic gradient descent algorithm, which is employed in SGNS \textit{word2vec}, is more robust than SVD and can enhance generalization and effectiveness of {\it word2vec} model \autocite{ma2018power, smith2020generalization, zhang2019algorithmic}.
+
+%
+% S10 TEXT
+\paragraph*{S10 Text}
 \label{si:text:organizations}
@@
 %
-% S9 TEXT
-\paragraph*{S10 Text}
+% S11 TEXT
+\paragraph*{S11 Text}
 \label{si:text:disambiguation}
@@
 %
-% S10 TEXT
-\paragraph*{S11 Text}
+% S12 TEXT
+\paragraph*{S12 Text}
 \label{si:text:network_ranking}
@@
 %
-% S11 TEXT
-\paragraph*{S12 Text}
+% S13 TEXT
+\paragraph*{S13 Text}
 \label{si:text:boomerang_speculation}
@@
 \clearpage
+
 \begin{landscape}
@@
 	\textbf{Correlation between flux and distance over metrics, experimental parameters}.
-	Each cell corresponds to the correlation (measured with $r^{2}$) between the real-world flux between scientific organizations, comparing the embedding distance against baseline metrics, and across subsets of mobility data and by definitions of organization population.
+	Each cell corresponds to the correlation (measured with $R^{2}$) between the real-world flux between scientific organizations, comparing the embedding distance against baseline metrics, and across subsets of mobility data and by definitions of organization population.
 	The asterisk denotes the top-performing distance metric by column.
-	Distance metrics are ordered from highest $r^{2}$ to lowest, based on global mobility with organization population defined using all mobile and non-mobile authors.
+	Distance metrics are ordered from highest $R^{2}$ to lowest, based on global mobility with organization population defined using all mobile and non-mobile authors.
 	``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
@@
 		``Raw freq'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
-		Embedding distance, measured as the cosine distance between embedding vectors, explains more of the flux than baselines in nearly every case, except using raw frequency population and domestic and international mobility, where direct-factorization approaches~\autocite{levy2014neural} work better.
+		Embedding distance, measured as the cosine distance between embedding vectors, explains more of the flux than baselines in nearly every case, except using raw frequency population and domestic and international mobility, where direct optimization of the gravity law works better, as well as Levy's factorization~\autocite{levy2014neural} for domestic and international only mobility.
 }
@@
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.489 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.325 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.325 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.251 \hspace{6pt}\huxbpad{6pt}} &
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity MDS euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.355 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.165 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.161 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.328 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.112 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.115 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.369 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.174 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.164 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's euclidean} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.341 \hspace{6pt}\huxbpad{6pt}} &
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's cosine} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.208 \hspace{6pt}\huxbpad{6pt}} &
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.122 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.118 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.122 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.118 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.133 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.138 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.056 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.047 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.05 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's dot} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.004 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.013 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.004 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.004 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.039 \hspace{6pt}\huxbpad{6pt}} &
@@
 
-\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\hhline{}
 \arrayrulecolor{black}
@@
 
-\end{landscape} % End r2 table page
+\end{landscape}
 
@@
 		``Raw freq'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
-		Embedding distance, measured as the cosine distance between embedding vectors, results in better predictions of mobility than baselines in nearly every case, however direct-factorization approaches~\autocite{levy2014neural} perform better for domestic and international mobility when raw frequency is used to define populations.
+		Embedding distance, measured as the cosine distance between embedding vectors, results in better predictions of mobility than baselines in nearly every case, however Levy's 's factorization~\autocite{levy2014neural} perform better in the case of international and domestic only mobility when using raw frequency populations.
 }
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's euclidean} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.803 \hspace{6pt}\huxbpad{6pt}} &
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's cosine} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.881 \hspace{6pt}\huxbpad{6pt}} &
@@
 
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity MDS euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.904 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.944 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.93 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.907 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.972 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.955 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.793 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.838 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.821 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR cosine} \hspace{6pt}\huxbpad{6pt}} &
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.933 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.939 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.923 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.92 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.946 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.927 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.853 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.865 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.847 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's dot} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.987 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.995 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.98 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.98 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.979 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.014 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.996 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.996 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.853 \hspace{6pt}\huxbpad{6pt}} &
@@
 
-\end{landscape}
+\end{landscape} % End r2 table page
 
@@
 		``Raw freq'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
-		Embedding distance, measured as the cosine distance between embedding vectors, results in better predictions for global mobility with ``All'; and ``Mobile only'' definitions of population, though the direct-factorization approach~\autocite{levy2014neural} perform better for in other cases.
+		Embedding distance, measured as the cosine distance between embedding vectors, results in better predictions for global mobility with ``All'; and ``Mobile only'' definitions of population, though direvt gravity-law opimization with MDS performs better when using raw frequencies to measure organization population, and Levy's factorization~\autocite{levy2014neural} perform better here with domestic and international only mobility.
 }
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's euclidean} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.78 \hspace{6pt}\huxbpad{6pt}} &
@@
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.822 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.703 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.703 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.711 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.691 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity MDS euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.795 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.91 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.898 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.808 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.957 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.939 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.691 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.802 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.79 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's cosine} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.927 \hspace{6pt}\huxbpad{6pt}} &
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.965 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.965 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.95 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.955 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.958 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.941 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.873 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.883 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.866 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's dot} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.99 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.998 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.983 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.983 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.977 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.015 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.997 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.997 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.845 \hspace{6pt}\huxbpad{6pt}} &
@@
 		Cosine distance between embedding vectors generated with \textit{word2vec} explains more of the flux, and better predicts flux when used in the gravity model of mobility than geographic distance and other baselines.
-		Shown is the correlation between the flux and embedding distances, measured with $r^{2}$ (left), and the prediction error when using the distance as input to the gravity model of mobility.
+		Shown is the correlation between the flux and embedding distances, measured with $R^{2}$ (left), and the prediction error when using the distance as input to the gravity model of mobility.
+    The asterisk denotes the top-performing metric.
 		For prediction error, we show results based on both the exponential and power-law forms of the gravity model.
@@
 		In all cases, organization population is defined as the mean annualized number of unique mobile and non-mobile authors, and flux is calculated for all global mobility.
-		Baselines include the top-performing distance metrics calculated between vectors obtained by personalized-page rank (PPR), singular value decomposition (SVD), laplacian eigenmap, and direct-factorization~\autocite{levy2014neural} approaches, as well as the geographic distance between organizations.
+		Baselines include the top-performing distance metrics calculated between vectors obtained by personalized-page rank (PPR), singular value decomposition (SVD), laplacian eigenmap, direct-factorization following Levy's approach~\autocite{levy2014neural}, and direct optimization of the gravity model using SVD and multidimensional scaling (MDS), as well as the geographic distance between organizations.
 		Embedding distance better explains and predicts flux than any other baseline, though there is some variation by experimental parameters (Table~\ref{supp:table:r2_table}, Table~\ref{supp:table:rmse_exp_table}, and Table~\ref{supp:table:rmse_power_table}).

### 2021-02-26 workflow/scripts/CalculatePredictedVsActual.R
mior changes to figures

@@ -112,13 +112,13 @@ if (opt$distance == "geo") {
 } else if (opt$distance == "gravsvd") {
   agg <- agg %>%
     mutate(
-      distance = gravsvd_distance,
+      distance = log(gravsvd_distance),
       distance.log = log(gravsvd_distance)
     )
 } else if (opt$distance == "gravmds") {
   agg <- agg %>%
     mutate(
-      distance = gravmds_distance,
+      distance = log(gravmds_distance),
       distance.log = log(gravmds_distance)
     )
 }

### 2021-02-26 workflow/scripts/PlotDistanceMetricPerformance.R

@@ -58,7 +58,7 @@ plotdata <- data.table::rbindlist(list(r2, rmse), use.names = T) %>%
                     levels = rev(metric_levels),
                     labels = rev(c("Embedding\ncosine distance",
                                "Gravity MDS\neuc. distance",
-                               "Factorized euc.\ndistance",
+                               "Levy's euc.\ndistance",
                                "SVD distance",
                                "Laplacian\neigenmap\ndistance",
                                "PPR JSD",

### 2021-02-26 paper/rebuttal/rebuttal.tex
upate rebuttal letter
update rebuttal letter

@@
 The \textit{word2vec} model  implicitly approximates this matrix-factorization procedure, and so comparison to these ``Levy'' distances can demonstrate whether the approximation of neural embeddings outperform direct-calculations.
-Furthermore, we examined the embedding with the direct optimization of gravity law.
+Furthermore, we computed an embedding that attempts to directly-optimize for a gravity-law relationship between relations, one created using singular-vector decomposition (SVD) and another with multidimensional scaling (MDS).
 
@@
 		Shown is the correlation between the flux and embedding distances, measured with $R^{2}$ (left), and the prediction error when using the distance as input to the gravity model of mobility.
+    The asterisk denotes the top-performing metric.
 		For prediction error, we show results based on both the exponential and power-law forms of the gravity model.
 		All embedding-based methods use dimensions of 300.
-		Embedding distance is obtained from neural embeddings learned with window size of 1 and $\gamma = 1$.
-		The metric with the highest correlation and lowest prediction error are marked with an asterisk. 
+		Here, embedding distance is obtained from neural embeddings learned with window size of 1 and $\gamma = 1$.
 		In all cases, organization population is defined as the mean annualized number of unique mobile and non-mobile authors, and flux is calculated for all global mobility.
-		Baselines include the top-performing distance metrics calculated between vectors obtained by personalized-page rank (PPR), singular value decomposition (SVD), laplacian eigenmap, and direct-factorization~\autocite{levy2014neural} approaches, as well as the geographic distance between organizations.
+		Baselines include the top-performing distance metrics calculated between vectors obtained by personalized-page rank (PPR), singular value decomposition (SVD), laplacian eigenmap, direct-factorization following Levy's approach~\autocite{levy2014neural}, and direct optimization of the gravity model using SVD and multidimensional scaling (MDS), as well as the geographic distance between organizations.
 		Embedding distance better explains and predicts flux than any other baseline, though there is some variation by experimental parameters (Table~\ref{supp:table:r2_table}, Table~\ref{supp:table:rmse_exp_table}, and Table~\ref{supp:table:rmse_power_table}).
@@
 Although the euclidean distance between directly-factorized vectors performs comparably, and even narrowly beats out the embedding distance under certain experimental conditions (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}); \textit{word2vec} shows the msot consistent and robust performance, as suggested by Levy \& Goldberg~\autocite{levy2014neural}.
-\todo{@dakoda please write the new result with direct optimization of gravity law}
+Directly-optimizing the gravity model results in comparable performance to Levy's factorization approach, narroly beating out both in prediction error for certain definitions of organization population.
+Still, the embedding distance, with its stochastic optimization algortihm reliably outperforms these directly-optimized  baselines.
 
@@
 	\textbf{Correlation between flux and distance over metrics, experimental parameters}.
-			Each cell corresponds to the correlation (measured with $r^{2}$) between the real-world flux between scientific organizations, comparing the embedding distance against baseline metrics, and across subsets of mobility data and by definitions of organization population.
+	Each cell corresponds to the correlation (measured with $R^{2}$) between the real-world flux between scientific organizations, comparing the embedding distance against baseline metrics, and across subsets of mobility data and by definitions of organization population.
 	The asterisk denotes the top-performing distance metric by column.
-			Distance metrics are ordered from highest $r^{2}$ to lowest, based on global mobility with organization population defined using all mobile and non-mobile authors.
+	Distance metrics are ordered from highest $R^{2}$ to lowest, based on global mobility with organization population defined using all mobile and non-mobile authors.
 	``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
@@
 		``Raw freq'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
-			Embedding distance, measured as the cosine distance between embedding vectors, explains more of the flux than baselines in nearly every case, except using raw frequency population and domestic and international mobility, where direct-factorization approaches~\autocite{levy2014neural} work better.
+		Embedding distance, measured as the cosine distance between embedding vectors, explains more of the flux than baselines in nearly every case, except using raw frequency population and domestic and international mobility, where direct optimization of the gravity law works better, as well as Levy's factorization~\autocite{levy2014neural} for domestic and international only mobility.
 }
@@
 \begin{threeparttable}
+\small
  \setlength{\tabcolsep}{0pt}
 \begin{tabular}{l l l l l l l l l l}
-
-					\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-					\arrayrulecolor{black}
 
@@
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.489 \hspace{6pt}\huxbpad{6pt}} &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.325 \hspace{6pt}\huxbpad{6pt}}                                                &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.325 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.251 \hspace{6pt}\huxbpad{6pt}} &
@@
 
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity MDS euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.355 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.165 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.161 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.328 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.112 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.115 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.369 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.174 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.164 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's euclidean} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.341 \hspace{6pt}\huxbpad{6pt}} &
@@
 
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized cosine} \hspace{6pt}\huxbpad{6pt}}    &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's cosine} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.208 \hspace{6pt}\huxbpad{6pt}} &
@@
 
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized dot} \hspace{6pt}\huxbpad{6pt}}       &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.122 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.118 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.122 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.118 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.133 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.138 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.056 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.047 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.05 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's dot} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.004 \hspace{6pt}\huxbpad{6pt}} &
@@
 		``Raw freq'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
-			Embedding distance, measured as the cosine distance between embedding vectors, results in better predictions of mobility than baselines in nearly every case, however direct-factorization approaches~\autocite{levy2014neural} perform better for domestic and international mobility when raw frequency is used to define populations.
+		Embedding distance, measured as the cosine distance between embedding vectors, results in better predictions of mobility than baselines in nearly every case, however Levy's 's factorization~\autocite{levy2014neural} perform better in the case of international and domestic only mobility when using raw frequency populations.
 }
@@
 \begin{threeparttable}
+\small
  \setlength{\tabcolsep}{0pt}
@@
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding cosine} \hspace{6pt}\huxbpad{6pt}} &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.713 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.76 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.737 \hspace{6pt}\huxbpad{6pt}}                                              &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.702 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.749 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.713 \hspace{6pt}\huxbpad{6pt}}                                              &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.715 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.764 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.748 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-					\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-					\arrayrulecolor{black}
-
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized euclidean} \hspace{6pt}\huxbpad{6pt}} &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.803 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.791 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.771 \hspace{6pt}\huxbpad{6pt}}                                               &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.743 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.784 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.76 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.73 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.784 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.749 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.714 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.762 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.745 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.78 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.776 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.755 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.847 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.822 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.703 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.711 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.691 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity MDS euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.795 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.91 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.898 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.808 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.957 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.939 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.691 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.802 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.79 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.822 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.831 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.864 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.879 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.863 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.783 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.809 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.795 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.839 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.785 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.761 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.89 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.834 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.81 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.792 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.752 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.728 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Laplacian cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.87 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.837 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.801 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.937 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.919 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.886 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.804 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.772 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.735 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Geographic} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}} &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.867 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}}                                               &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.725 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.726 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.705 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-					\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-					\arrayrulecolor{black}
-
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding dot} \hspace{6pt}\huxbpad{6pt}}        &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.803 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.825 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.811 \hspace{6pt}\huxbpad{6pt}}                                               &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.851 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.87 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.854 \hspace{6pt}\huxbpad{6pt}}                                               &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.769 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.798 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.784 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-					\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-					\arrayrulecolor{black}
-
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{SVD cosine} \hspace{6pt}\huxbpad{6pt}}           &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.859 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.835 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.815 \hspace{6pt}\huxbpad{6pt}}                                               &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.905 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.879 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.888 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.933 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.906 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.852 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}} &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.841 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.82 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.82 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.812 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.792 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-					\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-					\arrayrulecolor{black}
-
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Laplacian cosine} \hspace{6pt}\huxbpad{6pt}}     &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.878 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.891 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.867 \hspace{6pt}\huxbpad{6pt}}                                               &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.894 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.933 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.904 \hspace{6pt}\huxbpad{6pt}}                                               &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.835 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.837 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.815 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-					\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-					\arrayrulecolor{black}
-
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized cosine} \hspace{6pt}\huxbpad{6pt}}    &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.881 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.875 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.86 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.898 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.882 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.866 \hspace{6pt}\huxbpad{6pt}}                                               &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.858 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.841 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.851 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
@@
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR JSD} \hspace{6pt}\huxbpad{6pt}} &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.888 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.847 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.835 \hspace{6pt}\huxbpad{6pt}}                                               &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.889 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.85 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.838 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.871 \hspace{6pt}\huxbpad{6pt}} &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.828 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.814 \hspace{6pt}\huxbpad{6pt}}                                               &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.834 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.819 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.865 \hspace{6pt}\huxbpad{6pt}} &
@@
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.92 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.927 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.91 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.885 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.918 \hspace{6pt}\huxbpad{6pt}} &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.925 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.908 \hspace{6pt}\huxbpad{6pt}}                                               &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.884 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.916 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.894 \hspace{6pt}\huxbpad{6pt}}                                               &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.896 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.812 \hspace{6pt}\huxbpad{6pt}} &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.814 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.796 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-					\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-					\arrayrulecolor{black}
-
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Geographic} \hspace{6pt}\huxbpad{6pt}}           &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.929 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.951 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.928 \hspace{6pt}\huxbpad{6pt}}                                               &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.973 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.002 \hspace{6pt}\huxbpad{6pt}}                                                 &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.815 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.797 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.927 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.926 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.911 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.93 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.924 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.909 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.861 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.872 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.854 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.965 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.965 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.95 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.955 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.958 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.941 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.873 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.883 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.866 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.99 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.998 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.983 \hspace{6pt}\huxbpad{6pt}} &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.856 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.875 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.853 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-					\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-					\arrayrulecolor{black}
-
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized dot} \hspace{6pt}\huxbpad{6pt}}       &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.987 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.995 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.98 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.979 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.014 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.996 \hspace{6pt}\huxbpad{6pt}}                                               &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.853 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.867 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.849 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.977 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.015 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.997 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.845 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.86 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.841 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
@@
 		``Raw freq'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
-			Embedding distance, measured as the cosine distance between embedding vectors, results in better predictions for global mobility with ``All'; and ``Mobile only'' definitions of population, though the direct-factorization approach~\autocite{levy2014neural} perform better for in other cases.
+		Embedding distance, measured as the cosine distance between embedding vectors, results in better predictions for global mobility with ``All'; and ``Mobile only'' definitions of population, though direvt gravity-law opimization with MDS performs better when using raw frequencies to measure organization population, and Levy's factorization~\autocite{levy2014neural} perform better here with domestic and international only mobility.
 }
@@
 
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's euclidean} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.78 \hspace{6pt}\huxbpad{6pt}} &
@@
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.822 \hspace{6pt}\huxbpad{6pt}} &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.703 \hspace{6pt}\huxbpad{6pt}}                                                &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.703 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.711 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.691 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity MDS euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.795 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.91 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.898 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.808 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.957 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.939 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.691 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.802 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.79 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
@@
 
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized cosine} \hspace{6pt}\huxbpad{6pt}}    &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's cosine} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.927 \hspace{6pt}\huxbpad{6pt}} &
@@
 
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Factorized dot} \hspace{6pt}\huxbpad{6pt}}       &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.965 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.965 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.95 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.955 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.958 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.941 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.873 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.883 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.866 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's dot} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.99 \hspace{6pt}\huxbpad{6pt}} &

### 2021-02-26 notebooks/metric_performance_tables.rmd

---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

```{r}
library(tidyverse)
library(readr)
library(huxtable)
rmse <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Stat/aggregate_rmse.csv")
```

```{r}
r2 <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Stat/aggregate_r2.csv")

metric_levels <- c("emb", "levyeuc", "dot", "pprjsd", "svdcos", "levycos", "geo",
                   "lapcos", "pprcos", "levydot")

metric_labels <- c("Embedding cosine", "Factorized euclidean", "Embedding dot", "PPR JSD", 
                   "SVD cosine", "Factorized cosine", "Geographic", "Laplacian cosine", "PPR cosine", "Factorized dot")

r2.tab <- r2 %>%
  filter(traj == "precedence") %>%
  filter(dim == 300) %>%
  filter(ws == 1) %>%
  filter(gamma == 1.0) %>%
  select(metric, case, sizetype, r2) %>%
  arrange(desc(r2)) %>%
  mutate(
    case = factor(case, levels = c("global", "same-country", "diff-country")),
    sizetype = factor(sizetype, levels = c("all", "mobile", "freq"))
  ) %>%
  arrange(case, sizetype, desc(r2)) %>%
  group_by(case, sizetype) %>%
  mutate(
    r2 = ifelse(max(r2) == r2, paste0("*", round(r2, 3)), as.character(round(r2, 3)))
  ) %>%
  group_by(metric, case, sizetype) %>%
  ungroup() %>%
  pivot_wider(names_from = c("case", "sizetype"), values_from = "r2") %>%
  #select(-id) %>%
  mutate(
    metric = factor(metric, metric_levels, metric_labels)
  ) %>%
  rename(" " = metric)

r2.hux <- as_hux(r2.tab) %>%
  set_contents(1, 2:10, rep(c("Global", "Domestic", "International"), 3)) %>%
  insert_row("", "All", "", "", "Mobile only", "", "", "Raw freq", "", "", after = 0) %>% 
  merge_cells(1, 2:4) %>% 
  merge_cells(1, 5:7) %>% 
  merge_cells(1, 8:10) %>%
  set_tb_padding(1, everywhere, 0) %>% 
  set_bold(1, everywhere) %>%
  map_align(by_cols(c("left", rep("right", 9)))) %>%
  set_align(1, everywhere, "center") %>% 
  #map_align(row = 1, by_cols(rep("center", 10))) %>%
  set_header_rows(1:2, TRUE) %>% 
  set_header_cols(1, TRUE) %>% 
  style_headers(bold = TRUE) %>%
  set_right_border(1:12, 1, value = 0.5) %>%
  set_right_border(1:12, 4, value = 0.5) %>%
  set_right_border(1:12, 7, value = 0.5) %>%
  set_bottom_border(2, 1:10, value = 0.5)

r2.hux %>%
  print_latex()
```

```{r}
rmse <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Stat/aggregate_rmse.csv")

metric_levels <- c("emb", "levyeuc", "dot", "pprjsd", "svdcos", "levycos", "geo",
                   "lapcos", "pprcos", "levydot")

metric_labels <- c("Embedding cosine", "Factorized euclidean", "Embedding dot", "PPR JSD", 
                   "SVD cosine", "Factorized cosine", "Geographic", "Laplacian cosine", "PPR cosine", "Factorized dot")

rmse.tab <- rmse %>%
  filter(dim == 300) %>%
  filter(ws == 1) %>%
  filter(gamma == 1.0) %>%
  rename(rmse = error.exp) %>%
  #gather(model, rmse, error.exp, error.power) %>%
  select(metric, case, sizetype, rmse) %>%
  arrange(rmse) %>%
  mutate(
    case = factor(case, levels = c("global", "same", "different")),
    sizetype = factor(sizetype, levels = c("all", "mobile", "freq"))
  ) %>%
  arrange(case, sizetype, rmse) %>%
  group_by(case, sizetype) %>%
  mutate(
    rmse = ifelse(min(rmse) == rmse, paste0("*", round(rmse, 3)), as.character(round(rmse, 3)))
  ) %>%
  group_by(metric, case, sizetype) %>%
  ungroup() %>%
  pivot_wider(names_from = c("case", "sizetype"), values_from = "rmse") %>%
  #select(-id) %>%
  mutate(
    metric = factor(metric, metric_levels, metric_labels)
  ) %>%
  rename(" " = metric)

rmse.hux <- as_hux(rmse.tab) %>%
  set_contents(1, 2:10, rep(c("Global", "Domestic", "International"), 3)) %>%
  insert_row("", "All", "", "", "Mobile only", "", "", "Raw freq", "", "", after = 0) %>% 
  merge_cells(1, 2:4) %>% 
  merge_cells(1, 5:7) %>% 
  merge_cells(1, 8:10) %>%
  set_tb_padding(1, everywhere, 0) %>% 
  set_bold(1, everywhere) %>%
  map_align(by_cols(c("left", rep("right", 9)))) %>%
  set_align(1, everywhere, "center") %>% 
  #map_align(row = 1, by_cols(rep("center", 10))) %>%
  set_header_rows(1:2, TRUE) %>% 
  set_header_cols(1, TRUE) %>% 
  style_headers(bold = TRUE) %>%
  set_right_border(1:12, 1, value = 0.5) %>%
  set_right_border(1:12, 4, value = 0.5) %>%
  set_right_border(1:12, 7, value = 0.5) %>%
  set_bottom_border(2, 1:10, value = 0.5)

rmse.hux %>%
  print_latex()

```

Now the same table, with the power-law model
```{r}
rmse.tab <- rmse %>%
  filter(dim == 300) %>%
  filter(ws == 1) %>%
  filter(gamma == 1.0) %>%
  rename(rmse = error.power) %>%
  #gather(model, rmse, error.exp, error.power) %>%
  select(metric, case, sizetype, rmse) %>%
  arrange(rmse) %>%
  mutate(
    case = factor(case, levels = c("global", "same", "different")),
    sizetype = factor(sizetype, levels = c("all", "mobile", "freq"))
  ) %>%
  arrange(case, sizetype, rmse) %>%
  group_by(case, sizetype) %>%
  mutate(
    rmse = ifelse(min(rmse) == rmse, paste0("*", round(rmse, 3)), as.character(round(rmse, 3)))
  ) %>%
  group_by(metric, case, sizetype) %>%
  ungroup() %>%
  pivot_wider(names_from = c("case", "sizetype"), values_from = "rmse") %>%
  #select(-id) %>%
  mutate(
    metric = factor(metric, metric_levels, metric_labels)
  ) %>%
  rename(" " = metric)

rmse.hux <- as_hux(rmse.tab) %>%
  set_contents(1, 2:10, rep(c("Global", "Domestic", "International"), 3)) %>%
  insert_row("", "All", "", "", "Mobile only", "", "", "Raw freq", "", "", after = 0) %>% 
  merge_cells(1, 2:4) %>% 
  merge_cells(1, 5:7) %>% 
  merge_cells(1, 8:10) %>%
  set_tb_padding(1, everywhere, 0) %>% 
  set_bold(1, everywhere) %>%
  map_align(by_cols(c("left", rep("right", 9)))) %>%
  set_align(1, everywhere, "center") %>% 
  #map_align(row = 1, by_cols(rep("center", 10))) %>%
  set_header_rows(1:2, TRUE) %>% 
  set_header_cols(1, TRUE) %>% 
  style_headers(bold = TRUE) %>%
  set_right_border(1:12, 1, value = 0.5) %>%
  set_right_border(1:12, 4, value = 0.5) %>%
  set_right_border(1:12, 7, value = 0.5) %>%
  set_bottom_border(2, 1:10, value = 0.5)

rmse.hux %>%
  print_latex()
```

### 2021-02-26 paper/current/supp.tex

@@
 
-\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-\arrayrulecolor{black}
-
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}c!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{0pt + 1em}\centering \hspace{6pt} \textbf{} \hspace{6pt}\huxbpad{0pt}} &
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.122 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.118 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.122 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.122 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.118 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.133 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.138 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.138 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.056 \hspace{6pt}\huxbpad{6pt}} &
@@
 
-\hhline{}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's dot} \hspace{6pt}\huxbpad{6pt}} &
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's dot} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.004 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.013 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.004 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.004 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.039 \hspace{6pt}\huxbpad{6pt}} &
@@
 
-\hhline{}
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
 \arrayrulecolor{black}
@@
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding cosine} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.713 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.76 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.737 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.702 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.749 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.713 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.715 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.764 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.748 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.743 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.784 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.76 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.73 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.784 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.749 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.714 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.762 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.745 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
@@
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's euclidean} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.803 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.791 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.771 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.78 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.776 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.755 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.847 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.822 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.703 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.711 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.691 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity MDS euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.795 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.91 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.898 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.808 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.957 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.939 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.691 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.802 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.79 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.822 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.831 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.864 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.879 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.863 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.783 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.809 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.795 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.839 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.785 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.761 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.89 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.834 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.81 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.792 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.752 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.728 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Laplacian cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.87 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.837 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.801 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.937 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.919 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.886 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.804 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.772 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.735 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Geographic} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.867 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.725 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.726 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.705 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding dot} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.803 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.825 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.811 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.851 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.87 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.854 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.769 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.798 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.784 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.859 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.835 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.815 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.905 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.879 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.888 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.933 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.906 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.852 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.841 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.82 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.82 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.812 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.792 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Laplacian cosine} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.878 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.891 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.867 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.894 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.933 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.904 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.835 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.837 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.815 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's cosine} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.881 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.875 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.86 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.898 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.882 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.866 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.858 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.841 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.851 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
@@
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR JSD} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.888 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.847 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.835 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.889 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.85 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.838 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.871 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.828 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.814 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.834 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.819 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.865 \hspace{6pt}\huxbpad{6pt}} &
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity MDS euclidean} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.904 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.944 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.93 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.907 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.972 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.955 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.793 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.838 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.821 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-\arrayrulecolor{black}
-
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.92 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.927 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.91 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.885 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.918 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.925 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.908 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.884 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.916 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.894 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.896 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.812 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.814 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.796 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Geographic} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.929 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.951 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.928 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.973 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.002 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.815 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.797 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.927 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.926 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.911 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.93 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.924 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.909 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.861 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.872 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.854 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.965 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.965 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.95 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.955 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.958 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.941 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.873 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.883 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.866 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.99 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.998 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.983 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.856 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.875 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.853 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.933 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.939 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.923 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.92 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.946 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.927 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.853 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.865 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.847 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's dot} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.987 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.995 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.98 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.979 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.014 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.996 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.853 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.867 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.849 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{}
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.977 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.015 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.997 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.845 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.86 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.841 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
 \arrayrulecolor{black}
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.965 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.965 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.95 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.95 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.955 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.958 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.941 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.941 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.873 \hspace{6pt}\huxbpad{6pt}} &
@@
 
-\hhline{}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's dot} \hspace{6pt}\huxbpad{6pt}} &
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's dot} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.99 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.998 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.983 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.983 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.977 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.015 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.997 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.997 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.845 \hspace{6pt}\huxbpad{6pt}} &

### 2021-03-02 paper/rebuttal/rebuttal.tex
make letter one page

@@
 \usepackage{hyperref}
+\usepackage{romannum}
 
@@
 \bigskip
-\noindent Dear Dr. Sutherland and Referees, \\
+\thispagestyle{empty}
+\vspace{-0.4cm}
+\noindent Dear Dr. Sutherland and Referees,\\
+\vspace{-0.1cm}
 
@@
 While reflecting on these comments and our manuscript, we have made a theoretical breakthrough that addresses the primary issues;
-namely, we have discovered a mathematical connection between the \textit{word2vec} (skip-gram) model and the gravity model.
-Furthermore, our subsequent experiments show that our approach's performance is robust, exceeding other baselines.
+namely, we have discovered a mathematical equivalence between the \textit{word2vec} (skip-gram) model and the gravity model.
+Furthermore, our subsequent experiments show that our approach's performance is robust, exceeding many other baselines.
 Therefore, with these changes, we are confident that our paper is significantly stronger, and its contribution more wide-reaching and impactful.
@@
 We have developed the mathematical and theoretical basis of our approach for embedding mobility, and made additional updates to our experiments and manuscript, addressing the three main issues raised by referees:
-
+\vspace{-0.3cm}
 \begin{enumerate}
@@
 \end{enumerate}
-
+\vspace{-0.3cm}
 Addressing the first point, we have identified an underlying mathematical equivalence between the Gravity Model of Mobility and the neural embedding technique \textit{word2vec}.
@@
 
-For the second point, we have also conducted experiments comparing the performance of neural embedding to an embedding derived by a singular value decomposition of the mobility network, and of a Laplacian eigenmap embedding.
-Additionally, we compare \textit{word2vec} model to another matrix factorization approach, which \textit{word2vec} approximates.
-We find that the embedding distance from \textit{word2vec} outperforms all baselines in explaining and predicting real-world mobility.
+For the second point, we have also conducted experiments comparing the performance of neural embedding to (\romannum{1}) a singular value decomposition of the mobility network,  (\romannum{2}) a Laplacian eigenmap embedding  (\romannum{3}) a \textit{word2vec} model with matrix factorization,  and  (\romannum{4}) a direct optimization according to the gravity law.
+We find that the embedding distance from \textit{word2vec} outperforms all baselines, even the direct optimization of gravity law with the multidimensional scaling, in explaining and predicting real-world mobility.
 
@@
 
+\pagenumbering{arabic}
 \clearpage

### 2021-03-02 paper/rebuttal/rebuttal.tex
make letter one page
replace bm with vect command

@@
 \usepackage{framed}
+\newcommand{\vect}[1]{\boldsymbol{#1}}
 \definecolor{shadecolor}{RGB}{210, 210, 210}
@@
 \def\tnull{{\text{null}}}
-\def\vec#1{{\bm #1}}
+\def\vec#1{{\vect #1}}
 \def\mat#1{\mathbf{#1}}
@@
 \noindent Dear Dr. Sutherland and Referees,\\
-\vspace{-0.1cm}
+\vspace{-0.25cm}
 
@@
 \label{sec:theory}
-Why does \textit{word2vec} with the skip-gram with negative sampling model (SGNS) work so well to model human mobility?
+Why does \textit{word2vec} with the skip-gram with negative sampling model (SGNS) work so well to model mobility?
 Here, we demonstrate that the SGNS model and the gravity model of mobility are mathematically equivalent.
@@
 \begin{equation}
-	p(j \given i) = \frac{\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:cond_prob_w2v}
+	p(j \given i) = \frac{\exp(\vect{u}_j \cdot \vect{v}_{i})}{Z_i}, \label{eq:cond_prob_w2v}
 \end{equation}
-where $\bm{v}$ and $\bm{u}$ are the ``in-vector'' and ``out-vector'', respectively,  $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
+where $\vect{v}$ and $\vect{u}$ are the ``in-vector'' and ``out-vector'', respectively,  $Z_i=\sum_{j' \in \mathcal{A}} \exp(\vect{u}_{j'} \cdot \vect{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
 In general, calculating $Z_i$ is computationally expensive and there are two common approximation:
@@
 \subsection{An implicit bias in the negative sampling}
-Although negative sampling is the most common approximation, it is known that it is a biased estimator~\autocite{Chia2010,Dyer2014} that optimizes an objective function different from {\it word2vec}.
+Although negative sampling is the most common approximation, it is a biased estimator~\autocite{Chia2010,Dyer2014} that optimizes a different objective function.
 
@@
 A target-context word pair $(i,j)$ is sampled from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$ are sampled from a noise distribution $p_0(\ell)=P^\gamma(\ell)$.
-($P(j)$ is the fraction of $j$ in the data, and $\gamma>0$ is a parameter).
+($P(j)$ is the fraction of $j$ in the data, and $\gamma>0$ is a hyper-parameter).
 Then, given a target-context word pair $(i,j)$, the model predicts whether it is a positive or negative sample using a sigmoid function:
@@
 	\label{eq:sigmoid}
-	\frac{1}{1 + \exp\left( - \bm{u}_j \cdot \bm{v}_i \right)}.
+	\frac{1}{1 + \exp\left( - \vect{u}_j \cdot \vect{v}_i \right)}.
 \end{align}
@@
 So, the model with the negative sampling optimizes $\tilde f(x)$, not $f(x)$.
-In case of the {\it word2vec}, the instance is the dot similarity $x=\bm{u}_i \cdot \bm{v}_j$,  $f(x)=\exp(x)$, and $p_0(j)=P^\gamma(j)$, and the SGNS word2vec actually optimize the following conditional probability:
+In case of the {\it word2vec}, the instance is the dot similarity $x=\vect{u}_i \cdot \vect{v}_j$,  $f(x)=\exp(x)$, and $p_0(j)=P^\gamma(j)$, and the SGNS word2vec actually optimize the following conditional probability:
 \begin{align}
-	P\left(j \given i \right):= \frac{P^\gamma (j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
+	P\left(j \given i \right):= \frac{P^\gamma (j)\exp(\vect{u}_j \cdot \vect{v}_{i})}{Z_i},
 	\label{eq:real_cond}
 \end{align}
-where $Z_i=\sum_{j' \in \mathcal{A}} P^\gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
+where $Z_i=\sum_{j' \in \mathcal{A}} P^\gamma (j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})$.
 
@@
 \begin{align}
-	\hat{T}_{ij}= P(i) P(j\given i) = \frac{P(i)P^\gamma (j)\exp(\bm{v}_j \cdot \bm{v}_{i})}{Z_i}. \label{eq:prob_w2v_ng0}
+	\hat{T}_{ij}= P(i) P(j\given i) = \frac{P(i)P^\gamma (j)\exp(\vect{u}_j \cdot \vect{v}_{i})}{Z_i}. \label{eq:prob_w2v_ng0}
 \end{align}
-where we have redefined $Z_i=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
-
-Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimial in-vectors and out-vectors such that $\bm{u}_i = \bm{v}_i$ \autocite{levy2014neural}.
-Setting $\gamma = 1$ and substituting $\bm{u}_i = \bm{v}_j$ into Eq.~\ref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
+where we have redefined $Z_i=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})$.
+
+Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimial in-vectors and out-vectors such that $\vect{u}_i = \vect{v}_i$ \autocite{levy2014neural}.
+Setting $\gamma = 1$ and substituting $\vect{u}_i = \vect{v}_j$ into Eq.~\ref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
 \begin{align}
-	\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)P(j)\exp(\bm{v}_j \cdot \bm{v}_{i})}{Z_i}. \label{eq:flow_w2v_ng1}
+	\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)P(j)\exp(\vect{v}_j \cdot \vect{v}_{i})}{Z_i}. \label{eq:flow_w2v_ng1}
 \end{align}
@@
 \begin{align}
-	\hat{T_{ij}}=  C P(i) P(j)  \exp(\bm{v}_j \cdot \bm{v}_{i}), \label{eq:flow_w2v_ng0}
+	\hat{T_{ij}}=  C P(i) P(j)  \exp(\vect{v}_j \cdot \vect{v}_{i}), \label{eq:flow_w2v_ng0}
 \end{align}

### 2021-03-02 paper/rebuttal/rebuttal.tex
fixing math error

@@
 	\label{eq:sigmoid}
-	\frac{1}{1 + \exp\left( - \vect{u}_j \cdot \vect{v}_i \right)}.
+	 p(positive|j,i) = \frac{1}{1 + f(x)^{-1}}
 \end{align}
+where $x=\vect{u}_i \cdot \vect{v}_j$,  $f(x)=\exp(x)$.
 
@@
 	\label{eq:sigmoid2}
-	\frac{1}{1 + \exp\left( -f(x) + \log p_0(x) \right)}.
+	p(positive|j,i) = \frac{1}{1 + p_0(x)f(x)^{-1}}.
 \end{align}
 
-Rewriting the sigmoid function for the negative sampling (Eq.~\ref{eq:sigmoid}) where the bias-corrected sigmoid function yields
+Define $\tilde f(x) = f(x) p_0(x)$ and rewriting the sigmoid function for the negative sampling (Eq.~\ref{eq:sigmoid}) in terms of bias-corrected sigmoid function yields
 \begin{align}
 	\label{eq:sigmoid3}
-	\frac{1}{1 + \exp\left[ - \tilde f(x) + \log p_0(x)  \right]},
+	\frac{1}{1 + p_0(x) \tilde f(x)^{-1}}
 \end{align}
-where we have defined
-\begin{align}
-	\label{eq:unnormalized}
-	\tilde f(x) = f(x) p_0(x).
-\end{align}
+
 So, the model with the negative sampling optimizes $\tilde f(x)$, not $f(x)$.

### 2021-03-02 paper/rebuttal/rebuttal.tex
add notes
update section 2

@@
 	\label{eq:sigmoid}
-	 p(positive|j,i) = \frac{1}{1 + f(x)^{-1}}
+	 p_{NS}(positive|j,i) = \frac{1}{1 + f(x)^{-1}}
 \end{align}
@@
 This procedure does not guarantee that the embedding optimally converges to the original conditional probability from Eq.~\ref{eq:cond_prob_w2v}, even when increasing the training samples and iterations~\autocite{Chia2010,Dyer2014} because negative sampling has implicit bias.
-This problem is addressed by the noise contrastive estimation (NCE) \autocite{Chia2010}, which fits the following probability model,
+This problem is addressed by the noise contrastive estimation (NCE) \autocite{Chia2010, dyer2014notes}, which fits the following probability model,
 \begin{align}
@@
 where $f(x)$ is the unnormalized probability for an instance $x$.
-As in negative sampling, NCE fits the model based on a binary classification task, with positive and negative samples randomly drawn from the given data and a noise distribution $p_0$, respectively, using a bias-corrected sigmoid function:
+As in negative sampling, NCE optimize actual $f(x)$ based on a binary classification task, with positive and negative samples randomly drawn from the given data and a noise distribution $p_0$, respectively, using a bias-corrected sigmoid function:
 \begin{align}
 	\label{eq:sigmoid2}
-	p(positive|j,i) = \frac{1}{1 + p_0(x)f(x)^{-1}}.
+	p_{NCE}(positive|j,i) = \frac{1}{1 + p_0(x)f(x)^{-1}}.
 \end{align}
 
-Define $\tilde f(x) = f(x) p_0(x)$ and rewriting the sigmoid function for the negative sampling (Eq.~\ref{eq:sigmoid}) in terms of bias-corrected sigmoid function yields
+Defining $\tilde f(x) = f(x) p_0(x)$ and rewriting the sigmoid function for the negative sampling (Eq.~\ref{eq:sigmoid}) in terms of bias-corrected sigmoid function yields
 \begin{align}
 	\label{eq:sigmoid3}
-	\frac{1}{1 + p_0(x) \tilde f(x)^{-1}}
+	p_{NS}(positive|j,i)  = \frac{1}{1 + p_0(x) \tilde f(x)^{-1}}
 \end{align}
@@
 The \textit{word2vec} model  implicitly approximates this matrix-factorization procedure, and so comparison to these ``Levy'' distances can demonstrate whether the approximation of neural embeddings outperform direct-calculations.
-Furthermore, we computed an embedding that attempts to directly-optimize for a gravity-law relationship between relations, one created using singular-vector decomposition (SVD) and another with multidimensional scaling (MDS).
+Furthermore, we computed an embedding that attempts to directly-optimize for a gravity-law relationship between locations, one created using singular-vector decomposition (SVD) and another with multidimensional scaling (MDS).
 
@@
 We now report all main results using $\gamma = 1.0$, however we also compare its performance to embeddings learned using $\gamma = 0.75$, as we do with the number of embedded dimensions and window size.
+\todo{@dakoda could you update here on comparing two results?}
 
@@
 We find that, using the best performing dimensions (300) and window size (1),  $\gamma = 1.0$, and for default experimental parameters (global mobility, population defined using all mobile and non-mobile scholars), that the embedding distance, or cosine distance between vectors learned through neural embedding, explains more of the flux, and leads to better predictions than other baselines (Fig.~\ref{fig:supp:distancemetrics}).
-This performance advantage holds when considering both the exponential and the power-law forms of the gravity model of mobility.
-Although the euclidean distance between directly-factorized vectors performs comparably, and even narrowly beats out the embedding distance under certain experimental conditions (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}); \textit{word2vec} shows the msot consistent and robust performance, as suggested by Levy \& Goldberg~\autocite{levy2014neural}.
-Directly-optimizing the gravity model results in comparable performance to Levy's factorization approach, narroly beating out both in prediction error for certain definitions of organization population.
-Still, the embedding distance, with its stochastic optimization algortihm reliably outperforms these directly-optimized  baselines.
+This performance advantage holds across the exponential and the power-law forms of the gravity model of mobility.
+Although the euclidean distance between directly-factorized vectors performs comparably, and even narrowly beats out the embedding distance under few experimental conditions (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}); our approach shows the most consistent and robust performance and even outperform the direct optimization of the gravity models.
 
@@
 Why do neural-embedding approaches, which rely on stochastic gradient descent, outperform direct matrix factorization, especially given that \textit{word2vec} \emph{is} implicitly approximating factorization?
-An issue in the matrix factorization approach is that it is extremely sensitive to small flows between affiliations.
+An issue in the matrix factorization approach is that it is sensitive to small values.
 The matrix factorization approach embeds affiliations $i$ and $j$ such that their dot similarity is as close as to $\log (T_{ij} / P(i) P(j))$.
-If the flow $T_{ij}$ is considerably small or zero, the dot similarity goes $-\infty$, pushing $i$ and $j$ very far from the other affiliations in the embedding space~\autocite{levy2014neural, Qui2018}.
+If the flow $T_{ij}$ is considerably small or zero, the dot similarity goes $-\infty$, pushing $i$ and $j$ away in the embedding space~\autocite{levy2014neural, Qui2018}.
 This is particularly problematic when the window size is small because most affiliation pairs would have no flow, which is indeed the case in our experiments.
@@
 However, this changes the data to which we fit the model, and small flows still have a considerably strong impact on the embedding.
-
 Also, it is well known that SVD itself is vulnerable to outliers \autocite{xu2012robust, huber1981robust, xu1995robust, chandrasekaran2011rank, candes2011robust}.

### 2021-03-02 paper/rebuttal/rebuttal.tex
amend comment in reviwer 1

@@
 	They have now been incorporated into our manuscript's introduction.
-	Although there are existing work on trajectory-based mobility embedding, we argue that our new result establishing the mathematical equivalence of \textit{word2vec} and the gravity law represents a novel and substantial contribution.
+	Although there are existing work on trajectory-based mobility embedding, we argue that our new result establishing the mathematical equivalence of \textit{word2vec} and the gravity law, as well as our extensive evaluation with many baselines represents a novel and substantial contribution.
 }
@@
 	Namely, we find that \emph{SGNS is a gravity model}.
-	This finding demonstrates why SGNS performs so well, and demonstrates the utility of the model for studying contexts where gravity relationships are expected, such as in human mobility.
+	This finding explains why SGNS performs so well, and demonstrates the utility of the model for studying contexts where gravity relationships are expected, such as in human mobility.
 	We refer you to Section 1 of this letter, above, for an investigation of this connection, and how we adjusted our manuscript given this breakthrough.
 
-	Additionally, we compared the performance of SGNS to several baselines, including the distances between vectors obtained with singular-value decomposition, Laplacian eigenmap, and also Levy
-	\& Goldberg's~\autocite{levy2014neural} matrix factorization, the last of which directly calculates what SGNS only approximates.
-	We find that in nearly every case, SGNS outperforms all of these baselines, further illustrating the potential of such models for embedding and studying mobility.
+	Additionally, we compared the performance of SGNS to several baselines, including the distances between vectors obtained with the singular-value decomposition, the Laplacian eigenmap, the Levy
+	\& Goldberg's~\autocite{levy2014neural} matrix factorization \textit{word2vec}, and directly optimization of the gravity model with singular-value decomposition and multidimensional scaling.
+	We find that in nearly every setting, SGNS outperforms all of these baselines, further illustrating the potential of such models for embedding and studying mobility.
 	We refer you to Section 2 of this rebuttal letter, above, for more detailed results and the changes we made to our manuscript.

### 2021-03-02 paper/rebuttal/rebuttal.tex
add methods exp

@@
 These alternatives included the geographic distance between locations, the distance most commonly used in definitions of the gravity model of mobility, along with the dot product similarity between embedding vectors, and the cosine distance and Jensen-Shannon divergence between vectors obtained from a personalized-page-ranking procedure on the underlying mobility network.
-
-Following the advice of the referees, we also add additional baselines to illustrate how the embedding distance performs compared to simpler embedding alternatives.
-The first of these baselines uses the distance between vectors in an embedding space produced through a singular-value decomposition of the underlying location co-occurrence matrix.
-The third baseline is the distance between vectors obtained through a Laplacian eigenmap embedding of the location of the matrix.
-
-In addition to these suggested baselines, we also consider distances derived from embeddings learned through matrix factorization following the procedure outlined by Levy \& Goldberg~\autocite{levy2014neural}.
-The \textit{word2vec} model  implicitly approximates this matrix-factorization procedure, and so comparison to these ``Levy'' distances can demonstrate whether the approximation of neural embeddings outperform direct-calculations.
-Furthermore, we computed an embedding that attempts to directly-optimize for a gravity-law relationship between locations, one created using singular-vector decomposition (SVD) and another with multidimensional scaling (MDS).
+Following the advice of the referees, we also add additional baselines to illustrate how the embedding distance performs compared to simpler embedding alternatives and also more advanced approach as follow:
+
+\vspace{-0.5cm}
+\paragraph{SVD on concurrence matrix}The first of these baselines uses the distance between vectors in an embedding space produced through a singular-value decomposition of the underlying location co-occurrence matrix.
+First, we construct the co-occurrence matrix of $N$ organizations, $A_{ij}$ given by the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory.
+Then, we apply truncated singular vector decomposition with $d=300$ on the flow matrix $A$ directly.
+
+\vspace{-0.3cm}
+\paragraph{Laplacian Eigenmap} Similarly, we consider Laplacian Eigenmap embeddings~\autocite{belkin2003laplacian} as a baseline, which is one of the most fundamental approaches for graph embedding.
+First, we construct the co-occurrence matrix of $N$ organizations, $A_{ij}$ given by the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory and degree matrix $D$ which is the diagonal matrix for which $D_{ii}=\sum_j {A_{ij}}$.
+Then we construct graph Lapalcian matrix $L = D-A$  and apply truncated singular vector decomposition in the matrix $L$ with $d=300$.
+
+\vspace{-0.3cm}
+\paragraph{Levy's  symmetric SVD \textit{word2vec} distance} In addition to these suggested baselines, we also consider distances derived from embeddings learned through matrix factorization following the procedure outlined by Levy \& Goldberg~\autocite{levy2014neural}.
+Based on idea of \textit{word2vec} is just implicit matrix factorization, Levy proposed symmetric SVD \textit{word2vec} embedding, which should directly compute the embedding that \textit{word2vec} only attempts to efficiently approximate.
+First, we construct the matrix of $N$ organization
+\begin{equation}
+ M_{ij} = \log(\frac{N(i,j) |D|}{N(i) N(j)}) - \log(k),
+\end{equation}
+where $N(i,j)$ is the number of times the location pair $(i,j)$ appears given the window size $w$ in the total corpus $D$ ,$N(i)=\sum_{j=N}^i N(i,j)$ as the number of items $i$ occurred given the window size $w$ in $D$, and k is the number of negative samples.
+We used $w=1$ and $k=5$ which is same setting in the our main result.
+Then, we factorized matrix $M$ with truncated singular vector decomposition in the matrix with $d=300$ into $U_d \Sigma_d V_d$, and used the embedding vector as $U_d\sqrt{\Sigma_d}$.
+
+\vspace{-0.3cm}
+\paragraph{Direct optimization of gravity model} Finally, we create an embedding by optimizing for the gravity law directly. 
+Specifically, we construct a gravity matrix of $N$ organizations, where each cell of the matrix is calculated as $T_{ij}/m_i m_j$, where $T_{ij}$ is co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory, and $m_i$ and $m_j$ are the organizations' populations, defined here as the mean annual member of unique mobile and non-mobile authors affiliated.
+We then embed the gravity matrix using two approaches: a truncated singular-vector decomposition (SVD), and with multidimensional scaling (MDS), which embeds each location in a N-dimensional space such that pairwise distances are preserved as well as possible.
+Typically, MDS uses euclidean distance to measure distance between vectors.
 
@@
 	Additionally, we compared the performance of SGNS to several baselines, including the distances between vectors obtained with the singular-value decomposition, the Laplacian eigenmap, the Levy
-	\& Goldberg's~\autocite{levy2014neural} matrix factorization \textit{word2vec}, and directly optimization of the gravity model with singular-value decomposition and multidimensional scaling.
+	\& Goldberg's~\autocite{levy2014neural} matrix factorization \textit{word2vec}, and the directly optimization of the gravity model with singular-value decomposition and multidimensional scaling.
 	We find that in nearly every setting, SGNS outperforms all of these baselines, further illustrating the potential of such models for embedding and studying mobility.
@@
 }
-
+\clearpage
 \subsection{Response to Referee 4}

### 2021-03-02 paper/rebuttal/rebuttal.tex
start page count at 1 after cover letter
rebuttal edits

@@
 \clearpage
+\setcounter{page}{1}
 \tableofcontents
@@
 \vspace{-0.5cm}
-\paragraph{SVD on concurrence matrix}The first of these baselines uses the distance between vectors in an embedding space produced through a singular-value decomposition of the underlying location co-occurrence matrix.
+\paragraph{SVD on co-occurrence matrix:}The first of these baselines uses the distance between vectors in an embedding space produced through a singular-value decomposition of the underlying location co-occurrence matrix.
 First, we construct the co-occurrence matrix of $N$ organizations, $A_{ij}$ given by the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory.
@@
 \vspace{-0.3cm}
-\paragraph{Laplacian Eigenmap} Similarly, we consider Laplacian Eigenmap embeddings~\autocite{belkin2003laplacian} as a baseline, which is one of the most fundamental approaches for graph embedding.
+\paragraph{Laplacian Eigenmap:} Similarly, we consider Laplacian Eigenmap embeddings~\autocite{belkin2003laplacian} as a baseline, which is one of the most fundamental approaches for graph embedding.
 First, we construct the co-occurrence matrix of $N$ organizations, $A_{ij}$ given by the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory and degree matrix $D$ which is the diagonal matrix for which $D_{ii}=\sum_j {A_{ij}}$.
@@
 \vspace{-0.3cm}
-\paragraph{Levy's  symmetric SVD \textit{word2vec} distance} In addition to these suggested baselines, we also consider distances derived from embeddings learned through matrix factorization following the procedure outlined by Levy \& Goldberg~\autocite{levy2014neural}.
-Based on idea of \textit{word2vec} is just implicit matrix factorization, Levy proposed symmetric SVD \textit{word2vec} embedding, which should directly compute the embedding that \textit{word2vec} only attempts to efficiently approximate.
+\paragraph{Levy's  symmetric SVD \textit{word2vec} distance:} In addition to these suggested baselines, we also consider distances derived from embeddings learned through matrix factorization following the procedure outlined by Levy \& Goldberg~\autocite{levy2014neural}.
+Based on idea of \textit{word2vec} is implicit matrix factorization, Levy proposed symmetric SVD \textit{word2vec} embedding, which should directly compute the embedding that \textit{word2vec} only attempts to efficiently approximate.
 First, we construct the matrix of $N$ organization
 \begin{equation}
- M_{ij} = \log(\frac{N(i,j) |D|}{N(i) N(j)}) - \log(k),
+ M_{ij} = \log\left(\frac{N(i,j) |D|}{N(i) N(j)}\right) - \log(k),
 \end{equation}
@@
 \vspace{-0.3cm}
-\paragraph{Direct optimization of gravity model} Finally, we create an embedding by optimizing for the gravity law directly. 
+\paragraph{Direct optimization of gravity model:} Finally, we create an embedding by optimizing for the gravity law directly. 
 Specifically, we construct a gravity matrix of $N$ organizations, where each cell of the matrix is calculated as $T_{ij}/m_i m_j$, where $T_{ij}$ is co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory, and $m_i$ and $m_j$ are the organizations' populations, defined here as the mean annual member of unique mobile and non-mobile authors affiliated.
@@
 We now report all main results using $\gamma = 1.0$, however we also compare its performance to embeddings learned using $\gamma = 0.75$, as we do with the number of embedded dimensions and window size.
-\todo{@dakoda could you update here on comparing two results?}
+We plot the performance of each combination of hyperparemters by their ability to explain real-world flux of scientific mobility (Fig.~\ref{fig:supp:hyperparameter}), and observe no noticeable difference in performance between values of $\gamma = 0.75$ and $\gamma = 1.0$.
+Figures in the updated manuscript have been re-drawn with $\gamma = 1.0$, and the findings remain qualitatively similar.
+As a side benefit, including the hyperparemter of $\gamma$ also effectively doubles the number of embeddings trained, and that results are so similar across different embedding provides further evidence of the robustness of the approach applied to our data.
+
+%
+% Figure - Hyperparameter performance
+%
+\begin{figure}[ht!]
+	\centering
+	\includegraphics[width=0.8\textwidth]{\figdir/Descriptive/hyperparameter_performance.pdf}
+	\caption{
+		\textbf{Larger dimensions, smaller window size improves embedding performance.}
+		The correlation, or amount of flux explained by the embedding distance with varying skip-gram negative sampling hyperparameters.
+		Window size refers to $w$, the size of the context window that defines the context in a trajectory.
+		Smaller window sizes result in an embedding that explain more flux.
+		Embedding dimensions refer to the size of the embedding vector.
+		Larger vectors perform better, though little difference between 200 and 300.
+		Gamma refers to the $\gamma$ parameter in word2vec, which shapes the negative sampling distribution.
+		A value of $\gamma = 0.75$ is the default for word2vec.
+		There is virtually no difference in performance based on $\gamma$.
+		All variants perform better on same-country pairs of organizations than on all organizations.
+		All variants perform worse on different-country pairs on organizations.
+		Embeddings with larger dimensions outperform mid-size embeddings for the different-country case.
+	}
+
+	\label{fig:supp:hyperparameter}
+\end{figure}
 
@@
 \begin{itemize}
+	\item Re-drawn figures with embeddings using $\gamma = 1.0$, and included performance differences in Fig.~\ref{fig:supp:hyperparameter}, which was added to the supporting materials. 
 	\item Added Fig~\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table} to the manuscript.

### 2021-03-03 paper/rebuttal/rebuttal.tex
formating letter

@@
 \usepackage{amssymb}
-\usepackage[margin=1in]{geometry}
+\usepackage[margin=1in, top=1cm]{geometry}
 \usepackage{enumitem}
@@
 We have developed the mathematical and theoretical basis of our approach for embedding mobility, and made additional updates to our experiments and manuscript, addressing the three main issues raised by referees:
-\vspace{-0.3cm}
+
 \begin{enumerate}
@@
 \end{enumerate}
-\vspace{-0.3cm}
+
 Addressing the first point, we have identified an underlying mathematical equivalence between the Gravity Model of Mobility and the neural embedding technique \textit{word2vec}.

### 2021-03-03 paper/rebuttal/rebuttal.tex
editing margins

--- 2021-03-02 paper/rebuttal/rebuttal.tex
@@
 \date{}
+
+\newgeometry{margin=1in, top=1cm}
 \begin{document}
@@
 We have developed the mathematical and theoretical basis of our approach for embedding mobility, and made additional updates to our experiments and manuscript, addressing the three main issues raised by referees:
-\vspace{-0.3cm}
+\vspace{-0.1cm}
 \begin{enumerate}
@@
 \end{enumerate}
-\vspace{-0.3cm}
+\vspace{-0.1cm}
 Addressing the first point, we have identified an underlying mathematical equivalence between the Gravity Model of Mobility and the neural embedding technique \textit{word2vec}.
@@
 \clearpage
+\newgeometry{margin=1in}
 \setcounter{page}{1}

### 2021-03-03 paper/rebuttal/rebuttal.tex
sorry for huge commit, this commit deals with some errors in math part

@@
 Negative sampling trains {\it word2vec} using a binary classification task as follows.
-A target-context word pair $(i,j)$ is sampled from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$ are sampled from a noise distribution $p_0(\ell)=P^\gamma(\ell)$.
-($P(j)$ is the fraction of $j$ in the data, and $\gamma>0$ is a hyper-parameter).
+A target-context word pair $(i,j)$ is sampled from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$ are sampled from a noise distribution $p_0(\ell)=N(\ell)^\gamma / \sum_{x}{N(x)^\gamma} $.
+($N(\ell)$ is frequency of $\ell$ in the dataset, $\gamma>0$ is a parameter).
 Then, given a target-context word pair $(i,j)$, the model predicts whether it is a positive or negative sample using a sigmoid function:
@@
 So, the model with the negative sampling optimizes $\tilde f(x)$, not $f(x)$.
-In case of the {\it word2vec}, the instance is the dot similarity $x=\vect{u}_i \cdot \vect{v}_j$,  $f(x)=\exp(x)$, and $p_0(j)=P^\gamma(j)$, and the SGNS word2vec actually optimize the following conditional probability:
-\begin{align}
-	P\left(j \given i \right):= \frac{P^\gamma (j)\exp(\vect{u}_j \cdot \vect{v}_{i})}{Z_i},
+In case of the {\it word2vec}, the instance is the dot similarity $x=\vect{u}_i \cdot \vect{v}_j$,  $f(x)=\exp(x)$, and $p_0(x)=p_0(j)=N(j)^\gamma / \sum_{x}{N(j)^\gamma}$, and the SGNS word2vec actually optimize the following conditional probability:
+\begin{equation}
+\begin{split}
+	P\left(j \given i \right) &:= \frac{N(j)^\gamma \exp(\vect{u}_j \cdot \vect{v}_{i}) / \sum_{x}{N(x)^\gamma}}{\sum_{j'\ \in \mathcal{A}} N(j')^\gamma  \exp(\vect{u}_j' \cdot \vect{v}_{i}) /\sum_{x}{N(x)^\gamma} } \\
+	&  = \frac{N(j)^\gamma \exp(\vect{u}_j \cdot \vect{v}_{i})}{\sum_{j'\ \in \mathcal{A}} N(j')^\gamma \exp(\vect{u}_{j'} \cdot \vect{v}_{i})} ,\\
+	& = \frac{N(j)^\gamma \exp(\vect{u}_j \cdot \vect{v}_{i})}{Z'_i} ,
+	\end{split}
 	\label{eq:real_cond}
-\end{align}
-where $Z_i=\sum_{j' \in \mathcal{A}} P^\gamma (j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})$.
+\end{equation}
+where $Z'_i=\sum_{j' \in \mathcal{A}}  N(j')^\gamma \exp(\vect{u}_{j'} \cdot \vect{v}_{i})$.
 
@@
 \begin{align}
-	\hat{T}_{ij}= P(i) P(j\given i) = \frac{P(i)P^\gamma (j)\exp(\vect{u}_j \cdot \vect{v}_{i})}{Z_i}. \label{eq:prob_w2v_ng0}
+	\hat{T}_{ij}= N(i) P(j\given i) = \frac{N(i) N(j)^\gamma \exp(\vect{u}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:prob_w2v_ng0}
 \end{align}
-where we have redefined $Z_i=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})$.
+where we have redefined $Z'_i=\sum_{j' \in \mathcal{A}}  N(j)^\gamma \exp(\vect{u}_{j'} \cdot \vect{v}_{i})$.
 
@@
 \begin{align}
-	\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)P(j)\exp(\vect{v}_j \cdot \vect{v}_{i})}{Z_i}. \label{eq:flow_w2v_ng1}
+	\hat{T_{ij}}= N(i) P(j\given i) = \frac{N(i)N(j)\exp(\vect{v}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:flow_w2v_ng1}
 \end{align}
@@
 \begin{align}
-	\hat{T_{ij}}=  C P(i) P(j)  \exp(\vect{v}_j \cdot \vect{v}_{i}), \label{eq:flow_w2v_ng0}
+	\hat{T_{ij}}=  C N(i) N(j)  \exp(\vect{v}_j \cdot \vect{v}_{i}), \label{eq:flow_w2v_ng0}
 \end{align}
@@
 
-In other words, \emph{word2vec with the negative sampling is a equivalent to a gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
+In other words, \emph{word2vec with the negative sampling is a equivalent to a gravity model}, with the mass given by the location's frequency $f(i)$, and the distance measured by their dot similarities.
 While the gravity model predicts mobility flows from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given mobility flow.

### 2021-03-03 paper/rebuttal/rebuttal.tex
commit for merge

--- 2021-03-03 paper/rebuttal/rebuttal.tex
@@
-\documentclass[12pt,a4paper]{article}
+\documentclass[12pt,a4paper,draft]{article}
 \usepackage{graphicx}
@@
 \begin{equation}
-	\frac{1}{T}\sum_{t = 1}^{T} \sum_{-w \leq \tau \leq w, \tau \neq 0} \log p(a_{t + \tau} \vert a_{t}),
+	{\cal J}^{\text{SGNS}} = \frac{1}{T}\sum_{t = 1}^{T} \sum_{-w \leq \tau \leq w, \tau \neq 0} \log P(a_{t + \tau} \vert a_{t}), \label{eq:word2vec-obj}
 \end{equation}
@@
 \begin{equation}
-	p(j \given i) = \frac{\exp(\vect{u}_j \cdot \vect{v}_{i})}{Z_i}, \label{eq:cond_prob_w2v}
+	P(j \given i) = \frac{\exp(\vect{u}_j \cdot \vect{v}_{i})}{Z_i}, \label{eq:cond_prob_w2v}
 \end{equation}
@@
 \subsection{An implicit bias in the negative sampling}
-Although negative sampling is the most common approximation, it is a biased estimator~\autocite{Chia2010,Dyer2014} that optimizes a different objective function.
+
+Although negative sampling is the most common approximation, it is a biased estimator~\autocite{Chia2010,Dyer2014} that does not ensure to yield the optimal embeddings in terms of the objective function, ${\cal J}^{\text{SGNS}}$.
+This bias in negative sampling is the indispensable piece between wor2vec and the gravity model.
 
 Negative sampling trains {\it word2vec} using a binary classification task as follows.
-A target-context word pair $(i,j)$ is sampled from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$ are sampled from a noise distribution $p_0(\ell)=P^\gamma(\ell)$.
-($P(j)$ is the fraction of $j$ in the data, and $\gamma>0$ is a hyper-parameter).
-Then, given a target-context word pair $(i,j)$, the model predicts whether it is a positive or negative sample using a sigmoid function:
+For each target word $i$, we sample a context word $j$ from the given data and label it as positive, denoted by $Y_{j}=1$.
+Then, we sample $k$ words $\ell$ from a noise distribution $p_0(\ell)$ and label them as negative, denoted by $Y_{\ell}=0$.
+In word2vec, the noise distribution is given by $p_0(\ell) \propto P^\gamma (\ell)$, where $P(j)$ is the fraction of $j$ in the data, and $\gamma>0$ is a hyper-parameter.
+Then, for the sampled words, we fit a logistic regression model:
 \begin{align}
-	\label{eq:sigmoid}
-	 p_{NS}(positive|j,i) = \frac{1}{1 + f(x)^{-1}}
+	\label{eq:logistic-regress}
+	P(Y_{j} = 1; \vect{v}_{i}, \vect{u}_j) = \frac{1}{1 + \exp(-\vect{u}_j \cdot \vect{v}_{i})},
 \end{align}
-where $x=\vect{u}_i \cdot \vect{v}_j$,  $f(x)=\exp(x)$.
-
-This procedure does not guarantee that the embedding optimally converges to the original conditional probability from Eq.~\ref{eq:cond_prob_w2v}, even when increasing the training samples and iterations~\autocite{Chia2010,Dyer2014} because negative sampling has implicit bias.
-This problem is addressed by the noise contrastive estimation (NCE) \autocite{Chia2010, dyer2014notes}, which fits the following probability model,
+by maximizing the log-likelihood:
+\begin{align}
+	\label{eq:log-likelihood-logistic-regress}
+	{\cal J}^{\text{NG}} _j = \sum_{j \in {\cal D}} \left[ Y_{j} \log P(Y_{j} = 1; \vect{v}_{i}, \vect{u}_j) + (1-Y_{j}) \log P(Y_{j} = 0; \vect{v}_{i}, \vect{u}_j)\right],
+\end{align}
+where ${\cal D}$ is the set of all sampled words.
+
+An underappreciated fact is that maximizing ${\cal J}^{\text{NG}}$ does not guarantee
+to yield the optimum embedding in terms of the original word2vec objective function ${\cal J}^{\text{SGNS}}$ even if we increase the training samples and iterations~\autocite{Chia2010,Dyer2014}.
+To make this bias more explicit, let us consider an unbiased estimator similar to negative sampling, \ie the noise contrastive estimation (NCE).
+
+NCE is an unbiased estimator for probability models of the form:
+\begin{align}
+	\label{eq:prior}
+	\frac{ \exp\left( f(x) \right) }{ \sum_{ x' \in {\cal X}} \exp\left( f(x') \right) }
+\end{align}
+
+NCE trains a model using a binary classification task in the same way as in negative sampling but using Bayesian formalism for logistic regression.
+Specifically, before the training, we have a prior belief that $1$ in $1+k$ words is sampled from the given data, which can be modeled as prior probabilities
+\begin{align}
+	\label{eq:prior}
+	P_0(Y_{j} = 1) = \frac{1}{k + 1},\quad P_0(Y_{j} = 0) = \frac{k}{k + 1},
+\end{align}
+Using the Bayes rule, the posterior probability for $Y_{j}$ given word $j$ is given by
+\begin{align}
+	\label{eq:posterior}
+	P\left(Y_{j} \vert j\right) = \frac{
+		P\left(j \vert Y_{j}\right)P(Y_{j})
+	}{
+		P_0(j)
+	}.
+\end{align}
+Bearing in mind that word $j$ is sampled from the given data if $Y_{j}=1$ and from the noise distribution $p_0$ if $Y_j = 0$.
+Therefore, the class-conditional probability, $P\left(j \vert Y_{j}\right)$, is given by
+\begin{align}
+	\label{eq:class-cond}
+	P(j \vert Y_{j} = 1) & = \frac{\exp(\vect{u}_j \cdot \vect{v}_{i})}{Z_i},
+	\quad
+	P(j \vert Y_{j} = 0)  = p_0 (j).
+\end{align}
+Putting Eqs.~\eqref{eq:prior}, \eqref{eq:posterior} and \eqref{eq:class-cond} together, the posterior probability for $Y_j$ is given by
 \begin{align}
 	\label{eq:nce}
-	f(x) / \sum_{x'} f(x'),
+	P\left(Y_{j} = 1 \vert j\right) = \frac{
+		\exp(\vect{u}_j \cdot \vect{v}_{i})/Z_i
+	}{
+		\exp(\vect{u}_j \cdot \vect{v}_{i})/Z_i  + kp_0(j)
+	},
 \end{align}
-where $f(x)$ is the unnormalized probability for an instance $x$.
-As in negative sampling, NCE optimize actual $f(x)$ based on a binary classification task, with positive and negative samples randomly drawn from the given data and a noise distribution $p_0$, respectively, using a bias-corrected sigmoid function:
+which can be rewritten in form of sigmoid function:
 \begin{align}
-	\label{eq:sigmoid2}
-	p_{NCE}(positive|j,i) = \frac{1}{1 + p_0(x)f(x)^{-1}}.
+	\label{eq:nce}
+	P\left(Y_{j}=1 \vert j\right) = \frac{
+		1
+	}{
+		1 + \exp\left[ - \vect{u}_j \cdot \vect{v}_{i}  + \ln p_0(j) - c \right]
+	},
 \end{align}
-
-Defining $\tilde f(x) = f(x) p_0(x)$ and rewriting the sigmoid function for the negative sampling (Eq.~\ref{eq:sigmoid}) in terms of bias-corrected sigmoid function yields
+where $c = \ln Z_i - \ln k$ is a constant.
+NCE uses the posterior probability to predict the label of individual word.
+The log-likelihood for the posterior probability is given by
 \begin{align}
-	\label{eq:sigmoid3}
-	p_{NS}(positive|j,i)  = \frac{1}{1 + p_0(x) \tilde f(x)^{-1}}
+	\label{eq:log-likelihood-logistic-regress}
+	{\cal J}^{\text{NCE}} _j = \sum_{j \in {\cal D}} \left[ Y_{j} \log P(Y_{j} = 1\vert j) + (1-Y_{j}) \log P(Y_{j} = 0 \vert j)\right].
 \end{align}
-
-So, the model with the negative sampling optimizes $\tilde f(x)$, not $f(x)$.
-In case of the {\it word2vec}, the instance is the dot similarity $x=\vect{u}_i \cdot \vect{v}_j$,  $f(x)=\exp(x)$, and $p_0(j)=P^\gamma(j)$, and the SGNS word2vec actually optimize the following conditional probability:
+Crucially, NCE is an unbiased estimator that ensures the convergence to the optimal embedding in terms of the original word2vec's objective function, ${\cal J}^{\text{SGNS}}$~\autocite{Chia2010,Dyer2014}.
+
+Returning to negative sampling, what model does negative sampling train?
+The logistic regression model of negative sampling (Eq.~\eqref{eq:logistic-regress}) can be rewritten in form of that of NCE as follow:
 \begin{align}
-	P\left(j \given i \right):= \frac{P^\gamma (j)\exp(\vect{u}_j \cdot \vect{v}_{i})}{Z_i},
-	\label{eq:real_cond}
+	P\left(Y_{j}=1 \vert j\right) = \frac{
+		1
+	}{
+		1 + \exp\left[ - \left( \vect{u}_j \cdot \vect{v}_{i} + \ln p_0(j) - c \right) + \ln p_0(j) - c \right]
+	},
 \end{align}
-where $Z_i=\sum_{j' \in \mathcal{A}} P^\gamma (j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})$.
 

### 2021-03-03 paper/rebuttal/rebuttal.tex

@@
 to yield the optimum embedding in terms of the original word2vec objective function ${\cal J}^{\text{SGNS}}$ even if we increase the training samples and iterations~\autocite{Chia2010,Dyer2014}.
-To make this bias more explicit, let us consider an unbiased estimator similar to negative sampling, \ie the noise contrastive estimation (NCE).
-
-NCE is an unbiased estimator for probability models of the form:
+To make this bias explicit, let us consider the unbiased variant of negative samplig, \ie the noise contrastive estimation (NCE)~\autocite{Chia2010,Dyer2014}.
+NCE is an unbiased estimator for a probability model $P_m$ of the form:
 \begin{align}
-	\label{eq:prior}
-	\frac{ \exp\left( f(x) \right) }{ \sum_{ x' \in {\cal X}} \exp\left( f(x') \right) }
+	\label{eq:nce-model}
+	P_m(x) = \frac{ f(x) }{\sum_{ x' \in {\cal X}} f(x') },
 \end{align}
-
-NCE trains a model using a binary classification task in the same way as in negative sampling but using Bayesian formalism for logistic regression.
-Specifically, before the training, we have a prior belief that $1$ in $1+k$ words is sampled from the given data, which can be modeled as prior probabilities
+where $f$ is the non-negative likelihood function of data $x$, and ${\cal X}$ is the set of all data.
+This general form includes the word2vec model (Eq.~\eqref{eq:cond_prob_w2v}), where $f(x) = \exp(x)$ and $x = \vect{u}_j \cdot \vect{v}_{i}$.
+NCE trains the probability model using a binary classification task in the same way as in negative sampling but using a Bayesian formalism for logistic regression.
+Specifically, before the training, we know that $1$ in $1+k$ words is sampled from the given data, which can be modeled as prior probabilities
 \begin{align}
@@
 	}{
-		P_0(j)
+		P_0(Y_j)
 	}.
@@
 Bearing in mind that word $j$ is sampled from the given data if $Y_{j}=1$ and from the noise distribution $p_0$ if $Y_j = 0$.
-Therefore, the class-conditional probability, $P\left(j \vert Y_{j}\right)$, is given by
+Assuming that the given data is generated from the probability model to be fit, the class-conditional probability, $P\left(j \vert Y_{j}\right)$, is given by
 \begin{align}
 	\label{eq:class-cond}
-	P(j \vert Y_{j} = 1) & = \frac{\exp(\vect{u}_j \cdot \vect{v}_{i})}{Z_i},
+	P(j \vert Y_{j} = 1) & = P_m(\vect{u}_j \cdot \vect{v}_{i}),
 	\quad
@@
 	P\left(Y_{j} = 1 \vert j\right) = \frac{
-		\exp(\vect{u}_j \cdot \vect{v}_{i})/Z_i
+		P_m(\vect{u}_j \cdot \vect{v}_{i})
 	}{
-		\exp(\vect{u}_j \cdot \vect{v}_{i})/Z_i  + kp_0(j)
+		P_m(\vect{u}_j \cdot \vect{v}_{i})  + kp_0(j)
 	},
@@
 	}{
-		1 + \exp\left[ - \vect{u}_j \cdot \vect{v}_{i}  + \ln p_0(j) - c \right]
+		1 + \exp\left[ - \ln f(\vect{u}_j \cdot \vect{v}_{i})  + \ln p_0(j) + c \right]
 	},
 \end{align}
-where $c = \ln Z_i - \ln k$ is a constant.
-NCE uses the posterior probability to predict the label of individual word.
-The log-likelihood for the posterior probability is given by
+where $c = -\ln k + \ln\sum_{ x' \in {\cal X}} f(x') $ is a constant.
+NCE maximizes the log-likelihood
 \begin{align}
@@
 \end{align}
-Crucially, NCE is an unbiased estimator that ensures the convergence to the optimal embedding in terms of the original word2vec's objective function, ${\cal J}^{\text{SGNS}}$~\autocite{Chia2010,Dyer2014}.
-
-Returning to negative sampling, what model does negative sampling train?
-The logistic regression model of negative sampling (Eq.~\eqref{eq:logistic-regress}) can be rewritten in form of that of NCE as follow:
+by calculating the gradients for embedding vectors $\vect{u}_j$, $\vect{v}_{i}$ and iteratively updating them.
+An important consequence of this framework is that NCE is an unbiased estimator that has convergence to the optimal embedding in terms of the original word2vec's objective function, ${\cal J}^{\text{SGNS}}$~\autocite{Chia2010,Dyer2014} if we increase the number of words to sample and the training iterations.
+
+Let us revisit negative sampling from the perspective of NCE.
+We rewrite the logistic regression model in negative sampling (Eq.~\eqref{eq:logistic-regress}) in form of the posterior probability:
 \begin{align}
-	P\left(Y_{j}=1 \vert j\right) = \frac{
+	P\left(Y_{j}=1 \vert j\right) & = \frac{
 		1
 	}{
-		1 + \exp\left[ - \left( \vect{u}_j \cdot \vect{v}_{i} + \ln p_0(j) - c \right) + \ln p_0(j) - c \right]
-	},
+		1 + \exp\left[ - \left( \vect{u}_j \cdot \vect{v}_{i} + \ln p_0(j) + c \right) + \ln p_0(j) + c \right]
+	}                                        \\
+	                              & = \frac{
+		1
+	}{
+		1 + \exp\left[ - \ln f(\vect{u}_j \cdot \vect{v}_{i}) + \ln p_0(j) + c \right]
+	}.
 \end{align}
+where we define the likelihood function $f$ by
+\begin{align}
+	f(\vect{u}_j \cdot \vect{v}_{i}) = \exp\left( \vect{u}_j \cdot \vect{v}_{i} + \ln p_0(j) + c\right).
+\end{align}
+which is the unbiased estimator for the probability model
+\begin{align}
+	\label{eq:unbiasef}
+	P_m(\vect{u}_j \cdot \vect{v}_{i}) & = \frac{ f(\vect{u}_j \cdot \vect{v}_{i}) }{\sum_{ j' \in {\cal A}} f(\vect{u}_{j'} \cdot \vect{v}_{i}) }, \\
+	                                   & = \frac{  p_0(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{Z' _i},
+\end{align}
+where $Z'_i=\sum_{j' \in \mathcal{A}}  p_0(j')^\gamma \exp(\vect{u}_{j'} \cdot \vect{v}_{i})$.
 

### 2021-03-04 paper/rebuttal/rebuttal.tex
update SGNS -> SG

@@
-\documentclass[12pt,a4paper,draft]{article}
+\documentclass[12pt,a4paper]{article}
 \usepackage{graphicx}
@@
 A location, $a_{t}$, is considered to have context locations, $a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}$, that appear in the window surrounding $a_t$ up to a time lag of $w$, where $w$ is the window size parameter truncated at $t - w \geq 0$ and $t + w \leq T$.
-Then, the SGNS model learns probability $p(a_{t + \tau} \vert a_{t})$, where $-w\leq \tau\leq w$ and $\tau \neq 0$,  by maximizing its log likelihood given by
+Then, the skip-gram \textit{word2vec} learns probability $p(a_{t + \tau} \vert a_{t})$, where $-w\leq \tau\leq w$ and $\tau \neq 0$,  by maximizing its log likelihood given by
 %
@@
 \begin{equation}
-	{\cal J}^{\text{SGNS}} = \frac{1}{T}\sum_{t = 1}^{T} \sum_{-w \leq \tau \leq w, \tau \neq 0} \log P(a_{t + \tau} \vert a_{t}), \label{eq:word2vec-obj}
+	{\cal J} = \frac{1}{T}\sum_{t = 1}^{T} \sum_{-w \leq \tau \leq w, \tau \neq 0} \log P(a_{t + \tau} \vert a_{t}), \label{eq:word2vec-obj}
 \end{equation}
@@
 
-Although negative sampling is the most common approximation, it is a biased estimator~\autocite{Chia2010,Dyer2014} that does not ensure to yield the optimal embeddings in terms of the objective function, ${\cal J}^{\text{SGNS}}$.
+Although negative sampling is the most common approximation, it is a biased estimator~\autocite{Chia2010,Dyer2014} that does not ensure to yield the optimal embeddings in terms of the objective function, ${\cal J}$.
 This bias in negative sampling is the indispensable piece between wor2vec and the gravity model.
@@
 Then, we sample $k$ words $\ell$ from a noise distribution $p_0(\ell)$ and label them as negative, denoted by $Y_{\ell}=0$.
-In word2vec, the noise distribution is given by $p_0(\ell) \propto P^\gamma (\ell)$, where $P(j)$ is the fraction of $j$ in the data, and $\gamma>0$ is a hyper-parameter.
+In \textit{word2vec}, the noise distribution is given by $p_0(\ell) \propto P^\gamma (\ell)$, where $P(j)$ is the fraction of $j$ in the data, and $\gamma>0$ is a hyper-parameter.
 Then, for the sampled words, we fit a logistic regression model:

### 2021-03-04 paper/rebuttal/rebuttal.tex
update some notations

@@
 	\label{eq:log-likelihood-logistic-regress}
-	{\cal J}^{\text{NG}} _j = \sum_{j \in {\cal D}} \left[ Y_{j} \log P(Y_{j} = 1; \vect{v}_{i}, \vect{u}_j) + (1-Y_{j}) \log P(Y_{j} = 0; \vect{v}_{i}, \vect{u}_j)\right],
+	{\cal J}^{\text{NS}} _j = \sum_{j \in {\cal D}} \left[ Y_{j} \log P(Y_{j} = 1; \vect{v}_{i}, \vect{u}_j) + (1-Y_{j}) \log P(Y_{j} = 0; \vect{v}_{i}, \vect{u}_j)\right],
 \end{align}
@@
 
-An underappreciated fact is that maximizing ${\cal J}^{\text{NG}}$ does not guarantee
-to yield the optimum embedding in terms of the original word2vec objective function ${\cal J}^{\text{SGNS}}$ even if we increase the training samples and iterations~\autocite{Chia2010,Dyer2014}.
+An underappreciated fact is that maximizing ${\cal J}^{\text{NS}}$ does not guarantee
+to yield the optimum embedding in terms of the original skip-gram word2vec objective function ${\cal J}$ even if we increase the training samples and iterations~\autocite{Chia2010,Dyer2014}.
 To make this bias explicit, let us consider the unbiased variant of negative samplig, \ie the noise contrastive estimation (NCE)~\autocite{Chia2010,Dyer2014}.
@@
 	\label{eq:nce}
-	P\left(Y_{j} = 1 \vert j\right) = \frac{
+	P^{NCE}\left(Y_{j} = 1 \vert j\right) = \frac{
 		P_m(\vect{u}_j \cdot \vect{v}_{i})
@@
 	\label{eq:nce}
-	P\left(Y_{j}=1 \vert j\right) = \frac{
+	P^{NCE}\left(Y_{j}=1 \vert j\right) = \frac{
 		1
@@
 	\label{eq:log-likelihood-logistic-regress}
-	{\cal J}^{\text{NCE}} _j = \sum_{j \in {\cal D}} \left[ Y_{j} \log P(Y_{j} = 1\vert j) + (1-Y_{j}) \log P(Y_{j} = 0 \vert j)\right].
+	{\cal J}^{\text{NCE}} _j = \sum_{j \in {\cal D}} \left[ Y_{j} \log P^{NCE}(Y_{j} = 1\vert j) + (1-Y_{j}) \log P^{NCE}(Y_{j} = 0 \vert j)\right].
 \end{align}
 by calculating the gradients for embedding vectors $\vect{u}_j$, $\vect{v}_{i}$ and iteratively updating them.
-An important consequence of this framework is that NCE is an unbiased estimator that has convergence to the optimal embedding in terms of the original word2vec's objective function, ${\cal J}^{\text{SGNS}}$~\autocite{Chia2010,Dyer2014} if we increase the number of words to sample and the training iterations.
+An important consequence of this framework is that NCE is an unbiased estimator that has convergence to the optimal embedding in terms of the original word2vec's objective function, ${\cal J}$~\autocite{Chia2010,Dyer2014} if we increase the number of words to sample and the training iterations.
 
@@
 \begin{align}
-	P\left(Y_{j}=1 \vert j\right) & = \frac{
+	P^{NS}\left(Y_{j}=1 \vert j\right) & = \frac{
 		1
@@
 	\label{eq:unbiasef}
-	P_m(\vect{u}_j \cdot \vect{v}_{i}) & = \frac{ f(\vect{u}_j \cdot \vect{v}_{i}) }{\sum_{ j' \in {\cal A}} f(\vect{u}_{j'} \cdot \vect{v}_{i}) }, \\
-	                                   & = \frac{  p_0(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{Z' _i},
+	P_m^{NS}(\vect{u}_j \cdot \vect{v}_{i}) & = \frac{ f(\vect{u}_j \cdot \vect{v}_{i}) }{\sum_{ j' \in {\cal A}} f(\vect{u}_{j'} \cdot \vect{v}_{i}) }, \\
+	                                   & = \frac{  p_0(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{\sum_{j' \in \mathcal{A}}  p_0(j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})}, \\
+	                                   & = \frac{  P^\gamma(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{\sum_{j' \in \mathcal{A}}  P^\gamma(j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})} \hspace{0.3cm}(\because p_0(\ell) \propto P^\gamma (\ell)),
 \end{align}
-where $Z'_i=\sum_{j' \in \mathcal{A}}  p_0(j')^\gamma \exp(\vect{u}_{j'} \cdot \vect{v}_{i})$.
+where  $P(j)$ is the fraction of $j$ in the data. Taking together, conditional probability of SGNS \textit{word2vec} actually optimize is
+\begin{align}
+	P^{NS}(j\given i) = P_m^{NS}(\vect{u}_j \cdot \vect{v}_{i})  =  \frac{  P^\gamma(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{Z'_i},
+\end{align}
+ where $Z'_i=\sum_{j' \in \mathcal{A}}  P^\gamma(j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})$.
 
@@
 \begin{align}
-	\hat{T}_{ij}= N(i) P(j\given i) = \frac{N(i) N(j)^\gamma \exp(\vect{u}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:prob_w2v_ng0}
+	\hat{T}_{ij} \propto  P(i) P(j\given i) \propto  \frac{P(i) P(j)^\gamma \exp(\vect{u}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:prob_w2v_ng0}
 \end{align}

### 2021-03-04 paper/rebuttal/rebuttal.tex
update following section
typo

@@
 \end{align}
-where we have redefined $Z'_i=\sum_{j' \in \mathcal{A}}  N(j)^\gamma \exp(\vect{u}_{j'} \cdot \vect{v}_{i})$.
+where we have redefined $Z'_i=\sum_{j' \in \mathcal{A}}  P^\gamma(j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})$.
 
@@
 \begin{align}
-	\hat{T_{ij}}= N(i) P(j\given i) = \frac{N(i)N(j)\exp(\vect{v}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:flow_w2v_ng1}
+	\hat{T_{ij}} \propto  P(i) P(j\given i) = \frac{P(i)P(j)\exp(\vect{v}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:flow_w2v_ng1}
 \end{align}
@@
 \begin{align}
-	\hat{T_{ij}}=  C N(i) N(j)  \exp(\vect{v}_j \cdot \vect{v}_{i}), \label{eq:flow_w2v_ng0}
+	\hat{T_{ij}} \propto  P(i) P(j)  \exp(\vect{v}_j \cdot \vect{v}_{i}), \label{eq:flow_w2v_ng0}
 \end{align}
@@
 \end{equation}
-where $N(i,j)$ is the number of times the location pair $(i,j)$ appears given the window size $w$ in the total corpus $D$ ,$N(i)=\sum_{j=N}^i N(i,j)$ as the number of items $i$ occurred given the window size $w$ in $D$, and k is the number of negative samples.
+where $N(i,j)$ is the number of times the location pair $(i,j)$ appears given the window size $w$ in the total corpus $D$, $N(i)=\sum_{j=N}^i N(i,j)$ as the number of items $i$ occurred given the window size $w$ in $D$, and k is the number of negative samples.
 We used $w=1$ and $k=5$ which is same setting in the our main result.

### 2021-03-08 paper/rebuttal/rebuttal.tex
update letter

@@
 
-We thank all the referees for their thoughtful and helpful comments and critiques, all of which provided valuable insights.
+We thank all the referees for their thoughtful and helpful comments and critiques.
 We acknowledge that our initial submission had a substantial gap regarding the choice of the \textit{word2vec} model, its connection with the gravity model of mobility, and its evaluation.
 While reflecting on these comments and our manuscript, we have made a theoretical breakthrough that addresses the primary issues;
-namely, we have discovered a mathematical equivalence between the \textit{word2vec} (skip-gram) model and the gravity model.
-Furthermore, our subsequent experiments show that our approach's performance is robust, exceeding many other baselines.
-Therefore, with these changes, we are confident that our paper is significantly stronger, and its contribution more wide-reaching and impactful.
+namely, we have discovered \emph{a mathematical equivalence between the \textit{word2vec} (skip-gram with negative sampling) model and the gravity model.}
+
+Furthermore, our subsequent experiments show that our approach's performance is robust, exceeding many other baselines, even direct optimization of the gravity model.
+Therefore, with these changes, we are confident that our paper is substantially stronger with a qualitative leap.
 Thus, we would like to request a reconsideration of our manuscript.
@@
 	\itemsep0em
-	\item Our approach and analysis lacked theoretical justification and grounding, and the application of \textit{word2vec} to mobility was arbitrary
-	\item Performance of \textit{word2vec} is not well understood in the context of other, simpler embedding techniques
-	\item Our findings were not sufficiently grounded in the literature of neural embeddings and mobility
+	\item The lack of theoretical justification and grounding for the application of \textit{word2vec} to mobility
+	\item The lack of simpler baselines to understand the performance of \textit{word2vec} 
+	\item The lack of sufficient grounding in the literature of neural embeddings and mobility
 \end{enumerate}
 \vspace{-0.1cm}
-Addressing the first point, we have identified an underlying mathematical equivalence between the Gravity Model of Mobility and the neural embedding technique \textit{word2vec}.
-Namely, we demonstrate that \textit{word2vec} 's objective function is equivalent to the gravity law and thus \textit{word2vec} learns gravity-like relationships between entities, whether it be language or locations.
+We address the first point by presenting the mathematical equivalence between the Gravity Model of Mobility and the skip-gram negative sampling \textit{word2vec} model.
+Namely, we demonstrate that \textit{word2vec}'s objective function is equivalent to the gravity law and thus \textit{word2vec} learns gravity-like relationships between entities, whether it be language or locations.
 This development constitutes a major breakthrough in our understanding of neural embeddings, and provides theoretical justification for their application to mobility.
 
-For the second point, we have also conducted experiments comparing the performance of neural embedding to (\romannum{1}) a singular value decomposition of the mobility network,  (\romannum{2}) a Laplacian eigenmap embedding  (\romannum{3}) a \textit{word2vec} model with matrix factorization,  and  (\romannum{4}) a direct optimization according to the gravity law.
+For the second point, we have conducted experiments comparing the performance of neural embedding to (\romannum{1}) a singular value decomposition of the mobility network,  (\romannum{2}) a Laplacian eigenmap embedding  (\romannum{3}) a \textit{word2vec} model with matrix factorization,  and  (\romannum{4}) a direct optimization according at the gravity law.
 We find that the embedding distance from \textit{word2vec} outperforms all baselines, even the direct optimization of gravity law with the multidimensional scaling, in explaining and predicting real-world mobility.
 
-Finally, addressing the third point, we take steps to better ground our manuscript in the existing literature, integrating the reviewer's suggested articles into our manuscript.
-
-In the attached detailed response, we outline the connection between \textit{word2vec} and the gravity model (section 1), and comparisons to baselines (section 2).
-We then provide a point-by-point response to each of the reviewer's comments in section 3.
+Finally, addressing the third point, we have cooperated relevant literature to better ground our manuscript in the existing studies.
+
+In the attached detailed response, we outline the connection between \textit{word2vec} and the gravity model (Section 1), and comparisons to baselines (Section 2).
+We then provide a point-by-point response to each of the reviewer's comments in Section 3.
 

### 2021-03-08 paper/rebuttal/rebuttal.tex
update 1.3

@@
 \begin{align}
-	\hat{T}_{ij} \propto  P(i) P(j\given i) \propto  \frac{P(i) P(j)^\gamma \exp(\vect{u}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:prob_w2v_ng0}
+	\widehat{T}_{ij} \propto  P(i) P(j\given i) \propto  \frac{P(i) P(j)^\gamma \exp(\vect{u}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:prob_w2v_ng0}
 \end{align}
@@
 
-Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimial in-vectors and out-vectors such that $\vect{u}_i = \vect{v}_i$ \autocite{levy2014neural}.
-Setting $\gamma = 1$ and substituting $\vect{u}_i = \vect{v}_j$ into Eq.~\ref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
+Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimial in-vectors and out-vectors such that $\vect{v}_i = \vect{u}_i$ \autocite{levy2014neural}.
+Setting $\gamma = 1$ and substituting $\vect{v}_i = \vect{u}_i$ into Eq.~\ref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
 \begin{align}
-	\hat{T_{ij}} \propto  P(i) P(j\given i) = \frac{P(i)P(j)\exp(\vect{v}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:flow_w2v_ng1}
+	\widehat{T}_{ij} \propto  P(i) P(j\given i) = \frac{P(i)P(j)\exp(\vect{v}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:flow_w2v_ng1}
 \end{align}
 
-The flow $\hat{T}_{ij}$ is symmetric (\ie $\hat{T}_{ij}=\hat{T}_{ji}$) because the skip-gram model neglects whether the context $j$ appears before or after the target $i$ in the trajectory.
+The flow $\widehat{T}_{ij}$ is symmetric (\ie $\widehat{T}_{ij}=\widehat{T}_{ji}$) because the skip-gram model neglects whether the context $j$ appears before or after the target $i$ in the trajectory.
 If we swap $i$ and $j$ in Eq.~\ref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
-Therefore, to ensure $\hat{T}_{ij} = \hat{T}_{ji}$, the denominator $Z_i$ should be a constant.
+Therefore, to ensure $\widehat{T}_{ij}=\widehat{T}_{ji}$, the denominator $Z_i$ should be a constant.
 
@@
 \begin{align}
-	\hat{T_{ij}} \propto  P(i) P(j)  \exp(\vect{v}_j \cdot \vect{v}_{i}), \label{eq:flow_w2v_ng0}
+	\widehat{T}_{ij} \propto  P(i) P(j)  \exp(\vect{v}_j \cdot \vect{v}_{i}), \label{eq:flow_w2v_ng0}
 \end{align}
@@
 
-In other words, \emph{word2vec with the negative sampling is a equivalent to a gravity model}, with the mass given by the location's frequency $f(i)$, and the distance measured by their dot similarities.
+In other words, \emph{word2vec with the skip-gram negative sampling is equivalent to the gravity model}, with the mass given by the location's frequency $f(i)$, and the distance measured by their dot similarities.
 While the gravity model predicts mobility flows from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given mobility flow.
@@
 
-In practice, because we do not have unlimited amounts of data (which is also noisy) and the optimization may not find the true optimum, the idealized result may not hold.
-Indeed, we tend to find that the in- and out-vectors tend to be different and that the cosine similarity tends to better capture real-world mobility than the dot similarity.
+In practice, because we only have limited amounts of noisy data and the optimization may not find the true optimum, the mathematical result may not hold.
+Indeed, we find that the in- and out-vectors tend to be different and that the cosine similarity tends to better capture real-world mobility than the dot similarity.
 Nevertheless, a model with dot similarity is still the second best after cosine similarity (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and the embedding distance still outperforms all alternatives we considered.

### 2021-03-08 paper/rebuttal/rebuttal.tex
update 2.*

@@
 \end{align}
-where $C$ is a positive constant.
 
@@
 The first is $\gamma$, a hyper-parameter of the \textit{word2vec} model, which defines the exponent which shapes the negative sampling distribution.
-The default of `\texttt{gensim's} implementation of \textit{word2vec} is to set $\gamma = 0.75$, and this was the value used in our original manuscript.
-However, to connect \textit{word2vec} to the gravity model of mobility, we assume $\gamma = 1.0$ (see section 1).
+The default of \texttt{gensim} implementation of \textit{word2vec} is to set $\gamma = 0.75$, and this was the value used in our original manuscript.
+However, to connect \textit{word2vec} to the gravity model of mobility, we assume $\gamma = 1.0$ (see Section 1).
 We now report all main results using $\gamma = 1.0$, however we also compare its performance to embeddings learned using $\gamma = 0.75$, as we do with the number of embedded dimensions and window size.
@@
 We find that, using the best performing dimensions (300) and window size (1),  $\gamma = 1.0$, and for default experimental parameters (global mobility, population defined using all mobile and non-mobile scholars), that the embedding distance, or cosine distance between vectors learned through neural embedding, explains more of the flux, and leads to better predictions than other baselines (Fig.~\ref{fig:supp:distancemetrics}).
-This performance advantage holds across the exponential and the power-law forms of the gravity model of mobility.
+This performance advantage holds across \emph{the exponential and the power-law forms of the gravity model of mobility}.
 Although the euclidean distance between directly-factorized vectors performs comparably, and even narrowly beats out the embedding distance under few experimental conditions (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}); our approach shows the most consistent and robust performance and even outperform the direct optimization of the gravity models.

### 2021-03-08 paper/rebuttal/rebuttal.tex
finshing my pass

@@
 \clearpage
-\section{Point-by-point discussion}
+\section{Point-by-point response}
 All of the referees presented us with excellent, insightful comments and we feel that the changes implemented as a consequence have signiﬁcantly strengthened the manuscript.
 Here we offer further discussion, and introduce several results and figures to support certain arguments.
-
+\todo{@dakoda, could you check the numbering comment from yy?}
 \subsection{Response to Referee 1}
@@
 
-	“We however, note that all results shown here are robust to this stochasticity, likely emerging from the limited ``vocabulary'' of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories).
+	“We note that all results shown here are robust to this stochasticity, likely emerging from the limited ``vocabulary'' of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories).
 Applications of word2vec to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random fluctuations.”
@@
 \response{Thank you for this feedback.
-	You are correct that it was a conscious choice to not report statistical significance in the form of a P-value.
+	You are correct that it was a conscious choice to not report statistical significance in the form of a $p$-value.
 	The use of statistical significance is contentious, and Nature itself has hosted some of this debate~\autocite{amrhein2019statistics}.
-	As such, we avoided p-values in our research when it made sense to do so.
+	As such, we avoided $p$-values in our research when it made sense to do so.
 	In our analysis, all significance levels were below 0.0001, with most computationally indistinguishable from zero.
-	However, we recognize that p-values can help readers interpret results.
+	However, we recognize that $p$-values can help readers interpret results.
 	As such, we have opted to add to a sentence such as \say{\textit{Correlation is calculated on the data in the log-log scale ($p < 0.0001$ across all fits)}.} or similar to relevant figures in the main text and supporting materials.
@@
 	We carefully read out the Barthélemy, Physics Reports 499, 1, 2011, and referenced it in our manuscript.
-	Also, we report the performance of the flux estimation and prediction using different deterrence functions (see Section 2, above), finding that the absolute values vary, the pattern doesn't change---the embedding distance robustly outperforms geographic distance regardless of the function used.
+	Also, we report the performance of the flux estimation and prediction using different deterrence functions (see Section 2, above), finding that although the absolute values vary, the pattern doesn't change---the embedding distance robustly outperforms geographic distance regardless of the function used.
 	We add the following line to the methods noting this point,
@@
 	\say{The decay function $f(r_{ij})$ defines the effect of distance, and so different decay functions can model fundamentally different mechanism [...] such as the cost functions for a given distance and the spatial granularity of the observation.
-		For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case though there is no qualitative difference---the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Supporting Information).}
+		For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each cases though there is no qualitative difference---the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Supporting Information).}
 
@@
 	fits well with the simple system with no spatial memory~\autocite{chen2015distance}.
-	However, the embedding distance fits well with the exponential decay function, perhaps demonstrating that the real-world spatial complexity of mobility is encoded in the \textit{word2vec} embedding space as simpler pairwise distances, likely resulting from underlying connection we established between \textit{word2vec} and the gravity model (see section 1, above).
+	However, the embedding distance fits well with the exponential decay function, perhaps demonstrating that the real-world spatial complexity of mobility is encoded in the \textit{word2vec} embedding space as simpler pairwise distances, likely resulting from underlying connection we established between \textit{word2vec} and the gravity model (see Section 1, above).
 
@@
 
-	In addition, we provided more explicit mathematical detail of word2vec in the new subsection entitled “word2vec and the gravity model” (see section 1, above).
+	In addition, we provided more explicit mathematical detail of word2vec in the new subsection entitled “word2vec and the gravity model” (see Section 1, above).
 
@@
 
-	A full search of the parameter space would certainly be interesting and useful, however we believe that set of parameters we considered here is sufficient to establish the utility of the approach, and demonstrate that performance is only slightly different based on different parameters.
-	We note that in previous work from our group, we explored the optimal dimensions for graph embedding~\autocite{gu2020dimensions}, finding that while a minimum number of dimensions is necessary, increasing the dimensions does not detract from performance, a property common across deep learning methods.
+	A full search of the hyper-parameter space would certainly be interesting and useful, however we believe that set of hyper-parameters we considered here is sufficient to establish the utility of the approach, and demonstrate that performance is only slightly different based on different hyper-parameters.
+	There are previous studies on the optimal dimensionality of word embedding \autocite{yin2018understand, yin2018dimensionality}. Also, 
+	we note that in previous work from our group, we explored the optimal dimensions for graph embedding~\autocite{gu2020dimensions}, finding that while a sufficient number of dimensions is necessary to capture the structure, increasing the dimensions does not detract from performance, a property common across deep learning methods.
 	Given that there is little performance difference between $d = 100$ and $d = 300$, we opt to use the larger embeddings at $d = 300$, which are large enough to capture the complexity of mobility, yet small enough to allow an efficient computational workflow.
@@
 	We agree that the revolution in neural embeddings offers great promise in mobility and look forward to reading and also working on these future studies; however, we argue that our contribution is most well-founded, and best serves the scientific community, by working with simpler and more established models (see Section 2, this letter), especially concerning the mathematical link we uncovered.
-Moreover, these deep models require a tremendous amount of training data ($\sim$3 billion words in Bert) and model parameters, making their use more cumbersome.
-
-	To highlight the importance of altenrative models, however, we add the following line to our conclusion: \say{\textit{Future studies may also consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality.
-}}.
+Moreover, these deep models require a tremendous amount of training data ($\sim$3 billion words in Bert) and model parameters, making their use infeasible in applicants most
+
+	To highlight the importance of altenrative models, however, we add the following line to our conclusion: \say{\textit{Future studies may also consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality.}}.
 
@@
 
-	However, while these topics are exciting, we believe that that they fall outside the scope of the current manuscript, especially given the discoveries we made concerning a fundamental connection between the gravity law of mobility and \textit{word2vec}.
+	However, while these topics are exciting, we believe that that they fall outside the scope of the current manuscript, especially given the discoveries we made concerning a fundamental connection between the gravity law of mobility and \textit{word2vec}, which adds a substantial amount of new result to the manuscript.
 }
@@
 	In the future, however, we hope to have access to a fully-representative sample of mobility data to study the effects of COVID-19 on global scientific labor flows.
-	We can use techniqeus developed by other researchers, such as those used by Hamilton, Leskovec, \& Jurafsky (\href{https://nlp.stanford.edu/projects/histwords/}{[link]}), to align embeddings trained on different data in order to quantify the changes in global mobility.
+	We can use techniqeus developed by other researchers, such as those used by Hamilton, Leskovec, \& Jurafsky \autocite{hamilton-etal-2016-diachronic}, to align embeddings trained on different data in order to quantify the changes in global mobility.
 	We look forward to approaching this, as well as other exciting projects in the future.
@@
 			``Raw freq'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
-			Embedding distance, measured as the cosine distance between embedding vectors, results in better predictions of mobility than baselines in nearly every case, however Levy's 's factorization~\autocite{levy2014neural} perform better in the case of international and domestic only mobility when using raw frequency populations.
+			Embedding distance, measured as the cosine distance between embedding vectors, results in better predictions of mobility than baselines in nearly every case, however Levy's factorization~\autocite{levy2014neural} perform better in the case of international and domestic only mobility when using raw frequency populations.
 		}

### 2021-03-08 paper/rebuttal/rebuttal.tex
finally got numbering working

@@
 
+\newcounter{comment}[subsection]
+
 %
@@
 \tcbuselibrary{breakable}
-\newtcolorbox[auto counter,
-					  number within=subsection,
- 				       list type=subsubsection,
- 				       list inside=toc]{sectionbox}[1]{colback=white,
+\newtcolorbox[list inside=toc]{sectionbox}[1]{colback=white,
  				       												 colframe=black,
@@
  				       												 coltitle=black,
- 				       												fonttitle=\bfseries, title={Comment \thetcbcounter},
- 				       												list entry={Comment \thetcbcounter\quad}, breakable}
+ 				       												 fonttitle=\bfseries, 
+ 				       												 phantom=\refstepcounter{comment},
+ 				       												 title={Comment \arabic{section}.\arabic{comment}},
+ 				       												 list entry={Comment \arabic{section}.\arabic{comment}\quad}, breakable}
 
@@
 %\newcommand{\rcomment}[1]{{\bigskip\begin{snugshade}\begin{quotation}\noindent #1 \end{quotation}\end{snugshade} }}
+
 \newcommand{\rcomment}[1]{%
@@
 }
+
 \newcommand{\correction}[2]{{\begin{quotation}\noindent {#1}{\it #2} \end{quotation} }}
@@
 Here we offer further discussion, and introduce several results and figures to support certain arguments.
-\todo{@dakoda, could you check the numbering comment from yy?}
 \subsection{Response to Referee 1}
+\setcounter{section}{1}
 
@@
 \clearpage
+\setcounter{section}{3}
 \subsection{Response to Referee 2}
+\setcounter{section}{2}
 
@@
 \clearpage
+\setcounter{section}{3}
 \subsection{Response to Referee 3}
+\setcounter{section}{3}
 
@@
 }
+
+%
+% Response to referee 4
+%
 \clearpage
+\setcounter{section}{3}
 \subsection{Response to Referee 4}
+\setcounter{section}{4}
 

### 2021-03-08 paper/rebuttal/rebuttal.tex
reflect YY's comment in sec 1.2

@@
 
-Although negative sampling is the most common approximation, it is a biased estimator~\autocite{Chia2010,Dyer2014} that does not ensure to yield the optimal embeddings in terms of the objective function, ${\cal J}$.
-This bias in negative sampling is the indispensable piece between wor2vec and the gravity model.
+Although negative sampling is the most common approximation, it is a biased estimator~\autocite{Chia2010,Dyer2014} that does not yield the optimal embeddings in terms of the objective function, ${\cal J}$.
+This bias in negative sampling turns out to be a critical piece that connects wor2vec and the gravity model.
 
@@
 Then, we sample $k$ words $\ell$ from a noise distribution $p_0(\ell)$ and label them as negative, denoted by $Y_{\ell}=0$.
-In \textit{word2vec}, the noise distribution is given by $p_0(\ell) \propto P^\gamma (\ell)$, where $P(j)$ is the fraction of $j$ in the data, and $\gamma>0$ is a hyper-parameter.
+In \textit{word2vec}, the noise distribution is given by $p_0(\ell) \propto P^\gamma (\ell)$, where $P(j)$ is the fraction of $j$ in the data, and $\gamma$ is a hyper-parameter.
 Then, for the sampled words, we fit a logistic regression model:
@@
 	\label{eq:log-likelihood-logistic-regress}
-	{\cal J}^{\text{NS}} _j = \sum_{j \in {\cal D}} \left[ Y_{j} \log P(Y_{j} = 1; \vect{v}_{i}, \vect{u}_j) + (1-Y_{j}) \log P(Y_{j} = 0; \vect{v}_{i}, \vect{u}_j)\right],
+	{\cal J}^{\text{NS}} = \sum_{i \in {\cal A}} \sum_{j \in {\cal D}} \left[ Y_{j} \log P(Y_{j} = 1; \vect{v}_{i}, \vect{u}_j) + (1-Y_{j}) \log P(Y_{j} = 0; \vect{v}_{i}, \vect{u}_j)\right],
 \end{align}
-where ${\cal D}$ is the set of all sampled words.
+where ${\cal D}$ is the set of all sampled context words.
 
@@
 to yield the optimum embedding in terms of the original skip-gram word2vec objective function ${\cal J}$ even if we increase the training samples and iterations~\autocite{Chia2010,Dyer2014}.
-To make this bias explicit, let us consider the unbiased variant of negative samplig, \ie the noise contrastive estimation (NCE)~\autocite{Chia2010,Dyer2014}.
+To make this bias explicit, let us consider the unbiased variant of negative sampling, \ie the noise contrastive estimation (NCE)~\autocite{Chia2010,Dyer2014}.
 NCE is an unbiased estimator for a probability model $P_m$ of the form:
@@
 This general form includes the word2vec model (Eq.~\eqref{eq:cond_prob_w2v}), where $f(x) = \exp(x)$ and $x = \vect{u}_j \cdot \vect{v}_{i}$.
-NCE trains the probability model using a binary classification task in the same way as in negative sampling but using a Bayesian formalism for logistic regression.
+NCE fits the probability model using a binary classification task in the same way as in negative sampling but using a Bayesian formalism for logistic regression.
 Specifically, before the training, we know that $1$ in $1+k$ words is sampled from the given data, which can be modeled as prior probabilities
@@
 	\label{eq:prior}
-	P_0(Y_{j} = 1) = \frac{1}{k + 1},\quad P_0(Y_{j} = 0) = \frac{k}{k + 1},
+	P_0(Y_{j} = 1) = \frac{1}{k + 1},\quad P_0(Y_{j} = 0) = \frac{k}{k + 1}.
 \end{align}
@@
 	}{
-		P_0(Y_j)
+		P\left(j \vert Y_{j} = 0\right)P(Y_{j} = 0)
+		+ P\left(j \vert Y_{j} = 1\right)P(Y_{j} = 1)
 	}.
@@
 Bearing in mind that word $j$ is sampled from the given data if $Y_{j}=1$ and from the noise distribution $p_0$ if $Y_j = 0$.
-Assuming that the given data is generated from the probability model to be fit, the class-conditional probability, $P\left(j \vert Y_{j}\right)$, is given by
+Assuming that the given data is generated from the probability model to fit, the class-conditional probability, $P\left(j \vert Y_{j}\right)$, is given by
 \begin{align}
@@
 	\label{eq:nce}
-	P^{NCE}\left(Y_{j} = 1 \vert j\right) = \frac{
+	P\left(Y_{j} = 1 \vert j\right) & =
+	\frac{
+		P_m(\vect{u}_j \cdot \vect{v}_{i}) / (k + 1)
+	}{
+		P_m(\vect{u}_j \cdot \vect{v}_{i}) / (k + 1)  + kp_0(j) / (k + 1)
+	}                                          \\
+	                                & = \frac{
 		P_m(\vect{u}_j \cdot \vect{v}_{i})
@@
 	\label{eq:nce}
-	P^{NCE}\left(Y_{j}=1 \vert j\right) = \frac{
+	P\left(Y_{j}=1 \vert j\right) =
+	 & = \frac{
+		1
+	}{
+		1 + kp_0(j) / P_m(\vect{u}_j \cdot \vect{v}_{i})
+	}           \\
+	 & = \frac{
+		1
+	}{
+		1 + \exp\left[ \ln kp_0(j) - \ln P_m(\vect{u}_j \cdot \vect{v}_{i}) \right]
+	}           \\
+	 & = \frac{
 		1
@@
 \end{align}
-where $c = -\ln k + \ln\sum_{ x' \in {\cal X}} f(x') $ is a constant.
+where $c = \ln k + \ln\sum_{ x' \in {\cal X}} f(x') $ is a constant.
 NCE maximizes the log-likelihood
@@
 	\label{eq:log-likelihood-logistic-regress}
-	{\cal J}^{\text{NCE}} _j = \sum_{j \in {\cal D}} \left[ Y_{j} \log P^{NCE}(Y_{j} = 1\vert j) + (1-Y_{j}) \log P^{NCE}(Y_{j} = 0 \vert j)\right].
+	{\cal J}^{\text{NCE}} = \sum_{i \in {\cal A}}\sum_{j \in {\cal D}} \left[ Y_{j} \log P(Y_{j} = 1\vert j) + (1-Y_{j}) \log P(Y_{j} = 0 \vert j)\right].
 \end{align}
@@
 		1 + \exp\left[ - \ln f(\vect{u}_j \cdot \vect{v}_{i}) + \ln p_0(j) + c \right]
-	}.
+	},
 \end{align}
@@
 \begin{align}
-	f(\vect{u}_j \cdot \vect{v}_{i}) = \exp\left( \vect{u}_j \cdot \vect{v}_{i} + \ln p_0(j) + c\right).
+	f(\vect{u}_j \cdot \vect{v}_{i}) = \exp\left( \vect{u}_j \cdot \vect{v}_{i} + \ln p_0(j) + c\right),
 \end{align}
@@
 	                                        & = \frac{  p_0(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{\sum_{j' \in \mathcal{A}}  p_0(j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})},                                                                      \\
-	                                   & = \frac{  P^\gamma(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{\sum_{j' \in \mathcal{A}}  P^\gamma(j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})} \hspace{0.3cm}(\because p_0(\ell) \propto P^\gamma (\ell)),
+	                                        & = \frac{  P^\gamma(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{\sum_{j' \in \mathcal{A}}  P^\gamma(j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})} \hspace{0.3cm}(\because p_0(\ell) \propto P^\gamma (\ell)).
 \end{align}
-where  $P(j)$ is the fraction of $j$ in the data. Taking together, conditional probability of SGNS \textit{word2vec} actually optimize is
+Taken together, the conditional probability that SGNS \textit{word2vec} actually optimizes is
 \begin{align}

### 2021-03-09 paper/rebuttal/rebuttal.tex
minor edit
change law to the model in letter

@@
 \vspace{-0.1cm}
-We address the first point by presenting the mathematical equivalence between the Gravity Model of Mobility and the skip-gram negative sampling \textit{word2vec} model.
-Namely, we demonstrate that \textit{word2vec}'s objective function is equivalent to the gravity law and thus \textit{word2vec} learns gravity-like relationships between entities, whether it be language or locations.
+We address the first point by presenting a mathematical equivalence between the Gravity Model of Mobility and the skip-gram negative sampling \textit{word2vec} model.
+Namely, we demonstrate that \textit{word2vec}'s objective function is equivalent to the gravity model and thus \textit{word2vec} learns gravity-like relationships between entities, whether it be language or locations.
 This development constitutes a major breakthrough in our understanding of neural embeddings, and provides theoretical justification for their application to mobility.
 
-For the second point, we have conducted experiments comparing the performance of neural embedding to (\romannum{1}) a singular value decomposition of the mobility network,  (\romannum{2}) a Laplacian eigenmap embedding  (\romannum{3}) a \textit{word2vec} model with matrix factorization,  and  (\romannum{4}) a direct optimization according at the gravity law.
+For the second point, we have conducted experiments comparing the performance of neural embedding to (\romannum{1}) a singular value decomposition of the mobility network,  (\romannum{2}) a Laplacian eigenmap embedding  (\romannum{3}) a \textit{word2vec} model with matrix factorization,  and  (\romannum{4}) a direct optimization according at the gravity model.
 We find that the embedding distance from \textit{word2vec} outperforms all baselines, even the direct optimization of gravity law with the multidimensional scaling, in explaining and predicting real-world mobility.

### 2021-03-09 paper/rebuttal/rebuttal.tex
add bib

--- 2021-03-08 paper/rebuttal/rebuttal.tex
@@
 	We agree that the revolution in neural embeddings offers great promise in mobility and look forward to reading and also working on these future studies; however, we argue that our contribution is most well-founded, and best serves the scientific community, by working with simpler and more established models (see Section 2, this letter), especially concerning the mathematical link we uncovered.
-Moreover, these deep models require a tremendous amount of training data ($\sim$3 billion words in Bert) and model parameters, making their use infeasible in applicants most
+Moreover, these deep models require a tremendous amount of training data ($\sim$3 billion words in Bert) and model parameters, making their use infeasible in applicants most.
 
@@
 
-	However, while these topics are exciting, we believe that that they fall outside the scope of the current manuscript, especially given the discoveries we made concerning a fundamental connection between the gravity law of mobility and \textit{word2vec}, which adds a substantial amount of new result to the manuscript.
+	However, while these topics are exciting, we believe that that they fall outside the scope of the current manuscript, especially given the discoveries we made concerning a fundamental connection between the gravity law of mobility and \textit{word2vec}, which adds a substantial amount of new results to the manuscript.
 }

### 2021-03-09 paper/rebuttal/rebuttal.tex
fix notation and typos

--- 2021-03-08 paper/rebuttal/rebuttal.tex
@@
 Although negative sampling is the most common approximation, it is a biased estimator~\autocite{Chia2010,Dyer2014} that does not yield the optimal embeddings in terms of the objective function, ${\cal J}$.
-This bias in negative sampling turns out to be a critical piece that connects wor2vec and the gravity model.
+This bias in negative sampling turns out to be the critical piece that connects word2vec and the gravity model.
 
@@
 In \textit{word2vec}, the noise distribution is given by $p_0(\ell) \propto P^\gamma (\ell)$, where $P(j)$ is the fraction of $j$ in the data, and $\gamma$ is a hyper-parameter.
-Then, for the sampled words, we fit a logistic regression model:
+Then, for the sampled words, we fit a logistic regression model
 \begin{align}
 	\label{eq:logistic-regress}
-	P(Y_{j} = 1; \vect{v}_{i}, \vect{u}_j) = \frac{1}{1 + \exp(-\vect{u}_j \cdot \vect{v}_{i})},
+	P^{\text{NS}}(Y_{j} = 1; \vect{v}_{i}, \vect{u}_j) = \frac{1}{1 + \exp(-\vect{u}_j \cdot \vect{v}_{i})},
 \end{align}
@@
 	\label{eq:log-likelihood-logistic-regress}
-	{\cal J}^{\text{NS}} = \sum_{i \in {\cal A}} \sum_{j \in {\cal D}} \left[ Y_{j} \log P(Y_{j} = 1; \vect{v}_{i}, \vect{u}_j) + (1-Y_{j}) \log P(Y_{j} = 0; \vect{v}_{i}, \vect{u}_j)\right],
+	{\cal J}^{\text{NS}} = \sum_{i \in {\cal A}} \sum_{j \in {\cal D}} \left[ Y_{j} \log P^{\text{NS}}(Y_{j} = 1; \vect{v}_{i}, \vect{u}_j) + (1-Y_{j}) \log P^{\text{NS}}(Y_{j} = 0; \vect{v}_{i}, \vect{u}_j)\right],
 \end{align}
@@
 \end{align}
-where $f$ is the non-negative likelihood function of data $x$, and ${\cal X}$ is the set of all data.
+where $f$ is a non-negative likelihood function of data $x$, and ${\cal X}$ is the set of all data.
 This general form includes the word2vec model (Eq.~\eqref{eq:cond_prob_w2v}), where $f(x) = \exp(x)$ and $x = \vect{u}_j \cdot \vect{v}_{i}$.
@@
 	\label{eq:prior}
-	P_0(Y_{j} = 1) = \frac{1}{k + 1},\quad P_0(Y_{j} = 0) = \frac{k}{k + 1}.
+	P(Y_{j} = 1) = \frac{1}{k + 1},\quad P(Y_{j} = 0) = \frac{k}{k + 1}.
 \end{align}
@@
 	\label{eq:nce}
-	P\left(Y_{j}=1 \vert j\right) =
+	P^{\text{NCE}}\left(Y_{j}=1 \vert j\right) =
 	 & = \frac{
@@
 	\label{eq:log-likelihood-logistic-regress}
-	{\cal J}^{\text{NCE}} = \sum_{i \in {\cal A}}\sum_{j \in {\cal D}} \left[ Y_{j} \log P(Y_{j} = 1\vert j) + (1-Y_{j}) \log P(Y_{j} = 0 \vert j)\right].
+	{\cal J}^{\text{NCE}} = \sum_{i \in {\cal A}}\sum_{j \in {\cal D}} \left[ Y_{j} \log P^{\text{NCE}}(Y_{j} = 1\vert j) + (1-Y_{j}) \log P^{\text{NCE}}(Y_{j} = 0 \vert j)\right].
 \end{align}

### 2021-03-09 paper/current/main.tex
update math part in menuscript

@@
      }
+\newcommand{\vect}[1]{\boldsymbol{#1}}
 
@@
 
-Why does the embedding distance predict actual mobility flows better than the geographic distance?
-Here, we demonstrate that the SGNS model and the gravity model of mobility are mathematically equivalent, explaining its ability to learn gravity-like relationships between locations.
+Why does \textit{word2vec} with the skip-gram with negative sampling model (SGNS) work so well to model mobility?
+Here, we demonstrate that the SGNS model and the gravity model of mobility are mathematically equivalent.
 
@@
 A target location $a_t=i$ is considered to have a context location $a_{t'}=j$ that appears in the previous or subsequent $w$ locations in the trajectory, \ie  $j \in [a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}]$.
-	{\it Word2vec} learns an embedding by estimating the probability that location $i$ has context $j$:
+	{\it word2vec} learns an embedding by estimating the probability that location $i$ has context $j$:
 \begin{align}
@@
 	\label{eq:flow_w2v}
-	\hat{T}_{ij} = P(i) P(j\given i) = \frac{P(i)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
+	\hat{T}_{ij} \propto P(i) P(j\given i) = \frac{P(i)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
 \end{align}
-where $P(i)$ is the probability that location $i$ appears in the trajectory.
-Because computing $Z_i$ is computationally demanding, multiple approximation methods have been proposed, the most popular being negative sampling~\autocite{mikolov2013word2vec}.
-Negative sampling finds embedding vectors by solving a binary classification task in which the model classifies whether a given target-context location pair $(i, j)$ comes from the data or from artificially generated ``negative'' samples.
-The negative pair $(i,j)$ is sampled in proportion to $P^\gamma(j)$ with parameter $\gamma \geq 0$.
+where $P(j)$ is the fraction of $j$ in the data.
+In general, calculating $Z_i$ is computationally expensive and there are two common approximation: hierarchical softmax \autocite{morin2005hierarchical} and negative sampling \autocite{mikolov2013word2vec}.
+Due to its simplicity and performance, negative sampling is the most widely used strategy, which we also adopt in our study.
 
-As a heuristic, the negative sampling has a bias and maximizes a different objective function~\autocite{Gutmann2010}.
-When taking into account this bias, {\it word2vec} with the negative sampling fits a probability model given by
+Although negative sampling is the most common approximation, it is a biased estimator~\autocite{Chia2010,Dyer2014} and fits the different probability model.
+When taking into account this bias, {\it word2vec} with the skip-gram and negative sampling fits a probability model given by
 \begin{align}
-	P\left(j \given i \right):= \frac{P^ \gamma(j) \exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:prob_w2v_ng0}
+	P\left(j \given i \right):= \frac{P^ \gamma(j) \exp(\bm{u}_j \cdot \bm{v}_{i})}{Z'_i}, \label{eq:prob_w2v_ng0}
 \end{align}
-where we redefine the normalization constant as $Z_i=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$. (See the Methods for the full derivation).
+where we redefine the normalization constant as $Z'_i=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
+(See the Methods and Supporting Information for the full derivation).
 
-Parameter $\gamma=1$ is a choice that ensures that when the embedding dimension is sufficiently large, there exists optimial in-vectors and out-vectors such that $\bm{u}_i = \bm{v}_i$~\autocite{levy2014neural}.
-Setting $\gamma = 1$ and substituting $\bm{u}_i = \bm{v}_j$ into Eq.~\eqref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
+Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimial in-vectors and out-vectors such that $\vect{v}_i = \vect{u}_i$ \autocite{levy2014neural}.
+Setting $\gamma = 1$ and substituting $\vect{v}_i = \vect{u}_i$ into Eq.~\ref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
 \begin{align}
-	\hat{T}_{ij}= P(i) P(j\given i) = \frac{P(i)P(j)\exp(\bm{v}_j \cdot \bm{v}_{i})}{Z_i}. \label{eq:flow_w2v_ng1}
+	\widehat{T}_{ij} \propto  P(i) P(j\given i) = \frac{P(i)P(j)\exp(\vect{v}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:flow_w2v_ng1}
 \end{align}
-The flow $\hat{T}_{ij}$ is symmetric (\ie $\hat{T}_{ij}=\hat{T}_{ji}$) because {\it word2vec} neglects whether the context $j$ appears before or after the target $i$ in the trajectory.
-If we swap $i$ and $j$ in Eq.~\eqref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
-Therefore, to ensure $\hat{T}_{ij} = \hat{T}_{ji}$, the denominator $Z_i$ must be a constant.
+
+The flow $\widehat{T}_{ij}$ is symmetric (\ie $\widehat{T}_{ij}=\widehat{T}_{ji}$) because the skip-gram model neglects whether the context $j$ appears before or after the target $i$ in the trajectory.
+If we swap $i$ and $j$ in Eq.~\ref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
+Therefore, to ensure $\widehat{T}_{ij}=\widehat{T}_{ji}$, the denominator $Z_i$ should be a constant.
 
@@
 \begin{align}
-	\hat{T}_{ij}=  C P(i) P(j)  \exp(\bm{v}_j \cdot \bm{v}_{i}), \label{eq:flow_w2v_ng0}
+	\hat{T}_{ij}=  C P(i) P(j)  \exp(\bm{v}_j \cdot \bm{v}_{i}). \label{eq:flow_w2v_ng0}
 \end{align}
-where $C$ is a positive constant.
-In other words, \emph{word2vec with the negative sampling is equivalent to the gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
-While the gravity model generates mobility flow from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given mobility flow.
+
+In other words, \emph{word2vec with the skip-gram negative sampling is equivalent to the gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
+While the gravity model predicts mobility flows from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given mobility flow.
 Therefore, the embedding distance is inherently tied to the mobility flow, and hence, has greater predictive power than the geographic distance and other baselines.
 
-In practice, because we do not have unlimited amounts of data (which is also noisy) and the optimization may not find the true optimum, the idealized result may not hold. 
-Indeed, we tend to find that the in- and out-vectors tend to be different and that the cosine similarity tends to better capture real-world mobility than the dot similarity.
+In practice, because we only have limited amounts of noisy data and the optimization may not find the true optimum, the mathematical result may not hold.
+Indeed, we find that the in- and out-vectors tend to be different and that the cosine similarity tends to better capture real-world mobility than the dot similarity.
 This result echos other applications of word embedding, such as word analogy testing~\autocite{levy2015improving}, in which cosine distance also outperformed dot similarity.
 Nevertheless, a model with dot similarity is still the second best after cosine similarity (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and the embedding distance still outperforms all alternatives we considered.
-Although finding an optimal embedding is difficult in practice, careful tuning of the optimization algorithm would close the gap between our mathematical and numerical results.
 
@@
 Negative sampling trains {\it word2vec} using a binary classification task as follows.
-A target-context word pair $(i,j)$ is sampled from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$ are sampled from a noise distribution $p_0(\ell)=P^\gamma(\ell)$.
-($P(j)$ is the fraction of $j$ in the data, and $\gamma>0$ is a parameter).
+A target-context word pair $(i,j)$ is sampled from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$ are sampled from a noise distribution $p_0(\ell)=f(\ell)^\gamma / \sum_{\ell'}{f(\ell')^\gamma} $.
+($f(\ell)$ is frequency of $\ell$ in the dataset, $\gamma>0$ is a parameter).
 Then, given a target-context word pair $(i,j)$, the model predicts whether it is a positive or negative sample using sigmoid function:

### 2021-03-09 paper/current/main.tex
remove redundant para

@@
 \begin{equation}
-	\frac{1}{T}\sum_{t = 1}^{T} \sum_{-w \leq \tau \leq w, \tau \neq 0} \log p(a_{t + \tau} \vert a_{t}),
+	{\cal J} = \frac{1}{T}\sum_{t = 1}^{T} \sum_{-w \leq \tau \leq w, \tau \neq 0} \log p(a_{t + \tau} \vert a_{t}),
 \end{equation}
@@
 For scientific mobility, across each training iteration, the order of organizations within a single year is randomized to remove unclear sequential order.
-
-There is an alternative implementation of \textit{word2vec} based on a matrix factorization~\autocite{levy2014neural,Qiu2018}, which optimizes the same objective function as for \texttt{gensim} but in a different way.
-The matrix factorization approach generates embedding vectors such that the dot similarity for locations $i$ and $j$ is as close as $q_{ij}= \log(T_{ij} / s_i s_j) + \text{const}$.
-An issue is that the generated embedding vectors can be largely affected by small flows $T_{ij}$ in the data.
-For example, if there is no flow between locations $i$ and $j$ (\ie, $T_{ij} = 0$), then $q_{ij} = -\infty$, pushing $i$ and $j$ to the infinite horizon of the embedding space.
-To remedy this problem, one can add a small amount of flow between such locations or exclude them from the embedding~\autocite{levy2014neural,Qiu2018}.
-However, this may change the data to which we fit the model, and small flows may still have profound impact on the embedding space.
-Therefore, we adopt the \texttt{gensim} implementation of the \textit{word2vec}.
-Our simulations show that, in the prediction task of mobility flow, \texttt{gensim}'s word2vec performs better than the matrix factorization approach in xxx out of the xxx datasets (Fig.~??).
 

### 2021-03-09 paper/current/main.tex
split math part and move detail derivation to the supp

@@
 
-Negative sampling is a biased estimator~\autocite{Chia2010,Dyer2014} that optimizes a distinct model  from {\it word2vec}.
 Negative sampling trains {\it word2vec} using a binary classification task as follows.
-A target-context word pair $(i,j)$ is sampled from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$ are sampled from a noise distribution $p_0(\ell)=f(\ell)^\gamma / \sum_{\ell'}{f(\ell')^\gamma} $.
-($f(\ell)$ is frequency of $\ell$ in the dataset, $\gamma>0$ is a parameter).
-Then, given a target-context word pair $(i,j)$, the model predicts whether it is a positive or negative sample using sigmoid function:
+For each target word $i$, we sample a context word $j$ from the given data and label it as positive, denoted by $Y_{j}=1$.
+Then, we sample $k$ words $\ell$ from a noise distribution $p_0(\ell)$ and label them as negative, denoted by $Y_{\ell}=0$.
+In \textit{word2vec}, the noise distribution is given by $p_0(\ell) \propto P^\gamma (\ell)$, where $P(j)$ is the fraction of $j$ in the data, and $\gamma$ is a hyper-parameter.
+Then, for the sampled words, we fit a logistic regression model
 \begin{align}
-	\label{eq:sigmoid}
-	\frac{1}{1 + \exp\left( - \bm{u}_j \cdot \bm{v}_i \right)}.
+	\label{eq:logistic-regress}
+	P^{\text{NS}}(Y_{j} = 1; \vect{v}_{i}, \vect{u}_j) = \frac{1}{1 + \exp(-\vect{u}_j \cdot \vect{v}_{i})},
 \end{align}
+by maximizing the log-likelihood:
+\begin{align}
+	\label{eq:log-likelihood-logistic-regress}
+	{\cal J}^{\text{NS}} = \sum_{i \in {\cal A}} \sum_{j \in {\cal D}} \left[ Y_{j} \log P^{\text{NS}}(Y_{j} = 1; \vect{v}_{i}, \vect{u}_j) + (1-Y_{j}) \log P^{\text{NS}}(Y_{j} = 0; \vect{v}_{i}, \vect{u}_j)\right],
+\end{align}
+where ${\cal D}$ is the set of all sampled context words.
 
 This procedure does not guarantee that the embedding optimally converges, even when increasing the training samples and iterations~\autocite{Chia2010,Dyer2014}.
-This problem is addressed by the noise contrastive estimation (NCE) \autocite{Chia2010}, which fits a probability model in the form:
+To make this bias explicit, let us consider the unbiased variant of negative sampling, \ie the noise contrastive estimation (NCE)~\autocite{Chia2010,Dyer2014}.
+NCE is an unbiased estimator for a probability model $P_m$ of the form:
+\begin{align}
+	\label{eq:nce-model}
+	P_m(x) = \frac{ f(x) }{\sum_{ x' \in {\cal X}} f(x') },
+\end{align}
+where $f$ is a non-negative likelihood function of data $x$, and ${\cal X}$ is the set of all data. NCE fits a logistic regression model:
 \begin{align}
 	\label{eq:nce}
-	f(x) / \sum_{x'} f(x'),
+	P^{\text{NCE}}\left(Y_{j}=1 \vert j\right) = \frac{
+		1
+	}{
+		1 + \exp\left[ - \ln f(\vect{u}_j \cdot \vect{v}_{i})  + \ln p_0(j) + c \right]
+	},
 \end{align}
-where $f(x)$ is the non-normalized probability for an instance $x$.
-As in negative sampling, NCE fits the model based on a binary classification task, with positive and negative samples randomly drawn from the given data and a noise distribution $p_0$, respectively, using a bias-corrected sigmoid function:
+where $c = \ln k + \ln\sum_{ x' \in {\cal X}} f(x') $ is a constant and maximizes the log-likelihood
 \begin{align}
-	\label{eq:sigmoid2}
-	\frac{1}{1 + \exp\left( -f(x) + \log p_0(x) \right)}.
+	\label{eq:log-likelihood-logistic-regress}
+	{\cal J}^{\text{NCE}} = \sum_{i \in {\cal A}}\sum_{j \in {\cal D}} \left[ Y_{j} \log P^{\text{NCE}}(Y_{j} = 1\vert j) + (1-Y_{j}) \log P^{\text{NCE}}(Y_{j} = 0 \vert j)\right].
 \end{align}
-In case of the {\it word2vec}, the instance is the dot similarity $x=\bm{u}_i \cdot \bm{v}_j$,  $f(x)=\exp(x)$, and $p_0(j)=P^\gamma(j)$.
+by calculating the gradients for embedding vectors $\vect{u}_j$, $\vect{v}_{i}$ and iteratively updating them.
+Note that NCE is an unbiased estimator that has convergence to the optimal embedding in terms of the original word2vec's objective function, ${\cal J}$~\autocite{Chia2010,Dyer2014} if we increase the number of words to sample and the training iterations.
 
-Rewriting the sigmoid function for the negative sampling (Eq.~\eqref{eq:sigmoid}) in form of the bias-corrected sigmoid function yields
+Let us revisit negative sampling from the perspective of NCE.
+We rewrite the logistic regression model in negative sampling (Eq.~\eqref{eq:logistic-regress}) in form of the posterior probability:
 \begin{align}
-	\label{eq:sigmoid3}
-	\frac{1}{1 + \exp\left[ - \tilde f(x) + \log p_0(x)  \right]},
+	P^{NS}\left(Y_{j}=1 \vert j\right) & = \frac{
+		1
+	}{
+		1 + \exp\left[ - \left( \vect{u}_j \cdot \vect{v}_{i} + \ln p_0(j) + c \right) + \ln p_0(j) + c \right]
+	}                                             \\
+	                                   & = \frac{
+		1
+	}{
+		1 + \exp\left[ - \ln f(\vect{u}_j \cdot \vect{v}_{i}) + \ln p_0(j) + c \right]
+	},
 \end{align}
-where we have defined
+where we define the likelihood function $f$ by
 \begin{align}
-	\label{eq:unnormalized}
-	\tilde f(x) = f(x) p_0(x).
+	f(\vect{u}_j \cdot \vect{v}_{i}) = \exp\left( \vect{u}_j \cdot \vect{v}_{i} + \ln p_0(j) + c\right),
 \end{align}
-This bias-corrected sigmoid function fits a probability model:
+which is the unbiased estimator for the probability model
 \begin{align}
-	f'(x) / \sum_{x'} f'(x),
+	\label{eq:unbiasef}
+	P_m^{NS}(\vect{u}_j \cdot \vect{v}_{i}) & = \frac{ f(\vect{u}_j \cdot \vect{v}_{i}) }{\sum_{ j' \in {\cal A}} f(\vect{u}_{j'} \cdot \vect{v}_{i}) },                                                                                               \\
+	                                        & = \frac{  p_0(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{\sum_{j' \in \mathcal{A}}  p_0(j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})},                                                                      \\
+	                                        & = \frac{  P^\gamma(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{\sum_{j' \in \mathcal{A}}  P^\gamma(j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})} \hspace{0.3cm}(\because p_0(\ell) \propto P^\gamma (\ell)).
 \end{align}
-or, by substituting $x=\bm{u}_i \cdot \bm{v}_j$, $f(x)=\exp(x)$, and $p_0(j)=P^\gamma (j)$,
+Taken together, the conditional probability that SGNS \textit{word2vec} actually optimizes is
 \begin{align}
-	P\left(j \given i \right):= \frac{P^\gamma (j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
+	P^{NS}(j\given i) = P_m^{NS}(\vect{u}_j \cdot \vect{v}_{i})  =  \frac{  P^\gamma(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{Z'_i},
 \end{align}
-where $Z_i=\sum_{j' \in \mathcal{A}} P^\gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
+where $Z'_i=\sum_{j' \in \mathcal{A}}  P^\gamma(j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})$.
 

### 2021-03-09 paper/current/main.tex
add refer text

@@
 Third, neural embeddings are an inherently stochastic procedure, and so results may change across different iterations.
-We however, note that all results shown here are robust to this stochasticity, likely emerging from the limited ``vocabulary'' of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories).
+We note that all results shown here are robust to this stochasticity, likely emerging from the limited ``vocabulary'' of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories).
 Applications of \textit{word2vec }to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random fluctuations.
@@
 \end{align}
-by calculating the gradients for embedding vectors $\vect{u}_j$, $\vect{v}_{i}$ and iteratively updating them.
+by calculating the gradients for embedding vectors $\vect{u}_j$, $\vect{v}_{i}$ and iteratively updating them (see Supporting Information for full derivation).
 Note that NCE is an unbiased estimator that has convergence to the optimal embedding in terms of the original word2vec's objective function, ${\cal J}$~\autocite{Chia2010,Dyer2014} if we increase the number of words to sample and the training iterations.

### 2021-03-09 paper/current/supp.tex

@@
 \def\figdir{../Figs}
-
+\newcommand{\vect}[1]{\boldsymbol{#1}}
 % define a command to setup the format of supporting infomration figures and tables.
@@
 \begin{equation}
- M_{ij} = \log(\frac{N(i,j) |D|}{N(i) N(j)}) - \log(k),
+ M_{ij} = \log\left( \frac{N(i,j) |D|}{N(i) N(j)} \right)- \log k,
 \end{equation}
@@
 
+% S11 TEXT
+\paragraph*{S12 Text}
+\label{si:text:disambiguation}
+{\bf Derivation of Eq.\ref{eq:nce} - Noise Contrastive Estimation}
+
+The noise contrastive estimation (NCE)~\autocite{Chia2010,Dyer2014}.
+NCE is an unbiased estimator for a probability model $P_m$ of the form:
+\begin{align}
+	\label{eq:nce-model}
+	P_m(x) = \frac{ f(x) }{\sum_{ x' \in {\cal X}} f(x') },
+\end{align}
+where $f$ is a non-negative likelihood function of data $x$, and ${\cal X}$ is the set of all data.
+This general form includes the word2vec model (Eq.~\eqref{eq:cond_prob_w2v}), where $f(x) = \exp(x)$ and $x = \vect{u}_j \cdot \vect{v}_{i}$.
+NCE fits the probability model using a binary classification task in the same way as in negative sampling but using a Bayesian formalism for logistic regression.
+Specifically, before the training, we know that $1$ in $1+k$ words is sampled from the given data, which can be modeled as prior probabilities
+\begin{align}
+	\label{eq:prior}
+	P(Y_{j} = 1) = \frac{1}{k + 1},\quad P(Y_{j} = 0) = \frac{k}{k + 1}.
+\end{align}
+Using the Bayes rule, the posterior probability for $Y_{j}$ given word $j$ is given by
+\begin{align}
+	\label{eq:posterior}
+	P\left(Y_{j} \vert j\right) = \frac{
+		P\left(j \vert Y_{j}\right)P(Y_{j})
+	}{
+		P\left(j \vert Y_{j} = 0\right)P(Y_{j} = 0)
+		+ P\left(j \vert Y_{j} = 1\right)P(Y_{j} = 1)
+	}.
+\end{align}
+Bearing in mind that word $j$ is sampled from the given data if $Y_{j}=1$ and from the noise distribution $p_0$ if $Y_j = 0$.
+Assuming that the given data is generated from the probability model to fit, the class-conditional probability, $P\left(j \vert Y_{j}\right)$, is given by
+\begin{align}
+	\label{eq:class-cond}
+	P(j \vert Y_{j} = 1) & = P_m(\vect{u}_j \cdot \vect{v}_{i}),
+	\quad
+	P(j \vert Y_{j} = 0)  = p_0 (j).
+\end{align}
+Putting Eqs.~\eqref{eq:prior}, \eqref{eq:posterior} and \eqref{eq:class-cond} together, the posterior probability for $Y_j$ is given by
+\begin{align}
+	\label{eq:nce}
+	P\left(Y_{j} = 1 \vert j\right) & =
+	\frac{
+		P_m(\vect{u}_j \cdot \vect{v}_{i}) / (k + 1)
+	}{
+		P_m(\vect{u}_j \cdot \vect{v}_{i}) / (k + 1)  + kp_0(j) / (k + 1)
+	}                                          \\
+	                                & = \frac{
+		P_m(\vect{u}_j \cdot \vect{v}_{i})
+	}{
+		P_m(\vect{u}_j \cdot \vect{v}_{i})  + kp_0(j)
+	},
+\end{align}
+which can be rewritten in form of sigmoid function:
+\begin{align}
+	\label{eq:nce}
+	P^{\text{NCE}}\left(Y_{j}=1 \vert j\right) =
+	 & = \frac{
+		1
+	}{
+		1 + kp_0(j) / P_m(\vect{u}_j \cdot \vect{v}_{i})
+	}           \\
+	 & = \frac{
+		1
+	}{
+		1 + \exp\left[ \ln kp_0(j) - \ln P_m(\vect{u}_j \cdot \vect{v}_{i}) \right]
+	}           \\
+	 & = \frac{
+		1
+	}{
+		1 + \exp\left[ - \ln f(\vect{u}_j \cdot \vect{v}_{i})  + \ln p_0(j) + c \right]
+	},
+\end{align}
+where $c = \ln k + \ln\sum_{ x' \in {\cal X}} f(x') $ is a constant.
+NCE maximizes the log-likelihood
+\begin{align}
+	\label{eq:log-likelihood-logistic-regress}
+	{\cal J}^{\text{NCE}} = \sum_{i \in {\cal A}}\sum_{j \in {\cal D}} \left[ Y_{j} \log P^{\text{NCE}}(Y_{j} = 1\vert j) + (1-Y_{j}) \log P^{\text{NCE}}(Y_{j} = 0 \vert j)\right].
+\end{align}
+by calculating the gradients for embedding vectors $\vect{u}_j$, $\vect{v}_{i}$ and iteratively updating them.
+An important consequence of this framework is that NCE is an unbiased estimator that has convergence to the optimal embedding in terms of the original word2vec's objective function, ${\cal J}$~ if we increase the number of words to sample and the training iterations \autocite{Chia2010,Dyer2014}.
+
 %
 % S12 TEXT
-\paragraph*{S12 Text}
+\paragraph*{S13 Text}
 \label{si:text:network_ranking}
@@
 % S13 TEXT
-\paragraph*{S13 Text}
+\paragraph*{S14 Text}
 \label{si:text:boomerang_speculation}
@@
 \clearpage
-
+\todo{@dakoda, could you update the table?}
 \begin{landscape}

### 2021-03-10 paper/rebuttal/rebuttal.tex
update letter

@@
 We acknowledge that our initial submission had a substantial gap regarding the choice of the \textit{word2vec} model, its connection with the gravity model of mobility, and its evaluation.
-While reflecting on these comments and our manuscript, we have made a theoretical breakthrough that addresses the primary issues;
+While reflecting on these comments and our manuscript, we have made a theoretical breakthrough that addresses the fundamental issues;
 namely, we have discovered \emph{a mathematical equivalence between the \textit{word2vec} (skip-gram with negative sampling) model and the gravity model.}
@@
 	\itemsep0em
-	\item The lack of theoretical justification and grounding for the application of \textit{word2vec} to mobility
+	\item The lack of theoretical justification and grounding for the application of \textit{word2vec}
 	\item The lack of simpler baselines to understand the performance of \textit{word2vec}
@@
 
-For the second point, we have conducted experiments comparing the performance of neural embedding to (\romannum{1}) a singular value decomposition of the mobility network,  (\romannum{2}) a Laplacian eigenmap embedding  (\romannum{3}) a \textit{word2vec} model with matrix factorization,  and  (\romannum{4}) a direct optimization according at the gravity law.
-We find that the embedding distance from \textit{word2vec} outperforms all baselines, even the direct optimization of gravity law with the multidimensional scaling, in explaining and predicting real-world mobility.
-
-Finally, addressing the third point, we have cooperated relevant literature to better ground our manuscript in the existing studies.
+For the second point, we have conducted experiments comparing the performance of neural embedding to (\romannum{1}) a singular value decomposition of the mobility network,  (\romannum{2}) a Laplacian eigenmap embedding  (\romannum{3}) a \textit{word2vec} model with matrix factorization,  and  (\romannum{4}) a direct optimization of the gravity model.
+We find that the embedding distance from \textit{word2vec} outperforms all baselines, even the direct optimization of gravity model with the multidimensional scaling, in explaining and predicting real-world mobility.
+
+Finally, addressing the third point, we have incorporated relevant literature to better ground our manuscript in the existing studies.
 

### 2021-03-10 paper/rebuttal/rebuttal.tex
reflect yy's comments

@@
 \clearpage
+\thispagestyle{empty}
 \newgeometry{margin=1in}
@@
 \tableofcontents
+\thispagestyle{empty}
 \clearpage
@@
 \label{sec:theory}
+\thispagestyle{empty}
 Why does \textit{word2vec} with the skip-gram with negative sampling model (SGNS) work so well to model mobility?
@@
 Although negative sampling is the most common approximation, it is a biased estimator~\autocite{Chia2010,Dyer2014} that does not yield the optimal embeddings in terms of the objective function, ${\cal J}$.
-This bias in negative sampling turns out to be the critical piece that connects word2vec and the gravity model.
+This bias in negative sampling turns out to be the key piece that connects word2vec and the gravity model.
 
@@
 by calculating the gradients for embedding vectors $\vect{u}_j$, $\vect{v}_{i}$ and iteratively updating them.
-An important consequence of this framework is that NCE is an unbiased estimator that has convergence to the optimal embedding in terms of the original word2vec's objective function, ${\cal J}$~\autocite{Chia2010,Dyer2014} if we increase the number of words to sample and the training iterations.
+An important consequence of this framework is that NCE is an unbiased estimator that has convergence to the optimal embedding in terms of the original word2vec's objective function, ${\cal J}$~\autocite{Chia2010,Dyer2014}, if we increase the number of words to sample and the training iterations.
 
@@
 \begin{align}
-	P^{NS}\left(Y_{j}=1 \vert j\right) & = \frac{
+	P^{\text{NS}}\left(Y_{j}=1 \vert j\right) & = \frac{
 		1
@@
 	\label{eq:unbiasef}
-	P_m^{NS}(\vect{u}_j \cdot \vect{v}_{i}) & = \frac{ f(\vect{u}_j \cdot \vect{v}_{i}) }{\sum_{ j' \in {\cal A}} f(\vect{u}_{j'} \cdot \vect{v}_{i}) },                                                                                               \\
+	P_m^{\text{NS}}(\vect{u}_j \cdot \vect{v}_{i}) & = \frac{ f(\vect{u}_j \cdot \vect{v}_{i}) }{\sum_{ j' \in {\cal A}} f(\vect{u}_{j'} \cdot \vect{v}_{i}) },                                                                                               \\
 	                                        & = \frac{  p_0(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{\sum_{j' \in \mathcal{A}}  p_0(j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})},                                                                      \\
@@
 \begin{align}
-	P^{NS}(j\given i) = P_m^{NS}(\vect{u}_j \cdot \vect{v}_{i})  =  \frac{  P^\gamma(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{Z'_i},
+	P^{\text{NS}}(j\given i) = P_m^{\text{NS}}(\vect{u}_j \cdot \vect{v}_{i})  =  \frac{  P^\gamma(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{Z'_i},\
 \end{align}
@@
 
-In practice, because we only have limited amounts of noisy data and the optimization may not find the true optimum, the mathematical result may not hold.
+In practice, because we only have limited amounts of noisy data and the optimization may not find the true optimum, the mathematical result may only approximately hold.
 Indeed, we find that the in- and out-vectors tend to be different and that the cosine similarity tends to better capture real-world mobility than the dot similarity.
@@
 	We carefully read out the Barthélemy, Physics Reports 499, 1, 2011, and referenced it in our manuscript.
-	Also, we report the performance of the flux estimation and prediction using different deterrence functions (see Section 2, above), finding that although the absolute values vary, the pattern doesn't change---the embedding distance robustly outperforms geographic distance regardless of the function used.
+		It has been argued that the power-law decay function fits well with the geographical distance because power-law gravity model is more suitable for analyzing large, complex, and scale-free spatial systems with long-range spatial memory, whereas exponential gravity model
+	fits well with the simpler system with no spatial memory~\autocite{chen2015distance}.
+	We report the performance of the flux estimation and prediction using different deterrence functions (see Section 2, above), finding that although the absolute values vary, the pattern doesn't change---the embedding distance robustly outperforms geographic distance regardless of the function used.
+Also, we shows why embedding distance fits well with exponential gravity model with the underling connection between \textit{word2vec} and the gravity model (see Section 1, above).
 	We add the following line to the methods noting this point,
@@
 		For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each cases though there is no qualitative difference---the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Supporting Information).}
-
-	We find the article that geographical distance ﬁts well with the power-law decay function because power-based gravity model can be more suitable for analyzing large, complex, and scale-free spatial systems with long-range spatial memory, while exponential-based gravity model
-	fits well with the simple system with no spatial memory~\autocite{chen2015distance}.
-	However, the embedding distance fits well with the exponential decay function, perhaps demonstrating that the real-world spatial complexity of mobility is encoded in the \textit{word2vec} embedding space as simpler pairwise distances, likely resulting from underlying connection we established between \textit{word2vec} and the gravity model (see Section 1, above).
 
@@
 	Thank you for this comment.
-	We however, do not believe that this is a problem in our analysis.
+	We do not, however, believe that this is a problem in our analysis.
 	Raw co-occurrence, which is used to define our ``flux'' between organizations, is always calculated using all organizations in a trajectory, and so window size does not affect flux.
@@
 	What is notable about our findings, therefore, is that even though a model trained with $w = 1$ generates fewer training samples, it still outperforms settings with $w > 1$, which use more training samples, and which should capture higher-order structures in the data.
-	We speculate that this is because the word2vec model with $w = 1$ is equvelant to the gravity model of mobility (see Section 1).
+	We speculate that this is because the word2vec model with $w = 1$ is equivalent to the gravity model of mobility (see Section 1).
 }
@@
 	There are previous studies on the optimal dimensionality of word embedding \autocite{yin2018understand, yin2018dimensionality}. Also,
-	we note that in previous work from our group, we explored the optimal dimensions for graph embedding~\autocite{gu2020dimensions}, finding that while a sufficient number of dimensions is necessary to capture the structure, increasing the dimensions does not detract from performance, a property common across deep learning methods.
+	we note that in previous work from our group, we explored the optimal dimensions for graph embedding~\autocite{gu2020dimensions}, finding that while a sufficient number of dimensions is necessary to capture the structure, increasing the dimensions does not heavily deteriorate from performance, a property common across deep learning methods.
 	Given that there is little performance difference between $d = 100$ and $d = 300$, we opt to use the larger embeddings at $d = 300$, which are large enough to capture the complexity of mobility, yet small enough to allow an efficient computational workflow.
@@
 	We think that there is a great deal of potential in methods like BERT for representing mobility data.
-	What initially drew us to \textit{word2vec}, however, was its simplicity, its ubiquity, and its mathematical tractability (at least compared to other, more sophisticated approaches).
-	This last attribute proved very useful, as in exploring the mathematical properties of the model, we discovered a deep connection between \textit{word2vec} and the gravity model of mobility, which explains why it learns such effective gravity-like relationships between entities (see Section 1, this letter).
-	We believe hat this new discovery, now included in the manuscript, justifies our use of \textit{word2vec} here.
+	What initially drew us to \textit{word2vec}, however, was its simplicity, ubiquity, and mathematical tractability (at least compared to other, more sophisticated approaches).
+	This last attribute proved very useful, as in exploring the mathematical properties of the model, we discovered a deep connection between \textit{word2vec} and the gravity model of mobility, which explains why it learns gravity-like relationships between entities (see Section 1, this letter).
+	We believe that this new discovery, now included in the manuscript, strongly ground our use of \textit{word2vec} here.
 
@@
 \response{Thank you for this suggestion.
-	We looked into this, using UMAP to reduce the country-level embeddings from 300 down to 30 dimensions, however the results from this were incomprehensible, and inferior to those using 300 dimensions.
+	We looked into this, using UMAP to reduce the country-level embeddings from 300 down to 30 dimensions, however the results from this were incomprehensible, much inferior to those using 300 dimensions.
 	Many dimensionality reduction techniques reduce the number of dimensions by maintaining pairwise distances between vectors, so that the result can be well-suited for clustering algorithms.
@@
 	In your particular example, an embedding distance trained using sequences of co-authorship on the same paper might be better to capture the \textit{collaborative} distance between institutions.
-	Then, using that distance, one could measure the ``embedding distance'' spanned by all authors in the byline, and relate this to questions impact to determine whether (a)typical collaborations relate to impact.
+	Then, using that distance, one could measure the ``embedding distance'' spanned by all authors in the byline, and answer the question whether typical collaborations relate to impact or not.
 	This is certainly a topic that is in our mind for future study.

### 2021-03-10 paper/rebuttal/rebuttal.tex
change some grammar error

@@
 Namely, we demonstrate that \textit{word2vec}'s objective function is equivalent to the gravity law and thus \textit{word2vec} learns gravity-like relationships between entities, whether it be language or locations.
-This development constitutes a major breakthrough in our understanding of neural embeddings, and provides theoretical justification for their application to mobility.
+This development constitutes a major breakthrough in our understanding of neural embeddings and provides a theoretical justification for their application to mobility.
 
@@
 This connection provides strong theoretical justification to our choice of \textit{word2vec}, and constitutes a major breakthrough of our understanding of neural embeddings.
-In addition, this motivates the use of SGNS for future study of human mobility.
+In addition, this motivates the use of SGNS for the future study of human mobility.
 
@@
 Indeed, we find that the in- and out-vectors tend to be different and that the cosine similarity tends to better capture real-world mobility than the dot similarity.
-Nevertheless, a model with dot similarity is still the second best after cosine similarity (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and the embedding distance still outperforms all alternatives we considered.
+Nevertheless, a model with dot similarity is still the second-best after cosine similarity (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and the embedding distance still outperforms all alternatives we considered.
 
@@
 \paragraph{Direct optimization of gravity model:} Finally, we create an embedding by optimizing for the gravity law directly.
-Specifically, we construct a gravity matrix of $N$ organizations, where each cell of the matrix is calculated as $T_{ij}/m_i m_j$, where $T_{ij}$ is co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory, and $m_i$ and $m_j$ are the organizations' populations, defined here as the mean annual member of unique mobile and non-mobile authors affiliated.
-We then embed the gravity matrix using two approaches: a truncated singular-vector decomposition (SVD), and with multidimensional scaling (MDS), which embeds each location in a N-dimensional space such that pairwise distances are preserved as well as possible.
-Typically, MDS uses euclidean distance to measure distance between vectors.
+Specifically, we construct a gravity matrix of $N$ organizations, where each cell of the matrix is calculated as $T_{ij}/m_i m_j$, where $T_{ij}$ is the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory, and $m_i$ and $m_j$ are the organizations' populations, defined here as the mean annual member of unique mobile and non-mobile authors affiliated.
+We then embed the gravity matrix using two approaches: a truncated singular-vector decomposition (SVD), and multidimensional scaling (MDS), which embeds each location in an N-dimensional space such that pairwise distances are preserved as well as possible.
+Typically, MDS uses euclidean distance to measure the distance between vectors.
 
@@
 However, to connect \textit{word2vec} to the gravity model of mobility, we assume $\gamma = 1.0$ (see Section 1).
-We now report all main results using $\gamma = 1.0$, however we also compare its performance to embeddings learned using $\gamma = 0.75$, as we do with the number of embedded dimensions and window size.
+We now report all main results using $\gamma = 1.0$ and also compare its performance to embeddings learned using $\gamma = 0.75$, as we do with the number of embedded dimensions and window size.
 We plot the performance of each combination of hyperparemters by their ability to explain real-world flux of scientific mobility (Fig.~\ref{fig:supp:hyperparameter}), and observe no noticeable difference in performance between values of $\gamma = 0.75$ and $\gamma = 1.0$.
 Figures in the updated manuscript have been re-drawn with $\gamma = 1.0$, and the findings remain qualitatively similar.
-As a side benefit, including the hyperparemter of $\gamma$ also effectively doubles the number of embeddings trained, and that results are so similar across different embedding provides further evidence of the robustness of the approach applied to our data.
+As a side benefit, including the hyperparameter of $\gamma$ also effectively doubles the number of embeddings trained, and that results are so similar across different embedding provides further evidence of the robustness of the approach applied to our data.
 
@@
 Our original manuscript defined the population of an organization as its average annual number of unique mobile and non-mobile authors who publish with that organizational affiliation.
-However, because non-mobile authors do not have mobility trajectories, and are thus not included in training of the embedding, this definition of population introduces additional, potentially confounding information into the experiment.
+However, because non-mobile authors do not have mobility trajectories, and are thus not included in the training of the embedding, this definition of population introduces additional, potentially confounding information into the experiment.
 To tease apart the impact of population definitions, we consider two additional definitions.
@@
 		All embedding-based methods use dimensions of 300.
-		Here, embedding distance is obtained from neural embeddings learned with window size of 1 and $\gamma = 1$.
+		Here, embedding distance is obtained from neural embeddings learned with a window size of 1 and $\gamma = 1$.
 		In all cases, organization population is defined as the mean annualized number of unique mobile and non-mobile authors, and flux is calculated for all global mobility.
@@
 
-We find that, using the best performing dimensions (300) and window size (1),  $\gamma = 1.0$, and for default experimental parameters (global mobility, population defined using all mobile and non-mobile scholars), that the embedding distance, or cosine distance between vectors learned through neural embedding, explains more of the flux, and leads to better predictions than other baselines (Fig.~\ref{fig:supp:distancemetrics}).
+We find that using the best performing dimensions (300) and window size (1),  $\gamma = 1.0$, and for default experimental parameters (global mobility, population defined using all mobile and non-mobile scholars), that the embedding distance or cosine distance between vectors learned through neural embedding, explains more of the flux, and leads to better predictions than other baselines (Fig.~\ref{fig:supp:distancemetrics}).
 This performance advantage holds across \emph{the exponential and the power-law forms of the gravity model of mobility}.
@@
 	They have now been incorporated into our manuscript's introduction.
-	Although there are existing work on trajectory-based mobility embedding, we argue that our new result establishing the mathematical equivalence of \textit{word2vec} and the gravity law, as well as our extensive evaluation with many baselines represents a novel and substantial contribution.
+	Although there are existing works on trajectory-based mobility embedding, we argue that our new result establishing the mathematical equivalence of \textit{word2vec} and the gravity law, as well as our extensive evaluation with many baselines represents a novel and substantial contribution.
 }
@@
 	Namely, we find that \emph{SGNS is a gravity model}.
-	This finding explains why SGNS performs so well, and demonstrates the utility of the model for studying contexts where gravity relationships are expected, such as in human mobility.
+	This finding explains why SGNS performs so well and demonstrates the utility of the model for studying contexts where gravity relationships are expected, such as in human mobility.
 	We refer you to Section 1 of this letter, above, for an investigation of this connection, and how we adjusted our manuscript given this breakthrough.
@@
 \response{Thank you for this comment.
-While robustness is a general concern for these methods, we found that their application to our datasets were in fact quite robust, and observed no evidence that findings were the result of methodological artefacts.
+While robustness is a general concern for these methods, we found that their application to our datasets were in fact quite robust, and observed no evidence that findings were the result of methodological artifacts.
 This is confirmed in extra work done in response to these reviews.
@@
 	About 8,661 organizations are represented across over three million career trajectories of scientists, such that nearly every organization appears enough times, and in enough contexts, to produce a robust vector representation.
-	However, this may not hold true for all problem domains—for example, natural language includes many millions of tokens, many of which will occur only a few times, allowing stochasticity to have a much stronger effect on the final representation.
+	However, this may not hold true for all problem domains—for example, the natural language includes many millions of tokens, many of which will occur only a few times, allowing stochasticity to have a much stronger effect on the final representation.
 	Heeding this as a general concern, we have added the following sentence to our limitations paragraph in our conclusion:
@@
 	For example, we state in figure 2's caption that \say{\textit{99\% confidence intervals are plotted for the mean flux in each bin based on a normal distribution.}}, which should give readers enough information to reproduce the confidence intervals following their standard definition.
-	Other confidence intervals, such as intervals for the loess regression line in figure 6, are calculated using the smoothing functions in the \texttt{ggplot2} package of R, and refer readers to the relevant documentation.
+	Other confidence intervals, such as intervals for the loess regression line in figure 6, are calculated using the smoothing functions in the \texttt{ggplot2} package of R and refer readers to the relevant documentation.
 }
@@
 	We carefully read out the Barthélemy, Physics Reports 499, 1, 2011, and referenced it in our manuscript.
-		It has been argued that the power-law decay function fits well with the geographical distance because power-law gravity model is more suitable for analyzing large, complex, and scale-free spatial systems with long-range spatial memory, whereas exponential gravity model
-	fits well with the simpler system with no spatial memory~\autocite{chen2015distance}.
+		It has been argued that the power-law decay function fits well with the geographical distance because the power-law gravity model is more suitable for analyzing large, complex, and scale-free spatial systems with long-range spatial memory, whereas the exponential gravity model fits well with the simpler system with no spatial memory~\autocite{chen2015distance}.
 	We report the performance of the flux estimation and prediction using different deterrence functions (see Section 2, above), finding that although the absolute values vary, the pattern doesn't change---the embedding distance robustly outperforms geographic distance regardless of the function used.
-Also, we shows why embedding distance fits well with exponential gravity model with the underling connection between \textit{word2vec} and the gravity model (see Section 1, above).
+Also, we show why embedding distance fits well with the exponential gravity model with the underlying connection between \textit{word2vec} and the gravity model (see Section 1, above).
 	We add the following line to the methods noting this point,
@@
 	\say{The decay function $f(r_{ij})$ defines the effect of distance, and so different decay functions can model fundamentally different mechanism [...] such as the cost functions for a given distance and the spatial granularity of the observation.
-		For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each cases though there is no qualitative difference---the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Supporting Information).}
+		For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case though there is no qualitative difference---the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Supporting Information).}
 
@@
 	Raw co-occurrence, which is used to define our ``flux'' between organizations, is always calculated using all organizations in a trajectory, and so window size does not affect flux.
-	Window size does affect \textit{word2vec}, however setting a smaller/larger window size should not make results incomparable.
+	Window size does affect \textit{word2vec} and setting a smaller/larger window size should not make results incomparable.
 	When we set $w = 1$, \textit{word2vec} will generate training pairs at most 1 position away from each target location, for all possible targets.
@@
 
-	To highlight the importance of altenrative models, however, we add the following line to our conclusion: \say{\textit{Future studies may also consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality.}}.
+	To highlight the importance of alternative models, however, we add the following line to our conclusion: \say{\textit{Future studies may also consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality.}}.
 
@@
 	Your recommendation of collaboration (based on the author byline) and advisor-student pairs are especially interesting, and we would aim to address these areas in future studies.
-	However, given the importance of mobility to science, the importance of human mobility more generally, and the connection we discovered between \textit{word2vec} and the gravity model, that a focus of co-affiliation, which most closely aligns with ideas of mobility, is the most reasonable data to use for this manuscript.
+	However, given the importance of mobility to science, the importance of human mobility more generally, and the connection we discovered between \textit{word2vec} and the gravity model, that a focus on co-affiliation, which most closely aligns with ideas of mobility, is the most reasonable data to use for this manuscript.
 }
@@
 \response{Thank you for this suggestion.
-	We looked into this, using UMAP to reduce the country-level embeddings from 300 down to 30 dimensions, however the results from this were incomprehensible, much inferior to those using 300 dimensions.
+	We looked into this, using UMAP to reduce the country-level embeddings from 300 down to 30 dimensions, however, the results from this were incomprehensible, much inferior to those using 300 dimensions.
 	Many dimensionality reduction techniques reduce the number of dimensions by maintaining pairwise distances between vectors, so that the result can be well-suited for clustering algorithms.
@@
 	We agree that comparing the radiation model would be incredibly interesting.
-	However, we originally did not use radiation model because our dataset on scientific mobility lacked clear directionality, which is required by the radiation model of mobility.
+	However, we originally did not use the radiation model because our dataset on scientific mobility lacked clear directionality, which is required by the radiation model of mobility.
 	Scientific mobility is incredibly complex, the most common form of mobility being co-affiliation, or a researcher holding multiple affiliations simultaneously.
@@
 	In your particular example, an embedding distance trained using sequences of co-authorship on the same paper might be better to capture the \textit{collaborative} distance between institutions.
-	Then, using that distance, one could measure the ``embedding distance'' spanned by all authors in the byline, and answer the question whether typical collaborations relate to impact or not.
-	This is certainly a topic that is in our mind for future study.
+	Then, using that distance, one could measure the ``embedding distance'' spanned by all authors in the byline and answer the question of whether typical collaborations relate to impact or not.
+	This is certainly a topic that is in our minds for future study.
 	In the case of scientific mobility, we might also consider the ``embedding distance'' spanned by an individual's career, and relate this to their demographics and scientific impact.
@@
 
-\response{This is an excellent idea, and one that we have been interesting in addressing as well.
-	Unfortunately, however, we do not have access to such data, at least not in large enough quantiaties to be representative.
+\response{This is an excellent idea and one that we have been interested in addressing as well.
+	Unfortunately, however, we do not have access to such data, at least not in large enough quantities to be representative.
 	Publications are on a time lag, compared to actual events.
 	For example, a researcher may write a paper while studying at university $A$, but then before the final paper is published, move to university $B$, so while they now have a $B$ affiliation, in our data all we see is the $A$ one.
-	As such, we would not necessarily expect to  see the impact of COVID on bibliometric data until later in 2021 or early 2022, when researchers have had the chance to publich with their new institution.
-	We also not that some activity will, of course, be visible, especially given the number of researchers rapidly publishing on the subject of COVID-19, however we consider this to be an unrepresentative sample, given that it is concentrated in a few disciplines.
+	As such, we would not necessarily expect to see the impact of COVID on bibliometric data until later in 2021 or early 2022, when researchers have had the chance to publish with their new institution.
+	We also not that some activity will, of course, be visible, especially given the number of researchers rapidly publishing on the subject of COVID-19, however, we consider this to be an unrepresentative sample, given that it is concentrated in a few disciplines.
 
 	In the future, however, we hope to have access to a fully-representative sample of mobility data to study the effects of COVID-19 on global scientific labor flows.
-	We can use techniqeus developed by other researchers, such as those used by Hamilton, Leskovec, \& Jurafsky \autocite{hamilton-etal-2016-diachronic}, to align embeddings trained on different data in order to quantify the changes in global mobility.
+	We can use techniques developed by other researchers, such as those used by Hamilton, Leskovec, \& Jurafsky \autocite{hamilton-etal-2016-diachronic}, to align embeddings trained on different data in order to quantify the changes in global mobility.
 	We look forward to approaching this, as well as other exciting projects in the future.

### 2021-03-10 paper/rebuttal/rebuttal.tex
remove header
law to the model

@@
 %
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-\lhead{Nature---Response to Reviews}
-\rhead{\thepage}
-\chead{}
 
@@
 We address the first point by presenting the mathematical equivalence between the Gravity Model of Mobility and the skip-gram negative sampling \textit{word2vec} model.
-Namely, we demonstrate that \textit{word2vec}'s objective function is equivalent to the gravity law and thus \textit{word2vec} learns gravity-like relationships between entities, whether it be language or locations.
+Namely, we demonstrate that \textit{word2vec}'s objective function is equivalent to the gravity model and thus \textit{word2vec} learns gravity-like relationships between entities, whether it be language or locations.
 This development constitutes a major breakthrough in our understanding of neural embeddings and provides a theoretical justification for their application to mobility.
@@
 \vspace{-0.3cm}
-\paragraph{Direct optimization of gravity model:} Finally, we create an embedding by optimizing for the gravity law directly.
+\paragraph{Direct optimization of gravity model:} Finally, we create an embedding by optimizing for the gravity model directly.
 Specifically, we construct a gravity matrix of $N$ organizations, where each cell of the matrix is calculated as $T_{ij}/m_i m_j$, where $T_{ij}$ is the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory, and $m_i$ and $m_j$ are the organizations' populations, defined here as the mean annual member of unique mobile and non-mobile authors affiliated.
@@
 	They have now been incorporated into our manuscript's introduction.
-	Although there are existing works on trajectory-based mobility embedding, we argue that our new result establishing the mathematical equivalence of \textit{word2vec} and the gravity law, as well as our extensive evaluation with many baselines represents a novel and substantial contribution.
+	Although there are existing works on trajectory-based mobility embedding, we argue that our new result establishing the mathematical equivalence of \textit{word2vec} and the gravity model, as well as our extensive evaluation with many baselines represents a novel and substantial contribution.
 }
@@
 			``Raw freq'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
-			Embedding distance, measured as the cosine distance between embedding vectors, explains more of the flux than baselines in nearly every case, except using raw frequency population and domestic and international mobility, where direct optimization of the gravity law works better, as well as Levy's factorization~\autocite{levy2014neural} for domestic and international only mobility.
+			Embedding distance, measured as the cosine distance between embedding vectors, explains more of the flux than baselines in nearly every case, except using raw frequency population and domestic and international mobility, where direct optimization of the gravity model works better, as well as Levy's factorization~\autocite{levy2014neural} for domestic and international only mobility.
 		}
@@
 			``Raw freq'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
-			Embedding distance, measured as the cosine distance between embedding vectors, results in better predictions for global mobility with ``All'; and ``Mobile only'' definitions of population, though direvt gravity-law opimization with MDS performs better when using raw frequencies to measure organization population, and Levy's factorization~\autocite{levy2014neural} perform better here with domestic and international only mobility.
+			Embedding distance, measured as the cosine distance between embedding vectors, results in better predictions for global mobility with ``All'; and ``Mobile only'' definitions of population, though direct optimization of the gravity model with MDS performs better when using raw frequencies to measure organization population, and Levy's factorization~\autocite{levy2014neural} perform better here with domestic and international only mobility.
 		}

### 2021-03-10 paper/current/main.tex
update main paper

@@
 To validate our approach, we evaluate the quality of vector representations with their performance in predicting real-world mobility flows using the gravity model framework~\autocite{zipf1946gravity}.
-The Gravity Model is a widely used mobility model~\autocite{curiel2018citygravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity} that models the \textit{expected flux}, $\hat{T}_{ij}$, between locations based on their populations and distance:
+The gravity model is a widely used mobility model~\autocite{curiel2018citygravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity} that connects the \textit{expected flux}, $\hat{T}_{ij}$, between locations based on their populations and distance:
 
@@
 For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}), though there is no qualitative difference---the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
-Beyond the fitting on the data, we would like to argue that geographical distance fits well with the power-law decay function because it is more suitable for analyzing large, complex, and scale-free spatial systems\autocite{chen2015distance}, while embedding distance fits well with the exponential decay function, which we will show later in the section of mathematical relation between \textit{word2vec}and the gravity model.
+Beyond the fitting on the data, we would like to argue that geographical distance fits well with the power-law decay function because it is more suitable for analyzing large, complex, and scale-free spatial systems\autocite{chen2015distance}, while embedding distance fits well with the exponential decay function, which we will show later in the section of mathematical relation between \textit{word2vec} and the gravity model.
 
@@
 The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores calculated from the underlying mobility network (Fig.~\ref{fig:supp:distancemetrics}, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurence matrix, Levy's symmetric \textit{word2vec}\autocite{levy2014neural}, and even direct optimization of the gravity model (Fig.~supp\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
-In sum, our results demonstrate that, consistently and efficiently , the embedding distance better captures patterns of actual mobility than does the geographic distance.
+The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurence matrix, Levy's symmetric \textit{word2vec}\autocite{levy2014neural}, and even direct optimization of the gravity model (Fig.\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+In sum, our results demonstrate that, consistently and efficiently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
 
@@
 
-Although negative sampling is the most common approximation, it is a biased estimator~\autocite{Chia2010,Dyer2014} and fits the different probability model.
+Although negative sampling is the most common approximation, it is a biased estimator~\autocite{Chia2010,Dyer2014} and fits a different probability model.
 When taking into account this bias, {\it word2vec} with the skip-gram and negative sampling fits a probability model given by
@@
 In other words, \emph{word2vec with the skip-gram negative sampling is equivalent to the gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
-While the gravity model predicts mobility flows from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given mobility flow.
+While the gravity model predicts mobility flows from the given mass and locations, {\it word2vec} finds locations that best explain the given mobility flow.
 Therefore, the embedding distance is inherently tied to the mobility flow, and hence, has greater predictive power than the geographic distance and other baselines.
 
-In practice, because we only have limited amounts of noisy data and the optimization may not find the true optimum, the mathematical result may not hold.
+In practice, because we only have limited amounts of noisy data and the optimization may not find the true optimum, the mathematical result may only approximately hold.
 Indeed, we find that the in- and out-vectors tend to be different and that the cosine similarity tends to better capture real-world mobility than the dot similarity.
 This result echos other applications of word embedding, such as word analogy testing~\autocite{levy2015improving}, in which cosine distance also outperformed dot similarity.
-Nevertheless, a model with dot similarity is still the second best after cosine similarity (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and the embedding distance still outperforms all alternatives we considered.
+Nevertheless, a model with dot similarity is still the second-best after cosine similarity (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and the embedding distance still outperforms all alternatives we considered.
 

### 2021-03-10 paper/current/supp.tex
add efficency

@@
 \label{si:text:Raw SVD}
-{\bf Singular vector decomposition distance.}
-
-We use the truncated singular vector decomposition (SVD) on the underlying mobility co-occurrence matrix as a baseline embedding.
+{\bf Singular valuer decomposition distance.}
+
+We use the truncated singular value decomposition (SVD) on the underlying mobility co-occurrence matrix as a baseline embedding.
 In short, truncated SVD performs linear low-rank approximation of the matrix with given dimensions, $d$.
@@
 We note that the MDS embedding actually has the lowest prediction error when organizations' populations are defined as the raw frequency during prediction with the power-law model (RMSE = $0.691$, Table~\ref{supp:table:rmse_power_table});
-however, we note that the MDS distnace is defined with a population of``All'' mobile and non-mobile scholars, whereas the predictions made in Table~\ref{supp:table:rmse_power_table} use the raw frequency, which likely confounds this result.
+however, we note that the MDS distnace is defined with a population of ``All'' mobile and non-mobile scholars, whereas the predictions made in Table~\ref{supp:table:rmse_power_table} use the raw frequency, which likely confounds this result.
+Also, running time of MDS ($\sim$ 30 mins) is substantially longer than that of \textit{word2vec} ($\sim$ 5 mins), which indicates our approach has advantages in terms of efficiency as well.
 

### 2021-03-10 paper/rebuttal/rebuttal.tex
add comment
removed p-b-p comments from the TOC in rebuttal

@@
 \tcbuselibrary{breakable}
-\newtcolorbox[list inside=toc]{sectionbox}[1]{colback=white,
+\newtcolorbox[]{sectionbox}[1]{colback=white,
  				       												 colframe=black,
@@
 \clearpage
-\thispagestyle{empty}
 \newgeometry{margin=1in}
@@
 \tableofcontents
-\thispagestyle{empty}
 \clearpage

### 2021-03-10 paper/rebuttal/rebuttal.tex
text weaks to rebuttal

@@
 \thispagestyle{empty}
-Why does \textit{word2vec} with the skip-gram with negative sampling model (SGNS) work so well to model mobility?
-Here, we demonstrate that the SGNS model and the gravity model of mobility are mathematically equivalent.
-This connection provides strong theoretical justification to our choice of \textit{word2vec}, and constitutes a major breakthrough of our understanding of neural embeddings.
+Why does the \textit{word2vec} with skip-gram and negative sampling (SGNS) model work so well to model mobility?
+Here, we demonstrate that SGNS and the gravity model of mobility are mathematically equivalent.
+This connection provides strong theoretical justification to our choice of \textit{word2vec} to model mobility, and constitutes a major breakthrough of our understanding of neural embeddings.
 In addition, this motivates the use of SGNS for the future study of human mobility.
@@
 \subsection{\textit{word2vec} algorithm}
-Imagine a trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), where $a_{t}$ is the $t$th location in the trajectory.
+Imagine a trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), where $a_{t}$ is the $t$\textsuperscript{th} location in the trajectory.
 A location, $a_{t}$, is considered to have context locations, $a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}$, that appear in the window surrounding $a_t$ up to a time lag of $w$, where $w$ is the window size parameter truncated at $t - w \geq 0$ and $t + w \leq T$.
-Then, the skip-gram \textit{word2vec} learns probability $p(a_{t + \tau} \vert a_{t})$, where $-w\leq \tau\leq w$ and $\tau \neq 0$,  by maximizing its log likelihood given by
+Then, the skip-gram \textit{word2vec} model learns probabilities $p(a_{t + \tau} \vert a_{t})$, where $-w\leq \tau\leq w$ and $\tau \neq 0$,  by maximizing its log likelihood given by
 %
@@
 where $\vect{v}$ and $\vect{u}$ are the ``in-vector'' and ``out-vector'', respectively,  $Z_i=\sum_{j' \in \mathcal{A}} \exp(\vect{u}_{j'} \cdot \vect{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
-In general, calculating $Z_i$ is computationally expensive and there are two common approximation:
+In general, calculating $Z_i$ is computationally expensive, so two kinds of approximations are commonly used:
 hierarchical softmax \autocite{morin2005hierarchical} and negative sampling \autocite{mikolov2013word2vec}.
@@
 Although negative sampling is the most common approximation, it is a biased estimator~\autocite{Chia2010,Dyer2014} that does not yield the optimal embeddings in terms of the objective function, ${\cal J}$.
-This bias in negative sampling turns out to be the key piece that connects word2vec and the gravity model.
+This bias in negative sampling turns out to be key to the connection between word2vec and the gravity model.
 
@@
 	\item We also added the section \textbf{An implicit bias in the negative sampling} to the methods section of our manuscript.
-	\item Since the formulation of the gravity used in the above derivations assumes $\gamma = 1$, we use $\gamma = 1$ for all reported results. No results have been substantively changed.
+	\item Since the formulation of the gravity used in the above derivations assumes $\gamma = 1$, we use $\gamma = 1$ for all reported results. No findings have substantively changed.
 	\item We added a sentence to the paper speculating on why cosine similarity works best.
@@
 	About 8,661 organizations are represented across over three million career trajectories of scientists, such that nearly every organization appears enough times, and in enough contexts, to produce a robust vector representation.
-	However, this may not hold true for all problem domains—for example, the natural language includes many millions of tokens, many of which will occur only a few times, allowing stochasticity to have a much stronger effect on the final representation.
+	However, this may not hold true for all problem domains—for example, natural language includes many millions of tokens, many of which will occur only a few times, allowing stochasticity to have a much stronger effect on the final representation.
 	Heeding this as a general concern, we have added the following sentence to our limitations paragraph in our conclusion:
@@
 
-\response{Thank you for pointing this out.
-	We carefully read out the Barthélemy, Physics Reports 499, 1, 2011, and referenced it in our manuscript.
-		It has been argued that the power-law decay function fits well with the geographical distance because the power-law gravity model is more suitable for analyzing large, complex, and scale-free spatial systems with long-range spatial memory, whereas the exponential gravity model fits well with the simpler system with no spatial memory~\autocite{chen2015distance}.
-	We report the performance of the flux estimation and prediction using different deterrence functions (see Section 2, above), finding that although the absolute values vary, the pattern doesn't change---the embedding distance robustly outperforms geographic distance regardless of the function used.
-Also, we show why embedding distance fits well with the exponential gravity model with the underlying connection between \textit{word2vec} and the gravity model (see Section 1, above).
-	We add the following line to the methods noting this point,
+\response{Thank you for noting this.
+	We carefully read out the Barthélemy, Physics Reports 499, 1, 2011, and found it incredibly educational, referencing it in our manuscript.		
+	It has been argued that the power-law decay function is appropriate for modelling geographic distance the model is more suitable for analyzing large, complex, and scale-free spatial systems with long-range spatial memory, whereas the exponential gravity model fits well with the simpler system with no spatial memory~\autocite{chen2015distance}.
+	We report the performance of the flux estimation and prediction using both deterrence functions (see Section 2, above), finding that although the absolute values vary, the qualitative pattern remains the same---the embedding distance outperforms geographic distance regardless of the function used.
+	 We also elaborate on the connection between the embedding distance and exponential model during out discussion on \textit{word2vec} and the gravity model of mobility (see Section 1, above).
+	 In addition, we add the following line to our manuscript, noting these considerations,
 
@@
 	There are previous studies on the optimal dimensionality of word embedding \autocite{yin2018understand, yin2018dimensionality}. Also,
-	we note that in previous work from our group, we explored the optimal dimensions for graph embedding~\autocite{gu2020dimensions}, finding that while a sufficient number of dimensions is necessary to capture the structure, increasing the dimensions does not heavily deteriorate from performance, a property common across deep learning methods.
+	we note that in previous work from our group, we explored the optimal dimensions for graph embedding~\autocite{gu2020dimensions}, finding that while a sufficient number of dimensions is necessary to capture the structure, increasing the dimensions does not heavily deteriorate the performance, a property common across deep learning methods.
 	Given that there is little performance difference between $d = 100$ and $d = 300$, we opt to use the larger embeddings at $d = 300$, which are large enough to capture the complexity of mobility, yet small enough to allow an efficient computational workflow.
@@
 	This last attribute proved very useful, as in exploring the mathematical properties of the model, we discovered a deep connection between \textit{word2vec} and the gravity model of mobility, which explains why it learns gravity-like relationships between entities (see Section 1, this letter).
-	We believe that this new discovery, now included in the manuscript, strongly ground our use of \textit{word2vec} here.
+	We believe that this new discovery, now included in the manuscript, strongly grounds our use of \textit{word2vec} here.
 

### 2021-03-10 paper/current/main.tex
update main paper
tweaks in main text

@@
 	As understanding mobility is becoming critical for contemporary society, finding frameworks that can capture this complexity is of paramount importance.
-	Here, we illustrate a mathematical connection between the neural embedding model \textit{word2ec}~\autocite{mikolov2013word2vec} and the gravity model of mobility and, using three distinct human trajectory datasets, demonstrate that a neural embedding model can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
+	Here, we reveal a mathematical connection between the neural embedding model \textit{word2ec}~\autocite{mikolov2013word2vec} and the gravity model of mobility and, using three distinct human trajectory datasets, demonstrate that a neural embedding model can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
 	Focusing on the case of scientific mobility, we show that embeddings of scientific organizations uncover cultural and linguistic relations, and even academic prestige, at multiple levels of granularity.
@@
 Although negative sampling is the most common approximation, it is a biased estimator~\autocite{Chia2010,Dyer2014} and fits a different probability model.
-When taking into account this bias, {\it word2vec} with the skip-gram and negative sampling fits a probability model given by
+When taking into account this bias, {\it word2vec} with skip-gram and negative sampling fits a probability model given by
 \begin{align}
@@
 This result echos other applications of word embedding, such as word analogy testing~\autocite{levy2015improving}, in which cosine distance also outperformed dot similarity.
-Nevertheless, a model with dot similarity is still the second-best after cosine similarity (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and the embedding distance still outperforms all alternatives we considered.
+Nevertheless, a model with dot similarity has the second-best performance after cosine similarity (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and the embedding distance still outperforms all alternatives we considered.
 
@@
 for making available the dataset of Korean accommodation reservation data.
-For their comments, we thank Guillaume Cabanac, Cassidy R. Sugimoto, Vincent Lariviére, Alessandro Flammini, Filippo Menczer, Lili Miao, Xiaoran Yan, and Inho Hong.
+For their comments, we thank Guillaume Cabanac, Cassidy R. Sugimoto, Vincent Lariviére, Alessandro Flammini, Filippo Menczer, Lili Miao, Xiaoran Yan, Inho Hong, and Esteban Moro Egido.
 This material is based upon work supported by the Air Force Office of Scientific Research under award number FA9550-19-1-0391.

### 2021-03-10 paper/rebuttal/rebuttal.tex
singular vector -> singular value

@@
 First, we construct the co-occurrence matrix of $N$ organizations, $A_{ij}$ given by the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory.
-Then, we apply truncated singular vector decomposition with $d=300$ on the flow matrix $A$ directly.
+Then, we apply truncated singular value decomposition with $d=300$ on the flow matrix $A$ directly.
 
@@
 First, we construct the co-occurrence matrix of $N$ organizations, $A_{ij}$ given by the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory and degree matrix $D$ which is the diagonal matrix for which $D_{ii}=\sum_j {A_{ij}}$.
-Then we construct graph Lapalcian matrix $L = D-A$  and apply truncated singular vector decomposition in the matrix $L$ with $d=300$.
+Then we construct graph Lapalcian matrix $L = D-A$  and apply truncated singular value decomposition in the matrix $L$ with $d=300$.
 
@@
 We used $w=1$ and $k=5$ which is same setting in the our main result.
-Then, we factorized matrix $M$ with truncated singular vector decomposition in the matrix with $d=300$ into $U_d \Sigma_d V_d$, and used the embedding vector as $U_d\sqrt{\Sigma_d}$.
+Then, we factorized matrix $M$ with truncated singular value decomposition in the matrix with $d=300$ into $U_d \Sigma_d V_d$, and used the embedding vector as $U_d\sqrt{\Sigma_d}$.
 
@@
 Specifically, we construct a gravity matrix of $N$ organizations, where each cell of the matrix is calculated as $T_{ij}/m_i m_j$, where $T_{ij}$ is the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory, and $m_i$ and $m_j$ are the organizations' populations, defined here as the mean annual member of unique mobile and non-mobile authors affiliated.
-We then embed the gravity matrix using two approaches: a truncated singular-vector decomposition (SVD), and multidimensional scaling (MDS), which embeds each location in an N-dimensional space such that pairwise distances are preserved as well as possible.
+We then embed the gravity matrix using two approaches: a truncated singular-value decomposition (SVD), and multidimensional scaling (MDS), which embeds each location in an N-dimensional space such that pairwise distances are preserved as well as possible.
 Typically, MDS uses euclidean distance to measure the distance between vectors.

### 2021-03-10 paper/current/supp.tex
singular vector -> singular value

@@
 \label{si:text:Raw SVD}
-{\bf Singular valuer decomposition distance.}
+{\bf Singular value decomposition distance.}
 
@@
 
-We then embed the gravity matrix using two approaches: a truncated singular-vector decomposition (SVD), and with multidimensional scaling (MDS), which embeds each location in a N-dimensional space such that pairwise distances are preserved as well as possible.
+We then embed the gravity matrix using two approaches: a truncated singular value decomposition (SVD), and with multidimensional scaling (MDS), which embeds each location in a N-dimensional space such that pairwise distances are preserved as well as possible.
 Typically, MDS uses euclidean distance to measure distance between vectors.
@@
 
-It is also well known that singular-vector decomposition (SVD) is vulnerable to outliers~\autocite{xu2012robust, huber1981robust, xu1995robust, chandrasekaran2011rank, candes2011robust}.
+It is also well known that singular value decomposition (SVD) is vulnerable to outliers~\autocite{xu2012robust, huber1981robust, xu1995robust, chandrasekaran2011rank, candes2011robust}.
 The stochastic gradient descent algorithm, which is employed in SGNS \textit{word2vec}, is more robust than SVD and can enhance generalization and effectiveness of {\it word2vec} model \autocite{ma2018power, smith2020generalization, zhang2019algorithmic}.

### 2021-03-10 paper/rebuttal/rebuttal.tex
fix rmse tables

@@
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding cosine} \hspace{6pt}\huxbpad{6pt}} &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.743 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.784 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.76 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.73 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.784 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.749 \hspace{6pt}\huxbpad{6pt}}                                               &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.714 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.762 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.745 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.713 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.76 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.737 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.702 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.749 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.713 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.715 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.764 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.748 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
@@
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's euclidean} \hspace{6pt}\huxbpad{6pt}} &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.78 \hspace{6pt}\huxbpad{6pt}}                                                   &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.776 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.755 \hspace{6pt}\huxbpad{6pt}}                                               &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.803 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.791 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.771 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.867 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.725 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.726 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.705 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.803 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.825 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.811 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.851 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.87 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.854 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.769 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.798 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.784 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.859 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.835 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.815 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.841 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.82 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.82 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.812 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.792 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Laplacian cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.878 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.891 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.867 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.894 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.933 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.904 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.835 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.837 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.815 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.881 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.875 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.86 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.898 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.882 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.866 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.858 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.841 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR JSD} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.888 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.847 \hspace{6pt}\huxbpad{6pt}} &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.822 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.703 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.711 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.691 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-					\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-					\arrayrulecolor{black}
-
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity MDS euclidean} \hspace{6pt}\huxbpad{6pt}} &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.795 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.91 \hspace{6pt}\huxbpad{6pt}}                                                   &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.898 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.808 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.957 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.939 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.691 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.802 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.79 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-					\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-					\arrayrulecolor{black}
-
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding dot} \hspace{6pt}\huxbpad{6pt}}         &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.822 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.831 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.864 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.879 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.863 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.783 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.809 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.795 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-					\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-					\arrayrulecolor{black}
-
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{SVD cosine} \hspace{6pt}\huxbpad{6pt}}            &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.839 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.785 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.761 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.89 \hspace{6pt}\huxbpad{6pt}}                                                   &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.834 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.81 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.792 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.752 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.728 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-					\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-					\arrayrulecolor{black}
-
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Laplacian cosine} \hspace{6pt}\huxbpad{6pt}}      &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.87 \hspace{6pt}\huxbpad{6pt}}                                                   &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.837 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.801 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.937 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.919 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.886 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.804 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.772 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.735 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-					\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-					\arrayrulecolor{black}
-
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Geographic} \hspace{6pt}\huxbpad{6pt}}            &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.905 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.879 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.888 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.933 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.906 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.852 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.851 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-					\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-					\arrayrulecolor{black}
-
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR JSD} \hspace{6pt}\huxbpad{6pt}}               &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.889 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.85 \hspace{6pt}\huxbpad{6pt}}                                                   &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.838 \hspace{6pt}\huxbpad{6pt}}                                                &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.835 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.871 \hspace{6pt}\huxbpad{6pt}} &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.834 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.819 \hspace{6pt}\huxbpad{6pt}}                                                &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.828 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.814 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.865 \hspace{6pt}\huxbpad{6pt}} &
@@
 
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity MDS euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.904 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.944 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.93 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.907 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.972 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.955 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.793 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.838 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.821 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.918 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.925 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.908 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.884 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.916 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.894 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.812 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.814 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.796 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Geographic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.929 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.951 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.928 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.973 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.002 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.983 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.856 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.875 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.853 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.933 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.939 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.923 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.92 \hspace{6pt}\huxbpad{6pt}} &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.927 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.91 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.885 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.918 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.896 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.812 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.815 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.797 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-					\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-					\arrayrulecolor{black}
-
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's cosine} \hspace{6pt}\huxbpad{6pt}}         &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.927 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.926 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.911 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.93 \hspace{6pt}\huxbpad{6pt}}                                                   &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.924 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.909 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.861 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.872 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.854 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-					\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-					\arrayrulecolor{black}
-
-					\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity SVD cosine} \hspace{6pt}\huxbpad{6pt}}    &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.965 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.965 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.95 \hspace{6pt}\huxbpad{6pt}}                                                 &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.955 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.958 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.941 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.873 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.883 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.866 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.946 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.927 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.853 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.865 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.847 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
@@
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's dot} \hspace{6pt}\huxbpad{6pt}} &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.99 \hspace{6pt}\huxbpad{6pt}}                                                   &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.998 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.983 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.977 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.015 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.997 \hspace{6pt}\huxbpad{6pt}}                                                &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.845 \hspace{6pt}\huxbpad{6pt}}                                                  &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.86 \hspace{6pt}\huxbpad{6pt}}                                                   &
-					\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.841 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.987 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.995 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.98 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.979 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.014 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.996 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.853 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.867 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.849 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 

### 2021-03-10 paper/current/supp.tex
fix rmse tables

@@
 We note that the MDS embedding actually has the lowest prediction error when organizations' populations are defined as the raw frequency during prediction with the power-law model (RMSE = $0.691$, Table~\ref{supp:table:rmse_power_table});
-however, we note that the MDS distnace is defined with a population of ``All'' mobile and non-mobile scholars, whereas the predictions made in Table~\ref{supp:table:rmse_power_table} use the raw frequency, which likely confounds this result.
-Also, running time of MDS ($\sim$ 30 mins) is substantially longer than that of \textit{word2vec} ($\sim$ 5 mins), which indicates our approach has advantages in terms of efficiency as well.
+however, we note that the MDS distance is defined with a population of ``All'' mobile and non-mobile scholars, whereas the predictions made in Table~\ref{supp:table:rmse_power_table} using the raw frequency, which likely confounds this result.
+MDS is also computationally-intensive, requiring upwards of 6 times more time to compute (on the machine used in this analysis) than the more computationally efficient \textit{word2vec} model.
 
@@
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding cosine} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.743 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.784 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.76 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.73 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.784 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.749 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.714 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.762 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.745 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.713 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.76 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.737 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.702 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.749 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.713 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.715 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.764 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.748 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
@@
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's euclidean} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.78 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.776 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.755 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.803 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.791 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.771 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.867 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.725 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.726 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.705 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding dot} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.803 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.825 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.811 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.851 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.87 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.854 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.769 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.798 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.784 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.859 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.835 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.815 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.841 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.82 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.82 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.812 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.792 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Laplacian cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.878 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.891 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.867 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.894 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.933 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.904 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.835 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.837 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.815 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.881 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.875 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.86 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.898 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.882 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.866 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.858 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.841 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR JSD} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.888 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.847 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.822 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.703 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.711 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.691 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity MDS euclidean} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.795 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.91 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.898 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.808 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.957 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.939 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.691 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.802 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.79 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding dot} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.822 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.831 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.864 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.879 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.863 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.783 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.809 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.795 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.839 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.785 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.761 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.89 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.834 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.81 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.792 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.752 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.728 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Laplacian cosine} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.87 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.837 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.801 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.937 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.919 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.886 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.804 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.772 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.735 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Geographic} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.905 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.879 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.888 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.933 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.906 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.852 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.851 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR JSD} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.889 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.85 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.838 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.835 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.871 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.834 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.819 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.828 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.814 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.865 \hspace{6pt}\huxbpad{6pt}} &
@@
 
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity MDS euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.904 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.944 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.93 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.907 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.972 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.955 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.793 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.838 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.821 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{PPR cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.918 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.925 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.908 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.884 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.916 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.894 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.812 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.814 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.796 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Geographic} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.929 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.951 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.928 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.973 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.002 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.983 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.856 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.875 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.853 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.933 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.939 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.923 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.92 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.927 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.91 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.885 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.918 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.896 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.812 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.815 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.797 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's cosine} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.927 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.926 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.911 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.93 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.924 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.909 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.861 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.872 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.854 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.965 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.965 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.95 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.955 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.958 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.941 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.873 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.883 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.866 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.946 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.927 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.853 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.865 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.847 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
@@
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's dot} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.99 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.998 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.983 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.977 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.015 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.997 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.845 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.86 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.841 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.987 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.995 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.98 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.979 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1.014 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.996 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.853 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.867 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.849 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 

### 2021-03-10 paper/current/supp.tex
supp text tweak

@@
 To circumvent this problem, previous studies~\autocite{levy2014neural, Qui2018} added a constant flow between the affiliation pairs with no flow. 
-However, this alters the underlying data, and these small flows can still have a strong impact on the embedding.
+However, in addition to altering the underlying data, these small flows can still have a strong impact on the embedding.
 
@@
 \label{si:text:disambiguation}
-{\bf Author name dismabiguation.}
+{\bf Author name disambiguation.}
 

### 2021-03-10 paper/rebuttal/rebuttal.tex
add some text emphasizing contribution

@@
 We acknowledge that our initial submission had a substantial gap regarding the choice of the \textit{word2vec} model, its connection with the gravity model of mobility, and its evaluation.
-While reflecting on these comments and our manuscript, we have made a theoretical breakthrough that addresses the fundamental issues;
+While reflecting on these comments and our manuscript, we have made a theoretical breakthrough that addresses the fundamental issues, and dramatically expands the scope of our contribution;
 namely, we have discovered \emph{a mathematical equivalence between the \textit{word2vec} (skip-gram with negative sampling) model and the gravity model.}
@@
 Namely, we demonstrate that \textit{word2vec}'s objective function is equivalent to the gravity model and thus \textit{word2vec} learns gravity-like relationships between entities, whether it be language or locations.
-This development constitutes a major breakthrough in our understanding of neural embeddings and provides a theoretical justification for their application to mobility.
+This development constitutes a major breakthrough in our understanding of neural embeddings, and in addition to justifying their use in our study, also opens the door for further research applying them to the study of mobility.
 
@@
 	This finding explains why SGNS performs so well and demonstrates the utility of the model for studying contexts where gravity relationships are expected, such as in human mobility.
-	We refer you to Section 1 of this letter, above, for an investigation of this connection, and how we adjusted our manuscript given this breakthrough.
+	We refer you to Section 1 of this letter, above, for an investigation of this connection, which we believe to be not only a justification of our choice of the \textit{word2vec} model to study mobility, but also a major contribution to the understanding of neural embeddings and the gravity model themselves.
 

### 2021-03-10 paper/current/main.tex
add some text emphasizing contribution

@@
 	As understanding mobility is becoming critical for contemporary society, finding frameworks that can capture this complexity is of paramount importance.
-	Here, we reveal a mathematical connection between the neural embedding model \textit{word2ec}~\autocite{mikolov2013word2vec} and the gravity model of mobility and, using three distinct human trajectory datasets, demonstrate that a neural embedding model can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
+	Here, we reveal that the neural embedding model \textit{word2ec}~\autocite{mikolov2013word2vec} is mathematically equivalent to the gravity model of mobility and, using three distinct human trajectory datasets, demonstrate that a neural embedding model can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
 	Focusing on the case of scientific mobility, we show that embeddings of scientific organizations uncover cultural and linguistic relations, and even academic prestige, at multiple levels of granularity.
 	Furthermore, the embedding vectors reveal universal relationships between organizational characteristics and their place in the global landscape of scientific mobility.	
-	The ability to learn scalable, dense, and meaningful representations of mobility directly from the data can open up a new avenue of studying mobility across domains.
+	The ability to learn scalable, dense, and meaningful representations of mobility directly from the data can open up new avenues for the study of mobility across domains.
 
@@
 
-While we focus on three domains of mobility, this approach may be broadly applicable to other kinds of mobility data that is expected to follow a gravity-like pattern, such as general human migration, transit-network mobility, and more.
-Moreover, this approach can be used to learn a functional distance even between entities for which no physical analog exists, such as between occupational categories based on individuals' career trajectories.
+In revealing the correspondence between neural embeddings and the gravity model, the study of human mobility can move beyond geographic and network-based models of mobility, and instead leverage the high-order structure from individuals' mobility trajectories.
+While we focus on three domains of mobility, this approach could be applied to many different domains, such as general human migration, transit-network mobility, and more.
+Once learned, functional distances between locations, such as countries, cities, or organizations, can be published to support future research.
+Moreover, this approach can be used to learn a functional distance even between entities for which no geographic analog exists, such as between occupational categories based on individuals' career trajectories.
 In addition to providing a functional distance that supports modeling and predicting mobility patterns, the structure of the neural embedding space is amenable to a range of unique applications for studying mobility.
@@
 
-In spite of its promise, our study has several limitations.
+This approach, and our study, also have several limitations.
 First, the skip-gram \textit{word2vec} model does not leverage directionality, meaning that embedding will be less effective at capturing mobility for which directionality is critical.
-Future studies may also consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality.
+Future studies may consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality, as well as their correspondance to asymetric mobility models, such as the radiation model~\cite{simini2012universal}.
 Second, the neural embedding approach is most useful in cases of mobility between discrete geographic units such as between countries, cities, and businesses; this approach is less useful in the case of mobility between locations represented using geographic coordinates, such as in the modeling of animal movements.
-Neither of these methodological limitations is insurmountable, and future work can aim to incorporate directionality and identify meaningful representations of continuous mobility data.
 Third, neural embeddings are an inherently stochastic procedure, and so results may change across different iterations.
-We note that all results shown here are robust to this stochasticity, likely emerging from the limited ``vocabulary'' of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories).
-Applications of \textit{word2vec }to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random fluctuations.
+However, in this study we observe all results to be robust to stochasticity, likely emerging from the limited ``vocabulary'' of scientific mobility, airports, and accommodations (several thousand) and the relatively0massive datasets used to learn representations (several million trajectories).
+Applications of \textit{word2vec} to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random fluctuations.
 Finally, the case of scientific mobility presents domain-specific limitations.
 Reliance on bibliometric metadata means that we capture only long-term mobility such as migration, rather than the array or more frequent short-term mobility such as conference travel and temporary visits.
-The kinds of mobility we do capture---migration, and co-affiliation---although conceptually different, are treated identically by our model.
+The kinds of mobility we do capture---migration and co-affiliation---although conceptually different, are treated identically by our model.
 Also, our data might further suffer from bias based on publication rates: researchers at prestigious organizations tend to have more publications, leading to these organizations appearing more frequently in affiliation trajectories.
@@
 Unprecedented health crises such as the COVID-19 pandemic threaten to bring drastic global changes to travel and migration by tightening borders and halting travel.
-With the changing paradigm of global mobility, we need now, more than ever, new tools and approaches to capture and understand human mobility in order to inform sensible, effective, sustainable, and humane policies.
+By revealing the correspondence between neural embedding and the gravity model and revealing their utility and efficacy, our study opens a new avenue in the study of mobility.
+Mobility is at the core of many global challenges, and the insights brought forth by our tool can be put to use to inform a better understanding of human mobility, and to support inform a sensible, effective, sustainable, and humane policies.
 

### 2021-03-14 paper/rebuttal/rebuttal.tex
implement yy comments

@@
 Furthermore, our subsequent experiments show that our approach's performance is robust, exceeding many other baselines, even direct optimization of the gravity model.
-Therefore, with these changes, we are confident that our paper is substantially stronger with a qualitative leap.
+Therefore, with these changes, we are confident that our paper is substantially stronger, exhibiting a qualitative leap.
 Thus, we would like to request a reconsideration of our manuscript.
@@
 \vspace{-0.1cm}
-We address the first point by presenting the mathematical equivalence between the Gravity Model of Mobility and the skip-gram negative sampling \textit{word2vec} model.
-Namely, we demonstrate that \textit{word2vec}'s objective function is equivalent to the gravity model and thus \textit{word2vec} learns gravity-like relationships between entities, whether it be language or locations.
-This development constitutes a major breakthrough in our understanding of neural embeddings, and in addition to justifying their use in our study, also opens the door for further research applying them to the study of mobility.
+We address the first point by presenting the mathematical equivalence between the gravity model of mobility and the skip-gram negative sampling \textit{word2vec} model.
+Namely, we demonstrate that \textit{word2vec}'s objective function is equivalent to the gravity model due to the implicit bias of negative sampling,  and thus \textit{word2vec} learns gravity-like relationships between entities, whether it be language or locations.
+We believe that this development constitutes a major breakthrough in our understanding of neural embeddings, and in addition to justifying their use in our study, also opens the door for further research applying them to the study of mobility.
 
@@
 	\item We also added the section \textbf{An implicit bias in the negative sampling} to the methods section of our manuscript.
-	\item Since the formulation of the gravity used in the above derivations assumes $\gamma = 1$, we use $\gamma = 1$ for all reported results. No findings have substantively changed.
+	\item Since the formulation of the gravity used in the above derivations assumes $\gamma = 1$, we use $\gamma = 1$ for all reported evaluation results. No findings have substantively changed.
 	\item We added a sentence to the paper speculating on why cosine similarity works best.

### 2021-03-14 paper/rebuttal/rebuttal.tex
implement stasa comments on rebuttal

@@
 We thank all the referees for their thoughtful and helpful comments and critiques.
-We acknowledge that our initial submission had a substantial gap regarding the choice of the \textit{word2vec} model, its connection with the gravity model of mobility, and its evaluation.
+We acknowledge that our initial submission had a substantial gap regarding the choice of the \textit{word2vec} model, its relationship to the gravity model of mobility, and its evaluation.
 While reflecting on these comments and our manuscript, we have made a theoretical breakthrough that addresses the fundamental issues, and dramatically expands the scope of our contribution;
@@
 Furthermore, our subsequent experiments show that our approach's performance is robust, exceeding many other baselines, even direct optimization of the gravity model.
-Therefore, with these changes, we are confident that our paper is substantially stronger, exhibiting a qualitative leap.
+Therefore, we are confident that these changes have brought a qualitative leap in the significance of our findings.
 Thus, we would like to request a reconsideration of our manuscript.
-Again, we are incredibly appreciative of these comments, which provided the insight and motivation needed to make these breakthroughs.
+Again, we are incredibly appreciative of the referees' comments, which provided the insight and motivation needed to make these breakthroughs.
 
@@
 For the second point, we have conducted experiments comparing the performance of neural embedding to (\romannum{1}) a singular value decomposition of the mobility network,  (\romannum{2}) a Laplacian eigenmap embedding  (\romannum{3}) a \textit{word2vec} model with matrix factorization,  and  (\romannum{4}) a direct optimization of the gravity model.
-We find that the embedding distance from \textit{word2vec} outperforms all baselines, even the direct optimization of gravity model with the multidimensional scaling, in explaining and predicting real-world mobility.
-
-Finally, addressing the third point, we have incorporated relevant literature to better ground our manuscript in the existing studies.
+We find that the embedding distance from \textit{word2vec} outperforms all baselines, including the direct optimization of gravity model with the multidimensional scaling, in explaining and predicting real-world mobility.
+
+Finally, in order to address the third point, we have incorporated relevant literature to better ground our manuscript in the existing studies.
 
@@
 These alternatives included the geographic distance between locations, the distance most commonly used in definitions of the gravity model of mobility, along with the dot product similarity between embedding vectors, and the cosine distance and Jensen-Shannon divergence between vectors obtained from a personalized-page-ranking procedure on the underlying mobility network.
-Following the advice of the referees, we also add additional baselines to illustrate how the embedding distance performs compared to simpler embedding alternatives and also more advanced approach as follow:
+Following the advice of the referees, we also add additional baselines to illustrate how the embedding distance performs compared to simpler embedding alternatives and also to a more advanced approach as follows:
 
@@
 \paragraph{Levy's  symmetric SVD \textit{word2vec} distance:} In addition to these suggested baselines, we also consider distances derived from embeddings learned through matrix factorization following the procedure outlined by Levy \& Goldberg~\autocite{levy2014neural}.
-Based on idea of \textit{word2vec} is implicit matrix factorization, Levy proposed symmetric SVD \textit{word2vec} embedding, which should directly compute the embedding that \textit{word2vec} only attempts to efficiently approximate.
+Observing that \textit{word2vec} is implicit matrix factorization, Levy proposed a symmetric SVD embedding that directly calculate the embedding that \textit{word2vec} attempts to approximate. 
+Here, we compare the performance of \textit{word2vec} embeddings against those calculated directly using Levy's SVD. 
 First, we construct the matrix of $N$ organization
@@
 where $N(i,j)$ is the number of times the location pair $(i,j)$ appears given the window size $w$ in the total corpus $D$, $N(i)=\sum_{j=N}^i N(i,j)$ as the number of items $i$ occurred given the window size $w$ in $D$, and k is the number of negative samples.
-We used $w=1$ and $k=5$ which is same setting in the our main result.
+We used $w=1$ and $k=5$ which is the same setting as in our main result.
 Then, we factorized matrix $M$ with truncated singular value decomposition in the matrix with $d=300$ into $U_d \Sigma_d V_d$, and used the embedding vector as $U_d\sqrt{\Sigma_d}$.
@@
 \paragraph{Direct optimization of gravity model:} Finally, we create an embedding by optimizing for the gravity model directly.
-Specifically, we construct a gravity matrix of $N$ organizations, where each cell of the matrix is calculated as $T_{ij}/m_i m_j$, where $T_{ij}$ is the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory, and $m_i$ and $m_j$ are the organizations' populations, defined here as the mean annual member of unique mobile and non-mobile authors affiliated.
+Specifically, we construct a gravity matrix of $N$ organizations, where each cell of the matrix is calculated as $T_{ij}/m_i m_j$, where $T_{ij}$ is the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory, and $m_i$ and $m_j$ are the organizations' populations, defined here as the mean annual number of unique mobile and non-mobile authors affiliated.
 We then embed the gravity matrix using two approaches: a truncated singular-value decomposition (SVD), and multidimensional scaling (MDS), which embeds each location in an N-dimensional space such that pairwise distances are preserved as well as possible.
-Typically, MDS uses euclidean distance to measure the distance between vectors.
+Typically, MDS uses Euclidean distance to measure the distance between vectors.
 
@@
 The first is $\gamma$, a hyper-parameter of the \textit{word2vec} model, which defines the exponent which shapes the negative sampling distribution.
-The default of \texttt{gensim} implementation of \textit{word2vec} is to set $\gamma = 0.75$, and this was the value used in our original manuscript.
+The default of \texttt{gensim} implementation of \textit{word2vec} is set to $\gamma = 0.75$, and this was the value used in our original manuscript.
 However, to connect \textit{word2vec} to the gravity model of mobility, we assume $\gamma = 1.0$ (see Section 1).
 We now report all main results using $\gamma = 1.0$ and also compare its performance to embeddings learned using $\gamma = 0.75$, as we do with the number of embedded dimensions and window size.
-We plot the performance of each combination of hyperparemters by their ability to explain real-world flux of scientific mobility (Fig.~\ref{fig:supp:hyperparameter}), and observe no noticeable difference in performance between values of $\gamma = 0.75$ and $\gamma = 1.0$.
+We plot the performance of each combination of hyperparameters by their ability to explain real-world flux of scientific mobility (Fig.~\ref{fig:supp:hyperparameter}), and observe no noticeable difference in performance between values of $\gamma = 0.75$ and $\gamma = 1.0$.
 Figures in the updated manuscript have been re-drawn with $\gamma = 1.0$, and the findings remain qualitatively similar.
@@
 		Window size refers to $w$, the size of the context window that defines the context in a trajectory.
-		Smaller window sizes result in an embedding that explain more flux.
+		Smaller window sizes result in an embedding that explains more flux.
 		Embedding dimensions refer to the size of the embedding vector.
-		Larger vectors perform better, though little difference between 200 and 300.
-		Gamma refers to the $\gamma$ parameter in word2vec, which shapes the negative sampling distribution.
-		A value of $\gamma = 0.75$ is the default for word2vec.
+		Larger vectors perform better, though with little difference between 200 and 300.
+		Gamma refers to the $\gamma$ parameter in \textit{word2vec}, which shapes the negative sampling distribution.
+		A value of $\gamma = 0.75$ is the default for \textit{word2vec}.
 		There is virtually no difference in performance based on $\gamma$.
-		All variants perform better on same-country pairs of organizations than on all organizations.
-		All variants perform worse on different-country pairs on organizations.
+		All variants perform better on same-country organization pairs, and worse on different-country pairs, than on all pairs of  of organizations than on all pairs.
 		Embeddings with larger dimensions outperform mid-size embeddings for the different-country case.
@@
 		In all cases, organization population is defined as the mean annualized number of unique mobile and non-mobile authors, and flux is calculated for all global mobility.
-		Baselines include the top-performing distance metrics calculated between vectors obtained by personalized-page rank (PPR), singular value decomposition (SVD), laplacian eigenmap, direct-factorization following Levy's approach~\autocite{levy2014neural}, and direct optimization of the gravity model using SVD and multidimensional scaling (MDS), as well as the geographic distance between organizations.
+		Baselines include the top-performing distance metrics calculated between vectors obtained by personalized-page rank (PPR), singular value decomposition (SVD), Laplacian eigenmap, direct-factorization following Levy's approach~\autocite{levy2014neural}, and direct optimization of the gravity model using SVD and multidimensional scaling (MDS), as well as the geographic distance between organizations.
 		Embedding distance better explains and predicts flux than any other baseline, though there is some variation by experimental parameters (Table~\ref{supp:table:r2_table}, Table~\ref{supp:table:rmse_exp_table}, and Table~\ref{supp:table:rmse_power_table}).
@@
 
-We find that using the best performing dimensions (300) and window size (1),  $\gamma = 1.0$, and for default experimental parameters (global mobility, population defined using all mobile and non-mobile scholars), that the embedding distance or cosine distance between vectors learned through neural embedding, explains more of the flux, and leads to better predictions than other baselines (Fig.~\ref{fig:supp:distancemetrics}).
+We observe that the cosine distance between embedding vectors, which we call here the "Embedding Distance", explains more of the flux, and results in lower prediction error than all baselines we considered (See Fig.~\ref{fig:supp:distancemetrics}).
 This performance advantage holds across \emph{the exponential and the power-law forms of the gravity model of mobility}.
-Although the euclidean distance between directly-factorized vectors performs comparably, and even narrowly beats out the embedding distance under few experimental conditions (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}); our approach shows the most consistent and robust performance and even outperform the direct optimization of the gravity models.
+Although the Euclidean distance between directly-factorized vectors performs comparably, and even narrowly beats the embedding distance under certain experimental settings (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}); our approach shows the most consistent and robust performance, outperforming even the direct optimization of the gravity models.
 
@@
 The matrix factorization approach embeds affiliations $i$ and $j$ such that their dot similarity is as close as to $\log (T_{ij} / P(i) P(j))$.
-If the flow $T_{ij}$ is considerably small or zero, the dot similarity goes $-\infty$, pushing $i$ and $j$ away in the embedding space~\autocite{levy2014neural, Qui2018}.
+If the flow $T_{ij}$ is considerably small or zero, the dot similarity approaches $-\infty$, pushing $i$ and $j$ away in the embedding space~\autocite{levy2014neural, Qui2018}.
 This is particularly problematic when the window size is small because most affiliation pairs would have no flow, which is indeed the case in our experiments.
@@
 	\item Added Fig~\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table} to the manuscript.
-	\item We have added sentence speculating on SGD performance differences into supporting materials
+	\item Added sentence speculating on SGD performance differences into supporting materials
 \end{itemize}
@@
 
+	However, the novelty of this work is quite narrow, as there are several prior works that develop trajectory-based embeddings of human mobility based on the word2vec algorithm.
+For example, the following references all propose word2vec-inspired embeddings of human mobility data:
+
 	\begin{itemize}
@@
 
-	However, the novelty of this work is quite narrow, as there are several prior works that develop trajectory-based embeddings of human mobility based on the word2vec algorithm.
-For example, the following references all propose word2vec-inspired embeddings of human mobility data:
-
 	Notably, the location embedding methodology in Liu et al (2016) (see Section 3.1) is essentially the same as the approach used in the submitted manuscript, and the work by Liu et al (2016) is well-known with over 100 citations.
@@
 	They have now been incorporated into our manuscript's introduction.
-	Although there are existing works on trajectory-based mobility embedding, we argue that our new result establishing the mathematical equivalence of \textit{word2vec} and the gravity model, as well as our extensive evaluation with many baselines represents a novel and substantial contribution.
+	Although there are existing works on trajectory-based mobility embedding, we argue that our new result establishing the mathematical equivalence of \textit{word2vec} and the gravity model, together with our extensive evaluation of baselines, represents a novel and substantial contribution.
 }
@@
 	“We note that all results shown here are robust to this stochasticity, likely emerging from the limited ``vocabulary'' of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories).
-Applications of word2vec to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random fluctuations.”
+Applications of \textit{word2vec} to problem domains where the ratio of the vocabulary to data is smaller, however, should be implemented with caution to ensure that findings are not the result of random fluctuations.”
 
@@
 
-	We have also provided detail about how confidence intervals were calculated in relevant figure captions.
+	We have also provided information on how confidence intervals were calculated in relevant figure captions.
 	For example, we state in figure 2's caption that \say{\textit{99\% confidence intervals are plotted for the mean flux in each bin based on a normal distribution.}}, which should give readers enough information to reproduce the confidence intervals following their standard definition.
-	Other confidence intervals, such as intervals for the loess regression line in figure 6, are calculated using the smoothing functions in the \texttt{ggplot2} package of R and refer readers to the relevant documentation.
+	Other confidence intervals, such as intervals for the loess regression line in figure 6, are calculated using the smoothing functions in the \texttt{ggplot2} package of R and we refer readers to the relevant documentation.
 }
@@
 
-\response{We believe that our new mathematical results substantially improve the manuscript and extend its contribution and demonstrates novel scientific insight, and justifies the use of word2vec towards mobility data.
+\response{We believe that our new mathematical results substantially improve the manuscript, extends its contribution, demonstrates novel scientific insight, and justifies the use of \textit{word2vec} towards mobility data.
 By adding this, and addressing your other points (above), we believe that the revised manuscript sufficiently remedies your concerns.
@@
 	We carefully read out the Barthélemy, Physics Reports 499, 1, 2011, and found it incredibly educational, referencing it in our manuscript.		
-	It has been argued that the power-law decay function is appropriate for modelling geographic distance the model is more suitable for analyzing large, complex, and scale-free spatial systems with long-range spatial memory, whereas the exponential gravity model fits well with the simpler system with no spatial memory~\autocite{chen2015distance}.
+	Past work has argued that the power-law decay function is appropriate for modelling geographic distance---being more suitable for the analysis of large, complex, and scale-free spatial systems with long-range spatial memory---whereas the exponential gravity model fits well with the simpler system with no spatial memory~\autocite{chen2015distance}, such as might be encoded in the \textit{word2vec} embedding space.
 	We report the performance of the flux estimation and prediction using both deterrence functions (see Section 2, above), finding that although the absolute values vary, the qualitative pattern remains the same---the embedding distance outperforms geographic distance regardless of the function used.
-	 We also elaborate on the connection between the embedding distance and exponential model during out discussion on \textit{word2vec} and the gravity model of mobility (see Section 1, above).
+	 We also elaborate on the connection between the embedding distance and exponential model in our discussion on the relationship between \textit{word2vec} and the gravity model of mobility (see Section 1, above).
 	 In addition, we add the following line to our manuscript, noting these considerations,
@@
 	\medskip
-	\say{The decay function $f(r_{ij})$ defines the effect of distance, and so different decay functions can model fundamentally different mechanism [...] such as the cost functions for a given distance and the spatial granularity of the observation.
+	\say{The decay function $f(r_{ij})$ defines the effect of distance, and so different decay functions can model fundamentally different mechanisms [...] such as the cost functions for a given distance and the spatial granularity of the observation.
 		For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case though there is no qualitative difference---the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Supporting Information).}
@@
 }
-\response{Thank you, we have remedied these comments and have updates the manuscript accordingly,
+\response{Thank you, we have addressed these comments and have updated the manuscript accordingly,
 }
@@
 }
-\response{Thank you, we agree that the trend is flat, rather than decreasing. We have adjusted the text accordingly, and also added a grid to the figure so that it can be more easily read.
+\response{Thank you, we agree that the trend is flat, rather than decreasing. We have adjusted the text accordingly, and also added a grid to the figure so that it can be read more easily.
 
@@
 
-	We agree that the revolution in neural embeddings offers great promise in mobility and look forward to reading and also working on these future studies; however, we argue that our contribution is most well-founded, and best serves the scientific community, by working with simpler and more established models (see Section 2, this letter), especially concerning the mathematical link we uncovered.
-Moreover, these deep models require a tremendous amount of training data ($\sim$3 billion words in Bert) and model parameters, making their use infeasible in applicants most.
-
-	To highlight the importance of alternative models, however, we add the following line to our conclusion: \say{\textit{Future studies may also consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality.}}.
+	We agree that the new revolutions in neural embeddings offer huge potential for the study of human mobility, however we argue that our contribution is dependent on \textit{word2vec}, both for its equivelance with the gravity model of mobility, as well as for the model's simplicity and ubiquity.
+	\textit{Word2vec} is also efficient; deep neural models often require tremendous amounts of training data ($\sim$3 billion words in BERT) and model parameters, making them infeasible for most studies of mobility.
+	We hope that this manuscript serves as a foundation that others can build upon, applying more and more sophisticated neural embedding techniques to gain deeper insights into mobility data.
+
+	To highlight the importance of alternative models, however, we added the following line to our conclusion: \say{\textit{Future studies may also consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality.}}.
 
@@
 	Thank you for this comment!
-	We feel that applying these embeddings to other areas of scientific activity would be incredibly enlightening!
-	Your recommendation of collaboration (based on the author byline) and advisor-student pairs are especially interesting, and we would aim to address these areas in future studies.
-	However, given the importance of mobility to science, the importance of human mobility more generally, and the connection we discovered between \textit{word2vec} and the gravity model, that a focus on co-affiliation, which most closely aligns with ideas of mobility, is the most reasonable data to use for this manuscript.
+	We feel that applying these embeddings to other areas of scientific activity would be incredibly enlightening.
+	Your recommendation of collaboration (based on the author byline) and advisor-student pairs are especially interesting, and we intend to approach such questions in future studies. 
+	However, for this manuscript, we believe that mobility is the most appropriate area of study, due to the importance of mobility to science, economics, and innovation, as well as the fundamental mathematical relationship between \textit{word2vec} and the gravity model of mobility, which we discovered since our first submission.
 }
@@
 \response{Thank you for this suggestion.
-	We looked into this, using UMAP to reduce the country-level embeddings from 300 down to 30 dimensions, however, the results from this were incomprehensible, much inferior to those using 300 dimensions.
+	We looked into this, using UMAP to reduce the country-level embeddings from 300 down to 30 dimensions, however, the results were incomprehensible, and much inferior to those using 300 dimensions.
 	Many dimensionality reduction techniques reduce the number of dimensions by maintaining pairwise distances between vectors, so that the result can be well-suited for clustering algorithms.
 	However, our approach already uses raw pairwise similarities to perform hierarchical clustering, so approximating this distance in 30 dimensions, and then using the new distances to perform clustering is redundant.
-	We also find that the curse of dimensional is not a major issue in our analysis, at least given the size of our data and the number of locations represented---\textit{word2vec} seems able to learn dense vector-space representations.
+	We also find that the curse of dimensionality is not a major issue in our analysis, at least given the size of our data and the number of locations represented---\textit{word2vec} seems able to learn dense vector-space representations.
 }
@@
 
-\response{Thank you, we have edited the text to read as “We quantify the relative importance of geography (by region), and language (by the most widely-spoken language of each country) using the element-centric clustering similarity, a method that can compare hierarchical clustering and disjoint clustering (geography, language...) at the different level of hierarchy by explicitly adjusting a scaling parameter $r$, acting like a zooming lens”
+\response{Thank you, we have edited the text to read as “We quantify the relative importance of geography (by region), and language (by the most widely-spoken language of each country) using the element-centric clustering similarity, a method that can compare hierarchical clustering and disjoint clustering (geography, language...) at the different levels of hierarchy by explicitly adjusting a scaling parameter $r$, acting like a zooming lens”
 }
@@
 	We believe that this is an interesting topic and we hope to investigate it in the future.
-	In your particular example, an embedding distance trained using sequences of co-authorship on the same paper might be better to capture the \textit{collaborative} distance between institutions.
+	In your particular example, an embedding distance trained using sequences of co-authorship on the same paper might better capture the \textit{collaborative} distance between institutions.
 	Then, using that distance, one could measure the ``embedding distance'' spanned by all authors in the byline and answer the question of whether typical collaborations relate to impact or not.
-	This is certainly a topic that is in our minds for future study.
+	This is certainly a topic that  we intend to pursue in a future study.
 	In the case of scientific mobility, we might also consider the ``embedding distance'' spanned by an individual's career, and relate this to their demographics and scientific impact.
 
-	However, while these topics are exciting, we believe that that they fall outside the scope of the current manuscript, especially given the discoveries we made concerning a fundamental connection between the gravity law of mobility and \textit{word2vec}, which adds a substantial amount of new results to the manuscript.
+	However, while these topics are exciting, we believe that they fall outside the scope of the current manuscript, especially given the discoveries we made concerning a fundamental connection between the gravity law of mobility and \textit{word2vec}, which adds a substantial amount of new results to the manuscript.
 }
@@
 	As such, we would not necessarily expect to see the impact of COVID on bibliometric data until later in 2021 or early 2022, when researchers have had the chance to publish with their new institution.
-	We also not that some activity will, of course, be visible, especially given the number of researchers rapidly publishing on the subject of COVID-19, however, we consider this to be an unrepresentative sample, given that it is concentrated in a few disciplines.
+	We also note that some activity will, of course, be visible, especially given the number of researchers rapidly publishing on the subject of COVID-19, however, we consider this to be an unrepresentative sample, given that it is concentrated in a few disciplines.
 
@@
 			\textbf{Correlation between flux and distance over metrics, experimental parameters}.
-			Each cell corresponds to the correlation (measured with $R^{2}$) between the real-world flux between scientific organizations, comparing the embedding distance against baseline metrics, and across subsets of mobility data and by definitions of organization population.
+			Each cell corresponds to the correlation between the real-world flux between scientific organizations (measured with $R^{2}$) and baseline metrics, shown by subsets of mobility data and by definitions of organization population.
 			The asterisk denotes the top-performing distance metric by column.
@@
 			\textbf{Prediction error between actual and predicted mobility with exponential gravity model, by metrics and experimental parameters}.
-			Each cell corresponds to the prediction error (measured with root mean squared error) between the real-world flux between scientific organizations and predictions made with the exponential form of the gravity model of mobility.
-			The prediction error is shown for the embedding distance compared against baselines, subsets of mobility data, and definitions of organization population.
+			Each cell corresponds to the prediction error (measured with root mean squared error) when using each distance as input to the exponential form of the gravity model of mobility to predict the flux between organizations, shown by subsets of mobility data, and by definitions of organization population.
 			The asterisk denotes the top-performing distance metric by column (lowest prediction error).
@@
 			\textbf{Prediction error between actual and predicted mobility with power-law gravity model, by metrics and experimental parameters}.
-			Each cell corresponds to the prediction error (measured with root mean squared error) between the real-world flux between scientific organizations and predictions made with the power-law form of the gravity model of mobility.
-			The prediction error is shown for the embedding distance compared against baselines, subsets of mobility data, and definitions of organization population.
+			Each cell corresponds to the prediction error (measured with root mean squared error) when using each distance as input to the power-law form of the gravity model of mobility to predict the flux between organizations, shown by subsets of mobility data, and by definitions of organization population.
 			The asterisk denotes the top-performing distance metric by column (lowest prediction error).

### 2021-03-14 paper/current/main.tex
implement stasa comments on rebuttal

@@
 We define the distance function in terms of either the geographic distance between locations or their functional distance in the vector space, which is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.
-The decay function $f(r_{ij})$ defines the effect of distance, and so different decay functions can model fundamentally different mechanism \autocite{barthelemy2011spatial} such as the cost functions for a given distance and the spatial granularity of the observation.
+The decay function $f(r_{ij})$ defines the effect of distance, and so different decay functions can model fundamentally different mechanisms \autocite{barthelemy2011spatial} such as the cost functions for a given distance and the spatial granularity of the observation.
 For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}), though there is no qualitative difference---the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).

### 2021-03-14 paper/current/supp.tex
remove todo comment
implement stasa comments on rebuttal

@@
 \clearpage
-\todo{@dakoda, could you update the table?}
 \begin{landscape}
@@
 	\textbf{Correlation between flux and distance over metrics, experimental parameters}.
-	Each cell corresponds to the correlation (measured with $R^{2}$) between the real-world flux between scientific organizations, comparing the embedding distance against baseline metrics, and across subsets of mobility data and by definitions of organization population.
+			Each cell corresponds to the correlation between the real-world flux between scientific organizations (measured with $R^{2}$) and baseline metrics, shown by subsets of mobility data and by definitions of organization population.
 			The asterisk denotes the top-performing distance metric by column.
@@
 			``Raw freq'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
-		Embedding distance, measured as the cosine distance between embedding vectors, explains more of the flux than baselines in nearly every case, except using raw frequency population and domestic and international mobility, where direct optimization of the gravity law works better, as well as Levy's factorization~\autocite{levy2014neural} for domestic and international only mobility.
+			Embedding distance, measured as the cosine distance between embedding vectors, explains more of the flux than baselines in nearly every case, except using raw frequency population and domestic and international mobility, where direct optimization of the gravity model works better, as well as Levy's factorization~\autocite{levy2014neural} for domestic and international only mobility.
 }
@@
 	\textbf{Prediction error between actual and predicted mobility with exponential gravity model, by metrics and experimental parameters}.
-	Each cell corresponds to the prediction error (measured with root mean squared error) between the real-world flux between scientific organizations and predictions made with the exponential form of the gravity model of mobility.
-	The prediction error is shown for the embedding distance compared against baselines, subsets of mobility data, and definitions of organization population.
+	Each cell corresponds to the prediction error (measured with root mean squared error) when using each distance as input to the exponential form of the gravity model of mobility to predict the flux between organizations, shown by subsets of mobility data, and by definitions of organization population.
 	The asterisk denotes the top-performing distance metric by column (lowest prediction error).
@@
 	\textbf{Prediction error between actual and predicted mobility with power-law gravity model, by metrics and experimental parameters}.
-	Each cell corresponds to the prediction error (measured with root mean squared error) between the real-world flux between scientific organizations and predictions made with the power-law form of the gravity model of mobility.
-	The prediction error is shown for the embedding distance compared against baselines, subsets of mobility data, and definitions of organization population.
+	Each cell corresponds to the prediction error (measured with root mean squared error) when using each distance as input to the power-law form of the gravity model of mobility to predict the flux between organizations, shown by subsets of mobility data, and by definitions of organization population.
 	The asterisk denotes the top-performing distance metric by column (lowest prediction error).

### 2021-03-15 paper/current/main.tex
stasa main text comments

--- 2021-03-10 paper/current/main.tex
@@
 As a scientist's career progresses, they move between organizations or pick up additional (simultaneous) affiliations forming \textit{affiliation trajectories} (Fig.~\ref{fig:methods:mobility_sentence}).
-Thus, the trajectories encode both migration and co-affiliation---the holding of multiple simultaneous co-affiliations involving the sharing of time and capital between locations---that is typical of scientific mobility~\autocite{rodrigues2016mobility, sugimoto2017mostimpact} (see \SI).
+Thus, the trajectories encode both migration and co-affiliation---the holding of multiple simultaneous affiliations involving the sharing of time and capital between locations---that is typical of scientific mobility~\autocite{rodrigues2016mobility, sugimoto2017mostimpact} (see \SI).
 
@@
 This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}, networks~\autocite{grover2016node2vec, linzhuo2020hyperbolic} and trajectories\autocite{liu2016exploring, feng2017poi2vec, yao2018representing, cao2019habit2vec, crivellari2019motion, solomon2018predict}.
-It works under the notion that a good representation should facilitate prediction,  so learns a mapping of words that predicts the target word with surrounding words (context).
+It works under the notion that a good representation should facilitate prediction, learning a mapping between words that can predict a target word based on its context (surrounding words). 
 The model is also computationally efficient, robust to noise, and can encode relations between entities as geometric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.
@@
 
-To validate our approach, we evaluate the quality of vector representations with their performance in predicting real-world mobility flows using the gravity model framework~\autocite{zipf1946gravity}.
+To validate our approach, we evaluate the quality of vector representations based on their performance in predicting real-world mobility flows using the gravity model framework~\autocite{zipf1946gravity}.
 The gravity model is a widely used mobility model~\autocite{curiel2018citygravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity} that connects the \textit{expected flux}, $\hat{T}_{ij}$, between locations based on their populations and distance:
@@
 \end{equation}
-where $m_{i}$ is the population of locations $i$,  $f(r_{ij})$ is a decay function with respect to distance between locations, and $C$ is a constant estimated from data (see Methods).
+where $m_{i}$ is the population of location $i$,  $f(r_{ij})$ is a decay function with respect to distance between locations, and $C$ is a constant estimated from data (see Methods).
 For the flight itinerary data, we use population $m_{i}$ as the total number of unique passengers who passed through each airport, for the Korean accommodation reservation data, we use the total number of unique customers who booked with each accommodation, and for scientific mobility, we use the mean annual number of unique mobile and non-mobile authors who were affiliated with each organization.
@@
 We define the distance function in terms of either the geographic distance between locations or their functional distance in the vector space, which is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.
-The decay function $f(r_{ij})$ defines the effect of distance, and so different decay functions can model fundamentally different mechanism \autocite{barthelemy2011spatial} such as the cost functions for a given distance and the spatial granularity of the observation.
-For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}), though there is no qualitative difference---the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
-Beyond the fitting on the data, we would like to argue that geographical distance fits well with the power-law decay function because it is more suitable for analyzing large, complex, and scale-free spatial systems\autocite{chen2015distance}, while embedding distance fits well with the exponential decay function, which we will show later in the section of mathematical relation between \textit{word2vec} and the gravity model.
+The decay function $f(r_{ij})$ defines the effect of distance, and different decay functions can model fundamentally different mechanisms \autocite{barthelemy2011spatial} such as the cost functions for a given distance and the spatial granularity of the observation.
+For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}).
+Though there is no qualitative difference, the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+The power-law decay function performs best with the geographic distance, likely resulting from the  function's suitability for large, complex, and scale-free spatial systems~\autocite{chen2015distance};
+performance of the embedding distance is similar between the functional forms, though best for the exponential form, which stems from an underlying connection between the function and \textit{word2vec} that we discuss later.
 
@@
 Why does \textit{word2vec} with the skip-gram with negative sampling model (SGNS) work so well to model mobility?
-Here, we demonstrate that the SGNS model and the gravity model of mobility are mathematically equivalent.
+The reason for that is the mathematical equivalence between the SGNS model and the gravity model which we demonstrate below.
 
@@
 where $P(j)$ is the fraction of $j$ in the data.
-In general, calculating $Z_i$ is computationally expensive and there are two common approximation: hierarchical softmax \autocite{morin2005hierarchical} and negative sampling \autocite{mikolov2013word2vec}.
+In general, calculating $Z_i$ is computationally expensive and there are two common approximations: hierarchical softmax \autocite{morin2005hierarchical} and negative sampling \autocite{mikolov2013word2vec}.
 Due to its simplicity and performance, negative sampling is the most widely used strategy, which we also adopt in our study.
@@
 
-In the remainder of the paper, we focus on scientific mobility and interrogate the geometric space generated by the neural embedding to sheds light on the multi-faceted relationships between organizations.
+In the remainder of the paper, we focus on scientific mobility and interrogate the geometric space generated by the neural embedding to shed light on the multi-faceted relationships between organizations.
 To explore the topological structure of the embedding, we use a topology-based dimensionality reduction method (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation of the embedding space (Fig.~\ref{fig:projection}a).
@@
 For example, re-projecting organizations located in Western, Southern, and Southeastern Asia with UMAP (Fig.~\ref{fig:projection}b) reveals a gradient of countries between Egypt and the Philippines that largely corresponds to geography, but with some exceptions seemingly stemming from cultural and religious similarity;
-Malaysia, with its official religion of Islam, is nearer to Middle Eastern countries in the embedding space than many geographically-closer South Asian countries.
+Malaysia, with its official religion of Islam, is nearer to Middle Eastern countries in the embedding space than to many geographically-closer South Asian countries.
 We validate this finding quantitatively with the cosine distance between nations (the centroids of organizations vectors belonging to that country).
@@
 		\textbf{Geography, then language, conditions international mobility.}
-		\textbf{a.} Hierarchically clustered similarity matrix of country vectors aggregated as the mean of all organization vectors within the country, excluding the United States and countries with at most 25 organizations.
+		\textbf{a.} Hierarchically clustered similarity matrix of country vectors aggregated as the mean of all organization vectors within the country, excluding the United States and countries with less than 25 organizations.
 		Color of matrix cells corresponds to the cosine similarity between country vectors.
@@
 Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphasis on teaching, such as Barry University and California State University at Long Beach.
-By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reason about the prestige of organizations for which rankings are often low-resolution, incomplete, or entirely absent, such as regional and liberal arts universities (Fig.~\ref{fig:semaxis}d), research institutes (Fig.~\ref{fig:semaxis}e), and government organizations (Fig.~\ref{fig:semaxis}f).
+By projecting other types of organizations onto the prestige axis, SemAxis offers a new way of representing a continuous spectrum of organizational prestige for which rankings are often low-resolution, incomplete, or entirely absent, such as for regional and liberal arts universities (Fig.~\ref{fig:semaxis}d), research institutes (Fig.~\ref{fig:semaxis}e), and government organizations (Fig.~\ref{fig:semaxis}f).
 Their estimated prestige is speculative, though we find that it significantly correlates with their citation impact (Fig.~\ref{fig:supp:sector_semaxis_impact}).
@@
 Third, neural embeddings are an inherently stochastic procedure, and so results may change across different iterations.
-However, in this study we observe all results to be robust to stochasticity, likely emerging from the limited ``vocabulary'' of scientific mobility, airports, and accommodations (several thousand) and the relatively0massive datasets used to learn representations (several million trajectories).
-Applications of \textit{word2vec} to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random fluctuations.
+However, in this study we observe all results to be robust to stochasticity, likely emerging from the limited ``vocabulary'' of scientific mobility, airports, and accommodations (several thousand) and the relatively massive datasets used to learn representations (several million trajectories).
+Applications of \textit{word2vec} to problem domains where the ratio of the vocabulary to data is smaller, however, should be implemented with caution to ensure that findings are not the result of random fluctuations.
 Finally, the case of scientific mobility presents domain-specific limitations.
-Reliance on bibliometric metadata means that we capture only long-term mobility such as migration, rather than the array or more frequent short-term mobility such as conference travel and temporary visits.
+Reliance on bibliometric metadata means that we capture only long-term mobility such as migration, rather than the array of more frequent short-term mobility such as conference travel and temporary visits.
 The kinds of mobility we do capture---migration and co-affiliation---although conceptually different, are treated identically by our model.
@@
 At the same time, other nations, such as China, are growing into major scientific powers and attractors of talent~\autocite{cao2020returning}.
-Unprecedented health crises such as the COVID-19 pandemic threaten to bring drastic global changes to travel and migration by tightening borders and halting travel.
+Unprecedented health crises such as the COVID-19 pandemic threaten to bring drastic global changes to migration by tightening borders and halting travel.
 By revealing the correspondence between neural embedding and the gravity model and revealing their utility and efficacy, our study opens a new avenue in the study of mobility.
-Mobility is at the core of many global challenges, and the insights brought forth by our tool can be put to use to inform a better understanding of human mobility, and to support inform a sensible, effective, sustainable, and humane policies.
+Mobility is at the core of many global challenges, and the insights brought forth by our tool can be put to use to inform a better understanding of human mobility, and to inform sensible, effective, sustainable, and humane policies.
 

### 2021-03-15 paper/rebuttal/rebuttal.tex
took a path upto section 1.3

@@
-\documentclass[12pt,a4paper]{article}
+\documentclass[12pt,draft,a4paper]{article}
 \usepackage{graphicx}
@@
 For the second point, we have conducted experiments comparing the performance of neural embedding to (\romannum{1}) a singular value decomposition of the mobility network,  (\romannum{2}) a Laplacian eigenmap embedding  (\romannum{3}) a \textit{word2vec} model with matrix factorization,  and  (\romannum{4}) a direct optimization of the gravity model.
-We find that the embedding distance from \textit{word2vec} outperforms all baselines, including the direct optimization of gravity model with the multidimensional scaling, in explaining and predicting real-world mobility.
+We find that the embedding distance provided by \textit{word2vec} outperforms all baselines, including the direct optimization of gravity model with the multidimensional scaling, in explaining and predicting real-world mobility.
 
@@
 Why does the \textit{word2vec} with skip-gram and negative sampling (SGNS) model work so well to model mobility?
-Here, we demonstrate that SGNS and the gravity model of mobility are mathematically equivalent.
+Here, we demonstrate that SGNS {\it word2vec} and the gravity model of mobility are mathematically equivalent.
 This connection provides strong theoretical justification to our choice of \textit{word2vec} to model mobility, and constitutes a major breakthrough of our understanding of neural embeddings.
-In addition, this motivates the use of SGNS for the future study of human mobility.
+In addition, this motivates the use of SGNS {\it word2vec} for the future study of human mobility.
 
@@
 \begin{equation}
-	{\cal J} = \frac{1}{T}\sum_{t = 1}^{T} \sum_{-w \leq \tau \leq w, \tau \neq 0} \log P(a_{t + \tau} \vert a_{t}), \label{eq:word2vec-obj}
+	{\cal J} = \frac{1}{T}\sum_{t = 1}^{T} \sum_{ \substack{-w \leq \tau \leq w, \\ 0 \leq t+\tau \leq T \\\tau \neq 0}} \log P(a_{t + \tau} \vert a_{t}), \label{eq:word2vec-obj}
 \end{equation}
-where,
+where
 
@@
 Although negative sampling is the most common approximation, it is a biased estimator~\autocite{Chia2010,Dyer2014} that does not yield the optimal embeddings in terms of the objective function, ${\cal J}$.
-This bias in negative sampling turns out to be key to the connection between word2vec and the gravity model.
-
-Negative sampling trains {\it word2vec} using a binary classification task as follows.
+This bias in negative sampling turns out to be key to the connection between {\it word2vec} and the gravity model.
+
+Negative sampling trains {\it word2vec} as follows.
 For each target word $i$, we sample a context word $j$ from the given data and label it as positive, denoted by $Y_{j}=1$.
@@
 An underappreciated fact is that maximizing ${\cal J}^{\text{NS}}$ does not guarantee
-to yield the optimum embedding in terms of the original skip-gram word2vec objective function ${\cal J}$ even if we increase the training samples and iterations~\autocite{Chia2010,Dyer2014}.
+to yield the optimum embedding in terms of the original skip-gram {\it word2vec} objective function ${\cal J}$ even if we increase the training samples and iterations~\autocite{Chia2010,Dyer2014}.
 To make this bias explicit, let us consider the unbiased variant of negative sampling, \ie the noise contrastive estimation (NCE)~\autocite{Chia2010,Dyer2014}.
@@
 where $f$ is a non-negative likelihood function of data $x$, and ${\cal X}$ is the set of all data.
-This general form includes the word2vec model (Eq.~\eqref{eq:cond_prob_w2v}), where $f(x) = \exp(x)$ and $x = \vect{u}_j \cdot \vect{v}_{i}$.
-NCE fits the probability model using a binary classification task in the same way as in negative sampling but using a Bayesian formalism for logistic regression.
+This general form includes the {\it word2vec} model (Eq.~\eqref{eq:cond_prob_w2v}), where $f(x) = \exp(x)$ and $x = \vect{u}_j \cdot \vect{v}_{i}$.
+NCE fits the probability model using a binary classification task in the same way as in negative sampling but using a Bayesian logistic regression.
 Specifically, before the training, we know that $1$ in $1+k$ words is sampled from the given data, which can be modeled as prior probabilities
@@
 	\label{eq:log-likelihood-logistic-regress}
-	{\cal J}^{\text{NCE}} = \sum_{i \in {\cal A}}\sum_{j \in {\cal D}} \left[ Y_{j} \log P^{\text{NCE}}(Y_{j} = 1\vert j) + (1-Y_{j}) \log P^{\text{NCE}}(Y_{j} = 0 \vert j)\right].
+	{\cal J}^{\text{NCE}} = \sum_{i \in {\cal A}}\sum_{j \in {\cal D}} \left[ Y_{j} \log P^{\text{NCE}}(Y_{j} = 1\vert j) + (1-Y_{j}) \log P^{\text{NCE}}(Y_{j} = 0 \vert j)\right],
 \end{align}
-by calculating the gradients for embedding vectors $\vect{u}_j$, $\vect{v}_{i}$ and iteratively updating them.
-An important consequence of this framework is that NCE is an unbiased estimator that has convergence to the optimal embedding in terms of the original word2vec's objective function, ${\cal J}$~\autocite{Chia2010,Dyer2014}, if we increase the number of words to sample and the training iterations.
+by calculating the gradients of ${\cal J}^{\text{NCE}}$ with respect to $\vect{u}_j$, $\vect{v}_{i}$ and iteratively updating them.
+An important consequence of this framework is that NCE is an unbiased estimator that has convergence to the optimal embedding in terms of the original {\it word2vec}'s objective function, ${\cal J}$ if we increase the number of words to sample and the training iterations~\autocite{Chia2010,Dyer2014}.
 
@@
 
-Taking into account the implicit bias in the negative sampling  and setting $w=1$, the \textit{word2vec} predicts the flow between locations with
+Taking into account the implicit bias in the negative sampling  and setting $w=1$, \textit{word2vec} predicts the flow between locations with
 \begin{align}
-	\widehat{T}_{ij} \propto  P(i) P(j\given i) \propto  \frac{P(i) P(j)^\gamma \exp(\vect{u}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:prob_w2v_ng0}
+	\widehat{T}_{ij} =  N(i) P(j\given i) = \frac{N(i) P(j)^\gamma \exp(\vect{u}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:prob_w2v_ng0}
 \end{align}
-where we have redefined $Z'_i=\sum_{j' \in \mathcal{A}}  P^\gamma(j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})$.
-
+where $N(i) = N P(i)$ is the frequency of location $i$ in all trajectories, and $N$ is the sum of the frequencies of all locations.
 Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimial in-vectors and out-vectors such that $\vect{v}_i = \vect{u}_i$ \autocite{levy2014neural}.
-Setting $\gamma = 1$ and substituting $\vect{v}_i = \vect{u}_i$ into Eq.~\ref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
+Setting $\gamma = 1$ and substituting $\vect{v}_i = \vect{u}_i$ and $N(i) = N P(i)$ into Eq.~\eqref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
 \begin{align}
-	\widehat{T}_{ij} \propto  P(i) P(j\given i) = \frac{P(i)P(j)\exp(\vect{v}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:flow_w2v_ng1}
+	\widehat{T}_{ij} =  N \frac{P(i)P(j)\exp(\vect{v}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:flow_w2v_ng1}
 \end{align}
@@
 The flow $\widehat{T}_{ij}$ is symmetric (\ie $\widehat{T}_{ij}=\widehat{T}_{ji}$) because the skip-gram model neglects whether the context $j$ appears before or after the target $i$ in the trajectory.
-If we swap $i$ and $j$ in Eq.~\ref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
+If we swap $i$ and $j$ in Eq.~\eqref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
 Therefore, to ensure $\widehat{T}_{ij}=\widehat{T}_{ji}$, the denominator $Z_i$ should be a constant.
 
-Taken together, the {\it word2vec} model with the negative sampling predicts a flow in the same form as in the gravity model:
+Taken together, the {\it word2vec} model with negative sampling predicts a flow in the same form as in the gravity model:
 \begin{align}
@@
 
-In other words, \emph{word2vec with the skip-gram negative sampling is equivalent to the gravity model}, with the mass given by the location's frequency $f(i)$, and the distance measured by their dot similarities.
+In other words, \emph{word2vec with skip-gram negative sampling is equivalent to the gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
 While the gravity model predicts mobility flows from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given mobility flow.

### 2021-03-15 paper/rebuttal/rebuttal.tex
unset draft mode
edit Laplacian Eigenmap part

@@
-\documentclass[12pt,draft,a4paper]{article}
+\documentclass[12pt,a4paper]{article}
 \usepackage{graphicx}
@@
 \paragraph{Laplacian Eigenmap:} Similarly, we consider Laplacian Eigenmap embeddings~\autocite{belkin2003laplacian} as a baseline, which is one of the most fundamental approaches for graph embedding.
-First, we construct the co-occurrence matrix of $N$ organizations, $A_{ij}$ given by the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory and degree matrix $D$ which is the diagonal matrix for which $D_{ii}=\sum_j {A_{ij}}$.
-Then we construct graph Lapalcian matrix $L = D-A$  and apply truncated singular value decomposition in the matrix $L$ with $d=300$.
+We generate Laplacian Eigenmap embeddings by applying a truncated singular value decomposition to matrix $L$ given by $L=D - A$, where
+$A$ is the co-occurrence matrix of $N$ organizations with element $A_{ij}$ indicating the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory, and $D$ is the diagonal matrix with diagonals $D_{ii}=\sum_j {A_{ij}}$.
+We set the dimension to $d=300$.
 
@@
 \paragraph{Levy's  symmetric SVD \textit{word2vec} distance:} In addition to these suggested baselines, we also consider distances derived from embeddings learned through matrix factorization following the procedure outlined by Levy \& Goldberg~\autocite{levy2014neural}.
-Observing that \textit{word2vec} is implicit matrix factorization, Levy proposed a symmetric SVD embedding that directly calculate the embedding that \textit{word2vec} attempts to approximate.
+Observing that \textit{word2vec} is implicit matrix factorization, Levy proposed a symmetric SVD embedding that directly calculates the embedding that \textit{word2vec} attempts to approximate.
 Here, we compare the performance of \textit{word2vec} embeddings against those calculated directly using Levy's SVD.
-First, we construct the matrix of $N$ organization
+First, we construct the matrix of $N$ organizations
 \begin{equation}
@@
 \end{equation}
-where $N(i,j)$ is the number of times the location pair $(i,j)$ appears given the window size $w$ in the total corpus $D$, $N(i)=\sum_{j=N}^i N(i,j)$ as the number of items $i$ occurred given the window size $w$ in $D$, and k is the number of negative samples.
+where $N(i,j)$ is the number of times the location pair $(i,j)$ appears given the window size $w$ in the total corpus $D$, $N(i)=\sum_{j=N}^i N(i,j)$ as the number of items $i$ occurred given the window size $w$ in $D$, and $k$ is the number of negative samples.
 We used $w=1$ and $k=5$ which is the same setting as in our main result.

### 2021-03-15 paper/rebuttal/rebuttal.tex
Lavy's symmetric SVD: first pass

@@
 \vspace{-0.3cm}
-\paragraph{Laplacian Eigenmap:} Similarly, we consider Laplacian Eigenmap embeddings~\autocite{belkin2003laplacian} as a baseline, which is one of the most fundamental approaches for graph embedding.
+\paragraph{Laplacian Eigenmap:} As the second baseline, we consider Laplacian Eigenmap embeddings~\autocite{belkin2003laplacian}, which is one of the most fundamental approaches for graph embedding.
 We generate Laplacian Eigenmap embeddings by applying a truncated singular value decomposition to matrix $L$ given by $L=D - A$, where
-$A$ is the co-occurrence matrix of $N$ organizations with element $A_{ij}$ indicating the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory, and $D$ is the diagonal matrix with diagonals $D_{ii}=\sum_j {A_{ij}}$.
+$A$ is the co-occurrence matrix of $N$ organizations with element $A_{ij}$ indicating the number of the co-occurrences of organizations $i$ and $j$ in the same affiliation trajectory, and $D$ is the diagonal matrix with diagonals $D_{ii}=\sum_j {A_{ij}}$.
 We set the dimension to $d=300$.
@@
 \paragraph{Levy's  symmetric SVD \textit{word2vec} distance:} In addition to these suggested baselines, we also consider distances derived from embeddings learned through matrix factorization following the procedure outlined by Levy \& Goldberg~\autocite{levy2014neural}.
-Observing that \textit{word2vec} is implicit matrix factorization, Levy proposed a symmetric SVD embedding that directly calculates the embedding that \textit{word2vec} attempts to approximate.
+They utilize SVD to train the {\it word2vec}'s model observing that training \textit{word2vec} can be understood as a factorization of a matrix.
 Here, we compare the performance of \textit{word2vec} embeddings against those calculated directly using Levy's SVD.
@@
 \end{equation}
-where $N(i,j)$ is the number of times the location pair $(i,j)$ appears given the window size $w$ in the total corpus $D$, $N(i)=\sum_{j=N}^i N(i,j)$ as the number of items $i$ occurred given the window size $w$ in $D$, and $k$ is the number of negative samples.
+where $N(i,j)$ is the number of times the location pair $(i,j)$ appears given the window size $w$ in the total corpus $D$, $N(i)=\sum_{j=1}^N N(i,j)$ as the number of items $i$ occurred given the window size $w$ in $D$, and $k$ is the number of negative samples.
 We used $w=1$ and $k=5$ which is the same setting as in our main result.
-Then, we factorized matrix $M$ with truncated singular value decomposition in the matrix with $d=300$ into $U_d \Sigma_d V_d$, and used the embedding vector as $U_d\sqrt{\Sigma_d}$.
+Then, we factorized matrix $M$  into $V_d \Sigma_d U_d$ using truncated SVD with $d=300$, and used $V_d\sqrt{\Sigma_d}$ as the in-vectors.
 

### 2021-03-15 paper/rebuttal/rebuttal.tex
took a path: section 2.4.

@@
 
-For the second point, we have conducted experiments comparing the performance of neural embedding to (\romannum{1}) a singular value decomposition of the mobility network,  (\romannum{2}) a Laplacian eigenmap embedding  (\romannum{3}) a \textit{word2vec} model with matrix factorization,  and  (\romannum{4}) a direct optimization of the gravity model.
+For the second point, we have conducted experiments comparing the performance of neural embedding to (\romannum{1}) the singular value decomposition of the mobility network,  (\romannum{2}) a Laplacian eigenmap embedding  (\romannum{3}) a \textit{word2vec} model with matrix factorization,  and  (\romannum{4}) a direct optimization of the gravity model.
 We find that the embedding distance provided by \textit{word2vec} outperforms all baselines, including the direct optimization of gravity model with the multidimensional scaling, in explaining and predicting real-world mobility.
@@
 \vspace{-0.5cm}
-\paragraph{SVD on co-occurrence matrix:}The first of these baselines uses the distance between vectors in an embedding space produced through a singular-value decomposition of the underlying location co-occurrence matrix.
+\paragraph{SVD on co-occurrence matrix:}The first of these baselines uses the distance between vectors in an embedding space produced through the singular value decomposition (SVD) of the underlying location co-occurrence matrix.
 First, we construct the co-occurrence matrix of $N$ organizations, $A_{ij}$ given by the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory.
-Then, we apply truncated singular value decomposition with $d=300$ on the flow matrix $A$ directly.
+Then, we apply the truncated SVD with $d=300$ on the flow matrix $A$ directly.
 
@@
 We generate Laplacian Eigenmap embeddings by applying a truncated singular value decomposition to matrix $L$ given by $L=D - A$, where
-$A$ is the co-occurrence matrix of $N$ organizations with element $A_{ij}$ indicating the number of the co-occurrences of organizations $i$ and $j$ in the same affiliation trajectory, and $D$ is the diagonal matrix with diagonals $D_{ii}=\sum_j {A_{ij}}$.
+$A$ is the co-occurrence matrix of $N$ organizations with element $A_{ij}$ indicating the number of co-occurrences of organizations $i$ and $j$ in the same affiliation trajectory, and $D$ is the diagonal matrix with diagonals $D_{ii}=\sum_j {A_{ij}}$.
 We set the dimension to $d=300$.
@@
 \begin{equation}
+	\label{eq:levyword2vec}
 	M_{ij} = \log\left(\frac{N(i,j) |D|}{N(i) N(j)}\right) - \log(k),
@@
 \paragraph{Direct optimization of gravity model:} Finally, we create an embedding by optimizing for the gravity model directly.
-Specifically, we construct a gravity matrix of $N$ organizations, where each cell of the matrix is calculated as $T_{ij}/m_i m_j$, where $T_{ij}$ is the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory, and $m_i$ and $m_j$ are the organizations' populations, defined here as the mean annual number of unique mobile and non-mobile authors affiliated.
-We then embed the gravity matrix using two approaches: a truncated singular-value decomposition (SVD), and multidimensional scaling (MDS), which embeds each location in an N-dimensional space such that pairwise distances are preserved as well as possible.
+Specifically, we construct a gravity matrix of $N$ organizations, where each cell of the matrix is calculated as $T_{ij}/m_i m_j$, where $T_{ij}$ is the number of co-occurrences of organizations $i$ and $j$ in the same affiliation trajectory, and $m_i$ and $m_j$ are the organizations' populations, defined here as the mean annual number of unique mobile and non-mobile authors affiliated.
+We then embed the gravity matrix using two approaches: the truncated SVD, and multidimensional scaling (MDS), which embeds each location in an N-dimensional space such that pairwise distances are preserved as well as possible.
 Typically, MDS uses Euclidean distance to measure the distance between vectors.
@@
 		A value of $\gamma = 0.75$ is the default for \textit{word2vec}.
-		There is virtually no difference in performance based on $\gamma$.
-		All variants perform better on same-country organization pairs, and worse on different-country pairs, than on all pairs of  of organizations than on all pairs.
+		There is virtually no difference in performance for different $\gamma$ values.
+		All variants perform better on same-country organization pairs, and worse on different-country pairs, than on all pairs of organizations.
 		Embeddings with larger dimensions outperform mid-size embeddings for the different-country case.
@@
 
-We observe that the cosine distance between embedding vectors, which we call here the "Embedding Distance", explains more of the flux, and results in lower prediction error than all baselines we considered (See Fig.~\ref{fig:supp:distancemetrics}).
+We observe that the cosine distance between embedding vectors, which we call here the ``Embedding Distance'', explains more of the flux, and results in lower prediction error than all baselines we considered (See Fig.~\ref{fig:supp:distancemetrics}).
 This performance advantage holds across \emph{the exponential and the power-law forms of the gravity model of mobility}.
@@
 
-\subsection{Why do neural embeddings outperform direct matrix factorization?}
-Why do neural-embedding approaches, which rely on stochastic gradient descent, outperform direct matrix factorization, especially given that \textit{word2vec} \emph{is} implicitly approximating factorization?
-An issue in the matrix factorization approach is that it is sensitive to small values.
-The matrix factorization approach embeds affiliations $i$ and $j$ such that their dot similarity is as close as to $\log (T_{ij} / P(i) P(j))$.
-If the flow $T_{ij}$ is considerably small or zero, the dot similarity approaches $-\infty$, pushing $i$ and $j$ away in the embedding space~\autocite{levy2014neural, Qui2018}.
-This is particularly problematic when the window size is small because most affiliation pairs would have no flow, which is indeed the case in our experiments.
-To circumvent this problem, the previous studies~\autocite{levy2014neural, Qui2018} add a constant flow between the affiliation pairs with no flow.
-However, this changes the data to which we fit the model, and small flows still have a considerably strong impact on the embedding.
+\subsection{Why do neural embeddings outperform matrix factorization?}
+Why do neural embedding approaches outperform Levy's {\it word2vec} based on matrix factorization?
+%Why do neural-embedding approaches, which rely on stochastic gradient descent, outperform direct matrix factorization, especially given that \textit{word2vec} \emph{is} implicitly approximating factorization?
+We find that Levy's {\it word2vec} suffers from extreme values in the matrix to factorize, which are numerous when window size is small.
+Remind that Levy's {\it word2vec} generates embeddings by factorizing matrix $M$ with entries
+$M_{ij} = \log\left[N(i,j)|D|/ (N(i) N(j))\right] - \log k$ based on the SVD (Eq.~\eqref{eq:levyword2vec}), where
+$N(i,j)$ is the number of co-occurrences of organizations $i$ and $j$ in the context window.
+An issue is that when $N(i,j)$ is closer to zero, $M_{ij}$ goes to $-\infty$.
+To prevent such extreme values, a constant is added to $N(i,j)$ if $N(i,j)=0$ in Levy's {\it word2vec}~\autocite{levy2014neural, Qui2018}.
+However, this changes the data to which we fit the model, and small $N(i,j)$ values, which are likely to arise due to noise in data, still have a profound impact on the embedding.
+The problem is aggravated when the size, $w$, of context window is small.
+As the window size becomes smaller, two institutions are less likely to co-appear in the same window, yielding more affiliation pairs with $N(i,j)=0$, which is the case in our experiment (i.e., we set the context window size $w=1$).
+%This is particularly problematic when the context window is small and most affiliation pairs would have no direct flow, leading to $N(i,j)=0$ for most affiliation pairs $(i,j)$.
 Also, it is well known that SVD itself is vulnerable to outliers \autocite{xu2012robust, huber1981robust, xu1995robust, chandrasekaran2011rank, candes2011robust}.
-The stochastic gradient descent algorithm (SGD), which is employed in SGNS \textit{word2vec}, is more robust than SVD and can enhance generalization and effectiveness of {\it word2vec} model \autocite{ma2018power, smith2020generalization, zhang2019algorithmic}.
+The stochastic gradient descent algorithm (SGD), which is employed in neural embedding approaches, is more robust than SVD and can enhance the generalization and effectiveness of {\it word2vec}~\autocite{ma2018power, smith2020generalization, zhang2019algorithmic}.
 

### 2021-03-15 paper/rebuttal/rebuttal.tex
second pass

@@
 Why do neural embedding approaches outperform Levy's {\it word2vec} based on matrix factorization?
-%Why do neural-embedding approaches, which rely on stochastic gradient descent, outperform direct matrix factorization, especially given that \textit{word2vec} \emph{is} implicitly approximating factorization?
-We find that Levy's {\it word2vec} suffers from extreme values in the matrix to factorize, which are numerous when window size is small.
-Remind that Levy's {\it word2vec} generates embeddings by factorizing matrix $M$ with entries
-$M_{ij} = \log\left[N(i,j)|D|/ (N(i) N(j))\right] - \log k$ based on the SVD (Eq.~\eqref{eq:levyword2vec}), where
-$N(i,j)$ is the number of co-occurrences of organizations $i$ and $j$ in the context window.
+We find that Levy's {\it word2vec} suffers from extreme values in the matrix to factorize, which are numerous when the context window size is small.
+Remind that Levy's {\it word2vec} generates embeddings by factorizing matrix $M$ given by Eq.~\eqref{eq:levyword2vec}, i.e.,
+\begin{equation}
+	M_{ij} = \log\left(\frac{N(i,j) |D|}{N(i) N(j)}\right) - \log k, \nonumber
+\end{equation}
+based on the SVD where $N(i,j)$ is the number of co-occurrences of organizations $i$ and $j$ in the context window.
 An issue is that when $N(i,j)$ is closer to zero, $M_{ij}$ goes to $-\infty$.
@@
 However, this changes the data to which we fit the model, and small $N(i,j)$ values, which are likely to arise due to noise in data, still have a profound impact on the embedding.
-The problem is aggravated when the size, $w$, of context window is small.
-As the window size becomes smaller, two institutions are less likely to co-appear in the same window, yielding more affiliation pairs with $N(i,j)=0$, which is the case in our experiment (i.e., we set the context window size $w=1$).
-%This is particularly problematic when the context window is small and most affiliation pairs would have no direct flow, leading to $N(i,j)=0$ for most affiliation pairs $(i,j)$.
+This problem is aggravated when the context window size $w$ is small.
+As the window size $w$ becomes smaller, two institutions are less likely to co-appear in the same window, yielding more affiliation pairs with $N(i,j)=0$, which is the case in our experiment (i.e., we set the context window size $w=1$).
 Also, it is well known that SVD itself is vulnerable to outliers \autocite{xu2012robust, huber1981robust, xu1995robust, chandrasekaran2011rank, candes2011robust}.

### 2021-03-16 paper/rebuttal/rebuttal.tex
unset draft mode
change the notation for the number of organizations from N to C

@@
 \paragraph{SVD on co-occurrence matrix:}The first of these baselines uses the distance between vectors in an embedding space produced through the singular value decomposition (SVD) of the underlying location co-occurrence matrix.
-First, we construct the co-occurrence matrix of $N$ organizations, $A_{ij}$ given by the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory.
+First, we construct the co-occurrence matrix of $C$ organizations, $A_{ij}$ given by the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory.
 Then, we apply the truncated SVD with $d=300$ on the flow matrix $A$ directly.
@@
 We generate Laplacian Eigenmap embeddings by applying a truncated singular value decomposition to matrix $L$ given by $L=D - A$, where
-$A$ is the co-occurrence matrix of $N$ organizations with element $A_{ij}$ indicating the number of co-occurrences of organizations $i$ and $j$ in the same affiliation trajectory, and $D$ is the diagonal matrix with diagonals $D_{ii}=\sum_j {A_{ij}}$.
+$A$ is the co-occurrence matrix of $C$ organizations with element $A_{ij}$ indicating the number of co-occurrences of organizations $i$ and $j$ in the same affiliation trajectory, and $D$ is the diagonal matrix with diagonals $D_{ii}=\sum_j {A_{ij}}$.
 We set the dimension to $d=300$.
@@
 Here, we compare the performance of \textit{word2vec} embeddings against those calculated directly using Levy's SVD.
-First, we construct the matrix of $N$ organizations
+First, we construct the $C\times C$ matrix $M$ whose entries $M_{ij}$ are given by
 \begin{equation}
@@
 \paragraph{Direct optimization of gravity model:} Finally, we create an embedding by optimizing for the gravity model directly.
-Specifically, we construct a gravity matrix of $N$ organizations, where each cell of the matrix is calculated as $T_{ij}/m_i m_j$, where $T_{ij}$ is the number of co-occurrences of organizations $i$ and $j$ in the same affiliation trajectory, and $m_i$ and $m_j$ are the organizations' populations, defined here as the mean annual number of unique mobile and non-mobile authors affiliated.
+Specifically, we construct a gravity matrix of $C$ organizations, where each cell of the matrix is calculated as $T_{ij}/m_i m_j$, where $T_{ij}$ is the number of co-occurrences of organizations $i$ and $j$ in the same affiliation trajectory, and $m_i$ and $m_j$ are the organizations' populations, defined here as the mean annual number of unique mobile and non-mobile authors affiliated.
 We then embed the gravity matrix using two approaches: the truncated SVD, and multidimensional scaling (MDS), which embeds each location in an N-dimensional space such that pairwise distances are preserved as well as possible.

### 2021-03-16 paper/rebuttal/rebuttal.tex
resolve notational conflict

@@
 \paragraph{SVD on co-occurrence matrix:}The first of these baselines uses the distance between vectors in an embedding space produced through the singular value decomposition (SVD) of the underlying location co-occurrence matrix.
-First, we construct the co-occurrence matrix of $C$ organizations, $A_{ij}$ given by the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory.
+First, we construct the co-occurrence matrix of all organizations, $A_{ij}$ given by the co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory.
 Then, we apply the truncated SVD with $d=300$ on the flow matrix $A$ directly.
@@
 We generate Laplacian Eigenmap embeddings by applying a truncated singular value decomposition to matrix $L$ given by $L=D - A$, where
-$A$ is the co-occurrence matrix of $C$ organizations with element $A_{ij}$ indicating the number of co-occurrences of organizations $i$ and $j$ in the same affiliation trajectory, and $D$ is the diagonal matrix with diagonals $D_{ii}=\sum_j {A_{ij}}$.
+$A$ is the co-occurrence matrix of all organizations with element $A_{ij}$ indicating the number of co-occurrences of organizations $i$ and $j$ in the same affiliation trajectory, and $D$ is the diagonal matrix with diagonals $D_{ii}=\sum_j {A_{ij}}$.
 We set the dimension to $d=300$.
@@
 Here, we compare the performance of \textit{word2vec} embeddings against those calculated directly using Levy's SVD.
-First, we construct the $C\times C$ matrix $M$ whose entries $M_{ij}$ are given by
+First, we construct a matrix $M$ whose entries $M_{ij}$ are given by
 \begin{equation}
@@
 \paragraph{Direct optimization of gravity model:} Finally, we create an embedding by optimizing for the gravity model directly.
-Specifically, we construct a gravity matrix of $C$ organizations, where each cell of the matrix is calculated as $T_{ij}/m_i m_j$, where $T_{ij}$ is the number of co-occurrences of organizations $i$ and $j$ in the same affiliation trajectory, and $m_i$ and $m_j$ are the organizations' populations, defined here as the mean annual number of unique mobile and non-mobile authors affiliated.
+Specifically, we construct a gravity matrix of all organizations, where each cell of the matrix is calculated as $T_{ij}/m_i m_j$, where $T_{ij}$ is the number of co-occurrences of organizations $i$ and $j$ in the same affiliation trajectory, and $m_i$ and $m_j$ are the organizations' populations, defined here as the mean annual number of unique mobile and non-mobile authors affiliated.
 We then embed the gravity matrix using two approaches: the truncated SVD, and multidimensional scaling (MDS), which embeds each location in an N-dimensional space such that pairwise distances are preserved as well as possible.

### 2021-03-16 workflow/clustering_figure/script/draw_clustering_figure_country_level.py
redraw clustering figure

@@ -53,7 +53,7 @@ def draw_figure(
 
     # Get representative vector, calculate pairwise similarity, and do hierarchical clustering.
     target_countries = [
-        k for k, v in Counter(country_list).items() if v >= 25 and k != "United States"
+        k for k, v in Counter(country_list).items() if v >= 27 
     ]
 
     # First, get all pairwise distances and save to a file
@@ -102,6 +102,7 @@ def draw_figure(
     name_convert_dict["Taiwan, Province of China"] = "Taiwan"
     name_convert_dict["Iran, Islamic Republic of"] = "Iran"
     name_convert_dict["United Kingdom"] = "U.K."
+    name_convert_dict["United States"] = "U.S."
     name_convert_dict["Russian Federation"] = "Russia"
     name_convert_dict["South Africa"] = "S. Africa"
     name_convert_dict["Czech Republic"] = "Czech"
@@ -122,7 +123,7 @@ def draw_figure(
         "zh": "#FF5722",
         "de": "#F5CC26",
         "pt": "#009688",
-        "nl": "#BDA661",
+        "nl": "#a18b47",
         "fr": "#d3d3d3",
         "es": "#d3d3d3",
         "it": "#d3d3d3",
@@ -201,7 +202,7 @@ def draw_figure(
         sim_mtx,
         cmap="viridis_r",
         yticklabels=target_countries,
-        vmax=0.776,
+        vmax=0.786,
         row_linkage=linked,
         col_linkage=linked,
         row_colors=[
@@ -235,29 +236,29 @@ def draw_figure(
     from matplotlib.patches import Rectangle
 
     ax.add_patch(
-        Rectangle((-4.6, 0), 4.6, 7, fill=False, clip_on=False, edgecolor="black", lw=3)
+        Rectangle((-4.7, 0), 4.7, 9, fill=False, clip_on=False, edgecolor="black", lw=3)
     )
     ax.add_patch(
-        Rectangle((-4.6, 7), 4.6, 4, fill=False, clip_on=False, edgecolor="black", lw=3)
+        Rectangle((-4.7, 9), 4.7, 4, fill=False, clip_on=False, edgecolor="black", lw=3)
     )
     ax.add_patch(
         Rectangle(
-            (-4.6, 11), 4.6, 6, fill=False, clip_on=False, edgecolor="black", lw=3
+            (-4.7, 13), 4.7, 5, fill=False, clip_on=False, edgecolor="black", lw=3
[…]

### 2021-03-16 paper/current/main.tex

@@
 The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores calculated from the underlying mobility network (Fig.~\ref{fig:supp:distancemetrics}, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurence matrix, Levy's symmetric \textit{word2vec}\autocite{levy2014neural}, and even direct optimization of the gravity model (Fig.\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurrence matrix, Levy's symmetric \textit{word2vec}\autocite{levy2014neural}, and even direct optimization of the gravity model (Fig.\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
 In sum, our results demonstrate that, consistently and efficiently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
@@
 		\textbf{b.} Predictions of flux between airport pairs made using embedding distance (top) outperform those made using geographic distance (bottom).
-		Boxplots show the distribution of actual flux for binned values of predicted flux.
+		Box-plots show the distribution of actual flux for binned values of predicted flux.
 		Box color corresponds to the degree to which the distribution overlaps with $y = x$;
@@
 
-Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimial in-vectors and out-vectors such that $\vect{v}_i = \vect{u}_i$ \autocite{levy2014neural}.
+Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimal in-vectors and out-vectors such that $\vect{v}_i = \vect{u}_i$ \autocite{levy2014neural}.
 Setting $\gamma = 1$ and substituting $\vect{v}_i = \vect{u}_i$ into Eq.~\ref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
 \begin{align}
-	\widehat{T}_{ij} \propto  P(i) P(j\given i) = \frac{P(i)P(j)\exp(\vect{v}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:flow_w2v_ng1}
+	\widehat{T}_{ij} \propto  N(i) P(j\given i) = \frac{NP(i)P(j)\exp(\vect{v}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:flow_w2v_ng1}
 \end{align}
+where $N(i) = NP(i)$ is the frequency of location $i$ in the data, and $N=\sum_{i \in {\cal A}} N(i)$ is the sum of frequencies of all locations.
 
@@
 First, the skip-gram \textit{word2vec} model does not leverage directionality, meaning that embedding will be less effective at capturing mobility for which directionality is critical.
-Future studies may consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality, as well as their correspondance to asymetric mobility models, such as the radiation model~\cite{simini2012universal}.
+Future studies may consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality, as well as their correspondence to asymmetric mobility models, such as the radiation model~\cite{simini2012universal}.
 Second, the neural embedding approach is most useful in cases of mobility between discrete geographic units such as between countries, cities, and businesses; this approach is less useful in the case of mobility between locations represented using geographic coordinates, such as in the modeling of animal movements.
@@
 
-Negative sampling trains {\it word2vec} using a binary classification task as follows.
+Negative sampling trains {\it word2vec} as follows.
 For each target word $i$, we sample a context word $j$ from the given data and label it as positive, denoted by $Y_{j}=1$.
@@
 Let us revisit negative sampling from the perspective of NCE.
-We rewrite the logistic regression model in negative sampling (Eq.~\eqref{eq:logistic-regress}) in form of the posterior probability:
+We rewrite the logistic regression model in negative sampling (Eq.~\ref{eq:logistic-regress}) in form of the posterior probability:
 \begin{align}
@@
 We also use network-based distances, calculating vectors using a Personalized Page Rank approach and measuring the distance between them using cosine distance and Jensen-Shannon Divergence (see \SI).
-Finally, we compare the embedding distance against embeddings calculated through direct matrix factorization, following the approach that \textit{word2vec} implicitley approximates~\autocite{levy2014neural}.
+Finally, we compare the embedding distance against embeddings calculated through direct matrix factorization, following the approach that \textit{word2vec} implicitly approximates~\autocite{levy2014neural}.
 
@@
 
-We model co-occurences $T_{ij}$ for locations $i$ and $j$ (referred to as flux), using the gravity law of mobility~\autocite{zipf1946gravity}.
+We model co-occurrences $T_{ij}$ for locations $i$ and $j$ (referred to as flux), using the gravity law of mobility~\autocite{zipf1946gravity}.
 The gravity law of mobility, which was inspired by Newton's law of gravity, postulates that attraction between two locations is a function of their population and the distance between them.

### 2021-03-16 paper/current/main.tex
changed clustering fig text

--- 2021-03-15 paper/current/main.tex
@@
 In doing so, we can examine the country-level structure that governs scientific mobility.
-We define the representative vector of each country as the average of their organizational vectors and, using their cosine similarities, perform hierarchical clustering of nations that have at least 25 organizations represented in the embedding space, excluding the United States which is a dominant hub well connected to most other countries (see Fig.
+We define the representative vector of each country as the average of their organizational vectors and, using their cosine similarities, perform hierarchical clustering of nations that have at least 25 organizations represented in the embedding space (see Fig.
 \ref{fig:clustering}a).
-The six identified clusters roughly correspond to countries in East-Asia (orange), Scandinavia (dark purple), the British Commonwealth (light purple), and Central and Eastern Europe (light blue), and then two remaining diverse clusters contain a mix of European, Latin American, and Mediterranean countries.
-The cluster structure shows that not only geography but also linguistic ties between countries are related to scientific mobility.
+The six identified clusters roughly correspond to countries in Asia and North America (orange), Northern Europe (dark blue), the British Commonwealth and Iran (purple), Central and Eastern Europe (light blue), South America and Iberia (dark green), and Western Europe and the Mediterranean (light green).
+The cluster structure shows that not only geography but also linguistic ties and cultural between countries are related to scientific mobility.
 
@@
 		\textbf{Geography, then language, conditions international mobility.}
-		\textbf{a.} Hierarchically clustered similarity matrix of country vectors aggregated as the mean of all organization vectors within the country, excluding the United States and countries with less than 25 organizations.
+		\textbf{a.} Hierarchically clustered similarity matrix of country vectors aggregated as the mean of all organization vectors within countries with at least 25 organizations.
 		Color of matrix cells corresponds to the cosine similarity between country vectors.

### 2021-03-16 paper/rebuttal/rebuttal.tex

@@
 	\label{eq:levyword2vec}
-	M_{ij} = \log\left(\frac{N(i,j) |D|}{N(i) N(j)}\right) - \log(k),
+	M_{ij} = \log\left(\frac{N(i,j) N}{N(i) N(j)}\right) - \log(k),
 \end{equation}
-where $N(i,j)$ is the number of times the location pair $(i,j)$ appears given the window size $w$ in the total corpus $D$, $N(i)=\sum_{j=1}^N N(i,j)$ as the number of items $i$ occurred given the window size $w$ in $D$, and $k$ is the number of negative samples.
+where $N(i,j)$ is the number of times that the center-context location pair $(i,j)$ appears in the context window, $N(i)=\sum_{j\in {\cal A}} N(i,j)$ is the number of times that $i$ appears as the center location in all center-context location pairs, $N=\sum_{i \in {\cal A}} N(i)$ is the number of all center-context location pairs, and $k$ is the number of negative samples.
 We used $w=1$ and $k=5$ which is the same setting as in our main result.
@@
 
-	We agree that the new revolutions in neural embeddings offer huge potential for the study of human mobility, however we argue that our contribution is dependent on \textit{word2vec}, both for its equivelance with the gravity model of mobility, as well as for the model's simplicity and ubiquity.
+	We agree that the new revolutions in neural embeddings offer huge potential for the study of human mobility, however we argue that our contribution is dependent on \textit{word2vec}, both for its equivalence with the gravity model of mobility, as well as for the model's simplicity and ubiquity.
 	\textit{Word2vec} is also efficient; deep neural models often require tremendous amounts of training data ($\sim$3 billion words in BERT) and model parameters, making them infeasible for most studies of mobility.

### 2021-03-17 workflow/visualize_embedding/script/draw_california_figure_si.py
redraw_viz_figs

@@ -36,12 +36,8 @@ def draw_figure(
     )
 
     size_data = pd.read_csv(INPUT_SIZE_FILE, sep="\t", dtype={"cwts_org_no": str})
-    size_data = size_data.drop(size_data.index[len(size_data) - 1])
-    size_data.person_count = size_data.person_count.astype(int)
-    mean_size_dict = (
-        size_data.groupby("cwts_org_no")["person_count"].apply(np.mean).to_dict()
-    )
-    size_list = np.array([mean_size_dict[inst] for inst in institute_list])
+    size_dict = size_data.set_index('cwts_org_no')['size'].to_dict()
+    size_list = np.array([size_dict[inst] for inst in institute_list])
 
     rcParams["figure.figsize"] = 20, 18
     if FONT_PATH:
@@ -62,49 +58,49 @@ def draw_figure(
     argumented_size_list = np.array([np.log(size) / np.log(1.1) for size in size_list])
 
     plt.scatter(
-        -umap_coords[:, 0],
-        umap_coords[:, 1],
+        -umap_coords[:, 1],
+        umap_coords[:, 0],
         s=argumented_size_list * 1.5,
         c=c_list,
         linewidth=0.4,
         edgecolor="white",
     )
 
-    plt.text(3, -3.7, "San Francisco\nBay Area", c="black", fontproperties=large_prop)
-    plt.text(-3, 0.6, "Los Angeles", c="black", fontproperties=large_prop)
-    plt.text(-4.6, -3.6, "San Diego", c="black", fontproperties=large_prop)
+#     plt.text(3, -3.7, "San Francisco\nBay Area", c="black", fontproperties=large_prop)
+#     plt.text(-3, 0.6, "Los Angeles", c="black", fontproperties=large_prop)
+#     plt.text(-4.6, -3.6, "San Diego", c="black", fontproperties=large_prop)
 
-    ## Univ annoa
-    c = awesome_c_list[4]
-    plt.text(-0.4, -5.1, "California State \nSystem", c=c, fontproperties=prop)
-    plt.text(0.65, -2.4, "Stanford", c=c, fontproperties=prop)
-    plt.text(-0.65, -1.85, "Caltech", c=c, fontproperties=prop)
[…]

### 2021-03-17 workflow/visualize_embedding/script/draw_massachusetts_figure.py

@@ -34,12 +34,8 @@ def draw_figure(
     )
 
     size_data = pd.read_csv(INPUT_SIZE_FILE, sep="\t", dtype={"cwts_org_no": str})
-    size_data = size_data.drop(size_data.index[len(size_data) - 1])
-    size_data.person_count = size_data.person_count.astype(int)
-    mean_size_dict = (
-        size_data.groupby("cwts_org_no")["person_count"].apply(np.mean).to_dict()
-    )
-    size_list = np.array([mean_size_dict[inst] for inst in institute_list])
+    size_dict = size_data.set_index('cwts_org_no')['size'].to_dict()
+    size_list = np.array([size_dict[inst] for inst in institute_list])
 
     rcParams["figure.figsize"] = 20, 18
     if FONT_PATH:
@@ -61,36 +57,36 @@ def draw_figure(
         linewidth=0.3,
         edgecolor="white",
     )
-    plt.text(4.7, -4.3, "Boston,\nCambridge", c="black", fontproperties=large_prop)
-    plt.text(7, -1.8, "Worcester", c="black", fontproperties=large_prop)
+#     plt.text(4.7, -4.3, "Boston,\nCambridge", c="black", fontproperties=large_prop)
+#     plt.text(7, -1.8, "Worcester", c="black", fontproperties=large_prop)
 
-    ## Univ annoate
-    c = awesome_c_list[4]
-    plt.text(8.2, -2.8, "The UMass\nSystem", c=c, fontproperties=prop)
-    plt.text(4.1, -2.8, "MIT", c=c, fontproperties=prop)
-    plt.text(4.0, -4.6, "Harvard", c=c, fontproperties=prop)
-    plt.text(6.1, -4.1, "Boston \nUniversity", c=c, fontproperties=prop)
-    plt.text(5.8, -5, "Northeastern\nUniversity", c=c, fontproperties=prop)
-    plt.text(7.5, -1.4, "Clark University", c=c, fontproperties=prop)
-    plt.text(3.2, -6.3, "Tufts\nUniversity", c=c, fontproperties=prop)
-    plt.text(6.7, -5.6, "Brandeis\nUniversity", c=c, fontproperties=prop)
+#     ## Univ annoate
+#     c = awesome_c_list[4]
+#     plt.text(8.2, -2.8, "The UMass\nSystem", c=c, fontproperties=prop)
[…]

### 2021-03-17 workflow/visualize_embedding/script/draw_pennsylvania_figure_si.py

@@ -34,12 +34,8 @@ def draw_figure(
     )
 
     size_data = pd.read_csv(INPUT_SIZE_FILE, sep="\t", dtype={"cwts_org_no": str})
-    size_data = size_data.drop(size_data.index[len(size_data) - 1])
-    size_data.person_count = size_data.person_count.astype(int)
-    mean_size_dict = (
-        size_data.groupby("cwts_org_no")["person_count"].apply(np.mean).to_dict()
-    )
-    size_list = np.array([mean_size_dict[inst] for inst in institute_list])
+    size_dict = size_data.set_index('cwts_org_no')['size'].to_dict()
+    size_list = np.array([size_dict[inst] for inst in institute_list])
 
     rcParams["figure.figsize"] = 20, 18
     if FONT_PATH:
@@ -54,7 +50,7 @@ def draw_figure(
     argumented_size_list = np.array([np.log(size) / np.log(1.1) for size in size_list])
 
     plt.scatter(
-        umap_coords[:, 0],
+        -umap_coords[:, 0],
         umap_coords[:, 1],
         s=argumented_size_list * 1.5,
         c=c_list,
@@ -62,48 +58,48 @@ def draw_figure(
         edgecolor="white",
     )
 
-    plt.text(1.3, 3.8, "Pittsburgh", c="black", fontproperties=large_prop)
-    plt.text(2.4, 1.5, "Philadelphia", c="black", fontproperties=large_prop)
+#     plt.text(1.3, 3.8, "Pittsburgh", c="black", fontproperties=large_prop)
+#     plt.text(2.4, 1.5, "Philadelphia", c="black", fontproperties=large_prop)
 
-    ## Univ annoate
-    c = awesome_c_list[4]
-    plt.text(1.08, 4.6, "CMU", c=c, fontproperties=prop)
-    plt.text(5.08, 0.8, "UPenn", c=c, fontproperties=prop)
-    plt.text(3.65, 0.88, "Villanova", c=c, fontproperties=prop)
-    plt.text(2.82, -1.35, "Lehigh", c=c, fontproperties=prop)
-    plt.text(3, -2.7, "Pennsylvania\nState System", c=c, fontproperties=prop)
-    plt.text(1.35, 5.05, "Pittsburgh", c=c, fontproperties=prop)
[…]

### 2021-03-17 workflow/visualize_embedding/script/draw_usa_figure.py

@@ -35,12 +35,8 @@ def draw_figure(
     )
 
     size_data = pd.read_csv(INPUT_SIZE_FILE, sep="\t", dtype={"cwts_org_no": str})
-    size_data = size_data.drop(size_data.index[len(size_data) - 1])
-    size_data.person_count = size_data.person_count.astype(int)
-    mean_size_dict = (
-        size_data.groupby("cwts_org_no")["person_count"].apply(np.mean).to_dict()
-    )
-    size_list = np.array([mean_size_dict[inst] for inst in institute_list])
+    size_dict = size_data.set_index('cwts_org_no')['size'].to_dict()
+    size_list = np.array([size_dict[inst] for inst in institute_list])
 
     rcParams["figure.figsize"] = 20, 18
     if FONT_PATH:
@@ -54,57 +50,14 @@ def draw_figure(
     argumented_size_list = np.array([np.log(size) / np.log(1.3) for size in size_list])
 
     plt.scatter(
-        umap_coords[:, 0],
         umap_coords[:, 1],
+        umap_coords[:, 0],
         s=argumented_size_list * 1.5,
         c=c_list,
         linewidth=0.3,
         edgecolor="white",
     )
 
-    ## NorthEast annotate
-    c = awesome_c_list[2]
-    plt.text(6.3, -0.9, "New York", c=c, fontproperties=prop)
-    plt.text(3.5, 0.6, "New Jersey", c=c, fontproperties=prop)
-    plt.text(3.15, -0.8, "Pennsylvania", c=c, fontproperties=prop)
-    plt.text(-7.3, -3.1, "Pennsylvania,\nPittsburgh", c=c, fontproperties=prop)
-    plt.text(1.55, 3.8, "Massachusetts ", c=c, fontproperties=prop)
-    plt.text(2.4, 3.1, "Rhode Island", c=c, fontproperties=prop)
-    plt.text(1.85, 1.55, "Connecticut", c=c, fontproperties=prop)
-
-    # South annotate
-    c = awesome_c_list[3]
-    plt.text(-1, -5.3, "Texas", c=c, fontproperties=prop)
-    plt.text(-6.5, -1, "Maryland", c=c, fontproperties=prop)
-    plt.text(-4.9, -0.6, "North Carolina", c=c, fontproperties=prop)
[…]

### 2021-03-17 workflow/visualize_embedding/script/get_umap_coordinate.py

@@ -19,6 +19,7 @@ def get_umap_coordinate_by_level(
     TARGET,
     N_NEIGHBOR,
     MIN_DIST,
+    RANDOM_SEED,
     OUTPUT_FILE,
 ):
 
@@ -51,19 +52,20 @@ def get_umap_coordinate_by_level(
         institute_list,
         n_neighbor=N_NEIGHBOR,
         min_dist=MIN_DIST,
+        random_state=RANDOM_SEED,
         out_file_path=OUTPUT_FILE,
     )
 
 
 if __name__ == "__main__":
-    print(sys.argv)
     INPUT_EMBEDDING_FILE = sys.argv[1]
     INPUT_META_INFO_FILE = sys.argv[2]
     LEVEL = sys.argv[3]
     TARGET = sys.argv[4]
     N_NEIGHBOR = int(sys.argv[5])
     MIN_DIST = float(sys.argv[6])
-    OUTPUT_FILE = sys.argv[7]
+    RANDOM_SEED = int(sys.argv[7])
+    OUTPUT_FILE = sys.argv[8]
 
     get_umap_coordinate_by_level(
         INPUT_EMBEDDING_FILE,
@@ -72,5 +74,6 @@ if __name__ == "__main__":
         TARGET,
         N_NEIGHBOR,
         MIN_DIST,
+        RANDOM_SEED,
         OUTPUT_FILE,
     )

### 2021-03-17 paper/current/main.tex

@@
 We validate this finding quantitatively with the cosine distance between nations (the centroids of organizations vectors belonging to that country).
-Malaysia is nearer to many Islamic countries such as Iraq ($d = 0.29$), Pakistan ($d = 0.31$), and Saudi Arabia ($d = 0.41$)  than neighboring but Buddhist Thailand ($d = 0.43$) and predominantly-secular Vietnam ($d = 0.48$).
+Malaysia is nearer to many Islamic countries such as Iraq ($d = 0.27$), Pakistan ($d = 0.32$), and Saudi Arabia ($d = 0.41$)  than neighboring but Buddhist Thailand ($d = 0.43$) and neighboring Singapore ($d = 0.48$).
 
 Linguistic and historical ties also affect scientific mobility.
-We observe that Spanish-speaking Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), rather than Portuguese-speaking Brazil ($d = 0.34$ vs.
-$d = 0.52$ for Mexico and $d = 0.39$ vs.
+We observe that Spanish-speaking Latin American nations are positioned near Spain (Fig.~\ref{fig:projection}c), rather than Portuguese-speaking Brazil ($d = 0.35$ vs.
+$d = 0.54$ for Mexico and $d = 0.39$ vs.
 $d = 0.49$ for Chile) reflecting linguistic and cultural ties.
-Similarly, North-African countries that were once under French rule such as Morocco are closer to France ($d =0.35$) than to similarly geographically-distant European countries such as Spain ($d = 0.40$), Portugal ($d = 0.55$), and Italy ($d = 0.53$).
+Similarly, North-African countries that were once under French rule such as Morocco are closer to France ($d =0.32$) than to similarly geographically-distant European countries such as Spain ($d = 0.39$), Portugal ($d = 0.52$), and Italy ($d = 0.52$).
 Comparable patterns exist even within a single country.
-For example, organizations within Quebec in Canada are located nearer France ($d = 0.37$) than the United States ($d = 0.49$).
+For example, organizations within Quebec in Canada are located nearer France ($d = 0.37$) than the United States ($d = 0.51$).
 
@@
 Harvard \& MIT).
-For example, even though UMass Boston is located in Boston, it clusters with other universities in the UMass System ($d = 0.33$) rather than the other typically more highly-ranked and research-focused organizations in Boston ($d = 0.38$), implying a relative lack of mobility between the two systems.
+For example, even though UMass Boston is located in Boston, it clusters with other universities in the UMass System ($d = 0.29$) rather than the other typically more highly-ranked and research-focused organizations in Boston ($d = 0.39$), implying a relative lack of mobility between the two systems.
 Similar structures can be observed in other states such as among New York's CUNY and SUNY systems (Fig.~\ref{fig:supp:proj_newyork}), Pennsylvania's state system (Fig.~\ref{fig:supp:proj_pennsylvania}), Texas's Agricultural and Mechanical universities (Fig.~\ref{fig:supp:proj_texas}), and between the University of California and State University of California systems (Fig.~\ref{fig:supp:proj_california}).

### 2021-03-22 paper/rebuttal/rebuttal.tex
reflect yy comment

@@
 
-Furthermore, our subsequent experiments show that our approach's performance is robust, exceeding many other baselines, even direct optimization of the gravity model.
+Furthermore, our subsequent experiments show that our approach robustly outperforms exceeding many other baselines, even direct optimization of the gravity model.
 Therefore, we are confident that these changes have brought a qualitative leap in the significance of our findings.
@@
 Figures in the updated manuscript have been re-drawn with $\gamma = 1.0$, and the findings remain qualitatively similar.
+The most notable differences are observed in figures 3 (the UMAP projection of all organizations) and 4 (the clustering of country-level vectors);
+still, the findings from these plots are largely similar, and quantitative measurements associated with these plots robust. 
 As a side benefit, including the hyperparameter of $\gamma$ also effectively doubles the number of embeddings trained, and that results are so similar across different embedding provides further evidence of the robustness of the approach applied to our data.

### 2021-03-23 paper/current/main.tex
small edits

@@
 
-In revealing the correspondence between neural embeddings and the gravity model, the study of human mobility can move beyond geographic and network-based models of mobility, and instead leverage the high-order structure from individuals' mobility trajectories.
+In revealing the correspondence between neural embeddings and the gravity model, the study of human mobility can move beyond geographic and network-based models of mobility, and instead leverage the high-order structure from individuals' mobility trajectories using these robust and efficient methods.
 While we focus on three domains of mobility, this approach could be applied to many different domains, such as general human migration, transit-network mobility, and more.
@@
 First, the skip-gram \textit{word2vec} model does not leverage directionality, meaning that embedding will be less effective at capturing mobility for which directionality is critical.
-Future studies may consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality, as well as their correspondence to asymmetric mobility models, such as the radiation model~\cite{simini2012universal}.
+Future studies may consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality, as well as their correspondance to asymetric mobility models, such as the radiation model~\cite{simini2012universal}.
 Second, the neural embedding approach is most useful in cases of mobility between discrete geographic units such as between countries, cities, and businesses; this approach is less useful in the case of mobility between locations represented using geographic coordinates, such as in the modeling of animal movements.
@@
 
-Negative sampling trains {\it word2vec} as follows.
+Negative sampling trains {\it word2vec} using a binary classification task as follows.
 For each target word $i$, we sample a context word $j$ from the given data and label it as positive, denoted by $Y_{j}=1$.
@@
 We also use network-based distances, calculating vectors using a Personalized Page Rank approach and measuring the distance between them using cosine distance and Jensen-Shannon Divergence (see \SI).
-Finally, we compare the embedding distance against embeddings calculated through direct matrix factorization, following the approach that \textit{word2vec} implicitly approximates~\autocite{levy2014neural}.
+Finally, we compare the embedding distance against embeddings calculated through direct matrix factorization, following the approach that \textit{word2vec} implicitley approximates~\autocite{levy2014neural}.
 
@@
 
-We model co-occurrences $T_{ij}$ for locations $i$ and $j$ (referred to as flux), using the gravity law of mobility~\autocite{zipf1946gravity}.
+We model co-occurences $T_{ij}$ for locations $i$ and $j$ (referred to as flux), using the gravity law of mobility~\autocite{zipf1946gravity}.
 The gravity law of mobility, which was inspired by Newton's law of gravity, postulates that attraction between two locations is a function of their population and the distance between them.

### 2021-04-13 paper/current/supp.tex

@@
 	\label{eq:ppr}
-	p_i = (1 - \alpha) v_i + \alpha p_i W,
+	p_i = (1 - \alpha) W p_i +  \alpha v_i 
 \end{equation}
@@
 
-For this baseline, we report results using the cosine distance, euclidean distance, and dot product between the embedding vectors.
+For this baseline, we report results using the cosine distance, Euclidean distance, and dot product between the embedding vectors.
 We find that the dot product performs by far the worst, worse than any other baseline considered $R^{2} = 0.004$, Table~\ref{supp:table:r2_table}).
 The cosine distance performs better, but worse than geographic distance ($R^{2} = 0.212$, Table~\ref{supp:table:r2_table}).
-The euclidean distance performs best, explaining more of the flux than geographic distance, and only being below the embedding distance ($R^{2} = 0.341$, Table~\ref{supp:table:r2_table}).
-Focusing on the euclidean distance, we find that using it as input to the gravity model results in better predictions than geographic distance using both the exponential model (RMSE $= 0.803$, Table~\ref{supp:table:rmse_exp_table}) and power law models, (RMSE $= 0.78$, Table~\ref{supp:table:rmse_power_table}), though it performs slightly better with the power law formulation.
+The Euclidean distance performs best, explaining more of the flux than geographic distance, and only being below the embedding distance ($R^{2} = 0.341$, Table~\ref{supp:table:r2_table}).
+Focusing on the Euclidean distance, we find that using it as input to the gravity model results in better predictions than geographic distance using both the exponential model (RMSE $= 0.803$, Table~\ref{supp:table:rmse_exp_table}) and power law models, (RMSE $= 0.78$, Table~\ref{supp:table:rmse_power_table}), though it performs slightly better with the power law formulation.
 
@@
 We then embed the gravity matrix using two approaches: a truncated singular value decomposition (SVD), and with multidimensional scaling (MDS), which embeds each location in a N-dimensional space such that pairwise distances are preserved as well as possible.
-Typically, MDS uses euclidean distance to measure distance between vectors.
-
-For this result, we report results using the cosine distance between embedding vectors for the SVD embedding, and the logged euclidean distance for the MDS embedding. 
+Typically, MDS uses Euclidean distance to measure distance between vectors.
+
+For this result, we report results using the cosine distance between embedding vectors for the SVD embedding, and the logged Euclidean distance for the MDS embedding. 
 We observe that the gravity-optimized SVD cosine distance has poor performance, more weakly correlated with actual flux than geographic distance ($R^{2} = 0.122$, Table~\ref{supp:table:r2_table}), and similarly poor prediction error when used as input to the gravity mode.
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's Euclidean} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.341 \hspace{6pt}\huxbpad{6pt}} &
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's Euclidean} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.803 \hspace{6pt}\huxbpad{6pt}} &
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity MDS euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity MDS Euclidean} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.904 \hspace{6pt}\huxbpad{6pt}} &
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's Euclidean} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.78 \hspace{6pt}\huxbpad{6pt}} &
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity MDS euclidean} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity MDS Euclidean} \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.795 \hspace{6pt}\huxbpad{6pt}} &

### 2021-04-13 paper/current/main.tex
updated abstract for submission

@@
 % Refs
+%\usepackage{scicite}
 \usepackage[style=nature,
@@
 }
+
+\usepackage{times}
+
+% Setup the margins of the page
+\topmargin 0.0cm
+\oddsidemargin 0.2cm
+\textwidth 16cm
+\textheight 21cm
+\footskip 1.0cm
+
+%The next command sets up an environment for the abstract to your paper.
+
+\newenvironment{sciabstract}{%
+\begin{quote} \bf}
+{\end{quote}}
 
@@
 \date{\today}
+
+% Double-space the manuscript.
+
+\baselineskip24pt
+
 \maketitle %}}}
@@
 %
-
-\begin{abstract}
-
-	Human mobility and migration drive major societal phenomena such as the growth and evolution of cities~\autocite{wef2017migration, curiel2018citygravity},  epidemics~\autocite{kraemer2020covid, truscott2012epidemicgravity}, economies~\autocite{kaluza2010cargo, kerr2011immigration}, and innovation~\autocite{kaiser2018innovation, sugimoto2017mostimpact, petersen2018multiscale}.
-	Historically, human mobility has been strongly constrained by physical separation---geographic distance~\autocite{zipf1946gravity}.
-	However, geographic distance is becoming less relevant in the increasingly-globalized world~\autocite{czaika2018globalisation, buchan2009globalization} in which physical barriers are shrinking while linguistic, cultural, and historical relationships are becoming more important.
-	As understanding mobility is becoming critical for contemporary society, finding frameworks that can capture this complexity is of paramount importance.
-	Here, we reveal that the neural embedding model \textit{word2ec}~\autocite{mikolov2013word2vec} is mathematically equivalent to the gravity model of mobility and, using three distinct human trajectory datasets, demonstrate that a neural embedding model can encode nuanced relationships between locations into a vector-space, providing an effective measure of distance that reflects the multi-faceted structure of human mobility.
-	Focusing on the case of scientific mobility, we show that embeddings of scientific organizations uncover cultural and linguistic relations, and even academic prestige, at multiple levels of granularity.
-	Furthermore, the embedding vectors reveal universal relationships between organizational characteristics and their place in the global landscape of scientific mobility.
-	The ability to learn scalable, dense, and meaningful representations of mobility directly from the data can open up new avenues for the study of mobility across domains.
-
-\end{abstract}
+\newpage
+\begin{sciabstract}
+	Human mobility drives major societal phenomena including epidemics, economies, and innovation.
+	Historically, mobility was constrained by geographic distance, however, in the globalizing world, language, culture, and history are increasingly important.
+	We propose using the neural embedding model \textit{word2vec} for studying mobility and capturing its complexity.
+    \textit{Word2ec} is shown to be mathematically equivalent to the gravity model of mobility, and using using three human trajectory datasets, we demonstrate that it encodes nuanced relationships between locations into a vector-space, providing a measure of effective distance that outperforms baselines.
+	Focusing on the case of scientific mobility, we show that embeddings uncover cultural, linguistic, and hierarchical relationships at multiple levels of granularity.
+	Connecting neural embeddings to the gravity model opens up new avenues for the study of mobility.
+\end{sciabstract}
 

### 2021-04-15 paper/current/main.tex
switch to science citation style
reflect yy comment

@@
 %\usepackage{scicite}
-\usepackage[style=nature,
+\usepackage[style=science,
 					backend=biber,
@@
 	Historically, mobility was constrained by geographic distance, however, in the globalizing world, language, culture, and history are increasingly important.
-	We propose using the neural embedding model \textit{word2vec} for studying mobility and capturing its complexity.
-    \textit{Word2ec} is shown to be mathematically equivalent to the gravity model of mobility, and using using three human trajectory datasets, we demonstrate that it encodes nuanced relationships between locations into a vector-space, providing a measure of effective distance that outperforms baselines.
+	Here, we show the mathematical equivalence between \textit{word2vec} model and the gravity model of mobility and the demonstrate that, by using three human trajectory datasets, \textit{word2vec} encodes nuanced relationships between locations into a vector-space, providing a measure of effective distance.
 	Focusing on the case of scientific mobility, we show that embeddings uncover cultural, linguistic, and hierarchical relationships at multiple levels of granularity.

### 2021-04-19 paper/current/supp.tex
update the math
edit ppr

@@
 We examine the gravity model on the Personalized Page Rank (PPR)\autocite{jeh2003scaling} as a benchmark on the network.
-We construct the co-occurrence network of $N$ organizations, in which each edge between organizations $i$ and $j$ represents a co-occurence of $i$ and $j$ in the same affiliation trajectory, with weight $W_{ij}$ given by the sum of the co-occurences over all researchers.
+We construct the co-occurrence network of $N$ organizations, in which each edge between organizations $i$ and $j$ represents a co-occurence of $i$ and $j$ in the same affiliation trajectory, with weight given by the sum of the co-occurences over all researchers.
 and edges are co-occurrence between two organizations.
@@
 \end{equation}
-where $v_i$ is a column vector of length $N$ with entries that are all zero except the $i$th entry that equals to one, $W = (W_{ij})$ is the weighted adjacency matrix. We used $\alpha=0.9$ here.
+where $v_i$ is a column vector of length $N$ with entries that are all zero except the $i$th entry that equals to one, $W = (W_{ij})$ is the weighted transition matrix of the unbiased random walker.
+We used $\alpha=0.9$ here.
 

### 2021-08-05 paper/current/main.tex
reframe the first main result

@@
 Similarly, a student in South Korea is more likely to attend a university in Canada than one in North Korea~\autocite{unesco2019students}.
-Although geographic distance has been used as the most prominent basis for models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} models, there have been attempts to define alternative notions of distance, or functional distances~\autocite{boschma2005proximity, brown1970migration, kim2018functional}, from real-world data or \textit{a priori} relationships between geographic entities.
+Although geographic distance has been used as the most prominent basis for models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} models,  \js{these models could be enhance by adopting the concept of functional distances between places.
+There have been attempts to define alternative notions of distance, or functional distances~\autocite{boschma2005proximity, brown1970migration, kim2018functional}, from real-world data or \textit{a priori} relationships between geographic entities.}
 
@@
 
-Here, we apply a neural embedding framework to real-world mobility trajectories and demonstrate that it can encode the complex landscape of human mobility into a dense and continuous vector-space representation, from which we can not only derive a meaningful functional distance between locations but also probe relationships based on culture, language, and even prestige along with the geographic relationship.
+\js{Here, we apply a neural embedding framework to real-world mobility trajectories to derive the functional distance between locations and demonstrate that it can encode the complex landscape of human mobility into a dense and continuous vector-space representation that also can probe relationships based on culture, language, and even prestige along with the geographic relationship.}
 We embed trajectories from three massive datasets: U.S.
@@
 It works under the notion that a good representation should facilitate prediction, learning a mapping between words that can predict a target word based on its context (surrounding words).
-The model is also computationally efficient, robust to noise, and can encode relations between entities as geometric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.
+The model is also computationally efficient, \js{easy to run}, robust to noise, and can encode relations between entities as geometric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis, hashimoto2016word}.
 As a result, each location is encoded into a single vector representation, and vectors relate to one another based on the likelihood of locations appearing adjacent to one another in the same trajectory.
@@
 
-We show that the embedding distance better predicts actual mobility flows than the geographic distance across three disparate datasets.
-In the case of flight itineraries, the embedding distance explains more than twice the expected flux between airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}a) than does geographic distance ($R^{2} = 0.22$).
+\js{We prove that the gravity could be more powerful by using mobility-aware embedding distance between places as a distance measure.
+Our approach always better predicts actual mobility flows than the geographic distance and other baseline methods across three disparate datasets consistently.} In the case of flight itineraries, the embedding distance explains more than twice the expected flux between airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}a) than does geographic distance ($R^{2} = 0.22$).
 Also, the embedding distance produces better predictions of actual flux between airports than does the geographic distance (Fig.~\ref{fig:gravity_performance}b).
@@
 These patterns hold for the subsets of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d).
-The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores calculated from the underlying mobility network (Fig.~\ref{fig:supp:distancemetrics}, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurrence matrix, Levy's symmetric \textit{word2vec}\autocite{levy2014neural}, and even direct optimization of the gravity model (Fig.\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores calculated from the underlying mobility network (Fig.~\ref{fig:gravity_performance}, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurrence matrix, Levy's symmetric \textit{word2vec}\autocite{levy2014neural}, and even direct optimization of the gravity model (Fig.\ref{fig:gravity_performance} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
 In sum, our results demonstrate that, consistently and efficiently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
@@
 	\caption{
-		\textbf{Embedding distance encodes functional distance and better predicts mobility in flights, accommodation reservations, and global scientific mobility.}
+		\textbf{Embedding distance encodes functional distance and better predicts mobility in flights, accommodation reservations, and global scientific mobility compared to various baselines. }
 		\textbf{a.} Embedding distance (cosine distance between organization vectors, top) better explains the expected flux of passengers between U.S. airports than does geographic distance (bottom).
@@
 		Similarly, in the case of global scientific mobility, embedding distance explains the expected flux between organizations (\textbf{e)} and allows for better predictions (\textbf{f}) than geographic distance.
-	}
+		\js{\textbf{g.}  The correlation between the flux and baseline distances, measured with $R^{2}$, and  \textbf{h.}  the  root-mean-squared error between the actual and predicted values across various baselines.
+    The asterisk denotes the top-performing method.
+Our approach better explains and predicts flux than any other baseline (Table~\ref{supp:table:r2_table}, Table~\ref{supp:table:rmse_exp_table}, and Table~\ref{supp:table:rmse_power_table}).}}
 	\label{fig:gravity_performance}
@@
 While the gravity model predicts mobility flows from the given mass and locations, {\it word2vec} finds locations that best explain the given mobility flow.
+\js{Also, our finding is aligned with a perspective on word embedding methods as a metric recovery~\autocite{hashimoto2016word}, which recover the underlying metric of the semantic manifold not for a particular task.}
 Therefore, the embedding distance is inherently tied to the mobility flow, and hence, has greater predictive power than the geographic distance and other baselines.

### 2021-08-06 paper/current/main.tex
add ecsim

@@
 
+\subsection*{Element-centric clustering similarity}
+\js{
+Element-centric clustering similarity \autocite{gates2019element} is unified similarity embracing disjoint, overlapping, and hierarchically structured clustering.
+Element-centric clustering similarity captures cluster-induces relationships between through cluster affiliation graph where one vertex set is the original element $V=\{v_1, ...
+v_N\}$ and the other corresponds to the cluster $C=\{c_1, ...
+c_M\}$ as a bipartite graph $\mathcal{B} (V \cup C, \mathcal{R})$.
+an undirected edge $a_{i\beta} \in \mathcal{R}$  denote element $v_i$ is a member of cluster $c_\beta$.
+For hierarchically structured clustering.
+each cluster $c_\beta$ is assigned a hierarchical level $l_{\beta} \in [0,1]$ by re-scaling the dendrogram according to the maximum path length from the roots.
+The weight of the cluster affiliation edge is given by the hierarchy weight function $a_{i\beta}  = e^{rl_{\beta}}$ with scaling parameter $r$ which determine the relative importance of membership at different levels of hierarchy.
+Here, lower $r$ focuses on the higher level of the hierarchy, and lower levels are treated as a refinement of the higher level.
+Larger $r$ emphasizes lower-level cluster structure, and higher levels of the hierarchy are seen as an aggregation of the lower-level structure.
+If $r=0$, every cluster is treated equally.
+
+The cluster affiliation graph is projected onto  a cluster-induced element graph which is a weighted, directed graph summarizes the relationship induced by common cluster memberships.
+In the cluster-induced element graph,  each edge  between element $v_i$ and $v_j$ has weight $w_{ij} = \sum_{\gamma} \frac{a_{i\gamma}a_{j\gamma}}{\sum_{\kappa}a_{i\kappa} {\sum_{m}a_{m\gamma}}}$.
+Given a cluster-induces element graph with weighted matrix $W$, the personalized PageRank vector $p_i$  is used as membership-aware similarity between element $i$ and other elements in the graph.
+Then, the element-wise similarity of an element $v_i$ in two clustering  $\mathcal{A}$ and $\mathcal{B}$ is calculated with $S_i(\mathcal{A}, \mathcal{B}) = 1 - L_1(p_i^{\mathcal{A}},p_j^{\mathcal{B}})$, and the final elementric-centric similiarty of two clustering $\mathcal{A}$ and $\mathcal{B}$ is the average of the element-wise similarities, $S(\mathcal{A}, \mathcal{B}) =\frac{1}{N}\sum_{i=1}^{N} S_i(\mathcal{A}, \mathcal{B})$.}
+
 %

### 2021-08-06 paper/current/main.tex
add ecsim

@@
 \subsection*{Element-centric clustering similarity}
-\js{
-Element-centric clustering similarity \autocite{gates2019element} is unified similarity embracing disjoint, overlapping, and hierarchically structured clustering.
+
+\js{Element-centric clustering similarity \autocite{gates2019element} is unified similarity embracing disjoint, overlapping, and hierarchically structured clustering.
 Element-centric clustering similarity captures cluster-induces relationships between through cluster affiliation graph where one vertex set is the original element $V=\{v_1, ...
@@
 Larger $r$ emphasizes lower-level cluster structure, and higher levels of the hierarchy are seen as an aggregation of the lower-level structure.
-If $r=0$, every cluster is treated equally.
+If $r=0$, every cluster is treated equally.}
 
-The cluster affiliation graph is projected onto  a cluster-induced element graph which is a weighted, directed graph summarizes the relationship induced by common cluster memberships.
+\js{The cluster affiliation graph is projected onto  a cluster-induced element graph which is a weighted, directed graph summarizes the relationship induced by common cluster memberships.
 In the cluster-induced element graph,  each edge  between element $v_i$ and $v_j$ has weight $w_{ij} = \sum_{\gamma} \frac{a_{i\gamma}a_{j\gamma}}{\sum_{\kappa}a_{i\kappa} {\sum_{m}a_{m\gamma}}}$.

### 2021-08-06 paper/current/main.tex
add another figs

@@
 These patterns hold for the subsets of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d).
-The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores calculated from the underlying mobility network (Fig.~\ref{fig:gravity_performance}, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurrence matrix, Levy's symmetric \textit{word2vec}\autocite{levy2014neural}, and even direct optimization of the gravity model (Fig.\ref{fig:gravity_performance} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
-In sum, our results demonstrate that, consistently and efficiently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
-
 %
@@
 	\caption{
-		\textbf{Embedding distance encodes functional distance and better predicts mobility in flights, accommodation reservations, and global scientific mobility compared to various baselines. }
+		\textbf{Embedding distance encodes functional distance and better predicts mobility in flights, accommodation reservations, and global scientific mobility. }
 		\textbf{a.} Embedding distance (cosine distance between organization vectors, top) better explains the expected flux of passengers between U.S. airports than does geographic distance (bottom).
@@
 		For Korean accommodation reservations, embedding distance better explains the expected flux than does geographic distance (\textbf{c}), and produces better predictions (\textbf{d}).
-		Similarly, in the case of global scientific mobility, embedding distance explains the expected flux between organizations (\textbf{e)} and allows for better predictions (\textbf{f}) than geographic distance.
-		\js{\textbf{g.}  The correlation between the flux and baseline distances, measured with $R^{2}$, and  \textbf{h.}  the  root-mean-squared error between the actual and predicted values across various baselines.
-    The asterisk denotes the top-performing method.
-Our approach better explains and predicts flux than any other baseline (Table~\ref{supp:table:r2_table}, Table~\ref{supp:table:rmse_exp_table}, and Table~\ref{supp:table:rmse_power_table}).}}
+		Similarly, in the case of global scientific mobility, embedding distance explains the expected flux between organizations (\textbf{e)} and allows for better predictions (\textbf{f}) than geographic distance.}
 	\label{fig:gravity_performance}
+\end{figure}
+
+The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores calculated from the underlying mobility network (Fig.~\ref{fig:distancemetrics}, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurrence matrix, Levy's symmetric \textit{word2vec}\autocite{levy2014neural}, and even direct optimization of the gravity model (Fig.\ref{fig:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+In sum, our results demonstrate that, consistently and efficiently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
+
+\begin{figure}[ht!]
+	\centering
+	\includegraphics[width=0.7\textwidth]{\figdir/Descriptive/distance_metric_performance.pdf}
+	\caption{
+	\textbf{Neural embeddings outperform baselines for scientific mobility.}
+The correlation between the flux and baseline distances, measured with $R^{2}$ (left), and the  root-mean-squared error between the actual and predicted values across various baselines (right).
+    The asterisk indicates the top-performing method.
+Our approach better explains and predicts flux than any other baseline (Table~\ref{supp:table:r2_table}, Table~\ref{supp:table:rmse_exp_table}, and Table~\ref{supp:table:rmse_power_table}).}
+	\label{fig:distancemetrics}
 \end{figure}

### 2021-08-07 paper/current/main.tex
update figs and merge fig

--- 2021-08-06 paper/current/main.tex
@@
 Trajectories of scientific mobility are constructed using more than three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database (see Methods).
-As a scientist's career progresses, they move between organizations or pick up additional (simultaneous) affiliations forming \textit{affiliation trajectories} (Fig.~\ref{fig:methods:mobility_sentence}).
+As a scientist's career progresses, they move between organizations or pick up additional (simultaneous) affiliations forming \textit{affiliation trajectories} (Fig.~\ref{fig:gravity_performance}a).
 Thus, the trajectories encode both migration and co-affiliation---the holding of multiple simultaneous affiliations involving the sharing of time and capital between locations---that is typical of scientific mobility~\autocite{rodrigues2016mobility, sugimoto2017mostimpact} (see \SI).
@@
 As a result, each location is encoded into a single vector representation, and vectors relate to one another based on the likelihood of locations appearing adjacent to one another in the same trajectory.
-
-%
-% Figure - Example of mobility sentences
-%
-\begin{figure}[ht!]
-	\centering
-	\includegraphics[width=0.5\textwidth]{\figdir/mobility_example_combined.pdf}
-	\caption{
-		\textbf{Construction of affiliation trajectories from publication records.}
-		\textbf{a.}
-		An author published five papers across five time periods, with only one affiliation listed in the byline of each paper.
-		A unique identifier is assigned to each organization and they are assembled into an affiliation trajectory ordered by year of publication.
-		\textbf{b.}
-		If an author lists multiple organization affiliations within the same year, then organization IDs within that year are placed in random order in each training iteration of the \textit{word2vec} model (for more detail, see \SI).
-	}
-	\label{fig:methods:mobility_sentence}
-\end{figure}
 
@@
 These patterns hold for the subsets of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d).
-The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores calculated from the underlying mobility network (Fig.~\ref{fig:gravity_performance}, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurrence matrix, Levy's symmetric \textit{word2vec}\autocite{levy2014neural}, and even direct optimization of the gravity model (Fig.\ref{fig:gravity_performance} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
-In sum, our results demonstrate that, consistently and efficiently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
 
+%
+% Figure - Example of mobility sentences
+%
 %
@@
 %
-\begin{figure}[h!]
+\begin{figure}[!htp]
 	\centering
-	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance.pdf}
+	\includegraphics[width=0.9\textwidth]{\figdir/GravityLawFig/gravity_performance_new.pdf}
 	\caption{
-		\textbf{Embedding distance encodes functional distance and better predicts mobility in flights, accommodation reservations, and global scientific mobility compared to various baselines. }
-		\textbf{a.} Embedding distance (cosine distance between organization vectors, top) better explains the expected flux of passengers between U.S. airports than does geographic distance (bottom).
+		\textbf{Embedding distance encodes functional distance and better predicts mobility across three distinct human trajectory datasets. }
+		\textbf{a.} A unique identifier is assigned to each organization and they are assembled into an affiliation trajectory ordered by year of publication (top).
+If an author lists multiple organization affiliations within the same year,  we shuffle the order within that year in each training iteration (bottom, see \SI).
+		\textbf{b.} Neural embeddings outperform baselines for scientific mobility.
+The correlation between the flux and baseline distances $R^{2}$ (left), and the  root-mean-squared error between the actual and predicted values (right).
+The asterisk indicates the top-performing method.
+		\textbf{c.} Embedding distance (top) better explains the expected flux of passengers between U.S. airports than does geographic distance (bottom).
 		The red line is the line of the best fit.
-		Black dots are mean flux across binned distances.
-		99\% confidence intervals are plotted for the mean flux in each bin based on a normal distribution.
+		%Black dots are mean flux across binned distances.
+		99\% confidence intervals are plotted for the mean flux in each bin.
 		Correlation is calculated on the data in the log-log scale ($p < 0.0001$ across all fits).
-		The lightness of each hex bin indicates the frequency of organization pairs within it.
-		\textbf{b.} Predictions of flux between airport pairs made using embedding distance (top) outperform those made using geographic distance (bottom).
+		%The lightness of each hex bin indicates the frequency of organization pairs within it.
+		\textbf{d.} Predictions of flux between airport pairs made using embedding distance (top) outperform those made using geographic distance (bottom).
 		Box-plots show the distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps with $y = x$;
-		a perfect prediction yields all points on the black line.
+		Box color corresponds to the degree to which the distribution overlaps with $y = x$.
+		%a perfect prediction yields all points on the black line.
 		``RMSE'' is the root-mean-squared error between the actual and predicted values.
-		Results are consistent in the case of scientific mobility.
-		For Korean accommodation reservations, embedding distance better explains the expected flux than does geographic distance (\textbf{c}), and produces better predictions (\textbf{d}).
-		Similarly, in the case of global scientific mobility, embedding distance explains the expected flux between organizations (\textbf{e)} and allows for better predictions (\textbf{f}) than geographic distance.
-		\js{\textbf{g.}  The correlation between the flux and baseline distances, measured with $R^{2}$, and  \textbf{h.}  the  root-mean-squared error between the actual and predicted values across various baselines.
-    The asterisk denotes the top-performing method.
-Our approach better explains and predicts flux than any other baseline (Table~\ref{supp:table:r2_table}, Table~\ref{supp:table:rmse_exp_table}, and Table~\ref{supp:table:rmse_power_table}).}}
+	Embedding distance consistently produce powerful functional distance compare to geographic distance for Korean accommodation reservations (\textbf{e,f}), and global scientific mobility (\textbf{g,h})}
 	\label{fig:gravity_performance}
 \end{figure}
+
+The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores calculated from the underlying mobility network (Fig.~\ref{fig:gravity_performance}b, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurrence matrix, Levy's symmetric \textit{word2vec}\autocite{levy2014neural}, and even direct optimization of the gravity model (Fig.\ref{fig:gravity_performance}b and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+In sum, our results demonstrate that, consistently and efficiently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
 
@@
 In the case of Korean accommodation reservations, trajectories comprise a sequence of accommodations reserved over a customer's history.
-For scientific mobility, an``affiliation trajectories'' is constructed for each mobile author, which is built by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:methods:mobility_sentence}a.
-In more complex cases, such as listing multiple affiliations on the same paper or publishing with different affiliations on multiple publications in the same year, the order is randomized within that year, as shown in Fig.~\ref{fig:methods:mobility_sentence}b.
+For scientific mobility, an``affiliation trajectories'' is constructed for each mobile author, which is built by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:gravity_performance}a (top).
+In more complex cases, such as listing multiple affiliations on the same paper or publishing with different affiliations on multiple publications in the same year, the order is randomized within that year, as shown in Fig.~\ref{fig:gravity_performance}a (bottom).
 

### 2021-09-01 notebooks/embedding_boomerang_plots.rmd
update notebooks

@@
 
-df <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Embeddings/precedence/factors/d300_ws1_precedence_w2vfactors.csv") %>%
+df <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Embeddings/precedence/factors/d300_ws1_precedence_gamma1.0_w2vfactors.csv") %>%
   select(cwts_org_no, l2norm) %>%
@@
 
-sizes <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/raw/2008-2019_inst_sizes.txt", delim = "\t") %>%
-  group_by(cwts_org_no) %>%
-  summarize(
-    size = mean(person_count)
-  )
+sizes <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/2008-2019_inst_sizes_all.txt", delim = "\t")
 
@@
   theme_minimal() +
-  annotate(geom = "label", x = 1.5e4, y = 3.6, label = "Harvard", size = 3.5) +
-  annotate(geom = "label", x = 1.6e3, y = 3.65, label = "Princeton", size = 3.5) +
-  annotate(geom = "label", x = 8.5e3, y = 5.9, label = "Univ Tennessee\nKnoxville", size = 3.5) +
+  annotate(geom = "label", x = 1.6e4, y = 3.55, label = "Harvard", size = 3.5) +
+  annotate(geom = "label", x = 1.6e3, y = 3.5, label = "Princeton", size = 3.5) +
+  annotate(geom = "label", x = 8.5e3, y = 5.8, label = "Univ Tennessee\nKnoxville", size = 3.5) +
   annotate(geom = "label", x = 1.8e2, y = 1.55, label = "Univ Alaska\nFairbanks", size = 3.5) +
-  annotate(geom = "label", x = 4e2, y = 6.2, label = "NY Medical College", size = 3.5) +
-  annotate(geom = "label", x = 2e1, y = 4.6, label = "Univ Michigan\nFlint", size = 3.4) +
+  annotate(geom = "label", x = 4e2, y = 6.0, label = "NY Medical College", size = 3.5) +
+  annotate(geom = "label", x = 1.5e1, y = 4.6, label = "Univ Michigan\nFlint", size = 3.4) +
   annotate(geom = "label", x = 6.8e1, y = 2.48, label = "Barry University", size = 3.5) +

### 2021-09-01 workflow/scripts/CalculatePredictedVsActual.R
fix bugs in code

@@ -112,7 +112,7 @@ if (opt$distance == "geo") {
 } else if (opt$distance == "gravsvd") {
   agg <- agg %>%
     mutate(
-      distance = log(gravsvd_distance),
+      distance = gravsvd_distance,
       distance.log = log(gravsvd_distance)
     )
 } else if (opt$distance == "gravmds") {

### 2021-09-01 paper/current/main.tex
update abstract

@@
 	Historically, mobility was constrained by geographic distance, however, in the globalizing world, language, culture, and history are increasingly important.
-	Here, we show the mathematical equivalence between \textit{word2vec} model and the gravity model of mobility and the demonstrate that, by using three human trajectory datasets, \textit{word2vec} encodes nuanced relationships between locations into a vector-space, providing a measure of effective distance.
+	Here, we show a mathematical equivalence between \textit{word2vec} model and the gravity model of mobility and demonstrate that, by using three human trajectory datasets, \textit{word2vec} encodes nuanced relationships between locations into a vector-space, providing a measure of effective distance.
 	Focusing on the case of scientific mobility, we show that embeddings uncover cultural, linguistic, and hierarchical relationships at multiple levels of granularity.

### 2021-09-01 paper/current/main.tex
update introduction

@@
 Similarly, a student in South Korea is more likely to attend a university in Canada than one in North Korea~\autocite{unesco2019students}.
-Although geographic distance has been used as the most prominent basis for models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} models,  \js{these models could be enhance by adopting the concept of functional distances between places.
-There have been attempts to define alternative notions of distance, or functional distances~\autocite{boschma2005proximity, brown1970migration, kim2018functional}, from real-world data or \textit{a priori} relationships between geographic entities.}
+Although geographic distance has been used as the most prominent basis for models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} models, the decreasing relevance of geography calls for alternative ways of conceptualizing ``distance''~\autocite{boschma2005proximity, brown1970migration, kim2018functional}.
 
@@
 Networks offer a solution to representing many dimensions of mobility, yet edges only encode simple relationships between connected entities.
-Capturing the complexity of mobility requires moving beyond simple functional distances and networks, to learning high-dimensional landscapes of mobility that incorporate the many facets of mobility into a single fine-grained and continuous representation.
+Capturing the complexity of mobility requires moving beyond simple functional distances and networks, to learning high-dimensional landscapes of mobility that incorporate many facets of mobility into a single fine-grained and continuous representation.
 
-\js{Here, we apply a neural embedding framework to real-world mobility trajectories to derive the functional distance between locations and demonstrate that it can encode the complex landscape of human mobility into a dense and continuous vector-space representation that also can probe relationships based on culture, language, and even prestige along with the geographic relationship.}
-We embed trajectories from three massive datasets: U.S.
+Here, we demonstrate that the \textit{word2vec} model (Skip-Gram Negative Sampling) is equivalent to the gravity law of mobility, a fundamental mobility framework. 
+We then empirically test the resulting representation by its ability to derive functional effective distances between from trajectories.
+After validating that it accurately represents real-world data, we demonstrate \textit{word2vec}'s capacity for encoding rich information relating to geography, culture, language, and even prestige, at multiple scales of analysis.
+We embed trajectories from three datasets: U.S.
 passenger flight itinerary records, Korean accommodation reservations, and a dataset of scientists' career mobility between organizations captured in bibliometric records (Detailed descriptions are available in the Methods).
 
-The flight itinerary data, from the Airline Origin and Destination Survey, consists of records of more than 300 million itineraries between 1993 and 2020 documenting domestic flights between 828 airports in the United States.
-A trajectory is constructed for each passenger flight itinerary, forming an ordered sequence of unique identifiers of the origin and destination airports.
-The Korean accommodation reservations consist of customer reservation histories across 2018 and 2020 for 1,038 unique accommodation locations in Seoul, South Korea.
-A trajectory is constructed for each customer, containing the ordered sequences of accommodations they reserved over time.
-Finally, we use scientific mobility data that captures the affiliation trajectories of nearly 3 million scientists across ten years.
 We focus in more detail on scientific mobility due to its richness and importance.
@@
 In spite of its importance, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, deville2014career}, being further confounded by the diminishing role of geography in shaping the landscape of scientific mobility.
-
 Trajectories of scientific mobility are constructed using more than three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database (see Methods).
@@
 
-A vector-space embedding of locations (airports, accommodations, and organizations) is learned by using trajectories as input to the standard with skip-gram negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
+Here, we study the skip-gram negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
 This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}, networks~\autocite{grover2016node2vec, linzhuo2020hyperbolic} and trajectories\autocite{liu2016exploring, feng2017poi2vec, yao2018representing, cao2019habit2vec, crivellari2019motion, solomon2018predict}.
 It works under the notion that a good representation should facilitate prediction, learning a mapping between words that can predict a target word based on its context (surrounding words).
-The model is also computationally efficient, \js{easy to run}, robust to noise, and can encode relations between entities as geometric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis, hashimoto2016word}.
+The model is also computationally efficient, easy to use, robust to noise, and can encode relations between entities as geometric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis, hashimoto2016word}.
 As a result, each location is encoded into a single vector representation, and vectors relate to one another based on the likelihood of locations appearing adjacent to one another in the same trajectory.
 
-To validate our approach, we evaluate the quality of vector representations based on their performance in predicting real-world mobility flows using the gravity model framework~\autocite{zipf1946gravity}.
-The gravity model is a widely used mobility model~\autocite{curiel2018citygravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity} that connects the \textit{expected flux}, $\hat{T}_{ij}$, between locations based on their populations and distance:
+Our study builds on the gravity model framework~\autocite{zipf1946gravity}.
+This is a widely-used, fundamental mobility model~\autocite{curiel2018citygravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity} that connects the \textit{expected flux}, $\hat{T}_{ij}$, between locations based on their populations and distance:
 
@@
 DB1B is a sample of 10 percent of domestic airline tickets between 1993 and 2020, comprising 307,760,841 passenger itineraries between 828 U.S. airports.
+A trajectory is constructed for each passenger flight itinerary, forming an ordered sequence of unique identifiers of the origin and destination airports.
 Each itinerary is associated with a trajectory of airports including the origin, destination, and intermediary stops.
@@
 The data contains customer-level reservation trajectories spanning the period of August 2018 through July 2020 and comprising 1,038 unique accommodation locations in Seoul, South Korea.
+A trajectory is constructed for each customer, containing the ordered sequences of accommodations they reserved over time.
 

### 2021-09-01 paper/current/main.tex
move up math section
edit math section

@@
 %
+% Wordvec and the gravity model
+\subsection*{word2vec and the gravity model}
+
+We first demonstrate the mathematical equivalence between the SGNS model and the gravity model.
+The {\it word2vec} model takes a location trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), as input.
+A target location $a_t=i$ is considered to have a context location $a_{t'}=j$ that appears in the previous or subsequent $w$ locations in the trajectory, \ie  $j \in [a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}]$.
+	{\it word2vec} learns an embedding by estimating the probability that location $i$ has context $j$:
+\begin{align}
+	P\left(j \given i \right):= \frac{\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:prob_w2v_ng}
+\end{align}
+where the denominator $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
+Although {\it word2vec} generates two embedding vectors $\bm{v_i}$ and $\bm{u}_i$---referred to as the in-vector and out-vector, respectively---we follow convention to use the in-vector $\bm{v}_i$ as an embedding of location $i$.
+
+When $w=1$ (Fig.~\ref{fig:supp:hyperparameter}), the flow can be written as
+\begin{align}
+	\label{eq:flow_w2v}
+	\hat{T}_{ij} \propto P(i) P(j\given i) = \frac{P(i)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
+\end{align}
+where $P(j)$ is the fraction of $j$ in the data.
+In general, calculating $Z_i$ is computationally expensive and there are two common approximations: hierarchical softmax \autocite{morin2005hierarchical} and negative sampling \autocite{mikolov2013word2vec}.
+Due to its simplicity and performance, negative sampling is the most widely used strategy, which we also adopt in our study.
+
+Although negative sampling is the most common approximation, it is a biased estimator~\autocite{Chia2010,Dyer2014} and fits a different probability model.
+When taking into account this bias, {\it word2vec} with skip-gram and negative sampling fits a probability model given by
+\begin{align}
+	P\left(j \given i \right):= \frac{P^ \gamma(j) \exp(\bm{u}_j \cdot \bm{v}_{i})}{Z'_i}, \label{eq:prob_w2v_ng0}
+\end{align}
+where we redefine the normalization constant as $Z'_i=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
+(See the Methods and Supporting Information for the full derivation).
+
+Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimal in-vectors and out-vectors such that $\vect{v}_i = \vect{u}_i$ \autocite{levy2014neural}.
+Setting $\gamma = 1$ and substituting $\vect{v}_i = \vect{u}_i$ into Eq.~\ref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
+\begin{align}
+	\widehat{T}_{ij} \propto  N(i) P(j\given i) = \frac{NP(i)P(j)\exp(\vect{v}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:flow_w2v_ng1}
+\end{align}
+where $N(i) = NP(i)$ is the frequency of location $i$ in the data, and $N=\sum_{i \in {\cal A}} N(i)$ is the sum of frequencies of all locations.
+
+The flow $\widehat{T}_{ij}$ is symmetric (\ie $\widehat{T}_{ij}=\widehat{T}_{ji}$) because the skip-gram model neglects whether the context $j$ appears before or after the target $i$ in the trajectory.
+If we swap $i$ and $j$ in Eq.~\ref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
+Therefore, to ensure $\widehat{T}_{ij}=\widehat{T}_{ji}$, the denominator $Z_i$ should be a constant.
+
+Taken together, the {\it word2vec} model with the negative sampling predicts a flow in the same form as in the gravity model:
+\begin{align}
+	\hat{T}_{ij}=  C P(i) P(j)  \exp(\bm{v}_j \cdot \bm{v}_{i}). \label{eq:flow_w2v_ng0}
+\end{align}
+
+In other words, \emph{word2vec with the skip-gram negative sampling is equivalent to the gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
+While the gravity model describes mobility flows from the given mass and locations, {\it word2vec} finds locations that best explain the given mobility flow. 
+\js{Also, our finding is aligned with a perspective on word embedding methods as a metric recovery~\autocite{hashimoto2016word}, which recover the underlying metric of the semantic manifold not for a particular task.}
+
+In practice, because we only have limited amounts of noisy data and the optimization may not find the true optimum, the mathematical result may only approximately hold.
+Indeed, we find that the in- and out-vectors tend to be different and that the cosine similarity tends to better capture real-world mobility than the dot similarity.
+This result echos other applications of word embedding, such as word analogy testing~\autocite{levy2015improving}, in which cosine distance also outperformed dot similarity.
+Nevertheless, a model with dot similarity has the second-best performance after cosine similarity (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and the embedding distance still outperforms all alternatives we considered.
+
+%
 % Subsection: Embedding performance
@@
 In sum, our results demonstrate that, consistently and efficiently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
-
-\subsection*{word2vec and the gravity model}
-
-Why does \textit{word2vec} with the skip-gram with negative sampling model (SGNS) work so well to model mobility?
-The reason for that is the mathematical equivalence between the SGNS model and the gravity model which we demonstrate below.
-
-The {\it word2vec} model takes a location trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), as input.
-A target location $a_t=i$ is considered to have a context location $a_{t'}=j$ that appears in the previous or subsequent $w$ locations in the trajectory, \ie  $j \in [a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}]$.
-	{\it word2vec} learns an embedding by estimating the probability that location $i$ has context $j$:
-\begin{align}
-	P\left(j \given i \right):= \frac{\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:prob_w2v_ng}
-\end{align}
-where the denominator $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
-Although {\it word2vec} generates two embedding vectors $\bm{v_i}$ and $\bm{u}_i$---referred to as the in-vector and out-vector, respectively---we follow convention to use the in-vector $\bm{v}_i$ as an embedding of location $i$.
-
-Our experiments show that {\it word2vec} best explains real-world mobility flow when $w=1$ (Fig.~\ref{fig:supp:hyperparameter}), with the flow predicted by
-\begin{align}
-	\label{eq:flow_w2v}
-	\hat{T}_{ij} \propto P(i) P(j\given i) = \frac{P(i)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
-\end{align}
-where $P(j)$ is the fraction of $j$ in the data.
-In general, calculating $Z_i$ is computationally expensive and there are two common approximations: hierarchical softmax \autocite{morin2005hierarchical} and negative sampling \autocite{mikolov2013word2vec}.
-Due to its simplicity and performance, negative sampling is the most widely used strategy, which we also adopt in our study.
-
-Although negative sampling is the most common approximation, it is a biased estimator~\autocite{Chia2010,Dyer2014} and fits a different probability model.
-When taking into account this bias, {\it word2vec} with skip-gram and negative sampling fits a probability model given by
-\begin{align}
-	P\left(j \given i \right):= \frac{P^ \gamma(j) \exp(\bm{u}_j \cdot \bm{v}_{i})}{Z'_i}, \label{eq:prob_w2v_ng0}
-\end{align}
-where we redefine the normalization constant as $Z'_i=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
-(See the Methods and Supporting Information for the full derivation).
-
-Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimal in-vectors and out-vectors such that $\vect{v}_i = \vect{u}_i$ \autocite{levy2014neural}.
-Setting $\gamma = 1$ and substituting $\vect{v}_i = \vect{u}_i$ into Eq.~\ref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
-\begin{align}
-	\widehat{T}_{ij} \propto  N(i) P(j\given i) = \frac{NP(i)P(j)\exp(\vect{v}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:flow_w2v_ng1}
-\end{align}
-where $N(i) = NP(i)$ is the frequency of location $i$ in the data, and $N=\sum_{i \in {\cal A}} N(i)$ is the sum of frequencies of all locations.
-
-The flow $\widehat{T}_{ij}$ is symmetric (\ie $\widehat{T}_{ij}=\widehat{T}_{ji}$) because the skip-gram model neglects whether the context $j$ appears before or after the target $i$ in the trajectory.
-If we swap $i$ and $j$ in Eq.~\ref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
-Therefore, to ensure $\widehat{T}_{ij}=\widehat{T}_{ji}$, the denominator $Z_i$ should be a constant.
-
-Taken together, the {\it word2vec} model with the negative sampling predicts a flow in the same form as in the gravity model:
-\begin{align}
-	\hat{T}_{ij}=  C P(i) P(j)  \exp(\bm{v}_j \cdot \bm{v}_{i}). \label{eq:flow_w2v_ng0}
-\end{align}
-
-In other words, \emph{word2vec with the skip-gram negative sampling is equivalent to the gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
-While the gravity model predicts mobility flows from the given mass and locations, {\it word2vec} finds locations that best explain the given mobility flow.
-\js{Also, our finding is aligned with a perspective on word embedding methods as a metric recovery~\autocite{hashimoto2016word}, which recover the underlying metric of the semantic manifold not for a particular task.}
-Therefore, the embedding distance is inherently tied to the mobility flow, and hence, has greater predictive power than the geographic distance and other baselines.
-
-In practice, because we only have limited amounts of noisy data and the optimization may not find the true optimum, the mathematical result may only approximately hold.
-Indeed, we find that the in- and out-vectors tend to be different and that the cosine similarity tends to better capture real-world mobility than the dot similarity.
-This result echos other applications of word embedding, such as word analogy testing~\autocite{levy2015improving}, in which cosine distance also outperformed dot similarity.
-Nevertheless, a model with dot similarity has the second-best performance after cosine similarity (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and the embedding distance still outperforms all alternatives we considered.
 

### 2021-09-01 paper/current/main.tex
move end paragraph back down to appropriate place under empirical results
update empirical test section

@@
 
-In practice, because we only have limited amounts of noisy data and the optimization may not find the true optimum, the mathematical result may only approximately hold.
-Indeed, we find that the in- and out-vectors tend to be different and that the cosine similarity tends to better capture real-world mobility than the dot similarity.
-This result echos other applications of word embedding, such as word analogy testing~\autocite{levy2015improving}, in which cosine distance also outperformed dot similarity.
-Nevertheless, a model with dot similarity has the second-best performance after cosine similarity (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and the embedding distance still outperforms all alternatives we considered.
-
 %
@@
 
-\js{We prove that the gravity could be more powerful by using mobility-aware embedding distance between places as a distance measure.
-Our approach always better predicts actual mobility flows than the geographic distance and other baseline methods across three disparate datasets consistently.} In the case of flight itineraries, the embedding distance explains more than twice the expected flux between airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}a) than does geographic distance ($R^{2} = 0.22$).
+Given their equivalence, we expect that the \textit{word2vec} embedding can encode effective functional distances between locations according to the gravity law. 
+Here, we test this notion using three human mobility datasets, showing that \textit{word2vec}  consistently offers a better representation of actual mobility flows than baselines methods.
+In the case of flight itineraries, the embedding distance explains more than twice the expected flux between airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}a) than does geographic distance ($R^{2} = 0.22$), which has traditionally been used to quantify distance for the gravity model.
 Also, the embedding distance produces better predictions of actual flux between airports than does the geographic distance (Fig.~\ref{fig:gravity_performance}b).
@@
 In sum, our results demonstrate that, consistently and efficiently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
+
+In practice, because we only have limited amounts of noisy data and the optimization may not find the true optimum, the mathematical result may only approximately hold.
+Indeed, we find that the in- and out-vectors tend to be different and that the cosine similarity tends to better capture real-world mobility than the dot similarity.
+This result echos other applications of word embedding, such as word analogy testing~\autocite{levy2015improving}, in which cosine distance also outperformed dot similarity.
+Nevertheless, a model with dot similarity has the second-best performance after cosine similarity (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and the embedding distance still outperforms all alternatives we considered.
 

### 2021-09-01 paper/current/main.tex
update element-centric methods subsection

@@
 
-\js{Element-centric clustering similarity \autocite{gates2019element} is unified similarity embracing disjoint, overlapping, and hierarchically structured clustering.
-Element-centric clustering similarity captures cluster-induces relationships between through cluster affiliation graph where one vertex set is the original element $V=\{v_1, ...
+Element-centric clustering similarity \autocite{gates2019element} is a similarity measure that can produce disjoint, overlapping, and hierarchically-structured clusterings. 
+Element-centric clustering similarity captures cluster-induced relationships between elements through a cluster affiliation graph where one vertex set is the original element $V=\{v_1, ...
 v_N\}$ and the other corresponds to the cluster $C=\{c_1, ...
 c_M\}$ as a bipartite graph $\mathcal{B} (V \cup C, \mathcal{R})$.
-an undirected edge $a_{i\beta} \in \mathcal{R}$  denote element $v_i$ is a member of cluster $c_\beta$.
-For hierarchically structured clustering.
-each cluster $c_\beta$ is assigned a hierarchical level $l_{\beta} \in [0,1]$ by re-scaling the dendrogram according to the maximum path length from the roots.
-The weight of the cluster affiliation edge is given by the hierarchy weight function $a_{i\beta}  = e^{rl_{\beta}}$ with scaling parameter $r$ which determine the relative importance of membership at different levels of hierarchy.
-Here, lower $r$ focuses on the higher level of the hierarchy, and lower levels are treated as a refinement of the higher level.
+An undirected edge $a_{i\beta} \in \mathcal{R}$ denotes element $v_i$ as a member of cluster $c_\beta$. 
+For hierarchically structured clustering, each cluster $c_\beta$ is assigned a hierarchical level $l_{\beta} \in [0,1]$ by re-scaling the dendrogram according to the maximum path length from its roots.
+The weight of the cluster affiliation edge is given by the hierarchy weight function $a_{i\beta}  = e^{rl_{\beta}}$ with scaling parameter $r$ which determines the relative importance of membership at different levels of hierarchy.
+Here, lower $r$ focuses on the higher levels of the hierarchy, and lower levels are treated as a refinement of the higher level. 
 Larger $r$ emphasizes lower-level cluster structure, and higher levels of the hierarchy are seen as an aggregation of the lower-level structure. 
-If $r=0$, every cluster is treated equally.}
+If $r=0$, every cluster is treated equally.
 
-\js{The cluster affiliation graph is projected onto  a cluster-induced element graph which is a weighted, directed graph summarizes the relationship induced by common cluster memberships.
+The cluster affiliation graph is projected onto a cluster-induced element graph which is a weighted, directed graph summarizing the relationship induced by common cluster memberships. 
 In the cluster-induced element graph, each edge  between element $v_i$ and $v_j$ has weight $w_{ij} = \sum_{\gamma} \frac{a_{i\gamma}a_{j\gamma}}{\sum_{\kappa}a_{i\kappa} {\sum_{m}a_{m\gamma}}}$. 
 Given a cluster-induces element graph with weighted matrix $W$, the personalized PageRank vector $p_i$  is used as membership-aware similarity between element $i$ and other elements in the graph. 
-Then, the element-wise similarity of an element $v_i$ in two clustering  $\mathcal{A}$ and $\mathcal{B}$ is calculated with $S_i(\mathcal{A}, \mathcal{B}) = 1 - L_1(p_i^{\mathcal{A}},p_j^{\mathcal{B}})$, and the final elementric-centric similiarty of two clustering $\mathcal{A}$ and $\mathcal{B}$ is the average of the element-wise similarities, $S(\mathcal{A}, \mathcal{B}) =\frac{1}{N}\sum_{i=1}^{N} S_i(\mathcal{A}, \mathcal{B})$.}
+Then, the element-wise similarity of an element $v_i$ in two clusters  $\mathcal{A}$ and $\mathcal{B}$ is calculated with $S_i(\mathcal{A}, \mathcal{B}) = 1 - L_1(p_i^{\mathcal{A}},p_j^{\mathcal{B}})$, and the final element-centric similarity of two clustering $\mathcal{A}$ and $\mathcal{B}$ is found as the average of the element-wise similarities, $S(\mathcal{A}, \mathcal{B}) =\frac{1}{N}\sum_{i=1}^{N} S_i(\mathcal{A}, \mathcal{B})$.
 

### 2021-09-02 notebooks/metric_performance_tables.rmd

@@
 metric_levels <- c("emb", "levyeuc", "dot", "pprjsd", "svdcos", "levycos", "geo",
-                   "lapcos", "pprcos", "levydot")
+                   "lapcos", "pprcos", "levydot", "gravsvd", "gravmds")
 
-metric_labels <- c("Embedding cosine", "Factorized euclidean", "Embedding dot", "PPR JSD", 
-                   "SVD cosine", "Factorized cosine", "Geographic", "Laplacian cosine", "PPR cosine", "Factorized dot")
+metric_labels <- c("Embedding cosine", "Levy's euclidean", "Embedding dot", "PPR JSD", 
+                   "SVD cosine", "Levy's cosine", "Geographic", "Laplacian cosine", "PPR cosine", "Levy's dot", "Gravity SVD cosine", "Gravity MDS euclidean")
 
@@
   style_headers(bold = TRUE) %>%
-  set_right_border(1:12, 1, value = 0.5) %>%
-  set_right_border(1:12, 4, value = 0.5) %>%
-  set_right_border(1:12, 7, value = 0.5) %>%
+  set_right_border(1:14, 1, value = 0.5) %>%
+  set_right_border(1:14, 4, value = 0.5) %>%
+  set_right_border(1:14, 7, value = 0.5) %>%
   set_bottom_border(2, 1:10, value = 0.5)

### 2021-09-02 notebooks/network_centralities.rmd

---
title: "Network Centralities"
output: html_notebook
---

```{r}

library(tidyverse)
library(readr)

meta <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t")

l2norm  <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Embeddings/precedence/factors/d300_ws1_precedence_w2vfactors.csv") %>%
  select(cwts_org_no, l2norm)

sizes <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/raw/2008-2019_inst_sizes.txt", delim = "\t") %>%
  group_by(cwts_org_no) %>%
  summarize(
    size = mean(person_count)
  )

types <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/org_types.csv")

semaxis <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/SemAxis/precedence/prestige/times_d300_ws1_n5_precedence_semaxis.csv")
country <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/country_metadata.csv")
leiden <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/leiden_ranking.csv")
times <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/times_ranking.csv")
centralities <- read_csv('/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Network/precedence_net_centralities.csv')
impact <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/org_impact_scores.txt", delim = "\t")
```

```{r}

# Impact rankings
# Semaxis rankings
# Sizes 
# Metadata 
# Org type
base_data <- impact %>%
  mutate(mncs = as.numeric(mncs)) %>%
  left_join(meta, by = "cwts_org_no") %>%
  filter(country_iso_alpha == "USA") %>%
  left_join(types, by = "org_type") %>%
  left_join(sizes)

  filter(size > 50) %>%

  arrange(desc(mncs)) %>%
  mutate(impact_rank = row_number()) %>%
  left_join(semaxis, by = "cwts_org_no") %>%
  arrange(desc(sim)) %>%
  mutate(semaxis_rank = row_number())

print(dim(df))

# Correlation test
cor.test( ~ impact_rank + semaxis_rank,
            data = df,
            method = "spearman",
            continuity = FALSE,
            conf.level = 0.95)
```

```{r}

thresholds <- c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100, 110, 120, 130, 140, 150)

all.sectors <- data.table::rbindlist(lapply(c("Institute", "Government", "Teaching"), function(sector) {
  for_sector <- data.table::rbindlist(lapply(thresholds, function(x) {
    df <- base_data %>%
      filter(org_type_simplified == sector) %>%
      filter(size > x) %>%
      arrange(desc(mncs)) %>%
      mutate(impact_rank = row_number()) %>%
      left_join(semaxis, by = "cwts_org_no") %>%
      arrange(desc(sim)) %>%
      mutate(semaxis_rank = row_number())

    if (dim(df)[1] > 10) {
      test <- cor.test( ~ impact_rank + semaxis_rank,
              data = df,
              method = "spearman",
              continuity = FALSE,
              conf.level = 0.95)
      stat = test$estimate[[1]]
    } else {
      stat = NA
    }

    return(data.frame(statistic = stat, threshold = x, sector = sector, n = dim(df)[1]))
  }))

}))

plotdata <- all.sectors %>%
  mutate(statistic = abs(statistic)) %>%
  mutate(
    sector = factor(sector, levels = c("Teaching", "Institute", "Government")),
    sector = factor(sector, 
                    labels = c("Regional & Liberal\nArts Colleges", 
                               "Research Institute",
                               "Government Organization"))
  )

plotdata %>%
  ggplot(aes(x = threshold, y = statistic, color = sector)) +
  geom_point() +
  geom_line() +
  geom_text(data = plotdata %>% filter(threshold %in% c(0, 50, 100)),
            aes(label = paste0("n=", n), x = threshold, y = abs(statistic)),
            vjust = -0.5, hjust = -0.25
  ) +
  scale_x_continuous(limits = c(-10, NA)) +
  facet_wrap(~sector) +
  theme_minimal() +
  theme(
    text = element_text(family = 'Helvetica', size = 12),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    legend.position = "none",
    strip.text = element_text(face = "bold", size = 14),
    plot.title = element_text(face = "bold")
  ) +
  xlab("Threshold for # of yearly authors") +
  ylab(latex2exp::TeX("Spearman's $\\rho")) +
  ggtitle("SemAxis rank vs. MNCS rank by size threshold")

ggsave("~/Desktop/rho_impact_semaxis_rank.png", width = 8, height = 4)
```

```{r}
plot <- centralities %>%
  left_join(meta, by = "cwts_org_no") %>%
  left_join(l2norm, by = c("cwts_org_no")) %>%
  mutate(eigen = log10(eigen)) %>%
  ggplot(aes(x = eigen, y = l2norm)) +
  geom_point() +
  #scale_x_continuous(limits = c(-10, 0)) +
  #theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    text = element_text(family = "Helvetica", size = 14),
    axis.title.x = element_text(angle = 0, size = 16, face = "bold", vjust = 0.5),
    axis.title.y = element_text(angle = 90, size = 16, face = "bold"),
  )

plot

#plotly::ggplotly(plot)
```

```{r}
sizes %>%
  left_join(centralities) %>%
  ggplot(aes(x = (size), y = (eigen))) +
  geom_point() +
  scale_x_log10(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
  scale_y_log10(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
  ggpmisc::stat_poly_eq(formula = y ~ x,
                          geom = "text_npc",
                          aes(label = paste(..rr.label.., sep = "~~~")),
                          parse=TRUE,
                          label.x.npc = 0.1,
                          label.y.npc = 0.96,
                          rr.digits = 2,
                          size = 7
  ) +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    text = element_text(family = "Helvetica", size = 14),
    axis.title.x = element_text(angle = 0, size = 16, face = "bold", vjust = 0.5),
    axis.title.y = element_text(angle = 90, size = 16, face = "bold"),
  ) +
  annotation_logticks(sides = "b") +
  xlab("Organization size") +
  ylab("Eigenvector centrality")

```

### 2021-09-02 notebooks/w2v_factors_plots.rmd

---
title: "Mobility W2V Factors"
output: html_notebook
---

```{r}
library(readr)
library(tidyverse)
factors <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Embeddings/precedence/factors/d300_ws1_precedence_w2vfactors.csv")

meta <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t")

mobile <- read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/raw/mobile_researcher_trajectories.txt", delim = "\t")
```

8,445

3,709,869

```{r}
mobile2 <- mobile %>%
  group_by(cluster_id) %>%
  summarize(
    count = n()
  )
```

```{r}
mobile %>%
  group_by(cwts_org_no) %>%
  summarize(
    count = n()
  ) %>%
  arrange(desc(count)) %>%
  mutate(
    index = row_number(),
    ind = factor(index)
  ) %>%
  ggplot(aes(x = index, y = count)) +
  geom_point() +
  scale_y_log10() +
  theme_minimal() +
  xlab("Org Index") +
  ylab("Frequency")
```

```{r}
library(readxl)
carnegie <- read_excel("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/CCIHE2018-PublicData.xlsx", sheet = "Data", trim_ws = T)
uni_crosswalk <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/carnegie_cwts_us_uni_crosswalk.csv")
leiden = read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/leiden_ranking.csv")
census <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/usa_states_to_regions.csv")
inst_sizes = read_delim("/Users/dakotamurray/Dropbox/SME-dropbox/Data/raw/2008-2019_inst_sizes.txt", delim = "\t") %>% 
  group_by(cwts_org_no) %>%
  summarize(
    count = mean(person_count)
  )

org_types <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Additional/org_types.csv")
```

```{r}
meta.all <- meta %>% 
  filter(country_iso_alpha == "USA" & org_type_code == "U") %>%
  left_join(uni_crosswalk, by = "cwts_org_no") %>%
  left_join(org_types, by = "org_type") %>%
  left_join(leiden, by = "cwts_org_no") %>%
  left_join(census, by = "region") %>%
  left_join(inst_sizes, by = "cwts_org_no") %>%
  left_join(carnegie, by = c("cc_id" = "UNITID"))

mobile.usa <- mobile %>%
  inner_join(meta.all['cwts_org_no']) %>%
  group_by(cluster_id) %>%
  mutate(
    traj_len = length(cwts_org_no)
  ) %>%
  group_by(cwts_org_no) %>%
  summarize(
    mean_traj_len = mean(traj_len),
    num_traj = length(unique(cluster_id)),
    num_total = n()
  )

mobile.usa

factors.usa <- factors %>%
  inner_join(meta.all, by = "cwts_org_no") %>%
  left_join(mobile.usa, by = "cwts_org_no") %>%
  mutate(
    research = recode(BASIC2018, `15` = "R1", `16` = "R2", `17` = "R3", .default = "Other"),
    urban = recode(LOCALE, 
                   `11` = "City", `12` = "City", `13` = "City",
                   `21` = "Suburb", `22` = "Suburb", `23` = "Suburb",
                   .default = "Rural"),
    urban = factor(urban, levels = c("Rural", "Suburb", "City"))
  ) %>%
  arrange(desc(impact_frac_mncs)) %>%
  mutate(
    leiden_rank = row_number()
  )

factors.usa
```

```{r}
factors.usa %>%
  group_by(census_division) %>%
  mutate(
    med = median(s_i)
  ) %>%
  ungroup() %>%
  mutate(
    type = factor(census_division),
    type = reorder(type, desc(med))
  ) %>%
  ggplot(aes(x = type, y = s_i)) +
  geom_violin() +
  geom_jitter(width = 0.1, alpha = 0.5) +
  geom_boxplot(width=0.1) +
  scale_y_log10(labels = function(x) { parse(text=paste0("10^", log10(x))) }) +
  theme_minimal() +
  theme(
    text = element_text(family = "Helvetica", size = 12),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.title.x = element_blank()
  ) +
  ylab(bquote(~log[10]~(s['in'])))
```

```{r}
factors.usa %>%
  group_by(urban) %>%
  mutate(
    med = median(s_i)
  ) %>%
  ungroup() %>%
  mutate(
    type = factor(urban),
    type = reorder(type, desc(med))
  ) %>%
  filter(!is.na(type)) %>%
  ggplot(aes(x = type, y = s_i)) +
  geom_violin() +
  geom_jitter(width = 0.1, alpha = 0.5) +
  geom_boxplot(width=0.1) +
  scale_y_log10(labels = function(x) { parse(text=paste0("10^", log10(x))) }) +
  theme_minimal() +
  theme(
    text = element_text(family = "Helvetica", size = 12),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.title.x = element_blank()
  ) +
  ylab(bquote(~log[10]~(s['in'])))
```

```{r}
factors.usa %>%
  group_by(research) %>%
  mutate(
    med = median(s_i)
  ) %>%
  ungroup() %>%
  mutate(
    type = factor(research),
    type = reorder(type, desc(med))
  ) %>%
  filter(!is.na(type)) %>%
  ggplot(aes(x = type, y = s_i)) +
  geom_violin() +
  geom_jitter(width = 0.1, alpha = 0.5) +
  geom_boxplot(width=0.1) +
  scale_y_log10(labels = function(x) { parse(text=paste0("10^", log10(x))) }) +
  theme_minimal() +
  theme(
    text = element_text(family = "Helvetica", size = 12),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks = element_line(),
    axis.ticks.length=unit(-0.25, "cm"), 
    axis.ticks.margin=unit(0.5, "cm")
  ) +
  ylab(bquote(~log[10]~(s['in'])))
```

```{r}
plot <- factors.usa %>%
  gather(key, measure, s_i, gravity_potential) %>%
  mutate(
    #measure = log10(measure),
    key = factor(key, 
                 levels = c("s_i", "gravity_potential"),
                 labels = c("s_i", "phi"))
  ) %>%
  ggplot(aes(x = num_traj, y = measure, label = full_name)) +
  geom_point() +
  facet_wrap(~key) +
  scale_x_log10(
    #breaks = c(1, 5)
  ) +
  scale_y_log10(
    #breaks = c(0, 8)
  ) +
  theme_minimal() +
  theme(
    text = element_text(family = "Helvetica"),
    strip.text = element_text(face = "bold"),
    axis.title = element_text(face = "bold"),
    panel.grid = element_blank(),
    panel.border = element_rect(size = 0.5, fill = NA)
  ) +
  xlab("# Trajectories with University") +
  ylab("Measure")

plot
plotly.plot <- ggplotly(plot, tooltip = "all")
plotly.plot
```

```{r}

plot <- factors.usa %>%
  ggplot(aes(x = s_i, y = mean_traj_len, label = full_name)) +
  geom_point() +
  scale_x_log10() +
  theme_minimal() +
  theme(
    text = element_text(family = "Helvetica"),
    strip.text = element_text(face = "bold"),
    axis.title = element_text(face = "bold"),
    panel.grid = element_blank(),
    panel.border = element_rect(size = 0.5, fill = NA)
  ) +
  ylab("Mean Trajectory Length") +
  xlab("s_i")

plot
plotly.plot <- ggplotly(plot, tooltip = "all")
plotly.plot
```

```{r}
factors.usa %>%
  ggplot(aes(x = impact_frac_mncs, y = mean_traj_len)) +
  geom_point()

```

```{r}
data <- factors.usa %>%
  select(s_i, gravity_potential, count, leiden_rank, FALLENR17, GRFTF17, GRCIP4PR, HUM_RSD, OTHER_RSD, STEM_RSD, SOCSC_RSD, `S&ER&D`, `NONS&ER&D`, full_name) %>%
  mutate(s_i = log10(s_i),
         gravity_potential = log10(gravity_potential),
         count = log10(count)) %>%
  na.omit()

library(plotly)
```

```{r}
count <- 0
breaks_fun <- function(x) {
  count <<- count + 1L
  switch(
    floor(count / 2),
    c(1, 4),
    c(0, 6),
    c(1, 400),
    c(0, 120),
    c(0, 2e+06),
    c(0, 1e+05),
    c(0, 6e+4),
    c(0, 20000),
    c(0, 600),
    c(0, 100),
    c(0, 150),
    c(0, 250)
  )
}

plot <- data %>%
  gather(key, value, count, leiden_rank, FALLENR17, GRFTF17, GRCIP4PR, HUM_RSD, OTHER_RSD, STEM_RSD, SOCSC_RSD, `S&ER&D`, `NONS&ER&D`, gravity_potential) %>%
  mutate(
    key = factor(key, 
                 levels = c("count", "gravity_potential", "leiden_rank", "GRCIP4PR",
                            "S&ER&D", "NONS&ER&D", "FALLENR17", "GRFTF17", 
                            "STEM_RSD", "SOCSC_RSD", "HUM_RSD", "OTHER_RSD"),
                 labels = c("Log10(#authors)", "Log10(Φ)", "Leiden Rank",  "#Doctoral Fields",
                            "S&E $ (1000's)", "Non S&E $ (1000's)", "Total Enrollment", "Graduate Enrollment", 
                            "#STEM PhDs", "#Soc. Sci. PhDs", "#Humanities PhDs", "#Other PhDs"))
  ) %>%
  ggplot(aes(x = value, y = s_i, label = full_name)) +
  geom_point(alpha = 0.8, size = 1) +
  facet_wrap(~key, scale = "free_x", nrow = 3) +
  stat_smooth(method = "loess",
              formula = y ~ x,
              color = "dodgerblue4",
              size = 0.5,
              fullrange = T) +
  stat_smooth(method = "lm",
              formula = y ~ x,
              color = "firebrick4",
              size = 1,
              fullrange = T) +
  ggpmisc::stat_poly_eq(formula = y ~ x,
                        geom = "text_npc",
                        aes(label = paste(..rr.label.., sep = "~~~")),
                        parse=TRUE,
                        label.x.npc = 0.95,
                        rr.digits = 1,
                        size = 3,
                        color = "firebrick4"
  ) +
  scale_x_continuous(
    breaks = breaks_fun,
    expand = c(0.1, 0)
  ) +
  scale_y_continuous(
    breaks = c(0, 4, 8),
    labels = function(x) { parse(text=paste0("10^", x)) },
  ) +
  theme_minimal() +
  theme(
    text = element_text(family = "Helvetica", size = 12),
    axis.title = element_text(size = 14, face = "bold"),
    axis.title.x = element_blank(),
    panel.spacing = unit(0.2, "lines"),
    panel.spacing.x = unit(0.5, "lines"),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    panel.border = element_rect(size = 0.5, fill = NA),
    strip.text = element_text(face = "bold"),
    axis.ticks = element_line()
  ) +
  ylab(bquote(~log[10]~(s['in'])))

ggsave("~/Desktop/all_factors_pulling.pdf", plot, height = 6, width = 8)
#plotly.plot <- ggplotly(plot, tooltip = "all")
#plotly.plot
#htmlwidgets::saveWidget(plotly.plot, "~/Desktop/all_factors_pulling.html")
```

```{r}
count <- 0
breaks_fun <- function(x) {
  count <<- count + 1L
  switch(
    count,
    c(1, 4),
    c(1, 7),
    c(1, 400),
    c(0, 120),
    c(0, 2e+06),
    c(0, 1e+05),
    c(0, 6e+4),
    c(0, 20000),
    c(0, 600),
    c(0, 100),
    c(0, 150),
    c(0, 250)
  )
}

plot <- data %>%
  gather(key, value, count, leiden_rank, FALLENR17, GRFTF17, GRCIP4PR, HUM_RSD, OTHER_RSD, STEM_RSD, SOCSC_RSD, `S&ER&D`, `NONS&ER&D`, s_i) %>%
  mutate(
    key = factor(key, 
                 levels = c("count", "s_i", "leiden_rank", "GRCIP4PR",
                            "S&ER&D", "NONS&ER&D", "FALLENR17", "GRFTF17", 
                            "STEM_RSD", "SOCSC_RSD", "HUM_RSD", "OTHER_RSD"),
                 labels = c("Log10(#authors)", "Log10(s)", "Leiden Rank",  "#Doctoral Fields",
                            "S&E $ (1000's)", "Non S&E $ (1000's)", "Total Enrollment", "Graduate Enrollment", 
                            "#STEM PhDs", "#Soc. Sci. PhDs", "#Humanities PhDs", "#Other PhDs"))
  ) %>%
  ggplot(aes(x = value, y = gravity_potential, label = full_name)) +
  geom_point(alpha = 0.8, size = 1) +
  facet_wrap(~key, scale = "free_x", nrow = 3) +
  stat_smooth(method = "loess",
              formula = y ~ x,
              color = "dodgerblue4",
              size = 0.5,
              fullrange = T) +
  stat_smooth(method = "lm",
              formula = y ~ x,
              color = "firebrick4",
              size = 1,
              fullrange = T) +
  ggpmisc::stat_poly_eq(formula = y ~ x,
                        geom = "text_npc",
                        aes(label = paste(..rr.label.., sep = "~~~")),
                        parse=TRUE,
                        label.x.npc = 0.95,
                        rr.digits = 1,
                        size = 3,
                        color = "firebrick4"
  ) +
  scale_x_continuous(
    breaks = breaks_fun,
    expand = c(0.1, 0)
  ) +
  scale_y_continuous(
    breaks = c(0, 4, 8),
    labels = function(x) { parse(text=paste0("10^", x)) },
  ) +
  theme_minimal() +
  theme(
    text = element_text(family = "Helvetica", size = 12),
    axis.title = element_text(size = 14, face = "bold"),
    axis.title.x = element_blank(),
    panel.spacing = unit(0.2, "lines"),
    panel.spacing.x = unit(0.5, "lines"),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    panel.border = element_rect(size = 0.5, fill = NA),
    strip.text = element_text(face = "bold"),
    axis.ticks = element_line()
  ) +
  ylab(bquote(~log[10]~(phi)))

ggsave("~/Desktop/all_factors_potential.pdf", plot, height = 6, width = 8)
#plotly.plot <- ggplotly(plot, tooltip = "all")
#plotly.plot
#htmlwidgets::saveWidget(plotly.plot, "~/Desktop/all_factors_potential.html")
```

```{r}
data %>%
  rename(measure = "s_i", to.copmare = "gravity_potential")

data
```

```{r}
summary(lm(log(s_i) ~ log(count) + census_division, data = factors.usa))
```

```{r}
summary(lm(log(s_i) ~ log(count) + research, data = factors.usa))
```

```{r}
summary(lm(log(s_i) ~ log(count) + leiden_rank, data = factors.usa))
```

```{r}
summary(lm(log(s_i) ~ log(count) + urban, data = factors.usa))
```

# Total enrollment
```{r}
summary(lm(log10(s_i) ~ log(count) + FALLENR17, data = factors.usa))
```

# Graduate full-time enrollment
```{r}
summary(lm(log10(s_i) ~ log10(count) + GRFTF17, data = factors.usa))
```

# Number of programs in which a graduate degree is conferred
```{r}
summary(lm(log(s_i) ~ log(count) + GRCIP4PR, data = factors.usa))
```

# Number of doctors degrees conferred
```{r}
summary(lm(log(s_i) ~ log(count) + DOCRSDEG, data = factors.usa))
```

# Number of doctors degrees conferred
```{r}
summary(lm(log(s_i) ~ log(count) + HUM_RSD + OTHER_RSD + STEM_RSD + SOCSC_RSD, data = factors.usa))
```

# R&D Expenditure for STEM (S&ER&D) and Non-STEM (NONS$ER&D) research
```{r}
summary(lm(log(s_i) ~ log(count) + `S&ER&D` + `NONS&ER&D`, data = factors.usa))
```

### 2021-09-02 paper/submissions/science/main.tex

--- 2021-09-01 paper/current/main.tex
@@
 \usepackage{graphicx}
-\def\figdir{../Figs}
+\def\figdir{../../Figs}
 
@@
 %\usepackage{scicite}
-\usepackage[style=science,
+\usepackage[style=nature,
 					backend=biber,
@@
 	Historically, mobility was constrained by geographic distance, however, in the globalizing world, language, culture, and history are increasingly important.
-	Here, we show a mathematical equivalence between \textit{word2vec} model and the gravity model of mobility and demonstrate that, by using three human trajectory datasets, \textit{word2vec} encodes nuanced relationships between locations into a vector-space, providing a measure of effective distance.
+	We propose using the neural embedding model \textit{word2vec} for studying mobility and capturing its complexity.
+    \textit{Word2ec} is shown to be mathematically equivalent to the gravity model of mobility, and using using three human trajectory datasets, we demonstrate that it encodes nuanced relationships between locations into a vector-space, providing a measure of effective distance that outperforms baselines.
 	Focusing on the case of scientific mobility, we show that embeddings uncover cultural, linguistic, and hierarchical relationships at multiple levels of granularity.
@@
 Similarly, a student in South Korea is more likely to attend a university in Canada than one in North Korea~\autocite{unesco2019students}.
-Although geographic distance has been used as the most prominent basis for models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} models, the decreasing relevance of geography calls for alternative ways of conceptualizing ``distance''~\autocite{boschma2005proximity, brown1970migration, kim2018functional}.
+Although geographic distance has been used as the most prominent basis for models of mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation~\autocite{simini2012universal} models, there have been attempts to define alternative notions of distance, or functional distances~\autocite{boschma2005proximity, brown1970migration, kim2018functional}, from real-world data or \textit{a priori} relationships between geographic entities.
 
@@
 Networks offer a solution to representing many dimensions of mobility, yet edges only encode simple relationships between connected entities.
-Capturing the complexity of mobility requires moving beyond simple functional distances and networks, to learning high-dimensional landscapes of mobility that incorporate many facets of mobility into a single fine-grained and continuous representation.
+Capturing the complexity of mobility requires moving beyond simple functional distances and networks, to learning high-dimensional landscapes of mobility that incorporate the many facets of mobility into a single fine-grained and continuous representation.
 
-Here, we demonstrate that the \textit{word2vec} model (Skip-Gram Negative Sampling) is equivalent to the gravity law of mobility, a fundamental mobility framework. 
-We then empirically test the resulting representation by its ability to derive functional effective distances between from trajectories.
-After validating that it accurately represents real-world data, we demonstrate \textit{word2vec}'s capacity for encoding rich information relating to geography, culture, language, and even prestige, at multiple scales of analysis.
-We embed trajectories from three datasets: U.S.
+Here, we apply a neural embedding framework to real-world mobility trajectories and demonstrate that it can encode the complex landscape of human mobility into a dense and continuous vector-space representation, from which we can not only derive a meaningful functional distance between locations but also probe relationships based on culture, language, and even prestige along with the geographic relationship.
+We embed trajectories from three massive datasets: U.S.
 passenger flight itinerary records, Korean accommodation reservations, and a dataset of scientists' career mobility between organizations captured in bibliometric records (Detailed descriptions are available in the Methods).
 
+The flight itinerary data, from the Airline Origin and Destination Survey, consists of records of more than 300 million itineraries between 1993 and 2020 documenting domestic flights between 828 airports in the United States.
+A trajectory is constructed for each passenger flight itinerary, forming an ordered sequence of unique identifiers of the origin and destination airports.
+The Korean accommodation reservations consist of customer reservation histories across 2018 and 2020 for 1,038 unique accommodation locations in Seoul, South Korea.
+A trajectory is constructed for each customer, containing the ordered sequences of accommodations they reserved over time.
+Finally, we use scientific mobility data that captures the affiliation trajectories of nearly 3 million scientists across ten years.
 We focus in more detail on scientific mobility due to its richness and importance.
@@
 In spite of its importance, understandings of scientific mobility have been limited by the sheer scope and complexity of the phenomenon~\autocite{robinson2019mobility, deville2014career}, being further confounded by the diminishing role of geography in shaping the landscape of scientific mobility.
+
 Trajectories of scientific mobility are constructed using more than three million name-disambiguated authors who were \textit{mobile}---having more than one affiliation---between 2008 and 2019, as evidenced by their publications indexed in the Web of Science database (see Methods).
-As a scientist's career progresses, they move between organizations or pick up additional (simultaneous) affiliations forming \textit{affiliation trajectories} (Fig.~\ref{fig:gravity_performance}a).
+As a scientist's career progresses, they move between organizations or pick up additional (simultaneous) affiliations forming \textit{affiliation trajectories} (Fig.~\ref{fig:methods:mobility_sentence}).
 Thus, the trajectories encode both migration and co-affiliation---the holding of multiple simultaneous affiliations involving the sharing of time and capital between locations---that is typical of scientific mobility~\autocite{rodrigues2016mobility, sugimoto2017mostimpact} (see \SI).
 
-Here, we study the skip-gram negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
+A vector-space embedding of locations (airports, accommodations, and organizations) is learned by using trajectories as input to the standard with skip-gram negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
 This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}, networks~\autocite{grover2016node2vec, linzhuo2020hyperbolic} and trajectories\autocite{liu2016exploring, feng2017poi2vec, yao2018representing, cao2019habit2vec, crivellari2019motion, solomon2018predict}.
 It works under the notion that a good representation should facilitate prediction, learning a mapping between words that can predict a target word based on its context (surrounding words).
-The model is also computationally efficient, easy to use, robust to noise, and can encode relations between entities as geometric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis, hashimoto2016word}.
+The model is also computationally efficient, robust to noise, and can encode relations between entities as geometric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis}.
 As a result, each location is encoded into a single vector representation, and vectors relate to one another based on the likelihood of locations appearing adjacent to one another in the same trajectory.
 
-Our study builds on the gravity model framework~\autocite{zipf1946gravity}.
-This is a widely-used, fundamental mobility model~\autocite{curiel2018citygravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity} that connects the \textit{expected flux}, $\hat{T}_{ij}$, between locations based on their populations and distance:
+%
+% Figure - Example of mobility sentences
+%
+\begin{figure}[ht!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{\figdir/mobility_example_combined.pdf}
+	\caption{
+		\textbf{Construction of affiliation trajectories from publication records.}
+		\textbf{a.}
+		An author published five papers across five time periods, with only one affiliation listed in the byline of each paper.
+		A unique identifier is assigned to each organization and they are assembled into an affiliation trajectory ordered by year of publication.
+		\textbf{b.}
+		If an author lists multiple organization affiliations within the same year, then organization IDs within that year are placed in random order in each training iteration of the \textit{word2vec} model (for more detail, see \SI).
+	}
+	\label{fig:methods:mobility_sentence}
+\end{figure}
+
+To validate our approach, we evaluate the quality of vector representations based on their performance in predicting real-world mobility flows using the gravity model framework~\autocite{zipf1946gravity}.
+The gravity model is a widely used mobility model~\autocite{curiel2018citygravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity} that connects the \textit{expected flux}, $\hat{T}_{ij}$, between locations based on their populations and distance:
 
@@
 %
-% Wordvec and the gravity model
+% Subsection: Embedding performance
+%
+%
+\subsection*{Embeddings provide functional distance between locations}
+
+We show that the embedding distance better predicts actual mobility flows than the geographic distance across three disparate datasets.
+In the case of flight itineraries, the embedding distance explains more than twice the expected flux between airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}a) than does geographic distance ($R^{2} = 0.22$).
+Also, the embedding distance produces better predictions of actual flux between airports than does the geographic distance (Fig.~\ref{fig:gravity_performance}b).
+In the case of Korean accommodation reservations, embedding distance better explains the expected flux ($R^{2} = 0.57$, Fig.~\ref{fig:gravity_performance}c) than does geographic distance ($R^{2} = 0.25$), and predictions made using the embedding distance outperform those made with geographic distance (Fig.~\ref{fig:gravity_performance}d).
+This performance is consistent in the case of scientific mobility:
+the embedding distance explains more than twice the expected flux ($R^{2} = 0.48$, Fig.~\ref{fig:gravity_performance}e) than does the geographic distance ($R^{2} = 0.22$), and predictions made using the embedding distance outperform those using the geographic distance (Fig.~\ref{fig:gravity_performance}f).
+These patterns hold for the subsets of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d).
+The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores calculated from the underlying mobility network (Fig.~\ref{fig:supp:distancemetrics}, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurrence matrix, Levy's symmetric \textit{word2vec}\autocite{levy2014neural}, and even direct optimization of the gravity model (Fig.\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+In sum, our results demonstrate that, consistently and efficiently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
+
+%
+% Figure - Gravity law performance
+%
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance.pdf}
+	\caption{
+		\textbf{Embedding distance encodes functional distance and better predicts mobility in flights, accommodation reservations, and global scientific mobility.}
+		\textbf{a.} Embedding distance (cosine distance between organization vectors, top) better explains the expected flux of passengers between U.S. airports than does geographic distance (bottom).
+		The red line is the line of the best fit.
+		Black dots are mean flux across binned distances.
+		99\% confidence intervals are plotted for the mean flux in each bin based on a normal distribution.
+		Correlation is calculated on the data in the log-log scale ($p < 0.0001$ across all fits).
+		The lightness of each hex bin indicates the frequency of organization pairs within it.
+		\textbf{b.} Predictions of flux between airport pairs made using embedding distance (top) outperform those made using geographic distance (bottom).
+		Box-plots show the distribution of actual flux for binned values of predicted flux.
+		Box color corresponds to the degree to which the distribution overlaps with $y = x$;
+		a perfect prediction yields all points on the black line.
+		``RMSE'' is the root-mean-squared error between the actual and predicted values.
+		Results are consistent in the case of scientific mobility.
+		For Korean accommodation reservations, embedding distance better explains the expected flux than does geographic distance (\textbf{c}), and produces better predictions (\textbf{d}).
+		Similarly, in the case of global scientific mobility, embedding distance explains the expected flux between organizations (\textbf{e)} and allows for better predictions (\textbf{f}) than geographic distance.
+	}
+	\label{fig:gravity_performance}
+\end{figure}
+
 \subsection*{word2vec and the gravity model}
 
-We first demonstrate the mathematical equivalence between the SGNS model and the gravity model.
+Why does \textit{word2vec} with the skip-gram with negative sampling model (SGNS) work so well to model mobility?
+The reason for that is the mathematical equivalence between the SGNS model and the gravity model which we demonstrate below.
+
 The {\it word2vec} model takes a location trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), as input.
@@
 
-When $w=1$ (Fig.~\ref{fig:supp:hyperparameter}), the flow can be written as
+Our experiments show that {\it word2vec} best explains real-world mobility flow when $w=1$ (Fig.~\ref{fig:supp:hyperparameter}), with the flow predicted by
 \begin{align}
@@
 In other words, \emph{word2vec with the skip-gram negative sampling is equivalent to the gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
-While the gravity model describes mobility flows from the given mass and locations, {\it word2vec} finds locations that best explain the given mobility flow. 
-\js{Also, our finding is aligned with a perspective on word embedding methods as a metric recovery~\autocite{hashimoto2016word}, which recover the underlying metric of the semantic manifold not for a particular task.}
+While the gravity model predicts mobility flows from the given mass and locations, {\it word2vec} finds locations that best explain the given mobility flow.
+Therefore, the embedding distance is inherently tied to the mobility flow, and hence, has greater predictive power than the geographic distance and other baselines.
 
@@
 Nevertheless, a model with dot similarity has the second-best performance after cosine similarity (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and the embedding distance still outperforms all alternatives we considered.
-
-%
-% Subsection: Embedding performance
-%
-%
-\subsection*{Embeddings provide functional distance between locations}
-
-\js{We prove that the gravity could be more powerful by using mobility-aware embedding distance between places as a distance measure.
-Our approach always better predicts actual mobility flows than the geographic distance and other baseline methods across three disparate datasets consistently.} In the case of flight itineraries, the embedding distance explains more than twice the expected flux between airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}a) than does geographic distance ($R^{2} = 0.22$).
-Also, the embedding distance produces better predictions of actual flux between airports than does the geographic distance (Fig.~\ref{fig:gravity_performance}b).
-In the case of Korean accommodation reservations, embedding distance better explains the expected flux ($R^{2} = 0.57$, Fig.~\ref{fig:gravity_performance}c) than does geographic distance ($R^{2} = 0.25$), and predictions made using the embedding distance outperform those made with geographic distance (Fig.~\ref{fig:gravity_performance}d).
-This performance is consistent in the case of scientific mobility:
-the embedding distance explains more than twice the expected flux ($R^{2} = 0.48$, Fig.~\ref{fig:gravity_performance}e) than does the geographic distance ($R^{2} = 0.22$), and predictions made using the embedding distance outperform those using the geographic distance (Fig.~\ref{fig:gravity_performance}f).
-These patterns hold for the subsets of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d).
-
-%
-% Figure - Example of mobility sentences
-%
-%
-% Figure - Gravity law performance
-%
-\begin{figure}[!htp]
-	\centering
-	\includegraphics[width=0.9\textwidth]{\figdir/GravityLawFig/gravity_performance_new.pdf}
-	\caption{
-		\textbf{Embedding distance encodes functional distance and better predicts mobility across three distinct human trajectory datasets. }
-		\textbf{a.} A unique identifier is assigned to each organization and they are assembled into an affiliation trajectory ordered by year of publication (top).
-If an author lists multiple organization affiliations within the same year,  we shuffle the order within that year in each training iteration (bottom, see \SI).
-		\textbf{b.} Neural embeddings outperform baselines for scientific mobility.
-The correlation between the flux and baseline distances $R^{2}$ (left), and the  root-mean-squared error between the actual and predicted values (right).
-The asterisk indicates the top-performing method.
-		\textbf{c.} Embedding distance (top) better explains the expected flux of passengers between U.S. airports than does geographic distance (bottom).
-		The red line is the line of the best fit.
-		%Black dots are mean flux across binned distances.
-		99\% confidence intervals are plotted for the mean flux in each bin.
-		Correlation is calculated on the data in the log-log scale ($p < 0.0001$ across all fits).
-		%The lightness of each hex bin indicates the frequency of organization pairs within it.
-		\textbf{d.} Predictions of flux between airport pairs made using embedding distance (top) outperform those made using geographic distance (bottom).
-		Box-plots show the distribution of actual flux for binned values of predicted flux.
-		Box color corresponds to the degree to which the distribution overlaps with $y = x$.
-		%a perfect prediction yields all points on the black line.
-		``RMSE'' is the root-mean-squared error between the actual and predicted values.
-	Embedding distance consistently produce powerful functional distance compare to geographic distance for Korean accommodation reservations (\textbf{e,f}), and global scientific mobility (\textbf{g,h})}
-	\label{fig:gravity_performance}
-\end{figure}
-
-The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores calculated from the underlying mobility network (Fig.~\ref{fig:gravity_performance}b, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurrence matrix, Levy's symmetric \textit{word2vec}\autocite{levy2014neural}, and even direct optimization of the gravity model (Fig.\ref{fig:gravity_performance}b and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
-In sum, our results demonstrate that, consistently and efficiently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
 
@@
 DB1B is a sample of 10 percent of domestic airline tickets between 1993 and 2020, comprising 307,760,841 passenger itineraries between 828 U.S. airports.
-A trajectory is constructed for each passenger flight itinerary, forming an ordered sequence of unique identifiers of the origin and destination airports.
 Each itinerary is associated with a trajectory of airports including the origin, destination, and intermediary stops.
@@
 The data contains customer-level reservation trajectories spanning the period of August 2018 through July 2020 and comprising 1,038 unique accommodation locations in Seoul, South Korea.
-A trajectory is constructed for each customer, containing the ordered sequences of accommodations they reserved over time.
 
@@
 In the case of Korean accommodation reservations, trajectories comprise a sequence of accommodations reserved over a customer's history.
-For scientific mobility, an``affiliation trajectories'' is constructed for each mobile author, which is built by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:gravity_performance}a (top).
-In more complex cases, such as listing multiple affiliations on the same paper or publishing with different affiliations on multiple publications in the same year, the order is randomized within that year, as shown in Fig.~\ref{fig:gravity_performance}a (bottom).
+For scientific mobility, an``affiliation trajectories'' is constructed for each mobile author, which is built by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:methods:mobility_sentence}a.
+In more complex cases, such as listing multiple affiliations on the same paper or publishing with different affiliations on multiple publications in the same year, the order is randomized within that year, as shown in Fig.~\ref{fig:methods:mobility_sentence}b.
 
@@
 
-\subsection*{Element-centric clustering similarity}
-
-\js{Element-centric clustering similarity \autocite{gates2019element} is unified similarity embracing disjoint, overlapping, and hierarchically structured clustering.
-Element-centric clustering similarity captures cluster-induces relationships between through cluster affiliation graph where one vertex set is the original element $V=\{v_1, ...
-v_N\}$ and the other corresponds to the cluster $C=\{c_1, ...
-c_M\}$ as a bipartite graph $\mathcal{B} (V \cup C, \mathcal{R})$.
-an undirected edge $a_{i\beta} \in \mathcal{R}$  denote element $v_i$ is a member of cluster $c_\beta$.
-For hierarchically structured clustering.
-each cluster $c_\beta$ is assigned a hierarchical level $l_{\beta} \in [0,1]$ by re-scaling the dendrogram according to the maximum path length from the roots.
-The weight of the cluster affiliation edge is given by the hierarchy weight function $a_{i\beta}  = e^{rl_{\beta}}$ with scaling parameter $r$ which determine the relative importance of membership at different levels of hierarchy.
-Here, lower $r$ focuses on the higher level of the hierarchy, and lower levels are treated as a refinement of the higher level.
-Larger $r$ emphasizes lower-level cluster structure, and higher levels of the hierarchy are seen as an aggregation of the lower-level structure.
-If $r=0$, every cluster is treated equally.}
-
-\js{The cluster affiliation graph is projected onto  a cluster-induced element graph which is a weighted, directed graph summarizes the relationship induced by common cluster memberships.
-In the cluster-induced element graph,  each edge  between element $v_i$ and $v_j$ has weight $w_{ij} = \sum_{\gamma} \frac{a_{i\gamma}a_{j\gamma}}{\sum_{\kappa}a_{i\kappa} {\sum_{m}a_{m\gamma}}}$.
-Given a cluster-induces element graph with weighted matrix $W$, the personalized PageRank vector $p_i$  is used as membership-aware similarity between element $i$ and other elements in the graph.
-Then, the element-wise similarity of an element $v_i$ in two clustering  $\mathcal{A}$ and $\mathcal{B}$ is calculated with $S_i(\mathcal{A}, \mathcal{B}) = 1 - L_1(p_i^{\mathcal{A}},p_j^{\mathcal{B}})$, and the final elementric-centric similiarty of two clustering $\mathcal{A}$ and $\mathcal{B}$ is the average of the element-wise similarities, $S(\mathcal{A}, \mathcal{B}) =\frac{1}{N}\sum_{i=1}^{N} S_i(\mathcal{A}, \mathcal{B})$.}
-
 %

### 2021-09-02 paper/current/main.tex
edit few lines

@@
 %
-\section{Introduction}\label{sec:introduction} %{{{
+\section*{Introduction}\label{sec:introduction} %{{{
 
@@
 As a result, each location is encoded into a single vector representation, and vectors relate to one another based on the likelihood of locations appearing adjacent to one another in the same trajectory.
+Also,  \textit{word2vec} can be intepreted as a metric recovery, which recover the underlying metric of the semantic manifold ~\autocite{hashimoto2016word}.
 
@@
 
+\section*{Results}
 %
@@
 While the gravity model describes mobility flows from the given mass and locations, {\it word2vec} finds locations that best explain the given mobility flow.
-\js{Also, our finding is aligned with a perspective on word embedding methods as a metric recovery~\autocite{hashimoto2016word}, which recover the underlying metric of the semantic manifold not for a particular task.}
 

### 2021-09-07 paper/current/main.tex
reflect yy's comment

@@
 	Focusing on the case of scientific mobility, we show that embeddings uncover cultural, linguistic, and hierarchical relationships at multiple levels of granularity.
-	Connecting neural embeddings to the gravity model opens up new avenues for the study of mobility.
+	Connecting neural embeddings to the gravity model may open up new avenues for the computational study of mobility.
 \end{sciabstract}
@@
 Here, we demonstrate that the \textit{word2vec} model (Skip-Gram Negative Sampling) is equivalent to the gravity law of mobility, a fundamental mobility framework. 
-We then empirically test the resulting representation by its ability to derive functional effective distances between from trajectories.
+We then empirically test the resulting representation by its ability to derive functional effective distances from trajectories.
 After validating that it accurately represents real-world data, we demonstrate \textit{word2vec}'s capacity for encoding rich information relating to geography, culture, language, and even prestige, at multiple scales of analysis.
@@
 Here, we study the skip-gram negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
-This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}, networks~\autocite{grover2016node2vec, linzhuo2020hyperbolic} and trajectories\autocite{liu2016exploring, feng2017poi2vec, yao2018representing, cao2019habit2vec, crivellari2019motion, solomon2018predict}.
+This neural embedding model, originally designed for learning  with embedding~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}, networks~\autocite{grover2016node2vec, linzhuo2020hyperbolic} and trajectories\autocite{liu2016exploring, feng2017poi2vec, yao2018representing, cao2019habit2vec, crivellari2019motion, solomon2018predict}.
 It works under the notion that a good representation should facilitate prediction, learning a mapping between words that can predict a target word based on its context (surrounding words).
 The model is also computationally efficient, easy to use, robust to noise, and can encode relations between entities as geometric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis, hashimoto2016word}.
-As a result, each location is encoded into a single vector representation, and vectors relate to one another based on the likelihood of locations appearing adjacent to one another in the same trajectory.
+When applied to the trajectory data, each location is encoded into a single vector representation, and vectors relate to one another based on the likelihood of locations appearing adjacent to one another in the same trajectory.
 Also,  \textit{word2vec} can be intepreted as a metric recovery, which recover the underlying metric of the semantic manifold ~\autocite{hashimoto2016word}.
@@
 
-The gravity model dictates that the expected flow, $\hat{T}_{ij}$, ($\hat{T}_{ij }= \hat{T}_{ji}$), is proportional to the locations' population, $\hat{T}_{ij} \propto m_{i} m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
+The gravity model employs two natural assumptions that the expected flow, $\hat{T}_{ij}$, ($\hat{T}_{ij }= \hat{T}_{ji}$), is proportional to the locations' population, $\hat{T}_{ij} \propto m_{i} m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
 We define the distance function in terms of either the geographic distance between locations or their functional distance in the vector space, which is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.
@@
 	\caption{
-		\textbf{Embedding distance encodes functional distance and better predicts mobility across three distinct human trajectory datasets. }
+		\textbf{Embedding distance encodes functional distance that fits the gravity model of mobility best across three distinct human trajectory datasets. }
 		\textbf{a.} A unique identifier is assigned to each organization and they are assembled into an affiliation trajectory ordered by year of publication (top).
@@
 		``RMSE'' is the root-mean-squared error between the actual and predicted values.
-	Embedding distance consistently produce powerful functional distance compare to geographic distance for Korean accommodation reservations (\textbf{e,f}), and global scientific mobility (\textbf{g,h})}
+	Embedding distance consistently produce powerful functional distance for Korean accommodation reservations (\textbf{e,f}), and global scientific mobility (\textbf{g,h})}
 	\label{fig:gravity_performance}
@@
 
-The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized-page rank scores calculated from the underlying mobility network (Fig.~\ref{fig:gravity_performance}b, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized Page Rank scores calculated from the underlying mobility network (Fig.~\ref{fig:gravity_performance}b, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
 The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurrence matrix, Levy's symmetric \textit{word2vec}\autocite{levy2014neural}, and even direct optimization of the gravity model (Fig.\ref{fig:gravity_performance}b and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
@@
 Just as the embedding space makes it possible to \textit{zoom in} on subsets of organizations, it is also possible to \textit{zoom out} by aggregating organizational vectors.
-In doing so, we can examine the country-level structure that governs scientific mobility.
+In doing so, we can examine the large-scale structure that governs scientific mobility.
 We define the representative vector of each country as the average of their organizational vectors and, using their cosine similarities, perform hierarchical clustering of nations that have at least 25 organizations represented in the embedding space (see Fig.
@@
 We demonstrated that a functional distance derived from the embedding can be used with the gravity model of mobility to better predict real-world mobility than does geographic distance.
-Embedding distance outperformed geographic distance across distinct and disparate domains, including U.S. flight itineraries, Korean hotel accommodation reservations, and global scientific mobility.
+Embedding distance outperformed geographic distance and other alternative methods across distinct and disparate domains, including U.S.
+flight itineraries, Korean hotel accommodation reservations, and global scientific mobility.
 We discover that this performance results from neural embeddings implicitly learning gravity law relationships between locations, making them particularly well suited to representing mobility.

### 2021-10-27 paper/current/main.tex
update main text
Updates to make the distinction between prediction and validation more apparent. Other general changes in tone and focus throughout

--- 2021-09-02 paper/current/main.tex
@@
 	Historically, mobility was constrained by geographic distance, however, in the globalizing world, language, culture, and history are increasingly important.
-	Here, we show a mathematical equivalence between \textit{word2vec} model and the gravity model of mobility and demonstrate that, by using three human trajectory datasets, \textit{word2vec} encodes nuanced relationships between locations into a vector-space, providing a measure of effective distance.
-	Focusing on the case of scientific mobility, we show that embeddings uncover cultural, linguistic, and hierarchical relationships at multiple levels of granularity.
+	Here, we show a mathematical equivalence between \textit{word2vec} model and the gravity model of mobility and demonstrate that, by using three human trajectory datasets, \textit{word2vec} encodes nuanced relationships between locations into an accurate and meaningful vector-space, providing a functional distance between locations, as well as a representation for studying the many dimensions of mobility.
+	Focusing on the case of scientific mobility, we show that embeddings implicitly learn cultural, linguistic, and hierarchical relationships at multiple levels of granularity.
 	Connecting neural embeddings to the gravity model opens up new avenues for the study of mobility.
@@
 Here, we demonstrate that the \textit{word2vec} model (Skip-Gram Negative Sampling) is equivalent to the gravity law of mobility, a fundamental mobility framework. 
-We then empirically test the resulting representation by its ability to derive functional effective distances between from trajectories.
-After validating that it accurately represents real-world data, we demonstrate \textit{word2vec}'s capacity for encoding rich information relating to geography, culture, language, and even prestige, at multiple scales of analysis.
+We then empirically test the resulting representation by its ability to derive from mobility trajectories the functional distances between locations.
+After validating that it accurately represents real-world data, we leverage unique embedding-based methods to demonstrate \textit{word2vec}'s capacity for encoding rich information relating to geography, culture, language, and even prestige, at multiple scales of analysis.
 We embed trajectories from three datasets: U.S.
@@
 
-We focus in more detail on scientific mobility due to its richness and importance.
+We focus in most detail on scientific mobility due to its richness and importance.
 Scientific mobility---which is a central driver of the globalized scientific enterprise~\autocite{czaika2018globalisation, box2008competition} and strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, morgan2018prestige}---is not only an important topic in the Science of Science but also ideal for our study thanks to its well-known structural properties such as the centrality of scientifically advanced countries and the strong prestige hierarchy~\autocite{clauset2015hierarchy, deville2014career}.
@@
 Here, we study the skip-gram negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
-This neural embedding model, originally designed for learning language models~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}, networks~\autocite{grover2016node2vec, linzhuo2020hyperbolic} and trajectories\autocite{liu2016exploring, feng2017poi2vec, yao2018representing, cao2019habit2vec, crivellari2019motion, solomon2018predict}.
+This neural embedding model, originally designed for learning models of language~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}, networks~\autocite{grover2016node2vec, perozzi2014deepwalk, linzhuo2020hyperbolic} and trajectories\autocite{liu2016exploring, feng2017poi2vec, yao2018representing, cao2019habit2vec, crivellari2019motion, solomon2018predict}.
 It works under the notion that a good representation should facilitate prediction, learning a mapping between words that can predict a target word based on its context (surrounding words).
@@
 The gravity model dictates that the expected flow, $\hat{T}_{ij}$, ($\hat{T}_{ij }= \hat{T}_{ji}$), is proportional to the locations' population, $\hat{T}_{ij} \propto m_{i} m_{j}$, and decays as a function of their distance, $f(r_{ij})$.
-We define the distance function in terms of either the geographic distance between locations or their functional distance in the vector space, which is calculated as the cosine distance between their vectors, termed the \textit{embedding distance}.
+Traditionally, the decay function has been defined in terms of geographic distance, due to its intuitiveness and availability. 
+Here, we also consider the \textit{embedding distance}, calculated as the cosine distance between location vectors modeled by \textit{word2vec}. 
 The decay function $f(r_{ij})$ defines the effect of distance, and different decay functions can model fundamentally different mechanisms \autocite{barthelemy2011spatial} such as the cost functions for a given distance and the spatial granularity of the observation.
 For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}).
-Though there is no qualitative difference, the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
-The power-law decay function performs best with the geographic distance, likely resulting from the  function's suitability for large, complex, and scale-free spatial systems~\autocite{chen2015distance};
-performance of the embedding distance is similar between the functional forms, though best for the exponential form, which stems from an underlying connection between the function and \textit{word2vec} that we discuss later.
+Our results show embedding distance to be a better representation of mobility than geographic distance, no matter decay function (see Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+However, we note that the geographic distance best models real-world mobility with the power-law decay function, likely resulting from the function's suitability for large, complex, and scale-free spatial systems~\autocite{chen2015distance};
+the embedding distance, in contrast, models our mobility data best for the exponential decay function, which stems from an underlying connection between the function and \textit{word2vec}.
 
@@
 
-In other words, \emph{word2vec with the skip-gram negative sampling is equivalent to the gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
-While the gravity model describes mobility flows from the given mass and locations, {\it word2vec} finds locations that best explain the given mobility flow.
+In other words, \emph{word2vec with skip-gram negative sampling is equivalent to the gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
+While the gravity model describes mobility flows from the given mass and locations, {\it word2vec} 
+finds locations that best explain the given mobility flow. 
+This makes \textit{word2vec} a powerful tool for learning models of mobility.
 
@@
 
-Given their equivalence, we expect that the \textit{word2vec} embedding can encode effective functional distances between locations according to the gravity law. 
-Here, we test this notion using three human mobility datasets, showing that \textit{word2vec}  consistently offers a better representation of actual mobility flows than baselines methods.
+To ensure that \textit{word2vec} learns an accurate representation of mobility that encodes meaningful functional distances, we devise an empirical validation task. 
+Past studies have utilized a range of validating tasks for assessing the accuracy \textit{word2vec}, including analogy completion~\cite{mikolov2013word2vec} and human surveys~\cite{kozlowski2018geometry}, in the case of natural language, or link prediction, in the case of network embedding~\cite{perozzi2014deepwalk, grover2016node2vec}.
+Here, we expect that an accurate representation of the mobility data should provide a functional distance that better models the flux between institutions than does geographic distance, which is at present the most widely measure used in the gravity model.
+We test this notion using three human mobility datasets, showing that \textit{word2vec} consistently offers a better representation of actual mobility flows than geographic distance, as well as alternative network and direct optimization approaches.
+
 In the case of flight itineraries, the embedding distance explains more than twice the expected flux between airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}a) than does geographic distance ($R^{2} = 0.22$), which has traditionally been used to quantify distance for the gravity model.
@@
 To explore the topological structure of the embedding, we use a topology-based dimensionality reduction method (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation of the embedding space (Fig.~\ref{fig:projection}a).
-By showing relationships between individual organizations, rather than aggregates such as nations or cities, this projection constitutes the largest and highest resolution ``map'' of scientific mobility to date.
+By leveraging the unique characteristics of \textit{word2vec}, we are able to show the relationships between individual organizations, rather than aggregates such as nations or cities, this projection constitutes the largest and highest resolution ``map'' of scientific mobility to date.
 
@@
 
-Prestige hierarchy is known to underpin the dynamics of scientific mobility, in which researchers tend to move to similar or less prestigious organizations~\autocite{deville2014career, clauset2015hierarchy}.
+The embedding space can also encode more fine-grained relationships between entities. 
+For examples, prestige hierarchies are known to underpin the dynamics of scientific mobility, in which researchers tend to move to similar or less prestigious organizations~\autocite{deville2014career, clauset2015hierarchy}.
 Could the embedding space, to which no explicit prestige information is given, encode a prestige hierarchy?
@@
 Neural embedding approaches offer a novel, data-driven solution for efficiently learning an effective and robust representation of locations based on trajectory data, encoding the complex and multi-faceted nature of mobility.
-We demonstrated that a functional distance derived from the embedding can be used with the gravity model of mobility to better predict real-world mobility than does geographic distance.
-Embedding distance outperformed geographic distance across distinct and disparate domains, including U.S. flight itineraries, Korean hotel accommodation reservations, and global scientific mobility.
-We discover that this performance results from neural embeddings implicitly learning gravity law relationships between locations, making them particularly well suited to representing mobility.
-Focusing on scientific mobility, we find that the embedding successfully encodes many aspects of scientific mobility into a single representation, including global and regional geography, shared languages, and prestige hierarchies, even without explicit information on these factors.
+Its unique strength stems from our discovery that \textit{word2vec} is equivalent to a gravity model, making it a natural and theoretically-grounded tool for modeling mobility. 
+By virtue of this equivalency, \textit{word2vec} learns accurate representations of mobility across disparate domains, including U.S.
+flight itineraries, Korean hotel accommodation reservations, and global scientific mobility.
+Focusing on the case of scientific mobility, we leverage the unique topological structure of the embedding space to reveal how it encodes nuanced aspects of mobility, including global and regional geography, shared languages, and prestige hierarchies, all of which are learned using only the mobility trajectories of individuals.
 
 In revealing the correspondence between neural embeddings and the gravity model, the study of human mobility can move beyond geographic and network-based models of mobility, and instead leverage the high-order structure from individuals' mobility trajectories using these robust and efficient methods.
-While we focus on three domains of mobility, this approach could be applied to many different domains, such as general human migration, transit-network mobility, and more.
-Once learned, functional distances between locations, such as countries, cities, or organizations, can be published to support future research.
+While we focus on three domains of human mobility, this approach could be applied to many different domains, such as animal migration, transit-network mobility, international trade, and more.
+Once learned, functional distances between locations, such as countries, cities, or organizations, or the embedding model itself, can be published to facilitate re-use, and support reproducibility and transparency in cases when the underlying data is too sensitive to make available.
 Moreover, this approach can be used to learn a functional distance even between entities for which no geographic analog exists, such as between occupational categories based on individuals' career trajectories.
-In addition to providing a functional distance that supports modeling and predicting mobility patterns, the structure of the neural embedding space is amenable to a range of unique applications for studying mobility.
+In addition to providing a functional distance that supports modeling and predicting mobility patterns, the topology of the embedding space is amenable to a range of unique applications for studying mobility.
 As we have shown, the embedding space allows the visualization of the complex structure of scientific mobility at high resolution across multiple scales, providing a large and detailed map of the landscape of global scientific mobility.
-Embedding also allows us to quantitatively explore abstract notions such as academic prestige, and can potentially be generalized to other abstract axes.
+Other operations such as comparing entities or calculating aggregates, which could be complex and computationally-expensive for other methods, are here reduced to simple vector arithmetic. 
+Embeddings also allows us to quantitatively explore abstract notions such as academic prestige, and can potentially be generalized to other abstract axes.
 Investigation of the structure of the embedding space, such as the vector norm, reveals universal patterns based on the organization's size and their vector norm that could be leveraged in future studies of mobility.
@@
 By revealing the correspondence between neural embedding and the gravity model and revealing their utility and efficacy, our study opens a new avenue in the study of mobility.
-Mobility is at the core of many global challenges, and the insights brought forth by our tool can be put to use to inform a better understanding of human mobility, and to inform sensible, effective, sustainable, and humane policies.
 

### 2021-10-27 paper/current/main.tex

@@
 The model is also computationally efficient, easy to use, robust to noise, and can encode relations between entities as geometric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis, hashimoto2016word}.
-As a result, each location is encoded into a single vector representation, and vectors relate to one another based on the likelihood of locations appearing adjacent to one another in the same trajectory.
+When applied to the trajectory data, each location is encoded into a single vector representation, and vectors relate to one another based on the likelihood of locations appearing adjacent to one another in the same trajectory.
 Also,  \textit{word2vec} can be intepreted as a metric recovery, which recover the underlying metric of the semantic manifold ~\autocite{hashimoto2016word}.

### 2021-10-28 paper/current/main.tex
add detail purpose of the gravity model

@@
 Traditionally, the decay function has been defined in terms of geographic distance, due to its intuitiveness and availability.
-Here, we also consider the \textit{embedding distance}, calculated as the cosine distance between location vectors modeled by \textit{word2vec}.
+Here, we also consider the \textit{embedding distance}, calculated as the cosine distance between location vectors modeled by \textit{word2vec} to test the ability to encode the mobility data.
 The decay function $f(r_{ij})$ defines the effect of distance, and different decay functions can model fundamentally different mechanisms \autocite{barthelemy2011spatial} such as the cost functions for a given distance and the spatial granularity of the observation.

### 2021-10-28 paper/current/main.tex
rewrite with engaging manner

--- 2021-10-27 paper/current/main.tex
@@
 Traditionally, the decay function has been defined in terms of geographic distance, due to its intuitiveness and availability.
-Here, we also consider the \textit{embedding distance}, calculated as the cosine distance between location vectors modeled by \textit{word2vec}.
+Here, we also consider the \textit{embedding distance}, calculated as the cosine distance between location vectors modeled by \textit{word2vec}, to test the ability to encode the mobility data.
 The decay function $f(r_{ij})$ defines the effect of distance, and different decay functions can model fundamentally different mechanisms \autocite{barthelemy2011spatial} such as the cost functions for a given distance and the spatial granularity of the observation.
 For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}).
-Our results show embedding distance to be a better representation of mobility than geographic distance, no matter decay function (see Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+Our results show that embedding distance deriving from the \textit{word2vec} significantly improves the ability to predict mobility compare to geographical distance no matter decay function while providing useful representation of locations as well (see Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
 However, we note that the geographic distance best models real-world mobility with the power-law decay function, likely resulting from the function's suitability for large, complex, and scale-free spatial systems~\autocite{chen2015distance};

### 2021-10-28 paper/current/main.tex
rewrite with engaging manner

@@
 For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}).
-Our results show that embedding distance deriving from the \textit{word2vec} significantly improves the ability to predict mobility compare to geographical distance no matter decay function while providing useful representation of locations as well (see Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+Our results show that embedding distance deriving from the \textit{word2vec} significantly improves the ability to predict the mobility compare to geographical distance no matter decay function while providing the useful representation of locations as well (see Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
 However, we note that the geographic distance best models real-world mobility with the power-law decay function, likely resulting from the function's suitability for large, complex, and scale-free spatial systems~\autocite{chen2015distance};

### 2021-10-28 paper/current/main.tex
rewrite math part and use innter product

@@
 
-Here, we study the skip-gram negative sampling, or \textit{word2vec} neural-network architecture (see Methods).
+Here, we study the skip-gram negative sampling (SGNS), or \textit{word2vec} neural-network architecture (see Methods).
 This neural embedding model, originally designed for learning models of language~\autocite{mikolov2013word2vec}, has been making breakthroughs by revealing novel insights into texts~\autocite{tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}, networks~\autocite{grover2016node2vec, perozzi2014deepwalk, linzhuo2020hyperbolic} and trajectories\autocite{liu2016exploring, feng2017poi2vec, yao2018representing, cao2019habit2vec, crivellari2019motion, solomon2018predict}.
@@
 \end{align}
-where $P(j)$ is the fraction of $j$ in the data.
+where $P(j)$ is the fraction of location $j$'s frequency in the data.
 In general, calculating $Z_i$ is computationally expensive and there are two common approximations: hierarchical softmax \autocite{morin2005hierarchical} and negative sampling \autocite{mikolov2013word2vec}.
@@
 \end{align}
-where $N(i) = NP(i)$ is the frequency of location $i$ in the data, and $N=\sum_{i \in {\cal A}} N(i)$ is the sum of frequencies of all locations.
+where $N$ is the sum of frequencies of all locations and $N(i) = NP(i)$ is the frequency of location $i$ in the data.
 
@@
 
-In other words, \emph{word2vec with skip-gram negative sampling is equivalent to the gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
+In other words, \emph{word2vec with skip-gram negative sampling is mathematically equivalent to the gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
 While the gravity model describes mobility flows from the given mass and locations, {\it word2vec}
-finds locations that best explain the given mobility flow.
+estimates proper locations in the vector space which best explain the given mobility flow.
 This makes \textit{word2vec} a powerful tool for learning models of mobility.
@@
 To explore the topological structure of the embedding, we use a topology-based dimensionality reduction method (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation of the embedding space (Fig.~\ref{fig:projection}a).
-By leveraging the unique characteristics of \textit{word2vec}, we are able to show the relationships between individual organizations, rather than aggregates such as nations or cities, this projection constitutes the largest and highest resolution ``map'' of scientific mobility to date.
+By leveraging the unique characteristics of representation learning approach, we are able to show the relationships between individual organizations, rather than aggregates such as nations or cities, this projection constitutes the largest and highest resolution ``map'' of scientific mobility to date.
 

### 2021-10-28 paper/current/main.tex
handling some comments"

@@
 \end{align}
-where $N$ is the sum of frequencies of all locations and $N(i) = NP(i)$ is the frequency of location $i$ in the data.
+where $N$ is the sum of frequencies in all locations and $N(i) = NP(i)$ is the frequency of location $i$ in the data.
 
@@
 Nevertheless, cosine distance is often shown to be useful in practice~\autocite{lerman2007embedding, brown1970migration, kim2018functional}.
-We compare the performance of this cosine-based embedding distance against those derived using dot product similarity and euclidean distance.
+We compare the performance of this cosine-based embedding distance against those derived using inner product similarity and euclidean distance.
 

### 2021-10-28 paper/current/main.tex
update figs, update text

@@
 
-In the case of flight itineraries, the embedding distance explains more than twice the expected flux between airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}a) than does geographic distance ($R^{2} = 0.22$), which has traditionally been used to quantify distance for the gravity model.
-Also, the embedding distance produces better predictions of actual flux between airports than does the geographic distance (Fig.~\ref{fig:gravity_performance}b).
-In the case of Korean accommodation reservations, embedding distance better explains the expected flux ($R^{2} = 0.57$, Fig.~\ref{fig:gravity_performance}c) than does geographic distance ($R^{2} = 0.25$), and predictions made using the embedding distance outperform those made with geographic distance (Fig.~\ref{fig:gravity_performance}d).
+In the case of flight itineraries, the embedding distance explains more than twice the expected flux between airports ($R^{2} = 0.51$, Fig.~\ref{fig:gravity_performance}b) than does geographic distance ($R^{2} = 0.22$), which has traditionally been used to quantify distance for the gravity model.
+Also, the embedding distance produces better predictions of actual flux between airports than does the geographic distance (Fig.~\ref{fig:gravity_performance}c).
+In the case of Korean accommodation reservations, embedding distance better explains the expected flux ($R^{2} = 0.57$, Fig.~\ref{fig:gravity_performance}d) than does geographic distance ($R^{2} = 0.25$), and predictions made using the embedding distance outperform those made with geographic distance (Fig.~\ref{fig:gravity_performance}e).
 This performance is consistent in the case of scientific mobility:
-the embedding distance explains more than twice the expected flux ($R^{2} = 0.48$, Fig.~\ref{fig:gravity_performance}e) than does the geographic distance ($R^{2} = 0.22$), and predictions made using the embedding distance outperform those using the geographic distance (Fig.~\ref{fig:gravity_performance}f).
+the embedding distance explains more than twice the expected flux ($R^{2} = 0.48$, Fig.~\ref{fig:gravity_performance}f) than does the geographic distance ($R^{2} = 0.22$), and predictions made using the embedding distance outperform those using the geographic distance (Fig.~\ref{fig:gravity_performance}g).
 These patterns hold for the subsets of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d).
@@
 	\centering
-	\includegraphics[width=0.9\textwidth]{\figdir/GravityLawFig/gravity_performance_new.pdf}
+	\includegraphics[width=0.9\textwidth]{\figdir/GravityLawFig/gravity_performance_revised.pdf}
 	\caption{
-		\textbf{Embedding distance encodes functional distance that fits the gravity model of mobility best across three distinct human trajectory datasets. }
+		\textbf{Neural embedding provides functional distance that improves predictive power of the gravity model of mobility best across three distinct human trajectory datasets. }
 		\textbf{a.} A unique identifier is assigned to each organization and they are assembled into an affiliation trajectory ordered by year of publication (top).
 If an author lists multiple organization affiliations within the same year,  we shuffle the order within that year in each training iteration (bottom, see \SI).
-		\textbf{b.} Neural embeddings outperform baselines for scientific mobility.
-The correlation between the flux and baseline distances $R^{2}$ (left), and the  root-mean-squared error between the actual and predicted values (right).
-The asterisk indicates the top-performing method.
-		\textbf{c.} Embedding distance (top) better explains the expected flux of passengers between U.S. airports than does geographic distance (bottom).
+		\textbf{b.} Embedding distance (top) better explains the expected flux of passengers between U.S. airports than does geographic distance (bottom).
 		The red line is the line of the best fit.
-		%Black dots are mean flux across binned distances.
+		Black dots are mean flux across binned distances.
 		99\% confidence intervals are plotted for the mean flux in each bin.
 		Correlation is calculated on the data in the log-log scale ($p < 0.0001$ across all fits).
-		%The lightness of each hex bin indicates the frequency of organization pairs within it.
-		\textbf{d.} Predictions of flux between airport pairs made using embedding distance (top) outperform those made using geographic distance (bottom).
+		The lightness of each hex bin indicates the frequency of organization pairs within it.
+		\textbf{c.} Predictions of flux between airport pairs made using embedding distance (top) outperform those made using geographic distance (bottom).
 		Box-plots show the distribution of actual flux for binned values of predicted flux.
@@
 		``RMSE'' is the root-mean-squared error between the actual and predicted values.
-	Embedding distance consistently produce powerful functional distance for Korean accommodation reservations (\textbf{e,f}), and global scientific mobility (\textbf{g,h})}
+	Embedding distance consistently produce powerful functional distance for Korean accommodation reservations (\textbf{d,e}), and global scientific mobility (\textbf{f,g})}
 	\label{fig:gravity_performance}
@@
 
-The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized Page Rank scores calculated from the underlying mobility network (Fig.~\ref{fig:gravity_performance}b, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
-The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurrence matrix, Levy's symmetric \textit{word2vec}\autocite{levy2014neural}, and even direct optimization of the gravity model (Fig.\ref{fig:gravity_performance}b and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+The embedding distance also out-performs alternative diffusion-based network distance measures including the personalized Page Rank scores calculated from the underlying mobility network (Fig.~\ref{fig:supp:distancemetrics}, Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}).
+The embedding distance derived from neural embedding also explains more of the flux and better predicts mobility flows than simpler embedding baselines, such as distances derived from a singular-value decomposition and a Laplacian Eigenmap embedding~\autocite{belkin2003laplacian} of the underlying location co-occurrence matrix, Levy's symmetric \textit{word2vec}\autocite{levy2014neural}, and even direct optimization of the gravity model (Fig.\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
 In sum, our results demonstrate that, consistently and efficiently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
@@
 In practice, because we only have limited amounts of noisy data and the optimization may not find the true optimum, the mathematical result may only approximately hold.
-Indeed, we find that the in- and out-vectors tend to be different and that the cosine similarity tends to better capture real-world mobility than the dot similarity.
-This result echos other applications of word embedding, such as word analogy testing~\autocite{levy2015improving}, in which cosine distance also outperformed dot similarity.
-Nevertheless, a model with dot similarity has the second-best performance after cosine similarity (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and the embedding distance still outperforms all alternatives we considered.
+Indeed, we find that the in- and out-vectors tend to be different and that the cosine similarity tends to better capture real-world mobility than the inner product similarity.
+This result echos other applications of word embedding, such as word analogy testing~\autocite{levy2015improving}, in which cosine distance also outperformed the inner product similarity.
+Nevertheless, a model with the inner product similarity has the second-best performance after cosine similarity (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}), and the embedding distance still outperforms all alternatives we considered.
 

### 2021-11-08 paper/current/main.tex
minor changes

@@
 	Historically, mobility was constrained by geographic distance, however, in the globalizing world, language, culture, and history are increasingly important.
-	Here, we show a mathematical equivalence between \textit{word2vec} model and the gravity model of mobility and demonstrate that, by using three human trajectory datasets, \textit{word2vec} encodes nuanced relationships between locations into an accurate and meaningful vector-space, providing a functional distance between locations, as well as a representation for studying the many dimensions of mobility.
+	Here, we show a mathematical equivalence between \textit{word2vec} model and the gravity model of mobility and demonstrate that, by using three human trajectory datasets, \textit{word2vec} encodes nuanced relationships between locations into a systematic and meaningful vector-space, providing a functional distance between locations, as well as a representation for studying the many dimensions of mobility.
 	Focusing on the case of scientific mobility, we show that embeddings implicitly learn cultural, linguistic, and hierarchical relationships at multiple levels of granularity.
@@
 We then empirically test the resulting representation by its ability to derive from mobility trajectories the functional distances between locations.
-After validating that it accurately represents real-world data, we leverage unique embedding-based methods to demonstrate \textit{word2vec}'s capacity for encoding rich information relating to geography, culture, language, and even prestige, at multiple scales of analysis.
+After validating that it coherently represents real-world data, we leverage unique embedding-based methods to demonstrate \textit{word2vec}'s capacity for encoding rich information relating to geography, culture, language, and even prestige, at multiple scales of analysis.
 We embed trajectories from three datasets: U.S.
@@
 When applied to the trajectory data, each location is encoded into a single vector representation, and vectors relate to one another based on the likelihood of locations appearing adjacent to one another in the same trajectory.
-Also,  \textit{word2vec} can be intepreted as a metric recovery, which recover the underlying metric of the semantic manifold ~\autocite{hashimoto2016word}.
+Also,  \textit{word2vec} can be intepreted as a metric recovery, which recovers the underlying metric of the semantic manifold ~\autocite{hashimoto2016word}.
 
-Our study builds on the gravity model framework~\autocite{zipf1946gravity}.
-This is a widely-used, fundamental mobility model~\autocite{curiel2018citygravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity} that connects the \textit{expected flux}, $\hat{T}_{ij}$, between locations based on their populations and distance:
+Our study builds on the gravity model framework~\autocite{zipf1946gravity}, widely-used, fundamental mobility model~\autocite{curiel2018citygravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity} that connects the \textit{expected flux}, $\hat{T}_{ij}$, between locations based on their populations and distance:
 
@@
 Traditionally, the decay function has been defined in terms of geographic distance, due to its intuitiveness and availability.
-Here, we also consider the \textit{embedding distance}, calculated as the cosine distance between location vectors modeled by \textit{word2vec}, to test the ability to encode the mobility data.
+Here, we also consider the \textit{embedding distance}, calculated as the cosine distance between location vectors modeled by \textit{word2vec}, to test the ability to encode the complex relationships in the mobility data.
 The decay function $f(r_{ij})$ defines the effect of distance, and different decay functions can model fundamentally different mechanisms \autocite{barthelemy2011spatial} such as the cost functions for a given distance and the spatial granularity of the observation.
@@
 
-To ensure that \textit{word2vec} learns an accurate representation of mobility that encodes meaningful functional distances, we devise an empirical validation task.
-Past studies have utilized a range of validating tasks for assessing the accuracy \textit{word2vec}, including analogy completion~\cite{mikolov2013word2vec} and human surveys~\cite{kozlowski2018geometry}, in the case of natural language, or link prediction, in the case of network embedding~\cite{perozzi2014deepwalk, grover2016node2vec}.
-Here, we expect that an accurate representation of the mobility data should provide a functional distance that better models the flux between institutions than does geographic distance, which is at present the most widely measure used in the gravity model.
+To ensure that \textit{word2vec} learns an systematic representation of mobility that encodes meaningful functional distances, we devise an empirical validation task.
+Past studies have utilized a range of validating tasks for assessing the accuracy \textit{word2vec}, including analogy completion~\autocite{mikolov2013word2vec} and human surveys~\autocite{kozlowski2018geometry}, in the case of natural language, or link prediction, in the case of network embedding~\autocite{perozzi2014deepwalk, grover2016node2vec}.
+Here, we expect that an extracted representation from the mobility data should provide a functional distance that better models the flux between institutions than does geographic distance, which is at present the most widely measure used in the gravity model.
 We test this notion using three human mobility datasets, showing that \textit{word2vec} consistently offers a better representation of actual mobility flows than geographic distance, as well as alternative network and direct optimization approaches.
@@
 Its unique strength stems from our discovery that \textit{word2vec} is equivalent to a gravity model, making it a natural and theoretically-grounded tool for modeling mobility.
-By virtue of this equivalency, \textit{word2vec} learns accurate representations of mobility across disparate domains, including U.S.
+By virtue of this equivalency, \textit{word2vec} learns systematic representations of mobility across disparate domains, including U.S.
 flight itineraries, Korean hotel accommodation reservations, and global scientific mobility.
@@
 First, the skip-gram \textit{word2vec} model does not leverage directionality, meaning that embedding will be less effective at capturing mobility for which directionality is critical.
-Future studies may consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality, as well as their correspondance to asymetric mobility models, such as the radiation model~\cite{simini2012universal}.
+Future studies may consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality, as well as their correspondance to asymetric mobility models, such as the radiation model~\autocite{simini2012universal}.
 Second, the neural embedding approach is most useful in cases of mobility between discrete geographic units such as between countries, cities, and businesses; this approach is less useful in the case of mobility between locations represented using geographic coordinates, such as in the modeling of animal movements.

### 2022-02-25 paper/current/main.tex
updated manuscript with revisions

--- 2021-10-28 paper/current/main.tex
@@
 	Historically, mobility was constrained by geographic distance, however, in the globalizing world, language, culture, and history are increasingly important.
-	Here, we show a mathematical equivalence between \textit{word2vec} model and the gravity model of mobility and demonstrate that, by using three human trajectory datasets, \textit{word2vec} encodes nuanced relationships between locations into an accurate and meaningful vector-space, providing a functional distance between locations, as well as a representation for studying the many dimensions of mobility.
-	Focusing on the case of scientific mobility, we show that embeddings implicitly learn cultural, linguistic, and hierarchical relationships at multiple levels of granularity.
+	Here, we show a mathematical equivalence between \textit{word2vec} model and the gravity model of mobility and demonstrate that, by using three datasets of human mobility trajectories, \textit{word2vec} encodes nuanced relationships between discrete locations into an accurate and meaningful vector-space, providing a functional distance between locations, as well as a representation for studying the many dimensions of mobility.
+	Focusing on the case of scientific mobility, we show that embeddings can learn implicit information directly from mobility data, such as cultural, linguistic, and hierarchical relationships at multiple levels of granularity.
 	Connecting neural embeddings to the gravity model opens up new avenues for the study of mobility.
@@
 
-We focus in most detail on scientific mobility due to its richness and importance.
+We demonstrate the applicability of \textit{word2vec} in representing real-world mobility data by focusing on the case of scientific mobility, which we select due to its richness and importance. 
 Scientific mobility---which is a central driver of the globalized scientific enterprise~\autocite{czaika2018globalisation, box2008competition} and strongly related to innovation~\autocite{braunerhjelm2020labor, kaiser2018innovation}, impact~\autocite{sugimoto2017mostimpact, petersen2018multiscale}, collaboration~\autocite{rodrigues2016mobility}, and the diffusion of knowledge~\autocite{braunerhjelm2020labor, morgan2018prestige}---is not only an important topic in the Science of Science but also ideal for our study thanks to its well-known structural properties such as the centrality of scientifically advanced countries and the strong prestige hierarchy~\autocite{clauset2015hierarchy, deville2014career}.
@@
 It works under the notion that a good representation should facilitate prediction, learning a mapping between words that can predict a target word based on its context (surrounding words).
-The model is also computationally efficient, easy to use, robust to noise, and can encode relations between entities as geometric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis, hashimoto2016word}.
+The model is also computationally efficient, robust to noise, and can encode relations between entities as geometric relationships in the vector space~\autocite{levy2014neural, nakandala2017gendered, kozlowski2018geometry, an2018semaxis, hashimoto2016word}.
 When applied to the trajectory data, each location is encoded into a single vector representation, and vectors relate to one another based on the likelihood of locations appearing adjacent to one another in the same trajectory.
-Also,  \textit{word2vec} can be intepreted as a metric recovery, which recover the underlying metric of the semantic manifold ~\autocite{hashimoto2016word}.
+Also, \textit{word2vec} can be interpreted as a kind of metric recovery, which recovers the underlying metric of the semantic manifold ~\autocite{hashimoto2016word}.
+Although more sophisticated embedding techniques have been built atop \textit{word2vec}~\autocite{devlin2018bert, pennington2014glove}, some even adapted towards mobility data~\autocite{pennington2014glove, zhai2019beyond,gao2018place2vec, bo2017place2vec, simini2021deep}, the standard \textit{word2vec} model remains a powerful technique for representing mobility data, owing to its intuitiveness, accessibility, and mathematical equivalence to the gravity model of mobility.
 
-Our study builds on the gravity model framework~\autocite{zipf1946gravity}.
-This is a widely-used, fundamental mobility model~\autocite{curiel2018citygravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity} that connects the \textit{expected flux}, $\hat{T}_{ij}$, between locations based on their populations and distance:
+The gravity model framework~\autocite{zipf1946gravity} is a widely-used, fundamental mobility model~\autocite{curiel2018citygravity, jung2008highwaygravity, hong2016busgravity, truscott2012epidemicgravity} that connects the \textit{expected flux}, $\hat{T}_{ij}$, between locations based on their populations and distance:
 
@@
 These patterns hold for the subsets of only domestic (within-country organization pairs, Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:gravity_correlation}c) and only international mobility flows (across-country organization pairs, Fig.~\ref{fig:supp:gravity_correlation}d).
+We also find that the embedding distance outperforms a generalized version of the gravity model, which incorporates information on shared geography and language alongside geographic distance (see \SI).
 
@@
 In sum, our results demonstrate that, consistently and efficiently, the embedding distance better captures patterns of actual mobility than does the geographic distance.
+The embedding distances also outperforms alternatives in terms of the common part of commuters measure~\autocite{sorensen1948method} (Fig.~\ref{fig:supp:cpc-performance})
 
@@
 
-\subsection*{Embeddings capture global structure of mobility}
+\subsection*{Embeddings capture the global structure of mobility}
 
-In the remainder of the paper, we focus on scientific mobility and interrogate the geometric space generated by the neural embedding to shed light on the multi-faceted relationships between organizations.
+In the remainder of the paper, we focus on scientific mobility as a case study to interrogate the geometric space generated by the neural embedding.
+In the process, we also shed light on the multi-faceted relationships between organizations.
 To explore the topological structure of the embedding, we use a topology-based dimensionality reduction method (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation of the embedding space (Fig.~\ref{fig:projection}a).
@@
 flight itineraries, Korean hotel accommodation reservations, and global scientific mobility.
-Focusing on the case of scientific mobility, we leverage the unique topological structure of the embedding space to reveal how it encodes nuanced aspects of mobility, including global and regional geography, shared languages, and prestige hierarchies, all of which are learned using only the mobility trajectories of individuals.
+Focusing on the case of scientific mobility, we leverage the unique topological structure of the embedding space to reveal how it encodes nuanced aspects of mobility, including global and regional geography, shared languages, and prestige hierarchies.
 
-In revealing the correspondence between neural embeddings and the gravity model, the study of human mobility can move beyond geographic and network-based models of mobility, and instead leverage the high-order structure from individuals' mobility trajectories using these robust and efficient methods.
-While we focus on three domains of human mobility, this approach could be applied to many different domains, such as animal migration, transit-network mobility, international trade, and more.
+In revealing the correspondence between neural embeddings and the gravity model, the study of human mobility can move beyond geographic and network-based models of mobility, and instead leverage the high-order structure directly from individuals' mobility trajectories using these robust and efficient methods.
+This correspondence supplies a much-needed theoretical justification for the application of neural embedding techniques towards mobility data, and contributes to a better understanding of neural embedding techniques.
+In addition to being intuitive, accessible, and theoretically grounded, the \textit{word2vec} approach outlined here also has the advantage of learning complex and implicit features of mobility directly from raw trajectory data, rather than exploiting \textit{a priori} location features~\cite{simini2021deep}.
+
+While we focus on three domains of human mobility and illustrate its potential using scientific mobility, this approach is general and can be applied to many different domains, such as animal migration, transit-network mobility, and international trade.
 Once learned, functional distances between locations, such as countries, cities, or organizations, or the embedding model itself, can be published to facilitate re-use, and support reproducibility and transparency in cases when the underlying data is too sensitive to make available.
 Moreover, this approach can be used to learn a functional distance even between entities for which no geographic analog exists, such as between occupational categories based on individuals' career trajectories.
-In addition to providing a functional distance that supports modeling and predicting mobility patterns, the topology of the embedding space is amenable to a range of unique applications for studying mobility.
+In addition to providing a functional distance that supports modeling and predicting mobility patterns, we also demonstrate how the the topology of the embedding space can be leveraged to facilitate interpretation and application of the complex features of mobility.
 As we have shown, the embedding space allows the visualization of the complex structure of scientific mobility at high resolution across multiple scales, providing a large and detailed map of the landscape of global scientific mobility.
 Other operations such as comparing entities or calculating aggregates, which could be complex and computationally-expensive for other methods, are here reduced to simple vector arithmetic.
-Embeddings also allows us to quantitatively explore abstract notions such as academic prestige, and can potentially be generalized to other abstract axes.
+Embeddings also allows us to quantitatively explore abstract relationships between locations, such as academic prestige, and can potentially be generalized to other abstract axes.
 Investigation of the structure of the embedding space, such as the vector norm, reveals universal patterns based on the organization's size and their vector norm that could be leveraged in future studies of mobility.
@@
 Traditional hubs of migration have experienced many politically-motivated policy changes that affect scientific mobility, such as travel restrictions in the U.S.
-and U.K.~\autocite{chinchilla2018travelban}.
-At the same time, other nations, such as China, are growing into major scientific powers and attractors of talent~\autocite{cao2020returning}.
+and U.K.~\autocite{chinchilla2018travelban}, whereas other countries, such as China, have risen as major attractors of international talent~\autocite{cao2020returning}.
 Unprecedented health crises such as the COVID-19 pandemic threaten to bring drastic global changes to migration by tightening borders and halting travel.

### 2022-03-15 paper/current/supp.tex

@@
 
-% S11 TEXT
+% S12 TEXT
 \paragraph*{S12 Text}
@@
 Russia, in contrast, has a number of organization vectors of moderate norms, but also several isolated organizations with large vector norms ($\bar{l} = 3.08$, $s = 0.67$).
+
+%
+% S15 TEXT
+\paragraph*{S15 Text}
+\label{si:text:generalized_gravity_model}
+{\bf Generalized gravity model.}
+
+Generalized gravity models use external information about each location to inform mobility predictions. 
+    Here, we test whether a generalized gravity model that includes information about shared city, region, nation, continent, and language alongside geographic distance offers better predictions than embedding distance.
+    We specify the generalized model as follows,
+    \begin{equation}
+      \log{\frac{T_{ij}}{M_iM_j}} =  \gamma \log{d_{ij}} +  \sum_{x} \alpha^{x}*{g_{ij}^x} +  \sum_{x} \beta^{x}*{l_{ij}^x} 
+   \end{equation}
+    where $g_{ij}^{x}, x \in [\text{city, region, nation, and continent}]$ is a dummy variable that is given a value of 1 when two organizations are located in the same geographic city, region, nation, or continent, respectively;
+    otherwise, dummy variable is zero.
+    Similarly, $l_{ij}^x,  x \in [\text{language, language family}]$ is an dummy variable that is set to 1 if two organizations are in countries that share the same language or language family, respectively.
+
+    Better results are obtained using the generalized gravity model ($R^2=0.242$, $RSME=0.861$, and $CPC=0.383$) compared to standard gravity model using only geographical distance ($R^2=0.219$, $RSME=0.874$, and $CPC=0.373$).
+    However, the gravity model using embedding distance results in the best performance by a wide margin ($R^2=0.482$, $RSME=0.711$, and $CPC=0.459$). 
+    These findings demonstrate how the embedding space can encode the complex and multi-faceted nature of mobility into a single robust vector-space representation, even without any external information provided.
 
@@
 %
+% Figure — CPC Measures
+% 
+\begin{figure}
+    \centering
+    \includegraphics{\figdir/Descriptive/sizeall_precedence_exp_global_cpc-measures_d300_ws1_gamma1.0.pdf}
+    \caption{\textbf{Embedding distance outperforms alternatives in common part of commuters (CPC).}
+    The CPC measure is calculated for both the power and exponential form of the gravity model, with the highest value reported for each distance type. 
+    }
+    \label{fig:supp:cpc-performance}
+\end{figure}
+
+%
 % Figure - Global Network Projection

### 2022-04-04 paper/current/main.tex
updated main text with rebuttal changes

@@
 \begin{document} %{{{
-\title{Unsupervised embedding of trajectories captures the latent structure of mobility} %{{{
+\title{Unsupervised embedding of trajectories captures the latent structure of discrete mobility.} %{{{
 \author[1,\Yinyang]{Dakota Murray}
@@
 Also, \textit{word2vec} can be interpreted as a kind of metric recovery, which recovers the underlying metric of the semantic manifold ~\autocite{hashimoto2016word}.
-Although more sophisticated embedding techniques have been built atop \textit{word2vec}~\autocite{devlin2018bert, pennington2014glove}, some even adapted towards mobility data~\autocite{pennington2014glove, zhai2019beyond,gao2018place2vec, bo2017place2vec, simini2021deep}, the standard \textit{word2vec} model remains a powerful technique for representing mobility data, owing to its intuitiveness, accessibility, and mathematical equivalence to the gravity model of mobility.
+Although word2vec has been developed into more sophisticated embedding techniques~\autocite{devlin2018bert, pennington2014glove}, some adapted towards mobility data~\autocite{pennington2014glove, zhai2019beyond,gao2018place2vec, bo2017place2vec, simini2021deep}, the standard word2vec remains a powerful model for representing mobility data, owing to its simplicity, intuitiveness, accessibility, and mathematical equivalence to the gravity model of mobility.
 
@@
 Although {\it word2vec} generates two embedding vectors $\bm{v_i}$ and $\bm{u}_i$---referred to as the in-vector and out-vector, respectively---we follow convention to use the in-vector $\bm{v}_i$ as an embedding of location $i$.
+Training {\it word2vec} is computationally expensive because of $Z_i$ that extends over all $|{\cal A}|$ locations.
 
-When $w=1$ (Fig.~\ref{fig:supp:hyperparameter}), the flow can be written as
+Negative sampling is a widely used heuristics to efficiently train {\it word2vec} without calculating $Z_i$.
+Negative sampling was introduced as a \textit{simplified} version of Noise Contrastive Estimation (NCE)~\autocite{mikolov2013word2vec,Gutmann2010}. 
+We show that this simplification gives rise to the equivalence between SGNS word2vec and the gravity model.
+
+NCE is a generic estimator for probability model~\autocite{Gutmann2010}
+\begin{align}
+	\label{eq:nce-model}
+	P_m(x) = \frac{ f(x) }{\sum_{ x' \in {\cal X}} f(x') },
+\end{align}
+where $f$ is a positive real-valued likelihood function of data $x$, and ${\cal X}$ is the set of all data.
+Note that word2vec belongs to this class of probability models, with $x=\vect{u}_i\cdot \vect{v}_j$ and $f(x)=\exp(x)$.
+To train {\it word2vec} with NCE~\autocite{mikolov2013word2vec}, one samples a center-context pair $(i,j)$ from the given data and labels the pair as $Y=1$. 
+Then, one replaces the context location $j$ with a random location $j'$ sampled from a noise distribution $p_0(j')$ and labels the pair as $Y=0$. 
+NCE finds the embedding that can classify the center-context pairs using a logistic function 
+\begin{align}
+	\label{eq:nce}
+	P^{\text{NCE}}\left(Y_{j}=1 \vert j\right) = \frac{
+		1
+	}{
+		1 + \exp\left[ - \ln f(\vect{u}_j \cdot \vect{v}_{i})  + \ln p_0(j) \right]
+	},
+\end{align}
+by maximizing the log-likelihood
+\begin{align}
+	\label{eq:log-likelihood-logistic-regress}
+	{\cal J}^{\text{NCE}} = \sum_{i \in {\cal A}}\sum_{j \in {\cal D}} \left[ Y_{j} \log P^{\text{NCE}}(Y_{j} = 1\vert j) + (1-Y_{j}) \log P^{\text{NCE}}(Y_{j} = 0 \vert j)\right].
+\end{align}
+Note that NCE is an unbiased estimator that has asymptomatic convergence to the optimal embedding in terms of the original word2vec's objective function, ${\cal J}$~\autocite{Chia2010,Dyer2014}.
+
+Negative sampling simplifies NCE by dropping $ \ln p_0(j)$ in the logistic function, i.e.,
+\begin{align}
+	\label{eq:logistic-regress}
+	P^{\text{NS}}(Y_{j} = 1; \vect{v}_{i}, \vect{u}_j) = \frac{1}{1 + \exp(-\vect{u}_j \cdot \vect{v}_{i})}.
+\end{align}
+Despite its innocuous appearance, this simplification produces substantial biases. 
+To see this, we rewrite $P^{\text{NS}}$ in form of $P^{\text{NCE}}$ as 
+\begin{align}
+	P^{NS}\left(Y_{j}=1 \vert j\right) & = \frac{
+		1
+	}{
+		1 + \exp\left[ - \left( \vect{u}_j \cdot \vect{v}_{i} + \ln p_0(j) + c \right) + \ln p_0(j) + c \right]
+	}                                             \\
+	                                   & = \frac{
+		1
+	}{
+		1 + \exp\left[ - \ln f(\vect{u}_j \cdot \vect{v}_{i}) + \ln p_0(j) + c \right]
+	},
+\end{align}
+where we define the likelihood function $f$ by
+\begin{align}
+	f(\vect{u}_j \cdot \vect{v}_{i}) = \exp\left( \vect{u}_j \cdot \vect{v}_{i} + \ln p_0(j) + c\right),
+\end{align}
+which is the unbiased estimator for the probability model
+\begin{align}
+	\label{eq:unbiasef}
+	P_m^{NS}(\vect{u}_j \cdot \vect{v}_{i}) & = \frac{ f(\vect{u}_j \cdot \vect{v}_{i}) }{\sum_{ j' \in {\cal A}} f(\vect{u}_{j'} \cdot \vect{v}_{i}) },                                                                                               \\
+	                                        & = \frac{  p_0(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{\sum_{j' \in \mathcal{A}}  p_0(j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})},                                                                      \\
+	                                        & = \frac{  P^\gamma(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{\sum_{j' \in \mathcal{A}}  P^\gamma(j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})} \hspace{0.3cm}(\because p_0(\ell) \propto P^\gamma (\ell)).
+\end{align}
+Taken together, the conditional probability that SGNS \textit{word2vec} actually optimizes is
+\begin{align}
+\label{eq:ns_gamma}
+	P^{NS}(j\given i) = P_m^{NS}(\vect{u}_j \cdot \vect{v}_{i})  =  \frac{  P^\gamma(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{Z'_i},
+\end{align}
+where $Z'_i=\sum_{j' \in \mathcal{A}}  P^\gamma(j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})$.
+Equation \eqref{eq:ns_gamma}  makes clear the bias due to negative sampling, i.e., 
+the noise distribution $p_0(j)=P^\gamma(j)$ appears in the numerator and, thus, is a part of the {\it word2vec} model.
+
+Armed with this result, we can now show the equivalence between the SGNS {\it word2vec} model and the gravity model.
+We set the window length to $w=1$ to restrict {\it word2vec} to predict the first-order flux $\hat T_{ij}$ between locations, as is the case for the gravity model.
+Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimal in-vectors and out-vectors such that $\vect{v}_i = \vect{u}_i$ \autocite{levy2014neural}.
+By setting $\gamma=1$,  we have 
 \begin{align}
 	\label{eq:flow_w2v}
-	\hat{T}_{ij} \propto P(i) P(j\given i) = \frac{P(i)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
+	\hat{T}_{ij} \propto P(i) P^{NS}(j\given i) \propto \frac{P(i)P(j)\exp(\bm{u}_j \cdot \bm{u}_{i})}{Z_i}.
 \end{align}
-where $P(j)$ is the fraction of location $j$'s frequency in the data.
-In general, calculating $Z_i$ is computationally expensive and there are two common approximations: hierarchical softmax \autocite{morin2005hierarchical} and negative sampling \autocite{mikolov2013word2vec}.
-Due to its simplicity and performance, negative sampling is the most widely used strategy, which we also adopt in our study.
-
-Although negative sampling is the most common approximation, it is a biased estimator~\autocite{Chia2010,Dyer2014} and fits a different probability model.
-When taking into account this bias, {\it word2vec} with skip-gram and negative sampling fits a probability model given by
-\begin{align}
-	P\left(j \given i \right):= \frac{P^ \gamma(j) \exp(\bm{u}_j \cdot \bm{v}_{i})}{Z'_i}, \label{eq:prob_w2v_ng0}
-\end{align}
-where we redefine the normalization constant as $Z'_i=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.
-(See the Methods and Supporting Information for the full derivation).
-
-Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimal in-vectors and out-vectors such that $\vect{v}_i = \vect{u}_i$ \autocite{levy2014neural}.
-Setting $\gamma = 1$ and substituting $\vect{v}_i = \vect{u}_i$ into Eq.~\ref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
-\begin{align}
-	\widehat{T}_{ij} \propto  N(i) P(j\given i) = \frac{NP(i)P(j)\exp(\vect{v}_j \cdot \vect{v}_{i})}{Z'_i}. \label{eq:flow_w2v_ng1}
-\end{align}
-where $N$ is the sum of frequencies in all locations and $N(i) = NP(i)$ is the frequency of location $i$ in the data.
-
 The flow $\widehat{T}_{ij}$ is symmetric (\ie $\widehat{T}_{ij}=\widehat{T}_{ji}$) because the skip-gram model neglects whether the context $j$ appears before or after the target $i$ in the trajectory.
-If we swap $i$ and $j$ in Eq.~\ref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
+If we swap $i$ and $j$ in Eq.~\eqref{eq:flow_w2v}, the numerator remains the same but the denominator can be different.
 Therefore, to ensure $\widehat{T}_{ij}=\widehat{T}_{ji}$, the denominator $Z_i$ should be a constant.
-
 Taken together, the {\it word2vec} model with the negative sampling predicts a flow in the same form as in the gravity model:
@@
 To ensure that \textit{word2vec} learns an accurate representation of mobility that encodes meaningful functional distances, we devise an empirical validation task.
-Past studies have utilized a range of validating tasks for assessing the accuracy \textit{word2vec}, including analogy completion~\cite{mikolov2013word2vec} and human surveys~\cite{kozlowski2018geometry}, in the case of natural language, or link prediction, in the case of network embedding~\cite{perozzi2014deepwalk, grover2016node2vec}.
+Past studies have utilized a range of validating tasks for assessing the accuracy of \textit{word2vec}, including analogy completion~\cite{mikolov2013word2vec} and human surveys~\cite{kozlowski2018geometry}, in the case of natural language, or link prediction, in the case of network embedding~\cite{perozzi2014deepwalk, grover2016node2vec}.
 Here, we expect that an accurate representation of the mobility data should provide a functional distance that better models the flux between institutions than does geographic distance, which is at present the most widely measure used in the gravity model.

### 2022-04-05 paper/current/main.tex

@@
 To explore the topological structure of the embedding, we use a topology-based dimensionality reduction method (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation of the embedding space (Fig.~\ref{fig:projection}a).
-By leveraging the unique characteristics of representation learning approach, we are able to show the relationships between individual organizations, rather than aggregates such as nations or cities, this projection constitutes the largest and highest resolution ``map'' of scientific mobility to date.
+By leveraging the unique characteristics of representation learning approach, we are able to show the relationships between individual organizations, rather than aggregates such as nations or cities, producing the largest and highest resolution ``map'' of scientific mobility to date.
 

### 2022-11-22 paper/current/main.tex

@@
 For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each case (Fig.~\ref{fig:supp:predict_geo_bymodel} and Fig.~\ref{fig:supp:predict_emb_bymodel}).
-Our results show that embedding distance deriving from the \textit{word2vec} significantly improves the ability to predict the mobility compare to geographical distance no matter decay function while providing the useful representation of locations as well (see Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
-However, we note that the geographic distance best models real-world mobility with the power-law decay function, likely resulting from the function's suitability for large, complex, and scale-free spatial systems~\autocite{chen2015distance};
-the embedding distance, in contrast, models our mobility data best for the exponential decay function, which stems from an underlying connection between the function and \textit{word2vec}.
+Our results show that embedding distance deriving from the \textit{word2vec} significantly improves the ability to predict the mobility compared to geographical distance, no matter the decay function, while providing the useful representation of locations as well (see Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}).
+However, we note that the geographic distance best models real-world mobility with the power-law decay function, likely resulting from the function's suitability for large, complex, and scale-free spatial systems~\autocite{chen2015distance}.
+The embedding distance, in contrast, models our mobility data best for the exponential decay function, which stems from an underlying connection between the function and \textit{word2vec}.
 
@@
 Therefore, to ensure $\widehat{T}_{ij}=\widehat{T}_{ji}$, the denominator $Z_i$ should be a constant.
-Taken together, the {\it word2vec} model with the negative sampling predicts a flow in the same form as in the gravity model:
+Taken together, the {\it word2vec} model with the negative sampling predicts a flow in the same form as the gravity model:
 \begin{align}
@@
 Past studies have utilized a range of validating tasks for assessing the accuracy of \textit{word2vec}, including analogy completion~\cite{mikolov2013word2vec} and human surveys~\cite{kozlowski2018geometry}, in the case of natural language, or link prediction, in the case of network embedding~\cite{perozzi2014deepwalk, grover2016node2vec}.
-Here, we expect that an accurate representation of the mobility data should provide a functional distance that better models the flux between institutions than does geographic distance, which is at present the most widely measure used in the gravity model.
-We test this notion using three human mobility datasets, showing that \textit{word2vec} consistently offers a better representation of actual mobility flows than geographic distance, as well as alternative network and direct optimization approaches.
+Here, we expect that an accurate representation of the mobility data should provide a functional distance that better models the flux between institutions than does geographic distance, which is at present the most widely used measure in the gravity model.
+We test this notion using three human mobility datasets, showing that \textit{word2vec} consistently offers a better representation of actual mobility flows than geographic distance, or alternative network and direct optimization approaches.
 
@@
 In the remainder of the paper, we focus on scientific mobility as a case study to interrogate the geometric space generated by the neural embedding.
-In the process, we also shed light on the multi-faceted relationships between organizations.
+In the process, we also shed light on the multi-faceted relationships between scientific organizations.
 To explore the topological structure of the embedding, we use a topology-based dimensionality reduction method (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation of the embedding space (Fig.~\ref{fig:projection}a).
@@
 The embedding space also allows us to \textit{zoom in} on subsets and re-project them to reveal local relationships.
-For example, re-projecting organizations located in Western, Southern, and Southeastern Asia with UMAP (Fig.~\ref{fig:projection}b) reveals a gradient of countries between Egypt and the Philippines that largely corresponds to geography, but with some exceptions seemingly stemming from cultural and religious similarity;
-Malaysia, with its official religion of Islam, is nearer to Middle Eastern countries in the embedding space than to many geographically-closer South Asian countries.
-We validate this finding quantitatively with the cosine distance between nations (the centroids of organizations vectors belonging to that country).
+For example, re-projecting organizations located in Western, Southern, and Southeastern Asia with UMAP (Fig.~\ref{fig:projection}b) reveals a gradient of countries between Egypt and the Philippines that largely corresponds to geography, but with some exceptions seemingly stemming from cultural and religious similarity.
+For example, Malaysia, with its official religion of Islam, is nearer to Middle Eastern countries in the embedding space than to many geographically-closer South Asian countries.
+We validate this finding quantitatively with the cosine distance between nations (the centroids of organizations vectors belonging to a given country).
 Malaysia is nearer to many Islamic countries such as Iraq ($d = 0.27$), Pakistan ($d = 0.32$), and Saudi Arabia ($d = 0.41$)  than neighboring but Buddhist Thailand ($d = 0.43$) and neighboring Singapore ($d = 0.48$).
@@
 The six identified clusters roughly correspond to countries in Asia and North America (orange), Northern Europe (dark blue), the British Commonwealth and Iran (purple), Central and Eastern Europe (light blue), South America and Iberia (dark green), and Western Europe and the Mediterranean (light green).
-The cluster structure shows that not only geography but also linguistic ties and cultural between countries are related to scientific mobility.
+The cluster structure shows that not only geography but also linguistic and cultural ties between countries are related to scientific mobility.
 
-We quantify the relative importance of geography (by region), and language (by the most widely-spoken language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering and disjoint clustering (geography, language...) at the different level of hierarchy by explicitly adjusting a scaling parameter $r$, acting like a \textit{zooming lens}.
+We quantify the relative importance of geography (by region), and language (by the most widely-spoken language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering and disjoint clustering (geography, language...) at the different levels of hierarchy by explicitly adjusting a scaling parameter $r$, acting like a \textit{zooming lens}.
 If $r$ is high, the similarity is based on the lower levels of the dendrogram, whereas when $r$ is low, the similarity is based on higher levels.
@@
 The embedding space can also encode more fine-grained relationships between entities.
-For examples, prestige hierarchies are known to underpin the dynamics of scientific mobility, in which researchers tend to move to similar or less prestigious organizations~\autocite{deville2014career, clauset2015hierarchy}.
+For example, prestige hierarchies, in which researchers tend to move to similar or less prestigious organizations~\autocite{deville2014career, clauset2015hierarchy}, are known to underpin the dynamics of scientific mobility.
 Could the embedding space, to which no explicit prestige information is given, encode a prestige hierarchy?
 This question is tested by exploiting the geometric properties of the embedding space with SemAxis~\autocite{an2018semaxis}.
-Here, we use SemAxis to operationalize the abstract notion of academic prestige, defining an axis in the embedding space where poles are defined using known high- and low-ranked universities.
-As an external proxy of prestige, we use the Times Ranking of World Universities (we also use research impact from the Leiden Ranking~\autocite{waltman2012leidenrankings}, see \SI);
-the high-rank pole is defined as the average vector of the top five U.S.
+Here, we use SemAxis to operationalize the abstract notion of academic prestige, defining an axis in the embedding space are defined using known high- and low-ranked universities as poles.
+We use the Times Ranking of World Universities as an external proxy for prestige (we also use research impact from the Leiden Ranking~\autocite{waltman2012leidenrankings}, see \SI),
+The high-rank pole is defined as the average vector of the top five U.S.
 universities according to the rankings, whereas the low-rank pole is defined using the five bottom-ranked (geographically-matched by U.S.
@@
 
-The embedding space encodes the prestige hierarchy of U.S. universities that are coherent with real-world university rankings.
+The embedding space encodes the prestige hierarchy of U.S. universities that is coherent with real-world university rankings.
 The embedding-based ranking is strongly correlated with the Times ranking (Spearman's $\rho = 0.73$, Fig.~\ref{fig:semaxis}a).
@@
 The strongest outliers that were ranked more highly in the Times ranking than in the embedding-based ranking tend to be large state universities such as Arizona State University and the University of Florida.
-Those ranked higher in the embedding-based ranking tend to be relatively-small universities near major urban areas such as the University of San Francisco and the University of Maryland Baltimore County, possibly reflecting exchanges of scholars with nearby high-ranked institutions at these locations.
+Those ranked higher in the embedding-based ranking tend to be relatively-small universities near major urban areas such as the University of San Francisco and the University of Maryland Baltimore County, possibly reflecting exchanges of scholars with nearby highly-ranked institutions at these locations.
 In sum, our results suggest that the embedding space is capable of capturing information about academic prestige, even when the representation is learned using data without explicit information on the direction of mobility (as in other formal models~\autocite{clauset2015hierarchy}), or prestige.
@@
 Neural embedding approaches offer a novel, data-driven solution for efficiently learning an effective and robust representation of locations based on trajectory data, encoding the complex and multi-faceted nature of mobility.
-Its unique strength stems from our discovery that \textit{word2vec} is equivalent to a gravity model, making it a natural and theoretically-grounded tool for modeling mobility.
+We discovered that the unique strength of \textit{word2vec} stems from its equivalency to a gravity model, making it a natural and theoretically-grounded tool for modeling mobility.
 By virtue of this equivalency, \textit{word2vec} learns accurate representations of mobility across disparate domains, including U.S.
@@
 While we focus on three domains of human mobility and illustrate its potential using scientific mobility, this approach is general and can be applied to many different domains, such as animal migration, transit-network mobility, and international trade.
-Once learned, functional distances between locations, such as countries, cities, or organizations, or the embedding model itself, can be published to facilitate re-use, and support reproducibility and transparency in cases when the underlying data is too sensitive to make available.
+Once learned, functional distances between locations, such as countries, cities, or organizations, or the embedding model itself, can be published to facilitate re-use, and support reproducibility and transparency in cases when the underlying data is too sensitive to be made available.
 Moreover, this approach can be used to learn a functional distance even between entities for which no geographic analog exists, such as between occupational categories based on individuals' career trajectories.
-In addition to providing a functional distance that supports modeling and predicting mobility patterns, we also demonstrate how the the topology of the embedding space can be leveraged to facilitate interpretation and application of the complex features of mobility.
+In addition to providing a functional distance that supports modeling and predicting mobility patterns, we also demonstrate how the topology of the embedding space can be leveraged to facilitate interpretation and application of the complex features of mobility.
 As we have shown, the embedding space allows the visualization of the complex structure of scientific mobility at high resolution across multiple scales, providing a large and detailed map of the landscape of global scientific mobility.
-Other operations such as comparing entities or calculating aggregates, which could be complex and computationally-expensive for other methods, are here reduced to simple vector arithmetic.
-Embeddings also allows us to quantitatively explore abstract relationships between locations, such as academic prestige, and can potentially be generalized to other abstract axes.
+Other operations such as comparing entities or calculating aggregates, which could be complex and computationally expensive for other methods, are here reduced to simple vector arithmetic.
+Embeddings also allow us to quantitatively explore abstract relationships between locations, such as academic prestige, and can potentially be generalized to other abstract axes.
 Investigation of the structure of the embedding space, such as the vector norm, reveals universal patterns based on the organization's size and their vector norm that could be leveraged in future studies of mobility.
@@
 We embed trajectories by treating them analogously to sentences and locations analogously to words.
-For U.S. airport itinerary, trajectories are formed from the flight itineraries of individual passenger, in which airports correspond to unique identifiers.
+For U.S. airport itinerary data, trajectories are formed from the flight itineraries of individual passengers, in which airports correspond to unique identifiers.
 In the case of Korean accommodation reservations, trajectories comprise a sequence of accommodations reserved over a customer's history.
-For scientific mobility, an``affiliation trajectories'' is constructed for each mobile author, which is built by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:gravity_performance}a (top).
+For scientific mobility, an ``affiliation trajectory'' is constructed for each mobile author, which is built by concatenating together their ordered list of unique organization identifiers, as demonstrated in Fig.~\ref{fig:gravity_performance}a (top).
 In more complex cases, such as listing multiple affiliations on the same paper or publishing with different affiliations on multiple publications in the same year, the order is randomized within that year, as shown in Fig.~\ref{fig:gravity_performance}a (bottom).
@@
 
-To mitigate the effect of less common locations, we set $f_{\min} = 50$, limiting to locations appearing at least 50 times across the training trajectories;
-744 unique airport for U.S.
-airport itinerary, 1004 unique accommodations for Korean accommodation reservation data, and 6,580 unique organizations for scientific mobility appear in the resulting embedding.
+To mitigate the effect of less common locations, we set $f_{\min} = 50$, limiting to locations appearing at least 50 times across the training trajectories, resulting in embeddings reflecting 744 unique airports for the U.S.
+airport itinerary data, 1,004 unique accommodations for Korean accommodation reservation data, and 6,580 unique organizations for the scientific mobility data.
 We set $\alpha$ to its default value of 0.025 and iterate five times over all training trajectories.
@@
 by calculating the gradients for embedding vectors $\vect{u}_j$, $\vect{v}_{i}$ and iteratively updating them (see Supporting Information for full derivation).
-Note that NCE is an unbiased estimator that has convergence to the optimal embedding in terms of the original word2vec's objective function, ${\cal J}$~\autocite{Chia2010,Dyer2014} if we increase the number of words to sample and the training iterations.
+Note that NCE is an unbiased estimator that has convergence to the optimal embedding in terms of the original \textit{word2vec's} objective function, ${\cal J}$~\autocite{Chia2010,Dyer2014} if we increase the number of words to sample and the training iterations.
 
@@
 %% Distance calculations
-We calculate $T_{ij}$ as the total number of co-occurrence between two locations $i$ and $j$ across the data-set.
-In scientific mobility, $T_{ij} = 10$ indicates that the number of co-occurrence between both organization $i$ and $j$ between 2008 and 2019 is 10, as evidenced from their publications.
+We calculate $T_{ij}$ as the total number of co-occurrences between two locations $i$ and $j$ across the data-set.
+In scientific mobility, $T_{ij} = 10$ indicates that the number of co-occurrences between both organization $i$ and $j$ between 2008 and 2019 is 10, as evidenced from their publications.
 Here, we treat $T_{ij} = T_{ji}$ for the sake of simplicity and, in the case of scientific mobility, because directionality cannot easily be derived from bibliometric records, or may not be particularly informative (see \SI).
@@
 Nevertheless, cosine distance is often shown to be useful in practice~\autocite{lerman2007embedding, brown1970migration, kim2018functional}.
-We compare the performance of this cosine-based embedding distance against those derived using inner product similarity and euclidean distance.
+We compare the performance of this cosine-based embedding distance against those derived using inner product similarity and Euclidean distance.
 
@@
 \end{equation}
-where $m_{i}$ and $m_{j}$ are the population of locations, defined as the total number of passenger who passed through each airport for U.S.
-airport itineraries,  the total number of customer who booked with each accommodation for Korean accommodation reservations, and the yearly-average count of unique authors, both mobile and non-mobile, affiliated with each organization for scientific mobility.
+where $m_{i}$ and $m_{j}$ are the population of locations, defined as the total number of passengers who passed through each airport for U.S.
+airport itineraries,  the total number of customers who booked with each accommodation for Korean accommodation reservations, and the yearly-average count of unique authors, both mobile and non-mobile, affiliated with each organization for scientific mobility.
 $f(r_{ij})$ is a decay function of distance $r_{ij}$ between locations $i$ and $j$.
@@
 
-We consider separate variants of $f(r_{ij})$ for the geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$, report the best-fit model of each distance.
+We consider separate variants of $f(r_{ij})$ for the geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$, and report the best-fit model of each distance.
 For the geographic distance, we use the power-law function of the gravity law, $f(g_{ij})= g^{-\alpha}_{ij}$ (Eq.~\ref{eq:linear_flux_geo}).
@@
 The gravity law of mobility is sensitive to $T_{ij} = 0$, or zero movement between locations.
-In our dataset, non-zero flows account for only 4.2 \% of all possible pairs of the 6,580 organizations for scientific mobility, while 76.4\% of all possible pairs of the 744 airports for U.S.
-airport Itinerary and 62.5 \% of all possible pairs of the 1,004 accommodations for Korean accommodation reservation data.
+In our dataset, non-zero flows account for only 4.2 \% of all possible pairs of the 6,580 organizations for scientific mobility, 76.4\% of all possible pairs of the 744 airports for U.S.
+airport itinerary data, and 62.5 \% of all possible pairs of the 1,004 accommodations for Korean accommodation reservation data.
 This value is comparable to other common applications of the gravity law, such as phone calls, commuting, and migration \autocite{simini2012universal}.
@@
 \subsection*{SemAxis}
-SemAxis and similar studies~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} demonstrated that ``semantic axes'' can be found from an embedding space by defining the ``poles'' and the latent semantic relationship along the semantic axis can be extracted with simple arithmetic.
+SemAxis and similar studies~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} demonstrated that ``semantic axes'' can be found from an embedding space by defining the ``poles'' and that the latent semantic relationship along the semantic axis can be extracted with simple arithmetic.
 In the case of natural language, the poles of the axis could be ``good'' and ``bad'', ``surprising'' and ``unsurprising'', or ``masculine'' and ``feminine''.

### 2022-11-22 paper/current/supp.tex

@@
 As scholars move, they bring their knowledge, skills, and social connections with them---collectively the movements of researchers shape the structure and direction of the global scientific enterprise.
-For example, prestige-driven mobility between doctoral-granting and employing institution is highly unequal~\autocite{clauset2015hierarchy, deville2014career}, which affects the diffusion of ideas across academia~\autocite{morgan2018prestige}.
+For example, prestige-driven mobility between doctoral-granting and employing institutions is highly unequal~\autocite{clauset2015hierarchy, deville2014career}, which affects the diffusion of ideas across academia~\autocite{morgan2018prestige}.
 By placing researchers in new social settings, mobility can lead to the formation of new collaborative relationships~\autocite{rodrigues2016mobility}, which in turn spurs the further diffusion of knowledge and innovations~\autocite{braunerhjelm2020labor, azoulay2011diffusion, kaiser2018innovation, armano2017innovation}.
@@
 At the national level, the understanding of mobility has progressed beyond simplistic narratives of brain drain and brain gain, and instead adopts a new perspective of \textit{flows} of talent~\autocite{meyer2001network, ioannidis2014braindrain, gaillard1998circulation}.
-Under this flow model, a mobile researcher is viewed as contributing to both their origin and destination countries, a perspective that fosters that is evidenced by the strong science of open countries~\autocite{wagner2017open}.
+Under this flow model, a mobile researcher is viewed as contributing to both their origin and destination countries, a perspective that highlights the benefits of mobility to both the origin and destination countries.
 Perhaps because of these individual and national benefits, policy-makers have come to recognize the importance of global mobility~\autocite{box2008competition, oecd2010innovation}.
-Movement is a key mechanism that has clear impacts on the composition and direction of the global scientific workforce and our collective scientific understanding.
+Movement is a key mechanism that has clear impact on the composition and direction of the global scientific workforce and our collective scientific understanding.
 Understanding the structure and dynamics of mobility is thus essential for understanding global science.
@@
 
-There are many ways of modeling scientific mobility from bibliographic data, the first consideration being the unit of analysis.
+Modeling scientific mobility requires many considerations. 
+First, the unit of analysis must be set. 
 Most studies of mobility have focused on \textit{country-level} mobility--the flows of researchers across nations~\autocite{sugimoto2017mostimpact, scellato2015migrant, robinson-garcia2018indicators, franzoni2012foreign-born}.
 Practically, country-level analyses benefit from higher reliability, such that idiosyncrasies and errors inherent to bibliographic databases are mitigated by this higher level of aggregation.
-Epistemically, country-level analysis is useful for national science governance who aims to understand the status of their country in the global landscape and make informed policy decisions.
-Analyses at lower levels of analysis are far less common.
+Epistemically, country-level analysis is useful for national science governance which aims to understand the status of their country in the global landscape and make informed policy decisions.
+Analyses at lower units of analysis are far less common.
 \textit{Regional}-level scientific mobility--the flow of researchers between regions or cities within or across countries has been only minimally studied~\autocite{vaccario2019mobility}, possibly due to lack of reliable long-term data and lack of policy relevance to national-level lawmakers.
 \textit{Organization}-level mobility has the potential to inform institutional policy and to understand the composition of mobility within a single country or region, especially as it relates to organization performance, prestige, and inequality~\autocite{albarran2017topeconomic, deville2014career, morgan2018prestige, clauset2015hierarchy}.
-However, affiliation disambiguation and noise in bibliometric data makes large-scale organization-level analysis challenging.
+However, affiliation disambiguation and noise in bibliographic data makes large-scale organization-level analysis challenging.
 Here, we learn neural-network embeddings of scientific mobility at the level of organizations using a curated bibliographic database.
-These embeddings are robust to noise, and so are capable of representing clear structure even amid issues with organizational disambiguation.
+These embeddings are robust to noise, and so are capable of representing clear structure despite issues with organizational disambiguation.
 In doing so, embeddings also capture a more detailed understanding of mobility than has been previously studied.
@@
 However, scientific mobility is more complicated.
-For example, scientists often hold multiple affiliations at a time~\autocite{markova2016synchronous}, listing them as co-affiliations on a single paper, or even choosing a subset of affiliations to use fohabeultiple simultaneous projects~\autocite{robinson2019mobility}.
+For example, scientists often hold multiple affiliations at a time~\autocite{markova2016synchronous}, listing them as co-affiliations on a single paper, or even choosing a subset of affiliations to use across multiple simultaneous projects~\autocite{robinson2019mobility}.
 Even clearly-directional migration to another institution is complex--researchers may continue to publish with an old affiliation for projects that began before their move, and they may maintain social and organizational links to their old institution (e.g., collaborators, projects, graduate students) such that there is no clear breakage after migrating.
@@
 Due to the complexity of scientific mobility, we make the simplifying assumption that all scientific mobility is \textit{symmetric} or without direction such that any move from an organization $A$ to organization $B$ is equivalent to a move from $B$ to $A$.
-By assuming non-directional mobility, all mobility events are commensurate, meaning that they can be treated identically in our analysis--this allows us to represent the complexity of mobility without making decisions about the directional of their mobility or which is their main affiliation.
+By assuming non-directional mobility, all mobility events are commensurate, meaning that they can be treated identically in our analysis--this allows us to represent the complexity of mobility without making decisions regarding the directionality of researchers' mobility or main affiliation.
 Moreover, this assumption has the practical advantage of matching the data format expected by the \textit{word2vec} model, as well as the theoretical advantage of adhering to the symmetricity assumption of the gravity model of mobility.
@@
 For example, an author who published with affiliation $A$ in $t_{0}$, and affiliations $B$ and $C$ in $t_{1}$ could appear as one of $(A, B, C)$ or $(A, C, B)$ in each training iteration.
-This effectively removes the effect of order within a year, as the order cannot be meaningfully established based on co-affiliations in a single paper, or on different affiliations listed on separate papers, for which its date of publication may not be representative of the actual completion of the project.
+This effectively removes the effect of order within a year, as the order cannot be meaningfully established based on co-affiliations in a single paper, or on different affiliations listed on separate papers, for which the date of publication may not be representative of the actual completion of the project.
 
 Other than restricting to only mobile researchers, we do not perform any filtering or reductions to affiliation trajectories.
-In the case than an author publishes with organization $A$ four times in $t_{0}$, and affiliation $B$ two times in $t_{1}$, then their trajectory will be $(A, A, A, A, B, B)$.
+In the case that an author publishes with organization $A$ four times in $t_{0}$, and affiliation $B$ two times in $t_{1}$,  their trajectory will be $(A, A, A, A, B, B)$.
 Although mobile authors who publish more papers will have longer trajectories, \textit{word2vec} will skip duplicate consecutive organization IDs, mitigating the impact of long repetitive trajectories.
@@
 \label{si:text:ppr_dist}
-{\bf Network-based personalized page rank distances.}
+{\bf Network-based personalized Page Rank distances.}
 
@@
 The Personalized Page Rank is a ranking algorithm for nodes based on a random walk process on networks.
-The walker visiting at a node moves to a neighboring node chosen randomly with a probability proportionally to the weight of the edge in one step.
+At each step, the walker visiting a node moves to a neighboring node chosen randomly with a probability proportional to the weight of the edge.
 Furthermore, with probability $\alpha$, the walker is teleported back to the starting node.
@@
 \end{equation}
-where $v_i$ is a column vector of length $N$ with entries that are all zero except the $i$th entry that equals to one, $W = (W_{ij})$ is the weighted transition matrix of the unbiased random walker.
+where $v_i$ is a column vector of length $N$ with entries that are all zero except the $i$th entry that equals one, $W = (W_{ij})$ is the weighted transition matrix of the unbiased random walker.
 We used $\alpha=0.9$ here.
 
- We can think $p_i$ as a representation vector of the organization $i$, and calculate the distance between organizations $i$ and $j$, $d_{ij}$ with measuring distance between $p_i$ and $p_j$ to examine the gravity law.
+We can think of $p_i$ as a representation vector of the organization $i$, and calculate the distance between organizations $i$ and $j$, $d_{ij}$, with measuring distance between $p_i$ and $p_j$ to examine the gravity law.
 We consider two distance measures in this analysis.
 The first one is cosine distance which is used for our embedding method, $d_{ij} = 1 - \frac{\bm{p}_{i} \cdot \bm{p}_{j}}{\lVert \bm{p}_{i} \rVert \lVert \bm{p}_{j} \rVert}$.
-Also, if we think $p_i$ as a discrete probability distribution, then we can consider Jensen–Shannon divergence (JSD), can be written as,
+Also, if we think of $p_i$ as a discrete probability distribution, then we can consider Jensen–Shannon divergence (JSD), which can be written as,
 
@@
 In both cases, the performance is under the performance of the model with geographical distance.
-Even though the length of the PPR vectors is extremely larger than the length of our embedding vectors, result with the embedding distance outperforms both of them.
+Even though the length of the PPR vectors is much larger than the length of our embedding vectors, the result with the embedding distance outperforms both of them.
 
@@
 
-We calculate distance between organizations in the SVD embedding space using cosine distance, finding that it explains slighly more of the flux between organizations than does geographic distance ($R^2=0.247$, Table~\ref{supp:table:r2_table}).
+We calculate the distance between organizations in the SVD embedding space using cosine distance, finding that it explains slighly more of the flux between organizations than geographic distance ($R^2=0.247$, Table~\ref{supp:table:r2_table}).
 When used as an input to the gravity model, this distance produces better predictions than geographic distance using both the exponential (RMSE $= 0.859$, Table~\ref{supp:table:rmse_exp_table}) and power-law models (RMSE $= 0.839$, Table~\ref{supp:table:rmse_exp_table}), performing slightly better with the power-law formulation.
@@
 
-We also compare the \textit{word2vec} embedding distnace against a baseline of direct matrix factorization approach, using the symmetric SVD  \textit{word2vec} method~\autocite{levy2014neural}.
-Based on idea of \textit{word2vec} is just implicit matrix factorization, Levy proposed symmetric SVD \textit{word2vec} embedding, which should directly compute the embedding that \textit{word2vec} only attempts to efficiently approximate.
-First, we construct the matrix of $N$ organization
+We also compare the \textit{word2vec} embedding distance against a baseline of direct matrix factorization approach, using the symmetric SVD  \textit{word2vec} method~\autocite{levy2014neural}.
+Based on notion that \textit{word2vec} is equivalent to implicit matrix factorization, Levy proposed symmetric SVD \textit{word2vec} embedding, which should directly compute the embedding that \textit{word2vec} only attempts to efficiently approximate.
+First, we construct the matrix of $N$ organizations
 
@@
 \end{equation}
-where $N(i,j)$ is the number of times the location pair $(i,j)$ appears given the window size $w$ in the total corpus $D$ ,$N(i)=\sum_{j=N}^i N(i,j)$ as the number of items $i$ occurred given the window size $w$ in $D$, and k is the number of negative samples.
-We used $w=1$ and $k=5$ which is same setting in the our main result.
+where $N(i,j)$ is the number of times the location pair $(i,j)$ appears given the window size $w$ in the total corpus $D$, $N(i)=\sum_{j=N}^i N(i,j)$ as the number of items $i$ occurred given the window size $w$ in $D$, and $k$ is the number of negative samples.
+We used $w=1$ and $k=5$ which is the same setting as in our main result.
 Then, we factorized matrix $M$ with truncated singular value decomposition in the matrix with $d=300$ into $U_d \Sigma_d V_d$, and used the embedding vector as $U_d\sqrt{\Sigma_d}$.
@@
 Finally, we create an embedding by optimizing for the gravity law directly. 
-Specifically, we construct a gravity matrix of $N$ organizations, where each cell of the matrix is calculated as $T_{ij}/m_i m_j$, where $T_{ij}$ is co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory, and $m_i$ and $m_j$ are the organizations' populations, defined here as the mean annual member of unique mobile and non-mobile authors affiliated.
-
-We then embed the gravity matrix using two approaches: a truncated singular value decomposition (SVD), and with multidimensional scaling (MDS), which embeds each location in a N-dimensional space such that pairwise distances are preserved as well as possible.
+Specifically, we construct a gravity matrix of $N$ organizations, where each cell of the matrix is calculated as $T_{ij}/m_i m_j$, where $T_{ij}$ is co-occurrence of organizations $i$ and $j$ in the same affiliation trajectory, and $m_i$ and $m_j$ are the organizations' populations, defined here as the mean annual number of unique mobile and non-mobile authors affiliated.
+
+We then embed the gravity matrix using two approaches: a truncated singular value decomposition (SVD) and multidimensional scaling (MDS), which embeds each location in a N-dimensional space such that pairwise distances are preserved as well as possible.
 Typically, MDS uses Euclidean distance to measure distance between vectors.
 
-For this result, we report results using the cosine distance between embedding vectors for the SVD embedding, and the logged Euclidean distance for the MDS embedding. 
+For this analysis, we report results using the cosine distance between embedding vectors for the SVD embedding, and the logged Euclidean distance for the MDS embedding. 
 We observe that the gravity-optimized SVD cosine distance has poor performance, more weakly correlated with actual flux than geographic distance ($R^{2} = 0.122$, Table~\ref{supp:table:r2_table}), and similarly poor prediction error when used as input to the gravity mode.
-In contrast, the cosine distance between MDS vectors has the second-highest correlation with actual flux, after only the embedding distance ($R^{2} = 0.355$, Table~\ref{supp:table:r2_table}), and third best for predicting actual flux using both the power-law version of the gravity model (RMSE = $0.795$, Table~\ref{supp:table:rmse_power_table}), though performance is much lower using the exponential form (RMSE = $0.904$, Table~\ref{supp:table:rmse_exp_table}).
-We note that the MDS embedding actually has the lowest prediction error when organizations' populations are defined as the raw frequency during prediction with the power-law model (RMSE = $0.691$, Table~\ref{supp:table:rmse_power_table});
-however, we note that the MDS distance is defined with a population of ``All'' mobile and non-mobile scholars, whereas the predictions made in Table~\ref{supp:table:rmse_power_table} using the raw frequency, which likely confounds this result.
+In contrast, the cosine distance between MDS vectors has the second-highest correlation with actual flux, after only the embedding distance ($R^{2} = 0.355$, Table~\ref{supp:table:r2_table}), and third best for predicting actual flux using both the power-law version of the gravity model (RMSE = $0.795$, Table~\ref{supp:table:rmse_power_table}) and the exponential form (RMSE = $0.904$, Table~\ref{supp:table:rmse_exp_table}).
+We note that the MDS embedding actually has the lowest error when organizations' populations are defined as the raw frequency when using the power-law model (RMSE = $0.691$, Table~\ref{supp:table:rmse_power_table}).
+However, we note that the MDS distance is defined with a population of ``all'' mobile and non-mobile scholars, whereas the predictions made in Table~\ref{supp:table:rmse_power_table} use the raw frequency, which likely confounds this result.
 MDS is also computationally-intensive, requiring upwards of 6 times more time to compute (on the machine used in this analysis) than the more computationally efficient \textit{word2vec} model.
@@
 
-Affiliations mapped to one of 8,661 organizations, disambiguated following that originally designed for the Leiden Rankings of World Universities~\autocite{waltman2012leidenrankings}.
+Affiliations are mapped to one of 8,661 organizations and disambiguated following the procedure originally designed for the Leiden Rankings of World Universities~\autocite{waltman2012leidenrankings}.
 Organizational records were associated with a full name, a type indicating the sector (e.g., University, Government, Industry), and an identifier for the country and city of the organization.
@@
 
-Author-name disambiguation, the problem of associating names on papers with individuals authors, remains difficult for the use of bibliometric data~\autocite{dangelo2020disambiguation}.
+Author-name disambiguation, the problem of associating names on papers with individuals authors, remains difficult for the use of bibliographic data~\autocite{dangelo2020disambiguation}.
 Authors in our dataset have been disambiguated using a rule-based algorithm that makes use of author and paper metadata, such as physical addresses, co-authors, and journal, to score papers on the likelihood of belonging to an author cluster---a cluster of publications believed to have been authored by the same individual~\autocite{caron2014disambiguation}.
-We limit our period of analysis to the period of 2008 to 2019, as in 2008 the Web of Science began indexing additional author-level metadata such as full names and email addresses.
+We limit our analysis to the period from 2008 to 2019, as in 2008 the Web of Science began indexing additional author-level metadata such as full names and email addresses.
 The disambiguation algorithm is conservative, favoring splitting clusters over merging.
@@
 where $f$ is a non-negative likelihood function of data $x$, and ${\cal X}$ is the set of all data.
-This general form includes the word2vec model (Eq.~\eqref{eq:cond_prob_w2v}), where $f(x) = \exp(x)$ and $x = \vect{u}_j \cdot \vect{v}_{i}$.
+This general form includes the \textit{word2vec} model (Eq.~\eqref{eq:cond_prob_w2v}), where $f(x) = \exp(x)$ and $x = \vect{u}_j \cdot \vect{v}_{i}$.
 NCE fits the probability model using a binary classification task in the same way as in negative sampling but using a Bayesian formalism for logistic regression.
@@
 by calculating the gradients for embedding vectors $\vect{u}_j$, $\vect{v}_{i}$ and iteratively updating them.
-An important consequence of this framework is that NCE is an unbiased estimator that has convergence to the optimal embedding in terms of the original word2vec's objective function, ${\cal J}$~ if we increase the number of words to sample and the training iterations \autocite{Chia2010,Dyer2014}.
-
-%
-% S12 TEXT
+An important consequence of this framework is that NCE is an unbiased estimator that has convergence to the optimal embedding in terms of the original \textit{word2vec's} objective function, ${\cal J}$~ if we increase the number of words to sample and the training iterations \autocite{Chia2010,Dyer2014}.
+
+%
+% S13 TEXT
 \paragraph*{S13 Text}
@@
 
-The performance of the embedding ranking in reconstructing the Times ranking is comparable to that of network-derived measures such as degree strength (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_times_compare}a) and eigencentrality centrality (Spearman's $\rho = 0.76$, Fig.~\ref{fig:supp:centrality_times_compare}b).
+The performance of the embedding ranking in reconstructing the Times ranking is comparable to that of network-derived measures such as degree strength (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_times_compare}a) and eigenvector centrality (Spearman's $\rho = 0.76$, Fig.~\ref{fig:supp:centrality_times_compare}b).
 However, while both embedding- and network-based measures relate to university prestige, they are qualitatively and quantitatively different.
@@
 %
-% S13 TEXT
+% S14 TEXT
 \paragraph*{S14 Text}
@@
     otherwise, dummy variable is zero.
-    Similarly, $l_{ij}^x,  x \in [\text{language, language family}]$ is an dummy variable that is set to 1 if two organizations are in countries that share the same language or language family, respectively.
+    Similarly, $l_{ij}^x,  x \in [\text{language, language family}]$ is a dummy variable that is set to 1 if two organizations are in countries that share the same language or language family, respectively.
 

### 2022-11-28 paper/current/main.tex
second_round_revision

@@
 \end{align}
-The flow $\widehat{T}_{ij}$ is symmetric (\ie $\widehat{T}_{ij}=\widehat{T}_{ji}$) because the skip-gram model neglects whether the context $j$ appears before or after the target $i$ in the trajectory.
-If we swap $i$ and $j$ in Eq.~\eqref{eq:flow_w2v}, the numerator remains the same but the denominator can be different.
-Therefore, to ensure $\widehat{T}_{ij}=\widehat{T}_{ji}$, the denominator $Z_i$ should be a constant.
+The flow $\widehat{T}_{ij}$ is symmetric (\ie $\widehat{T}_{ij}=\widehat{T}_{ji}$) because the skip-gram model neglects whether the context $j$ appears before or after the target $i$ in the trajectory which produces,
+\begin{align}
+	\label{eq:unbiasef2}
+	T_{ij}=T_{ji} &\iff \frac{P(j) f(\vect{u}_j \cdot \vect{u}_{i}) }{Z_i} P(i) = \frac{P(i)  f(\vect{u}_i \cdot \vect{u}_{j}) }{Z_j} P(j) \nonumber \\
+	&\iff \frac{1}{Z_i}= \frac{1}{Z_j}  \nonumber \\
+	&\iff Z_i = Z_j
+\end{align}
 Taken together, the {\it word2vec} model with the negative sampling predicts a flow in the same form as the gravity model:
@@
 This makes \textit{word2vec} a powerful tool for learning models of mobility.
+
+We further demonstrate the ability of \textit{word2vec} to effectively represent gravity-like relationships with an synthetic benchmark.
+Namely, we train a \textit{word2vec} model using synthetic mobility trajectories that strictly adhere to the gravity model (see Supporting Information for details).
+We find that distances in the embedding space strongly correlates with distances in the synthetic space which was explicitly structured according to the gravity model (Pearson correlation of 0.943 and 0.801, depending on the distance metric used, Fig.
+S4).
+The results of this experiment align with a previous study which interpreted \textit{word2vec} as able to recover the metric underlying a semantic manifold~\autocite{hashimoto2016word}.
 
@@
 Similar patterns can be found across many of the 30 countries with the most total researchers (Fig.~\ref{fig:concave30}; see \SI{} for more discussion).
+Although we speculate on potential explanations for this pattern (see \SI{} for more discussion), we don't intend to make general claims about scientific mobility, or mobility more generally, but rather to illustrate how \textit{word2vec} can facilitate new kinds of investigations into mobility.
+Further work is necessary to determine what causes this curve pattern in so many countries and whether the same pattern can be found in other domains of human mobility.
 
@@
 
-While we focus on three domains of human mobility and illustrate its potential using scientific mobility, this approach is general and can be applied to many different domains, such as animal migration, transit-network mobility, and international trade.
+While we focus on three domains of human mobility and illustrate its potential using scientific mobility, this approach is general and can be applied to many different domains, such as animal migration, transit-network mobility,  discretized cell-phone location data,  and international trade.
 Once learned, functional distances between locations, such as countries, cities, or organizations, or the embedding model itself, can be published to facilitate re-use, and support reproducibility and transparency in cases when the underlying data is too sensitive to be made available.

### 2022-11-28 paper/current/supp.tex
second_round_revision

@@
 For example, an author who published with affiliation $A$ in $t_{0}$, and affiliations $B$ and $C$ in $t_{1}$ could appear as one of $(A, B, C)$ or $(A, C, B)$ in each training iteration.
-This effectively removes the effect of order within a year, as the order cannot be meaningfully established based on co-affiliations in a single paper, or on different affiliations listed on separate papers, for which the date of publication may not be representative of the actual completion of the project.
+This effectively removes the effect of order within a year, as the order cannot be mFigeaningfully established based on co-affiliations in a single paper, or on different affiliations listed on separate papers, for which the date of publication may not be representative of the actual completion of the project.
 
@@
 
+\paragraph*{S4 Text}
+\label{si:text:synthetic_exp}
+{\bf Demonstration on ability of \textit{word2vec} to effectively represent gravity-like relationships with a simulation experiment}
+
+We conducted an additional experiment to test the ability of \textit{word2vec} to recover the metric between locations, and to further demonstrate its equivalency with the gravity model.
+Specifically, we perform a synthetic benchmark to test whether \textit{word2vec} can effectively recover gravity-like relationships in data that is known to contain them.
+
+We start by generating synthetic mobility trajectories structured according the gravity model.
+For this purpose, we first generate an artificial ``geographic'' space.
+1,000 points are generated in a 2-dimensional space, with their coordinates distributed evenly between -1 and 1.
+These points act as the ``locations'' in our simulation.
+Each point is also assigned a ``mass'' randomly drawn from a power-law distribution $p(x) \propto x^{-k}$ (we use $k=2$) that is meant to represent the ``population'' or ``size'' of each location.
+
+With this simulated geography in place, we calculate the pairwise distance matrix $r_{ij}^{synthetic}$, which is then used to calculate a transition matrix between points, defined as $T_{ij} = M_i M_j f(r_{ij})$, with transition probabilities following the gravity law.
+The purpose of this transition matrix is to define the likelihood of movement between points (or \textit{locations}) in our simulated geography based on their mass and pairwise distances.
+We conduct this experiment with two different transition matrices, one based on cosine distance where $f(r_{ij})=e^{-\beta r_{ij}}$ and another with euclidean distance where $f(r_{ij})=r_{ij}^{-\alpha}$.
+For simplicity, we use $\beta=2$ and $\alpha=2$, though the analysis was repeated for multiple parameters in order to assess robustness.
+
+Finally, synthetic trajectories are generated based on the probabilities in the transition matrix.
+Specifically, we use a random walker based approach, where random walkers are initialized in locations with a probability proportional to their mass and transition between points according to the transition matrix.
+These synthetic trajectories are then used to train the skip-gram \textit{word2vec} model. 
+For parameters, we set window size to $w=1$ and the embedding dimension to $d=100$.
+
+From the embedding trained with synthetic trajectories, we calculate the pairwise embedding distances between points, $r_{ij}^{embedding}$.
+To evaluate the ability \textit{word2vec} to recover the known gravity-like structure of the synthetic data, we compare the embedding distance to the distances between the 1,000 points in the synthetic space, $r_{ij}^{synthetic}$ using the Pearson correlation coefficient.
+This result is repeated 100 times, and the correlation coefficients are aggregated across iterations.
+
+We find that \textit{word2vec} effectively recovers the gravity-like relationships in the synthetic data. 
+Based on cosine distance, the Pearson correlation between the embedding and synthetic distances is 0.943, with a standard error of 0.01. 
+Based on euclidean distance, the correlation was 0.801, with a standard error of 0.01.
+To better illustrate this point, Fig. \ref{fig:supp:synthetic_exp} shows the correlation for one representative iteration of this experiment.
+
+\
+
 %
 % S4 TEXT
-\paragraph*{S4 Text}
+\paragraph*{S5 Text}
 \label{si:text:ppr_dist}
@@
 % S5 Text
-\paragraph*{S5 Text}
+\paragraph*{S6 Text}
 \label{si:text:Raw SVD}
@@
 % S8 Text
-\paragraph*{S8 Text}
+\paragraph*{S9 Text}
 \label{si:text:direct}
@@
 % S9 Text
-\paragraph*{S9 Text}
+\paragraph*{S10 Text}
 \label{si:text:whynueralbetter}
@@
 % S10 TEXT
-\paragraph*{S10 Text}
+\paragraph*{S11 Text}
 \label{si:text:organizations}
@@
 % S11 TEXT
-\paragraph*{S11 Text}
+\paragraph*{S12 Text}
 \label{si:text:disambiguation}
@@
 % S12 TEXT
-\paragraph*{S12 Text}
+\paragraph*{S13 Text}
 \label{si:text:disambiguation}
@@
 % S13 TEXT
-\paragraph*{S13 Text}
+\paragraph*{S14 Text}
 \label{si:text:network_ranking}
@@
 % S14 TEXT
-\paragraph*{S14 Text}
+\paragraph*{S15 Text}
 \label{si:text:boomerang_speculation}
@@
 % S15 TEXT
-\paragraph*{S15 Text}
+\paragraph*{S16 Text}
 \label{si:text:generalized_gravity_model}
@@
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.888 \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.847 \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 
+7 \hspace{6pt}\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.835 \hspace{6pt}\huxbpad{6pt}} &
@@
 	\label{fig:supp:rcdf_by_scale}
+\end{figure}
+
+\newpage
+%
+% Figure - reverse CDF by scale
+%
+\begin{figure}[p!]
+	\centering
+	\includegraphics[width=0.8\textwidth]{\figdir/rebuttal/test_result.pdf}
+	    \caption{\textbf{Neural embedding recovers the underlying distance from trajectories.
+}\textbf{a.} The trajectories generated with cosine distance an \textbf{b.} The trajectories generated with euclidean distance.
+Illustratively, we show the result of the representative iteration of the experiment whose correlation is close to the average.
+The embedding distance shows a good agreement with underlying distance.
+Orange dots represent the average embedding distance across binned synthetic distances with standard error.
+    }
+	\label{fig:supp:synthetic_exp}
 \end{figure}

### 2022-12-05 paper/current/supp.tex
revision_second_round

@@
 We conduct this experiment with two different transition matrices, one based on cosine distance where $f(r_{ij})=e^{-\beta r_{ij}}$ and another with euclidean distance where $f(r_{ij})=r_{ij}^{-\alpha}$.
-For simplicity, we use $\beta=2$ and $\alpha=2$, though the analysis was repeated for multiple parameters in order to assess robustness.
+For simplicity, we use $\beta=2$ and $\alpha=2$.
 
@@
 To better illustrate this point, Fig. \ref{fig:supp:synthetic_exp} shows the correlation for one representative iteration of this experiment.
+
+In order to evaluate the robustness of the outcome across hyperparameter settings, we repeat our synthetic benchmark (using cosine distance) varying values for the mass exponent, $k$ and distance exponent $\beta$.
+In Fig. \ref{fig:supp:synthetic_robust}) presents the average Pearson correlation between the synthetic and embedding distance over ten iterations with for different values of $k$ and $\beta$. 
+This shows our findings to be robust. 
+Neural embedding consistently recovers the distance from the synthetic trajectories across a broad range of hyperparameter values. 
+A low correlation occurs only when the mass distribution is too heterogeneous ($k < 1.9$).
+In a heterogeneous mass distribution, most of the trajectories will concentrate on just a few high-mass locations, regardless of distance, which makes learning a distance challenging.
+Meanwhile, the exponent of the city population usually ranges between 2 and 3~\autocite{clauset2009power}.
 
@@
 
+\newpage
+%
+% Figure - reverse CDF by scale
+%
+\begin{figure}[p!]
+	\centering
+	\includegraphics[width=0.8\textwidth]{\figdir/rebuttal/robustness_check.pdf}
+	    \caption{\textbf{Neural embedding consistently recovers the underlying distance from trajectories across diverse hyperparameter settings.} We repeat our synthetic benchmark varying mass exponent $k$ and distance exponent $\beta$.
+The color of each cell represents the average Pearson correlation of the synthetic distance and embedding distances over ten repetitions with given $k$ and $\beta$.}
+	\label{fig:supp:synthetic_robust}
+\end{figure}
+
 %

### 2023-08-24 notebooks/revision_analysis.Rmd
many small changes

---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
lookup_file("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/institution_lookup_fixed.txt", delim="\t")
geo <- read_csv("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Derived/SemAxis/precedence/geography/coasts_d300_ws1_gamma1.0_n20_semaxis.csv")

new <- orgs %>%
  filter(country_iso_alpha == "USA") %>%
  left_join(geo, by = "cwts_org_no") %>%
  select(cwts_org_no, sim, longitude)
```

```{r}
# Sectors may be one of: All, University, Teaching, Institute, or Government"
SECTOR <- "All"

# Load organization meta-info
lookup <- read_delim("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t", col_types = readr::cols()) %>%
  filter(country_iso_alpha == "USA") %>% # select only the specified country
  select(cwts_org_no, country_iso_alpha, region, org_type_code, org_type, latitude, longitude)

axis2 <- read_csv("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Derived/SemAxis/precedence/prestige/leiden_d300_ws1_n5_gamma1.0_precedence_semaxis.csv", col_types = readr::cols())

org_types <-  read_csv("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/org_types.csv")

# Load the axis data and filter to only specified countries
sims <- read_csv("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Derived/SemAxis/precedence/geography/coasts_d300_ws1_gamma1.0_n20_semaxis.csv", col_types = readr::cols()) %>%
  inner_join(lookup, by = "cwts_org_no") %>%
  inner_join(axis2, by = "cwts_org_no") %>%
  left_join(org_types, by = "org_type")

# Enforce orientation. Not sure how we can automate this, so we will
# likely have to create separate rules for each kind of axis we choose
# I am defining these rules here based on what we know about the data already, namely
# which regions have more and less elite, or which are more or near the coasts.
cali_avg <- mean(subset(sims, region == "California")$sim.x)
mass_avg <- mean(subset(sims, region == "Massachusetts")$sim.x)
if (cali_avg > mass_avg) {
  sims$sim.x <- -sims$sim.x
}

ny_avg <- mean(subset(sims, region == "New York")$sim.y)
bama_avg <- mean(subset(sims, region == "Alabama")$sim.y)
if (bama_avg > ny_avg) {
  sims$sim.y <- -sims$sim.y
}

if (SECTOR != "All") {
  sims <- sims %>% filter(org_type_simplified == SECTOR)  
}

table(sims$org_type_simplified)

#
cor.test(~ longitude + sim.x,
            data = sims,
            method = "spearman",
            continuity = FALSE,
            conf.level = 0.99)
```

```{r}

leiden <- read_csv("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/leiden_ranking.csv")

# Load organization meta-info
lookup <- read_delim("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t", col_types = readr::cols()) %>%
  #filter(country_iso_alpha == "CHN") %>% # select only the specified country
  select(cwts_org_no, country_iso_alpha, region, org_type_code, org_type, latitude, longitude)

res_list <- lapply(
  c("USA","CHN","DEU","GBR","JPN","ITA","KOR","ESP","CAN","AUS"),
  function(x) {
    axis <- read_csv(
      sprintf(
      "/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Derived/SemAxis/OTHER_COUNTRIES/precedence/prestige/%s_leiden_d300_ws1_n5_gamma1.0_precedence_semaxis.csv", 
        x), 
      col_types = readr::cols()
    ) # end read_csv
    sims <- lookup %>%
      inner_join(axis, by = "cwts_org_no") %>%
      inner_join(leiden, by = "cwts_org_no") %>%
      filter(country_iso_alpha == x)

    t <- cor.test(~ impact_frac_mncs + sim,
                data = sims,
                method = "spearman",
                continuity = FALSE,
                conf.level = 0.99)

   return(data.frame(
       Country=x,
       `Count of orgs` = dim(sims)[1], 
       `Spearmans rho` = abs(t$estimate)
      )
    )

  }
)

df = data.table::rbindlist(res_list)

library(stargazer)
stargazer(df, summary=F, rownames=F)

```

Individual-level analysis
- Look at the RoG of 
```{r}
people <- read_delim("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Misc/2008-2019_people_details.tsv", delim="\t") %>%
  select(-first_name, -full_name)

times <- read_csv("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/times_ranking.csv")

# Load organization meta-info
lookup <- read_delim("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t", col_types = readr::cols()) %>%
  #filter(country_iso_alpha == "CHN") %>% # select only the specified country
  select(cwts_org_no, country_iso_alpha, org_type_code)

traj <- read_delim("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Raw/precedence_mobility_trajectories.txt", delim="\t") %>%
  left_join(lookup, by = "cwts_org_no") %>%
  group_by(cluster_id) %>%
  filter(first(country_iso_alpha) =="USA" & first(org_type_code) == "U") %>%
  distinct(cluster_id, cwts_org_no, .keep_all = TRUE) %>%
  filter(row_number() <= 2) # get first 2 per group
  filter(length(unique(country_iso_alpha)) == 1) # Limit to those who stay within US

# So what is the analysis exactly?
  # Begin with only authors in the United States who have been affiliated with a uni
  # Mark each author by the prestige of their first university...
    # What about age? Could control for it
    # Also can control for total number of moves, which will effect RoG...
    # Perhaps control for gender?

# What is the question we want to answer?
  # Do we want to use radius of gyration, or is the distance from one to the next 
  # enough? What does it mean to do a typical vs. atypical move?
  # Maybe instead of RoG, we use something even simpler...the embedding distance between the moves...
  # Then, we don't have to introduce any new concepts. I don't think gender should be a aprt of it. We have a whole section about prestige, so we should stick to that narrative.

# Maybe something like, "holding all else constant, what is the largest driver of making a typical vs. atypical move?
# By avoiding the RoG, and just using first-second, we can simplify a lot of things. # Depending on where you start, holding other factors equal, is a person more likely
# to travel between a nearby or a distant university, measured by the embedding space. 
```

```{r}
# We need to investigate whether there is some kind of symmetry in the mobility patterns
# of smaller and larger universities...
library(igraph)
library(tidyverse)
# Load organization meta-info
lookup <- read_delim("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t", col_types = readr::cols()) %>%
  select(cwts_org_no, wos_name, country_iso_alpha, org_type_code) %>%
  filter(country_iso_alpha == "USA" & org_type_code == "U")
sizes <- read_delim("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/2008-2019_inst_sizes_all.txt", delim="\t")
edges <- read_csv("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Derived/Network/precedence_flows_edgelist.csv")
```

```{r}
# First, get the total degree...
g <- graph.data.frame(edges, directed=FALSE)
df <- data.frame(degree(g, mode="all"))
df$cwts_org_no <- as.numeric(row.names(df))
colnames(df)[1] <- "degree"

sizes %>%
  left_join(lookup, by = "cwts_org_no") %>%
  filter(country_iso_alpha == "USA") %>%
  inner_join(df, by = "cwts_org_no") %>%
  ggplot(aes(x = size, y = degree)) + 
  geom_point() +
  scale_x_log10()
# What this shows is that as the size of the institution increases, the degree centrality also increases...
```

```{r}
code <- 1179
# UMich Flint
umich <- edges %>%
  filter(Source == code | Target == code)

library(DescTools)

res <- lapply(unique(lookup$cwts_org_no), function(org) {
  sub_df <- edges %>%
    filter(Source == org | Target == org)

  return(data.frame(cwts_org_no = org, gini = Gini(sub_df$weight)))
})

all_gini <- data.table::rbindlist(res)

p <- all_gini %>%
  left_join(lookup, by = "cwts_org_no") %>%
  left_join(sizes, by = "cwts_org_no") %>%
  filter(size >= 10) %>%
  ggplot(aes(x = size, y = gini, label=wos_name)) +
  geom_point() +
  scale_x_log10()
# Calculate gini index

ggplotly(p)
# 
# How do we get at the idea of "different contexts"?
# That is, how do we test the idea that its not just the distribution across topics, but the 
# occurrence in very different "topics", that's a bit more abstract to test...
#
# I guess we could use embedding distance? That is, perhaps smaller colleges are connected with 
# a more disparate collection of other universities??? That is, people from smaller colleges 
# are move likely to take atypical paths, whereas those in more elite colleges are likely to 
# follow more standard paths...perhaps this is something??
#
# We could look at international connectivity of universities, the proportion of their 
# researchers that are internationally mobile?? That might correlate with the curve, and 
# get at the idea of comparing different curves

```

```{r}
dist <- read_csv("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Derived/Descriptive/org/aggregate/precedence/aggregate_org_distances_precedence_d300_ws1_gamma1.0_sizeall.csv")

colnames(dist)
```

```{r}
res <- lapply(unique(lookup$cwts_org_no), function(org) {
  sub_df <- dist %>%
    filter(org1 == org | org2 == org)

  return(data.frame(cwts_org_no = org, gini = Gini(sub_df$emb_distance)))
})

all_gini <- data.table::rbindlist(res)

library(plotly)
p <- all_gini %>%
  left_join(lookup, by = "cwts_org_no") %>%
  left_join(sizes, by = "cwts_org_no") %>%
  filter(size >= 10) %>%
  ggplot(aes(x = size, y = gini, label=wos_name)) +
  geom_point() +
  geom_smooth(method="loess") +
  scale_x_log10()

ggplotly(p)

# The idea is that the L2-norm scales with frequency, until we hit bigger more "universal" terms, 
# at which case the scaling is counterbalanced by appearing in a greater diversity of contexts, which 
# in turn "average out" the vector until its norm is small, because it isn't weighted towards any 
# particular context
#
# So the idea says more about big elite colleges, rather than it does about symmetry. So we don't 
# really need to show symmetry between elite and non-elite, but rather simply that elite colleges 
# appear in a greater variety of contexts...
#
#
# So these results show that yes, more elite universities share their researchers with a wider
# variety of places...but can we talk about this further???
#
# But I still don't think it touches on the idea of compression in the embedding space.

```

---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
lookup_file("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/institution_lookup_fixed.txt", delim="\t")
geo <- read_csv("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Derived/SemAxis/precedence/geography/coasts_d300_ws1_gamma1.0_n20_semaxis.csv")

new <- orgs %>%
  filter(country_iso_alpha == "USA") %>%
  left_join(geo, by = "cwts_org_no") %>%
  select(cwts_org_no, sim, longitude)
```

```{r}
# Sectors may be one of: All, University, Teaching, Institute, or Government"
SECTOR <- "All"

# Load organization meta-info
lookup <- read_delim("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t", col_types = readr::cols()) %>%
  filter(country_iso_alpha == "USA") %>% # select only the specified country
  select(cwts_org_no, country_iso_alpha, region, org_type_code, org_type, latitude, longitude)

axis2 <- read_csv("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Derived/SemAxis/precedence/prestige/leiden_d300_ws1_n5_gamma1.0_precedence_semaxis.csv", col_types = readr::cols())

org_types <-  read_csv("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/org_types.csv")

# Load the axis data and filter to only specified countries
sims <- read_csv("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Derived/SemAxis/precedence/geography/coasts_d300_ws1_gamma1.0_n20_semaxis.csv", col_types = readr::cols()) %>%
  inner_join(lookup, by = "cwts_org_no") %>%
  inner_join(axis2, by = "cwts_org_no") %>%
  left_join(org_types, by = "org_type")

# Enforce orientation. Not sure how we can automate this, so we will
# likely have to create separate rules for each kind of axis we choose
# I am defining these rules here based on what we know about the data already, namely
# which regions have more and less elite, or which are more or near the coasts.
cali_avg <- mean(subset(sims, region == "California")$sim.x)
mass_avg <- mean(subset(sims, region == "Massachusetts")$sim.x)
if (cali_avg > mass_avg) {
  sims$sim.x <- -sims$sim.x
}

ny_avg <- mean(subset(sims, region == "New York")$sim.y)
bama_avg <- mean(subset(sims, region == "Alabama")$sim.y)
if (bama_avg > ny_avg) {
  sims$sim.y <- -sims$sim.y
}

if (SECTOR != "All") {
  sims <- sims %>% filter(org_type_simplified == SECTOR)  
}

table(sims$org_type_simplified)

#
cor.test(~ longitude + sim.x,
            data = sims,
            method = "spearman",
            continuity = FALSE,
            conf.level = 0.99)
```

```{r}

leiden <- read_csv("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/leiden_ranking.csv")

# Load organization meta-info
lookup <- read_delim("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t", col_types = readr::cols()) %>%
  #filter(country_iso_alpha == "CHN") %>% # select only the specified country
  select(cwts_org_no, country_iso_alpha, region, org_type_code, org_type, latitude, longitude)

res_list <- lapply(
  c("USA","CHN","DEU","GBR","JPN","ITA","KOR","ESP","CAN","AUS"),
  function(x) {
    axis <- read_csv(
      sprintf(
      "/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Derived/SemAxis/OTHER_COUNTRIES/precedence/prestige/%s_leiden_d300_ws1_n5_gamma1.0_precedence_semaxis.csv", 
        x), 
      col_types = readr::cols()
    ) # end read_csv
    sims <- lookup %>%
      inner_join(axis, by = "cwts_org_no") %>%
      inner_join(leiden, by = "cwts_org_no") %>%
      filter(country_iso_alpha == x)

    t <- cor.test(~ impact_frac_mncs + sim,
                data = sims,
                method = "spearman",
                continuity = FALSE,
                conf.level = 0.99)

   return(data.frame(
       Country=x,
       `Count of orgs` = dim(sims)[1], 
       `Spearmans rho` = abs(t$estimate)
      )
    )

  }
)

df = data.table::rbindlist(res_list)

library(stargazer)
stargazer(df, summary=F, rownames=F)

```

Individual-level analysis
- Look at the RoG of 
```{r}
people <- read_delim("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Misc/2008-2019_people_details.tsv", delim="\t") %>%
  select(-first_name, -full_name)

times <- read_csv("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/times_ranking.csv")

# Load organization meta-info
lookup <- read_delim("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t", col_types = readr::cols()) %>%
  #filter(country_iso_alpha == "CHN") %>% # select only the specified country
  select(cwts_org_no, country_iso_alpha, org_type_code)

traj <- read_delim("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Raw/precedence_mobility_trajectories.txt", delim="\t") %>%
  left_join(lookup, by = "cwts_org_no") %>%
  group_by(cluster_id) %>%
  filter(first(country_iso_alpha) =="USA" & first(org_type_code) == "U") %>%
  distinct(cluster_id, cwts_org_no, .keep_all = TRUE) %>%
  filter(row_number() <= 2) # get first 2 per group
  filter(length(unique(country_iso_alpha)) == 1) # Limit to those who stay within US

# So what is the analysis exactly?
  # Begin with only authors in the United States who have been affiliated with a uni
  # Mark each author by the prestige of their first university...
    # What about age? Could control for it
    # Also can control for total number of moves, which will effect RoG...
    # Perhaps control for gender?

# What is the question we want to answer?
  # Do we want to use radius of gyration, or is the distance from one to the next 
  # enough? What does it mean to do a typical vs. atypical move?
  # Maybe instead of RoG, we use something even simpler...the embedding distance between the moves...
  # Then, we don't have to introduce any new concepts. I don't think gender should be a aprt of it. We have a whole section about prestige, so we should stick to that narrative. 
  # Perhaps could we do something w/ attrition???

# Maybe something like, "holding all else constant, what is the largest driver of making a typical vs. atypical move?
# By avoiding the RoG, and just using first-second, we can simplify a lot of things. # Depending on where you start, holding other factors equal, is a person more likely
# to travel between a nearby or a distant university, measured by the embedding space. 
```

```{r}
# We need to investigate whether there is some kind of symmetry in the mobility patterns
# of smaller and larger universities...
library(igraph)
library(tidyverse)
# Load organization meta-info
lookup <- read_delim("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t", col_types = readr::cols()) %>%
  select(cwts_org_no, wos_name, country_iso_alpha, org_type_code) %>%
  filter(country_iso_alpha == "USA" & org_type_code == "U")
sizes <- read_delim("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/2008-2019_inst_sizes_all.txt", delim="\t")
edges <- read_csv("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Derived/Network/precedence_flows_edgelist.csv")
```

```{r}
# First, get the total degree...
g <- graph.data.frame(edges, directed=FALSE)
df <- data.frame(degree(g, mode="all"))
df$cwts_org_no <- as.numeric(row.names(df))
colnames(df)[1] <- "degree"

sizes %>%
  left_join(lookup, by = "cwts_org_no") %>%
  filter(country_iso_alpha == "USA") %>%
  inner_join(df, by = "cwts_org_no") %>%
  ggplot(aes(x = size, y = degree)) + 
  geom_point() +
  scale_x_log10()
# What this shows is that as the size of the institution increases, the degree centrality also increases...
```

```{r}
library(DescTools)

lookup <- read_delim("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t", col_types = readr::cols()) %>%
  select(cwts_org_no, wos_name, country_iso_alpha, org_type_code) %>%
  filter(country_iso_alpha == "USA" & org_type_code == "U")

res <- lapply(unique(lookup$cwts_org_no), function(org) {
  sub_df <- edges %>%
    filter(Source == org | Target == org)

  return(data.frame(cwts_org_no = org, gini = Gini(sub_df$weight)))
})

all_gini <- data.table::rbindlist(res)

p <- all_gini %>%
  left_join(lookup, by = "cwts_org_no") %>%
  left_join(sizes, by = "cwts_org_no") %>%
  filter(size >= 10) %>%
  ggplot(aes(x = size, y = gini, label=wos_name)) +
  geom_point() +
  scale_x_log10()
# Calculate gini index

ggplotly(p)
# 
# How do we get at the idea of "different contexts"?
# That is, how do we test the idea that its not just the distribution across topics, but the 
# occurrence in very different "topics", that's a bit more abstract to test...
#
# I guess we could use embedding distance? That is, perhaps smaller colleges are connected with 
# a more disparate collection of other universities??? That is, people from smaller colleges 
# are move likely to take atypical paths, whereas those in more elite colleges are likely to 
# follow more standard paths...perhaps this is something??
#
# We could look at international connectivity of universities, the proportion of their 
# researchers that are internationally mobile?? That might correlate with the curve, and 
# get at the idea of comparing different curves

```

```{r}
dist <- read_csv("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Derived/Descriptive/org/aggregate/precedence/aggregate_org_distances_precedence_d300_ws1_gamma1.0_sizeall.csv")

colnames(dist)
```

```{r}
library(plotly)

lookup <- read_delim("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t", col_types = readr::cols()) %>%
  select(cwts_org_no, wos_name, country_iso_alpha, org_type_code) %>%
  filter((country_iso_alpha %in% c("USA", "CHN", "EGY", "BRA", "AUS")) & org_type_code == "U")

# What fraction of their total mobility is international???
dist <- dist %>%
  mutate(international = org1_country != org2_country)

res <- lapply(unique(lookup$cwts_org_no), function(org) {
  sub_df <- dist %>%
    filter(org1 == org | org2 == org) %>%
    mutate(international = factor(international, levels = c(TRUE, FALSE))) %>%
    complete(international, fill= list(count=0)) %>%
    group_by(international) %>%
    summarize(count = sum(count)) %>%
    ungroup() %>%
    filter(!is.na(international)) %>%
    pivot_wider(names_from = international, values_from = count) %>%
    mutate(cwts_org_no = org)

  return(sub_df)
})

all_gini <- data.table::rbindlist(res)

p <- all_gini %>%
  mutate(international = `TRUE` / (`TRUE` + `FALSE`)) %>%
  left_join(lookup, by = "cwts_org_no") %>%
  left_join(sizes, by = "cwts_org_no") %>%
  filter(size >= 10) %>%
  ggplot(aes(x = size, y = international, label=wos_name, color=country_iso_alpha)) +
  geom_point() +
  geom_smooth(method="loess") +
  scale_x_log10()

ggplotly(p)

# The idea is that the L2-norm scales with frequency, until we hit bigger more "universal" terms, 
# at which case the scaling is counterbalanced by appearing in a greater diversity of contexts, which 
# in turn "average out" the vector until its norm is small, because it isn't weighted towards any 
# particular context
#
# So the idea says more about big elite colleges, rather than it does about symmetry. So we don't 
# really need to show symmetry between elite and non-elite, but rather simply that elite colleges 
# appear in a greater variety of contexts...
#
#
# So these results show that yes, more elite universities share their researchers with a wider
# variety of places...but can we talk about this further???
#
# But I still don't think it touches on the idea of compression in the embedding space.
# Maybe number of different countries??
```

```{r}
library(plotly)

lookup <- read_delim("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/institution_lookup_with_states.txt", delim = "\t", col_types = readr::cols()) %>%
  select(cwts_org_no, wos_name, country_iso_alpha, org_type_code) %>%
  filter((country_iso_alpha %in% c("USA", "CHN", "EGY", "BRA", "GBR")) & org_type_code == "U")

countries <- unique(c(dist$org1_country, dist$org2_country))
# 
res <- lapply(unique(lookup$cwts_org_no), function(org) {
  sub_df <- dist %>%
    filter(org1 == org | org2 == org) %>%
    filter(org1_country != org2_country) %>%
    mutate(
      # make sure destination is always org2
      destination = ifelse(org1 == org, org2_country, org1_country)
    ) %>%
    mutate(destination = factor(destination, levels=countries)) %>%
    complete(destination, fill=list(count=0)) %>%
    # group by destination
    group_by(destination) %>% 
    summarize(
      cwts_org_no = org,
      count = sum(count)
    ) %>%
    ungroup()

  return(data.frame(cwts_org_no = org, gini = Gini(sub_df$count)))
})

res[[3]]
all_gini <- data.table::rbindlist(res)

p <- all_gini %>%
  left_join(lookup, by = "cwts_org_no") %>%
  left_join(sizes, by = "cwts_org_no") %>%
  filter(size >= 10) %>%
  ggplot(aes(x = size, y = gini, label=wos_name, color=country_iso_alpha)) +
  geom_point() +
  geom_smooth(method="loess") +
  scale_x_log10()

p

all_gini
# So we should calculate "more people from a more narrow set of places", or "more people from a broader 
# set of places..."
#
# So if we do a GINI index, but fill in all missing countries with a zero, then that could be a good way of
# showing this...
# I bet we see something even more stark when we do this gini calculation...
```

```{r}
library(igraph)

#' This adds the gadd graph to the main graph, g, and wires all of its vertices
#' to the central vertex of g
attach_to_center <- function(g, gadd) {
  g <- g + gadd + edges(as.vector(rbind(1, gorder(g) + 1:gorder(gadd))))
}

nIter <- 4
nChild <- 6

# The initial graph
g <- make_empty_graph(5, directed = FALSE) + edges(1,2,1,3,1,4,1,5,2,3,3,4,4,5,5,2)

for (j in 1:nIter) {
  g0 <- g
  for (i in 1:nChild) {
    g <- attach_to_center(g, g0)
  }
}

V(g)
```

```{r}
library(igraph)
library(tidyverse)
# Lets create a random graph with the same degree seq
edges <- read_csv("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Derived/Network/precedence_flows_edgelist.csv")
g0 <- graph.data.frame(edges, directed=FALSE)

#sample_degseq(degree_distribution(g0))
my_fit_g0 <- fit_power_law(degree(g0, mode = "all"), implementation = "plfit")

g1 <- sample_fitness_pl(length(V(g0)), length(E(g0)), my_fit_g0$alpha)
#my_fit_g1 <- fit_power_law(degree(g1, mode = "all"), implementation = "plfit")

# for every node, generate a number of random walkers equal to its degree...
#g1 <- sample_pa(10000, m=100, power=6.83, directed=F)
#g1 <- g0
library(igraph)
traj <- sapply(names(V(g1)), function(x1) {
  d <- as.numeric(degree(g1, x1)) # get degree of node

  # sample trajectories starting at the node
  l <- sapply(c(1:d), function(x2) {
    paste(as.numeric(random_walk(g1, start=x1, steps=3)), collapse=" ")
  })

  return(l)
})

write_graph(g1, file="~/Desktop/murray_sample_network.gml")
write.csv(unlist(traj), "~/Desktop/mobility_network_trajectories_pa-model.csv")
```

```{r}
as.numeric(degree(g1, '1292'))
random_walk(g1, start='1292', steps=3)
```

```{r}
names(sapply(V(g1), function(x1) { x1 }))
new_traj
unlist(traj)
(unlist(traj))

edges %>%
  filter(Source == '1' | Target == '1')
```

```{r}
#hist(log10(degree_distribution(g1)))

```

```{r}
library(tidyverse)
df2 <- read_csv("~/Desktop/mobility_network_trajectories_real_final.csv")

sizes <- read_delim("/Users/dmurray/Dropbox (Personal)/SME-dropbox/Data/Additional/2008-2019_inst_sizes_all.txt", delim="\t") %>%
  mutate(all_size = )
df2
df2 %>%
  mutate(token = as.character(token)) %>%
  left_join(sizes, by = c(cwts_org_no=token)) %>%
  ggplot(aes(x = size, y = norm)) +
  geom_point() +
  scale_x_log10()
```

### 2023-08-24 paper/current/nature-comm-physics/main.tex
many small changes

--- 2022-11-28 paper/current/main.tex
@@
 \author[1,\Yinyang]{Dakota Murray}
-\author[1,2,\Yinyang]{Jisung Yoon}
-\author[1]{Sadamori Kojaku}
-\author[3,4]{Rodrigo Costas}
-\author[2,5,6]{Woo-Sung Jung}
+\author[1,2,3,\Yinyang]{Jisung Yoon}
+\author[1, \Yinyang]{Sadamori Kojaku}
+\author[4,5]{Rodrigo Costas}
+\author[6,7]{Woo-Sung Jung}
 \author[1]{Staša Milojević \thanks{smilojev@indiana.edu}}
-\author[1,7,8]{Yong-Yeol Ahn \thanks{yyahn@iu.edu}}
+\author[1,8,9]{Yong-Yeol Ahn \thanks{yyahn@iu.edu}}
 
 \affil[1]{Center for Complex Networks and Systems Research, Luddy School of Informatics, Computing, and Engineering, Indiana University, Bloomington, IN 47408, USA}
-\affil[2]{Department of Industrial and Management Engineering, Pohang University of Science and Technology,
+\affil[2]{Kellogg School of Management at Northwestern University, Evanston, IL 60208, USA.}
+\affil[3]{Northwestern Institute on Complex Systems, Evanston, IL 60208, USA.}
+\affil[4]{Centre for Science and Technology Studies (CWTS), Leiden University, P.O. Box 905,
+	2300 AX Leiden, The Netherlands}
+\affil[5]{DST-NRF Centre of Excellence in Scientometrics and Science, Technology and Innovation Policy, Stellenbosch University, Stellenbosch, South Africa}
+\affil[6]{Department of Physics, Pohang University of Science and Technology,
 	Pohang 37673, Republic of Korea.}
-\affil[3]{Centre for Science and Technology Studies (CWTS), Leiden University, P.O. Box 905,
-	2300 AX Leiden, The Netherlands}
-\affil[4]{DST-NRF Centre of Excellence in Scientometrics and Science, Technology and Innovation Policy, Stellenbosch University, Stellenbosch, South Africa}
-\affil[5]{Department of Physics, Pohang University of Science and Technology,
+\affil[7]{Department of Industrial and Management Engineering, Pohang University of Science and Technology,
 	Pohang 37673, Republic of Korea.}
-\affil[6]{Asia Pacific Center for Theoretical Physics, Pohang 37673, Republic of Korea.}
-\affil[7]{Network Science Institute, Indiana University, Bloomington (IUNI), IN 47408, USA}
-\affil[8]{Connection Science, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
+\affil[8]{Network Science Institute, Indiana University, Bloomington (IUNI), IN 47408, USA}
+\affil[9]{Connection Science, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
 
-\affil[\Yinyang]{These authors contributed equally: Jisung Yoon, Dakota Murray.}
+\affil[\Yinyang]{These authors contributed equally: Sadamori Kojaku, Jisung Yoon, Dakota Murray, }
 
@@
 	Here, we show a mathematical equivalence between \textit{word2vec} model and the gravity model of mobility and demonstrate that, by using three datasets of human mobility trajectories, \textit{word2vec} encodes nuanced relationships between discrete locations into an accurate and meaningful vector-space, providing a functional distance between locations, as well as a representation for studying the many dimensions of mobility.
-	Focusing on the case of scientific mobility, we show that embeddings can learn implicit information directly from mobility data, such as cultural, linguistic, and hierarchical relationships at multiple levels of granularity.
+	Focusing on the case of scientific mobility, we show that embeddings can learn implicit information,  such as cultural, linguistic, and hierarchical relationships at multiple levels of granularity,  directly from mobility data.
 	Connecting neural embeddings to the gravity model opens up new avenues for the study of mobility.
@@
 Here, we demonstrate that the \textit{word2vec} model (Skip-Gram Negative Sampling) is equivalent to the gravity law of mobility, a fundamental mobility framework.
-We then empirically test the resulting representation by its ability to derive from mobility trajectories the functional distances between locations.
-After validating that it accurately represents real-world data, we leverage unique embedding-based methods to demonstrate \textit{word2vec}'s capacity for encoding rich information relating to geography, culture, language, and even prestige, at multiple scales of analysis.
+We then empirically test the resulting representation by its ability to derive the functional distances between locations from mobility trajectories.
+After validating that it accurately represents real-world data, we leverage unique embedding-based methods to demonstrate \textit{word2vec}'s capacity for encoding rich information related to geography, culture, language, and even prestige, at multiple scales of analysis.
 We embed trajectories from three datasets: U.S.
@@
 For the flight itinerary data, we use population $m_{i}$ as the total number of unique passengers who passed through each airport, for the Korean accommodation reservation data, we use the total number of unique customers who booked with each accommodation, and for scientific mobility, we use the mean annual number of unique mobile and non-mobile authors who were affiliated with each organization.
-$\hat{T}_{ij}$, which is often referred to as ``expected flux''~\autocite{simini2012universal}, is the expected frequency of the co-occurrence of location $i$ and $j$ in the trajectory in the gravity model.
+$\hat{T}_{ij}$, which is often referred to as ``expected flux''~\autocite{simini2012universal},  as the expected frequency of the co-occurrence of location $i$ and $j$ in the trajectory in the gravity model.
 
@@
 where $f$ is a positive real-valued likelihood function of data $x$, and ${\cal X}$ is the set of all data.
-Note that word2vec belongs to this class of probability models, with $x=\vect{u}_i\cdot \vect{v}_j$ and $f(x)=\exp(x)$.
+Note that {\it word2vec} belongs to this class of probability models, with $x=\vect{u}_i\cdot \vect{v}_j$ and $f(x)=\exp(x)$.
 To train {\it word2vec} with NCE~\autocite{mikolov2013word2vec}, one samples a center-context pair $(i,j)$ from the given data and labels the pair as $Y=1$. 

### 2023-08-24 paper/current/nature-comm-physics/notes/2021-0105-word2vec-vs-gravity-model/main.tex
many small changes

--- 2021-01-12 paper/current/notes/2021-0105-word2vec-vs-gravity-model/main.tex
@@
 \end{equation}
-where $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector", respectively, and $Z_i=\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{i})$ is a normalization constant,
-and $\mathcal{A}$ is the set of all locations.
-Under restricting window size to be one, the expected flow between center location $a_i$ and context location $a_j$ is given by
+where $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector", respectively,  $Z_i=\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations.
+Under restricting window size to be one, the expected flow between center location $i$ and context location $j$ is given by
 \begin{align}
@@
 Although there are some similarities, Eq.~\ref{eq:flow_w2v} does not have a population term $m_i$.
-In additionm the distance can be asymmetric, $r_{ij}=- \bm{u}_{j} \cdot \bm{v}_{i} \neq - \bm{u}_{i} \cdot \bm{v}_{j}=r_{ji}$.
+In addition, the distance can be asymmetric, $r_{ij}=- \bm{u}_{j} \cdot \bm{v}_{i} \neq - \bm{u}_{i} \cdot \bm{v}_{j}=r_{ji}$.
 
@@
 \end{align}
-In the \textit{word2vec}, the flow $\hat{T_{ij}}_{ij}$ is symmetric by design (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because the word2vec neglects whether the context $j$ appears later or earlier from center $i$.
+In the \textit{word2vec}, the flow $\hat{T_{ij}}_{ij}$ is symmetric by design (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because the model neglects whether the context $j$ appears later or earlier from center $i$.
 Therefore, we have
@@
 
-Many probability models including the word2vec can be represented in form
+Many probability models including the \textit{word2vec} can be represented in form
 \begin{align}
@@
 \end{align}
-For the word2vec, the correct expression of word2vec optimized with the negative sampling is given by
+For the \textit{word2vec}, the correct expression optimized with the negative sampling is given by
 \begin{align}

### 2023-08-24 paper/current/nature-comm-physics/notes/gm-vs-w2v/main.tex
many small changes

--- 2020-04-29 paper/current/notes/gm-vs-w2v/main.tex
@@
 
+% comment out when submitting
 % for quick author comments 
 \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
+\usepackage{soul}
+\usepackage{ulem}
 \definecolor{light-gray}{gray}{0.8}
@@
 \definecolor{light-green}{RGB}{76, 175, 80}
-\def\del#1{ {\color{light-gray}{#1}} }
+%\def\del#1{ {\color{light-gray}{#1}} }
 \def\yy#1{\footnote{\color{red}\textbf{yy: #1}} }
@@
 \def\jisung#1{\footnote{\color{light-green}\textbf{js: #1}} }
+
+% Track Changes
+\definecolor{myblue}{RGB}{33,150,243}
+\definecolor{mygreen}{RGB}{76, 175, 80}
+\definecolor{purple}{RGB}{170, 0, 255}
+
+\newcommand{\add}[1]{{\leavevmode\color{blue}#1}}
+\newcommand{\del}[1]{{\leavevmode\color{red}\sout{#1}}}
+\newcommand{\change}[3][]{{\del{#2}\add{#3}$^{\textcolor{blue}{\text{#1}}}$}}
+\newcommand{\comment}[1]{
+    \begin{enumerate}[label*=(\arabic*)]
+    #1
+    \end{enumerate}
+}
 
@@
 We assume that the in-vectors are equal to the out-vectors, i.e., $\vec{v}_j = \vec{u}_j$.
-Then, the dot similarity for $\vec{u}_i$ and $\vec{v}_j$ is given by 
+Exploiting $d^2 (\vec{u},\vec{u}')=||\vec{u}||^2 + ||\vec{u}'||^2 - 2\vec{u} ^\top \vec{u}'$, the dot similarity for $\vec{u}_i$ and $\vec{v}_j$ is given by 
 \begin{align}
@@
 
-In migration study, $M_i$ is often fixed to the number of people at a point $i$ (e.g., city and country), which is a restricted version of the gravity model.
-We show that the word2vec is free from the restriction and automatically learns the mass $M_i$ from data, which may not be equal to the number of people at a point.
+How should $M_i$ be chosen? The choice of $M_i$ is entirely unconstrained.
+In migration study, one sets $M_i$ to exogenous variables such as population at the point in priori and then estimates other parameters, e.g., $G$.
+We show that the word2vec automatically estimates the mass $M_i$ from data without exogenous variables. 
+The estimated $M_i$ may not be equal to the number of people at a point.
 
@@
     \pi_i &= G' Z_i \nonumber \\
-        &= G' s_i \sum_{\ell=1}^N s_\ell f\left(d\left(\vec{u}_i,\vec{u}_\ell\right)\right) \nonumber \\ 
-        &= G' s_i ^2 - s_i \Phi(\vec{u}_i), \label{eq:flow_gravity_model_2} %\nonumber \\ 
+        &= G' s_i \sum_{\ell=1}^N s_\ell f\left(d\left(\vec{u}_i,\vec{u}_\ell\right)\right)\\
+        &= -G' s_i \Phi(\vec{u}_i), \label{eq:flow_gravity_model_2} \\ %\nonumber \\ 
 \end{align}
-where $\Phi(\vec{u})$ is the potential given by 
+where we have defined $\Phi(\vec{u})$ by 
 \begin{align}
-    \Phi(\vec{u}):=-G' \sum_{\ell=1, \vec{u}\neq \vec{u}_\ell}^N s_\ell f\left(d\left(\vec{u},\vec{u}_\ell\right)\right).
+    \Phi(\vec{u}):=-G' \sum_{\ell=1}^N s_\ell f\left(d\left(\vec{u},\vec{u}_\ell\right)\right).
 \end{align}
-Potential $\Phi(\vec{u})$ is analogous to the gravitational potential, i.e., $-GM/d$, where $M$ is the mass and $d$ is the distance from the mass.
-In other words,  $\Phi(\vec{u})$ is the gravitational potential for the field, where 
-each point $\ell$ has a mass $s_{\ell}$ and is away from $\vec{u}$ with distance $d(\vec{u},\vec{u}_\ell)$, and the effect of the mass decays by the factor of $\exp\left[d(\vec{u},\vec{u}_\ell) ^2 /2\right]$.
+In other words, $\pi_i$ is proportional to the product of $s_i$ and $\Phi(\vec{u})$.
+Therefore, points with a large $\pi_i$ tend to have a large $s_i$ value.
+What does $\Phi(\vec{u})$ represent? 
+Variable $\Phi(\vec{u})$ is analogous to the gravitational potential in mechanical physics, which takes form $-GM/d$, where $M$ is the mass and $d$ is the distance from the mass.
+%In other words,  $\Phi(\vec{u})$ can be seen as the gravitational potential for the field, where 
+%each point $\ell$ has a mass $s_{\ell}$ and is away from $\vec{u}$ with distance $d(\vec{u},\vec{u}_\ell)$, and the effect of the mass decays by the factor of $\exp\left[d(\vec{u},\vec{u}_\ell) ^2 /2\right]$.
+Point $\vec{u}$ has a large $\Phi(\vec{u})$ if there are many points $\ell$ around $\vec{u}$ that have a large $\vec{s}_\ell$.
+Potential $\Phi(\vec{u})$ is similar to the eigen centrality for networks that assigns a large centrality score for the node with many neighbors with a large centrality scores.
 

### 2023-08-24 paper/current/nature-comm-physics/supp.tex
many small changes

--- 2022-12-05 paper/current/supp.tex
@@
 For example, an author who published with affiliation $A$ in $t_{0}$, and affiliations $B$ and $C$ in $t_{1}$ could appear as one of $(A, B, C)$ or $(A, C, B)$ in each training iteration.
-This effectively removes the effect of order within a year, as the order cannot be mFigeaningfully established based on co-affiliations in a single paper, or on different affiliations listed on separate papers, for which the date of publication may not be representative of the actual completion of the project.
+This effectively removes the effect of order within a year, as the order cannot be meaningfully established based on co-affiliations in a single paper, or on different affiliations listed on separate papers, for which the date of publication may not be representative of the actual completion of the project.
 
@@
 
-We start by generating synthetic mobility trajectories structured according the gravity model.
+We start by generating synthetic mobility trajectories structured according to the gravity model.
 For this purpose, we first generate an artificial ``geographic'' space.
@@
 The purpose of this transition matrix is to define the likelihood of movement between points (or \textit{locations}) in our simulated geography based on their mass and pairwise distances.
-We conduct this experiment with two different transition matrices, one based on cosine distance where $f(r_{ij})=e^{-\beta r_{ij}}$ and another with euclidean distance where $f(r_{ij})=r_{ij}^{-\alpha}$.
+We conduct this experiment with two different transition matrices, one based on cosine distance where $f(r_{ij})=e^{-\beta r_{ij}}$ and another with Euclidean distance where $f(r_{ij})=r_{ij}^{-\alpha}$.
 For simplicity, we use $\beta=2$ and $\alpha=2$.
@@
 From the embedding trained with synthetic trajectories, we calculate the pairwise embedding distances between points, $r_{ij}^{embedding}$.
-To evaluate the ability \textit{word2vec} to recover the known gravity-like structure of the synthetic data, we compare the embedding distance to the distances between the 1,000 points in the synthetic space, $r_{ij}^{synthetic}$ using the Pearson correlation coefficient.
+To evaluate the ability of \textit{word2vec} to recover the known gravity-like structure of the synthetic data, we compare the embedding distance to the distances between the 1,000 points in the synthetic space, $r_{ij}^{synthetic}$ using the Pearson correlation coefficient.
 This result is repeated 100 times, and the correlation coefficients are aggregated across iterations.
@@
 Based on cosine distance, the Pearson correlation between the embedding and synthetic distances is 0.943, with a standard error of 0.01. 
-Based on euclidean distance, the correlation was 0.801, with a standard error of 0.01.
+Based on Euclidean distance, the correlation was 0.801, with a standard error of 0.01.
 To better illustrate this point, Fig. \ref{fig:supp:synthetic_exp} shows the correlation for one representative iteration of this experiment.
@@
 In order to evaluate the robustness of the outcome across hyperparameter settings, we repeat our synthetic benchmark (using cosine distance) varying values for the mass exponent, $k$ and distance exponent $\beta$.
-In Fig. \ref{fig:supp:synthetic_robust}) presents the average Pearson correlation between the synthetic and embedding distance over ten iterations with for different values of $k$ and $\beta$. 
+Fig. \ref{fig:supp:synthetic_robust} presents the average Pearson correlation between the synthetic and embedding distance over ten iterations with for different values of $k$ and $\beta$. 
 This shows our findings to be robust. 

### 2023-08-24 paper/current/pnas/main.tex
many small changes

--- 2023-08-24 paper/current/nature-comm-physics/main.tex
@@
 \usepackage{amssymb}
-\usepackage{newtxmath}
+\usepackage{newtxtext,newtxmath}
 \DeclareMathAlphabet{\mathpzc}{T1}{pzc}{m}{it}
@@
 %\newcommand{\ptyref}[1]{Property~\ref{#1}}
-
-% for quick author comments
-\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
-\definecolor{light-gray}{gray}{0.8}
-\def\del#1{ {\color{light-gray}{#1}} }
-\def\yy#1{ {\color{red}\textbf{yy: #1}} }
-\def\dk#1{ {\color{red}\textbf{dk: #1}} }
-\def\js#1{ {\color{red}\textbf{js: #1}} }
-\def\sk#1{ {\color{red}\textbf{sk: #1}} }
 
@@
 
+Just as the embedding space makes it possible to \textit{zoom in} on subsets of organizations, it is also possible to \textit{zoom out} by aggregating organizational vectors.
+In doing so, we identify distinct clusters of countries, organized by their language, culture, and geographic proximity.
+Moreover, we find that
+
 %
@@
 Further work is necessary to determine what causes this curve pattern in so many countries and whether the same pattern can be found in other domains of human mobility.
-
-%
-% Figure - Boomerang
-%
-\begin{figure}[h!]
-	\centering
-	\includegraphics[width=\textwidth]{\figdir/Math/boomerang.pdf}
-	\caption{
-		\textbf{Size of organization embedding vectors captures prestige and size of organizations.}
-		\textbf{a.} Size (L2 norm) of organization embedding vectors compared to the number of researchers for U.S. universities.
-		Color indicates the rank of the university from the Times ranking, with 1 being the highest ranked university.
-		Uncolored points are universities not listed on the Times ranking.
-		A concave-shape emerges, wherein larger universities tend to be more distant from the origin (large L2 norm); however, the more prestigious universities tend to have smaller L2 norms.
-		\textbf{b.} We find a similar concave-curve pattern across many countries such as the United States, China, Australia, Brazil, and others (\textbf{inset}, and Fig.~\ref{fig:concave30}).
-		Some countries exhibit variants of this pattern, such as Egypt, which is missing the right side of the curve.
-		The loess regression lines are shown for each selected country, and for the aggregate of remaining countries, with ribbons mapping to the 99\% confidence intervals based on a normal distribution.
-		Loess lines are also shown for organizations in Australia, Brazil, and Egypt (\textbf{inset}).
-	}
-	\label{fig:length}
-\end{figure}
 

### 2023-08-24 paper/current/pnas/supp.tex
many small changes

--- 2023-08-24 paper/current/nature-comm-physics/supp.tex
@@
 \label{si:text:boomerang_speculation}
-{\bf Speculation on variations of the convex-curve pattern.}
+{\bf A convex-curve pattern in organization prestige.}
+We also find that the size (L2 norm) of the organization embedding vectors provides insights into the characteristics of organizations (Fig.~\ref{fig:length}).
+Up to a point (around 1,000 researchers), the size of U.S. organization's vectors tends to increase proportionally to the number of researchers (both mobile and non-mobile) with published work;
+these organizations are primarily teaching-focused institutions, agencies, and hospitals that either are not ranked or have a low ranking.
+However, at around 1,000 researchers, the size of the vector \emph{decreases} as the number of researchers increases.
+These organizations are primarily research-intensive and prestigious universities with higher rank, research outputs, R\&D funding, and doctoral students (Fig.~\ref{fig:supp:length_vs_metaInfo}).
+A similar pattern has been observed in applications of neural embedding to natural language, in which the size of word vectors were found to represent the word's \emph{specificity}, i.e., the word associated with the vector frequently co-appears with particular context words\autocite{schakel2015measuring}.
+If the word in question is universal, appearing frequently in many different contexts, it would not have a large norm due to a lack of strong association with a particular context.
+Likewise, an organization with a small norm, such as Harvard, appears in many contexts alongside many different organizations in affiliation trajectories---it is well-connected.
+The concavity of the curve emerges in part from the relationship between the size of the vector and the expected connectedness of the organization, given its size ($R^{2} = 0.17$).
+Large, prestigious, and well-funded research universities such as Princeton and Harvard have smaller vector norms because they appear in many different contexts compared to more teaching-focused organizations such as NY Medical College, and the University of Michigan at Flint.
+Some universities, such as the University of Alaska at Fairbanks, have considerably small vectors, which may be a result of their remote locations and unique circumstances.
+
+We report that this curve is almost universal across many countries.
+For instance, China's curve closely mirrors that of the United States (Fig.~\ref{fig:length}b).
+Smaller but scientifically advanced countries such as Australia and other populous countries such as Brazil also exhibit curves similar to the United States (Fig.~\ref{fig:length}b, inset).
+Other nations exhibit different curves which lack the portions with decreasing norm, probably indicating the lack of internationally-prestigious institutions.
+Similar patterns can be found across many of the 30 countries with the most total researchers (Fig.~\ref{fig:concave30}).
+Although we speculate on potential explanations for this pattern below, we don't intend to make general claims about scientific mobility, or mobility more generally, but rather to illustrate how \textit{word2vec} can facilitate new kinds of investigations into mobility.
+Further work is necessary to determine what causes this curve pattern in so many countries and whether the same pattern can be found in other domains of human mobility.
 
@@
 %
+% Figure - Boomerang
+%
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\textwidth]{\figdir/Math/boomerang.pdf}
+	\caption{
+		\textbf{Size of organization embedding vectors captures prestige and size of organizations.}
+		\textbf{a.} Size (L2 norm) of organization embedding vectors compared to the number of researchers for U.S. universities.
+		Color indicates the rank of the university from the Times ranking, with 1 being the highest ranked university.
+		Uncolored points are universities not listed on the Times ranking.
+		A concave-shape emerges, wherein larger universities tend to be more distant from the origin (large L2 norm); however, the more prestigious universities tend to have smaller L2 norms.
+		\textbf{b.} We find a similar concave-curve pattern across many countries such as the United States, China, Australia, Brazil, and others (\textbf{inset}, and Fig.~\ref{fig:concave30}).
+		Some countries exhibit variants of this pattern, such as Egypt, which is missing the right side of the curve.
+		The loess regression lines are shown for each selected country, and for the aggregate of remaining countries, with ribbons mapping to the 99\% confidence intervals based on a normal distribution.
+		Loess lines are also shown for organizations in Australia, Brazil, and Egypt (\textbf{inset}).
+	}
+	\label{fig:length}
+\end{figure}
+
+%
 % Figure - length by factors

### 2023-08-24 workflow/scripts/GeneratePrestigeAxisOrgCodes_OtherCountries.R

@@ -19,8 +19,8 @@ option_list = list(
               help="Name of the ranking variable to use from the file"),
   make_option(c("--lookup"), action="store", default=NA, type='character',
               help="Path to file containing org information, for filtering"),
-  make_option(c("--regions"), action="store", default=NA, type='character',
-              help="Path to file containing region information"),
+  make_option(c("--country"), action="store", default=NA, type='character',
+              help="3-digit ISO country code"),
   make_option(c("--norgs"), action="store", default=NA, type='integer',
               help="Number of orgs to sample from prestige poles"),
   make_option(c("-o", "--output"), action="store", default=NA, type='character',
@@ -28,14 +28,12 @@ option_list = list(
 ) # end option_list
 opt = parse_args(OptionParser(option_list=option_list))
 
-regions <- read_csv(opt$regions, col_types = cols())
 lookup <- read_delim(opt$lookup, col_types = cols(), delim = "\t")
 
 df <- readr::read_csv(opt$input, col_types = cols()) %>%
   rename(score = opt$variable) %>%
   left_join(lookup, by = "cwts_org_no") %>%
-  filter(country_iso_alpha == "USA" & org_type_code == "U") %>%
-  left_join(regions, by = "region")
+  filter(country_iso_alpha == opt$country & org_type_code == "U")
 
 
 elite <- df %>%
@@ -45,14 +43,9 @@ elite <- df %>%
 # Count th enumber of univeristies per region among elite univeristies
 t <- table(elite$census_division)
 
-# Sample non-elite univeristies from bottom-ranked universiteis of each region
-nonelite <- data.table::rbindlist(lapply(1:length(t), function(index) {
-  sub_df <- df %>%
-      filter(census_division == names(t[index])) %>%
-      top_n(-t[index], score) %>%
-      sample_n(t[index]) # ensure that the right number is sampled, in case of ties
-  return(sub_df)
-})) %>%
+# Sample non-elite univeristies
+nonelite <- df %>%
+  top_n(-opt$norgs, score) %>%
   mutate(type = "Non-elite")
 
 prestige <- data.table::rbindlist(list(elite, nonelite)) %>%
